### 2023-04-11 article/article.tex
adding files

% xelatex --shell-escape compared.tex 
% pandoc -s article.tex --pdf-engine=xelatex --pdf-engine-opt=-shell-escape -o article.html
\documentclass{article}
\usepackage[english]{babel}
%\usepackage{testhyphens}
\usepackage{multicol}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{amssymb}% http://ctan.org/pkg/amssymb
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage{longtable}
\usepackage[style=alphabetic, backend=biber]{biblatex}
\addbibresource{references.bib}
\usepackage[inline]{enumitem}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{cleveref}

%%%%%%% https://tex.stackexchange.com/questions/16790/write18-capturing-shell-script-output-as-command-variable
\usepackage{xparse}
\ExplSyntaxOn
\NewDocumentCommand{\captureshell}{som}
 {
  \sdaau_captureshell:Ne \l__sdaau_captureshell_out_tl { #3 }
  \IfBooleanT { #1 }
   {% we may need to stringify the result
    \tl_set:Nx \l__sdaau_captureshell_out_tl
     { \tl_to_str:N \l__sdaau_captureshell_out_tl }
   }
  \IfNoValueTF { #2 }
   {
    \tl_use:N \l__sdaau_captureshell_out_tl
   }
   {
    \tl_set_eq:NN #2 \l__sdaau_captureshell_out_tl
   }
 }

\tl_new:N \l__sdaau_captureshell_out_tl

\cs_new_protected:Nn \sdaau_captureshell:Nn
 {
  \sys_get_shell:nnN { #2 } { } #1
  \tl_trim_spaces:N #1 % remove leading and trailing spaces
 }
\cs_generate_variant:Nn \sdaau_captureshell:Nn { Ne }
\ExplSyntaxOff
%%%%%%%

\title{Improving the portuguese hyphenation rules}
\author{Leonardo Araújo}
\begin{document}
\maketitle

\captureshell*[\NumberOfDefaultRules]{wc -l ../data/default.TeX.pt-br.patterns | cut -d' ' -f1}

\captureshell*[\NumberOfNewRules]{wc -l ../data/patch.TeX.pt-br.patterns | cut -d' ' -f1}

% 6 dictionaries --- 5 commas
\captureshell*[\DictionarySize]{../scripts/dicstats.sh}

% https://www.texdev.net/2009/10/06/what-does-write18-mean/
\captureshell*[\NumberOfSixHyphens]{../scripts/dicstats.sh 6}
\captureshell*[\NumberOfFiveHyphens]{../scripts/dicstats.sh 5}
\captureshell*[\NumberOfFourHyphen]{../scripts/dicstats.sh 4}
\captureshell*[\NumberOfThreeHyphens]{../scripts/dicstats.sh 3}
\captureshell*[\NumberOfTwoHyphens]{../scripts/dicstats.sh 2}
\captureshell*[\NumberOfOneHyphens]{../scripts/dicstats.sh 1}
\captureshell*[\NumberOfNoHyphens]{../scripts/dicstats.sh 0}
% run to update values
%\immediate\write18{../scripts/hyphenationagreements.sh > ../data/hyphagreements}
\captureshell*[\NumberOfSixAgrees]{../scripts/gethyphenationagreements.sh 6}
\captureshell*[\NumberOfFiveAgrees]{../scripts/gethyphenationagreements.sh 5}
\captureshell*[\NumberOfFourAgrees]{../scripts/gethyphenationagreements.sh 4}
\captureshell*[\NumberOfThreeAgrees]{../scripts/gethyphenationagreements.sh 3}
\captureshell*[\NumberOfTwoAgrees]{../scripts/gethyphenationagreements.sh 2}
\captureshell*[\NumberOfOneAgrees]{../scripts/gethyphenationagreements.sh 1}

\begin{abstract}
    Portuguese hyphenation rules are available for more than 35
    years and have done a good job. Nonetheless they still make mistakes and
    leave some hyphenation points unmarked. Although most undetected
    hyphenation points are located near word boundaries, what will be
    irrelevant for \TeX{} typographic purposes, they are still useful to
    hyphenate proper nouns, new words or pseudoword, and for usage in other
    applications, such as text-to-speech conversion. A list of
    \DictionarySize{} hyphenated words acquired from online dictionaries was
    used along \emph{patgen} to create improved rules, leading to better hyphenation
    of Portuguese words.
\end{abstract}

\section{Introduction}
Hyphenation in text wrapping was not used for a long time. Words should fit
entirely in a line, or they would be broken in arbitrary places. First no
marker at all was used to sign the wrapping of a word, what could create
confusion and undesirable meaning. Therefore, ortographers advocated for the
use of a sign to indicate this break. Portuguese faced the same gradual
introduction of a hyphenation sign to mark words wrapping across lines. Even
though the usage of a hyphenation sign ($=$) was advocated by orthographers
\cite{gandavo1574}, few documents used such sign until the end of the 18th
century \cite{araujo2015}.

In some cases, hyphenation hinders smooth reading and should be avoided in
child literature, for example. In opposition, large or small spaces between
words also impose difficulty in the reading process, making hyphenation
fundamental when texts use short line lengths. As a line gets shorter, the
number of breaking candidates between words decreases, leading to awkward
spaces between words and among letters. For that matter, automatic hyphenation
plays an important role in good typesetting.

%Automatic hyphenation plays an important role in good typesetting and
%it is fundamental when a text uses short line lengths. As a line gets
%shorter, the number of breaking candidates between words decreases,
%creating awkward spaces between words and among letters.

\TeX{} is a typesetting system which carefully deals with these issues,
automatically arranging text on a page to create a good reading experience.
Automatic hyphenation is an important part on this process,
promoting an even-tempered distribution of elements on the page.
%Hyphenation is therefore an important part on this process.
%A good readability depends on an even-tempered distribution of elements
%on the page.
Line height and length, paragraph length, font size and typeface,
letter and word-spacing, are some factors which influence the text legibility
and readability. Space between words should not be too long creating lakes and
rivers in the text, nor too tight, impairing the legibility and readability.

Another important matter to consider is ambiguities that might be created when
a word is partitioned during the hyphenation process. In English we should
avoid hyphenations such as re-cover, re-form, re-sign, the-rapist,
depart-mental and mans-laughter (in Portuguese, some examples are:
\emph{de-putada}, \emph{fede-ração}, \emph{acu-mula}, \emph{após-tolo},
\emph{cú-bico}). Hyphenations that might lead the reader to pronounce a word
incorrectly should also be prevented. That is the case of
\emph{considera-tion}, in Enslish (and \emph{pe-rigo} in Portuguese).

In some situations, hyphenation is also a matter of style. Some partitioning
choices sound better than others. These conflicting alternatives typically
arises when a words has many possible hyphenation points. Consider
ar-chae-ol-o-gist (or ar-che-ol-o-gist), which is preferably partitioned as
archae-ologist (or arche-ologist) in opposition to archaeol-ogist (or
archeol-ogist) or archaeolo-gist (or archeolo-gist). It is preferable to keep
whole morphemes together. In the previous example: archae (or arche, meaning
ancient, primitive)
%\footnote{archae- comes from the Ancient Greek ἀρχαῖος (arkhaîos, `ancient',
%`primitive'), from ἀρχή (arkhḗ, `beginning').}
%https://en.wiktionary.org/wiki/archae-
and -ologist (one who studies the topic). In Portuguese, it is also more
elegant to avoid splits between double consonants or vowels, even if an
hyphenation point do exists between those letters. For example,
\emph{pressu-rizar} is preferable over \emph{pres-surizar} and
\emph{empreen-dedor} is preferable over \emph{empre-endedor}. Even so,
exceptions exists, it is preferable to partition \emph{micro-organismo}
rather than \emph{microor-ganismo} (keeping morphemes together is favored
over splitting a double vowel).

The general rule for Portuguese hyphenation is to split a word into its
syllables. A syllable is made of a mandatory nucleus, filled by a vowel, and
optional peripheral consonants (before or after the nucleus). In some
situations, the syllabic division does not respect the ethnologic constituents.
The usage of the prefixes \emph{bis-} and \emph{in-} are examples of this
circumstance. The correct syllabifications are \emph{bi-sa-vô},
\emph{i-na-ti-vo} and \emph{i-nobs-tan-te}\footnote{The rule of syllable
division could lead to two possible partitions: \emph{i-nobs-tan-te} and
\emph{in-obs-tan-te}, but the first is preferable.}, where the prefixes are
split into two syllables. But, as pointed previously, it is preferable to keep
morphemes together rather than splitting them apart, therefore the we should
favor the hyphenation \emph{bisa-vô} over \emph{bi-savô} and \emph{ina-tivo}
over \emph{i-nativo}. This last example could also lead to a misunderstanding
since the word \emph{nativo} (\emph{native} in English) emerges from this word
break.

Each language has its own hyphenation rules. They might be grouped into two
groups: those which hyphenation is driven by morphology (etymology) and those
driven by pronunciation. An algorithmic approach might use a logic system to
analyse words and apply the hyphenation rules of a given language. An algorithm
must be written for each language, as hyphenation rules vary extensively.
Although a logic system might be fast and compact, inevitably it will have to
deal with exceptions through hard-coded rules.

The automation of this process might use a dictionary based approach, which
will restrict the hyphenation possibilities to those entries in the dictionary,
an algorithmic base approach, which might be applied to whatever sequence found
in a text, or a mix of bothe approaches. An algorithmic approach might use a
logic system to analyse words and apply the hyphenation rules of a given
language. A rule base model might include the recognition of prefixes,
suffixes, morphemes, or some sequences suitable for the inclusion of a break.
Another approach is the usage of pattern matching. Given a corpus of
hyphenation examples in a language, it is necessary to identify those sequence
of letters that define a point where hyphenation is suitable or not. Patterns
might include prefixes, suffixes, exceptions and special hyphenation rules of a
given language. Such approach might be used for different languages, by
providing hyphenation examples in a target language to extract patterns and
rules.

Only the analysis of immediate surrounding might not be enough to determine a
potential break point. For example, consider \emph{dem-o-crat} and \emph{de-moc-ra-cy},
where immediate surrounding of \emph{e} does not suffice to determine the break
location. Even after chosen patterns that makes hyphenation pretty
straightforward, there might be exceptions. Consider the sequence \emph{tion}. It
seems safe to always place a break before this pattern. However, the word
\emph{cation} is hyphenated as \emph{cat-ion}, making is etymology determinant to the way
this word will be split.

A word with different meanings may be hyphenated differently according to its
meaning. `For instance, the Swedish word form \emph{glassko} has three different
meanings, and can be hyphenated as \emph{glas-sko} (glass shoe),
\emph{glass-ko} (ice cream cow) and in the non-standard way,
\emph{glass-sko} (ice cream shoe).' \cite{nemeth2006}. In Portuguese, the
word \emph{sublinha} might be hiphenated in two different forms:
\emph{su-bli-nha} when representing the inflected form of verb
\emph{sublinhar} (underline as a verb) or \emph{sub-li-nha} when refering
to the line under (underline as a noun).

% hyphenation might change with syntactic function
% part of speech (PoS)

Machine learning approach was used by to hyphenate Norwegian text
\cite{kristensen2001}. It was found that the \TeX{} approach, in general,
performed better then a neural network. Both approaches had similar
performance on finding the correct hyphenation points and avoiding wrong
hyphenation points on a small word list (the neural network performed slightly
better on finding the correct hyphenation points). Nonetheless, \TeX{} approach overcame
the neural network on a large word list, regarding the avoidance of wrong
hyphenations.

The original \TeX{} hyphenation algorithm was introduced by Knuth 1977
\cite{knuth1977}. It was focused on the English language and used three main
rules:(1) suffix removal; (2) prefix removal; and (3)
vowel-consonant-consonant-vowel (vccv) breaking. Tests showed it could find
40\% of the allowed hyphen locations \cite{liang1983}. The hyphenation
algorithm proposed by Frank M. Liang and adopted in \TeX{} uses the notion of
competing patterns. A database of hyphenated words is swept, looking for
hyphenating and inhibiting patterns. The algorithm introduced in \TeX{}82 uses
five alternating levels of hyphenating and inhibiting patterns. The program
for patten generation, based on a corpus, PATGEN was created Liang
\cite{liangbreitenlohner1999} and was used to create hyphenating patterns for
many languages
\cite{sojka1995,sojka1995a,sojka2005thesis,sojka2003,scannell2003}.

The effective hyphenation of words by \TeX{} will actually depends on the following factors:
\begin{enumerate*}[label=\arabic*)]
    \item document language, which will determine which set of patterns to apply;
    \item characters used, since some might block hyphenation at their edges;
    \item the value of the internal variables \verb|lefthyphenmin| and \verb|righthyphenmin|,
        which defines the minimum sequence length of characters at the left and right borders
        before any hyphenation is allowed.
\end{enumerate*}

% Some hyphenation rules are not possible with TeX algorithm.
% For example, the german word Schiffahrt should be hyphenated as Schiff-fahrt.
% Although it is no longer the recommend written form, it was the most usual
% until 2003 (see graph in schifffart.png from google ngrams).
% Also the old hyphenating rules of German grammatic stated the following
% hyphenations Bäk-ker (for the word Bäcker, what is now hyphenated as Bä-cker),
% Zuk-ker (for the word Zucker, what is now hyphenated as Zu-cker),
% pak-ken (for packen, and now pa-cken) and trok-ken (for trocken, now tro-cken).

%which contain archeo can be alternatively spelt with archaeo or archæo.

%GÂNDAVO, Pero de Magalhães de. Regras que ensinam a maneira de escrever e
%orthographia da lingoa portuguesa, etc. Lisboa: Antonio Gonsalvez, 1574

%  HIFENIZAÇÃO EM PORTUGUÊS
% Antonio Martins de ARAÚJO and Toru MARUYAMA

\section{Patterns for \TeX{} hyphenation} 
The patterns used in \TeX{} hyphenation are of the form: \texttt{4z1z2}. Each
pattern is made of a sequence of letters and numbers. Odd numbers indicate a
good hyphenation point, whereas even numbers indicate a bad place to break.
The given example states that the sequence has a good breaking point between
the first and the second \emph{z} and an hyphenation should be inhibited before
the first \emph{z} and after the second \emph{z}. For example, the hyphenation
of the word \emph{piz-za}, \emph{fiz-zle} and \emph{mezzanine} use this rule,
where we see the hyphen placed between the two \emph{z}'s and no hyphen before,
nor after the \emph{z}'s. The pattern may also use period symbol (\emph{.}) to
indicate word boundaries. The pattern \texttt{.s2h2} applies to beginning of
words, implying that the \emph{s} and the \emph{h} should stick together in
beginning of a word and an hyphenation should also be inhibited after the
\emph{h}. For example, this pattern is used in \emph{Sher-lock}.

Hyphenation rules are organized in levels, from 1 to 9, where odd numbers
represent hyphenating levels and even numbers represent inhibiting levels. Each
level works as an exception level of it predecessor. For example, the rule
\texttt{sh1er} indicate a good hyphenation point between the \emph{h} and the
\emph{e} in the sequence \emph{sher}. A rule at a higher level, as
\texttt{.s2h2}, implies an exception to the lower level rule. When we see
\emph{sher}, in the beginning of a word, the rule \texttt{.s2h2} applies and
hyphenation proposed by the lower level rule \texttt{sh1er} should be hindered.
That is the case in the hyphenation of the word \emph{Sher-lock}. The full
example is provided in \Cref{sherlockhyphenation}, where we might see all
English rules that takes place in the hyphenation of \emph{Sher-lock}.

\begin{lstlisting}[language={}, caption={Example of rules applyied in the
hyphenation of the word \emph{Sherlock}. Example done using a port of \TeX{}'s
hyphenation algorithm to Go provided at
\url{https://github.com/speedata/hyphenation}.}, label=sherlockhyphenation]
   .   s   h   e   r   l   o   c   k   .
     0   0   2   |   |   |   |   |   |    .sh2
     0   2   0   |   |   |   |   |   |    s2h
     0   0   1   0   0   |   |   |   |    sh1er
     |   |   |   0   1   0   |   |   |    r1l
     |   |   |   0   3   0   4   |   |    r3lo4
     |   |   |   |   |   |   0   0   1    ck1
max: 0   2   2   0   3   0   4   0   1
final: s   h   e   r - l   o   c   k -
\end{lstlisting}

A pattern will consist of a string made of characters (from the language
alphabet) possibly with a number in between, expressing the
hyphenation/inhibition level and possibly word boundaries marker (the period)
at the pattern edges. When there is no number between characters in a pattern,
a zero is assumed, which means \emph{undefined} and no hyphenation point will
be suggest at that location.

\section{PATGEN}
PATGEN uses a list of hyphenated words to define rules at different
levels and lengths, based on the patterns found in the data. It start with
short patterns and increases until a maximum pattern length, allowed by the
user, is reached. As it advances, creating longer patterns, it also establishes
exceptions. In some cases, the analysis of long patterns might be necessary,
since some hyphenation points might depend on characters far away from the
breaking point\footnote{Some examples of hyphenation dependency on characters
far from the break point: \emph{dem-o-crat} and \emph{de-moc-ra-cy};
\emph{as-pi-rin} and \emph{aspir-ing}; \emph{de-mon-stra-tive} and
\emph{dem-on-stra-tion}.}.

PATEGEN works on glyph indices rather than character codes. Each glyph is
represented by a single byte. That amount to 256 indices, where 13 of them are
reserved for the digits 0-9 and the characters `.', `-' and `*'. The remaining 243
are used to represent symbols of the given language. To run PATGEN, it is required a
translation file, which defines the values of some language specific parameters
(in the first line) and defines the many forms in which language symbols might
appear (all following lines). In the first line, positions 1 and 2 are used to
set the value of \verb|lefthyphenmin|, positions 3 and 4 are for
\verb|righthyphenmin|. These values defines the shortest length of a string
that might be generated by an hyphenation procedure. In order to set a single
digit value, leave the first position blank, that is, put a blank space in
position 1 and 3 for \verb|lefthyphenmin| and \verb|righthyphenmin|
respectively. Positions 5, 6 and 7 are used to define alternative values for
the special characters `.', `-' and `*'. The following lines uses a delimiter
to surround each `letter' of the desired language alphabet and also its
alternative representations. The first position of the line defines the
delimiter and each symbol of the language may use as many positions as
necessary, since not using the value reserved for the delimiter. Consider the
example for defining the letter `e' in Portuguese: 
\begin{verbatim}
XeXEXéXêXÉXÊX\'{e}X\^{e}X\'{E}X\^{E}XX 
\end{verbatim}
It represents the many ways in which it might be found: lowercase, uppercase,
with or without acute or circumflex accents. In this definition, we have
assumed that the many forms in which we may find the character \emph{e} and
\emph{e} will be equivalent for hyphenation (pattern matching) purpose. As
another example, see the line defining the character $\pi$ (taken from
\cite{haralambous2021}): \begin{verbatim} #p#P#\varpi ## \end{verbatim}

The translate file and the dictionary file should use the same encoding. Even
if it is a multi byte encoding, the translation file express how to deal with a
sequence of bytes representing a glyph and PATGEN will work fine as long as
there are at most 243 symbols in the given language.
The dictionary file is a list of already hyphenated words from which PATGEN
will look for patterns and create hyphenation rules.

Those rules are organized
in different levels, from 1 to 9, where odd numbers represent hyphenating
levels and even numbers represent inhibiting levels. Each level works as an
inhibiting level of it predecessor. A pattern will consist of a string made of
characters (from the language alphabet) possibly with a number in between,
expressing the hyphenation/inhibition level and possibly word boundaries marker
(the period) at the pattern edges. When there is no number between characters
in a pattern, a zero is assumed, which means \emph{undefined} and no
hyphenation point will be suggest at that location.

\section{\TeX{} hyphenation rules for portuguese}\label{sec-tex-hyphen-pt}

\cite{rezende1987} created the first patters for Portuguese hyphenation in
\TeX{}. It was lastly updated in 2015 with the contributions from José João
Dias Almeida \cite{hyphpt}. The set has \NumberOfDefaultRules{}
rules\footnote{The set of rules for Portuguese hyphenation is short when
compared to rules in other languages. For example, English currently has 4938
rules, Russian has 7023 rules and German has 34011 rules.} and are able to
correctly hyphenate the majority of Portuguese words. We propose here to
analyse the performance of the default rules and add new rules to improve
hyphenation by correcting some issues and taking in account non-typical
patterns.

In order to apprise the performance of each set of rules, we need a list of
correctly hyphenated words that are used in a language. We use the frequency of
occurrence to avoid selecting really rare words. To build a large list with
such information, we relied on data collected from online dictionaries and
corpora of Portuguese. We also looked up Portuguese grammars to check on the
hyphenation (translineation) rules and we made some manual corrections on the
data.

In 1990, Portuguese went under a Language Orthographic Agreement. The adopting
transition period started in 2009 and ended as it turned mandatory in 2016.
Even after the agreement, some words still hold different spellings in the
participant countries. It is desirable to have hyphenation rules that might
work properly, despite those idiosyncrasies.  For example, the word
\emph{reception} might be written as \emph{receção} (Portugal) or
\emph{recepção} (Brazil); the word \emph{action} might be written as
\emph{acção} (Portugal) or \emph{ação} (Brazil); and the word \emph{project} might be
written as \emph{projecto} (Portugal) or \emph{projeto} (Brazil).

% We have used the Portuguese Wikipedia dump as our Portuguese corpus. Texts in Wikipedia might be written by Brazilian or Portuguese contributors, the both spellings may appear.

% cat /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | tr -dc '0-9\n' | paste -sd+ | bc
% 302226482
% cat /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | awk '{CUMCOUNT+=$1; if(CUMCOUNT < 287115158) print;}' >/tmp/ptwikitop95.txt
% cat /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | awk '{CUMCOUNT+=$1; if(CUMCOUNT < 299204217) print;}' >/tmp/ptwikitop99.txt
% cat /tmp/ptwikitop99.txt | tr -d "0-9 " |  while read -r word; do if ! grep -q "^${word}," hyphenations.csv; then echo $word; fi; done > /tmp/ptwikitop99_notinlist.txt

We started using
\href{https://www.linguateca.pt/cetenfolha/index_info.html}{CETENFolha} as the
source corpus. Using only this corpus led to two problems: many words were
still missing and it was built on text from 1994, prior to the Orthographic
Agreement. We decided to incorporate the list of words from
\href{https://www.palavras.net/}{Palavras NET} and afterwards we also included
words from the \href{https://pt.wikipedia.org}{Portuguese Wikipedia} dump.
Although the list of words created was huge, we kept only those words we could
find their hyphenation on at least one of the following online dictionaries: 
\href{https://michaelis.uol.com.br/}{Michaelis},
\href{https://dicionario.priberam.org/}{Priberam},
\href{https://pt.wiktionary.org}{Wikcionário},
\href{https://aulete.com.br/}{Aulete},
\href{http://www.portaldalinguaportuguesa.org/}{Portal da Língua Portuguesa} e
\href{https://www.dicio.com.br/}{Dicio}.
This leads to the creation of a dictionary with \DictionarySize{} words.

Table \ref{tblstats} presents the number of words with a given number of
hyphenation found the dictionaries. It also presents the number of words that
have the highest agreed hyphenation. We will present some examples below. To
reference the cells in the table we will not consider the header line and
column. For example, the word \emph{como} was hyphenated by the six
dictionaries as \emph{co-mo}. It will add one to the counts on both lines
where the hyphenations number is 6 (first column). The word \emph{sua} was
hyphenated as \emph{su-a} in 4 dictionaries and a \emph{sua} in one
dictionary. It will add one in the first line, second column (since hyphenations
were found in 5 dictionaries). It will also add one on the second line, third
column (since the most frequent hyphenation was found in 4 dictionaries). It is
clear now why we might have the number of same hyphenations (specially for
small values) greater the number of hyphenations found.

\begin{table}
\centering
\caption{Considering the six dictionaries used, the first line of this table
presents the number words that a given number of hyphenations were found in the
dictionaries. The second line presents the number of words that have a given
number of hyphenation as its most frequent form found in the
dictionaries.}\label{tblstats}
\small
\begin{tabular}{*{8}{l}}
    hyphenations & 6 & 5 & 4 & 3 & 2 & 1 & 0 \\
    \hline
    hyphenations found & \NumberOfSixHyphens{} & \NumberOfFiveHyphens{} &
    \NumberOfFourHyphen{} & \NumberOfThreeHyphens{} & \NumberOfTwoHyphens{} &
    \NumberOfOneHyphens{} & \NumberOfNoHyphens{} \\

    same hyphenations & \NumberOfSixAgrees{} & \NumberOfFiveAgrees{} &
    \NumberOfFourAgrees{} & \NumberOfThreeAgrees{} & \NumberOfTwoAgrees{} &
    \NumberOfOneAgrees{} & n/a
\end{tabular}
\end{table}

\section{Grammar rules for hyphenation in Portuguese}
When there is no space left in line for a whole word, it might be split in two
using a hyphen as an indication of such procedure. In Portuguese, hyphenations
are allowed on syllables boundaries. According to the Grammar
\cite{cunha2016,bergstrom2011}, some rules might still apply:
\begin{enumerate}
    \item\label{rule-di-triphthong} diphthong or triphthong should not be split
	(e.g. \emph{m\underline{\emph{ui}}-to}, \emph{Pa-ra-g\underline{\emph{uai}}});
    \item\label{rule-unstressed} the sequences \emph{ia}, \emph{ie}, \emph{io}, \emph{oa}, \emph{ua},
	\emph{ue} and \emph{uo}, when in final unstressed position, should not be split 
	(e.g. \emph{gló-r\underline{\emph{ia}}}, \emph{vi-tó-r\underline{\emph{ia}}}, 
	\emph{cá-r\underline{\emph{ie}}}, \emph{es-pé-c\underline{\emph{ie}}}, 
	\emph{Má-r\underline{\emph{io}}}, \emph{má-g\underline{\emph{oa}}}, 
	\emph{ré-g\underline{\emph{ua}}}, \emph{tê-n\underline{\emph{ue}}}, 
	\emph{con-tí-g\underline{\emph{uo}}}, \emph{am-bí-g\underline{\emph{uo}}});
    \item\label{rule-c-clusters} consonant clusters starting a syllable should not be
	split (e.g. \emph{\underline{\emph{pn}}eu-má-ti-co}, \emph{\underline{\emph{ps}}i-có-lo-go}, 
	\emph{\underline{\emph{mn}}e-mô-ni-co});
    \item\label{rules-digraphs-ns} the digraphs \emph{ch}, \emph{lh}, \emph{nh}, \emph{gu}, \emph{qu} 
	should not be split (e.g. \emph{ra-\underline{\emph{ch}}ar},
	\emph{a-bro-\underline{\emph{lh}}os}, \emph{ma-\underline{\emph{nh}}ã},
	\emph{\underline{\emph{gu}}i-tar-ra}, \emph{\underline{\emph{qu}}in-to});
    \item\label{rule-nasalization} a vowel and its following nasalization marker (a graphic
	nasal consonant) should not be split (e.g. \emph{\underline{\emph{am}}-bição},
	\emph{m\underline{\emph{an}}-cha});
    \item\label{rule-rising} rising diphthong should not be split (e.g.
	\emph{a-b\underline{\emph{ai}}-xo}; \emph{c\underline{\emph{au}}-te-la}, 
	\emph{pa-p\underline{\emph{éi}}s}, \emph{cha-p\underline{\emph{éu}}}, 
	\emph{pre-f\underline{\emph{ei}}-to}, \emph{r\underline{\emph{eu}}-nir},
	\emph{n\underline{\emph{oi}}-te}; \emph{ca-la-b\underline{\emph{ou}}-ço}, 
	\emph{as-te-r\underline{\emph{ói}}-de}; 
	\emph{re-tri-b\underline{\emph{ui}}});

    \hspace{10em} \hbox to 5cm{\leaders\hbox to 10pt{\hss . \hss}\hfil}

    \item\label{rule-hiatus} hiatus vowels and those vowel sequences where each vowel
	belongs to a different syllable should be split (e.g.
	\emph{sa\underline{\emph{-ú-}}de}, \emph{ra\underline{\emph{-i-}}nha}, \emph{d\underline{\emph{o-e}}r},
	\emph{v\underline{\emph{o-o}}s}), the same procedure is used splitting diphthongs
	in different syllables (e.g. \emph{c\underline{\emph{ai-ai}}s}) or diphthong and
	vowel in different syllables (e.g. \emph{en-s\underline{\emph{ai-o}}s});
    \item\label{rule-consonants} consonant sequences, when in different syllables, should
	be split (e.g. \emph{a\underline{\emph{f-t}}a}, \emph{a\underline{\emph{b-d}}i-car},
	\emph{re\underline{\emph{s-c}}i-são}, \emph{a\underline{\emph{b-s}}o-lu-to});
    \item\label{rule-digraphs} the following consonant digraphs should be split:
	\emph{rr}, \emph{ss}, \emph{mm}, \emph{nn}, \emph{sc}, \emph{sç} and
	\emph{xc} (e.g. \emph{te\underline{\emph{r-r}}a}, \emph{pro-fe\underline{\emph{s-s}}or},
	\emph{co-mu\underline{\emph{m-m}}en-te}, \emph{co\underline{\emph{n-n}}os-co},
	\emph{de\underline{\emph{s-c}}er}, \emph{cre\underline{\emph{s-ç}}a}, \emph{e\underline{\emph{x-c}}e-der}).
\end{enumerate}

In some situations a hyphen should be repeated in the start of the following
line: 
\begin{enumerate}
\item when a compound word using a hyphen is split across lines (e.g.
    \emph{couve-/-flor}, \emph{ex-/-presidente});
\item when a different meaning could be conveyed when splitting a pronoun (e.g.
    \emph{prazer de ver-/-me}\footnote{Possible conveyed meanings: 
    \emph{pleasure in seeing me} or \emph{worm's pleasure}.}). 
\end{enumerate}

It should be avoided to leave a single vowel in the end or start of a line (e.g.
the word \emph{san-guí-nea} should be split only on the hyphen gave in the
example, avoiding the split that would leave the final vowel \emph{a}
left alone in the start of a new line: \emph{sanguíne-a}). It is also considered a better approach
to avoid splitting disyllables made of four letters (e.g. \emph{para},
\emph{como}, \emph{cede}).

... to continue
\vspace{10ex}

Foi criado um conjunto de \NumberOfNewRules{} regras para aprimorar as hifenizações no
português. Analisando um conjunto de 37798 palavras, as regras padrão apresentam
1368 erros (1273 pontos de hifenização não marcados e 125 pontos marcados
erroneamente)\footnote{A soma não é 1368 pois temos 30 casos em que os dois
tipos de erros ocorrem.}, enquanto as novas regras apresentaram 132 erros (118
pontos de hifenização não marcados e 35 pontos marcados
erroneamente)\footnote{35 palavras apresentam ambos tipos de erro.}.
%%% <<< fazer correção após correção manual das hifenizações tidas como corretas.

Foi criado um conjunto de 37798 palavras obtidas do corpus
\href{https://www.linguateca.pt/cetenfolha/index_info.html}{CETENFolha},
juntamente com palavras do \href{https://www.palavras.net/}{Palavras NET} e
algumas palavras do corpus baseado na
\href{https://pt.wikipedia.org}{Wikipedia}. 
Foram mantidas apenas as palavras
para as quais encontrou-se a hifenização nos seguintes dicionários online:
\href{https://michaelis.uol.com.br/}{Michaelis},
\href{https://dicionario.priberam.org/}{Priberam},
\href{https://pt.wiktionary.org}{Wikcionário},
\href{https://aulete.com.br/}{Aulete},
\href{http://www.portaldalinguaportuguesa.org/}{Portal da Língua Portuguesa} e
\href{https://www.dicio.com.br/}{Dicio}.
Adotamos como hifenização `correta' aquela que ao menos 4 dicionários
concordavam. Algumas hifenizações foram realizadas manualmente pelo autor.
Considerando a frequência de ocorrência das palavras nos corpus, o conjuto de
palavras escolhido representa 55\% do total das ocorrências relativo ao
Wikipedia e 58\% em relação ao CETENFolha.
% Corpus Wikipedia
%
% 166341424 / 302226482 = 0.55
% 
% soma da freq. de occ. das palavras utilizadas
% cat portuguese_4_utf8.dic portuguese_extra_utf8.dic | tr -d '-' | while read -r word; do grep "[0-9]\+ ${word}$" /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | head -n 1 | tr -dc '0-9\n'; done | paste -s -d+ - | bc 
% = 166341424
%
% soma da freq. de occ. de todas palavras no corpus
% cat /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | tr -dc '0-9\n' | paste -s -d+ - | bc
% = 302226482
%
% CETENFolha
% 13314084 / 22728804 = 0.5857
Este percentual é relativamente baixo, mas deve-se ao fato de que não obtivemos
sucesso em encontrar a hifenização de muitas palavras nos dicionários
analisados e também por não observarmos um consenso de ao menos 4 dicionários
com uma mesma hifenização.

Analisando os erros resultantes da hifenização utilizando as regras padrão do
TeX, foram estabelecidas algumas regras como forma de abarcar um conjunto maior
de palavras. Tais regras são elencadas a seguir, expondo também as regras de
exceção necessárias e um exemplo onde a regra será utilizada.

\begin{enumerate}
\item regra: \texttt{p2si}, \texttt{p2sí} -- psicologia, psíquico\\
exceção: \texttt{p3sia}, \texttt{p3sin} -- epilepsia, rodopsina

\item regra: \texttt{t2c} -- tchau%, tcheco

\item regra: \texttt{p2neu} -- pneumonia

\item regra: \texttt{.g2no}, \texttt{.g2nó} -- gnomo, gnóstico

\item regra: \texttt{.p2t} -- ptose%, pterossauro

\item regra: \texttt{su2b3r}, \texttt{su2b3l} -- sublunar, subrotina
exceção: \texttt{su3b4li1nh}, \texttt{su3b4li1ma}, \texttt{su3b4li1me}, \texttt{su3b4li1mid} -- sublinhar, sublimar, sublime, sublimidade

\item regra: \texttt{1sô} -- subsônico

\item regra: \texttt{1p2seu1d} -- pseudônimo

\item regra: \texttt{c2za} -- czar

\item regra: \texttt{.s2} -- stalinismo

\item regra: \texttt{.t2} -- tsunami

\item regra: \texttt{a1â}, \texttt{a1ã}, \texttt{a1é}, \texttt{a1í}, \texttt{a1ó}, \texttt{a1ô}, \texttt{a1ú}, \texttt{e1á}, \texttt{e1â}, \texttt{e1ã}, \texttt{e1ê}, \texttt{e1í}, \texttt{e1ó}, \texttt{e1ô}, \texttt{e1ú}, \texttt{i1á}, \texttt{i1ã}, \texttt{i1ã}, \texttt{i1é}, \texttt{i1ó}, \texttt{i1ú}, \texttt{o1á}, \texttt{o1ã}, \texttt{o1é}, \texttt{o1ê}, \texttt{o1í}, \texttt{o1ó}, \texttt{u1á}, \texttt{u1ã}, \texttt{u1é}, \texttt{u1ê}, \texttt{u1í} --  abraâmico, abraão, aéreo, país, caótico, faraônico, saúde, balneário, oceânico, campeã, veêm, veículo, teórico, napoleônico, conteúdo, diário, região, soviético, periódico, viúva, razoável, joão, poético, boêmia, heroísmo, alcoólico, usuário, itapuã, suécia, cauê, suíça \\
exceção: \texttt{1gu2é}, \texttt{1gu2ê}, \texttt{1gu2í}, \texttt{1qu2á}, \texttt{1qu2é}, \texttt{1qu2ê}, \texttt{1qu2í} -- alguém, português, linguística, aquático, inquérito, sequência, química

\item regra: \texttt{a1ir.}, \texttt{u1ir.} -- sair, diminuir

\item regra: \texttt{í1a} -- baía

\item regra: \texttt{1lô} -- camelô

\item regra: \texttt{1cô} -- recôncavo

\item regra: \texttt{e1in1c}, \texttt{e1in1f}, \texttt{e1in1g}, \texttt{e1in1s}, \texttt{e1in1t}, \texttt{e1in1v} -- reincidência, reinfecção, reingressa, reinserção, reintegração, reinventar
exceção: \texttt{e1in2st}, \texttt{e1in2sc} -- reinstalado, reinscrever

\item regra: \texttt{o1in} -- coincidência, agroindustrial, bioinformática, amendoins, gastrointestinal
exceção: \texttt{o1ina} -- boina

\item regra: \texttt{a1ind}, \texttt{a1i1nh} -- ainda, rainha

\item regra: \texttt{o1i1nh} -- moinho

\item regra: \texttt{1bô}, \texttt{1dô}, \texttt{1fô}, \texttt{1gô}, \texttt{1pô}, \texttt{1mô}, \texttt{1nô}, \texttt{1rô}, \texttt{1tô}, \texttt{1vô}, \texttt{1xô}, \texttt{1zô} -- robô, judô,  telefônica, xangô, capô, sumô, econômico, tarô, chatô, vovô, saxônia, amazônia

\item regra: \texttt{e1im} -- reimpresso, coimbra, coimperador
exceção: \texttt{que2i}, \texttt{te2im} -- queimar, queimadura, teimosia, tirateima

\item regra: \texttt{au1i1c}, \texttt{du1i1c}, \texttt{u1i1ç}, \texttt{u1i1d}, \texttt{cu2i}, \texttt{dru2i}, \texttt{flu2id}, \texttt{bu1i1n}, \texttt{cu1i1n}, \texttt{fu1i1n}, \texttt{nu1i1n}, \texttt{ru1i1na}, \texttt{ru1i1no}, \texttt{su1i1ti}, \texttt{tu1i1ti}, \texttt{u1iz} -- cacauicultor, sanduicheira, constituição, continuidade, cuidador, druida, fluido, tabuinha, picuinha, fuinha, genuinamente, arruinado, arruinou, jesuitismo, intuitivo, juizado 
exceção: \texttt{cu3i1da1de}, \texttt{bu1i2n1d}, \texttt{bu1i2n1t}  -- acuidade, contribuindo, contribuinte

\item regra: \texttt{.m2n} -- mnemônico

\item regra: \texttt{1gu4á}, \texttt{1gu4ã}, \texttt{1qu4ã} -- jaraguá, saguão, quão

\item regra: \texttt{1çô} -- maçônico

\item regra: \texttt{i1ur} -- diurno

\item regra: \texttt{í1o} -- íon

\item regra: \texttt{pro1i1b} -- proibição

\item regra: \texttt{i1un} -- triunfar

%\item regra: \texttt{u3ó} -- fluór

\item regra: \texttt{1qu4ó}, \texttt{1qu4â} -- quórum, equânime

\item regra: \texttt{é3o} -- alvéolo

\item regra: \texttt{i4a.}, \texttt{i4e.}, \texttt{i4o.}, \texttt{o4a.}, \texttt{u4a.} -- economia, espécie, vazio, destoa, institua

\item regra: \texttt{z1z}, \texttt{p1p}, \texttt{z2z.} -- pizza, shopping, jazz

% As sequências gráficas ia, ie, io, oa, ua quando em posição
% final átona, que são normalmente pronunciadas como ditongos
% crescentes, mas que podem corresponder foneticamente a duas
% vogais (hiato), sobretudo quando pronunciadas pausadamente:
% vitó-ria, espé-cie, exercí-cio, nó-doa, lé-gua, tê-nue, ambí-guo.
\end{enumerate}

O conjunto de \NumberOfNewRules{} regras é apresentado a seguir:
\begin{multicols}{4}
    \verbatiminput{patch.TeX.pt-br.patterns}
\end{multicols}

A Tabela \ref{tab-resultados} apresenta os erros cometidos no conjunto das
37798 palavras analisadas. As palavras omitidas são aquelas que foram
hifenizadas corretamente pelos dois conjuntos de regra. Utilizamos aqui a
marcação adotada pelo \emph{Patgen}: \texttt{*} para indicar pontos de
hifenização corretamente marcados, \texttt{.} para indicar pontos de hifenização
marcados erroneamente e \texttt{-} para indicar pontos de hifenização não
encontrados. Os pontos marcados erroneamente e aqueles não encontrados são
considerados erros. Quando ocorre algum erro de hifenização, marcaremos a
palavra com \xmark. Quando não houver erro algum, marcaremos a palavra com
\cmark. Ao final, podemos verificar que as regras padrão apresentaram 1368 erros
(3,62\%) e as novas regras 132 erros (0,35\%).

\begin{longtable}{l l l}
\caption{Comparativo dos erros cometidos pelos dois conjuntos de regras de
hifenização.}\label{tab-resultados}\\
    \hline
    palavra & regras padrão & regras adicionais \\
    \hline
    \endhead
    \input{comparedresults.tex}
\end{longtable}

\printbibliography

\end{document}

### 2023-04-11 article/comparedresults.tex
adding files

ainda & a-in*da \xmark & a*in*da \cmark \\
país & pa-ís \xmark & pa*ís \cmark \\
região & re*gi-ão \xmark & re*gi*ão \cmark \\
saúde & sa-ú*de \xmark & sa*ú*de \cmark \\
período & pe*rí-o*do \xmark & pe*rí*o*do \cmark \\
juiz & ju-iz \xmark & ju*iz \cmark \\
união & u*ni-ão \xmark & u*ni*ão \cmark \\
econômico & e*co-nô*mi*co \xmark & e*co*nô*mi*co \cmark \\
aí & a-í \xmark & a*í \cmark \\
sair & sa-ir \xmark & sa*ir \cmark \\
opinião & o*pi*ni-ão \xmark & o*pi*ni*ão \cmark \\
constituição & cons*ti*tu-i*ção \xmark & cons*ti*tu*i*ção \cmark \\
saída & sa-í*da \xmark & sa*í*da \cmark \\
luís & lu-ís \xmark & lu*ís \cmark \\
campeão & cam*pe-ão \xmark & cam*pe*ão \cmark \\
aliás & a*li-ás \xmark & a*li*ás \cmark \\
distribuição & dis*tri*bu-i*ção \xmark & dis*tri*bu*i*ção \cmark \\
avião & a*vi-ão \xmark & a*vi*ão \cmark \\
diário & di-á*ri*o \xmark & di*á*ri*o \cmark \\
diária & di-á*ri*a \xmark & di*á*ri*a \cmark \\
daí & da-í \xmark & da*í \cmark \\
cair & ca-ir \xmark & ca*ir \cmark \\
paraíba & pa*ra-í*ba \xmark & pa*ra*í*ba \cmark \\
prejuízo & pre*ju-í*zo \xmark & pre*ju*í*zo \cmark \\
judiciário & ju*di*ci-á*ri*o \xmark & ju*di*ci*á*ri*o \cmark \\
suíça & su-í*ça \xmark & su*í*ça \cmark \\
influência & in*flu-ên*ci*a \xmark & in*flu*ên*ci*a \cmark \\
depoimento & de*po-i*men*to \xmark & de*po-i*men*to \xmark \\
instituição & ins*ti*tu-i*ção \xmark & ins*ti*tu*i*ção \cmark \\
consequência & con*se-quên*ci*a \xmark & con*se*quên*ci*a \cmark \\
usuário & u*su-á*ri*o \xmark & u*su*á*ri*o \cmark \\
contribuição & con*tri*bu-i*ção \xmark & con*tri*bu*i*ção \cmark \\
diminuir & di*mi*nu-ir \xmark & di*mi*nu*ir \cmark \\
fenômeno & fe-nô*me*no \xmark & fe*nô*me*no \cmark \\
ruim & ru-im \xmark & ru-im \xmark \\
construir & cons*tru-ir \xmark & cons*tru*ir \cmark \\
veículo & ve-í*cu*lo \xmark & ve*í*cu*lo \cmark \\
cocaína & co*ca-í*na \xmark & co*ca*í*na \cmark \\
paul & pa-ul \xmark & pa-ul \xmark \\
reunir & re-u*nir \xmark & re-u*nir \xmark \\
continuidade & con*ti*nu-i*da*de \xmark & con*ti*nu*i*da*de \cmark \\
diálogo & di-á*lo*go \xmark & di*á*lo*go \cmark \\
atrair & a*tra-ir \xmark & a*tra*ir \cmark \\
ocasião & o*ca*si-ão \xmark & o*ca*si*ão \cmark \\
sebastião & se*bas*ti-ão \xmark & se*bas*ti*ão \cmark \\
sequência & se-quên*ci*a \xmark & se*quên*ci*a \cmark \\
substituir & subs*ti*tu-ir \xmark & subs*ti*tu*ir \cmark \\
incluir & in*clu-ir \xmark & in*clu*ir \cmark \\
gaúcho & ga-ú*cho \xmark & ga*ú*cho \cmark \\
poluição & po*lu-i*ção \xmark & po*lu*i*ção \cmark \\
proibido & pro-i*bi*do \xmark & pro*i*bi*do \cmark \\
rainha & ra-i*nha \xmark & ra*i*nha \cmark \\
religião & re*li*gi-ão \xmark & re*li*gi*ão \cmark \\
paraíso & pa*ra-í*so \xmark & pa*ra*í*so \cmark \\
frequência & fre-quên*ci*a \xmark & fre*quên*ci*a \cmark \\
distribuir & dis*tri*bu-ir \xmark & dis*tri*bu*ir \cmark \\
substituição & subs*ti*tu-i*ção \xmark & subs*ti*tu*i*ção \cmark \\
contribuinte & con*tri*bu-in*te \xmark & con*tri*bu*in*te \cmark \\
conteúdo & con*te-ú*do \xmark & con*te*ú*do \cmark \\
leão & le-ão \xmark & le*ão \cmark \\
concluir & con*clu-ir \xmark & con*clu*ir \cmark \\
proibição & pro-i*bi*ção \xmark & pro*i*bi*ção \cmark \\
sociólogo & so*ci-ó*lo*go \xmark & so*ci*ó*lo*go \cmark \\
construído & cons*tru-í*do \xmark & cons*tru*í*do \cmark \\
maceió & ma*cei-ó \xmark & ma*cei*ó \cmark \\
diminuição & di*mi*nu-i*ção \xmark & di*mi*nu*i*ção \cmark \\
crediário & cre*di-á*ri*o \xmark & cre*di*á*ri*o \cmark \\
pivô & pi-vô \xmark & pi*vô \cmark \\
substituído & subs*ti*tu-í*do \xmark & subs*ti*tu*í*do \cmark \\
razoável & ra*zo-á*vel \xmark & ra*zo*á*vel \cmark \\
juíza & ju-í*za \xmark & ju*í*za \cmark \\
coincidência & co-in*ci*dên*ci*a \xmark & co*in*ci*dên*ci*a \cmark \\
rebelião & re*be*li-ão \xmark & re*be*li*ão \cmark \\
noticiário & no*ti*ci-á*ri*o \xmark & no*ti*ci*á*ri*o \cmark \\
olimpíada & o*lim*pí-a*da \xmark & o*lim*pí*a*da \cmark \\
imobiliário & i*mo*bi*li-á*ri*o \xmark & i*mo*bi*li*á*ri*o \cmark \\
austríaco & aus*trí-a*co \xmark & aus*trí*a*co \cmark \\
penitenciária & pe*ni*ten*ci-á*ri*a \xmark & pe*ni*ten*ci*á*ri*a \cmark \\
psicologia & p.si*co*lo*gi*a \xmark & psi*co*lo*gi*a \cmark \\
contribuir & con*tri*bu-ir \xmark & con*tri*bu*ir \cmark \\
aéreo & a-é*re*o \xmark & a*é*re*o \cmark \\
psicanálise & p.si*ca*ná*li*se \xmark & psi*ca*ná*li*se \cmark \\
vestuário & ves*tu-á*ri*o \xmark & ves*tu*á*ri*o \cmark \\
destruição & des*tru-i*ção \xmark & des*tru*i*ção \cmark \\
viúva & vi-ú*va \xmark & vi*ú*va \cmark \\
distribuído & dis*tri*bu-í*do \xmark & dis*tri*bu*í*do \cmark \\
juízo & ju-í*zo \xmark & ju*í*zo \cmark \\
constituinte & cons*ti*tu-in*te \xmark & cons*ti*tu-in*te \xmark \\
presidenciável & pre*si*den*ci-á*vel \xmark & pre*si*den*ci*á*vel \cmark \\
viável & vi-á*vel \xmark & vi*á*vel \cmark \\
suíço & su-í*ço \xmark & su*í*ço \cmark \\
destruir & des*tru-ir \xmark & des*tru*ir \cmark \\
saído & sa-í*do \xmark & sa*í*do \cmark \\
concluído & con*clu-í*do \xmark & con*clu*í*do \cmark \\
distribuidora & dis*tri*bu-i*do*ra \xmark & dis*tri*bu*i*do*ra \cmark \\
imobiliária & i*mo*bi*li-á*ri*a \xmark & i*mo*bi*li*á*ri*a \cmark \\
sinfônica & sin-fô*ni*ca \xmark & sin*fô*ni*ca \cmark \\
uísque & u-ís*que \xmark & u*ís*que \cmark \\
poética & po-é*ti*ca \xmark & po*é*ti*ca \cmark \\
prostituição & pros*ti*tu-i*ção \xmark & pros*ti*tu*i*ção \cmark \\
rodoviário & ro*do*vi-á*ri*o \xmark & ro*do*vi*á*ri*o \cmark \\
bicampeão & bi*cam*pe-ão \xmark & bi*cam*pe*ão \cmark \\
psicológico & p.si*co*ló*gi*co \xmark & psi*co*ló*gi*co \cmark \\
proibir & pro-i*bir \xmark & pro*i*bir \cmark \\
triunfo & tri-un*fo \xmark & tri*un*fo \cmark \\
variável & va*ri-á*vel \xmark & va*ri*á*vel \cmark \\
criciúma & cri*ci-ú*ma \xmark & cri*ci*ú*ma \cmark \\
sinônimo & si-nô*ni*mo \xmark & si*nô*ni*mo \cmark \\
legião & le*gi-ão \xmark & le*gi*ão \cmark \\
caído & ca-í*do \xmark & ca*í*do \cmark \\
equívoco & e-quí*vo*co \xmark & e*quí*vo*co \cmark \\
baía & ba-í-a \xmark & ba*í*a \cmark \\
quilômetro & qui-lô*me*tro \xmark & qui*lô*me*tro \cmark \\
raiz & ra-iz \xmark & ra-iz \xmark \\
psiquiatra & p.si*qui*a*tra \xmark & psi*qui*a*tra \cmark \\
tricampeão & tri*cam*pe-ão \xmark & tri*cam*pe*ão \cmark \\
psicanalista & p.si*ca*na*lis*ta \xmark & psi*ca*na*lis*ta \cmark \\
ruído & ru-í*do \xmark & ru*í*do \cmark \\
possuir & pos*su-ir \xmark & pos*su*ir \cmark \\
coibir & co-i*bir \xmark & co-i*bir \xmark \\
soviético & so*vi-é*ti*co \xmark & so*vi*é*ti*co \cmark \\
inviável & in*vi-á*vel \xmark & in*vi*á*vel \cmark \\
alô & a-lô \xmark & a*lô \cmark \\
heroína & he*ro-í*na \xmark & he*ro*í*na \cmark \\
destruído & des*tru-í*do \xmark & des*tru*í*do \cmark \\
telefônico & te*le-fô*ni*co \xmark & te*le*fô*ni*co \cmark \\
saí & sa-í \xmark & sa*í \cmark \\
suíte & su-í*te \xmark & su*í*te \cmark \\
asiático & a*si-á*ti*co \xmark & a*si*á*ti*co \cmark \\
irônico & i-rô*ni*co \xmark & i*rô*ni*co \cmark \\
avô & a-vô \xmark & a*vô \cmark \\
restituição & res*ti*tu-i*ção \xmark & res*ti*tu*i*ção \cmark \\
atribuir & a*tri*bu-ir \xmark & a*tri*bu*ir \cmark \\
ingenuidade & in*ge*nu-i*da*de \xmark & in*ge*nu*i*da*de \cmark \\
psicólogo & p.si*có*lo*go \xmark & psi*có*lo*go \cmark \\
pneu & p.neu \xmark & pneu \cmark \\
tetracampeão & te*tra*cam*pe-ão \xmark & te*tra*cam*pe*ão \cmark \\
vestiário & ves*ti-á*ri*o \xmark & ves*ti*á*ri*o \cmark \\
proteína & pro*te-í*na \xmark & pro*te*í*na \cmark \\
espião & es*pi-ão \xmark & es*pi*ão \cmark \\
ciúme & ci-ú*me \xmark & ci*ú*me \cmark \\
napoleão & na*po*le-ão \xmark & na*po*le*ão \cmark \\
teórica & te-ó*ri*ca \xmark & te*ó*ri*ca \cmark \\
intermediário & in*ter*me*di-á*ri*o \xmark & in*ter*me*di*á*ri*o \cmark \\
constituir & cons*ti*tu-ir \xmark & cons*ti*tu*ir \cmark \\
embrião & em*bri-ão \xmark & em*bri*ão \cmark \\
autônomo & au-tô*no*mo \xmark & au*tô*no*mo \cmark \\
confiável & con*fi-á*vel \xmark & con*fi*á*vel \cmark \\
teórico & te-ó*ri*co \xmark & te*ó*ri*co \cmark \\
estômago & es-tô*ma*go \xmark & es*tô*ma*go \cmark \\
termômetro & ter-mô*me*tro \xmark & ter*mô*me*tro \cmark \\
homônimo & ho-mô*ni*mo \xmark & ho*mô*ni*mo \cmark \\
excluído & ex*clu-í*do \xmark & ex*clu*í*do \cmark \\
penitenciário & pe*ni*ten*ci-á*ri*o \xmark & pe*ni*ten*ci*á*ri*o \cmark \\
cardíaco & car*dí-a*co \xmark & car*dí*a*co \cmark \\
mutuário & mu*tu-á*ri*o \xmark & mu*tu*á*ri*o \cmark \\
aquém & a-quém \xmark & a*quém \cmark \\
viário & vi-á*ri*o \xmark & vi*á*ri*o \cmark \\
despoluição & des*po*lu-i*ção \xmark & des*po*lu*i*ção \cmark \\
medíocre & me*dí-o*cre \xmark & me*dí*o*cre \cmark \\
reintegração & re-in*te*gra*ção \xmark & re*in*te*gra*ção \cmark \\
marquês & mar-quês \xmark & mar*quês \cmark \\
beneficiário & be*ne*fi*ci-á*ri*o \xmark & be*ne*fi*ci*á*ri*o \cmark \\
atribuição & a*tri*bu-i*ção \xmark & a*tri*bu*i*ção \cmark \\
balneário & bal*ne-á*ri*o \xmark & bal*ne*á*ri*o \cmark \\
coreógrafo & co*re-ó*gra*fo \xmark & co*re*ó*gra*fo \cmark \\
incômodo & in-cô*mo*do \xmark & in*cô*mo*do \cmark \\
sanduíche & san*du-í*che \xmark & san*du*í*che \cmark \\
pecuária & pe*cu-á*ri*a \xmark & pe*cu*á*ri*a \cmark \\
cirurgião & ci*rur*gi-ão \xmark & ci*rur*gi*ão \cmark \\
jaú & ja-ú \xmark & ja*ú \cmark \\
reconstruir & re*cons*tru-ir \xmark & re*cons*tru*ir \cmark \\
influir & in*flu-ir \xmark & in*flu*ir \cmark \\
santuário & san*tu-á*ri*o \xmark & san*tu*á*ri*o \cmark \\
sutiã & su*ti-ã \xmark & su*ti*ã \cmark \\
poético & po-é*ti*co \xmark & po*é*ti*co \cmark \\
ensaísta & en*sa-ís*ta \xmark & en*sa*ís*ta \cmark \\
porquê & por-quê \xmark & por*quê \cmark \\
biólogo & bi-ó*lo*go \xmark & bi*ó*lo*go \cmark \\
extrair & ex*tra-ir \xmark & ex*tra*ir \cmark \\
reconstituição & re*cons*ti*tu-i*ção \xmark & re*cons*ti*tu*i*ção \cmark \\
anfitrião & an*fi*tri-ão \xmark & an*fi*tri*ão \cmark \\
anônimo & a-nô*ni*mo \xmark & a*nô*ni*mo \cmark \\
aquático & a-quá*ti*co \xmark & a*quá*ti*co \cmark \\
excluir & ex*clu-ir \xmark & ex*clu*ir \cmark \\
filarmônica & fi*lar-mô*ni*ca \xmark & fi*lar*mô*ni*ca \cmark \\
juizado & ju-i*za*do \xmark & ju*i*za*do \cmark \\
peão & pe-ão \xmark & pe*ão \cmark \\
previdenciário & pre*vi*den*ci-á*ri*o \xmark & pre*vi*den*ci*á*ri*o \cmark \\
constituído & cons*ti*tu-í*do \xmark & cons*ti*tu*í*do \cmark \\
pornô & por-nô \xmark & por*nô \cmark \\
psiquiátrico & p.si*qui-á*tri*co \xmark & psi*qui*á*tri*co \cmark \\
moinho & mo-i*nho \xmark & mo*i*nho \cmark \\
obstruir & obs*tru-ir \xmark & obs*tru*ir \cmark \\
psiquiatria & p.si*qui*a*tri*a \xmark & psi*qui*a*tri*a \cmark \\
reindexação & re-in*de*xa*ção \xmark & re-in*de*xa*ção \xmark \\
aquário & a-quá*ri*o \xmark & a*quá*ri*o \cmark \\
amendoim & a*men*do-im \xmark & a*men*do-im \xmark \\
baú & ba-ú \xmark & ba*ú \cmark \\
distribuidor & dis*tri*bu-i*dor \xmark & dis*tri*bu*i*dor \cmark \\
trair & tra-ir \xmark & tra*ir \cmark \\
intuição & in*tu-i*ção \xmark & in*tu*i*ção \cmark \\
petroquímica & pe*tro-quí*mi*ca \xmark & pe*tro*quí*mi*ca \cmark \\
evoluir & e*vo*lu-ir \xmark & e*vo*lu*ir \cmark \\
petroquímico & pe*tro-quí*mi*co \xmark & pe*tro*quí*mi*co \cmark \\
asiática & a*si-á*ti*ca \xmark & a*si*á*ti*ca \cmark \\
dinamarquês & di*na*mar-quês \xmark & di*na*mar*quês \cmark \\
tcheco & t.che*co \xmark & tche*co \cmark \\
diminuído & di*mi*nu-í*do \xmark & di*mi*nu*í*do \cmark \\
instituir & ins*ti*tu-ir \xmark & ins*ti*tu*ir \cmark \\
lampião & lam*pi-ão \xmark & lam*pi*ão \cmark \\
arquitetônico & ar*qui*te-tô*ni*co \xmark & ar*qui*te*tô*ni*co \cmark \\
atraído & a*tra-í*do \xmark & a*tra*í*do \cmark \\
gastronômico & gas*tro-nô*mi*co \xmark & gas*tro*nô*mi*co \cmark \\
vibrião & vi*bri-ão \xmark & vi*bri*ão \cmark \\
caraíba & ca*ra-í*ba \xmark & ca*ra*í*ba \cmark \\
ferroviário & fer*ro*vi-á*ri*o \xmark & fer*ro*vi*á*ri*o \cmark \\
mobiliário & mo*bi*li-á*ri*o \xmark & mo*bi*li*á*ri*o \cmark \\
robô & ro-bô \xmark & ro*bô \cmark \\
traído & tra-í*do \xmark & tra*í*do \cmark \\
chatô & cha-tô \xmark & cha*tô \cmark \\
viés & vi-és \xmark & vi*és \cmark \\
biquíni & bi-quí*ni \xmark & bi*quí*ni \cmark \\
pneumonia & p.neu*mo*ni*a \xmark & pneu*mo*ni*a \cmark \\
galeão & ga*le-ão \xmark & ga*le*ão \cmark \\
pseudônimo & p.seu-dô*ni*mo \xmark & pseu*dô*ni*mo \cmark \\
psicologicamente & p.si*co*lo*gi*ca*men*te \xmark & psi*co*lo*gi*ca*men*te \cmark \\
tatuí & ta*tu-í \xmark & ta*tu*í \cmark \\
anuário & a*nu-á*ri*o \xmark & a*nu*á*ri*o \cmark \\
contrair & con*tra-ir \xmark & con*tra*ir \cmark \\
curió & cu*ri-ó \xmark & cu*ri*ó \cmark \\
egoísmo & e*go-ís*mo \xmark & e*go*ís*mo \cmark \\
poliéster & po*li-és*ter \xmark & po*li*és*ter \cmark \\
caótico & ca-ó*ti*co \xmark & ca*ó*ti*co \cmark \\
descontraído & des*con*tra-í*do \xmark & des*con*tra*í*do \cmark \\
hanseníase & han*se*ní-a*se \xmark & han*se*ní*a*se \cmark \\
macedônia & ma*ce-dô*ni*a \xmark & ma*ce*dô*ni*a \cmark \\
heroísmo & he*ro-ís*mo \xmark & he*ro*ís*mo \cmark \\
instituído & ins*ti*tu-í*do \xmark & ins*ti*tu*í*do \cmark \\
periódico & pe*ri-ó*di*co \xmark & pe*ri*ó*di*co \cmark \\
abdômen & ab-dô*men \xmark & ab*dô*men \cmark \\
paraibano & pa*ra-i*ba*no \xmark & pa*ra-i*ba*no \xmark \\
psíquico & p.sí*qui*co \xmark & psí*qui*co \cmark \\
reconstituir & re*cons*ti*tu-ir \xmark & re*cons*ti*tu*ir \cmark \\
oásis & o-á*sis \xmark & o*á*sis \cmark \\
parnaíba & par*na-í*ba \xmark & par*na*í*ba \cmark \\
usufruir & u*su*fru-ir \xmark & u*su*fru*ir \cmark \\
camelô & ca*me-lô \xmark & ca*me*lô \cmark \\
maníaco & ma*ní-a*co \xmark & ma*ní*a*co \cmark \\
sabiá & sa*bi-á \xmark & sa*bi*á \cmark \\
agronômico & a*gro-nô*mi*co \xmark & a*gro*nô*mi*co \cmark \\
astronômico & as*tro-nô*mi*co \xmark & as*tro*nô*mi*co \cmark \\
psicopata & p.si*co*pa*ta \xmark & psi*co*pa*ta \cmark \\
geógrafo & ge-ó*gra*fo \xmark & ge*ó*gra*fo \cmark \\
ideário & i*de-á*ri*o \xmark & i*de*á*ri*o \cmark \\
piá & pi-á \xmark & pi*á \cmark \\
alcoólatra & al*co-ó*la*tra \xmark & al*co*ó*la*tra \cmark \\
biógrafo & bi-ó*gra*fo \xmark & bi*ó*gra*fo \cmark \\
coincidir & co-in*ci*dir \xmark & co*in*ci*dir \cmark \\
escorpião & es*cor*pi-ão \xmark & es*cor*pi*ão \cmark \\
fluência & flu-ên*ci*a \xmark & flu*ên*ci*a \cmark \\
ruína & ru-í*na \xmark & ru*í*na \cmark \\
delinquência & de*lin-quên*ci*a \xmark & de*lin*quên*ci*a \cmark \\
contraído & con*tra-í*do \xmark & con*tra*í*do \cmark \\
diluir & di*lu-ir \xmark & di*lu*ir \cmark \\
psicose & p.si*co*se \xmark & psi*co*se \cmark \\
bioquímica & bi*o-quí*mi*ca \xmark & bi*o*quí*mi*ca \cmark \\
fluidez & flu-i*dez \xmark & flu-i*dez \xmark \\
futevôlei & fu*te-vô*lei \xmark & fu*te*vô*lei \cmark \\
judaísmo & ju*da-ís*mo \xmark & ju*da*ís*mo \cmark \\
viúvo & vi-ú*vo \xmark & vi*ú*vo \cmark \\
capô & ca-pô \xmark & ca*pô \cmark \\
casuísmo & ca*su-ís*mo \xmark & ca*su*ís*mo \cmark \\
receituário & re*cei*tu-á*ri*o \xmark & re*cei*tu*á*ri*o \cmark \\
agrião & a*gri-ão \xmark & a*gri*ão \cmark \\
comerciário & co*mer*ci-á*ri*o \xmark & co*mer*ci*á*ri*o \cmark \\
estereótipo & es*te*re-ó*ti*po \xmark & es*te*re*ó*ti*po \cmark \\
psicoterapia & p.si*co*te*ra*pi*a \xmark & psi*co*te*ra*pi*a \cmark \\
vascaíno & vas*ca-í*no \xmark & vas*ca*í*no \cmark \\
arquitetônica & ar*qui*te-tô*ni*ca \xmark & ar*qui*te*tô*ni*ca \cmark \\
macroeconômico & ma*cro*e*co-nô*mi*co \xmark & ma*cro*e*co*nô*mi*co \cmark \\
restituir & res*ti*tu-ir \xmark & res*ti*tu*ir \cmark \\
rutherford & ru-ther*ford \xmark & ru-ther*ford \xmark \\
triunfal & tri-un*fal \xmark & tri*un*fal \cmark \\
guardião & guar*di-ão \xmark & guar*di*ão \cmark \\
oriundo & o*ri-un*do \xmark & o*ri*un*do \cmark \\
arqueólogo & ar*que-ó*lo*go \xmark & ar*que*ó*lo*go \cmark \\
carbônico & car-bô*ni*co \xmark & car*bô*ni*co \cmark \\
stalinista & s.ta*li*nis*ta \xmark & sta*li*nis*ta \cmark \\
egoísta & e*go-ís*ta \xmark & e*go*ís*ta \cmark \\
portuário & por*tu-á*ri*o \xmark & por*tu*á*ri*o \cmark \\
recaída & re*ca-í*da \xmark & re*ca*í*da \cmark \\
reiniciar & re-i*ni*ci*ar \xmark & re-i*ni*ci*ar \xmark \\
reurbanização & re-ur*ba*ni*za*ção \xmark & re-ur*ba*ni*za*ção \xmark \\
teólogo & te-ó*lo*go \xmark & te*ó*lo*go \cmark \\
baião & bai-ão \xmark & bai*ão \cmark \\
genuíno & ge*nu-í*no \xmark & ge*nu*í*no \cmark \\
hegemônico & he*ge-mô*ni*co \xmark & he*ge*mô*ni*co \cmark \\
resquício & res-quí*ci*o \xmark & res*quí*ci*o \cmark \\
retribuição & re*tri*bu-i*ção \xmark & re*tri*bu*i*ção \cmark \\
confluência & con*flu-ên*ci*a \xmark & con*flu*ên*ci*a \cmark \\
fluir & flu-ir \xmark & flu*ir \cmark \\
imperdoável & im*per*do-á*vel \xmark & im*per*do*á*vel \cmark \\
distrair & dis*tra-ir \xmark & dis*tra*ir \cmark \\
guaíba & gua-í*ba \xmark & gua*í*ba \cmark \\
intuitivo & in*tu-i*ti*vo \xmark & in*tu*i*ti*vo \cmark \\
orquídea & or-quí*de*a \xmark & or*quí*de*a \cmark \\
semiótica & se*mi-ó*ti*ca \xmark & se*mi*ó*ti*ca \cmark \\
vovô & vo-vô \xmark & vo*vô \cmark \\
campainha & cam*pa-i*nha \xmark & cam*pa*i*nha \cmark \\
czar & c.zar \xmark & czar \cmark \\
diluição & di*lu-i*ção \xmark & di*lu*i*ção \cmark \\
distraído & dis*tra-í*do \xmark & dis*tra*í*do \cmark \\
eloquência & e*lo-quên*ci*a \xmark & e*lo*quên*ci*a \cmark \\
insubstituível & in*subs*ti*tu-í*vel \xmark & in*subs*ti*tu*í*vel \cmark \\
reinventar & re-in*ven*tar \xmark & re*in*ven*tar \cmark \\
retribuir & re*tri*bu-ir \xmark & re*tri*bu*ir \cmark \\
rubéola & ru*bé-o*la \xmark & ru*bé*o*la \cmark \\
abruptamente & a.b-rup*ta*men*te \xmark & a.b-rup*ta*men*te \xmark \\
maniqueísmo & ma*ni*que-ís*mo \xmark & ma*ni*que*ís*mo \cmark \\
antiquário & an*ti-quá*ri*o \xmark & an*ti*quá*ri*o \cmark \\
harmônica & har-mô*ni*ca \xmark & har*mô*ni*ca \cmark \\
judô & ju-dô \xmark & ju*dô \cmark \\
maniqueísta & ma*ni*que-ís*ta \xmark & ma*ni*que*ís*ta \cmark \\
tchau & t.chau \xmark & tchau \cmark \\
moído & mo-í*do \xmark & mo*í*do \cmark \\
psicanalítico & p.si*ca*na*lí*ti*co \xmark & psi*ca*na*lí*ti*co \cmark \\
caíco & ca-í*co \xmark & ca*í*co \cmark \\
descontinuidade & des*con*ti*nu-i*da*de \xmark & des*con*ti*nu*i*da*de \cmark \\
tarô & ta-rô \xmark & ta*rô \cmark \\
absenteísmo & ab*sen*te-ís*mo \xmark & ab*sen*te*ís*mo \cmark \\
anuência & a*nu-ên*ci*a \xmark & a*nu*ên*ci*a \cmark \\
etíope & e*tí-o*pe \xmark & e*tí*o*pe \cmark \\
ofurô & o*fu-rô \xmark & o*fu*rô \cmark \\
panteão & pan*te-ão \xmark & pan*te*ão \cmark \\
atômico & a-tô*mi*co \xmark & a*tô*mi*co \cmark \\
corroído & cor*ro-í*do \xmark & cor*ro*í*do \cmark \\
destituído & des*ti*tu-í*do \xmark & des*ti*tu*í*do \cmark \\
estagiário & es*ta*gi-á*ri*o \xmark & es*ta*gi*á*ri*o \cmark \\
inadiável & i*na*di-á*vel \xmark & i*na*di*á*vel \cmark \\
instruído & ins*tru-í*do \xmark & ins*tru*í*do \cmark \\
amazônico & a*ma-zô*ni*co \xmark & a*ma*zô*ni*co \cmark \\
anuidade & a*nu-i*da*de \xmark & a*nu*i*da*de \cmark \\
evoluído & e*vo*lu-í*do \xmark & e*vo*lu*í*do \cmark \\
faísca & fa-ís*ca \xmark & fa*ís*ca \cmark \\
harmônico & har-mô*ni*co \xmark & har*mô*ni*co \cmark \\
patriótico & pa*tri-ó*ti*co \xmark & pa*tri*ó*ti*co \cmark \\
presidiário & pre*si*di-á*ri*o \xmark & pre*si*di*á*ri*o \cmark \\
reconstruído & re*cons*tru-í*do \xmark & re*cons*tru*í*do \cmark \\
tricô & tri-cô \xmark & tri*cô \cmark \\
antiético & an*ti-é*ti*co \xmark & an*ti*é*ti*co \cmark \\
cronômetro & cro-nô*me*tro \xmark & cro*nô*me*tro \cmark \\
destituição & des*ti*tu-i*ção \xmark & des*ti*tu*i*ção \cmark \\
fiúza & fi-ú*za \xmark & fi*ú*za \cmark \\
píer & pí-er \xmark & pí-er \xmark \\
psique & p.si*que \xmark & psi*que \cmark \\
recair & re*ca-ir \xmark & re*ca*ir \cmark \\
sinfônico & sin-fô*ni*co \xmark & sin*fô*ni*co \cmark \\
triunfante & tri-un*fan*te \xmark & tri*un*fan*te \cmark \\
adail & a*da-il \xmark & a*da-il \xmark \\
atônito & a-tô*ni*to \xmark & a*tô*ni*to \cmark \\
birô & bi-rô \xmark & bi*rô \cmark \\
cafeína & ca*fe-í*na \xmark & ca*fe*í*na \cmark \\
ideólogo & i*de-ó*lo*go \xmark & i*de*ó*lo*go \cmark \\
inequívoco & i*ne-quí*vo*co \xmark & i*ne*quí*vo*co \cmark \\
míope & mí-o*pe \xmark & mí*o*pe \cmark \\
poá & po-á \xmark & po*á \cmark \\
stalinismo & s.ta*li*nis*mo \xmark & sta*li*nis*mo \cmark \\
suíno & su-í*no \xmark & su*í*no \cmark \\
voyeurismo & voy-eu*ris*mo \xmark & voy-eu*ris*mo \xmark \\
camaleão & ca*ma*le-ão \xmark & ca*ma*le*ão \cmark \\
dióxido & di-ó*xi*do \xmark & di*ó*xi*do \cmark \\
geólogo & ge-ó*lo*go \xmark & ge*ó*lo*go \cmark \\
ilíada & i*lí-a*da \xmark & i*lí*a*da \cmark \\
impermeável & im*per*me-á*vel \xmark & im*per*me*á*vel \cmark \\
jesuíta & je*su-í*ta \xmark & je*su*í*ta \cmark \\
suástica & su-ás*ti*ca \xmark & su*ás*ti*ca \cmark \\
bioquímico & bi*o-quí*mi*co \xmark & bi*o*quí*mi*co \cmark \\
buquê & bu-quê \xmark & bu*quê \cmark \\
esôfago & e-sô*fa*go \xmark & e*sô*fa*go \cmark \\
folião & fo*li-ão \xmark & fo*li*ão \cmark \\
quilowatt & qui*lo-watt \xmark & qui*lo-watt \xmark \\
ruir & ru-ir \xmark & ru*ir \cmark \\
altruísmo & al*tru-ís*mo \xmark & al*tru*ís*mo \cmark \\
equânime & e-quâ*ni*me \xmark & e*quâ*ni*me \cmark \\
fruição & fru-i*ção \xmark & fru*i*ção \cmark \\
insaciável & in*sa*ci-á*vel \xmark & in*sa*ci*á*vel \cmark \\
caída & ca-í*da \xmark & ca*í*da \cmark \\
ciático & ci-á*ti*co \xmark & ci*á*ti*co \cmark \\
gavião & ga*vi-ão \xmark & ga*vi*ão \cmark \\
gratuidade & gra*tu-i*da*de \xmark & gra*tu*i*da*de \cmark \\
irremediável & ir*re*me*di-á*vel \xmark & ir*re*me*di*á*vel \cmark \\
ladainha & la*da-i*nha \xmark & la*da*i*nha \cmark \\
piauiense & pi*au-i*en*se \xmark & pi*au-i*en*se \xmark \\
prostituir & pros*ti*tu-ir \xmark & pros*ti*tu*ir \cmark \\
triunfar & tri-un*far \xmark & tri*un*far \cmark \\
acuidade & a*cu-i*da*de \xmark & a*cu*i*da*de \cmark \\
adriático & a*dri-á*ti*co \xmark & a*dri*á*ti*co \cmark \\
afrodisíaco & a*fro*di*sí-a*co \xmark & a*fro*di*sí*a*co \cmark \\
bioética & bi*o-é*ti*ca \xmark & bi*o*é*ti*ca \cmark \\
cocô & co-cô \xmark & co*cô \cmark \\
instruir & ins*tru-ir \xmark & ins*tru*ir \cmark \\
paradisíaco & pa*ra*di*sí-a*co \xmark & pa*ra*di*sí*a*co \cmark \\
poluir & po*lu-ir \xmark & po*lu*ir \cmark \\
possuído & pos*su-í*do \xmark & pos*su*í*do \cmark \\
sublinha & su.b-li*nha \xmark & su.b-li*nha \xmark \\
antibiótico & an*ti*bi-ó*ti*co \xmark & an*ti*bi*ó*ti*co \cmark \\
apreciável & a*pre*ci-á*vel \xmark & a*pre*ci*á*vel \cmark \\
desobstruir & de*sobs*tru-ir \xmark & de*sobs*tru*ir \cmark \\
destruidor & des*tru-i*dor \xmark & des*tru*i*dor \cmark \\
diáspora & di-ás*po*ra \xmark & di*ás*po*ra \cmark \\
diluído & di*lu-í*do \xmark & di*lu*í*do \cmark \\
maiúsculo & mai-ús*cu*lo \xmark & mai*ús*cu*lo \cmark \\
miúdo & mi-ú*do \xmark & mi*ú*do \cmark \\
pentacampeão & pen*ta*cam*pe-ão \xmark & pen*ta*cam*pe*ão \cmark \\
retraído & re*tra-í*do \xmark & re*tra*í*do \cmark \\
subtrair & sub*tra-ir \xmark & sub*tra*ir \cmark \\
suéter & su-é*ter \xmark & su*é*ter \cmark \\
açaí & a*ça-í \xmark & a*ça*í \cmark \\
alcoólico & al*co-ó*li*co \xmark & al*co*ó*li*co \cmark \\
despoluir & des*po*lu-ir \xmark & des*po*lu*ir \cmark \\
diurno & di-ur*no \xmark & di*ur*no \cmark \\
inexequível & i*ne*xe-quí*vel \xmark & i*ne*xe*quí*vel \cmark \\
prontuário & pron*tu-á*ri*o \xmark & pron*tu*á*ri*o \cmark \\
psicoterapeuta & p.si*co*te*ra*peu*ta \xmark & psi*co*te*ra*peu*ta \cmark \\
saúva & sa-ú*va \xmark & sa*ú*va \cmark \\
tabelião & ta*be*li-ão \xmark & ta*be*li*ão \cmark \\
abrupto & a.b-rup*to \xmark & a.b-rup*to \xmark \\
destituir & des*ti*tu-ir \xmark & des*ti*tu*ir \cmark \\
dionisíaco & di*o*ni*sí-a*co \xmark & di*o*ni*sí*a*co \cmark \\
lacônico & la-cô*ni*co \xmark & la*cô*ni*co \cmark \\
megawatt & me*ga-watt \xmark & me*ga-watt \xmark \\
poliuretano & po*li-u*re*ta*no \xmark & po*li*u*re*ta*no \cmark \\
protozoário & pro*to*zo-á*ri*o \xmark & pro*to*zo*á*ri*o \cmark \\
reincidente & re-in*ci*den*te \xmark & re*in*ci*den*te \cmark \\
reintegrar & re-in*te*grar \xmark & re*in*te*grar \cmark \\
reinvenção & re-in*ven*ção \xmark & re*in*ven*ção \cmark \\
afluência & a*flu-ên*ci*a \xmark & a*flu*ên*ci*a \cmark \\
assiduidade & as*si*du-i*da*de \xmark & as*si*du*i*da*de \cmark \\
coágulo & co-á*gu*lo \xmark & co*á*gu*lo \cmark \\
cuíca & cu-í*ca \xmark & cu*í*ca \cmark \\
faraó & fa*ra-ó \xmark & fa*ra*ó \cmark \\
fundiário & fun*di-á*ri*o \xmark & fun*di*á*ri*o \cmark \\
incendiário & in*cen*di-á*ri*o \xmark & in*cen*di*á*ri*o \cmark \\
itapuã & i*ta*pu-ã \xmark & i*ta*pu*ã \cmark \\
parcimônia & par*ci-mô*ni*a \xmark & par*ci*mô*ni*a \cmark \\
psicótico & p.si*có*ti*co \xmark & psi*có*ti*co \cmark \\
redemoinho & re*de*mo-i*nho \xmark & re*de*mo*i*nho \cmark \\
redistribuir & re*dis*tri*bu-ir \xmark & re*dis*tri*bu*ir \cmark \\
reintrodução & re-in*tro*du*ção \xmark & re*in*tro*du*ção \cmark \\
triunfalismo & tri-un*fa*lis*mo \xmark & tri*un*fa*lis*mo \cmark \\
zodíaco & zo*dí-a*co \xmark & zo*dí*a*co \cmark \\
aminoácido & a*mi*no-á*ci*do \xmark & a*mi*no*á*ci*do \cmark \\
arruinar & ar*ru-i*nar \xmark & ar*ru*i*nar \cmark \\
ateísmo & a*te-ís*mo \xmark & a*te*ís*mo \cmark \\
caim & ca-im \xmark & ca-im \xmark \\
exequível & e*xe-quí*vel \xmark & e*xe*quí*vel \cmark \\
inconsequência & in*con*se-quên*ci*a \xmark & in*con*se*quên*ci*a \cmark \\
laquê & la-quê \xmark & la*quê \cmark \\
megalomaníaco & me*ga*lo*ma*ní-a*co \xmark & me*ga*lo*ma*ní*a*co \cmark \\
pantaleão & pan*ta*le-ão \xmark & pan*ta*le*ão \cmark \\
poluidor & po*lu-i*dor \xmark & po*lu*i*dor \cmark \\
preâmbulo & pre-âm*bu*lo \xmark & pre*âm*bu*lo \cmark \\
arcaísmo & ar*ca-ís*mo \xmark & ar*ca*ís*mo \cmark \\
auréola & au*ré-o*la \xmark & au*ré*o*la \cmark \\
autodestruição & au*to*des*tru-i*ção \xmark & au*to*des*tru*i*ção \cmark \\
casuística & ca*su-ís*ti*ca \xmark & ca*su*ís*ti*ca \cmark \\
desunião & de*su*ni-ão \xmark & de*su*ni*ão \cmark \\
elogiável & e*lo*gi-á*vel \xmark & e*lo*gi*á*vel \cmark \\
gnomo & g.no*mo \xmark & gno*mo \cmark \\
neurocirurgião & neu*ro*ci*rur*gi-ão \xmark & neu*ro*ci*rur*gi*ão \cmark \\
pediátrico & pe*di-á*tri*co \xmark & pe*di*á*tri*co \cmark \\
permeável & per*me-á*vel \xmark & per*me*á*vel \cmark \\
piraí & pi*ra-í \xmark & pi*ra*í \cmark \\
psicodélico & p.si*co*dé*li*co \xmark & psi*co*dé*li*co \cmark \\
psicotécnico & p.si*co*téc*ni*co \xmark & psi*co*téc*ni*co \cmark \\
saíra & sa-í*ra \xmark & sa*í*ra \cmark \\
sobressair & so*bres*sa-ir \xmark & so*bres*sa*ir \cmark \\
subliminar & su.b-li*mi*nar \xmark & sub*li*mi*nar \cmark \\
ajuizado & a*ju-i*za*do \xmark & a*ju*i*za*do \cmark \\
antipoluição & an*ti*po*lu-i*ção \xmark & an*ti*po*lu*i*ção \cmark \\
arquétipo & ar-qué*ti*po \xmark & ar*qué*ti*po \cmark \\
dadaísmo & da*da-ís*mo \xmark & da*da*ís*mo \cmark \\
descontrair & des*con*tra-ir \xmark & des*con*tra*ir \cmark \\
gasômetro & ga-sô*me*tro \xmark & ga*sô*me*tro \cmark \\
hidroviário & hi*dro*vi-á*ri*o \xmark & hi*dro*vi*á*ri*o \cmark \\
inegociável & i*ne*go*ci-á*vel \xmark & i*ne*go*ci*á*vel \cmark \\
maiúscula & mai-ús*cu*la \xmark & mai*ús*cu*la \cmark \\
miúdas & mi-ú*das \xmark & mi*ú*das \cmark \\
perequê & pe*re-quê \xmark & pe*re*quê \cmark \\
recôncavo & re-côn*ca*vo \xmark & re*côn*ca*vo \cmark \\
saquê & sa-quê \xmark & sa*quê \cmark \\
ancião & an*ci-ão \xmark & an*ci*ão \cmark \\
bafômetro & ba-fô*me*tro \xmark & ba*fô*me*tro \cmark \\
bongô & bon-gô \xmark & bon*gô \cmark \\
ciberespaço & ci*be.r-es*pa*ço \xmark & ci*be.r-es*pa*ço \xmark \\
condômino & con-dô*mi*no \xmark & con*dô*mi*no \cmark \\
dadaísta & da*da-ís*ta \xmark & da*da*ís*ta \cmark \\
freático & fre-á*ti*co \xmark & fre*á*ti*co \cmark \\
hipocondríaco & hi*po*con*drí-a*co \xmark & hi*po*con*drí*a*co \cmark \\
indaiá & in*dai-á \xmark & in*dai*á \cmark \\
jacuí & ja*cu-í \xmark & ja*cu*í \cmark \\
maleável & ma*le-á*vel \xmark & ma*le*á*vel \cmark \\
ministeriável & mi*nis*te*ri-á*vel \xmark & mi*nis*te*ri*á*vel \cmark \\
obituário & o*bi*tu-á*ri*o \xmark & o*bi*tu*á*ri*o \cmark \\
picuinha & pi*cu-i*nha \xmark & pi*cu-i*nha \xmark \\
platô & pla-tô \xmark & pla*tô \cmark \\
possuidor & pos*su-i*dor \xmark & pos*su*i*dor \cmark \\
psicodelismo & p.si*co*de*lis*mo \xmark & psi*co*de*lis*mo \cmark \\
reinserção & re-in*ser*ção \xmark & re*in*ser*ção \cmark \\
suingue & su-in*gue \xmark & su-in*gue \xmark \\
triunfalista & tri-un*fa*lis*ta \xmark & tri*un*fa*lis*ta \cmark \\
varíola & va*rí-o*la \xmark & va*rí*o*la \cmark \\
apoteótico & a*po*te-ó*ti*co \xmark & a*po*te*ó*ti*co \cmark \\
bainha & ba-i*nha \xmark & ba*i*nha \cmark \\
bibliófilo & bi*bli-ó*fi*lo \xmark & bi*bli*ó*fi*lo \cmark \\
caimento & ca-i*men*to \xmark & ca-i*men*to \xmark \\
cambuí & cam*bu-í \xmark & cam*bu*í \cmark \\
cauim & cau-im \xmark & cau-im \xmark \\
darwinismo & dar-wi*nis*mo \xmark & dar-wi*nis*mo \xmark \\
eclesiástico & e*cle*si-ás*ti*co \xmark & e*cle*si*ás*ti*co \cmark \\
estuário & es*tu-á*ri*o \xmark & es*tu*á*ri*o \cmark \\
gigolô & gi*go-lô \xmark & gi*go*lô \cmark \\
imbuído & im*bu-í*do \xmark & im*bu*í*do \cmark \\
bastião & bas*ti-ão \xmark & bas*ti*ão \cmark \\
caíque & ca-í*que \xmark & ca*í*que \cmark \\
coincidente & co-in*ci*den*te \xmark & co*in*ci*den*te \cmark \\
flúor & flú-or \xmark & flú-or \xmark \\
incongruência & in*con*gru-ên*ci*a \xmark & in*con*gru*ên*ci*a \cmark \\
indissociável & in*dis*so*ci-á*vel \xmark & in*dis*so*ci*á*vel \cmark \\
invariável & in*va*ri-á*vel \xmark & in*va*ri*á*vel \cmark \\
mostruário & mos*tru-á*ri*o \xmark & mos*tru*á*ri*o \cmark \\
néon & né-on \xmark & né*on \cmark \\
oboé & o*bo-é \xmark & o*bo*é \cmark \\
oceânico & o*ce-â*ni*co \xmark & o*ce*â*ni*co \cmark \\
panteísmo & pan*te-ís*mo \xmark & pan*te*ís*mo \cmark \\
platônico & pla-tô*ni*co \xmark & pla*tô*ni*co \cmark \\
pneumologia & p.neu*mo*lo*gi*a \xmark & pneu*mo*lo*gi*a \cmark \\
proibitivo & pro-i*bi*ti*vo \xmark & pro*i*bi*ti*vo \cmark \\
raquítico & ra-quí*ti*co \xmark & ra*quí*ti*co \cmark \\
reinterpretação & re-in*ter*pre*ta*ção \xmark & re*in*ter*pre*ta*ção \cmark \\
subtraído & sub*tra-í*do \xmark & sub*tra*í*do \cmark \\
suinocultura & su-i*no*cul*tu*ra \xmark & su*i*no*cul*tu*ra \cmark \\
sumô & su-mô \xmark & su*mô \cmark \\
tainha & ta-i*nha \xmark & ta*i*nha \cmark \\
acordeão & a*cor*de-ão \xmark & a*cor*de*ão \cmark \\
aético & a-é*ti*co \xmark & a*é*ti*co \cmark \\
baiuca & bai-u*ca \xmark & bai-u*ca \xmark \\
centurião & cen*tu*ri-ão \xmark & cen*tu*ri*ão \cmark \\
comediógrafo & co*me*di-ó*gra*fo \xmark & co*me*di*ó*gra*fo \cmark \\
conduíte & con*du-í*te \xmark & con*du*í*te \cmark \\
coroinha & co*ro-i*nha \xmark & co*ro*i*nha \cmark \\
ergonômico & er*go-nô*mi*co \xmark & er*go*nô*mi*co \cmark \\
gaélico & ga-é*li*co \xmark & ga*é*li*co \cmark \\
grandiloquência & gran*di*lo-quên*ci*a \xmark & gran*di*lo*quên*ci*a \cmark \\
impatriótico & im*pa*tri-ó*ti*co \xmark & im*pa*tri*ó*ti*co \cmark \\
megalômano & me*ga-lô*ma*no \xmark & me*ga*lô*ma*no \cmark \\
miríade & mi*rí-a*de \xmark & mi*rí*a*de \cmark \\
neófito & ne-ó*fi*to \xmark & ne*ó*fi*to \cmark \\
nipônico & ni-pô*ni*co \xmark & ni*pô*ni*co \cmark \\
obstruído & obs*tru-í*do \xmark & obs*tru*í*do \cmark \\
pecuniário & pe*cu*ni-á*ri*o \xmark & pe*cu*ni*á*ri*o \cmark \\
psicopatologia & p.si*co*pa*to*lo*gi*a \xmark & psi*co*pa*to*lo*gi*a \cmark \\
reindexar & re-in*de*xar \xmark & re-in*de*xar \xmark \\
reinstalar & re-ins*ta*lar \xmark & re*ins*ta*lar \cmark \\
reintroduzir & re-in*tro*du*zir \xmark & re*in*tro*du*zir \cmark \\
teleinformática & te*le-in*for*má*ti*ca \xmark & te*le*in*for*má*ti*ca \cmark \\
timbaúba & tim*ba-ú*ba \xmark & tim*ba*ú*ba \cmark \\
agônico & a-gô*ni*co \xmark & a*gô*ni*co \cmark \\
anatômico & a*na-tô*mi*co \xmark & a*na*tô*mi*co \cmark \\
anômalo & a-nô*ma*lo \xmark & a*nô*ma*lo \cmark \\
ataúde & a*ta-ú*de \xmark & a*ta*ú*de \cmark \\
auê & au-ê \xmark & au*ê \cmark \\
bestiário & bes*ti-á*ri*o \xmark & bes*ti*á*ri*o \cmark \\
boá & bo-á \xmark & bo*á \cmark \\
copião & co*pi-ão \xmark & co*pi*ão \cmark \\
ensaística & en*sa-ís*ti*ca \xmark & en*sa*ís*ti*ca \cmark \\
fonoaudiólogo & fo*no*au*di-ó*lo*go \xmark & fo*no*au*di*ó*lo*go \cmark \\
imiscuir & i*mis*cu-ir \xmark & i*mis*cu-ir \xmark \\
jupiá & ju*pi-á \xmark & ju*pi*á \cmark \\
monoteísmo & mo*no*te-ís*mo \xmark & mo*no*te*ís*mo \cmark \\
nagô & na-gô \xmark & na*gô \cmark \\
psicofarmacologia & p.si*co*far*ma*co*lo*gi*a \xmark & psi*co*far*ma*co*lo*gi*a \cmark \\
psicologismo & p.si*co*lo*gis*mo \xmark & psi*co*lo*gis*mo \cmark \\
ruindade & ru-in*da*de \xmark & ru-in*da*de \xmark \\
sanduicheria & san*du-i*che*ri*a \xmark & san*du*i*che*ri*a \cmark \\
sociável & so*ci-á*vel \xmark & so*ci*á*vel \cmark \\
sublevação & su.b-le*va*ção \xmark & sub*le*va*ção \cmark \\
abstrair & abs*tra-ir \xmark & abs*tra*ir \cmark \\
alaúde & a*la-ú*de \xmark & a*la*ú*de \cmark \\
almôndega & al-môn*de*ga \xmark & al*môn*de*ga \cmark \\
antiaéreo & an*ti*a-é*re*o \xmark & an*ti*a*é*re*o \cmark \\
atrabiliário & a*tra*bi*li-á*ri*o \xmark & a*tra*bi*li*á*ri*o \cmark \\
bangalô & ban*ga-lô \xmark & ban*ga*lô \cmark \\
bôer & bô-er \xmark & bô-er \xmark \\
breviário & bre*vi-á*ri*o \xmark & bre*vi*á*ri*o \cmark \\
canônico & ca-nô*ni*co \xmark & ca*nô*ni*co \cmark \\
carnaúba & car*na-ú*ba \xmark & car*na*ú*ba \cmark \\
doído & do-í*do \xmark & do*í*do \cmark \\
ensaísmo & en*sa-ís*mo \xmark & en*sa*ís*mo \cmark \\
esfiha & es*fi-ha \xmark & es*fi-ha \xmark \\
graúna & gra-ú*na \xmark & gra*ú*na \cmark \\
hemodiálise & he*mo*di-á*li*se \xmark & he*mo*di*á*li*se \cmark \\
hinduísmo & hin*du-ís*mo \xmark & hin*du*ís*mo \cmark \\
influído & in*flu-í*do \xmark & in*flu-í*do \xmark \\
intuir & in*tu-ir \xmark & in*tu*ir \cmark \\
latifundiário & la*ti*fun*di-á*ri*o \xmark & la*ti*fun*di*á*ri*o \cmark \\
mimeógrafo & mi*me-ó*gra*fo \xmark & mi*me*ó*gra*fo \cmark \\
pajeú & pa*je-ú \xmark & pa*je*ú \cmark \\
prosaísmo & pro*sa-ís*mo \xmark & pro*sa*ís*mo \cmark \\
psicodrama & p.si*co*dra*ma \xmark & psi*co*dra*ma \cmark \\
psicopedagogia & p.si*co*pe*da*go*gi*a \xmark & psi*co*pe*da*go*gi*a \cmark \\
quinquênio & quin-quê*ni*o \xmark & quin*quê*ni*o \cmark \\
radiofrequência & ra*di*o*fre-quên*ci*a \xmark & ra*di*o*fre*quên*ci*a \cmark \\
reinstituir & re-ins*ti*tu-ir \xmark & re*ins*ti*tu*ir \cmark \\
supercampeão & su*per*cam*pe-ão \xmark & su*per*cam*pe*ão \cmark \\
supersônico & su*per-sô*ni*co \xmark & su*per*sô*ni*co \cmark \\
tragicômico & tra*gi-cô*mi*co \xmark & tra*gi*cô*mi*co \cmark \\
tríade & trí-a*de \xmark & trí*a*de \cmark \\
vacuidade & va*cu-i*da*de \xmark & va*cu*i*da*de \cmark \\
agogô & a*go-gô \xmark & a*go*gô \cmark \\
altruísta & al*tru-ís*ta \xmark & al*tru*ís*ta \cmark \\
antiácido & an*ti-á*ci*do \xmark & an*ti*á*ci*do \cmark \\
autobiógrafo & au*to*bi-ó*gra*fo \xmark & au*to*bi*ó*gra*fo \cmark \\
beduíno & be*du-í*no \xmark & be*du*í*no \cmark \\
bordô & bor-dô \xmark & bor*dô \cmark \\
casuístico & ca*su-ís*ti*co \xmark & ca*su*ís*ti*co \cmark \\
czarina & c.za*ri*na \xmark & cza*ri*na \cmark \\
demoníaco & de*mo*ní-a*co \xmark & de*mo*ní*a*co \cmark \\
desconstruir & des*cons*tru-ir \xmark & des*cons*tru*ir \cmark \\
ergômetro & er-gô*me*tro \xmark & er*gô*me*tro \cmark \\
evoé & e*vo-é \xmark & e*vo*é \cmark \\
graúdo & gra-ú*do \xmark & gra*ú*do \cmark \\
iídiche & i-í*di*che \xmark & i*í*di*che \cmark \\
impronunciável & im*pro*nun*ci-á*vel \xmark & im*pro*nun*ci*á*vel \cmark \\
influenciável & in*flu*en*ci-á*vel \xmark & in*flu*en*ci*á*vel \cmark \\
irrefreável & ir*re*fre-á*vel \xmark & ir*re*fre*á*vel \cmark \\
irretorquível & ir*re*tor-quí*vel \xmark & ir*re*tor*quí*vel \cmark \\
jataí & ja*ta-í \xmark & ja*ta*í \cmark \\
juquiá & ju*qui-á \xmark & ju*qui*á \cmark \\
painho & pa-i*nho \xmark & pa*i*nho \cmark \\
pindaíba & pin*da-í*ba \xmark & pin*da*í*ba \cmark \\
pneumologista & p.neu*mo*lo*gis*ta \xmark & pneu*mo*lo*gis*ta \cmark \\
porciúncula & por*ci-ún*cu*la \xmark & por*ci*ún*cu*la \cmark \\
prolegômenos & pro*le-gô*me*nos \xmark & pro*le*gô*me*nos \cmark \\
psiquismo & p.si*quis*mo \xmark & psi*quis*mo \cmark \\
quiproquó & qui*pro-quó \xmark & qui*pro*quó \cmark \\
refluir & re*flu-ir \xmark & re*flu*ir \cmark \\
reimplantar & re-im*plan*tar \xmark & re*im*plan*tar \cmark \\
reurbanizar & re-ur*ba*ni*zar \xmark & re-ur*ba*ni*zar \xmark \\
reutilizar & re-u*ti*li*zar \xmark & re-u*ti*li*zar \xmark \\
sainte & sa-in*te \xmark & sa-in*te \xmark \\
tsunami & t.su*na*mi \xmark & tsu*na*mi \cmark \\
usucapião & u*su*ca*pi-ão \xmark & u*su*ca*pi*ão \cmark \\
zebuíno & ze*bu-í*no \xmark & ze*bu*í*no \cmark \\
aeroportuário & a*e*ro*por*tu-á*ri*o \xmark & a*e*ro*por*tu*á*ri*o \cmark \\
agroquímica & a*gro-quí*mi*ca \xmark & a*gro*quí*mi*ca \cmark \\
ajuizar & a*ju-i*zar \xmark & a*ju*i*zar \cmark \\
baraúna & ba*ra-ú*na \xmark & ba*ra*ú*na \cmark \\
casuísta & ca*su-ís*ta \xmark & ca*su*ís*ta \cmark \\
catatônico & ca*ta-tô*ni*co \xmark & ca*ta*tô*ni*co \cmark \\
conteudista & con*te-u*dis*ta \xmark & con*te-u*dis*ta \xmark \\
continuísta & con*ti*nu-ís*ta \xmark & con*ti*nu*ís*ta \cmark \\
czarista & c.za*ris*ta \xmark & cza*ris*ta \cmark \\
decair & de*ca-ir \xmark & de*ca*ir \cmark \\
deísta & de-ís*ta \xmark & de*ís*ta \cmark \\
diácono & di-á*co*no \xmark & di*á*co*no \cmark \\
elegíaco & e*le*gí-a*co \xmark & e*le*gí*a*co \cmark \\
faraônico & fa*ra-ô*ni*co \xmark & fa*ra*ô*ni*co \cmark \\
feérico & fe-é*ri*co \xmark & fe*é*ri*co \cmark \\
hidroavião & hi*dro*a*vi-ão \xmark & hi*dro*a*vi*ão \cmark \\
hodômetro & ho-dô*me*tro \xmark & ho*dô*me*tro \cmark \\
inconciliável & in*con*ci*li-á*vel \xmark & in*con*ci*li*á*vel \cmark \\
ioiô & i.o-i.ô \xmark & i.o-i.ô \xmark \\
macrobiótica & ma*cro*bi-ó*ti*ca \xmark & ma*cro*bi*ó*ti*ca \cmark \\
marruá & mar*ru-á \xmark & mar*ru*á \cmark \\
meteórico & me*te-ó*ri*co \xmark & me*te*ó*ri*co \cmark \\
panteísta & pan*te-ís*ta \xmark & pan*te*ís*ta \cmark \\
papaína & pa*pa-í*na \xmark & pa*pa*í*na \cmark \\
patuá & pa*tu-á \xmark & pa*tu*á \cmark \\
perdoável & per*do-á*vel \xmark & per*do*á*vel \cmark \\
prostituído & pros*ti*tu-í*do \xmark & pros*ti*tu*í*do \cmark \\
pulôver & pu-lô*ver \xmark & pu*lô*ver \cmark \\
ravióli & ra*vi-ó*li \xmark & ra*vi*ó*li \cmark \\
reincorporação & re-in*cor*po*ra*ção \xmark & re*in*cor*po*ra*ção \cmark \\
reingresso & re-in*gres*so \xmark & re*in*gres*so \cmark \\
reinquirir & re-in*qui*rir \xmark & re-in*qui*rir \xmark \\
reinstalação & re-ins*ta*la*ção \xmark & re*ins*ta*la*ção \cmark \\
reinterpretar & re-in*ter*pre*tar \xmark & re*in*ter*pre*tar \cmark \\
saião & sai-ão \xmark & sai*ão \cmark \\
samaúma & sa*ma-ú*ma \xmark & sa*ma*ú*ma \cmark \\
sublocação & su.b-lo*ca*ção \xmark & sub*lo*ca*ção \cmark \\
turboélice & tur*bo-é*li*ce \xmark & tur*bo*é*li*ce \cmark \\
ventoinha & ven*to-i*nha \xmark & ven*to*i*nha \cmark \\
voyeurista & voy-eu*ris*ta \xmark & voy-eu*ris*ta \xmark \\
alagoinha & a*la*go-i*nha \xmark & a*la*go*i*nha \cmark \\
aluvião & a*lu*vi-ão \xmark & a*lu*vi*ão \cmark \\
amiúde & a*mi-ú*de \xmark & a*mi*ú*de \cmark \\
amoníaco & a*mo*ní-a*co \xmark & a*mo*ní*a*co \cmark \\
antagônico & an*ta-gô*ni*co \xmark & an*ta*gô*ni*co \cmark \\
antiquíssimo & an*ti-quís*si*mo \xmark & an*ti*quís*si*mo \cmark \\
babuíno & ba*bu-í*no \xmark & ba*bu*í*no \cmark \\
bahamense & ba-ha*men*se \xmark & ba-ha*men*se \xmark \\
barômetro & ba-rô*me*tro \xmark & ba*rô*me*tro \cmark \\
bibelô & bi*be-lô \xmark & bi*be*lô \cmark \\
biótipo & bi-ó*ti*po \xmark & bi*ó*ti*po \cmark \\
bisavô & bi*sa-vô \xmark & bi*sa*vô \cmark \\
bocaiuva & bo*cai-u*va \xmark & bo*cai-u*va \xmark \\
borderô & bor*de-rô \xmark & bor*de*rô \cmark \\
brechtiano & bre.ch*ti*a*no \xmark & bre.ch*ti*a*no \xmark \\
cariótipo & ca*ri-ó*ti*po \xmark & ca*ri*ó*ti*po \cmark \\
chororô & cho*ro-rô \xmark & cho*ro*rô \cmark \\
copaíba & co*pa-í*ba \xmark & co*pa*í*ba \cmark \\
czarismo & c.za*ris*mo \xmark & cza*ris*mo \cmark \\
darwinista & dar-wi*nis*ta \xmark & dar-wi*nis*ta \xmark \\
decaída & de*ca-í*da \xmark & de*ca*í*da \cmark \\
diálise & di-á*li*se \xmark & di*á*li*se \cmark \\
diástole & di-ás*to*le \xmark & di*ás*to*le \cmark \\
esquálido & es-quá*li*do \xmark & es*quá*li*do \cmark \\
esvair & es*va-ir \xmark & es*va*ir \cmark \\
farisaísmo & fa*ri*sa-ís*mo \xmark & fa*ri*sa*ís*mo \cmark \\
fiduciário & fi*du*ci-á*ri*o \xmark & fi*du*ci*á*ri*o \cmark \\
filarmônico & fi*lar-mô*ni*co \xmark & fi*lar*mô*ni*co \cmark \\
financiável & fi*nan*ci-á*vel \xmark & fi*nan*ci*á*vel \cmark \\
fruir & fru-ir \xmark & fru*ir \cmark \\
fuzuê & fu*zu-ê \xmark & fu*zu*ê \cmark \\
geômetra & ge-ô*me*tra \xmark & ge*ô*me*tra \cmark \\
gnose & g.no*se \xmark & gno*se \cmark \\
jabô & ja-bô \xmark & ja*bô \cmark \\
janaúba & ja*na-ú*ba \xmark & ja*na*ú*ba \cmark \\
lusíada & lu*sí-a*da \xmark & lu*sí*a*da \cmark \\
maçônico & ma-çô*ni*co \xmark & ma*çô*ni*co \cmark \\
macrobiótico & ma*cro*bi-ó*ti*co \xmark & ma*cro*bi*ó*ti*co \cmark \\
mafuá & ma*fu-á \xmark & ma*fu*á \cmark \\
manômetro & ma-nô*me*tro \xmark & ma*nô*me*tro \cmark \\
mediúnico & me*di-ú*ni*co \xmark & me*di*ú*ni*co \cmark \\
microrregião & mi*cror*re*gi-ão \xmark & mi*cror*re*gi*ão \cmark \\
neoplatônico & ne*o*pla-tô*ni*co \xmark & ne*o*pla*tô*ni*co \cmark \\
patchuli & pat*chu*li \cmark & pat-chu*li \xmark \\
pecuário & pe*cu-á*ri*o \xmark & pe*cu*á*ri*o \cmark \\
psicolinguista & p.si*co*lin*guis*ta \xmark & psi*co*lin*guis*ta \cmark \\
psicolinguística & p.si*co*lin*guís*ti*ca \xmark & psi*co*lin*guís*ti*ca \cmark \\
psicomotor & p.si*co*mo*tor \xmark & psi*co*mo*tor \cmark \\
psicomotricista & p.si*co*mo*tri*cis*ta \xmark & psi*co*mo*tri*cis*ta \cmark \\
psicopatia & p.si*co*pa*ti*a \xmark & psi*co*pa*ti*a \cmark \\
psicopedagogo & p.si*co*pe*da*go*go \xmark & psi*co*pe*da*go*go \cmark \\
psicossomática & p.si*cos*so*má*ti*ca \xmark & psi*cos*so*má*ti*ca \cmark \\
reconstituinte & re*cons*ti*tu-in*te \xmark & re*cons*ti*tu-in*te \xmark \\
reincidir & re-in*ci*dir \xmark & re*in*ci*dir \cmark \\
saruê & sa*ru-ê \xmark & sa*ru*ê \cmark \\
subaquático & su*ba-quá*ti*co \xmark & su*ba*quá*ti*co \cmark \\
subliteratura & su.b-li*te*ra*tu*ra \xmark & sub*li*te*ra*tu*ra \cmark \\
subsidiário & sub*si*di-á*ri*o \xmark & sub*si*di*á*ri*o \cmark \\
substituível & subs*ti*tu-í*vel \xmark & subs*ti*tu*í*vel \cmark \\
teutônico & teu-tô*ni*co \xmark & teu*tô*ni*co \cmark \\
tmese & t.me*se \xmark & tme*se \cmark \\
toboágua & to*bo-á*gua \xmark & to*bo*á*gua \cmark \\
aldeão & al*de-ão \xmark & al*de*ão \cmark \\
amniocentese & am*ni*o*cen*te*se \cmark & a.m-ni*o*cen*te*se \xmark \\
anamnese & a*nam*ne*se \cmark & a*na.m-ne*se \xmark \\
anauê & a*nau-ê \xmark & a*nau*ê \cmark \\
antipatriótico & an*ti*pa*tri-ó*ti*co \xmark & an*ti*pa*tri*ó*ti*co \cmark \\
antônimo & an-tô*ni*mo \xmark & an*tô*ni*mo \cmark \\
antropônimo & an*tro-pô*ni*mo \xmark & an*tro*pô*ni*mo \cmark \\
aviário & a*vi-á*ri*o \xmark & a*vi*á*ri*o \cmark \\
babalaô & ba*ba*la-ô \xmark & ba*ba*la*ô \cmark \\
braúna & bra-ú*na \xmark & bra*ú*na \cmark \\
corruíra & cor*ru-í*ra \xmark & cor*ru*í*ra \cmark \\
corrupião & cor*ru*pi-ão \xmark & cor*ru*pi*ão \cmark \\
decaído & de*ca-í*do \xmark & de*ca*í*do \cmark \\
deificação & de-i*fi*ca*ção \xmark & de-i*fi*ca*ção \xmark \\
demiurgo & de*mi-ur*go \xmark & de*mi*ur*go \cmark \\
descair & des*ca-ir \xmark & des*ca*ir \cmark \\
desembainhar & de*sem*ba-i*nhar \xmark & de*sem*ba*i*nhar \cmark \\
diáfano & di-á*fa*no \xmark & di*á*fa*no \cmark \\
dicotômico & di*co-tô*mi*co \xmark & di*co*tô*mi*co \cmark \\
dodecafônico & do*de*ca-fô*ni*co \xmark & do*de*ca*fô*ni*co \cmark \\
ensaístico & en*sa-ís*ti*co \xmark & en*sa*ís*ti*co \cmark \\
entusiástico & en*tu*si-ás*ti*co \xmark & en*tu*si*ás*ti*co \cmark \\
epônimo & e-pô*ni*mo \xmark & e*pô*ni*mo \cmark \\
espectrofotômetro & es*pec*tro*fo-tô*me*tro \xmark & es*pec*tro*fo*tô*me*tro \cmark \\
estatuária & es*ta*tu-á*ri*a \xmark & es*ta*tu*á*ri*a \cmark \\
faim & fa-im \xmark & fa-im \xmark \\
fitoquímica & fi*to-quí*mi*ca \xmark & fi*to*quí*mi*ca \cmark \\
formaldeído & for*mal*de-í*do \xmark & for*mal*de*í*do \cmark \\
fuinha & fu-i*nha \xmark & fu*i*nha \cmark \\
gabião & ga*bi-ão \xmark & ga*bi*ão \cmark \\
gauchada & ga-u*cha*da \xmark & ga-u*cha*da \xmark \\
gauchismo & ga-u*chis*mo \xmark & ga-u*chis*mo \xmark \\
geriátrico & ge*ri-á*tri*co \xmark & ge*ri*á*tri*co \cmark \\
gipsita & gip*si*ta \cmark & gip-si*ta \xmark \\
guião & gui-ão \xmark & gui*ão \cmark \\
ilíaco & i*lí-a*co \xmark & i*lí*a*co \cmark \\
iniciático & i*ni*ci-á*ti*co \xmark & i*ni*ci*á*ti*co \cmark \\
itapuá & i*ta*pu-á \xmark & i*ta*pu*á \cmark \\
japuí & ja*pu-í \xmark & ja*pu*í \cmark \\
jesuítico & je*su-í*ti*co \xmark & je*su*í*ti*co \cmark \\
lamaísmo & la*ma-ís*mo \xmark & la*ma*ís*mo \cmark \\
mantô & man-tô \xmark & man*tô \cmark \\
metapsicologia & me*tap*si*co*lo*gi*a \cmark & me*tap-si*co*lo*gi*a \xmark \\
mitocôndria & mi*to-côn*dri*a \xmark & mi*to*côn*dri*a \cmark \\
miudeza & mi-u*de*za \xmark & mi-u*de*za \xmark \\
monomaníaco & mo*no*ma*ní-a*co \xmark & mo*no*ma*ní*a*co \cmark \\
museólogo & mu*se-ó*lo*go \xmark & mu*se*ó*lo*go \cmark \\
ninfomaníaca & nin*fo*ma*ní-a*ca \xmark & nin*fo*ma*ní*a*ca \cmark \\
nobiliárquico & no*bi*li-ár*qui*co \xmark & no*bi*li*ár*qui*co \cmark \\
odômetro & o-dô*me*tro \xmark & o*dô*me*tro \cmark \\
orgiástico & or*gi-ás*ti*co \xmark & or*gi*ás*ti*co \cmark \\
painço & pa-in*ço \xmark & pa-in*ço \xmark \\
pantagruélico & pan*ta*gru-é*li*co \xmark & pan*ta*gru*é*li*co \cmark \\
parquímetro & par-quí*me*tro \xmark & par*quí*me*tro \cmark \\
pixaim & pi*xa-im \xmark & pi*xa-im \xmark \\
pneumática & p.neu*má*ti*ca \xmark & pneu*má*ti*ca \cmark \\
pneumático & p.neu*má*ti*co \xmark & pneu*má*ti*co \cmark \\
preá & pre-á \xmark & pre*á \cmark \\
priápico & pri-á*pi*co \xmark & pri*á*pi*co \cmark \\
psicopedagógico & p.si*co*pe*da*gó*gi*co \xmark & psi*co*pe*da*gó*gi*co \cmark \\
psicossomático & p.si*cos*so*má*ti*co \xmark & psi*cos*so*má*ti*co \cmark \\
psicotrópico & p.si*co*tró*pi*co \xmark & psi*co*tró*pi*co \cmark \\
pterossauro & p.te*ros*sau*ro \xmark & pte*ros*sau*ro \cmark \\
quilohertz & qui*lo-hertz \xmark & qui*lo-hertz \xmark \\
recôndito & re-côn*di*to \xmark & re*côn*di*to \cmark \\
reimplantação & re-im*plan*ta*ção \xmark & re*im*plan*ta*ção \cmark \\
reincorporar & re-in*cor*po*rar \xmark & re*in*cor*po*rar \cmark \\
reingressar & re-in*gres*sar \xmark & re*in*gres*sar \cmark \\
reinvestir & re-in*ves*tir \xmark & re*in*ves*tir \cmark \\
restituível & res*ti*tu-í*vel \xmark & res*ti*tu*í*vel \cmark \\
retrair & re*tra-ir \xmark & re*tra*ir \cmark \\
rodamoinho & ro*da*mo-i*nho \xmark & ro*da*mo*i*nho \cmark \\
roído & ro-í*do \xmark & ro*í*do \cmark \\
ruão & ru-ão \xmark & ru*ão \cmark \\
salomônico & sa*lo-mô*ni*co \xmark & sa*lo*mô*ni*co \cmark \\
sardônico & sar-dô*ni*co \xmark & sar*dô*ni*co \cmark \\
semiólogo & se*mi-ó*lo*go \xmark & se*mi*ó*lo*go \cmark \\
solipsismo & so*lip*sis*mo \cmark & so*lip-sis*mo \xmark \\
sumaúma & su*ma-ú*ma \xmark & su*ma*ú*ma \cmark \\
tataravô & ta*ta*ra-vô \xmark & ta*ta*ra*vô \cmark \\
termoquímica & ter*mo-quí*mi*ca \xmark & ter*mo*quí*mi*ca \cmark \\
topônimo & to-pô*ni*mo \xmark & to*pô*ni*mo \cmark \\
toxicômano & to*xi-cô*ma*no \xmark & to*xi*cô*ma*no \cmark \\
trisavô & tri*sa-vô \xmark & tri*sa*vô \cmark \\
triunvirato & tri-un*vi*ra*to \xmark & tri*un*vi*ra*to \cmark \\
voyeurístico & voy-eu*rís*ti*co \xmark & voy-eu*rís*ti*co \xmark \\
xintoísmo & xin*to-ís*mo \xmark & xin*to*ís*mo \cmark \\
absenteísta & ab*sen*te-ís*ta \xmark & ab*sen*te*ís*ta \cmark \\
aeroviário & a*e*ro*vi-á*ri*o \xmark & a*e*ro*vi*á*ri*o \cmark \\
afluir & a*flu-ir \xmark & a*flu*ir \cmark \\
agroquímico & a*gro-quí*mi*co \xmark & a*gro*quí*mi*co \cmark \\
aguaí & a*gua-í \xmark & a*gua*í \cmark \\
alquímico & al-quí*mi*co \xmark & al*quí*mi*co \cmark \\
amnesia & am*ne*si*a \cmark & a.m-ne*si*a \xmark \\
amnésico & am*né*si*co \cmark & a.m-né*si*co \xmark \\
anafrodisíaco & a*na*fro*di*sí-a*co \xmark & a*na*fro*di*sí*a*co \cmark \\
antialcoólico & an*ti*al*co-ó*li*co \xmark & an*ti*al*co*ó*li*co \cmark \\
antinômico & an*ti-nô*mi*co \xmark & an*ti*nô*mi*co \cmark \\
anuir & a*nu-ir \xmark & a*nu*ir \cmark \\
arapuá & a*ra*pu-á \xmark & a*ra*pu*á \cmark \\
aríete & a*rí-e*te \xmark & a*rí-e*te \xmark \\
associável & as*so*ci-á*vel \xmark & as*so*ci*á*vel \cmark \\
atribuível & a*tri*bu-í*vel \xmark & a*tri*bu*í*vel \cmark \\
babilônico & ba*bi-lô*ni*co \xmark & ba*bi*lô*ni*co \cmark \\
balaustrada & ba*la-us*tra*da \xmark & ba*la-us*tra*da \xmark \\
beócio & be-ó*ci*o \xmark & be*ó*ci*o \cmark \\
biófilo & bi-ó*fi*lo \xmark & bi*ó*fi*lo \cmark \\
biunívoco & bi-u*ní*vo*co \xmark & bi*u*ní*vo*co \cmark \\
boião & boi-ão \xmark & boi*ão \cmark \\
boiuna & boi-u*na \xmark & boi*u*na \cmark \\
butiá & bu*ti-á \xmark & bu*ti*á \cmark \\
caingangue & ca-in*gan*gue \xmark & ca-in*gan*gue \xmark \\
carnaíba & car*na-í*ba \xmark & car*na*í*ba \cmark \\
caúna & ca-ú*na \xmark & ca*ú*na \cmark \\
ciática & ci-á*ti*ca \xmark & ci*á*ti*ca \cmark \\
clepsidra & clep*si*dra \cmark & clep-si*dra \xmark \\
codeína & co*de-í*na \xmark & co*de*í*na \cmark \\
conciliábulo & con*ci*li-á*bu*lo \xmark & con*ci*li*á*bu*lo \cmark \\
conciliável & con*ci*li-á*vel \xmark & con*ci*li*á*vel \cmark \\
condoído & con*do-í*do \xmark & con*do*í*do \cmark \\
confluir & con*flu-ir \xmark & con*flu*ir \cmark \\
congruência & con*gru-ên*ci*a \xmark & con*gru*ên*ci*a \cmark \\
crapô & cra-pô \xmark & cra*pô \cmark \\
criptônimo & crip-tô*ni*mo \xmark & crip*tô*ni*mo \cmark \\
deão & de-ão \xmark & de*ão \cmark \\
decacampeão & de*ca*cam*pe-ão \xmark & de*ca*cam*pe*ão \cmark \\
demiúrgico & de*mi-úr*gi*co \xmark & de*mi*úr*gi*co \cmark \\
depreciável & de*pre*ci-á*vel \xmark & de*pre*ci*á*vel \cmark \\
descaída & des*ca-í*da \xmark & des*ca*í*da \cmark \\
dzeta & d.ze*ta \xmark & d.ze*ta \xmark \\
elefantíase & e*le*fan*tí-a*se \xmark & e*le*fan*tí*a*se \cmark \\
eletroímã & e*le*tro-í*mã \xmark & e*le*tro*í*mã \cmark \\
eólico & e-ó*li*co \xmark & e*ó*li*co \cmark \\
eólio & e-ó*li*o \xmark & e*ó*li*o \cmark \\
epifenômeno & e*pi*fe-nô*me*no \xmark & e*pi*fe*nô*me*no \cmark \\
escarabeídeo & es*ca*ra*be-í*de*o \xmark & es*ca*ra*be*í*de*o \cmark \\
espadaúdo & es*pa*da-ú*do \xmark & es*pa*da*ú*do \cmark \\
espeleólogo & es*pe*le-ó*lo*go \xmark & es*pe*le*ó*lo*go \cmark \\
faiscante & fa-is*can*te \xmark & fa-is*can*te \xmark \\
feiura & fei-u*ra \xmark & fei*u*ra \cmark \\
fotômetro & fo-tô*me*tro \xmark & fo*tô*me*tro \cmark \\
franqueável & fran*que-á*vel \xmark & fran*que*á*vel \cmark \\
gastrointestinal & gas*tro-in*tes*ti*nal \xmark & gas*tro*in*tes*ti*nal \cmark \\
gauchar & ga-u*char \xmark & ga-u*char \xmark \\
gnosticismo & g.nos*ti*cis*mo \xmark & gnos*ti*cis*mo \cmark \\
gnóstico & g.nós*ti*co \xmark & gnós*ti*co \cmark \\
gnu & g.nu \xmark & g.nu \xmark \\
grafomaníaco & gra*fo*ma*ní-a*co \xmark & gra*fo*ma*ní*a*co \cmark \\
grafômano & gra-fô*ma*no \xmark & gra*fô*ma*no \cmark \\
grapiúna & gra*pi-ú*na \xmark & gra*pi*ú*na \cmark \\
heterônimo & he*te-rô*ni*mo \xmark & he*te*rô*ni*mo \cmark \\
hexacampeão & he*xa*cam*pe-ão \xmark & he*xa*cam*pe*ão \cmark \\
hinduísta & hin*du-ís*ta \xmark & hin*du*ís*ta \cmark \\
holonômico & ho*lo-nô*mi*co \xmark & ho*lo*nô*mi*co \cmark \\
homofônico & ho*mo-fô*ni*co \xmark & ho*mo*fô*ni*co \cmark \\
ibijaú & i*bi*ja-ú \xmark & i*bi*ja*ú \cmark \\
idiótico & i*di-ó*ti*co \xmark & i*di*ó*ti*co \cmark \\
imbuir & im*bu-ir \xmark & im*bu*ir \cmark \\
inclinômetro & in*cli-nô*me*tro \xmark & in*cli*nô*me*tro \cmark \\
irreconciliável & ir*re*con*ci*li-á*vel \xmark & ir*re*con*ci*li*á*vel \cmark \\
irreligião & ir*re*li*gi-ão \xmark & ir*re*li*gi*ão \cmark \\
irrenunciável & ir*re*nun*ci-á*vel \xmark & ir*re*nun*ci*á*vel \cmark \\
isquêmico & is-quê*mi*co \xmark & is*quê*mi*co \cmark \\
itapiúna & i*ta*pi-ú*na \xmark & i*ta*pi*ú*na \cmark \\
juá & ju-á \xmark & ju*á \cmark \\
lamaísta & la*ma-ís*ta \xmark & la*ma*ís*ta \cmark \\
luteína & lu*te-í*na \xmark & lu*te*í*na \cmark \\
macrorregião & ma*cror*re*gi-ão \xmark & ma*cror*re*gi*ão \cmark \\
mandrião & man*dri-ão \xmark & man*dri*ão \cmark \\
masdeísmo & mas*de-ís*mo \xmark & mas*de*ís*mo \cmark \\
maué & mau-é \xmark & mau*é \cmark \\
mediático & me*di-á*ti*co \xmark & me*di*á*ti*co \cmark \\
melômano & me-lô*ma*no \xmark & me*lô*ma*no \cmark \\
mnemônica & m.ne-mô*ni*ca \xmark & mne*mô*ni*ca \cmark \\
moinha & mo-i*nha \xmark & mo*i*nha \cmark \\
monômero & mo-nô*me*ro \xmark & mo*nô*me*ro \cmark \\
monoquíni & mo*no-quí*ni \xmark & mo*no*quí*ni \cmark \\
monoteísta & mo*no*te-ís*ta \xmark & mo*no*te*ís*ta \cmark \\
mortuárias & mor*tu-á*ri*as \xmark & mor*tu*á*ri*as \cmark \\
mucuim & mu*cu-im \xmark & mu*cu-im \xmark \\
negligenciável & ne*gli*gen*ci-á*vel \xmark & ne*gli*gen*ci*á*vel \cmark \\
neuropsiquiatria & neu*rop*si*qui*a*tri*a \cmark & neu*rop-si*qui*a*tri*a \xmark \\
oboísta & o*bo-ís*ta \xmark & o*bo*ís*ta \cmark \\
ofidiário & o*fi*di-á*ri*o \xmark & o*fi*di*á*ri*o \cmark \\
oleína & o*le-í*na \xmark & o*le*í*na \cmark \\
opiáceo & o*pi-á*ce*o \xmark & o*pi*á*ce*o \cmark \\
pancreático & pan*cre-á*ti*co \xmark & pan*cre*á*ti*co \cmark \\
panô & pa-nô \xmark & pa*nô \cmark \\
parquê & par-quê \xmark & par*quê \cmark \\
parvoíce & par*vo-í*ce \xmark & par*vo*í*ce \cmark \\
patenteável & pa*ten*te-á*vel \xmark & pa*ten*te*á*vel \cmark \\
peã & pe-ã \xmark & pe*ã \cmark \\
periósteo & pe*ri-ós*te*o \xmark & pe*ri*ós*te*o \cmark \\
picuá & pi*cu-á \xmark & pi*cu*á \cmark \\
piquê & pi-quê \xmark & pi*quê \cmark \\
piromaníaco & pi*ro*ma*ní-a*co \xmark & pi*ro*ma*ní*a*co \cmark \\
piruá & pi*ru-á \xmark & pi*ru*á \cmark \\
piúria & pi-ú*ri*a \xmark & pi*ú*ri*a \cmark \\
plagiário & pla*gi-á*ri*o \xmark & pla*gi*á*ri*o \cmark \\
plebeísmo & ple*be-ís*mo \xmark & ple*be*ís*mo \cmark \\
plenipotenciário & ple*ni*po*ten*ci-á*ri*o \xmark & ple*ni*po*ten*ci*á*ri*o \cmark \\
pneumatologia & p.neu*ma*to*lo*gi*a \xmark & pneu*ma*to*lo*gi*a \cmark \\
pneumônico & p.neu-mô*ni*co \xmark & pneu*mô*ni*co \cmark \\
polifônico & po*li-fô*ni*co \xmark & po*li*fô*ni*co \cmark \\
politeísmo & po*li*te-ís*mo \xmark & po*li*te*ís*mo \cmark \\
politeísta & po*li*te-ís*ta \xmark & po*li*te*ís*ta \cmark \\
politiquês & po*li*ti-quês \xmark & po*li*ti*quês \cmark \\
procaína & pro*ca-í*na \xmark & pro*ca*í*na \cmark \\
pronunciável & pro*nun*ci-á*vel \xmark & pro*nun*ci*á*vel \cmark \\
pseudociência & p.seu*do*ci*ên*ci*a \xmark & pseu*do*ci*ên*ci*a \cmark \\
psicofísico & p.si*co*fí*si*co \xmark & psi*co*fí*si*co \cmark \\
psicologizar & p.si*co*lo*gi*zar \xmark & psi*co*lo*gi*zar \cmark \\
psicometria & p.si*co*me*tri*a \xmark & psi*co*me*tri*a \cmark \\
psicomotricidade & p.si*co*mo*tri*ci*da*de \xmark & psi*co*mo*tri*ci*da*de \cmark \\
psicopatológico & p.si*co*pa*to*ló*gi*co \xmark & psi*co*pa*to*ló*gi*co \cmark \\
psicoprofilaxia & p.si*co*pro*fi*la*xi*a \xmark & psi*co*pro*fi*la*xi*a \cmark \\
psicossexual & p.si*cos*se*xu*al \xmark & psi*cos*se*xu*al \cmark \\
psicoterapêutico & p.si*co*te*ra*pêu*ti*co \xmark & psi*co*te*ra*pêu*ti*co \cmark \\
psiquê & p.si-quê \xmark & psi*quê \cmark \\
psitacismo & p.si*ta*cis*mo \xmark & psi*ta*cis*mo \cmark \\
psoríase & p.so*rí-a*se \xmark & p.so*rí*a*se \xmark \\
ptose & p.to*se \xmark & pto*se \cmark \\
puído & pu-í*do \xmark & pu*í*do \cmark \\
putrião & pu*tri-ão \xmark & pu*tri*ão \cmark \\
questiúncula & ques*ti-ún*cu*la \xmark & ques*ti*ún*cu*la \cmark \\
reimportar & re-im*por*tar \xmark & re*im*por*tar \cmark \\
reimpressão & re-im*pres*são \xmark & re*im*pres*são \cmark \\
reinscrever & re-ins*cre*ver \xmark & re*ins*cre*ver \cmark \\
reinserir & re-in*se*rir \xmark & re*in*se*rir \cmark \\
remediável & re*me*di-á*vel \xmark & re*me*di*á*vel \cmark \\
rubiácea & ru*bi-á*ce*a \xmark & ru*bi*á*ce*a \cmark \\
ruinoso & ru-i*no*so \xmark & ru*i*no*so \cmark \\
sainha & sa-i*nha \xmark & sa*i*nha \cmark \\
sardônica & sar-dô*ni*ca \xmark & sar*dô*ni*ca \cmark \\
satiríase & sa*ti*rí-a*se \xmark & sa*ti*rí*a*se \cmark \\
setentrião & se*ten*tri-ão \xmark & se*ten*tri*ão \cmark \\
sievert & si.e*vert \xmark & si.e*vert \xmark \\
sismômetro & sis-mô*me*tro \xmark & sis*mô*me*tro \cmark \\
solipsista & so*lip*sis*ta \cmark & so*lip-sis*ta \xmark \\
suaíle & su*a-í*le \xmark & su*a*í*le \cmark \\
sublevado & su.b-le*va*do \xmark & sub*le*va*do \cmark \\
sublocar & su.b-lo*car \xmark & sub*lo*car \cmark \\
sublocatário & su.b-lo*ca*tá*ri*o \xmark & sub*lo*ca*tá*ri*o \cmark \\
subsônico & sub-sô*ni*co \xmark & sub*sô*ni*co \cmark \\
sucuriú & su*cu*ri-ú \xmark & su*cu*ri*ú \cmark \\
suingar & su-in*gar \xmark & su-in*gar \xmark \\
tacômetro & ta-cô*me*tro \xmark & ta*cô*me*tro \cmark \\
taiuiá & tai-ui-á \xmark & tai-ui*á \xmark \\
taiwanês & tai-wa*nês \xmark & tai-wa*nês \xmark \\
talião & ta*li-ão \xmark & ta*li*ão \cmark \\
tchecoslovaco & t.che*cos*lo*va*co \xmark & tche*cos*lo*va*co \cmark \\
teísta & te-ís*ta \xmark & te*ís*ta \cmark \\
teiú & tei-ú \xmark & tei*ú \cmark \\
telômero & te-lô*me*ro \xmark & te*lô*me*ro \cmark \\
teníase & te*ní-a*se \xmark & te*ní*a*se \cmark \\
terciário & ter*ci-á*ri*o \xmark & ter*ci*á*ri*o \cmark \\
torreão & tor*re-ão \xmark & tor*re*ão \cmark \\
transeunte & tran*se-un*te \xmark & tran*se-un*te \xmark \\
triádico & tri-á*di*co \xmark & tri*á*di*co \cmark \\
tripanossomíase & tri*pa*nos*so*mí-a*se \xmark & tri*pa*nos*so*mí*a*se \cmark \\
triunfador & tri-un*fa*dor \xmark & tri*un*fa*dor \cmark \\
truísmo & tru-ís*mo \xmark & tru*ís*mo \cmark \\
tuim & tu-im \xmark & tu-im \xmark \\
tuiuiú & tui-ui-ú \xmark & tui-ui*ú \xmark \\
tumultuário & tu*mul*tu-á*ri*o \xmark & tu*mul*tu*á*ri*o \cmark \\
tzarista & t.za*ris*ta \xmark & tza*ris*ta \cmark \\
vietcongue & vi*et*con*gue \cmark & vi*et-con*gue \xmark \\
vitriólico & vi*tri-ó*li*co \xmark & vi*tri*ó*li*co \cmark \\
vitríolo & vi*trí-o*lo \xmark & vi*trí*o*lo \cmark \\
xilocaína & xi*lo*ca-í*na \xmark & xi*lo*ca*í*na \cmark \\
abluir & a*blu-ir \xmark & a*blu*ir \cmark \\
balaústre & ba*la-ús*tre \xmark & ba*la*ús*tre \cmark \\
cabriúva & ca*bri-ú*va \xmark & ca*bri*ú*va \cmark \\
daguerreótipo & da*guer*re-ó*ti*po \xmark & da*guer*re*ó*ti*po \cmark \\
daltônico & dal-tô*ni*co \xmark & dal*tô*ni*co \cmark \\
ecônomo & e-cô*no*mo \xmark & e*cô*no*mo \cmark \\
egoístico & e*go-ís*ti*co \xmark & e*go*ís*ti*co \cmark \\
eletrocardiógrafo & e*le*tro*car*di-ó*gra*fo \xmark & e*le*tro*car*di*ó*gra*fo \cmark \\
eletroquímica & e*le*tro-quí*mi*ca \xmark & e*le*tro*quí*mi*ca \cmark \\
eletroquímico & e*le*tro-quí*mi*co \xmark & e*le*tro*quí*mi*co \cmark \\
embainhar & em*ba-i*nhar \xmark & em*ba*i*nhar \cmark \\
faiscar & fa-is*car \xmark & fa-is*car \xmark \\
faúlha & fa-ú*lha \xmark & fa*ú*lha \cmark \\
galvanômetro & gal*va-nô*me*tro \xmark & gal*va*nô*me*tro \cmark \\
hagiógrafo & ha*gi-ó*gra*fo \xmark & ha*gi*ó*gra*fo \cmark \\
hebraísmo & he*bra-ís*mo \xmark & he*bra*ís*mo \cmark \\
hebraísta & he*bra-ís*ta \xmark & he*bra*ís*ta \cmark \\
hipertônico & hi*per-tô*ni*co \xmark & hi*per*tô*ni*co \cmark \\
historiógrafo & his*to*ri-ó*gra*fo \xmark & his*to*ri*ó*gra*fo \cmark \\
histrião & his*tri-ão \xmark & his*tri*ão \cmark \\
jesuitismo & je*su-i*tis*mo \xmark & je*su*i*tis*mo \cmark \\
macedônico & ma*ce-dô*ni*co \xmark & ma*ce*dô*ni*co \cmark \\
ninfomaníaco & nin*fo*ma*ní-a*co \xmark & nin*fo*ma*ní*a*co \cmark \\
paquímetro & pa-quí*me*tro \xmark & pa*quí*me*tro \cmark \\
tabuinha & ta*bu-i*nha \xmark & ta*bu*i*nha \cmark \\
taquígrafo & ta-quí*gra*fo \xmark & ta*quí*gra*fo \cmark \\
taquímetro & ta-quí*me*tro \xmark & ta*quí*me*tro \cmark \\
tectônico & tec-tô*ni*co \xmark & tec*tô*ni*co \cmark \\
xintoísta & xin*to-ís*ta \xmark & xin*to*ís*ta \cmark \\
abiótica & a*bi-ó*ti*ca \xmark & a*bi*ó*ti*ca \cmark \\
abiótico & a*bi-ó*ti*co \xmark & a*bi*ó*ti*co \cmark \\
abraâmico & a*bra-â*mi*co \xmark & a*bra*â*mi*co \cmark \\
abstraído & abs*tra-í*do \xmark & abs*tra*í*do \cmark \\
acauã & a*cau-ã \xmark & a*cau*ã \cmark \\
acelerômetro & a*ce*le-rô*me*tro \xmark & a*ce*le*rô*me*tro \cmark \\
acetaldeído & a*ce*tal*de-í*do \xmark & a*ce*tal*de*í*do \cmark \\
acroleína & a*cro*le-í*na \xmark & a*cro*le*í*na \cmark \\
adônis & a-dô*nis \xmark & a*dô*nis \cmark \\
ainsa & a-in*sa \xmark & a-in*sa \xmark \\
aiquidô & ai*qui-dô \xmark & ai*qui*dô \cmark \\
alcíone & al*cí-o*ne \xmark & al*cí*o*ne \cmark \\
aldeído & al*de-í*do \xmark & al*de*í*do \cmark \\
aleúte & a*le-ú*te \xmark & a*le*ú*te \cmark \\
aliá & a*li-á \xmark & a*li*á \cmark \\
almóada & al*mó-a*da \xmark & al*mó-a*da \xmark \\
aloé & a*lo-é \xmark & a*lo*é \cmark \\
aloés & a*lo-és \xmark & a*lo*és \cmark \\
aluá & a*lu-á \xmark & a*lu*á \cmark \\
alvéolo & al*vé-o*lo \xmark & al*vé*o*lo \cmark \\
amebíase & a*me*bí-a*se \xmark & a*me*bí*a*se \cmark \\
âmnio & âm*ni*o \cmark & â.m-ni*o \xmark \\
ancilostomíase & an*ci*los*to*mí-a*se \xmark & an*ci*los*to*mí*a*se \cmark \\
anemômetro & a*ne-mô*me*tro \xmark & a*ne*mô*me*tro \cmark \\
anfião & an*fi-ão \xmark & an*fi*ão \cmark \\
anfictião & an*fic*ti-ão \xmark & an*fic*ti*ão \cmark \\
anião & a*ni-ão \xmark & a*ni*ão \cmark \\
aórtico & a-ór*ti*co \xmark & a*ór*ti*co \cmark \\
apuí & a*pu-í \xmark & a*pu*í \cmark \\
aquífero & a-quí*fe*ro \xmark & a*quí*fe*ro \cmark \\
areão & a*re-ão \xmark & a*re*ão \cmark \\
areópago & a*re-ó*pa*go \xmark & a*re*ó*pa*go \cmark \\
arquidiácono & ar*qui*di-á*co*no \xmark & ar*qui*di*á*co*no \cmark \\
arteríola & ar*te*rí-o*la \xmark & ar*te*rí*o*la \cmark \\
assiriólogo & as*si*ri-ó*lo*go \xmark & as*si*ri*ó*lo*go \cmark \\
astroquímica & as*tro-quí*mi*ca \xmark & as*tro*quí*mi*ca \cmark \\
ateísta & a*te-ís*ta \xmark & a*te*ís*ta \cmark \\
autoimunidade & au*to-i*mu*ni*da*de \xmark & au*to-i*mu*ni*da*de \xmark \\
autônimo & au-tô*ni*mo \xmark & au*tô*ni*mo \cmark \\
autonômico & au*to-nô*mi*co \xmark & au*to*nô*mi*co \cmark \\
averroísmo & a*ver*ro-ís*mo \xmark & a*ver*ro*ís*mo \cmark \\
bacteriófago & bac*te*ri-ó*fa*go \xmark & bac*te*ri*ó*fa*go \cmark \\
baleárico & ba*le-á*ri*co \xmark & ba*le*á*ri*co \cmark \\
banjoísta & ban*jo-ís*ta \xmark & ban*jo*ís*ta \cmark \\
batuíra & ba*tu-í*ra \xmark & ba*tu*í*ra \cmark \\
behaviorismo & be-ha*vi*o*ris*mo \xmark & be-ha*vi*o*ris*mo \xmark \\
benjoim & ben*jo-im \xmark & ben*jo-im \xmark \\
bibliógrafo & bi*bli-ó*gra*fo \xmark & bi*bli*ó*gra*fo \cmark \\
bilião & bi*li-ão \xmark & bi*li*ão \cmark \\
biótico & bi-ó*ti*co \xmark & bi*ó*ti*co \cmark \\
biótopo & bi-ó*to*po \xmark & bi*ó*to*po \cmark \\
biscainho & bis*ca-i*nho \xmark & bis*ca*i*nho \cmark \\
blastômero & blas-tô*me*ro \xmark & blas*tô*me*ro \cmark \\
boé & bo-é \xmark & bo*é \cmark \\
bosníaco & bos*ní-a*co \xmark & bos*ní*a*co \cmark \\
braquiópode & bra*qui-ó*po*de \xmark & bra*qui*ó*po*de \cmark \\
bué & bu-é \xmark & bu*é \cmark \\
cafarnaum & ca*far*na-um \xmark & ca*far*na-um \xmark \\
cajuína & ca*ju-í*na \xmark & ca*ju*í*na \cmark \\
camião & ca*mi-ão \xmark & ca*mi*ão \cmark \\
candidíase & can*di*dí-a*se \xmark & can*di*dí*a*se \cmark \\
canoísta & ca*no-ís*ta \xmark & ca*no*ís*ta \cmark \\
carnaubal & car*na-u*bal \xmark & car*na-u*bal \xmark \\
caroá & ca*ro-á \xmark & ca*ro*á \cmark \\
caseína & ca*se-í*na \xmark & ca*se*í*na \cmark \\
catequético & ca*te-qué*ti*co \xmark & ca*te*qué*ti*co \cmark \\
catião & ca*ti-ão \xmark & ca*ti*ão \cmark \\
cauã & cau-ã \xmark & cau*ã \cmark \\
celíaco & ce*lí-a*co \xmark & ce*lí*a*co \cmark \\
cnidário & c.ni*dá*ri*o \xmark & c.ni*dá*ri*o \xmark \\
coimbrão & co-im*brão \xmark & co*im*brão \cmark \\
coleóptero & co*le-óp*te*ro \xmark & co*le*óp*te*ro \cmark \\
contraindicação & con*tra-in*di*ca*ção \xmark & con*tra*in*di*ca*ção \cmark \\
contribuidor & con*tri*bu-i*dor \xmark & con*tri*bu*i*dor \cmark \\
coriáceo & co*ri-á*ce*o \xmark & co*ri*á*ce*o \cmark \\
curião & cu*ri-ão \xmark & cu*ri*ão \cmark \\
curiúva & cu*ri-ú*va \xmark & cu*ri*ú*va \cmark \\
cuxiú & cu*xi-ú \xmark & cu*xi*ú \cmark \\
decurião & de*cu*ri-ão \xmark & de*cu*ri*ão \cmark \\
deiscente & de-is*cen*te \xmark & de-is*cen*te \xmark \\
deísmo & de-ís*mo \xmark & de*ís*mo \cmark \\
díade & dí-a*de \xmark & dí*a*de \cmark \\
diádico & di-á*di*co \xmark & di*á*di*co \cmark \\
diádoco & di-á*do*co \xmark & di*á*do*co \cmark \\
diáfise & di-á*fi*se \xmark & di*á*fi*se \cmark \\
diatômico & di*a-tô*mi*co \xmark & di*a*tô*mi*co \cmark \\
diérese & di-é*re*se \xmark & di*é*re*se \cmark \\
diferenciável & di*fe*ren*ci-á*vel \xmark & di*fe*ren*ci*á*vel \cmark \\
difluência & di*flu-ên*ci*a \xmark & di*flu*ên*ci*a \cmark \\
díodo & dí-o*do \xmark & dí*o*do \cmark \\
domiciliário & do*mi*ci*li-á*ri*o \xmark & do*mi*ci*li*á*ri*o \cmark \\
dríade & drí-a*de \xmark & drí*a*de \cmark \\
elastômero & e*las-tô*me*ro \xmark & e*las*tô*me*ro \cmark \\
eluição & e*lu-i*ção \xmark & e*lu*i*ção \cmark \\
éon & é-on \xmark & é*on \cmark \\
epicôndilo & e*pi-côn*di*lo \xmark & e*pi*côn*di*lo \cmark \\
épsilon & ép*si*lon \cmark & ép-si*lon \xmark \\
equidna & e*quid*na \cmark & e*qui.d*na \xmark \\
estatuário & es*ta*tu-á*ri*o \xmark & es*ta*tu*á*ri*o \cmark \\
esteárico & es*te-á*ri*co \xmark & es*te*á*ri*co \cmark \\
estereoquímica & es*te*re*o-quí*mi*ca \xmark & es*te*re*o*quí*mi*ca \cmark \\
etnônimo & et-nô*ni*mo \xmark & et*nô*ni*mo \cmark \\
eucariótico & eu*ca*ri-ó*ti*co \xmark & eu*ca*ri*ó*ti*co \cmark \\
eurasiático & eu*ra*si-á*ti*co \xmark & eu*ra*si*á*ti*co \cmark \\
europeísmo & eu*ro*pe-ís*mo \xmark & eu*ro*pe*ís*mo \cmark \\
europeísta & eu*ro*pe-ís*ta \xmark & eu*ro*pe*ís*ta \cmark \\
evangeliário & e*van*ge*li-á*ri*o \xmark & e*van*ge*li*á*ri*o \cmark \\
feroês & fe*ro-ês \xmark & fe*ro*ês \cmark \\
fiável & fi-á*vel \xmark & fi*á*vel \cmark \\
fisiólogo & fi*si-ó*lo*go \xmark & fi*si*ó*lo*go \cmark \\
fluídico & flu-í*di*co \xmark & flu-í*di*co \xmark \\
foliáceo & fo*li-á*ce*o \xmark & fo*li*á*ce*o \cmark \\
folíolo & fo*lí-o*lo \xmark & fo*lí*o*lo \cmark \\
fotoperíodo & fo*to*pe*rí-o*do \xmark & fo*to*pe*rí*o*do \cmark \\
fotoquímica & fo*to-quí*mi*ca \xmark & fo*to*quí*mi*ca \cmark \\
fotoquímico & fo*to-quí*mi*co \xmark & fo*to*quí*mi*co \cmark \\
friável & fri-á*vel \xmark & fri*á*vel \cmark \\
ftálico & f.tá*li*co \xmark & f.tá*li*co \xmark \\
fuá & fu-á \xmark & fu*á \cmark \\
genômico & ge-nô*mi*co \xmark & ge*nô*mi*co \cmark \\
genuinidade & ge*nu-i*ni*da*de \xmark & ge*nu*i*ni*da*de \cmark \\
geoquímica & ge*o-quí*mi*ca \xmark & ge*o*quí*mi*ca \cmark \\
geoquímico & ge*o-quí*mi*co \xmark & ge*o*quí*mi*co \cmark \\
geotectônica & ge*o*tec-tô*ni*ca \xmark & ge*o*tec*tô*ni*ca \cmark \\
gimnodesportivo & gim*no*des*por*ti*vo \cmark & gi.m-no*des*por*ti*vo \xmark \\
glaciário & gla*ci-á*ri*o \xmark & gla*ci*á*ri*o \cmark \\
glicoproteína & gli*co*pro*te-í*na \xmark & gli*co*pro*te*í*na \cmark \\
gnaisse & g.nais*se \xmark & g.nais*se \xmark \\
goês & go-ês \xmark & go*ês \cmark \\
graxaim & gra*xa-im \xmark & gra*xa-im \xmark \\
helíaco & he*lí-a*co \xmark & he*lí*a*co \cmark \\
henoteísmo & he*no*te-ís*mo \xmark & he*no*te*ís*mo \cmark \\
heptacampeão & hep*ta*cam*pe-ão \xmark & hep*ta*cam*pe*ão \cmark \\
heteroátomo & he*te*ro-á*to*mo \xmark & he*te*ro*á*to*mo \cmark \\
higiénico & hi*gi-é*ni*co \xmark & hi*gi*é*ni*co \cmark \\
hióideo & hi-ói*de*o \xmark & hi*ói*de*o \cmark \\
hipersônico & hi*per-sô*ni*co \xmark & hi*per*sô*ni*co \cmark \\
hipocôndrio & hi*po-côn*dri*o \xmark & hi*po*côn*dri*o \cmark \\
hipomaníaco & hi*po*ma*ní-a*co \xmark & hi*po*ma*ní*a*co \cmark \\
histoquímica & his*to-quí*mi*ca \xmark & his*to*quí*mi*ca \cmark \\
iá & i-á \xmark & i*á \cmark \\
ião & i-ão \xmark & i*ão \cmark \\
iatroquímica & i*a*tro-quí*mi*ca \xmark & i*a*tro*quí*mi*ca \cmark \\
icônico & i-cô*ni*co \xmark & i*cô*ni*co \cmark \\
ictiólogo & ic*ti-ó*lo*go \xmark & ic*ti*ó*lo*go \cmark \\
indeiscente & in*de-is*cen*te \xmark & in*de-is*cen*te \xmark \\
indemnização & in*dem*ni*za*ção \cmark & in*de.m-ni*za*ção \xmark \\
indemnizar & in*dem*ni*zar \cmark & in*de.m-ni*zar \xmark \\
instituidor & ins*ti*tu-i*dor \xmark & ins*ti*tu*i*dor \cmark \\
intercambiável & in*ter*cam*bi-á*vel \xmark & in*ter*cam*bi*á*vel \cmark \\
interferômetro & in*ter*fe-rô*me*tro \xmark & in*ter*fe*rô*me*tro \cmark \\
íon & í-on \xmark & í*on \cmark \\
ipsilateral & ip*si*la*te*ral \cmark & ip-si*la*te*ral \xmark \\
ípsilon & íp*si*lon \cmark & íp-si*lon \xmark \\
isômero & i-sô*me*ro \xmark & i*sô*me*ro \cmark \\
isotônico & i*so-tô*ni*co \xmark & i*so*tô*ni*co \cmark \\
itaúba & i*ta-ú*ba \xmark & i*ta*ú*ba \cmark \\
jandaíra & jan*da-í*ra \xmark & jan*da*í*ra \cmark \\
jaó & ja-ó \xmark & ja*ó \cmark \\
jauá & jau-á \xmark & jau*á \cmark \\
jihadista & ji-ha*dis*ta \xmark & ji-ha*dis*ta \xmark \\
joinvilense & jo-in*vi*len*se \xmark & jo-in*vi*len*se \xmark \\
jundiá & jun*di-á \xmark & jun*di*á \cmark \\
jutaí & ju*ta-í \xmark & ju*ta*í \cmark \\
kuwaitiano & ku-wai*ti*a*no \xmark & ku-wai*ti*a*no \xmark \\
lemna & lem*na \cmark & le.m-na \xmark \\
lemniscata & lem*nis*ca*ta \cmark & le.m-nis*ca*ta \xmark \\
lemnisco & lem*nis*co \cmark & le.m-nis*co \xmark \\
leônico & le-ô*ni*co \xmark & le*ô*ni*co \cmark \\
lidocaína & li*do*ca-í*na \xmark & li*do*ca*í*na \cmark \\
liechtensteinense & li*e.ch*tens*tei*nen*se \xmark & li*e.ch*tens*tei*nen*se \xmark \\
limnologia & lim*no*lo*gi*a \cmark & li.m-no*lo*gi*a \xmark \\
litíase & li*tí-a*se \xmark & li*tí*a*se \cmark \\
macaúba & ma*ca-ú*ba \xmark & ma*ca*ú*ba \cmark \\
magnetômetro & mag*ne-tô*me*tro \xmark & mag*ne*tô*me*tro \cmark \\
maís & ma-ís \xmark & ma*ís \cmark \\
malauiano & ma*lau-i*a*no \xmark & ma*lau-i*a*no \xmark \\
malônico & ma-lô*ni*co \xmark & ma*lô*ni*co \cmark \\
maruí & ma*ru-í \xmark & ma*ru*í \cmark \\
maruim & ma*ru-im \xmark & ma*ru-im \xmark \\
meã & me-ã \xmark & me*ã \cmark \\
meão & me-ão \xmark & me*ão \cmark \\
meiótico & mei-ó*ti*co \xmark & mei*ó*ti*co \cmark \\
microbiólogo & mi*cro*bi-ó*lo*go \xmark & mi*cro*bi*ó*lo*go \cmark \\
midríase & mi*drí-a*se \xmark & mi*drí*a*se \cmark \\
miíase & mi-í-a*se \xmark & mi*í*a*se \cmark \\
miliário & mi*li-á*ri*o \xmark & mi*li*á*ri*o \cmark \\
mnemônico & m.ne-mô*ni*co \xmark & mne*mô*ni*co \cmark \\
monofônico & mo*no-fô*ni*co \xmark & mo*no*fô*ni*co \cmark \\
moquém & mo-quém \xmark & mo*quém \cmark \\
morrião & mor*ri-ão \xmark & mor*ri*ão \cmark \\
neodarwinismo & ne*o*dar-wi*nis*mo \xmark & ne*o*dar-wi*nis*mo \xmark \\
nobiliário & no*bi*li-á*ri*o \xmark & no*bi*li*á*ri*o \cmark \\
nucléolo & nu*clé-o*lo \xmark & nu*clé*o*lo \cmark \\
octaédrico & oc*ta-é*dri*co \xmark & oc*ta*é*dri*co \cmark \\
odeão & o*de-ão \xmark & o*de*ão \cmark \\
oídio & o-í*di*o \xmark & o*í*di*o \cmark \\
omíada & o*mí-a*da \xmark & o*mí*a*da \cmark \\
omnipotente & om*ni*po*ten*te \cmark & o.m-ni*po*ten*te \xmark \\
omnisciente & om*nis*ci*en*te \cmark & o.m-nis*ci*en*te \xmark \\
omnívoro & om*ní*vo*ro \cmark & o.m-ní*vo*ro \xmark \\
oócito & o-ó*ci*to \xmark & o*ó*ci*to \cmark \\
orfeão & or*fe-ão \xmark & or*fe*ão \cmark \\
oriá & o*ri-á \xmark & o*ri*á \cmark \\
ortodôntico & or*to-dôn*ti*co \xmark & or*to*dôn*ti*co \cmark \\
ossuário & os*su-á*ri*o \xmark & os*su*á*ri*o \cmark \\
osteíte & os*te-í*te \xmark & os*te*í*te \cmark \\
ostiário & os*ti-á*ri*o \xmark & os*ti*á*ri*o \cmark \\
paleógrafo & pa*le-ó*gra*fo \xmark & pa*le*ó*gra*fo \cmark \\
paleólogo & pa*le-ó*lo*go \xmark & pa*le*ó*lo*go \cmark \\
panenteísmo & pa*nen*te-ís*mo \xmark & pa*nen*te*ís*mo \cmark \\
patauá & pa*tau-á \xmark & pa*tau*á \cmark \\
patoá & pa*to-á \xmark & pa*to*á \cmark \\
pecíolo & pe*cí-o*lo \xmark & pe*cí*o*lo \cmark \\
pequiá & pe*qui-á \xmark & pe*qui*á \cmark \\
periélio & pe*ri-é*li*o \xmark & pe*ri*é*li*o \cmark \\
píon & pí-on \xmark & pí*on \cmark \\
pitiríase & pi*ti*rí-a*se \xmark & pi*ti*rí*a*se \cmark \\
pium & pi-um \xmark & pi-um \xmark \\
planctônico & planc-tô*ni*co \xmark & planc*tô*ni*co \cmark \\
pneuma & p.neu*ma \xmark & pneu*ma \cmark \\
pneumonite & p.neu*mo*ni*te \xmark & pneu*mo*ni*te \cmark \\
pneumotórax & p.neu*mo*tó*rax \xmark & pneu*mo*tó*rax \cmark \\
poliúria & po*li-ú*ri*a \xmark & po*li*ú*ri*a \cmark \\
poraquê & po*ra-quê \xmark & po*ra*quê \cmark \\
preênsil & pre-ên*sil \xmark & pre*ên*sil \cmark \\
príon & prí-on \xmark & prí*on \cmark \\
procariótico & pro*ca*ri-ó*ti*co \xmark & pro*ca*ri*ó*ti*co \cmark \\
procônsul & pro-côn*sul \xmark & pro*côn*sul \cmark \\
proteólise & pro*te-ó*li*se \xmark & pro*te*ó*li*se \cmark \\
pseudocientífico & p.seu*do*ci*en*tí*fi*co \xmark & pseu*do*ci*en*tí*fi*co \cmark \\
pseudofruto & p.seu*do*fru*to \xmark & pseu*do*fru*to \cmark \\
psicadélico & p.si*ca*dé*li*co \xmark & psi*ca*dé*li*co \cmark \\
psicoativo & p.si*co*a*ti*vo \xmark & psi*co*a*ti*vo \cmark \\
psicocirurgia & p.si*co*ci*rur*gi*a \xmark & psi*co*ci*rur*gi*a \cmark \\
psicofisiologia & p.si*co*fi*si*o*lo*gi*a \xmark & psi*co*fi*si*o*lo*gi*a \cmark \\
psicofonia & p.si*co*fo*ni*a \xmark & psi*co*fo*ni*a \cmark \\
psicografia & p.si*co*gra*fi*a \xmark & psi*co*gra*fi*a \cmark \\
psicopompo & p.si*co*pom*po \xmark & psi*co*pom*po \cmark \\
psicoterápico & p.si*co*te*rá*pi*co \xmark & psi*co*te*rá*pi*co \cmark \\
psoas & p.so*as \xmark & p.so*as \xmark \\
pterodáctilo & p.te*ro*dác*ti*lo \xmark & pte*ro*dác*ti*lo \cmark \\
ptialina & p.ti*a*li*na \xmark & pti*a*li*na \cmark \\
ptolemaico & p.to*le*mai*co \xmark & pto*le*mai*co \cmark \\
radioquímica & ra*di*o-quí*mi*ca \xmark & ra*di*o*quí*mi*ca \cmark \\
randômico & ran-dô*mi*co \xmark & ran*dô*mi*co \cmark \\
reciário & re*ci-á*ri*o \xmark & re*ci*á*ri*o \cmark \\
reimpresso & re-im*pres*so \xmark & re*im*pres*so \cmark \\
reimprimir & re-im*pri*mir \xmark & re*im*pri*mir \cmark \\
sambaíba & sam*ba-í*ba \xmark & sam*ba*í*ba \cmark \\
samnita & sam*ni*ta \cmark & sa.m-ni*ta \xmark \\
saxônico & sa-xô*ni*co \xmark & sa*xô*ni*co \cmark \\
semiárido & se*mi-á*ri*do \xmark & se*mi*á*ri*do \cmark \\
semiótico & se*mi-ó*ti*co \xmark & se*mi*ó*ti*co \cmark \\
semipermeável & se*mi*per*me-á*vel \xmark & se*mi*per*me*á*vel \cmark \\
sépsis & sép*sis \cmark & sép-sis \xmark \\
serôdio & se-rô*di*o \xmark & se*rô*di*o \cmark \\
serventuário & ser*ven*tu-á*ri*o \xmark & ser*ven*tu*á*ri*o \cmark \\
siálico & si-á*li*co \xmark & si*á*li*co \cmark \\
siríaco & si*rí-a*co \xmark & si*rí*a*co \cmark \\
sonômetro & so-nô*me*tro \xmark & so*nô*me*tro \cmark \\
suaíli & su*a-í*li \xmark & su*a*í*li \cmark \\
subatômico & su*ba-tô*mi*co \xmark & su*ba*tô*mi*co \cmark \\
subdiácono & sub*di-á*co*no \xmark & sub*di*á*co*no \cmark \\
sublevar & su.b-le*var \xmark & sub*le*var \cmark \\
subliminal & su.b-li*mi*nal \xmark & sub*li*mi*nal \cmark \\
sublinear & su.b-li*ne*ar \xmark & sub*li*ne*ar \cmark \\
sublingual & su.b-lin*gual \xmark & sub*lin*gual \cmark \\
sublunar & su.b-lu*nar \xmark & sub*lu*nar \cmark \\
subsequência & sub*se-quên*ci*a \xmark & sub*se*quên*ci*a \cmark \\
substituinte & subs*ti*tu-in*te \xmark & subs*ti*tu-in*te \xmark \\
coimbra & co-im*bra \xmark & co*im*bra \cmark \\
coimperador & co-im*pe*ra*dor \xmark & co*im*pe*ra*dor \cmark \\
reimposição & re-im*po*si*ção \xmark & re*im*po*si*ção \cmark \\
bioimpressão & bi*o-im*pres*são \xmark & bi*o*im*pres*são \cmark \\
neoimpressionista & ne*o-im*pres*si*o*nis*ta \xmark & ne*o*im*pres*si*o*nis*ta \cmark \\
autoimposto & au*to-im*pos*to \xmark & au*to*im*pos*to \cmark \\
reimplementação & re-im*ple*men*ta*ção \xmark & re*im*ple*men*ta*ção \cmark \\
teleimpressor & te*le-im*pres*sor \xmark & te*le*im*pres*sor \cmark \\
reimposta & re-im*pos*ta \xmark & re*im*pos*ta \cmark \\
reimplementar & re-im*ple*men*tar \xmark & re*im*ple*men*tar \cmark \\
reimpulsionar & re-im*pul*si*o*nar \xmark & re*im*pul*si*o*nar \cmark \\
autoimposição & au*to-im*po*si*ção \xmark & au*to*im*po*si*ção \cmark \\
cacauicultor & ca*cau-i*cul*tor \xmark & ca*cau*i*cul*tor \cmark \\
sanduiche & san*du-i*che \xmark & san*du*i*che \cmark \\
ruidosamente & ru-i*do*sa*men*te \xmark & ru*i*do*sa*men*te \cmark \\
promiscuidade & pro*mis*cu-i*da*de \xmark & pro*mis*cu*i*da*de \cmark \\
inocuidade & i*no*cu-i*da*de \xmark & i*no*cu*i*da*de \cmark \\
reincidência & re-in*ci*dên*ci.a \xmark & re*in*ci*dên*ci.a \xmark \\
reincluir & re-in*clu-ir \xmark & re*in*clu*ir \cmark \\
reinfecção & re-in*fec*ção \xmark & re*in*fec*ção \cmark \\
reinforçar & re-in*for*çar \xmark & re*in*for*çar \cmark \\
reinsurgir & re-in*sur*gir \xmark & re*in*sur*gir \cmark \\
reinstalado & re-ins*ta*la*do \xmark & re*ins*ta*la*do \cmark \\
reinstituído & re-ins*ti*tu-í*do \xmark & re*ins*ti*tu*í*do \cmark \\
reinvindicar & re-in*vin*di*car \xmark & re*in*vin*di*car \cmark \\
bioincrustação & bi*o-in*crus*ta*ção \xmark & bi*o*in*crus*ta*ção \cmark \\
agroindustrial & a*gro-in*dus*tri*al \xmark & a*gro*in*dus*tri*al \cmark \\
bioindicadores & bi*o-in*di*ca*do*res \xmark & bi*o*in*di*ca*do*res \cmark \\
autoindulgência & au*to-in*dul*gên*ci.a \xmark & au*to*in*dul*gên*ci.a \xmark \\
autoinduzida & au*to-in*du*zi*da \xmark & au*to*in*du*zi*da \cmark \\
microindústria & mi*cro-in*dús*tri*a \xmark & mi*cro*in*dús*tri*a \cmark \\
tecnoindustrial & tec*no-in*dus*tri*al \xmark & tec*no*in*dus*tri*al \cmark \\
bioinformática & bi*o-in*for*má*ti*ca \xmark & bi*o*in*for*má*ti*ca \cmark \\
coinfecção & co-in*fec*ção \xmark & co*in*fec*ção \cmark \\
geoinformação & ge.o-in*for*ma*ção \xmark & ge.o*in*for*ma*ção \xmark \\
autoinfecção & au*to-in*fec*ção \xmark & au*to*in*fec*ção \cmark \\
neuroinformática & neu*ro-in*for*má*ti*ca \xmark & neu*ro*in*for*má*ti*ca \cmark \\
amendoins & a*men*do-ins \xmark & a*men*do*ins \cmark \\
videoinstalação & vi*de*o-ins*ta*la*ção \xmark & vi*de*o*ins*ta*la*ção \cmark \\
autointitulado & au*to-in*ti*tu*la*do \xmark & au*to*in*ti*tu*la*do \cmark \\
saindo & sa-in*do \xmark & sa*in*do \cmark \\
caindo & ca-in*do \xmark & ca*in*do \cmark \\
contraindicações & con*tra-in*di*ca*ções \xmark & con*tra*in*di*ca*ções \cmark \\
abstraindo & abs*tra-in*do \xmark & abs*tra*in*do \cmark \\
prainha & pra-i*nha \xmark & pra*i*nha \cmark \\
lagoinha & la*go-i*nha \xmark & la*go*i*nha \cmark \\
canoinha & ca*no-i*nha \xmark & ca*no*i*nha \cmark \\
reimpresso & re-im*pres*so \xmark & re*im*pres*so \cmark \\
genuino & ge*nu-i*no \xmark & ge*nu*i*no \cmark \\
ruina & ru-i*na \xmark & ru*i*na \cmark \\
arruinado & ar*ru-i*na*do \xmark & ar*ru*i*na*do \cmark \\
arruinou & ar*ru-i*nou \xmark & ar*ru*i*nou \cmark \\
suino & su-i*no \xmark & su*i*no \cmark \\
suina & su-i*na \xmark & su*i*na \cmark \\
ajuizamento & a*ju-i*za*men*to \xmark & a*ju*i*za*men*to \cmark \\
luiz & lu-iz \xmark & lu*iz \cmark \\
luiza & lu-i*za \xmark & lu*i*za \cmark \\
amnésia & a-m.né*si*a \xmark & a*mné*si*a \cmark \\
amniota & a-m.ni*o*ta \xmark & a*mni*o*ta \cmark \\
amniótico & a-m.ni-ó*ti*co \xmark & a*mni*ó*ti*co \cmark \\
diuréticos & di-u*ré*ti*cos \xmark & di*u*ré*ti*cos \cmark \\
diurese & di-u*re*se \xmark & di*u*re*se \cmark \\
feiurinha & fei-u*ri*nha \xmark & fei*u*ri*nha \cmark \\
íodo & í-o*do \xmark & í*o*do \cmark \\
íons & í-ons \xmark & í*ons \cmark \\
antíope & an*tí-o*pe \xmark & an*tí*o*pe \cmark \\
médiuns & mé*di-uns \xmark & mé*di*uns \cmark \\
fluór & flu-ór \xmark & flu*ór \cmark \\
sequóia & se-quói*a \xmark & se*quói*a \cmark \\
subquântico & sub-quân*ti*co \xmark & sub*quân*ti*co \cmark \\
\\
\hline
37798 & 1368 & 132 \\
\hline

### 2023-04-11 scripts/dicstats.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+
+if [ $# -eq 0 ]
+then
+    tail -n +2 ../data/hyphenations.csv | grep -Pv "[,]{5}$" | wc -l | cut -d' ' -f1
+    #cat hyphenations.csv | grep -vP "^[^,][,]{5}" | wc -l | cut -d' ' -f1
+else
+    N=$1
+    N=$((N+1))
+    tail -n +2 ../data/hyphenations.csv | awk -F, '{cnt=0; for(i=1; i<=NF; i++) if($i != "") cnt++;}{print NF,cnt}' | sort | uniq -c | grep -P "[0-9]+ 7 $N" | sed 's/^ *//g' | cut -d' ' -f1
+fi

### 2023-04-11 scripts/gethyphenationagreements.sh

@@ -1,0 +1,3 @@
+#!/bin/bash
+
+cat ../data/hyphagreements | cut -d' ' -f1 | grep "($1)" | wc -l 

### 2023-04-11 scripts/getpatternsfromtex.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+
+# usage:
+# ./getpatternsfromtex.sh INPUT_TeX_FILE
+# ./getpatternsfromtex.sh /usr/local/texlive/2023/texmf-dist/tex/generic/hyph-utf8/patterns/tex/hyph-pt.tex > ../data/default.TeX.pt-br.patterns
+
+STARTLINE=$(($(grep -no "\\\\patterns{" $1 | cut -d: -f1)+1))
+PATLENGTH=$(($(tail -n +$STARTLINE $1 | grep -n -m1 "}" | cut -d: -f1)-1))
+tail -n +$STARTLINE $1 | head -n $PATLENGTH

### 2023-04-11 scripts/gohyphen.go

@@ -1,0 +1,49 @@
+package main
+
+import (
+	"fmt"
+	"log"
+	"os"
+	"github.com/speedata/hyphenation"
+)
+
+// go get github.com/speedata/hyphenation
+// go mod init github.com/speedata
+// go run gohyphen.go
+// go build gohyphen.go
+// ./gohyphen dicfile word
+
+func main() {
+	filename := os.Args[1] 
+	r, err := os.Open(filename)
+	if err != nil {
+		log.Fatal(err)
+	}
+	l, err := hyphenation.New(r)
+	if err != nil {
+		log.Fatal(err)
+	}
+
+	var h []int
+	word := os.Args[2]
+	h = l.Hyphenate(word)
+	//fmt.Println(word, h) // [3 6] and [2 5 7 9]
+	//fmt.Println(h)
+
+	hword := "";
+	j := 0
+	i := 0
+	for  _, c := range word { 
+	    hword = hword + string(c)
+	    //hword = hword + string(word[i])
+	    if(j < len(h) && h[j]-1 == i) {
+		hword = hword + "-"
+		j++
+	    }
+	    i++
+	}
+	fmt.Println( hword )
+
+	//str := l.DebugHyphenate(word)
+	//fmt.Println(str)
+}

### 2023-04-11 scripts/gohyphenfull.go

@@ -1,0 +1,34 @@
+package main
+
+import (
+	"fmt"
+	"log"
+	"os"
+
+	"github.com/speedata/hyphenation"
+)
+
+// go get github.com/speedata/hyphenation
+// go mod init github.com/speedata
+// go run gohyphen.go
+// go build gohyphen.go
+// ./gohyphen dicfile word
+
+func main() {
+	filename := os.Args[1] 
+	r, err := os.Open(filename)
+	if err != nil {
+		log.Fatal(err)
+	}
+	l, err := hyphenation.New(r)
+	if err != nil {
+		log.Fatal(err)
+	}
+
+	//var h []int
+	word := os.Args[2]
+	//h = l.Hyphenate(word)
+	//fmt.Println(word, h) // [3 6] and [2 5 7 9]
+	str := l.DebugHyphenate(word)
+	fmt.Println(str)
+}

### 2023-04-11 scripts/hyphenationagreements.sh

@@ -1,0 +1,45 @@
+#!/bin/bash
+
+# https://unix.stackexchange.com/questions/609866/regular-awk-easily-sort-array-indexes-to-output-them-in-the-chosen-order
+cat ../data/hyphenations.csv | 
+awk -F "," '{
+   delete a; delete xa; delete idxs;
+   for(i=2; i<=NF; i++) if($i) a[$i]+=1;
+   #for(aa in sa) printf "%s(%d)\t",aa,a[aa]; if(length(a)>0) print ""
+
+   for(aa in a) xa[a[aa]]=aa;
+   #for(x in xa) printf "%s :: %d ",xa[x],x;
+   
+   n = sort(xa,idxs,"-r")    
+   for (i=1; i<=n; i++) {
+        idx = idxs[i]
+	printf "%s(%d)%s", xa[idx], idx, (i<n ? OFS : ORS)
+   }
+
+   } 
+ 
+   function sort(arr, idxs, args,      i, str, cmd) {
+      for (i in arr) {
+         gsub(/\047/, "\047\\\047\047", i)
+         str = str i ORS
+      }
+
+      cmd = "printf \047%s\047 \047" str "\047 |sort " args
+
+      i = 0
+      while ( (cmd | getline idx) > 0 ) {
+         idxs[++i] = idx
+      }
+
+      close(cmd)
+
+      return i
+   }    
+   ' |
+   if [ $# -eq 0 ]
+   then
+       tee /dev/null
+   else
+       cut -d' ' -f1 | grep "($1)" | wc -l
+   fi
+

### 2023-04-11 scripts/checkhyphenation.sh
adding checkhyphenation.sh

@@ -1,0 +1,52 @@
+#!/bin/bash
+
+# Check a test hyphenation form against a known correct form.  The output mark
+# the missing hyphenation points with hyphens (-), the wrong hyphenation points
+# with period (.), and the correct hyphenation points with asterisk (*).
+#
+# usage: 
+# ./checkhyphenation.sh correct test 
+#
+# example:
+# ./checkhyphenation.sh tra-ba-lho trab-a-lho
+#
+# tra-b.a*lho
+#    ^ ^ ^
+#    | | |
+#    | | + -- correct
+#    | + ---- wrong
+#    + ------ missed
+
+hword=$1
+rword=$2
+#echo "$hword $rword"
+s1=$(echo $hword | sed 's/-//g')
+s2=$(echo $rword | sed 's/-//g')
+if [[ "$s1" != "$s2" ]]
+then
+    exit -1
+fi
+j=0
+for (( i=0; i<${#hword}; i++ )); 
+do        
+   if [[ "${hword:$i:1}" == "${rword:$j:1}" ]]
+   then
+       if [[ "${hword:$i:1}" == "-" ]] # correct breaking point
+       then
+	   echo -n "*"
+       else
+           echo -n "${hword:$i:1}"
+       fi
+       ((j++))
+   elif [[ "${hword:$i:1}" == "-" ]] # missing breaking point
+   then
+       echo -n "-"
+   elif [[ "${rword:$j:1}" == "-" ]] # wrong breaking point
+   then
+       echo -n "."
+       ((j++))
+       ((i--))
+   fi
+done
+
+echo""

### 2023-04-11 scripts/comparehyphenations.sh
adding comparehyphenations.sh

@@ -1,0 +1,86 @@
+#!/bin/bash
+
+# Compare a two (or more) hyphenations. The first form given is assumed the correct one.
+# As a result, the count of correct and wrong hyphenation-parts for each form presented.
+#
+# usage:
+# ./comparehyphenations.sh correct test1 test2 ...
+#
+# example:
+# ./comparehyphenations.sh gi-ná-sio gi-ná-sio
+#       3       0
+#   (correct)(wrong)
+#
+# ./comparehyphenations.sh gi-ná-sio gi-ná-si-o
+# 	2	1
+#   (correct)(wrong)
+#
+# ./comparehyphenations.sh gi-ná-si-o gi-ná-sio
+#	2	2
+#   (correct)(wrong)
+#
+# ./comparehyphenations.sh gi-ná-sio gi-ná-si-o giná-sio
+#	2	1
+#	1	2
+#   (correct)(wrong)
+
+args=("$@")
+right=${args[0]}
+argslen=${#args[@]}
+rword=$(echo $right | tr -d '-')
+
+fail=0
+# check if all given hyphenated forms are for the same sequence (word)
+for (( j=1; j<argslen; j++ ));
+do
+    word=$(echo ${args[$j]} | tr -d '-')
+    [[ "$rword" != "$word" ]] && fail=1
+done
+
+if [[ "$fail" == 1 ]]; then
+    echo "failed! words are different"
+    exit 1
+fi
+
+IFS='-' read -ra rightH <<< "$right"
+rhlen=${#rightH[@]}
+
+# use C style for loop syntax to read all values and indexes
+for (( j=1; j<argslen; j++ ));
+do
+  rcount=0
+  wcount=0
+  word=${args[$j]}
+  IFS='-' read -ra wordH <<< "$word"
+  wlen=${#wordH[@]}
+  k=0
+  for (( i=0; i<rhlen; i++ ));
+  do
+    if (( k > wlen )); then
+	((wcount++))
+    else
+	if [[ "${rightH[i]}" == "${wordH[k]}" ]]; then
+	    ((rcount++))
+	    ((k++))
+	else
+	    ((wcount++))
+	    STR=$(echo "${rightH[@]:0:i+1}" | tr -d ' ')
+	    SUB=$(echo "${wordH[@]:0:k+1}" | tr -d ' ')
+	    if [[ "$STR" == *"$SUB"* ]]; then
+		((k++))
+	    fi
+	fi
+    fi  
[…]

### 2023-04-11 scripts/getauletehyphenation.sh
adding scripts to get hyphenations from online dictionaries

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+word=$1
+word4url=$(echo $word | perl -p -e 's/([^A-Za-z0-9])/sprintf("%%%02X", ord($1))/seg' | sed 's/%0A$//g')
+curlresult=$(curl -s "https://aulete.com.br/$word4url/" | ascii2uni -a U -q)
+wordhyph=$(echo $curlresult | grep -P -m 1 -o '<textarea name="textarea" class="oculta" id="copy">\([^\)]+\)' | grep -P -m 1 -o '\([^\)]+\)' | sed -e 's/(//' -e 's/)//' | tr '.' '-' | tr -s '-')
+wordrebuilt=$(echo $wordhyph | sed 's/-//g')
+if [[ "$word" == "$wordrebuilt" ]]; then
+  echo -e "$wordhyph"
+fi

### 2023-04-11 scripts/getdiciohyphenation.sh

@@ -1,0 +1,28 @@
+#!/bin/bash
+
+word=$1
+word4url=$(echo $word | iconv -f utf8 -t ascii//TRANSLIT)
+bword="$word4url"
+i=1
+while [ $i -le 9 ]
+do
+    curlresult=$(curl -s "https://www.dicio.com.br/$word4url/" | ascii2uni -a U -q)
+    urltitleword=$(echo $curlresult | grep -Po "<title>[^<]+</title>" | sed -e 's/<title>//' -e 's/<\/title>//' | awk '{print tolower($0)}' | cut -d' ' -f1)
+    notfound=$(echo $curlresult | grep -A 1 '<div class="title-header">' | grep "<h1>Não encontrada</h1>")
+    if [ -z "${notfound// }" ]; then
+	if [ "$word" = "$urltitleword" ]; then
+	    if echo $curlresult | grep -q "Separação silábica"; then
+		break
+	    fi
+	fi
+    else
+	exit 1
+    fi
+    i=$(( $i + 1 ))
+    word4url="$bword-$i"
+done
+wordhyph=$(echo $curlresult | grep -Po "Separação silábica:\s+<b>[^<]+</b>" | grep -P -m 1 -o '<b>[^<]+</b>' | sed -e 's/<b>//' -e 's/<\/b>//' | sed -e 's/^\-//g' -e 's/\-$//g' | awk '{print tolower($0)}')
+wordrebuilt=$(echo $wordhyph | sed 's/-//g')
+if [[ "$word" == "$wordrebuilt" ]]; then
+    echo -e "$wordhyph"
+fi

### 2023-04-11 scripts/gethyphenations.sh

@@ -1,0 +1,70 @@
+#!/bin/bash
+
+# get portuguese hyphenations from online dictionaries:
+# michaelis, priberam, wiktionary, aulete, portal, dicio
+
+# usage example
+# ./gethyphenations.sh word
+# ./gethyphenations.sh filename
+# cat filename | ./gethyphenations.sh
+#
+# files should have one word per line
+
+INPUT=""
+if [[ -p /dev/stdin ]]; then # read from stdin
+    INPUT="$(cat -)"
+elif [ -f "$1" ]; then # read from file
+    INPUT="$(cat $1)"
+else # read from argument
+    tmp="$*"
+    INPUT=${tmp// /$'\n'}
+    OUTPUTFILE='/dev/stdout'
+fi
+
+if [[ -z "${INPUT}" ]]; then
+  exit 0
+fi
+
+if [[ -z "${OUTPUTFILE}" ]]; then  
+    OUTPUTFILE="../data/hyphenations.csv"
+    if [ -f "$OUTPUTFILE" ] 
+    then
+      echo "appending output to $OUTPUTFILE"
+    else
+      echo "writing output to $OUTPUTFILE"
+      echo -e "palavra,michaelis,priberam,wiktionary,aulete,portal,dicio" > "$OUTPUTFILE"
+    fi
+fi
+
+TMPFM=$(mktemp) || exit 1
+TMPFP=$(mktemp) || exit 1
+TMPFW=$(mktemp) || exit 1
+TMPFA=$(mktemp) || exit 1
+TMPFO=$(mktemp) || exit 1
+TMPFD=$(mktemp) || exit 1
+trap 'rm -f "$TMPFM" "$TMPFP" "$TMPFW" "$TMPFA" "$TMPFO" "$TMPFD"' EXIT
+
+while read word
+do
+    if [ "$OUTPUTFILE" == "/dev/stdout" ] || ! grep -q "^$word," "$OUTPUTFILE"
+    then
[…]

### 2023-04-11 scripts/getmichaelishyphenation.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+word=$1
+word4url=$(echo $word | perl -p -e 's/([^A-Za-z0-9])/sprintf("%%%02X", ord($1))/seg' | sed 's/%0A$//g')
+curlresult=$(curl -s "https://michaelis.uol.com.br/moderno-portugues/busca/portugues-brasileiro/$word4url/" | ascii2uni -a U -q)
+wordhyph=$(echo $curlresult | grep -P -m 1 -o '<Es>[^<]+</Es>' | sed -e 's/<Es>//' -e 's/<\/Es>//' | tr '·' '-' | tr -s '-')
+wordrebuilt=$(echo $wordhyph | sed 's/-//g')
+if [[ "$word" == "$wordrebuilt" ]]; then
+  echo -e "$wordhyph" 
+fi

### 2023-04-11 scripts/getportalhyphenations.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+word=$1
+grep "^$word\s" hyphenation-portal.tsv | head -n 1 | cut -f2

### 2023-04-11 scripts/getpriberamhyphenation.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+word=$1
+word4url=$(echo $word | perl -p -e 's/([^A-Za-z0-9])/sprintf("%%%02X", ord($1))/seg' | sed 's/%0A$//g')
+curlresult=$(curl -s "https://dicionario.priberam.org/$word4url" | ascii2uni -a U -q)
+wordhyph=$(echo $curlresult | grep -P -o '<span\ class="varpt"><span\ style="font\-size:1\.5em;"><b>[^<]+</b>' | grep -P -m 1 -o '<b>[^<]+</b>' |sed -e 's/<b>//' -e 's/<\/b>//'| tr '·' '-' | tr -s '-' | sed -e 's/^\-//g' -e 's/\-$//g')
+wordrebuilt=$(echo $wordhyph | sed 's/-//g')
+if [[ "$word" == "$wordrebuilt" ]]; then
+    echo -e "$wordhyph"
+fi

### 2023-04-11 scripts/getwiktionaryhyphenation.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+
+word=$1
+word4url=$(echo $word | perl -p -e 's/([^A-Za-z0-9])/sprintf("%%%02X", ord($1))/seg' | sed 's/%0A$//g')
+curlresult=$(curl -s "https://pt.wiktionary.org/w/api.php?action=parse&page=$word4url&prop=wikitext&format=json" | ascii2uni -a U -q)
+wordhyph=$(echo $curlresult | grep -Po "{(proparoxítona|paroxítona|oxítona)[^}]+}" | head -n1 | tr -d {} | sed -e 's/proparoxítona//g' -e 's/paroxítona//g' -e 's/oxítona//g' -e's/^|//g' -e 's/lang=[a-z]\+//g' -e 's/|$//g' | tr '|' '-')
+wordrebuilt=$(echo $wordhyph | sed 's/-//g')
+if [[ "$word" == "$wordrebuilt" ]]; then
+   echo -e "$wordhyph" 
+fi
+

### 2023-04-11 scripts/getwordsfrompalavrasnet.sh
adding getwordsfrompalavrasnet.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+
+letters=( "a" "á" "â" "b" "c" "d" "e" "é" "ê" "f" "g" "h" "i" "í" "j" "k" "l" "m" "n" "o" "ó" "ô" "p" "q" "r" "s" "t" "u" "ú" "v" "w" "x" "y" "z" )
+for c in "${letters[@]}"
+do
+#    curl -s -A "Mozilla/5.0 (X11; Linux x86_64; rv:60.0) Gecko/20100101 Firefox/81.0" "https://www.palavras.net/search.php?i=$c" | grep "Com esta procura que tem realizado há demasiados resultados" | sed 's/<\/a>/<\/a>\n/g' | grep -o '<a.*a>' | sed -e 's/<a[^>]\+>//g' -e 's/<\/a>//g' | sed 's/<.\+>//g' |  sed '/^$/d'
+    curl -s -A "Mozilla/5.0 (X11; Linux x86_64; rv:60.0) Gecko/20100101 Firefox/81.0" "https://www.palavras.net/search.php?i=$c" | grep "Palavras com [0-9] letras" | sed 's/<\/a>/<\/a>\n/g' | grep -o '<a.*a>' | sed -e 's/<a[^>]\+>//g' -e 's/<\/a>//g' | sed 's/<.\+>//g' |  sed '/^$/d'
+    sleep 3s
+done

### 2023-04-13 article/article.tex
adding widespread of TeX hyphenations

@@
 \end{enumerate*}
+
+Despite the fact that \TeX{} hyphenation algorithm and rules are old, they are,
+to these days, the most frequently used even outside the \TeX{}'s world. For
+example, Hunspell is a spell checker and morphological analyzer that is adopted
+in may software (e.g. LibreOffice, OpenOffice.org, Mozilla Firefox, Mozilla
+Thunderbird, Google Chrome, macOS, InDesign, memoQ, Opera, Affinity Publisher,
+among others \cite{hunspell}). Hunspell uses \TeX{} hyphenation rules
+\cite{hunspellhyphen}, making \TeX{} hyphenation widespread in the computer
+world. That is a result of \TeX{} approach simplicity and versatility. The
+algorithm works well, it is currently used in 66 languages
+\cite{texhyphenrules} and it is possible to design new rules for those missing
+languages.
 
@@
 
+\section{Creating the dictionary}
+A \emph{bash} script was created to crawl on six online dictionaries and extract a word hyphenation, when found.
+
+\section{Old Text}
+
 Foi criado um conjunto de \NumberOfNewRules{} regras para aprimorar as hifenizações no

### 2023-04-13 article/article.tex
compund word hyphenations

@@
 languages.
+
+Unfortunately, some specific hyphenation rules are not possible to be
+implemented using the \TeX{} hyphenation algorithm. In German, for example,
+there are no hyphens in compound words. Additionally, when words are hyphenated
+some letters might also change. Furthermore, the spelling reform made changes,
+making it necessary to create a different set of rules. For example, the German
+word \emph{Schiffahrt} should be hyphenated as \emph{Schiff-fahrt}, preserving
+the \emph{f}s from each word that make this compound. The hyphenation should
+insert a \emph{f} that is not part of the written form. That was not a problem
+for the old written form of the word: \emph{Schifffahrt}. Also, the old
+hyphenating rules of German grammar stated the hyphenation \emph{Bäk-ker} for
+the word \emph{Bäcker}, \emph{Zuk-ker} for the word \emph{Zucker} and
+\emph{pak-ken} for the word \emph{packen}. Now those words are hyphenated as
+\emph{Bä-cker}, \emph{Zu-cker} and \emph{pa-cken}, respectively. Some words
+have also changed their hyphenation point after the spelling reform. For
+example, \emph{Fen-ster} became \emph{Fens-ter}and \emph{mei-stens} became
+\emph{meis-tens}. Some problems in compound word hyphenation in \TeX{} are
+discussed in \cite{sojka1995a}.
 

### 2023-04-14 article/article.tex
update

--- 2023-04-13 article/article.tex
@@
 Despite the fact that \TeX{} hyphenation algorithm and rules are old, they are,
-to these days, the most frequently used even outside the \TeX{}'s world. For
-example, Hunspell is a spell checker and morphological analyzer that is adopted
-in may software (e.g. LibreOffice, OpenOffice.org, Mozilla Firefox, Mozilla
-Thunderbird, Google Chrome, macOS, InDesign, memoQ, Opera, Affinity Publisher,
-among others \cite{hunspell}). Hunspell uses \TeX{} hyphenation rules
-\cite{hunspellhyphen}, making \TeX{} hyphenation widespread in the computer
-world. That is a result of \TeX{} approach simplicity and versatility. The
-algorithm works well, it is currently used in 66 languages
-\cite{texhyphenrules} and it is possible to design new rules for those missing
-languages.
+to these days, the most frequently used even outside the \TeX{}'s world. The
+grounds for this is Hunspell, a spell checker and morphological analyzer that
+is adopted in may software (e.g. LibreOffice, OpenOffice.org, Mozilla Firefox,
+Mozilla Thunderbird, Google Chrome, macOS, InDesign, memoQ, Opera, Affinity
+Publisher, among others \cite{hunspell}). Hunspell uses \TeX{} hyphenation
+rules \cite{hunspellhyphen,levien1998}, making \TeX{} hyphenation widespread in
+the computer world. That is a result of \TeX{} approach simplicity and
+versatility.  The algorithm works well, it currently has rules for 66 languages
+\cite{texhyphenrules} and it is possible to design new rules for those still
+missing.
+
+Unfortunately, some specific hyphenation rules are not possible to be
+implemented using the \TeX{} hyphenation algorithm. In German, for example,
+when words are hyphenated, some letters might change or a letter might be
+inserted.  Compound words have no hyphens, leading to long sequences of letters
+with no visible separation and even repetitions of a same letter, such as in
+\emph{Wasserrinne} and \emph{Schifffahrt}. Furthermore, the German spelling
+reform made some changes, making it necessary to create a different set of
+rules for German hyphenation.  For example, the word \emph{Schiffahrt} should
+be hyphenated as \emph{Schiff-fahrt}, preserving the \emph{f}s from each word
+that makes this compound. The hyphenation should insert a \emph{f} that is not
+part of the written form. That was not a problem for the old written form of
+the word: \emph{Schifffahrt}. Also, the old hyphenating rules of German grammar
+stated the hyphenation \emph{Bäk-ker} for the word \emph{Bäcker},
+\emph{Zuk-ker} for the word \emph{Zucker} and \emph{pak-ken} for the word
+\emph{packen}. Now those words are hyphenated as \emph{Bä-cker}, \emph{Zu-cker}
+and \emph{pa-cken}, respectively. Some words have also changed their
+hyphenation point after the spelling reform. For example, \emph{Fen-ster}
+became \emph{Fens-ter}and \emph{mei-stens} became \emph{meis-tens}. Some
+problems in compound word hyphenation in \TeX{} are discussed in
+\cite{sojka1995a}.
 

### 2023-04-18 article/article.tex
updates from alines

@@
 \title{Improving the portuguese hyphenation rules}
-\author{Leonardo Araújo}
+\author{Leonardo Araújo \and Aline de Lima Benevides}
 \begin{document}
@@
 \section{Grammar rules for hyphenation in Portuguese}
-When there is no space left in line for a whole word, it might be split in two
-using a hyphen as an indication of such procedure. In Portuguese, hyphenations
-are allowed on syllables boundaries. According to the Grammar
-\cite{cunha2016,bergstrom2011}, some rules might still apply:
+
+There is a wide range of writing systems, including logographic, syllabic, and
+alphabetic writing systems. We might group the writing systems into three
+cateories: alphabetic, phonemic and logographic. Although they are distinct
+categories, some writing systems be built on an interplay of these categories
+\cite{coulmas2003}. The principles that guide an alphabetic writing system or
+a phonemic writing system can vary significantly based on the specific language
+and its history, but we might highlight some of the key points: 
+\begin{enumerate*}[label=\arabic*)]
+    \item the most usual principle consists on representing the sounds of a
+	language with written symbols, using one or a combination of symbols to
+	represent each sound (e.g. the orthographic system of Portuguese uses
+	an alphabet of 27 letters that aim to represent different sounds of the
+	language); 
+    \item etymology also plays an important role, where the
+	spelling of a word reflects its origins and history (e.g. the French
+	language often reflects the Latin roots of words in its spelling);
+    \item morphology is used as a guide in structuring many languages, where
+	they use specific letters or symbols to indicate word endings,
+	prefixes, or suffixes (e.g. Russian uses different forms of the
+	Cyrillic alphabet to indicate gender and case in its nouns); 
+    \item the way a language has evolved over time also contribute (e.g. the 
+	spelling of many English words has changed over time to reflect changes 
+	in pronunciation);
+\end{enumerate*}
+The principles that guide orthographic systems for languages with logographic
+writing systems like Chinese ideograms, cuneiform writing, and Egyptian
+hieroglyphs differ significantly from those of alphabetic writing systems. In
+logographic writing systems, individual symbols or characters represent entire
+words or ideas rather than phonemes or sounds. As a result, the principles that
+guide their orthographic systems are based more on semantic and visual
+principles rather than phonemic principles.
+
+As a result of the alphabetical writing system of the Portuguese, its spelling
+is guided by phonological principles \cite{cagliari2015}. The fact that
+spelling reflects, to some extent, the way words are pronounced, means that the
+hyphenation of words is also influenced by the phonemic system, where words are
+divided into syllables. It is noteworthy that different languages divide words
+based on different principles, for example, English tends to be guided by
+morphological principles, such as \emph{walk-ing}, \emph{un-happy},
+\emph{work-s} and \emph{ear-ly}. Also, other factors affect word hyphenation in
+English, such as the presence of doubled consonants and digraphs. There are also 
+a myriad of exceptions that might be grasped into rules.
+% https://english.stackexchange.com/questions/385/what-are-the-rules-for-splitting-words-at-the-end-of-a-line
+
+Merely stating that an orthographic system is guided by phonological issues
+does not necessarily mean that its hyphenation rules directly reflect the way a
+word is pronounced. This is because the orthographic system operates according
+to its own specific rules. For instance, although vowel clusters that produce a
+single sound (i.e., digraphs) are pronounced within a single syllable in words
+like \emph{chave}, \emph{ilha}, \emph{shampoo}, \emph{carro}, and \emph{bird},
+their representation in writing determines how they are separated.
+Specifically, different consonants within a digraph must remain together, while
+different consonants are separated. As a result, we have \emph{i-lha} but \emph{car}.
+
+%When there is no space left in line for a whole word, it might be split in two
+%using a hyphen as an indication of such procedure. 
+In Portuguese, hyphenations are allowed on syllables boundaries. According to
+the Grammar \cite{cunha2016,bergstrom2011}, some rules might still apply:
 \begin{enumerate}
@@
 A \emph{bash} script was created to crawl on six online dictionaries and extract a word hyphenation, when found.
+
+\section{Updating the rules}
+
+\section{Creating a new set of rules using Patgen}
+
+\section{Comparing the set of rules}
 

### 2023-04-18 article/article.tex
updates from alines

@@
 rules, Russian has 7023 rules and German has 34011 rules.} and are able to
-correctly hyphenate the majority of Portuguese words. We propose here to
-analyse the performance of the default rules and add new rules to improve
+correctly hyphenate the majority of Portuguese words. 
+% - detalhar as regras de Rezende e Dias 
+% - contabilizar a quantidade de palavras que não são contempladas pela proposta do autor
+% - analisar a necessidade de excluir alguma regra (ao invés de apenas acrescentar novas)
+
+In front of these cases, we propose here to analyse the performance of the default rules in order to add new rules to improve
 hyphenation by correcting some issues and taking in account non-typical
-patterns.
+patterns. We describe the methodology used in the section \ref{sec-methodology}.
+
+\section{Methodology}\label{sec-methodology}
 
 In order to apprise the performance of each set of rules, we need a list of
-correctly hyphenated words that are used in a language. We use the frequency of
-occurrence to avoid selecting really rare words. To build a large list with
-such information, we relied on data collected from online dictionaries and
-corpora of Portuguese. We also looked up Portuguese grammars to check on the
-hyphenation (translineation) rules and we made some manual corrections on the
-data.
+correctly hyphenated words that are used in Portuguese. For that, we use the
+frequency of occurrence to avoid selecting really rare words. To build a large
+list with such information, we relied on data collected from online
+dictionaries and corpora of Portuguese. We also looked up Portuguese grammars
+to check on the hyphenation (\emph{translineation}) rules and we made some manual
+corrections on the data.
 
-In 1990, Portuguese went under a Language Orthographic Agreement. The adopting
-transition period started in 2009 and ended as it turned mandatory in 2016.
-Even after the agreement, some words still hold different spellings in the
-participant countries. It is desirable to have hyphenation rules that might
-work properly, despite those idiosyncrasies.  For example, the word
-\emph{reception} might be written as \emph{receção} (Portugal) or
-\emph{recepção} (Brazil); the word \emph{action} might be written as
-\emph{acção} (Portugal) or \emph{ação} (Brazil); and the word \emph{project} might be
-written as \emph{projecto} (Portugal) or \emph{projeto} (Brazil).
+\subsection{Data collection}\label{sec-data-coll}
+
+Initially we selected \href{https://www.linguateca.pt/cetenfolha/index_info.html}{CETENFolha} 
+as the source corpus. Using only this corpus led to two problems: many words
+were still missing and it was built on text from 1994, prior to the
+Orthographic Agreement. This problem is a result of the Orthographic Agreement
+of the Portuguese Language, carried out in 1990.
+
+The Agreement's adopting transition period started in 2009 and ended as it
+turned mandatory in 2016.  Even after the agreement, some words still hold
+different spellings in the participant countries. It is desirable to have
+hyphenation rules that might work properly, despite those idiosyncrasies.  For
+example, the word \emph{reception} might be written as \emph{receção}
+(Portugal) or \emph{recepção} (Brazil); the word \emph{action} might be written
+as \emph{acção} (Portugal) or \emph{ação} (Brazil); and the word \emph{project}
+might be written as \emph{projecto} (Portugal) or \emph{projeto} (Brazil).
 
@@
 
-We started using
-\href{https://www.linguateca.pt/cetenfolha/index_info.html}{CETENFolha} as the
-source corpus. Using only this corpus led to two problems: many words were
-still missing and it was built on text from 1994, prior to the Orthographic
-Agreement. We decided to incorporate the list of words from
+Because of these idiosyncrasies, we decided to incorporate the list of words from
 \href{https://www.palavras.net/}{Palavras NET} and afterwards we also included
@@
 Table \ref{tblstats} presents the number of words with a given number of
-hyphenation found the dictionaries. It also presents the number of words that
-have the highest agreed hyphenation. We will present some examples below. To
-reference the cells in the table we will not consider the header line and
-column. For example, the word \emph{como} was hyphenated by the six
-dictionaries as \emph{co-mo}. It will add one to the counts on both lines
-where the hyphenations number is 6 (first column). The word \emph{sua} was
-hyphenated as \emph{su-a} in 4 dictionaries and a \emph{sua} in one
-dictionary. It will add one in the first line, second column (since hyphenations
-were found in 5 dictionaries). It will also add one on the second line, third
-column (since the most frequent hyphenation was found in 4 dictionaries). It is
-clear now why we might have the number of same hyphenations (specially for
-small values) greater the number of hyphenations found.
+hyphenation found in the dictionaries. It also presents the number of words
+that have the highest agreed hyphenation. For example, the word \emph{como}
+was hyphenated by the six dictionaries as \emph{co-mo}. It will add one to the
+counts on both lines where the hyphenations number is 6 (first column). The
+word \emph{sua} was hyphenated as \emph{su-a} in 4 dictionaries, \emph{sua} in
+one dictionary and one dictionary did not provide its hyphenation. Therefore,
+it will add one in the first line, second column (since hyphenations were found
+in 5 dictionaries). It will also add one on the second line, third column
+(since the most frequent hyphenation was found in 4 dictionaries). It is clear
+now why we might have the number of same hyphenations (specially for small
+values) greater the number of hyphenations found.
 
@@
 \end{table}
+
+In summary, data from \emph{CETENFolha} and \emph{Palavras NET} were compiled.
+Their words were hyphenated based on the hyphenation orignal \TeX{} rules and
+contrasted with the dictionary results. The performance was appraised and the
+errors systematized, in order to find in the literature possible rules that
+could complement and improve it.
 
@@
 %using a hyphen as an indication of such procedure. 
-In Portuguese, hyphenations are allowed on syllables boundaries. According to
-the Grammar \cite{cunha2016,bergstrom2011}, some rules might still apply:
+In Portuguese, hyphenations are allowed on syllables boundaries and, in general, follow phonological principles. 
+According to
+the Grammar \cite{cunha2016,bergstrom2011,cegalla2008}, some rules might still apply:
 \begin{enumerate}
@@
 	\emph{\underline{\emph{mn}}e-mô-ni-co});
-    \item\label{rules-digraphs-ns} the digraphs \emph{ch}, \emph{lh}, \emph{nh}, \emph{gu}, \emph{qu} 
+    \item\label{rules-digraphs-ns} the digraphs\footnote{One should not confuse consonant clusters 
+	with digraphs, since the latter represent only one sound, while the former represent two or more sounds.}
+	\emph{ch}, \emph{lh}, \emph{nh}, \emph{gu}, \emph{qu} 
 	should not be split (e.g. \emph{ra-\underline{\emph{ch}}ar},
@@
 	\emph{\underline{\emph{gu}}i-tar-ra}, \emph{\underline{\emph{qu}}in-to});
-    \item\label{rule-nasalization} a vowel and its following nasalization marker (a graphic
-	nasal consonant) should not be split (e.g. \emph{\underline{\emph{am}}-bição},
+    \item\label{rule-guqu} bigrams like \emph{gu} and \emph{qu} whose vowel \emph{u} is not 
+	pronounced are never separated from the vowel or diphthong that follows it 
+	(e.g. \emph{ne-\underline{\emph{gu}e}}, \emph{pe-\underline{\emph{qu}e}});
+    \item\label{rule-nasalization} since they are digraphs, a vowel and its following 
+	nasalization marker (a graphic nasal consonant) should not be split (e.g. \emph{\underline{\emph{am}}-bição},
 	\emph{m\underline{\emph{an}}-cha});
+    \item\label{rule-decreasing} decreasing diphthongs should not be split (e.g. 
+	\emph{\underline{\emph{ai}}-ro-so}, \emph{ca-d\underline{\emph{ei}}-ra}, 
+	\emph{o-ra-ç\underline{\emph{ão}}});
     \item\label{rule-rising} rising diphthong should not be split (e.g.
@@
 	\emph{re-tri-b\underline{\emph{ui}}});
+    \item\label{rule-singlev} disyllables whose syllable has a single vowel should 
+	not be split (e.g. \emph{\underline{\emph{a}}to}, \emph{ru\underline{\emph{a}}}, 
+	\emph{\underline{\emph{ó}}dio}, \emph{\underline{\emph{u}}nha});
+    \item\label{rule-orphan} words with more than two syllables, when divided, cannot 
+	isolate a syllable composed of a single vowel (e.g. \emph{\underline{\emph{a}}gos-to}, 
+	\emph{la-go\underline{\emph{a}}}, \emph{\underline{\emph{i}}da-de});
 
@@
 \emph{como}, \emph{cede}).
+
+Systematizing the rules that guide syllable boundarie and, consequently,
+hyphenation in Portuguese proved to be fundamental for the improvement of the
+\TeX{} hyphenator rules, since they indicate the possible or prohibited contexts
+of hyphenation. Expomos, a seguir, uma análise comparativa...
 

### 2023-04-19 article/article.tex
text fix

@@
 
-There is a wide range of writing systems, including logographic, syllabic, and
-alphabetic writing systems. We might group the writing systems into three
-cateories: alphabetic, phonemic and logographic. Although they are distinct
-categories, some writing systems be built on an interplay of these categories
-\cite{coulmas2003}. The principles that guide an alphabetic writing system or
-a phonemic writing system can vary significantly based on the specific language
-and its history, but we might highlight some of the key points: 
+There is a wide range of writing systems. They might be categorized into
+logographic, syllabic, and alphabetic writing systems.  Although they are
+distinct categories, writing systems might be built on an interplay of these
+categories \cite{coulmas2003}. The principles that guide an alphabetic writing
+system or a phonemic writing system can vary significantly based on the
+specific language and its history. Nevertheless, we might highlight here some
+of its key points:
 \begin{enumerate*}[label=\arabic*)]
@@
 	Cyrillic alphabet to indicate gender and case in its nouns); 
-    \item the way a language has evolved over time also contribute (e.g. the 
-	spelling of many English words has changed over time to reflect changes 
-	in pronunciation);
+    \item the way a language has evolved over time also contribute to its 
+	written form (e.g. the spelling of many English words have changed 
+	over time to reflect changes in pronunciation);
 \end{enumerate*}
@@
 
-As a result of the alphabetical writing system of the Portuguese, its spelling
-is guided by phonological principles \cite{cagliari2015}. The fact that
-spelling reflects, to some extent, the way words are pronounced, means that the
+Portuguese uses an alphabetical writing system, ensuing that its spelling is
+guided by phonological principles \cite{cagliari2015}. The fact that spelling
+reflects, to some extent, the way words are pronounced, means that the
 hyphenation of words is also influenced by the phonemic system, where words are
@@
 \emph{work-s} and \emph{ear-ly}. Also, other factors affect word hyphenation in
-English, such as the presence of doubled consonants and digraphs. There are also 
+English, such as the presence of doubled consonants and digraphs\footnote{One
+should not confuse consonant clusters with digraphs, since the latter represent
+only one sound, while the former represent two or more sounds.}. There are also
 a myriad of exceptions that might be grasped into rules.
@@
 	\emph{\underline{\emph{mn}}e-mô-ni-co});
-    \item\label{rules-digraphs-ns} the digraphs\footnote{One should not confuse consonant clusters 
-	with digraphs, since the latter represent only one sound, while the former represent two or more sounds.}
-	\emph{ch}, \emph{lh}, \emph{nh}, \emph{gu}, \emph{qu} 
+    \item\label{rules-digraphs-ns} the digraphs	\emph{ch}, \emph{lh}, \emph{nh}, \emph{gu}, \emph{qu} 
 	should not be split (e.g. \emph{ra-\underline{\emph{ch}}ar},
 	\emph{a-bro-\underline{\emph{lh}}os}, \emph{ma-\underline{\emph{nh}}ã},
-	\emph{\underline{\emph{gu}}i-tar-ra}, \emph{\underline{\emph{qu}}in-to});
+	\emph{bur-\underline{\emph{gu}}e-sa}, \emph{\underline{\emph{qu}}in-to});
     \item\label{rule-guqu} bigrams like \emph{gu} and \emph{qu} whose vowel \emph{u} is not 

### 2023-04-24 article/article.tex
text added - fix issue #1

@@
 %using a hyphen as an indication of such procedure.
-In Portuguese, hyphenations are allowed on syllables boundaries and, in general, follow phonological principles. 
-According to
-the Grammar \cite{cunha2016,bergstrom2011,cegalla2008}, some rules might still apply:
+
+In Portuguese, hyphenations are allowed on syllables boundaries and, in
+general, follow phonological principles.  According to the Grammar
+\cite{cunha2016,bergstrom2011,cegalla2008}, some rules might still apply:
 \begin{enumerate}
@@
 	\emph{\underline{\emph{mn}}e-mô-ni-co});
-    \item\label{rules-digraphs-ns} the digraphs	\emph{ch}, \emph{lh}, \emph{nh}, \emph{gu}, \emph{qu} 
+    \item\label{rules-digraphs-ns} the digraphs	\emph{ch}, \emph{lh}, \emph{nh}
 	should not be split (e.g. \emph{ra-\underline{\emph{ch}}ar},
-	\emph{a-bro-\underline{\emph{lh}}os}, \emph{ma-\underline{\emph{nh}}ã},
-	\emph{bur-\underline{\emph{gu}}e-sa}, \emph{\underline{\emph{qu}}in-to});
+	\emph{a-bro-\underline{\emph{lh}}os}, \emph{ma-\underline{\emph{nh}}ã};
     \item\label{rule-guqu} bigrams like \emph{gu} and \emph{qu} whose vowel \emph{u} is not 
@@
 \section{Comparing the set of rules} 
+Let us remember that the standard \TeX{} hyphenation rules, proposed by
+\cite{hyphpt}, amount to XXX errors, in a set of XXXX words.  Among those, XXX
+correspond to places where the hyphenation was not carried out and XXX to
+mismarkings. Faced with the errors made by the standard hyphenator, a set of
+\NumberOfNewRules{} rules were established, which reduced the errors to XXXX,
+with XXXX unmarked hyphenation places and XXX mismarkings.  Such rules are
+presented and exemplified below, as well as the necessary exception rules and
+an example in which the application of the rule is demonstrated.
 

### 2023-04-24 article/article.tex
adding text fix #2

@@
 
+\subsection{Results from the new set of rules}
+Although the XXX erroneous words have some common characteristics, which would
+allow, to some extent, to reduce the amount of hyphenation errors, there is a
+limitation arising from the way \TeX{}'s rules are conceived. We present,
+below, the systematists found in these data that could be predicted by another
+structure of rules:
+
+\begin{description} 
+    \item[Morphological determination:] Prefixes such as \emph{re-},
+	\emph{sub-}, \emph{cyber-} and \emph{auto-} require separating the
+	prefix from its stem, what runs into phonological issues. For example,
+	\emph{reiniciar} and \emph{sublinhar}, as they contain prefixes, should
+	be hyphenated as \emph{re-i-ni-ci-ar} and \emph{sub-li-nhar},
+	respecting the morphological formation of the word. However,
+	considering that the Portuguese language hyphenates its words from
+	syllabic phonological correlates, words that require morphological
+	information, such as those, do not have their hyphenation performed
+	properly. They add up, in our corpus, to twelve words (eight words with
+	\emph{re-} and one case with \emph{auto-}, \emph{meta-}, \emph{sub-},
+	\emph{cyber-}, \emph{geo-} or \emph{neuro-}).
+
+    \item[Foreignness:] There is a group of 20 words in the corpus that are
+	terminologies or words that were incorporated into the Portuguese
+	language without full phonological adaptation, such as
+	\emph{darwinismo}, \emph{quilowatt} and \emph{esfiha}. The lack of
+	adaptation makes the phonological pattern very specific to the word,
+	making it impossible to incorporate in \TeX{}'s rules alongside the
+	other rules. The solution is to add them to the exception word list.
+
+    \item[Word-initial consonant clusters:] Portuguese has few cases of
+	consonant clusters at the beginning of a word. They, in general, are
+	etymological remnants and are currently unproductive in the language,
+	since there are no neologisms with this pattern. Encounters like
+	\emph{ps-} and \emph{pn-} are more frequent, as they are present in
+	words like \emph{psicologia} and \emph{pneu}, which have an average
+	frequency in the language. They might be predicted by rules, which
+	comprise XXX words. However, there are consonant clusters that are
+	found in very specific and low frequency words. Although possible, it
+	is not worth adding very specific rules using the consonant clusters
+	contained in the words \emph{dzeta}, \emph{gnu}, \emph{cnidário},
+	\emph{ftálico} and \emph{gnaisse} -- that is, just five words.
+\end{description}
+
 \section{Creating a new set of rules using Patgen}

### 2023-04-26 scripts/createhyphenationdictionary.sh
adding script to create an hyphenation dictionary based on the data from online dictionaries and script to flag potential problems

@@ -1,0 +1,27 @@
+#!/bin/bash
+# Create Hyphenation Dictionary 
+# It uses hyphenations from Michaelis, Priberam, Wikitionary, Aulete, Portal and Dicio stored in the source file hyphenations.csv.
+#
+# usage: 
+# ./createhyphenationdictionary.sh N where N is a number from 1 to 6
+# (since the source file hyphenations.csv has hyphenations from 6 dictionaries)
+#
+# example: 
+# create a dictionary of hyphenations where 4 dictionaries agree
+# ./createhyphenationdictionary.sh 5 > ../data/hyphenations_5.dic 
+# create a dictionary from the hyphenations where 6 dictionaries agree
+# ./createhyphenationdictionary.sh 6 > ../data/hyphenations_6.dic
+
+N=$1
+FILE="../data/hyphenations.csv"
+
+awk -F "," -v N=$N '{
+	delete a; 
+	for(i=2; i<=NF; i++) 
+	    if($i) 
+		a[$i]+=1;
+	for(aa in a) 
+	    if(a[aa] == N) 
+		#printf "%s(%d)\n",aa,a[aa]; 
+		printf "%s\n",aa;
+	}' "$FILE"

### 2023-04-26 scripts/flagwronghyphens.sh

@@ -1,0 +1,47 @@
+#!/bin/bash
+#
+#
+#
+#
+
+V="[aeiouáàãâéêíóõôú]" # vowel
+C="[^-aeiouáàãâéêíóõôú]" # consonant
+CH="[^-aeiouáàãâéêíóõôúh]" # consonant not h
+
+function join_by { local IFS="$1"; shift; echo "$*"; }
+
+patterns=(
+    "^${C}+-|-${C}+-|-${C}+$|^${C}$" # cannot have a sequence only consonants and no vowel in hyphenated segments: consonant clusters alone in a syllable are not allowed in Portuguese
+    "c-h|l-h|n-h|g-u|q-u" # the digraphs ch, lh, nh, gu, qu should not be split
+    "[gq]u-${V}-${C}${V}|[gq]u-${V}-${C}{2}" # bigrams like gu and qu whose vowel u is not pronounced are never separated from the vowel or diphthong that follows it
+    "${V}-[nm]${CH}|${V}-[nm]$" # since they are digraphs, a vowel and its following nasalization marker (a graphic nasal consonant) should not be split
+    "rr|ss|mm|nn|sc|sç|xc" # the following consonant digraphs should be split: rr, ss, mm, nn, sc, sç and xc 
+    # those rules are commented since TeX already avoids leaving a single character orphan
+    # removing those hyphens in the source dictionary would lead to hyphenation rules unfitted to other purposes, such as text-to-speech conversion
+    #"^([^-]+-){2,}${V}$|^${V}(-[^-]+){2,}$" # words with more than two syllables, when divided, cannot isolate a syllable composed of a single vowel.
+    #"^${V}+-[^-]+$|^[^-]+-${V}+$" # disyllables whose syllable has a single vowel should not be split
+    "^-|-$" # malformed hyphenation (starting or ending with hyphen)
+)
+
+pattern=$(join_by \| "${patterns[@]}")
+
+process_input() {
+  while read line
+  do
+   echo $line | grep -P "${pattern}"
+  done
+}
+
+input="${1:-/dev/stdin}"
+
+if [[ -f $input || -p $input ]]; then # if a file is given as argument
+  process_input < "$input"
+else
+  if [[ ! -t 0 ]]; then # if stdin has data
+    process_input
+  else
+    process_input <<< "$input"
+  fi
+fi
+
+

### 2023-04-28 article/article.tex
adding information about lefthyphenmin and righthyphenmin

@@
 \usepackage{cleveref}
+\usepackage{fancyvrb}
 
@@
 \begin{document}
+\VerbatimFootnotes
 \maketitle
@@
 
-\section{Introduction}
+\section{Introduction}\label{sec-intro}
 Hyphenation in text wrapping was not used for a long time. Words should fit
@@
     \item characters used, since some might block hyphenation at their edges;
-    \item the value of the internal variables \verb|lefthyphenmin| and \verb|righthyphenmin|,
+    \item the value of the internal variables \verb|lefthyphenmin| and \verb|righthyphenmin|\footnote{
+	The variables \verb|lefthyphenmin| and \verb|righthyphenmin| are language dependant and
+	are defined in \emph{tlpobj} files (\verb|/usr/local/texlive/20XX/tlpkg/tlpobj/hyphen-xxxxxx.tlpobj|). 
+	Default values varies in the range from 1 to 3. 
+    	English and Portuguese, for example, use \verb|lefthyphenmin=2| and \verb|righthyphenmin=3|.},
+	% ls /usr/local/texlive/2023/tlpkg/tlpobj/*.tlpobj | while read -r filename; do grep -Po "lefthyphenmin=[0-9]\s+righthyphenmin=[0-9]" $filename; done | tr '\t' ' ' | tr -s ' ' | sort | uniq -c
+	%      17 lefthyphenmin=1 righthyphenmin=1
+        %       6 lefthyphenmin=1 righthyphenmin=2
+        %       1 lefthyphenmin=1 righthyphenmin=3
+        %      49 lefthyphenmin=2 righthyphenmin=2
+        %       9 lefthyphenmin=2 righthyphenmin=3
         which defines the minimum sequence length of characters at the left and right borders
@@
 
-\section{Patterns for \TeX{} hyphenation} 
+\section{Patterns for \TeX{} hyphenation}\label{sec-patt4TeX} 
 The patterns used in \TeX{} hyphenation are of the form: \texttt{4z1z2}. Each
@@
 
-\section{PATGEN}
+\section{PATGEN}\label{sec-patgen}
 PATGEN uses a list of hyphenated words to define rules at different
@@
 
+Note that rules \ref{rule-singlev} and \ref{rule-orphan} are fiddling rules in \TeX{} hyphenation, 
+since \TeX{} already has directives to avoid hyphenated widows and orphans. 
+As mentioned in \Cref{sec-intro}, the variables \verb|lefthyphenmin| and \verb|righthyphenmin|
+are used to control the minimum length for fragments of hyphenated words.
+This is the ground why we will not consider rules \ref{rule-singlev} and \ref{rule-orphan}
+when analysing and elaborating the hyphenation rules.
+
 In some situations a hyphen should be repeated in the start of the following
@@
 
-Systematizing the rules that guide syllable boundarie and, consequently,
+Systematizing the rules that guide syllable boundaries and, consequently,
 hyphenation in Portuguese proved to be fundamental for the improvement of the

### 2023-05-02 article/article.tex
fix issue #5

@@
 single sound (i.e., digraphs) are pronounced within a single syllable in words
-like \emph{chave}, \emph{ilha}, \emph{shampoo}, \emph{carro}, and \emph{bird},
+like \emph{chave}, \emph{ilha}, \emph{shampoo}, \emph{carro}, and \emph{pássaro},
 their representation in writing determines how they are separated.

### 2023-05-02 article/article.tex
new section fix issue #4

@@
 In summary, data from \emph{CETENFolha} and \emph{Palavras NET} were compiled.
-Their words were hyphenated based on the hyphenation orignal \TeX{} rules and
+Their words were hyphenated based on the hyphenation original \TeX{} rules and
 contrasted with the dictionary results. The performance was appraised and the
@@
 
-\section{Grammar rules for hyphenation in Portuguese}
+\section{Writing systems}\label{sec-writing-systems}
 
@@
 principles rather than phonemic principles.
+
+\section{Grammar rules for hyphenation in Portuguese}\label{sec-grammar-port}
 

### 2023-05-02 article/article.tex
fix #6

@@
 does not necessarily mean that its hyphenation rules directly reflect the way a
-word is pronounced. This is because the orthographic system operates according
-to its own specific rules. For instance, although vowel clusters that produce a
-single sound (i.e., digraphs) are pronounced within a single syllable in words
-like \emph{chave}, \emph{ilha}, \emph{shampoo}, \emph{carro}, and \emph{pássaro},
-their representation in writing determines how they are separated.
-Specifically, different consonants within a digraph must remain together, while
-different consonants are separated. As a result, we have \emph{i-lha} but \emph{car}.
+word is pronounced -- this is because Portuguese does not have a direct
+letter-sound correspondence, and vice versa.  The orthographic system operates
+according to its own specific rules. For instance, although vowel clusters that
+produce a single sound (i.e., digraphs) are pronounced within a single syllable
+in words like \emph{chave}, \emph{ilha}, \emph{shampoo}, \emph{carro}, and
+\emph{pássaro}, their representation in writing determines how they are
+separated.  Specifically, different consonants within a digraph must remain
+together, while different consonants are separated. As a result, we have
+\emph{i-lha} but \emph{car-ro}.
 

### 2023-05-02 article/article.tex
fix #9

@@
 	\emph{ftálico} and \emph{gnaisse} -- that is, just five words.
+
+    \item[Abbreviations, Acronyms, or Initialisms:] Whether for efficiency, 
+	convenience, clarity or jargon, it is usual the usage of a shortening 
+	version of a word or a phrase. 
+	Abbreviation a way to shorten a word of phrase. Some examples in our
+	Portuguese corpus are: 
+	\emph{etc.}\footnote{Latin expression \emph{et cetera}, meaning 
+	`and other similar things'.}, 
+	\emph{Dr.}\footnote{\emph{doutor} (doctor, person with PhD title, but popularly used to designate an erudite individual)}, 
+	\emph{Exmo.}\footnote{\emph{Excelentíssimo} (honourable)},
+	\emph{cap.}\footnote{\emph{capítulo} (chapter)}, \emph{Univ.}\footnote{Universidade (university)}, 
+	\emph{ed.}\footnote{\emph{edição} (edition)}, 
+	\emph{s.n.}\footenote{sine nomine, Latin expression meaning `without a name', 
+	mostly used in the context of publishing.}.
+	Initialism consists of a set of initial 
+	letters of words that form an shortened version. They are not always 
+	understood by the set of hyphenation rules described in this work, 
+	since they do not follow orthographic (or phonotactic) standards of 
+	the language. In the corpus, it is possible to find some abbreviations, 
+	such as \emph{SESC}\footnote{Serviço Social do Comércio}, 
+	\emph{INSS}\footnote{\emph{Instituto Nacional do Seguro Social} (National Institute of Social Security)}, 
+	\emph{PCdoB}\footnote{\emph{Partido Comunista do Brasil} (Communist Party of Brazil)},
+	\emph{PM}\footnote{\emph{Polícia Militar} (military police)} and 
+	\emph{UFRJ}\footnote{Universidade Federal do Rio de Janeiro}.
+	Acronym is a type of abbreviation that shortens a phrase by combining
+	the first letter (or letters) of each word, creating a new pronounceable word.
+	Some example from the corpus are: 
+	\emph{Anatel}\footnote{\emph{Agência Nacional de Telecomunicações} (National Telecommunications Agency)},
+	\emph{Ovni}\footnote{\emph{Objeto voador não identificado} (unidentified flying object - UFO)},
+	\emph{Sida}\footnote{\emph{Síndrome da Imunodeficiência Adquirida} (acquired immunodeficiency syndrome - AIDS)} (in Portugal) and
+	\emph{Mercosul}\footnote{\emph{Mercado Comum do Sul} (Southern Common Market).}.
 \end{description}

### 2023-07-12 scripts/createhyphenlistmetro.sh
adding scripts to grab metro hyphenations

@@ -1,0 +1,77 @@
+#!/bin/bash
+
+metros=(
+    "metro-abc"
+    "metrobh"
+    "metro-brasilia"
+    "metro-campinas"
+    "metro-curitiba"
+    "metro-maringa"
+    "metro-portoalegre"
+    "metro-rio"
+    "metro-sao-paulo"
+)
+
+# Number of CPU cores
+M=$(nproc)
+
+tmpdir=$(mktemp -d)
+trap 'cleanup' EXIT
+
+cleanup() {
+    read -p "Do you want to remove the temporary folder $tmpdir? [Y/N] " response
+    case "$response" in
+        [yY])
+            rm -rf "$tmpdir"
+            ;;
+        *)
+            echo "Temporary folder $tmpdir will not be removed."
+            ;;
+    esac
+}
+
+printf '%s\n' "${metros[@]}" | parallel -j $M ./getmetrohyphens.sh {} ${tmpdir}
+
+find . -type f -name "${tmpdir}/*.txt" -exec cat {} + >> "${tmpdir}/merged_files"
+cat "${tmpdir}/merged_files" | awk '{print tolower($0)}' | sort | tr -s '-' | uniq > "${tmpdir}/metro_hyphens.txt"
+
+cat "${tmpdir}/metro_hyphens.txt" |
+    awk '{ 
+	hyphen=$0
+	gsub(/-/, "", $0)
+	word=$0
+	if (word in dic) {
+	    pos = index(hyphen, "-");
+	    value = dic[word]
+	    newvalue = ""
+	    count=0
+	    for (i = 1; i <= length(value); i++) {
+		c = substr(value, i, 1)
+		newvalue = newvalue c
+		if (c != "-") {
+		    count++
+		    if (count+1 == pos && substr(value, i+1, 1) != "-") {
+			newvalue = newvalue "-"
+		    }
+	        }   
+	    }
+	    dic[word] = newvalue
+	} else { dic[word] = hyphen }
+	}
+
+	END {
+        # Print the dictionary
+        for (key in dic) {
+        print key, dic[key]
+        }
+        }'| sort | cut -d' ' -f2 > "${tmpdir}/metro_jointhyphens.txt"
+
+tmpfile1=$(mktemp)
+tmpfile2=$(mktemp)
[…]

### 2023-07-12 scripts/getmetrohyphens.sh

@@ -1,0 +1,47 @@
+#!/bin/bash
+
+# usage:
+# ./getmetrohyphens.sh which-metro output-folder
+# example:
+# ./getmetrohyphens.sh metro-campinas /tmp/
+
+whichmetro=$1
+ofolder=$2
+
+base_url="https://rm.metrolatam.com/pdf/YYYY/MM/DD/YYYYMMDD_${whichmetro}.pdf"
+base_filename="${ofolder}/${whichmetro}_YYYYMMDD.txt"
+
+start_date="2011-07-01"  # date of the first edition of Metro 
+end_date=$(date +%Y-%m-%d)  # current date
+
+# Convert start and end dates to UNIX timestamps
+start_timestamp=$(date -d "$start_date" +%s)
+end_timestamp=$(date -d "$end_date" +%s)
+
+# Calculate the number of days between start and end dates
+days=$(( (end_timestamp - start_timestamp) / (60*60*24) ))
+
+if [ ! -d "${ofolder}/${whichmetro}" ]; then 
+  mkdir "${ofolder}/${whichmetro}"
+fi
+
+# Generate the integer number for each date in the range
+for ((i = 0; i <= days; i++)); do
+  current_date=$(date -u -d "$start_date +$i days" +%Y-%m-%d)
+  year=$(date -d "$current_date" -u +%Y)
+  month=$(date -d "$current_date" -u +%m)
+  day=$(date -d "$current_date" -u +%d)
+  # Replace the placeholders in the template URL with the current year, month, and day
+  url=${base_url//YYYY/$year}
+  url=${url//MM/$month}
+  url=${url//DD/$day}
+  url=${url//YYYYMMDD/$(date -d "$current_date" -u +%Y%m%d)}
+  filename=${base_filename//YYYY/$year}
+  filename=${filename//MM/$month}
+  filename=${filename//DD/$day}
+  echo "$url"
+  wget -q "$url" -O "${ofolder}/${whichmetro}.pdf"
+  pdftotext -bbox-layout "${ofolder}/${whichmetro}.pdf"
+  lynx --dump "${ofolder}/${whichmetro}.html" | grep -Po "[A-Za-záéíóúàâêôãõüç]+\-\s+[A-Za-záéíóúàâêôãõüç]+" | tr -d ' ' > "${ofolder}/${whichmetro}/$filename"
+done
+

### 2023-07-12 scripts/gethyphenations.sh
updates in gethyphenations.sh

@@ -10,6 +10,14 @@
 #
 # files should have one word per line
 
+if ! command -v gawk &> /dev/null
+then
+    echo "gawk could not be found"
+    echo "please install GNU AWK"
+    exit
+fi
+
+
 INPUT=""
 if [[ -p /dev/stdin ]]; then # read from stdin
     INPUT="$(cat -)"
@@ -68,3 +76,6 @@ do
     fi
 done < <(echo "${INPUT}")
 
+# some dictionary entries might have a leading or tailing - (hyphen)
+# we use the following gawk script to remove it
+gawk -i inplace -F, 'BEGIN{OFS=FS} {for (i=1;i<=NF;i++) gsub(/^[ -]+|[ -]+$/,"",$i); print $0}' $OUTPUTFILE

### 2023-07-13 article/article.tex
fix #9
fix #10

@@
 a word is partitioned during the hyphenation process. In English we should
-avoid hyphenations such as re-cover, re-form, re-sign, the-rapist,
-depart-mental and mans-laughter (in Portuguese, some examples are:
+avoid hyphenations such as \emph{re-cover}, \emph{re-form}, \emph{re-sign}, \emph{the-rapist},
+\emph{depart-mental} and \emph{mans-laughter} (in Portuguese, some examples are:
 \emph{de-putada}, \emph{fede-ração}, \emph{acu-mula}, \emph{após-tolo},
@@
 	\emph{ed.}\footnote{\emph{edição} (edition)}, 
-	\emph{s.n.}\footenote{sine nomine, Latin expression meaning `without a name', 
+	\emph{s.n.}\footnote{sine nomine, Latin expression meaning `without a name', 
 	mostly used in the context of publishing.}.

### 2023-07-13 article/article.tex
fix #11

@@
 arises when a words has many possible hyphenation points. Consider
-ar-chae-ol-o-gist (or ar-che-ol-o-gist), which is preferably partitioned as
-archae-ologist (or arche-ologist) in opposition to archaeol-ogist (or
-archeol-ogist) or archaeolo-gist (or archeolo-gist). It is preferable to keep
-whole morphemes together. In the previous example: archae (or arche, meaning
-ancient, primitive)
+\emph{ar-chae-ol-o-gist} (\emph{or ar-che-ol-o-gist}), which is preferably partitioned as
+\emph{archae-ologist} (or \emph{arche-ologist}) in opposition to \emph{archaeol-ogist} (or
+\emph{archeol-ogist}) or \emph{archaeolo-gist} (or \emph{archeolo-gist}). It is preferable to keep
+whole morphemes together. In the previous example: \emph{archae} (or \emph{arche}, meaning
+``ancient'', ``primitive'')
 %\footnote{archae- comes from the Ancient Greek ἀρχαῖος (arkhaîos, `ancient',
@@
 %https://en.wiktionary.org/wiki/archae-
-and -ologist (one who studies the topic). In Portuguese, it is also more
+and \emph{-ologist} (``one who studies the topic''). In Portuguese, it is also more
 elegant to avoid splits between double consonants or vowels, even if an

### 2023-07-13 article/article.tex
fix #12

@@
 rules:(1) suffix removal; (2) prefix removal; and (3)
-vowel-consonant-consonant-vowel (vccv) breaking. Tests showed it could find
+vowel-consonant-consonant-vowel (VCCV) breaking. Tests showed it could find
 40\% of the allowed hyphen locations \cite{liang1983}. The hyphenation

### 2023-07-13 article/article.tex
fix #13
fix #14

@@
 hyphenation point after the spelling reform. For example, \emph{Fen-ster}
-became \emph{Fens-ter}and \emph{mei-stens} became \emph{meis-tens}. Some
+became \emph{Fens-ter} and \emph{mei-stens} became \emph{meis-tens}. Some
 problems in compound word hyphenation in \TeX{} are discussed in
@@
 the first \emph{z} and after the second \emph{z}. For example, the hyphenation
-of the word \emph{piz-za}, \emph{fiz-zle} and \emph{mezzanine} use this rule,
+of the word \emph{piz-za}, \emph{fiz-zle} and \emph{mez-zanine} use this rule,
 where we see the hyphen placed between the two \emph{z}'s and no hyphen before,

### 2023-07-13 article/article.tex
fix #15

@@
 an algorithmic base approach, which might be applied to whatever sequence found
-in a text, or a mix of bothe approaches. An algorithmic approach might use a
-logic system to analyse words and apply the hyphenation rules of a given
-language. A rule base model might include the recognition of prefixes,
+in a text, or a mix of both approaches. 
+%An algorithmic approach might use a logic system to analyse words and apply
+%the hyphenation rules of a given language. 
+A rule base model might include the recognition of prefixes,
 suffixes, morphemes, or some sequences suitable for the inclusion of a break.
@@
 levels and even numbers represent inhibiting levels. Each level works as an
-inhibiting level of it predecessor. A pattern will consist of a string made of
-characters (from the language alphabet) possibly with a number in between,
-expressing the hyphenation/inhibition level and possibly word boundaries marker
-(the period) at the pattern edges. When there is no number between characters
-in a pattern, a zero is assumed, which means \emph{undefined} and no
-hyphenation point will be suggest at that location.
+inhibiting level of it predecessor. 
+%A pattern will consist of a string made of
+%characters (from the language alphabet) possibly with a number in between,
+%expressing the hyphenation/inhibition level and possibly word boundaries marker
+%(the period) at the pattern edges. When there is no number between characters
+%in a pattern, a zero is assumed, which means \emph{undefined} and no
+%hyphenation point will be suggest at that location.
 

### 2023-07-13 article/article.tex
fix #17

@@
-% xelatex --shell-escape compared.tex 
+% xelatex --shell-escape article.tex 
 % pandoc -s article.tex --pdf-engine=xelatex --pdf-engine-opt=-shell-escape -o article.html
@@
 of its key points:
-\begin{enumerate*}[label=\arabic*)]
+\begin{enumerate}[label=\arabic*)]
     \item the most usual principle consists on representing the sounds of a
@@
 	over time to reflect changes in pronunciation);
-\end{enumerate*}
+\end{enumerate}
 The principles that guide orthographic systems for languages with logographic

### 2023-07-13 article/article.tex
fix #18 also fix Oxford commas

@@
 avoid hyphenations such as \emph{re-cover}, \emph{re-form}, \emph{re-sign}, \emph{the-rapist},
-\emph{depart-mental} and \emph{mans-laughter} (in Portuguese, some examples are:
+\emph{depart-mental}, and \emph{mans-laughter} (in Portuguese, some examples are:
 \emph{de-putada}, \emph{fede-ração}, \emph{acu-mula}, \emph{após-tolo},
@@
 circumstance. The correct syllabifications are \emph{bi-sa-vô},
-\emph{i-na-ti-vo} and \emph{i-nobs-tan-te}\footnote{The rule of syllable
+\emph{i-na-ti-vo}, and \emph{i-nobs-tan-te}\footnote{The rule of syllable
 division could lead to two possible partitions: \emph{i-nobs-tan-te} and
@@
 morphological principles, such as \emph{walk-ing}, \emph{un-happy},
-\emph{work-s} and \emph{ear-ly}. Also, other factors affect word hyphenation in
+\emph{work-s}, and \emph{ear-ly}. Also, other factors affect word hyphenation in
 English, such as the presence of doubled consonants and digraphs\footnote{One
@@
 letter-sound correspondence, and vice versa.  The orthographic system operates
-according to its own specific rules. For instance, although vowel clusters that
+according to its own specific rules. For instance, although consonant clusters that
 produce a single sound (i.e., digraphs) are pronounced within a single syllable
@@
 together, while different consonants are separated. As a result, we have
-\emph{i-lha} but \emph{car-ro}.
+\emph{cha-ve}, \emph{i-lha}, and \emph{sham-poo}, but \emph{car-ro}.
 
@@
     \item[Morphological determination:] Prefixes such as \emph{re-},
-	\emph{sub-}, \emph{cyber-} and \emph{auto-} require separating the
+	\emph{sub-}, \emph{cyber-}, and \emph{auto-} require separating the
 	prefix from its stem, what runs into phonological issues. For example,
@@
 	language without full phonological adaptation, such as
-	\emph{darwinismo}, \emph{quilowatt} and \emph{esfiha}. The lack of
+	\emph{darwinismo}, \emph{quilowatt}, and \emph{esfiha}. The lack of
 	adaptation makes the phonological pattern very specific to the word,
@@
 	contained in the words \emph{dzeta}, \emph{gnu}, \emph{cnidário},
-	\emph{ftálico} and \emph{gnaisse} -- that is, just five words.
+	\emph{ftálico}, and \emph{gnaisse} -- that is, just five words.
 
@@
 	\emph{PCdoB}\footnote{\emph{Partido Comunista do Brasil} (Communist Party of Brazil)},
-	\emph{PM}\footnote{\emph{Polícia Militar} (military police)} and 
+	\emph{PM}\footnote{\emph{Polícia Militar} (military police)}, and 
 	\emph{UFRJ}\footnote{Universidade Federal do Rio de Janeiro}.

### 2023-07-14 article/article.tex
fix #19
fix issue #24
fix #26

@@
 \captureshell*[\NumberOfOneAgrees]{../scripts/gethyphenationagreements.sh 1}
+
+\newcounter{numberRulesGroups}
 
@@
 separated.  Specifically, different consonants within a digraph must remain
-together, while different consonants are separated. As a result, we have
+together, while identical consonants are separated. As a result, we have
 \emph{cha-ve}, \emph{i-lha}, and \emph{sham-poo}, but \emph{car-ro}.
@@
 \begin{enumerate}
-\item regra: \texttt{p2si}, \texttt{p2sí} -- psicologia, psíquico\\
+\item\label{rulegrp_psi} regra: \texttt{p2si}, \texttt{p2sí} -- psicologia, psíquico\\
 exceção: \texttt{p3sia}, \texttt{p3sin} -- epilepsia, rodopsina
 
-\item regra: \texttt{t2c} -- tchau%, tcheco
+\item\label{rulegrp_tc} regra: \texttt{t2c} -- tchau%, tcheco
 
-\item regra: \texttt{p2neu} -- pneumonia
+\item\label{rulegrp_pneu} regra: \texttt{p2neu} -- pneumonia
 
-\item regra: \texttt{.g2no}, \texttt{.g2nó} -- gnomo, gnóstico
+\item\label{rulegrp_gno} regra: \texttt{.g2no}, \texttt{.g2nó} -- gnomo, gnóstico
 
-\item regra: \texttt{.p2t} -- ptose%, pterossauro
+\item\label{rulegrp_pt} regra: \texttt{.p2t} -- ptose%, pterossauro
 
-\item regra: \texttt{su2b3r}, \texttt{su2b3l} -- sublunar, subrotina
+\item\label{rulegrp_cza} regra: \texttt{c2za} -- czar
+
+\item\label{rulegrp_s2} regra: \texttt{.s2} -- stalinismo
+
+\item\label{rulegrp_t2} regra: \texttt{.t2} -- tsunami
+
+\item\label{rulegrp_mn} regra: \texttt{.m2n} -- mnemônico
+
+\item\label{rulegrp_zz} regra: \texttt{z1z}, \texttt{p1p}, \texttt{z2z.} -- pizza, shopping, jazz
+
+\item\label{rulegrp_sub} regra: \texttt{su2b3r}, \texttt{su2b3l} -- sublunar, subrotina
 exceção: \texttt{su3b4li1nh}, \texttt{su3b4li1ma}, \texttt{su3b4li1me}, \texttt{su3b4li1mid} -- sublinhar, sublimar, sublime, sublimidade
 
-\item regra: \texttt{1sô} -- subsônico
+\item\label{rulegrp_so} regra: \texttt{1sô} -- subsônico
 
-\item regra: \texttt{1p2seu1d} -- pseudônimo
+\item\label{rulegrp_pseu} regra: \texttt{1p2seu1d} -- pseudônimo
 
-\item regra: \texttt{c2za} -- czar
+\item\label{rulegrp_ein} regra: \texttt{e1in1c}, \texttt{e1in1f}, \texttt{e1in1g}, \texttt{e1in1s}, \texttt{e1in1t}, \texttt{e1in1v} -- reincidência, reinfecção, reingressa, reinserção, reintegração, reinventar
+exceção: \texttt{e1in2st}, \texttt{e1in2sc} -- reinstalado, reinscrever
 
-\item regra: \texttt{.s2} -- stalinismo
+\item\label{rulegrp_oin} regra: \texttt{o1in} -- coincidência, agroindustrial, bioinformática, amendoins, gastrointestinal
+exceção: \texttt{o1ina} -- boina
 
-\item regra: \texttt{.t2} -- tsunami
+\item\label{rulegrp_eim} regra: \texttt{e1im} -- reimpresso, coimbra, coimperador
+exceção: \texttt{que2i}, \texttt{te2im} -- queimar, queimadura, teimosia, tirateima
 
-\item regra: \texttt{a1â}, \texttt{a1ã}, \texttt{a1é}, \texttt{a1í}, \texttt{a1ó}, \texttt{a1ô}, \texttt{a1ú}, \texttt{e1á}, \texttt{e1â}, \texttt{e1ã}, \texttt{e1ê}, \texttt{e1í}, \texttt{e1ó}, \texttt{e1ô}, \texttt{e1ú}, \texttt{i1á}, \texttt{i1ã}, \texttt{i1ã}, \texttt{i1é}, \texttt{i1ó}, \texttt{i1ú}, \texttt{o1á}, \texttt{o1ã}, \texttt{o1é}, \texttt{o1ê}, \texttt{o1í}, \texttt{o1ó}, \texttt{u1á}, \texttt{u1ã}, \texttt{u1é}, \texttt{u1ê}, \texttt{u1í} --  abraâmico, abraão, aéreo, país, caótico, faraônico, saúde, balneário, oceânico, campeã, veêm, veículo, teórico, napoleônico, conteúdo, diário, região, soviético, periódico, viúva, razoável, joão, poético, boêmia, heroísmo, alcoólico, usuário, itapuã, suécia, cauê, suíça \\
+\item\label{rulegrp_aa} regra: \texttt{a1â}, \texttt{a1ã}, \texttt{a1é}, \texttt{a1í}, \texttt{a1ó}, \texttt{a1ô}, \texttt{a1ú}, \texttt{e1á}, \texttt{e1â}, \texttt{e1ã}, \texttt{e1ê}, \texttt{e1í}, \texttt{e1ó}, \texttt{e1ô}, \texttt{e1ú}, \texttt{i1á}, \texttt{i1ã}, \texttt{i1ã}, \texttt{i1é}, \texttt{i1ó}, \texttt{i1ú}, \texttt{o1á}, \texttt{o1ã}, \texttt{o1é}, \texttt{o1ê}, \texttt{o1í}, \texttt{o1ó}, \texttt{u1á}, \texttt{u1ã}, \texttt{u1é}, \texttt{u1ê}, \texttt{u1í} --  abraâmico, abraão, aéreo, país, caótico, faraônico, saúde, balneário, oceânico, campeã, veêm, veículo, teórico, napoleônico, conteúdo, diário, região, soviético, periódico, viúva, razoável, joão, poético, boêmia, heroísmo, alcoólico, usuário, itapuã, suécia, cauê, suíça \\
 exceção: \texttt{1gu2é}, \texttt{1gu2ê}, \texttt{1gu2í}, \texttt{1qu2á}, \texttt{1qu2é}, \texttt{1qu2ê}, \texttt{1qu2í} -- alguém, português, linguística, aquático, inquérito, sequência, química
 
-\item regra: \texttt{a1ir.}, \texttt{u1ir.} -- sair, diminuir
+\item\label{rulegrp_air} regra: \texttt{a1ir.}, \texttt{u1ir.} -- sair, diminuir
 
-\item regra: \texttt{í1a} -- baía
+\item\label{rulegrp_ia} regra: \texttt{í1a} -- baía
 
-\item regra: \texttt{1lô} -- camelô
+\item\label{rulegrp_ain} regra: \texttt{a1ind}, \texttt{a1i1nh} -- ainda, rainha
 
-\item regra: \texttt{1cô} -- recôncavo
+\item\label{rulegrp_oin} regra: \texttt{o1i1nh} -- moinho
 
-\item regra: \texttt{e1in1c}, \texttt{e1in1f}, \texttt{e1in1g}, \texttt{e1in1s}, \texttt{e1in1t}, \texttt{e1in1v} -- reincidência, reinfecção, reingressa, reinserção, reintegração, reinventar
-exceção: \texttt{e1in2st}, \texttt{e1in2sc} -- reinstalado, reinscrever
-
-\item regra: \texttt{o1in} -- coincidência, agroindustrial, bioinformática, amendoins, gastrointestinal
-exceção: \texttt{o1ina} -- boina
-
-\item regra: \texttt{a1ind}, \texttt{a1i1nh} -- ainda, rainha
-
-\item regra: \texttt{o1i1nh} -- moinho
-
-\item regra: \texttt{1bô}, \texttt{1dô}, \texttt{1fô}, \texttt{1gô}, \texttt{1pô}, \texttt{1mô}, \texttt{1nô}, \texttt{1rô}, \texttt{1tô}, \texttt{1vô}, \texttt{1xô}, \texttt{1zô} -- robô, judô,  telefônica, xangô, capô, sumô, econômico, tarô, chatô, vovô, saxônia, amazônia
-
-\item regra: \texttt{e1im} -- reimpresso, coimbra, coimperador
-exceção: \texttt{que2i}, \texttt{te2im} -- queimar, queimadura, teimosia, tirateima
-
-\item regra: \texttt{au1i1c}, \texttt{du1i1c}, \texttt{u1i1ç}, \texttt{u1i1d}, \texttt{cu2i}, \texttt{dru2i}, \texttt{flu2id}, \texttt{bu1i1n}, \texttt{cu1i1n}, \texttt{fu1i1n}, \texttt{nu1i1n}, \texttt{ru1i1na}, \texttt{ru1i1no}, \texttt{su1i1ti}, \texttt{tu1i1ti}, \texttt{u1iz} -- cacauicultor, sanduicheira, constituição, continuidade, cuidador, druida, fluido, tabuinha, picuinha, fuinha, genuinamente, arruinado, arruinou, jesuitismo, intuitivo, juizado
+\item\label{rulegrp_aui} regra: \texttt{au1i1c}, \texttt{du1i1c}, \texttt{u1i1ç}, \texttt{u1i1d}, \texttt{cu2i}, \texttt{dru2i}, \texttt{flu2id}, \texttt{bu1i1n}, \texttt{cu1i1n}, \texttt{fu1i1n}, \texttt{nu1i1n}, \texttt{ru1i1na}, \texttt{ru1i1no}, \texttt{su1i1ti}, \texttt{tu1i1ti}, \texttt{u1iz} -- cacauicultor, sanduicheira, constituição, continuidade, cuidador, druida, fluido, tabuinha, picuinha, fuinha, genuinamente, arruinado, arruinou, jesuitismo, intuitivo, juizado
 exceção: \texttt{cu3i1da1de}, \texttt{bu1i2n1d}, \texttt{bu1i2n1t}  -- acuidade, contribuindo, contribuinte
 
-\item regra: \texttt{.m2n} -- mnemônico
+\item\label{rulegrp_gua} regra: \texttt{1gu4á}, \texttt{1gu4ã}, \texttt{1qu4ã} -- jaraguá, saguão, quão
 
-\item regra: \texttt{1gu4á}, \texttt{1gu4ã}, \texttt{1qu4ã} -- jaraguá, saguão, quão
+\item\label{rulegrp_iur} regra: \texttt{i1ur} -- diurno
 
-\item regra: \texttt{1çô} -- maçônico
+\item\label{rulegrp_io} regra: \texttt{í1o} -- íon
 
-\item regra: \texttt{i1ur} -- diurno
+\item\label{rulegrp_proi} regra: \texttt{pro1i1b} -- proibição
 
-\item regra: \texttt{í1o} -- íon
+\item\label{rulegrp_iun} regra: \texttt{i1un} -- triunfar
 
-\item regra: \texttt{pro1i1b} -- proibição
+\item\label{rulegrp_quo} regra: \texttt{1qu4ó}, \texttt{1qu4â} -- quórum, equânime
 
-\item regra: \texttt{i1un} -- triunfar
+%\item\label{rulegrp_uo} regra: \texttt{u3ó} -- fluór
 
-%\item regra: \texttt{u3ó} -- fluór
+\item\label{rulegrp_eo} regra: \texttt{é3o} -- alvéolo
 
-\item regra: \texttt{1qu4ó}, \texttt{1qu4â} -- quórum, equânime
+\item\label{rulegrp_ia} regra: \texttt{i4a.}, \texttt{i4e.}, \texttt{i4o.}, \texttt{o4a.}, \texttt{u4a.} -- economia, espécie, vazio, destoa, institua
 
-\item regra: \texttt{é3o} -- alvéolo
+\item\label{rulegrp_lo} regra: \texttt{1lô} -- camelô
 
-\item regra: \texttt{i4a.}, \texttt{i4e.}, \texttt{i4o.}, \texttt{o4a.}, \texttt{u4a.} -- economia, espécie, vazio, destoa, institua
+\item\label{rulegrp_co} regra: \texttt{1cô} -- recôncavo
 
-\item regra: \texttt{z1z}, \texttt{p1p}, \texttt{z2z.} -- pizza, shopping, jazz
+\item\label{rulegrp_bo} regra: \texttt{1bô}, \texttt{1dô}, \texttt{1fô}, \texttt{1gô}, \texttt{1pô}, \texttt{1mô}, \texttt{1nô}, \texttt{1rô}, \texttt{1tô}, \texttt{1vô}, \texttt{1xô}, \texttt{1zô} -- robô, judô,  telefônica, xangô, capô, sumô, econômico, tarô, chatô, vovô, saxônia, amazônia
+
+\item\label{rulegrp_cco} regra: \texttt{1çô} -- maçônico
 
@@
 % vitó-ria, espé-cie, exercí-cio, nó-doa, lé-gua, tê-nue, ambí-guo.
+    \setcounter{numberRulesGroups}{\value{enumi}}
 \end{enumerate}
+
+The \NumberOfNewRules{} rules were grouped above in a list of
+\arabic{numberRulesGroups} types of rules. They may be further organized into four
+large groups. The first, which comprises rules \ref{rulegrp_psi} to
+\ref{rulegrp_zz}, includes consonant clusters such as \emph{czar}, \emph{ptose}
+and \emph{gnomo}. They, unlike the examples that will be exposed in section
+\ref{secxxx} (exceptions - item 9 currently), present a set of derived words,
+which makes their marking advantageous in view of the number of cases that are
+included in this marking rule. The second group, comprising rules
+\ref{rulegrp_sub} to \ref{rulegrp_eim}, delimits the morphological boundary
+between prefixes and radicals. As noted, although phonological issues guide the
+separation of numerous words in Portuguese, there are also those that are
+guided by morphology. This is the case of words that have the prefixes
+\emph{sub-} and \emph{re-}, such as \emph{sublunar} and \emph{reinserção}. The
+third group, comprising rules \ref{rulegrp_aa} to \ref{rulegrp_ia}, seeks to
+understand a set of words that have vowel combinations that do not follow the
+general rules. This is because the Portuguese language has vowel encounters
+with the second vowel graphically marked that can be separated, forming
+hiatuses, such as \emph{caótico}, \emph{balneário} and \emph{razoável}, while
+there are also words with a similar structure that constitute a diphthong, such
+as português, \emph{alguém} and \emph{linguística}. It is remarkable, of
+course, that the latter are formed by the digraphs \emph{qu-} and \emph{gu-},
+while the former by vowels other than \emph{i} and \emph{u}. The fourth and
+last group, in turn, which comprises rules \ref{rulegrp_lo} to
+\ref{rulegrp_cco}, which are counterparts of rules that were already in the
+default rules, but did not contemplate the cases with certain accents. They
+were then added to encompass words such as \emph{camelô}, \emph{recôncavo},
+\emph{amazônia}, and \emph{maçônico}.
+
+It is important to highlight that the words included in these rules are, in general, of low frequency and were incorporated into the Portuguese language without a phonotactic adaptation, which causes these idiosyncrasies and exceptions to the language.
+They are characterized as marked cases, since it is not possible to defend that they reproduce a phonological pattern of the language because they are not productive, that is, they are not taken as an example and/or derive new words.
 

### 2023-07-14 article/article.tex
fix issue #23

@@
 \usepackage{fancyvrb}
+\usepackage{siunitx}
 
@@
 \section{Updating the rules}
+Let us remember that the standard \TeX{} hyphenation rules, proposed by
+\cite{rezende1987,hyphpt}, when tested against a set of \num{\DictionarySize}
+words, present 1,368 (????) errors, of which 1,273 (????) correspond to places
+where the hyphenation was not carried out and 125 (????) to erroneous markings.
+Faced with the errors made by the standard hyphenator, a set of \num{\NumberOfNewRules} rules were
+established, which reduced the errors to 132 (???), with 118 (????) places
+where the hyphenation was not marked and 35 (????) where there was erroneous
+marking. Such rules are presented and exemplified below, as well as the
+necessary exception rules and an example in which the application of the rule
+is demonstrated.
 

### 2023-07-18 article/article.tex
fix #27 - table still needs update and would fit better as an attachment
text update

@@
 rather than \emph{microor-ganismo} (keeping morphemes together is favored
-over splitting a double vowel).
+over splitting a double vowel). Numerous factors come into play when choosing
+the optimal hyphenation point for a word.
 
@@
 split into two syllables. But, as pointed previously, it is preferable to keep
-morphemes together rather than splitting them apart, therefore the we should
-favor the hyphenation \emph{bisa-vô} over \emph{bi-savô} and \emph{ina-tivo}
+morphemes together rather than splitting them apart, therefore we should
+favor the hyphenation \emph{bisa-vô} over \emph{bi-savô}, and \emph{ina-tivo}
 over \emph{i-nativo}. This last example could also lead to a misunderstanding
@@
 
-Machine learning approach was used by to hyphenate Norwegian text
+Machine learning approach was used to hyphenate Norwegian text
 \cite{kristensen2001}. It was found that the \TeX{} approach, in general,
@@
 \cite{knuth1977}. It was focused on the English language and used three main
-rules:(1) suffix removal; (2) prefix removal; and (3)
-vowel-consonant-consonant-vowel (VCCV) breaking. Tests showed it could find
-40\% of the allowed hyphen locations \cite{liang1983}. The hyphenation
-algorithm proposed by Frank M. Liang and adopted in \TeX{} uses the notion of
-competing patterns. A database of hyphenated words is swept, looking for
-hyphenating and inhibiting patterns. The algorithm introduced in \TeX{}82 uses
-five alternating levels of hyphenating and inhibiting patterns. The program
-for patten generation, based on a corpus, PATGEN was created Liang
-\cite{liangbreitenlohner1999} and was used to create hyphenating patterns for
-many languages
-\cite{sojka1995,sojka1995a,sojka2005thesis,sojka2003,scannell2003}.
+rules:
+\begin{enumerate*}[label=(\arabic*)]
+ \item suffix removal; 
+ \item prefix removal; and 
+ \item vowel-consonant-consonant-vowel (VCCV) breaking. 
+\end{enumerate*}
+Tests showed it could find
+40\% of the allowed hyphen locations \cite{liang1983}. 
+The hyphenation algorithm proposed by Frank M. Liang and adopted in \TeX{}
+utilizes competing patterns. The \TeX{}82 algorithm employs five alternating
+levels of hyphenating and inhibiting patterns. The program for pattern
+generation, known as PATGEN, was created by Liang \cite{liangbreitenlohner1999}
+and has been utilized to generate hyphenating patterns for numerous languages
+\cite{sojka1995,sojka1995a,sojka2005thesis,sojka2003,scannell2003}. It involves
+sweeping a database of hyphenated words in a language to identify both
+hyphenating and inhibiting patterns, ultimately creating a list of competing
+patterns for that specific language.
 
 The effective hyphenation of words by \TeX{} will actually depends on the following factors:
-\begin{enumerate*}[label=\arabic*)]
+\begin{enumerate*}[label=(\arabic*)]
     \item document language, which will determine which set of patterns to apply;
@@
 Despite the fact that \TeX{} hyphenation algorithm and rules are old, they are,
-to these days, the most frequently used even outside the \TeX{}'s world. The
-grounds for this is Hunspell, a spell checker and morphological analyzer that
-is adopted in may software (e.g. LibreOffice, OpenOffice.org, Mozilla Firefox,
-Mozilla Thunderbird, Google Chrome, macOS, InDesign, memoQ, Opera, Affinity
-Publisher, among others \cite{hunspell}). Hunspell uses \TeX{} hyphenation
-rules \cite{hunspellhyphen,levien1998}, making \TeX{} hyphenation widespread in
-the computer world. That is a result of \TeX{} approach simplicity and
-versatility.  The algorithm works well, it currently has rules for 66 languages
-\cite{texhyphenrules} and it is possible to design new rules for those still
-missing.
+to these days, the most frequently used approach, even outside the \TeX{}'s
+world. The grounds for this is Hunspell, a spell checker and morphological
+analyzer that is adopted in many softwares (e.g. LibreOffice, OpenOffice.org,
+Mozilla Firefox, Mozilla Thunderbird, Google Chrome, macOS, InDesign, memoQ,
+Opera, Affinity Publisher, among others \cite{hunspell}). Hunspell uses \TeX{}
+hyphenation rules \cite{hunspellhyphen,levien1998}, making \TeX{} hyphenation
+widespread in the computer world. That is a result of \TeX{} approach
+simplicity and versatility.  The algorithm works effectively, as it already
+supports rules for 66 languages \cite{texhyphenrules}, and offers the
+flexibility to create rules for any currently unsupported languages.
 
-Unfortunately, some specific hyphenation rules are not possible to be
-implemented using the \TeX{} hyphenation algorithm. In German, for example,
-when words are hyphenated, some letters might change or a letter might be
-inserted.  Compound words have no hyphens, leading to long sequences of letters
-with no visible separation and even repetitions of a same letter, such as in
-\emph{Wasserrinne} and \emph{Schifffahrt}. Furthermore, the German spelling
-reform made some changes, making it necessary to create a different set of
-rules for German hyphenation.  For example, the word \emph{Schiffahrt} should
-be hyphenated as \emph{Schiff-fahrt}, preserving the \emph{f}s from each word
-that makes this compound. The hyphenation should insert a \emph{f} that is not
-part of the written form. That was not a problem for the old written form of
-the word: \emph{Schifffahrt}. Also, the old hyphenating rules of German grammar
-stated the hyphenation \emph{Bäk-ker} for the word \emph{Bäcker},
-\emph{Zuk-ker} for the word \emph{Zucker} and \emph{pak-ken} for the word
-\emph{packen}. Now those words are hyphenated as \emph{Bä-cker}, \emph{Zu-cker}
-and \emph{pa-cken}, respectively. Some words have also changed their
-hyphenation point after the spelling reform. For example, \emph{Fen-ster}
-became \emph{Fens-ter} and \emph{mei-stens} became \emph{meis-tens}. Some
-problems in compound word hyphenation in \TeX{} are discussed in
-\cite{sojka1995a}.
+Unfortunately, certain hyphenation rules cannot be implemented using the \TeX{}
+hyphenation algorithm. In languages like German, hyphenation can lead to letter
+changes or insertions. Additionally, compound words lack hyphens, resulting in
+extended letter sequences without visible separation and even repetitions of
+the same letter, as seen in examples like \emph{Wasserrinne} and
+\emph{Schifffahrt}.  Furthermore, the German spelling reform made some changes,
+making it necessary to create a different set of rules for German hyphenation.
+For example, the word \emph{Schiffahrt} should be hyphenated as
+\emph{Schiff-fahrt}, preserving the \emph{f}s from each word that makes this
+compound. The hyphenation should insert a \emph{f} that is not part of the
+written form. That was not a problem for the old written form of the word:
+\emph{Schifffahrt}. Also, the old hyphenating rules of German grammar stated
+the hyphenation \emph{Bäk-ker} for the word \emph{Bäcker}, \emph{Zuk-ker} for
+the word \emph{Zucker} and \emph{pak-ken} for the word \emph{packen}. Now those
+words are hyphenated as \emph{Bä-cker}, \emph{Zu-cker} and \emph{pa-cken},
+respectively. Some words have also changed their hyphenation point after the
+spelling reform. For example, \emph{Fen-ster} became \emph{Fens-ter} and
+\emph{mei-stens} became \emph{meis-tens}. Some problems in compound word
+hyphenation in \TeX{} are discussed in \cite{sojka1995a}.
 
@@
 \section{PATGEN}\label{sec-patgen}
-PATGEN uses a list of hyphenated words to define rules at different
-levels and lengths, based on the patterns found in the data. It start with
-short patterns and increases until a maximum pattern length, allowed by the
-user, is reached. As it advances, creating longer patterns, it also establishes
-exceptions. In some cases, the analysis of long patterns might be necessary,
-since some hyphenation points might depend on characters far away from the
-breaking point\footnote{Some examples of hyphenation dependency on characters
-far from the break point: \emph{dem-o-crat} and \emph{de-moc-ra-cy};
-\emph{as-pi-rin} and \emph{aspir-ing}; \emph{de-mon-stra-tive} and
-\emph{dem-on-stra-tion}.}.
 
-PATEGEN works on glyph indices rather than character codes. Each glyph is
-represented by a single byte. That amount to 256 indices, where 13 of them are
-reserved for the digits 0-9 and the characters `.', `-' and `*'. The remaining 243
-are used to represent symbols of the given language. To run PATGEN, it is required a
-translation file, which defines the values of some language specific parameters
-(in the first line) and defines the many forms in which language symbols might
-appear (all following lines). In the first line, positions 1 and 2 are used to
-set the value of \verb|lefthyphenmin|, positions 3 and 4 are for
-\verb|righthyphenmin|. These values defines the shortest length of a string
-that might be generated by an hyphenation procedure. In order to set a single
-digit value, leave the first position blank, that is, put a blank space in
-position 1 and 3 for \verb|lefthyphenmin| and \verb|righthyphenmin|
-respectively. Positions 5, 6 and 7 are used to define alternative values for
-the special characters `.', `-' and `*'. The following lines uses a delimiter
-to surround each `letter' of the desired language alphabet and also its
-alternative representations. The first position of the line defines the
-delimiter and each symbol of the language may use as many positions as
-necessary, since not using the value reserved for the delimiter. Consider the
-example for defining the letter `e' in Portuguese: 
+PATGEN utilizes a list of hyphenated words to define rules at various levels
+and lengths, based on the patterns found in the data. It starts with short
+patterns and incrementally increases their length until reaching the maximum
+pattern length allowed by the user.  The objective is to keep the patterns as
+concise as possible, as this enhances their generalizability.  As it advances
+and incorporates longer patterns, PATGEN establishes exceptions.  In certain
+cases, analyzing long patterns may be necessary, as some hyphenation points
+could depend on characters far away from the breaking point\footnote{Some
+    examples of hyphenation dependency on characters far from the break point:
+    \emph{dem-o-crat} and \emph{de-moc-ra-cy}; \emph{as-pi-rin} and
+    \emph{aspir-ing}; \emph{de-mon-stra-tive} and \emph{dem-on-stra-tion}.
+}.
+
+PATEGEN works on glyph\footnote{\emph{Glyph} is commonly used in linguistics,
+typography, and computer graphics to refer to a specific graphical
+representation of a character or symbol, which can be the entire symbol or a
+distinct visual element within it.} indices rather than character codes. Each
+glyph is represented by a single byte. That amount to 256 indices, where 13 of
+them are reserved for the digits 0-9 and the characters `.', `-', and `*'. The
+remaining 243 are used to represent symbols of the given language.  To run
+PATGEN, a translation file is necessary. This file defines the values of
+certain language-specific parameters (in the first line) and enumerates the
+various forms in which language symbols may appear (all subsequent lines).  In
+the first line, positions 1 and 2 are used to set the value of
+\verb|lefthyphenmin|, and positions 3 and 4 are used to set the value of
+\verb|righthyphenmin|.  These values determine the minimum length of a string
+that may be generated by a hyphenation procedure. To set a single-digit value,
+leave the first position blank, i.e., place a space in position 1 and 3 for
+\verb|lefthyphenmin| and \verb|righthyphenmin|, respectively.  Positions 5, 6
+and 7 are used to define alternative values for the special characters `.', `-'
+and `*'.  The following lines use a delimiter to enclose each 'letter' of the
+desired language alphabet, including its alternative representations.  The
+first position of the line defines the delimiter, and each symbol of the
+language can occupy as many positions as necessary, as long as the reserved
+value for the delimiter is not used in the symbol's definition.  Consider the
+following example for defining the letter `e' in Portuguese: 
 \begin{verbatim}
@@
 \end{verbatim}
-It represents the many ways in which it might be found: lowercase, uppercase,
-with or without acute or circumflex accents. In this definition, we have
-assumed that the many forms in which we may find the character \emph{e} and
-\emph{e} will be equivalent for hyphenation (pattern matching) purpose. As
-another example, see the line defining the character $\pi$ (taken from
-\cite{haralambous2021}): \begin{verbatim} #p#P#\varpi ## \end{verbatim}
+It represents the many ways in which the letter `e' might be found: lowercase,
+uppercase, with or without acute or circumflex accents. Note that we have used
+the direct input (using UTF-8 or other encoding that support the accented `e'
+character) and also the compositional counterpart using the escape codes that
+define each accent.  In this definition, we have assumed that the many forms in
+which we may find the character \emph{e} will be equivalent for
+hyphenation (pattern matching) purpose. As another example, see the next line
+which defines the character $\pi$ (taken from \cite{haralambous2021}):
+\begin{verbatim} 
+#p#P#\varpi ## 
+\end{verbatim}
 
-The translate file and the dictionary file should use the same encoding. Even
-if it is a multi byte encoding, the translation file express how to deal with a
-sequence of bytes representing a glyph and PATGEN will work fine as long as
-there are at most 243 symbols in the given language.
-The dictionary file is a list of already hyphenated words from which PATGEN
-will look for patterns and create hyphenation rules.
+The dictionary file is a list of pre-hyphenated words from which PATGEN
+extracts patterns to create hyphenation rules. To ensure PATGEN's proper
+functionality, the translation file and the dictionary file must utilize the
+same encoding, even if it is a multi-byte encoding. The translation file
+describes how to handle byte sequences representing a glyph, and PATGEN will
+work seamlessly when there are at most 243 symbols in the given language.
 
-Those rules are organized
-in different levels, from 1 to 9, where odd numbers represent hyphenating
-levels and even numbers represent inhibiting levels. Each level works as an
-inhibiting level of it predecessor. 
+%Those rules are organized
+%in different levels, from 1 to 9, where odd numbers represent hyphenating
+%levels and even numbers represent inhibiting levels. Each level works as an
+%inhibiting level of it predecessor. 
 %A pattern will consist of a string made of
@@
 \section{\TeX{} hyphenation rules for portuguese}\label{sec-tex-hyphen-pt}
-
-\cite{rezende1987} created the first patters for Portuguese hyphenation in
-\TeX{}. It was lastly updated in 2015 with the contributions from José João
-Dias Almeida \cite{hyphpt}. The set has \NumberOfDefaultRules{}
-rules\footnote{The set of rules for Portuguese hyphenation is short when
+\cite{rezende1987} was the first to create patterns for Portuguese hyphenation
+in \TeX{}. The pattern set was last updated in 2015, incorporating
+contributions from José João Dias Almeida \cite{hyphpt}, resulting in a total
+of 307 rules\footnote{The set of rules for Portuguese hyphenation is short when
 compared to rules in other languages. For example, English currently has 4938
-rules, Russian has 7023 rules and German has 34011 rules.} and are able to
-correctly hyphenate the majority of Portuguese words. 
+rules, Russian has 7023 rules and German has 34011 rules.}. 
+These rules effectively hyphenate the majority of Portuguese words.
 % - detalhar as regras de Rezende e Dias 
@@
 
-In front of these cases, we propose here to analyse the performance of the default rules in order to add new rules to improve
-hyphenation by correcting some issues and taking in account non-typical
-patterns. We describe the methodology used in the section \ref{sec-methodology}.
+However, in light of certain cases, we propose an analysis of the default rules
+to identify areas for improvement. By addressing specific issues and
+considering non-typical patterns, we aim to enhance hyphenation accuracy. The
+methodology used for this analysis is described in Section
+\ref{sec-methodology}.
 
 \section{Methodology}\label{sec-methodology}
-
-In order to apprise the performance of each set of rules, we need a list of
-correctly hyphenated words that are used in Portuguese. For that, we use the
-frequency of occurrence to avoid selecting really rare words. To build a large
-list with such information, we relied on data collected from online
-dictionaries and corpora of Portuguese. We also looked up Portuguese grammars
-to check on the hyphenation (\emph{translineation}) rules and we made some manual
-corrections on the data.
+To assess the performance of each set of rules, we require a list of correctly
+hyphenated words in Portuguese. 
+We utilized word frequency data to avoid selecting excessively rare words, creating a minimal representative set. 
+A comprehensive list was compiled using data from online dictionaries and
+Portuguese corpora. Additionally, we referred to Portuguese grammars to
+validate hyphenation (\emph{translineation}) rules and manually corrected the data as
+needed.
 
@@
 
-Initially we selected \href{https://www.linguateca.pt/cetenfolha/index_info.html}{CETENFolha} 
-as the source corpus. Using only this corpus led to two problems: many words
-were still missing and it was built on text from 1994, prior to the
-Orthographic Agreement. This problem is a result of the Orthographic Agreement
-of the Portuguese Language, carried out in 1990.
-
-The Agreement's adopting transition period started in 2009 and ended as it
-turned mandatory in 2016.  Even after the agreement, some words still hold
-different spellings in the participant countries. It is desirable to have
-hyphenation rules that might work properly, despite those idiosyncrasies.  For
-example, the word \emph{reception} might be written as \emph{receção}
-(Portugal) or \emph{recepção} (Brazil); the word \emph{action} might be written
-as \emph{acção} (Portugal) or \emph{ação} (Brazil); and the word \emph{project}
-might be written as \emph{projecto} (Portugal) or \emph{projeto} (Brazil).
+Initially, we selected
+\href{https://www.linguateca.pt/cetenfolha/index_info.html}{CETENFolha}
+CETENFolha as the source corpus, but this approach presented two issues: many
+words were still missing, and the corpus was based on text from 1994, prior to
+the implementation of the Orthographic Agreement.  The Orthographic Agreement
+of the Portuguese Language was conducted in 1990, and its transition period
+started in 2009, becoming mandatory in 2016. However, even after the agreement,
+some words continue to have different spellings in the participating countries.
+To address these idiosyncrasies, we aim to develop hyphenation rules that
+accommodate variations in spelling. For instance, the word \emph{reception}
+might be written as \emph{receção} (Portugal) or \emph{recepção} (Brazil); the
+word \emph{action} might be written as \emph{acção} (Portugal) or \emph{ação}
+(Brazil); and the word \emph{project} might be written as \emph{projecto}
+(Portugal) or \emph{projeto} (Brazil).
 
@@
 O conjunto de \NumberOfNewRules{} regras é apresentado a seguir:
-\begin{multicols}{4}
-    \verbatiminput{patch.TeX.pt-br.patterns}
+\begin{multicols}{6}
+    \footnotesize
+    \verbatiminput{../data/patch.TeX.pt-br.patterns}
 \end{multicols}

### 2023-07-19 article/article.tex
adding description of default TeX rules

@@
 These rules effectively hyphenate the majority of Portuguese words.
-% - detalhar as regras de Rezende e Dias 
-% - contabilizar a quantidade de palavras que não são contempladas pela proposta do autor
-% - analisar a necessidade de excluir alguma regra (ao invés de apenas acrescentar novas)
 
@@
 \ref{sec-methodology}.
+
+%
+% FILE="../data/default.TeX.pt-br.patterns"; grep "^1..$" "$FILE" | awk '{print substr($0, 0, 2)}' | sort | uniq -c | while read line; do p=$(echo $line | cut -d' ' -f2); c=$(grep "^$p[^0-9]$" "$FILE" | awk '{print substr($0, 3)}' | tr '\n' ' '); printf "$line $c \n"; done | cut -d' ' -f1 | paste -sd+ | bc
+%
+Out of the default \TeX{} rules, 252 follow the pattern \verb|1CV|, which
+represents the recurring CV syllables in Portuguese.  As for the consonants,
+there are typically 18 considered (\verb|b|, \verb|c|, \verb|ç|, \verb|d|,
+\verb|f|, \verb|g|, \verb|j|, \verb|k|, \verb|l|, \verb|m|, \verb|n|, \verb|p|,
+\verb|r|, \verb|s|, \verb|t|, \verb|v|, \verb|x|, and \verb|z|) that can
+combine with 14 vowels (\verb|a|, \verb|e|, \verb|i|, \verb|o|, \verb|u|,
+\verb|á|, \verb|â|, \verb|ã|, \verb|é|, \verb|í|, \verb|ó|, \verb|ú|, \verb|ê|,
+and \verb|õ|), resulting in these CV patterns that indicate favorable
+hyphenation points before the consonants.  It is worth noting that there might
+be other rules or exceptions in the hyphenation patterns not covered by these
+default rules.  To accommodate exceptions, 23 additional rules were created for
+cases involving consonants \verb|b|, \verb|c|, \verb|d|, \verb|f|, \verb|g|,
+\verb|k|, \verb|p|, \verb|t|, \verb|v|, or \verb|w| followed by \verb|l| or
+\verb|r|; or \verb|c|, \verb|l| or \verb|n| followed by \verb|h|.
+
+%
+% FILE="../data/default.TeX.pt-br.patterns"; grep -v "^1..$" "$FILE" | grep "2" | awk '{print substr($0, 2, 1)}' | sort | uniq | while read line; doc=$(grep "^1${line}2.$" "$FILE" | tr -d '12' | awk '{print substr($0, 2, 1)}' | tr '\n' ' '); printf "$line $c\n"; done
+%
+Moreover, 23 distinct patterns were introduced to indicate hyphenation points
+between vowels or between \verb|c|'s, \verb|r|'s, and \verb|s|'s.
+
+%
+% FILE="../data/default.TeX.pt-br.patterns"; grep -v "^1..$" "$FILE" | grep -v "2" | grep "3" | wc -l
+%
+Additionally, 8 patterns adhere to the \verb|1[gq]u4V|, signaling beneficial
+hyphenation points before \verb|g| or \verb|q|, followed by a sequence of
+\verb|u| and a vowel, with an inhibiting point between the \verb|u| and the
+subsequent vowel.
+
+Lastly, there is a single pattern represented as \verb|1-|, denoting that a
+hyphen indeed serves as a beneficial hyphenation point."
+
+% - contabilizar a quantidade de palavras que não são contempladas pela proposta do autor
+% - analisar a necessidade de excluir alguma regra (ao invés de apenas acrescentar novas)
 

### 2023-07-31 scripts/checkaccents.sh
adding check accents script

@@ -1,0 +1,73 @@
+#!/bin/bash
+
+#words=("dá" "pás" "mês" "só" "pós" "fé" "trás" "ca-ra-jás" "ca-fé" "in-vés" "pa-ra-béns" "po-rém" "pa-péis" "cha-péu" "I-lhéus" "rou-xi-nóis" "tui-ui-ú" "teiús" "jú-ri" "jú-ris" "ví-rus" "ca-rá-ter" "têx-til" "tó-rax" "hí-fen" "fó-rum" "fó-runs" "ór-gão" "ór-gãos" "í-mã" "í-mãs" "bí-ceps" "pró-ton" "pró-tons" "á-geis" "i-mun-dí-ci-e" "lí-rio" "tú-neis" "tê-nue" "jó-quei" "nó-doa" "ce-ri-mô-nia" "his-tó-ria" "lú-ci-do" "sé-cu-lo" "pró-xi-mo" "he-ro-í-na" "ca-fe-í-na" "ju-í-zo" "fa-ís-ca" "con-traí-la" "Gra-jaú" "aí" "raí-zes")
+#printf "%s\n" "${words[@]}" |
+
+patterns=(
+    "^(?!.*-).*[aáeéêoóô]s?" # monosyllables
+    "^(?=(.*-){1,}).*([áãéêóô]s?|é[iumn]s?|óis?|ão|ões) 0$" # oxytone
+    "^(?=(.*-){1,}).*([i]s?|u[mn]?s?|o[mn]s?|[rlxn]|ão?s?|ps|[aeou][iu]s?|i[eu]s?) 1$" # paroxytone
+    "^(?=(.*-){2,}).* 2$" # proparoxytone 
+    "^([^íú]+-)?[íú]s?(-.*|\s)\d$" # hiatus with í or ú
+    )
+
+
+awk -F\- '
+    /[áéíóúãõâêôàèìòùÁÉÍÓÚÃÕÂÊÔÀÈÌÒÙ]+/{ 
+    n = split($0, syllables, "-");
+    for (i = 1; i <= n; i++) { if (match(syllables[i],/[áéíóúãõâêôàèìòùÁÉÍÓÚÃÕÂÊÔÀÈÌÒÙ]+/)) {print $0,n-i; break;} } 
+    }
+' "${1:-/dev/stdin}" |
+    while read line;
+    do
+	echo $line
+	for pattern in "${patterns[@]}"; do
[…]

### 2023-07-31 article/article.tex
update content and fix #28

@@
 \usepackage{multicol}
+\usepackage{multirow}
 \usepackage{verbatim}
@@
 \usepackage{siunitx}
+\sisetup{
+  group-separator = {\,},
+  group-minimum-digits = 3,
+  output-decimal-marker = {.},
+}
+\usepackage{booktabs}
 
@@
 
-% 6 dictionaries --- 5 commas
-\captureshell*[\DictionarySize]{../scripts/dicstats.sh}
+\captureshell*[\DictionarySize]{../scripts/dicstats.sh} % number of words that have at least one hyphenation
+\captureshell*[\CorpusSize]{../scripts/dicstats.sh -1} % total number of words in the corpus used (same as $ wc -l ../data/hyphenatios.csv)
 
 % https://www.texdev.net/2009/10/06/what-does-write18-mean/
+% number of words that hyphenations were found in N online dictionaries
 \captureshell*[\NumberOfSixHyphens]{../scripts/dicstats.sh 6}  
@@
     applications, such as text-to-speech conversion. A list of
-    \DictionarySize{} hyphenated words acquired from online dictionaries was
+    \num{\DictionarySize} hyphenated words acquired from online dictionaries was
     used along \emph{patgen} to create improved rules, leading to better hyphenation
@@
 \href{https://www.linguateca.pt/cetenfolha/index_info.html}{CETENFolha}
-CETENFolha as the source corpus, but this approach presented two issues: many
+as the source corpus, but this approach presented two issues: many
 words were still missing, and the corpus was based on text from 1994, prior to
@@
 % cat /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | awk '{CUMCOUNT+=$1; if(CUMCOUNT < 299204217) print;}' >/tmp/ptwikitop99.txt
-% cat /tmp/ptwikitop99.txt | tr -d "0-9 " |  while read -r word; do if ! grep -q "^${word}," hyphenations.csv; then echo $word; fi; done > /tmp/ptwikitop99_notinlist.txt
-
-Because of these idiosyncrasies, we decided to incorporate the list of words from
-\href{https://www.palavras.net/}{Palavras NET} and afterwards we also included
-words from the \href{https://pt.wikipedia.org}{Portuguese Wikipedia} dump.
-Although the list of words created was huge, we kept only those words we could
-find their hyphenation on at least one of the following online dictionaries: 
+% cat /tmp/ptwikitop99.txt | tr -d "0-9 " |  while read -r word; do if ! grep -q "^${word}," ../data/hyphenations.csv; then echo $word; fi; done > /tmp/ptwikitop99_notinlist.txt
+% cat /home/leoca/ee/research/hyphenation/listapalavrasnet.txt | awk '{print tolower($0)}' | while read -r word; do if !
+grep -qP "^\s*[0-9]+\s*${word}$" /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt; then echo $word; fi; done > /tmp/list_of_palavrasnet_not_in_wikipedia.txt
+
+% wc -l /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt
+% 1746947
+% wc -l /tmp/ptwikitop99_notinlist.txt
+% 42017
+% from 1746947 of wikipedia, only 42017 are not in list
+
+Due to the peculiarities mentioned, we made the decision to integrate the word
+list from \href{https://www.palavras.net/}{Palavras NET}, and subsequently, we
+augmented it with words sourced from the
+\href{https://pt.wikipedia.org}{Portuguese Wikipedia} dump. From the Wikipedia
+data, we narrowed down the selection to a subset of \num{50721} words,
+accounting for 95\% of occurrences in the corpus. This threshold was set to
+filter out typos and infrequent words. The initial word list became quite
+extensive, comprising \num{\CorpusSize} words. However, we refined the list by
+retaining only those words for which we could find hyphenation data in at least
+one of the following online dictionaries:
 \href{https://michaelis.uol.com.br/}{Michaelis},
@@
 \href{https://aulete.com.br/}{Aulete},
-\href{http://www.portaldalinguaportuguesa.org/}{Portal da Língua Portuguesa} e
+\href{http://www.portaldalinguaportuguesa.org/}{Portal da Língua Portuguesa}, and
 \href{https://www.dicio.com.br/}{Dicio}.
-This leads to the creation of a dictionary with \DictionarySize{} words.
-
-Table \ref{tblstats} presents the number of words with a given number of
-hyphenation found in the dictionaries. It also presents the number of words
-that have the highest agreed hyphenation. For example, the word \emph{como}
-was hyphenated by the six dictionaries as \emph{co-mo}. It will add one to the
-counts on both lines where the hyphenations number is 6 (first column). The
-word \emph{sua} was hyphenated as \emph{su-a} in 4 dictionaries, \emph{sua} in
-one dictionary and one dictionary did not provide its hyphenation. Therefore,
-it will add one in the first line, second column (since hyphenations were found
-in 5 dictionaries). It will also add one on the second line, third column
-(since the most frequent hyphenation was found in 4 dictionaries). It is clear
-now why we might have the number of same hyphenations (specially for small
-values) greater the number of hyphenations found.
+Consequently, this curation process resulted in a final dictionary containing
+\num{\DictionarySize} words.
+
+Table \ref{tblstats} presents the number of distinct words with a given number
+of hyphenations found in the dictionaries.  Additionally, it displays the
+number of words that received the highest agreed-upon hyphenation.  For
+instance, the word \emph{como} was consistently hyphenated as \emph{co-mo} in
+all six dictionaries.  Therefore, it contributes to both the counts in the
+column representing six hyphenations (first column).  On the other hand, the
+word \emph{sua} received different hyphenations: \emph{su-a} in four
+dictionaries, \emph{sua} in one dictionary, and one dictionary did not provide
+any hyphenation result.  This leads to an increment in the first line, second
+column (since hyphenations were found in five dictionaries) and the second
+line, third column (since the most frequent hyphenation was found in four
+dictionaries). It is evident now that the number of identical hyphenations can
+exceed the total number of hyphenations found, especially for smaller values.
 
@@
 \small
-\begin{tabular}{*{8}{l}}
+\begin{tabular}{@{ }l@{ } *{7}{@{ }S[table-format=6]@{ }}}
     hyphenations & 6 & 5 & 4 & 3 & 2 & 1 & 0 \\
@@
 
-In summary, data from \emph{CETENFolha} and \emph{Palavras NET} were compiled.
-Their words were hyphenated based on the hyphenation original \TeX{} rules and
-contrasted with the dictionary results. The performance was appraised and the
-errors systematized, in order to find in the literature possible rules that
-could complement and improve it.
+In summary, our data compilation involved \emph{CETENFolha}, \emph{Palavras
+NET}, and \emph{Wikipedia}, and hyphenated the words using the original \TeX{}
+TEX hyphenation rules.  Subsequently, we compared the hyphenated results with
+those obtained from the dictionary. By conducting a thorough performance
+appraisal, we systematized the errors and delved into the relevant literature
+to identify potential rules that could complement and enhance the existing
+hyphenation system.
 
@@
 
-There is a wide range of writing systems. They might be categorized into
-logographic, syllabic, and alphabetic writing systems.  Although they are
-distinct categories, writing systems might be built on an interplay of these
-categories \cite{coulmas2003}. The principles that guide an alphabetic writing
-system or a phonemic writing system can vary significantly based on the
-specific language and its history. Nevertheless, we might highlight here some
-of its key points:
+There is a diverse array of writing systems, categorized into logographic,
+syllabic, and alphabetic systems. Although distinct, these systems can be built
+on an interplay of these categories \cite{coulmas2003}. The principles guiding
+an alphabetic or phonemic writing system vary significantly based on the
+language and its history. Here are some key points worth highlighting:
 \begin{enumerate}[label=\arabic*)]
-    \item the most usual principle consists on representing the sounds of a
+    \item The most common principle involves representing the sounds of a
 	language with written symbols, using one or a combination of symbols to
-	represent each sound (e.g. the orthographic system of Portuguese uses
-	an alphabet of 27 letters that aim to represent different sounds of the
-	language); 
-    \item etymology also plays an important role, where the
-	spelling of a word reflects its origins and history (e.g. the French
-	language often reflects the Latin roots of words in its spelling);
-    \item morphology is used as a guide in structuring many languages, where
-	they use specific letters or symbols to indicate word endings,
-	prefixes, or suffixes (e.g. Russian uses different forms of the
-	Cyrillic alphabet to indicate gender and case in its nouns); 
-    \item the way a language has evolved over time also contribute to its 
-	written form (e.g. the spelling of many English words have changed 
-	over time to reflect changes in pronunciation);
+	represent each sound (e.g., the orthographic system of Portuguese uses
+	an alphabet of 27 letters to represent different sounds of the
+	language).
+    \item Etymology also plays a crucial role, where the spelling of a word
+	reflects its origins and historical development (e.g., the French
+	language often reflects the Latin roots of words in its spelling).
+    \item Morphology serves as a guide in structuring many languages, using
+	specific letters or symbols to indicate word endings, prefixes, or
+	suffixes (e.g., Russian uses different forms of the Cyrillic alphabet
+	to indicate gender and case in its nouns).
+    \item The evolution of a language over time also contributes to its written
+	form (e.g., the spelling of many English words has changed over time to
+	reflect changes in pronunciation).
 \end{enumerate}
-The principles that guide orthographic systems for languages with logographic
-writing systems like Chinese ideograms, cuneiform writing, and Egyptian
-hieroglyphs differ significantly from those of alphabetic writing systems. In
-logographic writing systems, individual symbols or characters represent entire
-words or ideas rather than phonemes or sounds. As a result, the principles that
-guide their orthographic systems are based more on semantic and visual
-principles rather than phonemic principles.
+Orthographic systems for languages with logographic writing systems, such as
+Chinese ideograms, cuneiform writing, and Egyptian hieroglyphs, differ
+significantly from alphabetic writing systems. In logographic systems,
+individual symbols or characters represent entire words or ideas, rather than
+phonemes or sounds. As a result, the principles guiding their orthographic
+systems are based more on semantic and visual principles than on phonemic
+principles.
 
@@
 
-Portuguese uses an alphabetical writing system, ensuing that its spelling is
-guided by phonological principles \cite{cagliari2015}. The fact that spelling
-reflects, to some extent, the way words are pronounced, means that the
-hyphenation of words is also influenced by the phonemic system, where words are
-divided into syllables. It is noteworthy that different languages divide words
-based on different principles, for example, English tends to be guided by
-morphological principles, such as \emph{walk-ing}, \emph{un-happy},
-\emph{work-s}, and \emph{ear-ly}. Also, other factors affect word hyphenation in
-English, such as the presence of doubled consonants and digraphs\footnote{One
-should not confuse consonant clusters with digraphs, since the latter represent
-only one sound, while the former represent two or more sounds.}. There are also
-a myriad of exceptions that might be grasped into rules.
+Portuguese employs an alphabetical writing system, which means its spelling is
+guided by phonological principles \cite{cagliari2015}. The correlation between
+spelling and pronunciation influences word hyphenation, as words are divided
+into syllables based on the phonemic system. It is important to note that
+different languages follow diverse principles for word division. For example,
+English is primarily guided by morphological principles, evident in words like
+\emph{walk-ing}, \emph{un-happy}, \emph{work-s}, and \emph{ear-ly}.
+Additionally, other factors, such as the presence of doubled consonants and
+digraphs, also impact word hyphenation in English. Furthermore, there exist
+numerous exceptions that may be categorized into rules.
 % https://english.stackexchange.com/questions/385/what-are-the-rules-for-splitting-words-at-the-end-of-a-line
@@
 Merely stating that an orthographic system is guided by phonological issues
-does not necessarily mean that its hyphenation rules directly reflect the way a
-word is pronounced -- this is because Portuguese does not have a direct
-letter-sound correspondence, and vice versa.  The orthographic system operates
-according to its own specific rules. For instance, although consonant clusters that
-produce a single sound (i.e., digraphs) are pronounced within a single syllable
-in words like \emph{chave}, \emph{ilha}, \emph{shampoo}, \emph{carro}, and
-\emph{pássaro}, their representation in writing determines how they are
-separated.  Specifically, different consonants within a digraph must remain
-together, while identical consonants are separated. As a result, we have
-\emph{cha-ve}, \emph{i-lha}, and \emph{sham-poo}, but \emph{car-ro}.
+does not necessarily mean that its hyphenation rules directly mirror the word's
+pronunciation. This is particularly evident in Portuguese, where there is not
+always a one-to-one letter-sound correspondence. The orthographic system
+operates based on its specific rules. For example, consider consonant clusters
+that create a single sound (digraphs) in words like \emph{chave}, \emph{ilha},
+\emph{shampoo}, \emph{carro}, and \emph{pássaro}. While these digraphs are
+pronounced as one sound within a single syllable, their representation in
+writing determines how they are divided. Specifically, different consonants
+within a digraph must remain together, whereas identical consonants are
+separated. As a result, we observe hyphenations like \emph{cha-ve},
+\emph{i-lha}, and \emph{sham-poo}, but \emph{car-ro}.
 
@@
 
-Note that rules \ref{rule-singlev} and \ref{rule-orphan} are fiddling rules in \TeX{} hyphenation, 
-since \TeX{} already has directives to avoid hyphenated widows and orphans. 
-As mentioned in \Cref{sec-intro}, the variables \verb|lefthyphenmin| and \verb|righthyphenmin|
-are used to control the minimum length for fragments of hyphenated words.
-This is the ground why we will not consider rules \ref{rule-singlev} and \ref{rule-orphan}
-when analysing and elaborating the hyphenation rules.
-
-In some situations a hyphen should be repeated in the start of the following
-line: 
+Note that rules \ref{rule-singlev} and \ref{rule-orphan} are fiddling rules in
+\TeX{} hyphenation, since \TeX{} already has directives to avoid hyphenated
+widows and orphans.  As mentioned in \Cref{sec-intro}, the variables
+\verb|lefthyphenmin| and \verb|righthyphenmin| are used to control the minimum
+length for fragments of hyphenated words.  For this reason, we will not take
+into account rules \ref{rule-singlev} and \ref{rule-orphan} during the analysis
+and development of the hyphenation rules.
+
+In some situations a hyphen should be repeated at the start of the following
+line. They are: 
 \begin{enumerate}
-\item when a compound word using a hyphen is split across lines (e.g.
-    \emph{couve-/-flor}, \emph{ex-/-presidente});
-\item when a different meaning could be conveyed when splitting a pronoun (e.g.
+\item cases where compound words using a hyphen are split across lines (e.g.,
+    \emph{couve-/-flor}, \emph{ex-/-presidente}); and
+\item cases where splitting a pronoun could result in a different meaning (e.g.,
     \emph{prazer de ver-/-me}\footnote{Possible conveyed meanings: 
@@
 
-It should be avoided to leave a single vowel in the end or start of a line (e.g.
-the word \emph{san-guí-nea} should be split only on the hyphen gave in the
-example, avoiding the split that would leave the final vowel \emph{a}
-left alone in the start of a new line: \emph{sanguíne-a}). It is also considered a better approach
-to avoid splitting disyllables made of four letters (e.g. \emph{para},
-\emph{como}, \emph{cede}).
+To ensure proper hyphenation and readability, certain guidelines should be
+followed. Avoiding a single vowel at the end or start of a line is crucial
+(e.g., \emph{san-guí-nea} should be split only on the provided hyphens,
+avoiding a split that leaves the final vowel \emph{a} alone at the start of a
+new line: \emph{sanguíne-a}). Additionally, it is advisable to refrain from
+splitting disyllables consisting of four letters (e.g., \emph{para},
+\emph{como}, \emph{cede}).  These considerations lead to more aesthetically
+pleasing and intelligible text.
 
@@
 \section{Creating the dictionary}
-A \emph{bash} script was created to crawl on six online dictionaries and extract a word hyphenation, when found.
+
+A bash script, named \texttt{gethyphenations.sh}, was developed to crawl six
+online dictionaries and extract word hyphenations whenever available. The
+process involves launching parallel threads for each word in the list, querying
+a specific online dictionary, and retrieving the corresponding hyphenation. For
+this purpose, individual scripts were created for each dictionary:
+\texttt{getmichaelishyphenation.sh} for \href{https://michaelis.uol.com.br/}{Michaelis},
+\texttt{getpriberamhyphenation.sh} for \href{https://dicionario.priberam.org/}{Priberam},
+\texttt{getwiktionaryhyphenation.sh} for \href{https://pt.wiktionary.org}{Wikcionário},
+\texttt{getauletehyphenation.sh} for \href{https://aulete.com.br/}{Aulete},
+\texttt{getportalhyphenations.sh} for \href{http://www.portaldalinguaportuguesa.org/}{Portal da Língua Portuguesa}, and
+\texttt{getdiciohyphenation.sh} for \href{https://www.dicio.com.br/}{Dicio}.
+This systematic approach ensures efficient and accurate extraction of
+hyphenations from various online sources.
 
@@
 	\emph{re-} and one case with \emph{auto-}, \emph{meta-}, \emph{sub-},
-	\emph{cyber-}, \emph{geo-} or \emph{neuro-}).
+	\emph{cyber-}, \emph{geo-} or \emph{neuro-}, those results are presented
+	in Table \ref{tab-mor-syl}).
+	% $ { head -n 1 ../data/hyphenations.csv; grep "^sublinhar," ../data/hyphenations.csv; } | column -t -s,
+	% su-bli-nhar (priberam, wiktionary, aulete)
+	% sub-li-nhar (michaelis, portal, dicio)
+
+	% $ { head -n 1 ../data/hyphenations.csv; grep "^auto[a-z]\+," ../data/hyphenations.csv | grep -v ",,,";} | column -t -s,
+
+	\begin{table}
+	\scriptsize
+	\caption{Hyphenation in the dictionaries of words having conflict between morphological and syllabic information.}
+	\label{tab-mor-syl}
+        \begin{tabular}{ll*{6}{c}}
+	\toprule
+	    word                   & hyphenation  & \multicolumn{6}{c}{dictionary} \\
+             &                                    & michaelis & priberam & wikitionary & aulete & portal & dicio \\
+	\midrule
+        \multirow{2}{*}{sublinhar} & su-bli-nhar  &           & x        & x           & x      &        &       \\
+				   & sub-li-nhar  & x         &          &             &        & x      &       \\
+	\multirow{2}{*}{reiniciar} & rei-ni-ci-ar &           &          & x           &        & x      &       \\
+				   & re-i-ni-ci-ar & x        & x        &             & x      &        & x     \\
+	\bottomrule
+	\end{tabular}
+	\end{table}
 
@@
 
-    \item[Abbreviations, Acronyms, or Initialisms:] Whether for efficiency, 
-	convenience, clarity or jargon, it is usual the usage of a shortening 
-	version of a word or a phrase. 
-	Abbreviation a way to shorten a word of phrase. Some examples in our
-	Portuguese corpus are: 
-	\emph{etc.}\footnote{Latin expression \emph{et cetera}, meaning 
-	`and other similar things'.}, 
+    \item[Abbreviations, Acronyms, or Initialisms:] 
+       Whether for efficiency, convenience, clarity, or specialized jargon, 
+       it is common to use shortened versions of words or phrases. Abbreviation is a method employed to achieve this shortening. In our Portuguese corpus, we find examples such as 
+       \emph{etc.}\footnote{Latin expression \emph{et cetera}, meaning `and other similar things'.}, 
        \emph{Dr.}\footnote{\emph{doutor} (doctor, person with PhD title, but popularly used to designate an erudite individual)}, 
@@
        \emph{ed.}\footnote{\emph{edição} (edition)}, 
-	\emph{s.n.}\footnote{sine nomine, Latin expression meaning `without a name', 
-	mostly used in the context of publishing.}.
-	Initialism consists of a set of initial 
-	letters of words that form an shortened version. They are not always 
-	understood by the set of hyphenation rules described in this work, 
-	since they do not follow orthographic (or phonotactic) standards of 
-	the language. In the corpus, it is possible to find some abbreviations, 
-	such as \emph{SESC}\footnote{Serviço Social do Comércio}, 
+       \emph{s.n.}\footnote{sine nomine, Latin expression meaning `without a name', mostly used in the context of publishing.}.
+
+       Another form of abbreviation is an initialism, which consists of using
+       the initial letters of words to create a shortened version. However,
+       initialisms may not always conform to the hyphenation rules described in
+       this work, as they do not necessarily follow the orthographic or
+       phonotactic standards of the language. Some abbreviations found in the
+       corpus include 
+       \emph{SESC}\footnote{Serviço Social do Comércio}, 
        \emph{INSS}\footnote{\emph{Instituto Nacional do Seguro Social} (National Institute of Social Security)}, 
@@
        \emph{UFRJ}\footnote{Universidade Federal do Rio de Janeiro}.
-	Acronym is a type of abbreviation that shortens a phrase by combining
-	the first letter (or letters) of each word, creating a new pronounceable word.
-	Some example from the corpus are: 
+
+       Acronyms are a specific type of abbreviation where the first letters (or
+       groups of letters) of each word are combined to form a new pronounceable
+       word. In the corpus, we encounter examples like 
        \emph{Anatel}\footnote{\emph{Agência Nacional de Telecomunicações} (National Telecommunications Agency)},
@@
        \emph{Mercosul}\footnote{\emph{Mercado Comum do Sul} (Southern Common Market).}.
+
+       These various forms of abbreviation play an important role in written
+       language, providing concise ways to represent longer words or phrases.
+       It is important to note that abbreviations, acronyms, and initialisms
+       are generally treated as single units and are not hyphenated.
+
 \end{description}
@@
 mismarkings. Faced with the errors made by the standard hyphenator, a set of
-\NumberOfNewRules{} rules were established, which reduced the errors to XXXX,
+\num{\NumberOfNewRules} rules were established, which reduced the errors to XXXX,
 with XXXX unmarked hyphenation places and XXX mismarkings.  Such rules are
@@
 
-Foi criado um conjunto de \NumberOfNewRules{} regras para aprimorar as hifenizações no
-português. Analisando um conjunto de 37798 palavras, as regras padrão apresentam
+Foi criado um conjunto de \num{\NumberOfNewRules} regras para aprimorar as hifenizações no
+português. Analisando um conjunto de \num{37798} palavras, as regras padrão apresentam
 1368 erros (1273 pontos de hifenização não marcados e 125 pontos marcados
@@
 there are also words with a similar structure that constitute a diphthong, such
-as português, \emph{alguém} and \emph{linguística}. It is remarkable, of
+as \emph{português}, \emph{alguém} and \emph{linguística}. It is remarkable, of
 course, that the latter are formed by the digraphs \emph{qu-} and \emph{gu-},

### 2023-07-31 scripts/dicstats.sh
update dicstats.sh

@@ -2,10 +2,18 @@
 
 if [ $# -eq 0 ]
 then
+    # number of words that have at least one hyphenation found
     tail -n +2 ../data/hyphenations.csv | grep -Pv "[,]{5}$" | wc -l | cut -d' ' -f1
     #cat hyphenations.csv | grep -vP "^[^,][,]{5}" | wc -l | cut -d' ' -f1
 else
-    N=$1
-    N=$((N+1))
-    tail -n +2 ../data/hyphenations.csv | awk -F, '{cnt=0; for(i=1; i<=NF; i++) if($i != "") cnt++;}{print NF,cnt}' | sort | uniq -c | grep -P "[0-9]+ 7 $N" | sed 's/^ *//g' | cut -d' ' -f1
+    if [[ $1 =~ ^-?[0-9]+$ ]]; then
+	if [ $1 -lt 0 ]; then
+	    wc -l ../data/hyphenations.csv | cut -d' ' -f1
+	else
+	    # number of words that have N hyphenations found
+	    N=$1
+            N=$((N+1))
+            tail -n +2 ../data/hyphenations.csv | awk -F, '{cnt=0; for(i=1; i<=NF; i++) if($i != "") cnt++;}{print NF,cnt}' | sort | uniq -c | grep -P "[0-9]+ 7 $N" | sed 's/^ *//g' | cut -d' ' -f1
+	fi
+    fi
 fi

### 2023-08-02 scripts/fixerrors.sh
adding fix errors script to fix some errors in hyphenations.csv file

@@ -1,0 +1,34 @@
+#!/bin/bash
+
+# 1) removes empty space and underscore from each field.
+#
+# 2) check if the field has a hyphenated word (we consider that a string with
+# more that 4 characters, no dash and at least two vowels non contiguous is a
+# word that was not hyphenated)
+#
+# 3) check if the field value, after removing the dashes, has the righteous word
+#
+# 4) print the fields after those tests
+#
+# usage:
+# ./fixerrors.sh ../data/hyphenations.csv > /tmp/hyphenations.csv
+# diff --suppress-common-lines ../data/hyphenations.csv /tmp/hyphenations.csv | more
+# cp /tmp/hyphenations.csv ../data/hyphenations.csv
+
+FILE=$1
+awk -F, '
+	BEGIN{OFS=FS}
+	NR == 1 { print; }
+	NR > 1 {
+	    printf "%s%s", $1, OFS; 
+	    for (i=2;i<=NF;i++) {
+		gsub(/[_ ]/, "", $i);
+		if (length($i)>4 && $i !~ /-/ && $i ~ /[aeiou][^aeiou]+[aeiou]/)
+		    $i="";
+		str=$i; 
+		gsub("-","",str); 
+		if(str==$1) printf "%s", $i;
+    	        if (i < NF) printf "%s", OFS;
+		else printf "%s", RS;
+		} 
+	}' $FILE

### 2023-08-02 scripts/hyphenationagreements.sh
fix hyphagreements

@@ -1,45 +1,31 @@
 #!/bin/bash
 
 # https://unix.stackexchange.com/questions/609866/regular-awk-easily-sort-array-indexes-to-output-them-in-the-chosen-order
-cat ../data/hyphenations.csv | 
-awk -F "," '{
-   delete a; delete xa; delete idxs;
-   for(i=2; i<=NF; i++) if($i) a[$i]+=1;
-   #for(aa in sa) printf "%s(%d)\t",aa,a[aa]; if(length(a)>0) print ""
+tail -n +2 ../data/hyphenations.csv | 
+awk '
+   BEGIN {FS=OFS=","}
+   {
+   delete hyph_list; delete n_tuple;  
+   for(i=2; i<=NF; i++) if($i) hyph_list[$i]+=1;
+   #for(h in hyph_list) printf "%s(%d)\t",h,hyph_list[h]; if(length(h)>0) print ""
 
-   for(aa in a) xa[a[aa]]=aa;
+   #for(aa in a) xa[a[aa]]=aa;
    #for(x in xa) printf "%s :: %d ",xa[x],x;
-   
-   n = sort(xa,idxs,"-r")    
-   for (i=1; i<=n; i++) {
-        idx = idxs[i]
-	printf "%s(%d)%s", xa[idx], idx, (i<n ? OFS : ORS)
+   c = 0;
+   for(h in hyph_list) {
+       c++;
+       n_tuple[c] = "(" hyph_list[h] "," h ")"
+   }
+   n = length(n_tuple);
+   asort(n_tuple)
+   #for (i = 1; i <= n; i++) print n_tuple[i];
+   for (i = n; i >= 1; i--) {
+       gsub(/[\(\)]/, "", n_tuple[i])
+       split(n_tuple[i], parts, ",")
+       #print parts[2] "," parts[1]
+       printf "%s(%d)%s", parts[2], parts[1], (i>1 ? OFS : ORS)
    }
 
    } 
- 
-   function sort(arr, idxs, args,      i, str, cmd) {
-      for (i in arr) {
-         gsub(/\047/, "\047\\\047\047", i)
-         str = str i ORS
-      }
-
-      cmd = "printf \047%s\047 \047" str "\047 |sort " args
-
-      i = 0
-      while ( (cmd | getline idx) > 0 ) {
-         idxs[++i] = idx
-      }
-
-      close(cmd)
-
-      return i
-   }    
-   ' |
[…]

### 2023-08-02 scripts/gethyphenationagreements.sh
updating gethyphenationagreements.sh

@@ -1,3 +1,3 @@
 #!/bin/bash
 
-cat ../data/hyphagreements | cut -d' ' -f1 | grep "($1)" | wc -l 
+cat ../data/hyphagreements | cut -d',' -f1 | grep "($1)" | wc -l 

### 2023-08-02 scripts/hyphenationagreementscsvfile.sh
adding hyphenationagreementscsvfile.sh

@@ -1,0 +1,16 @@
+#!/bin/bash
+
+temp_file=$(mktemp)
+trap 'rm -f "$temp_file"' EXIT ERR INT
+cat ../data/hyphagreements | while read line; do word=$(echo "${line%%(*}" | tr -d '-'); echo "$word,$line"; done > "$temp_file"
+cat "$temp_file" | 
+    awk -F, '
+    BEGIN{OFS=FS} 
+    {
+	for (i=1; i<=NF; i++) gsub("^[[:space:]-]+|[[:space:]-]+$", "", $i);
+	if(NF>max_nf) max_nf=NF; rows[NR]=$0
+    } 
+    END{for(i=1;i<=NR;i++){n=split(rows[i],cols,","); for(j=1;j<max_nf;j++){printf "%s%s", cols[j], OFS} print cols[j]}}
+    ' > ../data/hyphagreements.csv
+
+

### 2023-08-02 scripts/checkaccents.sh
updates in checkaccents

@@ -6,7 +6,7 @@
 patterns=(
     "^(?!.*-).*[aáeéêoóô]s?" # monosyllables
     "^(?=(.*-){1,}).*([áãéêóô]s?|é[iumn]s?|óis?|ão|ões) 0$" # oxytone
-    "^(?=(.*-){1,}).*([i]s?|u[mn]?s?|o[mn]s?|[rlxn]|ão?s?|ps|[aeou][iu]s?|i[eu]s?) 1$" # paroxytone
+    "^(?=(.*-){1,}).*([i]s?|u[mn]?s?|o[mn]s?|[rlxn]|ão?s?|ps|[aeo]is?|[ui][iu]s?|i[aeou]s?|u[ao]s?) 1$" # paroxytone 
     "^(?=(.*-){2,}).* 2$" # proparoxytone 
     "^([^íú]+-)?[íú]s?(-.*|\s)\d$" # hiatus with í or ú
     )
@@ -20,10 +20,9 @@ awk -F\- '
 ' "${1:-/dev/stdin}" |
     while read line;
     do
-	echo $line
 	for pattern in "${patterns[@]}"; do
-	    if grep -q "$pattern" <<< "$line"; then
-		echo "$line"
+	    if grep -qP "$pattern" <<< "$line"; then
+		cut -d' ' -f1 <<< "$line"
 		break
 	    fi
 	done
@@ -58,7 +57,7 @@ awk -F\- '
 #   terminadas em i/is"us, r, l, x, n, um/uns, ão/ãos, ã/ãs, ps, on/ons:
 #   júri/júris"vírus, caráter, têxtil, tórax, hífen (hifens não tem acento),
 #   fórum/fóruns"órgão/órgãos, ímã/ímãs, bíceps, próton/prótons.  Nas palavras
-#   paroxítonas terminadas em ditongo oral (ai"au, ei, eu, ie, iu, oi, ou, ui), 
+#   paroxítonas terminadas em ditongo oral (ai, ei, oi, ui, ia, ie, io, iu, au, eu, ou, iu)
 #   acentua-se a vogal da sílaba tônica: ágeis"imundície, lírio, túneis, tênue, 
 #   jóquei"nódoa, cerimônia, história.
 # 

### 2023-08-02 scripts/flagwronghyphens.sh
update flagwronghyphens.sh

@@ -5,6 +5,7 @@
 #
 
 V="[aeiouáàãâéêíóõôú]" # vowel
+A="[áàãâéêíóõôú]" # accented vowel
 C="[^-aeiouáàãâéêíóõôú]" # consonant
 CH="[^-aeiouáàãâéêíóõôúh]" # consonant not h
 
@@ -28,7 +29,16 @@ pattern=$(join_by \| "${patterns[@]}")
 process_input() {
   while read line
   do
-   echo $line | grep -P "${pattern}"
+    errline=$(echo "$line" | grep -P "${pattern}")
+    if [[ -z "${errline// }" ]] && [[ "$line" =~ $A ]]; then
+	acc=$(echo "$line" | ./checkaccents.sh)
+	if [[ -z "$acc" ]]; then
+	    errline="$line"
+	fi
+    fi
+    if [[ ! -z "${errline// }" ]]; then
+	echo "$errline"
+    fi
   done
 }
 

### 2023-10-13 article/article.tex
revision of section 1

@@
 \section{Introduction}\label{sec-intro}
+
 Hyphenation in text wrapping was not used for a long time. Words should fit
-entirely in a line, or they would be broken in arbitrary places. First no
-marker at all was used to sign the wrapping of a word, what could create
-confusion and undesirable meaning. Therefore, ortographers advocated for the
-use of a sign to indicate this break. Portuguese faced the same gradual
-introduction of a hyphenation sign to mark words wrapping across lines. Even
-though the usage of a hyphenation sign ($=$) was advocated by orthographers
-\cite{gandavo1574}, few documents used such sign until the end of the 18th
-century \cite{araujo2015}.
+entirely in a line, or they would be broken in arbitrary places.  Initially, no
+markers were used to indicate word wrapping, leading to potential confusion and
+unintended interpretations. As a result, orthographers advocated for the
+introduction of a sign to indicate such breaks. Portuguese faced the same
+gradual introduction of a hyphenation sign to mark words wrapping across lines.
+Even though the usage of a hyphenation sign ($=$) was advocated by
+orthographers \cite{gandavo1574}, few documents used such sign until the end of
+the 18th century \cite{araujo2015}.
 
 In some cases, hyphenation hinders smooth reading and should be avoided in
-child literature, for example. In opposition, large or small spaces between
-words also impose difficulty in the reading process, making hyphenation
-fundamental when texts use short line lengths. As a line gets shorter, the
-number of breaking candidates between words decreases, leading to awkward
-spaces between words and among letters. For that matter, automatic hyphenation
-plays an important role in good typesetting.
+child literature. In opposition, both excessive spacing and insufficient
+spacing between words also impose difficulty in the reading process, making
+hyphenation fundamental when texts use short line lengths. As a line gets
+shorter, the number of breaking candidates between words decreases, leading to
+awkward spaces between words and among letters. For that matter, automatic
+hyphenation plays an important role in good typesetting.
 
@@
 %on the page.
-Line height and length, paragraph length, font size and typeface,
-letter and word-spacing, are some factors which influence the text legibility
+Line height and line length, paragraph length, font size and typeface,
+letter-spacing, and word-spacing are some factors which influence the text legibility
 and readability. Space between words should not be too long creating lakes and
@@
 circumstance. The correct syllabifications are \emph{bi-sa-vô},
-\emph{i-na-ti-vo}, and \emph{i-nobs-tan-te}\footnote{The rule of syllable
+\emph{i-nobs-tan-te}\footnote{The rule of syllable
 division could lead to two possible partitions: \emph{i-nobs-tan-te} and
-\emph{in-obs-tan-te}, but the first is preferable.}, where the prefixes are
-split into two syllables. But, as pointed previously, it is preferable to keep
-morphemes together rather than splitting them apart, therefore we should
-favor the hyphenation \emph{bisa-vô} over \emph{bi-savô}, and \emph{ina-tivo}
-over \emph{i-nativo}. This last example could also lead to a misunderstanding
+\emph{in-obs-tan-te}, but the first is preferable.}, and \emph{i-na-ti-vo}, 
+where the prefixes are split into two syllables. 
+But, as pointed out previously, it is preferable to keep
+morphemes together rather than splitting them apart. Therefore we should
+favor the hyphenation \emph{bisa-vô} over \emph{bi-savô}, \emph{inobs-tante} 
+over \emph{i-nobstante}, and \emph{ina-tivo} over \emph{i-nativo}. 
+This last example could also lead to a misunderstanding
 since the word \emph{nativo} (\emph{native} in English) emerges from this word
@@
 
-Each language has its own hyphenation rules. They might be grouped into two
-groups: those which hyphenation is driven by morphology (etymology) and those
-driven by pronunciation. An algorithmic approach might use a logic system to
-analyse words and apply the hyphenation rules of a given language. An algorithm
-must be written for each language, as hyphenation rules vary extensively.
-Although a logic system might be fast and compact, inevitably it will have to
-deal with exceptions through hard-coded rules.
-
-The automation of this process might use a dictionary based approach, which
-will restrict the hyphenation possibilities to those entries in the dictionary,
-an algorithmic base approach, which might be applied to whatever sequence found
-in a text, or a mix of both approaches. 
-%An algorithmic approach might use a logic system to analyse words and apply
-%the hyphenation rules of a given language. 
-A rule base model might include the recognition of prefixes,
-suffixes, morphemes, or some sequences suitable for the inclusion of a break.
-Another approach is the usage of pattern matching. Given a corpus of
-hyphenation examples in a language, it is necessary to identify those sequence
-of letters that define a point where hyphenation is suitable or not. Patterns
-might include prefixes, suffixes, exceptions and special hyphenation rules of a
-given language. Such approach might be used for different languages, by
-providing hyphenation examples in a target language to extract patterns and
-rules.
-
-Only the analysis of immediate surrounding might not be enough to determine a
-potential break point. For example, consider \emph{dem-o-crat} and \emph{de-moc-ra-cy},
-where immediate surrounding of \emph{e} does not suffice to determine the break
-location. Even after chosen patterns that makes hyphenation pretty
-straightforward, there might be exceptions. Consider the sequence \emph{tion}. It
-seems safe to always place a break before this pattern. However, the word
-\emph{cation} is hyphenated as \emph{cat-ion}, making is etymology determinant to the way
-this word will be split.
-
-A word with different meanings may be hyphenated differently according to its
-meaning. `For instance, the Swedish word form \emph{glassko} has three different
+Each language has its hyphenation rules, which can be categorized into two
+groups: those driven by morphology (etymology) and those driven by
+pronunciation.  An algorithmic approach employs a logical system to analyze
+words and apply the hyphenation rules of a specific language. Since hyphenation
+rules vary significantly between languages, a unique algorithm must be
+developed for each one. While a logic-based system can be efficient and
+compact, it still needs to address exceptions through hard-coded rules.
+
+%The automation of this process might use a dictionary based approach, which
+%will restrict the hyphenation possibilities to those entries in the dictionary,
+%an algorithmic base approach, which might be applied to whatever sequence found
+%in a text, or a mix of both approaches. 
+%%An algorithmic approach might use a logic system to analyse words and apply
+%%the hyphenation rules of a given language. 
+%A rule base model might include the recognition of prefixes,
+%suffixes, morphemes, or some sequences suitable for the inclusion of a break.
+%Another approach is the usage of pattern matching. Given a corpus of
+%hyphenation examples in a language, it is necessary to identify those sequence
+%of letters that define a point where hyphenation is suitable or not. Patterns
+%might include prefixes, suffixes, exceptions and special hyphenation rules of a
+%given language. Such approach might be used for different languages, by
+%providing hyphenation examples in a target language to extract patterns and
+%rules.
+
+The automation of this process can employ various approaches, including:
+\begin{description}
+\item[Dictionary-Based Approach:] This method restricts hyphenation
+    possibilities to entries found in the dictionary.
+\item[Algorithmic-Based Approach:] This approach can be applied to any sequence
+    encountered in a text.
+\item[Rule-Based Model:] This model recognizes prefixes, suffixes, morphemes,
+    or specific sequences suitable for hyphenation.
+\item[Pattern Matching:] By using a corpus of hyphenation examples in a
+    language, this approach identifies letter sequences that determine suitable
+    hyphenation points. Patterns encompass prefixes, suffixes, exceptions, and
+    special hyphenation rules of the language.
+\item[Mixed Approach:] This approach combines two or more of the previously
+    described methods to enhance hyphenation accuracy and flexibility.
+\end{description}
+
+Analyzing only the immediate surroundings may not always suffice to determine a
+potential hyphenation point. For instance, consider \emph{de-moc-ra-cy} and \emph{dem-o-crat},
+where the immediate surrounding of the letter \emph{e} does not provide a clear
+indication of the hyphenation point. 
+Even when facing chosen patterns that typically make hyphenation
+straightforward, exceptions can arise. Take the sequence \emph{tion}, for example.
+It may seem logical to place a break before this pattern, but the word \emph{cation}
+is hyphenated as \emph{cat-ion}, highlighting the influence of etymology on the way
+a word is split.
+
+A word with multiple meanings may have distinct hyphenations based on its intended meaning.
+`For instance, the Swedish word form \emph{glassko} has three different
 meanings, and can be hyphenated as \emph{glas-sko} (glass shoe),
@@
 \emph{glass-sko} (ice cream shoe).' \cite{nemeth2006}. In Portuguese, the
-word \emph{sublinha} might be hiphenated in two different forms:
-\emph{su-bli-nha} when representing the inflected form of verb
-\emph{sublinhar} (underline as a verb) or \emph{sub-li-nha} when refering
+word \emph{sublinha} might be hiphenated in two different ways:
+\emph{su-bli-nha} when representing the inflected form of the verb
+\emph{sublinhar} (to underline) or \emph{sub-li-nha} when refering
 to the line under (underline as a noun).
@@
 
-Machine learning approach was used to hyphenate Norwegian text
-\cite{kristensen2001}. It was found that the \TeX{} approach, in general,
-performed better then a neural network. Both approaches had similar
-performance on finding the correct hyphenation points and avoiding wrong
-hyphenation points on a small word list (the neural network performed slightly
-better on finding the correct hyphenation points). Nonetheless, \TeX{} approach overcame
-the neural network on a large word list, regarding the avoidance of wrong
-hyphenations.
-
-The original \TeX{} hyphenation algorithm was introduced by Knuth 1977
-\cite{knuth1977}. It was focused on the English language and used three main
-rules:
+Machine learning techniques were employed to hyphenate Norwegian text
+\cite{kristensen2001}. The study revealed that, overall, the \TeX{} approach
+outperformed a neural network.  Both methods demonstrated similar performance
+in identifying correct hyphenation points and minimizing incorrect hyphenations
+when tested on a small word list (with the neural network slightly
+outperforming in correctly recognizing hyphenation points).  However, when
+tested on a larger word list, the \TeX{} approach proved superior in avoiding
+incorrect hyphenations compared to the neural network.
+
+The original \TeX{} hyphenation algorithm, introduced by Knuth in 1977
+\cite{knuth1977}, primarily focused on the English language and employed three
+main rules:
 \begin{enumerate*}[label=(\arabic*)]
@@
  \item prefix removal; and 
- \item vowel-consonant-consonant-vowel (VCCV) breaking. 
+ \item the Vowel-Consonant-Consonant-Vowel (VCCV) breaking rule\footnote{The 
+     VCCV rule in hyphenation patterns, places the syllable boundary between 
+     two consecutive consonants when they appear between two vowels. For example, 
+     in the word \emph{sudden}, the syllable break occurs between the \emph{d} and 
+     the second \emph{d}, making it \emph{sud-den}. 
+     The VCCV pattern is a relatively common syllable division pattern in English.
+     This rule ensures accurate 
+     hyphenation, maintaining word readability and pronunciation when words are 
+     split at the end of a line in printed text.}. 
 \end{enumerate*}
-Tests showed it could find
-40\% of the allowed hyphen locations \cite{liang1983}. 
-The hyphenation algorithm proposed by Frank M. Liang and adopted in \TeX{}
-utilizes competing patterns. The \TeX{}82 algorithm employs five alternating
-levels of hyphenating and inhibiting patterns. The program for pattern
-generation, known as PATGEN, was created by Liang \cite{liangbreitenlohner1999}
-and has been utilized to generate hyphenating patterns for numerous languages
+Tests demonstrated that it could identify 40\% of allowable hyphen locations
+\cite{liang1983}.  The \TeX{} hyphenation algorithm later adopted the approach
+proposed by Frank M. Liang, which involves competing patterns.  The \TeX{}82
+algorithm employs five alternating levels of hyphenating and inhibiting
+patterns. The program for pattern generation, known as PATGEN, was created by
+Liang \cite{liangbreitenlohner1999} and has been utilized to generate
+hyphenating patterns for numerous languages
 \cite{sojka1995,sojka1995a,sojka2005thesis,sojka2003,scannell2003}. It involves
@@
 % Antonio Martins de ARAÚJO and Toru MARUYAMA
+
+Moreover, as mentioned earlier, certain hyphenations may be preferred for
+stylistic reasons, or to avoid ambiguity, or for better reading experience.
+Some words might have multiple hyphenations, depending on the intended meaning.
+In such cases, \TeX{} may not efficiently address the hyphenation challenge, as
+it would necessitate case-by-case handling.
 

### 2023-10-16 article/article.tex
updates

@@
 hyphenation algorithm. In languages like German, hyphenation can lead to letter
-changes or insertions. Additionally, compound words lack hyphens, resulting in
+change or insertion. Additionally, compound words lack hyphens, resulting in
 extended letter sequences without visible separation and even repetitions of
@@
 \emph{Schiff-fahrt}, preserving the \emph{f}s from each word that makes this
-compound. The hyphenation should insert a \emph{f} that is not part of the
+compound. The hyphenation should insert an \emph{f} that is not part of the
 written form. That was not a problem for the old written form of the word:
@@
 \section{Patterns for \TeX{} hyphenation}\label{sec-patt4TeX} 
-The patterns used in \TeX{} hyphenation are of the form: \texttt{4z1z2}. Each
+If we consider only the Latin alphabet, with no diacritcs, the patterns used 
+in \TeX{} hyphenation are of the form: \texttt{\^{}\textbackslash{}.?[0-9]?([a-zA-Z]+[0-9]?)+\textbackslash{}.?\$},
+where we have described it using a regular expression\footnote{
+    Regular expressions (regex) are powerful search patterns used in text processing to find, match, and manipulate strings of text.
+They are a fundamental tool in programming and are supported in many programming languages.
+    The regex given here uses the Perl syntax and might be broken in the following
+    parts: \texttt{\^{}} and \texttt{\$} mark the start and end of the string;
+    \texttt{\textbackslash{}.?} specifies an optional period; \texttt{[0-9]?} allows for an optional single digit;
+    \texttt{([a-zA-Z]+[0-9]?)+} matches sequences of letters (both uppercase and lowercase) interleaved with optional digits.
+}. 
+One example of such pattern is \texttt{4z1z2}. Each
 pattern is made of a sequence of letters and numbers. Odd numbers indicate a

### 2023-11-08 article/article.tex
updating text

@@
 \usepackage{longtable}
-\usepackage[style=alphabetic, backend=biber]{biblatex}
+\usepackage[style=authoryear, backend=biber]{biblatex}
 \addbibresource{references.bib}
@@
 \usepackage{fancyvrb}
+\usepackage{soul}
 \usepackage{siunitx}
@@
 \usepackage{booktabs}
+
+\usepackage[textsize=tiny,textwidth=3.5cm,color=blue!10]{todonotes}
 
@@
 %\immediate\write18{../scripts/hyphenationagreements.sh > ../data/hyphagreements}
-\captureshell*[\NumberOfSixAgrees]{../scripts/gethyphenationagreements.sh 6}
-\captureshell*[\NumberOfFiveAgrees]{../scripts/gethyphenationagreements.sh 5}
+\captureshell*[\NumberOfSixAgrees]{cat ../data/hyphenations6.dic | wc -l}
+% run to update hyphen5 dic
+%\immediate\write18{../scripts/get51.sh > ../data/hyphenations5.dic}
+%\immediate\write18{../manualcorrections.sh ../data/hyphenations5.dic}
+\captureshell*[\NumberOfFiveAgrees]{cat ../data/hyphenations5.dic | wc -l} %#{../scripts/gethyphenationagreements.sh 5}
+\captureshell*[\NumberOfSixFiveAgrees]{cat ../data/hyphenations6.dic ../data/hyphenations5.dic | wc -l}
 \captureshell*[\NumberOfFourAgrees]{../scripts/gethyphenationagreements.sh 4}
@@
 \captureshell*[\NumberOfOneAgrees]{../scripts/gethyphenationagreements.sh 1}
+
+\captureshell*[\ExceptionRulesCV]{../scripts/listrules.sh 1}
+\captureshell*[\ExceptionRulesLR]{../scripts/listrules.sh 2[lr]}
+\captureshell*[\ExceptionRulesCLNH]{../scripts/listrules.sh [cln]2h}
+\captureshell*[\ExceptionRulesThree]{../scripts/listrules.sh 3}
+\captureshell*[\ExceptionRulesFour]{../scripts/listrules.sh 4}
+
+\captureshell*[\NumberOfAppProp]{grep ':' ../data/hyphenations.csv | wc -l} % number of apparent proparoxytones
+
+% number of words correctly hyphenated using default TeX rules when analysing the words in hyphenations6.dic
+\captureshell*[\NumberOfCorrectSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -c}
+
+% number of words with wrong hyphenations using default TeX rules when analysing the words in hyphenations6.dic
+\captureshell*[\NumberOfWrongSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -w}
+
+% number of words with missing hyphenations using default TeX rules when analysing the words in hyphenations6.dic
+\captureshell*[\NumberOfMissingSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -m}
 
@@
 Even though the usage of a hyphenation sign ($=$) was advocated by
-orthographers \cite{gandavo1574}, few documents used such sign until the end of
-the 18th century \cite{araujo2015}.
+orthographers \parencite{gandavo1574}, few documents used such sign until the end of
+the 18th century \parencite{araujo2015}.
 
@@
 \emph{glass-ko} (ice cream cow) and in the non-standard way,
-\emph{glass-sko} (ice cream shoe).' \cite{nemeth2006}. In Portuguese, the
+\emph{glass-sko} (ice cream shoe)' \parencite{nemeth2006}. In Portuguese, the
 word \emph{sublinha} might be hiphenated in two different ways:
@@
 Machine learning techniques were employed to hyphenate Norwegian text
-\cite{kristensen2001}. The study revealed that, overall, the \TeX{} approach
+\parencite{kristensen2001}. The study revealed that, overall, the \TeX{} approach
 outperformed a neural network.  Both methods demonstrated similar performance
@@
 
-The original \TeX{} hyphenation algorithm, introduced by Knuth in 1977
-\cite{knuth1977}, primarily focused on the English language and employed three
+The original \TeX{} hyphenation algorithm, introduced by %Knuth in 1977
+\textcite{knuth1977}, primarily focused on the English language and employed three
 main rules:
@@
 Tests demonstrated that it could identify 40\% of allowable hyphen locations
-\cite{liang1983}.  The \TeX{} hyphenation algorithm later adopted the approach
+\parencite{liang1983}.  The \TeX{} hyphenation algorithm later adopted the approach
 proposed by Frank M. Liang, which involves competing patterns.  The \TeX{}82
@@
 patterns. The program for pattern generation, known as PATGEN, was created by
-Liang \cite{liangbreitenlohner1999} and has been utilized to generate
+%Liang 
+\parencite{liangbreitenlohner1999} and has been utilized to generate
 hyphenating patterns for numerous languages
-\cite{sojka1995,sojka1995a,sojka2005thesis,sojka2003,scannell2003}. It involves
+\parencite{sojka1995,sojka1995a,sojka2005thesis,sojka2003,scannell2003}. It involves
 sweeping a database of hyphenated words in a language to identify both
@@
 Mozilla Firefox, Mozilla Thunderbird, Google Chrome, macOS, InDesign, memoQ,
-Opera, Affinity Publisher, among others \cite{hunspell}). Hunspell uses \TeX{}
-hyphenation rules \cite{hunspellhyphen,levien1998}, making \TeX{} hyphenation
+Opera, Affinity Publisher, among others \parencite{hunspell}). Hunspell uses \TeX{}
+hyphenation rules \parencite{hunspellhyphen,levien1998}, making \TeX{} hyphenation
 widespread in the computer world. That is a result of \TeX{} approach
 simplicity and versatility.  The algorithm works effectively, as it already
-supports rules for 66 languages \cite{texhyphenrules}, and offers the
+supports rules for 66 languages \parencite{texhyphenrules}, and offers the
 flexibility to create rules for any currently unsupported languages.
@@
 \emph{mei-stens} became \emph{meis-tens}. Some problems in compound word
-hyphenation in \TeX{} are discussed in \cite{sojka1995a}.
+hyphenation in \TeX{} are discussed in \textcite{sojka1995a}.
 
@@
 \section{Patterns for \TeX{} hyphenation}\label{sec-patt4TeX}
-If we consider only the Latin alphabet, with no diacritcs, the patterns used 
-in \TeX{} hyphenation are of the form: \texttt{\^{}\textbackslash{}.?[0-9]?([a-zA-Z]+[0-9]?)+\textbackslash{}.?\$},
+
+To simplify, if we consider only the Latin alphabet, with no diacritcs, the patterns used 
+in \TeX{} hyphenation are of the form: \texttt{\^{}\textbackslash{}.?[0-9]?([a-z]+[0-9]?)+\textbackslash{}.?\$},
 where we have described it using a regular expression\footnote{
@@
     \texttt{\textbackslash{}.?} specifies an optional period; \texttt{[0-9]?} allows for an optional single digit;
-    \texttt{([a-zA-Z]+[0-9]?)+} matches sequences of letters (both uppercase and lowercase) interleaved with optional digits.
+    \texttt{([a-z]+[0-9]?)+} matches sequences of lowercase letters interleaved with optional digits.
 }. 
@@
 where we see the hyphen placed between the two \emph{z}'s and no hyphen before,
-nor after the \emph{z}'s. The pattern may also use period symbol (\emph{.}) to
-indicate word boundaries. The pattern \texttt{.s2h2} applies to beginning of
+nor after the \emph{z}'s. Patterns may also use period symbol (\emph{.}) to
+indicate word boundaries. The pattern \texttt{.sh2} applies to beginning of
 words, implying that the \emph{s} and the \emph{h} should stick together in
@@
 \emph{e} in the sequence \emph{sher}. A rule at a higher level, as
-\texttt{.s2h2}, implies an exception to the lower level rule. When we see
-\emph{sher}, in the beginning of a word, the rule \texttt{.s2h2} applies and
+\texttt{.sh2}, implies an exception to the lower level rule. When we see
+\emph{sher}, in the beginning of a word, the rule \texttt{.sh2} applies and
 hyphenation proposed by the lower level rule \texttt{sh1er} should be hindered.
 That is the case in the hyphenation of the word \emph{Sher-lock}. The full
-example is provided in \Cref{sherlockhyphenation}, where we might see all
-English rules that takes place in the hyphenation of \emph{Sher-lock}.
-
+example is provided in \Cref{sherlockhyphenation}, where we might see all pertinent
+English rules taking place in the hyphenation of \emph{Sher-lock} and \emph{sher-iff}.
+
+\noindent\begin{minipage}{\linewidth}
 \begin{lstlisting}[language={}, caption={Example of rules applyied in the
@@
 \end{lstlisting}
+\end{minipage}
 
@@
 and 7 are used to define alternative values for the special characters `.', `-'
-and `*'.  The following lines use a delimiter to enclose each 'letter' of the
+and `*'.  The following lines use a delimiter to enclose each `letter' of the
 desired language alphabet, including its alternative representations.  The
@@
 hyphenation (pattern matching) purpose. As another example, see the next line
-which defines the character $\pi$ (taken from \cite{haralambous2021}):
+which defines the character $\pi$ (taken from \textcite{haralambous2021}):
 \begin{verbatim} 
@@
 
-The dictionary file is a list of pre-hyphenated words from which PATGEN
-extracts patterns to create hyphenation rules. To ensure PATGEN's proper
-functionality, the translation file and the dictionary file must utilize the
-same encoding, even if it is a multi-byte encoding. The translation file
-describes how to handle byte sequences representing a glyph, and PATGEN will
-work seamlessly when there are at most 243 symbols in the given language.
+PATGEN also needs a dictionary file, which is a list of pre-hyphenated words
+from which PATGEN extracts patterns to create hyphenation rules. To ensure
+PATGEN's proper functionality, the translation file and the dictionary file
+must utilize the same encoding, even if it is a multi-byte encoding. The
+translation file describes how to handle byte sequences representing a glyph,
+and PATGEN will work seamlessly when there are at most 243 symbols in the given
+language.
 
@@
 \section{\TeX{} hyphenation rules for portuguese}\label{sec-tex-hyphen-pt}
-\cite{rezende1987} was the first to create patterns for Portuguese hyphenation
+\textcite{rezende1987} was the first to create patterns for Portuguese hyphenation
 in \TeX{}. The pattern set was last updated in 2015, incorporating
-contributions from José João Dias Almeida \cite{hyphpt}, resulting in a total
+contributions from %José João Dias Almeida 
+\textcite{hyphpt}, resulting in a total
 of 307 rules\footnote{The set of rules for Portuguese hyphenation is short when
@@
 %
-Out of the default \TeX{} rules, 252 follow the pattern \verb|1CV|, which
+Out of the default \TeX{} rules, 252 (82\%) follow the pattern \verb|1CV|, which
 represents the recurring CV syllables in Portuguese.  As for the consonants,
@@
 and \verb|õ|), resulting in these CV patterns that indicate favorable
-hyphenation points before the consonants.  It is worth noting that there might
+hyphenation points before the consonants\footnote{The complete list of these
+252 patterns is given here: \ExceptionRulesCV{}.}. 
+It is worth noting that there might
 be other rules or exceptions in the hyphenation patterns not covered by these
-default rules.  To accommodate exceptions, 23 additional rules were created for
+default rules.  To accommodate exceptions, 20 additional rules were created for
 cases involving consonants \verb|b|, \verb|c|, \verb|d|, \verb|f|, \verb|g|,
 \verb|k|, \verb|p|, \verb|t|, \verb|v|, or \verb|w| followed by \verb|l| or
-\verb|r|; or \verb|c|, \verb|l| or \verb|n| followed by \verb|h|.
-
+\verb|r|\footnote{The 20 additional rules are: \ExceptionRulesLR{}.}
+; and 3 additional rules for \verb|c|, \verb|l| or \verb|n| followed by \verb|h|\footnote{
+Those 3 rules are: \ExceptionRulesCLNH{}.}.
 %
@@
 Moreover, 23 distinct patterns were introduced to indicate hyphenation points
-between vowels or between \verb|c|'s, \verb|r|'s, and \verb|s|'s.
-
+between vowels or between \verb|c|'s, \verb|r|'s, and \verb|s|'s\footnote{
+Those patterns are: \ExceptionRulesThree{}.
+}. 
 %
@@
 \verb|u| and a vowel, with an inhibiting point between the \verb|u| and the
-subsequent vowel.
-
+subsequent vowel\footnote{They are the following: \ExceptionRulesFour{}.}.
+%
 Lastly, there is a single pattern represented as \verb|1-|, denoting that a
@@
 \section{Methodology}\label{sec-methodology}
-To assess the performance of each set of rules, we require a list of correctly
-hyphenated words in Portuguese. 
-We utilized word frequency data to avoid selecting excessively rare words, creating a minimal representative set. 
-A comprehensive list was compiled using data from online dictionaries and
-Portuguese corpora. Additionally, we referred to Portuguese grammars to
-validate hyphenation (\emph{translineation}) rules and manually corrected the data as
-needed.
+
+To assess the performance of each set of rules, we require a collection of
+correctly hyphenated Portuguese words. We employed word frequency data to
+ensure we selected representative, commonly used words, avoiding excessively
+rare ones. Our comprehensive word list was curated using online dictionaries,
+Portuguese corpora, and verified against Portuguese grammars to validate
+hyphenation rules. We also performed manual corrections where necessary.
+We should not expect an entire corpus to follow a set of conventions for a written 
+language nor uniformity among a variety of corpora, especially those harvested from the Internet.
+``It is notoriously difficult to prescribe rules governing the use of a written language; it is even more difficult
+to get people to `follow the rules.' This is in large part due to the nature of written language, in which
+the conventions are not always in line with actual usage and are subject to frequent change'' \parencite[p.~14]{palmer2010}.
 
@@
 instance, the word \emph{como} was consistently hyphenated as \emph{co-mo} in
-all six dictionaries.  Therefore, it contributes to both the counts in the
+all six dictionaries, therefore, it contributes to both the counts in the
 column representing six hyphenations (first column).  On the other hand, the
@@
 NET}, and \emph{Wikipedia}, and hyphenated the words using the original \TeX{}
-TEX hyphenation rules.  Subsequently, we compared the hyphenated results with
+hyphenation rules.  Subsequently, we compared the hyphenated results with
 those obtained from the dictionary. By conducting a thorough performance
@@
 syllabic, and alphabetic systems. Although distinct, these systems can be built
-on an interplay of these categories \cite{coulmas2003}. The principles guiding
-an alphabetic or phonemic writing system vary significantly based on the
-language and its history. Here are some key points worth highlighting:
+on an interplay of these categories \parencite{coulmas2003,palmer2010}. 
+The principles guiding an alphabetic or phonemic writing system vary significantly 
+based on the language and its history. Here are some key points worth highlighting:
 \begin{enumerate}[label=\arabic*)]
@@
 principles.
+Hyphenation is a feature of alphabetic scripts where words are composed of letters, 
+and spaces or hyphens are used to separate words, syllables, or parts of words. 
+Logographic writing systems, such as the Chinese, 
+function differently and do not employ hyphenation \parencite{honorof2006}.
 
@@
 Portuguese employs an alphabetical writing system, which means its spelling is
-guided by phonological principles \cite{cagliari2015}. The correlation between
+guided by phonological principles \parencite{cagliari2015}. The correlation between
 spelling and pronunciation influences word hyphenation, as words are divided
@@
 \emph{walk-ing}, \emph{un-happy}, \emph{work-s}, and \emph{ear-ly}.
-Additionally, other factors, such as the presence of doubled consonants and
-digraphs, also impact word hyphenation in English. Furthermore, there exist
-numerous exceptions that may be categorized into rules.
+Additionally, other factors also impact word hyphenation in English, such as 
+the distinction between long and short vowels, which function within the context
+of open or closed syllable, repectively; and the presence of doubled consonants and
+digraphs \parencite{lin2011,yavas2020}. 
+Furthermore, there exist numerous exceptions that may be categorized into rules.
 % https://english.stackexchange.com/questions/385/what-are-the-rules-for-splitting-words-at-the-end-of-a-line
@@
 Merely stating that an orthographic system is guided by phonological issues
-does not necessarily mean that its hyphenation rules directly mirror the word's
-pronunciation. This is particularly evident in Portuguese, where there is not
-always a one-to-one letter-sound correspondence. The orthographic system
-operates based on its specific rules. For example, consider consonant clusters
-that create a single sound (digraphs) in words like \emph{chave}, \emph{ilha},
-\emph{shampoo}, \emph{carro}, and \emph{pássaro}. While these digraphs are
-pronounced as one sound within a single syllable, their representation in
-writing determines how they are divided. Specifically, different consonants
-within a digraph must remain together, whereas identical consonants are
-separated. As a result, we observe hyphenations like \emph{cha-ve},
-\emph{i-lha}, and \emph{sham-poo}, but \emph{car-ro}.
+does not necessarily mean that its hyphenation rules directly mirror the
+phonetic counterpart. This is notably apparent in Portuguese, where a strict
+one-to-one correspondence between letters and sounds is not always observed.
+The orthographic system operates according to its specific rules. For example,
+consider consonant clusters that create a single sound (digraphs) in words like
+\emph{\underline{ch}ave}, \emph{i\underline{lh}a}, \emph{\underline{sh}ampoo}, \emph{ca\underline{rr}o}, and \emph{ma\underline{ss}a}.
+While these digraphs are pronounced as one sound within a single syllable,
+their representation in writing determines how they are divided. Specifically,
+different consonants within a digraph must remain together, whereas identical
+consonants are separated. As a result, we observe hyphenations like
+\emph{cha-ve}, \emph{i-lha}, and \emph{sham-poo}, but \emph{car-ro} and \emph{mas-sa}.
 
@@
 general, follow phonological principles.  According to the Grammar
-\cite{cunha2016,bergstrom2011,cegalla2008}, some rules might still apply:
+\parencite{cunha2016,bergstrom2011,cegalla2008}, some rules might still apply:
 \begin{enumerate}
     \item\label{rule-di-triphthong} diphthong or triphthong should not be split
-	(e.g. \emph{m\underline{\emph{ui}}-to}, \emph{Pa-ra-g\underline{\emph{uai}}});
+	(e.g. \emph{m\underline{ui}-to}, \emph{Pa-ra-g\underline{uai}});
     \item\label{rule-unstressed} the sequences \emph{ia}, \emph{ie}, \emph{io}, \emph{oa}, \emph{ua},
 	\emph{ue} and \emph{uo}, when in final unstressed position, should not be split 
-	(e.g. \emph{gló-r\underline{\emph{ia}}}, \emph{vi-tó-r\underline{\emph{ia}}}, 
-	\emph{cá-r\underline{\emph{ie}}}, \emph{es-pé-c\underline{\emph{ie}}}, 
-	\emph{Má-r\underline{\emph{io}}}, \emph{má-g\underline{\emph{oa}}}, 
-	\emph{ré-g\underline{\emph{ua}}}, \emph{tê-n\underline{\emph{ue}}}, 
-	\emph{con-tí-g\underline{\emph{uo}}}, \emph{am-bí-g\underline{\emph{uo}}});
+	(e.g. \emph{gló-r\underline{ia}}, \emph{vi-tó-r\underline{ia}}, 
+	\emph{cá-r\underline{ie}}, \emph{es-pé-c\underline{ie}}, 
+	\emph{Má-r\underline{io}}, \emph{má-g\underline{oa}}, 
+	\emph{ré-g\underline{ua}}, \emph{tê-n\underline{ue}}, 
+	\emph{con-tí-g\underline{uo}}, \emph{am-bí-g\underline{uo}});
     \item\label{rule-c-clusters} consonant clusters starting a syllable should not be
-	split (e.g. \emph{\underline{\emph{pn}}eu-má-ti-co}, \emph{\underline{\emph{ps}}i-có-lo-go}, 
-	\emph{\underline{\emph{mn}}e-mô-ni-co});
+	split (e.g. \emph{\underline{pn}eu-má-ti-co}, \emph{\underline{ps}i-có-lo-go}, 
+	\emph{\underline{mn}e-mô-ni-co});
     \item\label{rules-digraphs-ns} the digraphs	\emph{ch}, \emph{lh}, \emph{nh}
-	should not be split (e.g. \emph{ra-\underline{\emph{ch}}ar},
-	\emph{a-bro-\underline{\emph{lh}}os}, \emph{ma-\underline{\emph{nh}}ã};
+	should not be split (e.g. \emph{ra-\underline{ch}ar},
+	\emph{a-bro-\underline{lh}os}, \emph{ma-\underline{nh}ã};
     \item\label{rule-guqu} bigrams like \emph{gu} and \emph{qu} whose vowel \emph{u} is not 
 	pronounced are never separated from the vowel or diphthong that follows it 
-	(e.g. \emph{ne-\underline{\emph{gu}e}}, \emph{pe-\underline{\emph{qu}e}});
+	(e.g. \emph{ne-\underline{gue}}, \emph{pe-\underline{que}});
     \item\label{rule-nasalization} since they are digraphs, a vowel and its following 
-	nasalization marker (a graphic nasal consonant) should not be split (e.g. \emph{\underline{\emph{am}}-bição},
-	\emph{m\underline{\emph{an}}-cha});
+	nasalization marker (a graphic nasal consonant) should not be split (e.g. \emph{\underline{am}-bição},
+	\emph{m\underline{an}-cha});
     \item\label{rule-decreasing} decreasing diphthongs should not be split (e.g. 
-	\emph{\underline{\emph{ai}}-ro-so}, \emph{ca-d\underline{\emph{ei}}-ra}, 
-	\emph{o-ra-ç\underline{\emph{ão}}});
+	\emph{\underline{ai}-ro-so}, \emph{ca-d\underline{ei}-ra}, 
+	\emph{o-ra-ç\underline{ão}});
     \item\label{rule-rising} rising diphthong should not be split (e.g.
-	\emph{a-b\underline{\emph{ai}}-xo}; \emph{c\underline{\emph{au}}-te-la}, 
-	\emph{pa-p\underline{\emph{éi}}s}, \emph{cha-p\underline{\emph{éu}}}, 
-	\emph{pre-f\underline{\emph{ei}}-to}, \emph{r\underline{\emph{eu}}-nir},
-	\emph{n\underline{\emph{oi}}-te}; \emph{ca-la-b\underline{\emph{ou}}-ço}, 
-	\emph{as-te-r\underline{\emph{ói}}-de}; 
-	\emph{re-tri-b\underline{\emph{ui}}});
+	\emph{a-b\underline{ai}-xo}; \emph{c\underline{au}-te-la}, 
+	\emph{pa-p\underline{éi}s}, \emph{cha-p\underline{éu}}, 
+	\emph{pre-f\underline{ei}-to}, \emph{r\underline{eu}-nir},
+	\emph{n\underline{oi}-te}; \emph{ca-la-b\underline{ou}-ço}, 
+	\emph{as-te-r\underline{ói}-de}; 
+	\emph{re-tri-b\underline{ui}});
     \item\label{rule-singlev} disyllables whose syllable has a single vowel should 
-	not be split (e.g. \emph{\underline{\emph{a}}to}, \emph{ru\underline{\emph{a}}}, 
-	\emph{\underline{\emph{ó}}dio}, \emph{\underline{\emph{u}}nha});
+	not be split (e.g. \emph{\underline{a}to}, \emph{ru\underline{a}}, 
+	\emph{\underline{ó}dio}, \emph{\underline{u}nha});
     \item\label{rule-orphan} words with more than two syllables, when divided, cannot 
-	isolate a syllable composed of a single vowel (e.g. \emph{\underline{\emph{a}}gos-to}, 
-	\emph{la-go\underline{\emph{a}}}, \emph{\underline{\emph{i}}da-de});
+	isolate a syllable composed of a single vowel (e.g. \emph{\underline{a}gos-to}, 
+	\emph{la-go\underline{a}}, \emph{\underline{i}da-de});
 
@@
 	belongs to a different syllable should be split (e.g.
-	\emph{sa\underline{\emph{-ú-}}de}, \emph{ra\underline{\emph{-i-}}nha}, \emph{d\underline{\emph{o-e}}r},
-	\emph{v\underline{\emph{o-o}}s}), the same procedure is used splitting diphthongs
-	in different syllables (e.g. \emph{c\underline{\emph{ai-ai}}s}) or diphthong and
-	vowel in different syllables (e.g. \emph{en-s\underline{\emph{ai-o}}s});
+	\emph{sa\underline{-ú-}de}, \emph{ra\underline{-i-}nha}, \emph{d\underline{o-e}r},
+	\emph{v\underline{o-o}s}), the same procedure is used splitting diphthongs
+	in different syllables (e.g. \emph{c\underline{ai-ai}s}) or diphthong and
+	vowel in different syllables (e.g. \emph{en-s\underline{ai-o}s});
     \item\label{rule-consonants} consonant sequences, when in different syllables, should
-	be split (e.g. \emph{a\underline{\emph{f-t}}a}, \emph{a\underline{\emph{b-d}}i-car},
-	\emph{re\underline{\emph{s-c}}i-são}, \emph{a\underline{\emph{b-s}}o-lu-to});
+	be split (e.g. \emph{a\underline{f-t}a}, \emph{a\underline{b-d}i-car},
+	\emph{re\underline{s-c}i-são}, \emph{a\underline{b-s}o-lu-to});
     \item\label{rule-digraphs} the following consonant digraphs should be split:
 	\emph{rr}, \emph{ss}, \emph{mm}, \emph{nn}, \emph{sc}, \emph{sç} and
-	\emph{xc} (e.g. \emph{te\underline{\emph{r-r}}a}, \emph{pro-fe\underline{\emph{s-s}}or},
-	\emph{co-mu\underline{\emph{m-m}}en-te}, \emph{co\underline{\emph{n-n}}os-co},
-	\emph{de\underline{\emph{s-c}}er}, \emph{cre\underline{\emph{s-ç}}a}, \emph{e\underline{\emph{x-c}}e-der}).
+	\emph{xc} (e.g. \emph{te\underline{r-r}a}, \emph{pro-fe\underline{s-s}or},
+	\emph{co-mu\underline{\emph{m-m}}en-te}, \emph{co\underline{n-n}os-co},
+	\emph{de\underline{s-c}er}, \emph{cre\underline{s-ç}a}, \emph{e\underline{x-c}e-der}).
 \end{enumerate}
 
-Note that rules \ref{rule-singlev} and \ref{rule-orphan} are fiddling rules in
-\TeX{} hyphenation, since \TeX{} already has directives to avoid hyphenated
+Rules \ref{rule-singlev} and \ref{rule-orphan} are primarily aimed at ensuring
+proper readability of the text, aligning with \TeX{} approach to deal with
 widows and orphans. As mentioned in \Cref{sec-intro}, the variables
 \verb|lefthyphenmin| and \verb|righthyphenmin| are used to control the minimum
-length for fragments of hyphenated words.  For this reason, we will not take
-into account rules \ref{rule-singlev} and \ref{rule-orphan} during the analysis
-and development of the hyphenation rules.
+length for fragments of hyphenated words. For that reason, rules
+\ref{rule-singlev} and \ref{rule-orphan} are fiddling rules in \TeX{}
+hyphenation, and that is not reason to take than in account in our analysis to
+improve Portuguese hyphenation rules. Furthermore, get the full hyphenation of
+words might be useful for text-to-speech applications \cite{libossek2000,trogkanis2010}.
+
+Additionally, it is advisable to refrain from
+splitting disyllables consisting of four letters (e.g., \emph{para},
+\emph{como}, \emph{cede}). This considerations also lead to more aesthetically
+pleasing and intelligible text, and \TeX{}'s control of isolated fragments already
+address this issue.
+
+%Note that rules \ref{rule-singlev} and \ref{rule-orphan} are fiddling rules in
+%\TeX{} hyphenation, since \TeX{} already has directives to avoid hyphenated
+%widows and orphans.  As mentioned in \Cref{sec-intro}, the variables
+%\verb|lefthyphenmin| and \verb|righthyphenmin| are used to control the minimum
+%length for fragments of hyphenated words.  For this reason, we will not take
+%into account rules \ref{rule-singlev} and \ref{rule-orphan} during the analysis
+%and development of the hyphenation rules.
 
@@
 
-To ensure proper hyphenation and readability, certain guidelines should be
-followed. Avoiding a single vowel at the end or start of a line is crucial
-(e.g., \emph{san-guí-nea} should be split only on the provided hyphens,
-avoiding a split that leaves the final vowel \emph{a} alone at the start of a
-new line: \emph{sanguíne-a}). Additionally, it is advisable to refrain from
-splitting disyllables consisting of four letters (e.g., \emph{para},
-\emph{como}, \emph{cede}).  These considerations lead to more aesthetically
-pleasing and intelligible text.
+%To ensure proper hyphenation and readability, certain guidelines should be
+%followed. Avoiding a single vowel at the end or start of a line is crucial
+%(e.g., \emph{san-guí-nea} should be split only on the provided hyphens,
+%avoiding a split that leaves the final vowel \emph{a} alone at the start of a
+%new line: \emph{sanguíne-a}). Additionally, it is advisable to refrain from
+%splitting disyllables consisting of four letters (e.g., \emph{para},
+%\emph{como}, \emph{cede}).  These considerations lead to more aesthetically
+%pleasing and intelligible text.
 
@@
 This systematic approach ensures efficient and accurate extraction of
-hyphenations from various online sources.
+hyphenations from various online sources. The resulting data is stored in a CSV\footnote{
+    Comma-separated values (CSV) is a text file format defined in \href{https://datatracker.ietf.org/doc/html/rfc4180}{RFC 4180}.
+    In CSV, commas are used to separate values, and each line in the file represents a new record. Records consist of fields separated by delimiters, typically a single comma.
+} file named \texttt{hyphenations.csv}.
+
+\subsection{Establishing a gold standard}
+
+To construct our gold standard for hyphenation, we will compare the
+hyphenations offered by all six dictionaries. We'll determine the total count
+of unique hyphenations across these dictionaries using the script
+\texttt{hyphenationagreements.sh}.
+
+As our initial hyphenation reference, we will consider those cases where all
+six dictionaries agree. This list comprises \num{\NumberOfSixAgrees} words,
+and their hyphenations are stored in \texttt{hyphenations6.dic}.
+
+For any disagreement, we must be cautious and examine each case.
+We might be tempted to chose the majority vote approach, selection
+those hyphenations that have the most supporters, but it is unclear 
+how the hyphenations on those online dictionaries were curated, 
+many might use algorithmic approach, leading to potential flaws shared
+among them. 
+For example, 5 dictionaries use the hyphenation 
+\emph{quart-zo} while just one uses the rightful one, \emph{quar-tzo}.
+The same happens with \emph{de-sem-ba-i-nhar} and \emph{de-sem-bai-nhar},
+the former one receiving the majority of the votes, despite being wrong.
+Some strings might accept more than one hyphenation. For example, 
+\emph{sub-li-nha} and \emph{su-bli-nha} represent two different words.
+The former is the substantive \emph{underline} and the latter is a flexed form of the verb \emph{to underline}.
+\todo{Aline, segue a lista dos casos duvidosos que encontrei com votos 5 a 1. Marquei em negrito aqueles
+    que considero ser a forma correta.
+    quart-zo(5), \textbf{quar-tzo}(1) (assim também trocar quart-zi-to por \textbf{quar-tzi-to)}; \textbf{sub-li-nha}(5), \textbf{su-bli-nha}(1); 
+    de-sem-ba-i-nhar(5), \textbf{de-sem-bai-nhar}(1); ap-nei-a(5), \textbf{a-pnei-a}(1); 
+    disp-nei-a(5), dispneia(1) (\textbf{dis-pnei-a}, forma não encontrada nos dicionários); 
+    hi-pe-ral-ge-si-a(5), \textbf{hi-per-al-ge-si-a}(1);
+    in-de-is-cen-te(5), \textbf{in-deis-cen-te}(1); jo-in-vi-len-se(5), \textbf{join-vi-len-se}(1); 
+    ne-er-lan-dês(5), \textbf{neer-lan-dês}(1). Os demais casos de 5 a 1 são proparoxítonas aparentes.
+}
+The procedure to create the second list of hyphenated words was:
+\begin{enumerate*}[label=\arabic*)]
+  \item select those hyphenations agreed by five dictionaries that have no other hyphenation proposal (5 to 0 votes);
+  \item from those that have another proposal, check if it is an apparent proparoxytone,
+      \begin{enumerate*}[label=\alph*)]
+	  \item if it has a diacritic, select the paroxytone option,
+	  \item if not, select the proparoxytone option.
+      \end{enumerate*}
+  \item if it is not an apparent proparoxytone case, select the hyphenation with five votes.
+\end{enumerate*}
+This procedure is implemented in the script \texttt{get51.sh}.
+Just a few hyphenations were manually corrected. They are: \emph{quar-tzo}, 
+\emph{quar-tzi-to}, \emph{su-bli-nha} (was added), \emph{de-sem-bai-nhar},
+\emph{a-pnei-a}, \emph{dis-pnei-a}, \emph{hi-per-al-ge-si-a}, \emph{join-vi-len-se}, and \emph{neer-lan-dês}.
+The final list is stored in \texttt{hyphenations5.dic} and holds \num{\NumberOfFiveAgrees} additional hyphenations.
+Using the two lists created so far, we have in total \num{\NumberOfSixFiveAgrees} hyphenations.
+
+% results from script ./get51.sh
+% cases where majority vote might go wrong:
+% sub-li-nha(5),su-bli-nha(1) % both are valid
+% de-sem-ba-i-nhar(5),de-sem-bai-nhar(1) % de-sem-bai-nhar seems to be the correct choice
+% ap-nei-a(5),a-pnei-a(1) % ??
+% disp-nei-a(5),dispneia(1) or dis-pnei-a?
+% hi-pe-ral-ge-si-a(5),hi-per-al-ge-si-a(1)
+% in-de-is-cen-te(5),in-deis-cen-te(1)
+% jo-in-vi-len-se(5),join-vi-len-se(1)
+% ne-er-lan-dês(5),neer-lan-dês(1)
+% the remaining are apparent proparoxytones
+
+For those hyphenations that have 4 votes, we used basically the same approach
+as before. We noticed many words had only 4 votes (no alternative hyphenation was provided
+by any dictionary), and they were hyphenated as proparoxytones. They were, in fact, 
+apparent proparoxytones. Those cases were easy to target by looking
+for diacritics in the third to last syllable and a sequence \emph{V-V} in the end.
+We transformed those cases into paroxytones by removing the last hyphen.
+The remaining cases, where an alternative hyphenation was found, we checked for
+diacritics, selecting the paroxytone option when found and selection the
+proparoxytone option when not. For the reaming cases with alternative option,
+we simply select the most voted one. This procedure is implemented in script 
+\texttt{get4.sh}.
+
+% analisar os resultados das hifenizações através da análise de frequência das sílabas
+% as silabas de baixa frequência podem ser indicativos de erros... verificar a origem delas
+% cat ../data/hyphenations6.dic ../data/hyphenations5.dic ../data/hyphenations4.dic | tr '-' '\n' | sort | uniq -c | sort -nr > /tmp/syls
+% grep -P "\s+1\s[^0-9]+$" /tmp/syls | tr -d '1' | sed 's/^\s\+//g' | while read syl; do grep "^$syl-\|-$syl-\|-$syl$" ../data/hyphenations6.dic; done > /tmp/rare
+% grep -P "\s+1\s[^0-9]+$" /tmp/syls | tr -d '1' | sed 's/^\s\+//g' | while read syl; do grep "^$syl-\|-$syl-\|-$syl$" ../data/hyphenations5.dic; done >> /tmp/rare
+% grep -P "\s+1\s[^0-9]+$" /tmp/syls | tr -d '1' | sed 's/^\s\+//g' | while read syl; do grep "^$syl-\|-$syl-\|-$syl$" ../data/hyphenations4.dic; done >> /tmp/rare
+% grep -P "\s+1\s[^0-9]+$" /tmp/syls | tr -d '1' | sed 's/^\s\+//g' | while read syl; do grep --color=always "^$syl-\|-$syl-\|-$syl$" <(cat ../data/hyphenations6.dic ../data/hyphenations5.dic ../data/hyphenations4.dic); done | ansi2html > /tmp/rare.html
+
+% fun-ci-o-ná-ri-o > fun-ci-o-ná-rio
+% co-mí-ci-o > co-mí-cio
+% con-vê-ni-o > con-vê-nio
+% cri-té-ri-o > cri-té-rio
+% ple-ná-ri-o > ple-ná-rio
+% cre-di-á-ri-o > cre-di-á-rio
+% es-tá-gi-o > es-tá-gio
+% in-ter-ban-cá-ri-o > in-ter-ban-cá-rio
+% ur-gên-ci-a > ur-gên-cia
+% i-mo-bi-li-á-ri-a > i-mo-bi-li-á-ria
+% re-vo-lu-ci-o-ná-ri-o > re-vo-lu-ci-o-ná-rio
+% ve-ló-ri-o > ve-ló-rio
+% es-có-ci-a > es-có-cia
+% for-mu-lá-ri-o > for-mu-lá-rio
+% or-ça-men-tá-ri-o > or-ça-men-tá-rio
+
+% ag-nós-ti-co(5),a-gnós-ti-co(1)   << ?
+% co-i-bir(5),coi-bir(1)            << both are correct?
+% drui-da(5),dru-i-da(1)            << drui-da is correct, since an hiatus would require an accent dru-í-da
+% flui-do(5),flu-i-do(1)            << as there is no diacritic it should be flui-do
+%					fluido (sem acento) - substantivo: flui-do (ditongo) -- exemplo: O fluido de freio acabou.
+%					fluido (com acento) - forma verbal: flu-í-do (hiato) -- exemplo: A discussão para aprovar reformas no país não tem fluído como esperavam os governantes.
+% sub-li-nha(5),su-bli-nha(1)       << sub-linha or su-blinha (sublinhar) 
+% man-ti-do(5) mantido(1)           << mantido clearly was not hyphenated 
+% quart-zo(5),quar-tzo(1)           << quar-tzo sounds like the correct choice
+% den-ti-frí-ci-o(5),den-ti-frí-cio(1) << it should be marked as apparent proparoxytones but no one did
+
+%compare_strings() {
+%    # Trim leading and trailing whitespace from the first string
+%    string1_trimmed="${1#"${1%%[![:space:]]*}"}"
+%    string1_trimmed="${string1_trimmed%"${string1_trimmed##*[![:space:]]}"}"
+%
+%    # Trim leading and trailing whitespace from the second string
+%    string2_trimmed="${2#"${2%%[![:space:]]*}"}"
+%    string2_trimmed="${string2_trimmed%"${string2_trimmed##*[![:space:]]}"}"
+%
+%    if [ "$string1_trimmed" == "$string2_trimmed" ]; then
+%        return 0  # Strings are equal
+%    else
+%        return 1  # Strings are different
+%    fi
+%}
+
+% grep "(5)" ../data/hyphagreements | grep "(1)" | head | tr -d '()0-9' | while read line; do word1=$(echo $line | cut -d, -f1); word2=$(echo $line | cut -d, -f2); count1=$(grep -o '-' <<< "$word1" | wc -l); count2=$(grep -o '-' <<< "$word2" | wc -l); if [ $count1 -gt $count2 ]; then w1=$(echo $word1 | sed 's/\(.*\)-/\1/'); compare_strings "$w1" "word2"; result=$?; if [ $result -ne 0 ]; then echo "c1: $line $w1 $word2"; od -c <<< "$w1"; od -c <<< "$word2"; fi; elif [ $count1 -lt $count2 ]; then w2=$(echo $word2 | sed 's/\(.*\)-/\1/'); compare_strings "$w2" "word1"; result=$?; if [ $result -ne 0 ]; then echo "c2: $line $word1 $w2"; fi; else compare_strings "$word1" "word2"; result=$?; if [ $result -ne 0 ]; then echo $line; fi; fi; done
+
+After performing all procedures above described to create our golden hyphenation
+dictionary, we might still need manual corrections.
+All manual corrections are written in the file \texttt{replacements.txt} and
+the script \texttt{manualcorrections.sh} is used to perform these corrections.
+
+In some dictionaries, words are usually marked with a colon (`:') to indicate a
+dubious ending, classifying them as `apparent proparoxytones'. In Portuguese,
+words ending in \emph{ea}, \emph{eo}, \emph{ia}, \emph{ie}, \emph{io},
+\emph{ua}, \emph{ue}, or \emph{uo}, with the stressed syllable before these
+endings, can be considered either paroxytones ending in a rising diphthong or
+proparoxytones ending in a hiatus. The words \emph{his-tó-ri:a} and \emph{on-du-la-tó-ri:o}
+are examples of words marked as apparent proparoxytones, meaning they might
+be regarded as paroxytones \emph{his-tó-ria} and \emph{on-du-la-tó-rio} or
+as proparoxytones \emph{his-tó-ri-a} and \emph{on-du-la-tó-ri-o}.
+The script \texttt{hyphenationagreements.sh} might deal with these apparent proparoxytones
+in four different ways: we might keep the hyphenations with the colon mark to
+indicate an apparent proparoxytones; or we might only the paroxytones or only the proparoxytones
+counterpart; or we may count both paroxytones and proparoxytones.
+As there is no consensus in the literature, we have decided to count both
+hyphenations. In our hyphenation dictionary, we have found \NumberOfAppProp{} words
+marked as apparent proparoxytones.
 
@@
 Let us remember that the standard \TeX{} hyphenation rules, proposed by
-\cite{rezende1987,hyphpt}, when tested against a set of \num{\DictionarySize}
+\textcite{rezende1987,hyphpt}, when tested against a set of \num{\DictionarySize}
 words, present 1,368 (????) errors, of which 1,273 (????) correspond to places
@@
 is demonstrated.
+
+% get the error rate from default TeX rules in this dic file
+% ./checkhyphenation.sh correct test
+% ./gocreateresultfile.sh ../data/hyphenations6.dic ../data/default.TeX.pt-br.patterns > ../data/hyphenations6result-default-patterns.dic
+% grep -v "[\.\-]" ../data/hyphenations6result-default-patterns.dic | wc -l
+% 15536
+% NumberOfCorrectSix NumberOfWrongSix NumberOfMissingSix
+% correct: 15536; wrong: 30 (30); missing: 277 (276,1)
+Using the default \TeX{} hyphenation rules we have found \NumberOfCorrectSix{}
+words correctly hyphenated, \NumberOfWrongSix{} words with wrong hyphenation
+points introduced by the default rules, and \NumberOfMissingSix{} words with at
+least a missing hyphenation point (among those words only \texttt{ba-í-a} had
+two missing hyphenation points).
+
+% cat ../data/default.TeX.pt-br.patterns ../data/patch.TeX.pt-br.patterns > ../data/patched-default.TeX.pt-br.patterns
+% ./gocreateresultfile.sh ../data/hyphenations6.dic ../data/patched-default.TeX.pt-br.patterns > ../data/hyphenations6result-patched-patterns.dic
+% ./resultfilemetrics.sh -f ../data/hyphenations6result-patched-patterns.dic -a
+% correct: 15826; wrong: 2 (2); missing: 13 (13)
 
@@
 Let us remember that the standard \TeX{} hyphenation rules, proposed by
-\cite{hyphpt}, amount to XXX errors, in a set of XXXX words.  Among those, XXX
+\textcite{hyphpt}, amount to XXX errors, in a set of XXXX words.  Among those, XXX
 correspond to places where the hyphenation was not carried out and XXX to
@@
 an example in which the application of the rule is demonstrated.
+
+\section{Universal syllabic pattern generation}
+Universal syllabic pattern generation by Jakub Máca, Petr Sojka, Ondřej Sojka (TUG 2023).
 
@@
 
-\item\label{rulegrp_eim} regra: \texttt{e1im} -- reimpresso, coimbra, coimperador
-exceção: \texttt{que2i}, \texttt{te2im} -- queimar, queimadura, teimosia, tirateima
+\item\label{rulegrp_eim} regra: \texttt{e1imp} -- reimpresso%, coimbra, coimperador
+%exceção: \texttt{que2i}, \texttt{te2im} -- queimar, queimadura, teimosia, tirateima
 
@@
 
+\item\label{rulegrp_uo} regra: \texttt{ú1o} -- flúor
+
 \item\label{rulegrp_proi} regra: \texttt{pro1i1b} -- proibição
@@
 
-%\item\label{rulegrp_uo} regra: \texttt{u3ó} -- fluór
-
 \item\label{rulegrp_eo} regra: \texttt{é3o} -- alvéolo
 
-\item\label{rulegrp_ia} regra: \texttt{i4a.}, \texttt{i4e.}, \texttt{i4o.}, \texttt{o4a.}, \texttt{u4a.} -- economia, espécie, vazio, destoa, institua
+\item\label{rulegrp_ia} \st{regra: \texttt{i4a.}, \texttt{i4e.}, \texttt{i4o.}, \texttt{o4a.}, \texttt{u4a.} -- economia, espécie, vazio, destoa, institua}
 

### 2023-11-24 article/article.tex
fix Issue #31
fix Issue #32

@@
 }.
-One example of such pattern is \texttt{4z1z2}. Each
-pattern is made of a sequence of letters and numbers. Odd numbers indicate a
+One example of such pattern is \texttt{4z1z2}, which is composed of a sequence
+of letters and numbers. Odd numbers indicate a
 good hyphenation point, whereas even numbers indicate a bad place to break.
@@
 be other rules or exceptions in the hyphenation patterns not covered by these
-default rules.  To accommodate exceptions, 20 additional rules were created for
-cases involving consonants \verb|b|, \verb|c|, \verb|d|, \verb|f|, \verb|g|,
-\verb|k|, \verb|p|, \verb|t|, \verb|v|, or \verb|w| followed by \verb|l| or
-\verb|r|\footnote{The 20 additional rules are: \ExceptionRulesLR{}.}
-; and 3 additional rules for \verb|c|, \verb|l| or \verb|n| followed by \verb|h|\footnote{
-Those 3 rules are: \ExceptionRulesCLNH{}.}.
-%
+default rules.  To accommodate exceptions, \textcite{rezende1987} proposes the 
+following rules: 
+\begin{itemize}
+    \item 20 rules that created for cases involving consonants \verb|b|, \verb|c|, \verb|d|, \verb|f|, \verb|g|, \verb|k|, \verb|p|, \verb|t|, \verb|v|, or \verb|w| followed by \verb|l| or \verb|r|\footnote{The 20 additional rules are: \ExceptionRulesLR{}.};
+    \item 3 rules for \verb|c|, \verb|l| or \verb|n| followed by \verb|h|\footnote{Those 3 rules are: \ExceptionRulesCLNH{}.}.
     % FILE="../data/default.TeX.pt-br.patterns"; grep -v "^1..$" "$FILE" | grep "2" | awk '{print substr($0, 2, 1)}' | sort | uniq | while read line; doc=$(grep "^1${line}2.$" "$FILE" | tr -d '12' | awk '{print substr($0, 2, 1)}' | tr '\n' ' '); printf "$line $c\n"; done
-%
-Moreover, 23 distinct patterns were introduced to indicate hyphenation points
-between vowels or between \verb|c|'s, \verb|r|'s, and \verb|s|'s\footnote{
-Those patterns are: \ExceptionRulesThree{}.
-}. 
-%
+    \item 23 distinct patterns were introduced to indicate hyphenation points between vowels or between \verb|c|'s, \verb|r|'s, and \verb|s|'s\footnote{Those patterns are: \ExceptionRulesThree{}.}. 
     % FILE="../data/default.TeX.pt-br.patterns"; grep -v "^1..$" "$FILE" | grep -v "2" | grep "3" | wc -l
-%
-Additionally, 8 patterns adhere to the \verb|1[gq]u4V|, signaling beneficial
-hyphenation points before \verb|g| or \verb|q|, followed by a sequence of
-\verb|u| and a vowel, with an inhibiting point between the \verb|u| and the
-subsequent vowel\footnote{They are the following: \ExceptionRulesFour{}.}.
-%
-Lastly, there is a single pattern represented as \verb|1-|, denoting that a
-hyphen indeed serves as a beneficial hyphenation point."
+    \item 8 patterns adhere to the \verb|1[gq]u4V|, signaling beneficial hyphenation points before \verb|g| or \verb|q|, followed by a sequence of \verb|u| and a vowel, with an inhibiting point between the \verb|u| and the subsequent vowel\footnote{They are the following: \ExceptionRulesFour{}.}.
+    \item 1 pattern represented as \verb|1-|, denoting that a hyphen indeed serves as a beneficial hyphenation point.
+\end{itemize}
 

### 2023-11-24 article/article.tex
fix Issue #33
fix Issue #34

@@
 
-\section{Grammar rules for hyphenation in Portuguese}\label{sec-grammar-port}
+\section{Portuguese spelling system}\label{sec-grammar-port}
 
@@
 the distinction between long and short vowels, which function within the context
-of open or closed syllable, repectively; and the presence of doubled consonants and
+of open or closed syllable, respectively; and the presence of doubled consonants and
 digraphs \parencite{lin2011,yavas2020}. 

### 2023-11-24 article/article.tex
fix Issue #35
fix Issue #37
fix Issue #40

@@
 	pronounced are never separated from the vowel or diphthong that follows it 
-	(e.g. \emph{ne-\underline{gue}}, \emph{pe-\underline{que}});
+	(e.g. \emph{U-ru-\underline{guai}}, \emph{pe-\underline{que}});
     \item\label{rule-nasalization} since they are digraphs, a vowel and its following 
@@
 improve Portuguese hyphenation rules. Furthermore, get the full hyphenation of
-words might be useful for text-to-speech applications \cite{libossek2000,trogkanis2010}.
+words might be useful for text-to-speech applications \parencite{libossek2000,trogkanis2010}.
 
@@
 
-In some dictionaries, words are usually marked with a colon (`:') to indicate a
-dubious ending, classifying them as `apparent proparoxytones'. In Portuguese,
-words ending in \emph{ea}, \emph{eo}, \emph{ia}, \emph{ie}, \emph{io},
-\emph{ua}, \emph{ue}, or \emph{uo}, with the stressed syllable before these
-endings, can be considered either paroxytones ending in a rising diphthong or
-proparoxytones ending in a hiatus. The words \emph{his-tó-ri:a} and \emph{on-du-la-tó-ri:o}
-are examples of words marked as apparent proparoxytones, meaning they might
-be regarded as paroxytones \emph{his-tó-ria} and \emph{on-du-la-tó-rio} or
-as proparoxytones \emph{his-tó-ri-a} and \emph{on-du-la-tó-ri-o}.
-The script \texttt{hyphenationagreements.sh} might deal with these apparent proparoxytones
-in four different ways: we might keep the hyphenations with the colon mark to
-indicate an apparent proparoxytones; or we might only the paroxytones or only the proparoxytones
-counterpart; or we may count both paroxytones and proparoxytones.
-As there is no consensus in the literature, we have decided to count both
-hyphenations. In our hyphenation dictionary, we have found \NumberOfAppProp{} words
-marked as apparent proparoxytones.
+In certain dictionaries, words are commonly annotated with a colon (`:') to
+signify a potential variation in pronunciation or production, specifically as a
+diphthong or hiatus, classifying them as `apparent proparoxytones'.  In
+Portuguese, words ending in \emph{ea}, \emph{eo}, \emph{ia}, \emph{ie},
+\emph{io}, \emph{ua}, \emph{ue}, or \emph{uo}, with the stressed syllable
+before these endings, can be considered either paroxytones ending in a rising
+diphthong or proparoxytones ending in a hiatus. The words \emph{his-tó-ri:a}
+and \emph{on-du-la-tó-ri:o} are examples of words marked as apparent
+proparoxytones, meaning they might be regarded as paroxytones \emph{his-tó-ria}
+and \emph{on-du-la-tó-rio} or as proparoxytones \emph{his-tó-ri-a} and
+\emph{on-du-la-tó-ri-o}.  The script \texttt{hyphenationagreements.sh} might
+deal with these apparent proparoxytones in four different ways: we might keep
+the hyphenations with the colon mark to indicate an apparent proparoxytones; or
+we might only the paroxytones or only the proparoxytones counterpart; or we may
+count both paroxytones and proparoxytones.  As there is no consensus in the
+literature, we have decided to count both hyphenations. In our hyphenation
+dictionary, we have found \NumberOfAppProp{} words marked as apparent
+proparoxytones.
 

### 2023-11-29 article/article.tex
fix issue #42
fix #39

@@
       \begin{enumerate*}[label=\alph*)]
-	  \item if it has a diacritic, select the paroxytone option,
-	  \item if not, select the proparoxytone option.
+	  \item if it has a diacritic, select the paroxytone option (e.g. select \emph{po-lí-cia} instead of \emph{po-lí-ci-a} and \emph{pe-rí-neo} instead of \emph{pe-rí-ne-o}),
+	  \item if not, select the proparoxytone option (e.g.
+select \emph{au-to-ri-a} instead of \emph{au-to-ri-a} and \emph{mar-ce-nei-ro} instead of \emph{mar-ce-neiro})\footnote{We just have to make sure we are not selecting those cases where there is a sequence of the form \texttt{[gq]u-[aeio]} (using regex notation), as in \emph{a-pa-zi-gu-ar} and \emph{en-xa-gu-ar}.}.
+	      % [gq]u-[aeio]
       \end{enumerate*}
@@
 	    word                   & hyphenation  & \multicolumn{6}{c}{dictionary} \\
-             &                                    & michaelis & priberam & wikitionary & aulete & portal & dicio \\
+             &                                    & Michaelis & Priberam & Wikitionary & Aulete & Portal & Dicio \\
 	\midrule

### 2023-11-29 scripts/get51.sh

@@ -1,0 +1,96 @@
+#!/bin/bash
+
+compare_strings() {
+    # Trim leading and trailing whitespace from the first string
+    string1_trimmed="${1#"${1%%[![:space:]]*}"}"
+    string1_trimmed="${string1_trimmed%"${string1_trimmed##*[![:space:]]}"}"
+
+    # Trim leading and trailing whitespace from the second string
+    string2_trimmed="${2#"${2%%[![:space:]]*}"}"
+    string2_trimmed="${string2_trimmed%"${string2_trimmed##*[![:space:]]}"}"
+
+    if [ "$string1_trimmed" == "$string2_trimmed" ]; then
+        return 0  # Strings are equal
+    else
+        return 1  # Strings are different
+    fi
+}
+
+
+contains_diacritics() {
+    string="$1"
+
+    # Define a regular expression to match diacritic characters
+    diacritics_regex='[áéíóúÁÉÍÓÚàèìòùÀÈÌÒÙäëïöüÄËÏÖÜâêîôûÂÊÎÔÛãẽĩõũÃẼĨÕŨ]'
+
+    if echo "$string" | grep -q -P "$diacritics_regex"; then
+        return 0  # The string contains diacritic characters
+    else
+        return 1  # The string does not contain diacritic characters
+    fi
+}
+
+grep "(5)" ../data/hyphagreements | grep -v "(1)" | grep -v "(2)" | tr -d '()0-9' > ../data/hyphenations5.dic
+
+grep "(5)" ../data/hyphagreements | 
+    grep "(1)\|(2)" | 
+while read line; do 
+  cline=$(echo $line | tr -d '()0-9')
+  word1=$(echo $cline | cut -d, -f1); 
+  word2=$(echo $cline | cut -d, -f2); 
+  count1=$(grep -o '-' <<< "$word1" | wc -l); 
+  count2=$(grep -o '-' <<< "$word2" | wc -l); 
+  #echo "$word1 $count1 --- $word2 $count2";
+  if [ $count1 -gt $count2 ]; then 
+    w1=$(echo $word1 | sed 's/\(.*\)-/\1/'); 
+    compare_strings "$w1" "$word2"; 
+    result=$?;
+    if [ $result -ne 0 ]; then
+      echo "$word1"
+      #echo "c1: $line --->[$w1]x[$word2]";
+    else # apparent proparoxytone
[…]

### 2024-04-18 article/article.tex
updates

--- 2023-11-24 article/article.tex
@@
 
-\usepackage[textsize=tiny,textwidth=3.5cm,color=blue!10]{todonotes}
+%\usepackage[textsize=tiny,textwidth=3.5cm,color=blue!10]{todonotes}
 
@@
 %%%%%%%
+
+\usepackage{rotating}
+\usepackage{bytefield}
 
@@
 words and apply the hyphenation rules of a specific language. Since hyphenation
-rules vary significantly between languages, a unique algorithm must be
+rules vary significantly between languages, an algorithm must be
 developed for each one. While a logic-based system can be efficient and
@@
 Unfortunately, certain hyphenation rules cannot be implemented using the \TeX{}
-hyphenation algorithm. In languages like German, hyphenation can lead to letter
+hyphenation algorithm. For example, in German, hyphenation can lead to letter
 change or insertion.  Additionally, compound words lack hyphens, resulting in
@@
 the hyphenation \emph{Bäk-ker} for the word \emph{Bäcker}, \emph{Zuk-ker} for
-the word \emph{Zucker} and \emph{pak-ken} for the word \emph{packen}. Now those
+the word \emph{Zucker} and \emph{pak-ken} for the word \emph{packen}. Nowadays, those
 words are hyphenated as \emph{Bä-cker}, \emph{Zu-cker} and \emph{pa-cken},
@@
 One example of such pattern is \texttt{4z1z2}, which is composed of a sequence
-of letters and numbers. Odd numbers indicate a
-good hyphenation point, whereas even numbers indicate a bad place to break.
-The given example states that the sequence has a good breaking point between
-the first and the second \emph{z} and an hyphenation should be inhibited before
-the first \emph{z} and after the second \emph{z}. For example, the hyphenation
-of the word \emph{piz-za}, \emph{fiz-zle} and \emph{mez-zanine} use this rule,
-where we see the hyphen placed between the two \emph{z}'s and no hyphen before,
-nor after the \emph{z}'s. Patterns may also use period symbol (\emph{.}) to
-indicate word boundaries. The pattern \texttt{.sh2} applies to beginning of
-words, implying that the \emph{s} and the \emph{h} should stick together in
-beginning of a word and an hyphenation should also be inhibited after the
-\emph{h}. For example, this pattern is used in \emph{Sher-lock}.
+of letters and numbers. In general, we use characters/symbols from the language
+alphabet, along with Hindu-Arabic numbers, to express either hyphenation
+facilitation or inhibition.  Odd numbers indicate a good hyphenation point,
+whereas even numbers indicate a bad place to break.  The given example states
+that the sequence has a good breaking point between the first and the second
+\emph{z} and an hyphenation should be inhibited before the first \emph{z} and
+after the second \emph{z}. For example, the hyphenation of the word
+\emph{piz-za}, \emph{fiz-zle} and \emph{mez-zanine} use this rule, where we see
+the hyphen placed between the two \emph{z}'s and no hyphen before, nor after
+the \emph{z}'s. Patterns may also use period symbol (\emph{.}) to indicate word
+boundaries. The pattern \texttt{.sh2} applies to beginning of words, implying
+that the \emph{s} and the \emph{h} should stick together in beginning of a word
+and an hyphenation should also be inhibited after the \emph{h}. For example,
+this pattern is used in \emph{Sher-lock}.
 
@@
 example is provided in \Cref{sherlockhyphenation}, where we might see all pertinent
-English rules taking place in the hyphenation of \emph{Sher-lock} and \emph{sher-iff}.
+English rules taking place in the hyphenation of \emph{Sher-lock}.
 
@@
 
-A pattern will consist of a string made of characters (from the language
+In summary, a pattern will consist of a string made of characters (from the language
 alphabet) possibly with a number in between, expressing the
-hyphenation/inhibition level and possibly word boundaries marker (the period)
-at the pattern edges. When there is no number between characters in a pattern,
+hyphenation/inhibition level. Occasionally word boundaries marker (the period)
+is used at the pattern edges. When there is no number between characters in a pattern,
 a zero is assumed, which means \emph{undefined} and no hyphenation point will
@@
 
-PATGEN utilizes a list of hyphenated words to define rules at various levels
-and lengths, based on the patterns found in the data. It starts with short
+PATGEN utilizes a list of hyphenated words to extract patterns and use them to define rules at various levels and lengths.
+It starts with short
 patterns and incrementally increases their length until reaching the maximum
@@
 them are reserved for the digits 0-9 and the characters `.', `-', and `*'. The
-remaining 243 are used to represent symbols of the given language.  To run
+remaining 243 are used to represent symbols of a given language.  To run
 PATGEN, a translation file is necessary. This file defines the values of
@@
 and 7 are used to define alternative values for the special characters `.', `-'
-and `*'.  The following lines use a delimiter to enclose each `letter' of the
+and `*'.  
+\begin{center}
+\begin{bytefield}[endianness=little,bitwidth=0.11111\linewidth,boxformatting={\centering}]{7}
+\bitheader[lsb=1]{1-7} \\
+\bitbox{2}{lefthyphenmin} & \bitbox{2}{righthyphenmin} & \bitbox{1}{.} & \bitbox{1}{-} & \bitbox{1}{*} \\
+\end{bytefield}
+\end{center}
+The following lines use a delimiter to enclose each `letter' of the
 desired language alphabet, including its alternative representations.  The
@@
 language can occupy as many positions as necessary, as long as the reserved
-value for the delimiter is not used in the symbol's definition.  Consider the
+value for the delimiter is not used in the symbol's definition. The defining lines ends
+when the delimiter appears twice in a roll. Consider the
 following example for defining the letter `e' in Portuguese:
-\begin{verbatim}
-XeXEXéXêXÉXÊX\'{e}X\^{e}X\'{E}X\^{E}XX 
-\end{verbatim}
-It represents the many ways in which the letter `e' might be found: lowercase,
+\verb|XeXEXéXêXÉXÊX\'{e}X\^{e}X\'{E}X\^{E}XX|.
+\newcommand{\bitlabel}[2]{%
+    \bitbox[]{#1}{%
+	\raisebox{0pt}[4ex][0pt]{%
+	    \turnbox{45}{\fontsize{7}{7}\selectfont#2}%
+	}%
+    }%
+}
+\vspace{5ex}
+\begin{center}
+\begin{bytefield}[bitwidth=1.9em,boxformatting={\centering\tiny}]{20}
+\bitlabel{1}{delimiter} & \bitlabel{1}{letter e} &
+\bitlabel{1}{delimiter} & \bitlabel{1}{letter E} &
+\bitlabel{1}{delimiter} & \bitlabel{1}{letter é} &
+\bitlabel{1}{delimiter} & \bitlabel{1}{letter ê} &
+\bitlabel{1}{delimiter} & \bitlabel{1}{letter É} &
+\bitlabel{1}{delimiter} & \bitlabel{1}{letter Ê} &
+\bitlabel{1}{delimiter} & \bitlabel{1}{TeX sequence for é} &
+\bitlabel{1}{delimiter} & \bitlabel{1}{TeX sequence for ê} &
+\bitlabel{1}{delimiter} & \bitlabel{1}{TeX sequence for É} &
+\bitlabel{1}{delimiter} & \bitlabel{1}{TeX sequence for Ê} \\
+\bitheader[lsb=1]{1-20} \\
+\bitbox{1}{X} & \bitbox{1}{e} & \bitbox{1}{X} & \bitbox{1}{E} &
+\bitbox{1}{X} & \bitbox{1}{é} & \bitbox{1}{X} & \bitbox{1}{ê} &
+\bitbox{1}{X} & \bitbox{1}{É} & \bitbox{1}{X} & \bitbox{1}{Ê} &
+\bitbox{1}{X} & \bitbox{1}{\textbackslash{}'\{e\}} & \bitbox{1}{X} & \bitbox{1}{\textbackslash{}\^{}\{e\}} &
+\bitbox{1}{X} & \bitbox{1}{\textbackslash{}'\{E\}} & \bitbox{1}{X} & \bitbox{1}{\textbackslash{}\^{}\{E\}}
+\end{bytefield}
+\end{center}
+%\begin{verbatim}
+%XeXEXéXêXÉXÊX\'{e}X\^{e}X\'{E}X\^{E}XX 
+%\end{verbatim}
+We have adopted \verb|X| as the delimiter. This line represents the many ways in which the letter `e' might be found: lowercase,
 uppercase, with or without acute or circumflex accents. Note that we have used
 the direct input (using UTF-8 or other encoding that support the accented `e'
-character) and also the compositional counterpart using the escape codes that
-define each accent.  In this definition, we have assumed that the many forms in
+character) and also the compositional counterpart using the appropriate \TeX{} control sequence that
+instructs \TeX{} to place accent on the letter.  In this definition, we have assumed that the many forms in
 which we may find the character \emph{e} will be equivalent for
@@
 which defines the character $\pi$ (taken from \textcite{haralambous2021}):
-\begin{verbatim} 
-#p#P#\varpi ## 
-\end{verbatim}
+\verb|#p#P#\varpi ##|.
+%\begin{verbatim} 
+%#p#P#\varpi ## 
+%\end{verbatim}
 
@@
 \begin{itemize}
-    \item 20 rules that created for cases involving consonants \verb|b|, \verb|c|, \verb|d|, \verb|f|, \verb|g|, \verb|k|, \verb|p|, \verb|t|, \verb|v|, or \verb|w| followed by \verb|l| or \verb|r|\footnote{The 20 additional rules are: \ExceptionRulesLR{}.};
-    \item 3 rules for \verb|c|, \verb|l| or \verb|n| followed by \verb|h|\footnote{Those 3 rules are: \ExceptionRulesCLNH{}.}.
+    \item 20 rules created for cases involving consonants \verb|b|, \verb|c|, \verb|d|, \verb|f|, \verb|g|, \verb|k|, \verb|p|, \verb|t|, \verb|v|, or \verb|w| followed by \verb|l| or \verb|r|\footnote{The 20 additional rules are: \ExceptionRulesLR{}.};
+    \item 3 rules for \verb|c|, \verb|l| or \verb|n| followed by \verb|h|\footnote{Those 3 rules are: \ExceptionRulesCLNH{}.};
     % FILE="../data/default.TeX.pt-br.patterns"; grep -v "^1..$" "$FILE" | grep "2" | awk '{print substr($0, 2, 1)}' | sort | uniq | while read line; doc=$(grep "^1${line}2.$" "$FILE" | tr -d '12' | awk '{print substr($0, 2, 1)}' | tr '\n' ' '); printf "$line $c\n"; done
-    \item 23 distinct patterns were introduced to indicate hyphenation points between vowels or between \verb|c|'s, \verb|r|'s, and \verb|s|'s\footnote{Those patterns are: \ExceptionRulesThree{}.}. 
+    \item 23 distinct patterns were introduced to indicate hyphenation points between vowels or between \verb|c|'s, \verb|r|'s, and \verb|s|'s\footnote{Those patterns are: \ExceptionRulesThree{}.}; 
     % FILE="../data/default.TeX.pt-br.patterns"; grep -v "^1..$" "$FILE" | grep -v "2" | grep "3" | wc -l
-    \item 8 patterns adhere to the \verb|1[gq]u4V|, signaling beneficial hyphenation points before \verb|g| or \verb|q|, followed by a sequence of \verb|u| and a vowel, with an inhibiting point between the \verb|u| and the subsequent vowel\footnote{They are the following: \ExceptionRulesFour{}.}.
+    \item 8 patterns adhere to the \verb|1[gq]u4V| pattern, signaling beneficial hyphenation points before \verb|g| or \verb|q|, followed by a sequence of \verb|u| and a vowel, with an inhibiting point between the \verb|u| and the subsequent vowel\footnote{They are the following: \ExceptionRulesFour{}.};
     \item 1 pattern represented as \verb|1-|, denoting that a hyphen indeed serves as a beneficial hyphenation point.
@@
 \caption{Considering the six dictionaries used, the first line of this table
-presents the number words that a given number of hyphenations were found in the
+presents the number of words that a given number of hyphenations were found in the
 dictionaries. The second line presents the number of words that have a given
@@
 
-There is a diverse array of writing systems, categorized into logographic,
+There is a diverse collection of writing systems, categorized into logographic,
 syllabic, and alphabetic systems. Although distinct, these systems can be built
@@
 digraphs \parencite{lin2011,yavas2020}.
+Although each language has its driving principles for the hyphenation process, 
+multiple factors come into play, leading to various solutions in certain scenarios.
+For instance, in Portuguese, the phonological principle would lead to \emph{hipe-rativo}, while 
+the morphological principle would lead to \emph{hiper-ativo}. Both approaches seem valid
+and are indeed found in online dictionaries\footnote{Looking at words with prefixes, 
+it seems that even on those words, the phonological approach was predominant on hyphenation,
+but we cannot tell if it is a byproduct of automatic hyphenation that might be used
+to hyphenate words on online dictionaries.}.
+Some rather rare words, such as \emph{hiperalgesia}, may not be subject to morphological 
+influences. Since it has a low frequency of occurrence, the individual may not be
+aware of its morphological components and therefore hyphenate it as \emph{hipe-ralgesia}.
+The form \emph{hiper-algesia} could also be accepted, emphasizing its morphological constituents. 
 Furthermore, there exist numerous exceptions that may be categorized into rules.
 % https://english.stackexchange.com/questions/385/what-are-the-rules-for-splitting-words-at-the-end-of-a-line
+
+% $ grep "^hiper[aeiou]" ../data/hyphenations.csv  | grep "-" | grep -o "hi-pe-r[aeiou]\|hi-per-[aeiou]" | sort | uniq -c
+% 16 hi-pe-ra
+%  1 hi-per-a
+% 29 hi-pe-re
+% 20 hi-pe-ri
+%  2 hi-per-i
+%  2 hi-pe-ro
+%  2 hi-pe-ru
 
@@
 consider consonant clusters that create a single sound (digraphs) in words like
-\emph{\underline{ch}ave}, \emph{i\underline{lh}a}, \emph{\underline{sh}ampoo}, \emph{ca\underline{rr}o}, and \emph{ma\underline{ss}a}.
+%\emph{\underline{ch}ave}, 
+\emph{a\underline{ch}ado},
+\emph{i\underline{lh}a}, 
+%\emph{\underline{sh}ampoo}, 
+\emph{su\underline{sh}i},
+\emph{ca\underline{rr}o}, and \emph{ma\underline{ss}a}.
 While these digraphs are pronounced as one sound within a single syllable,
@@
 consonants are separated. As a result, we observe hyphenations like
-\emph{cha-ve}, \emph{i-lha}, and \emph{sham-poo}, but \emph{car-ro} and \emph{mas-sa}.
+%\emph{cha-ve}, 
+\emph{a-cha-do},
+\emph{i-lha}, and 
+%\emph{sham-poo}, 
+\emph{su-shi},
+but \emph{car-ro} and \emph{mas-sa}.
 
@@
 \parencite{cunha2016,bergstrom2011,cegalla2008}, some rules might still apply:
+\begin{itemize}
+    \item[Non-Splitting Rules:]
 \begin{enumerate}
@@
 	\emph{la-go\underline{a}}, \emph{\underline{i}da-de});
-
-    \hspace{10em} \hbox to 5cm{\leaders\hbox to 10pt{\hss . \hss}\hfil}
-
+\end{enumerate}
+
+\item[Splitting Rules:]
+%    \hspace{10em} \hbox to 5cm{\leaders\hbox to 10pt{\hss . \hss}\hfil} 
+\begin{enumerate}[resume]
     \item\label{rule-hiatus} hiatus vowels and those vowel sequences where each vowel
@@
 \end{enumerate}
+\end{itemize}
 
@@
 widows and orphans. As mentioned in \Cref{sec-intro}, the variables
-\verb|lefthyphenmin| and \verb|righthyphenmin| are used to control the minimum
-length for fragments of hyphenated words. For that reason, rules
-\ref{rule-singlev} and \ref{rule-orphan} are fiddling rules in \TeX{}
-hyphenation, and that is not reason to take than in account in our analysis to
-improve Portuguese hyphenation rules. Furthermore, get the full hyphenation of
-words might be useful for text-to-speech applications \parencite{libossek2000,trogkanis2010}.
+\verb|lefthyphenmin| and \verb|righthyphenmin| control the minimum length for
+fragments of hyphenated words.  When those variables are set to values greater
+than one, Rules \ref{rule-singlev} and \ref{rule-orphan} become fiddling rules
+in \TeX{} hyphenation, and they could be disregarded. Notwithstanding, the full
+hyphenation of words is useful, particularly in text-to-speech applications
+\parencite{libossek2000,trogkanis2010}.
 
@@
 \emph{como}, \emph{cede}). This considerations also lead to more aesthetically
-pleasing and intelligible text, and \TeX{}'s control of isolated fragments already
+pleasing and intelligible text, and \TeX{}'s control of isolated fragments,
+through the variables \verb|\lefthyphenmin| and \verb|\righthyphenmin|, already
 address this issue.
@@
 
-Systematizing the rules that guide syllable boundaries and, consequently,
-hyphenation in Portuguese proved to be fundamental for the improvement of the
-\TeX{} hyphenator rules, since they indicate the possible or prohibited contexts
-of hyphenation. Expomos, a seguir, uma análise comparativa...
-
-... to continue
-\vspace{10ex}
-
-\section{Creating the dictionary}
+Systematizing the rules that guide syllable boundaries and hyphenation in
+Portuguese is a fundamental step to understand and improve the \TeX{}
+hyphenation rules. To ensure the accuracy of hyphenation rules and effectively
+compare their results, a hyphenation spelling dictionary serves as an
+indispensable reference. This dictionary provides a comprehensive listing of
+correctly hyphenated words, enabling the computation of the correctness of each
+set of hyphenation rules. By consulting the hyphenation spelling dictionary,
+one can verify whether the hyphenation patterns generated by a set of rules
+align with established standards. This process involves analyzing how well the
+hyphenation rules adhere to the accepted conventions of the language, ensuring
+that they effectively segment words without compromising readability or
+consistency. Moreover, by comparing the results obtained from different sets of
+hyphenation rules against the entries in the spelling dictionary, we can assess
+the efficacy and reliability of each approach. In section \ref{sec-dictionay},
+we will define the specifications of this reference dictionary, outlining its
+role in subsequent rule updates and rules generation.
+
+\section{Creating the dictionary}\label{sec-dictionay}
 
@@
 
-To construct our gold standard for hyphenation, we will compare the
-hyphenations offered by all six dictionaries. We'll determine the total count
+To establish our gold standard for hyphenation, we will compare the
+hyphenations offered by all six dictionaries. First, we will determine the total count
 of unique hyphenations across these dictionaries using the script
-\texttt{hyphenationagreements.sh}.
+\texttt{hyphenation\-agreements.sh}.
+It's worth noting that certain dictionaries annotate words with a colon (`:') to
+indicate potential variations in pronunciation or production.
+Particularly, `apparent proparoxytones' might appear marked by this colon sign, indicating 
+the possibility of a diphthongs or hiatuses in the word ending.
+In Portuguese, words ending in \emph{ea}, \emph{eo}, \emph{ia}, \emph{ie},
+\emph{io}, \emph{ua}, \emph{ue}, or \emph{uo}, with the stressed syllable
+before these endings, can be considered either paroxytones ending in a rising
+diphthong or proparoxytones ending in a hiatus. For instance, words like \emph{his-tó-ri:a}
+and \emph{on-du-la-tó-ri:o} are examples of words marked as apparent
+proparoxytones, suggesting they could be regarded as paroxytones (\emph{his-tó-ria}
+and \emph{on-du-la-tó-rio}) or proparoxytones (\emph{his-tó-ri-a} and
+\emph{on-du-la-tó-ri-o}). The script \texttt{hyphenationagreements.sh} 
+offers four potential approaches to handle these apparent proparoxytones:
+retaining the hyphenations with the colon mark to indicate an apparent proparoxytone; 
+selecting only the paroxytone or only the proparoxytone counterpart; or counting both paroxytones and proparoxytones. 
+Given the lack of consensus in the literature, our initial approach involves 
+counting both hyphenations, and we will detail below how we resolve this issue. 
+In our hyphenation dictionary, we have identified \NumberOfAppProp{} words marked as apparent proparoxytones.
 
 As our initial hyphenation reference, we will consider those cases where all
-six dictionaries agree. This list comprises \num{\NumberOfSixAgrees} words,
-and their hyphenations are stored in \texttt{hyphenations6.dic}.
-
-For any disagreement, we must be cautious and examine each case.
-We might be tempted to chose the majority vote approach, selection
+six dictionaries are in agreement. This comprehensive list comprises
+\num{\NumberOfSixAgrees} words. Their corresponding hyphenations are
+meticulously compiled and stored in the file \texttt{hyphenations6.dic}. This
+curated list serves as a benchmark for evaluating the accuracy and
+effectiveness of hyphenation rules generated through computational methods. It
+will establish a reliable baseline for our hyphenation analysis, enabling us to
+assess and refine our methodologies effectively.
+
+In case of disagreement, we must exercise caution and examine each instance.
+We might be tempted to choose the majority vote approach, simply selecting
 those hyphenations that have the most supporters, but it is unclear 
-how the hyphenations on those online dictionaries were curated, 
-many might use algorithmic approach, leading to potential flaws shared
+how the hyphenations on those online dictionaries were curated; 
+many might use algorithmic approaches, leading to potential flaws shared
 among them. 
 For example, 5 dictionaries use the hyphenation 
-\emph{quart-zo} while just one uses the rightful one, \emph{quar-tzo}.
-The same happens with \emph{de-sem-ba-i-nhar} and \emph{de-sem-bai-nhar},
-the former one receiving the majority of the votes, despite being wrong.
-Some strings might accept more than one hyphenation. For example, 
-\emph{sub-li-nha} and \emph{su-bli-nha} represent two different words.
-The former is the substantive \emph{underline} and the latter is a flexed form of the verb \emph{to underline}.
-\todo{Aline, segue a lista dos casos duvidosos que encontrei com votos 5 a 1. Marquei em negrito aqueles
-    que considero ser a forma correta.
-    quart-zo(5), \textbf{quar-tzo}(1) (assim também trocar quart-zi-to por \textbf{quar-tzi-to)}; \textbf{sub-li-nha}(5), \textbf{su-bli-nha}(1); 
-    de-sem-ba-i-nhar(5), \textbf{de-sem-bai-nhar}(1); ap-nei-a(5), \textbf{a-pnei-a}(1); 
-    disp-nei-a(5), dispneia(1) (\textbf{dis-pnei-a}, forma não encontrada nos dicionários); 
-    hi-pe-ral-ge-si-a(5), \textbf{hi-per-al-ge-si-a}(1);
-    in-de-is-cen-te(5), \textbf{in-deis-cen-te}(1); jo-in-vi-len-se(5), \textbf{join-vi-len-se}(1); 
-    ne-er-lan-dês(5), \textbf{neer-lan-dês}(1). Os demais casos de 5 a 1 são proparoxítonas aparentes.
-}
-The procedure to create the second list of hyphenated words was:
+\emph{quart-zo} while the dictionary Aulete (originally from Portugal) favors the hyphenation \emph{quar-tzo},
+which can be explained by the lack of an epenthetic vowel in European Portuguese\footnote{
+The online dictionary Aulete has its origins on the printed version known as \emph{Dicionário Caldas Aulete}.
+It is a dictionary from Portugal, reflecting the European Portuguese dialect.} \parencite{mateus}.
+% Epêntese Vocálica e Restrições de Acento no Português do Sul do Brasil, Gisela COLLISCHONN  - Universidade Federal do Rio Grande do Sul (UFRGS)
+% https://core.ac.uk/download/pdf/293615216.pdf
+Similarly, \emph{ap-nei-a} or \emph{a-pnei-a} and \emph{disp-nei-a} or \emph{dis-pnei-a} should
+be accepted considering, since there could be an epenthetic vowel (Brazilian Portuguese) or not (European Portuguese).
+The same happens with \emph{hiperalgesia}, already mentioned in Section \ref{sec-grammar-port}.
+Among other examples, we might also highlight \emph{neerlandês}, which appears 
+hyphenated as \emph{ne-er-lan-dês} in five dictionaries and as \emph{neer-lan-dês} in one.
+If we consider its pronunciation, we would prefer the former hyphenation, but the
+first one conforms better to regular written syllables in Portuguese.
+%The same happens with \emph{de-sem-ba-i-nhar} and \emph{de-sem-bai-nhar},
+%the former one receiving the majority of the votes.
+Some strings might accept more than one hyphenation, since they represent different words. For example, 
+\emph{sub-li-nha} and \emph{su-bli-nha}, where the former is the substantive \emph{underline} and the latter is a flexed form of the verb \emph{to underline}.
+%\todo{Aline, segue a lista dos casos duvidosos que encontrei com votos 5 a 1. Marquei em negrito aqueles
+%    que considero ser a forma correta.
+%    quart-zo(5), \textbf{quar-tzo}(1) (assim também trocar quart-zi-to por \textbf{quar-tzi-to)}; \textbf{sub-li-nha}(5), \textbf{su-bli-nha}(1); 
+%    de-sem-ba-i-nhar(5), \textbf{de-sem-bai-nhar}(1); ap-nei-a(5), \textbf{a-pnei-a}(1); 
+%    disp-nei-a(5), dispneia(1) (\textbf{dis-pnei-a}, forma não encontrada nos dicionários); 
+%    hi-pe-ral-ge-si-a(5), \textbf{hi-per-al-ge-si-a}(1);
+%    in-de-is-cen-te(5), \textbf{in-deis-cen-te}(1); jo-in-vi-len-se(5), \textbf{join-vi-len-se}(1); 
+%    ne-er-lan-dês(5), \textbf{neer-lan-dês}(1). Os demais casos de 5 a 1 são proparoxítonas aparentes.
+%}
+
+The procedure to create the second list of hyphenated words involved several steps:
 \begin{enumerate*}[label=\arabic*)]
-  \item select those hyphenations agreed by five dictionaries that have no other hyphenation proposal (5 to 0 votes);
-  \item from those that have another proposal, check if it is an apparent proparoxytone,
+  \item select those hyphenations agreed by five dictionaries, that have no alternative hyphenation proposal (5 to 0 votes);
+  \item from those with alternative proposals, exam whether they constituted apparent proparoxytones (these cases could arise from instances with 5 to 1 votes or 6 to 1 votes, as explained earlier), 
       \begin{enumerate*}[label=\alph*)]
-	  \item if it has a diacritic, select the paroxytone option,
-	  \item if not, select the proparoxytone option.
+	  \item if the word had a diacritic, select the paroxytone option (e.g. \emph{po-lí-cia} instead of \emph{po-lí-ci-a} and \emph{pe-rí-neo} instead of \emph{pe-rí-ne-o}),
+	  \item if not, choose the proparoxytone option (e.g.
+\emph{au-to-ri-a} instead of \emph{au-to-ri-a} and \emph{mar-ce-nei-ro} instead of \emph{mar-ce-neiro})\footnote{We just have to make sure we are not selecting those cases where there is a sequence of the form \texttt{[gq]u-[aeio]} (using regex notation), as in \emph{a-pa-zi-gu-ar} and \emph{en-xa-gu-ar}.}.
+	      % [gq]u-[aeio]
       \end{enumerate*}
-  \item if it is not an apparent proparoxytone case, select the hyphenation with five votes.
+  \item if the word did not fall into the apparent proparoxytone category, select the hyphenation with five votes.
 \end{enumerate*}
-This procedure is implemented in the script \texttt{get51.sh}.
-Just a few hyphenations were manually corrected. They are: \emph{quar-tzo}, 
-\emph{quar-tzi-to}, \emph{su-bli-nha} (was added), \emph{de-sem-bai-nhar},
-\emph{a-pnei-a}, \emph{dis-pnei-a}, \emph{hi-per-al-ge-si-a}, \emph{join-vi-len-se}, and \emph{neer-lan-dês}.
-The final list is stored in \texttt{hyphenations5.dic} and holds \num{\NumberOfFiveAgrees} additional hyphenations.
-Using the two lists created so far, we have in total \num{\NumberOfSixFiveAgrees} hyphenations.
+This procedure was implemented in the script \texttt{get51.sh}. 
+Only a few hyphenations required manual correction, including the following that were added:
+\emph{quar-tzo}, \emph{quar-tzi-to}, \emph{su-bli-nha}, \emph{a-pnei-a}, \emph{dis-pnei-a}, 
+\emph{hi-per-al-ge-si-a}, and \emph{neer-lan-dês}.
+The final list, containing \num{\NumberOfFiveAgrees} additional hyphenations, is stored in \texttt{hyphenations5.dic}, 
+bringing the total number of hyphenations across both lists to \num{\NumberOfSixFiveAgrees}.
 
@@
 
-For those hyphenations that have 4 votes, we used basically the same approach
-as before. We noticed many words had only 4 votes (no alternative hyphenation was provided
-by any dictionary), and they were hyphenated as proparoxytones. They were, in fact, 
-apparent proparoxytones. Those cases were easy to target by looking
-for diacritics in the third to last syllable and a sequence \emph{V-V} in the end.
-We transformed those cases into paroxytones by removing the last hyphen.
-The remaining cases, where an alternative hyphenation was found, we checked for
-diacritics, selecting the paroxytone option when found and selection the
-proparoxytone option when not. For the reaming cases with alternative option,
-we simply select the most voted one. This procedure is implemented in script 
+For those hyphenations with four votes, we adopted a similar approach to the
+one used previously. Many words garnered only four votes, indicating a lack of
+alternative hyphenations provided by any dictionary, and were thus initially
+hyphenated as proparoxytones. These instances were typically distinguished by
+diacritics in the third-to-last syllable and a \emph{V-V} sequence at the end.
+To address this, we converted these words into paroxytones by eliminating the
+final hyphen. In cases where alternative hyphenations were available, we
+assessed the presence of diacritics. If diacritics were detected, we chose the
+paroxytone option; otherwise, we defaulted to the proparoxytone option. In
+instances with multiple alternative options, we selected the option with the
+highest frequency of votes. This procedure is implemented in the script
 \texttt{get4.sh}.
@@
 
-After performing all procedures above described to create our golden hyphenation
-dictionary, we might still need manual corrections.
-All manual corrections are written in the file \texttt{replacements.txt} and
-the script \texttt{manualcorrections.sh} is used to perform these corrections.
-
-In certain dictionaries, words are commonly annotated with a colon (`:') to
-signify a potential variation in pronunciation or production, specifically as a
-diphthong or hiatus, classifying them as `apparent proparoxytones'.  In
-Portuguese, words ending in \emph{ea}, \emph{eo}, \emph{ia}, \emph{ie},
-\emph{io}, \emph{ua}, \emph{ue}, or \emph{uo}, with the stressed syllable
-before these endings, can be considered either paroxytones ending in a rising
-diphthong or proparoxytones ending in a hiatus. The words \emph{his-tó-ri:a}
-and \emph{on-du-la-tó-ri:o} are examples of words marked as apparent
-proparoxytones, meaning they might be regarded as paroxytones \emph{his-tó-ria}
-and \emph{on-du-la-tó-rio} or as proparoxytones \emph{his-tó-ri-a} and
-\emph{on-du-la-tó-ri-o}.  The script \texttt{hyphenationagreements.sh} might
-deal with these apparent proparoxytones in four different ways: we might keep
-the hyphenations with the colon mark to indicate an apparent proparoxytones; or
-we might only the paroxytones or only the proparoxytones counterpart; or we may
-count both paroxytones and proparoxytones.  As there is no consensus in the
-literature, we have decided to count both hyphenations. In our hyphenation
-dictionary, we have found \NumberOfAppProp{} words marked as apparent
-proparoxytones.
+After completing the aforementioned procedures to create our golden hyphenation
+dictionary, manual corrections may still be necessary to ensure its accuracy
+and reliability. These manual adjustments, which encompass the corrections
+described earlier, are documented in the file \texttt{replacements.txt}.
+Utilizing the script \texttt{manualcorrections.sh}, we meticulously apply these
+corrections to refine our hyphenation dictionary and enhance its effectiveness.
 

### 2024-04-18 scripts/get51.sh
updates

@@ -30,10 +30,13 @@ contains_diacritics() {
     fi
 }
 
+# get those 5 x 0 votes
 grep "(5)" ../data/hyphagreements | grep -v "(1)" | grep -v "(2)" | tr -d '()0-9' > ../data/hyphenations5.dic
 
-grep "(5)" ../data/hyphagreements | 
-    grep "(1)\|(2)" | 
+#grep "(5)" ../data/hyphagreements | 
+#    grep "(1)\|(2)" | 
+# get those 5 x 1, 5 x 2 or 6 x 1 votes
+cat <(grep "(5)" ../data/hyphagreements | grep "(1)\|(2)") <(grep "(6)" ../data/hyphagreements | grep "(1)") |
 while read line; do 
   cline=$(echo $line | tr -d '()0-9')
   word1=$(echo $cline | cut -d, -f1); 

### 2024-04-18 scripts/hyphenationagreements.sh

@@ -1,13 +1,43 @@
 #!/bin/bash
 
+valid_strings=("keep" "replace" "paroxytones" "proparoxytones")
+
+if [ $# -lt 1 ]; then
+    echo "Usage: $0 file [-p string]."
+    echo "The -p argument must be one of: ${valid_strings[*]}."
+    echo "  [keep] apparent proparoxytones (default),"
+    echo "  [replace] apparent proparoxytones by both paroxytones and proparoxytones,"
+    echo "  [paroxytones] use only the paroxytones case, or" 
+    echo "  [proparoxytones] use only the proparoxytones case."
+    exit 1
+fi
+
 input_source="${1:-/dev/stdin}"
 
 if [ "$input_source" != "/dev/stdin" ]; then
-    input_source=<(tail -n +2 "$input_source")
+    input_content=$(tail -n +2 "$input_source")
+else
+    input_content=$(cat)
+fi
+
+pstring="keep"
+if [ -n "$2" ] && [ "$2" == "-p" ]; then
+    if [ -n "$3" ]; then
+        provided_string="$3"
+	if [[ " ${valid_strings[*]} " == *" $provided_string "* ]]; then
+            pstring="$provided_string"
+        else
+            echo "Error: Invalid string argument. Must be one of: ${valid_strings[*]}"
+            exit 1
+        fi
+    else
+        echo "Error: The -p flag requires a string argument. Must be one of: ${valid_strings[*]}" 
+        exit 1
+    fi
 fi
 
 # https://unix.stackexchange.com/questions/609866/regular-awk-easily-sort-array-indexes-to-output-them-in-the-chosen-order
-awk '
+awk -v appprop="$pstring" '
    BEGIN {FS=OFS=","}
    {
    delete hyph_list; delete n_tuple;  
@@ -15,11 +45,15 @@ awk '
        # if($i) hyph_list[$i]+=1; 
        if($i) {
 	   # apparent proparoxytone
-	   if ($i ~ /:/) {
-	       hiatus = gensub(":", "-", "g", $i);
-	       diphthong = gensub(":", "", "g", $i);
-	       hyph_list[hiatus]+=1;
-	       hyph_list[diphthong]+=1;
+	   if (appprop != "keep" && $i ~ /:/) {
+	       if (appprop == "replace" || appprop == "proparoxytones") {
+		   hiatus = gensub(":", "-", "g", $i);
+		   hyph_list[hiatus]+=1;
[…]

### 2024-06-06 article/article.tex
updates

--- 2023-11-24 article/article.tex
@@
 \documentclass{article}
+\usepackage[a4paper,margin=2cm,nohead,foot=1cm]{geometry}
 \usepackage[english]{babel}
@@
 
+\usepackage{rotating}
+\usepackage{bytefield}
+%\usepackage{xstring}
+
+% Define a new list environment for rules
+\newlist{rules}{enumerate}{1}
+\setlist[rules,1]{label=\arabic*}
+
+% Custom label format for the rules environment
+\crefname{rulesi}{rule}{rules}
+\Crefname{rulesi}{Rule}{Rules}
+
+% Custom format for multiple references
+\crefformat{rulesi}{rule~#2#1#3}  % Use only the number for single reference
+\crefrangeformat{rulesi}{#3#1#4 to #5#2#6}  % Use the range format for range of references
+\crefmultiformat{rulesi}{rules~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3} % Use the number format for multiple references
+\Crefmultiformat{rulesi}{Rules~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3} % Use the number format for multiple references
+
+% https://tex.stackexchange.com/questions/1230/reference-name-of-description-list-item-in-latex
+\makeatletter
+\let\orgdescriptionlabel\descriptionlabel
+\renewcommand*{\descriptionlabel}[1]{%
+  \let\orglabel\label
+  \let\label\@gobble
+  \phantomsection
+  \edef\@currentlabel{#1}%
+  %\edef\@currentlabelname{#1}%
+  \let\label\orglabel
+  \orgdescriptionlabel{#1}%
+}
+\makeatother
+
 \title{Improving the portuguese hyphenation rules}
@@
 \begin{document}
-\VerbatimFootnotes
+\VerbatimFootnotes % Enable fancyvrb package to work in footnotes
 \maketitle
 
-\captureshell*[\NumberOfDefaultRules]{wc -l ../data/default.TeX.pt-br.patterns | cut -d' ' -f1}
-
-\captureshell*[\NumberOfNewRules]{wc -l ../data/patch.TeX.pt-br.patterns | cut -d' ' -f1}
-
-\captureshell*[\DictionarySize]{../scripts/dicstats.sh} % number of words that have at least one hyphenation
-\captureshell*[\CorpusSize]{../scripts/dicstats.sh -1} % total number of words in the corpus used (same as $ wc -l ../data/hyphenatios.csv)
-
-% https://www.texdev.net/2009/10/06/what-does-write18-mean/
-% number of words that hyphenations were found in N online dictionaries
-\captureshell*[\NumberOfSixHyphens]{../scripts/dicstats.sh 6}  
-\captureshell*[\NumberOfFiveHyphens]{../scripts/dicstats.sh 5}
-\captureshell*[\NumberOfFourHyphen]{../scripts/dicstats.sh 4}
-\captureshell*[\NumberOfThreeHyphens]{../scripts/dicstats.sh 3}
-\captureshell*[\NumberOfTwoHyphens]{../scripts/dicstats.sh 2}
-\captureshell*[\NumberOfOneHyphens]{../scripts/dicstats.sh 1}
-\captureshell*[\NumberOfNoHyphens]{../scripts/dicstats.sh 0}
-% run to update values
-%\immediate\write18{../scripts/hyphenationagreements.sh > ../data/hyphagreements}
-\captureshell*[\NumberOfSixAgrees]{cat ../data/hyphenations6.dic | wc -l}
-% run to update hyphen5 dic
-%\immediate\write18{../scripts/get51.sh > ../data/hyphenations5.dic}
-%\immediate\write18{../manualcorrections.sh ../data/hyphenations5.dic}
-\captureshell*[\NumberOfFiveAgrees]{cat ../data/hyphenations5.dic | wc -l} %#{../scripts/gethyphenationagreements.sh 5}
-\captureshell*[\NumberOfSixFiveAgrees]{cat ../data/hyphenations6.dic ../data/hyphenations5.dic | wc -l}
-\captureshell*[\NumberOfFourAgrees]{../scripts/gethyphenationagreements.sh 4}
-\captureshell*[\NumberOfThreeAgrees]{../scripts/gethyphenationagreements.sh 3}
-\captureshell*[\NumberOfTwoAgrees]{../scripts/gethyphenationagreements.sh 2}
-\captureshell*[\NumberOfOneAgrees]{../scripts/gethyphenationagreements.sh 1}
-
-\captureshell*[\ExceptionRulesCV]{../scripts/listrules.sh 1}
-\captureshell*[\ExceptionRulesLR]{../scripts/listrules.sh 2[lr]}
-\captureshell*[\ExceptionRulesCLNH]{../scripts/listrules.sh [cln]2h}
-\captureshell*[\ExceptionRulesThree]{../scripts/listrules.sh 3}
-\captureshell*[\ExceptionRulesFour]{../scripts/listrules.sh 4}
-
-\captureshell*[\NumberOfAppProp]{grep ':' ../data/hyphenations.csv | wc -l} % number of apparent proparoxytones
-
-% number of words correctly hyphenated using default TeX rules when analysing the words in hyphenations6.dic
-\captureshell*[\NumberOfCorrectSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -c}
-
-% number of words with wrong hyphenations using default TeX rules when analysing the words in hyphenations6.dic
-\captureshell*[\NumberOfWrongSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -w}
-
-% number of words with missing hyphenations using default TeX rules when analysing the words in hyphenations6.dic
-\captureshell*[\NumberOfMissingSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -m}
-
-\newcounter{numberRulesGroups}
+\input{defvariables.tex}
 
@@
 
-\section{Introduction}\label{sec-intro}
-
-Hyphenation in text wrapping was not used for a long time. Words should fit
-entirely in a line, or they would be broken in arbitrary places.  Initially, no
-markers were used to indicate word wrapping, leading to potential confusion and
-unintended interpretations. As a result, orthographers advocated for the
-introduction of a sign to indicate such breaks. Portuguese faced the same
-gradual introduction of a hyphenation sign to mark words wrapping across lines.
-Even though the usage of a hyphenation sign ($=$) was advocated by
-orthographers \parencite{gandavo1574}, few documents used such sign until the end of
-the 18th century \parencite{araujo2015}.
-
-In some cases, hyphenation hinders smooth reading and should be avoided in
-child literature. In opposition, both excessive spacing and insufficient
-spacing between words also impose difficulty in the reading process, making
-hyphenation fundamental when texts use short line lengths. As a line gets
-shorter, the number of breaking candidates between words decreases, leading to
-awkward spaces between words and among letters. For that matter, automatic
-hyphenation plays an important role in good typesetting.
-
-%Automatic hyphenation plays an important role in good typesetting and
-%it is fundamental when a text uses short line lengths. As a line gets
-%shorter, the number of breaking candidates between words decreases,
-%creating awkward spaces between words and among letters.
-
-\TeX{} is a typesetting system which carefully deals with these issues,
-automatically arranging text on a page to create a good reading experience.
-Automatic hyphenation is an important part on this process,
-promoting an even-tempered distribution of elements on the page.
-%Hyphenation is therefore an important part on this process.
-%A good readability depends on an even-tempered distribution of elements
-%on the page.
-Line height and line length, paragraph length, font size and typeface,
-letter-spacing, and word-spacing are some factors which influence the text legibility
-and readability. Space between words should not be too long creating lakes and
-rivers in the text, nor too tight, impairing the legibility and readability.
-
-Another important matter to consider is ambiguities that might be created when
-a word is partitioned during the hyphenation process. In English we should
-avoid hyphenations such as \emph{re-cover}, \emph{re-form}, \emph{re-sign}, \emph{the-rapist},
-\emph{depart-mental}, and \emph{mans-laughter} (in Portuguese, some examples are:
-\emph{de-putada}, \emph{fede-ração}, \emph{acu-mula}, \emph{após-tolo},
-\emph{cú-bico}). Hyphenations that might lead the reader to pronounce a word
-incorrectly should also be prevented. That is the case of
-\emph{considera-tion}, in Enslish (and \emph{pe-rigo} in Portuguese).
-
-In some situations, hyphenation is also a matter of style. Some partitioning
-choices sound better than others. These conflicting alternatives typically
-arises when a words has many possible hyphenation points. Consider
-\emph{ar-chae-ol-o-gist} (\emph{or ar-che-ol-o-gist}), which is preferably partitioned as
-\emph{archae-ologist} (or \emph{arche-ologist}) in opposition to \emph{archaeol-ogist} (or
-\emph{archeol-ogist}) or \emph{archaeolo-gist} (or \emph{archeolo-gist}). It is preferable to keep
-whole morphemes together. In the previous example: \emph{archae} (or \emph{arche}, meaning
-``ancient'', ``primitive'')
-%\footnote{archae- comes from the Ancient Greek ἀρχαῖος (arkhaîos, `ancient',
-%`primitive'), from ἀρχή (arkhḗ, `beginning').}
-%https://en.wiktionary.org/wiki/archae-
-and \emph{-ologist} (``one who studies the topic''). In Portuguese, it is also more
-elegant to avoid splits between double consonants or vowels, even if an
-hyphenation point do exists between those letters. For example,
-\emph{pressu-rizar} is preferable over \emph{pres-surizar} and
-\emph{empreen-dedor} is preferable over \emph{empre-endedor}. Even so,
-exceptions exists, it is preferable to partition \emph{micro-organismo}
-rather than \emph{microor-ganismo} (keeping morphemes together is favored
-over splitting a double vowel). Numerous factors come into play when choosing
-the optimal hyphenation point for a word.
-
-The general rule for Portuguese hyphenation is to split a word into its
-syllables. A syllable is made of a mandatory nucleus, filled by a vowel, and
-optional peripheral consonants (before or after the nucleus). In some
-situations, the syllabic division does not respect the ethnologic constituents.
-The usage of the prefixes \emph{bis-} and \emph{in-} are examples of this
-circumstance. The correct syllabifications are \emph{bi-sa-vô},
-\emph{i-nobs-tan-te}\footnote{The rule of syllable
-division could lead to two possible partitions: \emph{i-nobs-tan-te} and
-\emph{in-obs-tan-te}, but the first is preferable.}, and \emph{i-na-ti-vo}, 
-where the prefixes are split into two syllables. 
-But, as pointed out previously, it is preferable to keep
-morphemes together rather than splitting them apart. Therefore we should
-favor the hyphenation \emph{bisa-vô} over \emph{bi-savô}, \emph{inobs-tante} 
-over \emph{i-nobstante}, and \emph{ina-tivo} over \emph{i-nativo}. 
-This last example could also lead to a misunderstanding
-since the word \emph{nativo} (\emph{native} in English) emerges from this word
-break.
-
-Each language has its hyphenation rules, which can be categorized into two
-groups: those driven by morphology (etymology) and those driven by
-pronunciation.  An algorithmic approach employs a logical system to analyze
-words and apply the hyphenation rules of a specific language. Since hyphenation
-rules vary significantly between languages, a unique algorithm must be
-developed for each one. While a logic-based system can be efficient and
-compact, it still needs to address exceptions through hard-coded rules.
-
-%The automation of this process might use a dictionary based approach, which
-%will restrict the hyphenation possibilities to those entries in the dictionary,
-%an algorithmic base approach, which might be applied to whatever sequence found
-%in a text, or a mix of both approaches. 
-%%An algorithmic approach might use a logic system to analyse words and apply
-%%the hyphenation rules of a given language. 
-%A rule base model might include the recognition of prefixes,
-%suffixes, morphemes, or some sequences suitable for the inclusion of a break.
-%Another approach is the usage of pattern matching. Given a corpus of
-%hyphenation examples in a language, it is necessary to identify those sequence
-%of letters that define a point where hyphenation is suitable or not. Patterns
-%might include prefixes, suffixes, exceptions and special hyphenation rules of a
-%given language. Such approach might be used for different languages, by
-%providing hyphenation examples in a target language to extract patterns and
-%rules.
-
-The automation of this process can employ various approaches, including:
-\begin{description}
-\item[Dictionary-Based Approach:] This method restricts hyphenation
-    possibilities to entries found in the dictionary.
-\item[Algorithmic-Based Approach:] This approach can be applied to any sequence
-    encountered in a text.
-\item[Rule-Based Model:] This model recognizes prefixes, suffixes, morphemes,
-    or specific sequences suitable for hyphenation.
-\item[Pattern Matching:] By using a corpus of hyphenation examples in a
-    language, this approach identifies letter sequences that determine suitable
-    hyphenation points. Patterns encompass prefixes, suffixes, exceptions, and
-    special hyphenation rules of the language.
-\item[Mixed Approach:] This approach combines two or more of the previously
-    described methods to enhance hyphenation accuracy and flexibility.
-\end{description}
-
-Analyzing only the immediate surroundings may not always suffice to determine a
-potential hyphenation point. For instance, consider \emph{de-moc-ra-cy} and \emph{dem-o-crat},
-where the immediate surrounding of the letter \emph{e} does not provide a clear
-indication of the hyphenation point. 
-Even when facing chosen patterns that typically make hyphenation
-straightforward, exceptions can arise. Take the sequence \emph{tion}, for example.
-It may seem logical to place a break before this pattern, but the word \emph{cation}
-is hyphenated as \emph{cat-ion}, highlighting the influence of etymology on the way
-a word is split.
-
-A word with multiple meanings may have distinct hyphenations based on its intended meaning.
-`For instance, the Swedish word form \emph{glassko} has three different
-meanings, and can be hyphenated as \emph{glas-sko} (glass shoe),
-\emph{glass-ko} (ice cream cow) and in the non-standard way,
-\emph{glass-sko} (ice cream shoe)' \parencite{nemeth2006}. In Portuguese, the
-word \emph{sublinha} might be hiphenated in two different ways:
-\emph{su-bli-nha} when representing the inflected form of the verb
-\emph{sublinhar} (to underline) or \emph{sub-li-nha} when refering
-to the line under (underline as a noun).
-
-% hyphenation might change with syntactic function
-% part of speech (PoS)
-
-Machine learning techniques were employed to hyphenate Norwegian text
-\parencite{kristensen2001}. The study revealed that, overall, the \TeX{} approach
-outperformed a neural network.  Both methods demonstrated similar performance
-in identifying correct hyphenation points and minimizing incorrect hyphenations
-when tested on a small word list (with the neural network slightly
-outperforming in correctly recognizing hyphenation points).  However, when
-tested on a larger word list, the \TeX{} approach proved superior in avoiding
-incorrect hyphenations compared to the neural network.
-
-The original \TeX{} hyphenation algorithm, introduced by %Knuth in 1977
-\textcite{knuth1977}, primarily focused on the English language and employed three
-main rules:
-\begin{enumerate*}[label=(\arabic*)]
- \item suffix removal; 
- \item prefix removal; and 
- \item the Vowel-Consonant-Consonant-Vowel (VCCV) breaking rule\footnote{The 
-     VCCV rule in hyphenation patterns, places the syllable boundary between 
-     two consecutive consonants when they appear between two vowels. For example, 
-     in the word \emph{sudden}, the syllable break occurs between the \emph{d} and 
-     the second \emph{d}, making it \emph{sud-den}. 
-     The VCCV pattern is a relatively common syllable division pattern in English.
-     This rule ensures accurate 
-     hyphenation, maintaining word readability and pronunciation when words are 
-     split at the end of a line in printed text.}. 
-\end{enumerate*}
-Tests demonstrated that it could identify 40\% of allowable hyphen locations
-\parencite{liang1983}.  The \TeX{} hyphenation algorithm later adopted the approach
-proposed by Frank M. Liang, which involves competing patterns.  The \TeX{}82
-algorithm employs five alternating levels of hyphenating and inhibiting
-patterns. The program for pattern generation, known as PATGEN, was created by
-%Liang 
-\parencite{liangbreitenlohner1999} and has been utilized to generate
-hyphenating patterns for numerous languages
-\parencite{sojka1995,sojka1995a,sojka2005thesis,sojka2003,scannell2003}. It involves
-sweeping a database of hyphenated words in a language to identify both
-hyphenating and inhibiting patterns, ultimately creating a list of competing
-patterns for that specific language.
-
-The effective hyphenation of words by \TeX{} will actually depends on the following factors:
-\begin{enumerate*}[label=(\arabic*)]
-    \item document language, which will determine which set of patterns to apply;
-    \item characters used, since some might block hyphenation at their edges;
-    \item the value of the internal variables \verb|lefthyphenmin| and \verb|righthyphenmin|\footnote{
-	The variables \verb|lefthyphenmin| and \verb|righthyphenmin| are language dependant and
-	are defined in \emph{tlpobj} files (\verb|/usr/local/texlive/20XX/tlpkg/tlpobj/hyphen-xxxxxx.tlpobj|). 
-	Default values varies in the range from 1 to 3. 
-    	English and Portuguese, for example, use \verb|lefthyphenmin=2| and \verb|righthyphenmin=3|.},
-	% ls /usr/local/texlive/2023/tlpkg/tlpobj/*.tlpobj | while read -r filename; do grep -Po "lefthyphenmin=[0-9]\s+righthyphenmin=[0-9]" $filename; done | tr '\t' ' ' | tr -s ' ' | sort | uniq -c
-	%      17 lefthyphenmin=1 righthyphenmin=1
-        %       6 lefthyphenmin=1 righthyphenmin=2
-        %       1 lefthyphenmin=1 righthyphenmin=3
-        %      49 lefthyphenmin=2 righthyphenmin=2
-        %       9 lefthyphenmin=2 righthyphenmin=3
-        which defines the minimum sequence length of characters at the left and right borders
-        before any hyphenation is allowed.
-\end{enumerate*}
-
-Despite the fact that \TeX{} hyphenation algorithm and rules are old, they are,
-to these days, the most frequently used approach, even outside the \TeX{}'s
-world. The grounds for this is Hunspell, a spell checker and morphological
-analyzer that is adopted in many softwares (e.g. LibreOffice, OpenOffice.org,
-Mozilla Firefox, Mozilla Thunderbird, Google Chrome, macOS, InDesign, memoQ,
-Opera, Affinity Publisher, among others \parencite{hunspell}). Hunspell uses \TeX{}
-hyphenation rules \parencite{hunspellhyphen,levien1998}, making \TeX{} hyphenation
-widespread in the computer world. That is a result of \TeX{} approach
-simplicity and versatility.  The algorithm works effectively, as it already
-supports rules for 66 languages \parencite{texhyphenrules}, and offers the
-flexibility to create rules for any currently unsupported languages.
-
-Unfortunately, certain hyphenation rules cannot be implemented using the \TeX{}
-hyphenation algorithm. In languages like German, hyphenation can lead to letter
-change or insertion. Additionally, compound words lack hyphens, resulting in
-extended letter sequences without visible separation and even repetitions of
-the same letter, as seen in examples like \emph{Wasserrinne} and
-\emph{Schifffahrt}.  Furthermore, the German spelling reform made some changes,
-making it necessary to create a different set of rules for German hyphenation.
-For example, the word \emph{Schiffahrt} should be hyphenated as
-\emph{Schiff-fahrt}, preserving the \emph{f}s from each word that makes this
-compound. The hyphenation should insert an \emph{f} that is not part of the
-written form. That was not a problem for the old written form of the word:
-\emph{Schifffahrt}. Also, the old hyphenating rules of German grammar stated
-the hyphenation \emph{Bäk-ker} for the word \emph{Bäcker}, \emph{Zuk-ker} for
-the word \emph{Zucker} and \emph{pak-ken} for the word \emph{packen}. Now those
-words are hyphenated as \emph{Bä-cker}, \emph{Zu-cker} and \emph{pa-cken},
-respectively. Some words have also changed their hyphenation point after the
-spelling reform. For example, \emph{Fen-ster} became \emph{Fens-ter} and
-\emph{mei-stens} became \emph{meis-tens}. Some problems in compound word
-hyphenation in \TeX{} are discussed in \textcite{sojka1995a}.
-
-% Some hyphenation rules are not possible with TeX algorithm.
-% For example, the german word Schiffahrt should be hyphenated as Schiff-fahrt.
-% Although it is no longer the recommend written form, it was the most usual
-% until 2003 (see graph in schifffart.png from google ngrams).
-% Also the old hyphenating rules of German grammatic stated the following
-% hyphenations Bäk-ker (for the word Bäcker, what is now hyphenated as Bä-cker),
-% Zuk-ker (for the word Zucker, what is now hyphenated as Zu-cker),
-% pak-ken (for packen, and now pa-cken) and trok-ken (for trocken, now tro-cken).
-
-%which contain archeo can be alternatively spelt with archaeo or archæo.
-
-%GÂNDAVO, Pero de Magalhães de. Regras que ensinam a maneira de escrever e
-%orthographia da lingoa portuguesa, etc. Lisboa: Antonio Gonsalvez, 1574
-
-%  HIFENIZAÇÃO EM PORTUGUÊS
-% Antonio Martins de ARAÚJO and Toru MARUYAMA
-
-Moreover, as mentioned earlier, certain hyphenations may be preferred for
-stylistic reasons, or to avoid ambiguity, or for better reading experience.
-Some words might have multiple hyphenations, depending on the intended meaning.
-In such cases, \TeX{} may not efficiently address the hyphenation challenge, as
-it would necessitate case-by-case handling.
-
-\section{Patterns for \TeX{} hyphenation}\label{sec-patt4TeX}
-
-To simplify, if we consider only the Latin alphabet, with no diacritcs, the patterns used 
-in \TeX{} hyphenation are of the form: \texttt{\^{}\textbackslash{}.?[0-9]?([a-z]+[0-9]?)+\textbackslash{}.?\$},
-where we have described it using a regular expression\footnote{
-    Regular expressions (regex) are powerful search patterns used in text processing to find, match, and manipulate strings of text.
-They are a fundamental tool in programming and are supported in many programming languages.
-    The regex given here uses the Perl syntax and might be broken in the following
-    parts: \texttt{\^{}} and \texttt{\$} mark the start and end of the string;
-    \texttt{\textbackslash{}.?} specifies an optional period; \texttt{[0-9]?} allows for an optional single digit;
-    \texttt{([a-z]+[0-9]?)+} matches sequences of lowercase letters interleaved with optional digits.
-}.
-One example of such pattern is \texttt{4z1z2}, which is composed of a sequence
-of letters and numbers. Odd numbers indicate a
-good hyphenation point, whereas even numbers indicate a bad place to break.
-The given example states that the sequence has a good breaking point between
-the first and the second \emph{z} and an hyphenation should be inhibited before
-the first \emph{z} and after the second \emph{z}. For example, the hyphenation
-of the word \emph{piz-za}, \emph{fiz-zle} and \emph{mez-zanine} use this rule,
-where we see the hyphen placed between the two \emph{z}'s and no hyphen before,
-nor after the \emph{z}'s. Patterns may also use period symbol (\emph{.}) to
-indicate word boundaries. The pattern \texttt{.sh2} applies to beginning of
-words, implying that the \emph{s} and the \emph{h} should stick together in
-beginning of a word and an hyphenation should also be inhibited after the
-\emph{h}. For example, this pattern is used in \emph{Sher-lock}.
-
-Hyphenation rules are organized in levels, from 1 to 9, where odd numbers
-represent hyphenating levels and even numbers represent inhibiting levels. Each
-level works as an exception level of it predecessor. For example, the rule
-\texttt{sh1er} indicate a good hyphenation point between the \emph{h} and the
-\emph{e} in the sequence \emph{sher}. A rule at a higher level, as
-\texttt{.sh2}, implies an exception to the lower level rule. When we see
-\emph{sher}, in the beginning of a word, the rule \texttt{.sh2} applies and
-hyphenation proposed by the lower level rule \texttt{sh1er} should be hindered.
-That is the case in the hyphenation of the word \emph{Sher-lock}. The full
-example is provided in \Cref{sherlockhyphenation}, where we might see all pertinent
-English rules taking place in the hyphenation of \emph{Sher-lock} and \emph{sher-iff}.
-
-\noindent\begin{minipage}{\linewidth}
-\begin{lstlisting}[language={}, caption={Example of rules applyied in the
-hyphenation of the word \emph{Sherlock}. Example done using a port of \TeX{}'s
-hyphenation algorithm to Go provided at
-\url{https://github.com/speedata/hyphenation}.}, label=sherlockhyphenation]
-   .   s   h   e   r   l   o   c   k   .
-     0   0   2   |   |   |   |   |   |    .sh2
-     0   2   0   |   |   |   |   |   |    s2h
-     0   0   1   0   0   |   |   |   |    sh1er
-     |   |   |   0   1   0   |   |   |    r1l
-     |   |   |   0   3   0   4   |   |    r3lo4
-     |   |   |   |   |   |   0   0   1    ck1
-max: 0   2   2   0   3   0   4   0   1
-final: s   h   e   r - l   o   c   k -
-\end{lstlisting}
-\end{minipage}
-
-A pattern will consist of a string made of characters (from the language
-alphabet) possibly with a number in between, expressing the
-hyphenation/inhibition level and possibly word boundaries marker (the period)
-at the pattern edges. When there is no number between characters in a pattern,
-a zero is assumed, which means \emph{undefined} and no hyphenation point will
-be suggest at that location.
-
-\section{PATGEN}\label{sec-patgen}
-
-PATGEN utilizes a list of hyphenated words to define rules at various levels
-and lengths, based on the patterns found in the data. It starts with short
-patterns and incrementally increases their length until reaching the maximum
-pattern length allowed by the user.  The objective is to keep the patterns as
-concise as possible, as this enhances their generalizability.  As it advances
-and incorporates longer patterns, PATGEN establishes exceptions.  In certain
-cases, analyzing long patterns may be necessary, as some hyphenation points
-could depend on characters far away from the breaking point\footnote{Some
-    examples of hyphenation dependency on characters far from the break point:
-    \emph{dem-o-crat} and \emph{de-moc-ra-cy}; \emph{as-pi-rin} and
-    \emph{aspir-ing}; \emph{de-mon-stra-tive} and \emph{dem-on-stra-tion}.
-}.
-
-PATEGEN works on glyph\footnote{\emph{Glyph} is commonly used in linguistics,
-typography, and computer graphics to refer to a specific graphical
-representation of a character or symbol, which can be the entire symbol or a
-distinct visual element within it.} indices rather than character codes. Each
-glyph is represented by a single byte. That amount to 256 indices, where 13 of
-them are reserved for the digits 0-9 and the characters `.', `-', and `*'. The
-remaining 243 are used to represent symbols of the given language.  To run
-PATGEN, a translation file is necessary. This file defines the values of
-certain language-specific parameters (in the first line) and enumerates the
-various forms in which language symbols may appear (all subsequent lines).  In
-the first line, positions 1 and 2 are used to set the value of
-\verb|lefthyphenmin|, and positions 3 and 4 are used to set the value of
-\verb|righthyphenmin|.  These values determine the minimum length of a string
-that may be generated by a hyphenation procedure. To set a single-digit value,
-leave the first position blank, i.e., place a space in position 1 and 3 for
-\verb|lefthyphenmin| and \verb|righthyphenmin|, respectively.  Positions 5, 6
-and 7 are used to define alternative values for the special characters `.', `-'
-and `*'.  The following lines use a delimiter to enclose each `letter' of the
-desired language alphabet, including its alternative representations.  The
-first position of the line defines the delimiter, and each symbol of the
-language can occupy as many positions as necessary, as long as the reserved
-value for the delimiter is not used in the symbol's definition.  Consider the
-following example for defining the letter `e' in Portuguese: 
-\begin{verbatim}
-XeXEXéXêXÉXÊX\'{e}X\^{e}X\'{E}X\^{E}XX 
-\end{verbatim}
-It represents the many ways in which the letter `e' might be found: lowercase,
-uppercase, with or without acute or circumflex accents. Note that we have used
-the direct input (using UTF-8 or other encoding that support the accented `e'
-character) and also the compositional counterpart using the escape codes that
-define each accent.  In this definition, we have assumed that the many forms in
-which we may find the character \emph{e} will be equivalent for
-hyphenation (pattern matching) purpose. As another example, see the next line
-which defines the character $\pi$ (taken from \textcite{haralambous2021}):
-\begin{verbatim} 
-#p#P#\varpi ## 
-\end{verbatim}
-
-PATGEN also needs a dictionary file, which is a list of pre-hyphenated words
-from which PATGEN extracts patterns to create hyphenation rules. To ensure
-PATGEN's proper functionality, the translation file and the dictionary file
-must utilize the same encoding, even if it is a multi-byte encoding. The
-translation file describes how to handle byte sequences representing a glyph,
-and PATGEN will work seamlessly when there are at most 243 symbols in the given
-language.
-
-%Those rules are organized
-%in different levels, from 1 to 9, where odd numbers represent hyphenating
-%levels and even numbers represent inhibiting levels. Each level works as an
-%inhibiting level of it predecessor. 
-%A pattern will consist of a string made of
-%characters (from the language alphabet) possibly with a number in between,
-%expressing the hyphenation/inhibition level and possibly word boundaries marker
-%(the period) at the pattern edges. When there is no number between characters
-%in a pattern, a zero is assumed, which means \emph{undefined} and no
-%hyphenation point will be suggest at that location.
-
-\section{\TeX{} hyphenation rules for portuguese}\label{sec-tex-hyphen-pt}
-\textcite{rezende1987} was the first to create patterns for Portuguese hyphenation
-in \TeX{}. The pattern set was last updated in 2015, incorporating
-contributions from %José João Dias Almeida 
-\textcite{hyphpt}, resulting in a total
-of 307 rules\footnote{The set of rules for Portuguese hyphenation is short when
-compared to rules in other languages. For example, English currently has 4938
-rules, Russian has 7023 rules and German has 34011 rules.}. 
-These rules effectively hyphenate the majority of Portuguese words.
-
-However, in light of certain cases, we propose an analysis of the default rules
-to identify areas for improvement. By addressing specific issues and
-considering non-typical patterns, we aim to enhance hyphenation accuracy. The
-methodology used for this analysis is described in Section
-\ref{sec-methodology}.
-
-%
-% FILE="../data/default.TeX.pt-br.patterns"; grep "^1..$" "$FILE" | awk '{print substr($0, 0, 2)}' | sort | uniq -c | while read line; do p=$(echo $line | cut -d' ' -f2); c=$(grep "^$p[^0-9]$" "$FILE" | awk '{print substr($0, 3)}' | tr '\n' ' '); printf "$line $c \n"; done | cut -d' ' -f1 | paste -sd+ | bc
-%
-Out of the default \TeX{} rules, 252 (82\%) follow the pattern \verb|1CV|, which
-represents the recurring CV syllables in Portuguese.  As for the consonants,
-there are typically 18 considered (\verb|b|, \verb|c|, \verb|ç|, \verb|d|,
-\verb|f|, \verb|g|, \verb|j|, \verb|k|, \verb|l|, \verb|m|, \verb|n|, \verb|p|,
-\verb|r|, \verb|s|, \verb|t|, \verb|v|, \verb|x|, and \verb|z|) that can
-combine with 14 vowels (\verb|a|, \verb|e|, \verb|i|, \verb|o|, \verb|u|,
-\verb|á|, \verb|â|, \verb|ã|, \verb|é|, \verb|í|, \verb|ó|, \verb|ú|, \verb|ê|,
-and \verb|õ|), resulting in these CV patterns that indicate favorable
-hyphenation points before the consonants\footnote{The complete list of these
-252 patterns is given here: \ExceptionRulesCV{}.}. 
-It is worth noting that there might
-be other rules or exceptions in the hyphenation patterns not covered by these
-default rules.  To accommodate exceptions, \textcite{rezende1987} proposes the 
-following rules: 
-\begin{itemize}
-    \item 20 rules that created for cases involving consonants \verb|b|, \verb|c|, \verb|d|, \verb|f|, \verb|g|, \verb|k|, \verb|p|, \verb|t|, \verb|v|, or \verb|w| followed by \verb|l| or \verb|r|\footnote{The 20 additional rules are: \ExceptionRulesLR{}.};
-    \item 3 rules for \verb|c|, \verb|l| or \verb|n| followed by \verb|h|\footnote{Those 3 rules are: \ExceptionRulesCLNH{}.}.
-    % FILE="../data/default.TeX.pt-br.patterns"; grep -v "^1..$" "$FILE" | grep "2" | awk '{print substr($0, 2, 1)}' | sort | uniq | while read line; doc=$(grep "^1${line}2.$" "$FILE" | tr -d '12' | awk '{print substr($0, 2, 1)}' | tr '\n' ' '); printf "$line $c\n"; done
-    \item 23 distinct patterns were introduced to indicate hyphenation points between vowels or between \verb|c|'s, \verb|r|'s, and \verb|s|'s\footnote{Those patterns are: \ExceptionRulesThree{}.}. 
-    % FILE="../data/default.TeX.pt-br.patterns"; grep -v "^1..$" "$FILE" | grep -v "2" | grep "3" | wc -l
-    \item 8 patterns adhere to the \verb|1[gq]u4V|, signaling beneficial hyphenation points before \verb|g| or \verb|q|, followed by a sequence of \verb|u| and a vowel, with an inhibiting point between the \verb|u| and the subsequent vowel\footnote{They are the following: \ExceptionRulesFour{}.}.
-    \item 1 pattern represented as \verb|1-|, denoting that a hyphen indeed serves as a beneficial hyphenation point.
-\end{itemize}
-
-% - contabilizar a quantidade de palavras que não são contempladas pela proposta do autor
-% - analisar a necessidade de excluir alguma regra (ao invés de apenas acrescentar novas)
-
-\section{Methodology}\label{sec-methodology}
-
-To assess the performance of each set of rules, we require a collection of
-correctly hyphenated Portuguese words. We employed word frequency data to
-ensure we selected representative, commonly used words, avoiding excessively
-rare ones. Our comprehensive word list was curated using online dictionaries,
-Portuguese corpora, and verified against Portuguese grammars to validate
-hyphenation rules. We also performed manual corrections where necessary.
-We should not expect an entire corpus to follow a set of conventions for a written 
-language nor uniformity among a variety of corpora, especially those harvested from the Internet.
-``It is notoriously difficult to prescribe rules governing the use of a written language; it is even more difficult
-to get people to `follow the rules.' This is in large part due to the nature of written language, in which
-the conventions are not always in line with actual usage and are subject to frequent change'' \parencite[p.~14]{palmer2010}.
-
-\subsection{Data collection}\label{sec-data-coll}
-
-Initially, we selected
-\href{https://www.linguateca.pt/cetenfolha/index_info.html}{CETENFolha}
-as the source corpus, but this approach presented two issues: many
-words were still missing, and the corpus was based on text from 1994, prior to
-the implementation of the Orthographic Agreement. The Orthographic Agreement
-of the Portuguese Language was conducted in 1990, and its transition period
-started in 2009, becoming mandatory in 2016. However, even after the agreement,
-some words continue to have different spellings in the participating countries.
-To address these idiosyncrasies, we aim to develop hyphenation rules that
-accommodate variations in spelling. For instance, the word \emph{reception}
-might be written as \emph{receção} (Portugal) or \emph{recepção} (Brazil); the
-word \emph{action} might be written as \emph{acção} (Portugal) or \emph{ação}
-(Brazil); and the word \emph{project} might be written as \emph{projecto}
-(Portugal) or \emph{projeto} (Brazil).
-
-% We have used the Portuguese Wikipedia dump as our Portuguese corpus. Texts in Wikipedia might be written by Brazilian or Portuguese contributors, the both spellings may appear.
-
-% cat /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | tr -dc '0-9\n' | paste -sd+ | bc
-% 302226482
-% cat /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | awk '{CUMCOUNT+=$1; if(CUMCOUNT < 287115158) print;}' >/tmp/ptwikitop95.txt
-% cat /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | awk '{CUMCOUNT+=$1; if(CUMCOUNT < 299204217) print;}' >/tmp/ptwikitop99.txt
-% cat /tmp/ptwikitop99.txt | tr -d "0-9 " |  while read -r word; do if ! grep -q "^${word}," ../data/hyphenations.csv; then echo $word; fi; done > /tmp/ptwikitop99_notinlist.txt
-% cat /home/leoca/ee/research/hyphenation/listapalavrasnet.txt | awk '{print tolower($0)}' | while read -r word; do if !
-grep -qP "^\s*[0-9]+\s*${word}$" /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt; then echo $word; fi; done > /tmp/list_of_palavrasnet_not_in_wikipedia.txt
-
-% wc -l /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt
-% 1746947
-% wc -l /tmp/ptwikitop99_notinlist.txt
-% 42017
-% from 1746947 of wikipedia, only 42017 are not in list
-
-Due to the peculiarities mentioned, we made the decision to integrate the word
-list from \href{https://www.palavras.net/}{Palavras NET}, and subsequently, we
-augmented it with words sourced from the
-\href{https://pt.wikipedia.org}{Portuguese Wikipedia} dump. From the Wikipedia
-data, we narrowed down the selection to a subset of \num{50721} words,
-accounting for 95\% of occurrences in the corpus. This threshold was set to
-filter out typos and infrequent words. The initial word list became quite
-extensive, comprising \num{\CorpusSize} words. However, we refined the list by
-retaining only those words for which we could find hyphenation data in at least
-one of the following online dictionaries:
-\href{https://michaelis.uol.com.br/}{Michaelis},
-\href{https://dicionario.priberam.org/}{Priberam},
-\href{https://pt.wiktionary.org}{Wikcionário},
-\href{https://aulete.com.br/}{Aulete},
-\href{http://www.portaldalinguaportuguesa.org/}{Portal da Língua Portuguesa}, and
-\href{https://www.dicio.com.br/}{Dicio}.
-Consequently, this curation process resulted in a final dictionary containing
-\num{\DictionarySize} words.
-
-Table \ref{tblstats} presents the number of distinct words with a given number
-of hyphenations found in the dictionaries.  Additionally, it displays the
-number of words that received the highest agreed-upon hyphenation.  For
-instance, the word \emph{como} was consistently hyphenated as \emph{co-mo} in
-all six dictionaries, therefore, it contributes to both the counts in the
-column representing six hyphenations (first column).  On the other hand, the
-word \emph{sua} received different hyphenations: \emph{su-a} in four
-dictionaries, \emph{sua} in one dictionary, and one dictionary did not provide
-any hyphenation result.  This leads to an increment in the first line, second
-column (since hyphenations were found in five dictionaries) and the second
-line, third column (since the most frequent hyphenation was found in four
-dictionaries). It is evident now that the number of identical hyphenations can
-exceed the total number of hyphenations found, especially for smaller values.
-
-\begin{table}
-\centering
-\caption{Considering the six dictionaries used, the first line of this table
-presents the number words that a given number of hyphenations were found in the
-dictionaries. The second line presents the number of words that have a given
-number of hyphenation as its most frequent form found in the
-dictionaries.}\label{tblstats}
-\small
-\begin{tabular}{@{ }l@{ } *{7}{@{ }S[table-format=6]@{ }}}
-    hyphenations & 6 & 5 & 4 & 3 & 2 & 1 & 0 \\
-    \hline
-    hyphenations found & \NumberOfSixHyphens{} & \NumberOfFiveHyphens{} &
-    \NumberOfFourHyphen{} & \NumberOfThreeHyphens{} & \NumberOfTwoHyphens{} &
-    \NumberOfOneHyphens{} & \NumberOfNoHyphens{} \\
-
-    same hyphenations & \NumberOfSixAgrees{} & \NumberOfFiveAgrees{} &
-    \NumberOfFourAgrees{} & \NumberOfThreeAgrees{} & \NumberOfTwoAgrees{} &
-    \NumberOfOneAgrees{} & n/a
-\end{tabular}
-\end{table}
-
-In summary, our data compilation involved \emph{CETENFolha}, \emph{Palavras
-NET}, and \emph{Wikipedia}, and hyphenated the words using the original \TeX{}
-hyphenation rules.  Subsequently, we compared the hyphenated results with
-those obtained from the dictionary. By conducting a thorough performance
-appraisal, we systematized the errors and delved into the relevant literature
-to identify potential rules that could complement and enhance the existing
-hyphenation system.
-
-\section{Writing systems}\label{sec-writing-systems}
-
-There is a diverse array of writing systems, categorized into logographic,
-syllabic, and alphabetic systems. Although distinct, these systems can be built
-on an interplay of these categories \parencite{coulmas2003,palmer2010}. 
-The principles guiding an alphabetic or phonemic writing system vary significantly 
-based on the language and its history. Here are some key points worth highlighting:
-\begin{enumerate}[label=\arabic*)]
-    \item The most common principle involves representing the sounds of a
-	language with written symbols, using one or a combination of symbols to
-	represent each sound (e.g., the orthographic system of Portuguese uses
-	an alphabet of 27 letters to represent different sounds of the
-	language).
-    \item Etymology also plays a crucial role, where the spelling of a word
-	reflects its origins and historical development (e.g., the French
-	language often reflects the Latin roots of words in its spelling).
-    \item Morphology serves as a guide in structuring many languages, using
-	specific letters or symbols to indicate word endings, prefixes, or
-	suffixes (e.g., Russian uses different forms of the Cyrillic alphabet
-	to indicate gender and case in its nouns).
-    \item The evolution of a language over time also contributes to its written
-	form (e.g., the spelling of many English words has changed over time to
-	reflect changes in pronunciation).
-\end{enumerate}
-Orthographic systems for languages with logographic writing systems, such as
-Chinese ideograms, cuneiform writing, and Egyptian hieroglyphs, differ
-significantly from alphabetic writing systems. In logographic systems,
-individual symbols or characters represent entire words or ideas, rather than
-phonemes or sounds. As a result, the principles guiding their orthographic
-systems are based more on semantic and visual principles than on phonemic
-principles.
-Hyphenation is a feature of alphabetic scripts where words are composed of letters, 
-and spaces or hyphens are used to separate words, syllables, or parts of words. 
-Logographic writing systems, such as the Chinese, 
-function differently and do not employ hyphenation \parencite{honorof2006}.
-
-\section{Portuguese spelling system}\label{sec-grammar-port}
-
-Portuguese employs an alphabetical writing system, which means its spelling is
-guided by phonological principles \parencite{cagliari2015}. The correlation between
-spelling and pronunciation influences word hyphenation, as words are divided
-into syllables based on the phonemic system. It is important to note that
-different languages follow diverse principles for word division. For example,
-English is primarily guided by morphological principles, evident in words like
-\emph{walk-ing}, \emph{un-happy}, \emph{work-s}, and \emph{ear-ly}.
-Additionally, other factors also impact word hyphenation in English, such as 
-the distinction between long and short vowels, which function within the context
-of open or closed syllable, respectively; and the presence of doubled consonants and
-digraphs \parencite{lin2011,yavas2020}. 
-Furthermore, there exist numerous exceptions that may be categorized into rules.
-% https://english.stackexchange.com/questions/385/what-are-the-rules-for-splitting-words-at-the-end-of-a-line
-
-Merely stating that an orthographic system is guided by phonological issues
-does not necessarily mean that its hyphenation rules directly mirror the
-phonetic counterpart. This is notably apparent in Portuguese, where a strict
-one-to-one correspondence between letters and sounds is not always observed.
-The orthographic system operates according to its specific rules. For example,
-consider consonant clusters that create a single sound (digraphs) in words like
-\emph{\underline{ch}ave}, \emph{i\underline{lh}a}, \emph{\underline{sh}ampoo}, \emph{ca\underline{rr}o}, and \emph{ma\underline{ss}a}.
-While these digraphs are pronounced as one sound within a single syllable,
-their representation in writing determines how they are divided. Specifically,
-different consonants within a digraph must remain together, whereas identical
-consonants are separated. As a result, we observe hyphenations like
-\emph{cha-ve}, \emph{i-lha}, and \emph{sham-poo}, but \emph{car-ro} and \emph{mas-sa}.
-
-%When there is no space left in line for a whole word, it might be split in two
-%using a hyphen as an indication of such procedure.
-
-In Portuguese, hyphenations are allowed on syllables boundaries and, in
-general, follow phonological principles.  According to the Grammar
-\parencite{cunha2016,bergstrom2011,cegalla2008}, some rules might still apply:
-\begin{enumerate}
-    \item\label{rule-di-triphthong} diphthong or triphthong should not be split
-	(e.g. \emph{m\underline{ui}-to}, \emph{Pa-ra-g\underline{uai}});
-    \item\label{rule-unstressed} the sequences \emph{ia}, \emph{ie}, \emph{io}, \emph{oa}, \emph{ua},
-	\emph{ue} and \emph{uo}, when in final unstressed position, should not be split 
-	(e.g. \emph{gló-r\underline{ia}}, \emph{vi-tó-r\underline{ia}}, 
-	\emph{cá-r\underline{ie}}, \emph{es-pé-c\underline{ie}}, 
-	\emph{Má-r\underline{io}}, \emph{má-g\underline{oa}}, 
-	\emph{ré-g\underline{ua}}, \emph{tê-n\underline{ue}}, 
-	\emph{con-tí-g\underline{uo}}, \emph{am-bí-g\underline{uo}});
-    \item\label{rule-c-clusters} consonant clusters starting a syllable should not be
-	split (e.g. \emph{\underline{pn}eu-má-ti-co}, \emph{\underline{ps}i-có-lo-go}, 
-	\emph{\underline{mn}e-mô-ni-co});
-    \item\label{rules-digraphs-ns} the digraphs	\emph{ch}, \emph{lh}, \emph{nh}
-	should not be split (e.g. \emph{ra-\underline{ch}ar},
-	\emph{a-bro-\underline{lh}os}, \emph{ma-\underline{nh}ã};
-    \item\label{rule-guqu} bigrams like \emph{gu} and \emph{qu} whose vowel \emph{u} is not 
-	pronounced are never separated from the vowel or diphthong that follows it 
-	(e.g. \emph{U-ru-\underline{guai}}, \emph{pe-\underline{que}});
-    \item\label{rule-nasalization} since they are digraphs, a vowel and its following 
-	nasalization marker (a graphic nasal consonant) should not be split (e.g. \emph{\underline{am}-bição},
-	\emph{m\underline{an}-cha});
-    \item\label{rule-decreasing} decreasing diphthongs should not be split (e.g. 
-	\emph{\underline{ai}-ro-so}, \emph{ca-d\underline{ei}-ra}, 
-	\emph{o-ra-ç\underline{ão}});
-    \item\label{rule-rising} rising diphthong should not be split (e.g.
-	\emph{a-b\underline{ai}-xo}; \emph{c\underline{au}-te-la}, 
-	\emph{pa-p\underline{éi}s}, \emph{cha-p\underline{éu}}, 
-	\emph{pre-f\underline{ei}-to}, \emph{r\underline{eu}-nir},
-	\emph{n\underline{oi}-te}; \emph{ca-la-b\underline{ou}-ço}, 
-	\emph{as-te-r\underline{ói}-de}; 
-	\emph{re-tri-b\underline{ui}});
-    \item\label{rule-singlev} disyllables whose syllable has a single vowel should 
-	not be split (e.g. \emph{\underline{a}to}, \emph{ru\underline{a}}, 
-	\emph{\underline{ó}dio}, \emph{\underline{u}nha});
-    \item\label{rule-orphan} words with more than two syllables, when divided, cannot 
-	isolate a syllable composed of a single vowel (e.g. \emph{\underline{a}gos-to}, 
-	\emph{la-go\underline{a}}, \emph{\underline{i}da-de});
-
-    \hspace{10em} \hbox to 5cm{\leaders\hbox to 10pt{\hss . \hss}\hfil}
-
-    \item\label{rule-hiatus} hiatus vowels and those vowel sequences where each vowel
-	belongs to a different syllable should be split (e.g.
-	\emph{sa\underline{-ú-}de}, \emph{ra\underline{-i-}nha}, \emph{d\underline{o-e}r},
-	\emph{v\underline{o-o}s}), the same procedure is used splitting diphthongs
-	in different syllables (e.g. \emph{c\underline{ai-ai}s}) or diphthong and
-	vowel in different syllables (e.g. \emph{en-s\underline{ai-o}s});
-    \item\label{rule-consonants} consonant sequences, when in different syllables, should
-	be split (e.g. \emph{a\underline{f-t}a}, \emph{a\underline{b-d}i-car},
-	\emph{re\underline{s-c}i-são}, \emph{a\underline{b-s}o-lu-to});
-    \item\label{rule-digraphs} the following consonant digraphs should be split:
-	\emph{rr}, \emph{ss}, \emph{mm}, \emph{nn}, \emph{sc}, \emph{sç} and
-	\emph{xc} (e.g. \emph{te\underline{r-r}a}, \emph{pro-fe\underline{s-s}or},
-	\emph{co-mu\underline{\emph{m-m}}en-te}, \emph{co\underline{n-n}os-co},
-	\emph{de\underline{s-c}er}, \emph{cre\underline{s-ç}a}, \emph{e\underline{x-c}e-der}).
-\end{enumerate}
-
-Rules \ref{rule-singlev} and \ref{rule-orphan} are primarily aimed at ensuring
-proper readability of the text, aligning with \TeX{} approach to deal with
-widows and orphans. As mentioned in \Cref{sec-intro}, the variables
-\verb|lefthyphenmin| and \verb|righthyphenmin| are used to control the minimum
-length for fragments of hyphenated words. For that reason, rules
-\ref{rule-singlev} and \ref{rule-orphan} are fiddling rules in \TeX{}
-hyphenation, and that is not reason to take than in account in our analysis to
-improve Portuguese hyphenation rules. Furthermore, get the full hyphenation of
-words might be useful for text-to-speech applications \parencite{libossek2000,trogkanis2010}.
-
-Additionally, it is advisable to refrain from
-splitting disyllables consisting of four letters (e.g., \emph{para},
-\emph{como}, \emph{cede}). This considerations also lead to more aesthetically
-pleasing and intelligible text, and \TeX{}'s control of isolated fragments already
-address this issue.
-
-%Note that rules \ref{rule-singlev} and \ref{rule-orphan} are fiddling rules in
-%\TeX{} hyphenation, since \TeX{} already has directives to avoid hyphenated
-%widows and orphans.  As mentioned in \Cref{sec-intro}, the variables
-%\verb|lefthyphenmin| and \verb|righthyphenmin| are used to control the minimum
-%length for fragments of hyphenated words.  For this reason, we will not take
-%into account rules \ref{rule-singlev} and \ref{rule-orphan} during the analysis
-%and development of the hyphenation rules.
-
-In some situations a hyphen should be repeated at the start of the following
-line. They are: 
-\begin{enumerate}
-\item cases where compound words using a hyphen are split across lines (e.g.,
-    \emph{couve-/-flor}, \emph{ex-/-presidente}); and
-\item cases where splitting a pronoun could result in a different meaning (e.g.,
-    \emph{prazer de ver-/-me}\footnote{Possible conveyed meanings: 
-    \emph{pleasure in seeing me} or \emph{worm's pleasure}.}). 
-\end{enumerate}
-
-%To ensure proper hyphenation and readability, certain guidelines should be
-%followed. Avoiding a single vowel at the end or start of a line is crucial
-%(e.g., \emph{san-guí-nea} should be split only on the provided hyphens,
-%avoiding a split that leaves the final vowel \emph{a} alone at the start of a
-%new line: \emph{sanguíne-a}). Additionally, it is advisable to refrain from
-%splitting disyllables consisting of four letters (e.g., \emph{para},
-%\emph{como}, \emph{cede}).  These considerations lead to more aesthetically
-%pleasing and intelligible text.
-
-Systematizing the rules that guide syllable boundaries and, consequently,
-hyphenation in Portuguese proved to be fundamental for the improvement of the
-\TeX{} hyphenator rules, since they indicate the possible or prohibited contexts
-of hyphenation. Expomos, a seguir, uma análise comparativa...
-
-... to continue
-\vspace{10ex}
-
-\section{Creating the dictionary}
-
-A bash script, named \texttt{gethyphenations.sh}, was developed to crawl six
-online dictionaries and extract word hyphenations whenever available. The
-process involves launching parallel threads for each word in the list, querying
-a specific online dictionary, and retrieving the corresponding hyphenation. For
-this purpose, individual scripts were created for each dictionary:
-\texttt{getmichaelishyphenation.sh} for \href{https://michaelis.uol.com.br/}{Michaelis},
-\texttt{getpriberamhyphenation.sh} for \href{https://dicionario.priberam.org/}{Priberam},
-\texttt{getwiktionaryhyphenation.sh} for \href{https://pt.wiktionary.org}{Wikcionário},
-\texttt{getauletehyphenation.sh} for \href{https://aulete.com.br/}{Aulete},
-\texttt{getportalhyphenations.sh} for \href{http://www.portaldalinguaportuguesa.org/}{Portal da Língua Portuguesa}, and
-\texttt{getdiciohyphenation.sh} for \href{https://www.dicio.com.br/}{Dicio}.
-This systematic approach ensures efficient and accurate extraction of
-hyphenations from various online sources. The resulting data is stored in a CSV\footnote{
-    Comma-separated values (CSV) is a text file format defined in \href{https://datatracker.ietf.org/doc/html/rfc4180}{RFC 4180}.
-    In CSV, commas are used to separate values, and each line in the file represents a new record. Records consist of fields separated by delimiters, typically a single comma.
-} file named \texttt{hyphenations.csv}.
-
-\subsection{Establishing a gold standard}
-
-To construct our gold standard for hyphenation, we will compare the
-hyphenations offered by all six dictionaries. We'll determine the total count
-of unique hyphenations across these dictionaries using the script
-\texttt{hyphenationagreements.sh}.
-
-As our initial hyphenation reference, we will consider those cases where all
-six dictionaries agree. This list comprises \num{\NumberOfSixAgrees} words,
-and their hyphenations are stored in \texttt{hyphenations6.dic}.
-
-For any disagreement, we must be cautious and examine each case.
-We might be tempted to chose the majority vote approach, selection
-those hyphenations that have the most supporters, but it is unclear 
-how the hyphenations on those online dictionaries were curated, 
-many might use algorithmic approach, leading to potential flaws shared
-among them. 
-For example, 5 dictionaries use the hyphenation 
-\emph{quart-zo} while just one uses the rightful one, \emph{quar-tzo}.
-The same happens with \emph{de-sem-ba-i-nhar} and \emph{de-sem-bai-nhar},
-the former one receiving the majority of the votes, despite being wrong.
-Some strings might accept more than one hyphenation. For example, 
-\emph{sub-li-nha} and \emph{su-bli-nha} represent two different words.
-The former is the substantive \emph{underline} and the latter is a flexed form of the verb \emph{to underline}.
-\todo{Aline, segue a lista dos casos duvidosos que encontrei com votos 5 a 1. Marquei em negrito aqueles
-    que considero ser a forma correta.
-    quart-zo(5), \textbf{quar-tzo}(1) (assim também trocar quart-zi-to por \textbf{quar-tzi-to)}; \textbf{sub-li-nha}(5), \textbf{su-bli-nha}(1); 
-    de-sem-ba-i-nhar(5), \textbf{de-sem-bai-nhar}(1); ap-nei-a(5), \textbf{a-pnei-a}(1); 
-    disp-nei-a(5), dispneia(1) (\textbf{dis-pnei-a}, forma não encontrada nos dicionários); 
-    hi-pe-ral-ge-si-a(5), \textbf{hi-per-al-ge-si-a}(1);
-    in-de-is-cen-te(5), \textbf{in-deis-cen-te}(1); jo-in-vi-len-se(5), \textbf{join-vi-len-se}(1); 
-    ne-er-lan-dês(5), \textbf{neer-lan-dês}(1). Os demais casos de 5 a 1 são proparoxítonas aparentes.
-}
-The procedure to create the second list of hyphenated words was:
-\begin{enumerate*}[label=\arabic*)]
-  \item select those hyphenations agreed by five dictionaries that have no other hyphenation proposal (5 to 0 votes);
-  \item from those that have another proposal, check if it is an apparent proparoxytone,
-      \begin{enumerate*}[label=\alph*)]
-	  \item if it has a diacritic, select the paroxytone option,
-	  \item if not, select the proparoxytone option.
-      \end{enumerate*}
-  \item if it is not an apparent proparoxytone case, select the hyphenation with five votes.
-\end{enumerate*}
-This procedure is implemented in the script \texttt{get51.sh}.
-Just a few hyphenations were manually corrected. They are: \emph{quar-tzo}, 
-\emph{quar-tzi-to}, \emph{su-bli-nha} (was added), \emph{de-sem-bai-nhar},
-\emph{a-pnei-a}, \emph{dis-pnei-a}, \emph{hi-per-al-ge-si-a}, \emph{join-vi-len-se}, and \emph{neer-lan-dês}.
-The final list is stored in \texttt{hyphenations5.dic} and holds \num{\NumberOfFiveAgrees} additional hyphenations.
-Using the two lists created so far, we have in total \num{\NumberOfSixFiveAgrees} hyphenations.
-
-% results from script ./get51.sh
-% cases where majority vote might go wrong:
-% sub-li-nha(5),su-bli-nha(1) % both are valid
-% de-sem-ba-i-nhar(5),de-sem-bai-nhar(1) % de-sem-bai-nhar seems to be the correct choice
-% ap-nei-a(5),a-pnei-a(1) % ??
-% disp-nei-a(5),dispneia(1) or dis-pnei-a?
-% hi-pe-ral-ge-si-a(5),hi-per-al-ge-si-a(1)
-% in-de-is-cen-te(5),in-deis-cen-te(1)
-% jo-in-vi-len-se(5),join-vi-len-se(1)
-% ne-er-lan-dês(5),neer-lan-dês(1)
-% the remaining are apparent proparoxytones
-
-For those hyphenations that have 4 votes, we used basically the same approach
-as before. We noticed many words had only 4 votes (no alternative hyphenation was provided
-by any dictionary), and they were hyphenated as proparoxytones. They were, in fact, 
-apparent proparoxytones. Those cases were easy to target by looking
-for diacritics in the third to last syllable and a sequence \emph{V-V} in the end.
-We transformed those cases into paroxytones by removing the last hyphen.
-The remaining cases, where an alternative hyphenation was found, we checked for
-diacritics, selecting the paroxytone option when found and selection the
-proparoxytone option when not. For the reaming cases with alternative option,
-we simply select the most voted one. This procedure is implemented in script 
-\texttt{get4.sh}.
-
-% analisar os resultados das hifenizações através da análise de frequência das sílabas
-% as silabas de baixa frequência podem ser indicativos de erros... verificar a origem delas
-% cat ../data/hyphenations6.dic ../data/hyphenations5.dic ../data/hyphenations4.dic | tr '-' '\n' | sort | uniq -c | sort -nr > /tmp/syls
-% grep -P "\s+1\s[^0-9]+$" /tmp/syls | tr -d '1' | sed 's/^\s\+//g' | while read syl; do grep "^$syl-\|-$syl-\|-$syl$" ../data/hyphenations6.dic; done > /tmp/rare
-% grep -P "\s+1\s[^0-9]+$" /tmp/syls | tr -d '1' | sed 's/^\s\+//g' | while read syl; do grep "^$syl-\|-$syl-\|-$syl$" ../data/hyphenations5.dic; done >> /tmp/rare
-% grep -P "\s+1\s[^0-9]+$" /tmp/syls | tr -d '1' | sed 's/^\s\+//g' | while read syl; do grep "^$syl-\|-$syl-\|-$syl$" ../data/hyphenations4.dic; done >> /tmp/rare
-% grep -P "\s+1\s[^0-9]+$" /tmp/syls | tr -d '1' | sed 's/^\s\+//g' | while read syl; do grep --color=always "^$syl-\|-$syl-\|-$syl$" <(cat ../data/hyphenations6.dic ../data/hyphenations5.dic ../data/hyphenations4.dic); done | ansi2html > /tmp/rare.html
-
-% fun-ci-o-ná-ri-o > fun-ci-o-ná-rio
-% co-mí-ci-o > co-mí-cio
-% con-vê-ni-o > con-vê-nio
-% cri-té-ri-o > cri-té-rio
-% ple-ná-ri-o > ple-ná-rio
-% cre-di-á-ri-o > cre-di-á-rio
-% es-tá-gi-o > es-tá-gio
-% in-ter-ban-cá-ri-o > in-ter-ban-cá-rio
-% ur-gên-ci-a > ur-gên-cia
-% i-mo-bi-li-á-ri-a > i-mo-bi-li-á-ria
-% re-vo-lu-ci-o-ná-ri-o > re-vo-lu-ci-o-ná-rio
-% ve-ló-ri-o > ve-ló-rio
-% es-có-ci-a > es-có-cia
-% for-mu-lá-ri-o > for-mu-lá-rio
-% or-ça-men-tá-ri-o > or-ça-men-tá-rio
-
-% ag-nós-ti-co(5),a-gnós-ti-co(1)   << ?
-% co-i-bir(5),coi-bir(1)            << both are correct?
-% drui-da(5),dru-i-da(1)            << drui-da is correct, since an hiatus would require an accent dru-í-da
-% flui-do(5),flu-i-do(1)            << as there is no diacritic it should be flui-do
-%					fluido (sem acento) - substantivo: flui-do (ditongo) -- exemplo: O fluido de freio acabou.
-%					fluido (com acento) - forma verbal: flu-í-do (hiato) -- exemplo: A discussão para aprovar reformas no país não tem fluído como esperavam os governantes.
-% sub-li-nha(5),su-bli-nha(1)       << sub-linha or su-blinha (sublinhar) 
-% man-ti-do(5) mantido(1)           << mantido clearly was not hyphenated 
-% quart-zo(5),quar-tzo(1)           << quar-tzo sounds like the correct choice
-% den-ti-frí-ci-o(5),den-ti-frí-cio(1) << it should be marked as apparent proparoxytones but no one did
-
-%compare_strings() {
-%    # Trim leading and trailing whitespace from the first string
-%    string1_trimmed="${1#"${1%%[![:space:]]*}"}"
-%    string1_trimmed="${string1_trimmed%"${string1_trimmed##*[![:space:]]}"}"
-%
-%    # Trim leading and trailing whitespace from the second string
-%    string2_trimmed="${2#"${2%%[![:space:]]*}"}"
-%    string2_trimmed="${string2_trimmed%"${string2_trimmed##*[![:space:]]}"}"
-%
-%    if [ "$string1_trimmed" == "$string2_trimmed" ]; then
-%        return 0  # Strings are equal
-%    else
-%        return 1  # Strings are different
-%    fi
-%}
-
-% grep "(5)" ../data/hyphagreements | grep "(1)" | head | tr -d '()0-9' | while read line; do word1=$(echo $line | cut -d, -f1); word2=$(echo $line | cut -d, -f2); count1=$(grep -o '-' <<< "$word1" | wc -l); count2=$(grep -o '-' <<< "$word2" | wc -l); if [ $count1 -gt $count2 ]; then w1=$(echo $word1 | sed 's/\(.*\)-/\1/'); compare_strings "$w1" "word2"; result=$?; if [ $result -ne 0 ]; then echo "c1: $line $w1 $word2"; od -c <<< "$w1"; od -c <<< "$word2"; fi; elif [ $count1 -lt $count2 ]; then w2=$(echo $word2 | sed 's/\(.*\)-/\1/'); compare_strings "$w2" "word1"; result=$?; if [ $result -ne 0 ]; then echo "c2: $line $word1 $w2"; fi; else compare_strings "$word1" "word2"; result=$?; if [ $result -ne 0 ]; then echo $line; fi; fi; done
-
-After performing all procedures above described to create our golden hyphenation
-dictionary, we might still need manual corrections.
-All manual corrections are written in the file \texttt{replacements.txt} and
-the script \texttt{manualcorrections.sh} is used to perform these corrections.
-
-In certain dictionaries, words are commonly annotated with a colon (`:') to
-signify a potential variation in pronunciation or production, specifically as a
-diphthong or hiatus, classifying them as `apparent proparoxytones'.  In
-Portuguese, words ending in \emph{ea}, \emph{eo}, \emph{ia}, \emph{ie},
-\emph{io}, \emph{ua}, \emph{ue}, or \emph{uo}, with the stressed syllable
-before these endings, can be considered either paroxytones ending in a rising
-diphthong or proparoxytones ending in a hiatus. The words \emph{his-tó-ri:a}
-and \emph{on-du-la-tó-ri:o} are examples of words marked as apparent
-proparoxytones, meaning they might be regarded as paroxytones \emph{his-tó-ria}
-and \emph{on-du-la-tó-rio} or as proparoxytones \emph{his-tó-ri-a} and
-\emph{on-du-la-tó-ri-o}.  The script \texttt{hyphenationagreements.sh} might
-deal with these apparent proparoxytones in four different ways: we might keep
-the hyphenations with the colon mark to indicate an apparent proparoxytones; or
-we might only the paroxytones or only the proparoxytones counterpart; or we may
-count both paroxytones and proparoxytones.  As there is no consensus in the
-literature, we have decided to count both hyphenations. In our hyphenation
-dictionary, we have found \NumberOfAppProp{} words marked as apparent
-proparoxytones.
-
-\section{Updating the rules}
-Let us remember that the standard \TeX{} hyphenation rules, proposed by
-\textcite{rezende1987,hyphpt}, when tested against a set of \num{\DictionarySize}
-words, present 1,368 (????) errors, of which 1,273 (????) correspond to places
-where the hyphenation was not carried out and 125 (????) to erroneous markings.
-Faced with the errors made by the standard hyphenator, a set of \num{\NumberOfNewRules} rules were
-established, which reduced the errors to 132 (???), with 118 (????) places
-where the hyphenation was not marked and 35 (????) where there was erroneous
-marking. Such rules are presented and exemplified below, as well as the
-necessary exception rules and an example in which the application of the rule
-is demonstrated.
-
-% get the error rate from default TeX rules in this dic file
-% ./checkhyphenation.sh correct test
-% ./gocreateresultfile.sh ../data/hyphenations6.dic ../data/default.TeX.pt-br.patterns > ../data/hyphenations6result-default-patterns.dic
-% grep -v "[\.\-]" ../data/hyphenations6result-default-patterns.dic | wc -l
-% 15536
-% NumberOfCorrectSix NumberOfWrongSix NumberOfMissingSix
-% correct: 15536; wrong: 30 (30); missing: 277 (276,1)
-Using the default \TeX{} hyphenation rules we have found \NumberOfCorrectSix{}
-words correctly hyphenated, \NumberOfWrongSix{} words with wrong hyphenation
-points introduced by the default rules, and \NumberOfMissingSix{} words with at
-least a missing hyphenation point (among those words only \texttt{ba-í-a} had
-two missing hyphenation points).
-
-% cat ../data/default.TeX.pt-br.patterns ../data/patch.TeX.pt-br.patterns > ../data/patched-default.TeX.pt-br.patterns
-% ./gocreateresultfile.sh ../data/hyphenations6.dic ../data/patched-default.TeX.pt-br.patterns > ../data/hyphenations6result-patched-patterns.dic
-% ./resultfilemetrics.sh -f ../data/hyphenations6result-patched-patterns.dic -a
-% correct: 15826; wrong: 2 (2); missing: 13 (13)
-
-\subsection{Results from the new set of rules}
-Although the XXX erroneous words have some common characteristics, which would
-allow, to some extent, to reduce the amount of hyphenation errors, there is a
-limitation arising from the way \TeX{}'s rules are conceived. We present,
-below, the systematists found in these data that could be predicted by another
-structure of rules:
-
-\begin{description} 
-    \item[Morphological determination:] Prefixes such as \emph{re-},
-	\emph{sub-}, \emph{cyber-}, and \emph{auto-} require separating the
-	prefix from its stem, what runs into phonological issues. For example,
-	\emph{reiniciar} and \emph{sublinhar}, as they contain prefixes, should
-	be hyphenated as \emph{re-i-ni-ci-ar} and \emph{sub-li-nhar},
-	respecting the morphological formation of the word. However,
-	considering that the Portuguese language hyphenates its words from
-	syllabic phonological correlates, words that require morphological
-	information, such as those, do not have their hyphenation performed
-	properly. They add up, in our corpus, to twelve words (eight words with
-	\emph{re-} and one case with \emph{auto-}, \emph{meta-}, \emph{sub-},
-	\emph{cyber-}, \emph{geo-} or \emph{neuro-}, those results are presented
-	in Table \ref{tab-mor-syl}).
-	% $ { head -n 1 ../data/hyphenations.csv; grep "^sublinhar," ../data/hyphenations.csv; } | column -t -s,
-	% su-bli-nhar (priberam, wiktionary, aulete)
-	% sub-li-nhar (michaelis, portal, dicio)
-
-	% $ { head -n 1 ../data/hyphenations.csv; grep "^auto[a-z]\+," ../data/hyphenations.csv | grep -v ",,,";} | column -t -s,
-
-	\begin{table}
-	\scriptsize
-	\caption{Hyphenation in the dictionaries of words having conflict between morphological and syllabic information.}
-	\label{tab-mor-syl}
-        \begin{tabular}{ll*{6}{c}}
-	\toprule
-	    word                   & hyphenation  & \multicolumn{6}{c}{dictionary} \\
-             &                                    & michaelis & priberam & wikitionary & aulete & portal & dicio \\
-	\midrule
-        \multirow{2}{*}{sublinhar} & su-bli-nhar  &           & x        & x           & x      &        &       \\
-				   & sub-li-nhar  & x         &          &             &        & x      &       \\
-	\multirow{2}{*}{reiniciar} & rei-ni-ci-ar &           &          & x           &        & x      &       \\
-				   & re-i-ni-ci-ar & x        & x        &             & x      &        & x     \\
-	\bottomrule
-	\end{tabular}
-	\end{table}
-
-    \item[Foreignness:] There is a group of 20 words in the corpus that are
-	terminologies or words that were incorporated into the Portuguese
-	language without full phonological adaptation, such as
-	\emph{darwinismo}, \emph{quilowatt}, and \emph{esfiha}. The lack of
-	adaptation makes the phonological pattern very specific to the word,
-	making it impossible to incorporate in \TeX{}'s rules alongside the
-	other rules. The solution is to add them to the exception word list.
-
-    \item[Word-initial consonant clusters:] Portuguese has few cases of
-	consonant clusters at the beginning of a word. They, in general, are
-	etymological remnants and are currently unproductive in the language,
-	since there are no neologisms with this pattern. Encounters like
-	\emph{ps-} and \emph{pn-} are more frequent, as they are present in
-	words like \emph{psicologia} and \emph{pneu}, which have an average
-	frequency in the language. They might be predicted by rules, which
-	comprise XXX words. However, there are consonant clusters that are
-	found in very specific and low frequency words. Although possible, it
-	is not worth adding very specific rules using the consonant clusters
-	contained in the words \emph{dzeta}, \emph{gnu}, \emph{cnidário},
-	\emph{ftálico}, and \emph{gnaisse} -- that is, just five words.
-
-    \item[Abbreviations, Acronyms, or Initialisms:] 
-       Whether for efficiency, convenience, clarity, or specialized jargon, 
-       it is common to use shortened versions of words or phrases. Abbreviation is a method employed to achieve this shortening. In our Portuguese corpus, we find examples such as 
-       \emph{etc.}\footnote{Latin expression \emph{et cetera}, meaning `and other similar things'.}, 
-       \emph{Dr.}\footnote{\emph{doutor} (doctor, person with PhD title, but popularly used to designate an erudite individual)}, 
-       \emph{Exmo.}\footnote{\emph{Excelentíssimo} (honourable)},
-       \emph{cap.}\footnote{\emph{capítulo} (chapter)}, \emph{Univ.}\footnote{Universidade (university)}, 
-       \emph{ed.}\footnote{\emph{edição} (edition)}, 
-       \emph{s.n.}\footnote{sine nomine, Latin expression meaning `without a name', mostly used in the context of publishing.}.
-
-       Another form of abbreviation is an initialism, which consists of using
-       the initial letters of words to create a shortened version. However,
-       initialisms may not always conform to the hyphenation rules described in
-       this work, as they do not necessarily follow the orthographic or
-       phonotactic standards of the language. Some abbreviations found in the
-       corpus include 
-       \emph{SESC}\footnote{Serviço Social do Comércio}, 
-       \emph{INSS}\footnote{\emph{Instituto Nacional do Seguro Social} (National Institute of Social Security)}, 
-       \emph{PCdoB}\footnote{\emph{Partido Comunista do Brasil} (Communist Party of Brazil)},
-       \emph{PM}\footnote{\emph{Polícia Militar} (military police)}, and 
-       \emph{UFRJ}\footnote{Universidade Federal do Rio de Janeiro}.
-
-       Acronyms are a specific type of abbreviation where the first letters (or
-       groups of letters) of each word are combined to form a new pronounceable
-       word. In the corpus, we encounter examples like 
-       \emph{Anatel}\footnote{\emph{Agência Nacional de Telecomunicações} (National Telecommunications Agency)},
-       \emph{Ovni}\footnote{\emph{Objeto voador não identificado} (unidentified flying object - UFO)},
-       \emph{Sida}\footnote{\emph{Síndrome da Imunodeficiência Adquirida} (acquired immunodeficiency syndrome - AIDS)} (in Portugal) and
-       \emph{Mercosul}\footnote{\emph{Mercado Comum do Sul} (Southern Common Market).}.
-
-       These various forms of abbreviation play an important role in written
-       language, providing concise ways to represent longer words or phrases.
-       It is important to note that abbreviations, acronyms, and initialisms
-       are generally treated as single units and are not hyphenated.
-
-\end{description}
-
-\section{Creating a new set of rules using Patgen}
+\input{introduction.tex}
+\input{patterns.tex}
+\input{patgen.tex}
+\input{texrulespt.tex}
+\input{methodology.tex}
+\input{writingsystems.tex}
+\input{portuguesespelling.tex}
+\input{dictionary.tex}
+\input{resultsdefaultrules.tex}
+\input{updatingrules.tex}
+\input{limitations.tex}
+\input{patgenrules.tex}
 
@@
 
-\section{Old Text}
+% ==== OLD TEXT ====
+\section{Hyphenation rule patches}\label{sec-hyph-rpatches}
+OLD TEST
+
+OLD TEST
 
@@
 
-\begin{enumerate}
-\item\label{rulegrp_psi} regra: \texttt{p2si}, \texttt{p2sí} -- psicologia, psíquico\\
-exceção: \texttt{p3sia}, \texttt{p3sin} -- epilepsia, rodopsina
+\begin{rules}
+\item\label{rulegrp_psi} regra: \texttt{.p2si}, \texttt{.p2sí} -- psicologia, psíquico % update (word-initial pattern, exception not necessary (?)) 
+%\item\label{rulegrp_psi} regra: \texttt{p2si}, \texttt{p2sí} -- psicologia, psíquico\\
+%exceção: \texttt{p3sia}, \texttt{p3sin} -- epilepsia, rodopsina
 
@@
 \item\label{rulegrp_pt} regra: \texttt{.p2t} -- ptose%, pterossauro
+
+\item\label{rulegrp_tm} regra: \texttt{.t2m} -- tmese % [new rule] needs to be incorporated and checked
 
@@
 
-\item\label{rulegrp_sub} regra: \texttt{su2b3r}, \texttt{su2b3l} -- sublunar, subrotina
-exceção: \texttt{su3b4li1nh}, \texttt{su3b4li1ma}, \texttt{su3b4li1me}, \texttt{su3b4li1mid} -- sublinhar, sublimar, sublime, sublimidade
+\item\label{rulegrp_sub} regra: \texttt{su2b3r}, \texttt{su2b3l} -- sublunar, subrotina \\
+exceção: \texttt{.su3b4li}
+%exceção: \texttt{su3b4li1nh}, \texttt{su3b4li1ma}, \texttt{su3b4li1me}, \texttt{su3b4li1mid} -- sublinhar, sublimar, sublime, sublimidade
 
@@
 
-\item\label{rulegrp_ein} regra: \texttt{e1in1c}, \texttt{e1in1f}, \texttt{e1in1g}, \texttt{e1in1s}, \texttt{e1in1t}, \texttt{e1in1v} -- reincidência, reinfecção, reingressa, reinserção, reintegração, reinventar
-exceção: \texttt{e1in2st}, \texttt{e1in2sc} -- reinstalado, reinscrever
+%\item\label{rulegrp_ein} regra: \texttt{e1in1c}, \texttt{e1in1f}, \texttt{e1in1g}, \texttt{e1in1s}, \texttt{e1in1t}, \texttt{e1in1v} -- reincidência, reinfecção, reingressa, reinserção, reintegração, reinventar \\
+%exceção: \texttt{e1in2st}, \texttt{e1in2sc} -- reinstalado, reinscrever
+
+\item\label{rulegrp_ein} regra: \texttt{e1inc}, \texttt{e1inf}, \texttt{e1ing}, \texttt{e1ins}, \texttt{e1int}, \texttt{e1inv} -- reincidência, reinfecção, reingressa, reinserção, reintegração, reinventar \\
+% exceção: \texttt{e1in2st}, \texttt{e1in2sc} -- reinstalado, reinscrever
+
+\item\label{rulegrp_unit} regra: \texttt{u1int}, \texttt{u1ind} -- contribuinte, excluindo
 
@@
 
-\item\label{rulegrp_aa} regra: \texttt{a1â}, \texttt{a1ã}, \texttt{a1é}, \texttt{a1í}, \texttt{a1ó}, \texttt{a1ô}, \texttt{a1ú}, \texttt{e1á}, \texttt{e1â}, \texttt{e1ã}, \texttt{e1ê}, \texttt{e1í}, \texttt{e1ó}, \texttt{e1ô}, \texttt{e1ú}, \texttt{i1á}, \texttt{i1ã}, \texttt{i1ã}, \texttt{i1é}, \texttt{i1ó}, \texttt{i1ú}, \texttt{o1á}, \texttt{o1ã}, \texttt{o1é}, \texttt{o1ê}, \texttt{o1í}, \texttt{o1ó}, \texttt{u1á}, \texttt{u1ã}, \texttt{u1é}, \texttt{u1ê}, \texttt{u1í} --  abraâmico, abraão, aéreo, país, caótico, faraônico, saúde, balneário, oceânico, campeã, veêm, veículo, teórico, napoleônico, conteúdo, diário, região, soviético, periódico, viúva, razoável, joão, poético, boêmia, heroísmo, alcoólico, usuário, itapuã, suécia, cauê, suíça \\
+\item\label{rulegrp_aa} regra: \texttt{a1â}, \texttt{a1ã}, \texttt{a1é}, \texttt{a1í}, \texttt{a1ó}, \texttt{a1ô}, \texttt{a1ú}, \texttt{e1á}, \texttt{e1â}, \texttt{e1ã}, \texttt{e1é}, \texttt{e1ê}, \texttt{e1í}, \texttt{e1ó}, \texttt{e1ô}, \texttt{e1ú}, \texttt{é1o}, \texttt{i1á}, \texttt{i1ã}, \texttt{i1é}, \texttt{i1í}, \texttt{i1ó}, \texttt{i1u}, \texttt{i1ú}, \texttt{í1a}, \texttt{o1á}, \texttt{o1ã}, \texttt{o1é}, \texttt{o1ê}, \texttt{o1í}, \texttt{o1ó}, \texttt{u1á}, \texttt{u1ã}, \texttt{u1é}, \texttt{u1ê}, \texttt{u1í}, \texttt{ú1o} --  abraâmico, abraão, aéreo, país, caótico, faraônico, saúde, balneário, oceânico, campeã, feérico, veêm, veículo, teórico, napoleônico, conteúdo, néon, diário, região, soviético, iídiche, periódico, feiura, viúva, maníaco, razoável, joão, poético, boêmia, heroísmo, alcoólico, usuário, itapuã, suécia, cauê, suíça, flúor \\
 exceção: \texttt{1gu2é}, \texttt{1gu2ê}, \texttt{1gu2í}, \texttt{1qu2á}, \texttt{1qu2é}, \texttt{1qu2ê}, \texttt{1qu2í} -- alguém, português, linguística, aquático, inquérito, sequência, química
+% the inclusion of rules e1é, é1o, i1í and í1a cause problem and if exceptions are necessary
+
+\item\label{rulegrp_gua} regra: \texttt{1gu4á}, \texttt{1gu4ã}, \texttt{1qu4ã} -- jaraguá, saguão, quão
 
 \item\label{rulegrp_air} regra: \texttt{a1ir.}, \texttt{u1ir.} -- sair, diminuir
+
+\item\label{rulegrp_aiz} regra: \texttt{u1iz.}, \texttt{a1iz.} -- juiz, raiz
 
@@
 
-\item\label{rulegrp_aui} regra: \texttt{au1i1c}, \texttt{du1i1c}, \texttt{u1i1ç}, \texttt{u1i1d}, \texttt{cu2i}, \texttt{dru2i}, \texttt{flu2id}, \texttt{bu1i1n}, \texttt{cu1i1n}, \texttt{fu1i1n}, \texttt{nu1i1n}, \texttt{ru1i1na}, \texttt{ru1i1no}, \texttt{su1i1ti}, \texttt{tu1i1ti}, \texttt{u1iz} -- cacauicultor, sanduicheira, constituição, continuidade, cuidador, druida, fluido, tabuinha, picuinha, fuinha, genuinamente, arruinado, arruinou, jesuitismo, intuitivo, juizado
+\item\label{rulegrp_aui} regra: \texttt{au1i1c}, \texttt{du1i1c}, \texttt{u1i1ç}, \texttt{u1i1d}, \texttt{cu2i}, \texttt{dru2i}, \texttt{flu2id}, \texttt{bu1i1n}, \texttt{cu1i1n}, \texttt{fu1i1n}, \texttt{nu1i1n}, \texttt{ru1i1na}, \texttt{ru1i1no}, \texttt{su1i1ti}, \texttt{tu1i1ti}, \texttt{u1iz} -- cacauicultor, sanduicheira, constituição, continuidade, cuidador, druida, fluido, tabuinha, picuinha, fuinha, genuinamente, arruinado, arruinou, jesuitismo, intuitivo, juizado \\
 exceção: \texttt{cu3i1da1de}, \texttt{bu1i2n1d}, \texttt{bu1i2n1t}  -- acuidade, contribuindo, contribuinte
-
-\item\label{rulegrp_gua} regra: \texttt{1gu4á}, \texttt{1gu4ã}, \texttt{1qu4ã} -- jaraguá, saguão, quão
 
@@
 
-\item\label{rulegrp_lo} regra: \texttt{1lô} -- camelô
+%\item\label{rulegrp_lo} regra: \texttt{1lô} -- camelô
 
-\item\label{rulegrp_co} regra: \texttt{1cô} -- recôncavo
+%\item\label{rulegrp_co} regra: \texttt{1cô} -- recôncavo
 
-\item\label{rulegrp_bo} regra: \texttt{1bô}, \texttt{1dô}, \texttt{1fô}, \texttt{1gô}, \texttt{1pô}, \texttt{1mô}, \texttt{1nô}, \texttt{1rô}, \texttt{1tô}, \texttt{1vô}, \texttt{1xô}, \texttt{1zô} -- robô, judô,  telefônica, xangô, capô, sumô, econômico, tarô, chatô, vovô, saxônia, amazônia
+\item\label{rulegrp_bo} regra: \texttt{1bô}, \texttt{1cô}, \texttt{1dô}, \texttt{1fô}, \texttt{1gô}, \texttt{1lô}, \texttt{1pô}, \texttt{1mô}, \texttt{1nô}, \texttt{1rô}, \texttt{1tô}, \texttt{1vô}, \texttt{1xô}, \texttt{1zô} -- robô, recôncavo, judô, telefônica, xangô, camelô, capô, sumô, econômico, tarô, chatô, vovô, saxônia, amazônia
 
@@
     \setcounter{numberRulesGroups}{\value{enumi}}
-\end{enumerate}
+\end{rules}
 

### 2024-06-06 article/defvariables.tex
updates

\captureshell*[\NumberOfDefaultRules]{wc -l ../data/default.TeX.pt-br.patterns | cut -d' ' -f1}

\captureshell*[\NumberOfNewRules]{wc -l ../data/patch.TeX.pt-br.patterns | cut -d' ' -f1}

\captureshell*[\DictionarySize]{../scripts/dicstats.sh} % number of words that have at least one hyphenation
\captureshell*[\CorpusSize]{../scripts/dicstats.sh -1} % total number of words in the corpus used (same as $ wc -l ../data/hyphenatios.csv)

% https://www.texdev.net/2009/10/06/what-does-write18-mean/
% number of words that hyphenations were found in N online dictionaries
\captureshell*[\NumberOfSixHyphens]{../scripts/dicstats.sh 6}  
\captureshell*[\NumberOfFiveHyphens]{../scripts/dicstats.sh 5}
\captureshell*[\NumberOfFourHyphen]{../scripts/dicstats.sh 4}
\captureshell*[\NumberOfThreeHyphens]{../scripts/dicstats.sh 3}
\captureshell*[\NumberOfTwoHyphens]{../scripts/dicstats.sh 2}
\captureshell*[\NumberOfOneHyphens]{../scripts/dicstats.sh 1}
\captureshell*[\NumberOfNoHyphens]{../scripts/dicstats.sh 0}
\captureshell*[\NumberOfFourToSixHyphens]{../scripts/dicstats.sh 6../scripts/dicstats.sh 4-6}
% run to update values
%\immediate\write18{../scripts/hyphenationagreements.sh > ../data/hyphagreements}
\captureshell*[\NumberOfSixAgrees]{cat ../data/hyphenations6.dic | wc -l}
% run to update hyphen5 dic
%\immediate\write18{../scripts/get51.sh > ../data/hyphenations5.dic}
%\immediate\write18{../scripts/manualcorrections.sh ../data/hyphenations5.dic}
\captureshell*[\NumberOfFiveAgrees]{cat ../data/hyphenations5.dic | wc -l} %#{../scripts/gethyphenationagreements.sh 5}
\captureshell*[\NumberOfSixFiveAgrees]{cat ../data/hyphenations6.dic ../data/hyphenations5.dic | wc -l}
\captureshell*[\NumberOfFourAgrees]{../scripts/gethyphenationagreements.sh 4}
\captureshell*[\NumberOfThreeAgrees]{../scripts/gethyphenationagreements.sh 3}
\captureshell*[\NumberOfTwoAgrees]{../scripts/gethyphenationagreements.sh 2}
\captureshell*[\NumberOfOneAgrees]{../scripts/gethyphenationagreements.sh 1}

\captureshell*[\ExceptionRulesCV]{../scripts/listrules.sh 1}
\captureshell*[\ExceptionRulesLR]{../scripts/listrules.sh 2[lr]}
\captureshell*[\ExceptionRulesCLNH]{../scripts/listrules.sh [cln]2h}
\captureshell*[\ExceptionRulesThree]{../scripts/listrules.sh 3}
\captureshell*[\ExceptionRulesFour]{../scripts/listrules.sh 4}

\captureshell*[\NumberOfAppProp]{grep ':' ../data/hyphenations.csv | wc -l} % number of apparent proparoxytones

%\immediate\write18{../scripts/gocreateresultfile.sh ../data/hyphenations6.dic ../data/default.TeX.pt-br.patterns > ../data/hyphenations6result-default-patterns.dic}
\immediate\write18{../scripts/resultfileexamples.sh -w -f ../data/hyphenations6result-default-patterns.dic | sed ''s/$/\\n/g'' > /tmp/hyphenations6result-default-patterns_wrong.dic}
\AtEndDocument{\immediate\write18{rm -f /tmp/hyphenations6result-default-patterns_wrong.dic}}
\immediate\write18{../scripts/resultfileexamples.sh -m -n 20 -f ../data/hyphenations6result-default-patterns.dic | sed ''s/$/\\n/g'' > /tmp/hyphenations6result-default-patterns_missing.dic}
\AtEndDocument{\immediate\write18{rm -f /tmp/hyphenations6result-default-patterns_missing.dic}}
\immediate\write18{../scripts/resultfileexamples.sh -m -f ../data/hyphenations6result-default-patterns.dic | ../scripts/filtersurrounding.sh -c '-' -n 1 | sort | uniq -c | sort -nr | sed ''s/$/\\n/g'' > /tmp/hyphenations6result-default-patterns_missing_context}
\AtEndDocument{\immediate\write18{rm -f /tmp/hyphenations6result-default-patterns_missing_context}}
% number of words correctly hyphenated using default TeX rules when analysing the words in hyphenations6.dic
\captureshell*[\NumberOfCorrectSix]{../scripts/resultfilemetrics.sh -c -f ../data/hyphenations6result-default-patterns.dic}
% number of words with wrong hyphenations using default TeX rules when analysing the words in hyphenations6.dic
\captureshell*[\NumberOfWrongSix]{../scripts/resultfilemetrics.sh -w -f ../data/hyphenations6result-default-patterns.dic}
% number of words with missing hyphenations using default TeX rules when analysing the words in hyphenations6.dic
\captureshell*[\NumberOfMissingSix]{../scripts/resultfilemetrics.sh -m -f ../data/hyphenations6result-default-patterns.dic}
% total number of words in hyphenations6.dic
\captureshell*[\NumberOfTotalSix]{wc -l ../data/hyphenations6result-default-patterns.dic | awk '{print $1}'}

%\immediate\write18{../scripts/gocreateresultfile.sh ../data/hyphenations5.dic ../data/default.TeX.pt-br.patterns > ../data/hyphenations5result-default-patterns.dic}
%\immediate\write18{grep "\." ../data/hyphenations5result-default-patterns.dic > ../data/hyphenations5result-default-patterns_wrong.dic}
%\immediate\write18{grep "\-" ../data/hyphenations5result-default-patterns.dic > ../data/hyphenations5result-default-patterns_missing.dic}
% number of words correctly hyphenated using default TeX rules when analysing the words in hyphenations5.dic
\captureshell*[\NumberOfCorrectFive]{../scripts/resultfilemetrics.sh -c -f ../data/hyphenations5result-default-patterns.dic} 
% number of words with wrong hyphenations using default TeX rules when analysing the words in hyphenations5.dic
\captureshell*[\NumberOfWrongFive]{../scripts/resultfilemetrics.sh -w -f ../data/hyphenations5result-default-patterns.dic}
% number of words with missing hyphenations using default TeX rules when analysing the words in hyphenations5.dic
\captureshell*[\NumberOfMissingFive]{../scripts/resultfilemetrics.sh -m -f ../data/hyphenations5result-default-patterns.dic}
% total number of words in hyphenations6.dic
\captureshell*[\NumberOfTotalFive]{wc -l ../data/hyphenations5result-default-patterns.dic | awk '{print $1}'}

%\immediate\write18{../scripts/gocreateresultfile.sh ../data/hyphenations4.dic ../data/default.TeX.pt-br.patterns > ../data/hyphenations4result-default-patterns.dic}
%\immediate\write18{grep "\." ../data/hyphenations4result-default-patterns.dic > ../data/hyphenations4result-default-patterns_wrong.dic}
%\immediate\write18{grep "\-" ../data/hyphenations4result-default-patterns.dic > ../data/hyphenations4result-default-patterns_missing.dic}
% number of words correctly hyphenated using default TeX rules when analysing the words in hyphenations4.dic
\captureshell*[\NumberOfCorrectFour]{../scripts/resultfilemetrics.sh -c -f ../data/hyphenations4result-default-patterns.dic} 
% number of words with wrong hyphenations using default TeX rules when analysing the words in hyphenations4.dic
\captureshell*[\NumberOfWrongFour]{../scripts/resultfilemetrics.sh -w -f ../data/hyphenations4result-default-patterns.dic}
% number of words with missing hyphenations using default TeX rules when analysing the words in hyphenations4.dic
\captureshell*[\NumberOfMissingFour]{../scripts/resultfilemetrics.sh -m -f ../data/hyphenations4result-default-patterns.dic}
% total number of words in hyphenations4.dic
\captureshell*[\NumberOfTotalFour]{wc -l ../data/hyphenations4result-default-patterns.dic | awk '{print $1}'}

%\captureshell*[\ListOfWrongWordsSix]{../scripts/resultfileexamples.sh -w -n 20 -f ../data/hyphenations6result-default-patterns.dic}
%\captureshell*[\ListOfMissingWordsSix]{../scripts/resultfileexamples.sh -m -n 20 -f ../data/hyphenations6result-default-patterns.dic}
%\captureshell*[\ListOfWrongWordsFive]{../scripts/resultfileexamples.sh -w -n 20 -f ../data/hyphenations5result-default-patterns.dic}
%\captureshell*[\ListOfMissingWordsFive]{../scripts/resultfileexamples.sh -m -n 20 -f ../data/hyphenations5result-default-patterns.dic}
%\captureshell*[\ListOfWrongWordsFour]{../scripts/resultfileexamples.sh -w -n 20 -f ../data/hyphenations4result-default-patterns.dic}
%\captureshell*[\ListOfMissingWordsFour]{../scripts/resultfileexamples.sh -m -n 20 -f ../data/hyphenations4result-default-patterns.dic}

\captureshell*[\NumberOfCorrectSum]{../scripts/resultfilemetrics.sh -c -f ../data/hyphenations6result-default-patterns.dic -f ../data/hyphenations5result-default-patterns.dic -f ../data/hyphenations4result-default-patterns.dic}
\captureshell*[\NumberOfWrongSum]{../scripts/resultfilemetrics.sh -w -f ../data/hyphenations6result-default-patterns.dic -f ../data/hyphenations5result-default-patterns.dic -f ../data/hyphenations4result-default-patterns.dic}
\captureshell*[\NumberOfMissingSum]{../scripts/resultfilemetrics.sh -m -f ../data/hyphenations6result-default-patterns.dic -f ../data/hyphenations5result-default-patterns.dic -f ../data/hyphenations4result-default-patterns.dic}
\captureshell*[\NumberOfTotalSum]{wc -l ../data/hyphenations4result-default-patterns.dic ../data/hyphenations5result-default-patterns.dic ../data/hyphenations6result-default-patterns.dic | tail -n 1  | awk '{print $1}'}

\newcounter{numberRulesGroups}

### 2024-06-06 article/dictionary.tex
updates

\section{Creating the dictionary}\label{sec-dictionay}

A bash script, named \texttt{gethyphenations.sh}, was developed to crawl six
online dictionaries and extract word hyphenations whenever available. The
process involves launching parallel threads for each word in the list, querying
a specific online dictionary, and retrieving the corresponding hyphenation. For
this purpose, individual scripts were created for each dictionary:
\texttt{getmichaelishyphenation.sh} for \href{https://michaelis.uol.com.br/}{Michaelis},
\texttt{getpriberamhyphenation.sh} for \href{https://dicionario.priberam.org/}{Priberam},
\texttt{getwiktionaryhyphenation.sh} for \href{https://pt.wiktionary.org}{Wikcionário},
\texttt{getauletehyphenation.sh} for \href{https://aulete.com.br/}{Aulete},
\texttt{getportalhyphenations.sh} for \href{http://www.portaldalinguaportuguesa.org/}{Portal da Língua Portuguesa}, and
\texttt{getdiciohyphenation.sh} for \href{https://www.dicio.com.br/}{Dicio}.
This systematic approach ensures efficient and accurate extraction of
hyphenations from various online sources. The resulting data is stored in a CSV\footnote{
    Comma-separated values (CSV) is a text file format defined in \href{https://datatracker.ietf.org/doc/html/rfc4180}{RFC 4180}.
    In CSV, commas are used to separate values, and each line in the file represents a new record. Records consist of fields separated by delimiters, typically a single comma.
} file named \texttt{hyphenations.csv}.

\subsection{Establishing a gold standard}

To establish our gold standard for hyphenation, we will compare the
hyphenations offered by all six dictionaries. First, we will determine the total count
of unique hyphenations across these dictionaries using the script
\texttt{hyphenation\-agreements.sh}.
It's worth noting that certain dictionaries annotate words with a colon (`:') to
indicate potential variations in pronunciation or production.
Particularly, `apparent proparoxytones' might appear marked by this colon sign, indicating 
the possibility of a diphthongs or hiatuses in the word ending.
In Portuguese, words ending in \emph{ea}, \emph{eo}, \emph{ia}, \emph{ie},
\emph{io}, \emph{ua}, \emph{ue}, or \emph{uo}, with the stressed syllable
before these endings, can be considered either paroxytones ending in a rising
diphthong or proparoxytones ending in a hiatus. For instance, words like \emph{his-tó-ri:a}
and \emph{on-du-la-tó-ri:o} are examples of words marked as apparent
proparoxytones, suggesting they could be regarded as paroxytones (\emph{his-tó-ria}
and \emph{on-du-la-tó-rio}) or proparoxytones (\emph{his-tó-ri-a} and
\emph{on-du-la-tó-ri-o}). The script \texttt{hyphenationagreements.sh} 
offers four potential approaches to handle these apparent proparoxytones:
retaining the hyphenations with the colon mark to indicate an apparent proparoxytone; 
selecting only the paroxytone or only the proparoxytone counterpart; or counting both paroxytones and proparoxytones. 
Given the lack of consensus in the literature, our initial approach involves 
counting both hyphenations, and we will detail below how we resolve this issue. 
In our hyphenation dictionary, we have identified \NumberOfAppProp{} words marked as apparent proparoxytones.

As our initial hyphenation reference, we will consider those cases where all
six dictionaries are in agreement. This comprehensive list comprises
\num{\NumberOfSixAgrees} words. Their corresponding hyphenations are
meticulously compiled and stored in the file \texttt{hyphenations6.dic}. This
curated list serves as a benchmark for evaluating the accuracy and
effectiveness of hyphenation rules generated through computational methods. It
will establish a reliable baseline for our hyphenation analysis, enabling us to
assess and refine our methodologies effectively.

In case of disagreement, we must exercise caution and examine each instance.
We might be tempted to choose the majority vote approach, simply selecting
those hyphenations that have the most supporters, but it is unclear 
how the hyphenations on those online dictionaries were curated; 
many might use algorithmic approaches, leading to potential flaws shared
among them. 
For example, 5 dictionaries use the hyphenation 
\emph{quart-zo} while the dictionary Aulete (originally from Portugal) favors the hyphenation \emph{quar-tzo},
which can be explained by the lack of an epenthetic vowel in European Portuguese\footnote{
The online dictionary Aulete has its origins on the printed version known as \emph{Dicionário Caldas Aulete}.
It is a dictionary from Portugal, reflecting the European Portuguese dialect.} \parencite{mateus}.
% Epêntese Vocálica e Restrições de Acento no Português do Sul do Brasil, Gisela COLLISCHONN  - Universidade Federal do Rio Grande do Sul (UFRGS)
% https://core.ac.uk/download/pdf/293615216.pdf
Similarly, \emph{ap-nei-a} or \emph{a-pnei-a} and \emph{disp-nei-a} or \emph{dis-pnei-a} should
be accepted considering, since there could be an epenthetic vowel (Brazilian Portuguese) or not (European Portuguese).
The same happens with \emph{hiperalgesia}, already mentioned in Section \ref{sec-grammar-port}.
Among other examples, we might also highlight \emph{neerlandês}, which appears 
hyphenated as \emph{ne-er-lan-dês} in five dictionaries and as \emph{neer-lan-dês} in one.
If we consider its pronunciation, we would prefer the former hyphenation, but the
first one conforms better to regular written syllables in Portuguese.
%The same happens with \emph{de-sem-ba-i-nhar} and \emph{de-sem-bai-nhar},
%the former one receiving the majority of the votes.
Some strings might accept more than one hyphenation, since they represent different words. For example, 
\emph{sub-li-nha} and \emph{su-bli-nha}, where the former is the substantive \emph{underline} and the latter is a flexed form of the verb \emph{to underline}.
%\todo{Aline, segue a lista dos casos duvidosos que encontrei com votos 5 a 1. Marquei em negrito aqueles
%    que considero ser a forma correta.
%    quart-zo(5), \textbf{quar-tzo}(1) (assim também trocar quart-zi-to por \textbf{quar-tzi-to)}; \textbf{sub-li-nha}(5), \textbf{su-bli-nha}(1); 
%    de-sem-ba-i-nhar(5), \textbf{de-sem-bai-nhar}(1); ap-nei-a(5), \textbf{a-pnei-a}(1); 
%    disp-nei-a(5), dispneia(1) (\textbf{dis-pnei-a}, forma não encontrada nos dicionários); 
%    hi-pe-ral-ge-si-a(5), \textbf{hi-per-al-ge-si-a}(1);
%    in-de-is-cen-te(5), \textbf{in-deis-cen-te}(1); jo-in-vi-len-se(5), \textbf{join-vi-len-se}(1); 
%    ne-er-lan-dês(5), \textbf{neer-lan-dês}(1). Os demais casos de 5 a 1 são proparoxítonas aparentes.
%}

The procedure to create the second list of hyphenated words involved several steps:
\begin{enumerate*}[label=\arabic*)]
  \item select those hyphenations agreed by five dictionaries, that have no alternative hyphenation proposal (5 to 0 votes);
  \item from those with alternative proposals, exam whether they constituted apparent proparoxytones (these cases could arise from instances with 5 to 1 votes or 6 to 1 votes, as explained earlier), 
      \begin{enumerate*}[label=\alph*)]
	  \item if the word had a diacritic, select the paroxytone option (e.g. \emph{po-lí-cia} instead of \emph{po-lí-ci-a} and \emph{pe-rí-neo} instead of \emph{pe-rí-ne-o}),
	  \item if not, choose the proparoxytone option (e.g. \emph{au-to-ri-a} instead of \emph{au-to-ri-a} and \emph{mar-ce-nei-ro} instead of \emph{mar-ce-neiro})\footnote{We just have to make sure we are not selecting those cases where there is a sequence of the form \texttt{[gq]u-[aeio]} (using regex notation), as in \emph{a-pa-zi-gu-ar} and \emph{en-xa-gu-ar}.}.
	      % [gq]u-[aeio]
      \end{enumerate*}
  \item if the word did not fall into the apparent proparoxytone category, select the hyphenation with five votes.
\end{enumerate*}
This procedure was implemented in the script \texttt{get51.sh}. 
Only a few hyphenations required manual correction, including the following that were added:
\emph{quar-tzo}, \emph{quar-tzi-to}, \emph{su-bli-nha}, \emph{a-pnei-a}, \emph{dis-pnei-a}, 
\emph{hi-per-al-ge-si-a}, and \emph{neer-lan-dês}.
The final list, containing \num{\NumberOfFiveAgrees} additional hyphenations, is stored in \texttt{hyphenations5.dic}, 
bringing the total number of hyphenations across both lists to \num{\NumberOfSixFiveAgrees}.

% results from script ./get51.sh
% cases where majority vote might go wrong:
% sub-li-nha(5),su-bli-nha(1) % both are valid
% de-sem-ba-i-nhar(5),de-sem-bai-nhar(1) % de-sem-bai-nhar seems to be the correct choice
% ap-nei-a(5),a-pnei-a(1) % ??
% disp-nei-a(5),dispneia(1) or dis-pnei-a?
% hi-pe-ral-ge-si-a(5),hi-per-al-ge-si-a(1)
% in-de-is-cen-te(5),in-deis-cen-te(1)
% jo-in-vi-len-se(5),join-vi-len-se(1)
% ne-er-lan-dês(5),neer-lan-dês(1)
% the remaining are apparent proparoxytones

For those hyphenations with four votes, we adopted a similar approach to the
one used previously. Many words garnered only four votes, indicating a lack of
alternative hyphenations provided by any dictionary, and were thus initially
hyphenated as proparoxytones. These instances were typically distinguished by
diacritics in the third-to-last syllable and a \emph{V-V} sequence at the end.
To address this, we converted these words into paroxytones by eliminating the
final hyphen. In cases where alternative hyphenations were available, we
assessed the presence of diacritics. If diacritics were detected, we chose the
paroxytone option; otherwise, we defaulted to the proparoxytone option. In
instances with multiple alternative options, we selected the option with the
highest frequency of votes. This procedure is implemented in the script
\texttt{get4.sh}.

% analisar os resultados das hifenizações através da análise de frequência das sílabas
% as silabas de baixa frequência podem ser indicativos de erros... verificar a origem delas
% cat ../data/hyphenations6.dic ../data/hyphenations5.dic ../data/hyphenations4.dic | tr '-' '\n' | sort | uniq -c | sort -nr > /tmp/syls
% grep -P "\s+1\s[^0-9]+$" /tmp/syls | tr -d '1' | sed 's/^\s\+//g' | while read syl; do grep "^$syl-\|-$syl-\|-$syl$" ../data/hyphenations6.dic; done > /tmp/rare
% grep -P "\s+1\s[^0-9]+$" /tmp/syls | tr -d '1' | sed 's/^\s\+//g' | while read syl; do grep "^$syl-\|-$syl-\|-$syl$" ../data/hyphenations5.dic; done >> /tmp/rare
% grep -P "\s+1\s[^0-9]+$" /tmp/syls | tr -d '1' | sed 's/^\s\+//g' | while read syl; do grep "^$syl-\|-$syl-\|-$syl$" ../data/hyphenations4.dic; done >> /tmp/rare
% grep -P "\s+1\s[^0-9]+$" /tmp/syls | tr -d '1' | sed 's/^\s\+//g' | while read syl; do grep --color=always "^$syl-\|-$syl-\|-$syl$" <(cat ../data/hyphenations6.dic ../data/hyphenations5.dic ../data/hyphenations4.dic); done | ansi2html > /tmp/rare.html

% fun-ci-o-ná-ri-o > fun-ci-o-ná-rio
% co-mí-ci-o > co-mí-cio
% con-vê-ni-o > con-vê-nio
% cri-té-ri-o > cri-té-rio
% ple-ná-ri-o > ple-ná-rio
% cre-di-á-ri-o > cre-di-á-rio
% es-tá-gi-o > es-tá-gio
% in-ter-ban-cá-ri-o > in-ter-ban-cá-rio
% ur-gên-ci-a > ur-gên-cia
% i-mo-bi-li-á-ri-a > i-mo-bi-li-á-ria
% re-vo-lu-ci-o-ná-ri-o > re-vo-lu-ci-o-ná-rio
% ve-ló-ri-o > ve-ló-rio
% es-có-ci-a > es-có-cia
% for-mu-lá-ri-o > for-mu-lá-rio
% or-ça-men-tá-ri-o > or-ça-men-tá-rio

% ag-nós-ti-co(5),a-gnós-ti-co(1)   << ?
% co-i-bir(5),coi-bir(1)            << both are correct?
% drui-da(5),dru-i-da(1)            << drui-da is correct, since an hiatus would require an accent dru-í-da
% flui-do(5),flu-i-do(1)            << as there is no diacritic it should be flui-do
%					fluido (sem acento) - substantivo: flui-do (ditongo) -- exemplo: O fluido de freio acabou.
%					fluido (com acento) - forma verbal: flu-í-do (hiato) -- exemplo: A discussão para aprovar reformas no país não tem fluído como esperavam os governantes.
% sub-li-nha(5),su-bli-nha(1)       << sub-linha or su-blinha (sublinhar) 
% man-ti-do(5) mantido(1)           << mantido clearly was not hyphenated 
% quart-zo(5),quar-tzo(1)           << quar-tzo sounds like the correct choice
% den-ti-frí-ci-o(5),den-ti-frí-cio(1) << it should be marked as apparent proparoxytones but no one did

%compare_strings() {
%    # Trim leading and trailing whitespace from the first string
%    string1_trimmed="${1#"${1%%[![:space:]]*}"}"
%    string1_trimmed="${string1_trimmed%"${string1_trimmed##*[![:space:]]}"}"
%
%    # Trim leading and trailing whitespace from the second string
%    string2_trimmed="${2#"${2%%[![:space:]]*}"}"
%    string2_trimmed="${string2_trimmed%"${string2_trimmed##*[![:space:]]}"}"
%
%    if [ "$string1_trimmed" == "$string2_trimmed" ]; then
%        return 0  # Strings are equal
%    else
%        return 1  # Strings are different
%    fi
%}

% grep "(5)" ../data/hyphagreements | grep "(1)" | head | tr -d '()0-9' | while read line; do word1=$(echo $line | cut -d, -f1); word2=$(echo $line | cut -d, -f2); count1=$(grep -o '-' <<< "$word1" | wc -l); count2=$(grep -o '-' <<< "$word2" | wc -l); if [ $count1 -gt $count2 ]; then w1=$(echo $word1 | sed 's/\(.*\)-/\1/'); compare_strings "$w1" "word2"; result=$?; if [ $result -ne 0 ]; then echo "c1: $line $w1 $word2"; od -c <<< "$w1"; od -c <<< "$word2"; fi; elif [ $count1 -lt $count2 ]; then w2=$(echo $word2 | sed 's/\(.*\)-/\1/'); compare_strings "$w2" "word1"; result=$?; if [ $result -ne 0 ]; then echo "c2: $line $word1 $w2"; fi; else compare_strings "$word1" "word2"; result=$?; if [ $result -ne 0 ]; then echo $line; fi; fi; done

After completing the aforementioned procedures to create our golden hyphenation
dictionary, manual corrections may still be necessary to ensure its accuracy
and reliability. These manual adjustments, which encompass the corrections
described earlier, are documented in the file \texttt{replacements.txt}.
Utilizing the script \texttt{manualcorrections.sh}, we meticulously apply these
corrections to refine our hyphenation dictionary and enhance its effectiveness.

% results
% ./gocreateresultfile.sh ../data/hyphenations6.dic  ../data/default.TeX.pt-br.patterns > ../data/results_hyph6_dfpatt

### 2024-06-06 article/introduction.tex
updates

\section{Introduction}\label{sec-intro}

Hyphenation in text wrapping was not used for a long time. Words should fit
entirely in a line, or they would be broken in arbitrary places.  Initially, no
markers were used to indicate word wrapping, leading to potential confusion and
unintended interpretations. As a result, orthographers advocated for the
introduction of a sign to indicate such breaks. Portuguese faced the same
gradual introduction of a hyphenation sign to mark words wrapping across lines.
Even though the usage of a hyphenation sign ($=$) was advocated by
orthographers \parencite{gandavo1574}, few documents used such sign until the end of
the 18th century \parencite{araujo2015}.

In some cases, hyphenation hinders smooth reading and should be avoided in
child literature. In opposition, both excessive spacing and insufficient
spacing between words also impose difficulty in the reading process, making
hyphenation fundamental when texts use short line lengths. As a line gets
shorter, the number of breaking candidates between words decreases, leading to
awkward spaces between words and among letters. For that matter, automatic
hyphenation plays an important role in good typesetting.

%Automatic hyphenation plays an important role in good typesetting and
%it is fundamental when a text uses short line lengths. As a line gets
%shorter, the number of breaking candidates between words decreases,
%creating awkward spaces between words and among letters.

\TeX{} is a typesetting system which carefully deals with these issues,
automatically arranging text on a page to create a good reading experience.
Automatic hyphenation is an important part on this process,
promoting an even-tempered distribution of elements on the page.
%Hyphenation is therefore an important part on this process.
%A good readability depends on an even-tempered distribution of elements
%on the page.
Line height and line length, paragraph length, font size and typeface,
letter-spacing, and word-spacing are some factors which influence the text legibility
and readability. Space between words should not be too long creating lakes and
rivers in the text, nor too tight, impairing the legibility and readability.

Another important matter to consider is ambiguities that might be created when
a word is partitioned during the hyphenation process. In English we should
avoid hyphenations such as \emph{re-cover}, \emph{re-form}, \emph{re-sign}, \emph{the-rapist},
\emph{depart-mental}, and \emph{mans-laughter} (in Portuguese, some examples are:
\emph{de-putada}, \emph{fede-ração}, \emph{acu-mula}, \emph{após-tolo},
\emph{cú-bico}). Hyphenations that might lead the reader to pronounce a word
incorrectly should also be prevented. That is the case of
\emph{considera-tion}, in Enslish (and \emph{pe-rigo} in Portuguese).

In some situations, hyphenation is also a matter of style. Some partitioning
choices sound better than others. These conflicting alternatives typically
arises when a words has many possible hyphenation points. Consider
\emph{ar-chae-ol-o-gist} (\emph{or ar-che-ol-o-gist}), which is preferably partitioned as
\emph{archae-ologist} (or \emph{arche-ologist}) in opposition to \emph{archaeol-ogist} (or
\emph{archeol-ogist}) or \emph{archaeolo-gist} (or \emph{archeolo-gist}). It is preferable to keep
whole morphemes together. In the previous example: \emph{archae} (or \emph{arche}, meaning
``ancient'', ``primitive'')
%\footnote{archae- comes from the Ancient Greek ἀρχαῖος (arkhaîos, `ancient',
%`primitive'), from ἀρχή (arkhḗ, `beginning').}
%https://en.wiktionary.org/wiki/archae-
and \emph{-ologist} (``one who studies the topic''). In Portuguese, it is also more
elegant to avoid splits between double consonants or vowels, even if an
hyphenation point do exists between those letters. For example,
\emph{pressu-rizar} is preferable over \emph{pres-surizar} and
\emph{empreen-dedor} is preferable over \emph{empre-endedor}. Even so,
exceptions exists, it is preferable to partition \emph{micro-organismo}
rather than \emph{microor-ganismo} (keeping morphemes together is favored
over splitting a double vowel). Numerous factors come into play when choosing
the optimal hyphenation point for a word.

The general rule for Portuguese hyphenation is to split a word into its
syllables. A syllable is made of a mandatory nucleus, filled by a vowel, and
optional peripheral consonants (before or after the nucleus). In some
situations, the syllabic division does not respect the ethnologic constituents.
The usage of the prefixes \emph{bis-} and \emph{in-} are examples of this
circumstance. The correct syllabifications are \emph{bi-sa-vô},
\emph{i-nobs-tan-te}\footnote{The rule of syllable
division could lead to two possible partitions: \emph{i-nobs-tan-te} and
\emph{in-obs-tan-te}, but the first is preferable.}, and \emph{i-na-ti-vo}, 
where the prefixes are split into two syllables. 
But, as pointed out previously, it is preferable to keep
morphemes together rather than splitting them apart. Therefore we should
favor the hyphenation \emph{bisa-vô} over \emph{bi-savô}, \emph{inobs-tante} 
over \emph{i-nobstante}, and \emph{ina-tivo} over \emph{i-nativo}. 
This last example could also lead to a misunderstanding
since the word \emph{nativo} (\emph{native} in English) emerges from this word
break.

Each language has its hyphenation rules, which can be categorized into two
groups: those driven by morphology (etymology) and those driven by
pronunciation.  An algorithmic approach employs a logical system to analyze
words and apply the hyphenation rules of a specific language. Since hyphenation
rules vary significantly between languages, an algorithm must be
developed for each one. While a logic-based system can be efficient and
compact, it still needs to address exceptions through hard-coded rules.

%The automation of this process might use a dictionary based approach, which
%will restrict the hyphenation possibilities to those entries in the dictionary,
%an algorithmic base approach, which might be applied to whatever sequence found
%in a text, or a mix of both approaches. 
%%An algorithmic approach might use a logic system to analyse words and apply
%%the hyphenation rules of a given language. 
%A rule base model might include the recognition of prefixes,
%suffixes, morphemes, or some sequences suitable for the inclusion of a break.
%Another approach is the usage of pattern matching. Given a corpus of
%hyphenation examples in a language, it is necessary to identify those sequence
%of letters that define a point where hyphenation is suitable or not. Patterns
%might include prefixes, suffixes, exceptions and special hyphenation rules of a
%given language. Such approach might be used for different languages, by
%providing hyphenation examples in a target language to extract patterns and
%rules.

The automation of this process can employ various approaches, including:
\begin{description}
\item[Dictionary-Based Approach:] This method restricts hyphenation
    possibilities to entries found in the dictionary.
\item[Algorithmic-Based Approach:] This approach can be applied to any sequence
    encountered in a text.
\item[Rule-Based Model:] This model recognizes prefixes, suffixes, morphemes,
    or specific sequences suitable for hyphenation.
\item[Pattern Matching:] By using a corpus of hyphenation examples in a
    language, this approach identifies letter sequences that determine suitable
    hyphenation points. Patterns encompass prefixes, suffixes, exceptions, and
    special hyphenation rules of the language.
\item[Mixed Approach:] This approach combines two or more of the previously
    described methods to enhance hyphenation accuracy and flexibility.
\end{description}

Analyzing only the immediate surroundings may not always suffice to determine a
potential hyphenation point. For instance, consider \emph{de-moc-ra-cy} and \emph{dem-o-crat},
where the immediate surrounding of the letter \emph{e} does not provide a clear
indication of the hyphenation point. 
Even when facing chosen patterns that typically make hyphenation
straightforward, exceptions can arise. Take the sequence \emph{tion}, for example.
It may seem logical to place a break before this pattern, but the word \emph{cation}
is hyphenated as \emph{cat-ion}, highlighting the influence of etymology on the way
a word is split.

A word with multiple meanings may have distinct hyphenations based on its intended meaning.
`For instance, the Swedish word form \emph{glassko} has three different
meanings, and can be hyphenated as \emph{glas-sko} (glass shoe),
\emph{glass-ko} (ice cream cow) and in the non-standard way,
\emph{glass-sko} (ice cream shoe)' \parencite{nemeth2006}. In Portuguese, the
word \emph{sublinha} might be hiphenated in two different ways:
\emph{su-bli-nha} when representing the inflected form of the verb
\emph{sublinhar} (to underline) or \emph{sub-li-nha} when refering
to the line under (underline as a noun).

% hyphenation might change with syntactic function
% part of speech (PoS)

Machine learning techniques were employed to hyphenate Norwegian text
\parencite{kristensen2001}. The study revealed that, overall, the \TeX{} approach
outperformed a neural network.  Both methods demonstrated similar performance
in identifying correct hyphenation points and minimizing incorrect hyphenations
when tested on a small word list (with the neural network slightly
outperforming in correctly recognizing hyphenation points).  However, when
tested on a larger word list, the \TeX{} approach proved superior in avoiding
incorrect hyphenations compared to the neural network.

The original \TeX{} hyphenation algorithm, introduced by %Knuth in 1977
\textcite{knuth1977}, primarily focused on the English language and employed three
main rules:
\begin{enumerate*}[label=(\arabic*)]
 \item suffix removal; 
 \item prefix removal; and 
 \item the Vowel-Consonant-Consonant-Vowel (VCCV) breaking rule\footnote{The 
     VCCV rule in hyphenation patterns, places the syllable boundary between 
     two consecutive consonants when they appear between two vowels. For example, 
     in the word \emph{sudden}, the syllable break occurs between the \emph{d} and 
     the second \emph{d}, making it \emph{sud-den}. 
     The VCCV pattern is a relatively common syllable division pattern in English.
     This rule ensures accurate 
     hyphenation, maintaining word readability and pronunciation when words are 
     split at the end of a line in printed text.}. 
\end{enumerate*}
Tests demonstrated that it could identify 40\% of allowable hyphen locations
\parencite{liang1983}.  The \TeX{} hyphenation algorithm later adopted the approach
proposed by Frank M. Liang, which involves competing patterns.  The \TeX{}82
algorithm employs five alternating levels of hyphenating and inhibiting
patterns. The program for pattern generation, known as PATGEN, was created by
%Liang 
\parencite{liangbreitenlohner1999} and has been utilized to generate
hyphenating patterns for numerous languages
\parencite{sojka1995,sojka1995a,sojka2005thesis,sojka2003,scannell2003}. It involves
sweeping a database of hyphenated words in a language to identify both
hyphenating and inhibiting patterns, ultimately creating a list of competing
patterns for that specific language.

The effective hyphenation of words by \TeX{} will actually depends on the following factors:
\begin{enumerate*}[label=(\arabic*)]
    \item document language, which will determine which set of patterns to apply;
    \item characters used, since some might block hyphenation at their edges;
    \item the value of the internal variables \verb|lefthyphenmin| and \verb|righthyphenmin|\footnote{
	The variables \verb|lefthyphenmin| and \verb|righthyphenmin| are language dependant and
	are defined in \emph{tlpobj} files (\verb|/usr/local/texlive/20XX/tlpkg/tlpobj/hyphen-xxxxxx.tlpobj|). 
	Default values varies in the range from 1 to 3. 
    	English and Portuguese, for example, use \verb|lefthyphenmin=2| and \verb|righthyphenmin=3|.},
	% ls /usr/local/texlive/2023/tlpkg/tlpobj/*.tlpobj | while read -r filename; do grep -Po "lefthyphenmin=[0-9]\s+righthyphenmin=[0-9]" $filename; done | tr '\t' ' ' | tr -s ' ' | sort | uniq -c
	%      17 lefthyphenmin=1 righthyphenmin=1
        %       6 lefthyphenmin=1 righthyphenmin=2
        %       1 lefthyphenmin=1 righthyphenmin=3
        %      49 lefthyphenmin=2 righthyphenmin=2
        %       9 lefthyphenmin=2 righthyphenmin=3
        which defines the minimum sequence length of characters at the left and right borders
        before any hyphenation is allowed.
\end{enumerate*}

Despite the fact that \TeX{} hyphenation algorithm and rules are old, they are,
to these days, the most frequently used approach, even outside the \TeX{}'s
world. The grounds for this is Hunspell, a spell checker and morphological
analyzer that is adopted in many softwares (e.g. LibreOffice, OpenOffice.org,
Mozilla Firefox, Mozilla Thunderbird, Google Chrome, macOS, InDesign, memoQ,
Opera, Affinity Publisher, among others \parencite{hunspell}). Hunspell uses \TeX{}
hyphenation rules \parencite{hunspellhyphen,levien1998}, making \TeX{} hyphenation
widespread in the computer world. That is a result of \TeX{} approach
simplicity and versatility.  The algorithm works effectively, as it already
supports rules for 66 languages \parencite{texhyphenrules}, and offers the
flexibility to create rules for any currently unsupported languages.

Unfortunately, certain hyphenation rules cannot be implemented using the \TeX{}
hyphenation algorithm. For example, in German, hyphenation can lead to letter
change or insertion.  Additionally, compound words lack hyphens, resulting in
extended letter sequences without visible separation and even repetitions of
the same letter, as seen in examples like \emph{Wasserrinne} and
\emph{Schifffahrt}.  Furthermore, the German spelling reform made some changes,
making it necessary to create a different set of rules for German hyphenation.
For example, the word \emph{Schiffahrt} should be hyphenated as
\emph{Schiff-fahrt}, preserving the \emph{f}s from each word that makes this
compound. The hyphenation should insert an \emph{f} that is not part of the
written form. That was not a problem for the old written form of the word:
\emph{Schifffahrt}. Also, the old hyphenating rules of German grammar stated
the hyphenation \emph{Bäk-ker} for the word \emph{Bäcker}, \emph{Zuk-ker} for
the word \emph{Zucker} and \emph{pak-ken} for the word \emph{packen}. Nowadays, those
words are hyphenated as \emph{Bä-cker}, \emph{Zu-cker} and \emph{pa-cken},
respectively. Some words have also changed their hyphenation point after the
spelling reform. For example, \emph{Fen-ster} became \emph{Fens-ter} and
\emph{mei-stens} became \emph{meis-tens}. Some problems in compound word
hyphenation in \TeX{} are discussed in \textcite{sojka1995a}.

% Some hyphenation rules are not possible with TeX algorithm.
% For example, the german word Schiffahrt should be hyphenated as Schiff-fahrt.
% Although it is no longer the recommend written form, it was the most usual
% until 2003 (see graph in schifffart.png from google ngrams).
% Also the old hyphenating rules of German grammatic stated the following
% hyphenations Bäk-ker (for the word Bäcker, what is now hyphenated as Bä-cker),
% Zuk-ker (for the word Zucker, what is now hyphenated as Zu-cker),
% pak-ken (for packen, and now pa-cken) and trok-ken (for trocken, now tro-cken).

%which contain archeo can be alternatively spelt with archaeo or archæo.

%GÂNDAVO, Pero de Magalhães de. Regras que ensinam a maneira de escrever e
%orthographia da lingoa portuguesa, etc. Lisboa: Antonio Gonsalvez, 1574

%  HIFENIZAÇÃO EM PORTUGUÊS
% Antonio Martins de ARAÚJO and Toru MARUYAMA

Moreover, as mentioned earlier, certain hyphenations may be preferred for
stylistic reasons, or to avoid ambiguity, or for better reading experience.
Some words might have multiple hyphenations, depending on the intended meaning.
In such cases, \TeX{} may not efficiently address the hyphenation challenge, as
it would necessitate case-by-case handling.

### 2024-06-06 article/limitations.tex
updates

\section{Limitations}

In general, although the erroneous words share some common characteristics that
might allow for a reduction in hyphenation errors to some extent, there is a
limitation inherent in the way \TeX{}'s rules are conceived. Below, we present
the systematics found in these data that could be encompassed by a different
rule structure:

\begin{description} 
    \item[Morphological determination:\label{morpho-det}] Prefixes such as \emph{re-},
	\emph{sub-}, \emph{ciber-}, \emph{hiper-}, and \emph{auto-}, among others, require separating the
	prefix from its stem, which can lead to phonological issues. For example, words like
	\emph{reiniciar}, \emph{sublinhar}, \emph{ciberespaço}, \emph{hiperalgesia}, and \emph{autoimagem} contain prefixes and could be hyphenated as 
	\emph{re-i-ni-ci-ar}, \emph{sub-li-nhar}, \emph{ci-ber-es-pa-ço}, \emph{hi-per-al-ge-si-a}, and \emph{au-to-i-ma-gem}, 
	respectively, to respect their morphological formation. However,
        considering that Portuguese hyphenates its words based on syllabic phonological correlates, 
	words that require morphological information, such as these, might not have their hyphenation performed correctly. 
	%In our corpus, there are twelve such words (eight with \emph{re-}, and one each with \emph{auto-}, \emph{meta-}, \emph{sub-}, \emph{cyber-}, \emph{geo-}, or \emph{neuro-}). 
	These examples are presented in \Cref{tab-mor-syl}.
	% $ { head -n 1 ../data/hyphenations.csv; grep "^sublinhar," ../data/hyphenations.csv; } | column -t -s,
	% su-bli-nhar (priberam, wiktionary, aulete)
	% sub-li-nhar (michaelis, portal, dicio)

	% $ { head -n 1 ../data/hyphenations.csv; grep "^auto[a-z]\+," ../data/hyphenations.csv | grep -v ",,,";} | column -t -s,

	\begin{table}
	\centering
	\scriptsize
	\caption{Hyphenation in the dictionaries of words having conflict between morphological and syllabic information.}
	\label{tab-mor-syl}
        \begin{tabular}{ll*{6}{c}}
	\toprule
	    word                      & hyphenation       & \multicolumn{6}{c}{dictionary} \\
             &                                            & Michaelis & Priberam & Wikitionary & Aulete & Portal & Dicio \\
	\midrule
        \multirow{2}{*}{sublinhar}    & su-bli-nhar       &           & x        & x           & x      &        &       \\
				      & sub-li-nhar       & x         &          &             &        & x      &       \\
	\midrule
	\multirow{2}{*}{reiniciar}    & rei-ni-ci-ar      &           &          & x           &        & x      &       \\
				      & re-i-ni-ci-ar     & x         & x        &             & x      &        & x     \\
	\midrule
	\multirow{2}{*}{ciberespaço}  & ci-be-res-pa-ço   &           & x        &             &        & x      &       \\
				      & ci-ber-es-pa-ço   & x         &          & x           & x      &        & x     \\
	\midrule
	\multirow{2}{*}{hiperalgesia} & hi-pe-ral-ge-si-a & x         & x        &             & x      & x      & x     \\
				      & hi-per-al-ge-si-a &           &          & x           &        &        &       \\
	\midrule
	\multirow{2}{*}{autoimagem}   & au-toi-ma-gem     &           &          &             &        & x      &       \\
				      & au-to-i-ma-gem    & x         &          &             & x      &        & x     \\
	\bottomrule
	\end{tabular}
	\end{table}

    \item[Foreignness:\label{foreignness}] There is a group of words %20 words 
	in the corpus that are terminologies or words incorporated into the 
	Portuguese language without full phonological adaptation, such as 
	\emph{darwinismo}, \emph{quilowatt}, and \emph{esfiha}. The lack of
	adaptation makes the phonological pattern very specific to the word,
	making it impossible to incorporate their cases \TeX{}'s rules alongside the
	other rules. The solution is to add them to the exception word list.

    \item[Word-initial consonant clusters:\label{word-init-cc}] Portuguese has few cases of
	consonant clusters at the beginning of a word. They are, in general, 
	etymological remnants and are currently unproductive in the language,
	since there are no neologisms with this pattern. Encounters like
	\emph{ps-} and \emph{pn-} are more frequent, as they are present in
	words like \emph{psicologia} and \emph{pneu}, which have moderate 
	frequency in the language. These can be predicted by specific rules that would cover  
	49 and 13 words in the corpus, respectively.
	However, there are consonant clusters that are
	found in very specific and low-frequency words. Although possible, it
	is not worth adding very specific rules for clusters found in words like
	\emph{dzeta}, \emph{gnu}, \emph{cnidário},
	\emph{ftálico}, and \emph{gnaisse} -- which amount to only five words.

    \item[Abbreviations, Acronyms, or Initialisms:\label{abbrev}] 
       Whether for efficiency, convenience, clarity, or specialized jargon, 
       it is common to use shortened versions of words or phrases. \emph{Abbreviation} is 
       a method employed to achieve this shortening. In our Portuguese corpus, we find examples such as 
       \emph{etc.}\footnote{Latin expression \emph{et cetera}, meaning `and other similar things'.}, 
       \emph{Dr.}\footnote{\emph{doutor} (doctor, person with PhD title, but popularly used to designate an erudite individual)}, 
       \emph{Exmo.}\footnote{\emph{Excelentíssimo} (honourable)},
       \emph{cap.}\footnote{\emph{capítulo} (chapter)}, \emph{Univ.}\footnote{Universidade (university)}, 
       \emph{ed.}\footnote{\emph{edição} (edition)}, 
       \emph{s.n.}\footnote{sine nomine, Latin expression meaning `without a name', mostly used in the context of publishing.}.
       Another shortened form is an \emph{initialism}, which consists of using
       the initial letters of words to create a shortened version. However,
       initialisms may not always conform to the hyphenation rules described in
       this work, as they do not necessarily follow the orthographic or
       phonotactic standards of the language. Some abbreviations found in the
       corpus include 
       \emph{SESC}\footnote{Serviço Social do Comércio}, 
       \emph{INSS}\footnote{\emph{Instituto Nacional do Seguro Social} (National Institute of Social Security)}, 
       \emph{PCdoB}\footnote{\emph{Partido Comunista do Brasil} (Communist Party of Brazil)},
       \emph{PM}\footnote{\emph{Polícia Militar} (military police)}, and 
       \emph{UFRJ}\footnote{Universidade Federal do Rio de Janeiro}.
       \emph{Acronyms} are a specific type of shortening where the first letters (or
       groups of letters) of each word are combined to form a new pronounceable
       word. In the corpus, we encounter examples like 
       \emph{Anatel}\footnote{\emph{Agência Nacional de Telecomunicações} (National Telecommunications Agency)},
       \emph{Ovni}\footnote{\emph{Objeto voador não identificado} (unidentified flying object - UFO)},
       \emph{Sida}\footnote{\emph{Síndrome da Imunodeficiência Adquirida} (acquired immunodeficiency syndrome - AIDS)} (in Portugal) and
       \emph{Mercosul}\footnote{\emph{Mercado Comum do Sul} (Southern Common Market).}.
       These various shortened forms play an important role in written
       language, providing concise ways to represent longer words or phrases.
       It is important to note that abbreviations, acronyms, and initialisms
       are generally treated as single units and are not hyphenated.

\end{description}

### 2024-06-06 article/methodology.tex
updates

\section{Methodology}\label{sec-methodology}

To assess the performance of each set of rules, we require a collection of
correctly hyphenated Portuguese words. We employed word frequency data to
ensure we selected representative, commonly used words, avoiding excessively
rare ones. Our comprehensive word list was curated using online dictionaries,
Portuguese corpora, and verified against Portuguese grammars to validate
hyphenation rules. We also performed manual corrections where necessary.
We should not expect an entire corpus to follow a set of conventions for a written 
language nor uniformity among a variety of corpora, especially those harvested from the Internet.
``It is notoriously difficult to prescribe rules governing the use of a written language; it is even more difficult
to get people to `follow the rules.' This is in large part due to the nature of written language, in which
the conventions are not always in line with actual usage and are subject to frequent change'' \parencite[p.~14]{palmer2010}.

\subsection{Data collection}\label{sec-data-coll}

Initially, we selected
\href{https://www.linguateca.pt/cetenfolha/index_info.html}{CETENFolha}
as the source corpus, but this approach presented two issues: many
words were still missing, and the corpus was based on text from 1994, prior to
the implementation of the Orthographic Agreement. The Orthographic Agreement
of the Portuguese Language was conducted in 1990, and its transition period
started in 2009, becoming mandatory in 2016. However, even after the agreement,
some words continue to have different spellings in the participating countries.
To address these idiosyncrasies, we aim to develop hyphenation rules that
accommodate variations in spelling. For instance, the word \emph{reception}
might be written as \emph{receção} (Portugal) or \emph{recepção} (Brazil); the
word \emph{action} might be written as \emph{acção} (Portugal) or \emph{ação}
(Brazil); and the word \emph{project} might be written as \emph{projecto}
(Portugal) or \emph{projeto} (Brazil).

% We have used the Portuguese Wikipedia dump as our Portuguese corpus. Texts in Wikipedia might be written by Brazilian or Portuguese contributors, the both spellings may appear.

% cat /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | tr -dc '0-9\n' | paste -sd+ | bc
% 302226482
% cat /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | awk '{CUMCOUNT+=$1; if(CUMCOUNT < 287115158) print;}' >/tmp/ptwikitop95.txt
% cat /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | awk '{CUMCOUNT+=$1; if(CUMCOUNT < 299204217) print;}' >/tmp/ptwikitop99.txt
% cat /tmp/ptwikitop99.txt | tr -d "0-9 " |  while read -r word; do if ! grep -q "^${word}," ../data/hyphenations.csv; then echo $word; fi; done > /tmp/ptwikitop99_notinlist.txt
% cat /home/leoca/ee/research/hyphenation/listapalavrasnet.txt | awk '{print tolower($0)}' | while read -r word; do if ! grep -qP "^\s*[0-9]+\s*${word}$" /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt; then echo $word; fi; done > /tmp/list_of_palavrasnet_not_in_wikipedia.txt

% wc -l /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt
% 1746947
% wc -l /tmp/ptwikitop99_notinlist.txt
% 42017
% from 1746947 of wikipedia, only 42017 are not in list

Due to the peculiarities mentioned, we made the decision to integrate the word
list from \href{https://www.palavras.net/}{Palavras NET}, and subsequently, we
augmented it with words sourced from the
\href{https://pt.wikipedia.org}{Portuguese Wikipedia} dump. From the Wikipedia
data, we narrowed down the selection to a subset of \num{50721} words,
accounting for 95\% of occurrences in the corpus. This threshold was set to
filter out typos and infrequent words. The initial word list became quite
extensive, comprising \num{\CorpusSize} words. However, we refined the list by
retaining only those words for which we could find hyphenation data in at least
one of the following online dictionaries:
\href{https://michaelis.uol.com.br/}{Michaelis},
\href{https://dicionario.priberam.org/}{Priberam},
\href{https://pt.wiktionary.org}{Wikcionário},
\href{https://aulete.com.br/}{Aulete},
\href{http://www.portaldalinguaportuguesa.org/}{Portal da Língua Portuguesa}, and
\href{https://www.dicio.com.br/}{Dicio}.
Consequently, this curation process resulted in a final dictionary containing
\num{\DictionarySize} words.

Table \ref{tblstats} presents the number of distinct words with a given number
of hyphenations found in the dictionaries.  Additionally, it displays the
number of words that received the highest agreed-upon hyphenation.  For
instance, the word \emph{como} was consistently hyphenated as \emph{co-mo} in
all six dictionaries, therefore, it contributes to both the counts in the
column representing six hyphenations (first column).  On the other hand, the
word \emph{sua} received different hyphenations: \emph{su-a} in four
dictionaries, \emph{sua} in one dictionary, and one dictionary did not provide
any hyphenation result.  This leads to an increment in the first line, second
column (since hyphenations were found in five dictionaries) and the second
line, third column (since the most frequent hyphenation was found in four
dictionaries). It is evident now that the number of identical hyphenations can
exceed the total number of hyphenations found, especially for smaller values.

\begin{table}
\centering
\caption{Considering the six dictionaries used, the first line of this table
presents the number of words that a given number of hyphenations were found in the
dictionaries. The second line presents the number of words that have a given
number of hyphenation as its most frequent form found in the
dictionaries.}\label{tblstats}
\small
\begin{tabular}{@{ }l@{ } *{7}{@{ }S[table-format=6]@{ }}}
    hyphenations & 6 & 5 & 4 & 3 & 2 & 1 & 0 \\
    \hline
    hyphenations found & \NumberOfSixHyphens{} & \NumberOfFiveHyphens{} &
    \NumberOfFourHyphen{} & \NumberOfThreeHyphens{} & \NumberOfTwoHyphens{} &
    \NumberOfOneHyphens{} & \NumberOfNoHyphens{} \\

    same hyphenations & \NumberOfSixAgrees{} & \NumberOfFiveAgrees{} &
    \NumberOfFourAgrees{} & \NumberOfThreeAgrees{} & \NumberOfTwoAgrees{} &
    \NumberOfOneAgrees{} & n/a
\end{tabular}
\end{table}

In summary, our data compilation involved \emph{CETENFolha}, \emph{Palavras
NET}, and \emph{Wikipedia}, and hyphenated the words using the original \TeX{}
hyphenation rules.  Subsequently, we compared the hyphenated results with
those obtained from the dictionary. By conducting a thorough performance
appraisal, we systematized the errors and delved into the relevant literature
to identify potential rules that could complement and enhance the existing
hyphenation system.

### 2024-06-06 article/patgen.tex
updates

\section{Patgen}\label{sec-patgen}

\emph{Patgen} utilizes a list of hyphenated words to extract patterns and use them to define rules at various levels and lengths.
It starts with short
patterns and incrementally increases their length until reaching the maximum
pattern length allowed by the user.  The objective is to keep the patterns as
concise as possible, as this enhances their generalizability.  As it advances
and incorporates longer patterns, \emph{patgen} establishes exceptions.  In certain
cases, analyzing long patterns may be necessary, as some hyphenation points
could depend on characters far away from the breaking point\footnote{Some
    examples of hyphenation dependency on characters far from the break point:
    \emph{dem-o-crat} and \emph{de-moc-ra-cy}; \emph{as-pi-rin} and
    \emph{aspir-ing}; \emph{de-mon-stra-tive} and \emph{dem-on-stra-tion}.
}.

\emph{Patgen} works on glyph\footnote{\emph{Glyph} is commonly used in linguistics,
typography, and computer graphics to refer to a specific graphical
representation of a character or symbol, which can be the entire symbol or a
distinct visual element within it.} indices rather than character codes. Each
glyph is represented by a single byte. That amount to 256 indices, where 13 of
them are reserved for the digits 0-9 and the characters `.', `-', and `*'. The
remaining 243 are used to represent symbols of a given language.  To run
\emph{patgen}, a translation file is necessary. This file defines the values of
certain language-specific parameters (in the first line) and enumerates the
various forms in which language symbols may appear (all subsequent lines).  In
the first line, positions 1 and 2 are used to set the value of
\verb|lefthyphenmin|, and positions 3 and 4 are used to set the value of
\verb|righthyphenmin|.  These values determine the minimum length of a string
that may be generated by a hyphenation procedure. To set a single-digit value,
leave the first position blank, i.e., place a space in position 1 and 3 for
\verb|lefthyphenmin| and \verb|righthyphenmin|, respectively.  Positions 5, 6
and 7 are used to define alternative values for the special characters `.', `-'
and `*'.  
\begin{center}
\begin{bytefield}[endianness=little,bitwidth=0.11111\linewidth,boxformatting={\centering}]{7}
\bitheader[lsb=1]{1-7} \\
\bitbox{2}{lefthyphenmin} & \bitbox{2}{righthyphenmin} & \bitbox{1}{.} & \bitbox{1}{-} & \bitbox{1}{*} \\
\end{bytefield}
\end{center}
The following lines use a delimiter to enclose each `letter' of the
desired language alphabet, including its alternative representations.  The
first position of the line defines the delimiter, and each symbol of the
language can occupy as many positions as necessary, as long as the reserved
value for the delimiter is not used in the symbol's definition. The defining lines ends
when the delimiter appears twice in a roll. Consider the
following example for defining the letter `e' in Portuguese:
\verb|XeXEXéXêXÉXÊX\'{e}X\^{e}X\'{E}X\^{E}XX|.
\newcommand{\bitlabel}[2]{%
    \bitbox[]{#1}{%
	\raisebox{0pt}[4ex][0pt]{%
	    \turnbox{45}{\fontsize{7}{7}\selectfont#2}%
	}%
    }%
}
\vspace{7ex}
\begin{center}
\begin{bytefield}[bitwidth=1.9em,boxformatting={\centering\tiny}]{20}
\bitlabel{1}{delimiter} & \bitlabel{1}{letter e} &
\bitlabel{1}{delimiter} & \bitlabel{1}{letter E} &
\bitlabel{1}{delimiter} & \bitlabel{1}{letter é} &
\bitlabel{1}{delimiter} & \bitlabel{1}{letter ê} &
\bitlabel{1}{delimiter} & \bitlabel{1}{letter É} &
\bitlabel{1}{delimiter} & \bitlabel{1}{letter Ê} &
\bitlabel{1}{delimiter} & \bitlabel{1}{TeX sequence for é} &
\bitlabel{1}{delimiter} & \bitlabel{1}{TeX sequence for ê} &
\bitlabel{1}{delimiter} & \bitlabel{1}{TeX sequence for É} &
\bitlabel{1}{delimiter} & \bitlabel{1}{TeX sequence for Ê} \\
\bitheader[lsb=1]{1-20} \\
\bitbox{1}{X} & \bitbox{1}{e} & \bitbox{1}{X} & \bitbox{1}{E} &
\bitbox{1}{X} & \bitbox{1}{é} & \bitbox{1}{X} & \bitbox{1}{ê} &
\bitbox{1}{X} & \bitbox{1}{É} & \bitbox{1}{X} & \bitbox{1}{Ê} &
\bitbox{1}{X} & \bitbox{1}{\textbackslash{}'\{e\}} & \bitbox{1}{X} & \bitbox{1}{\textbackslash{}\^{}\{e\}} &
\bitbox{1}{X} & \bitbox{1}{\textbackslash{}'\{E\}} & \bitbox{1}{X} & \bitbox{1}{\textbackslash{}\^{}\{E\}}
\end{bytefield}
\end{center}
%\begin{verbatim}
%XeXEXéXêXÉXÊX\'{e}X\^{e}X\'{E}X\^{E}XX 
%\end{verbatim}
We have adopted \verb|X| as the delimiter. This line represents the many ways in which the letter `e' might be found: lowercase,
uppercase, with or without acute or circumflex accents. Note that we have used
the direct input (using UTF-8 or other encoding that support the accented `e'
character) and also the compositional counterpart using the appropriate \TeX{} control sequence that
instructs \TeX{} to place accent on the letter.  In this definition, we have assumed that the many forms in
which we may find the character \emph{e} will be equivalent for
hyphenation (pattern matching) purpose. As another example, see the next line
which defines the character $\pi$ (taken from \textcite{haralambous2021}):
\verb|#p#P#\varpi ##|.
%\begin{verbatim} 
%#p#P#\varpi ## 
%\end{verbatim}

\emph{Patgen} also needs a dictionary file, which is a list of pre-hyphenated words
from which \emph{Patgen} extracts patterns to create hyphenation rules. To ensure
\emph{Patgen}'s proper functionality, the translation file and the dictionary file
must utilize the same encoding, even if it is a multi-byte encoding. The
translation file describes how to handle byte sequences representing a glyph,
and \emph{Patgen} will work seamlessly when there are at most 243 symbols in the given
language.

%Those rules are organized
%in different levels, from 1 to 9, where odd numbers represent hyphenating
%levels and even numbers represent inhibiting levels. Each level works as an
%inhibiting level of it predecessor. 
%A pattern will consist of a string made of
%characters (from the language alphabet) possibly with a number in between,
%expressing the hyphenation/inhibition level and possibly word boundaries marker
%(the period) at the pattern edges. When there is no number between characters
%in a pattern, a zero is assumed, which means \emph{undefined} and no
%hyphenation point will be suggest at that location.

The syntax to run \emph{patgen} is described in \Cref{lst-patgen-syntax}
\begin{lstlisting}[language={bash}, basicstyle=\small\ttfamily, caption={Syntax to run patgen.}, label={lst-patgen-syntax}]
patgen dictionary_file initial_pattern_set output_file translation_file
\end{lstlisting}

The dictionary file is a list of correctly hyphenated words, one per line; 
the initial pattern file is a set of hyphenation rules to be used as a starting point;
the output file is the set of final rules created by \emph{patgen}; and the translation file
which maps the many forms each symbol in a language might appear in \TeX{} documents.
If it is desired to run \emph{patgen} from scratch, starting from an empty set of rules,
just use an empty file as the initial pattern set.

\emph{Patgen} uses a few parameters along its executions: 
\begin{description}
    \item[hyph\_start, hyph\_finish]: Two numbers between 1 and 9 (separated by a space), representing the desired pattern levels
	in the final set of rules. Odd pattern levels are hyphenating levels and even pattern levels are inhibiting levels. 
	Higher level numbers prevail over lower ones, creating exceptions, exceptions over exceptions, and so on... 
	\texttt{hyph\_start} and \texttt{hyph\_finish} specify the first and last levels, respectively, to be considered during the rule creation process.

    \item[pat\_start, pat\_finish]: Patterns at each level are chosen in order of increasing pattern length (usually starting with length 2). 
	This is controlled by the parameters \texttt{pat\_start} and \texttt{pat\_finish} specified at the beginning of each level. 
	These are the minimum and maximum lengths of patterns we are interesting in. Their values range between 1 and 15.

    \item[good weight, bad weight, threshold]: Each level of patterns is tested over all words in the dictionary.
	A pattern is only if it satisfies the following formula: $\alpha \times \#\text{good matches} - \beta \times \#\text{bad matches} \geq \eta$, where
	$\alpha$ is the \texttt{good weight}, $\beta$ is the \texttt{bad weight} and $\eta$ is the \texttt{threshold}.

\end{description}

### 2024-06-06 article/patgenrules.tex
updates

\section{Creating a new set of rules using Patgen}
In this section, we describe the process of creating a new set of hyphenation rules using \emph{patgen}.
This involves defining specific parameters, choosing a reference dictionary with correct hyphenations, and 
using a translation file tailored for \emph{patgen}. In the previous \Cref{sec-patgen} we have detailed 
how \emph{patgen} works.

A partial of the content of the translation file is shown in \Cref{lst-trafile}.

\begin{minipage}{\linewidth}
\lstinputlisting[language={}, numbers=left, numberstyle=\tiny, linerange={1-10}, basicstyle=\small\ttfamily, caption={Portuguese translation file.}, label={lst-trafile}]{../data/portuguese.tra}
\ldots
\lstinputlisting[language={}, numbers=left, numberstyle=\tiny, linerange={39-41}, firstnumber=39, basicstyle=\small\ttfamily]{../data/portuguese.tra}
\end{minipage}

%\emph{Patgen} uses a few parameters along its executions: 
%\begin{description}
%    \item[hyph\_start and hyph\_finish]: Two numbers between 1 and 9 (separated by a space), representing the desired pattern levels
%	in the final set of rules. Odd pattern levels are hyphenating levels and even pattern levels are inhibiting levels. 
%	Higher level numbers prevail over lower ones, creating exceptions, exceptions over exceptions, and so on... 
%	\texttt{hyph\_start} and \texttt{hyph\_finish} specify the first and last levels, respectively, to be considered during the rule creation process.
%
%    \item[pat\_start and pat\_finish]: Patterns at each level are chosen in order of increasing pattern length (usually starting with length 2). 
%	This is controlled by the parameters \texttt{pat\_start} and \texttt{pat\_finish} specified at the beginning of each level. 
%	These are the minimum and maximum lengths of patterns we are interesting in. Their values range between 1 and 15.
%
%    \item[good weight, bad weight, threshold]: Each level of patterns is tested over all words in the dictionary.
%	A pattern is only if it satisfies the following formula: $\alpha \times \#\text{good matches} - \beta \times \#\text{bad matches} \geq \eta$, where
%	$\alpha$ is the \texttt{good weight}, $\beta$ is the \texttt{bad weight} and $\eta$ is the \texttt{threshold}.
%
%\end{description}
%
%The syntax to run \emph{patgen} is described in \Cref{lst-patgen-syntax}
%\begin{lstlisting}[language={bash}, basicstyle=\small\ttfamily, caption={Syntax to run patgen.}, label={lst-patgen-syntax}]
%patgen dictionary_file initial_pattern_set output_file translation_file
%\end{lstlisting}

The parameters mentioned in \Cref{sec-patgen} to run \emph{patgen} are provided interactively during the execution of \emph{patgen}.
We might automatize this process using a script. The \Cref{lst-patgentest} presents the code block
responsible for passing these parameters to \emph{patgen}.
\lstinputlisting[language={bash}, linerange={76-83}, basicstyle=\small\ttfamily, breaklines=true, caption={Portuguese translation file.}, label={lst-patgentest}]{../scripts/patgentest.sh}
As an example of execution, when choosing \texttt{hyph\_start}=1, \texttt{hyph\_finish}=9, \texttt{pat\_start}=2, \texttt{pat\_finish}=5,
\texttt{good weight}=1, \texttt{bad weight}=1, and \texttt{threshold}=1, we achieve 99.97\%(86799) correct 
hyphenations, 0.01\%(12) incorrect hyphenations, and 0.03\%(25) missing hyphenations.
It produced a set of 799 rules, where just 123 are present in the handcrafted set of rules.

We have also used the approach used by \textcite{sojka2019} in creating the script \texttt{make-full-pattern}.
In this approach, the parameters are loaded from a file and might be distinct for each level.
We start from an empty set and create progressive higher order rules, always using the rules from the previous
step as the starting point at the next step.
Using this approach with the 8 level parameters they used to create hyphenation rules to German,
we achieved 99.98\%(86820) correct hyphenations, 0.01\%(9) incorrect hyphenations, and 0.00\%(4) missed hyphenations.
The result was a set of 593 rules, with only 69 in common with those handcrafted rules proposed earlier.

% patgen portuguese_utf8.dic portuguese.0.pat portuguese_utf8.out portuguese_utf8.tra

% $ cat ../data/hyphenations6.dic ../data/hyphenations5.dic ../data/hyphenations4.dic > ../data/portuguese.dic
% $ ./patgentest.sh -w "1 2 1" -h "1 9" -p "2 5"
% 86799 good, 12 bad, 25 missed
% 99.97 %, 0.01 %, 0.03 %
% 799 rules
% 123 lines in common with handcrafted rules

% $ ./patgentest.sh -w "1 1 1" -h "1 9" -p "2 5"
% 86791 good, 5 bad, 33 missed
% 99.96 %, 0.01 %, 0.04 %
% 704 rules
% 81 lines in common with handcrafted rules

% $ ./patgentest.sh -w "1 1 2" -h "1 9" -p "2 5"
% 86671 good, 93 bad, 153 missed
% 99.82 %, 0.11 %, 0.18 %
% 498 rules
% 72 lines in common with handcrafted rules

% make-full-pattern.sh DICTIONARY_FILE TRANSLATE_FILE PARAMETERS_FILE
%
% ./make-full-pattern.sh ../data/portuguese.dic ../data/portuguese.tra german8levels-orig.par
% 86820 good, 9 bad, 4 missed
% 100.00 %, 0.01 %, 0.00 %
% 593 rules
% 69 lines in common with handcrafted rules
%
% ./make-full-pattern.sh ../data/portuguese.dic ../data/portuguese.tra german8levels-orig.par ../data/patched-default.TeX.pt-br.patterns.v2
% 86818 good, 7 bad, 6 missed
% 99.99 %, 0.01 %, 0.01 %
% 1260 rules
% 421 lines in common with handcrafted rules
% 
% ./make-full-pattern.sh ../data/portuguese.dic ../data/portuguese.tra scannell.par
% 86815 good, 10 bad, 9 missed
% 99.99 %, 0.01 %, 0.01 %
% 1104 rules
% 44 lines in common with handcrafted rules
%
% ./make-full-pattern.sh ../data/portuguese.dic ../data/portuguese.tra scannell.par ../data/patched-default.TeX.pt-br.patterns.v2
% 86812 good, 7 bad, 12 missed
% 99.99 %, 0.01 %, 0.01 %
% 764 rules
% 429 lines in common with handcrafted rules

% ./apparentproparoxytonesfix.sh ../data/portuguese.dic
% ./make-full-pattern.sh ../data/portuguese_apparentproparoxytone.dic ../data/portuguese.tra german8levels-orig.par
% 86766 good, 9 bad, 4 missed
% 100.00 %, 0.01 %, 0.00 %
% 547 rules
% 69 lines in common with handcrafted rules

% ./make-full-pattern.sh ../data/portuguese_apparentproparoxytone.dic ../data/portuguese.tra scannell.par
% 86767 good, 10 bad, 3 missed
% 100.00 %, 0.01 %, 0.00 % 
% 1065 rules
% 44 lines in common with handcrafted rules

% ./make-full-pattern.sh ../data/portuguese_apparentproparoxytone.dic ../data/portuguese.tra german8levels-orig.par ../data/patched-default.TeX.pt-br.patterns.v2
% 86764 good, 7 bad, 6 missed
% 99.99 %, 0.01 %, 0.01 %
% 1182 rules 
% 421 lines in common with handcrafted rules

% ./gocreateresultfile.sh ../data/portuguese.dic portuguese.out > /tmp/portuguese_patgen_001.dic;
% ./resultfilemetrics.sh -f /tmp/portuguese_patgen_001.dic;
% correct: 32447; wrong: 12 (12); missing: 25 (25)
% 32447 good, 12 bad, 25 missed
% 99.89 %, 0.04 %, 0.07 %

% $ cat <(printf "1 5\n") <(printf -- '2 5\n1 2 1\n%.0s' {1..5}) <(printf "y") | patgen ../data/portuguese.dic ../data/patched-default.TeX.pt-br.patterns.v2 portuguese.out.2 ../data/portuguese.tra
% 86803 good, 429 bad, 21 missed
% 99.98 %, 0.49 %, 0.02 %

% create a test set using words with three hyphenations (3) in dictionary
% grep "(3)" ../data/hyphagreements | cut -d, -f1 | grep -v "(4)" | sed 's/([0-9])//g' > ../data/hyphenations3.dic
% ./apparentproparoxytonesfix.sh ../data/hyphenations3.dic
% ../data/hyphenations3_apparentproparoxytone.dic
% ./gocreateresultfile.sh ../data/hyphenations3_apparentproparoxytone.dic pattern.final > /tmp/portuguese3patfinal.dic;
% ./resultfilemetrics.sh -f /tmp/portuguese3patfinal.dic;
% correct: 647; wrong: 47 (46,1); missing: 7089 (1899,2088,1588,946,423,122,21,1,1)
%
% ./gocreateresultfile.sh ../data/hyphenations3_apparentproparoxytone.dic output_w111_h19_p25 > /tmp/portuguese3w111_h19_p25.dic;
% ./resultfilemetrics.sh -f /tmp/portuguese3w111_h19_p25.dic
% correct: 7465; wrong: 150 (143,6,1); missing: 183 (181,2) 
%
% ./gocreateresultfile.sh ../data/hyphenations3_apparentproparoxytone.dic ../data/patched-default.TeX.pt-br.patterns.v2 > /tmp/portuguese3patchv2.dic
% ./resultfilemetrics.sh -f /tmp/portuguese3patchv2.dic
% correct: 7335; wrong: 42 (40,2); missing: 385 (381,4)

The results from the set of rules crafted by \emph{patgen} seems outstanding, but we must be 
skeptical of its generalization power. To inquire on this matter, we decided to retrieve the
list of words where just three hyphenations were found in the dictionaries. We have also dealt
with apparent proparoxytones, to be consistent in our approach.  
In this new set, the number of correct, incorrect and missing hyphenations for each set of rules
is given \Cref{tbl-comres-hy3}.
\begin{table}[h]
\centering
\caption{Compared results between two use cases of \emph{patgen} and the handcrafted rule set.}\label{tbl-comres-hy3}
\begin{tabular}{llll}
rule set          & correct & incorrect & missing \\
\hline
fixed parameters  & 7465    & 150       & 183 \\
make-full-pattern & 647     & 47        & 7089 \\
handcrafted       & 7335    & 42        & 385 
\end{tabular}
\end{table}
It is important to hightlight that, among those 385 missing hyphenations in the handcrafted rules,
278 cases correspond to the last hyphen, leaving a single vowel as a final syllable.
Comparing to the other set of rules, we have 7 (in 183, for fixed parameters case), and 257 (in 7089, 
for the \texttt{make-full-pattern} script).

Establishing this comparison leave us no doubt that our handcrafted rules achieved the best
performance, also retaining a small number of useful rules, what leads to good generalization.

% $ grep "-" /tmp/portuguese3patchv2.dic | grep "\-[aeiouáéíóúãõâêô]$" | wc -l
% 278
% $ grep "-" /tmp/portuguese3w111_h19_p25.dic | grep "\-[aeiouáéíóúãõâêô]$" | wc -l
% 7

### 2024-06-06 article/patterns.tex
updates

\section{Patterns for \TeX{} hyphenation}\label{sec-patt4TeX}

To simplify, if we consider only the Latin alphabet, with no diacritcs, the patterns used 
in \TeX{} hyphenation are of the form: \texttt{\^{}\textbackslash{}.?[0-9]?([a-z]+[0-9]?)+\textbackslash{}.?\$},
where we have described it using a regular expression\footnote{
    Regular expressions (regex) are powerful search patterns used in text processing to find, match, and manipulate strings of text. They are a fundamental tool in programming and are supported in many programming languages.
    The regex given here uses the Perl syntax and might be broken in the following
    parts: \texttt{\^{}} and \texttt{\$} mark the start and end of the string;
    \texttt{\textbackslash{}.?} specifies an optional period; \texttt{[0-9]?} allows for an optional single digit;
    \texttt{([a-z]+[0-9]?)+} matches sequences of lowercase letters interleaved with optional digits.
}.
One example of such pattern is \texttt{4z1z2}, which is composed of a sequence
of letters and numbers. In general, we use characters/symbols from the language
alphabet, along with Hindu-Arabic numbers, to express either hyphenation
facilitation or inhibition.  Odd numbers indicate a good hyphenation point,
whereas even numbers indicate a bad place to break.  The given example states
that the sequence has a good breaking point between the first and the second
\emph{z} and an hyphenation should be inhibited before the first \emph{z} and
after the second \emph{z}. For example, the hyphenation of the word
\emph{piz-za}, \emph{fiz-zle} and \emph{mez-zanine} use this rule, where we see
the hyphen placed between the two \emph{z}'s and no hyphen before, nor after
the \emph{z}'s. Patterns may also use period symbol (\emph{.}) to indicate word
boundaries. The pattern \texttt{.sh2} applies to beginning of words, implying
that the \emph{s} and the \emph{h} should stick together in beginning of a word
and an hyphenation should also be inhibited after the \emph{h}. For example,
this pattern is used in \emph{Sher-lock}.

Hyphenation rules are organized in levels, from 1 to 9, where odd numbers
represent hyphenating levels and even numbers represent inhibiting levels. Each
level works as an exception level of it predecessor. For example, the rule
\texttt{sh1er} indicate a good hyphenation point between the \emph{h} and the
\emph{e} in the sequence \emph{sher}. A rule at a higher level, as
\texttt{.sh2}, implies an exception to the lower level rule. When we see
\emph{sher}, in the beginning of a word, the rule \texttt{.sh2} applies and
hyphenation proposed by the lower level rule \texttt{sh1er} should be hindered.
That is the case in the hyphenation of the word \emph{Sher-lock}. The full
example is provided in \Cref{sherlockhyphenation}, where we might see all pertinent
English rules taking place in the hyphenation of \emph{Sher-lock}.

\noindent\begin{minipage}{\linewidth}
\begin{lstlisting}[language={}, caption={Example of rules applyied in the
hyphenation of the word \emph{Sherlock}. Example done using a port of \TeX{}'s
hyphenation algorithm to Go provided at
\url{https://github.com/speedata/hyphenation}.}, label=sherlockhyphenation]
   .   s   h   e   r   l   o   c   k   .
     0   0   2   |   |   |   |   |   |    .sh2
     0   2   0   |   |   |   |   |   |    s2h
     0   0   1   0   0   |   |   |   |    sh1er
     |   |   |   0   1   0   |   |   |    r1l
     |   |   |   0   3   0   4   |   |    r3lo4
     |   |   |   |   |   |   0   0   1    ck1
max: 0   2   2   0   3   0   4   0   1
final: s   h   e   r - l   o   c   k -
\end{lstlisting}
\end{minipage}

In summary, a pattern will consist of a string made of characters (from the language
alphabet) possibly with a number in between, expressing the
hyphenation/inhibition level. Occasionally word boundaries marker (the period)
is used at the pattern edges. When there is no number between characters in a pattern,
a zero is assumed, which means \emph{undefined} and no hyphenation point will
be suggest at that location.

### 2024-06-06 article/portuguesespelling.tex
updates

\section{Portuguese spelling system}\label{sec-grammar-port}

Portuguese employs an alphabetical writing system, which means its spelling is
guided by phonological principles \parencite{cagliari2015}. The correlation between
spelling and pronunciation influences word hyphenation, as words are divided
into syllables based on the phonemic system. It is important to note that
different languages follow diverse principles for word division. For example,
English is primarily guided by morphological principles, evident in words like
\emph{walk-ing}, \emph{un-happy}, \emph{work-s}, and \emph{ear-ly}.
Additionally, other factors also impact word hyphenation in English, such as 
the distinction between long and short vowels, which function within the context
of open or closed syllable, respectively; and the presence of doubled consonants and
digraphs \parencite{lin2011,yavas2020}.
Although each language has its driving principles for the hyphenation process, 
multiple factors come into play, leading to various solutions in certain scenarios.
For instance, in Portuguese, the phonological principle would lead to \emph{hipe-rativo}, while 
the morphological principle would lead to \emph{hiper-ativo}. Both approaches seem valid
and are indeed found in online dictionaries\footnote{Looking at words with prefixes, 
it seems that even on those words, the phonological approach was predominant on hyphenation,
but we cannot tell if it is a byproduct of automatic hyphenation that might be used
to hyphenate words on online dictionaries.}.
Some rather rare words, such as \emph{hiperalgesia}, may not be subject to morphological 
influences. Since it has a low frequency of occurrence, the individual may not be
aware of its morphological components and therefore hyphenate it as \emph{hipe-ralgesia}.
The form \emph{hiper-algesia} could also be accepted, emphasizing its morphological constituents. 
Furthermore, there exist numerous exceptions that may be categorized into rules.
% https://english.stackexchange.com/questions/385/what-are-the-rules-for-splitting-words-at-the-end-of-a-line

% $ grep "^hiper[aeiou]" ../data/hyphenations.csv  | grep "-" | grep -o "hi-pe-r[aeiou]\|hi-per-[aeiou]" | sort | uniq -c
% 16 hi-pe-ra
%  1 hi-per-a
% 29 hi-pe-re
% 20 hi-pe-ri
%  2 hi-per-i
%  2 hi-pe-ro
%  2 hi-pe-ru

Merely stating that an orthographic system is guided by phonological issues
does not necessarily mean that its hyphenation rules directly mirror the
phonetic counterpart. This is notably apparent in Portuguese, where a strict
one-to-one correspondence between letters and sounds is not always observed.
The orthographic system operates according to its specific rules. For example,
consider consonant clusters that create a single sound (digraphs) in words like
%\emph{\underline{ch}ave}, 
\emph{a\underline{ch}ado},
\emph{i\underline{lh}a}, 
%\emph{\underline{sh}ampoo}, 
\emph{su\underline{sh}i},
\emph{ca\underline{rr}o}, and \emph{ma\underline{ss}a}.
While these digraphs are pronounced as one sound within a single syllable,
their representation in writing determines how they are divided. Specifically,
different consonants within a digraph must remain together, whereas identical
consonants are separated. As a result, we observe hyphenations like
%\emph{cha-ve}, 
\emph{a-cha-do},
\emph{i-lha}, and 
%\emph{sham-poo}, 
\emph{su-shi},
but \emph{car-ro} and \emph{mas-sa}.

%When there is no space left in line for a whole word, it might be split in two
%using a hyphen as an indication of such procedure.

In Portuguese, hyphenations are allowed on syllables boundaries and, in
general, follow phonological principles.  According to the Grammar
\parencite{cunha2016,bergstrom2011,cegalla2008}, some rules might still apply:
\begin{description}
    \item[Non-Splitting Rules]\

\begin{enumerate}
    \item\label{rule-di-triphthong} diphthong or triphthong should not be split
	(e.g. \emph{m\underline{ui}-to}, \emph{Pa-ra-g\underline{uai}});
    \item\label{rule-unstressed} the sequences \emph{ia}, \emph{ie}, \emph{io}, \emph{oa}, \emph{ua},
	\emph{ue} and \emph{uo}, when in final unstressed position, should not be split 
	(e.g. \emph{gló-r\underline{ia}}, \emph{vi-tó-r\underline{ia}}, 
	\emph{cá-r\underline{ie}}, \emph{es-pé-c\underline{ie}}, 
	\emph{Má-r\underline{io}}, \emph{má-g\underline{oa}}, 
	\emph{ré-g\underline{ua}}, \emph{tê-n\underline{ue}}, 
	\emph{con-tí-g\underline{uo}}, \emph{am-bí-g\underline{uo}});
    \item\label{rule-c-clusters} consonant clusters starting a syllable should not be
	split (e.g. \emph{\underline{pn}eu-má-ti-co}, \emph{\underline{ps}i-có-lo-go}, 
	\emph{\underline{mn}e-mô-ni-co});
    \item\label{rules-digraphs-ns} the digraphs	\emph{ch}, \emph{lh}, \emph{nh}
	should not be split (e.g. \emph{ra-\underline{ch}ar},
	\emph{a-bro-\underline{lh}os}, \emph{ma-\underline{nh}ã};
    \item\label{rule-guqu} bigrams like \emph{gu} and \emph{qu} whose vowel \emph{u} is not 
	pronounced are never separated from the vowel or diphthong that follows it 
	(e.g. \emph{U-ru-\underline{guai}}, \emph{pe-\underline{que}});
    \item\label{rule-nasalization} since they are digraphs, a vowel and its following 
	nasalization marker (a graphic nasal consonant) should not be split (e.g. \emph{\underline{am}-bição},
	\emph{m\underline{an}-cha});
    \item\label{rule-decreasing} decreasing diphthongs should not be split (e.g. 
	\emph{\underline{ai}-ro-so}, \emph{ca-d\underline{ei}-ra}, 
	\emph{o-ra-ç\underline{ão}});
    \item\label{rule-rising} rising diphthong should not be split (e.g.
	\emph{a-b\underline{ai}-xo}; \emph{c\underline{au}-te-la}, 
	\emph{pa-p\underline{éi}s}, \emph{cha-p\underline{éu}}, 
	\emph{pre-f\underline{ei}-to}, \emph{r\underline{eu}-nir},
	\emph{n\underline{oi}-te}; \emph{ca-la-b\underline{ou}-ço}, 
	\emph{as-te-r\underline{ói}-de}; 
	\emph{re-tri-b\underline{ui}});
    \item\label{rule-singlev} disyllables whose syllable has a single vowel should 
	not be split (e.g. \emph{\underline{a}to}, \emph{ru\underline{a}}, 
	\emph{\underline{ó}dio}, \emph{\underline{u}nha});
    \item\label{rule-orphan} words with more than two syllables, when divided, cannot 
	isolate a syllable composed of a single vowel (e.g. \emph{\underline{a}gos-to}, 
	\emph{la-go\underline{a}}, \emph{\underline{i}da-de});
\end{enumerate}

\item[Splitting Rules]\

%    \hspace{10em} \hbox to 5cm{\leaders\hbox to 10pt{\hss . \hss}\hfil} 
\begin{enumerate}[resume]
    \item\label{rule-hiatus} hiatus vowels and those vowel sequences where each vowel
	belongs to a different syllable should be split (e.g.
	\emph{sa\underline{-ú-}de}, \emph{ra\underline{-i-}nha}, \emph{d\underline{o-e}r},
	\emph{v\underline{o-o}s}), the same procedure is used splitting diphthongs
	in different syllables (e.g. \emph{c\underline{ai-ai}s}) or diphthong and
	vowel in different syllables (e.g. \emph{en-s\underline{ai-o}s});
    \item\label{rule-consonants} consonant sequences, when in different syllables, should
	be split (e.g. \emph{a\underline{f-t}a}, \emph{a\underline{b-d}i-car},
	\emph{re\underline{s-c}i-são}, \emph{a\underline{b-s}o-lu-to});
    \item\label{rule-digraphs} the following consonant digraphs should be split:
	\emph{rr}, \emph{ss}, \emph{mm}, \emph{nn}, \emph{sc}, \emph{sç} and
	\emph{xc} (e.g. \emph{te\underline{r-r}a}, \emph{pro-fe\underline{s-s}or},
	\emph{co-mu\underline{\emph{m-m}}en-te}, \emph{co\underline{n-n}os-co},
	\emph{de\underline{s-c}er}, \emph{cre\underline{s-ç}a}, \emph{e\underline{x-c}e-der}).
\end{enumerate}
\end{description}

Rules \ref{rule-singlev} and \ref{rule-orphan} are primarily aimed at ensuring
proper readability of the text, aligning with \TeX{} approach to deal with
widows and orphans. As mentioned in \Cref{sec-intro}, the variables
\verb|lefthyphenmin| and \verb|righthyphenmin| control the minimum length for
fragments of hyphenated words.  When those variables are set to values greater
than one, Rules \ref{rule-singlev} and \ref{rule-orphan} become fiddling rules
in \TeX{} hyphenation, and they could be disregarded. Notwithstanding, the full
hyphenation of words is useful, particularly in text-to-speech applications
\parencite{libossek2000,trogkanis2010}.

Additionally, it is advisable to refrain from
splitting disyllables consisting of four letters (e.g., \emph{para},
\emph{como}, \emph{cede}). This considerations also lead to more aesthetically
pleasing and intelligible text, and \TeX{}'s control of isolated fragments,
through the variables \verb|\lefthyphenmin| and \verb|\righthyphenmin|, already
address this issue.

%Note that rules \ref{rule-singlev} and \ref{rule-orphan} are fiddling rules in
%\TeX{} hyphenation, since \TeX{} already has directives to avoid hyphenated
%widows and orphans.  As mentioned in \Cref{sec-intro}, the variables
%\verb|lefthyphenmin| and \verb|righthyphenmin| are used to control the minimum
%length for fragments of hyphenated words.  For this reason, we will not take
%into account rules \ref{rule-singlev} and \ref{rule-orphan} during the analysis
%and development of the hyphenation rules.

In some situations a hyphen should be repeated at the start of the following
line. They are: 
\begin{enumerate}
\item cases where compound words using a hyphen are split across lines (e.g.,
    \emph{couve-/-flor}, \emph{ex-/-presidente}); and
\item cases where splitting a pronoun could result in a different meaning (e.g.,
    \emph{prazer de ver-/-me}\footnote{Possible conveyed meanings: 
    \emph{pleasure in seeing me} or \emph{worm's pleasure}.}). 
\end{enumerate}

%To ensure proper hyphenation and readability, certain guidelines should be
%followed. Avoiding a single vowel at the end or start of a line is crucial
%(e.g., \emph{san-guí-nea} should be split only on the provided hyphens,
%avoiding a split that leaves the final vowel \emph{a} alone at the start of a
%new line: \emph{sanguíne-a}). Additionally, it is advisable to refrain from
%splitting disyllables consisting of four letters (e.g., \emph{para},
%\emph{como}, \emph{cede}).  These considerations lead to more aesthetically
%pleasing and intelligible text.

Systematizing the rules that guide syllable boundaries and hyphenation in
Portuguese is a fundamental step to understand and improve the \TeX{}
hyphenation rules. To ensure the accuracy of hyphenation rules and effectively
compare their results, a hyphenation spelling dictionary serves as an
indispensable reference. This dictionary provides a comprehensive listing of
correctly hyphenated words, enabling the computation of the correctness of each
set of hyphenation rules. By consulting the hyphenation spelling dictionary,
one can verify whether the hyphenation patterns generated by a set of rules
align with established standards. This process involves analyzing how well the
hyphenation rules adhere to the accepted conventions of the language, ensuring
that they effectively segment words without compromising readability or
consistency. Moreover, by comparing the results obtained from different sets of
hyphenation rules against the entries in the spelling dictionary, we can assess
the efficacy and reliability of each approach. In section \ref{sec-dictionay},
we will define the specifications of this reference dictionary, outlining its
role in subsequent rule updates and rules generation.

### 2024-06-06 article/resultsdefaultrules.tex
updates

\section{Results for the default rules}

In this section we will apprise the performance of default \TeX{} hyphenation
rules on the list of hyphenated words, which creation was described in
\Cref{sec-dictionay}. \Cref{tab-default-results} summaries the results, showing
the number of words correctly hyphenated words by the default rules, the number
of words wrongly hyphenated and the number of words where a hyphenation point
was missed.

\begin{table}[htbp]
\centering
\caption{Results of \TeX{} default hyphenation rules on \texttt{hyphenations6}, \texttt{hyphenations5} and \texttt{hyphenations4} dictionaries.}
\label{tab-default-results}
\begin{tabular}{lrrrr}
\toprule
word list 	& \# correct 		& \# wrong 		& \# missing 		& \# entries 		\\
\midrule
hyphenations6 	& \NumberOfCorrectSix{}	& \NumberOfWrongSix{}	& \NumberOfMissingSix{}	& \NumberOfTotalSix{} 	\\
hyphenations5 	& \NumberOfCorrectFive{}& \NumberOfWrongFive{}	& \NumberOfMissingFive{}& \NumberOfTotalFive{} 	\\
hyphenations4 	& \NumberOfCorrectFour{}& \NumberOfWrongFour{}	& \NumberOfMissingFour{}& \NumberOfTotalFour{} 	\\
total		& \NumberOfCorrectSum{} & \NumberOfWrongSum{} 	& \NumberOfMissingSum{}	& \NumberOfTotalSum{}   \\
\bottomrule
\end{tabular}
\end{table}

For the list comprised in \texttt{hyphenations6}, below is the complete list of
\NumberOfWrongSix{} words that were incorrectly hyphenated:
% wrong
\begin{multicols}{3}
\setlength{\columnsep}{0pt}
\setlength{\parindent}{0pt}
\emph{
    \input{/tmp/hyphenations6result-default-patterns_wrong.dic}
}
\end{multicols}
In each instance, an erroneous hyphenation point was placed at the beginning of
a word, indicating a potential issue in recognizing certain prefixing morphemes
in the language.  Among those, 20 occurred in words containing the \emph{psi}
morpheme, where the algorithm erroneously hyphenated between the initial
\emph{p} and the following \emph{s}. Additionally, 3 cases involved the
starting \emph{gno} sequence, while the remaining errors were observed in the
sequences \emph{pneu} (3), \emph{tch} (1), \emph{tme} (1), \emph{pto} (1), and
\emph{sub} (1).

Those erroneous hyphenation points might be corrected by the introduction of a few rules:
\texttt{.p2si, .p2sí} (see \cref{rulegrp_psi}), \texttt{.g2no, .g2nó} (see \cref{rulegrp_gno}), 
\texttt{p2neu} (see \cref{rulegrp_pneu}),
\texttt{t2c} (see \cref{rulegrp_tc}), \texttt{.t2m} (see \cref{rulegrp_tm}), \texttt{.p2t} (see \cref{rulegrp_pt}) 
and \texttt{su2b3r}, \texttt{su2b3l}  (see \cref{rulegrp_sub}). They are deeply 
discussed in \Cref{sec-hyph-rpatches}.

% $ ../scripts/resultfileexamples.sh -m -f ../data/hyphenations6result-default-patterns.dic | grep -o "[^-]-[^-]" | sort | uniq -c | sort -nr | column

The first 20 examples of missing hyphenations are displayed in the following list:
% missing
\begin{multicols}{3}
\setlength{\columnsep}{0pt}
\setlength{\parindent}{0pt}
\emph{
\input{/tmp/hyphenations6result-default-patterns_missing.dic}
...
}
\end{multicols}
It is a long list with \NumberOfMissingSix{} entries, therefore it is
unavoidable to analyse it through clusters of certain patterns. It is presented
below the counts of immediate context in which those missing hyphenations were
found:
\begin{multicols}{5}
\setlength{\columnsep}{0pt}
\setlength{\parindent}{0pt}
\emph{
\input{/tmp/hyphenations6result-default-patterns_missing_context}
}
\end{multicols}

% number of words correctly hyphenated using default TeX rules when analysing the words in hyphenations6.dic
%\captureshell*[\NumberOfCorrectSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -c}

% number of words with wrong hyphenations using default TeX rules when analysing the words in hyphenations6.dic
%\captureshell*[\NumberOfWrongSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -w}

% number of words with missing hyphenations using default TeX rules when analysing the words in hyphenations6.dic
%\captureshell*[\NumberOfMissingSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -m}

% tra-b.a*lho
%    ^ ^ ^
%    | | |
%    | | + -- correct (*)
%    | + ---- wrong   (.)  
%    + ------ missed  (-)

On the top of the list we see the missing hyphen in \emph{u-i}, accounting for
38 cases. Among those, 34 were originated from the pattern \texttt{u-ir} in the
end of word and 13 from \texttt{a-ir} in the end of word. 
To fix them, We will include the rules \texttt{u1ir.} and \texttt{a1ir.} (see 
\cref{rulegrp_air}). The cases that are not covered by this rule are:
\emph{tu-im}, \emph{je*su-i*tis*mo}, \emph{ma*lau-i*a*no}, and
\emph{con*tri*bu-in*te}. On \Cref{sec-hyph-rpatches} we see how to deal with
them.

The default rules already include 17 separating rules for vowel sequences:
% vowel="[aeiouáãàâéêíóõôú]"; grep "$vowel[13579]$vowel" ../data/default.TeX.pt-br.patterns | sed ':a;N;$!ba;s/\n/ \\\\ /g'
\begin{multicols}{5}
\setlength{\columnsep}{0pt}
\setlength{\parindent}{0pt}
\texttt{a3a \\ a3e \\ a3o \\ e3a \\ e3e \\ e3o \\ i3a \\ i3e \\ i3i \\ i3o \\ i3â \\ i3ê \\ i3ô \\ o3a \\ o3e \\ o3o \\ u3a \\ u3e \\ u3o \\ u3u}
\end{multicols}
but there are just 3 rules to hyphenate between vowels when one has a diacritic: \texttt{i3â}, \texttt{i3ê}, \texttt{i3ô}.
We could then add more 29 rules to account for the missing hyphenations between vowels with diacritics and also the
missing rule \texttt{i1u}:
% ../scripts/resultfileexamples.sh -m -f ../data/hyphenations6result-default-patterns.dic | ../scripts/filtersurrounding.sh -c '-' -n 1 | sort | uniq -c | sort -nr | grep "[áàâãéêíóôõú]" | awk '{print $2}' | sort | sed ':a;N;$!ba;s/\n/ \\\\ /g'
\begin{multicols}{5}
\setlength{\columnsep}{0pt}
\setlength{\parindent}{0pt}
\texttt{
% complete set of 37 rules
%a1â \\ a1ã \\ a1é \\ a1í \\ a1ó \\ a1ô \\ a1ú \\ 
%e1á \\ e1â \\ e1ã \\ e1é \\ e1ê \\ e1í \\ e1ó \\ e1ô \\ e1ú \\ é1o \\ 
%i1á \\ i1ã \\ i1ã \\ i1é \\ i1í \\ i1ó \\ i1u \\ i1ú \\ í1a \\ 
%o1á \\ o1ã \\ o1é \\ o1ê \\ o1í \\ o1ó \\ 
%u1á \\ u1ã \\ u1é \\ u1ê \\ u1í \\ ú1o
%
% 29 rules necessary for hyphenations6 dic
a1é \\ a1í \\ a1ó \\ a1ú \\ 
e1á \\ e1â \\ e1ã \\ e1é \\ e1ê \\ e1í \\ e1ó \\ é1o \\ e1ú \\ 
i1á \\ i1ã \\ í1a \\ i1é \\ i1í \\ i1ó \\ í1o \\ i1u \\ i1ú \\ 
o1á \\ o1é \\ o1í \\ o1ó \\ 
u1á \\ u1ã \\ u1í \\ ú1o
}
%\emph{a-é \\ a-í \\ a-ó \\ a-ú \\ e-á \\ e-â \\ e-ã \\ e-é \\ e-ê \\ e-í \\ e-ó \\ é-o \\ e-ú \\ i-á \\ i-ã \\ í-a \\ i-é \\ i-í \\ i-ó \\ í-o \\ i-ú \\ o-á \\ o-é \\ o-í \\ o-ó \\ u-á \\ u-ã \\ u-í \\ ú-o}
\end{multicols}
See more about this on \cref{rulegrp_aa}. These rules will require exceptions for sequences with \emph{[qg]uV'} 
(where we used \emph{V'} to represent a vowel with a diacritic). See more on \cref{rulegrp_aa,rulegrp_gua}.

From the list of missing hyphenations above, we find another recurring pattern, a missing hyphen preceding \emph{q}: 
% ../scripts/resultfileexamples.sh -m -f ../data/hyphenations6result-default-patterns.dic | ../scripts/filtersurrounding.sh -c '-' -n 1 | sort | uniq -c | sort -nr | awk '{print $2}' | sort | grep "q$" | sort | sed ':a;N;$!ba;s/\n/ \\\\ /g'
\begin{multicols}{5}
\setlength{\columnsep}{0pt}
\setlength{\parindent}{0pt}
\emph{a-q \\ e-q \\ i-q \\ o-q \\ r-q \\ s-q \\ u-q}
\end{multicols}
That issue might be easily solved by adding a hyphenation rule: \texttt{1qu}, but as the \emph{q} is always followed by 
a sequence \emph{uV}, and there are already four hyphenation rules involving this sort of sequence in the default rules
(\texttt{1qu4a}, \texttt{1qu4e}, \texttt{1qu4i} and \texttt{1qu4o}), the rules 
% $ grep "q" ../data/patch.TeX.pt-br.patterns | awk '{print "\\texttt{" $1 "}"}' | sed ':a;N;$!ba;s/\n/, /g'
\texttt{1qu2á}, \texttt{1qu2é}, \texttt{1qu2ê}, \texttt{1qu2í}, \texttt{que2i}, \texttt{1qu4ã}, \texttt{1qu4ó}, \texttt{1qu4â}
could be added (see \cref{rulegrp_aa,rulegrp_gua,rulegrp_quo}) but they have not proven to be necessary.
%%% XXX check if they are not really necessary

The missing hyphens in \emph{a-v} and \emph{i-v} might be easily solved by introducing the rule \texttt{1vô} (see \cref{rulegrp_bo}) which 
complements the rule \texttt{1vo} already included in the default set of rules.
% pi-vô, a-vô, bi*sa-vô ...
Similarly, the missing hyphens \emph{e-l}, \emph{u-l}, \emph{o-l}, and \emph{a-l} are corrected by the introduction of the rule \texttt{1lô} rule (see \cref{rulegrp_bo}),
complementing the already included rule \texttt{1lo}.
In the same way, the rules \texttt{1cô}, \texttt{1gô}, \texttt{1bô}, \texttt{1tô}, \texttt{1rô}, and \texttt{1pô} (see \cref{rulegrp_bo}) 
should be added to fix the missing hyphens \emph{e-c}, \emph{i-c}, \emph{o-g}, \emph{o-b}, \emph{a-t}, \emph{a-r},
and \emph{a-p}, respectively.
% ca*me-lô, gi*go-lô, ..., bi*be-lô, su.b-lu*nar
%                                       rule 1b2l causes wrong hyphen
%
%    .   s   u   b   l   u   n   a   r   .
%     1   0   0   |   |   |   |   |   |    1su
%     |   |   1   2   0   |   |   |   |    1b2l
%     |   |   |   1   0   0   |   |   |    1lu
%     |   |   |   |   |   1   0   0   |    1na
%max: 1   0   1   2   0   1   0   0   0
%final: s   u - b   l   u - n   a   r
The missing hyphen \emph{b-l} happened in \emph{su.b-lu*nar}, which also has a wrong hyphenation.
Those errors were caused by the default rule \texttt{1b2l}. The introduction of rule \texttt{su2b3l} 
will help solve this matter (see details in \cref{rulegrp_sub}).

% e-c, i-c: missing rule 1cô
% o-g: missing rule 1gô
% o-b: missing rule 1bô
% a-t: missing rule 1tô
% a-r: missing rule 1rô
% a-p: missing rule 1pô

The remaining missing hyphen is \emph{o-w}, which comes from the foreign \emph{kilowatt}.
Those cases of words borrowed from other languages are dealt in the \ref{foreignness} topic ahead.
% o-w: qui*lo-watt

% number of words with missing hyphenations using default TeX rules when analysing the words in hyphenations6.dic

### 2024-06-06 article/texrulespt.tex
updates

\section{\TeX{} hyphenation rules for portuguese}\label{sec-tex-hyphen-pt}
\textcite{rezende1987} was the first to create patterns for Portuguese hyphenation
in \TeX{}. The pattern set was last updated in 2015, incorporating
contributions from %José João Dias Almeida 
\textcite{hyphpt}, resulting in a total
of 307 rules\footnote{The set of rules for Portuguese hyphenation is short when
compared to rules in other languages. For example, English currently has 4938
rules, Russian has 7023 rules and German has 34011 rules.}. 
These rules effectively hyphenate the majority of Portuguese words.

However, in light of certain cases, we propose an analysis of the default rules
to identify areas for improvement. By addressing specific issues and
considering non-typical patterns, we aim to enhance hyphenation accuracy. The
methodology used for this analysis is described in Section
\ref{sec-methodology}.

%
% FILE="../data/default.TeX.pt-br.patterns"; grep "^1..$" "$FILE" | awk '{print substr($0, 0, 2)}' | sort | uniq -c | while read line; do p=$(echo $line | cut -d' ' -f2); c=$(grep "^$p[^0-9]$" "$FILE" | awk '{print substr($0, 3)}' | tr '\n' ' '); printf "$line $c \n"; done | cut -d' ' -f1 | paste -sd+ | bc
%
Out of the default \TeX{} rules, 252 (82\%) follow the pattern \verb|1CV|, which
represents the recurring CV syllables in Portuguese.  As for the consonants,
there are typically 18 considered (\verb|b|, \verb|c|, \verb|ç|, \verb|d|,
\verb|f|, \verb|g|, \verb|j|, \verb|k|, \verb|l|, \verb|m|, \verb|n|, \verb|p|,
\verb|r|, \verb|s|, \verb|t|, \verb|v|, \verb|x|, and \verb|z|) that can
combine with 14 vowels (\verb|a|, \verb|e|, \verb|i|, \verb|o|, \verb|u|,
\verb|á|, \verb|â|, \verb|ã|, \verb|é|, \verb|í|, \verb|ó|, \verb|ú|, \verb|ê|,
and \verb|õ|), resulting in these CV patterns that indicate favorable
hyphenation points before the consonants\footnote{The complete list of these
252 patterns is given here: \ExceptionRulesCV{}.}. 
It is worth noting that there might
be other rules or exceptions in the hyphenation patterns not covered by these
default rules.  To accommodate exceptions, \textcite{rezende1987} proposes the 
following rules: 
\begin{itemize}
    \item 20 rules created for cases involving consonants \verb|b|, \verb|c|, \verb|d|, \verb|f|, \verb|g|, \verb|k|, \verb|p|, \verb|t|, \verb|v|, or \verb|w| followed by \verb|l| or \verb|r|\footnote{The 20 additional rules are: \ExceptionRulesLR{}.};
    \item 3 rules for \verb|c|, \verb|l| or \verb|n| followed by \verb|h|\footnote{Those 3 rules are: \ExceptionRulesCLNH{}.};
    % FILE="../data/default.TeX.pt-br.patterns"; grep -v "^1..$" "$FILE" | grep "2" | awk '{print substr($0, 2, 1)}' | sort | uniq | while read line; doc=$(grep "^1${line}2.$" "$FILE" | tr -d '12' | awk '{print substr($0, 2, 1)}' | tr '\n' ' '); printf "$line $c\n"; done
    \item 23 distinct patterns were introduced to indicate hyphenation points between vowels or between \verb|c|'s, \verb|r|'s, and \verb|s|'s\footnote{Those patterns are: \ExceptionRulesThree{}.}; 
    % FILE="../data/default.TeX.pt-br.patterns"; grep -v "^1..$" "$FILE" | grep -v "2" | grep "3" | wc -l
    \item 8 patterns adhere to the \verb|1[gq]u4V| pattern, signaling beneficial hyphenation points before \verb|g| or \verb|q|, followed by a sequence of \verb|u| and a vowel, with an inhibiting point between the \verb|u| and the subsequent vowel\footnote{They are the following: \ExceptionRulesFour{}.};
    \item 1 pattern represented as \verb|1-|, denoting that a hyphen indeed serves as a beneficial hyphenation point.
\end{itemize}

% - contabilizar a quantidade de palavras que não são contempladas pela proposta do autor
% - analisar a necessidade de excluir alguma regra (ao invés de apenas acrescentar novas)

### 2024-06-06 article/updatingrules.tex
updates

\section{Updating the rules}
We now begin incorporating the rules proposed in the previous section and
appraise the results of each one. During this process, we will consider the
necessity of updating those rules, including exceptions, or even discarding the
proposed rules if needed.

% cat ../data/default.TeX.pt-br.patterns <(echo -e "p2si\np2sí") > /tmp/patts
% ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts > /tmp/hyphenations6result_001.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations6result_001.dic
% correct: 15548; wrong: 10 (10); missing: 284 (283,1)

% cat ../data/default.TeX.pt-br.patterns <(echo -e "p2si\np2sí\n.g2no\n.g2nó\nt2c\np2neu\n.t2m\n.p2t\nsu2b3r\nsu2b3l") > /tmp/patts
% ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts > /tmp/hyphenations6result_001.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations6result_001.dic
% correct: 15552; wrong: 6 (6); missing: 286 (285,1)
%
% compare with the results of the default rules:
% diff -y --suppress-common-lines <(sort ../data/hyphenations6result-default-patterns.dic) <(sort /tmp/hyphenations6result_001.dic)
% 
% ./gohyphenfull ../data/default.TeX.pt-br.patterns psiquiátrico
%
% cat ../data/default.TeX.pt-br.patterns <(echo -e ".p2si\n.p2sí\n.g2no\n.g2nó\nt2c\np2neu\n.t2m\n.p2t\nsu2b3r\nsu2b3l") > /tmp/patts
% ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts > /tmp/hyphenations6result_001.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations6result_001.dic
% correct: 15562; wrong: 3 (3); missing: 279 (278,1)

After introducing the rules: \texttt{.p2si}, \texttt{.p2sí}, \texttt{.g2no}, \texttt{.g2nó}, \texttt{t2c}, 
\texttt{p2neu}, \texttt{.t2m}, \texttt{.p2t}, \texttt{su2b3r}, and \texttt{su2b3l}, 
the number of incorrect hyphenations decreased to 3, and the number of missing hyphenations decreased to 278.
At first sight, we expected the number of incorrect hyphenations to drop to zero. However, 
the introduction of rule \texttt{su2b3l} introduced hyphenation errors in \emph{su-b.li*me}, \emph{su-b.li*ma*ção} and \emph{su-b.li*ma*do}.

\noindent\begin{minipage}{\linewidth}
\begin{lstlisting}[language={}, caption={Hyphenation of the word \emph{sublime} after the indroduction of rule \texttt{su2b3l}. 
This rule introduces a wrong hyphenation point, demanding an exception rule to fix it.}, label=sublimehyphenation]
   .   s   u   b   l   i   m   e   .
     1   0   0   |   |   |   |   |    1su
     0   0   2   3   0   |   |   |    su2b3l
     |   |   1   2   0   |   |   |    1b2l
     |   |   |   1   0   0   |   |    1li
     |   |   |   |   |   1   0   0    1me
max: 1   0   2   3   0   1   0   0
final: s   u   b - l   i - m   e
\end{lstlisting}
\end{minipage}
\noindent{}By inserting the rule \texttt{.su3b4li}, we fixed the hyphenation errors caused by the introduction of the rule \texttt{su2b3l},
as illustrated in \Cref{sublimehyphenation}. This adjustment resulted in zero hyphenation errors and 276 missing hyphens.
% cat ../data/default.TeX.pt-br.patterns <(echo -e ".p2si\n.p2sí\n.g2no\n.g2nó\nt2c\np2neu\n.t2m\n.p2t\nsu2b3r\nsu2b3l\n.su3b4li") > /tmp/patts
% ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts > /tmp/hyphenations6result_001.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations6result_001.dic
% correct: 15565; wrong: 0 (); missing: 276 (275,1)

% 12 regra: su2b3r, su2b3l – sublunar, subrotina exceção: su3b4li1nh, su3b4li1ma,
% su3b4li1me, su3b4li1mid – sublinhar, sublimar, sublime, sublimidade

The next step is to introduce the rules o address the missing hyphenation points. These rules are: 
\texttt{a1ir.}, \texttt{u1ir.}, \texttt{i3â}, \texttt{i3ê}, \texttt{i3ô}, \texttt{1qu}, \texttt{1vô}, \texttt{1lô}, \texttt{1cô}, \texttt{1gô}, \texttt{1bô}, 
\texttt{1tô}, \texttt{1rô}, \texttt{1pô}, \texttt{a1é}, \texttt{a1í}, \texttt{a1ó}, \texttt{a1ú}, \texttt{e1á}, \texttt{e1â}, \texttt{e1ã}, 
\texttt{e1é}, \texttt{e1ê}, \texttt{e1í}, \texttt{e1ó}, \texttt{é1o}, \texttt{e1ú}, \texttt{i1á}, \texttt{i1ã}, \texttt{í1a}, \texttt{i1é}, 
\texttt{i1í}, \texttt{i1ó}, \texttt{í1o}, \texttt{i1u}, \texttt{i1ú}, \texttt{o1á}, \texttt{o1é}, \texttt{o1í}, \texttt{o1ó}, \texttt{u1á}, \texttt{u1ã}, 
\texttt{u1í}, \texttt{ú1o}.
% \texttt{1qu2á}, \texttt{1qu2é}, \texttt{1qu2ê}, \texttt{1qu2í}, \texttt{que2i}, \texttt{1qu4ã}, \texttt{1qu4ó}, \texttt{1qu4â}
% \texttt{1gu2é}, \texttt{1gu2ê}, \texttt{1gu2í} 
% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o" | tr -d ' ' | tr ',' '\n') > /tmp/patts2
% %%% a1â, a1ã, a1é, a1í, a1ó, a1ô, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, e1ô, e1ú, é1o, i1á, i1ã, i1é, i1í, i1ó, i1u, i1ú, í1a, o1á, o1ã, o1é, o1ê, o1í, o1ó, u1á, u1ã, u1é, u1ê, u1í, ú1o
% ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts2 > /tmp/hyphenations6result_002.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations6result_002.dic
% correct: 15804; wrong: 18 (18); missing: 19 (19)
% grep "\." /tmp/hyphenations6result_002.dic | grep -oP "[^\.\*\-]{1,2}\.[^\.\*\-]{1,2}" | sort | uniq -c | sort -nr | column
% 11 qu.í          4 qu.á          1 qu.ís         1 qu.ín         1 gu.ís
After inserting these rules, the number of incorrect hyphenations increases to 18 due to the inclusion of hyphens in \emph{qu.í}, \emph{gu.í} and \emph{qu.á}. 
To overcome these errors, we need to add exception rules: \texttt{1qu2á}, \texttt{1qu2í}, and \texttt{1gu2í}.
See more on this on \cref{rulegrp_aa,rulegrp_gua}.
% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í" | tr -d ' ' | tr ',' '\n') > /tmp/patts3
% ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts3 > /tmp/hyphenations6result_003.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations6result_003.dic
% correct: 15822; wrong: 0 (); missing: 19 (19)

We have reached a point where there is no wrong hyphenation but still there are 19 missing hyphenation. Here is the list of the missing ones:
\begin{multicols}{5}
\setlength{\columnsep}{0pt}
\setlength{\parindent}{0pt}
\emph{a-in*da \\ ra-i*nha \\ con*tri*bu-in*te \\ ra-iz \\ re-in*te*gra*ção \\ cam*pa-i*nha \\ re-in*te*grar \\ ta-i*nha \\ re-in*ci*dir \\ pa-in*ço \\ pi*xa-im \\ re-im*pres*são \\ tu-im \\ je*su-i*tis*mo \\ ben*jo-im \\ ma*lau-i*a*no \\ re-im*pri*mir}
\end{multicols}
\noindent{}Observing the instances above, 17 out of 19 involve a missing hyphen before the vowel \emph{i}. The following rules
will be used to solve those issues: \texttt{a1ind}, \texttt{a1i1nh} (see \cref{rulegrp_ain}), \texttt{e1imp} (see \cref{rulegrp_eim}), 
\texttt{e1inc}, \texttt{e1inf}, \texttt{e1ing}, \texttt{e1ins}, \texttt{e1int}, \texttt{e1inv}, (see \cref{rulegrp_ein}), 
\texttt{u1int}, \texttt{u1ind} (see \cref{rulegrp_unit}), and \texttt{u1iz.}, \texttt{a1iz.} (see \cref{rulegrp_aiz}).
% rulegrp_ain regra: a1ind, a1i1nh – ainda, rainha
% rulegrp_eim regra: e1imp – reimpresso
% rulegrp_ein regra: e1inc, e1inf, e1ing, e1ins, e1int, e1inv
% rulegrp_unit regra: u1int, u1ind -- contribuinte, excluindo
% rulegrp_aiz regra: u1iz., a1iz. -- juiz, raiz

% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz." | tr -d ' ' | tr ',' '\n') > /tmp/patts4
% ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts4 > /tmp/hyphenations6result_004.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations6result_004.dic
% correct: 15833; wrong: 0 (); missing: 8 (8)

After incorporating these rules, the number of missing hyphenations decrease to only 8:
\begin{multicols}{5}
\setlength{\columnsep}{0pt}
\setlength{\parindent}{0pt}
\emph{pa-ul \\ qui*lo-watt \\ pa-in*ço \\ pi*xa-im \\ tu-im \\ je*su-i*tis*mo \\  ben*jo-im  \\  ma*lau-i*a*no}
\end{multicols}
\noindent{}Since these remaining cases comprises only a few rare words, we now proceed to integrate the dictionary \texttt{hyphenations5} and 
evaluate the results of the current rules against this set. 
% ./gocreateresultfile.sh ../data/hyphenations5.dic /tmp/patts4 > /tmp/hyphenations5result_004.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations5result_004.dic
% correct: 14410; wrong: 1121 (1120,1); missing: 133 (133)
In this new dataset, the number of incorrect hyphenations
increases to 1121, with the majority stemming from apparent proparoxytones. These cases can be easily rectified by
avoiding the final hyphen which leaves the vowels \emph{a}, \emph{e} or \emph{o} alone in the last syllable.
To address this, we introduce rules \texttt{4a.}, \texttt{4e.}, \texttt{4o.} (see \cref{rulesxxx}).
While a more comprehensive rule set could be developed to account for all scenarios\footnote{A better rule would be to restrain the final hyphenation, leaving the vowel alone, if the preceding syllable has a vowel with diacritic. That would require an exhaustive list of all scenarios.}, we opted for these more concise rules despite their limitations. 
% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o." | tr -d ' ' | tr ',' '\n') > /tmp/patts5
% ./gocreateresultfile.sh ../data/hyphenations5.dic /tmp/patts5 > /tmp/hyphenations5result_005.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations5result_005.dic
% correct: 14720; wrong: 35 (35); missing: 900 (897,3) 
The addition of these rules reduces the number of wrong hyphenations to 35; however, it increases the number of missing hyphenations 
from 133 to 900. Among these, 770 additional missing hyphenations occur
before the final vowel of a word.
Considering the smaller number of cases, the perceived severity (a missing hyphen is deemed less problematic than an incorrect one), 
and the position of the word's end, we have chosen to retain these rules.

The resulting errors are shown in the following list:
\begin{multicols}{5}
\setlength{\columnsep}{0pt}
\setlength{\parindent}{0pt}
\emph{sa*gu.ão \\ p.seu-dô*ni*mo \\ s.ta*li*nis*mo \\ a.b-rup*to \\ su.b-li*mi*nar \\ quar-t.zi*to \\ c.za*ri*na \\ c.za*ris*ta \\ bre.ch*ti*a*no \\ c.za*ris*mo \\ su.b-li*te*ra*tu*ra \\ ca*ra*min*gu.ás \\ d.ze*ta \\ m.ne-mô*ni*ca \\ p.so*rí*a*se \\ t.za*ris*ta \\ g.nais*se \\ m.ne-mô*ni*co \\ p.so*as \\ su.b-lin*gual \\ es*tô*ma.go \\ núp*ci.as \\ su.b-li*nha \\ a*rá*bi.as \\ quar-t.zo \\ e*fe*mé*ri.de \\ cri*sân*te.mo \\ e*xé*qui.as \\ flâ*mu.la \\ a-p.nei-a \\ c.ni*dá*rio \\ dis-p.nei-a \\ gli*có*li.se \\ hi*pe.r-al*ge*si-a \\ ne.er*lan*dês}
\end{multicols}
\noindent{}From these, we have proposed the rules: \texttt{1gu4á}, \texttt{1gu4ã}, \texttt{1qu4ã} (see \cref{rulegrp_gua}),
\texttt{.m2n} (see \cref{rulegrp_mn}), \texttt{c2za} (see \cref{rulegrp_cza}), \texttt{.s2} (see \cref{rulegrp_s2}), and \texttt{1p2seu1d} (see \cref{rulegrp_pseu}).
% regra: 1gu4á, 1gu4ã, 1qu4ã – jaraguá, saguão, quão
% regra: .m2n – mnemônico
% regra: c2za – czar
% regra: .s2
% regra: 1p2seu1d – pseudônimo
% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d" | tr -d ' ' | tr ',' '\n') > /tmp/patts6
% ./gocreateresultfile.sh ../data/hyphenations5.dic /tmp/patts6 > /tmp/hyphenations5result_006.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations5result_006.dic
% correct: 14732; wrong: 21 (21); missing: 899 (896,3)

The inclusion of these rules leave us with 21 incorrect hyphenations and 899 missing ones.
The list of wrong hyphenations follows below:
\begin{multicols}{5}
\setlength{\columnsep}{0pt}
\setlength{\parindent}{0pt}
\emph{a.b-rup*to \\ su.b-li*mi*nar \\ quar-t.zi*to \\ bre.ch*ti*a*no \\ su.b-li*te*ra*tu*ra \\ d.ze*ta \\ p.so*rí*a*se \\ t.za*ris*ta \\ g.nais*se \\ p.so*as \\ su.b-lin*gual \\ núp*ci.as \\ su.b-li*nha \\ a*rá*bi.as \\ quar-t.zo \\ e*xé*qui.as \\ a-p.nei-a \\ c.ni*dá*rio \\ dis-p.nei-a \\ hi*pe.r-al*ge*si-a \\ ne.er*lan*dês}
\end{multicols}
\noindent{}Most of these cases occur in rare words or loanword. We decided not to address them.
Analyzing the missing hyphenation points, as mentioned earlier, most result from the rules (\texttt{4a.}, \texttt{4e.}, \texttt{4o.})
we proposed to handle apparent proparoxytones. This leave us with 125 missing hyphenations to address.
We observe that a few additional rules with diacritic counterpart need to be introduced: 
\texttt{1dô}, \texttt{1fô}, \texttt{1mô}, \texttt{1nô}, \texttt{1sô}, \texttt{1zô} (see \cref{xxx}), 
%\texttt{1ên} (see \cref{}), 
\texttt{u3é}, \texttt{1gu4é}, \texttt{1qu4é} (see \cref{xxxx}).
% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, u3é, 1gu4é, 1qu4é" | tr -d ' ' | tr ',' '\n') > /tmp/patts7
% ./gocreateresultfile.sh ../data/hyphenations5.dic /tmp/patts7 > /tmp/hyphenations5result_007.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations5result_007.dic
% correct: 14775; wrong: 21 (21); missing: 856 (853,3)
After incorporating these rules, we now have 21 incorrect and 856 missing hyphenations, 86 of which do not involve the final vowel.

% grep "-" /tmp/hyphenations5result_007.dic | grep -v "\-[aeo]$" | grep "\-[ií]\|[ií]\-" | wc -l
% grep "-" /tmp/hyphenations5result_007.dic | grep -v "\-[aeo]$" | grep -v "\-[ií]\|[ií]\-" | wc -l
% 50 involve a "i"
% 36 not
% grep "-" /tmp/hyphenations5result_007.dic | grep -v "\-[aeo]$" | grep "\-[ií]\|[ií]\-" | grep -oP "[^\-\*\.]{1,3}\-[^\-\*\.]{1,3}" | sort | uniq -c | sort -rn | while read -r count string; do grep_pattern="(^|\*|\.)${string}(\*|\.|$)"; matches=$(grep -E "$grep_pattern" /tmp/hyphenations5result_007.dic | tr '\n' ','); echo "$count $string : $matches"; done
%
% 5 tu-i : cons*ti*tu-i*ção,subs*ti*tu-i*ção,pros*ti*tu-i*ção,in*tu-i*ti*vo,des*ti*tu-i*ção,
% 5 bu-i : dis*tri*bu-i*ção,a*tri*bu-i*ção,re*tri*bu-i*ção,con*tri*bu-i*dor,con*tri*bu-i*ção,
% u1i1ç : des*po*lu-i*ção
% 3 co-in : co-in*ci*dir,co-in*ci*den*te,co-in*ci*dên*cia,
% 2 ru-im : ru-im,ma*ru-im,
% 2 ru-i : ar*ru-i*nar,ru-i*no*so,
% 2 nu-i : in*ge*nu-i*da*de,a*nu-i*da*de,
% 2 mo-i : mo-i*nho,mo-i*nha,
% 2 lu-i : e*lu-i*ção,a*lu-i*men*to,
% 2 cu-im : mu*cu-im,mi*cu-im,
% 2 cu-i : a*cu-i*da*de,pi*cu-i*nha,
% 1 tro-in : gas*tro-in*tes*ti*nal,
% 1 tai-wa : tai-wa*nês,
% 1 su-in : su-in*gue,
% 1 su-i : pos*su-i*dor,
% 1 sa-is : es*pon*sa-is,
% 1 ro-i : co*ro-i*nha,
% 1 rí-e : a*rí-e*te,
% 1 ra-is : ar*ra-is,
% 1 po-i : de*po-i*men*to,
% 1 ju-i : a*ju-i*zar,
% 1 jo-in : jo-in*vi*len*se,
% 1 fu-i : fu-i*nha,
% 1 fru-i : fru-i*ção,
% 1 flu-i : flu-i*dez,
% 1 fa-im : fa-im,
% 1 du-i : as*si*du-i*da*de,
% 1 do-im : a*men*do-im,
% 1 de-is : in*de-is*cen*te,
% 1 da-il : a*da-il,
% 1 co-i : co-i*bir,
% 1 cau-im : cau-im,
% 1 ca-im : ca-im,
% 1 au-i : pi*au-i*en*se,
%
% try add those rules:
% tu-i, bu-i, co-in, ru-i, nu-i, mo-i, lu-i, cu-i, o-in, u-in, su-i, ro-i, í-e, ra-is, po-i, ju-i, fu-i, fru-i, flu-i, du-i, do-im, co-i, au-i
% correct: 14787; wrong: 59 (59); missing: 812 (809,3)
% 
% improved
% tu-i, bu-i, co-in, nu-i, cu-i, o-in, u-in, su-i, í-e, ra-is, ju-i, fu-i, du-i, do-im, au-i
% u1i1ç

To account for a few more missing cases, we propose the inclusion of the following rules: 
\texttt{tu1i}, \texttt{bu1i}, \texttt{co1in}, \texttt{nu1i}, \texttt{cu1i}, \texttt{o1in}, \texttt{u1in}, \texttt{su1i}, \texttt{í1e}, \texttt{ra1is},
\texttt{ju1i}, \texttt{fu1i}, \texttt{du1i}, \texttt{do1im}, \texttt{au1i}, \texttt{u1i1ç}.
% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, u3é, 1gu4é, 1qu4é, tu1i, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç" | tr -d ' ' | tr ',' '\n') > /tmp/patts8
% ./gocreateresultfile.sh ../data/hyphenations5.dic /tmp/patts8 > /tmp/hyphenations5result_008.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations5result_008.dic
% correct: 14813; wrong: 21 (21); missing: 818 (815,3)
With these additions, the number of missing hyphenations drops to 818, with 772 cases involving final vowels,
as mentioned earlier. Among these, only two cases involve a final vowel with a diacritic: \emph{fu*zu-ê} and \emph{ba*ba*la-ô}).
The list of the remaining 46 follows:
\begin{multicols}{5}
\setlength{\columnsep}{0pt}
\setlength{\parindent}{0pt}
\emph{ru-im \\ flu-i*dez \\ a*da-il \\ voy-eu*ris*mo \\ a.b-rup*to \\ me*ga-watt \\ ca-im \\ su.b-li*mi*nar \\ dar-wi*nis*mo \\ quar-t.zi*to \\ re-ur*ba*ni*zar \\ voy-eu*ris*ta \\ ba-ha*men*se \\ dar-wi*nis*ta \\ ma-çô*ni*co \\ pat-chu*li \\ su.b-li*te*ra*tu*ra \\ fa-im \\ voy-eu*rís*ti*co \\ tai-wa*nês \\ a*bra-â*mi*co \\ ca*far*na-um \\ ku-wai*ti*a*no \\ ma*ru-im \\ su.b-lin*gual \\ te-ô*ni*mo \\ a*lu-i*men*to \\ mal-thu*si*a*nis*mo \\ mal-thu*si*a*no \\ in*flu-ên*cia \\ de*po-i*men*to \\ re-u*nir \\ co-i*bir \\ flu-ên*cia \\ con*flu-ên*cia \\ a*nu-ên*cia \\ su.b-li*nha \\ a*flu-ên*cia \\ in*con*gru-ên*cia \\ quar-t.zo \\ es*pon*sa-is \\ ba*la-us*tra*da \\ con*gru-ên*cia \\ tran*se-un*te \\ di*flu-ên*cia \\ in*de-is*cen*te}
\end{multicols}
From this list, we may create a new rule: \texttt{u1ê}, which would also require two exception rules: \texttt{gu2ê} and \texttt{qu2ê}.
% rules: u1ê (u3ê, since the default rule has a u3e)
%   exception rules: gu2ê, qu2ê
%
% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, u3é, 1gu4é, 1qu4é, tu1i, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç, u1ê, gu2ê, qu2ê" | tr -d ' ' | tr ',' '\n') > /tmp/patts9
% ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts9 > /tmp/hyphenations6result_009.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations6result_009.dic
% correct: 15302; wrong: 0 (); missing: 539 (539) 
% ./gocreateresultfile.sh ../data/hyphenations5.dic /tmp/patts9 > /tmp/hyphenations5result_009.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations5result_009.dic
% correct: 14817; wrong: 21 (21); missing: 809 (806,3)
% ./gocreateresultfile.sh ../data/hyphenations4.dic /tmp/patts9 > /tmp/hyphenations4result_009.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations4result_009.dic
% correct: 968; wrong: 0 (); missing: 29 (29)
Incorporating them, we solve the nine cases of missing hyphen \emph{u-ê}, dropping the number of missing hyphenations to 809.

We now move to the last dictionary file: \texttt{hyphenations4}. Using the rules we have developed so far,
% ./gocreateresultfile.sh ../data/hyphenations4.dic /tmp/patts8 > /tmp/hyphenations4result_008.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations4result_008.dic
% correct: 968; wrong: 0 (); missing: 29 (29)
we achieve 0 incorrect and 29 missing hyphenations in this dictionary. 
Of these, 26 involve final vowels, and the remaining 3 are:
\emph{re-in*de*xa*ção}, \emph{pa*ra-i*ba*no} and \emph{ru-ther*ford})
% $ grep "-" /tmp/hyphenations4result_009.dic | grep -v "\-[aeo]$".

% check list now after rules update above
% lis*bo-a \\ bi*o*gra*fi-a \\ re*en*ge*nha*ri-a \\ bi-a \\ co*or*de*na*do*ri-a \\ so*ci*o*lo*gi-a \\ cer*ve*ja*ri-a \\ tu-a \\ cu*ra*do*ri-a \\ cor*re*ri-a \\ ho*te*la*ri-a \\ co*ti-a \\ re-in*de*xa*ção \\ ba*lei-a \\ fi*si*o*lo*gi-a \\ gas*tro*no*mi-a \\ ca*cai-o \\ dan*ce*te*ri-a \\ ge*o*me*tri-a \\ pa*ra-i*ba*no \\ pa*ra*guai-a \\ chan*ce*la*ri-a \\ his*to*ri*o*gra*fi-a \\ ra*di*o*gra*fi-a \\ re*la*to*ri-a \\ te*le*dra*ma*tur*gi-a \\ ra*di*o*te*ra*pi-a \\ ru-ther*ford \\ jo*a*lhe*ri-a

% apparent proparoxytones + few missing: re-in*de*xa*ção, pa*ra-i*ba*no, ru-ther*ford

% u-ição - di*mi*nu-i*ção, des*tru-i*ção, res*ti*tu-i*ção, des*po*lu-i*ção, re*cons*ti*tu-i*ção, in*tu-i*ção
% u-idora - dis*tri*bu-i*do*ra, dis*tri*bu-i*dor
% 1fô - sin-fô*ni*ca
% 1nô - gas*tro-nô*mi*co, a*gro-nô*mi*co, as*tro-nô*mi*co, ma*cro*e*co-nô*mi*co
% 1dô - ma*ce-dô*nia, ab-dô*men
% pa*ra-i*ba*no
% ju-i*za*do
% re-in*de*xa*ção
% ru-ther*ford

% $ meld <(sort /tmp/patts9) <(sort ../data/patched-default.TeX.pt-br.patterns)
% regra (necessário incluir?)
% 1çô (sim), 1flu2íd (não), u1é (sim), 1gu2é (sim), 1qu2é (sim), 
% 1gu2ê (já tem), 1qu2ê (já tem), 1qu4â (não), 1qu4ó (não), 1xô (sim), a1â (sim), a1ã (sim), a1ô (sim), au1i1c (não)
% bu1i1n (não), bu1i2n1d (não), bu1i2n1t (não), cu2i (sim), cu3in (sim), cu3i1da1de (não), dru2i (não), du1i1c (não), e1ô (sim), é3o (já tem), 
% flu2id (não), fu1i1n (não), .g2nô (sim), i1un (não), i1ur (não), .ne4o (sim), u1i1d (não), nu1i1n (não), o1ã (sim), o1ê (sim), o1i1nh (não), 
% o1im (sim), o2i1na (sim), p1p (não), p3sia (não), p3sin (não), pro1i1b (sim), ru1i1na (não), ru1i1no (não), su1i1ti (não), z1z (não), z2z. (não)
%

% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, .g2nô, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, u3é, 1gu4é, 1qu4é, tu1i, tu2it, tu2id, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç, u1ê, gu2ê, qu2ê, 1çô, u1é, 1gu2é, 1qu2é, 1xô, a1â, a1ã, a1ô, cu2i, cu3in, e1ô, .ne4o, o1ã, o1ê, o1im, o2i1na, pro1i1b, co2ima" | tr -d ' ' | tr ',' '\n') > /tmp/patts10

% echo ".p2si, .p2sí, .g2no, .g2nó, .g2nô, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, u3é, 1gu4é, 1qu4é, tu1i, tu2it, tu2id, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç, u1ê, gu2ê, qu2ê, 1çô, u1é, 1gu2é, 1qu2é, 1xô, a1â, a1ã, a1ô, cu2i, cu3in, e1ô,.ne4o, o1ã, o1ê, o1im, o2i1na, pro1i1b, co2ima" | tr -d ' ' | tr ',' '\n' > ../data/patch.TeX.pt-br.patterns.v2

% cat ../data/default.TeX.pt-br.patterns ../data/patch.TeX.pt-br.patterns.v2 > ../data/patched-default.TeX.pt-br.patterns.v2

Considering some additional words that are not on the list, we gather an additional set of rules to 
be incorporated: 
\texttt{1çô} (e.g., \emph{ma-çô-ni-co}), 
\texttt{1xô} (e.g., \emph{a-xô-nio}, \emph{sa-xô-ni-co}),
\texttt{a1â} (e.g., \emph{a-bra-â-mi-co}), 
\texttt{a1ã} (e.g., \emph{a-bra-ão}, \emph{ca-na-ã}), 
\texttt{a1ô} (e.g., \emph{fa-ra-ô-ni-co}), 
\texttt{e1ô} (e.g., \emph{le-ô-ni-das}, \emph{na-po-le-ô-ni-co}),
\texttt{o1ã} (e.g., \emph{jo-ão}, \emph{la-go-ão}),
\texttt{o1ê} (e.g., \emph{bo-ê-mi-o}),
\texttt{cu2i} (e.g., \emph{cui-da-do}, \emph{cir-cui-to}; this rule requires the exception rule \texttt{cu3in} to avoid unintended errors in words like \emph{pi-cu-i-nha}, \emph{i-mis-cu-in-do}), 
\texttt{.ne4o} (e.g., \emph{neo-li-be-ral}, \emph{neo-na-zis-ta}),
\texttt{o1im} (e.g., \emph{co-im-bra}; this rule requires the exception rule \texttt{co2ima} to avoid unintended errors in words like \emph{coi-ma}),
\texttt{o2i1na} (e.g., \emph{boi-na}, \emph{coi-na}), and 
\texttt{pro1i1b} (e.g., \emph{pro-i-bir}).
After incorporating those rules, the number of incorrect and missing hyphenations, respectively,
will be: 0, 538 (\texttt{hyphenations6}); 21, 818 (\texttt{hyphenations5}); and 0, 33 (\texttt{hyphenations4}).

% novas regras para incluir: 1çô, 1xô, a1â, a1ã, a1ô, cu2i, cu3in, e1ô, .ne4o, o1ã, o1ê, o1im, o2i1na, pro1i1b, co2ima .
% resultado: 0, 538 (dic6); 21, 818 (dic5), 0, 33 (dic4)

%
% tu1i requer regra excessao: tu2it, tu2id
% co2ima : regra para coima e escoimar

% ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts10 > /tmp/hyphenations6result_010.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations6result_010.dic
% correct: 15303; wrong: 0 (); missing: 538 (538)
%
% ./gocreateresultfile.sh ../data/hyphenations5.dic /tmp/patts10 > /tmp/hyphenations5result_010.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations5result_010.dic
% correct: 14813; wrong: 21 (21); missing: 818 (813,5)
%
% ./gocreateresultfile.sh ../data/hyphenations4.dic /tmp/patts10 > /tmp/hyphenations4result_010.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations4result_010.dic
% correct: 964; wrong: 0 (); missing: 33 (33)

% hyphenations6result_008.dic: correct: 15287; wrong: 16 (16); missing: 539 (539)
% hyphenations5result_008.dic: correct: 14813; wrong: 21 (21); missing: 818 (815,3)
% hyphenations4result_008.dic: correct: 968; wrong: 0 (); missing: 29 (29)

% hyphenations6result_009.dic: correct: 15287; wrong: 16 (16); missing: 539 (539)
% hyphenations5result_009.dic: correct: 14822; wrong: 21 (21); missing: 809 (806,3)
% hyphenations4result_009.dic: correct: 968; wrong: 0 (); missing: 29 (29)

% hyphenations6result_010.dic: correct: 15303; wrong: 0 (); missing: 538 (538)
% hyphenations5result_010.dic: correct: 14813; wrong: 21 (21); missing: 818 (813,5)
% hyphenations4result_010.dic: correct: 964; wrong: 0 (); missing: 33 (33)

% e1in1c, e1in1f, e1in1g, e1in1s, e1in1t, e1in1v, e1in2sc, e1in2st
% $ grep "einv" ../data/hyphenations.csv | cut -d, -f1 | while read -r word; do ./gohyphen /tmp/patts9 $word; done | column

% rules to include:
% 1çô : ma-çô-ni-co, pa-çô
% u1é : su-é-cia, jo-su-é, su-é-ter, an-tu-ér-pia
%  exception rules: 1gu2é, 1qu2é
% 1xô : sa-xô-nia, a-xô-nio, ta-xô-no-mo
% a1â : a-bra-â-mi-co
% a1ã : a-bra-ão, ca-na-ã
% a1ô : fa-ra-ô-ni-co

% rules we could import from patch.TeX.pt-br.patterns (?)
% cu2i, tu2i1t, o2i1na
%
% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, u3é, 1gu4é, 1qu4é, tu1i, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç, cu2i, tu2i1t, o2i1na" | tr -d ' ' | tr ',' '\n') > /tmp/patts9
% ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts9 > /tmp/hyphenations6result_009.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations6result_009.dic
% correct: 15302; wrong: 0 (); missing: 539 (539) 
% ./gocreateresultfile.sh ../data/hyphenations5.dic /tmp/patts9 > /tmp/hyphenations5result_009.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations5result_009.dic
% correct: 14808; wrong: 21 (21); missing: 823 (820,3)
% ./gocreateresultfile.sh ../data/hyphenations4.dic /tmp/patts9 > /tmp/hyphenations4result_009.dic
% ./resultfilemetrics.sh -f /tmp/hyphenations4result_009.dic
% correct: 968; wrong: 0 (); missing: 29 (29)
%
% from thoses missing in hyphenations6result_009.dic, only 5 are not apparent proparoxytone: 
% pa-ul
% qui*lo-watt
% pa-in*ço
% pi*xa-im
% ben*jo-im

% 1çô
% 1flu2íd
% 1gu2é
% 1gu2ê
% 1qu2é
% 1qu2ê
% 1qu4â
% 1qu4ó
% 1xô
% a1â
% a1ã
% a1ô
% au1i1c
% bu1i1n
% bu1i2n1d
% bu1i2n1t
% cu1i1n
% * cu2i
% cu3i1da1de
% dru2i
% du1i1c
% e1in1c
% e1in1f
% e1in1g
% e1in1s
% e1in1t
% e1in1v
% e1in2sc
% e1in2st
% e1ô
% é3o
% flu2id
% fu1i1n
% .g2nô
% i1un
% i1ur
% .ne4o
% nu1i1n
% o1ã
% o1ê
% o1i1nh
% o1im
% * o2i1na
% p1p
% p2si
% p2sí
% p3sia
% p3sin
% pro1i1b
% ru1i1na
% ru1i1no
% su1i1ti
% su3b4li1ma
% su3b4li1me
% su3b4li1mid
% su3b4li1nh
% .t2
% tu1i1ti
% u1é
% u1ê
% u1i1d
% u1iz
% z1z
% z2z.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{10ex}
%%%%%%%%%%%%%
%Let us remember that the standard \TeX{} hyphenation rules, proposed by
%\textcite{rezende1987,hyphpt}, when tested against a set of \num{\DictionarySize}
%words, present 1,368 (????) errors, of which 1,273 (????) correspond to places
%where the hyphenation was not carried out and 125 (????) to erroneous markings.
%Faced with the errors made by the standard hyphenator, a set of \num{\NumberOfNewRules} rules were
%established, which reduced the errors to 132 (???), with 118 (????) places
%where the hyphenation was not marked and 35 (????) where there was erroneous
%marking. Such rules are presented and exemplified below, as well as the
%necessary exception rules and an example in which the application of the rule
%is demonstrated.
%
%
%

% get the error rate from default TeX rules in this dic file
% ./checkhyphenation.sh correct test
% ./gocreateresultfile.sh ../data/hyphenations6.dic ../data/default.TeX.pt-br.patterns > ../data/hyphenations6result-default-patterns.dic
% grep -v "[\.\-]" ../data/hyphenations6result-default-patterns.dic | wc -l
% 15536
% NumberOfCorrectSix NumberOfWrongSix NumberOfMissingSix
% correct: 15536; wrong: 30 (30); missing: 277 (276,1)
%
%
%Using the default \TeX{} hyphenation rules we have found \NumberOfCorrectSix{}
%words correctly hyphenated, \NumberOfWrongSix{} words with wrong hyphenation
%points introduced by the default rules, and \NumberOfMissingSix{} words with at
%least a missing hyphenation point (among those words only \texttt{ba-í-a} had
%two missing hyphenation points).

% cat ../data/default.TeX.pt-br.patterns ../data/patch.TeX.pt-br.patterns > ../data/patched-default.TeX.pt-br.patterns
% ./gocreateresultfile.sh ../data/hyphenations6.dic ../data/patched-default.TeX.pt-br.patterns > ../data/hyphenations6result-patched-patterns.dic
% ./resultfilemetrics.sh -f ../data/hyphenations6result-patched-patterns.dic -a
% correct: 15826; wrong: 2 (2); missing: 13 (13)

### 2024-06-06 article/writingsystems.tex
updates

\section{Writing systems}\label{sec-writing-systems}

There is a diverse collection of writing systems, categorized into logographic,
syllabic, and alphabetic systems. Although distinct, these systems can be built
on an interplay of these categories \parencite{coulmas2003,palmer2010}. 
The principles guiding an alphabetic or phonemic writing system vary significantly 
based on the language and its history. Here are some key points worth highlighting:
\begin{enumerate}[label=\arabic*)]
    \item The most common principle involves representing the sounds of a
	language with written symbols, using one or a combination of symbols to
	represent each sound (e.g., the orthographic system of Portuguese uses
	an alphabet of 27 letters to represent different sounds of the
	language).
    \item Etymology also plays a crucial role, where the spelling of a word
	reflects its origins and historical development (e.g., the French
	language often reflects the Latin roots of words in its spelling).
    \item Morphology serves as a guide in structuring many languages, using
	specific letters or symbols to indicate word endings, prefixes, or
	suffixes (e.g., Russian uses different forms of the Cyrillic alphabet
	to indicate gender and case in its nouns).
    \item The evolution of a language over time also contributes to its written
	form (e.g., the spelling of many English words has changed over time to
	reflect changes in pronunciation).
\end{enumerate}
Orthographic systems for languages with logographic writing systems, such as
Chinese ideograms, cuneiform writing, and Egyptian hieroglyphs, differ
significantly from alphabetic writing systems. In logographic systems,
individual symbols or characters represent entire words or ideas, rather than
phonemes or sounds. As a result, the principles guiding their orthographic
systems are based more on semantic and visual principles than on phonemic
principles.
Hyphenation is a feature of alphabetic scripts where words are composed of letters, 
and spaces or hyphens are used to separate words, syllables, or parts of words. 
Logographic writing systems, such as the Chinese, 
function differently and do not employ hyphenation \parencite{honorof2006}.

### 2024-06-14 article/appendix-table.tex
updates

% 
% #./createresulttable.sh --vowel | sort > ../article/comparedresults-appprop.tex
% #./removeduplicatedlines.sh ../article/comparedresults-appprop.tex
% 
% ./createresulttable2.sh > ../article/comparedresults.tex
% grep -v "[\.\-][aeiouáéíóúâêôãõ] " ../article/comparedresults.tex > ../article/comparedresults_nofinalvowel.tex
% # here is how to update the counts
% awk -F '&' '{print $2}' ../article/comparedresults_nofinalvowel.tex | grep -o '\\cmark' | wc -l
% awk -F '&' '{print $3}' ../article/comparedresults_nofinalvowel.tex | grep -o '\\cmark' | wc -l
\begin{small}
\begin{longtable}{l l l}
    \caption{Comparison of hyphenation results in a sample of words using the default rules and the proposed patched rules. In this sample we select cases where there are incorrect hyphenations from either set of rules and we are discarding those cases with incorrect hyphenation before a final vowel.}\label{tab-resultados}\\
\hline
word & defult rule result & patched rules result \\
\hline
\endfirsthead
\hline
word & defult rule result & patched rules result \\
\hline
\endhead
\input{comparedresults_nofinalvowel.tex}
\end{longtable}
\end{small}

### 2024-06-14 article/article.tex
updates

@@
 
+% Define a new counter for the custom list of rules
+\newcounter{numberRulesGroups}
 % Define a new list environment for rules
 \newlist{rules}{enumerate}{1}
-\setlist[rules,1]{label=\arabic*}
+\setlist[rules,1]{label=\arabic*, ref=\arabic*, before=\setcounter{numberRulesGroups}{0}}
 
@@
   \phantomsection
-  \edef\@currentlabel{#1}%
+  \edef\@currentlabel{#1\unskip}%
   %\edef\@currentlabelname{#1}%
@@
 \input{patgenrules.tex}
+\input{hyphenpatches.tex}
+\input{conclusion.tex}
 
-\section{Comparing the set of rules} 
-Let us remember that the standard \TeX{} hyphenation rules, proposed by
-\textcite{hyphpt}, amount to XXX errors, in a set of XXXX words.  Among those, XXX
-correspond to places where the hyphenation was not carried out and XXX to
-mismarkings. Faced with the errors made by the standard hyphenator, a set of
-\num{\NumberOfNewRules} rules were established, which reduced the errors to XXXX,
-with XXXX unmarked hyphenation places and XXX mismarkings.  Such rules are
-presented and exemplified below, as well as the necessary exception rules and
-an example in which the application of the rule is demonstrated.
+%\section{Comparing the set of rules} 
+%Let us remember that the standard \TeX{} hyphenation rules, proposed by
+%\textcite{hyphpt}, amount to XXX errors, in a set of XXXX words.  Among those, XXX
+%correspond to places where the hyphenation was not carried out and XXX to
+%mismarkings. Faced with the errors made by the standard hyphenator, a set of
+%\num{\NumberOfNewRules} rules were established, which reduced the errors to XXXX,
+%with XXXX unmarked hyphenation places and XXX mismarkings.  Such rules are
+%presented and exemplified below, as well as the necessary exception rules and
+%an example in which the application of the rule is demonstrated.
 
-\section{Universal syllabic pattern generation}
-Universal syllabic pattern generation by Jakub Máca, Petr Sojka, Ondřej Sojka (TUG 2023).
+%\section{Universal syllabic pattern generation}
+%Universal syllabic pattern generation by Jakub Máca, Petr Sojka, Ondřej Sojka (TUG 2023).
 
-% ==== OLD TEXT ====
-\section{Hyphenation rule patches}\label{sec-hyph-rpatches}
-OLD TEST
-
-OLD TEST
-
-Foi criado um conjunto de \num{\NumberOfNewRules} regras para aprimorar as hifenizações no
-português. Analisando um conjunto de \num{37798} palavras, as regras padrão apresentam
-1368 erros (1273 pontos de hifenização não marcados e 125 pontos marcados
-erroneamente)\footnote{A soma não é 1368 pois temos 30 casos em que os dois
-tipos de erros ocorrem.}, enquanto as novas regras apresentaram 132 erros (118
-pontos de hifenização não marcados e 35 pontos marcados
-erroneamente)\footnote{35 palavras apresentam ambos tipos de erro.}.
-%%% <<< fazer correção após correção manual das hifenizações tidas como corretas.
-
-Foi criado um conjunto de 37798 palavras obtidas do corpus
-\href{https://www.linguateca.pt/cetenfolha/index_info.html}{CETENFolha},
-juntamente com palavras do \href{https://www.palavras.net/}{Palavras NET} e
-algumas palavras do corpus baseado na
-\href{https://pt.wikipedia.org}{Wikipedia}. 
-Foram mantidas apenas as palavras
-para as quais encontrou-se a hifenização nos seguintes dicionários online:
-\href{https://michaelis.uol.com.br/}{Michaelis},
-\href{https://dicionario.priberam.org/}{Priberam},
-\href{https://pt.wiktionary.org}{Wikcionário},
-\href{https://aulete.com.br/}{Aulete},
-\href{http://www.portaldalinguaportuguesa.org/}{Portal da Língua Portuguesa} e
-\href{https://www.dicio.com.br/}{Dicio}.
-Adotamos como hifenização `correta' aquela que ao menos 4 dicionários
-concordavam. Algumas hifenizações foram realizadas manualmente pelo autor.
-Considerando a frequência de ocorrência das palavras nos corpus, o conjuto de
-palavras escolhido representa 55\% do total das ocorrências relativo ao
-Wikipedia e 58\% em relação ao CETENFolha.
-% Corpus Wikipedia
+%% ==== OLD TEXT ====
+%\section{Hyphenation rule patches}\label{sec-hyph-rpatches}
+%OLD TEST
 %
-% 166341424 / 302226482 = 0.55
+%OLD TEST
 %
-% soma da freq. de occ. das palavras utilizadas
-% cat portuguese_4_utf8.dic portuguese_extra_utf8.dic | tr -d '-' | while read -r word; do grep "[0-9]\+ ${word}$" /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | head -n 1 | tr -dc '0-9\n'; done | paste -s -d+ - | bc
-% = 166341424
+%Foi criado um conjunto de \num{\NumberOfNewRules} regras para aprimorar as hifenizações no
+%português. Analisando um conjunto de \num{37798} palavras, as regras padrão apresentam
+%1368 erros (1273 pontos de hifenização não marcados e 125 pontos marcados
+%erroneamente)\footnote{A soma não é 1368 pois temos 30 casos em que os dois
+%tipos de erros ocorrem.}, enquanto as novas regras apresentaram 132 erros (118
+%pontos de hifenização não marcados e 35 pontos marcados
+%erroneamente)\footnote{35 palavras apresentam ambos tipos de erro.}.
+%%%% <<< fazer correção após correção manual das hifenizações tidas como corretas.
 %
-% soma da freq. de occ. de todas palavras no corpus
-% cat /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | tr -dc '0-9\n' | paste -s -d+ - | bc
-% = 302226482
+%Foi criado um conjunto de 37798 palavras obtidas do corpus
+%\href{https://www.linguateca.pt/cetenfolha/index_info.html}{CETENFolha},
+%juntamente com palavras do \href{https://www.palavras.net/}{Palavras NET} e
+%algumas palavras do corpus baseado na
+%\href{https://pt.wikipedia.org}{Wikipedia}. 
+%Foram mantidas apenas as palavras
+%para as quais encontrou-se a hifenização nos seguintes dicionários online:
+%\href{https://michaelis.uol.com.br/}{Michaelis},
+%\href{https://dicionario.priberam.org/}{Priberam},
+%\href{https://pt.wiktionary.org}{Wikcionário},
+%\href{https://aulete.com.br/}{Aulete},
+%\href{http://www.portaldalinguaportuguesa.org/}{Portal da Língua Portuguesa} e
+%\href{https://www.dicio.com.br/}{Dicio}.
+%Adotamos como hifenização `correta' aquela que ao menos 4 dicionários
+%concordavam. Algumas hifenizações foram realizadas manualmente pelo autor.
+%Considerando a frequência de ocorrência das palavras nos corpus, o conjuto de
+%palavras escolhido representa 55\% do total das ocorrências relativo ao
+%Wikipedia e 58\% em relação ao CETENFolha.
+%% Corpus Wikipedia
+%%
+%% 166341424 / 302226482 = 0.55
+%% 
+%% soma da freq. de occ. das palavras utilizadas
+%% cat portuguese_4_utf8.dic portuguese_extra_utf8.dic | tr -d '-' | while read -r word; do grep "[0-9]\+ ${word}$" /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | head -n 1 | tr -dc '0-9\n'; done | paste -s -d+ - | bc
+%% = 166341424
+%%
+%% soma da freq. de occ. de todas palavras no corpus
+%% cat /ms/downloads/samples/wikipedia/ptwiki-latest-pages-articles-multistream_wordlist.txt | tr -dc '0-9\n' | paste -s -d+ - | bc
+%% = 302226482
+%%
+%% CETENFolha
+%% 13314084 / 22728804 = 0.5857
+%Este percentual é relativamente baixo, mas deve-se ao fato de que não obtivemos
+%sucesso em encontrar a hifenização de muitas palavras nos dicionários
+%analisados e também por não observarmos um consenso de ao menos 4 dicionários
+%com uma mesma hifenização.
 %
-% CETENFolha
-% 13314084 / 22728804 = 0.5857
-Este percentual é relativamente baixo, mas deve-se ao fato de que não obtivemos
-sucesso em encontrar a hifenização de muitas palavras nos dicionários
-analisados e também por não observarmos um consenso de ao menos 4 dicionários
-com uma mesma hifenização.
-
-Analisando os erros resultantes da hifenização utilizando as regras padrão do
-TeX, foram estabelecidas algumas regras como forma de abarcar um conjunto maior
-de palavras. Tais regras são elencadas a seguir, expondo também as regras de
-exceção necessárias e um exemplo onde a regra será utilizada.
-
-\begin{rules}
-\item\label{rulegrp_psi} regra: \texttt{.p2si}, \texttt{.p2sí} -- psicologia, psíquico % update (word-initial pattern, exception not necessary (?)) 
-%\item\label{rulegrp_psi} regra: \texttt{p2si}, \texttt{p2sí} -- psicologia, psíquico\\
-%exceção: \texttt{p3sia}, \texttt{p3sin} -- epilepsia, rodopsina
-
-\item\label{rulegrp_tc} regra: \texttt{t2c} -- tchau%, tcheco
-
-\item\label{rulegrp_pneu} regra: \texttt{p2neu} -- pneumonia
-
-\item\label{rulegrp_gno} regra: \texttt{.g2no}, \texttt{.g2nó} -- gnomo, gnóstico
-
-\item\label{rulegrp_pt} regra: \texttt{.p2t} -- ptose%, pterossauro
-
-\item\label{rulegrp_tm} regra: \texttt{.t2m} -- tmese % [new rule] needs to be incorporated and checked
-
-\item\label{rulegrp_cza} regra: \texttt{c2za} -- czar
-
-\item\label{rulegrp_s2} regra: \texttt{.s2} -- stalinismo
-
-\item\label{rulegrp_t2} regra: \texttt{.t2} -- tsunami
-
-\item\label{rulegrp_mn} regra: \texttt{.m2n} -- mnemônico
-
-\item\label{rulegrp_zz} regra: \texttt{z1z}, \texttt{p1p}, \texttt{z2z.} -- pizza, shopping, jazz
-
-\item\label{rulegrp_sub} regra: \texttt{su2b3r}, \texttt{su2b3l} -- sublunar, subrotina \\
-exceção: \texttt{.su3b4li}
-%exceção: \texttt{su3b4li1nh}, \texttt{su3b4li1ma}, \texttt{su3b4li1me}, \texttt{su3b4li1mid} -- sublinhar, sublimar, sublime, sublimidade
-
-\item\label{rulegrp_so} regra: \texttt{1sô} -- subsônico
-
-\item\label{rulegrp_pseu} regra: \texttt{1p2seu1d} -- pseudônimo
-
-%\item\label{rulegrp_ein} regra: \texttt{e1in1c}, \texttt{e1in1f}, \texttt{e1in1g}, \texttt{e1in1s}, \texttt{e1in1t}, \texttt{e1in1v} -- reincidência, reinfecção, reingressa, reinserção, reintegração, reinventar \\
-%exceção: \texttt{e1in2st}, \texttt{e1in2sc} -- reinstalado, reinscrever
-
-\item\label{rulegrp_ein} regra: \texttt{e1inc}, \texttt{e1inf}, \texttt{e1ing}, \texttt{e1ins}, \texttt{e1int}, \texttt{e1inv} -- reincidência, reinfecção, reingressa, reinserção, reintegração, reinventar \\
-% exceção: \texttt{e1in2st}, \texttt{e1in2sc} -- reinstalado, reinscrever
-
-\item\label{rulegrp_unit} regra: \texttt{u1int}, \texttt{u1ind} -- contribuinte, excluindo
-
-\item\label{rulegrp_oin} regra: \texttt{o1in} -- coincidência, agroindustrial, bioinformática, amendoins, gastrointestinal
-exceção: \texttt{o1ina} -- boina
-
-\item\label{rulegrp_eim} regra: \texttt{e1imp} -- reimpresso%, coimbra, coimperador
-%exceção: \texttt{que2i}, \texttt{te2im} -- queimar, queimadura, teimosia, tirateima
-
-\item\label{rulegrp_aa} regra: \texttt{a1â}, \texttt{a1ã}, \texttt{a1é}, \texttt{a1í}, \texttt{a1ó}, \texttt{a1ô}, \texttt{a1ú}, \texttt{e1á}, \texttt{e1â}, \texttt{e1ã}, \texttt{e1é}, \texttt{e1ê}, \texttt{e1í}, \texttt{e1ó}, \texttt{e1ô}, \texttt{e1ú}, \texttt{é1o}, \texttt{i1á}, \texttt{i1ã}, \texttt{i1é}, \texttt{i1í}, \texttt{i1ó}, \texttt{i1u}, \texttt{i1ú}, \texttt{í1a}, \texttt{o1á}, \texttt{o1ã}, \texttt{o1é}, \texttt{o1ê}, \texttt{o1í}, \texttt{o1ó}, \texttt{u1á}, \texttt{u1ã}, \texttt{u1é}, \texttt{u1ê}, \texttt{u1í}, \texttt{ú1o} --  abraâmico, abraão, aéreo, país, caótico, faraônico, saúde, balneário, oceânico, campeã, feérico, veêm, veículo, teórico, napoleônico, conteúdo, néon, diário, região, soviético, iídiche, periódico, feiura, viúva, maníaco, razoável, joão, poético, boêmia, heroísmo, alcoólico, usuário, itapuã, suécia, cauê, suíça, flúor \\
-exceção: \texttt{1gu2é}, \texttt{1gu2ê}, \texttt{1gu2í}, \texttt{1qu2á}, \texttt{1qu2é}, \texttt{1qu2ê}, \texttt{1qu2í} -- alguém, português, linguística, aquático, inquérito, sequência, química
-% the inclusion of rules e1é, é1o, i1í and í1a cause problem and if exceptions are necessary
-
-\item\label{rulegrp_gua} regra: \texttt{1gu4á}, \texttt{1gu4ã}, \texttt{1qu4ã} -- jaraguá, saguão, quão
-
-\item\label{rulegrp_air} regra: \texttt{a1ir.}, \texttt{u1ir.} -- sair, diminuir
-
-\item\label{rulegrp_aiz} regra: \texttt{u1iz.}, \texttt{a1iz.} -- juiz, raiz
-
-\item\label{rulegrp_ia} regra: \texttt{í1a} -- baía
-
-\item\label{rulegrp_ain} regra: \texttt{a1ind}, \texttt{a1i1nh} -- ainda, rainha
-
-\item\label{rulegrp_oin} regra: \texttt{o1i1nh} -- moinho
-
-\item\label{rulegrp_aui} regra: \texttt{au1i1c}, \texttt{du1i1c}, \texttt{u1i1ç}, \texttt{u1i1d}, \texttt{cu2i}, \texttt{dru2i}, \texttt{flu2id}, \texttt{bu1i1n}, \texttt{cu1i1n}, \texttt{fu1i1n}, \texttt{nu1i1n}, \texttt{ru1i1na}, \texttt{ru1i1no}, \texttt{su1i1ti}, \texttt{tu1i1ti}, \texttt{u1iz} -- cacauicultor, sanduicheira, constituição, continuidade, cuidador, druida, fluido, tabuinha, picuinha, fuinha, genuinamente, arruinado, arruinou, jesuitismo, intuitivo, juizado \\
-exceção: \texttt{cu3i1da1de}, \texttt{bu1i2n1d}, \texttt{bu1i2n1t}  -- acuidade, contribuindo, contribuinte
-
-\item\label{rulegrp_iur} regra: \texttt{i1ur} -- diurno
-
-\item\label{rulegrp_io} regra: \texttt{í1o} -- íon
-
-\item\label{rulegrp_uo} regra: \texttt{ú1o} -- flúor
-
-\item\label{rulegrp_proi} regra: \texttt{pro1i1b} -- proibição
-
-\item\label{rulegrp_iun} regra: \texttt{i1un} -- triunfar
-
-\item\label{rulegrp_quo} regra: \texttt{1qu4ó}, \texttt{1qu4â} -- quórum, equânime
-
-\item\label{rulegrp_eo} regra: \texttt{é3o} -- alvéolo
-
-\item\label{rulegrp_ia} \st{regra: \texttt{i4a.}, \texttt{i4e.}, \texttt{i4o.}, \texttt{o4a.}, \texttt{u4a.} -- economia, espécie, vazio, destoa, institua}
-
-%\item\label{rulegrp_lo} regra: \texttt{1lô} -- camelô
-
-%\item\label{rulegrp_co} regra: \texttt{1cô} -- recôncavo
-
-\item\label{rulegrp_bo} regra: \texttt{1bô}, \texttt{1cô}, \texttt{1dô}, \texttt{1fô}, \texttt{1gô}, \texttt{1lô}, \texttt{1pô}, \texttt{1mô}, \texttt{1nô}, \texttt{1rô}, \texttt{1tô}, \texttt{1vô}, \texttt{1xô}, \texttt{1zô} -- robô, recôncavo, judô, telefônica, xangô, camelô, capô, sumô, econômico, tarô, chatô, vovô, saxônia, amazônia
-
-\item\label{rulegrp_cco} regra: \texttt{1çô} -- maçônico
-
-% As sequências gráficas ia, ie, io, oa, ua quando em posição
-% final átona, que são normalmente pronunciadas como ditongos
-% crescentes, mas que podem corresponder foneticamente a duas
-% vogais (hiato), sobretudo quando pronunciadas pausadamente:
-% vitó-ria, espé-cie, exercí-cio, nó-doa, lé-gua, tê-nue, ambí-guo.
-    \setcounter{numberRulesGroups}{\value{enumi}}
-\end{rules}
-
-The \NumberOfNewRules{} rules were grouped above in a list of
-\arabic{numberRulesGroups} types of rules. They may be further organized into four
-large groups. The first, which comprises rules \ref{rulegrp_psi} to
-\ref{rulegrp_zz}, includes consonant clusters such as \emph{czar}, \emph{ptose}
-and \emph{gnomo}. They, unlike the examples that will be exposed in section
-\ref{secxxx} (exceptions - item 9 currently), present a set of derived words,
-which makes their marking advantageous in view of the number of cases that are
-included in this marking rule. The second group, comprising rules
-\ref{rulegrp_sub} to \ref{rulegrp_eim}, delimits the morphological boundary
-between prefixes and radicals. As noted, although phonological issues guide the
-separation of numerous words in Portuguese, there are also those that are
-guided by morphology. This is the case of words that have the prefixes
-\emph{sub-} and \emph{re-}, such as \emph{sublunar} and \emph{reinserção}. The
-third group, comprising rules \ref{rulegrp_aa} to \ref{rulegrp_ia}, seeks to
-understand a set of words that have vowel combinations that do not follow the
-general rules. This is because the Portuguese language has vowel encounters
-with the second vowel graphically marked that can be separated, forming
-hiatuses, such as \emph{caótico}, \emph{balneário} and \emph{razoável}, while
-there are also words with a similar structure that constitute a diphthong, such
-as \emph{português}, \emph{alguém} and \emph{linguística}. It is remarkable, of
-course, that the latter are formed by the digraphs \emph{qu-} and \emph{gu-},
-while the former by vowels other than \emph{i} and \emph{u}. The fourth and
-last group, in turn, which comprises rules \ref{rulegrp_lo} to
-\ref{rulegrp_cco}, which are counterparts of rules that were already in the
-default rules, but did not contemplate the cases with certain accents. They
-were then added to encompass words such as \emph{camelô}, \emph{recôncavo},
-\emph{amazônia}, and \emph{maçônico}.
-
-It is important to highlight that the words included in these rules are, in general, of low frequency and were incorporated into the Portuguese language without a phonotactic adaptation, which causes these idiosyncrasies and exceptions to the language.
+%Analisando os erros resultantes da hifenização utilizando as regras padrão do
+%TeX, foram estabelecidas algumas regras como forma de abarcar um conjunto maior
+%de palavras. Tais regras são elencadas a seguir, expondo também as regras de
+%exceção necessárias e um exemplo onde a regra será utilizada.
+%
+%\begin{rules}
+%\item\label{rulegrp_psi} regra: \texttt{.p2si}, \texttt{.p2sí} -- psicologia, psíquico % update (word-initial pattern, exception not necessary (?)) 
+%%\item\label{rulegrp_psi} regra: \texttt{p2si}, \texttt{p2sí} -- psicologia, psíquico\\
+%%exceção: \texttt{p3sia}, \texttt{p3sin} -- epilepsia, rodopsina
+%
+%\item\label{rulegrp_tc} regra: \texttt{t2c} -- tchau%, tcheco
+%
+%\item\label{rulegrp_pneu} regra: \texttt{p2neu} -- pneumonia
+%    
+%\item\label{rulegrp_gno} regra: \texttt{.g2no}, \texttt{.g2nó} -- gnomo, gnóstico
+%
+%\item\label{rulegrp_pt} regra: \texttt{.p2t} -- ptose%, pterossauro
+%
+%\item\label{rulegrp_tm} regra: \texttt{.t2m} -- tmese % [new rule] needs to be incorporated and checked
+%
+%\item\label{rulegrp_cza} regra: \texttt{c2za} -- czar
+%
+%\item\label{rulegrp_s2} regra: \texttt{.s2} -- stalinismo
+%
+%\item\label{rulegrp_t2} regra: \texttt{.t2} -- tsunami
+%
+%\item\label{rulegrp_mn} regra: \texttt{.m2n} -- mnemônico
+%
+%\item\label{rulegrp_zz} regra: \texttt{z1z}, \texttt{p1p}, \texttt{z2z.} -- pizza, shopping, jazz
+%
+%\item\label{rulegrp_sub} regra: \texttt{su2b3r}, \texttt{su2b3l} -- sublunar, subrotina \\
+%exceção: \texttt{.su3b4li}
+%%exceção: \texttt{su3b4li1nh}, \texttt{su3b4li1ma}, \texttt{su3b4li1me}, \texttt{su3b4li1mid} -- sublinhar, sublimar, sublime, sublimidade
+%
+%
+%\item\label{rulegrp_so} regra: \texttt{1sô} -- subsônico
+%
+%\item\label{rulegrp_pseu} regra: \texttt{1p2seu1d} -- pseudônimo
+%
+%%\item\label{rulegrp_ein} regra: \texttt{e1in1c}, \texttt{e1in1f}, \texttt{e1in1g}, \texttt{e1in1s}, \texttt{e1in1t}, \texttt{e1in1v} -- reincidência, reinfecção, reingressa, reinserção, reintegração, reinventar \\
+%%exceção: \texttt{e1in2st}, \texttt{e1in2sc} -- reinstalado, reinscrever
+%
+%\item\label{rulegrp_ein} regra: \texttt{e1inc}, \texttt{e1inf}, \texttt{e1ing}, \texttt{e1ins}, \texttt{e1int}, \texttt{e1inv} -- reincidência, reinfecção, reingressa, reinserção, reintegração, reinventar \\
+%% exceção: \texttt{e1in2st}, \texttt{e1in2sc} -- reinstalado, reinscrever
+%
+%\item\label{rulegrp_unit} regra: \texttt{u1int}, \texttt{u1ind} -- contribuinte, excluindo
+%
+%\item\label{rulegrp_oin} regra: \texttt{o1in} -- coincidência, agroindustrial, bioinformática, amendoins, gastrointestinal
+%exceção: \texttt{o1ina} -- boina
+%
+%\item\label{rulegrp_eim} regra: \texttt{e1imp} -- reimpresso%, coimbra, coimperador
+%%exceção: \texttt{que2i}, \texttt{te2im} -- queimar, queimadura, teimosia, tirateima
+%
+%\item\label{rulegrp_aa} regra: \texttt{a1â}, \texttt{a1ã}, \texttt{a1é}, \texttt{a1í}, \texttt{a1ó}, \texttt{a1ô}, \texttt{a1ú}, \texttt{e1á}, \texttt{e1â}, \texttt{e1ã}, \texttt{e1é}, \texttt{e1ê}, \texttt{e1í}, \texttt{e1ó}, \texttt{e1ô}, \texttt{e1ú}, \texttt{é1o}, \texttt{i1á}, \texttt{i1ã}, \texttt{i1é}, \texttt{i1í}, \texttt{i1ó}, \texttt{i1u}, \texttt{i1ú}, \texttt{í1a}, \texttt{o1á}, \texttt{o1ã}, \texttt{o1é}, \texttt{o1ê}, \texttt{o1í}, \texttt{o1ó}, \texttt{u1á}, \texttt{u1ã}, \texttt{u1é}, \texttt{u1ê}, \texttt{u1í}, \texttt{ú1o} --  abraâmico, abraão, aéreo, país, caótico, faraônico, saúde, balneário, oceânico, campeã, feérico, veêm, veículo, teórico, napoleônico, conteúdo, néon, diário, região, soviético, iídiche, periódico, feiura, viúva, maníaco, razoável, joão, poético, boêmia, heroísmo, alcoólico, usuário, itapuã, suécia, cauê, suíça, flúor \\
+%exceção: \texttt{1gu2é}, \texttt{1gu2ê}, \texttt{1gu2í}, \texttt{1qu2á}, \texttt{1qu2é}, \texttt{1qu2ê}, \texttt{1qu2í} -- alguém, português, linguística, aquático, inquérito, sequência, química
+%% the inclusion of rules e1é, é1o, i1í and í1a cause problem and if exceptions are necessary
+%
+%\item\label{rulegrp_gua} regra: \texttt{1gu4á}, \texttt{1gu4ã}, \texttt{1qu4ã} -- jaraguá, saguão, quão
+%
+%\item\label{rulegrp_air} regra: \texttt{a1ir.}, \texttt{u1ir.} -- sair, diminuir
+%
+%\item\label{rulegrp_aiz} regra: \texttt{u1iz.}, \texttt{a1iz.} -- juiz, raiz
+%
+%\item\label{rulegrp_ia} regra: \texttt{í1a} -- baía
+%
+%\item\label{rulegrp_ain} regra: \texttt{a1ind}, \texttt{a1i1nh} -- ainda, rainha
+%
+%\item\label{rulegrp_oin} regra: \texttt{o1i1nh} -- moinho
+%
+%\item\label{rulegrp_aui} regra: \texttt{au1i1c}, \texttt{du1i1c}, \texttt{u1i1ç}, \texttt{u1i1d}, \texttt{cu2i}, \texttt{dru2i}, \texttt{flu2id}, \texttt{bu1i1n}, \texttt{cu1i1n}, \texttt{fu1i1n}, \texttt{nu1i1n}, \texttt{ru1i1na}, \texttt{ru1i1no}, \texttt{su1i1ti}, \texttt{tu1i1ti}, \texttt{u1iz} -- cacauicultor, sanduicheira, constituição, continuidade, cuidador, druida, fluido, tabuinha, picuinha, fuinha, genuinamente, arruinado, arruinou, jesuitismo, intuitivo, juizado \\
+%exceção: \texttt{cu3i1da1de}, \texttt{bu1i2n1d}, \texttt{bu1i2n1t}  -- acuidade, contribuindo, contribuinte
+%
+%\item\label{rulegrp_iur} regra: \texttt{i1ur} -- diurno
+%
+%\item\label{rulegrp_io} regra: \texttt{í1o} -- íon
+%
+%\item\label{rulegrp_uo} regra: \texttt{ú1o} -- flúor
+%
+%\item\label{rulegrp_proi} regra: \texttt{pro1i1b} -- proibição
+%
+%\item\label{rulegrp_iun} regra: \texttt{i1un} -- triunfar
+%
+%\item\label{rulegrp_quo} regra: \texttt{1qu4ó}, \texttt{1qu4â} -- quórum, equânime
+%
+%\item\label{rulegrp_eo} regra: \texttt{é3o} -- alvéolo
+%
+%\item\label{rulegrp_ia} \st{regra: \texttt{i4a.}, \texttt{i4e.}, \texttt{i4o.}, \texttt{o4a.}, \texttt{u4a.} -- economia, espécie, vazio, destoa, institua}
+%
+%%\item\label{rulegrp_lo} regra: \texttt{1lô} -- camelô
+%
+%%\item\label{rulegrp_co} regra: \texttt{1cô} -- recôncavo
+%
+%\item\label{rulegrp_bo} regra: \texttt{1bô}, \texttt{1cô}, \texttt{1dô}, \texttt{1fô}, \texttt{1gô}, \texttt{1lô}, \texttt{1pô}, \texttt{1mô}, \texttt{1nô}, \texttt{1rô}, \texttt{1tô}, \texttt{1vô}, \texttt{1xô}, \texttt{1zô} -- robô, recôncavo, judô, telefônica, xangô, camelô, capô, sumô, econômico, tarô, chatô, vovô, saxônia, amazônia
+%
+%\item\label{rulegrp_cco} regra: \texttt{1çô} -- maçônico
+%
+%% As sequências gráficas ia, ie, io, oa, ua quando em posição
+%% final átona, que são normalmente pronunciadas como ditongos
+%% crescentes, mas que podem corresponder foneticamente a duas
+%% vogais (hiato), sobretudo quando pronunciadas pausadamente:
+%% vitó-ria, espé-cie, exercí-cio, nó-doa, lé-gua, tê-nue, ambí-guo.
+%    \setcounter{numberRulesGroups}{\value{enumi}}
+%\end{rules}
+%
+%The \NumberOfNewRules{} rules were grouped above in a list of
+%\arabic{numberRulesGroups} types of rules. They may be further organized into four
+%large groups. The first, which comprises rules \ref{rulegrp_psi} to
+%\ref{rulegrp_zz}, includes consonant clusters such as \emph{czar}, \emph{ptose}
+%and \emph{gnomo}. They, unlike the examples that will be exposed in section
+%\ref{secxxx} (exceptions - item 9 currently), present a set of derived words,
+%which makes their marking advantageous in view of the number of cases that are
+%included in this marking rule. The second group, comprising rules
+%\ref{rulegrp_sub} to \ref{rulegrp_eim}, delimits the morphological boundary
+%between prefixes and radicals. As noted, although phonological issues guide the
+%separation of numerous words in Portuguese, there are also those that are
+%guided by morphology. This is the case of words that have the prefixes
+%\emph{sub-} and \emph{re-}, such as \emph{sublunar} and \emph{reinserção}. The
+%third group, comprising rules \ref{rulegrp_aa} to \ref{rulegrp_ia}, seeks to
+%understand a set of words that have vowel combinations that do not follow the
+%general rules. This is because the Portuguese language has vowel encounters
+%with the second vowel graphically marked that can be separated, forming
+%hiatuses, such as \emph{caótico}, \emph{balneário} and \emph{razoável}, while
+%there are also words with a similar structure that constitute a diphthong, such
+%as \emph{português}, \emph{alguém} and \emph{linguística}. It is remarkable, of
+%course, that the latter are formed by the digraphs \emph{qu-} and \emph{gu-},
+%while the former by vowels other than \emph{i} and \emph{u}. The fourth and
+%last group, in turn, which comprises rules \ref{rulegrp_lo} to
+%\ref{rulegrp_cco}, which are counterparts of rules that were already in the
+%default rules, but did not contemplate the cases with certain accents. They
+%were then added to encompass words such as \emph{camelô}, \emph{recôncavo},
+%\emph{amazônia}, and \emph{maçônico}.
+%
+%It is important to highlight that the words included in these rules are, in general, of low frequency and were incorporated into the Portuguese language without a phonotactic adaptation, which causes these idiosyncrasies and exceptions to the language.
 They are characterized as marked cases, since it is not possible to defend that they reproduce a phonological pattern of the language because they are not productive, that is, they are not taken as an example and/or derive new words.
-
-O conjunto de \NumberOfNewRules{} regras é apresentado a seguir:
-\begin{multicols}{6}
-    \footnotesize
-    \verbatiminput{../data/patch.TeX.pt-br.patterns}
-\end{multicols}
-
-A Tabela \ref{tab-resultados} apresenta os erros cometidos no conjunto das
-37798 palavras analisadas. As palavras omitidas são aquelas que foram
-hifenizadas corretamente pelos dois conjuntos de regra. Utilizamos aqui a
-marcação adotada pelo \emph{Patgen}: \texttt{*} para indicar pontos de
-hifenização corretamente marcados, \texttt{.} para indicar pontos de hifenização
-marcados erroneamente e \texttt{-} para indicar pontos de hifenização não
-encontrados. Os pontos marcados erroneamente e aqueles não encontrados são
-considerados erros. Quando ocorre algum erro de hifenização, marcaremos a
-palavra com \xmark. Quando não houver erro algum, marcaremos a palavra com
-\cmark. Ao final, podemos verificar que as regras padrão apresentaram 1368 erros
-(3,62\%) e as novas regras 132 erros (0,35\%).
-
-\begin{longtable}{l l l}
-\caption{Comparativo dos erros cometidos pelos dois conjuntos de regras de
-hifenização.}\label{tab-resultados}\\
-    \hline
-    palavra & regras padrão & regras adicionais \\
-    \hline
-    \endhead
-    \input{comparedresults.tex}
-\end{longtable}
+%
+%
+%O conjunto de \NumberOfNewRules{} regras é apresentado a seguir:
+%\begin{multicols}{6}
+%    \footnotesize
+%    \verbatiminput{../data/patch.TeX.pt-br.patterns}
+%\end{multicols}
+%
+%A Tabela \ref{tab-resultados} apresenta os erros cometidos no conjunto das
+%37798 palavras analisadas. As palavras omitidas são aquelas que foram
+%hifenizadas corretamente pelos dois conjuntos de regra. Utilizamos aqui a
+%marcação adotada pelo \emph{Patgen}: \texttt{*} para indicar pontos de
+%hifenização corretamente marcados, \texttt{.} para indicar pontos de hifenização
+%marcados erroneamente e \texttt{-} para indicar pontos de hifenização não
+%encontrados. Os pontos marcados erroneamente e aqueles não encontrados são
+%considerados erros. Quando ocorre algum erro de hifenização, marcaremos a
+%palavra com \xmark. Quando não houver erro algum, marcaremos a palavra com
+%\cmark. Ao final, podemos verificar que as regras padrão apresentaram 1368 erros
+%(3,62\%) e as novas regras 132 erros (0,35\%).
+%
+%\begin{longtable}{l l l}
+%\caption{Comparativo dos erros cometidos pelos dois conjuntos de regras de
+%hifenização.}\label{tab-resultados}\\
+%    \hline
+%    palavra & regras padrão & regras adicionais \\
+%    \hline
+%    \endhead
+%    \input{comparedresults.tex}
+%\end{longtable}
+%
 
@@
 
+\appendix
+\section{Hyphenation results}
+\input{appendix-table.tex}
+
 \end{document}

### 2024-06-14 article/comparedresults-appprop.tex
updates

--- 2023-04-11 article/comparedresults.tex
@@
-ainda & a-in*da \xmark & a*in*da \cmark \\
-país & pa-ís \xmark & pa*ís \cmark \\
-região & re*gi-ão \xmark & re*gi*ão \cmark \\
-saúde & sa-ú*de \xmark & sa*ú*de \cmark \\
-período & pe*rí-o*do \xmark & pe*rí*o*do \cmark \\
-juiz & ju-iz \xmark & ju*iz \cmark \\
-união & u*ni-ão \xmark & u*ni*ão \cmark \\
-econômico & e*co-nô*mi*co \xmark & e*co*nô*mi*co \cmark \\
-aí & a-í \xmark & a*í \cmark \\
-sair & sa-ir \xmark & sa*ir \cmark \\
-opinião & o*pi*ni-ão \xmark & o*pi*ni*ão \cmark \\
-constituição & cons*ti*tu-i*ção \xmark & cons*ti*tu*i*ção \cmark \\
-saída & sa-í*da \xmark & sa*í*da \cmark \\
-luís & lu-ís \xmark & lu*ís \cmark \\
-campeão & cam*pe-ão \xmark & cam*pe*ão \cmark \\
-aliás & a*li-ás \xmark & a*li*ás \cmark \\
-distribuição & dis*tri*bu-i*ção \xmark & dis*tri*bu*i*ção \cmark \\
-avião & a*vi-ão \xmark & a*vi*ão \cmark \\
-diário & di-á*ri*o \xmark & di*á*ri*o \cmark \\
-diária & di-á*ri*a \xmark & di*á*ri*a \cmark \\
-daí & da-í \xmark & da*í \cmark \\
-cair & ca-ir \xmark & ca*ir \cmark \\
-paraíba & pa*ra-í*ba \xmark & pa*ra*í*ba \cmark \\
-prejuízo & pre*ju-í*zo \xmark & pre*ju*í*zo \cmark \\
-judiciário & ju*di*ci-á*ri*o \xmark & ju*di*ci*á*ri*o \cmark \\
-suíça & su-í*ça \xmark & su*í*ça \cmark \\
-influência & in*flu-ên*ci*a \xmark & in*flu*ên*ci*a \cmark \\
-depoimento & de*po-i*men*to \xmark & de*po-i*men*to \xmark \\
-instituição & ins*ti*tu-i*ção \xmark & ins*ti*tu*i*ção \cmark \\
-consequência & con*se-quên*ci*a \xmark & con*se*quên*ci*a \cmark \\
-usuário & u*su-á*ri*o \xmark & u*su*á*ri*o \cmark \\
-contribuição & con*tri*bu-i*ção \xmark & con*tri*bu*i*ção \cmark \\
-diminuir & di*mi*nu-ir \xmark & di*mi*nu*ir \cmark \\
-fenômeno & fe-nô*me*no \xmark & fe*nô*me*no \cmark \\
-ruim & ru-im \xmark & ru-im \xmark \\
-construir & cons*tru-ir \xmark & cons*tru*ir \cmark \\
-veículo & ve-í*cu*lo \xmark & ve*í*cu*lo \cmark \\
-cocaína & co*ca-í*na \xmark & co*ca*í*na \cmark \\
-paul & pa-ul \xmark & pa-ul \xmark \\
-reunir & re-u*nir \xmark & re-u*nir \xmark \\
-continuidade & con*ti*nu-i*da*de \xmark & con*ti*nu*i*da*de \cmark \\
-diálogo & di-á*lo*go \xmark & di*á*lo*go \cmark \\
-atrair & a*tra-ir \xmark & a*tra*ir \cmark \\
-ocasião & o*ca*si-ão \xmark & o*ca*si*ão \cmark \\
-sebastião & se*bas*ti-ão \xmark & se*bas*ti*ão \cmark \\
-sequência & se-quên*ci*a \xmark & se*quên*ci*a \cmark \\
-substituir & subs*ti*tu-ir \xmark & subs*ti*tu*ir \cmark \\
-incluir & in*clu-ir \xmark & in*clu*ir \cmark \\
-gaúcho & ga-ú*cho \xmark & ga*ú*cho \cmark \\
-poluição & po*lu-i*ção \xmark & po*lu*i*ção \cmark \\
-proibido & pro-i*bi*do \xmark & pro*i*bi*do \cmark \\
-rainha & ra-i*nha \xmark & ra*i*nha \cmark \\
-religião & re*li*gi-ão \xmark & re*li*gi*ão \cmark \\
-paraíso & pa*ra-í*so \xmark & pa*ra*í*so \cmark \\
-frequência & fre-quên*ci*a \xmark & fre*quên*ci*a \cmark \\
-distribuir & dis*tri*bu-ir \xmark & dis*tri*bu*ir \cmark \\
-substituição & subs*ti*tu-i*ção \xmark & subs*ti*tu*i*ção \cmark \\
-contribuinte & con*tri*bu-in*te \xmark & con*tri*bu*in*te \cmark \\
-conteúdo & con*te-ú*do \xmark & con*te*ú*do \cmark \\
-leão & le-ão \xmark & le*ão \cmark \\
-concluir & con*clu-ir \xmark & con*clu*ir \cmark \\
-proibição & pro-i*bi*ção \xmark & pro*i*bi*ção \cmark \\
-sociólogo & so*ci-ó*lo*go \xmark & so*ci*ó*lo*go \cmark \\
-construído & cons*tru-í*do \xmark & cons*tru*í*do \cmark \\
-maceió & ma*cei-ó \xmark & ma*cei*ó \cmark \\
-diminuição & di*mi*nu-i*ção \xmark & di*mi*nu*i*ção \cmark \\
-crediário & cre*di-á*ri*o \xmark & cre*di*á*ri*o \cmark \\
-pivô & pi-vô \xmark & pi*vô \cmark \\
-substituído & subs*ti*tu-í*do \xmark & subs*ti*tu*í*do \cmark \\
-razoável & ra*zo-á*vel \xmark & ra*zo*á*vel \cmark \\
-juíza & ju-í*za \xmark & ju*í*za \cmark \\
-coincidência & co-in*ci*dên*ci*a \xmark & co*in*ci*dên*ci*a \cmark \\
-rebelião & re*be*li-ão \xmark & re*be*li*ão \cmark \\
-noticiário & no*ti*ci-á*ri*o \xmark & no*ti*ci*á*ri*o \cmark \\
-olimpíada & o*lim*pí-a*da \xmark & o*lim*pí*a*da \cmark \\
-imobiliário & i*mo*bi*li-á*ri*o \xmark & i*mo*bi*li*á*ri*o \cmark \\
-austríaco & aus*trí-a*co \xmark & aus*trí*a*co \cmark \\
-penitenciária & pe*ni*ten*ci-á*ri*a \xmark & pe*ni*ten*ci*á*ri*a \cmark \\
-psicologia & p.si*co*lo*gi*a \xmark & psi*co*lo*gi*a \cmark \\
-contribuir & con*tri*bu-ir \xmark & con*tri*bu*ir \cmark \\
-aéreo & a-é*re*o \xmark & a*é*re*o \cmark \\
-psicanálise & p.si*ca*ná*li*se \xmark & psi*ca*ná*li*se \cmark \\
-vestuário & ves*tu-á*ri*o \xmark & ves*tu*á*ri*o \cmark \\
-destruição & des*tru-i*ção \xmark & des*tru*i*ção \cmark \\
-viúva & vi-ú*va \xmark & vi*ú*va \cmark \\
-distribuído & dis*tri*bu-í*do \xmark & dis*tri*bu*í*do \cmark \\
-juízo & ju-í*zo \xmark & ju*í*zo \cmark \\
-constituinte & cons*ti*tu-in*te \xmark & cons*ti*tu-in*te \xmark \\
-presidenciável & pre*si*den*ci-á*vel \xmark & pre*si*den*ci*á*vel \cmark \\
-viável & vi-á*vel \xmark & vi*á*vel \cmark \\
-suíço & su-í*ço \xmark & su*í*ço \cmark \\
-destruir & des*tru-ir \xmark & des*tru*ir \cmark \\
-saído & sa-í*do \xmark & sa*í*do \cmark \\
-concluído & con*clu-í*do \xmark & con*clu*í*do \cmark \\
-distribuidora & dis*tri*bu-i*do*ra \xmark & dis*tri*bu*i*do*ra \cmark \\
-imobiliária & i*mo*bi*li-á*ri*a \xmark & i*mo*bi*li*á*ri*a \cmark \\
-sinfônica & sin-fô*ni*ca \xmark & sin*fô*ni*ca \cmark \\
-uísque & u-ís*que \xmark & u*ís*que \cmark \\
-poética & po-é*ti*ca \xmark & po*é*ti*ca \cmark \\
-prostituição & pros*ti*tu-i*ção \xmark & pros*ti*tu*i*ção \cmark \\
-rodoviário & ro*do*vi-á*ri*o \xmark & ro*do*vi*á*ri*o \cmark \\
-bicampeão & bi*cam*pe-ão \xmark & bi*cam*pe*ão \cmark \\
-psicológico & p.si*co*ló*gi*co \xmark & psi*co*ló*gi*co \cmark \\
-proibir & pro-i*bir \xmark & pro*i*bir \cmark \\
-triunfo & tri-un*fo \xmark & tri*un*fo \cmark \\
-variável & va*ri-á*vel \xmark & va*ri*á*vel \cmark \\
-criciúma & cri*ci-ú*ma \xmark & cri*ci*ú*ma \cmark \\
-sinônimo & si-nô*ni*mo \xmark & si*nô*ni*mo \cmark \\
-legião & le*gi-ão \xmark & le*gi*ão \cmark \\
-caído & ca-í*do \xmark & ca*í*do \cmark \\
-equívoco & e-quí*vo*co \xmark & e*quí*vo*co \cmark \\
-baía & ba-í-a \xmark & ba*í*a \cmark \\
-quilômetro & qui-lô*me*tro \xmark & qui*lô*me*tro \cmark \\
-raiz & ra-iz \xmark & ra-iz \xmark \\
-psiquiatra & p.si*qui*a*tra \xmark & psi*qui*a*tra \cmark \\
-tricampeão & tri*cam*pe-ão \xmark & tri*cam*pe*ão \cmark \\
-psicanalista & p.si*ca*na*lis*ta \xmark & psi*ca*na*lis*ta \cmark \\
-ruído & ru-í*do \xmark & ru*í*do \cmark \\
-possuir & pos*su-ir \xmark & pos*su*ir \cmark \\
-coibir & co-i*bir \xmark & co-i*bir \xmark \\
-soviético & so*vi-é*ti*co \xmark & so*vi*é*ti*co \cmark \\
-inviável & in*vi-á*vel \xmark & in*vi*á*vel \cmark \\
-alô & a-lô \xmark & a*lô \cmark \\
-heroína & he*ro-í*na \xmark & he*ro*í*na \cmark \\
-destruído & des*tru-í*do \xmark & des*tru*í*do \cmark \\
-telefônico & te*le-fô*ni*co \xmark & te*le*fô*ni*co \cmark \\
-saí & sa-í \xmark & sa*í \cmark \\
-suíte & su-í*te \xmark & su*í*te \cmark \\
-asiático & a*si-á*ti*co \xmark & a*si*á*ti*co \cmark \\
-irônico & i-rô*ni*co \xmark & i*rô*ni*co \cmark \\
-avô & a-vô \xmark & a*vô \cmark \\
-restituição & res*ti*tu-i*ção \xmark & res*ti*tu*i*ção \cmark \\
-atribuir & a*tri*bu-ir \xmark & a*tri*bu*ir \cmark \\
-ingenuidade & in*ge*nu-i*da*de \xmark & in*ge*nu*i*da*de \cmark \\
-psicólogo & p.si*có*lo*go \xmark & psi*có*lo*go \cmark \\
-pneu & p.neu \xmark & pneu \cmark \\
-tetracampeão & te*tra*cam*pe-ão \xmark & te*tra*cam*pe*ão \cmark \\
-vestiário & ves*ti-á*ri*o \xmark & ves*ti*á*ri*o \cmark \\
-proteína & pro*te-í*na \xmark & pro*te*í*na \cmark \\
-espião & es*pi-ão \xmark & es*pi*ão \cmark \\
-ciúme & ci-ú*me \xmark & ci*ú*me \cmark \\
-napoleão & na*po*le-ão \xmark & na*po*le*ão \cmark \\
-teórica & te-ó*ri*ca \xmark & te*ó*ri*ca \cmark \\
-intermediário & in*ter*me*di-á*ri*o \xmark & in*ter*me*di*á*ri*o \cmark \\
-constituir & cons*ti*tu-ir \xmark & cons*ti*tu*ir \cmark \\
-embrião & em*bri-ão \xmark & em*bri*ão \cmark \\
-autônomo & au-tô*no*mo \xmark & au*tô*no*mo \cmark \\
-confiável & con*fi-á*vel \xmark & con*fi*á*vel \cmark \\
-teórico & te-ó*ri*co \xmark & te*ó*ri*co \cmark \\
-estômago & es-tô*ma*go \xmark & es*tô*ma*go \cmark \\
-termômetro & ter-mô*me*tro \xmark & ter*mô*me*tro \cmark \\
-homônimo & ho-mô*ni*mo \xmark & ho*mô*ni*mo \cmark \\
-excluído & ex*clu-í*do \xmark & ex*clu*í*do \cmark \\
-penitenciário & pe*ni*ten*ci-á*ri*o \xmark & pe*ni*ten*ci*á*ri*o \cmark \\
-cardíaco & car*dí-a*co \xmark & car*dí*a*co \cmark \\
-mutuário & mu*tu-á*ri*o \xmark & mu*tu*á*ri*o \cmark \\
-aquém & a-quém \xmark & a*quém \cmark \\
-viário & vi-á*ri*o \xmark & vi*á*ri*o \cmark \\
-despoluição & des*po*lu-i*ção \xmark & des*po*lu*i*ção \cmark \\
-medíocre & me*dí-o*cre \xmark & me*dí*o*cre \cmark \\
-reintegração & re-in*te*gra*ção \xmark & re*in*te*gra*ção \cmark \\
-marquês & mar-quês \xmark & mar*quês \cmark \\
-beneficiário & be*ne*fi*ci-á*ri*o \xmark & be*ne*fi*ci*á*ri*o \cmark \\
-atribuição & a*tri*bu-i*ção \xmark & a*tri*bu*i*ção \cmark \\
-balneário & bal*ne-á*ri*o \xmark & bal*ne*á*ri*o \cmark \\
-coreógrafo & co*re-ó*gra*fo \xmark & co*re*ó*gra*fo \cmark \\
-incômodo & in-cô*mo*do \xmark & in*cô*mo*do \cmark \\
-sanduíche & san*du-í*che \xmark & san*du*í*che \cmark \\
-pecuária & pe*cu-á*ri*a \xmark & pe*cu*á*ri*a \cmark \\
-cirurgião & ci*rur*gi-ão \xmark & ci*rur*gi*ão \cmark \\
-jaú & ja-ú \xmark & ja*ú \cmark \\
-reconstruir & re*cons*tru-ir \xmark & re*cons*tru*ir \cmark \\
-influir & in*flu-ir \xmark & in*flu*ir \cmark \\
-santuário & san*tu-á*ri*o \xmark & san*tu*á*ri*o \cmark \\
-sutiã & su*ti-ã \xmark & su*ti*ã \cmark \\
-poético & po-é*ti*co \xmark & po*é*ti*co \cmark \\
-ensaísta & en*sa-ís*ta \xmark & en*sa*ís*ta \cmark \\
-porquê & por-quê \xmark & por*quê \cmark \\
-biólogo & bi-ó*lo*go \xmark & bi*ó*lo*go \cmark \\
-extrair & ex*tra-ir \xmark & ex*tra*ir \cmark \\
-reconstituição & re*cons*ti*tu-i*ção \xmark & re*cons*ti*tu*i*ção \cmark \\
-anfitrião & an*fi*tri-ão \xmark & an*fi*tri*ão \cmark \\
-anônimo & a-nô*ni*mo \xmark & a*nô*ni*mo \cmark \\
-aquático & a-quá*ti*co \xmark & a*quá*ti*co \cmark \\
-excluir & ex*clu-ir \xmark & ex*clu*ir \cmark \\
-filarmônica & fi*lar-mô*ni*ca \xmark & fi*lar*mô*ni*ca \cmark \\
-juizado & ju-i*za*do \xmark & ju*i*za*do \cmark \\
-peão & pe-ão \xmark & pe*ão \cmark \\
-previdenciário & pre*vi*den*ci-á*ri*o \xmark & pre*vi*den*ci*á*ri*o \cmark \\
-constituído & cons*ti*tu-í*do \xmark & cons*ti*tu*í*do \cmark \\
-pornô & por-nô \xmark & por*nô \cmark \\
-psiquiátrico & p.si*qui-á*tri*co \xmark & psi*qui*á*tri*co \cmark \\
-moinho & mo-i*nho \xmark & mo*i*nho \cmark \\
-obstruir & obs*tru-ir \xmark & obs*tru*ir \cmark \\
-psiquiatria & p.si*qui*a*tri*a \xmark & psi*qui*a*tri*a \cmark \\
-reindexação & re-in*de*xa*ção \xmark & re-in*de*xa*ção \xmark \\
-aquário & a-quá*ri*o \xmark & a*quá*ri*o \cmark \\
-amendoim & a*men*do-im \xmark & a*men*do-im \xmark \\
-baú & ba-ú \xmark & ba*ú \cmark \\
-distribuidor & dis*tri*bu-i*dor \xmark & dis*tri*bu*i*dor \cmark \\
-trair & tra-ir \xmark & tra*ir \cmark \\
-intuição & in*tu-i*ção \xmark & in*tu*i*ção \cmark \\
-petroquímica & pe*tro-quí*mi*ca \xmark & pe*tro*quí*mi*ca \cmark \\
-evoluir & e*vo*lu-ir \xmark & e*vo*lu*ir \cmark \\
-petroquímico & pe*tro-quí*mi*co \xmark & pe*tro*quí*mi*co \cmark \\
-asiática & a*si-á*ti*ca \xmark & a*si*á*ti*ca \cmark \\
-dinamarquês & di*na*mar-quês \xmark & di*na*mar*quês \cmark \\
-tcheco & t.che*co \xmark & tche*co \cmark \\
-diminuído & di*mi*nu-í*do \xmark & di*mi*nu*í*do \cmark \\
-instituir & ins*ti*tu-ir \xmark & ins*ti*tu*ir \cmark \\
-lampião & lam*pi-ão \xmark & lam*pi*ão \cmark \\
-arquitetônico & ar*qui*te-tô*ni*co \xmark & ar*qui*te*tô*ni*co \cmark \\
-atraído & a*tra-í*do \xmark & a*tra*í*do \cmark \\
-gastronômico & gas*tro-nô*mi*co \xmark & gas*tro*nô*mi*co \cmark \\
-vibrião & vi*bri-ão \xmark & vi*bri*ão \cmark \\
-caraíba & ca*ra-í*ba \xmark & ca*ra*í*ba \cmark \\
-ferroviário & fer*ro*vi-á*ri*o \xmark & fer*ro*vi*á*ri*o \cmark \\
-mobiliário & mo*bi*li-á*ri*o \xmark & mo*bi*li*á*ri*o \cmark \\
-robô & ro-bô \xmark & ro*bô \cmark \\
-traído & tra-í*do \xmark & tra*í*do \cmark \\
-chatô & cha-tô \xmark & cha*tô \cmark \\
-viés & vi-és \xmark & vi*és \cmark \\
-biquíni & bi-quí*ni \xmark & bi*quí*ni \cmark \\
-pneumonia & p.neu*mo*ni*a \xmark & pneu*mo*ni*a \cmark \\
-galeão & ga*le-ão \xmark & ga*le*ão \cmark \\
-pseudônimo & p.seu-dô*ni*mo \xmark & pseu*dô*ni*mo \cmark \\
-psicologicamente & p.si*co*lo*gi*ca*men*te \xmark & psi*co*lo*gi*ca*men*te \cmark \\
-tatuí & ta*tu-í \xmark & ta*tu*í \cmark \\
-anuário & a*nu-á*ri*o \xmark & a*nu*á*ri*o \cmark \\
-contrair & con*tra-ir \xmark & con*tra*ir \cmark \\
-curió & cu*ri-ó \xmark & cu*ri*ó \cmark \\
-egoísmo & e*go-ís*mo \xmark & e*go*ís*mo \cmark \\
-poliéster & po*li-és*ter \xmark & po*li*és*ter \cmark \\
-caótico & ca-ó*ti*co \xmark & ca*ó*ti*co \cmark \\
-descontraído & des*con*tra-í*do \xmark & des*con*tra*í*do \cmark \\
-hanseníase & han*se*ní-a*se \xmark & han*se*ní*a*se \cmark \\
-macedônia & ma*ce-dô*ni*a \xmark & ma*ce*dô*ni*a \cmark \\
-heroísmo & he*ro-ís*mo \xmark & he*ro*ís*mo \cmark \\
-instituído & ins*ti*tu-í*do \xmark & ins*ti*tu*í*do \cmark \\
-periódico & pe*ri-ó*di*co \xmark & pe*ri*ó*di*co \cmark \\
-abdômen & ab-dô*men \xmark & ab*dô*men \cmark \\
-paraibano & pa*ra-i*ba*no \xmark & pa*ra-i*ba*no \xmark \\
-psíquico & p.sí*qui*co \xmark & psí*qui*co \cmark \\
-reconstituir & re*cons*ti*tu-ir \xmark & re*cons*ti*tu*ir \cmark \\
-oásis & o-á*sis \xmark & o*á*sis \cmark \\
-parnaíba & par*na-í*ba \xmark & par*na*í*ba \cmark \\
-usufruir & u*su*fru-ir \xmark & u*su*fru*ir \cmark \\
-camelô & ca*me-lô \xmark & ca*me*lô \cmark \\
-maníaco & ma*ní-a*co \xmark & ma*ní*a*co \cmark \\
-sabiá & sa*bi-á \xmark & sa*bi*á \cmark \\
-agronômico & a*gro-nô*mi*co \xmark & a*gro*nô*mi*co \cmark \\
-astronômico & as*tro-nô*mi*co \xmark & as*tro*nô*mi*co \cmark \\
-psicopata & p.si*co*pa*ta \xmark & psi*co*pa*ta \cmark \\
-geógrafo & ge-ó*gra*fo \xmark & ge*ó*gra*fo \cmark \\
-ideário & i*de-á*ri*o \xmark & i*de*á*ri*o \cmark \\
-piá & pi-á \xmark & pi*á \cmark \\
-alcoólatra & al*co-ó*la*tra \xmark & al*co*ó*la*tra \cmark \\
-biógrafo & bi-ó*gra*fo \xmark & bi*ó*gra*fo \cmark \\
-coincidir & co-in*ci*dir \xmark & co*in*ci*dir \cmark \\
-escorpião & es*cor*pi-ão \xmark & es*cor*pi*ão \cmark \\
-fluência & flu-ên*ci*a \xmark & flu*ên*ci*a \cmark \\
-ruína & ru-í*na \xmark & ru*í*na \cmark \\
-delinquência & de*lin-quên*ci*a \xmark & de*lin*quên*ci*a \cmark \\
-contraído & con*tra-í*do \xmark & con*tra*í*do \cmark \\
-diluir & di*lu-ir \xmark & di*lu*ir \cmark \\
-psicose & p.si*co*se \xmark & psi*co*se \cmark \\
-bioquímica & bi*o-quí*mi*ca \xmark & bi*o*quí*mi*ca \cmark \\
-fluidez & flu-i*dez \xmark & flu-i*dez \xmark \\
-futevôlei & fu*te-vô*lei \xmark & fu*te*vô*lei \cmark \\
-judaísmo & ju*da-ís*mo \xmark & ju*da*ís*mo \cmark \\
-viúvo & vi-ú*vo \xmark & vi*ú*vo \cmark \\
-capô & ca-pô \xmark & ca*pô \cmark \\
-casuísmo & ca*su-ís*mo \xmark & ca*su*ís*mo \cmark \\
-receituário & re*cei*tu-á*ri*o \xmark & re*cei*tu*á*ri*o \cmark \\
-agrião & a*gri-ão \xmark & a*gri*ão \cmark \\
-comerciário & co*mer*ci-á*ri*o \xmark & co*mer*ci*á*ri*o \cmark \\
-estereótipo & es*te*re-ó*ti*po \xmark & es*te*re*ó*ti*po \cmark \\
-psicoterapia & p.si*co*te*ra*pi*a \xmark & psi*co*te*ra*pi*a \cmark \\
-vascaíno & vas*ca-í*no \xmark & vas*ca*í*no \cmark \\
-arquitetônica & ar*qui*te-tô*ni*ca \xmark & ar*qui*te*tô*ni*ca \cmark \\
-macroeconômico & ma*cro*e*co-nô*mi*co \xmark & ma*cro*e*co*nô*mi*co \cmark \\
-restituir & res*ti*tu-ir \xmark & res*ti*tu*ir \cmark \\
-rutherford & ru-ther*ford \xmark & ru-ther*ford \xmark \\
-triunfal & tri-un*fal \xmark & tri*un*fal \cmark \\
-guardião & guar*di-ão \xmark & guar*di*ão \cmark \\
-oriundo & o*ri-un*do \xmark & o*ri*un*do \cmark \\
-arqueólogo & ar*que-ó*lo*go \xmark & ar*que*ó*lo*go \cmark \\
-carbônico & car-bô*ni*co \xmark & car*bô*ni*co \cmark \\
-stalinista & s.ta*li*nis*ta \xmark & sta*li*nis*ta \cmark \\
-egoísta & e*go-ís*ta \xmark & e*go*ís*ta \cmark \\
-portuário & por*tu-á*ri*o \xmark & por*tu*á*ri*o \cmark \\
-recaída & re*ca-í*da \xmark & re*ca*í*da \cmark \\
-reiniciar & re-i*ni*ci*ar \xmark & re-i*ni*ci*ar \xmark \\
-reurbanização & re-ur*ba*ni*za*ção \xmark & re-ur*ba*ni*za*ção \xmark \\
-teólogo & te-ó*lo*go \xmark & te*ó*lo*go \cmark \\
-baião & bai-ão \xmark & bai*ão \cmark \\
-genuíno & ge*nu-í*no \xmark & ge*nu*í*no \cmark \\
-hegemônico & he*ge-mô*ni*co \xmark & he*ge*mô*ni*co \cmark \\
-resquício & res-quí*ci*o \xmark & res*quí*ci*o \cmark \\
-retribuição & re*tri*bu-i*ção \xmark & re*tri*bu*i*ção \cmark \\
-confluência & con*flu-ên*ci*a \xmark & con*flu*ên*ci*a \cmark \\
-fluir & flu-ir \xmark & flu*ir \cmark \\
-imperdoável & im*per*do-á*vel \xmark & im*per*do*á*vel \cmark \\
-distrair & dis*tra-ir \xmark & dis*tra*ir \cmark \\
-guaíba & gua-í*ba \xmark & gua*í*ba \cmark \\
-intuitivo & in*tu-i*ti*vo \xmark & in*tu*i*ti*vo \cmark \\
-orquídea & or-quí*de*a \xmark & or*quí*de*a \cmark \\
-semiótica & se*mi-ó*ti*ca \xmark & se*mi*ó*ti*ca \cmark \\
-vovô & vo-vô \xmark & vo*vô \cmark \\
-campainha & cam*pa-i*nha \xmark & cam*pa*i*nha \cmark \\
-czar & c.zar \xmark & czar \cmark \\
-diluição & di*lu-i*ção \xmark & di*lu*i*ção \cmark \\
-distraído & dis*tra-í*do \xmark & dis*tra*í*do \cmark \\
-eloquência & e*lo-quên*ci*a \xmark & e*lo*quên*ci*a \cmark \\
-insubstituível & in*subs*ti*tu-í*vel \xmark & in*subs*ti*tu*í*vel \cmark \\
-reinventar & re-in*ven*tar \xmark & re*in*ven*tar \cmark \\
-retribuir & re*tri*bu-ir \xmark & re*tri*bu*ir \cmark \\
-rubéola & ru*bé-o*la \xmark & ru*bé*o*la \cmark \\
-abruptamente & a.b-rup*ta*men*te \xmark & a.b-rup*ta*men*te \xmark \\
-maniqueísmo & ma*ni*que-ís*mo \xmark & ma*ni*que*ís*mo \cmark \\
-antiquário & an*ti-quá*ri*o \xmark & an*ti*quá*ri*o \cmark \\
-harmônica & har-mô*ni*ca \xmark & har*mô*ni*ca \cmark \\
-judô & ju-dô \xmark & ju*dô \cmark \\
-maniqueísta & ma*ni*que-ís*ta \xmark & ma*ni*que*ís*ta \cmark \\
-tchau & t.chau \xmark & tchau \cmark \\
-moído & mo-í*do \xmark & mo*í*do \cmark \\
-psicanalítico & p.si*ca*na*lí*ti*co \xmark & psi*ca*na*lí*ti*co \cmark \\
-caíco & ca-í*co \xmark & ca*í*co \cmark \\
-descontinuidade & des*con*ti*nu-i*da*de \xmark & des*con*ti*nu*i*da*de \cmark \\
-tarô & ta-rô \xmark & ta*rô \cmark \\
-absenteísmo & ab*sen*te-ís*mo \xmark & ab*sen*te*ís*mo \cmark \\
-anuência & a*nu-ên*ci*a \xmark & a*nu*ên*ci*a \cmark \\
-etíope & e*tí-o*pe \xmark & e*tí*o*pe \cmark \\
-ofurô & o*fu-rô \xmark & o*fu*rô \cmark \\
-panteão & pan*te-ão \xmark & pan*te*ão \cmark \\
-atômico & a-tô*mi*co \xmark & a*tô*mi*co \cmark \\
-corroído & cor*ro-í*do \xmark & cor*ro*í*do \cmark \\
-destituído & des*ti*tu-í*do \xmark & des*ti*tu*í*do \cmark \\
-estagiário & es*ta*gi-á*ri*o \xmark & es*ta*gi*á*ri*o \cmark \\
-inadiável & i*na*di-á*vel \xmark & i*na*di*á*vel \cmark \\
-instruído & ins*tru-í*do \xmark & ins*tru*í*do \cmark \\
-amazônico & a*ma-zô*ni*co \xmark & a*ma*zô*ni*co \cmark \\
-anuidade & a*nu-i*da*de \xmark & a*nu*i*da*de \cmark \\
-evoluído & e*vo*lu-í*do \xmark & e*vo*lu*í*do \cmark \\
-faísca & fa-ís*ca \xmark & fa*ís*ca \cmark \\
-harmônico & har-mô*ni*co \xmark & har*mô*ni*co \cmark \\
-patriótico & pa*tri-ó*ti*co \xmark & pa*tri*ó*ti*co \cmark \\
-presidiário & pre*si*di-á*ri*o \xmark & pre*si*di*á*ri*o \cmark \\
-reconstruído & re*cons*tru-í*do \xmark & re*cons*tru*í*do \cmark \\
-tricô & tri-cô \xmark & tri*cô \cmark \\
-antiético & an*ti-é*ti*co \xmark & an*ti*é*ti*co \cmark \\
-cronômetro & cro-nô*me*tro \xmark & cro*nô*me*tro \cmark \\
-destituição & des*ti*tu-i*ção \xmark & des*ti*tu*i*ção \cmark \\
-fiúza & fi-ú*za \xmark & fi*ú*za \cmark \\
-píer & pí-er \xmark & pí-er \xmark \\
-psique & p.si*que \xmark & psi*que \cmark \\
-recair & re*ca-ir \xmark & re*ca*ir \cmark \\
-sinfônico & sin-fô*ni*co \xmark & sin*fô*ni*co \cmark \\
-triunfante & tri-un*fan*te \xmark & tri*un*fan*te \cmark \\
-adail & a*da-il \xmark & a*da-il \xmark \\
-atônito & a-tô*ni*to \xmark & a*tô*ni*to \cmark \\
-birô & bi-rô \xmark & bi*rô \cmark \\
-cafeína & ca*fe-í*na \xmark & ca*fe*í*na \cmark \\
-ideólogo & i*de-ó*lo*go \xmark & i*de*ó*lo*go \cmark \\
-inequívoco & i*ne-quí*vo*co \xmark & i*ne*quí*vo*co \cmark \\
-míope & mí-o*pe \xmark & mí*o*pe \cmark \\
-poá & po-á \xmark & po*á \cmark \\
-stalinismo & s.ta*li*nis*mo \xmark & sta*li*nis*mo \cmark \\
-suíno & su-í*no \xmark & su*í*no \cmark \\
-voyeurismo & voy-eu*ris*mo \xmark & voy-eu*ris*mo \xmark \\
-camaleão & ca*ma*le-ão \xmark & ca*ma*le*ão \cmark \\
-dióxido & di-ó*xi*do \xmark & di*ó*xi*do \cmark \\
-geólogo & ge-ó*lo*go \xmark & ge*ó*lo*go \cmark \\
-ilíada & i*lí-a*da \xmark & i*lí*a*da \cmark \\
-impermeável & im*per*me-á*vel \xmark & im*per*me*á*vel \cmark \\
-jesuíta & je*su-í*ta \xmark & je*su*í*ta \cmark \\
-suástica & su-ás*ti*ca \xmark & su*ás*ti*ca \cmark \\
-bioquímico & bi*o-quí*mi*co \xmark & bi*o*quí*mi*co \cmark \\
-buquê & bu-quê \xmark & bu*quê \cmark \\
-esôfago & e-sô*fa*go \xmark & e*sô*fa*go \cmark \\
-folião & fo*li-ão \xmark & fo*li*ão \cmark \\
-quilowatt & qui*lo-watt \xmark & qui*lo-watt \xmark \\
-ruir & ru-ir \xmark & ru*ir \cmark \\
-altruísmo & al*tru-ís*mo \xmark & al*tru*ís*mo \cmark \\
-equânime & e-quâ*ni*me \xmark & e*quâ*ni*me \cmark \\
-fruição & fru-i*ção \xmark & fru*i*ção \cmark \\
-insaciável & in*sa*ci-á*vel \xmark & in*sa*ci*á*vel \cmark \\
-caída & ca-í*da \xmark & ca*í*da \cmark \\
-ciático & ci-á*ti*co \xmark & ci*á*ti*co \cmark \\
-gavião & ga*vi-ão \xmark & ga*vi*ão \cmark \\
-gratuidade & gra*tu-i*da*de \xmark & gra*tu*i*da*de \cmark \\
-irremediável & ir*re*me*di-á*vel \xmark & ir*re*me*di*á*vel \cmark \\
-ladainha & la*da-i*nha \xmark & la*da*i*nha \cmark \\
-piauiense & pi*au-i*en*se \xmark & pi*au-i*en*se \xmark \\
-prostituir & pros*ti*tu-ir \xmark & pros*ti*tu*ir \cmark \\
-triunfar & tri-un*far \xmark & tri*un*far \cmark \\
-acuidade & a*cu-i*da*de \xmark & a*cu*i*da*de \cmark \\
-adriático & a*dri-á*ti*co \xmark & a*dri*á*ti*co \cmark \\
-afrodisíaco & a*fro*di*sí-a*co \xmark & a*fro*di*sí*a*co \cmark \\
-bioética & bi*o-é*ti*ca \xmark & bi*o*é*ti*ca \cmark \\
-cocô & co-cô \xmark & co*cô \cmark \\
-instruir & ins*tru-ir \xmark & ins*tru*ir \cmark \\
-paradisíaco & pa*ra*di*sí-a*co \xmark & pa*ra*di*sí*a*co \cmark \\
-poluir & po*lu-ir \xmark & po*lu*ir \cmark \\
-possuído & pos*su-í*do \xmark & pos*su*í*do \cmark \\
-sublinha & su.b-li*nha \xmark & su.b-li*nha \xmark \\
-antibiótico & an*ti*bi-ó*ti*co \xmark & an*ti*bi*ó*ti*co \cmark \\
-apreciável & a*pre*ci-á*vel \xmark & a*pre*ci*á*vel \cmark \\
-desobstruir & de*sobs*tru-ir \xmark & de*sobs*tru*ir \cmark \\
-destruidor & des*tru-i*dor \xmark & des*tru*i*dor \cmark \\
-diáspora & di-ás*po*ra \xmark & di*ás*po*ra \cmark \\
-diluído & di*lu-í*do \xmark & di*lu*í*do \cmark \\
-maiúsculo & mai-ús*cu*lo \xmark & mai*ús*cu*lo \cmark \\
-miúdo & mi-ú*do \xmark & mi*ú*do \cmark \\
-pentacampeão & pen*ta*cam*pe-ão \xmark & pen*ta*cam*pe*ão \cmark \\
-retraído & re*tra-í*do \xmark & re*tra*í*do \cmark \\
-subtrair & sub*tra-ir \xmark & sub*tra*ir \cmark \\
-suéter & su-é*ter \xmark & su*é*ter \cmark \\
-açaí & a*ça-í \xmark & a*ça*í \cmark \\
-alcoólico & al*co-ó*li*co \xmark & al*co*ó*li*co \cmark \\
-despoluir & des*po*lu-ir \xmark & des*po*lu*ir \cmark \\
-diurno & di-ur*no \xmark & di*ur*no \cmark \\
-inexequível & i*ne*xe-quí*vel \xmark & i*ne*xe*quí*vel \cmark \\
-prontuário & pron*tu-á*ri*o \xmark & pron*tu*á*ri*o \cmark \\
-psicoterapeuta & p.si*co*te*ra*peu*ta \xmark & psi*co*te*ra*peu*ta \cmark \\
-saúva & sa-ú*va \xmark & sa*ú*va \cmark \\
-tabelião & ta*be*li-ão \xmark & ta*be*li*ão \cmark \\
 abrupto & a.b-rup*to \xmark & a.b-rup*to \xmark \\
-destituir & des*ti*tu-ir \xmark & des*ti*tu*ir \cmark \\
-dionisíaco & di*o*ni*sí-a*co \xmark & di*o*ni*sí*a*co \cmark \\
-lacônico & la-cô*ni*co \xmark & la*cô*ni*co \cmark \\
-megawatt & me*ga-watt \xmark & me*ga-watt \xmark \\
-poliuretano & po*li-u*re*ta*no \xmark & po*li*u*re*ta*no \cmark \\
-protozoário & pro*to*zo-á*ri*o \xmark & pro*to*zo*á*ri*o \cmark \\
-reincidente & re-in*ci*den*te \xmark & re*in*ci*den*te \cmark \\
-reintegrar & re-in*te*grar \xmark & re*in*te*grar \cmark \\
-reinvenção & re-in*ven*ção \xmark & re*in*ven*ção \cmark \\
-afluência & a*flu-ên*ci*a \xmark & a*flu*ên*ci*a \cmark \\
-assiduidade & as*si*du-i*da*de \xmark & as*si*du*i*da*de \cmark \\
-coágulo & co-á*gu*lo \xmark & co*á*gu*lo \cmark \\
-cuíca & cu-í*ca \xmark & cu*í*ca \cmark \\
-faraó & fa*ra-ó \xmark & fa*ra*ó \cmark \\
-fundiário & fun*di-á*ri*o \xmark & fun*di*á*ri*o \cmark \\
-incendiário & in*cen*di-á*ri*o \xmark & in*cen*di*á*ri*o \cmark \\
-itapuã & i*ta*pu-ã \xmark & i*ta*pu*ã \cmark \\
-parcimônia & par*ci-mô*ni*a \xmark & par*ci*mô*ni*a \cmark \\
-psicótico & p.si*có*ti*co \xmark & psi*có*ti*co \cmark \\
-redemoinho & re*de*mo-i*nho \xmark & re*de*mo*i*nho \cmark \\
-redistribuir & re*dis*tri*bu-ir \xmark & re*dis*tri*bu*ir \cmark \\
-reintrodução & re-in*tro*du*ção \xmark & re*in*tro*du*ção \cmark \\
-triunfalismo & tri-un*fa*lis*mo \xmark & tri*un*fa*lis*mo \cmark \\
-zodíaco & zo*dí-a*co \xmark & zo*dí*a*co \cmark \\
-aminoácido & a*mi*no-á*ci*do \xmark & a*mi*no*á*ci*do \cmark \\
-arruinar & ar*ru-i*nar \xmark & ar*ru*i*nar \cmark \\
-ateísmo & a*te-ís*mo \xmark & a*te*ís*mo \cmark \\
-caim & ca-im \xmark & ca-im \xmark \\
-exequível & e*xe-quí*vel \xmark & e*xe*quí*vel \cmark \\
-inconsequência & in*con*se-quên*ci*a \xmark & in*con*se*quên*ci*a \cmark \\
-laquê & la-quê \xmark & la*quê \cmark \\
-megalomaníaco & me*ga*lo*ma*ní-a*co \xmark & me*ga*lo*ma*ní*a*co \cmark \\
-pantaleão & pan*ta*le-ão \xmark & pan*ta*le*ão \cmark \\
-poluidor & po*lu-i*dor \xmark & po*lu*i*dor \cmark \\
-preâmbulo & pre-âm*bu*lo \xmark & pre*âm*bu*lo \cmark \\
-arcaísmo & ar*ca-ís*mo \xmark & ar*ca*ís*mo \cmark \\
-auréola & au*ré-o*la \xmark & au*ré*o*la \cmark \\
-autodestruição & au*to*des*tru-i*ção \xmark & au*to*des*tru*i*ção \cmark \\
-casuística & ca*su-ís*ti*ca \xmark & ca*su*ís*ti*ca \cmark \\
-desunião & de*su*ni-ão \xmark & de*su*ni*ão \cmark \\
-elogiável & e*lo*gi-á*vel \xmark & e*lo*gi*á*vel \cmark \\
+apneia & a-p.nei*a \xmark & a-p.nei-a \xmark \\
+arábias & a*rá*bi.as \xmark & a*rá*bi.as \xmark \\
+brechtiano & bre.ch*ti*a*no \xmark & bre.ch*ti*a*no \xmark \\
+czarina & c.za*ri*na \xmark & cza*ri*na \cmark \\
+czarismo & c.za*ris*mo \xmark & cza*ris*mo \cmark \\
+czarista & c.za*ris*ta \xmark & cza*ris*ta \cmark \\
+dispneia & dis-p.nei*a \xmark & dis-p.nei-a \xmark \\
+dzeta & d.ze*ta \xmark & d.ze*ta \xmark \\
+exéquias & e*xé*qui.as \xmark & e*xé*qui.as \xmark \\
+gnaisse & g.nais*se \xmark & g.nais*se \xmark \\
 gnomo & g.no*mo \xmark & gno*mo \cmark \\
-neurocirurgião & neu*ro*ci*rur*gi-ão \xmark & neu*ro*ci*rur*gi*ão \cmark \\
-pediátrico & pe*di-á*tri*co \xmark & pe*di*á*tri*co \cmark \\
-permeável & per*me-á*vel \xmark & per*me*á*vel \cmark \\
-piraí & pi*ra-í \xmark & pi*ra*í \cmark \\
-psicodélico & p.si*co*dé*li*co \xmark & psi*co*dé*li*co \cmark \\
-psicotécnico & p.si*co*téc*ni*co \xmark & psi*co*téc*ni*co \cmark \\
-saíra & sa-í*ra \xmark & sa*í*ra \cmark \\
-sobressair & so*bres*sa-ir \xmark & so*bres*sa*ir \cmark \\
-subliminar & su.b-li*mi*nar \xmark & sub*li*mi*nar \cmark \\
-ajuizado & a*ju-i*za*do \xmark & a*ju*i*za*do \cmark \\
-antipoluição & an*ti*po*lu-i*ção \xmark & an*ti*po*lu*i*ção \cmark \\
-arquétipo & ar-qué*ti*po \xmark & ar*qué*ti*po \cmark \\
-dadaísmo & da*da-ís*mo \xmark & da*da*ís*mo \cmark \\
-descontrair & des*con*tra-ir \xmark & des*con*tra*ir \cmark \\
-gasômetro & ga-sô*me*tro \xmark & ga*sô*me*tro \cmark \\
-hidroviário & hi*dro*vi-á*ri*o \xmark & hi*dro*vi*á*ri*o \cmark \\
-inegociável & i*ne*go*ci-á*vel \xmark & i*ne*go*ci*á*vel \cmark \\
-maiúscula & mai-ús*cu*la \xmark & mai*ús*cu*la \cmark \\
-miúdas & mi-ú*das \xmark & mi*ú*das \cmark \\
-perequê & pe*re-quê \xmark & pe*re*quê \cmark \\
-recôncavo & re-côn*ca*vo \xmark & re*côn*ca*vo \cmark \\
-saquê & sa-quê \xmark & sa*quê \cmark \\
-ancião & an*ci-ão \xmark & an*ci*ão \cmark \\
-bafômetro & ba-fô*me*tro \xmark & ba*fô*me*tro \cmark \\
-bongô & bon-gô \xmark & bon*gô \cmark \\
-ciberespaço & ci*be.r-es*pa*ço \xmark & ci*be.r-es*pa*ço \xmark \\
-condômino & con-dô*mi*no \xmark & con*dô*mi*no \cmark \\
-dadaísta & da*da-ís*ta \xmark & da*da*ís*ta \cmark \\
-freático & fre-á*ti*co \xmark & fre*á*ti*co \cmark \\
-hipocondríaco & hi*po*con*drí-a*co \xmark & hi*po*con*drí*a*co \cmark \\
-indaiá & in*dai-á \xmark & in*dai*á \cmark \\
-jacuí & ja*cu-í \xmark & ja*cu*í \cmark \\
-maleável & ma*le-á*vel \xmark & ma*le*á*vel \cmark \\
-ministeriável & mi*nis*te*ri-á*vel \xmark & mi*nis*te*ri*á*vel \cmark \\
-obituário & o*bi*tu-á*ri*o \xmark & o*bi*tu*á*ri*o \cmark \\
-picuinha & pi*cu-i*nha \xmark & pi*cu-i*nha \xmark \\
-platô & pla-tô \xmark & pla*tô \cmark \\
-possuidor & pos*su-i*dor \xmark & pos*su*i*dor \cmark \\
-psicodelismo & p.si*co*de*lis*mo \xmark & psi*co*de*lis*mo \cmark \\
-reinserção & re-in*ser*ção \xmark & re*in*ser*ção \cmark \\
-suingue & su-in*gue \xmark & su-in*gue \xmark \\
-triunfalista & tri-un*fa*lis*ta \xmark & tri*un*fa*lis*ta \cmark \\
-varíola & va*rí-o*la \xmark & va*rí*o*la \cmark \\
-apoteótico & a*po*te-ó*ti*co \xmark & a*po*te*ó*ti*co \cmark \\
-bainha & ba-i*nha \xmark & ba*i*nha \cmark \\
-bibliófilo & bi*bli-ó*fi*lo \xmark & bi*bli*ó*fi*lo \cmark \\
-caimento & ca-i*men*to \xmark & ca-i*men*to \xmark \\
-cambuí & cam*bu-í \xmark & cam*bu*í \cmark \\
-cauim & cau-im \xmark & cau-im \xmark \\
-darwinismo & dar-wi*nis*mo \xmark & dar-wi*nis*mo \xmark \\
-eclesiástico & e*cle*si-ás*ti*co \xmark & e*cle*si*ás*ti*co \cmark \\
-estuário & es*tu-á*ri*o \xmark & es*tu*á*ri*o \cmark \\
-gigolô & gi*go-lô \xmark & gi*go*lô \cmark \\
-imbuído & im*bu-í*do \xmark & im*bu*í*do \cmark \\
-bastião & bas*ti-ão \xmark & bas*ti*ão \cmark \\
-caíque & ca-í*que \xmark & ca*í*que \cmark \\
-coincidente & co-in*ci*den*te \xmark & co*in*ci*den*te \cmark \\
-flúor & flú-or \xmark & flú-or \xmark \\
-incongruência & in*con*gru-ên*ci*a \xmark & in*con*gru*ên*ci*a \cmark \\
-indissociável & in*dis*so*ci-á*vel \xmark & in*dis*so*ci*á*vel \cmark \\
-invariável & in*va*ri-á*vel \xmark & in*va*ri*á*vel \cmark \\
-mostruário & mos*tru-á*ri*o \xmark & mos*tru*á*ri*o \cmark \\
-néon & né-on \xmark & né*on \cmark \\
-oboé & o*bo-é \xmark & o*bo*é \cmark \\
-oceânico & o*ce-â*ni*co \xmark & o*ce*â*ni*co \cmark \\
-panteísmo & pan*te-ís*mo \xmark & pan*te*ís*mo \cmark \\
-platônico & pla-tô*ni*co \xmark & pla*tô*ni*co \cmark \\
-pneumologia & p.neu*mo*lo*gi*a \xmark & pneu*mo*lo*gi*a \cmark \\
-proibitivo & pro-i*bi*ti*vo \xmark & pro*i*bi*ti*vo \cmark \\
-raquítico & ra-quí*ti*co \xmark & ra*quí*ti*co \cmark \\
-reinterpretação & re-in*ter*pre*ta*ção \xmark & re*in*ter*pre*ta*ção \cmark \\
-subtraído & sub*tra-í*do \xmark & sub*tra*í*do \cmark \\
-suinocultura & su-i*no*cul*tu*ra \xmark & su*i*no*cul*tu*ra \cmark \\
-sumô & su-mô \xmark & su*mô \cmark \\
-tainha & ta-i*nha \xmark & ta*i*nha \cmark \\
-acordeão & a*cor*de-ão \xmark & a*cor*de*ão \cmark \\
-aético & a-é*ti*co \xmark & a*é*ti*co \cmark \\
-baiuca & bai-u*ca \xmark & bai-u*ca \xmark \\
-centurião & cen*tu*ri-ão \xmark & cen*tu*ri*ão \cmark \\
-comediógrafo & co*me*di-ó*gra*fo \xmark & co*me*di*ó*gra*fo \cmark \\
-conduíte & con*du-í*te \xmark & con*du*í*te \cmark \\
-coroinha & co*ro-i*nha \xmark & co*ro*i*nha \cmark \\
-ergonômico & er*go-nô*mi*co \xmark & er*go*nô*mi*co \cmark \\
-gaélico & ga-é*li*co \xmark & ga*é*li*co \cmark \\
-grandiloquência & gran*di*lo-quên*ci*a \xmark & gran*di*lo*quên*ci*a \cmark \\
-impatriótico & im*pa*tri-ó*ti*co \xmark & im*pa*tri*ó*ti*co \cmark \\
-megalômano & me*ga-lô*ma*no \xmark & me*ga*lô*ma*no \cmark \\
-miríade & mi*rí-a*de \xmark & mi*rí*a*de \cmark \\
-neófito & ne-ó*fi*to \xmark & ne*ó*fi*to \cmark \\
-nipônico & ni-pô*ni*co \xmark & ni*pô*ni*co \cmark \\
-obstruído & obs*tru-í*do \xmark & obs*tru*í*do \cmark \\
-pecuniário & pe*cu*ni-á*ri*o \xmark & pe*cu*ni*á*ri*o \cmark \\
-psicopatologia & p.si*co*pa*to*lo*gi*a \xmark & psi*co*pa*to*lo*gi*a \cmark \\
-reindexar & re-in*de*xar \xmark & re-in*de*xar \xmark \\
-reinstalar & re-ins*ta*lar \xmark & re*ins*ta*lar \cmark \\
-reintroduzir & re-in*tro*du*zir \xmark & re*in*tro*du*zir \cmark \\
-teleinformática & te*le-in*for*má*ti*ca \xmark & te*le*in*for*má*ti*ca \cmark \\
-timbaúba & tim*ba-ú*ba \xmark & tim*ba*ú*ba \cmark \\
-agônico & a-gô*ni*co \xmark & a*gô*ni*co \cmark \\
-anatômico & a*na-tô*mi*co \xmark & a*na*tô*mi*co \cmark \\
-anômalo & a-nô*ma*lo \xmark & a*nô*ma*lo \cmark \\
-ataúde & a*ta-ú*de \xmark & a*ta*ú*de \cmark \\
-auê & au-ê \xmark & au*ê \cmark \\
-bestiário & bes*ti-á*ri*o \xmark & bes*ti*á*ri*o \cmark \\
-boá & bo-á \xmark & bo*á \cmark \\
-copião & co*pi-ão \xmark & co*pi*ão \cmark \\
-ensaística & en*sa-ís*ti*ca \xmark & en*sa*ís*ti*ca \cmark \\
-fonoaudiólogo & fo*no*au*di-ó*lo*go \xmark & fo*no*au*di*ó*lo*go \cmark \\
-imiscuir & i*mis*cu-ir \xmark & i*mis*cu-ir \xmark \\
-jupiá & ju*pi-á \xmark & ju*pi*á \cmark \\
-monoteísmo & mo*no*te-ís*mo \xmark & mo*no*te*ís*mo \cmark \\
-nagô & na-gô \xmark & na*gô \cmark \\
-psicofarmacologia & p.si*co*far*ma*co*lo*gi*a \xmark & psi*co*far*ma*co*lo*gi*a \cmark \\
-psicologismo & p.si*co*lo*gis*mo \xmark & psi*co*lo*gis*mo \cmark \\
-ruindade & ru-in*da*de \xmark & ru-in*da*de \xmark \\
-sanduicheria & san*du-i*che*ri*a \xmark & san*du*i*che*ri*a \cmark \\
-sociável & so*ci-á*vel \xmark & so*ci*á*vel \cmark \\
-sublevação & su.b-le*va*ção \xmark & sub*le*va*ção \cmark \\
-abstrair & abs*tra-ir \xmark & abs*tra*ir \cmark \\
-alaúde & a*la-ú*de \xmark & a*la*ú*de \cmark \\
-almôndega & al-môn*de*ga \xmark & al*môn*de*ga \cmark \\
-antiaéreo & an*ti*a-é*re*o \xmark & an*ti*a*é*re*o \cmark \\
-atrabiliário & a*tra*bi*li-á*ri*o \xmark & a*tra*bi*li*á*ri*o \cmark \\
-bangalô & ban*ga-lô \xmark & ban*ga*lô \cmark \\
-bôer & bô-er \xmark & bô-er \xmark \\
-breviário & bre*vi-á*ri*o \xmark & bre*vi*á*ri*o \cmark \\
-canônico & ca-nô*ni*co \xmark & ca*nô*ni*co \cmark \\
-carnaúba & car*na-ú*ba \xmark & car*na*ú*ba \cmark \\
-doído & do-í*do \xmark & do*í*do \cmark \\
-ensaísmo & en*sa-ís*mo \xmark & en*sa*ís*mo \cmark \\
-esfiha & es*fi-ha \xmark & es*fi-ha \xmark \\
-graúna & gra-ú*na \xmark & gra*ú*na \cmark \\
-hemodiálise & he*mo*di-á*li*se \xmark & he*mo*di*á*li*se \cmark \\
-hinduísmo & hin*du-ís*mo \xmark & hin*du*ís*mo \cmark \\
-influído & in*flu-í*do \xmark & in*flu-í*do \xmark \\
-intuir & in*tu-ir \xmark & in*tu*ir \cmark \\
-latifundiário & la*ti*fun*di-á*ri*o \xmark & la*ti*fun*di*á*ri*o \cmark \\
-mimeógrafo & mi*me-ó*gra*fo \xmark & mi*me*ó*gra*fo \cmark \\
-pajeú & pa*je-ú \xmark & pa*je*ú \cmark \\
-prosaísmo & pro*sa-ís*mo \xmark & pro*sa*ís*mo \cmark \\
-psicodrama & p.si*co*dra*ma \xmark & psi*co*dra*ma \cmark \\
-psicopedagogia & p.si*co*pe*da*go*gi*a \xmark & psi*co*pe*da*go*gi*a \cmark \\
-quinquênio & quin-quê*ni*o \xmark & quin*quê*ni*o \cmark \\
-radiofrequência & ra*di*o*fre-quên*ci*a \xmark & ra*di*o*fre*quên*ci*a \cmark \\
-reinstituir & re-ins*ti*tu-ir \xmark & re*ins*ti*tu*ir \cmark \\
-supercampeão & su*per*cam*pe-ão \xmark & su*per*cam*pe*ão \cmark \\
-supersônico & su*per-sô*ni*co \xmark & su*per*sô*ni*co \cmark \\
-tragicômico & tra*gi-cô*mi*co \xmark & tra*gi*cô*mi*co \cmark \\
-tríade & trí-a*de \xmark & trí*a*de \cmark \\
-vacuidade & va*cu-i*da*de \xmark & va*cu*i*da*de \cmark \\
-agogô & a*go-gô \xmark & a*go*gô \cmark \\
-altruísta & al*tru-ís*ta \xmark & al*tru*ís*ta \cmark \\
-antiácido & an*ti-á*ci*do \xmark & an*ti*á*ci*do \cmark \\
-autobiógrafo & au*to*bi-ó*gra*fo \xmark & au*to*bi*ó*gra*fo \cmark \\
-beduíno & be*du-í*no \xmark & be*du*í*no \cmark \\
-bordô & bor-dô \xmark & bor*dô \cmark \\
-casuístico & ca*su-ís*ti*co \xmark & ca*su*ís*ti*co \cmark \\
-czarina & c.za*ri*na \xmark & cza*ri*na \cmark \\
-demoníaco & de*mo*ní-a*co \xmark & de*mo*ní*a*co \cmark \\
-desconstruir & des*cons*tru-ir \xmark & des*cons*tru*ir \cmark \\
-ergômetro & er-gô*me*tro \xmark & er*gô*me*tro \cmark \\
-evoé & e*vo-é \xmark & e*vo*é \cmark \\
-graúdo & gra-ú*do \xmark & gra*ú*do \cmark \\
-iídiche & i-í*di*che \xmark & i*í*di*che \cmark \\
-impronunciável & im*pro*nun*ci-á*vel \xmark & im*pro*nun*ci*á*vel \cmark \\
-influenciável & in*flu*en*ci-á*vel \xmark & in*flu*en*ci*á*vel \cmark \\
-irrefreável & ir*re*fre-á*vel \xmark & ir*re*fre*á*vel \cmark \\
-irretorquível & ir*re*tor-quí*vel \xmark & ir*re*tor*quí*vel \cmark \\
-jataí & ja*ta-í \xmark & ja*ta*í \cmark \\
-juquiá & ju*qui-á \xmark & ju*qui*á \cmark \\
-painho & pa-i*nho \xmark & pa*i*nho \cmark \\
-pindaíba & pin*da-í*ba \xmark & pin*da*í*ba \cmark \\
-pneumologista & p.neu*mo*lo*gis*ta \xmark & pneu*mo*lo*gis*ta \cmark \\
-porciúncula & por*ci-ún*cu*la \xmark & por*ci*ún*cu*la \cmark \\
-prolegômenos & pro*le-gô*me*nos \xmark & pro*le*gô*me*nos \cmark \\
-psiquismo & p.si*quis*mo \xmark & psi*quis*mo \cmark \\
-quiproquó & qui*pro-quó \xmark & qui*pro*quó \cmark \\
-refluir & re*flu-ir \xmark & re*flu*ir \cmark \\
-reimplantar & re-im*plan*tar \xmark & re*im*plan*tar \cmark \\
-reurbanizar & re-ur*ba*ni*zar \xmark & re-ur*ba*ni*zar \xmark \\
-reutilizar & re-u*ti*li*zar \xmark & re-u*ti*li*zar \xmark \\
-sainte & sa-in*te \xmark & sa-in*te \xmark \\
-tsunami & t.su*na*mi \xmark & tsu*na*mi \cmark \\
-usucapião & u*su*ca*pi-ão \xmark & u*su*ca*pi*ão \cmark \\
-zebuíno & ze*bu-í*no \xmark & ze*bu*í*no \cmark \\
-aeroportuário & a*e*ro*por*tu-á*ri*o \xmark & a*e*ro*por*tu*á*ri*o \cmark \\
-agroquímica & a*gro-quí*mi*ca \xmark & a*gro*quí*mi*ca \cmark \\
-ajuizar & a*ju-i*zar \xmark & a*ju*i*zar \cmark \\
-baraúna & ba*ra-ú*na \xmark & ba*ra*ú*na \cmark \\
-casuísta & ca*su-ís*ta \xmark & ca*su*ís*ta \cmark \\
-catatônico & ca*ta-tô*ni*co \xmark & ca*ta*tô*ni*co \cmark \\
-conteudista & con*te-u*dis*ta \xmark & con*te-u*dis*ta \xmark \\
-continuísta & con*ti*nu-ís*ta \xmark & con*ti*nu*ís*ta \cmark \\
-czarista & c.za*ris*ta \xmark & cza*ris*ta \cmark \\
-decair & de*ca-ir \xmark & de*ca*ir \cmark \\
-deísta & de-ís*ta \xmark & de*ís*ta \cmark \\
-diácono & di-á*co*no \xmark & di*á*co*no \cmark \\
-elegíaco & e*le*gí-a*co \xmark & e*le*gí*a*co \cmark \\
-faraônico & fa*ra-ô*ni*co \xmark & fa*ra*ô*ni*co \cmark \\
-feérico & fe-é*ri*co \xmark & fe*é*ri*co \cmark \\
-hidroavião & hi*dro*a*vi-ão \xmark & hi*dro*a*vi*ão \cmark \\
-hodômetro & ho-dô*me*tro \xmark & ho*dô*me*tro \cmark \\
-inconciliável & in*con*ci*li-á*vel \xmark & in*con*ci*li*á*vel \cmark \\
-ioiô & i.o-i.ô \xmark & i.o-i.ô \xmark \\
-macrobiótica & ma*cro*bi-ó*ti*ca \xmark & ma*cro*bi*ó*ti*ca \cmark \\
-marruá & mar*ru-á \xmark & mar*ru*á \cmark \\
-meteórico & me*te-ó*ri*co \xmark & me*te*ó*ri*co \cmark \\
-panteísta & pan*te-ís*ta \xmark & pan*te*ís*ta \cmark \\
-papaína & pa*pa-í*na \xmark & pa*pa*í*na \cmark \\
-patuá & pa*tu-á \xmark & pa*tu*á \cmark \\
-perdoável & per*do-á*vel \xmark & per*do*á*vel \cmark \\
-prostituído & pros*ti*tu-í*do \xmark & pros*ti*tu*í*do \cmark \\
-pulôver & pu-lô*ver \xmark & pu*lô*ver \cmark \\
-ravióli & ra*vi-ó*li \xmark & ra*vi*ó*li \cmark \\
-reincorporação & re-in*cor*po*ra*ção \xmark & re*in*cor*po*ra*ção \cmark \\
-reingresso & re-in*gres*so \xmark & re*in*gres*so \cmark \\
-reinquirir & re-in*qui*rir \xmark & re-in*qui*rir \xmark \\
-reinstalação & re-ins*ta*la*ção \xmark & re*ins*ta*la*ção \cmark \\
-reinterpretar & re-in*ter*pre*tar \xmark & re*in*ter*pre*tar \cmark \\
-saião & sai-ão \xmark & sai*ão \cmark \\
-samaúma & sa*ma-ú*ma \xmark & sa*ma*ú*ma \cmark \\
-sublocação & su.b-lo*ca*ção \xmark & sub*lo*ca*ção \cmark \\
-turboélice & tur*bo-é*li*ce \xmark & tur*bo*é*li*ce \cmark \\
-ventoinha & ven*to-i*nha \xmark & ven*to*i*nha \cmark \\
-voyeurista & voy-eu*ris*ta \xmark & voy-eu*ris*ta \xmark \\
-alagoinha & a*la*go-i*nha \xmark & a*la*go*i*nha \cmark \\
-aluvião & a*lu*vi-ão \xmark & a*lu*vi*ão \cmark \\
-amiúde & a*mi-ú*de \xmark & a*mi*ú*de \cmark \\
-amoníaco & a*mo*ní-a*co \xmark & a*mo*ní*a*co \cmark \\
-antagônico & an*ta-gô*ni*co \xmark & an*ta*gô*ni*co \cmark \\
-antiquíssimo & an*ti-quís*si*mo \xmark & an*ti*quís*si*mo \cmark \\
-babuíno & ba*bu-í*no \xmark & ba*bu*í*no \cmark \\
-bahamense & ba-ha*men*se \xmark & ba-ha*men*se \xmark \\
-barômetro & ba-rô*me*tro \xmark & ba*rô*me*tro \cmark \\
-bibelô & bi*be-lô \xmark & bi*be*lô \cmark \\
-biótipo & bi-ó*ti*po \xmark & bi*ó*ti*po \cmark \\
-bisavô & bi*sa-vô \xmark & bi*sa*vô \cmark \\
-bocaiuva & bo*cai-u*va \xmark & bo*cai-u*va \xmark \\
-borderô & bor*de-rô \xmark & bor*de*rô \cmark \\
-brechtiano & bre.ch*ti*a*no \xmark & bre.ch*ti*a*no \xmark \\
-cariótipo & ca*ri-ó*ti*po \xmark & ca*ri*ó*ti*po \cmark \\
-chororô & cho*ro-rô \xmark & cho*ro*rô \cmark \\
-copaíba & co*pa-í*ba \xmark & co*pa*í*ba \cmark \\
-czarismo & c.za*ris*mo \xmark & cza*ris*mo \cmark \\
-darwinista & dar-wi*nis*ta \xmark & dar-wi*nis*ta \xmark \\
-decaída & de*ca-í*da \xmark & de*ca*í*da \cmark \\
-diálise & di-á*li*se \xmark & di*á*li*se \cmark \\
-diástole & di-ás*to*le \xmark & di*ás*to*le \cmark \\
-esquálido & es-quá*li*do \xmark & es*quá*li*do \cmark \\
-esvair & es*va-ir \xmark & es*va*ir \cmark \\
-farisaísmo & fa*ri*sa-ís*mo \xmark & fa*ri*sa*ís*mo \cmark \\
-fiduciário & fi*du*ci-á*ri*o \xmark & fi*du*ci*á*ri*o \cmark \\
-filarmônico & fi*lar-mô*ni*co \xmark & fi*lar*mô*ni*co \cmark \\
-financiável & fi*nan*ci-á*vel \xmark & fi*nan*ci*á*vel \cmark \\
-fruir & fru-ir \xmark & fru*ir \cmark \\
-fuzuê & fu*zu-ê \xmark & fu*zu*ê \cmark \\
-geômetra & ge-ô*me*tra \xmark & ge*ô*me*tra \cmark \\
 gnose & g.no*se \xmark & gno*se \cmark \\
-jabô & ja-bô \xmark & ja*bô \cmark \\
-janaúba & ja*na-ú*ba \xmark & ja*na*ú*ba \cmark \\
-lusíada & lu*sí-a*da \xmark & lu*sí*a*da \cmark \\
-maçônico & ma-çô*ni*co \xmark & ma*çô*ni*co \cmark \\
-macrobiótico & ma*cro*bi-ó*ti*co \xmark & ma*cro*bi*ó*ti*co \cmark \\
-mafuá & ma*fu-á \xmark & ma*fu*á \cmark \\
-manômetro & ma-nô*me*tro \xmark & ma*nô*me*tro \cmark \\
-mediúnico & me*di-ú*ni*co \xmark & me*di*ú*ni*co \cmark \\
-microrregião & mi*cror*re*gi-ão \xmark & mi*cror*re*gi*ão \cmark \\
-neoplatônico & ne*o*pla-tô*ni*co \xmark & ne*o*pla*tô*ni*co \cmark \\
-patchuli & pat*chu*li \cmark & pat-chu*li \xmark \\
-pecuário & pe*cu-á*ri*o \xmark & pe*cu*á*ri*o \cmark \\
-psicolinguista & p.si*co*lin*guis*ta \xmark & psi*co*lin*guis*ta \cmark \\
-psicolinguística & p.si*co*lin*guís*ti*ca \xmark & psi*co*lin*guís*ti*ca \cmark \\
-psicomotor & p.si*co*mo*tor \xmark & psi*co*mo*tor \cmark \\
-psicomotricista & p.si*co*mo*tri*cis*ta \xmark & psi*co*mo*tri*cis*ta \cmark \\
-psicopatia & p.si*co*pa*ti*a \xmark & psi*co*pa*ti*a \cmark \\
-psicopedagogo & p.si*co*pe*da*go*go \xmark & psi*co*pe*da*go*go \cmark \\
-psicossomática & p.si*cos*so*má*ti*ca \xmark & psi*cos*so*má*ti*ca \cmark \\
-reconstituinte & re*cons*ti*tu-in*te \xmark & re*cons*ti*tu-in*te \xmark \\
-reincidir & re-in*ci*dir \xmark & re*in*ci*dir \cmark \\
-saruê & sa*ru-ê \xmark & sa*ru*ê \cmark \\
-subaquático & su*ba-quá*ti*co \xmark & su*ba*quá*ti*co \cmark \\
-subliteratura & su.b-li*te*ra*tu*ra \xmark & sub*li*te*ra*tu*ra \cmark \\
-subsidiário & sub*si*di-á*ri*o \xmark & sub*si*di*á*ri*o \cmark \\
-substituível & subs*ti*tu-í*vel \xmark & subs*ti*tu*í*vel \cmark \\
-teutônico & teu-tô*ni*co \xmark & teu*tô*ni*co \cmark \\
-tmese & t.me*se \xmark & tme*se \cmark \\
-toboágua & to*bo-á*gua \xmark & to*bo*á*gua \cmark \\
-aldeão & al*de-ão \xmark & al*de*ão \cmark \\
-amniocentese & am*ni*o*cen*te*se \cmark & a.m-ni*o*cen*te*se \xmark \\
-anamnese & a*nam*ne*se \cmark & a*na.m-ne*se \xmark \\
-anauê & a*nau-ê \xmark & a*nau*ê \cmark \\
-antipatriótico & an*ti*pa*tri-ó*ti*co \xmark & an*ti*pa*tri*ó*ti*co \cmark \\
-antônimo & an-tô*ni*mo \xmark & an*tô*ni*mo \cmark \\
-antropônimo & an*tro-pô*ni*mo \xmark & an*tro*pô*ni*mo \cmark \\
-aviário & a*vi-á*ri*o \xmark & a*vi*á*ri*o \cmark \\
-babalaô & ba*ba*la-ô \xmark & ba*ba*la*ô \cmark \\
-braúna & bra-ú*na \xmark & bra*ú*na \cmark \\
-corruíra & cor*ru-í*ra \xmark & cor*ru*í*ra \cmark \\
-corrupião & cor*ru*pi-ão \xmark & cor*ru*pi*ão \cmark \\
-decaído & de*ca-í*do \xmark & de*ca*í*do \cmark \\
-deificação & de-i*fi*ca*ção \xmark & de-i*fi*ca*ção \xmark \\
-demiurgo & de*mi-ur*go \xmark & de*mi*ur*go \cmark \\
-descair & des*ca-ir \xmark & des*ca*ir \cmark \\
-desembainhar & de*sem*ba-i*nhar \xmark & de*sem*ba*i*nhar \cmark \\
-diáfano & di-á*fa*no \xmark & di*á*fa*no \cmark \\
-dicotômico & di*co-tô*mi*co \xmark & di*co*tô*mi*co \cmark \\
-dodecafônico & do*de*ca-fô*ni*co \xmark & do*de*ca*fô*ni*co \cmark \\
-ensaístico & en*sa-ís*ti*co \xmark & en*sa*ís*ti*co \cmark \\
-entusiástico & en*tu*si-ás*ti*co \xmark & en*tu*si*ás*ti*co \cmark \\
-epônimo & e-pô*ni*mo \xmark & e*pô*ni*mo \cmark \\
-espectrofotômetro & es*pec*tro*fo-tô*me*tro \xmark & es*pec*tro*fo*tô*me*tro \cmark \\
-estatuária & es*ta*tu-á*ri*a \xmark & es*ta*tu*á*ri*a \cmark \\
-faim & fa-im \xmark & fa-im \xmark \\
-fitoquímica & fi*to-quí*mi*ca \xmark & fi*to*quí*mi*ca \cmark \\
-formaldeído & for*mal*de-í*do \xmark & for*mal*de*í*do \cmark \\
-fuinha & fu-i*nha \xmark & fu*i*nha \cmark \\
-gabião & ga*bi-ão \xmark & ga*bi*ão \cmark \\
-gauchada & ga-u*cha*da \xmark & ga-u*cha*da \xmark \\
-gauchismo & ga-u*chis*mo \xmark & ga-u*chis*mo \xmark \\
-geriátrico & ge*ri-á*tri*co \xmark & ge*ri*á*tri*co \cmark \\
-gipsita & gip*si*ta \cmark & gip-si*ta \xmark \\
-guião & gui-ão \xmark & gui*ão \cmark \\
-ilíaco & i*lí-a*co \xmark & i*lí*a*co \cmark \\
-iniciático & i*ni*ci-á*ti*co \xmark & i*ni*ci*á*ti*co \cmark \\
-itapuá & i*ta*pu-á \xmark & i*ta*pu*á \cmark \\
-japuí & ja*pu-í \xmark & ja*pu*í \cmark \\
-jesuítico & je*su-í*ti*co \xmark & je*su*í*ti*co \cmark \\
-lamaísmo & la*ma-ís*mo \xmark & la*ma*ís*mo \cmark \\
-mantô & man-tô \xmark & man*tô \cmark \\
-metapsicologia & me*tap*si*co*lo*gi*a \cmark & me*tap-si*co*lo*gi*a \xmark \\
-mitocôndria & mi*to-côn*dri*a \xmark & mi*to*côn*dri*a \cmark \\
-miudeza & mi-u*de*za \xmark & mi-u*de*za \xmark \\
-monomaníaco & mo*no*ma*ní-a*co \xmark & mo*no*ma*ní*a*co \cmark \\
-museólogo & mu*se-ó*lo*go \xmark & mu*se*ó*lo*go \cmark \\
-ninfomaníaca & nin*fo*ma*ní-a*ca \xmark & nin*fo*ma*ní*a*ca \cmark \\
-nobiliárquico & no*bi*li-ár*qui*co \xmark & no*bi*li*ár*qui*co \cmark \\
-odômetro & o-dô*me*tro \xmark & o*dô*me*tro \cmark \\
-orgiástico & or*gi-ás*ti*co \xmark & or*gi*ás*ti*co \cmark \\
-painço & pa-in*ço \xmark & pa-in*ço \xmark \\
-pantagruélico & pan*ta*gru-é*li*co \xmark & pan*ta*gru*é*li*co \cmark \\
-parquímetro & par-quí*me*tro \xmark & par*quí*me*tro \cmark \\
-pixaim & pi*xa-im \xmark & pi*xa-im \xmark \\
+gnosiologia & g.no*si*o*lo*gi*a \xmark & gno*si*o*lo*gi-a \xmark \\
+gnosticismo & g.nos*ti*cis*mo \xmark & gnos*ti*cis*mo \cmark \\
+gnóstico & g.nós*ti*co \xmark & gnós*ti*co \cmark \\
+hiperalgesia & hi*pe.r-al*ge*si*a \xmark & hi*pe.r-al*ge*si-a \xmark \\
+mnemônica & m.ne-mô*ni*ca \xmark & mne*mô*ni*ca \cmark \\
+mnemônico & m.ne-mô*ni*co \xmark & mne*mô*ni*co \cmark \\
+neerlandês & ne.er*lan*dês \xmark & ne.er*lan*dês \xmark \\
+núpcias & núp*ci.as \xmark & núp*ci.as \xmark \\
 pneumática & p.neu*má*ti*ca \xmark & pneu*má*ti*ca \cmark \\
 pneumático & p.neu*má*ti*co \xmark & pneu*má*ti*co \cmark \\
-preá & pre-á \xmark & pre*á \cmark \\
-priápico & pri-á*pi*co \xmark & pri*á*pi*co \cmark \\
+pneumatologia & p.neu*ma*to*lo*gi*a \xmark & pneu*ma*to*lo*gi-a \xmark \\
+pneumococo & p.neu*mo*co*co \xmark & pneu*mo*co*co \cmark \\
+pneumoconiose & p.neu*mo*co*ni*o*se \xmark & pneu*mo*co*ni*o*se \cmark \\
+pneumogástrico & p.neu*mo*gás*tri*co \xmark & pneu*mo*gás*tri*co \cmark \\
+pneumologia & p.neu*mo*lo*gi*a \xmark & pneu*mo*lo*gi-a \xmark \\
+pneumonia & p.neu*mo*ni*a \xmark & pneu*mo*ni-a \xmark \\
+pneumônico & p.neu-mô*ni*co \xmark & pneu*mô*ni*co \cmark \\
+pneumotórax & p.neu*mo*tó*rax \xmark & pneu*mo*tó*rax \cmark \\
+pneu & p.neu \xmark & pneu \cmark \\
+pseudônimo & p.seu-dô*ni*mo \xmark & pseu*dô*ni*mo \cmark \\
+psicanálise & p.si*ca*ná*li*se \xmark & psi*ca*ná*li*se \cmark \\
+psicanalista & p.si*ca*na*lis*ta \xmark & psi*ca*na*lis*ta \cmark \\
+psicanalítico & p.si*ca*na*lí*ti*co \xmark & psi*ca*na*lí*ti*co \cmark \\
+psicodrama & p.si*co*dra*ma \xmark & psi*co*dra*ma \cmark \\
+psicografia & p.si*co*gra*fi*a \xmark & psi*co*gra*fi-a \xmark \\
+psicógrafo & p.si*có*gra*fo \xmark & psi*có*gra*fo \cmark \\
+psicolinguista & p.si*co*lin*guis*ta \xmark & psi*co*lin*guis*ta \cmark \\
+psicologia & p.si*co*lo*gi*a \xmark & psi*co*lo*gi-a \xmark \\
+psicologicamente & p.si*co*lo*gi*ca*men*te \xmark & psi*co*lo*gi*ca*men*te \cmark \\
+psicológico & p.si*co*ló*gi*co \xmark & psi*co*ló*gi*co \cmark \\
+psicologismo & p.si*co*lo*gis*mo \xmark & psi*co*lo*gis*mo \cmark \\
+psicologista & p.si*co*lo*gis*ta \xmark & psi*co*lo*gis*ta \cmark \\
+psicologizar & p.si*co*lo*gi*zar \xmark & psi*co*lo*gi*zar \cmark \\
+psicólogo & p.si*có*lo*go \xmark & psi*có*lo*go \cmark \\
+psicométrico & p.si*co*mé*tri*co \xmark & psi*co*mé*tri*co \cmark \\
+psicomotor & p.si*co*mo*tor \xmark & psi*co*mo*tor \cmark \\
+psicomotricidade & p.si*co*mo*tri*ci*da*de \xmark & psi*co*mo*tri*ci*da*de \cmark \\
+psicopata & p.si*co*pa*ta \xmark & psi*co*pa*ta \cmark \\
+psicopático & p.si*co*pá*ti*co \xmark & psi*co*pá*ti*co \cmark \\
+psicopatologia & p.si*co*pa*to*lo*gi*a \xmark & psi*co*pa*to*lo*gi-a \xmark \\
+psicopatológico & p.si*co*pa*to*ló*gi*co \xmark & psi*co*pa*to*ló*gi*co \cmark \\
+psicopedagogia & p.si*co*pe*da*go*gi*a \xmark & psi*co*pe*da*go*gi-a \xmark \\
 psicopedagógico & p.si*co*pe*da*gó*gi*co \xmark & psi*co*pe*da*gó*gi*co \cmark \\
+psicopedagogo & p.si*co*pe*da*go*go \xmark & psi*co*pe*da*go*go \cmark \\
+psicose & p.si*co*se \xmark & psi*co*se \cmark \\
+psicossexual & p.si*cos*se*xu*al \xmark & psi*cos*se*xu*al \cmark \\
 psicossomático & p.si*cos*so*má*ti*co \xmark & psi*cos*so*má*ti*co \cmark \\
+psicotécnico & p.si*co*téc*ni*co \xmark & psi*co*téc*ni*co \cmark \\
+psicoterapeuta & p.si*co*te*ra*peu*ta \xmark & psi*co*te*ra*peu*ta \cmark \\
+psicoterapia & p.si*co*te*ra*pi*a \xmark & psi*co*te*ra*pi-a \xmark \\
+psicoterápico & p.si*co*te*rá*pi*co \xmark & psi*co*te*rá*pi*co \cmark \\
+psicótico & p.si*có*ti*co \xmark & psi*có*ti*co \cmark \\
 psicotrópico & p.si*co*tró*pi*co \xmark & psi*co*tró*pi*co \cmark \\
+psique & p.si*que \xmark & psi*que \cmark \\
+psiquiatra & p.si*qui*a*tra \xmark & psi*qui*a*tra \cmark \\
+psiquiatria & p.si*qui*a*tri*a \xmark & psi*qui*a*tri-a \xmark \\
+psiquiátrico & p.si*qui-á*tri*co \xmark & psi*qui*á*tri*co \cmark \\
+psíquico & p.sí*qui*co \xmark & psí*qui*co \cmark \\
+psiquismo & p.si*quis*mo \xmark & psi*quis*mo \cmark \\
+psitaciforme & p.si*ta*ci*for*me \xmark & psi*ta*ci*for*me \cmark \\
+psitacismo & p.si*ta*cis*mo \xmark & psi*ta*cis*mo \cmark \\
+psoas & p.so*as \xmark & p.so*as \xmark \\
+psoríase & p.so*rí-a*se \xmark & p.so*rí*a*se \xmark \\
 pterossauro & p.te*ros*sau*ro \xmark & pte*ros*sau*ro \cmark \\
-quilohertz & qui*lo-hertz \xmark & qui*lo-hertz \xmark \\
-recôndito & re-côn*di*to \xmark & re*côn*di*to \cmark \\
-reimplantação & re-im*plan*ta*ção \xmark & re*im*plan*ta*ção \cmark \\
-reincorporar & re-in*cor*po*rar \xmark & re*in*cor*po*rar \cmark \\
-reingressar & re-in*gres*sar \xmark & re*in*gres*sar \cmark \\
-reinvestir & re-in*ves*tir \xmark & re*in*ves*tir \cmark \\
-restituível & res*ti*tu-í*vel \xmark & res*ti*tu*í*vel \cmark \\
-retrair & re*tra-ir \xmark & re*tra*ir \cmark \\
-rodamoinho & ro*da*mo-i*nho \xmark & ro*da*mo*i*nho \cmark \\
-roído & ro-í*do \xmark & ro*í*do \cmark \\
-ruão & ru-ão \xmark & ru*ão \cmark \\
-salomônico & sa*lo-mô*ni*co \xmark & sa*lo*mô*ni*co \cmark \\
-sardônico & sar-dô*ni*co \xmark & sar*dô*ni*co \cmark \\
-semiólogo & se*mi-ó*lo*go \xmark & se*mi*ó*lo*go \cmark \\
-solipsismo & so*lip*sis*mo \cmark & so*lip-sis*mo \xmark \\
-sumaúma & su*ma-ú*ma \xmark & su*ma*ú*ma \cmark \\
-tataravô & ta*ta*ra-vô \xmark & ta*ta*ra*vô \cmark \\
-termoquímica & ter*mo-quí*mi*ca \xmark & ter*mo*quí*mi*ca \cmark \\
-topônimo & to-pô*ni*mo \xmark & to*pô*ni*mo \cmark \\
-toxicômano & to*xi-cô*ma*no \xmark & to*xi*cô*ma*no \cmark \\
-trisavô & tri*sa-vô \xmark & tri*sa*vô \cmark \\
-triunvirato & tri-un*vi*ra*to \xmark & tri*un*vi*ra*to \cmark \\
-voyeurístico & voy-eu*rís*ti*co \xmark & voy-eu*rís*ti*co \xmark \\
-xintoísmo & xin*to-ís*mo \xmark & xin*to*ís*mo \cmark \\
-absenteísta & ab*sen*te-ís*ta \xmark & ab*sen*te*ís*ta \cmark \\
-aeroviário & a*e*ro*vi-á*ri*o \xmark & a*e*ro*vi*á*ri*o \cmark \\
-afluir & a*flu-ir \xmark & a*flu*ir \cmark \\
-agroquímico & a*gro-quí*mi*co \xmark & a*gro*quí*mi*co \cmark \\
-aguaí & a*gua-í \xmark & a*gua*í \cmark \\
-alquímico & al-quí*mi*co \xmark & al*quí*mi*co \cmark \\
-amnesia & am*ne*si*a \cmark & a.m-ne*si*a \xmark \\
-amnésico & am*né*si*co \cmark & a.m-né*si*co \xmark \\
-anafrodisíaco & a*na*fro*di*sí-a*co \xmark & a*na*fro*di*sí*a*co \cmark \\
-antialcoólico & an*ti*al*co-ó*li*co \xmark & an*ti*al*co*ó*li*co \cmark \\
-antinômico & an*ti-nô*mi*co \xmark & an*ti*nô*mi*co \cmark \\
-anuir & a*nu-ir \xmark & a*nu*ir \cmark \\
-arapuá & a*ra*pu-á \xmark & a*ra*pu*á \cmark \\
-aríete & a*rí-e*te \xmark & a*rí-e*te \xmark \\
-associável & as*so*ci-á*vel \xmark & as*so*ci*á*vel \cmark \\
-atribuível & a*tri*bu-í*vel \xmark & a*tri*bu*í*vel \cmark \\
-babilônico & ba*bi-lô*ni*co \xmark & ba*bi*lô*ni*co \cmark \\
-balaustrada & ba*la-us*tra*da \xmark & ba*la-us*tra*da \xmark \\
-beócio & be-ó*ci*o \xmark & be*ó*ci*o \cmark \\
-biófilo & bi-ó*fi*lo \xmark & bi*ó*fi*lo \cmark \\
-biunívoco & bi-u*ní*vo*co \xmark & bi*u*ní*vo*co \cmark \\
-boião & boi-ão \xmark & boi*ão \cmark \\
-boiuna & boi-u*na \xmark & boi*u*na \cmark \\
-butiá & bu*ti-á \xmark & bu*ti*á \cmark \\
-caingangue & ca-in*gan*gue \xmark & ca-in*gan*gue \xmark \\
-carnaíba & car*na-í*ba \xmark & car*na*í*ba \cmark \\
-caúna & ca-ú*na \xmark & ca*ú*na \cmark \\
-ciática & ci-á*ti*ca \xmark & ci*á*ti*ca \cmark \\
-clepsidra & clep*si*dra \cmark & clep-si*dra \xmark \\
-codeína & co*de-í*na \xmark & co*de*í*na \cmark \\
-conciliábulo & con*ci*li-á*bu*lo \xmark & con*ci*li*á*bu*lo \cmark \\
-conciliável & con*ci*li-á*vel \xmark & con*ci*li*á*vel \cmark \\
-condoído & con*do-í*do \xmark & con*do*í*do \cmark \\
-confluir & con*flu-ir \xmark & con*flu*ir \cmark \\
-congruência & con*gru-ên*ci*a \xmark & con*gru*ên*ci*a \cmark \\
-crapô & cra-pô \xmark & cra*pô \cmark \\
-criptônimo & crip-tô*ni*mo \xmark & crip*tô*ni*mo \cmark \\
-deão & de-ão \xmark & de*ão \cmark \\
-decacampeão & de*ca*cam*pe-ão \xmark & de*ca*cam*pe*ão \cmark \\
-demiúrgico & de*mi-úr*gi*co \xmark & de*mi*úr*gi*co \cmark \\
-depreciável & de*pre*ci-á*vel \xmark & de*pre*ci*á*vel \cmark \\
-descaída & des*ca-í*da \xmark & des*ca*í*da \cmark \\
-dzeta & d.ze*ta \xmark & d.ze*ta \xmark \\
-elefantíase & e*le*fan*tí-a*se \xmark & e*le*fan*tí*a*se \cmark \\
-eletroímã & e*le*tro-í*mã \xmark & e*le*tro*í*mã \cmark \\
-eólico & e-ó*li*co \xmark & e*ó*li*co \cmark \\
-eólio & e-ó*li*o \xmark & e*ó*li*o \cmark \\
-epifenômeno & e*pi*fe-nô*me*no \xmark & e*pi*fe*nô*me*no \cmark \\
-escarabeídeo & es*ca*ra*be-í*de*o \xmark & es*ca*ra*be*í*de*o \cmark \\
-espadaúdo & es*pa*da-ú*do \xmark & es*pa*da*ú*do \cmark \\
-espeleólogo & es*pe*le-ó*lo*go \xmark & es*pe*le*ó*lo*go \cmark \\
-faiscante & fa-is*can*te \xmark & fa-is*can*te \xmark \\
-feiura & fei-u*ra \xmark & fei*u*ra \cmark \\
-fotômetro & fo-tô*me*tro \xmark & fo*tô*me*tro \cmark \\
-franqueável & fran*que-á*vel \xmark & fran*que*á*vel \cmark \\
-gastrointestinal & gas*tro-in*tes*ti*nal \xmark & gas*tro*in*tes*ti*nal \cmark \\
-gauchar & ga-u*char \xmark & ga-u*char \xmark \\
-gnosticismo & g.nos*ti*cis*mo \xmark & gnos*ti*cis*mo \cmark \\
-gnóstico & g.nós*ti*co \xmark & gnós*ti*co \cmark \\
-gnu & g.nu \xmark & g.nu \xmark \\
-grafomaníaco & gra*fo*ma*ní-a*co \xmark & gra*fo*ma*ní*a*co \cmark \\
-grafômano & gra-fô*ma*no \xmark & gra*fô*ma*no \cmark \\
-grapiúna & gra*pi-ú*na \xmark & gra*pi*ú*na \cmark \\
-heterônimo & he*te-rô*ni*mo \xmark & he*te*rô*ni*mo \cmark \\
-hexacampeão & he*xa*cam*pe-ão \xmark & he*xa*cam*pe*ão \cmark \\
-hinduísta & hin*du-ís*ta \xmark & hin*du*ís*ta \cmark \\
-holonômico & ho*lo-nô*mi*co \xmark & ho*lo*nô*mi*co \cmark \\
-homofônico & ho*mo-fô*ni*co \xmark & ho*mo*fô*ni*co \cmark \\
-ibijaú & i*bi*ja-ú \xmark & i*bi*ja*ú \cmark \\
-idiótico & i*di-ó*ti*co \xmark & i*di*ó*ti*co \cmark \\
-imbuir & im*bu-ir \xmark & im*bu*ir \cmark \\
-inclinômetro & in*cli-nô*me*tro \xmark & in*cli*nô*me*tro \cmark \\
-irreconciliável & ir*re*con*ci*li-á*vel \xmark & ir*re*con*ci*li*á*vel \cmark \\
-irreligião & ir*re*li*gi-ão \xmark & ir*re*li*gi*ão \cmark \\
-irrenunciável & ir*re*nun*ci-á*vel \xmark & ir*re*nun*ci*á*vel \cmark \\
-isquêmico & is-quê*mi*co \xmark & is*quê*mi*co \cmark \\
-itapiúna & i*ta*pi-ú*na \xmark & i*ta*pi*ú*na \cmark \\
-juá & ju-á \xmark & ju*á \cmark \\
-lamaísta & la*ma-ís*ta \xmark & la*ma*ís*ta \cmark \\
-luteína & lu*te-í*na \xmark & lu*te*í*na \cmark \\
-macrorregião & ma*cror*re*gi-ão \xmark & ma*cror*re*gi*ão \cmark \\
-mandrião & man*dri-ão \xmark & man*dri*ão \cmark \\
-masdeísmo & mas*de-ís*mo \xmark & mas*de*ís*mo \cmark \\
-maué & mau-é \xmark & mau*é \cmark \\
-mediático & me*di-á*ti*co \xmark & me*di*á*ti*co \cmark \\
-melômano & me-lô*ma*no \xmark & me*lô*ma*no \cmark \\
-mnemônica & m.ne-mô*ni*ca \xmark & mne*mô*ni*ca \cmark \\
-moinha & mo-i*nha \xmark & mo*i*nha \cmark \\
-monômero & mo-nô*me*ro \xmark & mo*nô*me*ro \cmark \\
-monoquíni & mo*no-quí*ni \xmark & mo*no*quí*ni \cmark \\
-monoteísta & mo*no*te-ís*ta \xmark & mo*no*te*ís*ta \cmark \\
-mortuárias & mor*tu-á*ri*as \xmark & mor*tu*á*ri*as \cmark \\
-mucuim & mu*cu-im \xmark & mu*cu-im \xmark \\
-negligenciável & ne*gli*gen*ci-á*vel \xmark & ne*gli*gen*ci*á*vel \cmark \\
-neuropsiquiatria & neu*rop*si*qui*a*tri*a \cmark & neu*rop-si*qui*a*tri*a \xmark \\
-oboísta & o*bo-ís*ta \xmark & o*bo*ís*ta \cmark \\
-ofidiário & o*fi*di-á*ri*o \xmark & o*fi*di*á*ri*o \cmark \\
-oleína & o*le-í*na \xmark & o*le*í*na \cmark \\
-opiáceo & o*pi-á*ce*o \xmark & o*pi*á*ce*o \cmark \\
-pancreático & pan*cre-á*ti*co \xmark & pan*cre*á*ti*co \cmark \\
-panô & pa-nô \xmark & pa*nô \cmark \\
-parquê & par-quê \xmark & par*quê \cmark \\
-parvoíce & par*vo-í*ce \xmark & par*vo*í*ce \cmark \\
-patenteável & pa*ten*te-á*vel \xmark & pa*ten*te*á*vel \cmark \\
-peã & pe-ã \xmark & pe*ã \cmark \\
-periósteo & pe*ri-ós*te*o \xmark & pe*ri*ós*te*o \cmark \\
-picuá & pi*cu-á \xmark & pi*cu*á \cmark \\
-piquê & pi-quê \xmark & pi*quê \cmark \\
-piromaníaco & pi*ro*ma*ní-a*co \xmark & pi*ro*ma*ní*a*co \cmark \\
-piruá & pi*ru-á \xmark & pi*ru*á \cmark \\
-piúria & pi-ú*ri*a \xmark & pi*ú*ri*a \cmark \\
-plagiário & pla*gi-á*ri*o \xmark & pla*gi*á*ri*o \cmark \\
-plebeísmo & ple*be-ís*mo \xmark & ple*be*ís*mo \cmark \\
-plenipotenciário & ple*ni*po*ten*ci-á*ri*o \xmark & ple*ni*po*ten*ci*á*ri*o \cmark \\
-pneumatologia & p.neu*ma*to*lo*gi*a \xmark & pneu*ma*to*lo*gi*a \cmark \\
-pneumônico & p.neu-mô*ni*co \xmark & pneu*mô*ni*co \cmark \\
-polifônico & po*li-fô*ni*co \xmark & po*li*fô*ni*co \cmark \\
-politeísmo & po*li*te-ís*mo \xmark & po*li*te*ís*mo \cmark \\
-politeísta & po*li*te-ís*ta \xmark & po*li*te*ís*ta \cmark \\
-politiquês & po*li*ti-quês \xmark & po*li*ti*quês \cmark \\
-procaína & pro*ca-í*na \xmark & pro*ca*í*na \cmark \\
-pronunciável & pro*nun*ci-á*vel \xmark & pro*nun*ci*á*vel \cmark \\
-pseudociência & p.seu*do*ci*ên*ci*a \xmark & pseu*do*ci*ên*ci*a \cmark \\
-psicofísico & p.si*co*fí*si*co \xmark & psi*co*fí*si*co \cmark \\
-psicologizar & p.si*co*lo*gi*zar \xmark & psi*co*lo*gi*zar \cmark \\
-psicometria & p.si*co*me*tri*a \xmark & psi*co*me*tri*a \cmark \\
-psicomotricidade & p.si*co*mo*tri*ci*da*de \xmark & psi*co*mo*tri*ci*da*de \cmark \\
-psicopatológico & p.si*co*pa*to*ló*gi*co \xmark & psi*co*pa*to*ló*gi*co \cmark \\
-psicoprofilaxia & p.si*co*pro*fi*la*xi*a \xmark & psi*co*pro*fi*la*xi*a \cmark \\
-psicossexual & p.si*cos*se*xu*al \xmark & psi*cos*se*xu*al \cmark \\
-psicoterapêutico & p.si*co*te*ra*pêu*ti*co \xmark & psi*co*te*ra*pêu*ti*co \cmark \\
-psiquê & p.si-quê \xmark & psi*quê \cmark \\
-psitacismo & p.si*ta*cis*mo \xmark & psi*ta*cis*mo \cmark \\
-psoríase & p.so*rí-a*se \xmark & p.so*rí*a*se \xmark \\
 ptose & p.to*se \xmark & pto*se \cmark \\
-puído & pu-í*do \xmark & pu*í*do \cmark \\
-putrião & pu*tri-ão \xmark & pu*tri*ão \cmark \\
-questiúncula & ques*ti-ún*cu*la \xmark & ques*ti*ún*cu*la \cmark \\
-reimportar & re-im*por*tar \xmark & re*im*por*tar \cmark \\
-reimpressão & re-im*pres*são \xmark & re*im*pres*são \cmark \\
-reinscrever & re-ins*cre*ver \xmark & re*ins*cre*ver \cmark \\
-reinserir & re-in*se*rir \xmark & re*in*se*rir \cmark \\
-remediável & re*me*di-á*vel \xmark & re*me*di*á*vel \cmark \\
-rubiácea & ru*bi-á*ce*a \xmark & ru*bi*á*ce*a \cmark \\
-ruinoso & ru-i*no*so \xmark & ru*i*no*so \cmark \\
-sainha & sa-i*nha \xmark & sa*i*nha \cmark \\
-sardônica & sar-dô*ni*ca \xmark & sar*dô*ni*ca \cmark \\
-satiríase & sa*ti*rí-a*se \xmark & sa*ti*rí*a*se \cmark \\
-setentrião & se*ten*tri-ão \xmark & se*ten*tri*ão \cmark \\
-sievert & si.e*vert \xmark & si.e*vert \xmark \\
-sismômetro & sis-mô*me*tro \xmark & sis*mô*me*tro \cmark \\
-solipsista & so*lip*sis*ta \cmark & so*lip-sis*ta \xmark \\
-suaíle & su*a-í*le \xmark & su*a*í*le \cmark \\
-sublevado & su.b-le*va*do \xmark & sub*le*va*do \cmark \\
+quartzito & quar-t.zi*to \xmark & quar-t.zi*to \xmark \\
+quartzo & quar-t.zo \xmark & quar-t.zo \xmark \\
+stalinismo & s.ta*li*nis*mo \xmark & sta*li*nis*mo \cmark \\
+stalinista & s.ta*li*nis*ta \xmark & sta*li*nis*ta \cmark \\
+subliminar & su.b-li*mi*nar \xmark & su.b-li*mi*nar \xmark \\
+sublingual & su.b-lin*gual \xmark & su.b-lin*gual \xmark \\
+sublinha & su.b-li*nha \xmark & su.b-li*nha \xmark \\
+subliteratura & su.b-li*te*ra*tu*ra \xmark & su.b-li*te*ra*tu*ra \xmark \\
+sublocação & su.b-lo*ca*ção \xmark & sub*lo*ca*ção \cmark \\
 sublocar & su.b-lo*car \xmark & sub*lo*car \cmark \\
-sublocatário & su.b-lo*ca*tá*ri*o \xmark & sub*lo*ca*tá*ri*o \cmark \\
-subsônico & sub-sô*ni*co \xmark & sub*sô*ni*co \cmark \\
-sucuriú & su*cu*ri-ú \xmark & su*cu*ri*ú \cmark \\
-suingar & su-in*gar \xmark & su-in*gar \xmark \\
-tacômetro & ta-cô*me*tro \xmark & ta*cô*me*tro \cmark \\
-taiuiá & tai-ui-á \xmark & tai-ui*á \xmark \\
-taiwanês & tai-wa*nês \xmark & tai-wa*nês \xmark \\
-talião & ta*li-ão \xmark & ta*li*ão \cmark \\
-tchecoslovaco & t.che*cos*lo*va*co \xmark & tche*cos*lo*va*co \cmark \\
-teísta & te-ís*ta \xmark & te*ís*ta \cmark \\
-teiú & tei-ú \xmark & tei*ú \cmark \\
-telômero & te-lô*me*ro \xmark & te*lô*me*ro \cmark \\
-teníase & te*ní-a*se \xmark & te*ní*a*se \cmark \\
-terciário & ter*ci-á*ri*o \xmark & ter*ci*á*ri*o \cmark \\
-torreão & tor*re-ão \xmark & tor*re*ão \cmark \\
-transeunte & tran*se-un*te \xmark & tran*se-un*te \xmark \\
-triádico & tri-á*di*co \xmark & tri*á*di*co \cmark \\
-tripanossomíase & tri*pa*nos*so*mí-a*se \xmark & tri*pa*nos*so*mí*a*se \cmark \\
-triunfador & tri-un*fa*dor \xmark & tri*un*fa*dor \cmark \\
-truísmo & tru-ís*mo \xmark & tru*ís*mo \cmark \\
-tuim & tu-im \xmark & tu-im \xmark \\
-tuiuiú & tui-ui-ú \xmark & tui-ui*ú \xmark \\
-tumultuário & tu*mul*tu-á*ri*o \xmark & tu*mul*tu*á*ri*o \cmark \\
+sublunar & su.b-lu*nar \xmark & sub*lu*nar \cmark \\
+tcheco & t.che*co \xmark & tche*co \cmark \\
+tmese & t.me*se \xmark & tme*se \cmark \\
 tzarista & t.za*ris*ta \xmark & tza*ris*ta \cmark \\
-vietcongue & vi*et*con*gue \cmark & vi*et-con*gue \xmark \\
-vitriólico & vi*tri-ó*li*co \xmark & vi*tri*ó*li*co \cmark \\
-vitríolo & vi*trí-o*lo \xmark & vi*trí*o*lo \cmark \\
-xilocaína & xi*lo*ca-í*na \xmark & xi*lo*ca*í*na \cmark \\
-abluir & a*blu-ir \xmark & a*blu*ir \cmark \\
-balaústre & ba*la-ús*tre \xmark & ba*la*ús*tre \cmark \\
-cabriúva & ca*bri-ú*va \xmark & ca*bri*ú*va \cmark \\
-daguerreótipo & da*guer*re-ó*ti*po \xmark & da*guer*re*ó*ti*po \cmark \\
-daltônico & dal-tô*ni*co \xmark & dal*tô*ni*co \cmark \\
-ecônomo & e-cô*no*mo \xmark & e*cô*no*mo \cmark \\
-egoístico & e*go-ís*ti*co \xmark & e*go*ís*ti*co \cmark \\
-eletrocardiógrafo & e*le*tro*car*di-ó*gra*fo \xmark & e*le*tro*car*di*ó*gra*fo \cmark \\
-eletroquímica & e*le*tro-quí*mi*ca \xmark & e*le*tro*quí*mi*ca \cmark \\
-eletroquímico & e*le*tro-quí*mi*co \xmark & e*le*tro*quí*mi*co \cmark \\
-embainhar & em*ba-i*nhar \xmark & em*ba*i*nhar \cmark \\
-faiscar & fa-is*car \xmark & fa-is*car \xmark \\
-faúlha & fa-ú*lha \xmark & fa*ú*lha \cmark \\
-galvanômetro & gal*va-nô*me*tro \xmark & gal*va*nô*me*tro \cmark \\
-hagiógrafo & ha*gi-ó*gra*fo \xmark & ha*gi*ó*gra*fo \cmark \\
-hebraísmo & he*bra-ís*mo \xmark & he*bra*ís*mo \cmark \\
-hebraísta & he*bra-ís*ta \xmark & he*bra*ís*ta \cmark \\
-hipertônico & hi*per-tô*ni*co \xmark & hi*per*tô*ni*co \cmark \\
-historiógrafo & his*to*ri-ó*gra*fo \xmark & his*to*ri*ó*gra*fo \cmark \\
-histrião & his*tri-ão \xmark & his*tri*ão \cmark \\
-jesuitismo & je*su-i*tis*mo \xmark & je*su*i*tis*mo \cmark \\
-macedônico & ma*ce-dô*ni*co \xmark & ma*ce*dô*ni*co \cmark \\
-ninfomaníaco & nin*fo*ma*ní-a*co \xmark & nin*fo*ma*ní*a*co \cmark \\
-paquímetro & pa-quí*me*tro \xmark & pa*quí*me*tro \cmark \\
-tabuinha & ta*bu-i*nha \xmark & ta*bu*i*nha \cmark \\
-taquígrafo & ta-quí*gra*fo \xmark & ta*quí*gra*fo \cmark \\
-taquímetro & ta-quí*me*tro \xmark & ta*quí*me*tro \cmark \\
-tectônico & tec-tô*ni*co \xmark & tec*tô*ni*co \cmark \\
-xintoísta & xin*to-ís*ta \xmark & xin*to*ís*ta \cmark \\
-abiótica & a*bi-ó*ti*ca \xmark & a*bi*ó*ti*ca \cmark \\
-abiótico & a*bi-ó*ti*co \xmark & a*bi*ó*ti*co \cmark \\
-abraâmico & a*bra-â*mi*co \xmark & a*bra*â*mi*co \cmark \\
-abstraído & abs*tra-í*do \xmark & abs*tra*í*do \cmark \\
-acauã & a*cau-ã \xmark & a*cau*ã \cmark \\
-acelerômetro & a*ce*le-rô*me*tro \xmark & a*ce*le*rô*me*tro \cmark \\
-acetaldeído & a*ce*tal*de-í*do \xmark & a*ce*tal*de*í*do \cmark \\
-acroleína & a*cro*le-í*na \xmark & a*cro*le*í*na \cmark \\
-adônis & a-dô*nis \xmark & a*dô*nis \cmark \\
-ainsa & a-in*sa \xmark & a-in*sa \xmark \\
-aiquidô & ai*qui-dô \xmark & ai*qui*dô \cmark \\
-alcíone & al*cí-o*ne \xmark & al*cí*o*ne \cmark \\
-aldeído & al*de-í*do \xmark & al*de*í*do \cmark \\
-aleúte & a*le-ú*te \xmark & a*le*ú*te \cmark \\
-aliá & a*li-á \xmark & a*li*á \cmark \\
-almóada & al*mó-a*da \xmark & al*mó-a*da \xmark \\
-aloé & a*lo-é \xmark & a*lo*é \cmark \\
-aloés & a*lo-és \xmark & a*lo*és \cmark \\
-aluá & a*lu-á \xmark & a*lu*á \cmark \\
-alvéolo & al*vé-o*lo \xmark & al*vé*o*lo \cmark \\
-amebíase & a*me*bí-a*se \xmark & a*me*bí*a*se \cmark \\
-âmnio & âm*ni*o \cmark & â.m-ni*o \xmark \\
-ancilostomíase & an*ci*los*to*mí-a*se \xmark & an*ci*los*to*mí*a*se \cmark \\
-anemômetro & a*ne-mô*me*tro \xmark & a*ne*mô*me*tro \cmark \\
-anfião & an*fi-ão \xmark & an*fi*ão \cmark \\
-anfictião & an*fic*ti-ão \xmark & an*fic*ti*ão \cmark \\
-anião & a*ni-ão \xmark & a*ni*ão \cmark \\
-aórtico & a-ór*ti*co \xmark & a*ór*ti*co \cmark \\
-apuí & a*pu-í \xmark & a*pu*í \cmark \\
-aquífero & a-quí*fe*ro \xmark & a*quí*fe*ro \cmark \\
-areão & a*re-ão \xmark & a*re*ão \cmark \\
-areópago & a*re-ó*pa*go \xmark & a*re*ó*pa*go \cmark \\
-arquidiácono & ar*qui*di-á*co*no \xmark & ar*qui*di*á*co*no \cmark \\
-arteríola & ar*te*rí-o*la \xmark & ar*te*rí*o*la \cmark \\
-assiriólogo & as*si*ri-ó*lo*go \xmark & as*si*ri*ó*lo*go \cmark \\
-astroquímica & as*tro-quí*mi*ca \xmark & as*tro*quí*mi*ca \cmark \\
-ateísta & a*te-ís*ta \xmark & a*te*ís*ta \cmark \\
-autoimunidade & au*to-i*mu*ni*da*de \xmark & au*to-i*mu*ni*da*de \xmark \\
-autônimo & au-tô*ni*mo \xmark & au*tô*ni*mo \cmark \\
-autonômico & au*to-nô*mi*co \xmark & au*to*nô*mi*co \cmark \\
-averroísmo & a*ver*ro-ís*mo \xmark & a*ver*ro*ís*mo \cmark \\
-bacteriófago & bac*te*ri-ó*fa*go \xmark & bac*te*ri*ó*fa*go \cmark \\
-baleárico & ba*le-á*ri*co \xmark & ba*le*á*ri*co \cmark \\
-banjoísta & ban*jo-ís*ta \xmark & ban*jo*ís*ta \cmark \\
-batuíra & ba*tu-í*ra \xmark & ba*tu*í*ra \cmark \\
-behaviorismo & be-ha*vi*o*ris*mo \xmark & be-ha*vi*o*ris*mo \xmark \\
-benjoim & ben*jo-im \xmark & ben*jo-im \xmark \\
-bibliógrafo & bi*bli-ó*gra*fo \xmark & bi*bli*ó*gra*fo \cmark \\
-bilião & bi*li-ão \xmark & bi*li*ão \cmark \\
-biótico & bi-ó*ti*co \xmark & bi*ó*ti*co \cmark \\
-biótopo & bi-ó*to*po \xmark & bi*ó*to*po \cmark \\
-biscainho & bis*ca-i*nho \xmark & bis*ca*i*nho \cmark \\
-blastômero & blas-tô*me*ro \xmark & blas*tô*me*ro \cmark \\
-boé & bo-é \xmark & bo*é \cmark \\
-bosníaco & bos*ní-a*co \xmark & bos*ní*a*co \cmark \\
-braquiópode & bra*qui-ó*po*de \xmark & bra*qui*ó*po*de \cmark \\
-bué & bu-é \xmark & bu*é \cmark \\
-cafarnaum & ca*far*na-um \xmark & ca*far*na-um \xmark \\
-cajuína & ca*ju-í*na \xmark & ca*ju*í*na \cmark \\
-camião & ca*mi-ão \xmark & ca*mi*ão \cmark \\
-candidíase & can*di*dí-a*se \xmark & can*di*dí*a*se \cmark \\
-canoísta & ca*no-ís*ta \xmark & ca*no*ís*ta \cmark \\
-carnaubal & car*na-u*bal \xmark & car*na-u*bal \xmark \\
-caroá & ca*ro-á \xmark & ca*ro*á \cmark \\
-caseína & ca*se-í*na \xmark & ca*se*í*na \cmark \\
-catequético & ca*te-qué*ti*co \xmark & ca*te*qué*ti*co \cmark \\
-catião & ca*ti-ão \xmark & ca*ti*ão \cmark \\
-cauã & cau-ã \xmark & cau*ã \cmark \\
-celíaco & ce*lí-a*co \xmark & ce*lí*a*co \cmark \\
-cnidário & c.ni*dá*ri*o \xmark & c.ni*dá*ri*o \xmark \\
-coimbrão & co-im*brão \xmark & co*im*brão \cmark \\
-coleóptero & co*le-óp*te*ro \xmark & co*le*óp*te*ro \cmark \\
-contraindicação & con*tra-in*di*ca*ção \xmark & con*tra*in*di*ca*ção \cmark \\
-contribuidor & con*tri*bu-i*dor \xmark & con*tri*bu*i*dor \cmark \\
-coriáceo & co*ri-á*ce*o \xmark & co*ri*á*ce*o \cmark \\
-curião & cu*ri-ão \xmark & cu*ri*ão \cmark \\
-curiúva & cu*ri-ú*va \xmark & cu*ri*ú*va \cmark \\
-cuxiú & cu*xi-ú \xmark & cu*xi*ú \cmark \\
-decurião & de*cu*ri-ão \xmark & de*cu*ri*ão \cmark \\
-deiscente & de-is*cen*te \xmark & de-is*cen*te \xmark \\
-deísmo & de-ís*mo \xmark & de*ís*mo \cmark \\
-díade & dí-a*de \xmark & dí*a*de \cmark \\
-diádico & di-á*di*co \xmark & di*á*di*co \cmark \\
-diádoco & di-á*do*co \xmark & di*á*do*co \cmark \\
-diáfise & di-á*fi*se \xmark & di*á*fi*se \cmark \\
-diatômico & di*a-tô*mi*co \xmark & di*a*tô*mi*co \cmark \\
-diérese & di-é*re*se \xmark & di*é*re*se \cmark \\
-diferenciável & di*fe*ren*ci-á*vel \xmark & di*fe*ren*ci*á*vel \cmark \\
-difluência & di*flu-ên*ci*a \xmark & di*flu*ên*ci*a \cmark \\
-díodo & dí-o*do \xmark & dí*o*do \cmark \\
-domiciliário & do*mi*ci*li-á*ri*o \xmark & do*mi*ci*li*á*ri*o \cmark \\
-dríade & drí-a*de \xmark & drí*a*de \cmark \\
-elastômero & e*las-tô*me*ro \xmark & e*las*tô*me*ro \cmark \\
-eluição & e*lu-i*ção \xmark & e*lu*i*ção \cmark \\
-éon & é-on \xmark & é*on \cmark \\
-epicôndilo & e*pi-côn*di*lo \xmark & e*pi*côn*di*lo \cmark \\
-épsilon & ép*si*lon \cmark & ép-si*lon \xmark \\
-equidna & e*quid*na \cmark & e*qui.d*na \xmark \\
-estatuário & es*ta*tu-á*ri*o \xmark & es*ta*tu*á*ri*o \cmark \\
-esteárico & es*te-á*ri*co \xmark & es*te*á*ri*co \cmark \\
-estereoquímica & es*te*re*o-quí*mi*ca \xmark & es*te*re*o*quí*mi*ca \cmark \\
-etnônimo & et-nô*ni*mo \xmark & et*nô*ni*mo \cmark \\
-eucariótico & eu*ca*ri-ó*ti*co \xmark & eu*ca*ri*ó*ti*co \cmark \\
-eurasiático & eu*ra*si-á*ti*co \xmark & eu*ra*si*á*ti*co \cmark \\
-europeísmo & eu*ro*pe-ís*mo \xmark & eu*ro*pe*ís*mo \cmark \\
-europeísta & eu*ro*pe-ís*ta \xmark & eu*ro*pe*ís*ta \cmark \\
-evangeliário & e*van*ge*li-á*ri*o \xmark & e*van*ge*li*á*ri*o \cmark \\
-feroês & fe*ro-ês \xmark & fe*ro*ês \cmark \\
-fiável & fi-á*vel \xmark & fi*á*vel \cmark \\
-fisiólogo & fi*si-ó*lo*go \xmark & fi*si*ó*lo*go \cmark \\
-fluídico & flu-í*di*co \xmark & flu-í*di*co \xmark \\
-foliáceo & fo*li-á*ce*o \xmark & fo*li*á*ce*o \cmark \\
-folíolo & fo*lí-o*lo \xmark & fo*lí*o*lo \cmark \\
-fotoperíodo & fo*to*pe*rí-o*do \xmark & fo*to*pe*rí*o*do \cmark \\
-fotoquímica & fo*to-quí*mi*ca \xmark & fo*to*quí*mi*ca \cmark \\
-fotoquímico & fo*to-quí*mi*co \xmark & fo*to*quí*mi*co \cmark \\
-friável & fri-á*vel \xmark & fri*á*vel \cmark \\
-ftálico & f.tá*li*co \xmark & f.tá*li*co \xmark \\
-fuá & fu-á \xmark & fu*á \cmark \\
-genômico & ge-nô*mi*co \xmark & ge*nô*mi*co \cmark \\
-genuinidade & ge*nu-i*ni*da*de \xmark & ge*nu*i*ni*da*de \cmark \\
-geoquímica & ge*o-quí*mi*ca \xmark & ge*o*quí*mi*ca \cmark \\
-geoquímico & ge*o-quí*mi*co \xmark & ge*o*quí*mi*co \cmark \\
-geotectônica & ge*o*tec-tô*ni*ca \xmark & ge*o*tec*tô*ni*ca \cmark \\
-gimnodesportivo & gim*no*des*por*ti*vo \cmark & gi.m-no*des*por*ti*vo \xmark \\
-glaciário & gla*ci-á*ri*o \xmark & gla*ci*á*ri*o \cmark \\
-glicoproteína & gli*co*pro*te-í*na \xmark & gli*co*pro*te*í*na \cmark \\
-gnaisse & g.nais*se \xmark & g.nais*se \xmark \\
-goês & go-ês \xmark & go*ês \cmark \\
-graxaim & gra*xa-im \xmark & gra*xa-im \xmark \\
-helíaco & he*lí-a*co \xmark & he*lí*a*co \cmark \\
-henoteísmo & he*no*te-ís*mo \xmark & he*no*te*ís*mo \cmark \\
-heptacampeão & hep*ta*cam*pe-ão \xmark & hep*ta*cam*pe*ão \cmark \\
-heteroátomo & he*te*ro-á*to*mo \xmark & he*te*ro*á*to*mo \cmark \\
-higiénico & hi*gi-é*ni*co \xmark & hi*gi*é*ni*co \cmark \\
-hióideo & hi-ói*de*o \xmark & hi*ói*de*o \cmark \\
-hipersônico & hi*per-sô*ni*co \xmark & hi*per*sô*ni*co \cmark \\
-hipocôndrio & hi*po-côn*dri*o \xmark & hi*po*côn*dri*o \cmark \\
-hipomaníaco & hi*po*ma*ní-a*co \xmark & hi*po*ma*ní*a*co \cmark \\
-histoquímica & his*to-quí*mi*ca \xmark & his*to*quí*mi*ca \cmark \\
-iá & i-á \xmark & i*á \cmark \\
-ião & i-ão \xmark & i*ão \cmark \\
-iatroquímica & i*a*tro-quí*mi*ca \xmark & i*a*tro*quí*mi*ca \cmark \\
-icônico & i-cô*ni*co \xmark & i*cô*ni*co \cmark \\
-ictiólogo & ic*ti-ó*lo*go \xmark & ic*ti*ó*lo*go \cmark \\
-indeiscente & in*de-is*cen*te \xmark & in*de-is*cen*te \xmark \\
-indemnização & in*dem*ni*za*ção \cmark & in*de.m-ni*za*ção \xmark \\
-indemnizar & in*dem*ni*zar \cmark & in*de.m-ni*zar \xmark \\
-instituidor & ins*ti*tu-i*dor \xmark & ins*ti*tu*i*dor \cmark \\
-intercambiável & in*ter*cam*bi-á*vel \xmark & in*ter*cam*bi*á*vel \cmark \\
-interferômetro & in*ter*fe-rô*me*tro \xmark & in*ter*fe*rô*me*tro \cmark \\
-íon & í-on \xmark & í*on \cmark \\
-ipsilateral & ip*si*la*te*ral \cmark & ip-si*la*te*ral \xmark \\
-ípsilon & íp*si*lon \cmark & íp-si*lon \xmark \\
-isômero & i-sô*me*ro \xmark & i*sô*me*ro \cmark \\
-isotônico & i*so-tô*ni*co \xmark & i*so*tô*ni*co \cmark \\
-itaúba & i*ta-ú*ba \xmark & i*ta*ú*ba \cmark \\
-jandaíra & jan*da-í*ra \xmark & jan*da*í*ra \cmark \\
-jaó & ja-ó \xmark & ja*ó \cmark \\
-jauá & jau-á \xmark & jau*á \cmark \\
-jihadista & ji-ha*dis*ta \xmark & ji-ha*dis*ta \xmark \\
-joinvilense & jo-in*vi*len*se \xmark & jo-in*vi*len*se \xmark \\
-jundiá & jun*di-á \xmark & jun*di*á \cmark \\
-jutaí & ju*ta-í \xmark & ju*ta*í \cmark \\
-kuwaitiano & ku-wai*ti*a*no \xmark & ku-wai*ti*a*no \xmark \\
-lemna & lem*na \cmark & le.m-na \xmark \\
-lemniscata & lem*nis*ca*ta \cmark & le.m-nis*ca*ta \xmark \\
-lemnisco & lem*nis*co \cmark & le.m-nis*co \xmark \\
-leônico & le-ô*ni*co \xmark & le*ô*ni*co \cmark \\
-lidocaína & li*do*ca-í*na \xmark & li*do*ca*í*na \cmark \\
-liechtensteinense & li*e.ch*tens*tei*nen*se \xmark & li*e.ch*tens*tei*nen*se \xmark \\
-limnologia & lim*no*lo*gi*a \cmark & li.m-no*lo*gi*a \xmark \\
-litíase & li*tí-a*se \xmark & li*tí*a*se \cmark \\
-macaúba & ma*ca-ú*ba \xmark & ma*ca*ú*ba \cmark \\
-magnetômetro & mag*ne-tô*me*tro \xmark & mag*ne*tô*me*tro \cmark \\
-maís & ma-ís \xmark & ma*ís \cmark \\
-malauiano & ma*lau-i*a*no \xmark & ma*lau-i*a*no \xmark \\
-malônico & ma-lô*ni*co \xmark & ma*lô*ni*co \cmark \\
-maruí & ma*ru-í \xmark & ma*ru*í \cmark \\
-maruim & ma*ru-im \xmark & ma*ru-im \xmark \\
-meã & me-ã \xmark & me*ã \cmark \\
-meão & me-ão \xmark & me*ão \cmark \\
-meiótico & mei-ó*ti*co \xmark & mei*ó*ti*co \cmark \\
-microbiólogo & mi*cro*bi-ó*lo*go \xmark & mi*cro*bi*ó*lo*go \cmark \\
-midríase & mi*drí-a*se \xmark & mi*drí*a*se \cmark \\
-miíase & mi-í-a*se \xmark & mi*í*a*se \cmark \\
-miliário & mi*li-á*ri*o \xmark & mi*li*á*ri*o \cmark \\
-mnemônico & m.ne-mô*ni*co \xmark & mne*mô*ni*co \cmark \\
-monofônico & mo*no-fô*ni*co \xmark & mo*no*fô*ni*co \cmark \\
-moquém & mo-quém \xmark & mo*quém \cmark \\
-morrião & mor*ri-ão \xmark & mor*ri*ão \cmark \\
-neodarwinismo & ne*o*dar-wi*nis*mo \xmark & ne*o*dar-wi*nis*mo \xmark \\
-nobiliário & no*bi*li-á*ri*o \xmark & no*bi*li*á*ri*o \cmark \\
-nucléolo & nu*clé-o*lo \xmark & nu*clé*o*lo \cmark \\
-octaédrico & oc*ta-é*dri*co \xmark & oc*ta*é*dri*co \cmark \\
-odeão & o*de-ão \xmark & o*de*ão \cmark \\
-oídio & o-í*di*o \xmark & o*í*di*o \cmark \\
-omíada & o*mí-a*da \xmark & o*mí*a*da \cmark \\
-omnipotente & om*ni*po*ten*te \cmark & o.m-ni*po*ten*te \xmark \\
-omnisciente & om*nis*ci*en*te \cmark & o.m-nis*ci*en*te \xmark \\
-omnívoro & om*ní*vo*ro \cmark & o.m-ní*vo*ro \xmark \\
-oócito & o-ó*ci*to \xmark & o*ó*ci*to \cmark \\
-orfeão & or*fe-ão \xmark & or*fe*ão \cmark \\
-oriá & o*ri-á \xmark & o*ri*á \cmark \\
-ortodôntico & or*to-dôn*ti*co \xmark & or*to*dôn*ti*co \cmark \\
-ossuário & os*su-á*ri*o \xmark & os*su*á*ri*o \cmark \\
-osteíte & os*te-í*te \xmark & os*te*í*te \cmark \\
-ostiário & os*ti-á*ri*o \xmark & os*ti*á*ri*o \cmark \\
-paleógrafo & pa*le-ó*gra*fo \xmark & pa*le*ó*gra*fo \cmark \\
-paleólogo & pa*le-ó*lo*go \xmark & pa*le*ó*lo*go \cmark \\
-panenteísmo & pa*nen*te-ís*mo \xmark & pa*nen*te*ís*mo \cmark \\
-patauá & pa*tau-á \xmark & pa*tau*á \cmark \\
-patoá & pa*to-á \xmark & pa*to*á \cmark \\
-pecíolo & pe*cí-o*lo \xmark & pe*cí*o*lo \cmark \\
-pequiá & pe*qui-á \xmark & pe*qui*á \cmark \\
-periélio & pe*ri-é*li*o \xmark & pe*ri*é*li*o \cmark \\
-píon & pí-on \xmark & pí*on \cmark \\
-pitiríase & pi*ti*rí-a*se \xmark & pi*ti*rí*a*se \cmark \\
-pium & pi-um \xmark & pi-um \xmark \\
-planctônico & planc-tô*ni*co \xmark & planc*tô*ni*co \cmark \\
-pneuma & p.neu*ma \xmark & pneu*ma \cmark \\
-pneumonite & p.neu*mo*ni*te \xmark & pneu*mo*ni*te \cmark \\
-pneumotórax & p.neu*mo*tó*rax \xmark & pneu*mo*tó*rax \cmark \\
-poliúria & po*li-ú*ri*a \xmark & po*li*ú*ri*a \cmark \\
-poraquê & po*ra-quê \xmark & po*ra*quê \cmark \\
-preênsil & pre-ên*sil \xmark & pre*ên*sil \cmark \\
-príon & prí-on \xmark & prí*on \cmark \\
-procariótico & pro*ca*ri-ó*ti*co \xmark & pro*ca*ri*ó*ti*co \cmark \\
-procônsul & pro-côn*sul \xmark & pro*côn*sul \cmark \\
-proteólise & pro*te-ó*li*se \xmark & pro*te*ó*li*se \cmark \\
-pseudocientífico & p.seu*do*ci*en*tí*fi*co \xmark & pseu*do*ci*en*tí*fi*co \cmark \\
-pseudofruto & p.seu*do*fru*to \xmark & pseu*do*fru*to \cmark \\
-psicadélico & p.si*ca*dé*li*co \xmark & psi*ca*dé*li*co \cmark \\
-psicoativo & p.si*co*a*ti*vo \xmark & psi*co*a*ti*vo \cmark \\
-psicocirurgia & p.si*co*ci*rur*gi*a \xmark & psi*co*ci*rur*gi*a \cmark \\
-psicofisiologia & p.si*co*fi*si*o*lo*gi*a \xmark & psi*co*fi*si*o*lo*gi*a \cmark \\
-psicofonia & p.si*co*fo*ni*a \xmark & psi*co*fo*ni*a \cmark \\
-psicografia & p.si*co*gra*fi*a \xmark & psi*co*gra*fi*a \cmark \\
-psicopompo & p.si*co*pom*po \xmark & psi*co*pom*po \cmark \\
-psicoterápico & p.si*co*te*rá*pi*co \xmark & psi*co*te*rá*pi*co \cmark \\
-psoas & p.so*as \xmark & p.so*as \xmark \\
-pterodáctilo & p.te*ro*dác*ti*lo \xmark & pte*ro*dác*ti*lo \cmark \\
-ptialina & p.ti*a*li*na \xmark & pti*a*li*na \cmark \\
-ptolemaico & p.to*le*mai*co \xmark & pto*le*mai*co \cmark \\
-radioquímica & ra*di*o-quí*mi*ca \xmark & ra*di*o*quí*mi*ca \cmark \\
-randômico & ran-dô*mi*co \xmark & ran*dô*mi*co \cmark \\
-reciário & re*ci-á*ri*o \xmark & re*ci*á*ri*o \cmark \\
-reimpresso & re-im*pres*so \xmark & re*im*pres*so \cmark \\
-reimprimir & re-im*pri*mir \xmark & re*im*pri*mir \cmark \\
-sambaíba & sam*ba-í*ba \xmark & sam*ba*í*ba \cmark \\
-samnita & sam*ni*ta \cmark & sa.m-ni*ta \xmark \\
-saxônico & sa-xô*ni*co \xmark & sa*xô*ni*co \cmark \\
-semiárido & se*mi-á*ri*do \xmark & se*mi*á*ri*do \cmark \\
-semiótico & se*mi-ó*ti*co \xmark & se*mi*ó*ti*co \cmark \\
-semipermeável & se*mi*per*me-á*vel \xmark & se*mi*per*me*á*vel \cmark \\
-sépsis & sép*sis \cmark & sép-sis \xmark \\
-serôdio & se-rô*di*o \xmark & se*rô*di*o \cmark \\
-serventuário & ser*ven*tu-á*ri*o \xmark & ser*ven*tu*á*ri*o \cmark \\
-siálico & si-á*li*co \xmark & si*á*li*co \cmark \\
-siríaco & si*rí-a*co \xmark & si*rí*a*co \cmark \\
-sonômetro & so-nô*me*tro \xmark & so*nô*me*tro \cmark \\
-suaíli & su*a-í*li \xmark & su*a*í*li \cmark \\
-subatômico & su*ba-tô*mi*co \xmark & su*ba*tô*mi*co \cmark \\
-subdiácono & sub*di-á*co*no \xmark & sub*di*á*co*no \cmark \\
-sublevar & su.b-le*var \xmark & sub*le*var \cmark \\
-subliminal & su.b-li*mi*nal \xmark & sub*li*mi*nal \cmark \\
-sublinear & su.b-li*ne*ar \xmark & sub*li*ne*ar \cmark \\
-sublingual & su.b-lin*gual \xmark & sub*lin*gual \cmark \\
-sublunar & su.b-lu*nar \xmark & sub*lu*nar \cmark \\
-subsequência & sub*se-quên*ci*a \xmark & sub*se*quên*ci*a \cmark \\
-substituinte & subs*ti*tu-in*te \xmark & subs*ti*tu-in*te \xmark \\
-coimbra & co-im*bra \xmark & co*im*bra \cmark \\
-coimperador & co-im*pe*ra*dor \xmark & co*im*pe*ra*dor \cmark \\
-reimposição & re-im*po*si*ção \xmark & re*im*po*si*ção \cmark \\
-bioimpressão & bi*o-im*pres*são \xmark & bi*o*im*pres*são \cmark \\
-neoimpressionista & ne*o-im*pres*si*o*nis*ta \xmark & ne*o*im*pres*si*o*nis*ta \cmark \\
-autoimposto & au*to-im*pos*to \xmark & au*to*im*pos*to \cmark \\
-reimplementação & re-im*ple*men*ta*ção \xmark & re*im*ple*men*ta*ção \cmark \\
-teleimpressor & te*le-im*pres*sor \xmark & te*le*im*pres*sor \cmark \\
-reimposta & re-im*pos*ta \xmark & re*im*pos*ta \cmark \\
-reimplementar & re-im*ple*men*tar \xmark & re*im*ple*men*tar \cmark \\
-reimpulsionar & re-im*pul*si*o*nar \xmark & re*im*pul*si*o*nar \cmark \\
-autoimposição & au*to-im*po*si*ção \xmark & au*to*im*po*si*ção \cmark \\
-cacauicultor & ca*cau-i*cul*tor \xmark & ca*cau*i*cul*tor \cmark \\
-sanduiche & san*du-i*che \xmark & san*du*i*che \cmark \\
-ruidosamente & ru-i*do*sa*men*te \xmark & ru*i*do*sa*men*te \cmark \\
-promiscuidade & pro*mis*cu-i*da*de \xmark & pro*mis*cu*i*da*de \cmark \\
-inocuidade & i*no*cu-i*da*de \xmark & i*no*cu*i*da*de \cmark \\
-reincidência & re-in*ci*dên*ci.a \xmark & re*in*ci*dên*ci.a \xmark \\
-reincluir & re-in*clu-ir \xmark & re*in*clu*ir \cmark \\
-reinfecção & re-in*fec*ção \xmark & re*in*fec*ção \cmark \\
-reinforçar & re-in*for*çar \xmark & re*in*for*çar \cmark \\
-reinsurgir & re-in*sur*gir \xmark & re*in*sur*gir \cmark \\
-reinstalado & re-ins*ta*la*do \xmark & re*ins*ta*la*do \cmark \\
-reinstituído & re-ins*ti*tu-í*do \xmark & re*ins*ti*tu*í*do \cmark \\
-reinvindicar & re-in*vin*di*car \xmark & re*in*vin*di*car \cmark \\
-bioincrustação & bi*o-in*crus*ta*ção \xmark & bi*o*in*crus*ta*ção \cmark \\
-agroindustrial & a*gro-in*dus*tri*al \xmark & a*gro*in*dus*tri*al \cmark \\
-bioindicadores & bi*o-in*di*ca*do*res \xmark & bi*o*in*di*ca*do*res \cmark \\
-autoindulgência & au*to-in*dul*gên*ci.a \xmark & au*to*in*dul*gên*ci.a \xmark \\
-autoinduzida & au*to-in*du*zi*da \xmark & au*to*in*du*zi*da \cmark \\
-microindústria & mi*cro-in*dús*tri*a \xmark & mi*cro*in*dús*tri*a \cmark \\
-tecnoindustrial & tec*no-in*dus*tri*al \xmark & tec*no*in*dus*tri*al \cmark \\
-bioinformática & bi*o-in*for*má*ti*ca \xmark & bi*o*in*for*má*ti*ca \cmark \\
-coinfecção & co-in*fec*ção \xmark & co*in*fec*ção \cmark \\
-geoinformação & ge.o-in*for*ma*ção \xmark & ge.o*in*for*ma*ção \xmark \\
-autoinfecção & au*to-in*fec*ção \xmark & au*to*in*fec*ção \cmark \\
-neuroinformática & neu*ro-in*for*má*ti*ca \xmark & neu*ro*in*for*má*ti*ca \cmark \\
-amendoins & a*men*do-ins \xmark & a*men*do*ins \cmark \\
-videoinstalação & vi*de*o-ins*ta*la*ção \xmark & vi*de*o*ins*ta*la*ção \cmark \\
-autointitulado & au*to-in*ti*tu*la*do \xmark & au*to*in*ti*tu*la*do \cmark \\
-saindo & sa-in*do \xmark & sa*in*do \cmark \\
-caindo & ca-in*do \xmark & ca*in*do \cmark \\
-contraindicações & con*tra-in*di*ca*ções \xmark & con*tra*in*di*ca*ções \cmark \\
-abstraindo & abs*tra-in*do \xmark & abs*tra*in*do \cmark \\
-prainha & pra-i*nha \xmark & pra*i*nha \cmark \\
-lagoinha & la*go-i*nha \xmark & la*go*i*nha \cmark \\
-canoinha & ca*no-i*nha \xmark & ca*no*i*nha \cmark \\
-reimpresso & re-im*pres*so \xmark & re*im*pres*so \cmark \\
-genuino & ge*nu-i*no \xmark & ge*nu*i*no \cmark \\
-ruina & ru-i*na \xmark & ru*i*na \cmark \\
-arruinado & ar*ru-i*na*do \xmark & ar*ru*i*na*do \cmark \\
-arruinou & ar*ru-i*nou \xmark & ar*ru*i*nou \cmark \\
-suino & su-i*no \xmark & su*i*no \cmark \\
-suina & su-i*na \xmark & su*i*na \cmark \\
-ajuizamento & a*ju-i*za*men*to \xmark & a*ju*i*za*men*to \cmark \\
-luiz & lu-iz \xmark & lu*iz \cmark \\
-luiza & lu-i*za \xmark & lu*i*za \cmark \\
-amnésia & a-m.né*si*a \xmark & a*mné*si*a \cmark \\
-amniota & a-m.ni*o*ta \xmark & a*mni*o*ta \cmark \\
-amniótico & a-m.ni-ó*ti*co \xmark & a*mni*ó*ti*co \cmark \\
-diuréticos & di-u*ré*ti*cos \xmark & di*u*ré*ti*cos \cmark \\
-diurese & di-u*re*se \xmark & di*u*re*se \cmark \\
-feiurinha & fei-u*ri*nha \xmark & fei*u*ri*nha \cmark \\
-íodo & í-o*do \xmark & í*o*do \cmark \\
-íons & í-ons \xmark & í*ons \cmark \\
-antíope & an*tí-o*pe \xmark & an*tí*o*pe \cmark \\
-médiuns & mé*di-uns \xmark & mé*di*uns \cmark \\
-fluór & flu-ór \xmark & flu*ór \cmark \\
-sequóia & se-quói*a \xmark & se*quói*a \cmark \\
-subquântico & sub-quân*ti*co \xmark & sub*quân*ti*co \cmark \\
-\\
-\hline
-37798 & 1368 & 132 \\
-\hline

### 2024-06-14 article/comparedresults-sample.tex
updates

ministério & mi*nis*té*ri.o \xmark & mi*nis*té*rio \cmark \\
próprio & pró*pri.o \xmark & pró*prio \cmark \\
salário & sa*lá*ri.o \xmark & sa*lá*rio \cmark \\
secretário & se*cre*tá*ri.o \xmark & se*cre*tá*rio \cmark \\
contrário & con*trá*ri.o \xmark & con*trá*rio \cmark \\
horário & ho*rá*ri.o \xmark & ho*rá*rio \cmark \\
necessário & ne*ces*sá*ri.o \xmark & ne*ces*sá*rio \cmark \\
relatório & re*la*tó*ri.o \xmark & re*la*tó*rio \cmark \\
adversário & ad*ver*sá*ri.o \xmark & ad*ver*sá*rio \cmark \\
cenário & ce*ná*ri.o \xmark & ce*ná*rio \cmark \\
diário & di-á*ri.o \xmark & di*á*rio \cmark \\
escritório & es*cri*tó*ri.o \xmark & es*cri*tó*rio \cmark \\
judiciário & ju*di*ci-á*ri.o \xmark & ju*di*ci*á*rio \cmark \\
equilíbrio & e*qui*lí*bri.o \xmark & e*qui*lí*brio \cmark \\
proprietário & pro*pri*e*tá*ri.o \xmark & pro*pri*e*tá*rio \cmark \\
aniversário & a*ni*ver*sá*ri.o \xmark & a*ni*ver*sá*rio \cmark \\
usuário & u*su-á*ri.o \xmark & u*su*á*rio \cmark \\
sério & sé*ri.o \xmark & sé*rio \cmark \\
território & ter*ri*tó*ri.o \xmark & ter*ri*tó*rio \cmark \\
seminário & se*mi*ná*ri.o \xmark & se*mi*ná*rio \cmark \\
auditório & au*di*tó*ri.o \xmark & au*di*tó*rio \cmark \\
laboratório & la*bo*ra*tó*ri.o \xmark & la*bo*ra*tó*rio \cmark \\
bancário & ban*cá*ri.o \xmark & ban*cá*rio \cmark \\
monetário & mo*ne*tá*ri.o \xmark & mo*ne*tá*rio \cmark \\
repertório & re*per*tó*ri.o \xmark & re*per*tó*rio \cmark \\
cemitério & ce*mi*té*ri.o \xmark & ce*mi*té*rio \cmark \\
compulsório & com*pul*só*ri.o \xmark & com*pul*só*rio \cmark \\
calendário & ca*len*dá*ri.o \xmark & ca*len*dá*rio \cmark \\
obrigatório & o*bri*ga*tó*ri.o \xmark & o*bri*ga*tó*rio \cmark \\
mistério & mis*té*ri.o \xmark & mis*té*rio \cmark \\
documentário & do*cu*men*tá*ri.o \xmark & do*cu*men*tá*rio \cmark \\
tributário & tri*bu*tá*ri.o \xmark & tri*bu*tá*rio \cmark \\
polícia & po*lí*ci.a \xmark & po*lí*cia \cmark \\
agência & a*gên*ci.a \xmark & a*gên*cia \cmark \\
presidência & pre*si*dên*ci.a \xmark & pre*si*dên*cia \cmark \\
violência & vi*o*lên*ci.a \xmark & vi*o*lên*cia \cmark \\
experiência & ex*pe*ri*ên*ci.a \xmark & ex*pe*ri*ên*cia \cmark \\
tendência & ten*dên*ci.a \xmark & ten*dên*cia \cmark \\
importância & im*por*tân*ci.a \xmark & im*por*tân*cia \cmark \\
denúncia & de*nún*ci.a \xmark & de*nún*cia \cmark \\
existência & e*xis*tên*ci.a \xmark & e*xis*tên*cia \cmark \\
ciência & ci*ên*ci.a \xmark & ci*ên*cia \cmark \\
ausência & au*sên*ci.a \xmark & au*sên*cia \cmark \\
emergência & e*mer*gên*ci.a \xmark & e*mer*gên*cia \cmark \\
referência & re*fe*rên*ci.a \xmark & re*fe*rên*cia \cmark \\
influência & in*flu-ên*ci.a \xmark & in*flu*ên*cia \cmark \\
conferência & con*fe*rên*ci.a \xmark & con*fe*rên*cia \cmark \\
notícia & no*tí*ci.a \xmark & no*tí*cia \cmark \\
consequência & con*se-quên*ci.a \xmark & con*se*quên*cia \cmark \\
assistência & as*sis*tên*ci.a \xmark & as*sis*tên*cia \cmark \\
distância & dis*tân*ci.a \xmark & dis*tân*cia \cmark \\
resistência & re*sis*tên*ci.a \xmark & re*sis*tên*cia \cmark \\
consciência & cons*ci*ên*ci.a \xmark & cons*ci*ên*cia \cmark \\
eficiência & e*fi*ci*ên*ci.a \xmark & e*fi*ci*ên*cia \cmark \\
infância & in*fân*ci.a \xmark & in*fân*cia \cmark \\
inteligência & in*te*li*gên*ci.a \xmark & in*te*li*gên*cia \cmark \\
vigilância & vi*gi*lân*ci.a \xmark & vi*gi*lân*cia \cmark \\
competência & com*pe*tên*ci.a \xmark & com*pe*tên*cia \cmark \\
independência & in*de*pen*dên*ci.a \xmark & in*de*pen*dên*cia \cmark \\
início & i*ní*ci.o \xmark & i*ní*cio \cmark \\
comércio & co*mér*ci.o \xmark & co*mér*cio \cmark \\
negócio & ne*gó*ci.o \xmark & ne*gó*cio \cmark \\
palácio & pa*lá*ci.o \xmark & pa*lá*cio \cmark \\
anúncio & a*nún*ci.o \xmark & a*nún*cio \cmark \\
márcio & már*ci.o \xmark & már*cio \cmark \\
benefício & be*ne*fí*ci.o \xmark & be*ne*fí*cio \cmark \\
história & his*tó*ri.a \xmark & his*tó*ria \cmark \\
vitória & vi*tó*ri.a \xmark & vi*tó*ria \cmark \\
indústria & in*dús*tri.a \xmark & in*dús*tria \cmark \\
memória & me*mó*ri.a \xmark & me*mó*ria \cmark \\
miséria & mi*sé*ri.a \xmark & mi*sé*ria \cmark \\
secretária & se*cre*tá*ri.a \xmark & se*cre*tá*ria \cmark \\
médio & mé*di.o \xmark & mé*dio \cmark \\
rádio & rá*di.o \xmark & rá*dio \cmark \\
incêndio & in*cên*di.o \xmark & in*cên*dio \cmark \\
estúdio & es*tú*di.o \xmark & es*tú*dio \cmark \\
índio & ín*di.o \xmark & ín*dio \cmark \\
psicologia & p.si*co*lo*gi*a \xmark & psi*co*lo*gi-a \xmark \\
psicológico & p.si*co*ló*gi*co \xmark & psi*co*ló*gi*co \cmark \\
psiquiatra & p.si*qui*a*tra \xmark & psi*qui*a*tra \cmark \\
psicanalista & p.si*ca*na*lis*ta \xmark & psi*ca*na*lis*ta \cmark \\
psicólogo & p.si*có*lo*go \xmark & psi*có*lo*go \cmark \\
domínio & do*mí*ni.o \xmark & do*mí*nio \cmark \\
raciocínio & ra*ci*o*cí*ni.o \xmark & ra*ci*o*cí*nio \cmark \\
condomínio & con*do*mí*ni.o \xmark & con*do*mí*nio \cmark \\
alumínio & a*lu*mí*ni.o \xmark & a*lu*mí*nio \cmark \\
hélio & hé*li.o \xmark & hé*lio \cmark \\
monopólio & mo*no*pó*li.o \xmark & mo*no*pó*lio \cmark \\
auxílio & au*xí*li.o \xmark & au*xí*lio \cmark \\
colégio & co*lé*gi.o \xmark & co*lé*gio \cmark \\
prestígio & pres*tí*gi.o \xmark & pres*tí*gio \cmark \\
relógio & re*ló*gi.o \xmark & re*ló*gio \cmark \\
câmbio & câm*bi.o \xmark & câm*bio \cmark \\
intercâmbio & in*ter*câm*bi.o \xmark & in*ter*câm*bio \cmark \\
subúrbio & su*búr*bi.o \xmark & su*búr*bio \cmark \\
média & mé*di.a \xmark & mé*dia \cmark \\
mídia & mí*di.a \xmark & mí*dia \cmark \\
município & mu*ni*cí*pi.o \xmark & mu*ni*cí*pio \cmark \\
princípio & prin*cí*pi.o \xmark & prin*cí*pio \cmark \\
contemporâneo & con*tem*po*râ*ne.o \xmark & con*tem*po*râ*neo \cmark \\
mediterrâneo & me*di*ter*râ*ne.o \xmark & me*di*ter*râ*neo \cmark \\
autópsia & au*tóp*si.a \xmark & au*tóp*sia \cmark \\
eutanásia & eu*ta*ná*si.a \xmark & eu*ta*ná*sia \cmark \\
vídeo & ví*de.o \xmark & ví*deo \cmark \\
hominídeo & ho*mi*ní*de.o \xmark & ho*mi*ní*deo \cmark \\
alívio & a*lí*vi.o \xmark & a*lí*vio \cmark \\
sérvio & sér*vi.o \xmark & sér*vio \cmark \\
aéreo & a-é*re.o \xmark & a*é*reo \cmark \\
térreo & tér*re.o \xmark & tér*reo \cmark \\
pneumonia & p.neu*mo*ni*a \xmark & pneu*mo*ni-a \xmark \\
pneumática & p.neu*má*ti*ca \xmark & pneu*má*ti*ca \cmark \\
represália & re*pre*sá*li.a \xmark & re*pre*sá*lia \cmark \\
sandália & san*dá*li.a \xmark & san*dá*lia \cmark \\
ginásio & gi*ná*si.o \xmark & gi*ná*sio \cmark \\
múmia & mú*mi.a \xmark & mú*mia \cmark \\
hérnia & hér*ni.a \xmark & hér*nia \cmark \\
exímio & e*xí*mi.o \xmark & e*xí*mio \cmark \\
crustáceo & crus*tá*ce.o \xmark & crus*tá*ceo \cmark \\
sublunar & su.b-lu*nar \xmark & sub*lu*nar \cmark \\
sítio & sí*ti.o \xmark & sí*tio \cmark \\
equilíbrio & e*qui*lí*bri.o \xmark & e*qui*lí*brio \cmark \\
rodízio & ro*dí*zi.o \xmark & ro*dí*zio \cmark \\
arbítrio & ar*bí*tri.o \xmark & ar*bí*trio \cmark \\
angústia & an*gús*ti.a \xmark & an*gús*tia \cmark \\
colóquio & co*ló*qui.o \xmark & co*ló*quio \cmark \\
cópia & có*pi.a \xmark & có*pia \cmark \\
espécie & es*pé*ci.e \xmark & es*pé*cie \cmark \\
série & sé*ri.e \xmark & sé*rie \cmark \\
sanguínea & san*guí*ne.a \xmark & san*guí*nea \cmark \\
petróleo & pe*tró*le.o \xmark & pe*tró*leo \cmark \\
vácuo & vá*cu.o \xmark & vá*cuo \cmark \\
lascívia & las*cí*vi.a \xmark & las*cí*via \cmark \\
indústria & in*dús*tri.a \xmark & in*dús*tria \cmark \\
área & á*re.a \xmark & á*rea \cmark \\
exéquias & e*xé*qui.as \xmark & e*xé*qui.as \xmark \\
gnomo & g.no*mo \xmark & gno*mo \cmark \\
estratégia & es*tra*té*gi.a \xmark & es*tra*té*gia \cmark \\
epitáfio & e*pi*tá*fi.o \xmark & e*pi*tá*fio \cmark \\
máfia & má*fi.a \xmark & má*fia \cmark \\
assíduo & as*sí*du.o \xmark & as*sí*duo \cmark \\
czarina & c.za*ri*na \xmark & cza*ri*na \cmark \\
cucurbitácea & cu*cur*bi*tá*ce.a \xmark & cu*cur*bi*tá*cea \cmark \\
tíbia & tí*bi.a \xmark & tí*bia \cmark \\
pétreo & pé*tre.o \xmark & pé*treo \cmark \\
teleósteo & te*le-ós*te.o \xmark & te*le*ós*teo \cmark \\
stalinismo & s.ta*li*nis*mo \xmark & sta*li*nis*mo \cmark \\
ósseo & ós*se.o \xmark & ós*seo \cmark \\
psoríase & p.so*rí-a*se \xmark & p.so*rí*a*se \xmark \\
próprio & pró*pri.o \xmark & pró*prio \cmark \\
apneia & a-p.nei*a \xmark & a-p.nei-a \xmark \\
mnemônica & m.ne-mô*ni*ca \xmark & mne*mô*ni*ca \cmark \\
imbróglio & im*bró*gli.o \xmark & im*bró*glio \cmark \\
laríngeo & la*rín*ge.o \xmark & la*rín*geo \cmark \\
supérfluo & su*pér*flu.o \xmark & su*pér*fluo \cmark \\
núcleo & nú*cle.o \xmark & nú*cleo \cmark \\
dúzia & dú*zi.a \xmark & dú*zia \cmark \\
várzea & vár*ze.a \xmark & vár*zea \cmark \\
névoa & né*vo.a \xmark & né*voa \cmark \\
gávea & gá*ve.a \xmark & gá*vea \cmark \\
quartzo & quar-t.zo \xmark & quar-t.zo \xmark \\
quartzito & quar-t.zi*to \xmark & quar-t.zi*to \xmark \\
tzarista & t.za*ris*ta \xmark & tza*ris*ta \cmark \\
mútuo & mú*tu.o \xmark & mú*tuo \cmark \\
estátua & es*tá*tu.a \xmark & es*tá*tua \cmark \\
mênstruo & mêns*tru.o \xmark & mêns*truo \cmark \\
tmese & t.me*se \xmark & tme*se \cmark \\
abrótea & a*bró*te.a \xmark & a*bró*tea \cmark \\
tcheco & t.che*co \xmark & tche*co \cmark \\
exéquias & e*xé*qui.as \xmark & e*xé*qui.as \xmark \\
precípuo & pre*cí*pu.o \xmark & pre*cí*puo \cmark \\
ptose & p.to*se \xmark & pto*se \cmark \\
pterossauro & p.te*ros*sau*ro \xmark & pte*ros*sau*ro \cmark \\
psíquico & p.sí*qui*co \xmark & psí*qui*co \cmark \\
pseudônimo & p.seu-dô*ni*mo \xmark & pseu*dô*ni*mo \cmark \\
hiperalgesia & hi*pe.r-al*ge*si*a \xmark & hi*pe.r-al*ge*si-a \xmark \\
contínuo & con*tí*nu.o \xmark & con*tí*nuo \cmark \\
contínua & con*tí*nu.a \xmark & con*tí*nua \cmark \\
neerlandês & ne.er*lan*dês \xmark & ne.er*lan*dês \xmark \\
fêmea & fê*me.a \xmark & fê*mea \cmark \\
águia & á*gui.a \xmark & á*guia \cmark \\
mágoa & má*go.a \xmark & má*goa \cmark \\
gnóstico & g.nós*ti*co \xmark & gnós*ti*co \cmark \\
gnosticismo & g.nos*ti*cis*mo \xmark & gnos*ti*cis*mo \cmark \\
gnaisse & g.nais*se \xmark & g.nais*se \xmark \\
efígie & e*fí*gi.e \xmark & e*fí*gie \cmark \\
drágea & drá*ge.a \xmark & drá*gea \cmark \\
dzeta & d.ze*ta \xmark & d.ze*ta \xmark \\
mitocôndria & mi*to-côn*dri.a \xmark & mi*to*côn*dria \cmark \\
amêndoa & a*mên*do.a \xmark & a*mên*doa \cmark \\
côdea & cô*de.a \xmark & cô*dea \cmark \\
cnidário & c.ni*dá*ri.o \xmark & c.ni*dá*rio \xmark \\
núpcias & núp*ci.as \xmark & núp*ci.as \xmark \\
quíchua & quí*chu.a \xmark & quí*chua \cmark \\
fímbria & fím*bri.a \xmark & fím*bria \cmark \\
brechtiano & bre.ch*ti*a*no \xmark & bre.ch*ti*a*no \xmark \\
arábias & a*rá*bi.as \xmark & a*rá*bi.as \xmark \\
plúmbeo & plúm*be.o \xmark & plúm*beo \cmark \\
abrupto & a.b-rup*to \xmark & a.b-rup*to \xmark \\

### 2024-06-14 article/comparedresults.tex
updates

@@
+aarônico & a*a-rô*ni*co \xmark & a*a*rô*ni*co \cmark \\
+abadia & a*ba*di*a \cmark & a*ba*di-a \xmark \\
+abdômen & ab-dô*men \xmark & ab*dô*men \cmark \\
+abdominoplastia & ab*do*mi*no*plas*ti*a \cmark & ab*do*mi*no*plas*ti-a \xmark \\
+abecedário & a*be*ce*dá*ri.o \xmark & a*be*ce*dá*rio \cmark \\
+abiótico & a*bi-ó*ti*co \xmark & a*bi*ó*ti*co \cmark \\
+abissínio & a*bis*sí*ni.o \xmark & a*bis*sí*nio \cmark \\
+abluir & a*blu-ir \xmark & a*blu*ir \cmark \\
+aboio & a*boi*o \cmark & a*boi-o \xmark \\
+abraâmico & a*bra-â*mi*co \xmark & a*bra*â*mi*co \cmark \\
+abrangência & a*bran*gên*ci.a \xmark & a*bran*gên*cia \cmark \\
+abreugrafia & a*breu*gra*fi*a \cmark & a*breu*gra*fi-a \xmark \\
+abrótea & a*bró*te.a \xmark & a*bró*tea \cmark \\
+abrupto & a.b-rup*to \xmark & a.b-rup*to \xmark \\
+absenteísmo & ab*sen*te-ís*mo \xmark & ab*sen*te*ís*mo \cmark \\
+abstinência & abs*ti*nên*ci.a \xmark & abs*ti*nên*cia \cmark \\
+abstraído & abs*tra-í*do \xmark & abs*tra*í*do \cmark \\
+abstrair & abs*tra-ir \xmark & abs*tra*ir \cmark \\
+abulia & a*bu*li*a \cmark & a*bu*li-a \xmark \\
+abundância & a*bun*dân*ci*a \cmark & a*bun*dân*ci-a \xmark \\
+acácia & a*cá*ci.a \xmark & a*cá*cia \cmark \\
+academia & a*ca*de*mi*a \cmark & a*ca*de*mi-a \xmark \\
+açaí & a*ça-í \xmark & a*ça*í \cmark \\
+acatisia & a*ca*ti*si*a \cmark & a*ca*ti*si-a \xmark \\
+acefalia & a*ce*fa*li*a \cmark & a*ce*fa*li-a \xmark \\
+acéquia & a*cé*qui.a \xmark & a*cé*quia \cmark \\
+acessório & a*ces*só*ri.o \xmark & a*ces*só*rio \cmark \\
+acetaldeído & a*ce*tal*de-í*do \xmark & a*ce*tal*de*í*do \cmark \\
+acidemia & a*ci*de*mi*a \cmark & a*ci*de*mi-a \xmark \\
+acônito & a-cô*ni*to \xmark & a*cô*ni*to \cmark \\
+acordeão & a*cor*de-ão \xmark & a*cor*de*ão \cmark \\
+açoteia & a*ço*tei*a \cmark & a*ço*tei-a \xmark \\
+acrobacia & a*cro*ba*ci*a \cmark & a*cro*ba*ci-a \xmark \\
+acrofobia & a*cro*fo*bi*a \cmark & a*cro*fo*bi-a \xmark \\
+acromegalia & a*cro*me*ga*li*a \cmark & a*cro*me*ga*li-a \xmark \\
+actínio & ac*tí*ni.o \xmark & ac*tí*nio \cmark \\
+acuidade & a*cu-i*da*de \xmark & a*cu-i*da*de \xmark \\
+acurácia & a*cu*rá*ci.a \xmark & a*cu*rá*cia \cmark \\
+adágio & a*dá*gi.o \xmark & a*dá*gio \cmark \\
+adail & a*da-il \xmark & a*da-il \xmark \\
+adimplência & a*dim*plên*ci.a \xmark & a*dim*plên*cia \cmark \\
+adjutório & ad*ju*tó*ri.o \xmark & ad*ju*tó*rio \cmark \\
+adolescência & a*do*les*cên*ci.a \xmark & a*do*les*cên*cia \cmark \\
+adriático & a*dri-á*ti*co \xmark & a*dri*á*ti*co \cmark \\
+adultério & a*dul*té*ri.o \xmark & a*dul*té*rio \cmark \\
+adventício & ad*ven*tí*ci.o \xmark & ad*ven*tí*cio \cmark \\
+advérbio & ad*vér*bi.o \xmark & ad*vér*bio \cmark \\
+adversário & ad*ver*sá*ri.o \xmark & ad*ver*sá*rio \cmark \\
+advertência & ad*ver*tên*ci.a \xmark & ad*ver*tên*cia \cmark \\
+advocacia & ad*vo*ca*ci*a \cmark & ad*vo*ca*ci-a \xmark \\
+aéreo & a-é*re.o \xmark & a*é*reo \cmark \\
+aeróbio & a*e*ró*bi.o \xmark & a*e*ró*bio \cmark \\
+aerofobia & a*e*ro*fo*bi*a \cmark & a*e*ro*fo*bi-a \xmark \\
+aerofotografia & a*e*ro*fo*to*gra*fi*a \cmark & a*e*ro*fo*to*gra*fi-a \xmark \\
+aerografia & a*e*ro*gra*fi*a \cmark & a*e*ro*gra*fi-a \xmark \\
+aeronomia & a*e*ro*no*mi*a \cmark & a*e*ro*no*mi-a \xmark \\
+aeroportuário & a*e*ro*por*tu-á*ri.o \xmark & a*e*ro*por*tu*á*rio \cmark \\
+aerovia & a*e*ro*vi*a \cmark & a*e*ro*vi-a \xmark \\
+aeroviário & a*e*ro*vi-á*ri.o \xmark & a*e*ro*vi*á*rio \cmark \\
+aético & a-é*ti*co \xmark & a*é*ti*co \cmark \\
+afasia & a*fa*si*a \cmark & a*fa*si-a \xmark \\
+afélio & a*fé*li.o \xmark & a*fé*lio \cmark \\
+afluência & a*flu-ên*ci.a \xmark & a*flu*ên*cia \cmark \\
+afluir & a*flu-ir \xmark & a*flu*ir \cmark \\
+aforia & a*fo*ri*a \cmark & a*fo*ri-a \xmark \\
+afrodisíaco & a*fro*di*sí-a*co \xmark & a*fro*di*sí*a*co \cmark \\
+agamia & a*ga*mi*a \cmark & a*ga*mi-a \xmark \\
+agência & a*gên*ci.a \xmark & a*gên*cia \cmark \\
+agenesia & a*ge*ne*si*a \cmark & a*ge*ne*si-a \xmark \\
+aglossia & a*glos*si*a \cmark & a*glos*si-a \xmark \\
+agnosia & ag*no*si*a \cmark & ag*no*si-a \xmark \\
+agogô & a*go-gô \xmark & a*go*gô \cmark \\
+agonia & a*go*ni*a \cmark & a*go*ni-a \xmark \\
+agorafobia & a*go*ra*fo*bi*a \cmark & a*go*ra*fo*bi-a \xmark \\
+agrário & a*grá*ri.o \xmark & a*grá*rio \cmark \\
+agrião & a*gri-ão \xmark & a*gri*ão \cmark \\
+agronomia & a*gro*no*mi*a \cmark & a*gro*no*mi-a \xmark \\
+agronômico & a*gro-nô*mi*co \xmark & a*gro*nô*mi*co \cmark \\
+águia & á*gui.a \xmark & á*guia \cmark \\
+aia & ai*a \cmark & ai-a \xmark \\
+aí & a-í \xmark & a*í \cmark \\
 ainda & a-in*da \xmark & a*in*da \cmark \\
-país & pa-ís \xmark & pa*ís \cmark \\
-região & re*gi-ão \xmark & re*gi*ão \cmark \\
-saúde & sa-ú*de \xmark & sa*ú*de \cmark \\
-período & pe*rí-o*do \xmark & pe*rí*o*do \cmark \\
-juiz & ju-iz \xmark & ju*iz \cmark \\
-união & u*ni-ão \xmark & u*ni*ão \cmark \\
-econômico & e*co-nô*mi*co \xmark & e*co*nô*mi*co \cmark \\
-aí & a-í \xmark & a*í \cmark \\
-sair & sa-ir \xmark & sa*ir \cmark \\
-opinião & o*pi*ni-ão \xmark & o*pi*ni*ão \cmark \\
-constituição & cons*ti*tu-i*ção \xmark & cons*ti*tu*i*ção \cmark \\
-saída & sa-í*da \xmark & sa*í*da \cmark \\
-luís & lu-ís \xmark & lu*ís \cmark \\
-campeão & cam*pe-ão \xmark & cam*pe*ão \cmark \\
+aio & ai*o \cmark & ai-o \xmark \\
+ajuizar & a*ju-i*zar \xmark & a*ju*i*zar \cmark \\
+alaúde & a*la-ú*de \xmark & a*la*ú*de \cmark \\
+albergaria & al*ber*ga*ri*a \cmark & al*ber*ga*ri-a \xmark \\
+albugínea & al*bu*gí*ne*a \cmark & al*bu*gí*ne-a \xmark \\
+alcaidaria & al*cai*da*ri*a \cmark & al*cai*da*ri-a \xmark \\
+alcaravia & al*ca*ra*vi*a \cmark & al*ca*ra*vi-a \xmark \\
+alcaria & al*ca*ri*a \cmark & al*ca*ri-a \xmark \\
+alcateia & al*ca*tei*a \cmark & al*ca*tei-a \xmark \\
+alcíone & al*cí-o*ne \xmark & al*cí*o*ne \cmark \\
+alcoólatra & al*co-ó*la*tra \xmark & al*co*ó*la*tra \cmark \\
+alcoolemia & al*co*o*le*mi*a \cmark & al*co*o*le*mi-a \xmark \\
+alcoólico & al*co-ó*li*co \xmark & al*co*ó*li*co \cmark \\
+aldeão & al*de-ão \xmark & al*de*ão \cmark \\
+aldeia & al*dei*a \cmark & al*dei-a \xmark \\
+aldeído & al*de-í*do \xmark & al*de*í*do \cmark \\
+aleatório & a*le*a*tó*ri.o \xmark & a*le*a*tó*rio \cmark \\
+alegoria & a*le*go*ri*a \cmark & a*le*go*ri-a \xmark \\
+alegria & a*le*gri*a \cmark & a*le*gri-a \xmark \\
+aleia & a*lei*a \cmark & a*lei-a \xmark \\
+aleivosia & a*lei*vo*si*a \cmark & a*lei*vo*si-a \xmark \\
+alelopatia & a*le*lo*pa*ti*a \cmark & a*le*lo*pa*ti-a \xmark \\
+aleluia & a*le*lui*a \cmark & a*le*lui-a \xmark \\
+alergia & a*ler*gi*a \cmark & a*ler*gi-a \xmark \\
+alergologia & a*ler*go*lo*gi*a \cmark & a*ler*go*lo*gi-a \xmark \\
+aletria & a*le*tri*a \cmark & a*le*tri-a \xmark \\
+aleúte & a*le-ú*te \xmark & a*le*ú*te \cmark \\
+alexia & a*le*xi*a \cmark & a*le*xi-a \xmark \\
+alfaia & al*fai*a \cmark & al*fai-a \xmark \\
+alfaiataria & al*fai*a*ta*ri*a \cmark & al*fai*a*ta*ri-a \xmark \\
+alfarrábio & al*far*rá*bi.o \xmark & al*far*rá*bio \cmark \\
+alforria & al*for*ri*a \cmark & al*for*ri-a \xmark \\
+algaravia & al*ga*ra*vi*a \cmark & al*ga*ra*vi-a \xmark \\
+algarvio & al*gar*vi*o \cmark & al*gar*vi-o \xmark \\
+algofobia & al*go*fo*bi*a \cmark & al*go*fo*bi-a \xmark \\
+alheio & a*lhei*o \cmark & a*lhei-o \xmark \\
+aliá & a*li-á \xmark & a*li*á \cmark \\
+aliáceo & a*li-á*ce.o \xmark & a*li*á*ceo \cmark \\
 aliás & a*li-ás \xmark & a*li*ás \cmark \\
-distribuição & dis*tri*bu-i*ção \xmark & dis*tri*bu*i*ção \cmark \\
-avião & a*vi-ão \xmark & a*vi*ão \cmark \\
-diário & di-á*ri*o \xmark & di*á*ri*o \cmark \\
-diária & di-á*ri*a \xmark & di*á*ri*a \cmark \\
-daí & da-í \xmark & da*í \cmark \\
-cair & ca-ir \xmark & ca*ir \cmark \\
-paraíba & pa*ra-í*ba \xmark & pa*ra*í*ba \cmark \\
-prejuízo & pre*ju-í*zo \xmark & pre*ju*í*zo \cmark \\
-judiciário & ju*di*ci-á*ri*o \xmark & ju*di*ci*á*ri*o \cmark \\
-suíça & su-í*ça \xmark & su*í*ça \cmark \\
-influência & in*flu-ên*ci*a \xmark & in*flu*ên*ci*a \cmark \\
-depoimento & de*po-i*men*to \xmark & de*po-i*men*to \xmark \\
-instituição & ins*ti*tu-i*ção \xmark & ins*ti*tu*i*ção \cmark \\
-consequência & con*se-quên*ci*a \xmark & con*se*quên*ci*a \cmark \\
-usuário & u*su-á*ri*o \xmark & u*su*á*ri*o \cmark \\
-contribuição & con*tri*bu-i*ção \xmark & con*tri*bu*i*ção \cmark \\
-diminuir & di*mi*nu-ir \xmark & di*mi*nu*ir \cmark \\
-fenômeno & fe-nô*me*no \xmark & fe*nô*me*no \cmark \\
-ruim & ru-im \xmark & ru-im \xmark \\
-construir & cons*tru-ir \xmark & cons*tru*ir \cmark \\
-veículo & ve-í*cu*lo \xmark & ve*í*cu*lo \cmark \\
-cocaína & co*ca-í*na \xmark & co*ca*í*na \cmark \\
-paul & pa-ul \xmark & pa-ul \xmark \\
-reunir & re-u*nir \xmark & re-u*nir \xmark \\
-continuidade & con*ti*nu-i*da*de \xmark & con*ti*nu*i*da*de \cmark \\
-diálogo & di-á*lo*go \xmark & di*á*lo*go \cmark \\
-atrair & a*tra-ir \xmark & a*tra*ir \cmark \\
-ocasião & o*ca*si-ão \xmark & o*ca*si*ão \cmark \\
-sebastião & se*bas*ti-ão \xmark & se*bas*ti*ão \cmark \\
-sequência & se-quên*ci*a \xmark & se*quên*ci*a \cmark \\
-substituir & subs*ti*tu-ir \xmark & subs*ti*tu*ir \cmark \\
-incluir & in*clu-ir \xmark & in*clu*ir \cmark \\
-gaúcho & ga-ú*cho \xmark & ga*ú*cho \cmark \\
-poluição & po*lu-i*ção \xmark & po*lu*i*ção \cmark \\
-proibido & pro-i*bi*do \xmark & pro*i*bi*do \cmark \\
-rainha & ra-i*nha \xmark & ra*i*nha \cmark \\
-religião & re*li*gi-ão \xmark & re*li*gi*ão \cmark \\
-paraíso & pa*ra-í*so \xmark & pa*ra*í*so \cmark \\
-frequência & fre-quên*ci*a \xmark & fre*quên*ci*a \cmark \\
-distribuir & dis*tri*bu-ir \xmark & dis*tri*bu*ir \cmark \\
-substituição & subs*ti*tu-i*ção \xmark & subs*ti*tu*i*ção \cmark \\
-contribuinte & con*tri*bu-in*te \xmark & con*tri*bu*in*te \cmark \\
-conteúdo & con*te-ú*do \xmark & con*te*ú*do \cmark \\
-leão & le-ão \xmark & le*ão \cmark \\
-concluir & con*clu-ir \xmark & con*clu*ir \cmark \\
-proibição & pro-i*bi*ção \xmark & pro*i*bi*ção \cmark \\
-sociólogo & so*ci-ó*lo*go \xmark & so*ci*ó*lo*go \cmark \\
-construído & cons*tru-í*do \xmark & cons*tru*í*do \cmark \\
-maceió & ma*cei-ó \xmark & ma*cei*ó \cmark \\
-diminuição & di*mi*nu-i*ção \xmark & di*mi*nu*i*ção \cmark \\
-crediário & cre*di-á*ri*o \xmark & cre*di*á*ri*o \cmark \\
-pivô & pi-vô \xmark & pi*vô \cmark \\
-substituído & subs*ti*tu-í*do \xmark & subs*ti*tu*í*do \cmark \\
-razoável & ra*zo-á*vel \xmark & ra*zo*á*vel \cmark \\
-juíza & ju-í*za \xmark & ju*í*za \cmark \\
-coincidência & co-in*ci*dên*ci*a \xmark & co*in*ci*dên*ci*a \cmark \\
-rebelião & re*be*li-ão \xmark & re*be*li*ão \cmark \\
-noticiário & no*ti*ci-á*ri*o \xmark & no*ti*ci*á*ri*o \cmark \\
-olimpíada & o*lim*pí-a*da \xmark & o*lim*pí*a*da \cmark \\
-imobiliário & i*mo*bi*li-á*ri*o \xmark & i*mo*bi*li*á*ri*o \cmark \\
-austríaco & aus*trí-a*co \xmark & aus*trí*a*co \cmark \\
-penitenciária & pe*ni*ten*ci-á*ri*a \xmark & pe*ni*ten*ci*á*ri*a \cmark \\
-psicologia & p.si*co*lo*gi*a \xmark & psi*co*lo*gi*a \cmark \\
-contribuir & con*tri*bu-ir \xmark & con*tri*bu*ir \cmark \\
-aéreo & a-é*re*o \xmark & a*é*re*o \cmark \\
-psicanálise & p.si*ca*ná*li*se \xmark & psi*ca*ná*li*se \cmark \\
-vestuário & ves*tu-á*ri*o \xmark & ves*tu*á*ri*o \cmark \\
-destruição & des*tru-i*ção \xmark & des*tru*i*ção \cmark \\
-viúva & vi-ú*va \xmark & vi*ú*va \cmark \\
-distribuído & dis*tri*bu-í*do \xmark & dis*tri*bu*í*do \cmark \\
-juízo & ju-í*zo \xmark & ju*í*zo \cmark \\
-constituinte & cons*ti*tu-in*te \xmark & cons*ti*tu-in*te \xmark \\
-presidenciável & pre*si*den*ci-á*vel \xmark & pre*si*den*ci*á*vel \cmark \\
-viável & vi-á*vel \xmark & vi*á*vel \cmark \\
-suíço & su-í*ço \xmark & su*í*ço \cmark \\
-destruir & des*tru-ir \xmark & des*tru*ir \cmark \\
-saído & sa-í*do \xmark & sa*í*do \cmark \\
-concluído & con*clu-í*do \xmark & con*clu*í*do \cmark \\
-distribuidora & dis*tri*bu-i*do*ra \xmark & dis*tri*bu*i*do*ra \cmark \\
-imobiliária & i*mo*bi*li-á*ri*a \xmark & i*mo*bi*li*á*ri*a \cmark \\
-sinfônica & sin-fô*ni*ca \xmark & sin*fô*ni*ca \cmark \\
-uísque & u-ís*que \xmark & u*ís*que \cmark \\
-poética & po-é*ti*ca \xmark & po*é*ti*ca \cmark \\
-prostituição & pros*ti*tu-i*ção \xmark & pros*ti*tu*i*ção \cmark \\
-rodoviário & ro*do*vi-á*ri*o \xmark & ro*do*vi*á*ri*o \cmark \\
-bicampeão & bi*cam*pe-ão \xmark & bi*cam*pe*ão \cmark \\
-psicológico & p.si*co*ló*gi*co \xmark & psi*co*ló*gi*co \cmark \\
-proibir & pro-i*bir \xmark & pro*i*bir \cmark \\
-triunfo & tri-un*fo \xmark & tri*un*fo \cmark \\
-variável & va*ri-á*vel \xmark & va*ri*á*vel \cmark \\
-criciúma & cri*ci-ú*ma \xmark & cri*ci*ú*ma \cmark \\
-sinônimo & si-nô*ni*mo \xmark & si*nô*ni*mo \cmark \\
-legião & le*gi-ão \xmark & le*gi*ão \cmark \\
-caído & ca-í*do \xmark & ca*í*do \cmark \\
-equívoco & e-quí*vo*co \xmark & e*quí*vo*co \cmark \\
-baía & ba-í-a \xmark & ba*í*a \cmark \\
-quilômetro & qui-lô*me*tro \xmark & qui*lô*me*tro \cmark \\
-raiz & ra-iz \xmark & ra-iz \xmark \\
-psiquiatra & p.si*qui*a*tra \xmark & psi*qui*a*tra \cmark \\
-tricampeão & tri*cam*pe-ão \xmark & tri*cam*pe*ão \cmark \\
-psicanalista & p.si*ca*na*lis*ta \xmark & psi*ca*na*lis*ta \cmark \\
-ruído & ru-í*do \xmark & ru*í*do \cmark \\
-possuir & pos*su-ir \xmark & pos*su*ir \cmark \\
-coibir & co-i*bir \xmark & co-i*bir \xmark \\
-soviético & so*vi-é*ti*co \xmark & so*vi*é*ti*co \cmark \\
-inviável & in*vi-á*vel \xmark & in*vi*á*vel \cmark \\
+alimária & a*li*má*ri.a \xmark & a*li*má*ria \cmark \\
+alimentício & a*li*men*tí*ci.o \xmark & a*li*men*tí*cio \cmark \\
+alínea & a*lí*ne.a \xmark & a*lí*nea \cmark \\
+alívio & a*lí*vi.o \xmark & a*lí*vio \cmark \\
+almôndega & al-môn*de*ga \xmark & al*môn*de*ga \cmark \\
 alô & a-lô \xmark & a*lô \cmark \\
-heroína & he*ro-í*na \xmark & he*ro*í*na \cmark \\
-destruído & des*tru-í*do \xmark & des*tru*í*do \cmark \\
-telefônico & te*le-fô*ni*co \xmark & te*le*fô*ni*co \cmark \\
-saí & sa-í \xmark & sa*í \cmark \\
-suíte & su-í*te \xmark & su*í*te \cmark \\
-asiático & a*si-á*ti*co \xmark & a*si*á*ti*co \cmark \\
-irônico & i-rô*ni*co \xmark & i*rô*ni*co \cmark \\
-avô & a-vô \xmark & a*vô \cmark \\
-restituição & res*ti*tu-i*ção \xmark & res*ti*tu*i*ção \cmark \\
-atribuir & a*tri*bu-ir \xmark & a*tri*bu*ir \cmark \\
-ingenuidade & in*ge*nu-i*da*de \xmark & in*ge*nu*i*da*de \cmark \\
-psicólogo & p.si*có*lo*go \xmark & psi*có*lo*go \cmark \\
-pneu & p.neu \xmark & pneu \cmark \\
-tetracampeão & te*tra*cam*pe-ão \xmark & te*tra*cam*pe*ão \cmark \\
-vestiário & ves*ti-á*ri*o \xmark & ves*ti*á*ri*o \cmark \\
-proteína & pro*te-í*na \xmark & pro*te*í*na \cmark \\
-espião & es*pi-ão \xmark & es*pi*ão \cmark \\
-ciúme & ci-ú*me \xmark & ci*ú*me \cmark \\
-napoleão & na*po*le-ão \xmark & na*po*le*ão \cmark \\
-teórica & te-ó*ri*ca \xmark & te*ó*ri*ca \cmark \\
-intermediário & in*ter*me*di-á*ri*o \xmark & in*ter*me*di*á*ri*o \cmark \\
-constituir & cons*ti*tu-ir \xmark & cons*ti*tu*ir \cmark \\
-embrião & em*bri-ão \xmark & em*bri*ão \cmark \\
-autônomo & au-tô*no*mo \xmark & au*tô*no*mo \cmark \\
-confiável & con*fi-á*vel \xmark & con*fi*á*vel \cmark \\
-teórico & te-ó*ri*co \xmark & te*ó*ri*co \cmark \\
-estômago & es-tô*ma*go \xmark & es*tô*ma*go \cmark \\
-termômetro & ter-mô*me*tro \xmark & ter*mô*me*tro \cmark \\
-homônimo & ho-mô*ni*mo \xmark & ho*mô*ni*mo \cmark \\
-excluído & ex*clu-í*do \xmark & ex*clu*í*do \cmark \\
-penitenciário & pe*ni*ten*ci-á*ri*o \xmark & pe*ni*ten*ci*á*ri*o \cmark \\
-cardíaco & car*dí-a*co \xmark & car*dí*a*co \cmark \\
-mutuário & mu*tu-á*ri*o \xmark & mu*tu*á*ri*o \cmark \\
-aquém & a-quém \xmark & a*quém \cmark \\
-viário & vi-á*ri*o \xmark & vi*á*ri*o \cmark \\
-despoluição & des*po*lu-i*ção \xmark & des*po*lu*i*ção \cmark \\
-medíocre & me*dí-o*cre \xmark & me*dí*o*cre \cmark \\
-reintegração & re-in*te*gra*ção \xmark & re*in*te*gra*ção \cmark \\
-marquês & mar-quês \xmark & mar*quês \cmark \\
-beneficiário & be*ne*fi*ci-á*ri*o \xmark & be*ne*fi*ci*á*ri*o \cmark \\
-atribuição & a*tri*bu-i*ção \xmark & a*tri*bu*i*ção \cmark \\
-balneário & bal*ne-á*ri*o \xmark & bal*ne*á*ri*o \cmark \\
-coreógrafo & co*re-ó*gra*fo \xmark & co*re*ó*gra*fo \cmark \\
-incômodo & in-cô*mo*do \xmark & in*cô*mo*do \cmark \\
-sanduíche & san*du-í*che \xmark & san*du*í*che \cmark \\
-pecuária & pe*cu-á*ri*a \xmark & pe*cu*á*ri*a \cmark \\
-cirurgião & ci*rur*gi-ão \xmark & ci*rur*gi*ão \cmark \\
-jaú & ja-ú \xmark & ja*ú \cmark \\
-reconstruir & re*cons*tru-ir \xmark & re*cons*tru*ir \cmark \\
-influir & in*flu-ir \xmark & in*flu*ir \cmark \\
-santuário & san*tu-á*ri*o \xmark & san*tu*á*ri*o \cmark \\
-sutiã & su*ti-ã \xmark & su*ti*ã \cmark \\
-poético & po-é*ti*co \xmark & po*é*ti*co \cmark \\
-ensaísta & en*sa-ís*ta \xmark & en*sa*ís*ta \cmark \\
-porquê & por-quê \xmark & por*quê \cmark \\
-biólogo & bi-ó*lo*go \xmark & bi*ó*lo*go \cmark \\
-extrair & ex*tra-ir \xmark & ex*tra*ir \cmark \\
-reconstituição & re*cons*ti*tu-i*ção \xmark & re*cons*ti*tu*i*ção \cmark \\
-anfitrião & an*fi*tri-ão \xmark & an*fi*tri*ão \cmark \\
-anônimo & a-nô*ni*mo \xmark & a*nô*ni*mo \cmark \\
-aquático & a-quá*ti*co \xmark & a*quá*ti*co \cmark \\
-excluir & ex*clu-ir \xmark & ex*clu*ir \cmark \\
-filarmônica & fi*lar-mô*ni*ca \xmark & fi*lar*mô*ni*ca \cmark \\
-juizado & ju-i*za*do \xmark & ju*i*za*do \cmark \\
-peão & pe-ão \xmark & pe*ão \cmark \\
-previdenciário & pre*vi*den*ci-á*ri*o \xmark & pre*vi*den*ci*á*ri*o \cmark \\
-constituído & cons*ti*tu-í*do \xmark & cons*ti*tu*í*do \cmark \\
-pornô & por-nô \xmark & por*nô \cmark \\
-psiquiátrico & p.si*qui-á*tri*co \xmark & psi*qui*á*tri*co \cmark \\
-moinho & mo-i*nho \xmark & mo*i*nho \cmark \\
-obstruir & obs*tru-ir \xmark & obs*tru*ir \cmark \\
-psiquiatria & p.si*qui*a*tri*a \xmark & psi*qui*a*tri*a \cmark \\
-reindexação & re-in*de*xa*ção \xmark & re-in*de*xa*ção \xmark \\
-aquário & a-quá*ri*o \xmark & a*quá*ri*o \cmark \\
-amendoim & a*men*do-im \xmark & a*men*do-im \xmark \\
-baú & ba-ú \xmark & ba*ú \cmark \\
-distribuidor & dis*tri*bu-i*dor \xmark & dis*tri*bu*i*dor \cmark \\
-trair & tra-ir \xmark & tra*ir \cmark \\
-intuição & in*tu-i*ção \xmark & in*tu*i*ção \cmark \\
-petroquímica & pe*tro-quí*mi*ca \xmark & pe*tro*quí*mi*ca \cmark \\
-evoluir & e*vo*lu-ir \xmark & e*vo*lu*ir \cmark \\
-petroquímico & pe*tro-quí*mi*co \xmark & pe*tro*quí*mi*co \cmark \\
-asiática & a*si-á*ti*ca \xmark & a*si*á*ti*ca \cmark \\
-dinamarquês & di*na*mar-quês \xmark & di*na*mar*quês \cmark \\
-tcheco & t.che*co \xmark & tche*co \cmark \\
-diminuído & di*mi*nu-í*do \xmark & di*mi*nu*í*do \cmark \\
-instituir & ins*ti*tu-ir \xmark & ins*ti*tu*ir \cmark \\
-lampião & lam*pi-ão \xmark & lam*pi*ão \cmark \\
-arquitetônico & ar*qui*te-tô*ni*co \xmark & ar*qui*te*tô*ni*co \cmark \\
-atraído & a*tra-í*do \xmark & a*tra*í*do \cmark \\
-gastronômico & gas*tro-nô*mi*co \xmark & gas*tro*nô*mi*co \cmark \\
-vibrião & vi*bri-ão \xmark & vi*bri*ão \cmark \\
-caraíba & ca*ra-í*ba \xmark & ca*ra*í*ba \cmark \\
-ferroviário & fer*ro*vi-á*ri*o \xmark & fer*ro*vi*á*ri*o \cmark \\
-mobiliário & mo*bi*li-á*ri*o \xmark & mo*bi*li*á*ri*o \cmark \\
-robô & ro-bô \xmark & ro*bô \cmark \\
-traído & tra-í*do \xmark & tra*í*do \cmark \\
-chatô & cha-tô \xmark & cha*tô \cmark \\
-viés & vi-és \xmark & vi*és \cmark \\
-biquíni & bi-quí*ni \xmark & bi*quí*ni \cmark \\
-pneumonia & p.neu*mo*ni*a \xmark & pneu*mo*ni*a \cmark \\
-galeão & ga*le-ão \xmark & ga*le*ão \cmark \\
-pseudônimo & p.seu-dô*ni*mo \xmark & pseu*dô*ni*mo \cmark \\
-psicologicamente & p.si*co*lo*gi*ca*men*te \xmark & psi*co*lo*gi*ca*men*te \cmark \\
-tatuí & ta*tu-í \xmark & ta*tu*í \cmark \\
-anuário & a*nu-á*ri*o \xmark & a*nu*á*ri*o \cmark \\
-contrair & con*tra-ir \xmark & con*tra*ir \cmark \\
-curió & cu*ri-ó \xmark & cu*ri*ó \cmark \\
-egoísmo & e*go-ís*mo \xmark & e*go*ís*mo \cmark \\
-poliéster & po*li-és*ter \xmark & po*li*és*ter \cmark \\
-caótico & ca-ó*ti*co \xmark & ca*ó*ti*co \cmark \\
-descontraído & des*con*tra-í*do \xmark & des*con*tra*í*do \cmark \\
-hanseníase & han*se*ní-a*se \xmark & han*se*ní*a*se \cmark \\
-macedônia & ma*ce-dô*ni*a \xmark & ma*ce*dô*ni*a \cmark \\
-heroísmo & he*ro-ís*mo \xmark & he*ro*ís*mo \cmark \\
-instituído & ins*ti*tu-í*do \xmark & ins*ti*tu*í*do \cmark \\
-periódico & pe*ri-ó*di*co \xmark & pe*ri*ó*di*co \cmark \\
-abdômen & ab-dô*men \xmark & ab*dô*men \cmark \\
-paraibano & pa*ra-i*ba*no \xmark & pa*ra-i*ba*no \xmark \\
-psíquico & p.sí*qui*co \xmark & psí*qui*co \cmark \\
-reconstituir & re*cons*ti*tu-ir \xmark & re*cons*ti*tu*ir \cmark \\
-oásis & o-á*sis \xmark & o*á*sis \cmark \\
-parnaíba & par*na-í*ba \xmark & par*na*í*ba \cmark \\
-usufruir & u*su*fru-ir \xmark & u*su*fru*ir \cmark \\
-camelô & ca*me-lô \xmark & ca*me*lô \cmark \\
-maníaco & ma*ní-a*co \xmark & ma*ní*a*co \cmark \\
-sabiá & sa*bi-á \xmark & sa*bi*á \cmark \\
-agronômico & a*gro-nô*mi*co \xmark & a*gro*nô*mi*co \cmark \\
-astronômico & as*tro-nô*mi*co \xmark & as*tro*nô*mi*co \cmark \\
-psicopata & p.si*co*pa*ta \xmark & psi*co*pa*ta \cmark \\
-geógrafo & ge-ó*gra*fo \xmark & ge*ó*gra*fo \cmark \\
-ideário & i*de-á*ri*o \xmark & i*de*á*ri*o \cmark \\
-piá & pi-á \xmark & pi*á \cmark \\
-alcoólatra & al*co-ó*la*tra \xmark & al*co*ó*la*tra \cmark \\
-biógrafo & bi-ó*gra*fo \xmark & bi*ó*gra*fo \cmark \\
-coincidir & co-in*ci*dir \xmark & co*in*ci*dir \cmark \\
-escorpião & es*cor*pi-ão \xmark & es*cor*pi*ão \cmark \\
-fluência & flu-ên*ci*a \xmark & flu*ên*ci*a \cmark \\
-ruína & ru-í*na \xmark & ru*í*na \cmark \\
-delinquência & de*lin-quên*ci*a \xmark & de*lin*quên*ci*a \cmark \\
-contraído & con*tra-í*do \xmark & con*tra*í*do \cmark \\
-diluir & di*lu-ir \xmark & di*lu*ir \cmark \\
-psicose & p.si*co*se \xmark & psi*co*se \cmark \\
-bioquímica & bi*o-quí*mi*ca \xmark & bi*o*quí*mi*ca \cmark \\
-fluidez & flu-i*dez \xmark & flu-i*dez \xmark \\
-futevôlei & fu*te-vô*lei \xmark & fu*te*vô*lei \cmark \\
-judaísmo & ju*da-ís*mo \xmark & ju*da*ís*mo \cmark \\
-viúvo & vi-ú*vo \xmark & vi*ú*vo \cmark \\
-capô & ca-pô \xmark & ca*pô \cmark \\
-casuísmo & ca*su-ís*mo \xmark & ca*su*ís*mo \cmark \\
-receituário & re*cei*tu-á*ri*o \xmark & re*cei*tu*á*ri*o \cmark \\
-agrião & a*gri-ão \xmark & a*gri*ão \cmark \\
-comerciário & co*mer*ci-á*ri*o \xmark & co*mer*ci*á*ri*o \cmark \\
-estereótipo & es*te*re-ó*ti*po \xmark & es*te*re*ó*ti*po \cmark \\
-psicoterapia & p.si*co*te*ra*pi*a \xmark & psi*co*te*ra*pi*a \cmark \\
-vascaíno & vas*ca-í*no \xmark & vas*ca*í*no \cmark \\
-arquitetônica & ar*qui*te-tô*ni*ca \xmark & ar*qui*te*tô*ni*ca \cmark \\
-macroeconômico & ma*cro*e*co-nô*mi*co \xmark & ma*cro*e*co*nô*mi*co \cmark \\
-restituir & res*ti*tu-ir \xmark & res*ti*tu*ir \cmark \\
-rutherford & ru-ther*ford \xmark & ru-ther*ford \xmark \\
-triunfal & tri-un*fal \xmark & tri*un*fal \cmark \\
-guardião & guar*di-ão \xmark & guar*di*ão \cmark \\
-oriundo & o*ri-un*do \xmark & o*ri*un*do \cmark \\
-arqueólogo & ar*que-ó*lo*go \xmark & ar*que*ó*lo*go \cmark \\
-carbônico & car-bô*ni*co \xmark & car*bô*ni*co \cmark \\
-stalinista & s.ta*li*nis*ta \xmark & sta*li*nis*ta \cmark \\
-egoísta & e*go-ís*ta \xmark & e*go*ís*ta \cmark \\
-portuário & por*tu-á*ri*o \xmark & por*tu*á*ri*o \cmark \\
-recaída & re*ca-í*da \xmark & re*ca*í*da \cmark \\
-reiniciar & re-i*ni*ci*ar \xmark & re-i*ni*ci*ar \xmark \\
-reurbanização & re-ur*ba*ni*za*ção \xmark & re-ur*ba*ni*za*ção \xmark \\
-teólogo & te-ó*lo*go \xmark & te*ó*lo*go \cmark \\
-baião & bai-ão \xmark & bai*ão \cmark \\
-genuíno & ge*nu-í*no \xmark & ge*nu*í*no \cmark \\
-hegemônico & he*ge-mô*ni*co \xmark & he*ge*mô*ni*co \cmark \\
-resquício & res-quí*ci*o \xmark & res*quí*ci*o \cmark \\
-retribuição & re*tri*bu-i*ção \xmark & re*tri*bu*i*ção \cmark \\
-confluência & con*flu-ên*ci*a \xmark & con*flu*ên*ci*a \cmark \\
-fluir & flu-ir \xmark & flu*ir \cmark \\
-imperdoável & im*per*do-á*vel \xmark & im*per*do*á*vel \cmark \\
-distrair & dis*tra-ir \xmark & dis*tra*ir \cmark \\
-guaíba & gua-í*ba \xmark & gua*í*ba \cmark \\
-intuitivo & in*tu-i*ti*vo \xmark & in*tu*i*ti*vo \cmark \\
-orquídea & or-quí*de*a \xmark & or*quí*de*a \cmark \\
-semiótica & se*mi-ó*ti*ca \xmark & se*mi*ó*ti*ca \cmark \\
-vovô & vo-vô \xmark & vo*vô \cmark \\
-campainha & cam*pa-i*nha \xmark & cam*pa*i*nha \cmark \\
-czar & c.zar \xmark & czar \cmark \\
-diluição & di*lu-i*ção \xmark & di*lu*i*ção \cmark \\
-distraído & dis*tra-í*do \xmark & dis*tra*í*do \cmark \\
-eloquência & e*lo-quên*ci*a \xmark & e*lo*quên*ci*a \cmark \\
-insubstituível & in*subs*ti*tu-í*vel \xmark & in*subs*ti*tu*í*vel \cmark \\
-reinventar & re-in*ven*tar \xmark & re*in*ven*tar \cmark \\
-retribuir & re*tri*bu-ir \xmark & re*tri*bu*ir \cmark \\
-rubéola & ru*bé-o*la \xmark & ru*bé*o*la \cmark \\
-abruptamente & a.b-rup*ta*men*te \xmark & a.b-rup*ta*men*te \xmark \\
-maniqueísmo & ma*ni*que-ís*mo \xmark & ma*ni*que*ís*mo \cmark \\
-antiquário & an*ti-quá*ri*o \xmark & an*ti*quá*ri*o \cmark \\
-harmônica & har-mô*ni*ca \xmark & har*mô*ni*ca \cmark \\
-judô & ju-dô \xmark & ju*dô \cmark \\
-maniqueísta & ma*ni*que-ís*ta \xmark & ma*ni*que*ís*ta \cmark \\
-tchau & t.chau \xmark & tchau \cmark \\
-moído & mo-í*do \xmark & mo*í*do \cmark \\
-psicanalítico & p.si*ca*na*lí*ti*co \xmark & psi*ca*na*lí*ti*co \cmark \\
-caíco & ca-í*co \xmark & ca*í*co \cmark \\
-descontinuidade & des*con*ti*nu-i*da*de \xmark & des*con*ti*nu*i*da*de \cmark \\
-tarô & ta-rô \xmark & ta*rô \cmark \\
-absenteísmo & ab*sen*te-ís*mo \xmark & ab*sen*te*ís*mo \cmark \\
-anuência & a*nu-ên*ci*a \xmark & a*nu*ên*ci*a \cmark \\
-etíope & e*tí-o*pe \xmark & e*tí*o*pe \cmark \\
-ofurô & o*fu-rô \xmark & o*fu*rô \cmark \\
-panteão & pan*te-ão \xmark & pan*te*ão \cmark \\
-atômico & a-tô*mi*co \xmark & a*tô*mi*co \cmark \\
-corroído & cor*ro-í*do \xmark & cor*ro*í*do \cmark \\
-destituído & des*ti*tu-í*do \xmark & des*ti*tu*í*do \cmark \\
-estagiário & es*ta*gi-á*ri*o \xmark & es*ta*gi*á*ri*o \cmark \\
-inadiável & i*na*di-á*vel \xmark & i*na*di*á*vel \cmark \\
-instruído & ins*tru-í*do \xmark & ins*tru*í*do \cmark \\
+alódio & a*ló*di.o \xmark & a*ló*dio \cmark \\
+aloé & a*lo-é \xmark & a*lo*é \cmark \\
+aloés & a*lo-és \xmark & a*lo*és \cmark \\
+alometria & a*lo*me*tri*a \cmark & a*lo*me*tri-a \xmark \\
+alopatia & a*lo*pa*ti*a \cmark & a*lo*pa*ti-a \xmark \\
+alopecia & a*lo*pe*ci*a \cmark & a*lo*pe*ci-a \xmark \\
+alquimia & al*qui*mi*a \cmark & al*qui*mi-a \xmark \\
+alquímico & al-quí*mi*co \xmark & al*quí*mi*co \cmark \\
+alteia & al*tei*a \cmark & al*tei-a \xmark \\
+alternância & al*ter*nân*ci.a \xmark & al*ter*nân*cia \cmark \\
+altimetria & al*ti*me*tri*a \cmark & al*ti*me*tri-a \xmark \\
+altruísmo & al*tru-ís*mo \xmark & al*tru*ís*mo \cmark \\
+altruísta & al*tru-ís*ta \xmark & al*tru*ís*ta \cmark \\
+alucinatório & a*lu*ci*na*tó*ri.o \xmark & a*lu*ci*na*tó*rio \cmark \\
+aluimento & a*lu-i*men*to \xmark & a*lu-i*men*to \xmark \\
+aluir & a*lu-ir \xmark & a*lu*ir \cmark \\
+alumínio & a*lu*mí*ni.o \xmark & a*lu*mí*nio \cmark \\
+aluvião & a*lu*vi-ão \xmark & a*lu*vi*ão \cmark \\
+alvedrio & al*ve*dri*o \cmark & al*ve*dri-o \xmark \\
+alvenaria & al*ve*na*ri*a \cmark & al*ve*na*ri-a \xmark \\
+alvéolo & al*vé-o*lo \xmark & al*vé*o*lo \cmark \\
+amásia & a*má*si.a \xmark & a*má*sia \cmark \\
+amásio & a*má*si.o \xmark & a*má*sio \cmark \\
 amazônico & a*ma-zô*ni*co \xmark & a*ma*zô*ni*co \cmark \\
-anuidade & a*nu-i*da*de \xmark & a*nu*i*da*de \cmark \\
-evoluído & e*vo*lu-í*do \xmark & e*vo*lu*í*do \cmark \\
-faísca & fa-ís*ca \xmark & fa*ís*ca \cmark \\
-harmônico & har-mô*ni*co \xmark & har*mô*ni*co \cmark \\
-patriótico & pa*tri-ó*ti*co \xmark & pa*tri*ó*ti*co \cmark \\
-presidiário & pre*si*di-á*ri*o \xmark & pre*si*di*á*ri*o \cmark \\
-reconstruído & re*cons*tru-í*do \xmark & re*cons*tru*í*do \cmark \\
-tricô & tri-cô \xmark & tri*cô \cmark \\
-antiético & an*ti-é*ti*co \xmark & an*ti*é*ti*co \cmark \\
-cronômetro & cro-nô*me*tro \xmark & cro*nô*me*tro \cmark \\
-destituição & des*ti*tu-i*ção \xmark & des*ti*tu*i*ção \cmark \\
-fiúza & fi-ú*za \xmark & fi*ú*za \cmark \\
-píer & pí-er \xmark & pí-er \xmark \\
-psique & p.si*que \xmark & psi*que \cmark \\
-recair & re*ca-ir \xmark & re*ca*ir \cmark \\
-sinfônico & sin-fô*ni*co \xmark & sin*fô*ni*co \cmark \\
-triunfante & tri-un*fan*te \xmark & tri*un*fan*te \cmark \\
-adail & a*da-il \xmark & a*da-il \xmark \\
-atônito & a-tô*ni*to \xmark & a*tô*ni*to \cmark \\
-birô & bi-rô \xmark & bi*rô \cmark \\
-cafeína & ca*fe-í*na \xmark & ca*fe*í*na \cmark \\
-ideólogo & i*de-ó*lo*go \xmark & i*de*ó*lo*go \cmark \\
-inequívoco & i*ne-quí*vo*co \xmark & i*ne*quí*vo*co \cmark \\
-míope & mí-o*pe \xmark & mí*o*pe \cmark \\
-poá & po-á \xmark & po*á \cmark \\
-stalinismo & s.ta*li*nis*mo \xmark & sta*li*nis*mo \cmark \\
-suíno & su-í*no \xmark & su*í*no \cmark \\
-voyeurismo & voy-eu*ris*mo \xmark & voy-eu*ris*mo \xmark \\
-camaleão & ca*ma*le-ão \xmark & ca*ma*le*ão \cmark \\
-dióxido & di-ó*xi*do \xmark & di*ó*xi*do \cmark \\
-geólogo & ge-ó*lo*go \xmark & ge*ó*lo*go \cmark \\
-ilíada & i*lí-a*da \xmark & i*lí*a*da \cmark \\
-impermeável & im*per*me-á*vel \xmark & im*per*me*á*vel \cmark \\
-jesuíta & je*su-í*ta \xmark & je*su*í*ta \cmark \\
-suástica & su-ás*ti*ca \xmark & su*ás*ti*ca \cmark \\
-bioquímico & bi*o-quí*mi*co \xmark & bi*o*quí*mi*co \cmark \\
-buquê & bu-quê \xmark & bu*quê \cmark \\
-esôfago & e-sô*fa*go \xmark & e*sô*fa*go \cmark \\
-folião & fo*li-ão \xmark & fo*li*ão \cmark \\
-quilowatt & qui*lo-watt \xmark & qui*lo-watt \xmark \\
-ruir & ru-ir \xmark & ru*ir \cmark \\
-altruísmo & al*tru-ís*mo \xmark & al*tru*ís*mo \cmark \\
-equânime & e-quâ*ni*me \xmark & e*quâ*ni*me \cmark \\
-fruição & fru-i*ção \xmark & fru*i*ção \cmark \\
-insaciável & in*sa*ci-á*vel \xmark & in*sa*ci*á*vel \cmark \\
-caída & ca-í*da \xmark & ca*í*da \cmark \\
-ciático & ci-á*ti*co \xmark & ci*á*ti*co \cmark \\
-gavião & ga*vi-ão \xmark & ga*vi*ão \cmark \\
-gratuidade & gra*tu-i*da*de \xmark & gra*tu*i*da*de \cmark \\
-irremediável & ir*re*me*di-á*vel \xmark & ir*re*me*di*á*vel \cmark \\
-ladainha & la*da-i*nha \xmark & la*da*i*nha \cmark \\
-piauiense & pi*au-i*en*se \xmark & pi*au-i*en*se \xmark \\
-prostituir & pros*ti*tu-ir \xmark & pros*ti*tu*ir \cmark \\
-triunfar & tri-un*far \xmark & tri*un*far \cmark \\
-acuidade & a*cu-i*da*de \xmark & a*cu*i*da*de \cmark \\
-adriático & a*dri-á*ti*co \xmark & a*dri*á*ti*co \cmark \\
-afrodisíaco & a*fro*di*sí-a*co \xmark & a*fro*di*sí*a*co \cmark \\
-bioética & bi*o-é*ti*ca \xmark & bi*o*é*ti*ca \cmark \\
-cocô & co-cô \xmark & co*cô \cmark \\
-instruir & ins*tru-ir \xmark & ins*tru*ir \cmark \\
-paradisíaco & pa*ra*di*sí-a*co \xmark & pa*ra*di*sí*a*co \cmark \\
-poluir & po*lu-ir \xmark & po*lu*ir \cmark \\
-possuído & pos*su-í*do \xmark & pos*su*í*do \cmark \\
-sublinha & su.b-li*nha \xmark & su.b-li*nha \xmark \\
-antibiótico & an*ti*bi-ó*ti*co \xmark & an*ti*bi*ó*ti*co \cmark \\
-apreciável & a*pre*ci-á*vel \xmark & a*pre*ci*á*vel \cmark \\
-desobstruir & de*sobs*tru-ir \xmark & de*sobs*tru*ir \cmark \\
-destruidor & des*tru-i*dor \xmark & des*tru*i*dor \cmark \\
-diáspora & di-ás*po*ra \xmark & di*ás*po*ra \cmark \\
-diluído & di*lu-í*do \xmark & di*lu*í*do \cmark \\
-maiúsculo & mai-ús*cu*lo \xmark & mai*ús*cu*lo \cmark \\
-miúdo & mi-ú*do \xmark & mi*ú*do \cmark \\
-pentacampeão & pen*ta*cam*pe-ão \xmark & pen*ta*cam*pe*ão \cmark \\
-retraído & re*tra-í*do \xmark & re*tra*í*do \cmark \\
-subtrair & sub*tra-ir \xmark & sub*tra*ir \cmark \\
-suéter & su-é*ter \xmark & su*é*ter \cmark \\
-açaí & a*ça-í \xmark & a*ça*í \cmark \\
-alcoólico & al*co-ó*li*co \xmark & al*co*ó*li*co \cmark \\
-despoluir & des*po*lu-ir \xmark & des*po*lu*ir \cmark \\
-diurno & di-ur*no \xmark & di*ur*no \cmark \\
-inexequível & i*ne*xe-quí*vel \xmark & i*ne*xe*quí*vel \cmark \\
-prontuário & pron*tu-á*ri*o \xmark & pron*tu*á*ri*o \cmark \\
-psicoterapeuta & p.si*co*te*ra*peu*ta \xmark & psi*co*te*ra*peu*ta \cmark \\
-saúva & sa-ú*va \xmark & sa*ú*va \cmark \\
-tabelião & ta*be*li-ão \xmark & ta*be*li*ão \cmark \\
-abrupto & a.b-rup*to \xmark & a.b-rup*to \xmark \\
-destituir & des*ti*tu-ir \xmark & des*ti*tu*ir \cmark \\
-dionisíaco & di*o*ni*sí-a*co \xmark & di*o*ni*sí*a*co \cmark \\
-lacônico & la-cô*ni*co \xmark & la*cô*ni*co \cmark \\
-megawatt & me*ga-watt \xmark & me*ga-watt \xmark \\
-poliuretano & po*li-u*re*ta*no \xmark & po*li*u*re*ta*no \cmark \\
-protozoário & pro*to*zo-á*ri*o \xmark & pro*to*zo*á*ri*o \cmark \\
-reincidente & re-in*ci*den*te \xmark & re*in*ci*den*te \cmark \\
-reintegrar & re-in*te*grar \xmark & re*in*te*grar \cmark \\
-reinvenção & re-in*ven*ção \xmark & re*in*ven*ção \cmark \\
-afluência & a*flu-ên*ci*a \xmark & a*flu*ên*ci*a \cmark \\
-assiduidade & as*si*du-i*da*de \xmark & as*si*du*i*da*de \cmark \\
-coágulo & co-á*gu*lo \xmark & co*á*gu*lo \cmark \\
-cuíca & cu-í*ca \xmark & cu*í*ca \cmark \\
-faraó & fa*ra-ó \xmark & fa*ra*ó \cmark \\
-fundiário & fun*di-á*ri*o \xmark & fun*di*á*ri*o \cmark \\
-incendiário & in*cen*di-á*ri*o \xmark & in*cen*di*á*ri*o \cmark \\
-itapuã & i*ta*pu-ã \xmark & i*ta*pu*ã \cmark \\
-parcimônia & par*ci-mô*ni*a \xmark & par*ci*mô*ni*a \cmark \\
-psicótico & p.si*có*ti*co \xmark & psi*có*ti*co \cmark \\
-redemoinho & re*de*mo-i*nho \xmark & re*de*mo*i*nho \cmark \\
-redistribuir & re*dis*tri*bu-ir \xmark & re*dis*tri*bu*ir \cmark \\
-reintrodução & re-in*tro*du*ção \xmark & re*in*tro*du*ção \cmark \\
-triunfalismo & tri-un*fa*lis*mo \xmark & tri*un*fa*lis*mo \cmark \\
-zodíaco & zo*dí-a*co \xmark & zo*dí*a*co \cmark \\
+ambidestria & am*bi*des*tri*a \cmark & am*bi*des*tri-a \xmark \\
+ambrosia & am*bro*si*a \cmark & am*bro*si-a \xmark \\
+ambulância & am*bu*lân*ci.a \xmark & am*bu*lân*cia \cmark \\
+ambulatório & am*bu*la*tó*ri.o \xmark & am*bu*la*tó*rio \cmark \\
+amebíase & a*me*bí-a*se \xmark & a*me*bí*a*se \cmark \\
+ameia & a*mei*a \cmark & a*mei-a \xmark \\
+amélia & a*mé*li.a \xmark & a*mé*lia \cmark \\
+amêndoa & a*mên*do.a \xmark & a*mên*doa \cmark \\
+amendoim & a*men*do-im \xmark & a*men*do*im \cmark \\
+amenorreia & a*me*nor*rei*a \cmark & a*me*nor*rei-a \xmark \\
+amerício & a*me*rí*ci.o \xmark & a*me*rí*cio \cmark \\
+ameríndio & a*me*rín*di.o \xmark & a*me*rín*dio \cmark \\
 aminoácido & a*mi*no-á*ci*do \xmark & a*mi*no*á*ci*do \cmark \\
-arruinar & ar*ru-i*nar \xmark & ar*ru*i*nar \cmark \\
-ateísmo & a*te-ís*mo \xmark & a*te*ís*mo \cmark \\
-caim & ca-im \xmark & ca-im \xmark \\
-exequível & e*xe-quí*vel \xmark & e*xe*quí*vel \cmark \\
-inconsequência & in*con*se-quên*ci*a \xmark & in*con*se*quên*ci*a \cmark \\
-laquê & la-quê \xmark & la*quê \cmark \\
-megalomaníaco & me*ga*lo*ma*ní-a*co \xmark & me*ga*lo*ma*ní*a*co \cmark \\
-pantaleão & pan*ta*le-ão \xmark & pan*ta*le*ão \cmark \\
-poluidor & po*lu-i*dor \xmark & po*lu*i*dor \cmark \\
-preâmbulo & pre-âm*bu*lo \xmark & pre*âm*bu*lo \cmark \\
-arcaísmo & ar*ca-ís*mo \xmark & ar*ca*ís*mo \cmark \\
-auréola & au*ré-o*la \xmark & au*ré*o*la \cmark \\
-autodestruição & au*to*des*tru-i*ção \xmark & au*to*des*tru*i*ção \cmark \\
-casuística & ca*su-ís*ti*ca \xmark & ca*su*ís*ti*ca \cmark \\
-desunião & de*su*ni-ão \xmark & de*su*ni*ão \cmark \\
-elogiável & e*lo*gi-á*vel \xmark & e*lo*gi*á*vel \cmark \\
-gnomo & g.no*mo \xmark & gno*mo \cmark \\
-neurocirurgião & neu*ro*ci*rur*gi-ão \xmark & neu*ro*ci*rur*gi*ão \cmark \\
-pediátrico & pe*di-á*tri*co \xmark & pe*di*á*tri*co \cmark \\
-permeável & per*me-á*vel \xmark & per*me*á*vel \cmark \\
-piraí & pi*ra-í \xmark & pi*ra*í \cmark \\
-psicodélico & p.si*co*dé*li*co \xmark & psi*co*dé*li*co \cmark \\
-psicotécnico & p.si*co*téc*ni*co \xmark & psi*co*téc*ni*co \cmark \\
-saíra & sa-í*ra \xmark & sa*í*ra \cmark \\
-sobressair & so*bres*sa-ir \xmark & so*bres*sa*ir \cmark \\
-subliminar & su.b-li*mi*nar \xmark & sub*li*mi*nar \cmark \\
-ajuizado & a*ju-i*za*do \xmark & a*ju*i*za*do \cmark \\
-antipoluição & an*ti*po*lu-i*ção \xmark & an*ti*po*lu*i*ção \cmark \\
-arquétipo & ar-qué*ti*po \xmark & ar*qué*ti*po \cmark \\
-dadaísmo & da*da-ís*mo \xmark & da*da*ís*mo \cmark \\
-descontrair & des*con*tra-ir \xmark & des*con*tra*ir \cmark \\
-gasômetro & ga-sô*me*tro \xmark & ga*sô*me*tro \cmark \\
-hidroviário & hi*dro*vi-á*ri*o \xmark & hi*dro*vi*á*ri*o \cmark \\
-inegociável & i*ne*go*ci-á*vel \xmark & i*ne*go*ci*á*vel \cmark \\
-maiúscula & mai-ús*cu*la \xmark & mai*ús*cu*la \cmark \\
-miúdas & mi-ú*das \xmark & mi*ú*das \cmark \\
-perequê & pe*re-quê \xmark & pe*re*quê \cmark \\
-recôncavo & re-côn*ca*vo \xmark & re*côn*ca*vo \cmark \\
-saquê & sa-quê \xmark & sa*quê \cmark \\
-ancião & an*ci-ão \xmark & an*ci*ão \cmark \\
-bafômetro & ba-fô*me*tro \xmark & ba*fô*me*tro \cmark \\
-bongô & bon-gô \xmark & bon*gô \cmark \\
-ciberespaço & ci*be.r-es*pa*ço \xmark & ci*be.r-es*pa*ço \xmark \\
-condômino & con-dô*mi*no \xmark & con*dô*mi*no \cmark \\
-dadaísta & da*da-ís*ta \xmark & da*da*ís*ta \cmark \\
-freático & fre-á*ti*co \xmark & fre*á*ti*co \cmark \\
-hipocondríaco & hi*po*con*drí-a*co \xmark & hi*po*con*drí*a*co \cmark \\
-indaiá & in*dai-á \xmark & in*dai*á \cmark \\
-jacuí & ja*cu-í \xmark & ja*cu*í \cmark \\
-maleável & ma*le-á*vel \xmark & ma*le*á*vel \cmark \\
-ministeriável & mi*nis*te*ri-á*vel \xmark & mi*nis*te*ri*á*vel \cmark \\
-obituário & o*bi*tu-á*ri*o \xmark & o*bi*tu*á*ri*o \cmark \\
-picuinha & pi*cu-i*nha \xmark & pi*cu-i*nha \xmark \\
-platô & pla-tô \xmark & pla*tô \cmark \\
-possuidor & pos*su-i*dor \xmark & pos*su*i*dor \cmark \\
-psicodelismo & p.si*co*de*lis*mo \xmark & psi*co*de*lis*mo \cmark \\
-reinserção & re-in*ser*ção \xmark & re*in*ser*ção \cmark \\
-suingue & su-in*gue \xmark & su-in*gue \xmark \\
-triunfalista & tri-un*fa*lis*ta \xmark & tri*un*fa*lis*ta \cmark \\
-varíola & va*rí-o*la \xmark & va*rí*o*la \cmark \\
-apoteótico & a*po*te-ó*ti*co \xmark & a*po*te*ó*ti*co \cmark \\
-bainha & ba-i*nha \xmark & ba*i*nha \cmark \\
-bibliófilo & bi*bli-ó*fi*lo \xmark & bi*bli*ó*fi*lo \cmark \\
-caimento & ca-i*men*to \xmark & ca-i*men*to \xmark \\
-cambuí & cam*bu-í \xmark & cam*bu*í \cmark \\
-cauim & cau-im \xmark & cau-im \xmark \\
-darwinismo & dar-wi*nis*mo \xmark & dar-wi*nis*mo \xmark \\
-eclesiástico & e*cle*si-ás*ti*co \xmark & e*cle*si*ás*ti*co \cmark \\
-estuário & es*tu-á*ri*o \xmark & es*tu*á*ri*o \cmark \\
-gigolô & gi*go-lô \xmark & gi*go*lô \cmark \\
-imbuído & im*bu-í*do \xmark & im*bu*í*do \cmark \\
-bastião & bas*ti-ão \xmark & bas*ti*ão \cmark \\
-caíque & ca-í*que \xmark & ca*í*que \cmark \\
-coincidente & co-in*ci*den*te \xmark & co*in*ci*den*te \cmark \\
-flúor & flú-or \xmark & flú-or \xmark \\
-incongruência & in*con*gru-ên*ci*a \xmark & in*con*gru*ên*ci*a \cmark \\
-indissociável & in*dis*so*ci-á*vel \xmark & in*dis*so*ci*á*vel \cmark \\
-invariável & in*va*ri-á*vel \xmark & in*va*ri*á*vel \cmark \\
-mostruário & mos*tru-á*ri*o \xmark & mos*tru*á*ri*o \cmark \\
-néon & né-on \xmark & né*on \cmark \\
-oboé & o*bo-é \xmark & o*bo*é \cmark \\
-oceânico & o*ce-â*ni*co \xmark & o*ce*â*ni*co \cmark \\
-panteísmo & pan*te-ís*mo \xmark & pan*te*ís*mo \cmark \\
-platônico & pla-tô*ni*co \xmark & pla*tô*ni*co \cmark \\
-pneumologia & p.neu*mo*lo*gi*a \xmark & pneu*mo*lo*gi*a \cmark \\
-proibitivo & pro-i*bi*ti*vo \xmark & pro*i*bi*ti*vo \cmark \\
-raquítico & ra-quí*ti*co \xmark & ra*quí*ti*co \cmark \\
-reinterpretação & re-in*ter*pre*ta*ção \xmark & re*in*ter*pre*ta*ção \cmark \\
-subtraído & sub*tra-í*do \xmark & sub*tra*í*do \cmark \\
-suinocultura & su-i*no*cul*tu*ra \xmark & su*i*no*cul*tu*ra \cmark \\
-sumô & su-mô \xmark & su*mô \cmark \\
-tainha & ta-i*nha \xmark & ta*i*nha \cmark \\
-acordeão & a*cor*de-ão \xmark & a*cor*de*ão \cmark \\
-aético & a-é*ti*co \xmark & a*é*ti*co \cmark \\
-baiuca & bai-u*ca \xmark & bai-u*ca \xmark \\
-centurião & cen*tu*ri-ão \xmark & cen*tu*ri*ão \cmark \\
-comediógrafo & co*me*di-ó*gra*fo \xmark & co*me*di*ó*gra*fo \cmark \\
-conduíte & con*du-í*te \xmark & con*du*í*te \cmark \\
-coroinha & co*ro-i*nha \xmark & co*ro*i*nha \cmark \\
-ergonômico & er*go-nô*mi*co \xmark & er*go*nô*mi*co \cmark \\
-gaélico & ga-é*li*co \xmark & ga*é*li*co \cmark \\
-grandiloquência & gran*di*lo-quên*ci*a \xmark & gran*di*lo*quên*ci*a \cmark \\
-impatriótico & im*pa*tri-ó*ti*co \xmark & im*pa*tri*ó*ti*co \cmark \\
-megalômano & me*ga-lô*ma*no \xmark & me*ga*lô*ma*no \cmark \\
-miríade & mi*rí-a*de \xmark & mi*rí*a*de \cmark \\
-neófito & ne-ó*fi*to \xmark & ne*ó*fi*to \cmark \\
-nipônico & ni-pô*ni*co \xmark & ni*pô*ni*co \cmark \\
-obstruído & obs*tru-í*do \xmark & obs*tru*í*do \cmark \\
-pecuniário & pe*cu*ni-á*ri*o \xmark & pe*cu*ni*á*ri*o \cmark \\
-psicopatologia & p.si*co*pa*to*lo*gi*a \xmark & psi*co*pa*to*lo*gi*a \cmark \\
-reindexar & re-in*de*xar \xmark & re-in*de*xar \xmark \\
-reinstalar & re-ins*ta*lar \xmark & re*ins*ta*lar \cmark \\
-reintroduzir & re-in*tro*du*zir \xmark & re*in*tro*du*zir \cmark \\
-teleinformática & te*le-in*for*má*ti*ca \xmark & te*le*in*for*má*ti*ca \cmark \\
-timbaúba & tim*ba-ú*ba \xmark & tim*ba*ú*ba \cmark \\
-agônico & a-gô*ni*co \xmark & a*gô*ni*co \cmark \\
-anatômico & a*na-tô*mi*co \xmark & a*na*tô*mi*co \cmark \\
-anômalo & a-nô*ma*lo \xmark & a*nô*ma*lo \cmark \\
-ataúde & a*ta-ú*de \xmark & a*ta*ú*de \cmark \\
-auê & au-ê \xmark & au*ê \cmark \\
-bestiário & bes*ti-á*ri*o \xmark & bes*ti*á*ri*o \cmark \\
-boá & bo-á \xmark & bo*á \cmark \\
-copião & co*pi-ão \xmark & co*pi*ão \cmark \\
-ensaística & en*sa-ís*ti*ca \xmark & en*sa*ís*ti*ca \cmark \\
-fonoaudiólogo & fo*no*au*di-ó*lo*go \xmark & fo*no*au*di*ó*lo*go \cmark \\
-imiscuir & i*mis*cu-ir \xmark & i*mis*cu-ir \xmark \\
-jupiá & ju*pi-á \xmark & ju*pi*á \cmark \\
-monoteísmo & mo*no*te-ís*mo \xmark & mo*no*te*ís*mo \cmark \\
-nagô & na-gô \xmark & na*gô \cmark \\
-psicofarmacologia & p.si*co*far*ma*co*lo*gi*a \xmark & psi*co*far*ma*co*lo*gi*a \cmark \\
-psicologismo & p.si*co*lo*gis*mo \xmark & psi*co*lo*gis*mo \cmark \\
-ruindade & ru-in*da*de \xmark & ru-in*da*de \xmark \\
-sanduicheria & san*du-i*che*ri*a \xmark & san*du*i*che*ri*a \cmark \\
-sociável & so*ci-á*vel \xmark & so*ci*á*vel \cmark \\
-sublevação & su.b-le*va*ção \xmark & sub*le*va*ção \cmark \\
-abstrair & abs*tra-ir \xmark & abs*tra*ir \cmark \\
-alaúde & a*la-ú*de \xmark & a*la*ú*de \cmark \\
-almôndega & al-môn*de*ga \xmark & al*môn*de*ga \cmark \\
-antiaéreo & an*ti*a-é*re*o \xmark & an*ti*a*é*re*o \cmark \\
-atrabiliário & a*tra*bi*li-á*ri*o \xmark & a*tra*bi*li*á*ri*o \cmark \\
-bangalô & ban*ga-lô \xmark & ban*ga*lô \cmark \\
-bôer & bô-er \xmark & bô-er \xmark \\
-breviário & bre*vi-á*ri*o \xmark & bre*vi*á*ri*o \cmark \\
-canônico & ca-nô*ni*co \xmark & ca*nô*ni*co \cmark \\
-carnaúba & car*na-ú*ba \xmark & car*na*ú*ba \cmark \\
-doído & do-í*do \xmark & do*í*do \cmark \\
-ensaísmo & en*sa-ís*mo \xmark & en*sa*ís*mo \cmark \\
-esfiha & es*fi-ha \xmark & es*fi-ha \xmark \\
-graúna & gra-ú*na \xmark & gra*ú*na \cmark \\
-hemodiálise & he*mo*di-á*li*se \xmark & he*mo*di*á*li*se \cmark \\
-hinduísmo & hin*du-ís*mo \xmark & hin*du*ís*mo \cmark \\
-influído & in*flu-í*do \xmark & in*flu-í*do \xmark \\
-intuir & in*tu-ir \xmark & in*tu*ir \cmark \\
-latifundiário & la*ti*fun*di-á*ri*o \xmark & la*ti*fun*di*á*ri*o \cmark \\
-mimeógrafo & mi*me-ó*gra*fo \xmark & mi*me*ó*gra*fo \cmark \\
-pajeú & pa*je-ú \xmark & pa*je*ú \cmark \\
-prosaísmo & pro*sa-ís*mo \xmark & pro*sa*ís*mo \cmark \\
-psicodrama & p.si*co*dra*ma \xmark & psi*co*dra*ma \cmark \\
-psicopedagogia & p.si*co*pe*da*go*gi*a \xmark & psi*co*pe*da*go*gi*a \cmark \\
-quinquênio & quin-quê*ni*o \xmark & quin*quê*ni*o \cmark \\
-radiofrequência & ra*di*o*fre-quên*ci*a \xmark & ra*di*o*fre*quên*ci*a \cmark \\
-reinstituir & re-ins*ti*tu-ir \xmark & re*ins*ti*tu*ir \cmark \\
-supercampeão & su*per*cam*pe-ão \xmark & su*per*cam*pe*ão \cmark \\
-supersônico & su*per-sô*ni*co \xmark & su*per*sô*ni*co \cmark \\
-tragicômico & tra*gi-cô*mi*co \xmark & tra*gi*cô*mi*co \cmark \\
-tríade & trí-a*de \xmark & trí*a*de \cmark \\
-vacuidade & va*cu-i*da*de \xmark & va*cu*i*da*de \cmark \\
-agogô & a*go-gô \xmark & a*go*gô \cmark \\
-altruísta & al*tru-ís*ta \xmark & al*tru*ís*ta \cmark \\
-antiácido & an*ti-á*ci*do \xmark & an*ti*á*ci*do \cmark \\
-autobiógrafo & au*to*bi-ó*gra*fo \xmark & au*to*bi*ó*gra*fo \cmark \\
-beduíno & be*du-í*no \xmark & be*du*í*no \cmark \\
-bordô & bor-dô \xmark & bor*dô \cmark \\
-casuístico & ca*su-ís*ti*co \xmark & ca*su*ís*ti*co \cmark \\
-czarina & c.za*ri*na \xmark & cza*ri*na \cmark \\
-demoníaco & de*mo*ní-a*co \xmark & de*mo*ní*a*co \cmark \\
-desconstruir & des*cons*tru-ir \xmark & des*cons*tru*ir \cmark \\
-ergômetro & er-gô*me*tro \xmark & er*gô*me*tro \cmark \\
-evoé & e*vo-é \xmark & e*vo*é \cmark \\
-graúdo & gra-ú*do \xmark & gra*ú*do \cmark \\
-iídiche & i-í*di*che \xmark & i*í*di*che \cmark \\
-impronunciável & im*pro*nun*ci-á*vel \xmark & im*pro*nun*ci*á*vel \cmark \\
-influenciável & in*flu*en*ci-á*vel \xmark & in*flu*en*ci*á*vel \cmark \\
-irrefreável & ir*re*fre-á*vel \xmark & ir*re*fre*á*vel \cmark \\
-irretorquível & ir*re*tor-quí*vel \xmark & ir*re*tor*quí*vel \cmark \\
-jataí & ja*ta-í \xmark & ja*ta*í \cmark \\
-juquiá & ju*qui-á \xmark & ju*qui*á \cmark \\
-painho & pa-i*nho \xmark & pa*i*nho \cmark \\
-pindaíba & pin*da-í*ba \xmark & pin*da*í*ba \cmark \\
-pneumologista & p.neu*mo*lo*gis*ta \xmark & pneu*mo*lo*gis*ta \cmark \\
-porciúncula & por*ci-ún*cu*la \xmark & por*ci*ún*cu*la \cmark \\
-prolegômenos & pro*le-gô*me*nos \xmark & pro*le*gô*me*nos \cmark \\
-psiquismo & p.si*quis*mo \xmark & psi*quis*mo \cmark \\
-quiproquó & qui*pro-quó \xmark & qui*pro*quó \cmark \\
-refluir & re*flu-ir \xmark & re*flu*ir \cmark \\
-reimplantar & re-im*plan*tar \xmark & re*im*plan*tar \cmark \\
-reurbanizar & re-ur*ba*ni*zar \xmark & re-ur*ba*ni*zar \xmark \\
-reutilizar & re-u*ti*li*zar \xmark & re-u*ti*li*zar \xmark \\
-sainte & sa-in*te \xmark & sa-in*te \xmark \\
-tsunami & t.su*na*mi \xmark & tsu*na*mi \cmark \\
-usucapião & u*su*ca*pi-ão \xmark & u*su*ca*pi*ão \cmark \\
-zebuíno & ze*bu-í*no \xmark & ze*bu*í*no \cmark \\
-aeroportuário & a*e*ro*por*tu-á*ri*o \xmark & a*e*ro*por*tu*á*ri*o \cmark \\
-agroquímica & a*gro-quí*mi*ca \xmark & a*gro*quí*mi*ca \cmark \\
-ajuizar & a*ju-i*zar \xmark & a*ju*i*zar \cmark \\
-baraúna & ba*ra-ú*na \xmark & ba*ra*ú*na \cmark \\
-casuísta & ca*su-ís*ta \xmark & ca*su*ís*ta \cmark \\
-catatônico & ca*ta-tô*ni*co \xmark & ca*ta*tô*ni*co \cmark \\
-conteudista & con*te-u*dis*ta \xmark & con*te-u*dis*ta \xmark \\
-continuísta & con*ti*nu-ís*ta \xmark & con*ti*nu*ís*ta \cmark \\
-czarista & c.za*ris*ta \xmark & cza*ris*ta \cmark \\
-decair & de*ca-ir \xmark & de*ca*ir \cmark \\
-deísta & de-ís*ta \xmark & de*ís*ta \cmark \\
-diácono & di-á*co*no \xmark & di*á*co*no \cmark \\
-elegíaco & e*le*gí-a*co \xmark & e*le*gí*a*co \cmark \\
-faraônico & fa*ra-ô*ni*co \xmark & fa*ra*ô*ni*co \cmark \\
-feérico & fe-é*ri*co \xmark & fe*é*ri*co \cmark \\
-hidroavião & hi*dro*a*vi-ão \xmark & hi*dro*a*vi*ão \cmark \\
-hodômetro & ho-dô*me*tro \xmark & ho*dô*me*tro \cmark \\
-inconciliável & in*con*ci*li-á*vel \xmark & in*con*ci*li*á*vel \cmark \\
-ioiô & i.o-i.ô \xmark & i.o-i.ô \xmark \\
-macrobiótica & ma*cro*bi-ó*ti*ca \xmark & ma*cro*bi*ó*ti*ca \cmark \\
-marruá & mar*ru-á \xmark & mar*ru*á \cmark \\
-meteórico & me*te-ó*ri*co \xmark & me*te*ó*ri*co \cmark \\
-panteísta & pan*te-ís*ta \xmark & pan*te*ís*ta \cmark \\
-papaína & pa*pa-í*na \xmark & pa*pa*í*na \cmark \\
-patuá & pa*tu-á \xmark & pa*tu*á \cmark \\
-perdoável & per*do-á*vel \xmark & per*do*á*vel \cmark \\
-prostituído & pros*ti*tu-í*do \xmark & pros*ti*tu*í*do \cmark \\
-pulôver & pu-lô*ver \xmark & pu*lô*ver \cmark \\
-ravióli & ra*vi-ó*li \xmark & ra*vi*ó*li \cmark \\
-reincorporação & re-in*cor*po*ra*ção \xmark & re*in*cor*po*ra*ção \cmark \\
-reingresso & re-in*gres*so \xmark & re*in*gres*so \cmark \\
-reinquirir & re-in*qui*rir \xmark & re-in*qui*rir \xmark \\
-reinstalação & re-ins*ta*la*ção \xmark & re*ins*ta*la*ção \cmark \\
-reinterpretar & re-in*ter*pre*tar \xmark & re*in*ter*pre*tar \cmark \\
-saião & sai-ão \xmark & sai*ão \cmark \\
-samaúma & sa*ma-ú*ma \xmark & sa*ma*ú*ma \cmark \\
-sublocação & su.b-lo*ca*ção \xmark & sub*lo*ca*ção \cmark \\
-turboélice & tur*bo-é*li*ce \xmark & tur*bo*é*li*ce \cmark \\
-ventoinha & ven*to-i*nha \xmark & ven*to*i*nha \cmark \\
-voyeurista & voy-eu*ris*ta \xmark & voy-eu*ris*ta \xmark \\
-alagoinha & a*la*go-i*nha \xmark & a*la*go*i*nha \cmark \\
-aluvião & a*lu*vi-ão \xmark & a*lu*vi*ão \cmark \\
 amiúde & a*mi-ú*de \xmark & a*mi*ú*de \cmark \\
 amoníaco & a*mo*ní-a*co \xmark & a*mo*ní*a*co \cmark \\
+amontoa & a*mon*to*a \cmark & a*mon*to-a \xmark \\
+ampelografia & am*pe*lo*gra*fi*a \cmark & am*pe*lo*gra*fi-a \xmark \\
+anaeróbio & a*na*e*ró*bi.o \xmark & a*na*e*ró*bio \cmark \\
+anafilaxia & a*na*fi*la*xi*a \cmark & a*na*fi*la*xi-a \xmark \\
+anafrodisíaco & a*na*fro*di*sí-a*co \xmark & a*na*fro*di*sí*a*co \cmark \\
+analgesia & a*nal*ge*si*a \cmark & a*nal*ge*si-a \xmark \\
+analogia & a*na*lo*gi*a \cmark & a*na*lo*gi-a \xmark \\
+anarquia & a*nar*qui*a \cmark & a*nar*qui-a \xmark \\
+anatomia & a*na*to*mi*a \cmark & a*na*to*mi-a \xmark \\
+anatômico & a*na-tô*mi*co \xmark & a*na*tô*mi*co \cmark \\
+ancião & an*ci-ão \xmark & an*ci*ão \cmark \\
+ancilostomíase & an*ci*los*to*mí-a*se \xmark & an*ci*los*to*mí*a*se \cmark \\
+androfobia & an*dro*fo*bi*a \cmark & an*dro*fo*bi-a \xmark \\
+androginia & an*dro*gi*ni*a \cmark & an*dro*gi*ni-a \xmark \\
+andrologia & an*dro*lo*gi*a \cmark & an*dro*lo*gi-a \xmark \\
+anedonia & a*ne*do*ni*a \cmark & a*ne*do*ni-a \xmark \\
+anelídeo & a*ne*lí*de.o \xmark & a*ne*lí*deo \cmark \\
+anemia & a*ne*mi*a \cmark & a*ne*mi-a \xmark \\
+anemofilia & a*ne*mo*fi*li*a \cmark & a*ne*mo*fi*li-a \xmark \\
+anemômetro & a*ne-mô*me*tro \xmark & a*ne*mô*me*tro \cmark \\
+anestesia & a*nes*te*si*a \cmark & a*nes*te*si-a \xmark \\
+anestesiologia & a*nes*te*si*o*lo*gi*a \cmark & a*nes*te*si*o*lo*gi-a \xmark \\
+aneuploidia & a*neu*ploi*di*a \cmark & a*neu*ploi*di-a \xmark \\
+anfíbio & an*fí*bi.o \xmark & an*fí*bio \cmark \\
+anfibologia & an*fi*bo*lo*gi*a \cmark & an*fi*bo*lo*gi-a \xmark \\
+anfitrião & an*fi*tri-ão \xmark & an*fi*tri*ão \cmark \\
+angiologia & an*gi*o*lo*gi*a \cmark & an*gi*o*lo*gi-a \xmark \\
+angioplastia & an*gi*o*plas*ti*a \cmark & an*gi*o*plas*ti-a \xmark \\
+angústia & an*gús*ti.a \xmark & an*gús*tia \cmark \\
+anisogamia & a*ni*so*ga*mi*a \cmark & a*ni*so*ga*mi-a \xmark \\
+anisotropia & a*ni*so*tro*pi*a \cmark & a*ni*so*tro*pi-a \xmark \\
+anistia & a*nis*ti*a \cmark & a*nis*ti-a \xmark \\
+aniversário & a*ni*ver*sá*ri.o \xmark & a*ni*ver*sá*rio \cmark \\
+anodinia & a*no*di*ni*a \cmark & a*no*di*ni-a \xmark \\
+anomalia & a*no*ma*li*a \cmark & a*no*ma*li-a \xmark \\
+anomia & a*no*mi*a \cmark & a*no*mi-a \xmark \\
+anônimo & a-nô*ni*mo \xmark & a*nô*ni*mo \cmark \\
+anorexia & a*no*re*xi*a \cmark & a*no*re*xi-a \xmark \\
+anosmia & a*nos*mi*a \cmark & a*nos*mi-a \xmark \\
+anoxia & a*no*xi*a \cmark & a*no*xi-a \xmark \\
+anseio & an*sei*o \cmark & an*sei-o \xmark \\
 antagônico & an*ta-gô*ni*co \xmark & an*ta*gô*ni*co \cmark \\
+antecedência & an*te*ce*dên*ci.a \xmark & an*te*ce*dên*cia \cmark \\
+antiácido & an*ti-á*ci*do \xmark & an*ti*á*ci*do \cmark \\
+antialcoólico & an*ti*al*co-ó*li*co \xmark & an*ti*al*co*ó*li*co \cmark \\
+antibiótico & an*ti*bi-ó*ti*co \xmark & an*ti*bi*ó*ti*co \cmark \\
+antinomia & an*ti*no*mi*a \cmark & an*ti*no*mi-a \xmark \\
+antipatia & an*ti*pa*ti*a \cmark & an*ti*pa*ti-a \xmark \\
+antipatriótico & an*ti*pa*tri-ó*ti*co \xmark & an*ti*pa*tri*ó*ti*co \cmark \\
+antiquário & an*ti-quá*ri.o \xmark & an*ti*quá*rio \cmark \\
 antiquíssimo & an*ti-quís*si*mo \xmark & an*ti*quís*si*mo \cmark \\
+antissepsia & an*tis*sep*si*a \cmark & an*tis*sep*si-a \xmark \\
+antologia & an*to*lo*gi*a \cmark & an*to*lo*gi-a \xmark \\
+antônimo & an-tô*ni*mo \xmark & an*tô*ni*mo \cmark \\
+antonomásia & an*to*no*má*si.a \xmark & an*to*no*má*sia \cmark \\
+antropofagia & an*tro*po*fa*gi*a \cmark & an*tro*po*fa*gi-a \xmark \\
+antropologia & an*tro*po*lo*gi*a \cmark & an*tro*po*lo*gi-a \xmark \\
+antropometria & an*tro*po*me*tri*a \cmark & an*tro*po*me*tri-a \xmark \\
+antroponímia & an*tro*po*ní*mi.a \xmark & an*tro*po*ní*mia \cmark \\
+antropônimo & an*tro-pô*ni*mo \xmark & an*tro*pô*ni*mo \cmark \\
+antroposofia & an*tro*po*so*fi*a \cmark & an*tro*po*so*fi-a \xmark \\
+anuário & a*nu-á*ri.o \xmark & a*nu*á*rio \cmark \\
+anuência & a*nu-ên*ci.a \xmark & a*nu*ên*cia \cmark \\
+anuidade & a*nu-i*da*de \xmark & a*nu*i*da*de \cmark \\
+anuir & a*nu-ir \xmark & a*nu*ir \cmark \\
+anúncio & a*nún*ci.o \xmark & a*nún*cio \cmark \\
+aórtico & a-ór*ti*co \xmark & a*ór*ti*co \cmark \\
+apanágio & a*pa*ná*gi.o \xmark & a*pa*ná*gio \cmark \\
+aparência & a*pa*rên*ci.a \xmark & a*pa*rên*cia \cmark \\
+apatia & a*pa*ti*a \cmark & a*pa*ti-a \xmark \\
+apendicectomia & a*pen*di*cec*to*mi*a \cmark & a*pen*di*cec*to*mi-a \xmark \\
+apetência & a*pe*tên*ci.a \xmark & a*pe*tên*cia \cmark \\
+aplasia & a*pla*si*a \cmark & a*pla*si-a \xmark \\
+apneia & ap*nei*a \cmark & ap*nei-a \xmark \\
+apofonia & a*po*fo*ni*a \cmark & a*po*fo*ni-a \xmark \\
+apoio & a*poi*o \cmark & a*poi-o \xmark \\
+apologia & a*po*lo*gi*a \cmark & a*po*lo*gi-a \xmark \\
+apoplexia & a*po*ple*xi*a \cmark & a*po*ple*xi-a \xmark \\
+aporia & a*po*ri*a \cmark & a*po*ri-a \xmark \\
+aposentadoria & a*po*sen*ta*do*ri*a \cmark & a*po*sen*ta*do*ri-a \xmark \\
+apostasia & a*pos*ta*si*a \cmark & a*pos*ta*si-a \xmark \\
+apraxia & a*pra*xi*a \cmark & a*pra*xi-a \xmark \\
+apreciável & a*pre*ci-á*vel \xmark & a*pre*ci*á*vel \cmark \\
+apuí & a*pu-í \xmark & a*pu*í \cmark \\
+aquário & a-quá*ri.o \xmark & a*quá*rio \cmark \\
+aquático & a-quá*ti*co \xmark & a*quá*ti*co \cmark \\
+aquém & a-quém \xmark & a*quém \cmark \\
+aquícola & a-quí*co*la \xmark & a*quí*co*la \cmark \\
+aquiescência & a*qui*es*cên*ci.a \xmark & a*qui*es*cên*cia \cmark \\
+aquífero & a-quí*fe*ro \xmark & a*quí*fe*ro \cmark \\
+aquileia & a*qui*lei*a \cmark & a*qui*lei-a \xmark \\
+arábias & a*rá*bi.as \xmark & a*rá*bi.as \xmark \\
+aracnofobia & a*rac*no*fo*bi*a \cmark & a*rac*no*fo*bi-a \xmark \\
+aracnologia & a*rac*no*lo*gi*a \cmark & a*rac*no*lo*gi-a \xmark \\
+araucária & a*rau*cá*ri.a \xmark & a*rau*cá*ria \cmark \\
+arbitrário & ar*bi*trá*ri.o \xmark & ar*bi*trá*rio \cmark \\
+arbítrio & ar*bí*tri.o \xmark & ar*bí*trio \cmark \\
+arbóreo & ar*bó*re.o \xmark & ar*bó*reo \cmark \\
+arcaísmo & ar*ca-ís*mo \xmark & ar*ca*ís*mo \cmark \\
+ardência & ar*dên*ci.a \xmark & ar*dên*cia \cmark \\
+ardósia & ar*dó*si.a \xmark & ar*dó*sia \cmark \\
+árduo & ár*du.o \xmark & ár*duo \cmark \\
+área & á*re.a \xmark & á*rea \cmark \\
+areia & a*rei*a \cmark & a*rei-a \xmark \\
+argênteo & ar*gên*te*o \cmark & ar*gên*te-o \xmark \\
+argúcia & ar*gú*ci.a \xmark & ar*gú*cia \cmark \\
+aríete & a*rí-e*te \xmark & a*rí*e*te \cmark \\
+aristocracia & a*ris*to*cra*ci*a \cmark & a*ris*to*cra*ci-a \xmark \\
+armário & ar*má*ri.o \xmark & ar*má*rio \cmark \\
+armistício & ar*mis*tí*ci.o \xmark & ar*mis*tí*cio \cmark \\
+aromaterapia & a*ro*ma*te*ra*pi*a \cmark & a*ro*ma*te*ra*pi-a \xmark \\
+arqueologia & ar*que*o*lo*gi*a \cmark & ar*que*o*lo*gi-a \xmark \\
+arqueólogo & ar*que-ó*lo*go \xmark & ar*que*ó*lo*go \cmark \\
+arquétipo & ar-qué*ti*po \xmark & ar*qué*ti*po \cmark \\
+arquidiácono & ar*qui*di-á*co*no \xmark & ar*qui*di*á*co*no \cmark \\
+arquitetônica & ar*qui*te-tô*ni*ca \xmark & ar*qui*te*tô*ni*ca \cmark \\
+arquitetônico & ar*qui*te-tô*ni*co \xmark & ar*qui*te*tô*ni*co \cmark \\
+arrais & ar*ra-is \xmark & ar*ra-is \xmark \\
+arreio & ar*rei*o \cmark & ar*rei-o \xmark \\
+arrelia & ar*re*li*a \cmark & ar*re*li-a \xmark \\
+arrepio & ar*re*pi*o \cmark & ar*re*pi-o \xmark \\
+arritmia & ar*rit*mi*a \cmark & ar*rit*mi-a \xmark \\
+arroio & ar*roi*o \cmark & ar*roi-o \xmark \\
+arruinar & ar*ru-i*nar \xmark & ar*ru*i*nar \cmark \\
+artemísia & ar*te*mí*si.a \xmark & ar*te*mí*sia \cmark \\
+articulatório & ar*ti*cu*la*tó*ri*o \cmark & ar*ti*cu*la*tó*ri-o \xmark \\
+artifício & ar*ti*fí*ci.o \xmark & ar*ti*fí*cio \cmark \\
+artilharia & ar*ti*lha*ri*a \cmark & ar*ti*lha*ri-a \xmark \\
+artralgia & ar*tral*gi*a \cmark & ar*tral*gi-a \xmark \\
+artroscopia & ar*tros*co*pi*a \cmark & ar*tros*co*pi-a \xmark \\
+ascaridíase & as*ca*ri*dí-a*se \xmark & as*ca*ri*dí*a*se \cmark \\
+ascendência & as*cen*dên*ci.a \xmark & as*cen*dên*cia \cmark \\
+asfixia & as*fi*xi*a \cmark & as*fi*xi-a \xmark \\
+asiática & a*si-á*ti*ca \xmark & a*si*á*ti*ca \cmark \\
+asiático & a*si-á*ti*co \xmark & a*si*á*ti*co \cmark \\
+assassínio & as*sas*sí*ni.o \xmark & as*sas*sí*nio \cmark \\
+assédio & as*sé*di.o \xmark & as*sé*dio \cmark \\
+assepsia & as*sep*si*a \cmark & as*sep*si-a \xmark \\
+assessoria & as*ses*so*ri*a \cmark & as*ses*so*ri-a \xmark \\
+assiduidade & as*si*du-i*da*de \xmark & as*si*du*i*da*de \cmark \\
+assíduo & as*sí*du.o \xmark & as*sí*duo \cmark \\
+assimetria & as*si*me*tri*a \cmark & as*si*me*tri-a \xmark \\
+assistência & as*sis*tên*ci.a \xmark & as*sis*tên*cia \cmark \\
+associável & as*so*ci-á*vel \xmark & as*so*ci*á*vel \cmark \\
+assonância & as*so*nân*ci.a \xmark & as*so*nân*cia \cmark \\
+astenia & as*te*ni*a \cmark & as*te*ni-a \xmark \\
+astrolábio & as*tro*lá*bi.o \xmark & as*tro*lá*bio \cmark \\
+astrologia & as*tro*lo*gi*a \cmark & as*tro*lo*gi-a \xmark \\
+astronomia & as*tro*no*mi*a \cmark & as*tro*no*mi-a \xmark \\
+astronômico & as*tro-nô*mi*co \xmark & as*tro*nô*mi*co \cmark \\
+astúcia & as*tú*ci.a \xmark & as*tú*cia \cmark \\
+atalaia & a*ta*lai*a \cmark & a*ta*lai-a \xmark \\
+ataraxia & a*ta*ra*xi*a \cmark & a*ta*ra*xi-a \xmark \\
+ataúde & a*ta-ú*de \xmark & a*ta*ú*de \cmark \\
+ateísmo & a*te-ís*mo \xmark & a*te*ís*mo \cmark \\
+ateísta & a*te-ís*ta \xmark & a*te*ís*ta \cmark \\
+atelectasia & a*te*lec*ta*si*a \cmark & a*te*lec*ta*si-a \xmark \\
+atentatório & a*ten*ta*tó*ri.o \xmark & a*ten*ta*tó*rio \cmark \\
+atômico & a-tô*mi*co \xmark & a*tô*mi*co \cmark \\
+atonia & a*to*ni*a \cmark & a*to*ni-a \xmark \\
+atrabiliário & a*tra*bi*li-á*ri.o \xmark & a*tra*bi*li*á*rio \cmark \\
+atraído & a*tra-í*do \xmark & a*tra*í*do \cmark \\
+atrair & a*tra-ir \xmark & a*tra*ir \cmark \\
+atresia & a*tre*si*a \cmark & a*tre*si-a \xmark \\
+atribuição & a*tri*bu-i*ção \xmark & a*tri*bu*i*ção \cmark \\
+atribuir & a*tri*bu-ir \xmark & a*tri*bu*ir \cmark \\
+atribuível & a*tri*bu-í*vel \xmark & a*tri*bu*í*vel \cmark \\
+átrio & á*tri.o \xmark & á*trio \cmark \\
+atrofia & a*tro*fi*a \cmark & a*tro*fi-a \xmark \\
+audiência & au*di*ên*ci*a \cmark & au*di*ên*ci-a \xmark \\
+áudio & áu*di.o \xmark & áu*dio \cmark \\
+audiologia & au*di*o*lo*gi*a \cmark & au*di*o*lo*gi-a \xmark \\
+auditoria & au*di*to*ri*a \cmark & au*di*to*ri-a \xmark \\
+auditório & au*di*tó*ri.o \xmark & au*di*tó*rio \cmark \\
+augúrio & au*gú*ri.o \xmark & au*gú*rio \cmark \\
+áureo & áu*re.o \xmark & áu*reo \cmark \\
+auréola & au*ré-o*la \xmark & au*ré*o*la \cmark \\
+ausência & au*sên*ci.a \xmark & au*sên*cia \cmark \\
+auspício & aus*pí*ci.o \xmark & aus*pí*cio \cmark \\
+austríaco & aus*trí-a*co \xmark & aus*trí*a*co \cmark \\
+autarquia & au*tar*qui*a \cmark & au*tar*qui-a \xmark \\
+autobiografia & au*to*bi*o*gra*fi*a \cmark & au*to*bi*o*gra*fi-a \xmark \\
+autocracia & au*to*cra*ci*a \cmark & au*to*cra*ci-a \xmark \\
+autofagia & au*to*fa*gi*a \cmark & au*to*fa*gi-a \xmark \\
+autografia & au*to*gra*fi*a \cmark & au*to*gra*fi-a \xmark \\
+autônimo & au-tô*ni*mo \xmark & au*tô*ni*mo \cmark \\
+autonomia & au*to*no*mi*a \cmark & au*to*no*mi-a \xmark \\
+autônomo & au-tô*no*mo \xmark & au*tô*no*mo \cmark \\
+autópsia & au*tóp*si.a \xmark & au*tóp*sia \cmark \\
+autoria & au*to*ri*a \cmark & au*to*ri-a \xmark \\
+autoritário & au*to*ri*tá*ri.o \xmark & au*to*ri*tá*rio \cmark \\
+autotomia & au*to*to*mi*a \cmark & au*to*to*mi-a \xmark \\
+auxílio & au*xí*li.o \xmark & au*xí*lio \cmark \\
+avaria & a*va*ri*a \cmark & a*va*ri-a \xmark \\
+aveia & a*vei*a \cmark & a*vei-a \xmark \\
+avião & a*vi-ão \xmark & a*vi*ão \cmark \\
+aviário & a*vi-á*ri.o \xmark & a*vi*á*rio \cmark \\
+avô & a-vô \xmark & a*vô \cmark \\
+axiologia & a*xi*o*lo*gi*a \cmark & a*xi*o*lo*gi-a \xmark \\
+azálea & a*zá*le*a \cmark & a*zá*le-a \xmark \\
+azia & a*zi*a \cmark & a*zi-a \xmark \\
+azulejaria & a*zu*le*ja*ri*a \cmark & a*zu*le*ja*ri-a \xmark \\
+babalaô & ba*ba*la-ô \xmark & ba*ba*la*ô \cmark \\
 babuíno & ba*bu-í*no \xmark & ba*bu*í*no \cmark \\
+bacia & ba*ci*a \cmark & ba*ci-a \xmark \\
+bacio & ba*ci*o \cmark & ba*ci-o \xmark \\
+bactéria & bac*té*ri.a \xmark & bac*té*ria \cmark \\
+bacteriófago & bac*te*ri-ó*fa*go \xmark & bac*te*ri*ó*fa*go \cmark \\
+bacteriologia & bac*te*ri*o*lo*gi*a \cmark & bac*te*ri*o*lo*gi-a \xmark \\
+bafio & ba*fi*o \cmark & ba*fi-o \xmark \\
+bafômetro & ba-fô*me*tro \xmark & ba*fô*me*tro \cmark \\
 bahamense & ba-ha*men*se \xmark & ba-ha*men*se \xmark \\
-barômetro & ba-rô*me*tro \xmark & ba*rô*me*tro \cmark \\
+baia & bai*a \cmark & bai-a \xmark \\
+baía & ba-í-a \xmark & ba*í-a \xmark \\
+baião & bai-ão \xmark & bai*ão \cmark \\
+bainha & ba-i*nha \xmark & ba*i*nha \cmark \\
+baio & bai*o \cmark & bai-o \xmark \\
+baiuca & bai-u*ca \xmark & bai*u*ca \cmark \\
+baixaria & bai*xa*ri*a \cmark & bai*xa*ri-a \xmark \\
+baixio & bai*xi*o \cmark & bai*xi-o \xmark \\
+balaio & ba*lai*o \cmark & ba*lai-o \xmark \\
+balaustrada & ba*la-us*tra*da \xmark & ba*la-us*tra*da \xmark \\
+balaústre & ba*la-ús*tre \xmark & ba*la*ús*tre \cmark \\
+balboa & bal*bo*a \cmark & bal*bo-a \xmark \\
+balbucio & bal*bu*ci*o \cmark & bal*bu*ci-o \xmark \\
+balbúrdia & bal*búr*di.a \xmark & bal*búr*dia \cmark \\
+baldio & bal*di*o \cmark & bal*di-o \xmark \\
+baleia & ba*lei*a \cmark & ba*lei-a \xmark \\
+balneário & bal*ne-á*ri*o \xmark & bal*ne*á*ri-o \xmark \\
+bálteo & bál*te*o \cmark & bál*te-o \xmark \\
+bamboleio & bam*bo*lei*o \cmark & bam*bo*lei-o \xmark \\
+bancário & ban*cá*ri.o \xmark & ban*cá*rio \cmark \\
+bangalô & ban*ga-lô \xmark & ban*ga*lô \cmark \\
+barataria & ba*ra*ta*ri*a \cmark & ba*ra*ta*ri-a \xmark \\
+barateio & ba*ra*tei*o \cmark & ba*ra*tei-o \xmark \\
+barbárie & bar*bá*ri.e \xmark & bar*bá*rie \cmark \\
+barbearia & bar*be*a*ri*a \cmark & bar*be*a*ri-a \xmark \\
+bário & bá*ri.o \xmark & bá*rio \cmark \\
+bastião & bas*ti-ão \xmark & bas*ti*ão \cmark \\
+bateia & ba*tei*a \cmark & ba*tei-a \xmark \\
+bateria & ba*te*ri*a \cmark & ba*te*ri-a \xmark \\
+batimetria & ba*ti*me*tri*a \cmark & ba*ti*me*tri-a \xmark \\
+batráquio & ba*trá*qui.o \xmark & ba*trá*quio \cmark \\
+batuíra & ba*tu-í*ra \xmark & ba*tu*í*ra \cmark \\
+baú & ba-ú \xmark & ba*ú \cmark \\
+bazófia & ba*zó*fi.a \xmark & ba*zó*fia \cmark \\
+belisário & be*li*sá*ri.o \xmark & be*li*sá*rio \cmark \\
+beneficência & be*ne*fi*cên*ci.a \xmark & be*ne*fi*cên*cia \cmark \\
+beneficiário & be*ne*fi*ci-á*ri*o \xmark & be*ne*fi*ci*á*ri-o \xmark \\
+benefício & be*ne*fí*ci.o \xmark & be*ne*fí*cio \cmark \\
+benevolência & be*ne*vo*lên*ci.a \xmark & be*ne*vo*lên*cia \cmark \\
+benjoim & ben*jo-im \xmark & ben*jo*im \cmark \\
+beócio & be-ó*ci.o \xmark & be*ó*cio \cmark \\
+berçário & ber*çá*ri.o \xmark & ber*çá*rio \cmark \\
+berílio & be*rí*li.o \xmark & be*rí*lio \cmark \\
+béstia & bés*ti*a \cmark & bés*ti-a \xmark \\
+bia & bi*a \cmark & bi-a \xmark \\
 bibelô & bi*be-lô \xmark & bi*be*lô \cmark \\
+bibliofilia & bi*bli*o*fi*li*a \cmark & bi*bli*o*fi*li-a \xmark \\
+bibliófilo & bi*bli-ó*fi*lo \xmark & bi*bli*ó*fi*lo \cmark \\
+bibliografia & bi*bli*o*gra*fi*a \cmark & bi*bli*o*gra*fi-a \xmark \\
+bibliologia & bi*bli*o*lo*gi*a \cmark & bi*bli*o*lo*gi-a \xmark \\
+biblioteconomia & bi*bli*o*te*co*no*mi*a \cmark & bi*bli*o*te*co*no*mi-a \xmark \\
+bicampeão & bi*cam*pe-ão \xmark & bi*cam*pe*ão \cmark \\
+bicentenário & bi*cen*te*ná*ri.o \xmark & bi*cen*te*ná*rio \cmark \\
+bicicletário & bi*ci*cle*tá*ri.o \xmark & bi*ci*cle*tá*rio \cmark \\
+bicromia & bi*cro*mi*a \cmark & bi*cro*mi-a \xmark \\
+bigamia & bi*ga*mi*a \cmark & bi*ga*mi-a \xmark \\
+bijuteria & bi*ju*te*ri*a \cmark & bi*ju*te*ri-a \xmark \\
+bilheteria & bi*lhe*te*ri*a \cmark & bi*lhe*te*ri-a \xmark \\
+binário & bi*ná*ri.o \xmark & bi*ná*rio \cmark \\
+bioenergia & bi*o*e*ner*gi*a \cmark & bi*o*e*ner*gi-a \xmark \\
+bioética & bi*o-é*ti*ca \xmark & bi*o*é*ti*ca \cmark \\
+biófilo & bi-ó*fi*lo \xmark & bi*ó*fi*lo \cmark \\
+biogeografia & bi*o*ge*o*gra*fi*a \cmark & bi*o*ge*o*gra*fi-a \xmark \\
+biografia & bi*o*gra*fi*a \cmark & bi*o*gra*fi-a \xmark \\
+biógrafo & bi-ó*gra*fo \xmark & bi*ó*gra*fo \cmark \\
+biologia & bi*o*lo*gi*a \cmark & bi*o*lo*gi-a \xmark \\
+biólogo & bi-ó*lo*go \xmark & bi*ó*lo*go \cmark \\
+bioquímica & bi*o-quí*mi*ca \xmark & bi*o*quí*mi*ca \cmark \\
+biotecnologia & bi*o*tec*no*lo*gi*a \cmark & bi*o*tec*no*lo*gi-a \xmark \\
+biotério & bi*o*té*ri.o \xmark & bi*o*té*rio \cmark \\
+biótico & bi-ó*ti*co \xmark & bi*ó*ti*co \cmark \\
 biótipo & bi-ó*ti*po \xmark & bi*ó*ti*po \cmark \\
+biquíni & bi-quí*ni \xmark & bi*quí*ni \cmark \\
+birô & bi-rô \xmark & bi*rô \cmark \\
 bisavô & bi*sa-vô \xmark & bi*sa*vô \cmark \\
-bocaiuva & bo*cai-u*va \xmark & bo*cai-u*va \xmark \\
-borderô & bor*de-rô \xmark & bor*de*rô \cmark \\
+biscaia & bis*cai*a \cmark & bis*cai-a \xmark \\
+biscainho & bis*ca-i*nho \xmark & bis*ca*i*nho \cmark \\
+bizarria & bi*zar*ri*a \cmark & bi*zar*ri-a \xmark \\
+bloqueio & blo*quei*o \cmark & blo*quei-o \xmark \\
+boa & bo*a \cmark & bo-a \xmark \\
+boá & bo-á \xmark & bo*á \cmark \\
+bocaiuva & bo*cai-u*va \xmark & bo*cai*u*va \cmark \\
+boião & boi-ão \xmark & boi*ão \cmark \\
+boiuna & boi-u*na \xmark & boi*u*na \cmark \\
+boleia & bo*lei*a \cmark & bo*lei-a \xmark \\
+bombardeio & bom*bar*dei*o \cmark & bom*bar*dei-o \xmark \\
+bongô & bon-gô \xmark & bon*gô \cmark \\
+bonomia & bo*no*mi*a \cmark & bo*no*mi-a \xmark \\
+bordô & bor-dô \xmark & bor*dô \cmark \\
+borracharia & bor*ra*cha*ri*a \cmark & bor*ra*cha*ri-a \xmark \\
+bósnio & bós*ni.o \xmark & bós*nio \cmark \\
+boticário & bo*ti*cá*ri.o \xmark & bo*ti*cá*rio \cmark \\
+bovídeo & bo*ví*de.o \xmark & bo*ví*deo \cmark \\
+bradicardia & bra*di*car*di*a \cmark & bra*di*car*di-a \xmark \\
+brasílio & bra*sí*li.o \xmark & bra*sí*lio \cmark \\
+bravio & bra*vi*o \cmark & bra*vi-o \xmark \\
 brechtiano & bre.ch*ti*a*no \xmark & bre.ch*ti*a*no \xmark \\
+breviário & bre*vi-á*ri.o \xmark & bre*vi*á*rio \cmark \\
+brio & bri*o \cmark & bri-o \xmark \\
+broa & bro*a \cmark & bro-a \xmark \\
+bromatologia & bro*ma*to*lo*gi*a \cmark & bro*ma*to*lo*gi-a \xmark \\
+bromélia & bro*mé*li.a \xmark & bro*mé*lia \cmark \\
+brônquio & brôn*qui.o \xmark & brôn*quio \cmark \\
+bronquíolo & bron-quí-o*lo \xmark & bron*quí*o*lo \cmark \\
+bruxaria & bru*xa*ri*a \cmark & bru*xa*ri-a \xmark \\
+bué & bu-é \xmark & bu*é \cmark \\
+bugio & bu*gi*o \cmark & bu*gi-o \xmark \\
+buir & bu-ir \xmark & bu*ir \cmark \\
+bulício & bu*lí*ci.o \xmark & bu*lí*cio \cmark \\
+bulimia & bu*li*mi*a \cmark & bu*li*mi-a \xmark \\
+buquê & bu-quê \xmark & bu*quê \cmark \\
+burguesia & bur*gue*si*a \cmark & bur*gue*si-a \xmark \\
+burocracia & bu*ro*cra*ci*a \cmark & bu*ro*cra*ci-a \xmark \\
+búteo & bú*te*o \cmark & bú*te-o \xmark \\
+butiá & bu*ti-á \xmark & bu*ti*á \cmark \\
+búzio & bú*zi.o \xmark & bú*zio \cmark \\
+cacaio & ca*cai*o \cmark & ca*cai-o \xmark \\
+cacatua & ca*ca*tu*a \cmark & ca*ca*tu-a \xmark \\
+cacofonia & ca*co*fo*ni*a \cmark & ca*co*fo*ni-a \xmark \\
+cadeia & ca*dei*a \cmark & ca*dei-a \xmark \\
+cadência & ca*dên*ci.a \xmark & ca*dên*cia \cmark \\
+cafarnaum & ca*far*na-um \xmark & ca*far*na-um \xmark \\
+cafeína & ca*fe-í*na \xmark & ca*fe*í*na \cmark \\
+cafeteria & ca*fe*te*ri*a \cmark & ca*fe*te*ri-a \xmark \\
+cafraria & ca*fra*ri*a \cmark & ca*fra*ri-a \xmark \\
+caíco & ca-í*co \xmark & ca*í*co \cmark \\
+caída & ca-í*da \xmark & ca*í*da \cmark \\
+caído & ca-í*do \xmark & ca*í*do \cmark \\
+caim & ca-im \xmark & ca-im \xmark \\
+caíque & ca-í*que \xmark & ca*í*que \cmark \\
+cair & ca-ir \xmark & ca*ir \cmark \\
+cajuína & ca*ju-í*na \xmark & ca*ju*í*na \cmark \\
+calafrio & ca*la*fri*o \cmark & ca*la*fri-o \xmark \\
+calcário & cal*cá*ri*o \cmark & cal*cá*ri-o \xmark \\
+cálcio & cál*ci.o \xmark & cál*cio \cmark \\
+calcografia & cal*co*gra*fi*a \cmark & cal*co*gra*fi-a \xmark \\
+caleidoscópio & ca*lei*dos*có*pi.o \xmark & ca*lei*dos*có*pio \cmark \\
+calendário & ca*len*dá*ri.o \xmark & ca*len*dá*rio \cmark \\
+caligrafia & ca*li*gra*fi*a \cmark & ca*li*gra*fi-a \xmark \\
+calmaria & cal*ma*ri*a \cmark & cal*ma*ri-a \xmark \\
+caloria & ca*lo*ri*a \cmark & ca*lo*ri-a \xmark \\
+calorimetria & ca*lo*ri*me*tri*a \cmark & ca*lo*ri*me*tri-a \xmark \\
+calvário & cal*vá*ri.o \xmark & cal*vá*rio \cmark \\
+camaleão & ca*ma*le-ão \xmark & ca*ma*le*ão \cmark \\
+cambaio & cam*bai*o \cmark & cam*bai-o \xmark \\
+câmbio & câm*bi.o \xmark & câm*bio \cmark \\
+camboa & cam*bo*a \cmark & cam*bo-a \xmark \\
+cambraia & cam*brai*a \cmark & cam*brai-a \xmark \\
+cambuí & cam*bu-í \xmark & cam*bu*í \cmark \\
+camélia & ca*mé*li*a \cmark & ca*mé*li-a \xmark \\
+camelídeo & ca*me*lí*de.o \xmark & ca*me*lí*deo \cmark \\
+camelô & ca*me-lô \xmark & ca*me*lô \cmark \\
+camião & ca*mi-ão \xmark & ca*mi*ão \cmark \\
+camisaria & ca*mi*sa*ri*a \cmark & ca*mi*sa*ri-a \xmark \\
+campainha & cam*pa-i*nha \xmark & cam*pa*i*nha \cmark \\
+campanário & cam*pa*ná*ri.o \xmark & cam*pa*ná*rio \cmark \\
+campeão & cam*pe-ão \xmark & cam*pe*ão \cmark \\
+canaria & ca*na*ri*a \cmark & ca*na*ri-a \xmark \\
+canária & ca*ná*ri.a \xmark & ca*ná*ria \cmark \\
+cancerologia & can*ce*ro*lo*gi*a \cmark & can*ce*ro*lo*gi-a \xmark \\
+candeia & can*dei*a \cmark & can*dei-a \xmark \\
+candelária & can*de*lá*ri*a \cmark & can*de*lá*ri-a \xmark \\
+candidíase & can*di*dí-a*se \xmark & can*di*dí*a*se \cmark \\
+canhoneio & ca*nho*nei*o \cmark & ca*nho*nei-o \xmark \\
+canídeo & ca*ní*de.o \xmark & ca*ní*deo \cmark \\
+canoa & ca*no*a \cmark & ca*no-a \xmark \\
+canoísta & ca*no-ís*ta \xmark & ca*no*ís*ta \cmark \\
+cantaria & can*ta*ri*a \cmark & can*ta*ri-a \xmark \\
+cantoria & can*to*ri*a \cmark & can*to*ri-a \xmark \\
+caótico & ca-ó*ti*co \xmark & ca*ó*ti*co \cmark \\
+capadócio & ca*pa*dó*ci.o \xmark & ca*pa*dó*cio \cmark \\
+capatazia & ca*pa*ta*zi*a \cmark & ca*pa*ta*zi-a \xmark \\
+capelania & ca*pe*la*ni*a \cmark & ca*pe*la*ni-a \xmark \\
+capicua & ca*pi*cu*a \cmark & ca*pi*cu-a \xmark \\
+capitania & ca*pi*ta*ni*a \cmark & ca*pi*ta*ni-a \xmark \\
+capitânia & ca*pi*tâ*ni.a \xmark & ca*pi*tâ*nia \cmark \\
+capô & ca-pô \xmark & ca*pô \cmark \\
+caquexia & ca*que*xi*a \cmark & ca*que*xi-a \xmark \\
+caraíba & ca*ra-í*ba \xmark & ca*ra*í*ba \cmark \\
+carbonária & car*bo*ná*ri.a \xmark & car*bo*ná*ria \cmark \\
+carbonário & car*bo*ná*ri.o \xmark & car*bo*ná*rio \cmark \\
+carbônico & car-bô*ni*co \xmark & car*bô*ni*co \cmark \\
+carcerário & car*ce*rá*ri.o \xmark & car*ce*rá*rio \cmark \\
+cardápio & car*dá*pi.o \xmark & car*dá*pio \cmark \\
+cardíaco & car*dí-a*co \xmark & car*dí*a*co \cmark \\
+cardiologia & car*di*o*lo*gi*a \cmark & car*di*o*lo*gi-a \xmark \\
+carência & ca*rên*ci.a \xmark & ca*rên*cia \cmark \\
+carestia & ca*res*ti*a \cmark & ca*res*ti-a \xmark \\
+carícia & ca*rí*ci.a \xmark & ca*rí*cia \cmark \\
+cárie & cá*ri.e \xmark & cá*rie \cmark \\
 cariótipo & ca*ri-ó*ti*po \xmark & ca*ri*ó*ti*po \cmark \\
-chororô & cho*ro-rô \xmark & cho*ro*rô \cmark \\
+carnaúba & car*na-ú*ba \xmark & car*na*ú*ba \cmark \\
+carolíngio & ca*ro*lín*gi.o \xmark & ca*ro*lín*gio \cmark \\
+carotídeo & ca*ro*tí*de.o \xmark & ca*ro*tí*deo \cmark \\
+carpintaria & car*pin*ta*ri*a \cmark & car*pin*ta*ri-a \xmark \\
+carroceria & car*ro*ce*ri*a \cmark & car*ro*ce*ri-a \xmark \\
+cartapácio & car*ta*pá*ci.o \xmark & car*ta*pá*cio \cmark \\
+cartografia & car*to*gra*fi*a \cmark & car*to*gra*fi-a \xmark \\
+cartomancia & car*to*man*ci*a \cmark & car*to*man*ci-a \xmark \\
+cartório & car*tó*ri.o \xmark & car*tó*rio \cmark \\
+carvoaria & car*vo*a*ri*a \cmark & car*vo*a*ri-a \xmark \\
+casaria & ca*sa*ri*a \cmark & ca*sa*ri-a \xmark \\
+casario & ca*sa*ri*o \cmark & ca*sa*ri-o \xmark \\
+caseína & ca*se-í*na \xmark & ca*se*í*na \cmark \\
+casório & ca*só*ri.o \xmark & ca*só*rio \cmark \\
+cássia & cás*si.a \xmark & cás*sia \cmark \\
+casuísmo & ca*su-ís*mo \xmark & ca*su*ís*mo \cmark \\
+casuísta & ca*su-ís*ta \xmark & ca*su*ís*ta \cmark \\
+casuística & ca*su-ís*ti*ca \xmark & ca*su*ís*ti*ca \cmark \\
+casuístico & ca*su-ís*ti*co \xmark & ca*su*ís*ti*co \cmark \\
+catalepsia & ca*ta*lep*si*a \cmark & ca*ta*lep*si-a \xmark \\
+catatonia & ca*ta*to*ni*a \cmark & ca*ta*to*ni-a \xmark \\
+catequético & ca*te-qué*ti*co \xmark & ca*te*qué*ti*co \cmark \\
+catião & ca*ti-ão \xmark & ca*ti*ão \cmark \\
+catilinária & ca*ti*li*ná*ri.a \xmark & ca*ti*li*ná*ria \cmark \\
+catoptromancia & ca*top*tro*man*ci*a \cmark & ca*top*tro*man*ci-a \xmark \\
+catraia & ca*trai*a \cmark & ca*trai-a \xmark \\
+cauã & cau-ã \xmark & cau*ã \cmark \\
+cauim & cau-im \xmark & cau*im \cmark \\
+caúna & ca-ú*na \xmark & ca*ú*na \cmark \\
+cavalaria & ca*va*la*ri*a \cmark & ca*va*la*ri-a \xmark \\
+cávea & cá*ve*a \cmark & cá*ve-a \xmark \\
+ceceio & ce*cei*o \cmark & ce*cei-o \xmark \\
+cefaleia & ce*fa*lei*a \cmark & ce*fa*lei-a \xmark \\
+ceia & cei*a \cmark & cei-a \xmark \\
+cemitério & ce*mi*té*ri.o \xmark & ce*mi*té*rio \cmark \\
+cenário & ce*ná*ri.o \xmark & ce*ná*rio \cmark \\
+cenóbio & ce*nó*bi.o \xmark & ce*nó*bio \cmark \\
+cenografia & ce*no*gra*fi*a \cmark & ce*no*gra*fi-a \xmark \\
+cenotáfio & ce*no*tá*fi.o \xmark & ce*no*tá*fio \cmark \\
+censitário & cen*si*tá*ri.o \xmark & cen*si*tá*rio \cmark \\
+centáurea & cen*táu*re.a \xmark & cen*táu*rea \cmark \\
+centeio & cen*tei*o \cmark & cen*tei-o \xmark \\
+centenário & cen*te*ná*ri.o \xmark & cen*te*ná*rio \cmark \\
+centopeia & cen*to*pei*a \cmark & cen*to*pei-a \xmark \\
+centúria & cen*tú*ri.a \xmark & cen*tú*ria \cmark \\
+centurião & cen*tu*ri-ão \xmark & cen*tu*ri*ão \cmark \\
+cércea & cér*ce.a \xmark & cér*cea \cmark \\
+cerefólio & ce*re*fó*li.o \xmark & ce*re*fó*lio \cmark \\
+cério & cé*ri.o \xmark & cé*rio \cmark \\
+cerúleo & ce*rú*le.o \xmark & ce*rú*leo \cmark \\
+cervejaria & cer*ve*ja*ri*a \cmark & cer*ve*ja*ri-a \xmark \\
+cesárea & ce*sá*re.a \xmark & ce*sá*rea \cmark \\
+césio & cé*si.o \xmark & cé*sio \cmark \\
+cessionário & ces*si*o*ná*ri.o \xmark & ces*si*o*ná*rio \cmark \\
+cetáceo & ce*tá*ce.o \xmark & ce*tá*ceo \cmark \\
+chancelaria & chan*ce*la*ri*a \cmark & chan*ce*la*ri-a \xmark \\
+charrua & char*ru*a \cmark & char*ru-a \xmark \\
+charutaria & cha*ru*ta*ri*a \cmark & cha*ru*ta*ri-a \xmark \\
+chatô & cha-tô \xmark & cha*tô \cmark \\
+chefia & che*fi*a \cmark & che*fi-a \xmark \\
+cheia & chei*a \cmark & chei-a \xmark \\
+cheio & chei*o \cmark & chei-o \xmark \\
+chicória & chi*có*ri.a \xmark & chi*có*ria \cmark \\
+chio & chi*o \cmark & chi-o \xmark \\
+choperia & cho*pe*ri*a \cmark & cho*pe*ri-a \xmark \\
+churrascaria & chur*ras*ca*ri*a \cmark & chur*ras*ca*ri-a \xmark \\
+ciático & ci-á*ti*co \xmark & ci*á*ti*co \cmark \\
+ciclotimia & ci*clo*ti*mi*a \cmark & ci*clo*ti*mi-a \xmark \\
+ciclovia & ci*clo*vi*a \cmark & ci*clo*vi-a \xmark \\
+cidadania & ci*da*da*ni*a \cmark & ci*da*da*ni-a \xmark \\
+ciência & ci*ên*ci.a \xmark & ci*ên*cia \cmark \\
+cílio & cí*li.o \xmark & cí*lio \cmark \\
+cimério & ci*mé*ri.o \xmark & ci*mé*rio \cmark \\
+cinábrio & ci*ná*bri.o \xmark & ci*ná*brio \cmark \\
+cinefilia & ci*ne*fi*li*a \cmark & ci*ne*fi*li-a \xmark \\
+cinematografia & ci*ne*ma*to*gra*fi*a \cmark & ci*ne*ma*to*gra*fi-a \xmark \\
+cinescópio & ci*nes*có*pi.o \xmark & ci*nes*có*pio \cmark \\
+cinestesia & ci*nes*te*si*a \cmark & ci*nes*te*si-a \xmark \\
+cinofilia & ci*no*fi*li*a \cmark & ci*no*fi*li-a \xmark \\
+cinologia & ci*no*lo*gi*a \cmark & ci*no*lo*gi-a \xmark \\
+cinquentenário & cin*quen*te*ná*ri.o \xmark & cin*quen*te*ná*rio \cmark \\
+cintilografia & cin*ti*lo*gra*fi*a \cmark & cin*ti*lo*gra*fi-a \xmark \\
+cio & ci*o \cmark & ci-o \xmark \\
+circunferência & cir*cun*fe*rên*ci.a \xmark & cir*cun*fe*rên*cia \cmark \\
+circunstância & cir*cuns*tân*ci.a \xmark & cir*cuns*tân*cia \cmark \\
+círio & cí*ri.o \xmark & cí*rio \cmark \\
+cirurgia & ci*rur*gi*a \cmark & ci*rur*gi-a \xmark \\
+cirurgião & ci*rur*gi-ão \xmark & ci*rur*gi*ão \cmark \\
+cistoscopia & cis*tos*co*pi*a \cmark & cis*tos*co*pi-a \xmark \\
+citânia & ci*tâ*ni.a \xmark & ci*tâ*nia \cmark \\
+citologia & ci*to*lo*gi*a \cmark & ci*to*lo*gi-a \xmark \\
+ciúme & ci-ú*me \xmark & ci*ú*me \cmark \\
+cizânia & ci*zâ*ni.a \xmark & ci*zâ*nia \cmark \\
+claraboia & cla*ra*boi*a \cmark & cla*ra*boi-a \xmark \\
+clarividência & cla*ri*vi*dên*ci.a \xmark & cla*ri*vi*dên*cia \cmark \\
+claustrofobia & claus*tro*fo*bi*a \cmark & claus*tro*fo*bi-a \xmark \\
+clavicórdio & cla*vi*cór*di.o \xmark & cla*vi*cór*dio \cmark \\
+clemência & cle*mên*ci.a \xmark & cle*mên*cia \cmark \\
+cleptocracia & clep*to*cra*ci*a \cmark & clep*to*cra*ci-a \xmark \\
+cleptomania & clep*to*ma*ni*a \cmark & clep*to*ma*ni-a \xmark \\
+climatologia & cli*ma*to*lo*gi*a \cmark & cli*ma*to*lo*gi-a \xmark \\
+clorofórmio & clo*ro*fór*mi.o \xmark & clo*ro*fór*mio \cmark \\
+cnidário & c.ni*dá*ri.o \xmark & c.ni*dá*rio \xmark \\
+coa & co*a \cmark & co-a \xmark \\
+coágulo & co-á*gu*lo \xmark & co*á*gu*lo \cmark \\
+cobaia & co*bai*a \cmark & co*bai-a \xmark \\
+cobardia & co*bar*di*a \cmark & co*bar*di-a \xmark \\
+cocaína & co*ca-í*na \xmark & co*ca*í*na \cmark \\
+cocô & co-cô \xmark & co*cô \cmark \\
+côdea & cô*de.a \xmark & cô*dea \cmark \\
+codeína & co*de-í*na \xmark & co*de*í*na \cmark \\
+coerência & co*e*rên*ci.a \xmark & co*e*rên*cia \cmark \\
+coetâneo & co*e*tâ*ne*o \cmark & co*e*tâ*ne-o \xmark \\
+coexistência & co*e*xis*tên*ci.a \xmark & co*e*xis*tên*cia \cmark \\
+coibir & co-i*bir \xmark & co-i*bir \xmark \\
+coincidência & co-in*ci*dên*ci.a \xmark & co*in*ci*dên*cia \cmark \\
+coincidente & co-in*ci*den*te \xmark & co*in*ci*den*te \cmark \\
+coincidir & co-in*ci*dir \xmark & co*in*ci*dir \cmark \\
+colcheia & col*chei*a \cmark & col*chei-a \xmark \\
+colecistectomia & co*le*cis*tec*to*mi*a \cmark & co*le*cis*tec*to*mi-a \xmark \\
+colégio & co*lé*gi.o \xmark & co*lé*gio \cmark \\
+coleóptero & co*le-óp*te*ro \xmark & co*le*óp*te*ro \cmark \\
+colmeia & col*mei*a \cmark & col*mei-a \xmark \\
+colonia & co*lo*ni*a \cmark & co*lo*ni-a \xmark \\
+colonoscopia & co*lo*nos*co*pi*a \cmark & co*lo*nos*co*pi-a \xmark \\
+colóquio & co*ló*qui.o \xmark & co*ló*quio \cmark \\
+columbofilia & co*lum*bo*fi*li*a \cmark & co*lum*bo*fi*li-a \xmark \\
+combinatório & com*bi*na*tó*ri.o \xmark & com*bi*na*tó*rio \cmark \\
+comboio & com*boi*o \cmark & com*boi-o \xmark \\
+comédia & co*mé*di.a \xmark & co*mé*dia \cmark \\
+comediógrafo & co*me*di-ó*gra*fo \xmark & co*me*di*ó*gra*fo \cmark \\
+comentário & co*men*tá*ri.o \xmark & co*men*tá*rio \cmark \\
+comerciário & co*mer*ci-á*ri.o \xmark & co*mer*ci*á*rio \cmark \\
+comércio & co*mér*ci.o \xmark & co*mér*cio \cmark \\
+comício & co*mí*ci.o \xmark & co*mí*cio \cmark \\
+comissário & co*mis*sá*ri.o \xmark & co*mis*sá*rio \cmark \\
+companhia & com*pa*nhi*a \cmark & com*pa*nhi-a \xmark \\
+comparsaria & com*par*sa*ri*a \cmark & com*par*sa*ri-a \xmark \\
+compêndio & com*pên*di.o \xmark & com*pên*dio \cmark \\
+compensatório & com*pen*sa*tó*ri.o \xmark & com*pen*sa*tó*rio \cmark \\
+competência & com*pe*tên*ci.a \xmark & com*pe*tên*cia \cmark \\
+complacência & com*pla*cên*ci.a \xmark & com*pla*cên*cia \cmark \\
+compulsória & com*pul*só*ri.a \xmark & com*pul*só*ria \cmark \\
+compulsório & com*pul*só*ri.o \xmark & com*pul*só*rio \cmark \\
+conciliábulo & con*ci*li-á*bu*lo \xmark & con*ci*li*á*bu*lo \cmark \\
+conciliável & con*ci*li-á*vel \xmark & con*ci*li*á*vel \cmark \\
+concílio & con*cí*li.o \xmark & con*cí*lio \cmark \\
+concluído & con*clu-í*do \xmark & con*clu*í*do \cmark \\
+concluinte & con*clu-in*te \xmark & con*clu*in*te \cmark \\
+concluir & con*clu-ir \xmark & con*clu*ir \cmark \\
+concordância & con*cor*dân*ci.a \xmark & con*cor*dân*cia \cmark \\
+concórdia & con*cór*di.a \xmark & con*cór*dia \cmark \\
+concorrência & con*cor*rên*ci.a \xmark & con*cor*rên*cia \cmark \\
+concupiscência & con*cu*pis*cên*ci.a \xmark & con*cu*pis*cên*cia \cmark \\
+condenatório & con*de*na*tó*ri.o \xmark & con*de*na*tó*rio \cmark \\
+condescendência & con*des*cen*dên*ci.a \xmark & con*des*cen*dên*cia \cmark \\
+condoído & con*do-í*do \xmark & con*do*í*do \cmark \\
+condolência & con*do*lên*ci.a \xmark & con*do*lên*cia \cmark \\
+condomínio & con*do*mí*ni.o \xmark & con*do*mí*nio \cmark \\
+confeitaria & con*fei*ta*ri*a \cmark & con*fei*ta*ri-a \xmark \\
+conferência & con*fe*rên*ci.a \xmark & con*fe*rên*cia \cmark \\
+confessionário & con*fes*si*o*ná*ri.o \xmark & con*fes*si*o*ná*rio \cmark \\
+confiável & con*fi-á*vel \xmark & con*fi*á*vel \cmark \\
+confidência & con*fi*dên*ci.a \xmark & con*fi*dên*cia \cmark \\
+confluência & con*flu-ên*ci.a \xmark & con*flu*ên*cia \cmark \\
+confluir & con*flu-ir \xmark & con*flu*ir \cmark \\
+confraria & con*fra*ri*a \cmark & con*fra*ri-a \xmark \\
+congruência & con*gru-ên*ci.a \xmark & con*gru*ên*cia \cmark \\
+conluio & con*lui*o \cmark & con*lui-o \xmark \\
+consanguíneo & con*san*guí*ne.o \xmark & con*san*guí*neo \cmark \\
+consciência & cons*ci*ên*ci.a \xmark & cons*ci*ên*cia \cmark \\
+cônscio & côns*ci*o \cmark & côns*ci-o \xmark \\
+consentâneo & con*sen*tâ*ne.o \xmark & con*sen*tâ*neo \cmark \\
+consequência & con*se-quên*ci.a \xmark & con*se*quên*cia \cmark \\
+conservatório & con*ser*va*tó*ri.o \xmark & con*ser*va*tó*rio \cmark \\
+consílio & con*sí*li.o \xmark & con*sí*lio \cmark \\
+consistência & con*sis*tên*ci.a \xmark & con*sis*tên*cia \cmark \\
+consistório & con*sis*tó*ri*o \cmark & con*sis*tó*ri-o \xmark \\
+consonância & con*so*nân*ci*a \cmark & con*so*nân*ci-a \xmark \\
+consórcio & con*sór*ci.o \xmark & con*sór*cio \cmark \\
+conspícuo & cons*pí*cu.o \xmark & cons*pí*cuo \cmark \\
+constância & cons*tân*ci.a \xmark & cons*tân*cia \cmark \\
+constituição & cons*ti*tu-i*ção \xmark & cons*ti*tu*i*ção \cmark \\
+constituído & cons*ti*tu-í*do \xmark & cons*ti*tu*í*do \cmark \\
+constituinte & cons*ti*tu-in*te \xmark & cons*ti*tu*in*te \cmark \\
+constituir & cons*ti*tu-ir \xmark & cons*ti*tu*ir \cmark \\
+construído & cons*tru-í*do \xmark & cons*tru*í*do \cmark \\
+construir & cons*tru-ir \xmark & cons*tru*ir \cmark \\
+consuetudinário & con*su*e*tu*di*ná*ri.o \xmark & con*su*e*tu*di*ná*rio \cmark \\
+consultoria & con*sul*to*ri*a \cmark & con*sul*to*ri-a \xmark \\
+consultório & con*sul*tó*ri.o \xmark & con*sul*tó*rio \cmark \\
+contágio & con*tá*gi.o \xmark & con*tá*gio \cmark \\
+contaria & con*ta*ri*a \cmark & con*ta*ri-a \xmark \\
+contemporâneo & con*tem*po*râ*ne.o \xmark & con*tem*po*râ*neo \cmark \\
+conteúdo & con*te-ú*do \xmark & con*te*ú*do \cmark \\
+continência & con*ti*nên*ci.a \xmark & con*ti*nên*cia \cmark \\
+contingência & con*tin*gên*ci.a \xmark & con*tin*gên*cia \cmark \\
+contínua & con*tí*nu.a \xmark & con*tí*nua \cmark \\
+contínuo & con*tí*nu.o \xmark & con*tí*nuo \cmark \\
+contraditório & con*tra*di*tó*ri.o \xmark & con*tra*di*tó*rio \cmark \\
+contraído & con*tra-í*do \xmark & con*tra*í*do \cmark \\
+contrair & con*tra-ir \xmark & con*tra*ir \cmark \\
+contrário & con*trá*ri.o \xmark & con*trá*rio \cmark \\
+contribuição & con*tri*bu-i*ção \xmark & con*tri*bu*i*ção \cmark \\
+contribuidor & con*tri*bu-i*dor \xmark & con*tri*bu*i*dor \cmark \\
+contribuinte & con*tri*bu-in*te \xmark & con*tri*bu*in*te \cmark \\
+contribuir & con*tri*bu-ir \xmark & con*tri*bu*ir \cmark \\
+controladoria & con*tro*la*do*ri*a \cmark & con*tro*la*do*ri-a \xmark \\
+controvérsia & con*tro*vér*si.a \xmark & con*tro*vér*sia \cmark \\
+contumácia & con*tu*má*ci.a \xmark & con*tu*má*cia \cmark \\
+contundência & con*tun*dên*ci*a \cmark & con*tun*dên*ci-a \xmark \\
+conúbio & co*nú*bi.o \xmark & co*nú*bio \cmark \\
+conveniência & con*ve*ni*ên*ci.a \xmark & con*ve*ni*ên*cia \cmark \\
+convênio & con*vê*ni.o \xmark & con*vê*nio \cmark \\
+convergência & con*ver*gên*ci.a \xmark & con*ver*gên*cia \cmark \\
+convivência & con*vi*vên*ci.a \xmark & con*vi*vên*cia \cmark \\
+convívio & con*ví*vi*o \cmark & con*ví*vi-o \xmark \\
+coordenadoria & co*or*de*na*do*ri*a \cmark & co*or*de*na*do*ri-a \xmark \\
 copaíba & co*pa-í*ba \xmark & co*pa*í*ba \cmark \\
+cópia & có*pi.a \xmark & có*pia \cmark \\
+coprofilia & co*pro*fi*li*a \cmark & co*pro*fi*li-a \xmark \\
+coprolalia & co*pro*la*li*a \cmark & co*pro*la*li-a \xmark \\
+coreia & co*rei*a \cmark & co*rei-a \xmark \\
+coreografia & co*re*o*gra*fi*a \cmark & co*re*o*gra*fi-a \xmark \\
+coreógrafo & co*re-ó*gra*fo \xmark & co*re*ó*gra*fo \cmark \\
+coríntio & co*rín*ti.o \xmark & co*rín*tio \cmark \\
+córnea & cór*ne.a \xmark & cór*nea \cmark \\
+córneo & cór*ne.o \xmark & cór*neo \cmark \\
+cornucópia & cor*nu*có*pi.a \xmark & cor*nu*có*pia \cmark \\
+coroa & co*ro*a \cmark & co*ro-a \xmark \\
+coroinha & co*ro-i*nha \xmark & co*ro*i*nha \cmark \\
+corolário & co*ro*lá*ri.o \xmark & co*ro*lá*rio \cmark \\
+coronária & co*ro*ná*ri.a \xmark & co*ro*ná*ria \cmark \\
+coronário & co*ro*ná*ri.o \xmark & co*ro*ná*rio \cmark \\
+corpóreo & cor*pó*re.o \xmark & cor*pó*reo \cmark \\
+corregedoria & cor*re*ge*do*ri*a \cmark & cor*re*ge*do*ri-a \xmark \\
+correia & cor*rei*a \cmark & cor*rei-a \xmark \\
+correio & cor*rei*o \cmark & cor*rei-o \xmark \\
+correligionário & cor*re*li*gi*o*ná*ri.o \xmark & cor*re*li*gi*o*ná*rio \cmark \\
+correria & cor*re*ri*a \cmark & cor*re*ri-a \xmark \\
+correspondência & cor*res*pon*dên*ci.a \xmark & cor*res*pon*dên*cia \cmark \\
+corroído & cor*ro-í*do \xmark & cor*ro*í*do \cmark \\
+corsário & cor*sá*ri.o \xmark & cor*sá*rio \cmark \\
+cortesia & cor*te*si*a \cmark & cor*te*si-a \xmark \\
+corveia & cor*vei*a \cmark & cor*vei-a \xmark \\
+cosmogonia & cos*mo*go*ni*a \cmark & cos*mo*go*ni-a \xmark \\
+cosmografia & cos*mo*gra*fi*a \cmark & cos*mo*gra*fi-a \xmark \\
+cosmologia & cos*mo*lo*gi*a \cmark & cos*mo*lo*gi-a \xmark \\
+cotia & co*ti*a \cmark & co*ti-a \xmark \\
+cotovia & co*to*vi*a \cmark & co*to*vi-a \xmark \\
+coudelaria & cou*de*la*ri*a \cmark & cou*de*la*ri-a \xmark \\
+covardia & co*var*di*a \cmark & co*var*di-a \xmark \\
+coxia & co*xi*a \cmark & co*xi-a \xmark \\
+crânio & crâ*ni.o \xmark & crâ*nio \cmark \\
+crediário & cre*di-á*ri.o \xmark & cre*di*á*rio \cmark \\
+cretáceo & cre*tá*ce.o \xmark & cre*tá*ceo \cmark \\
+cria & cri*a \cmark & cri-a \xmark \\
+criciúma & cri*ci-ú*ma \xmark & cri*ci*ú*ma \cmark \\
+criminologia & cri*mi*no*lo*gi*a \cmark & cri*mi*no*lo*gi-a \xmark \\
+criptologia & crip*to*lo*gi*a \cmark & crip*to*lo*gi-a \xmark \\
+criptônimo & crip-tô*ni*mo \xmark & crip*tô*ni*mo \cmark \\
+cristalografia & cris*ta*lo*gra*fi*a \cmark & cris*ta*lo*gra*fi-a \xmark \\
+cristologia & cris*to*lo*gi*a \cmark & cris*to*lo*gi-a \xmark \\
+critério & cri*té*ri.o \xmark & cri*té*rio \cmark \\
+cromatografia & cro*ma*to*gra*fi*a \cmark & cro*ma*to*gra*fi-a \xmark \\
+crômio & crô*mi.o \xmark & crô*mio \cmark \\
+cromolitografia & cro*mo*li*to*gra*fi*a \cmark & cro*mo*li*to*gra*fi-a \xmark \\
+cromoterapia & cro*mo*te*ra*pi*a \cmark & cro*mo*te*ra*pi-a \xmark \\
+cronofotografia & cro*no*fo*to*gra*fi*a \cmark & cro*no*fo*to*gra*fi-a \xmark \\
+cronografia & cro*no*gra*fi*a \cmark & cro*no*gra*fi-a \xmark \\
+cronologia & cro*no*lo*gi*a \cmark & cro*no*lo*gi-a \xmark \\
+cronometria & cro*no*me*tri*a \cmark & cro*no*me*tri-a \xmark \\
+cronômetro & cro-nô*me*tro \xmark & cro*nô*me*tro \cmark \\
+crustáceo & crus*tá*ce.o \xmark & crus*tá*ceo \cmark \\
+cucurbitácea & cu*cur*bi*tá*ce.a \xmark & cu*cur*bi*tá*cea \cmark \\
+cuia & cui*a \cmark & cui-a \xmark \\
+cuíca & cu-í*ca \xmark & cu*í*ca \cmark \\
+culinária & cu*li*ná*ri.a \xmark & cu*li*ná*ria \cmark \\
+culinário & cu*li*ná*ri.o \xmark & cu*li*ná*rio \cmark \\
+culminância & cul*mi*nân*ci.a \xmark & cul*mi*nân*cia \cmark \\
+curadoria & cu*ra*do*ri*a \cmark & cu*ra*do*ri-a \xmark \\
+cúria & cú*ri.a \xmark & cú*ria \cmark \\
+curião & cu*ri-ão \xmark & cu*ri*ão \cmark \\
+curie & cu*ri*e \cmark & cu*ri-e \xmark \\
+curió & cu*ri-ó \xmark & cu*ri*ó \cmark \\
+cúrio & cú*ri.o \xmark & cú*rio \cmark \\
+curvilíneo & cur*vi*lí*ne.o \xmark & cur*vi*lí*neo \cmark \\
+custeio & cus*tei*o \cmark & cus*tei-o \xmark \\
+custódia & cus*tó*di.a \xmark & cus*tó*dia \cmark \\
+custódio & cus*tó*di.o \xmark & cus*tó*dio \cmark \\
+cutelaria & cu*te*la*ri*a \cmark & cu*te*la*ri-a \xmark \\
+cutia & cu*ti*a \cmark & cu*ti-a \xmark \\
+czarina & c.za*ri*na \xmark & cza*ri*na \cmark \\
 czarismo & c.za*ris*mo \xmark & cza*ris*mo \cmark \\
+czarista & c.za*ris*ta \xmark & cza*ris*ta \cmark \\
+dactiloscopia & dac*ti*los*co*pi*a \cmark & dac*ti*los*co*pi-a \xmark \\
+dadaísmo & da*da-ís*mo \xmark & da*da*ís*mo \cmark \\
+dadaísta & da*da-ís*ta \xmark & da*da*ís*ta \cmark \\
+daguerreótipo & da*guer*re-ó*ti*po \xmark & da*guer*re*ó*ti*po \cmark \\
+daí & da-í \xmark & da*í \cmark \\
+dália & dá*li.a \xmark & dá*lia \cmark \\
+daltônico & dal-tô*ni*co \xmark & dal*tô*ni*co \cmark \\
+danceteria & dan*ce*te*ri*a \cmark & dan*ce*te*ri-a \xmark \\
+darwinismo & dar-wi*nis*mo \xmark & dar-wi*nis*mo \xmark \\
 darwinista & dar-wi*nis*ta \xmark & dar-wi*nis*ta \xmark \\
+deão & de-ão \xmark & de*ão \cmark \\
+decacampeão & de*ca*cam*pe-ão \xmark & de*ca*cam*pe*ão \cmark \\
+decadência & de*ca*dên*ci.a \xmark & de*ca*dên*cia \cmark \\
 decaída & de*ca-í*da \xmark & de*ca*í*da \cmark \\
+decaído & de*ca-í*do \xmark & de*ca*í*do \cmark \\
+decair & de*ca-ir \xmark & de*ca*ir \cmark \\
+decalcomania & de*cal*co*ma*ni*a \cmark & de*cal*co*ma*ni-a \xmark \\
+decência & de*cên*ci.a \xmark & de*cên*cia \cmark \\
+decêndio & de*cên*di.o \xmark & de*cên*dio \cmark \\
+decisório & de*ci*só*ri.o \xmark & de*ci*só*rio \cmark \\
+declínio & de*clí*ni.o \xmark & de*clí*nio \cmark \\
+decorrência & de*cor*rên*ci.a \xmark & de*cor*rên*cia \cmark \\
+decurião & de*cu*ri-ão \xmark & de*cu*ri*ão \cmark \\
+defensoria & de*fen*so*ri*a \cmark & de*fen*so*ri-a \xmark \\
+deferência & de*fe*rên*ci.a \xmark & de*fe*rên*cia \cmark \\
+deficiência & de*fi*ci*ên*ci.a \xmark & de*fi*ci*ên*cia \cmark \\
+deficitário & de*fi*ci*tá*ri.o \xmark & de*fi*ci*tá*rio \cmark \\
+deia & dei*a \cmark & dei-a \xmark \\
+deísmo & de-ís*mo \xmark & de*ís*mo \cmark \\
+deísta & de-ís*ta \xmark & de*ís*ta \cmark \\
+delegacia & de*le*ga*ci*a \cmark & de*le*ga*ci-a \xmark \\
+deletério & de*le*té*ri.o \xmark & de*le*té*rio \cmark \\
+delícia & de*lí*ci.a \xmark & de*lí*cia \cmark \\
+delinquência & de*lin-quên*ci.a \xmark & de*lin*quên*cia \cmark \\
+delírio & de*lí*ri.o \xmark & de*lí*rio \cmark \\
+demagogia & de*ma*go*gi*a \cmark & de*ma*go*gi-a \xmark \\
+demasia & de*ma*si*a \cmark & de*ma*si-a \xmark \\
+demissionário & de*mis*si*o*ná*ri.o \xmark & de*mis*si*o*ná*rio \cmark \\
+demiurgo & de*mi-ur*go \xmark & de*mi*ur*go \cmark \\
+democracia & de*mo*cra*ci*a \cmark & de*mo*cra*ci-a \xmark \\
+demografia & de*mo*gra*fi*a \cmark & de*mo*gra*fi-a \xmark \\
+demoníaco & de*mo*ní-a*co \xmark & de*mo*ní*a*co \cmark \\
+demonologia & de*mo*no*lo*gi*a \cmark & de*mo*no*lo*gi-a \xmark \\
+dendrocronologia & den*dro*cro*no*lo*gi*a \cmark & den*dro*cro*no*lo*gi-a \xmark \\
+dendrologia & den*dro*lo*gi*a \cmark & den*dro*lo*gi-a \xmark \\
+densitometria & den*si*to*me*tri*a \cmark & den*si*to*me*tri-a \xmark \\
+dentifrício & den*ti*frí*ci.o \xmark & den*ti*frí*cio \cmark \\
+denúncia & de*nún*ci.a \xmark & de*nún*cia \cmark \\
+deontologia & de*on*to*lo*gi*a \cmark & de*on*to*lo*gi-a \xmark \\
+dependência & de*pen*dên*ci.a \xmark & de*pen*dên*cia \cmark \\
+depoimento & de*po-i*men*to \xmark & de*po*i*men*to \cmark \\
+depositário & de*po*si*tá*ri.o \xmark & de*po*si*tá*rio \cmark \\
+dermatologia & der*ma*to*lo*gi*a \cmark & der*ma*to*lo*gi-a \xmark \\
+desafio & de*sa*fi*o \cmark & de*sa*fi-o \xmark \\
+desarmonia & de*sar*mo*ni*a \cmark & de*sar*mo*ni-a \xmark \\
+desbloqueio & des*blo*quei*o \cmark & des*blo*quei-o \xmark \\
+descaída & des*ca-í*da \xmark & des*ca*í*da \cmark \\
+descair & des*ca-ir \xmark & des*ca*ir \cmark \\
+descendência & des*cen*dên*ci.a \xmark & des*cen*dên*cia \cmark \\
+desconstruir & des*cons*tru-ir \xmark & des*cons*tru*ir \cmark \\
+descontraído & des*con*tra-í*do \xmark & des*con*tra*í*do \cmark \\
+descontrair & des*con*tra-ir \xmark & des*con*tra*ir \cmark \\
+descortesia & des*cor*te*si*a \cmark & des*cor*te*si-a \xmark \\
+deselegância & de*se*le*gân*ci.a \xmark & de*se*le*gân*cia \cmark \\
+desembainhar & de*sem*ba-i*nhar \xmark & de*sem*ba*i*nhar \cmark \\
+desequilíbrio & de*se*qui*lí*bri.o \xmark & de*se*qui*lí*brio \cmark \\
+desfastio & des*fas*ti*o \cmark & des*fas*ti-o \xmark \\
+desídia & de*sí*di.a \xmark & de*sí*dia \cmark \\
+desinência & de*si*nên*ci.a \xmark & de*si*nên*cia \cmark \\
+desistência & de*sis*tên*ci.a \xmark & de*sis*tên*cia \cmark \\
+desmaio & des*mai*o \cmark & des*mai-o \xmark \\
+desnecessário & des*ne*ces*sá*ri.o \xmark & des*ne*ces*sá*rio \cmark \\
+desobediência & de*so*be*di*ên*ci.a \xmark & de*so*be*di*ên*cia \cmark \\
+desobstruir & de*sobs*tru-ir \xmark & de*sobs*tru*ir \cmark \\
+despoluição & des*po*lu-i*ção \xmark & des*po*lu*i*ção \cmark \\
+despoluir & des*po*lu-ir \xmark & des*po*lu*ir \cmark \\
+desprestígio & des*pres*tí*gi*o \cmark & des*pres*tí*gi-o \xmark \\
+destinatário & des*ti*na*tá*ri.o \xmark & des*ti*na*tá*rio \cmark \\
+destituição & des*ti*tu-i*ção \xmark & des*ti*tu*i*ção \cmark \\
+destituído & des*ti*tu-í*do \xmark & des*ti*tu*í*do \cmark \\
+destituir & des*ti*tu-ir \xmark & des*ti*tu*ir \cmark \\
+destruição & des*tru-i*ção \xmark & des*tru*i*ção \cmark \\
+destruído & des*tru-í*do \xmark & des*tru*í*do \cmark \\
+destruir & des*tru-ir \xmark & des*tru*ir \cmark \\
+desvario & des*va*ri*o \cmark & des*va*ri-o \xmark \\
+desvio & des*vi*o \cmark & des*vi-o \xmark \\
+deutério & deu*té*ri.o \xmark & deu*té*rio \cmark \\
+devaneio & de*va*nei*o \cmark & de*va*nei-o \xmark \\
+diaconia & di*a*co*ni*a \cmark & di*a*co*ni-a \xmark \\
+diácono & di-á*co*no \xmark & di*á*co*no \cmark \\
+diacronia & di*a*cro*ni*a \cmark & di*a*cro*ni-a \xmark \\
+díade & dí-a*de \xmark & dí*a*de \cmark \\
+dia & di*a \cmark & di-a \xmark \\
+diáfano & di-á*fa*no \xmark & di*á*fa*no \cmark \\
 diálise & di-á*li*se \xmark & di*á*li*se \cmark \\
+diálogo & di-á*lo*go \xmark & di*á*lo*go \cmark \\
+diária & di-á*ri.a \xmark & di*á*ria \cmark \\
+diário & di-á*ri.o \xmark & di*á*rio \cmark \\
+diarquia & di*ar*qui*a \cmark & di*ar*qui-a \xmark \\
+diarreia & di*ar*rei*a \cmark & di*ar*rei-a \xmark \\
+diáspora & di-ás*po*ra \xmark & di*ás*po*ra \cmark \\
 diástole & di-ás*to*le \xmark & di*ás*to*le \cmark \\
+dicionário & di*ci*o*ná*ri.o \xmark & di*ci*o*ná*rio \cmark \\
+dicotomia & di*co*to*mi*a \cmark & di*co*to*mi-a \xmark \\
+dicroísmo & di*cro-ís*mo \xmark & di*cro*ís*mo \cmark \\
+diérese & di-é*re*se \xmark & di*é*re*se \cmark \\
+diferenciável & di*fe*ren*ci-á*vel \xmark & di*fe*ren*ci*á*vel \cmark \\
+difluência & di*flu-ên*ci.a \xmark & di*flu*ên*cia \cmark \\
+difteria & dif*te*ri*a \cmark & dif*te*ri-a \xmark \\
+diglossia & di*glos*si*a \cmark & di*glos*si-a \xmark \\
+dignitário & dig*ni*tá*ri.o \xmark & dig*ni*tá*rio \cmark \\
+diligência & di*li*gên*ci.a \xmark & di*li*gên*cia \cmark \\
+diluído & di*lu-í*do \xmark & di*lu*í*do \cmark \\
+diluir & di*lu-ir \xmark & di*lu*ir \cmark \\
+dilúvio & di*lú*vi.o \xmark & di*lú*vio \cmark \\
+diminuição & di*mi*nu-i*ção \xmark & di*mi*nu*i*ção \cmark \\
+diminuído & di*mi*nu-í*do \xmark & di*mi*nu*í*do \cmark \\
+diminuir & di*mi*nu-ir \xmark & di*mi*nu*ir \cmark \\
+dinamarquês & di*na*mar-quês \xmark & di*na*mar*quês \cmark \\
+dinastia & di*nas*ti*a \cmark & di*nas*ti-a \xmark \\
+dionisíaco & di*o*ni*sí-a*co \xmark & di*o*ni*sí*a*co \cmark \\
+dióxido & di-ó*xi*do \xmark & di*ó*xi*do \cmark \\
+diplegia & di*ple*gi*a \cmark & di*ple*gi-a \xmark \\
+diplomacia & di*plo*ma*ci*a \cmark & di*plo*ma*ci-a \xmark \\
+diretoria & di*re*to*ri*a \cmark & di*re*to*ri-a \xmark \\
+diretório & di*re*tó*ri.o \xmark & di*re*tó*rio \cmark \\
+disartria & di*sar*tri*a \cmark & di*sar*tri-a \xmark \\
+discinesia & dis*ci*ne*si*a \cmark & dis*ci*ne*si-a \xmark \\
+discografia & dis*co*gra*fi*a \cmark & dis*co*gra*fi-a \xmark \\
+discordância & dis*cor*dân*ci.a \xmark & dis*cor*dân*cia \cmark \\
+discórdia & dis*cór*di.a \xmark & dis*cór*dia \cmark \\
+discrepância & dis*cre*pân*ci.a \xmark & dis*cre*pân*cia \cmark \\
+discricionário & dis*cri*ci*o*ná*ri.o \xmark & dis*cri*ci*o*ná*rio \cmark \\
+disenteria & di*sen*te*ri*a \cmark & di*sen*te*ri-a \xmark \\
+disfagia & dis*fa*gi*a \cmark & dis*fa*gi-a \xmark \\
+disfemia & dis*fe*mi*a \cmark & dis*fe*mi-a \xmark \\
+disfonia & dis*fo*ni*a \cmark & dis*fo*ni-a \xmark \\
+disforia & dis*fo*ri*a \cmark & dis*fo*ri-a \xmark \\
+disgenesia & dis*ge*ne*si*a \cmark & dis*ge*ne*si-a \xmark \\
+dislalia & dis*la*li*a \cmark & dis*la*li-a \xmark \\
+dislexia & dis*le*xi*a \cmark & dis*le*xi-a \xmark \\
+dismenorreia & dis*me*nor*rei*a \cmark & dis*me*nor*rei-a \xmark \\
+dispêndio & dis*pên*di.o \xmark & dis*pên*dio \cmark \\
+dispepsia & dis*pep*si*a \cmark & dis*pep*si-a \xmark \\
+displasia & dis*pla*si*a \cmark & dis*pla*si-a \xmark \\
+dispneia & disp*nei*a \cmark & disp*nei-a \xmark \\
+disprósio & dis*pró*si.o \xmark & dis*pró*sio \cmark \\
+disritmia & dis*rit*mi*a \cmark & dis*rit*mi-a \xmark \\
+dissacarídeo & dis*sa*ca*rí*de.o \xmark & dis*sa*ca*rí*deo \cmark \\
+dissidência & dis*si*dên*ci.a \xmark & dis*si*dên*cia \cmark \\
+dissídio & dis*sí*di.o \xmark & dis*sí*dio \cmark \\
+dissimetria & dis*si*me*tri*a \cmark & dis*si*me*tri-a \xmark \\
+dissonância & dis*so*nân*ci.a \xmark & dis*so*nân*cia \cmark \\
+distanásia & dis*ta*ná*si.a \xmark & dis*ta*ná*sia \cmark \\
+distância & dis*tân*ci.a \xmark & dis*tân*cia \cmark \\
+distimia & dis*ti*mi*a \cmark & dis*ti*mi-a \xmark \\
+distocia & dis*to*ci*a \cmark & dis*to*ci-a \xmark \\
+distonia & dis*to*ni*a \cmark & dis*to*ni-a \xmark \\
+distraído & dis*tra-í*do \xmark & dis*tra*í*do \cmark \\
+distrair & dis*tra-ir \xmark & dis*tra*ir \cmark \\
+distribuição & dis*tri*bu-i*ção \xmark & dis*tri*bu*i*ção \cmark \\
+distribuído & dis*tri*bu-í*do \xmark & dis*tri*bu*í*do \cmark \\
+distribuidora & dis*tri*bu-i*do*ra \xmark & dis*tri*bu*i*do*ra \cmark \\
+distribuidor & dis*tri*bu-i*dor \xmark & dis*tri*bu*i*dor \cmark \\
+distribuir & dis*tri*bu-ir \xmark & dis*tri*bu*ir \cmark \\
+distúrbio & dis*túr*bi.o \xmark & dis*túr*bio \cmark \\
+disúria & di*sú*ri.a \xmark & di*sú*ria \cmark \\
+diurno & di-ur*no \xmark & di*ur*no \cmark \\
+divergência & di*ver*gên*ci.a \xmark & di*ver*gên*cia \cmark \\
+divisória & di*vi*só*ri.a \xmark & di*vi*só*ria \cmark \\
+divisório & di*vi*só*ri.o \xmark & di*vi*só*rio \cmark \\
+divórcio & di*vór*ci.o \xmark & di*vór*cio \cmark \\
+doceria & do*ce*ri*a \cmark & do*ce*ri-a \xmark \\
+documentário & do*cu*men*tá*ri.o \xmark & do*cu*men*tá*rio \cmark \\
+dodecafonia & do*de*ca*fo*ni*a \cmark & do*de*ca*fo*ni-a \xmark \\
+dodecafônico & do*de*ca-fô*ni*co \xmark & do*de*ca*fô*ni*co \cmark \\
+doentio & do*en*ti*o \cmark & do*en*ti-o \xmark \\
+doído & do-í*do \xmark & do*í*do \cmark \\
+domiciliário & do*mi*ci*li-á*ri.o \xmark & do*mi*ci*li*á*rio \cmark \\
+domicílio & do*mi*cí*li.o \xmark & do*mi*cí*lio \cmark \\
+domínio & do*mí*ni.o \xmark & do*mí*nio \cmark \\
+donataria & do*na*ta*ri*a \cmark & do*na*ta*ri-a \xmark \\
+donatário & do*na*tá*ri.o \xmark & do*na*tá*rio \cmark \\
+dormitório & dor*mi*tó*ri*o \cmark & dor*mi*tó*ri-o \xmark \\
+doutrinário & dou*tri*ná*ri.o \xmark & dou*tri*ná*rio \cmark \\
+doxografia & do*xo*gra*fi*a \cmark & do*xo*gra*fi-a \xmark \\
+drágea & drá*ge.a \xmark & drá*gea \cmark \\
+dramaturgia & dra*ma*tur*gi*a \cmark & dra*ma*tur*gi-a \xmark \\
+dríade & drí-a*de \xmark & drí*a*de \cmark \\
+drogaria & dro*ga*ri*a \cmark & dro*ga*ri-a \xmark \\
+dromedário & dro*me*dá*ri.o \xmark & dro*me*dá*rio \cmark \\
+dúbio & dú*bi.o \xmark & dú*bio \cmark \\
+dulcineia & dul*ci*nei*a \cmark & dul*ci*nei-a \xmark \\
+duo & du*o \cmark & du-o \xmark \\
+duralumínio & du*ra*lu*mí*ni.o \xmark & du*ra*lu*mí*nio \cmark \\
+dúzia & dú*zi.a \xmark & dú*zia \cmark \\
+dzeta & d.ze*ta \xmark & d.ze*ta \xmark \\
+ébrio & é*bri*o \cmark & é*bri-o \xmark \\
+ebúrneo & e*búr*ne.o \xmark & e*búr*neo \cmark \\
+eclesiástico & e*cle*si-ás*ti*co \xmark & e*cle*si*ás*ti*co \cmark \\
+ecografia & e*co*gra*fi*a \cmark & e*co*gra*fi-a \xmark \\
+ecolalia & e*co*la*li*a \cmark & e*co*la*li-a \xmark \\
+ecologia & e*co*lo*gi*a \cmark & e*co*lo*gi-a \xmark \\
+econometria & e*co*no*me*tri*a \cmark & e*co*no*me*tri-a \xmark \\
+economia & e*co*no*mi*a \cmark & e*co*no*mi-a \xmark \\
+econômico & e*co-nô*mi*co \xmark & e*co*nô*mi*co \cmark \\
+ecônomo & e-cô*no*mo \xmark & e*cô*no*mo \cmark \\
+ecotoxicologia & e*co*to*xi*co*lo*gi*a \cmark & e*co*to*xi*co*lo*gi-a \xmark \\
+ectasia & ec*ta*si*a \cmark & ec*ta*si-a \xmark \\
+edifício & e*di*fí*ci.o \xmark & e*di*fí*cio \cmark \\
+editoria & e*di*to*ri*a \cmark & e*di*to*ri-a \xmark \\
+educandário & e*du*can*dá*ri.o \xmark & e*du*can*dá*rio \cmark \\
+eficácia & e*fi*cá*ci.a \xmark & e*fi*cá*cia \cmark \\
+eficiência & e*fi*ci*ên*ci.a \xmark & e*fi*ci*ên*cia \cmark \\
+efígie & e*fí*gi.e \xmark & e*fí*gie \cmark \\
+eflúvio & e*flú*vi.o \xmark & e*flú*vio \cmark \\
+egípcio & e*gíp*ci.o \xmark & e*gíp*cio \cmark \\
+egiptologia & e*gip*to*lo*gi*a \cmark & e*gip*to*lo*gi-a \xmark \\
+egoísmo & e*go-ís*mo \xmark & e*go*ís*mo \cmark \\
+egoísta & e*go-ís*ta \xmark & e*go*ís*ta \cmark \\
+egoístico & e*go-ís*ti*co \xmark & e*go*ís*ti*co \cmark \\
+egrégio & e*gré*gi.o \xmark & e*gré*gio \cmark \\
+eia & ei*a \cmark & ei-a \xmark \\
+elastômero & e*las-tô*me*ro \xmark & e*las*tô*me*ro \cmark \\
+elefantíase & e*le*fan*tí-a*se \xmark & e*le*fan*tí*a*se \cmark \\
+elegância & e*le*gân*ci.a \xmark & e*le*gân*cia \cmark \\
+elegia & e*le*gi*a \cmark & e*le*gi-a \xmark \\
+eletrocardiógrafo & e*le*tro*car*di-ó*gra*fo \xmark & e*le*tro*car*di*ó*gra*fo \cmark \\
+eletroímã & e*le*tro-í*mã \xmark & e*le*tro*í*mã \cmark \\
+eletroquímica & e*le*tro-quí*mi*ca \xmark & e*le*tro*quí*mi*ca \cmark \\
+eliminatória & e*li*mi*na*tó*ri.a \xmark & e*li*mi*na*tó*ria \cmark \\
+elogiável & e*lo*gi-á*vel \xmark & e*lo*gi*á*vel \cmark \\
+elogio & e*lo*gi*o \cmark & e*lo*gi-o \xmark \\
+eloquência & e*lo-quên*ci.a \xmark & e*lo*quên*cia \cmark \\
+elucidário & e*lu*ci*dá*ri.o \xmark & e*lu*ci*dá*rio \cmark \\
+eluição & e*lu-i*ção \xmark & e*lu*i*ção \cmark \\
+embainhar & em*ba-i*nhar \xmark & em*ba*i*nhar \cmark \\
+embolia & em*bo*li*a \cmark & em*bo*li-a \xmark \\
+embrião & em*bri-ão \xmark & em*bri*ão \cmark \\
+embriologia & em*bri*o*lo*gi*a \cmark & em*bri*o*lo*gi-a \xmark \\
+embrionário & em*bri*o*ná*ri.o \xmark & em*bri*o*ná*rio \cmark \\
+ementário & e*men*tá*ri*o \cmark & e*men*tá*ri-o \xmark \\
+emergência & e*mer*gên*ci.a \xmark & e*mer*gên*cia \cmark \\
+eminência & e*mi*nên*ci.a \xmark & e*mi*nên*cia \cmark \\
+emissário & e*mis*sá*ri.o \xmark & e*mis*sá*rio \cmark \\
+empáfia & em*pá*fi.a \xmark & em*pá*fia \cmark \\
+empatia & em*pa*ti*a \cmark & em*pa*ti-a \xmark \\
+empório & em*pó*ri.o \xmark & em*pó*rio \cmark \\
+encefalopatia & en*ce*fa*lo*pa*ti*a \cmark & en*ce*fa*lo*pa*ti-a \xmark \\
+enciclopédia & en*ci*clo*pé*di.a \xmark & en*ci*clo*pé*dia \cmark \\
+endemia & en*de*mi*a \cmark & en*de*mi-a \xmark \\
+endocárdio & en*do*cár*di.o \xmark & en*do*cár*dio \cmark \\
+endocrinologia & en*do*cri*no*lo*gi*a \cmark & en*do*cri*no*lo*gi-a \xmark \\
+endodontia & en*do*don*ti*a \cmark & en*do*don*ti-a \xmark \\
+endogamia & en*do*ga*mi*a \cmark & en*do*ga*mi-a \xmark \\
+endométrio & en*do*mé*tri.o \xmark & en*do*mé*trio \cmark \\
+endoscopia & en*dos*co*pi*a \cmark & en*dos*co*pi-a \xmark \\
+energia & e*ner*gi*a \cmark & e*ner*gi-a \xmark \\
+enfermaria & en*fer*ma*ri*a \cmark & en*fer*ma*ri-a \xmark \\
+engenharia & en*ge*nha*ri*a \cmark & en*ge*nha*ri-a \xmark \\
+enguia & en*gui*a \cmark & en*gui-a \xmark \\
+enjoo & en*jo*o \cmark & en*jo-o \xmark \\
+enologia & e*no*lo*gi*a \cmark & e*no*lo*gi-a \xmark \\
+ensaio & en*sai*o \cmark & en*sai-o \xmark \\
+ensaísmo & en*sa-ís*mo \xmark & en*sa*ís*mo \cmark \\
+ensaísta & en*sa-ís*ta \xmark & en*sa*ís*ta \cmark \\
+entalpia & en*tal*pi*a \cmark & en*tal*pi-a \xmark \\
+enteropatia & en*te*ro*pa*ti*a \cmark & en*te*ro*pa*ti-a \xmark \\
+entomologia & en*to*mo*lo*gi*a \cmark & en*to*mo*lo*gi-a \xmark \\
+entremeio & en*tre*mei*o \cmark & en*tre*mei-o \xmark \\
+entropia & en*tro*pi*a \cmark & en*tro*pi-a \xmark \\
+entusiástico & en*tu*si-ás*ti*co \xmark & en*tu*si*ás*ti*co \cmark \\
+envio & en*vi*o \cmark & en*vi-o \xmark \\
+envoltório & en*vol*tó*ri.o \xmark & en*vol*tó*rio \cmark \\
+enxertia & en*xer*ti*a \cmark & en*xer*ti-a \xmark \\
+enxovia & en*xo*vi*a \cmark & en*xo*vi-a \xmark \\
+enzimologia & en*zi*mo*lo*gi*a \cmark & en*zi*mo*lo*gi-a \xmark \\
+eólico & e-ó*li*co \xmark & e*ó*li*co \cmark \\
+éon & é-on \xmark & é*on \cmark \\
+eparquia & e*par*qui*a \cmark & e*par*qui-a \xmark \\
+epidemia & e*pi*de*mi*a \cmark & e*pi*de*mi-a \xmark \\
+epidemiologia & e*pi*de*mi*o*lo*gi*a \cmark & e*pi*de*mi*o*lo*gi-a \xmark \\
+epigrafia & e*pi*gra*fi*a \cmark & e*pi*gra*fi-a \xmark \\
+epilepsia & e*pi*lep*si*a \cmark & e*pi*lep*si-a \xmark \\
+epistemologia & e*pis*te*mo*lo*gi*a \cmark & e*pis*te*mo*lo*gi-a \xmark \\
+epitáfio & e*pi*tá*fi.o \xmark & e*pi*tá*fio \cmark \\
+epizootia & e*pi*zo*o*ti*a \cmark & e*pi*zo*o*ti-a \xmark \\
+epopeia & e*po*pei*a \cmark & e*po*pei-a \xmark \\
+equânime & e-quâ*ni*me \xmark & e*quâ*ni*me \cmark \\
+equídeo & e-quí*de.o \xmark & e*quí*deo \cmark \\
+equilíbrio & e*qui*lí*bri.o \xmark & e*qui*lí*brio \cmark \\
+equinócio & e*qui*nó*ci.o \xmark & e*qui*nó*cio \cmark \\
+equivalência & e*qui*va*lên*ci.a \xmark & e*qui*va*lên*cia \cmark \\
+equívoco & e-quí*vo*co \xmark & e*quí*vo*co \cmark \\
+erário & e*rá*ri.o \xmark & e*rá*rio \cmark \\
+érbio & ér*bi.o \xmark & ér*bio \cmark \\
+ergometria & er*go*me*tri*a \cmark & er*go*me*tri-a \xmark \\
+ergonomia & er*go*no*mi*a \cmark & er*go*no*mi-a \xmark \\
+ergonômico & er*go-nô*mi*co \xmark & er*go*nô*mi*co \cmark \\
+erotomania & e*ro*to*ma*ni*a \cmark & e*ro*to*ma*ni-a \xmark \\
+esbórnia & es*bór*ni.a \xmark & es*bór*nia \cmark \\
+escadaria & es*ca*da*ri*a \cmark & es*ca*da*ri-a \xmark \\
+escândio & es*cân*di.o \xmark & es*cân*dio \cmark \\
+escanteio & es*can*tei*o \cmark & es*can*tei-o \xmark \\
+escárnio & es*cár*ni.o \xmark & es*cár*nio \cmark \\
+escatologia & es*ca*to*lo*gi*a \cmark & es*ca*to*lo*gi-a \xmark \\
+esclerodermia & es*cle*ro*der*mi*a \cmark & es*cle*ro*der*mi-a \xmark \\
+escleroterapia & es*cle*ro*te*ra*pi*a \cmark & es*cle*ro*te*ra*pi-a \xmark \\
+escócia & es*có*ci.a \xmark & es*có*cia \cmark \\
+escólio & es*có*li.o \xmark & es*có*lio \cmark \\
+escória & es*có*ri.a \xmark & es*có*ria \cmark \\
+escorpião & es*cor*pi-ão \xmark & es*cor*pi*ão \cmark \\
+escorregadio & es*cor*re*ga*di*o \cmark & es*cor*re*ga*di-o \xmark \\
+escritório & es*cri*tó*ri.o \xmark & es*cri*tó*rio \cmark \\
+escriturário & es*cri*tu*rá*ri.o \xmark & es*cri*tu*rá*rio \cmark \\
+escrofulária & es*cro*fu*lá*ri.a \xmark & es*cro*fu*lá*ria \cmark \\
+escrutínio & es*cru*tí*ni.o \xmark & es*cru*tí*nio \cmark \\
+escuderia & es*cu*de*ri*a \cmark & es*cu*de*ri-a \xmark \\
+esculápio & es*cu*lá*pi.o \xmark & es*cu*lá*pio \cmark \\
+esfigmomanômetro & es*fig*mo*ma-nô*me*tro \xmark & es*fig*mo*ma*nô*me*tro \cmark \\
+esguio & es*gui*o \cmark & es*gui-o \xmark \\
+esofagectomia & e*so*fa*gec*to*mi*a \cmark & e*so*fa*gec*to*mi-a \xmark \\
+especiaria & es*pe*ci*a*ri*a \cmark & es*pe*ci*a*ri-a \xmark \\
+espécie & es*pé*ci.e \xmark & es*pé*cie \cmark \\
+espia & es*pi*a \cmark & es*pi-a \xmark \\
+espião & es*pi-ão \xmark & es*pi*ão \cmark \\
+esplenomegalia & es*ple*no*me*ga*li*a \cmark & es*ple*no*me*ga*li-a \xmark \\
+esponsais & es*pon*sa-is \xmark & es*pon*sa-is \xmark \\
+espontâneo & es*pon*tâ*ne.o \xmark & es*pon*tâ*neo \cmark \\
+espúrio & es*pú*ri.o \xmark & es*pú*rio \cmark \\
+esquadria & es*qua*dri*a \cmark & es*qua*dri-a \xmark \\
 esquálido & es-quá*li*do \xmark & es*quá*li*do \cmark \\
+esquizofrenia & es*qui*zo*fre*ni*a \cmark & es*qui*zo*fre*ni-a \xmark \\
+essência & es*sên*ci.a \xmark & es*sên*cia \cmark \\
+estacaria & es*ta*ca*ri*a \cmark & es*ta*ca*ri-a \xmark \\
+estacionário & es*ta*ci*o*ná*ri.o \xmark & es*ta*ci*o*ná*rio \cmark \\
+estadia & es*ta*di*a \cmark & es*ta*di-a \xmark \\
+estádio & es*tá*di.o \xmark & es*tá*dio \cmark \\
+estágio & es*tá*gi.o \xmark & es*tá*gio \cmark \\
+estamparia & es*tam*pa*ri*a \cmark & es*tam*pa*ri-a \xmark \\
+estância & es*tân*ci.a \xmark & es*tân*cia \cmark \\
+estátua & es*tá*tu.a \xmark & es*tá*tua \cmark \\
+esteárico & es*te-á*ri*co \xmark & es*te*á*ri*co \cmark \\
+esteatorreia & es*te*a*tor*rei*a \cmark & es*te*a*tor*rei-a \xmark \\
+esteio & es*tei*o \cmark & es*tei-o \xmark \\
+estelionatário & es*te*li*o*na*tá*ri.o \xmark & es*te*li*o*na*tá*rio \cmark \\
+estenografia & es*te*no*gra*fi*a \cmark & es*te*no*gra*fi-a \xmark \\
+estequiometria & es*te*qui*o*me*tri*a \cmark & es*te*qui*o*me*tri-a \xmark \\
+estéreo & es*té*re.o \xmark & es*té*reo \cmark \\
+estereótipo & es*te*re-ó*ti*po \xmark & es*te*re*ó*ti*po \cmark \\
+estígio & es*tí*gi.o \xmark & es*tí*gio \cmark \\
+estio & es*ti*o \cmark & es*ti-o \xmark \\
+estipêndio & es*ti*pên*di.o \xmark & es*ti*pên*dio \cmark \\
+estômago & es-tô*ma*go \xmark & es*tô*ma*go \cmark \\
+estomatologia & es*to*ma*to*lo*gi*a \cmark & es*to*ma*to*lo*gi-a \xmark \\
+estratégia & es*tra*té*gi.a \xmark & es*tra*té*gia \cmark \\
+estratigrafia & es*tra*ti*gra*fi*a \cmark & es*tra*ti*gra*fi-a \xmark \\
+estrebaria & es*tre*ba*ri*a \cmark & es*tre*ba*ri-a \xmark \\
+estreia & es*trei*a \cmark & es*trei-a \xmark \\
+estria & es*tri*a \cmark & es*tri-a \xmark \\
+estroboscópio & es*tro*bos*có*pi.o \xmark & es*tro*bos*có*pio \cmark \\
+estrôncio & es*trôn*ci.o \xmark & es*trôn*cio \cmark \\
+estuário & es*tu-á*ri.o \xmark & es*tu*á*rio \cmark \\
+estúdio & es*tú*di.o \xmark & es*tú*dio \cmark \\
+estultícia & es*tul*tí*ci.a \xmark & es*tul*tí*cia \cmark \\
+estúrdia & es*túr*di.a \xmark & es*túr*dia \cmark \\
 esvair & es*va-ir \xmark & es*va*ir \cmark \\
+etéreo & e*té*re.o \xmark & e*té*reo \cmark \\
+etimologia & e*ti*mo*lo*gi*a \cmark & e*ti*mo*lo*gi-a \xmark \\
+etiologia & e*ti*o*lo*gi*a \cmark & e*ti*o*lo*gi-a \xmark \\
+etíope & e*tí-o*pe \xmark & e*tí*o*pe \cmark \\
+etnia & et*ni*a \cmark & et*ni-a \xmark \\
+etnografia & et*no*gra*fi*a \cmark & et*no*gra*fi-a \xmark \\
+etnologia & et*no*lo*gi*a \cmark & et*no*lo*gi-a \xmark \\
+etnomusicologia & et*no*mu*si*co*lo*gi*a \cmark & et*no*mu*si*co*lo*gi-a \xmark \\
+etnônimo & et-nô*ni*mo \xmark & et*nô*ni*mo \cmark \\
+etologia & e*to*lo*gi*a \cmark & e*to*lo*gi-a \xmark \\
+eucariótico & eu*ca*ri-ó*ti*co \xmark & eu*ca*ri*ó*ti*co \cmark \\
+eucaristia & eu*ca*ris*ti*a \cmark & eu*ca*ris*ti-a \xmark \\
+eufonia & eu*fo*ni*a \cmark & eu*fo*ni-a \xmark \\
+euforia & eu*fo*ri*a \cmark & eu*fo*ri-a \xmark \\
+eugenia & eu*ge*ni*a \cmark & eu*ge*ni-a \xmark \\
+eulalia & eu*la*li*a \cmark & eu*la*li-a \xmark \\
+eurasiático & eu*ra*si-á*ti*co \xmark & eu*ra*si*á*ti*co \cmark \\
+európio & eu*ró*pi.o \xmark & eu*ró*pio \cmark \\
+eustasia & eus*ta*si*a \cmark & eus*ta*si-a \xmark \\
+eutanásia & eu*ta*ná*si.a \xmark & eu*ta*ná*sia \cmark \\
+evidência & e*vi*dên*ci.a \xmark & e*vi*dên*cia \cmark \\
+evoé & e*vo-é \xmark & e*vo*é \cmark \\
+evoluído & e*vo*lu-í*do \xmark & e*vo*lu*í*do \cmark \\
+evoluir & e*vo*lu-ir \xmark & e*vo*lu*ir \cmark \\
+excelência & ex*ce*lên*ci.a \xmark & ex*ce*lên*cia \cmark \\
+excluído & ex*clu-í*do \xmark & ex*clu*í*do \cmark \\
+excluir & ex*clu-ir \xmark & ex*clu*ir \cmark \\
+excrescência & ex*cres*cên*ci.a \xmark & ex*cres*cên*cia \cmark \\
+exéquias & e*xé*qui.as \xmark & e*xé*qui.as \xmark \\
+exequível & e*xe-quí*vel \xmark & e*xe*quí*vel \cmark \\
+exigência & e*xi*gên*ci.a \xmark & e*xi*gên*cia \cmark \\
+exímio & e*xí*mi.o \xmark & e*xí*mio \cmark \\
+existência & e*xis*tên*ci.a \xmark & e*xis*tên*cia \cmark \\
+exoftalmia & e*xof*tal*mi*a \cmark & e*xof*tal*mi-a \xmark \\
+exogamia & e*xo*ga*mi*a \cmark & e*xo*ga*mi-a \xmark \\
+exórdio & e*xór*di.o \xmark & e*xór*dio \cmark \\
+expedicionário & ex*pe*di*ci*o*ná*ri.o \xmark & ex*pe*di*ci*o*ná*rio \cmark \\
+experiência & ex*pe*ri*ên*ci.a \xmark & ex*pe*ri*ên*cia \cmark \\
+extermínio & ex*ter*mí*ni.o \xmark & ex*ter*mí*nio \cmark \\
+extrair & ex*tra-ir \xmark & ex*tra*ir \cmark \\
+extraordinário & ex*tra*or*di*ná*ri.o \xmark & ex*tra*or*di*ná*rio \cmark \\
+extravio & ex*tra*vi*o \cmark & ex*tra*vi-o \xmark \\
+exuberância & e*xu*be*rân*ci.a \xmark & e*xu*be*rân*cia \cmark \\
+factício & fac*tí*ci.o \xmark & fac*tí*cio \cmark \\
+faia & fai*a \cmark & fai-a \xmark \\
+faim & fa-im \xmark & fa-im \xmark \\
+faísca & fa-ís*ca \xmark & fa*ís*ca \cmark \\
+falácia & fa*lá*ci.a \xmark & fa*lá*cia \cmark \\
+falcatrua & fal*ca*tru*a \cmark & fal*ca*tru-a \xmark \\
+falência & fa*lên*ci.a \xmark & fa*lên*cia \cmark \\
+falésia & fa*lé*si.a \xmark & fa*lé*sia \cmark \\
+fancaria & fan*ca*ri*a \cmark & fan*ca*ri-a \xmark \\
+fantasia & fan*ta*si*a \cmark & fan*ta*si-a \xmark \\
+fantasmagoria & fan*tas*ma*go*ri*a \cmark & fan*tas*ma*go*ri-a \xmark \\
+faraó & fa*ra-ó \xmark & fa*ra*ó \cmark \\
+faríngeo & fa*rín*ge.o \xmark & fa*rín*geo \cmark \\
 farisaísmo & fa*ri*sa-ís*mo \xmark & fa*ri*sa*ís*mo \cmark \\
-fiduciário & fi*du*ci-á*ri*o \xmark & fi*du*ci*á*ri*o \cmark \\
+farmácia & far*má*ci.a \xmark & far*má*cia \cmark \\
+farmacopeia & far*ma*co*pei*a \cmark & far*ma*co*pei-a \xmark \\
+farmacoterapia & far*ma*co*te*ra*pi*a \cmark & far*ma*co*te*ra*pi-a \xmark \\
+fascínio & fas*cí*ni.o \xmark & fas*cí*nio \cmark \\
+fastígio & fas*tí*gi.o \xmark & fas*tí*gio \cmark \\
+fastio & fas*ti*o \cmark & fas*ti-o \xmark \\
+fatia & fa*ti*a \cmark & fa*ti-a \xmark \\
+faúlha & fa-ú*lha \xmark & fa*ú*lha \cmark \\
+fazendário & fa*zen*dá*ri.o \xmark & fa*zen*dá*rio \cmark \\
+feérico & fe-é*ri*co \xmark & fe*é*ri*co \cmark \\
+feio & fei*o \cmark & fei-o \xmark \\
+feitiçaria & fei*ti*ça*ri*a \cmark & fei*ti*ça*ri-a \xmark \\
+feitio & fei*ti*o \cmark & fei*ti-o \xmark \\
+feitoria & fei*to*ri*a \cmark & fei*to*ri-a \xmark \\
+feiura & fei-u*ra \xmark & fei*u*ra \cmark \\
+felídeo & fe*lí*de.o \xmark & fe*lí*deo \cmark \\
+felonia & fe*lo*ni*a \cmark & fe*lo*ni-a \xmark \\
+fêmea & fê*me.a \xmark & fê*mea \cmark \\
+fenício & fe*ní*ci.o \xmark & fe*ní*cio \cmark \\
+fenologia & fe*no*lo*gi*a \cmark & fe*no*lo*gi-a \xmark \\
+fenômeno & fe-nô*me*no \xmark & fe*nô*me*no \cmark \\
+fenomenologia & fe*no*me*no*lo*gi*a \cmark & fe*no*me*no*lo*gi-a \xmark \\
+féria & fé*ri.a \xmark & fé*ria \cmark \\
+férmio & fér*mi.o \xmark & fér*mio \cmark \\
+ferraria & fer*ra*ri*a \cmark & fer*ra*ri-a \xmark \\
+ferrovia & fer*ro*vi*a \cmark & fer*ro*vi-a \xmark \\
+fiável & fi-á*vel \xmark & fi*á*vel \cmark \\
+fibromialgia & fi*bro*mi*al*gi*a \cmark & fi*bro*mi*al*gi-a \xmark \\
+fichário & fi*chá*ri.o \xmark & fi*chá*rio \cmark \\
+ficologia & fi*co*lo*gi*a \cmark & fi*co*lo*gi-a \xmark \\
+fictício & fic*tí*ci.o \xmark & fic*tí*cio \cmark \\
+fideísmo & fi*de-ís*mo \xmark & fi*de*ís*mo \cmark \\
+fidúcia & fi*dú*ci.a \xmark & fi*dú*cia \cmark \\
+fiduciário & fi*du*ci-á*ri.o \xmark & fi*du*ci*á*rio \cmark \\
+filantropia & fi*lan*tro*pi*a \cmark & fi*lan*tro*pi-a \xmark \\
+filarmônica & fi*lar-mô*ni*ca \xmark & fi*lar*mô*ni*ca \cmark \\
 filarmônico & fi*lar-mô*ni*co \xmark & fi*lar*mô*ni*co \cmark \\
+filatelia & fi*la*te*li*a \cmark & fi*la*te*li-a \xmark \\
+filáucia & fi*láu*ci.a \xmark & fi*láu*cia \cmark \\
+filmografia & fil*mo*gra*fi*a \cmark & fil*mo*gra*fi-a \xmark \\
+filogenia & fi*lo*ge*ni*a \cmark & fi*lo*ge*ni-a \xmark \\
+filologia & fi*lo*lo*gi*a \cmark & fi*lo*lo*gi-a \xmark \\
+filosofia & fi*lo*so*fi*a \cmark & fi*lo*so*fi-a \xmark \\
+fímbria & fím*bri.a \xmark & fím*bria \cmark \\
 financiável & fi*nan*ci-á*vel \xmark & fi*nan*ci*á*vel \cmark \\
+finório & fi*nó*ri.o \xmark & fi*nó*rio \cmark \\
+fio & fi*o \cmark & fi-o \xmark \\
+fisiocracia & fi*si*o*cra*ci*a \cmark & fi*si*o*cra*ci-a \xmark \\
+fisiologia & fi*si*o*lo*gi*a \cmark & fi*si*o*lo*gi-a \xmark \\
+fisiólogo & fi*si-ó*lo*go \xmark & fi*si*ó*lo*go \cmark \\
+fisionomia & fi*si*o*no*mi*a \cmark & fi*si*o*no*mi-a \xmark \\
+fisioterapia & fi*si*o*te*ra*pi*a \cmark & fi*si*o*te*ra*pi-a \xmark \\
+fitopatologia & fi*to*pa*to*lo*gi*a \cmark & fi*to*pa*to*lo*gi-a \xmark \\
+fitotecnia & fi*to*tec*ni*a \cmark & fi*to*tec*ni-a \xmark \\
+fiúza & fi-ú*za \xmark & fi*ú*za \cmark \\
+flatulência & fla*tu*lên*ci.a \xmark & fla*tu*lên*cia \cmark \\
+floreio & flo*rei*o \cmark & flo*rei-o \xmark \\
+florilégio & flo*ri*lé*gi.o \xmark & flo*ri*lé*gio \cmark \\
+fluência & flu-ên*ci.a \xmark & flu*ên*cia \cmark \\
+fluidez & flu-i*dez \xmark & flu-i*dez \xmark \\
+fluídico & flu-í*di*co \xmark & flu*í*di*co \cmark \\
+fluir & flu-ir \xmark & flu*ir \cmark \\
+fluorescência & flu*o*res*cên*ci.a \xmark & flu*o*res*cên*cia \cmark \\
+flúor & flú-or \xmark & flú*or \cmark \\
+fobia & fo*bi*a \cmark & fo*bi-a \xmark \\
+folheio & fo*lhei*o \cmark & fo*lhei-o \xmark \\
+folia & fo*li*a \cmark & fo*li-a \xmark \\
+folião & fo*li-ão \xmark & fo*li*ão \cmark \\
+fonografia & fo*no*gra*fi*a \cmark & fo*no*gra*fi-a \xmark \\
+fonologia & fo*no*lo*gi*a \cmark & fo*no*lo*gi-a \xmark \\
+formaldeído & for*mal*de-í*do \xmark & for*mal*de*í*do \cmark \\
+formulário & for*mu*lá*ri.o \xmark & for*mu*lá*rio \cmark \\
+fosforescência & fos*fo*res*cên*ci.a \xmark & fos*fo*res*cên*cia \cmark \\
+fotocópia & fo*to*có*pi.a \xmark & fo*to*có*pia \cmark \\
+fotofobia & fo*to*fo*bi*a \cmark & fo*to*fo*bi-a \xmark \\
+fotogenia & fo*to*ge*ni*a \cmark & fo*to*ge*ni-a \xmark \\
+fotografia & fo*to*gra*fi*a \cmark & fo*to*gra*fi-a \xmark \\
+fotolitografia & fo*to*li*to*gra*fi*a \cmark & fo*to*li*to*gra*fi-a \xmark \\
+fotometria & fo*to*me*tri*a \cmark & fo*to*me*tri-a \xmark \\
+fotoquímica & fo*to-quí*mi*ca \xmark & fo*to*quí*mi*ca \cmark \\
+fotoquímico & fo*to-quí*mi*co \xmark & fo*to*quí*mi*co \cmark \\
+fototerapia & fo*to*te*ra*pi*a \cmark & fo*to*te*ra*pi-a \xmark \\
+fototipia & fo*to*ti*pi*a \cmark & fo*to*ti*pi-a \xmark \\
+fragrância & fra*grân*ci.a \xmark & fra*grân*cia \cmark \\
+frâncio & frân*ci.o \xmark & frân*cio \cmark \\
+francofonia & fran*co*fo*ni*a \cmark & fran*co*fo*ni-a \xmark \\
+franquia & fran*qui*a \cmark & fran*qui-a \xmark \\
+fraseologia & fra*se*o*lo*gi*a \cmark & fra*se*o*lo*gi-a \xmark \\
+fratricídio & fra*tri*cí*di.o \xmark & fra*tri*cí*dio \cmark \\
+freático & fre-á*ti*co \xmark & fre*á*ti*co \cmark \\
+freguesia & fre*gue*si*a \cmark & fre*gue*si-a \xmark \\
+freio & frei*o \cmark & frei-o \xmark \\
+freiria & frei*ri*a \cmark & frei*ri-a \xmark \\
+frenologia & fre*no*lo*gi*a \cmark & fre*no*lo*gi-a \xmark \\
+frequência & fre-quên*ci.a \xmark & fre*quên*cia \cmark \\
+fria & fri*a \cmark & fri-a \xmark \\
+friável & fri-á*vel \xmark & fri*á*vel \cmark \\
+frio & fri*o \cmark & fri-o \xmark \\
+frísio & frí*si.o \xmark & frí*sio \cmark \\
+frontaria & fron*ta*ri*a \cmark & fron*ta*ri-a \xmark \\
+frontispício & fron*tis*pí*ci.o \xmark & fron*tis*pí*cio \cmark \\
+fruição & fru-i*ção \xmark & fru*i*ção \cmark \\
 fruir & fru-ir \xmark & fru*ir \cmark \\
+frutaria & fru*ta*ri*a \cmark & fru*ta*ri-a \xmark \\
+fuá & fu-á \xmark & fu*á \cmark \\
+fúfio & fú*fi.o \xmark & fú*fio \cmark \\
+fugidio & fu*gi*di*o \cmark & fu*gi*di-o \xmark \\
+fuinha & fu-i*nha \xmark & fu*i*nha \cmark \\
+funcionário & fun*ci*o*ná*ri.o \xmark & fun*ci*o*ná*rio \cmark \\
+funerária & fu*ne*rá*ri.a \xmark & fu*ne*rá*ria \cmark \\
+funerário & fu*ne*rá*ri.o \xmark & fu*ne*rá*rio \cmark \\
+funéreo & fu*né*re.o \xmark & fu*né*reo \cmark \\
+funilaria & fu*ni*la*ri*a \cmark & fu*ni*la*ri-a \xmark \\
+fúria & fú*ri.a \xmark & fú*ria \cmark \\
+futevôlei & fu*te-vô*lei \xmark & fu*te*vô*lei \cmark \\
+futurologia & fu*tu*ro*lo*gi*a \cmark & fu*tu*ro*lo*gi-a \xmark \\
+fuzilaria & fu*zi*la*ri*a \cmark & fu*zi*la*ri-a \xmark \\
 fuzuê & fu*zu-ê \xmark & fu*zu*ê \cmark \\
-geômetra & ge-ô*me*tra \xmark & ge*ô*me*tra \cmark \\
+gabião & ga*bi-ão \xmark & ga*bi*ão \cmark \\
+gadolínio & ga*do*lí*ni.o \xmark & ga*do*lí*nio \cmark \\
+gaélico & ga-é*li*co \xmark & ga*é*li*co \cmark \\
+gaio & gai*o \cmark & gai-o \xmark \\
+galanteio & ga*lan*tei*o \cmark & ga*lan*tei-o \xmark \\
+galeão & ga*le-ão \xmark & ga*le*ão \cmark \\
+galeria & ga*le*ri*a \cmark & ga*le*ri-a \xmark \\
+galhardia & ga*lhar*di*a \cmark & ga*lhar*di-a \xmark \\
+galináceo & ga*li*ná*ce.o \xmark & ga*li*ná*ceo \cmark \\
+gálio & gá*li.o \xmark & gá*lio \cmark \\
+gâmbia & gâm*bi.a \xmark & gâm*bia \cmark \\
+gamboa & gam*bo*a \cmark & gam*bo-a \xmark \\
+ganância & ga*nân*ci.a \xmark & ga*nân*cia \cmark \\
+gandaia & gan*dai*a \cmark & gan*dai-a \xmark \\
+gânglio & gân*gli.o \xmark & gân*glio \cmark \\
+garantia & ga*ran*ti*a \cmark & ga*ran*ti-a \xmark \\
+garoa & ga*ro*a \cmark & ga*ro-a \xmark \\
+gastrectomia & gas*trec*to*mi*a \cmark & gas*trec*to*mi-a \xmark \\
+gastrointestinal & gas*tro-in*tes*ti*nal \xmark & gas*tro*in*tes*ti*nal \cmark \\
+gastronomia & gas*tro*no*mi*a \cmark & gas*tro*no*mi-a \xmark \\
+gastronômico & gas*tro-nô*mi*co \xmark & gas*tro*nô*mi*co \cmark \\
+gaúcho & ga-ú*cho \xmark & ga*ú*cho \cmark \\
+gaudério & gau*dé*ri.o \xmark & gau*dé*rio \cmark \\
+gáudio & gáu*di.o \xmark & gáu*dio \cmark \\
+gávea & gá*ve.a \xmark & gá*vea \cmark \\
+gavião & ga*vi-ão \xmark & ga*vi*ão \cmark \\
+gazua & ga*zu*a \cmark & ga*zu-a \xmark \\
+geio & gei*o \cmark & gei-o \xmark \\
+geleia & ge*lei*a \cmark & ge*lei-a \xmark \\
+gelosia & ge*lo*si*a \cmark & ge*lo*si-a \xmark \\
+gemologia & ge*mo*lo*gi*a \cmark & ge*mo*lo*gi-a \xmark \\
+gendarmaria & gen*dar*ma*ri*a \cmark & gen*dar*ma*ri-a \xmark \\
+genealogia & ge*ne*a*lo*gi*a \cmark & ge*ne*a*lo*gi-a \xmark \\
+genitália & ge*ni*tá*li.a \xmark & ge*ni*tá*lia \cmark \\
+geniturinário & ge*ni*tu*ri*ná*ri.o \xmark & ge*ni*tu*ri*ná*rio \cmark \\
+genocídio & ge*no*cí*di.o \xmark & ge*no*cí*dio \cmark \\
+gentio & gen*ti*o \cmark & gen*ti-o \xmark \\
+genuflexório & ge*nu*fle*xó*ri.o \xmark & ge*nu*fle*xó*rio \cmark \\
+genuíno & ge*nu-í*no \xmark & ge*nu*í*no \cmark \\
+geodesia & ge*o*de*si*a \cmark & ge*o*de*si-a \xmark \\
+geografia & ge*o*gra*fi*a \cmark & ge*o*gra*fi-a \xmark \\
+geógrafo & ge-ó*gra*fo \xmark & ge*ó*gra*fo \cmark \\
+geologia & ge*o*lo*gi*a \cmark & ge*o*lo*gi-a \xmark \\
+geólogo & ge-ó*lo*go \xmark & ge*ó*lo*go \cmark \\
+geometria & ge*o*me*tri*a \cmark & ge*o*me*tri-a \xmark \\
+gerânio & ge*râ*ni.o \xmark & ge*râ*nio \cmark \\
+gerência & ge*rên*ci.a \xmark & ge*rên*cia \cmark \\
+geriatria & ge*ri*a*tri*a \cmark & ge*ri*a*tri-a \xmark \\
+germania & ger*ma*ni*a \cmark & ger*ma*ni-a \xmark \\
+germânio & ger*mâ*ni.o \xmark & ger*mâ*nio \cmark \\
+gerontocracia & ge*ron*to*cra*ci*a \cmark & ge*ron*to*cra*ci-a \xmark \\
+gerúndio & ge*rún*di.o \xmark & ge*rún*dio \cmark \\
+gigolô & gi*go-lô \xmark & gi*go*lô \cmark \\
+ginásio & gi*ná*si.o \xmark & gi*ná*sio \cmark \\
+ginecologia & gi*ne*co*lo*gi*a \cmark & gi*ne*co*lo*gi-a \xmark \\
+ginecomastia & gi*ne*co*mas*ti*a \cmark & gi*ne*co*mas*ti-a \xmark \\
+gio & gi*o \cmark & gi-o \xmark \\
+giratório & gi*ra*tó*ri.o \xmark & gi*ra*tó*rio \cmark \\
+gíria & gí*ri.a \xmark & gí*ria \cmark \\
+giroscópio & gi*ros*có*pi.o \xmark & gi*ros*có*pio \cmark \\
+glaciário & gla*ci-á*ri.o \xmark & gla*ci*á*rio \cmark \\
+gládio & glá*di.o \xmark & glá*dio \cmark \\
+gladíolo & gla*dí-o*lo \xmark & gla*dí*o*lo \cmark \\
+gláucia & gláu*ci.a \xmark & gláu*cia \cmark \\
+glia & gli*a \cmark & gli-a \xmark \\
+glicemia & gli*ce*mi*a \cmark & gli*ce*mi-a \xmark \\
+glicínia & gli*cí*ni.a \xmark & gli*cí*nia \cmark \\
+glicoproteína & gli*co*pro*te-í*na \xmark & gli*co*pro*te*í*na \cmark \\
+glória & gló*ri.a \xmark & gló*ria \cmark \\
+glossário & glos*sá*ri.o \xmark & glos*sá*rio \cmark \\
+glossolalia & glos*so*la*li*a \cmark & glos*so*la*li-a \xmark \\
+glúteo & glú*te.o \xmark & glú*teo \cmark \\
+glutonaria & glu*to*na*ri*a \cmark & glu*to*na*ri-a \xmark \\
+gnaisse & g.nais*se \xmark & g.nais*se \xmark \\
+gnomo & g.no*mo \xmark & gno*mo \cmark \\
 gnose & g.no*se \xmark & gno*se \cmark \\
+gnosiologia & g.no*si*o*lo*gi*a \xmark & gno*si*o*lo*gi-a \xmark \\
+gnosticismo & g.nos*ti*cis*mo \xmark & gnos*ti*cis*mo \cmark \\
+gnóstico & g.nós*ti*co \xmark & gnós*ti*co \cmark \\
+gonorreia & go*nor*rei*a \cmark & go*nor*rei-a \xmark \\
+gorjeio & gor*jei*o \cmark & gor*jei-o \xmark \\
+grafia & gra*fi*a \cmark & gra*fi-a \xmark \\
+grafologia & gra*fo*lo*gi*a \cmark & gra*fo*lo*gi-a \xmark \\
+grafomaníaco & gra*fo*ma*ní-a*co \xmark & gra*fo*ma*ní*a*co \cmark \\
+gramatologia & gra*ma*to*lo*gi*a \cmark & gra*ma*to*lo*gi-a \xmark \\
+granulometria & gra*nu*lo*me*tri*a \cmark & gra*nu*lo*me*tri-a \xmark \\
+grapiúna & gra*pi-ú*na \xmark & gra*pi*ú*na \cmark \\
+graúdo & gra-ú*do \xmark & gra*ú*do \cmark \\
+graúna & gra-ú*na \xmark & gra*ú*na \cmark \\
+gregário & gre*gá*ri.o \xmark & gre*gá*rio \cmark \\
+gregório & gre*gó*ri.o \xmark & gre*gó*rio \cmark \\
+gritaria & gri*ta*ri*a \cmark & gri*ta*ri-a \xmark \\
+grosseria & gros*se*ri*a \cmark & gros*se*ri-a \xmark \\
+grua & gru*a \cmark & gru-a \xmark \\
+guardião & guar*di-ão \xmark & guar*di*ão \cmark \\
+guia & gui*a \cmark & gui-a \xmark \\
+guião & gui-ão \xmark & gui*ão \cmark \\
+guria & gu*ri*a \cmark & gu*ri-a \xmark \\
+hagiógrafo & ha*gi-ó*gra*fo \xmark & ha*gi*ó*gra*fo \cmark \\
+hamburgueria & ham*bur*gue*ri*a \cmark & ham*bur*gue*ri-a \xmark \\
+hanseático & han*se-á*ti*co \xmark & han*se*á*ti*co \cmark \\
+hanseníase & han*se*ní-a*se \xmark & han*se*ní*a*se \cmark \\
+harmonia & har*mo*ni*a \cmark & har*mo*ni-a \xmark \\
+harmônica & har-mô*ni*ca \xmark & har*mô*ni*ca \cmark \\
+harmônico & har-mô*ni*co \xmark & har*mô*ni*co \cmark \\
+harpia & har*pi*a \cmark & har*pi-a \xmark \\
+hebdomadário & heb*do*ma*dá*ri.o \xmark & heb*do*ma*dá*rio \cmark \\
+hebraísmo & he*bra-ís*mo \xmark & he*bra*ís*mo \cmark \\
+hebraísta & he*bra-ís*ta \xmark & he*bra*ís*ta \cmark \\
+hegemonia & he*ge*mo*ni*a \cmark & he*ge*mo*ni-a \xmark \\
+hegemônico & he*ge-mô*ni*co \xmark & he*ge*mô*ni*co \cmark \\
+helíaco & he*lí-a*co \xmark & he*lí*a*co \cmark \\
+heliógrafo & he*li-ó*gra*fo \xmark & he*li*ó*gra*fo \cmark \\
+hélio & hé*li.o \xmark & hé*lio \cmark \\
+helvécio & hel*vé*ci*o \cmark & hel*vé*ci-o \xmark \\
+hematologia & he*ma*to*lo*gi*a \cmark & he*ma*to*lo*gi-a \xmark \\
+hemeralopia & he*me*ra*lo*pi*a \cmark & he*me*ra*lo*pi-a \xmark \\
+hemiparesia & he*mi*pa*re*si*a \cmark & he*mi*pa*re*si-a \xmark \\
+hemiplegia & he*mi*ple*gi*a \cmark & he*mi*ple*gi-a \xmark \\
+hemisfério & he*mis*fé*ri.o \xmark & he*mis*fé*rio \cmark \\
+hemistíquio & he*mis*tí*qui.o \xmark & he*mis*tí*quio \cmark \\
+hemodiálise & he*mo*di-á*li*se \xmark & he*mo*di*á*li*se \cmark \\
+hemofilia & he*mo*fi*li*a \cmark & he*mo*fi*li-a \xmark \\
+hemorragia & he*mor*ra*gi*a \cmark & he*mor*ra*gi-a \xmark \\
+hemostasia & he*mos*ta*si*a \cmark & he*mos*ta*si-a \xmark \\
+hemoterapia & he*mo*te*ra*pi*a \cmark & he*mo*te*ra*pi-a \xmark \\
+hepatologia & he*pa*to*lo*gi*a \cmark & he*pa*to*lo*gi-a \xmark \\
+hepatomegalia & he*pa*to*me*ga*li*a \cmark & he*pa*to*me*ga*li-a \xmark \\
+hepatopatia & he*pa*to*pa*ti*a \cmark & he*pa*to*pa*ti-a \xmark \\
+heptacampeão & hep*ta*cam*pe-ão \xmark & hep*ta*cam*pe*ão \cmark \\
+herbáceo & her*bá*ce.o \xmark & her*bá*ceo \cmark \\
+hercúleo & her*cú*le.o \xmark & her*cú*leo \cmark \\
+hereditário & he*re*di*tá*ri.o \xmark & he*re*di*tá*rio \cmark \\
+heresia & he*re*si*a \cmark & he*re*si-a \xmark \\
+hermínio & her*mí*ni.o \xmark & her*mí*nio \cmark \\
+hérnia & hér*ni.a \xmark & hér*nia \cmark \\
+heroína & he*ro-í*na \xmark & he*ro*í*na \cmark \\
+heroísmo & he*ro-ís*mo \xmark & he*ro*ís*mo \cmark \\
+herpetologia & her*pe*to*lo*gi*a \cmark & her*pe*to*lo*gi-a \xmark \\
+heteria & he*te*ri*a \cmark & he*te*ri-a \xmark \\
+heteroátomo & he*te*ro-á*to*mo \xmark & he*te*ro*á*to*mo \cmark \\
+heterocromia & he*te*ro*cro*mi*a \cmark & he*te*ro*cro*mi-a \xmark \\
+heterodoxia & he*te*ro*do*xi*a \cmark & he*te*ro*do*xi-a \xmark \\
+heterofilia & he*te*ro*fi*li*a \cmark & he*te*ro*fi*li-a \xmark \\
+heterologia & he*te*ro*lo*gi*a \cmark & he*te*ro*lo*gi-a \xmark \\
+heteronímia & he*te*ro*ní*mi.a \xmark & he*te*ro*ní*mia \cmark \\
+heterônimo & he*te-rô*ni*mo \xmark & he*te*rô*ni*mo \cmark \\
+heteronomia & he*te*ro*no*mi*a \cmark & he*te*ro*no*mi-a \xmark \\
+hexacampeão & he*xa*cam*pe-ão \xmark & he*xa*cam*pe*ão \cmark \\
+hidroavião & hi*dro*a*vi-ão \xmark & hi*dro*a*vi*ão \cmark \\
+hidrocefalia & hi*dro*ce*fa*li*a \cmark & hi*dro*ce*fa*li-a \xmark \\
+hidrofobia & hi*dro*fo*bi*a \cmark & hi*dro*fo*bi-a \xmark \\
+hidrologia & hi*dro*lo*gi*a \cmark & hi*dro*lo*gi-a \xmark \\
+hidromancia & hi*dro*man*ci*a \cmark & hi*dro*man*ci-a \xmark \\
+hidropisia & hi*dro*pi*si*a \cmark & hi*dro*pi*si-a \xmark \\
+hidropônico & hi*dro-pô*ni*co \xmark & hi*dro*pô*ni*co \cmark \\
+hidroterapia & hi*dro*te*ra*pi*a \cmark & hi*dro*te*ra*pi-a \xmark \\
+hidrovia & hi*dro*vi*a \cmark & hi*dro*vi-a \xmark \\
+hidroviário & hi*dro*vi-á*ri.o \xmark & hi*dro*vi*á*rio \cmark \\
+hierarquia & hi*e*rar*qui*a \cmark & hi*e*rar*qui-a \xmark \\
+hilária & hi*lá*ri.a \xmark & hi*lá*ria \cmark \\
+hilário & hi*lá*ri.o \xmark & hi*lá*rio \cmark \\
+hinário & hi*ná*ri.o \xmark & hi*ná*rio \cmark \\
+hinduísmo & hin*du-ís*mo \xmark & hin*du*ís*mo \cmark \\
+hinologia & hi*no*lo*gi*a \cmark & hi*no*lo*gi-a \xmark \\
+hiperalgesia & hi*pe*ral*ge*si*a \cmark & hi*pe*ral*ge*si-a \xmark \\
+hiperbóreo & hi*per*bó*re.o \xmark & hi*per*bó*reo \cmark \\
+hipercalcemia & hi*per*cal*ce*mi*a \cmark & hi*per*cal*ce*mi-a \xmark \\
+hiperdulia & hi*per*du*li*a \cmark & hi*per*du*li-a \xmark \\
+hiperemia & hi*pe*re*mi*a \cmark & hi*pe*re*mi-a \xmark \\
+hipertermia & hi*per*ter*mi*a \cmark & hi*per*ter*mi-a \xmark \\
+hipertonia & hi*per*to*ni*a \cmark & hi*per*to*ni-a \xmark \\
+hipertrofia & hi*per*tro*fi*a \cmark & hi*per*tro*fi-a \xmark \\
+hipocalcemia & hi*po*cal*ce*mi*a \cmark & hi*po*cal*ce*mi-a \xmark \\
+hipocalemia & hi*po*ca*le*mi*a \cmark & hi*po*ca*le*mi-a \xmark \\
+hipocondríaco & hi*po*con*drí-a*co \xmark & hi*po*con*drí*a*co \cmark \\
+hipocondria & hi*po*con*dri*a \cmark & hi*po*con*dri-a \xmark \\
+hipocrisia & hi*po*cri*si*a \cmark & hi*po*cri*si-a \xmark \\
+hipoglicemia & hi*po*gli*ce*mi*a \cmark & hi*po*gli*ce*mi-a \xmark \\
+hipônimo & hi-pô*ni*mo \xmark & hi*pô*ni*mo \cmark \\
+hipoplasia & hi*po*pla*si*a \cmark & hi*po*pla*si-a \xmark \\
+hipotermia & hi*po*ter*mi*a \cmark & hi*po*ter*mi-a \xmark \\
+hipotonia & hi*po*to*ni*a \cmark & hi*po*to*ni-a \xmark \\
+hipotrofia & hi*po*tro*fi*a \cmark & hi*po*tro*fi-a \xmark \\
+hipoxemia & hi*po*xe*mi*a \cmark & hi*po*xe*mi-a \xmark \\
+histerectomia & his*te*rec*to*mi*a \cmark & his*te*rec*to*mi-a \xmark \\
+histeria & his*te*ri*a \cmark & his*te*ri-a \xmark \\
+histeroscopia & his*te*ros*co*pi*a \cmark & his*te*ros*co*pi-a \xmark \\
+histologia & his*to*lo*gi*a \cmark & his*to*lo*gi-a \xmark \\
+histopatologia & his*to*pa*to*lo*gi*a \cmark & his*to*pa*to*lo*gi-a \xmark \\
+histoquímica & his*to-quí*mi*ca \xmark & his*to*quí*mi*ca \cmark \\
+história & his*tó*ri.a \xmark & his*tó*ria \cmark \\
+historiografia & his*to*ri*o*gra*fi*a \cmark & his*to*ri*o*gra*fi-a \xmark \\
+hólmio & hól*mi.o \xmark & hól*mio \cmark \\
+holografia & ho*lo*gra*fi*a \cmark & ho*lo*gra*fi-a \xmark \\
+homeopatia & ho*me*o*pa*ti*a \cmark & ho*me*o*pa*ti-a \xmark \\
+homeostasia & ho*me*os*ta*si*a \cmark & ho*me*os*ta*si-a \xmark \\
+homicídio & ho*mi*cí*di.o \xmark & ho*mi*cí*dio \cmark \\
+homilia & ho*mi*li*a \cmark & ho*mi*li-a \xmark \\
+hominídeo & ho*mi*ní*de.o \xmark & ho*mi*ní*deo \cmark \\
+homofilia & ho*mo*fi*li*a \cmark & ho*mo*fi*li-a \xmark \\
+homofobia & ho*mo*fo*bi*a \cmark & ho*mo*fo*bi-a \xmark \\
+homofonia & ho*mo*fo*ni*a \cmark & ho*mo*fo*ni-a \xmark \\
+homografia & ho*mo*gra*fi*a \cmark & ho*mo*gra*fi-a \xmark \\
+homologia & ho*mo*lo*gi*a \cmark & ho*mo*lo*gi-a \xmark \\
+homonímia & ho*mo*ní*mi.a \xmark & ho*mo*ní*mia \cmark \\
+homônimo & ho-mô*ni*mo \xmark & ho*mô*ni*mo \cmark \\
+homoplasia & ho*mo*pla*si*a \cmark & ho*mo*pla*si-a \xmark \\
+homotetia & ho*mo*te*ti*a \cmark & ho*mo*te*ti-a \xmark \\
+horário & ho*rá*ri.o \xmark & ho*rá*rio \cmark \\
+hortênsia & hor*tên*si.a \xmark & hor*tên*sia \cmark \\
+hospedaria & hos*pe*da*ri*a \cmark & hos*pe*da*ri-a \xmark \\
+hospício & hos*pí*ci.o \xmark & hos*pí*cio \cmark \\
+hóstia & hós*ti.a \xmark & hós*tia \cmark \\
+hotelaria & ho*te*la*ri*a \cmark & ho*te*la*ri-a \xmark \\
+humanitário & hu*ma*ni*tá*ri.o \xmark & hu*ma*ni*tá*rio \cmark \\
+iconoclastia & i*co*no*clas*ti*a \cmark & i*co*no*clas*ti-a \xmark \\
+iconografia & i*co*no*gra*fi*a \cmark & i*co*no*gra*fi-a \xmark \\
+iconolatria & i*co*no*la*tri*a \cmark & i*co*no*la*tri-a \xmark \\
+iconologia & i*co*no*lo*gi*a \cmark & i*co*no*lo*gi-a \xmark \\
+icterícia & ic*te*rí*ci.a \xmark & ic*te*rí*cia \cmark \\
+ictiologia & ic*ti*o*lo*gi*a \cmark & ic*ti*o*lo*gi-a \xmark \\
+ictiólogo & ic*ti-ó*lo*go \xmark & ic*ti*ó*lo*go \cmark \\
+ideário & i*de-á*ri.o \xmark & i*de*á*rio \cmark \\
+ideia & i*dei*a \cmark & i*dei-a \xmark \\
+identitário & i*den*ti*tá*ri.o \xmark & i*den*ti*tá*rio \cmark \\
+ideologia & i*de*o*lo*gi*a \cmark & i*de*o*lo*gi-a \xmark \\
+ideólogo & i*de-ó*lo*go \xmark & i*de*ó*lo*go \cmark \\
+idílio & i*dí*li.o \xmark & i*dí*lio \cmark \\
+idiossincrasia & i*di*os*sin*cra*si*a \cmark & i*di*os*sin*cra*si-a \xmark \\
+idiotia & i*di*o*ti*a \cmark & i*di*o*ti-a \xmark \\
+idolatria & i*do*la*tri*a \cmark & i*do*la*tri-a \xmark \\
+ígneo & íg*ne.o \xmark & íg*neo \cmark \\
+ignorância & ig*no*rân*ci.a \xmark & ig*no*rân*cia \cmark \\
+igualitário & i*gua*li*tá*ri.o \xmark & i*gua*li*tá*rio \cmark \\
+iídiche & i-í*di*che \xmark & i*í*di*che \cmark \\
+íleo & í*le.o \xmark & í*leo \cmark \\
+ilhoa & i*lho*a \cmark & i*lho-a \xmark \\
+ilíaco & i*lí-a*co \xmark & i*lí*a*co \cmark \\
+ilíada & i*lí-a*da \xmark & i*lí*a*da \cmark \\
+iliteracia & i*li*te*ra*ci*a \cmark & i*li*te*ra*ci-a \xmark \\
+ilusório & i*lu*só*ri.o \xmark & i*lu*só*rio \cmark \\
+imaginária & i*ma*gi*ná*ri.a \xmark & i*ma*gi*ná*ria \cmark \\
+imaginário & i*ma*gi*ná*ri.o \xmark & i*ma*gi*ná*rio \cmark \\
+imbróglio & im*bró*gli.o \xmark & im*bró*glio \cmark \\
+imbuído & im*bu-í*do \xmark & im*bu*í*do \cmark \\
+imbuir & im*bu-ir \xmark & im*bu*ir \cmark \\
+iminência & i*mi*nên*ci.a \xmark & i*mi*nên*cia \cmark \\
+imobiliária & i*mo*bi*li-á*ri.a \xmark & i*mo*bi*li*á*ria \cmark \\
+imobiliário & i*mo*bi*li-á*ri.o \xmark & i*mo*bi*li*á*rio \cmark \\
+imodéstia & i*mo*dés*ti.a \xmark & i*mo*dés*tia \cmark \\
+impaciência & im*pa*ci*ên*ci.a \xmark & im*pa*ci*ên*cia \cmark \\
+impenitência & im*pe*ni*tên*ci.a \xmark & im*pe*ni*tên*cia \cmark \\
+imperdoável & im*per*do-á*vel \xmark & im*per*do*á*vel \cmark \\
+império & im*pé*ri.o \xmark & im*pé*rio \cmark \\
+impertinência & im*per*ti*nên*ci.a \xmark & im*per*ti*nên*cia \cmark \\
+ímpio & ím*pi.o \xmark & ím*pio \cmark \\
+implicância & im*pli*cân*ci.a \xmark & im*pli*cân*cia \cmark \\
+importância & im*por*tân*ci.a \xmark & im*por*tân*cia \cmark \\
+impotência & im*po*tên*ci.a \xmark & im*po*tên*cia \cmark \\
+imprevidência & im*pre*vi*dên*ci.a \xmark & im*pre*vi*dên*cia \cmark \\
+impronunciável & im*pro*nun*ci-á*vel \xmark & im*pro*nun*ci*á*vel \cmark \\
+impropério & im*pro*pé*ri.o \xmark & im*pro*pé*rio \cmark \\
+impróprio & im*pró*pri.o \xmark & im*pró*prio \cmark \\
+imprudência & im*pru*dên*ci.a \xmark & im*pru*dên*cia \cmark \\
+imunologia & i*mu*no*lo*gi*a \cmark & i*mu*no*lo*gi-a \xmark \\
+imunoterapia & i*mu*no*te*ra*pi*a \cmark & i*mu*no*te*ra*pi-a \xmark \\
+inadiável & i*na*di-á*vel \xmark & i*na*di*á*vel \cmark \\
+inapetência & i*na*pe*tên*ci.a \xmark & i*na*pe*tên*cia \cmark \\
+incandescência & in*can*des*cên*ci.a \xmark & in*can*des*cên*cia \cmark \\
+incendiário & in*cen*di-á*ri.o \xmark & in*cen*di*á*rio \cmark \\
+incêndio & in*cên*di.o \xmark & in*cên*dio \cmark \\
+incensário & in*cen*sá*ri.o \xmark & in*cen*sá*rio \cmark \\
+incidência & in*ci*dên*ci.a \xmark & in*ci*dên*cia \cmark \\
+inclemência & in*cle*mên*ci.a \xmark & in*cle*mên*cia \cmark \\
+incluir & in*clu-ir \xmark & in*clu*ir \cmark \\
+incômodo & in-cô*mo*do \xmark & in*cô*mo*do \cmark \\
+inconciliável & in*con*ci*li-á*vel \xmark & in*con*ci*li*á*vel \cmark \\
+inconfidência & in*con*fi*dên*ci.a \xmark & in*con*fi*dên*cia \cmark \\
+incongruência & in*con*gru-ên*ci.a \xmark & in*con*gru*ên*cia \cmark \\
+inconsciência & in*cons*ci*ên*ci.a \xmark & in*cons*ci*ên*cia \cmark \\
+inconsequência & in*con*se-quên*ci.a \xmark & in*con*se*quên*cia \cmark \\
+inconspícuo & in*cons*pí*cu.o \xmark & in*cons*pí*cuo \cmark \\
+inconstância & in*cons*tân*ci.a \xmark & in*cons*tân*cia \cmark \\
+incontinência & in*con*ti*nên*ci.a \xmark & in*con*ti*nên*cia \cmark \\
+inconveniência & in*con*ve*ni*ên*ci.a \xmark & in*con*ve*ni*ên*cia \cmark \\
+incumbência & in*cum*bên*ci.a \xmark & in*cum*bên*cia \cmark \\
+incúria & in*cú*ri.a \xmark & in*cú*ria \cmark \\
+indaiá & in*dai-á \xmark & in*dai*á \cmark \\
+indeiscente & in*de-is*cen*te \xmark & in*de-is*cen*te \xmark \\
+independência & in*de*pen*dên*ci.a \xmark & in*de*pen*dên*cia \cmark \\
+indício & in*dí*ci.o \xmark & in*dí*cio \cmark \\
+indigência & in*di*gên*ci.a \xmark & in*di*gên*cia \cmark \\
+índio & ín*di.o \xmark & ín*dio \cmark \\
+indolência & in*do*lên*ci.a \xmark & in*do*lên*cia \cmark \\
+indonésio & in*do*né*si.o \xmark & in*do*né*sio \cmark \\
+indumentária & in*du*men*tá*ri.a \xmark & in*du*men*tá*ria \cmark \\
+indústria & in*dús*tri.a \xmark & in*dús*tria \cmark \\
+inédia & i*né*di.a \xmark & i*né*dia \cmark \\
+ineficiência & i*ne*fi*ci*ên*ci.a \xmark & i*ne*fi*ci*ên*cia \cmark \\
+inegociável & i*ne*go*ci-á*vel \xmark & i*ne*go*ci*á*vel \cmark \\
+inequívoco & i*ne-quí*vo*co \xmark & i*ne*quí*vo*co \cmark \\
+inércia & i*nér*ci.a \xmark & i*nér*cia \cmark \\
+inexequível & i*ne*xe-quí*vel \xmark & i*ne*xe*quí*vel \cmark \\
+inexistência & i*ne*xis*tên*ci.a \xmark & i*ne*xis*tên*cia \cmark \\
+inexperiência & i*nex*pe*ri*ên*ci.a \xmark & i*nex*pe*ri*ên*cia \cmark \\
+infâmia & in*fâ*mi.a \xmark & in*fâ*mia \cmark \\
+infância & in*fân*ci.a \xmark & in*fân*cia \cmark \\
+infantaria & in*fan*ta*ri*a \cmark & in*fan*ta*ri-a \xmark \\
+infanticídio & in*fan*ti*cí*di.o \xmark & in*fan*ti*cí*dio \cmark \\
+inferência & in*fe*rên*ci.a \xmark & in*fe*rên*cia \cmark \\
+inflacionário & in*fla*ci*o*ná*ri.o \xmark & in*fla*ci*o*ná*rio \cmark \\
+inflamatório & in*fla*ma*tó*ri.o \xmark & in*fla*ma*tó*rio \cmark \\
+inflorescência & in*flo*res*cên*ci.a \xmark & in*flo*res*cên*cia \cmark \\
+influência & in*flu-ên*ci.a \xmark & in*flu*ên*cia \cmark \\
+influenciável & in*flu*en*ci-á*vel \xmark & in*flu*en*ci*á*vel \cmark \\
+influído & in*flu-í*do \xmark & in*flu*í*do \cmark \\
+influir & in*flu-ir \xmark & in*flu*ir \cmark \\
+infografia & in*fo*gra*fi*a \cmark & in*fo*gra*fi-a \xmark \\
+infortúnio & in*for*tú*ni.o \xmark & in*for*tú*nio \cmark \\
+infrutescência & in*fru*tes*cên*ci.a \xmark & in*fru*tes*cên*cia \cmark \\
+ingenuidade & in*ge*nu-i*da*de \xmark & in*ge*nu*i*da*de \cmark \\
+ingerência & in*ge*rên*ci.a \xmark & in*ge*rên*cia \cmark \\
+iniciático & i*ni*ci-á*ti*co \xmark & i*ni*ci*á*ti*co \cmark \\
+início & i*ní*ci.o \xmark & i*ní*cio \cmark \\
+injúria & in*jú*ri.a \xmark & in*jú*ria \cmark \\
+inocência & i*no*cên*ci.a \xmark & i*no*cên*cia \cmark \\
+inópia & i*nó*pi.a \xmark & i*nó*pia \cmark \\
+insaciável & in*sa*ci-á*vel \xmark & in*sa*ci*á*vel \cmark \\
+insídia & in*sí*di*a \cmark & in*sí*di-a \xmark \\
+insígnia & in*síg*ni.a \xmark & in*síg*nia \cmark \\
+insignificância & in*sig*ni*fi*cân*ci.a \xmark & in*sig*ni*fi*cân*cia \cmark \\
+insistência & in*sis*tên*ci.a \xmark & in*sis*tên*cia \cmark \\
+insolência & in*so*lên*ci.a \xmark & in*so*lên*cia \cmark \\
+insolvência & in*sol*vên*ci.a \xmark & in*sol*vên*cia \cmark \\
+inspiratório & ins*pi*ra*tó*ri*o \cmark & ins*pi*ra*tó*ri-o \xmark \\
+instância & ins*tân*ci.a \xmark & ins*tân*cia \cmark \\
+instantâneo & ins*tan*tâ*ne*o \cmark & ins*tan*tâ*ne-o \xmark \\
+instituído & ins*ti*tu-í*do \xmark & ins*ti*tu*í*do \cmark \\
+instituir & ins*ti*tu-ir \xmark & ins*ti*tu*ir \cmark \\
+instruído & ins*tru-í*do \xmark & ins*tru*í*do \cmark \\
+instruir & ins*tru-ir \xmark & ins*tru*ir \cmark \\
+insubstituível & in*subs*ti*tu-í*vel \xmark & in*subs*ti*tu*í*vel \cmark \\
+insuficiência & in*su*fi*ci*ên*ci.a \xmark & in*su*fi*ci*ên*cia \cmark \\
+inteligência & in*te*li*gên*ci.a \xmark & in*te*li*gên*cia \cmark \\
+interbancário & in*ter*ban*cá*ri.o \xmark & in*ter*ban*cá*rio \cmark \\
+intercambiável & in*ter*cam*bi-á*vel \xmark & in*ter*cam*bi*á*vel \cmark \\
+intercâmbio & in*ter*câm*bi.o \xmark & in*ter*câm*bio \cmark \\
+interdependência & in*ter*de*pen*dên*ci.a \xmark & in*ter*de*pen*dên*cia \cmark \\
+interferência & in*ter*fe*rên*ci.a \xmark & in*ter*fe*rên*cia \cmark \\
+interflúvio & in*ter*flú*vi.o \xmark & in*ter*flú*vio \cmark \\
+interlúdio & in*ter*lú*di.o \xmark & in*ter*lú*dio \cmark \\
+intermediário & in*ter*me*di-á*ri.o \xmark & in*ter*me*di*á*rio \cmark \\
+intermédio & in*ter*mé*di.o \xmark & in*ter*mé*dio \cmark \\
+intermitência & in*ter*mi*tên*ci.a \xmark & in*ter*mi*tên*cia \cmark \\
+interoceânico & in*te*ro*ce-â*ni*co \xmark & in*te*ro*ce*â*ni*co \cmark \\
+interplanetário & in*ter*pla*ne*tá*ri.o \xmark & in*ter*pla*ne*tá*rio \cmark \\
+interrogatório & in*ter*ro*ga*tó*ri.o \xmark & in*ter*ro*ga*tó*rio \cmark \\
+interstício & in*ters*tí*ci.o \xmark & in*ters*tí*cio \cmark \\
+interventoria & in*ter*ven*to*ri*a \cmark & in*ter*ven*to*ri-a \xmark \\
+intolerância & in*to*le*rân*ci.a \xmark & in*to*le*rân*cia \cmark \\
+intransigência & in*tran*si*gên*ci.a \xmark & in*tran*si*gên*cia \cmark \\
+intuição & in*tu-i*ção \xmark & in*tu*i*ção \cmark \\
+intuir & in*tu-ir \xmark & in*tu*ir \cmark \\
+intuitivo & in*tu-i*ti*vo \xmark & in*tu-i*ti*vo \xmark \\
+invariância & in*va*ri*ân*ci.a \xmark & in*va*ri*ân*cia \cmark \\
+invariável & in*va*ri-á*vel \xmark & in*va*ri*á*vel \cmark \\
+inventário & in*ven*tá*ri.o \xmark & in*ven*tá*rio \cmark \\
+inviável & in*vi-á*vel \xmark & in*vi*á*vel \cmark \\
+involuntário & in*vo*lun*tá*ri.o \xmark & in*vo*lun*tá*rio \cmark \\
+iódico & i-ó*di*co \xmark & i*ó*di*co \cmark \\
+irídio & i*rí*di.o \xmark & i*rí*dio \cmark \\
+ironia & i*ro*ni*a \cmark & i*ro*ni-a \xmark \\
+irônico & i-rô*ni*co \xmark & i*rô*ni*co \cmark \\
+iroquês & i*ro-quês \xmark & i*ro*quês \cmark \\
+irreconciliável & ir*re*con*ci*li-á*vel \xmark & ir*re*con*ci*li*á*vel \cmark \\
+irrefreável & ir*re*fre-á*vel \xmark & ir*re*fre*á*vel \cmark \\
+irremediável & ir*re*me*di-á*vel \xmark & ir*re*me*di*á*vel \cmark \\
+irrenunciável & ir*re*nun*ci-á*vel \xmark & ir*re*nun*ci*á*vel \cmark \\
+irretorquível & ir*re*tor-quí*vel \xmark & ir*re*tor*quí*vel \cmark \\
+irreverência & ir*re*ve*rên*ci.a \xmark & ir*re*ve*rên*cia \cmark \\
+irrisório & ir*ri*só*ri.o \xmark & ir*ri*só*rio \cmark \\
+isogamia & i*so*ga*mi*a \cmark & i*so*ga*mi-a \xmark \\
+isomeria & i*so*me*ri*a \cmark & i*so*me*ri-a \xmark \\
+isometria & i*so*me*tri*a \cmark & i*so*me*tri-a \xmark \\
+isomorfia & i*so*mor*fi*a \cmark & i*so*mor*fi-a \xmark \\
+isonomia & i*so*no*mi*a \cmark & i*so*no*mi-a \xmark \\
+isostasia & i*sos*ta*si*a \cmark & i*sos*ta*si-a \xmark \\
+isotônico & i*so-tô*ni*co \xmark & i*so*tô*ni*co \cmark \\
+isquemia & is*que*mi*a \cmark & is*que*mi-a \xmark \\
+itérbio & i*tér*bi.o \xmark & i*tér*bio \cmark \\
+itinerário & i*ti*ne*rá*ri.o \xmark & i*ti*ne*rá*rio \cmark \\
+ítrio & í*tri.o \xmark & í*trio \cmark \\
 jabô & ja-bô \xmark & ja*bô \cmark \\
-janaúba & ja*na-ú*ba \xmark & ja*na*ú*ba \cmark \\
+jactância & jac*tân*ci.a \xmark & jac*tân*cia \cmark \\
+jaculatória & ja*cu*la*tó*ri.a \xmark & ja*cu*la*tó*ria \cmark \\
+jandaia & jan*dai*a \cmark & jan*dai-a \xmark \\
+jaó & ja-ó \xmark & ja*ó \cmark \\
+jaracatiá & ja*ra*ca*ti-á \xmark & ja*ra*ca*ti*á \cmark \\
+jaú & ja-ú \xmark & ja*ú \cmark \\
+jejunostomia & je*ju*nos*to*mi*a \cmark & je*ju*nos*to*mi-a \xmark \\
+jesuíta & je*su-í*ta \xmark & je*su*í*ta \cmark \\
+jesuítico & je*su-í*ti*co \xmark & je*su*í*ti*co \cmark \\
+jesuitismo & je*su-i*tis*mo \xmark & je*su*i*tis*mo \cmark \\
+jia & ji*a \cmark & ji-a \xmark \\
+joalheria & jo*a*lhe*ri*a \cmark & jo*a*lhe*ri-a \xmark \\
+joia & joi*a \cmark & joi-a \xmark \\
+joinvilense & jo-in*vi*len*se \xmark & jo*in*vi*len*se \cmark \\
+joio & joi*o \cmark & joi-o \xmark \\
+juá & ju-á \xmark & ju*á \cmark \\
+judaísmo & ju*da-ís*mo \xmark & ju*da*ís*mo \cmark \\
+judia & ju*di*a \cmark & ju*di-a \xmark \\
+judiaria & ju*di*a*ri*a \cmark & ju*di*a*ri-a \xmark \\
+judiciário & ju*di*ci-á*ri.o \xmark & ju*di*ci*á*rio \cmark \\
+judô & ju-dô \xmark & ju*dô \cmark \\
+juizado & ju-i*za*do \xmark & ju*i*za*do \cmark \\
+juíza & ju-í*za \xmark & ju*í*za \cmark \\
+juiz & ju-iz \xmark & ju*iz \cmark \\
+juízo & ju-í*zo \xmark & ju*í*zo \cmark \\
+juquiá & ju*qui-á \xmark & ju*qui*á \cmark \\
+kuwaitiano & ku-wai*ti*a*no \xmark & ku-wai*ti*a*no \xmark \\
+lábia & lá*bi.a \xmark & lá*bia \cmark \\
+laboratório & la*bo*ra*tó*ri.o \xmark & la*bo*ra*tó*rio \cmark \\
+lacaio & la*cai*o \cmark & la*cai-o \xmark \\
+laçaria & la*ça*ri*a \cmark & la*ça*ri-a \xmark \\
+lacônico & la-cô*ni*co \xmark & la*cô*ni*co \cmark \\
+ladainha & la*da-i*nha \xmark & la*da*i*nha \cmark \\
+lagoa & la*go*a \cmark & la*go-a \xmark \\
+laia & lai*a \cmark & lai-a \xmark \\
+lamaísmo & la*ma-ís*mo \xmark & la*ma*ís*mo \cmark \\
+lâmia & lâ*mi.a \xmark & lâ*mia \cmark \\
+lampião & lam*pi-ão \xmark & lam*pi*ão \cmark \\
+lampreia & lam*prei*a \cmark & lam*prei-a \xmark \\
+lamúria & la*mú*ri.a \xmark & la*mú*ria \cmark \\
+lanifício & la*ni*fí*ci.o \xmark & la*ni*fí*cio \cmark \\
+laparoscopia & la*pa*ros*co*pi*a \cmark & la*pa*ros*co*pi-a \xmark \\
+laparotomia & la*pa*ro*to*mi*a \cmark & la*pa*ro*to*mi-a \xmark \\
+laquê & la-quê \xmark & la*quê \cmark \\
+larápio & la*rá*pi.o \xmark & la*rá*pio \cmark \\
+laríngeo & la*rín*ge.o \xmark & la*rín*geo \cmark \\
+lascívia & las*cí*vi.a \xmark & las*cí*via \cmark \\
+latifúndio & la*ti*fún*di.o \xmark & la*ti*fún*dio \cmark \\
+latinório & la*ti*nó*ri.o \xmark & la*ti*nó*rio \cmark \\
+latrocínio & la*tro*cí*ni.o \xmark & la*tro*cí*nio \cmark \\
+laudatório & lau*da*tó*ri.o \xmark & lau*da*tó*rio \cmark \\
+laurêncio & lau*rên*ci.o \xmark & lau*rên*cio \cmark \\
+lavatório & la*va*tó*ri.o \xmark & la*va*tó*rio \cmark \\
+lavradio & la*vra*di*o \cmark & la*vra*di-o \xmark \\
+leão & le-ão \xmark & le*ão \cmark \\
+legendário & le*gen*dá*ri.o \xmark & le*gen*dá*rio \cmark \\
+legião & le*gi-ão \xmark & le*gi*ão \cmark \\
+legionário & le*gi*o*ná*ri.o \xmark & le*gi*o*ná*rio \cmark \\
+leitaria & lei*ta*ri*a \cmark & lei*ta*ri-a \xmark \\
+leitoa & lei*to*a \cmark & lei*to-a \xmark \\
+lendário & len*dá*ri.o \xmark & len*dá*rio \cmark \\
+leniência & le*ni*ên*ci.a \xmark & le*ni*ên*cia \cmark \\
+lenocínio & le*no*cí*ni.o \xmark & le*no*cí*nio \cmark \\
+leoa & le*o*a \cmark & le*o-a \xmark \\
+lepidopterologia & le*pi*dop*te*ro*lo*gi*a \cmark & le*pi*dop*te*ro*lo*gi-a \xmark \\
+leporídeo & le*po*rí*de.o \xmark & le*po*rí*deo \cmark \\
+lésbio & lés*bi.o \xmark & lés*bio \cmark \\
+letargia & le*tar*gi*a \cmark & le*tar*gi-a \xmark \\
+letícia & le*tí*ci.a \xmark & le*tí*cia \cmark \\
+leucemia & leu*ce*mi*a \cmark & leu*ce*mi-a \xmark \\
+leucopenia & leu*co*pe*ni*a \cmark & leu*co*pe*ni-a \xmark \\
+leucoplasia & leu*co*pla*si*a \cmark & leu*co*pla*si-a \xmark \\
+leucotomia & leu*co*to*mi*a \cmark & leu*co*to*mi-a \xmark \\
+lexicografia & le*xi*co*gra*fi*a \cmark & le*xi*co*gra*fi-a \xmark \\
+lexicologia & le*xi*co*lo*gi*a \cmark & le*xi*co*lo*gi-a \xmark \\
+lezíria & le*zí*ri.a \xmark & le*zí*ria \cmark \\
+lia & li*a \cmark & li-a \xmark \\
+libertário & li*ber*tá*ri.o \xmark & li*ber*tá*rio \cmark \\
+líbio & lí*bi.o \xmark & lí*bio \cmark \\
+licantropia & li*can*tro*pi*a \cmark & li*can*tro*pi-a \xmark \\
+lício & lí*ci.o \xmark & lí*cio \cmark \\
+limnologia & lim*no*lo*gi*a \cmark & lim*no*lo*gi-a \xmark \\
+linóleo & li*nó*le*o \cmark & li*nó*le-o \xmark \\
+lírio & lí*ri*o \cmark & lí*ri-o \xmark \\
+lisboa & lis*bo*a \cmark & lis*bo-a \xmark \\
+lisimáquia & li*si*má*qui*a \cmark & li*si*má*qui-a \xmark \\
+litania & li*ta*ni*a \cmark & li*ta*ni-a \xmark \\
+litíase & li*tí-a*se \xmark & li*tí*a*se \cmark \\
+litígio & li*tí*gi.o \xmark & li*tí*gio \cmark \\
+lítio & lí*ti.o \xmark & lí*tio \cmark \\
+litispendência & li*tis*pen*dên*ci*a \cmark & li*tis*pen*dên*ci-a \xmark \\
+litografia & li*to*gra*fi*a \cmark & li*to*gra*fi-a \xmark \\
+litologia & li*to*lo*gi*a \cmark & li*to*lo*gi-a \xmark \\
+litotripsia & li*to*trip*si*a \cmark & li*to*trip*si-a \xmark \\
+liturgia & li*tur*gi*a \cmark & li*tur*gi-a \xmark \\
+livraria & li*vra*ri*a \cmark & li*vra*ri-a \xmark \\
+lixívia & li*xí*vi.a \xmark & li*xí*via \cmark \\
+loa & lo*a \cmark & lo-a \xmark \\
+lobectomia & lo*bec*to*mi*a \cmark & lo*bec*to*mi-a \xmark \\
+lobélia & lo*bé*li*a \cmark & lo*bé*li-a \xmark \\
+locatário & lo*ca*tá*ri.o \xmark & lo*ca*tá*rio \cmark \\
+logosofia & lo*go*so*fi*a \cmark & lo*go*so*fi-a \xmark \\
+lombalgia & lom*bal*gi*a \cmark & lom*bal*gi-a \xmark \\
+loteria & lo*te*ri*a \cmark & lo*te*ri-a \xmark \\
+lua & lu*a \cmark & lu-a \xmark \\
+ludoterapia & lu*do*te*ra*pi*a \cmark & lu*do*te*ra*pi-a \xmark \\
+luís & lu-ís \xmark & lu*ís \cmark \\
+luminescência & lu*mi*nes*cên*ci.a \xmark & lu*mi*nes*cên*cia \cmark \\
+lunário & lu*ná*ri.o \xmark & lu*ná*rio \cmark \\
 lusíada & lu*sí-a*da \xmark & lu*sí*a*da \cmark \\
+lusofobia & lu*so*fo*bi*a \cmark & lu*so*fo*bi-a \xmark \\
+lusofonia & lu*so*fo*ni*a \cmark & lu*so*fo*ni-a \xmark \\
+lutécio & lu*té*ci.o \xmark & lu*té*cio \cmark \\
+luteína & lu*te-í*na \xmark & lu*te*í*na \cmark \\
+luteria & lu*te*ri*a \cmark & lu*te*ri-a \xmark \\
+luxúria & lu*xú*ri.a \xmark & lu*xú*ria \cmark \\
+macadâmia & ma*ca*dâ*mi.a \xmark & ma*ca*dâ*mia \cmark \\
+macambúzio & ma*cam*bú*zi.o \xmark & ma*cam*bú*zio \cmark \\
+macaúba & ma*ca-ú*ba \xmark & ma*ca*ú*ba \cmark \\
+macedônia & ma*ce-dô*ni.a \xmark & ma*ce*dô*nia \cmark \\
+maceió & ma*cei-ó \xmark & ma*cei*ó \cmark \\
+macio & ma*ci*o \cmark & ma*ci-o \xmark \\
+maçonaria & ma*ço*na*ri*a \cmark & ma*ço*na*ri-a \xmark \\
 maçônico & ma-çô*ni*co \xmark & ma*çô*ni*co \cmark \\
+macrobiótica & ma*cro*bi-ó*ti*ca \xmark & ma*cro*bi*ó*ti*ca \cmark \\
 macrobiótico & ma*cro*bi-ó*ti*co \xmark & ma*cro*bi*ó*ti*co \cmark \\
+macroeconomia & ma*cro*e*co*no*mi*a \cmark & ma*cro*e*co*no*mi-a \xmark \\
+macroeconômico & ma*cro*e*co-nô*mi*co \xmark & ma*cro*e*co*nô*mi*co \cmark \\
+macronúcleo & ma*cro*nú*cle.o \xmark & ma*cro*nú*cleo \cmark \\
+macrorregião & ma*cror*re*gi-ão \xmark & ma*cror*re*gi*ão \cmark \\
+maestria & ma*es*tri*a \cmark & ma*es*tri-a \xmark \\
+máfia & má*fi.a \xmark & má*fia \cmark \\
 mafuá & ma*fu-á \xmark & ma*fu*á \cmark \\
+magia & ma*gi*a \cmark & ma*gi-a \xmark \\
+magistério & ma*gis*té*ri.o \xmark & ma*gis*té*rio \cmark \\
+magnésio & mag*né*si.o \xmark & mag*né*sio \cmark \\
+magnificência & mag*ni*fi*cên*ci.a \xmark & mag*ni*fi*cên*cia \cmark \\
+magnólia & mag*nó*li*a \cmark & mag*nó*li-a \xmark \\
+mágoa & má*go.a \xmark & má*goa \cmark \\
+maia & mai*a \cmark & mai-a \xmark \\
+maiólica & mai-ó*li*ca \xmark & mai*ó*li*ca \cmark \\
+maio & mai*o \cmark & mai-o \xmark \\
+maioria & mai*o*ri*a \cmark & mai*o*ri-a \xmark \\
+maís & ma-ís \xmark & ma*ís \cmark \\
+maiúscula & mai-ús*cu*la \xmark & mai*ús*cu*la \cmark \\
+maiúsculo & mai-ús*cu*lo \xmark & mai*ús*cu*lo \cmark \\
+majoritário & ma*jo*ri*tá*ri.o \xmark & ma*jo*ri*tá*rio \cmark \\
+malacologia & ma*la*co*lo*gi*a \cmark & ma*la*co*lo*gi-a \xmark \\
+malafaia & ma*la*fai*a \cmark & ma*la*fai-a \xmark \\
+malaio & ma*lai*o \cmark & ma*lai-o \xmark \\
+malauiano & ma*lau-i*a*no \xmark & ma*lau*i*a*no \cmark \\
+maleável & ma*le-á*vel \xmark & ma*le*á*vel \cmark \\
+maledicência & ma*le*di*cên*ci.a \xmark & ma*le*di*cên*cia \cmark \\
+malícia & ma*lí*ci.a \xmark & ma*lí*cia \cmark \\
+malthusianismo & mal-thu*si*a*nis*mo \xmark & mal-thu*si*a*nis*mo \xmark \\
+malthusiano & mal-thu*si*a*no \xmark & mal-thu*si*a*no \xmark \\
+malvasia & mal*va*si*a \cmark & mal*va*si-a \xmark \\
+mamário & ma*má*ri.o \xmark & ma*má*rio \cmark \\
+mamografia & ma*mo*gra*fi*a \cmark & ma*mo*gra*fi-a \xmark \\
+mancebia & man*ce*bi*a \cmark & man*ce*bi-a \xmark \\
+mandaçaia & man*da*çai*a \cmark & man*da*çai-a \xmark \\
+mandrião & man*dri-ão \xmark & man*dri*ão \cmark \\
+maneia & ma*nei*a \cmark & ma*nei-a \xmark \\
+maníaco & ma*ní-a*co \xmark & ma*ní*a*co \cmark \\
+mania & ma*ni*a \cmark & ma*ni-a \xmark \\
+maniqueísmo & ma*ni*que-ís*mo \xmark & ma*ni*que*ís*mo \cmark \\
+maniqueísta & ma*ni*que-ís*ta \xmark & ma*ni*que*ís*ta \cmark \\
 manômetro & ma-nô*me*tro \xmark & ma*nô*me*tro \cmark \\
-mediúnico & me*di-ú*ni*co \xmark & me*di*ú*ni*co \cmark \\
-microrregião & mi*cror*re*gi-ão \xmark & mi*cror*re*gi*ão \cmark \\
-neoplatônico & ne*o*pla-tô*ni*co \xmark & ne*o*pla*tô*ni*co \cmark \\
+mantô & man-tô \xmark & man*tô \cmark \\
+manuseio & ma*nu*sei*o \cmark & ma*nu*sei-o \xmark \\
+maquia & ma*qui*a \cmark & ma*qui-a \xmark \\
+maquinaria & ma*qui*na*ri*a \cmark & ma*qui*na*ri-a \xmark \\
+maquinário & ma*qui*ná*ri.o \xmark & ma*qui*ná*rio \cmark \\
+marambaia & ma*ram*bai*a \cmark & ma*ram*bai-a \xmark \\
+marcenaria & mar*ce*na*ri*a \cmark & mar*ce*na*ri-a \xmark \\
+marchetaria & mar*che*ta*ri*a \cmark & mar*che*ta*ri-a \xmark \\
+márcio & már*ci.o \xmark & már*cio \cmark \\
+maresia & ma*re*si*a \cmark & ma*re*si-a \xmark \\
+maria & ma*ri*a \cmark & ma*ri-a \xmark \\
+marinharia & ma*ri*nha*ri*a \cmark & ma*ri*nha*ri-a \xmark \\
+marquês & mar-quês \xmark & mar*quês \cmark \\
+martírio & mar*tí*ri.o \xmark & mar*tí*rio \cmark \\
+maruim & ma*ru-im \xmark & ma*ru-im \xmark \\
+masdeísmo & mas*de-ís*mo \xmark & mas*de*ís*mo \cmark \\
+mastectomia & mas*tec*to*mi*a \cmark & mas*tec*to*mi-a \xmark \\
+mastologia & mas*to*lo*gi*a \cmark & mas*to*lo*gi-a \xmark \\
+matéria & ma*té*ri.a \xmark & ma*té*ria \cmark \\
+matricídio & ma*tri*cí*di.o \xmark & ma*tri*cí*dio \cmark \\
+meão & me-ão \xmark & me*ão \cmark \\
+média & mé*di.a \xmark & mé*dia \cmark \\
+mediático & me*di-á*ti*co \xmark & me*di*á*ti*co \cmark \\
+mediocracia & me*di*o*cra*ci*a \cmark & me*di*o*cra*ci-a \xmark \\
+medíocre & me*dí-o*cre \xmark & me*dí*o*cre \cmark \\
+médio & mé*di.o \xmark & mé*dio \cmark \\
+mediterrâneo & me*di*ter*râ*ne.o \xmark & me*di*ter*râ*neo \cmark \\
+megalomaníaco & me*ga*lo*ma*ní-a*co \xmark & me*ga*lo*ma*ní*a*co \cmark \\
+megalomania & me*ga*lo*ma*ni*a \cmark & me*ga*lo*ma*ni-a \xmark \\
+megatério & me*ga*té*ri.o \xmark & me*ga*té*rio \cmark \\
+megawatt & me*ga-watt \xmark & me*ga-watt \xmark \\
+meia & mei*a \cmark & mei-a \xmark \\
+meio & mei*o \cmark & mei-o \xmark \\
+melancia & me*lan*ci*a \cmark & me*lan*ci-a \xmark \\
+melancolia & me*lan*co*li*a \cmark & me*lan*co*li-a \xmark \\
+melhoria & me*lho*ri*a \cmark & me*lho*ri-a \xmark \\
+melífluo & me*lí*flu.o \xmark & me*lí*fluo \cmark \\
+melodia & me*lo*di*a \cmark & me*lo*di-a \xmark \\
+melofobia & me*lo*fo*bi*a \cmark & me*lo*fo*bi-a \xmark \\
+melomania & me*lo*ma*ni*a \cmark & me*lo*ma*ni-a \xmark \\
+memória & me*mó*ri.a \xmark & me*mó*ria \cmark \\
+mendelévio & men*de*lé*vi.o \xmark & men*de*lé*vio \cmark \\
+meneio & me*nei*o \cmark & me*nei-o \xmark \\
+menorragia & me*nor*ra*gi*a \cmark & me*nor*ra*gi-a \xmark \\
+mênstruo & mêns*tru.o \xmark & mêns*truo \cmark \\
+mercadologia & mer*ca*do*lo*gi*a \cmark & mer*ca*do*lo*gi-a \xmark \\
+mercadoria & mer*ca*do*ri*a \cmark & mer*ca*do*ri-a \xmark \\
+mercancia & mer*can*ci*a \cmark & mer*can*ci-a \xmark \\
+mercearia & mer*ce*a*ri*a \cmark & mer*ce*a*ri-a \xmark \\
+mercenário & mer*ce*ná*ri.o \xmark & mer*ce*ná*rio \cmark \\
+mercúrio & mer*cú*ri.o \xmark & mer*cú*rio \cmark \\
+mergulhia & mer*gu*lhi*a \cmark & mer*gu*lhi-a \xmark \\
+meritocracia & me*ri*to*cra*ci*a \cmark & me*ri*to*cra*ci-a \xmark \\
+merovíngio & me*ro*vín*gi.o \xmark & me*ro*vín*gio \cmark \\
+mesquinharia & mes*qui*nha*ri*a \cmark & mes*qui*nha*ri-a \xmark \\
+metafonia & me*ta*fo*ni*a \cmark & me*ta*fo*ni-a \xmark \\
+metalografia & me*ta*lo*gra*fi*a \cmark & me*ta*lo*gra*fi-a \xmark \\
+metalurgia & me*ta*lur*gi*a \cmark & me*ta*lur*gi-a \xmark \\
+metaplasia & me*ta*pla*si*a \cmark & me*ta*pla*si-a \xmark \\
+meteórico & me*te-ó*ri*co \xmark & me*te*ó*ri*co \cmark \\
+meteorologia & me*te*o*ro*lo*gi*a \cmark & me*te*o*ro*lo*gi-a \xmark \\
+metodologia & me*to*do*lo*gi*a \cmark & me*to*do*lo*gi-a \xmark \\
+metonímia & me*to*ní*mi.a \xmark & me*to*ní*mia \cmark \\
+metrologia & me*tro*lo*gi*a \cmark & me*tro*lo*gi-a \xmark \\
+metrorragia & me*tror*ra*gi*a \cmark & me*tror*ra*gi-a \xmark \\
+mialgia & mi*al*gi*a \cmark & mi*al*gi-a \xmark \\
+micélio & mi*cé*li.o \xmark & mi*cé*lio \cmark \\
+micologia & mi*co*lo*gi*a \cmark & mi*co*lo*gi-a \xmark \\
+microbiólogo & mi*cro*bi-ó*lo*go \xmark & mi*cro*bi*ó*lo*go \cmark \\
+micróbio & mi*cró*bi.o \xmark & mi*cró*bio \cmark \\
+microcefalia & mi*cro*ce*fa*li*a \cmark & mi*cro*ce*fa*li-a \xmark \\
+microcirurgia & mi*cro*ci*rur*gi*a \cmark & mi*cro*ci*rur*gi-a \xmark \\
+microfonia & mi*cro*fo*ni*a \cmark & mi*cro*fo*ni-a \xmark \\
+microfotografia & mi*cro*fo*to*gra*fi*a \cmark & mi*cro*fo*to*gra*fi-a \xmark \\
+microscopia & mi*cros*co*pi*a \cmark & mi*cros*co*pi-a \xmark \\
+microscópio & mi*cros*có*pi.o \xmark & mi*cros*có*pio \cmark \\
+mictório & mic*tó*ri.o \xmark & mic*tó*rio \cmark \\
+micuim & mi*cu-im \xmark & mi*cu-im \xmark \\
+mídia & mí*di.a \xmark & mí*dia \cmark \\
+midríase & mi*drí-a*se \xmark & mi*drí*a*se \cmark \\
+migratório & mi*gra*tó*ri.o \xmark & mi*gra*tó*rio \cmark \\
+milenário & mi*le*ná*ri.o \xmark & mi*le*ná*rio \cmark \\
+milionário & mi*li*o*ná*ri*o \cmark & mi*li*o*ná*ri-o \xmark \\
+militância & mi*li*tân*ci.a \xmark & mi*li*tân*cia \cmark \\
+mimeógrafo & mi*me-ó*gra*fo \xmark & mi*me*ó*gra*fo \cmark \\
+mineralogia & mi*ne*ra*lo*gi*a \cmark & mi*ne*ra*lo*gi-a \xmark \\
+minério & mi*né*ri.o \xmark & mi*né*rio \cmark \\
+minifúndio & mi*ni*fún*di.o \xmark & mi*ni*fún*dio \cmark \\
+minissérie & mi*nis*sé*ri.e \xmark & mi*nis*sé*rie \cmark \\
+ministério & mi*nis*té*ri.o \xmark & mi*nis*té*rio \cmark \\
+minoria & mi*no*ri*a \cmark & mi*no*ri-a \xmark \\
+minoritário & mi*no*ri*tá*ri.o \xmark & mi*no*ri*tá*rio \cmark \\
+minúcia & mi*nú*ci.a \xmark & mi*nú*cia \cmark \\
+minudência & mi*nu*dên*ci.a \xmark & mi*nu*dên*cia \cmark \\
+míope & mí-o*pe \xmark & mí*o*pe \cmark \\
+miopia & mi*o*pi*a \cmark & mi*o*pi-a \xmark \\
+miríade & mi*rí-a*de \xmark & mi*rí*a*de \cmark \\
+misantropia & mi*san*tro*pi*a \cmark & mi*san*tro*pi-a \xmark \\
+miscelânea & mis*ce*lâ*ne.a \xmark & mis*ce*lâ*nea \cmark \\
+miséria & mi*sé*ri.a \xmark & mi*sé*ria \cmark \\
+misericórdia & mi*se*ri*cór*di.a \xmark & mi*se*ri*cór*dia \cmark \\
+misoginia & mi*so*gi*ni*a \cmark & mi*so*gi*ni-a \xmark \\
+missionário & mis*si*o*ná*ri.o \xmark & mis*si*o*ná*rio \cmark \\
+mistério & mis*té*ri.o \xmark & mis*té*rio \cmark \\
+mitocôndria & mi*to-côn*dri.a \xmark & mi*to*côn*dria \cmark \\
+mitografia & mi*to*gra*fi*a \cmark & mi*to*gra*fi-a \xmark \\
+mitologia & mi*to*lo*gi*a \cmark & mi*to*lo*gi-a \xmark \\
+mitomania & mi*to*ma*ni*a \cmark & mi*to*ma*ni-a \xmark \\
+miúdo & mi-ú*do \xmark & mi*ú*do \cmark \\
+mixaria & mi*xa*ri*a \cmark & mi*xa*ri-a \xmark \\
+mixórdia & mi*xór*di.a \xmark & mi*xór*dia \cmark \\
+mnemônica & m.ne-mô*ni*ca \xmark & mne*mô*ni*ca \cmark \\
+mnemônico & m.ne-mô*ni*co \xmark & mne*mô*ni*co \cmark \\
+moa & mo*a \cmark & mo-a \xmark \\
+mobília & mo*bí*li.a \xmark & mo*bí*lia \cmark \\
+mobiliário & mo*bi*li-á*ri.o \xmark & mo*bi*li*á*rio \cmark \\
+modéstia & mo*dés*ti.a \xmark & mo*dés*tia \cmark \\
+moído & mo-í*do \xmark & mo*í*do \cmark \\
+moinha & mo-i*nha \xmark & mo*i*nha \cmark \\
+moinho & mo-i*nho \xmark & mo*i*nho \cmark \\
+moio & moi*o \cmark & moi-o \xmark \\
+moldávio & mol*dá*vi.o \xmark & mol*dá*vio \cmark \\
+moléstia & mo*lés*ti.a \xmark & mo*lés*tia \cmark \\
+momentâneo & mo*men*tâ*ne.o \xmark & mo*men*tâ*neo \cmark \\
+monarquia & mo*nar*qui*a \cmark & mo*nar*qui-a \xmark \\
+monetário & mo*ne*tá*ri.o \xmark & mo*ne*tá*rio \cmark \\
+monitoria & mo*ni*to*ri*a \cmark & mo*ni*to*ri-a \xmark \\
+monocromia & mo*no*cro*mi*a \cmark & mo*no*cro*mi-a \xmark \\
+monofonia & mo*no*fo*ni*a \cmark & mo*no*fo*ni-a \xmark \\
+monografia & mo*no*gra*fi*a \cmark & mo*no*gra*fi-a \xmark \\
+monomaníaco & mo*no*ma*ní-a*co \xmark & mo*no*ma*ní*a*co \cmark \\
+monomania & mo*no*ma*ni*a \cmark & mo*no*ma*ni-a \xmark \\
+monômero & mo-nô*me*ro \xmark & mo*nô*me*ro \cmark \\
+monopólio & mo*no*pó*li.o \xmark & mo*no*pó*lio \cmark \\
+monossomia & mo*nos*so*mi*a \cmark & mo*nos*so*mi-a \xmark \\
+monoteísmo & mo*no*te-ís*mo \xmark & mo*no*te*ís*mo \cmark \\
+monoteísta & mo*no*te-ís*ta \xmark & mo*no*te*ís*ta \cmark \\
+monotonia & mo*no*to*ni*a \cmark & mo*no*to*ni-a \xmark \\
+montaria & mon*ta*ri*a \cmark & mon*ta*ri-a \xmark \\
+montepio & mon*te*pi*o \cmark & mon*te*pi-o \xmark \\
+moquém & mo-quém \xmark & mo*quém \cmark \\
+moradia & mo*ra*di*a \cmark & mo*ra*di-a \xmark \\
+moratória & mo*ra*tó*ri.a \xmark & mo*ra*tó*ria \cmark \\
+mordomia & mor*do*mi*a \cmark & mor*do*mi-a \xmark \\
+moreia & mo*rei*a \cmark & mo*rei-a \xmark \\
+morfologia & mor*fo*lo*gi*a \cmark & mor*fo*lo*gi-a \xmark \\
+morrião & mor*ri-ão \xmark & mor*ri*ão \cmark \\
+mostruário & mos*tru-á*ri.o \xmark & mos*tru*á*rio \cmark \\
+mouraria & mou*ra*ri*a \cmark & mou*ra*ri-a \xmark \\
+movelaria & mo*ve*la*ri*a \cmark & mo*ve*la*ri-a \xmark \\
+mucuim & mu*cu-im \xmark & mu*cu-im \xmark \\
+mulataria & mu*la*ta*ri*a \cmark & mu*la*ta*ri-a \xmark \\
+mulherio & mu*lhe*ri*o \cmark & mu*lhe*ri-o \xmark \\
+multimídia & mul*ti*mí*di.a \xmark & mul*ti*mí*dia \cmark \\
+multitudinário & mul*ti*tu*di*ná*ri*o \cmark & mul*ti*tu*di*ná*ri-o \xmark \\
+múmia & mú*mi.a \xmark & mú*mia \cmark \\
+município & mu*ni*cí*pi.o \xmark & mu*ni*cí*pio \cmark \\
+murmúrio & mur*mú*ri.o \xmark & mur*mú*rio \cmark \\
+museologia & mu*se*o*lo*gi*a \cmark & mu*se*o*lo*gi-a \xmark \\
+museólogo & mu*se-ó*lo*go \xmark & mu*se*ó*lo*go \cmark \\
+musicografia & mu*si*co*gra*fi*a \cmark & mu*si*co*gra*fi-a \xmark \\
+musicologia & mu*si*co*lo*gi*a \cmark & mu*si*co*lo*gi-a \xmark \\
+musicoterapia & mu*si*co*te*ra*pi*a \cmark & mu*si*co*te*ra*pi-a \xmark \\
+mustelídeo & mus*te*lí*de.o \xmark & mus*te*lí*deo \cmark \\
+mutuário & mu*tu-á*ri.o \xmark & mu*tu*á*rio \cmark \\
+mútuo & mú*tu.o \xmark & mú*tuo \cmark \\
+nanotecnologia & na*no*tec*no*lo*gi*a \cmark & na*no*tec*no*lo*gi-a \xmark \\
+napoleão & na*po*le-ão \xmark & na*po*le*ão \cmark \\
+natalício & na*ta*lí*ci.o \xmark & na*ta*lí*cio \cmark \\
+naufrágio & nau*frá*gi.o \xmark & nau*frá*gio \cmark \\
+navio & na*vi*o \cmark & na*vi-o \xmark \\
+necessário & ne*ces*sá*ri.o \xmark & ne*ces*sá*rio \cmark \\
+necrofagia & ne*cro*fa*gi*a \cmark & ne*cro*fa*gi-a \xmark \\
+necrofilia & ne*cro*fi*li*a \cmark & ne*cro*fi*li-a \xmark \\
+necrologia & ne*cro*lo*gi*a \cmark & ne*cro*lo*gi-a \xmark \\
+necromancia & ne*cro*man*ci*a \cmark & ne*cro*man*ci-a \xmark \\
+necropsia & ne*crop*si*a \cmark & ne*crop*si-a \xmark \\
+necrotério & ne*cro*té*ri.o \xmark & ne*cro*té*rio \cmark \\
+neerlandês & ne*er*lan*dês \cmark & ne*er*lan*dês \cmark \\
+nefrectomia & ne*frec*to*mi*a \cmark & ne*frec*to*mi-a \xmark \\
+nefrologia & ne*fro*lo*gi*a \cmark & ne*fro*lo*gi-a \xmark \\
+nefropatia & ne*fro*pa*ti*a \cmark & ne*fro*pa*ti-a \xmark \\
+negligência & ne*gli*gên*ci.a \xmark & ne*gli*gên*cia \cmark \\
+negócio & ne*gó*ci.o \xmark & ne*gó*cio \cmark \\
+neocolonialismo & ne*o*co*lo*ni*a*lis*mo \cmark & ne-o*co*lo*ni*a*lis*mo \xmark \\
+neodímio & ne*o*dí*mi.o \xmark & ne-o*dí*mio \xmark \\
+neofascista & ne*o*fas*cis*ta \cmark & ne-o*fas*cis*ta \xmark \\
+neófito & ne-ó*fi*to \xmark & ne*ó*fi*to \cmark \\
+neolatino & ne*o*la*ti*no \cmark & ne-o*la*ti*no \xmark \\
+neoliberalismo & ne*o*li*be*ra*lis*mo \cmark & ne-o*li*be*ra*lis*mo \xmark \\
+neoliberal & ne*o*li*be*ral \cmark & ne-o*li*be*ral \xmark \\
+neolítico & ne*o*lí*ti*co \cmark & ne-o*lí*ti*co \xmark \\
+neologismo & ne*o*lo*gis*mo \cmark & ne-o*lo*gis*mo \xmark \\
+neonatologia & ne*o*na*to*lo*gi*a \cmark & ne-o*na*to*lo*gi-a \xmark \\
+neonato & ne*o*na*to \cmark & ne-o*na*to \xmark \\
+neonazismo & ne*o*na*zis*mo \cmark & ne-o*na*zis*mo \xmark \\
+neonazista & ne*o*na*zis*ta \cmark & ne-o*na*zis*ta \xmark \\
+neon & ne*on \cmark & ne-on \xmark \\
+néon & né-on \xmark & né*on \cmark \\
+neoplasia & ne*o*pla*si*a \cmark & ne-o*pla*si-a \xmark \\
+neoplatonismo & ne*o*pla*to*nis*mo \cmark & ne-o*pla*to*nis*mo \xmark \\
+neozelandês & ne*o*ze*lan*dês \cmark & ne-o*ze*lan*dês \xmark \\
+nério & né*ri.o \xmark & né*rio \cmark \\
+néscio & nés*ci.o \xmark & nés*cio \cmark \\
+neuralgia & neu*ral*gi*a \cmark & neu*ral*gi-a \xmark \\
+neurastenia & neu*ras*te*ni*a \cmark & neu*ras*te*ni-a \xmark \\
+neurobiologia & neu*ro*bi*o*lo*gi*a \cmark & neu*ro*bi*o*lo*gi-a \xmark \\
+neurocirurgia & neu*ro*ci*rur*gi*a \cmark & neu*ro*ci*rur*gi-a \xmark \\
+neurocirurgião & neu*ro*ci*rur*gi-ão \xmark & neu*ro*ci*rur*gi*ão \cmark \\
+neurologia & neu*ro*lo*gi*a \cmark & neu*ro*lo*gi-a \xmark \\
+neuropatia & neu*ro*pa*ti*a \cmark & neu*ro*pa*ti-a \xmark \\
+neuropatologia & neu*ro*pa*to*lo*gi*a \cmark & neu*ro*pa*to*lo*gi-a \xmark \\
+neutropenia & neu*tro*pe*ni*a \cmark & neu*tro*pe*ni-a \xmark \\
+névoa & né*vo.a \xmark & né*voa \cmark \\
+nevralgia & ne*vral*gi*a \cmark & ne*vral*gi-a \xmark \\
+ninfomaníaca & nin*fo*ma*ní-a*ca \xmark & nin*fo*ma*ní*a*ca \cmark \\
+ninfomaníaco & nin*fo*ma*ní-a*co \xmark & nin*fo*ma*ní*a*co \cmark \\
+ninfomania & nin*fo*ma*ni*a \cmark & nin*fo*ma*ni-a \xmark \\
+nobélio & no*bé*li.o \xmark & no*bé*lio \cmark \\
+nobiliarquia & no*bi*li*ar*qui*a \cmark & no*bi*li*ar*qui-a \xmark \\
+nobiliárquico & no*bi*li-ár*qui*co \xmark & no*bi*li*ár*qui*co \cmark \\
+nomografia & no*mo*gra*fi*a \cmark & no*mo*gra*fi-a \xmark \\
+nonagenário & no*na*ge*ná*ri.o \xmark & no*na*ge*ná*rio \cmark \\
+noologia & no*o*lo*gi*a \cmark & no*o*lo*gi-a \xmark \\
+nosologia & no*so*lo*gi*a \cmark & no*so*lo*gi-a \xmark \\
+nostalgia & nos*tal*gi*a \cmark & nos*tal*gi-a \xmark \\
+notário & no*tá*ri.o \xmark & no*tá*rio \cmark \\
+notícia & no*tí*ci.a \xmark & no*tí*cia \cmark \\
+noticiário & no*ti*ci-á*ri.o \xmark & no*ti*ci*á*rio \cmark \\
+notocórdio & no*to*cór*di*o \cmark & no*to*cór*di-o \xmark \\
+notório & no*tó*ri.o \xmark & no*tó*rio \cmark \\
+núbio & nú*bi.o \xmark & nú*bio \cmark \\
+núcleo & nú*cle.o \xmark & nú*cleo \cmark \\
+núncio & nún*ci.o \xmark & nún*cio \cmark \\
+núpcias & núp*ci.as \xmark & núp*ci.as \xmark \\
+obediência & o*be*di*ên*ci.a \xmark & o*be*di*ên*cia \cmark \\
+obituário & o*bi*tu-á*ri.o \xmark & o*bi*tu*á*rio \cmark \\
+oblívio & o*blí*vi.o \xmark & o*blí*vio \cmark \\
+oboé & o*bo-é \xmark & o*bo*é \cmark \\
+oboísta & o*bo-ís*ta \xmark & o*bo*ís*ta \cmark \\
+obrigatório & o*bri*ga*tó*ri.o \xmark & o*bri*ga*tó*rio \cmark \\
+obséquio & ob*sé*qui.o \xmark & ob*sé*quio \cmark \\
+observância & ob*ser*vân*ci.a \xmark & ob*ser*vân*cia \cmark \\
+observatório & ob*ser*va*tó*ri.o \xmark & ob*ser*va*tó*rio \cmark \\
+obsolescência & ob*so*les*cên*ci.a \xmark & ob*so*les*cên*cia \cmark \\
+obstetrícia & obs*te*trí*ci.a \xmark & obs*te*trí*cia \cmark \\
+obstruído & obs*tru-í*do \xmark & obs*tru*í*do \cmark \\
+obstruir & obs*tru-ir \xmark & obs*tru*ir \cmark \\
+óbvio & ób*vi.o \xmark & ób*vio \cmark \\
+ocasião & o*ca*si-ão \xmark & o*ca*si*ão \cmark \\
+oceânico & o*ce-â*ni*co \xmark & o*ce*â*ni*co \cmark \\
+oceanografia & o*ce*a*no*gra*fi*a \cmark & o*ce*a*no*gra*fi-a \xmark \\
+oceanologia & o*ce*a*no*lo*gi*a \cmark & o*ce*a*no*lo*gi-a \xmark \\
+ócio & ó*ci.o \xmark & ó*cio \cmark \\
+oclocracia & o*clo*cra*ci*a \cmark & o*clo*cra*ci-a \xmark \\
+ocluir & o*clu-ir \xmark & o*clu*ir \cmark \\
+octaédrico & oc*ta-é*dri*co \xmark & oc*ta*é*dri*co \cmark \\
+octogenário & oc*to*ge*ná*ri.o \xmark & oc*to*ge*ná*rio \cmark \\
+odeão & o*de-ão \xmark & o*de*ão \cmark \\
+ódio & ó*di.o \xmark & ó*dio \cmark \\
+odisseia & o*dis*sei*a \cmark & o*dis*sei-a \xmark \\
+odômetro & o-dô*me*tro \xmark & o*dô*me*tro \cmark \\
+odontologia & o*don*to*lo*gi*a \cmark & o*don*to*lo*gi-a \xmark \\
+ofertório & o*fer*tó*ri.o \xmark & o*fer*tó*rio \cmark \\
+ofício & o*fí*ci.o \xmark & o*fí*cio \cmark \\
+ofidiário & o*fi*di-á*ri.o \xmark & o*fi*di*á*rio \cmark \\
+ofídio & o*fí*di.o \xmark & o*fí*dio \cmark \\
+oftalmia & of*tal*mi*a \cmark & of*tal*mi-a \xmark \\
+oftalmologia & of*tal*mo*lo*gi*a \cmark & of*tal*mo*lo*gi-a \xmark \\
+oftalmoplegia & of*tal*mo*ple*gi*a \cmark & of*tal*mo*ple*gi-a \xmark \\
+oftalmoscopia & of*tal*mos*co*pi*a \cmark & of*tal*mos*co*pi-a \xmark \\
+olaia & o*lai*a \cmark & o*lai-a \xmark \\
+olaria & o*la*ri*a \cmark & o*la*ri-a \xmark \\
+oleícola & o*le-í*co*la \xmark & o*le*í*co*la \cmark \\
+oleína & o*le-í*na \xmark & o*le*í*na \cmark \\
+oligarquia & o*li*gar*qui*a \cmark & o*li*gar*qui-a \xmark \\
+oligofrenia & o*li*go*fre*ni*a \cmark & o*li*go*fre*ni-a \xmark \\
+oligopólio & o*li*go*pó*li.o \xmark & o*li*go*pó*lio \cmark \\
+olimpíada & o*lim*pí-a*da \xmark & o*lim*pí*a*da \cmark \\
+oncologia & on*co*lo*gi*a \cmark & on*co*lo*gi-a \xmark \\
+ondulatório & on*du*la*tó*ri.o \xmark & on*du*la*tó*rio \cmark \\
+onomatopeia & o*no*ma*to*pei*a \cmark & o*no*ma*to*pei-a \xmark \\
+ontogenia & on*to*ge*ni*a \cmark & on*to*ge*ni-a \xmark \\
+ontologia & on*to*lo*gi*a \cmark & on*to*lo*gi-a \xmark \\
+oócito & o-ó*ci*to \xmark & o*ó*ci*to \cmark \\
+operário & o*pe*rá*ri.o \xmark & o*pe*rá*rio \cmark \\
+opinião & o*pi*ni-ão \xmark & o*pi*ni*ão \cmark \\
+ópio & ó*pi.o \xmark & ó*pio \cmark \\
+opróbrio & o*pró*bri.o \xmark & o*pró*brio \cmark \\
+optometria & op*to*me*tri*a \cmark & op*to*me*tri-a \xmark \\
+opulência & o*pu*lên*ci.a \xmark & o*pu*lên*cia \cmark \\
+oratória & o*ra*tó*ri.a \xmark & o*ra*tó*ria \cmark \\
+oratório & o*ra*tó*ri.o \xmark & o*ra*tó*rio \cmark \\
+orçamentário & or*ça*men*tá*ri.o \xmark & or*ça*men*tá*rio \cmark \\
+ordálio & or*dá*li.o \xmark & or*dá*lio \cmark \\
+ordinária & or*di*ná*ri.a \xmark & or*di*ná*ria \cmark \\
+ordinário & or*di*ná*ri.o \xmark & or*di*ná*rio \cmark \\
+orfeão & or*fe-ão \xmark & or*fe*ão \cmark \\
+organologia & or*ga*no*lo*gi*a \cmark & or*ga*no*lo*gi-a \xmark \\
+orgia & or*gi*a \cmark & or*gi-a \xmark \\
+oriá & o*ri-á \xmark & o*ri*á \cmark \\
+orifício & o*ri*fí*ci.o \xmark & o*ri*fí*cio \cmark \\
+oriundo & o*ri-un*do \xmark & o*ri*un*do \cmark \\
+ornitofilia & or*ni*to*fi*li*a \cmark & or*ni*to*fi*li-a \xmark \\
+ornitologia & or*ni*to*lo*gi*a \cmark & or*ni*to*lo*gi-a \xmark \\
+orogenia & o*ro*ge*ni*a \cmark & o*ro*ge*ni-a \xmark \\
+orografia & o*ro*gra*fi*a \cmark & o*ro*gra*fi-a \xmark \\
+ortodontia & or*to*don*ti*a \cmark & or*to*don*ti-a \xmark \\
+ortodôntico & or*to-dôn*ti*co \xmark & or*to*dôn*ti*co \cmark \\
+ortodoxia & or*to*do*xi*a \cmark & or*to*do*xi-a \xmark \\
+ortodromia & or*to*dro*mi*a \cmark & or*to*dro*mi-a \xmark \\
+ortopedia & or*to*pe*di*a \cmark & or*to*pe*di-a \xmark \\
+ortopraxia & or*to*pra*xi*a \cmark & or*to*pra*xi-a \xmark \\
+oscilatório & os*ci*la*tó*ri.o \xmark & os*ci*la*tó*rio \cmark \\
+ósmio & ós*mi.o \xmark & ós*mio \cmark \\
+ósseo & ós*se.o \xmark & ós*seo \cmark \\
+osteíte & os*te-í*te \xmark & os*te*í*te \cmark \\
+osteopatia & os*te*o*pa*ti*a \cmark & os*te*o*pa*ti-a \xmark \\
+otalgia & o*tal*gi*a \cmark & o*tal*gi-a \xmark \\
+otária & o*tá*ri.a \xmark & o*tá*ria \cmark \\
+otário & o*tá*ri.o \xmark & o*tá*rio \cmark \\
+otorrinolaringologia & o*tor*ri*no*la*rin*go*lo*gi*a \cmark & o*tor*ri*no*la*rin*go*lo*gi-a \xmark \\
+ourivesaria & ou*ri*ve*sa*ri*a \cmark & ou*ri*ve*sa*ri-a \xmark \\
+ousadia & ou*sa*di*a \cmark & ou*sa*di-a \xmark \\
+ouvidoria & ou*vi*do*ri*a \cmark & ou*vi*do*ri-a \xmark \\
+paciência & pa*ci*ên*ci.a \xmark & pa*ci*ên*cia \cmark \\
+padaria & pa*da*ri*a \cmark & pa*da*ri-a \xmark \\
+pagadoria & pa*ga*do*ri*a \cmark & pa*ga*do*ri-a \xmark \\
+painço & pa-in*ço \xmark & pa-in*ço \xmark \\
+paio & pai*o \cmark & pai-o \xmark \\
+país & pa-ís \xmark & pa*ís \cmark \\
+palácio & pa*lá*ci.o \xmark & pa*lá*cio \cmark \\
+paládio & pa*lá*di.o \xmark & pa*lá*dio \cmark \\
+palavrório & pa*la*vró*ri.o \xmark & pa*la*vró*rio \cmark \\
+paleógrafo & pa*le-ó*gra*fo \xmark & pa*le*ó*gra*fo \cmark \\
+palinologia & pa*li*no*lo*gi*a \cmark & pa*li*no*lo*gi-a \xmark \\
+pálio & pá*li.o \xmark & pá*lio \cmark \\
+palmatória & pal*ma*tó*ri.a \xmark & pal*ma*tó*ria \cmark \\
+panaceia & pa*na*cei*a \cmark & pa*na*cei-a \xmark \\
+panaria & pa*na*ri*a \cmark & pa*na*ri-a \xmark \\
+pancadaria & pan*ca*da*ri*a \cmark & pan*ca*da*ri-a \xmark \\
+pandemia & pan*de*mi*a \cmark & pan*de*mi-a \xmark \\
+panfletário & pan*fle*tá*ri*o \cmark & pan*fle*tá*ri-o \xmark \\
+pantagruélico & pan*ta*gru-é*li*co \xmark & pan*ta*gru*é*li*co \cmark \\
+panteão & pan*te-ão \xmark & pan*te*ão \cmark \\
+panteísmo & pan*te-ís*mo \xmark & pan*te*ís*mo \cmark \\
+panteísta & pan*te-ís*ta \xmark & pan*te*ís*ta \cmark \\
+papagaio & pa*pa*gai*o \cmark & pa*pa*gai-o \xmark \\
+papaia & pa*pai*a \cmark & pa*pai-a \xmark \\
+papelaria & pa*pe*la*ri*a \cmark & pa*pe*la*ri-a \xmark \\
+papua & pa*pu*a \cmark & pa*pu-a \xmark \\
+paquímetro & pa-quí*me*tro \xmark & pa*quí*me*tro \cmark \\
+paradisíaco & pa*ra*di*sí-a*co \xmark & pa*ra*di*sí*a*co \cmark \\
+parafernália & pa*ra*fer*ná*li.a \xmark & pa*ra*fer*ná*lia \cmark \\
+parafilia & pa*ra*fi*li*a \cmark & pa*ra*fi*li-a \xmark \\
+paraguaia & pa*ra*guai*a \cmark & pa*ra*guai-a \xmark \\
+paraguaio & pa*ra*guai*o \cmark & pa*ra*guai-o \xmark \\
+paraibano & pa*ra-i*ba*no \xmark & pa*ra-i*ba*no \xmark \\
+paraíba & pa*ra-í*ba \xmark & pa*ra*í*ba \cmark \\
+paraíso & pa*ra-í*so \xmark & pa*ra*í*so \cmark \\
+paralisia & pa*ra*li*si*a \cmark & pa*ra*li*si-a \xmark \\
+paranoia & pa*ra*noi*a \cmark & pa*ra*noi-a \xmark \\
+paranomásia & pa*ra*no*má*si.a \xmark & pa*ra*no*má*sia \cmark \\
+paraplegia & pa*ra*ple*gi*a \cmark & pa*ra*ple*gi-a \xmark \\
+parasitologia & pa*ra*si*to*lo*gi*a \cmark & pa*ra*si*to*lo*gi-a \xmark \\
+parceria & par*ce*ri*a \cmark & par*ce*ri-a \xmark \\
+páreo & pá*re.o \xmark & pá*reo \cmark \\
+paresia & pa*re*si*a \cmark & pa*re*si-a \xmark \\
+parestesia & pa*res*te*si*a \cmark & pa*res*te*si-a \xmark \\
+pária & pá*ri.a \xmark & pá*ria \cmark \\
+paritário & pa*ri*tá*ri*o \cmark & pa*ri*tá*ri-o \xmark \\
+parlatório & par*la*tó*ri.o \xmark & par*la*tó*rio \cmark \\
+parnaíba & par*na-í*ba \xmark & par*na*í*ba \cmark \\
+paródia & pa*ró*di.a \xmark & pa*ró*dia \cmark \\
+paroníquia & pa*ro*ní*qui*a \cmark & pa*ro*ní*qui-a \xmark \\
+paronomásia & pa*ro*no*má*si.a \xmark & pa*ro*no*má*sia \cmark \\
+paróquia & pa*ró*qui.a \xmark & pa*ró*quia \cmark \\
+parquê & par-quê \xmark & par*quê \cmark \\
+parquímetro & par-quí*me*tro \xmark & par*quí*me*tro \cmark \\
+parricídio & par*ri*cí*di.o \xmark & par*ri*cí*dio \cmark \\
+particípio & par*ti*cí*pi.o \xmark & par*ti*cí*pio \cmark \\
+partidário & par*ti*dá*ri.o \xmark & par*ti*dá*rio \cmark \\
+parusia & pa*ru*si*a \cmark & pa*ru*si-a \xmark \\
+parvoíce & par*vo-í*ce \xmark & par*vo*í*ce \cmark \\
+pascácio & pas*cá*ci.o \xmark & pas*cá*cio \cmark \\
+passamanaria & pas*sa*ma*na*ri*a \cmark & pas*sa*ma*na*ri-a \xmark \\
+passeio & pas*sei*o \cmark & pas*sei-o \xmark \\
+pastelaria & pas*te*la*ri*a \cmark & pas*te*la*ri-a \xmark \\
+pastoreio & pas*to*rei*o \cmark & pas*to*rei-o \xmark \\
 patchuli & pat*chu*li \cmark & pat-chu*li \xmark \\
-pecuário & pe*cu-á*ri*o \xmark & pe*cu*á*ri*o \cmark \\
-psicolinguista & p.si*co*lin*guis*ta \xmark & psi*co*lin*guis*ta \cmark \\
-psicolinguística & p.si*co*lin*guís*ti*ca \xmark & psi*co*lin*guís*ti*ca \cmark \\
-psicomotor & p.si*co*mo*tor \xmark & psi*co*mo*tor \cmark \\
-psicomotricista & p.si*co*mo*tri*cis*ta \xmark & psi*co*mo*tri*cis*ta \cmark \\
-psicopatia & p.si*co*pa*ti*a \xmark & psi*co*pa*ti*a \cmark \\
-psicopedagogo & p.si*co*pe*da*go*go \xmark & psi*co*pe*da*go*go \cmark \\
-psicossomática & p.si*cos*so*má*ti*ca \xmark & psi*cos*so*má*ti*ca \cmark \\
-reconstituinte & re*cons*ti*tu-in*te \xmark & re*cons*ti*tu-in*te \xmark \\
-reincidir & re-in*ci*dir \xmark & re*in*ci*dir \cmark \\
-saruê & sa*ru-ê \xmark & sa*ru*ê \cmark \\
-subaquático & su*ba-quá*ti*co \xmark & su*ba*quá*ti*co \cmark \\
-subliteratura & su.b-li*te*ra*tu*ra \xmark & sub*li*te*ra*tu*ra \cmark \\
-subsidiário & sub*si*di-á*ri*o \xmark & sub*si*di*á*ri*o \cmark \\
-substituível & subs*ti*tu-í*vel \xmark & subs*ti*tu*í*vel \cmark \\
-teutônico & teu-tô*ni*co \xmark & teu*tô*ni*co \cmark \\
-tmese & t.me*se \xmark & tme*se \cmark \\
-toboágua & to*bo-á*gua \xmark & to*bo*á*gua \cmark \\
-aldeão & al*de-ão \xmark & al*de*ão \cmark \\
-amniocentese & am*ni*o*cen*te*se \cmark & a.m-ni*o*cen*te*se \xmark \\
-anamnese & a*nam*ne*se \cmark & a*na.m-ne*se \xmark \\
-anauê & a*nau-ê \xmark & a*nau*ê \cmark \\
-antipatriótico & an*ti*pa*tri-ó*ti*co \xmark & an*ti*pa*tri*ó*ti*co \cmark \\
-antônimo & an-tô*ni*mo \xmark & an*tô*ni*mo \cmark \\
-antropônimo & an*tro-pô*ni*mo \xmark & an*tro*pô*ni*mo \cmark \\
-aviário & a*vi-á*ri*o \xmark & a*vi*á*ri*o \cmark \\
-babalaô & ba*ba*la-ô \xmark & ba*ba*la*ô \cmark \\
-braúna & bra-ú*na \xmark & bra*ú*na \cmark \\
-corruíra & cor*ru-í*ra \xmark & cor*ru*í*ra \cmark \\
-corrupião & cor*ru*pi-ão \xmark & cor*ru*pi*ão \cmark \\
-decaído & de*ca-í*do \xmark & de*ca*í*do \cmark \\
-deificação & de-i*fi*ca*ção \xmark & de-i*fi*ca*ção \xmark \\
-demiurgo & de*mi-ur*go \xmark & de*mi*ur*go \cmark \\
-descair & des*ca-ir \xmark & des*ca*ir \cmark \\
-desembainhar & de*sem*ba-i*nhar \xmark & de*sem*ba*i*nhar \cmark \\
-diáfano & di-á*fa*no \xmark & di*á*fa*no \cmark \\
-dicotômico & di*co-tô*mi*co \xmark & di*co*tô*mi*co \cmark \\
-dodecafônico & do*de*ca-fô*ni*co \xmark & do*de*ca*fô*ni*co \cmark \\
-ensaístico & en*sa-ís*ti*co \xmark & en*sa*ís*ti*co \cmark \\
-entusiástico & en*tu*si-ás*ti*co \xmark & en*tu*si*ás*ti*co \cmark \\
-epônimo & e-pô*ni*mo \xmark & e*pô*ni*mo \cmark \\
-espectrofotômetro & es*pec*tro*fo-tô*me*tro \xmark & es*pec*tro*fo*tô*me*tro \cmark \\
-estatuária & es*ta*tu-á*ri*a \xmark & es*ta*tu*á*ri*a \cmark \\
-faim & fa-im \xmark & fa-im \xmark \\
-fitoquímica & fi*to-quí*mi*ca \xmark & fi*to*quí*mi*ca \cmark \\
-formaldeído & for*mal*de-í*do \xmark & for*mal*de*í*do \cmark \\
-fuinha & fu-i*nha \xmark & fu*i*nha \cmark \\
-gabião & ga*bi-ão \xmark & ga*bi*ão \cmark \\
-gauchada & ga-u*cha*da \xmark & ga-u*cha*da \xmark \\
-gauchismo & ga-u*chis*mo \xmark & ga-u*chis*mo \xmark \\
-geriátrico & ge*ri-á*tri*co \xmark & ge*ri*á*tri*co \cmark \\
-gipsita & gip*si*ta \cmark & gip-si*ta \xmark \\
-guião & gui-ão \xmark & gui*ão \cmark \\
-ilíaco & i*lí-a*co \xmark & i*lí*a*co \cmark \\
-iniciático & i*ni*ci-á*ti*co \xmark & i*ni*ci*á*ti*co \cmark \\
-itapuá & i*ta*pu-á \xmark & i*ta*pu*á \cmark \\
-japuí & ja*pu-í \xmark & ja*pu*í \cmark \\
-jesuítico & je*su-í*ti*co \xmark & je*su*í*ti*co \cmark \\
-lamaísmo & la*ma-ís*mo \xmark & la*ma*ís*mo \cmark \\
-mantô & man-tô \xmark & man*tô \cmark \\
-metapsicologia & me*tap*si*co*lo*gi*a \cmark & me*tap-si*co*lo*gi*a \xmark \\
-mitocôndria & mi*to-côn*dri*a \xmark & mi*to*côn*dri*a \cmark \\
-miudeza & mi-u*de*za \xmark & mi-u*de*za \xmark \\
-monomaníaco & mo*no*ma*ní-a*co \xmark & mo*no*ma*ní*a*co \cmark \\
-museólogo & mu*se-ó*lo*go \xmark & mu*se*ó*lo*go \cmark \\
-ninfomaníaca & nin*fo*ma*ní-a*ca \xmark & nin*fo*ma*ní*a*ca \cmark \\
-nobiliárquico & no*bi*li-ár*qui*co \xmark & no*bi*li*ár*qui*co \cmark \\
-odômetro & o-dô*me*tro \xmark & o*dô*me*tro \cmark \\
-orgiástico & or*gi-ás*ti*co \xmark & or*gi*ás*ti*co \cmark \\
-painço & pa-in*ço \xmark & pa-in*ço \xmark \\
-pantagruélico & pan*ta*gru-é*li*co \xmark & pan*ta*gru*é*li*co \cmark \\
-parquímetro & par-quí*me*tro \xmark & par*quí*me*tro \cmark \\
+patenteável & pa*ten*te-á*vel \xmark & pa*ten*te*á*vel \cmark \\
+pátio & pá*ti.o \xmark & pá*tio \cmark \\
+patoá & pa*to-á \xmark & pa*to*á \cmark \\
+patogenia & pa*to*ge*ni*a \cmark & pa*to*ge*ni-a \xmark \\
+patologia & pa*to*lo*gi*a \cmark & pa*to*lo*gi-a \xmark \\
+pátria & pá*tri.a \xmark & pá*tria \cmark \\
+patrícia & pa*trí*ci.a \xmark & pa*trí*cia \cmark \\
+patrício & pa*trí*ci.o \xmark & pa*trí*cio \cmark \\
+pátrio & pá*tri.o \xmark & pá*trio \cmark \\
+patriótico & pa*tri-ó*ti*co \xmark & pa*tri*ó*ti*co \cmark \\
+patroa & pa*tro*a \cmark & pa*tro-a \xmark \\
+patuá & pa*tu-á \xmark & pa*tu*á \cmark \\
+patuleia & pa*tu*lei*a \cmark & pa*tu*lei-a \xmark \\
+paul & pa-ul \xmark & pa-ul \xmark \\
+pavio & pa*vi*o \cmark & pa*vi-o \xmark \\
+pavoa & pa*vo*a \cmark & pa*vo-a \xmark \\
+paxiúba & pa*xi-ú*ba \xmark & pa*xi*ú*ba \cmark \\
+peão & pe-ão \xmark & pe*ão \cmark \\
+peã & pe-ã \xmark & pe*ã \cmark \\
+pecíolo & pe*cí-o*lo \xmark & pe*cí*o*lo \cmark \\
+pecuária & pe*cu-á*ri.a \xmark & pe*cu*á*ria \cmark \\
+pecuário & pe*cu-á*ri.o \xmark & pe*cu*á*rio \cmark \\
+pecúlio & pe*cú*li.o \xmark & pe*cú*lio \cmark \\
+pecúnia & pe*cú*ni.a \xmark & pe*cú*nia \cmark \\
+pecuniário & pe*cu*ni-á*ri.o \xmark & pe*cu*ni*á*rio \cmark \\
+pedágio & pe*dá*gi.o \xmark & pe*dá*gio \cmark \\
+pedagogia & pe*da*go*gi*a \cmark & pe*da*go*gi-a \xmark \\
+pederastia & pe*de*ras*ti*a \cmark & pe*de*ras*ti-a \xmark \\
+pediatria & pe*di*a*tri*a \cmark & pe*di*a*tri-a \xmark \\
+pediátrico & pe*di-á*tri*co \xmark & pe*di*á*tri*co \cmark \\
+pedofilia & pe*do*fi*li*a \cmark & pe*do*fi*li-a \xmark \\
+pedofobia & pe*do*fo*bi*a \cmark & pe*do*fo*bi-a \xmark \\
+pedologia & pe*do*lo*gi*a \cmark & pe*do*lo*gi-a \xmark \\
+pedraria & pe*dra*ri*a \cmark & pe*dra*ri-a \xmark \\
+peia & pei*a \cmark & pei-a \xmark \\
+peixaria & pei*xa*ri*a \cmark & pei*xa*ri-a \xmark \\
+pelúcia & pe*lú*ci.a \xmark & pe*lú*cia \cmark \\
+pendência & pen*dên*ci.a \xmark & pen*dên*cia \cmark \\
+penedia & pe*ne*di*a \cmark & pe*ne*di-a \xmark \\
+peneplanície & pe*ne*pla*ní*ci.e \xmark & pe*ne*pla*ní*cie \cmark \\
+penitenciária & pe*ni*ten*ci-á*ri.a \xmark & pe*ni*ten*ci*á*ria \cmark \\
+penitenciário & pe*ni*ten*ci-á*ri.o \xmark & pe*ni*ten*ci*á*rio \cmark \\
+pentarquia & pen*tar*qui*a \cmark & pen*tar*qui-a \xmark \\
+penúria & pe*nú*ri.a \xmark & pe*nú*ria \cmark \\
+perdoável & per*do-á*vel \xmark & per*do*á*vel \cmark \\
+perdulário & per*du*lá*ri.o \xmark & per*du*lá*rio \cmark \\
+perfídia & per*fí*di.a \xmark & per*fí*dia \cmark \\
+perfumaria & per*fu*ma*ri*a \cmark & per*fu*ma*ri-a \xmark \\
+perícia & pe*rí*ci.a \xmark & pe*rí*cia \cmark \\
+periélio & pe*ri-é*li.o \xmark & pe*ri*é*lio \cmark \\
+periferia & pe*ri*fe*ri*a \cmark & pe*ri*fe*ri-a \xmark \\
+períneo & pe*rí*ne.o \xmark & pe*rí*neo \cmark \\
+periódico & pe*ri-ó*di*co \xmark & pe*ri*ó*di*co \cmark \\
+período & pe*rí-o*do \xmark & pe*rí*o*do \cmark \\
+peripécia & pe*ri*pé*ci.a \xmark & pe*ri*pé*cia \cmark \\
+periscópio & pe*ris*có*pi.o \xmark & pe*ris*có*pio \cmark \\
+periurbano & pe*ri-ur*ba*no \xmark & pe*ri*ur*ba*no \cmark \\
+permeável & per*me-á*vel \xmark & per*me*á*vel \cmark \\
+permeio & per*mei*o \cmark & per*mei-o \xmark \\
+pérsio & pér*si.o \xmark & pér*sio \cmark \\
+persistência & per*sis*tên*ci.a \xmark & per*sis*tên*cia \cmark \\
+pertinácia & per*ti*ná*ci.a \xmark & per*ti*ná*cia \cmark \\
+pertinência & per*ti*nên*ci.a \xmark & per*ti*nên*cia \cmark \\
+perua & pe*ru*a \cmark & pe*ru-a \xmark \\
+pescaria & pes*ca*ri*a \cmark & pes*ca*ri-a \xmark \\
+pessoa & pes*so*a \cmark & pes*so-a \xmark \\
+pestilência & pes*ti*lên*ci.a \xmark & pes*ti*lên*cia \cmark \\
+pétreo & pé*tre.o \xmark & pé*treo \cmark \\
+petróleo & pe*tró*le.o \xmark & pe*tró*leo \cmark \\
+petrologia & pe*tro*lo*gi*a \cmark & pe*tro*lo*gi-a \xmark \\
+petroquímica & pe*tro-quí*mi*ca \xmark & pe*tro*quí*mi*ca \cmark \\
+petroquímico & pe*tro-quí*mi*co \xmark & pe*tro*quí*mi*co \cmark \\
+petulância & pe*tu*lân*ci.a \xmark & pe*tu*lân*cia \cmark \\
+petúnia & pe*tú*ni*a \cmark & pe*tú*ni-a \xmark \\
+pia & pi*a \cmark & pi-a \xmark \\
+piá & pi-á \xmark & pi*á \cmark \\
+piauiense & pi*au-i*en*se \xmark & pi*au*i*en*se \cmark \\
+picardia & pi*car*di*a \cmark & pi*car*di-a \xmark \\
+pictografia & pic*to*gra*fi*a \cmark & pic*to*gra*fi-a \xmark \\
+picuinha & pi*cu-i*nha \xmark & pi*cu*i*nha \cmark \\
+piério & pi-é*ri.o \xmark & pi*é*rio \cmark \\
+pífio & pí*fi*o \cmark & pí*fi-o \xmark \\
+pigmeia & pig*mei*a \cmark & pig*mei-a \xmark \\
+píleo & pí*le*o \cmark & pí*le-o \xmark \\
+pilhéria & pi*lhé*ri*a \cmark & pi*lhé*ri-a \xmark \\
+pindaíba & pin*da-í*ba \xmark & pin*da*í*ba \cmark \\
+pintainho & pin*ta-i*nho \xmark & pin*ta*i*nho \cmark \\
+pio & pi*o \cmark & pi-o \xmark \\
+piraí & pi*ra-í \xmark & pi*ra*í \cmark \\
+pirataria & pi*ra*ta*ri*a \cmark & pi*ra*ta*ri-a \xmark \\
+piromancia & pi*ro*man*ci*a \cmark & pi*ro*man*ci-a \xmark \\
+piromaníaco & pi*ro*ma*ní-a*co \xmark & pi*ro*ma*ní*a*co \cmark \\
+piromania & pi*ro*ma*ni*a \cmark & pi*ro*ma*ni-a \xmark \\
+pirotecnia & pi*ro*tec*ni*a \cmark & pi*ro*tec*ni-a \xmark \\
+piruá & pi*ru-á \xmark & pi*ru*á \cmark \\
+piscatória & pis*ca*tó*ri.a \xmark & pis*ca*tó*ria \cmark \\
+pisoteio & pi*so*tei*o \cmark & pi*so*tei-o \xmark \\
+pitiríase & pi*ti*rí-a*se \xmark & pi*ti*rí*a*se \cmark \\
+pium & pi-um \xmark & pi*um \cmark \\
+pivô & pi-vô \xmark & pi*vô \cmark \\
 pixaim & pi*xa-im \xmark & pi*xa-im \xmark \\
+pizzaria & piz*za*ri*a \cmark & piz*za*ri-a \xmark \\
+plagiário & pla*gi-á*ri.o \xmark & pla*gi*á*rio \cmark \\
+plágio & plá*gi.o \xmark & plá*gio \cmark \\
+planetário & pla*ne*tá*ri.o \xmark & pla*ne*tá*rio \cmark \\
+planície & pla*ní*ci.e \xmark & pla*ní*cie \cmark \\
+plantio & plan*ti*o \cmark & plan*ti-o \xmark \\
+plateia & pla*tei*a \cmark & pla*tei-a \xmark \\
+platônico & pla-tô*ni*co \xmark & pla*tô*ni*co \cmark \\
+platô & pla-tô \xmark & pla*tô \cmark \\
+plebeísmo & ple*be-ís*mo \xmark & ple*be*ís*mo \cmark \\
+plenário & ple*ná*ri.o \xmark & ple*ná*rio \cmark \\
+plenilúnio & ple*ni*lú*ni.o \xmark & ple*ni*lú*nio \cmark \\
+pleurisia & pleu*ri*si*a \cmark & pleu*ri*si-a \xmark \\
+plúmbeo & plúm*be.o \xmark & plúm*beo \cmark \\
+plutocracia & plu*to*cra*ci*a \cmark & plu*to*cra*ci-a \xmark \\
+pluviometria & plu*vi*o*me*tri*a \cmark & plu*vi*o*me*tri-a \xmark \\
 pneumática & p.neu*má*ti*ca \xmark & pneu*má*ti*ca \cmark \\
 pneumático & p.neu*má*ti*co \xmark & pneu*má*ti*co \cmark \\
-preá & pre-á \xmark & pre*á \cmark \\
-priápico & pri-á*pi*co \xmark & pri*á*pi*co \cmark \\
-psicopedagógico & p.si*co*pe*da*gó*gi*co \xmark & psi*co*pe*da*gó*gi*co \cmark \\
-psicossomático & p.si*cos*so*má*ti*co \xmark & psi*cos*so*má*ti*co \cmark \\
-psicotrópico & p.si*co*tró*pi*co \xmark & psi*co*tró*pi*co \cmark \\
-pterossauro & p.te*ros*sau*ro \xmark & pte*ros*sau*ro \cmark \\
-quilohertz & qui*lo-hertz \xmark & qui*lo-hertz \xmark \\
-recôndito & re-côn*di*to \xmark & re*côn*di*to \cmark \\
-reimplantação & re-im*plan*ta*ção \xmark & re*im*plan*ta*ção \cmark \\
-reincorporar & re-in*cor*po*rar \xmark & re*in*cor*po*rar \cmark \\
-reingressar & re-in*gres*sar \xmark & re*in*gres*sar \cmark \\
-reinvestir & re-in*ves*tir \xmark & re*in*ves*tir \cmark \\
-restituível & res*ti*tu-í*vel \xmark & res*ti*tu*í*vel \cmark \\
-retrair & re*tra-ir \xmark & re*tra*ir \cmark \\
-rodamoinho & ro*da*mo-i*nho \xmark & ro*da*mo*i*nho \cmark \\
-roído & ro-í*do \xmark & ro*í*do \cmark \\
-ruão & ru-ão \xmark & ru*ão \cmark \\
-salomônico & sa*lo-mô*ni*co \xmark & sa*lo*mô*ni*co \cmark \\
-sardônico & sar-dô*ni*co \xmark & sar*dô*ni*co \cmark \\
-semiólogo & se*mi-ó*lo*go \xmark & se*mi*ó*lo*go \cmark \\
-solipsismo & so*lip*sis*mo \cmark & so*lip-sis*mo \xmark \\
-sumaúma & su*ma-ú*ma \xmark & su*ma*ú*ma \cmark \\
-tataravô & ta*ta*ra-vô \xmark & ta*ta*ra*vô \cmark \\
-termoquímica & ter*mo-quí*mi*ca \xmark & ter*mo*quí*mi*ca \cmark \\
-topônimo & to-pô*ni*mo \xmark & to*pô*ni*mo \cmark \\
-toxicômano & to*xi-cô*ma*no \xmark & to*xi*cô*ma*no \cmark \\
-trisavô & tri*sa-vô \xmark & tri*sa*vô \cmark \\
-triunvirato & tri-un*vi*ra*to \xmark & tri*un*vi*ra*to \cmark \\
-voyeurístico & voy-eu*rís*ti*co \xmark & voy-eu*rís*ti*co \xmark \\
-xintoísmo & xin*to-ís*mo \xmark & xin*to*ís*mo \cmark \\
-absenteísta & ab*sen*te-ís*ta \xmark & ab*sen*te*ís*ta \cmark \\
-aeroviário & a*e*ro*vi-á*ri*o \xmark & a*e*ro*vi*á*ri*o \cmark \\
-afluir & a*flu-ir \xmark & a*flu*ir \cmark \\
-agroquímico & a*gro-quí*mi*co \xmark & a*gro*quí*mi*co \cmark \\
-aguaí & a*gua-í \xmark & a*gua*í \cmark \\
-alquímico & al-quí*mi*co \xmark & al*quí*mi*co \cmark \\
-amnesia & am*ne*si*a \cmark & a.m-ne*si*a \xmark \\
-amnésico & am*né*si*co \cmark & a.m-né*si*co \xmark \\
-anafrodisíaco & a*na*fro*di*sí-a*co \xmark & a*na*fro*di*sí*a*co \cmark \\
-antialcoólico & an*ti*al*co-ó*li*co \xmark & an*ti*al*co*ó*li*co \cmark \\
-antinômico & an*ti-nô*mi*co \xmark & an*ti*nô*mi*co \cmark \\
-anuir & a*nu-ir \xmark & a*nu*ir \cmark \\
-arapuá & a*ra*pu-á \xmark & a*ra*pu*á \cmark \\
-aríete & a*rí-e*te \xmark & a*rí-e*te \xmark \\
-associável & as*so*ci-á*vel \xmark & as*so*ci*á*vel \cmark \\
-atribuível & a*tri*bu-í*vel \xmark & a*tri*bu*í*vel \cmark \\
-babilônico & ba*bi-lô*ni*co \xmark & ba*bi*lô*ni*co \cmark \\
-balaustrada & ba*la-us*tra*da \xmark & ba*la-us*tra*da \xmark \\
-beócio & be-ó*ci*o \xmark & be*ó*ci*o \cmark \\
-biófilo & bi-ó*fi*lo \xmark & bi*ó*fi*lo \cmark \\
-biunívoco & bi-u*ní*vo*co \xmark & bi*u*ní*vo*co \cmark \\
-boião & boi-ão \xmark & boi*ão \cmark \\
-boiuna & boi-u*na \xmark & boi*u*na \cmark \\
-butiá & bu*ti-á \xmark & bu*ti*á \cmark \\
-caingangue & ca-in*gan*gue \xmark & ca-in*gan*gue \xmark \\
-carnaíba & car*na-í*ba \xmark & car*na*í*ba \cmark \\
-caúna & ca-ú*na \xmark & ca*ú*na \cmark \\
-ciática & ci-á*ti*ca \xmark & ci*á*ti*ca \cmark \\
-clepsidra & clep*si*dra \cmark & clep-si*dra \xmark \\
-codeína & co*de-í*na \xmark & co*de*í*na \cmark \\
-conciliábulo & con*ci*li-á*bu*lo \xmark & con*ci*li*á*bu*lo \cmark \\
-conciliável & con*ci*li-á*vel \xmark & con*ci*li*á*vel \cmark \\
-condoído & con*do-í*do \xmark & con*do*í*do \cmark \\
-confluir & con*flu-ir \xmark & con*flu*ir \cmark \\
-congruência & con*gru-ên*ci*a \xmark & con*gru*ên*ci*a \cmark \\
-crapô & cra-pô \xmark & cra*pô \cmark \\
-criptônimo & crip-tô*ni*mo \xmark & crip*tô*ni*mo \cmark \\
-deão & de-ão \xmark & de*ão \cmark \\
-decacampeão & de*ca*cam*pe-ão \xmark & de*ca*cam*pe*ão \cmark \\
-demiúrgico & de*mi-úr*gi*co \xmark & de*mi*úr*gi*co \cmark \\
-depreciável & de*pre*ci-á*vel \xmark & de*pre*ci*á*vel \cmark \\
-descaída & des*ca-í*da \xmark & des*ca*í*da \cmark \\
-dzeta & d.ze*ta \xmark & d.ze*ta \xmark \\
-elefantíase & e*le*fan*tí-a*se \xmark & e*le*fan*tí*a*se \cmark \\
-eletroímã & e*le*tro-í*mã \xmark & e*le*tro*í*mã \cmark \\
-eólico & e-ó*li*co \xmark & e*ó*li*co \cmark \\
-eólio & e-ó*li*o \xmark & e*ó*li*o \cmark \\
-epifenômeno & e*pi*fe-nô*me*no \xmark & e*pi*fe*nô*me*no \cmark \\
-escarabeídeo & es*ca*ra*be-í*de*o \xmark & es*ca*ra*be*í*de*o \cmark \\
-espadaúdo & es*pa*da-ú*do \xmark & es*pa*da*ú*do \cmark \\
-espeleólogo & es*pe*le-ó*lo*go \xmark & es*pe*le*ó*lo*go \cmark \\
-faiscante & fa-is*can*te \xmark & fa-is*can*te \xmark \\
-feiura & fei-u*ra \xmark & fei*u*ra \cmark \\
-fotômetro & fo-tô*me*tro \xmark & fo*tô*me*tro \cmark \\
-franqueável & fran*que-á*vel \xmark & fran*que*á*vel \cmark \\
-gastrointestinal & gas*tro-in*tes*ti*nal \xmark & gas*tro*in*tes*ti*nal \cmark \\
-gauchar & ga-u*char \xmark & ga-u*char \xmark \\
-gnosticismo & g.nos*ti*cis*mo \xmark & gnos*ti*cis*mo \cmark \\
-gnóstico & g.nós*ti*co \xmark & gnós*ti*co \cmark \\
-gnu & g.nu \xmark & g.nu \xmark \\
-grafomaníaco & gra*fo*ma*ní-a*co \xmark & gra*fo*ma*ní*a*co \cmark \\
-grafômano & gra-fô*ma*no \xmark & gra*fô*ma*no \cmark \\
-grapiúna & gra*pi-ú*na \xmark & gra*pi*ú*na \cmark \\
-heterônimo & he*te-rô*ni*mo \xmark & he*te*rô*ni*mo \cmark \\
-hexacampeão & he*xa*cam*pe-ão \xmark & he*xa*cam*pe*ão \cmark \\
-hinduísta & hin*du-ís*ta \xmark & hin*du*ís*ta \cmark \\
-holonômico & ho*lo-nô*mi*co \xmark & ho*lo*nô*mi*co \cmark \\
-homofônico & ho*mo-fô*ni*co \xmark & ho*mo*fô*ni*co \cmark \\
-ibijaú & i*bi*ja-ú \xmark & i*bi*ja*ú \cmark \\
-idiótico & i*di-ó*ti*co \xmark & i*di*ó*ti*co \cmark \\
-imbuir & im*bu-ir \xmark & im*bu*ir \cmark \\
-inclinômetro & in*cli-nô*me*tro \xmark & in*cli*nô*me*tro \cmark \\
-irreconciliável & ir*re*con*ci*li-á*vel \xmark & ir*re*con*ci*li*á*vel \cmark \\
-irreligião & ir*re*li*gi-ão \xmark & ir*re*li*gi*ão \cmark \\
-irrenunciável & ir*re*nun*ci-á*vel \xmark & ir*re*nun*ci*á*vel \cmark \\
-isquêmico & is-quê*mi*co \xmark & is*quê*mi*co \cmark \\
-itapiúna & i*ta*pi-ú*na \xmark & i*ta*pi*ú*na \cmark \\
-juá & ju-á \xmark & ju*á \cmark \\
-lamaísta & la*ma-ís*ta \xmark & la*ma*ís*ta \cmark \\
-luteína & lu*te-í*na \xmark & lu*te*í*na \cmark \\
-macrorregião & ma*cror*re*gi-ão \xmark & ma*cror*re*gi*ão \cmark \\
-mandrião & man*dri-ão \xmark & man*dri*ão \cmark \\
-masdeísmo & mas*de-ís*mo \xmark & mas*de*ís*mo \cmark \\
-maué & mau-é \xmark & mau*é \cmark \\
-mediático & me*di-á*ti*co \xmark & me*di*á*ti*co \cmark \\
-melômano & me-lô*ma*no \xmark & me*lô*ma*no \cmark \\
-mnemônica & m.ne-mô*ni*ca \xmark & mne*mô*ni*ca \cmark \\
-moinha & mo-i*nha \xmark & mo*i*nha \cmark \\
-monômero & mo-nô*me*ro \xmark & mo*nô*me*ro \cmark \\
-monoquíni & mo*no-quí*ni \xmark & mo*no*quí*ni \cmark \\
-monoteísta & mo*no*te-ís*ta \xmark & mo*no*te*ís*ta \cmark \\
-mortuárias & mor*tu-á*ri*as \xmark & mor*tu*á*ri*as \cmark \\
-mucuim & mu*cu-im \xmark & mu*cu-im \xmark \\
-negligenciável & ne*gli*gen*ci-á*vel \xmark & ne*gli*gen*ci*á*vel \cmark \\
-neuropsiquiatria & neu*rop*si*qui*a*tri*a \cmark & neu*rop-si*qui*a*tri*a \xmark \\
-oboísta & o*bo-ís*ta \xmark & o*bo*ís*ta \cmark \\
-ofidiário & o*fi*di-á*ri*o \xmark & o*fi*di*á*ri*o \cmark \\
-oleína & o*le-í*na \xmark & o*le*í*na \cmark \\
-opiáceo & o*pi-á*ce*o \xmark & o*pi*á*ce*o \cmark \\
-pancreático & pan*cre-á*ti*co \xmark & pan*cre*á*ti*co \cmark \\
-panô & pa-nô \xmark & pa*nô \cmark \\
-parquê & par-quê \xmark & par*quê \cmark \\
-parvoíce & par*vo-í*ce \xmark & par*vo*í*ce \cmark \\
-patenteável & pa*ten*te-á*vel \xmark & pa*ten*te*á*vel \cmark \\
-peã & pe-ã \xmark & pe*ã \cmark \\
-periósteo & pe*ri-ós*te*o \xmark & pe*ri*ós*te*o \cmark \\
-picuá & pi*cu-á \xmark & pi*cu*á \cmark \\
-piquê & pi-quê \xmark & pi*quê \cmark \\
-piromaníaco & pi*ro*ma*ní-a*co \xmark & pi*ro*ma*ní*a*co \cmark \\
-piruá & pi*ru-á \xmark & pi*ru*á \cmark \\
-piúria & pi-ú*ri*a \xmark & pi*ú*ri*a \cmark \\
-plagiário & pla*gi-á*ri*o \xmark & pla*gi*á*ri*o \cmark \\
-plebeísmo & ple*be-ís*mo \xmark & ple*be*ís*mo \cmark \\
-plenipotenciário & ple*ni*po*ten*ci-á*ri*o \xmark & ple*ni*po*ten*ci*á*ri*o \cmark \\
-pneumatologia & p.neu*ma*to*lo*gi*a \xmark & pneu*ma*to*lo*gi*a \cmark \\
+pneumatologia & p.neu*ma*to*lo*gi*a \xmark & pneu*ma*to*lo*gi-a \xmark \\
+pneumococo & p.neu*mo*co*co \xmark & pneu*mo*co*co \cmark \\
+pneumoconiose & p.neu*mo*co*ni*o*se \xmark & pneu*mo*co*ni*o*se \cmark \\
+pneumogástrico & p.neu*mo*gás*tri*co \xmark & pneu*mo*gás*tri*co \cmark \\
+pneumologia & p.neu*mo*lo*gi*a \xmark & pneu*mo*lo*gi-a \xmark \\
+pneumonia & p.neu*mo*ni*a \xmark & pneu*mo*ni-a \xmark \\
 pneumônico & p.neu-mô*ni*co \xmark & pneu*mô*ni*co \cmark \\
+pneumotórax & p.neu*mo*tó*rax \xmark & pneu*mo*tó*rax \cmark \\
+pneu & p.neu \xmark & pneu \cmark \\
+poderio & po*de*ri*o \cmark & po*de*ri-o \xmark \\
+pódio & pó*di.o \xmark & pó*dio \cmark \\
+podologia & po*do*lo*gi*a \cmark & po*do*lo*gi-a \xmark \\
+poesia & po*e*si*a \cmark & po*e*si-a \xmark \\
+poética & po-é*ti*ca \xmark & po*é*ti*ca \cmark \\
+poético & po-é*ti*co \xmark & po*é*ti*co \cmark \\
+poia & poi*a \cmark & poi-a \xmark \\
+poio & poi*o \cmark & poi-o \xmark \\
+poliandria & po*li*an*dri*a \cmark & po*li*an*dri-a \xmark \\
+polia & po*li*a \cmark & po*li-a \xmark \\
+polícia & po*lí*ci.a \xmark & po*lí*cia \cmark \\
+policitemia & po*li*ci*te*mi*a \cmark & po*li*ci*te*mi-a \xmark \\
+policromia & po*li*cro*mi*a \cmark & po*li*cro*mi-a \xmark \\
+polidipsia & po*li*dip*si*a \cmark & po*li*dip*si-a \xmark \\
+poliéster & po*li-és*ter \xmark & po*li*és*ter \cmark \\
+polifagia & po*li*fa*gi*a \cmark & po*li*fa*gi-a \xmark \\
 polifônico & po*li-fô*ni*co \xmark & po*li*fô*ni*co \cmark \\
+poliginia & po*li*gi*ni*a \cmark & po*li*gi*ni-a \xmark \\
+polimorfia & po*li*mor*fi*a \cmark & po*li*mor*fi-a \xmark \\
+poliploidia & po*li*ploi*di*a \cmark & po*li*ploi*di-a \xmark \\
+polirritmia & po*lir*rit*mi*a \cmark & po*lir*rit*mi-a \xmark \\
+polissacarídeo & po*lis*sa*ca*rí*de.o \xmark & po*lis*sa*ca*rí*deo \cmark \\
+polissemia & po*lis*se*mi*a \cmark & po*lis*se*mi-a \xmark \\
 politeísmo & po*li*te-ís*mo \xmark & po*li*te*ís*mo \cmark \\
 politeísta & po*li*te-ís*ta \xmark & po*li*te*ís*ta \cmark \\
-politiquês & po*li*ti-quês \xmark & po*li*ti*quês \cmark \\
+poliúria & po*li-ú*ri.a \xmark & po*li*ú*ria \cmark \\
+poluir & po*lu-ir \xmark & po*lu*ir \cmark \\
+pontaria & pon*ta*ri*a \cmark & pon*ta*ri-a \xmark \\
+pontifício & pon*ti*fí*ci.o \xmark & pon*ti*fí*cio \cmark \\
+poraquê & po*ra-quê \xmark & po*ra*quê \cmark \\
+porcaria & por*ca*ri*a \cmark & por*ca*ri-a \xmark \\
+porfia & por*fi*a \cmark & por*fi-a \xmark \\
+pornografia & por*no*gra*fi*a \cmark & por*no*gra*fi-a \xmark \\
+pornô & por-nô \xmark & por*nô \cmark \\
+porquê & por-quê \xmark & por*quê \cmark \\
+portaria & por*ta*ri*a \cmark & por*ta*ri-a \xmark \\
+portfólio & port*fó*li.o \xmark & port*fó*lio \cmark \\
+portuário & por*tu-á*ri.o \xmark & por*tu*á*rio \cmark \\
+posologia & po*so*lo*gi*a \cmark & po*so*lo*gi-a \xmark \\
+possuído & pos*su-í*do \xmark & pos*su*í*do \cmark \\
+possuidor & pos*su-i*dor \xmark & pos*su*i*dor \cmark \\
+possuir & pos*su-ir \xmark & pos*su*ir \cmark \\
+potássio & po*tás*si.o \xmark & po*tás*sio \cmark \\
+potência & po*tên*ci.a \xmark & po*tên*cia \cmark \\
+pousio & pou*si*o \cmark & pou*si-o \xmark \\
+pradaria & pra*da*ri*a \cmark & pra*da*ri-a \xmark \\
+praia & prai*a \cmark & prai-a \xmark \\
+prataria & pra*ta*ri*a \cmark & pra*ta*ri-a \xmark \\
+preâmbulo & pre-âm*bu*lo \xmark & pre*âm*bu*lo \cmark \\
+preá & pre-á \xmark & pre*á \cmark \\
+precário & pre*cá*ri.o \xmark & pre*cá*rio \cmark \\
+precatório & pre*ca*tó*ri.o \xmark & pre*ca*tó*rio \cmark \\
+precípuo & pre*cí*pu.o \xmark & pre*cí*puo \cmark \\
+predominância & pre*do*mi*nân*ci.a \xmark & pre*do*mi*nân*cia \cmark \\
+predomínio & pre*do*mí*ni.o \xmark & pre*do*mí*nio \cmark \\
+preeminência & pre*e*mi*nên*ci.a \xmark & pre*e*mi*nên*cia \cmark \\
+preênsil & pre-ên*sil \xmark & pre*ên*sil \cmark \\
+prefácio & pre*fá*ci.o \xmark & pre*fá*cio \cmark \\
+preferência & pre*fe*rên*ci.a \xmark & pre*fe*rên*cia \cmark \\
+preia & prei*a \cmark & prei-a \xmark \\
+prejuízo & pre*ju-í*zo \xmark & pre*ju*í*zo \cmark \\
+prelazia & pre*la*zi*a \cmark & pre*la*zi-a \xmark \\
+prélio & pré*li.o \xmark & pré*lio \cmark \\
+prelúdio & pre*lú*di.o \xmark & pre*lú*dio \cmark \\
+prenúncio & pre*nún*ci.o \xmark & pre*nún*cio \cmark \\
+preparatório & pre*pa*ra*tó*ri.o \xmark & pre*pa*ra*tó*rio \cmark \\
+preponderância & pre*pon*de*rân*ci.a \xmark & pre*pon*de*rân*cia \cmark \\
+prepotência & pre*po*tên*ci.a \xmark & pre*po*tên*cia \cmark \\
+presbiopia & pres*bi*o*pi*a \cmark & pres*bi*o*pi-a \xmark \\
+presbitério & pres*bi*té*ri.o \xmark & pres*bi*té*rio \cmark \\
+presciência & pres*ci*ên*ci.a \xmark & pres*ci*ên*cia \cmark \\
+presépio & pre*sé*pi.o \xmark & pre*sé*pio \cmark \\
+presidência & pre*si*dên*ci.a \xmark & pre*si*dên*cia \cmark \\
+presidenciável & pre*si*den*ci-á*vel \xmark & pre*si*den*ci*á*vel \cmark \\
+presságio & pres*sá*gi.o \xmark & pres*sá*gio \cmark \\
+prestígio & pres*tí*gi.o \xmark & pres*tí*gio \cmark \\
+pretoria & pre*to*ri*a \cmark & pre*to*ri-a \xmark \\
+pretório & pre*tó*ri.o \xmark & pre*tó*rio \cmark \\
+previdenciário & pre*vi*den*ci-á*ri.o \xmark & pre*vi*den*ci*á*rio \cmark \\
+prévio & pré*vi.o \xmark & pré*vio \cmark \\
+primário & pri*má*ri.o \xmark & pri*má*rio \cmark \\
+primatologia & pri*ma*to*lo*gi*a \cmark & pri*ma*to*lo*gi-a \xmark \\
+primazia & pri*ma*zi*a \cmark & pri*ma*zi-a \xmark \\
+primórdio & pri*mór*di.o \xmark & pri*mór*dio \cmark \\
+princípio & prin*cí*pi.o \xmark & prin*cí*pio \cmark \\
+prioritário & pri*o*ri*tá*ri.o \xmark & pri*o*ri*tá*rio \cmark \\
+privilégio & pri*vi*lé*gi.o \xmark & pri*vi*lé*gio \cmark \\
+proa & pro*a \cmark & pro-a \xmark \\
 procaína & pro*ca-í*na \xmark & pro*ca*í*na \cmark \\
-pronunciável & pro*nun*ci-á*vel \xmark & pro*nun*ci*á*vel \cmark \\
-pseudociência & p.seu*do*ci*ên*ci*a \xmark & pseu*do*ci*ên*ci*a \cmark \\
-psicofísico & p.si*co*fí*si*co \xmark & psi*co*fí*si*co \cmark \\
+procariótico & pro*ca*ri-ó*ti*co \xmark & pro*ca*ri*ó*ti*co \cmark \\
+proctologia & proc*to*lo*gi*a \cmark & proc*to*lo*gi-a \xmark \\
+procuradoria & pro*cu*ra*do*ri*a \cmark & pro*cu*ra*do*ri-a \xmark \\
+prodígio & pro*dí*gi.o \xmark & pro*dí*gio \cmark \\
+proeminência & pro*e*mi*nên*ci.a \xmark & pro*e*mi*nên*cia \cmark \\
+profecia & pro*fe*ci*a \cmark & pro*fe*ci-a \xmark \\
+proficiência & pro*fi*ci*ên*ci.a \xmark & pro*fi*ci*ên*cia \cmark \\
+profícuo & pro*fí*cu.o \xmark & pro*fí*cuo \cmark \\
+profilaxia & pro*fi*la*xi*a \cmark & pro*fi*la*xi-a \xmark \\
+prolegômenos & pro*le-gô*me*nos \xmark & pro*le*gô*me*nos \cmark \\
+proletário & pro*le*tá*ri.o \xmark & pro*le*tá*rio \cmark \\
+promontório & pro*mon*tó*ri.o \xmark & pro*mon*tó*rio \cmark \\
+promotoria & pro*mo*to*ri*a \cmark & pro*mo*to*ri-a \xmark \\
+pronúncia & pro*nún*ci.a \xmark & pro*nún*cia \cmark \\
+propício & pro*pí*ci.o \xmark & pro*pí*cio \cmark \\
+proprietário & pro*pri*e*tá*ri.o \xmark & pro*pri*e*tá*rio \cmark \\
+próprio & pró*pri.o \xmark & pró*prio \cmark \\
+prosaísmo & pro*sa-ís*mo \xmark & pro*sa*ís*mo \cmark \\
+prosódia & pro*só*di.a \xmark & pro*só*dia \cmark \\
+prosopagnosia & pro*so*pag*no*si*a \cmark & pro*so*pag*no*si-a \xmark \\
+prosopopeia & pro*so*po*pei*a \cmark & pro*so*po*pei-a \xmark \\
+prostatectomia & pros*ta*tec*to*mi*a \cmark & pros*ta*tec*to*mi-a \xmark \\
+prostituição & pros*ti*tu-i*ção \xmark & pros*ti*tu*i*ção \cmark \\
+prostituir & pros*ti*tu-ir \xmark & pros*ti*tu*ir \cmark \\
+protactínio & pro*tac*tí*ni.o \xmark & pro*tac*tí*nio \cmark \\
+proteína & pro*te-í*na \xmark & pro*te*í*na \cmark \\
+proteólise & pro*te-ó*li*se \xmark & pro*te*ó*li*se \cmark \\
+prótio & pró*ti.o \xmark & pró*tio \cmark \\
+protofonia & pro*to*fo*ni*a \cmark & pro*to*fo*ni-a \xmark \\
+protozoário & pro*to*zo-á*ri.o \xmark & pro*to*zo*á*rio \cmark \\
+protuberância & pro*tu*be*rân*ci.a \xmark & pro*tu*be*rân*cia \cmark \\
+provedoria & pro*ve*do*ri*a \cmark & pro*ve*do*ri-a \xmark \\
+provérbio & pro*vér*bi.o \xmark & pro*vér*bio \cmark \\
+providência & pro*vi*dên*ci.a \xmark & pro*vi*dên*cia \cmark \\
+província & pro*vín*ci.a \xmark & pro*vín*cia \cmark \\
+provisório & pro*vi*só*ri.o \xmark & pro*vi*só*rio \cmark \\
+provocatório & pro*vo*ca*tó*ri.o \xmark & pro*vo*ca*tó*rio \cmark \\
+prudência & pru*dên*ci.a \xmark & pru*dên*cia \cmark \\
+pseudônimo & p.seu-dô*ni*mo \xmark & pseu*dô*ni*mo \cmark \\
+psicanálise & p.si*ca*ná*li*se \xmark & psi*ca*ná*li*se \cmark \\
+psicanalista & p.si*ca*na*lis*ta \xmark & psi*ca*na*lis*ta \cmark \\
+psicanalítico & p.si*ca*na*lí*ti*co \xmark & psi*ca*na*lí*ti*co \cmark \\
+psicodrama & p.si*co*dra*ma \xmark & psi*co*dra*ma \cmark \\
+psicografia & p.si*co*gra*fi*a \xmark & psi*co*gra*fi-a \xmark \\
+psicógrafo & p.si*có*gra*fo \xmark & psi*có*gra*fo \cmark \\
+psicolinguista & p.si*co*lin*guis*ta \xmark & psi*co*lin*guis*ta \cmark \\
+psicologia & p.si*co*lo*gi*a \xmark & psi*co*lo*gi-a \xmark \\
+psicologicamente & p.si*co*lo*gi*ca*men*te \xmark & psi*co*lo*gi*ca*men*te \cmark \\
+psicológico & p.si*co*ló*gi*co \xmark & psi*co*ló*gi*co \cmark \\
+psicologismo & p.si*co*lo*gis*mo \xmark & psi*co*lo*gis*mo \cmark \\
+psicologista & p.si*co*lo*gis*ta \xmark & psi*co*lo*gis*ta \cmark \\
 psicologizar & p.si*co*lo*gi*zar \xmark & psi*co*lo*gi*zar \cmark \\
-psicometria & p.si*co*me*tri*a \xmark & psi*co*me*tri*a \cmark \\
+psicólogo & p.si*có*lo*go \xmark & psi*có*lo*go \cmark \\
+psicométrico & p.si*co*mé*tri*co \xmark & psi*co*mé*tri*co \cmark \\
+psicomotor & p.si*co*mo*tor \xmark & psi*co*mo*tor \cmark \\
 psicomotricidade & p.si*co*mo*tri*ci*da*de \xmark & psi*co*mo*tri*ci*da*de \cmark \\
+psicopata & p.si*co*pa*ta \xmark & psi*co*pa*ta \cmark \\
+psicopático & p.si*co*pá*ti*co \xmark & psi*co*pá*ti*co \cmark \\
+psicopatologia & p.si*co*pa*to*lo*gi*a \xmark & psi*co*pa*to*lo*gi-a \xmark \\
 psicopatológico & p.si*co*pa*to*ló*gi*co \xmark & psi*co*pa*to*ló*gi*co \cmark \\
-psicoprofilaxia & p.si*co*pro*fi*la*xi*a \xmark & psi*co*pro*fi*la*xi*a \cmark \\
+psicopedagogia & p.si*co*pe*da*go*gi*a \xmark & psi*co*pe*da*go*gi-a \xmark \\
+psicopedagógico & p.si*co*pe*da*gó*gi*co \xmark & psi*co*pe*da*gó*gi*co \cmark \\
+psicopedagogo & p.si*co*pe*da*go*go \xmark & psi*co*pe*da*go*go \cmark \\
+psicose & p.si*co*se \xmark & psi*co*se \cmark \\
 psicossexual & p.si*cos*se*xu*al \xmark & psi*cos*se*xu*al \cmark \\
-psicoterapêutico & p.si*co*te*ra*pêu*ti*co \xmark & psi*co*te*ra*pêu*ti*co \cmark \\
-psiquê & p.si-quê \xmark & psi*quê \cmark \\
+psicossomático & p.si*cos*so*má*ti*co \xmark & psi*cos*so*má*ti*co \cmark \\
+psicotécnico & p.si*co*téc*ni*co \xmark & psi*co*téc*ni*co \cmark \\
+psicoterapeuta & p.si*co*te*ra*peu*ta \xmark & psi*co*te*ra*peu*ta \cmark \\
+psicoterapia & p.si*co*te*ra*pi*a \xmark & psi*co*te*ra*pi-a \xmark \\
+psicoterápico & p.si*co*te*rá*pi*co \xmark & psi*co*te*rá*pi*co \cmark \\
+psicótico & p.si*có*ti*co \xmark & psi*có*ti*co \cmark \\
+psicotrópico & p.si*co*tró*pi*co \xmark & psi*co*tró*pi*co \cmark \\
+psique & p.si*que \xmark & psi*que \cmark \\
+psiquiatra & p.si*qui*a*tra \xmark & psi*qui*a*tra \cmark \\
+psiquiatria & p.si*qui*a*tri*a \xmark & psi*qui*a*tri-a \xmark \\
+psiquiátrico & p.si*qui-á*tri*co \xmark & psi*qui*á*tri*co \cmark \\
+psíquico & p.sí*qui*co \xmark & psí*qui*co \cmark \\
+psiquismo & p.si*quis*mo \xmark & psi*quis*mo \cmark \\
+psitacídeo & p.si*ta*cí*de.o \xmark & psi*ta*cí*deo \cmark \\
+psitaciforme & p.si*ta*ci*for*me \xmark & psi*ta*ci*for*me \cmark \\
 psitacismo & p.si*ta*cis*mo \xmark & psi*ta*cis*mo \cmark \\
+psoas & p.so*as \xmark & p.so*as \xmark \\
 psoríase & p.so*rí-a*se \xmark & p.so*rí*a*se \xmark \\
+pterossauro & p.te*ros*sau*ro \xmark & pte*ros*sau*ro \cmark \\
 ptose & p.to*se \xmark & pto*se \cmark \\
-puído & pu-í*do \xmark & pu*í*do \cmark \\
-putrião & pu*tri-ão \xmark & pu*tri*ão \cmark \\
+pua & pu*a \cmark & pu-a \xmark \\
+pubescência & pu*bes*cên*ci.a \xmark & pu*bes*cên*cia \cmark \\
+publicitário & pu*bli*ci*tá*ri*o \cmark & pu*bli*ci*tá*ri-o \xmark \\
+pudicícia & pu*di*cí*ci.a \xmark & pu*di*cí*cia \cmark \\
+pulôver & pu-lô*ver \xmark & pu*lô*ver \cmark \\
+purgatório & pur*ga*tó*ri.o \xmark & pur*ga*tó*rio \cmark \\
+quadricromia & qua*dri*cro*mi*a \cmark & qua*dri*cro*mi-a \xmark \\
+quadringentenário & qua*drin*gen*te*ná*ri.o \xmark & qua*drin*gen*te*ná*rio \cmark \\
+quadrívio & qua*drí*vi.o \xmark & qua*drí*vio \cmark \\
+quantia & quan*ti*a \cmark & quan*ti-a \xmark \\
+quartzito & quart*zi*to \cmark & quart*zi*to \cmark \\
+quartzo & quart*zo \cmark & quart*zo \cmark \\
+quaternário & qua*ter*ná*ri.o \xmark & qua*ter*ná*rio \cmark \\
+quéchua & qué*chu*a \cmark & qué*chu-a \xmark \\
+queijaria & quei*ja*ri*a \cmark & quei*ja*ri-a \xmark \\
+questionário & ques*ti*o*ná*ri.o \xmark & ques*ti*o*ná*rio \cmark \\
 questiúncula & ques*ti-ún*cu*la \xmark & ques*ti*ún*cu*la \cmark \\
+quíchua & quí*chu.a \xmark & quí*chua \cmark \\
+quilômetro & qui-lô*me*tro \xmark & qui*lô*me*tro \cmark \\
+quilowatt & qui*lo-watt \xmark & qui*lo-watt \xmark \\
+quimioterapia & qui*mi*o*te*ra*pi*a \cmark & qui*mi*o*te*ra*pi-a \xmark \\
+quinário & qui*ná*ri.o \xmark & qui*ná*rio \cmark \\
+quinoa & qui*no*a \cmark & qui*no-a \xmark \\
+quinquênio & quin-quê*ni.o \xmark & quin*quê*nio \cmark \\
+quinquilharia & quin*qui*lha*ri*a \cmark & quin*qui*lha*ri-a \xmark \\
+quiproquó & qui*pro-quó \xmark & qui*pro*quó \cmark \\
+quiromancia & qui*ro*man*ci*a \cmark & qui*ro*man*ci-a \xmark \\
+raciocínio & ra*ci*o*cí*ni.o \xmark & ra*ci*o*cí*nio \cmark \\
+radiestesia & ra*di*es*te*si*a \cmark & ra*di*es*te*si-a \xmark \\
+radiografia & ra*di*o*gra*fi*a \cmark & ra*di*o*gra*fi-a \xmark \\
+radiólise & ra*di-ó*li*se \xmark & ra*di*ó*li*se \cmark \\
+radiologia & ra*di*o*lo*gi*a \cmark & ra*di*o*lo*gi-a \xmark \\
+rádio & rá*di.o \xmark & rá*dio \cmark \\
+radiotelescópio & ra*di*o*te*les*có*pi.o \xmark & ra*di*o*te*les*có*pio \cmark \\
+radioterapia & ra*di*o*te*ra*pi*a \cmark & ra*di*o*te*ra*pi-a \xmark \\
+ráfia & rá*fi*a \cmark & rá*fi-a \xmark \\
+raia & rai*a \cmark & rai-a \xmark \\
+rainha & ra-i*nha \xmark & ra*i*nha \cmark \\
+raio & rai*o \cmark & rai-o \xmark \\
+raiz & ra-iz \xmark & ra*iz \cmark \\
+ramaria & ra*ma*ri*a \cmark & ra*ma*ri-a \xmark \\
+ranário & ra*ná*ri.o \xmark & ra*ná*rio \cmark \\
+rancharia & ran*cha*ri*a \cmark & ran*cha*ri-a \xmark \\
+randômico & ran-dô*mi*co \xmark & ran*dô*mi*co \cmark \\
+rapsódia & rap*só*di.a \xmark & rap*só*dia \cmark \\
+raquítico & ra-quí*ti*co \xmark & ra*quí*ti*co \cmark \\
+rataria & ra*ta*ri*a \cmark & ra*ta*ri-a \xmark \\
+rateio & ra*tei*o \cmark & ra*tei-o \xmark \\
+ravióli & ra*vi-ó*li \xmark & ra*vi*ó*li \cmark \\
+razia & ra*zi*a \cmark & ra*zi-a \xmark \\
+razoável & ra*zo-á*vel \xmark & ra*zo*á*vel \cmark \\
+rebeldia & re*bel*di*a \cmark & re*bel*di-a \xmark \\
+rebelião & re*be*li-ão \xmark & re*be*li*ão \cmark \\
+recaída & re*ca-í*da \xmark & re*ca*í*da \cmark \\
+recair & re*ca-ir \xmark & re*ca*ir \cmark \\
+receio & re*cei*o \cmark & re*cei-o \xmark \\
+receituário & re*cei*tu-á*ri.o \xmark & re*cei*tu*á*rio \cmark \\
+recheio & re*chei*o \cmark & re*chei-o \xmark \\
+recôncavo & re-côn*ca*vo \xmark & re*côn*ca*vo \cmark \\
+recôndito & re-côn*di*to \xmark & re*côn*di*to \cmark \\
+reconstituição & re*cons*ti*tu-i*ção \xmark & re*cons*ti*tu*i*ção \cmark \\
+reconstituinte & re*cons*ti*tu-in*te \xmark & re*cons*ti*tu*in*te \cmark \\
+reconstituir & re*cons*ti*tu-ir \xmark & re*cons*ti*tu*ir \cmark \\
+reconstruído & re*cons*tru-í*do \xmark & re*cons*tru*í*do \cmark \\
+reconstruir & re*cons*tru-ir \xmark & re*cons*tru*ir \cmark \\
+recorrência & re*cor*rên*ci.a \xmark & re*cor*rên*cia \cmark \\
+recreio & re*crei*o \cmark & re*crei-o \xmark \\
+recria & re*cri*a \cmark & re*cri-a \xmark \\
+recua & re*cu*a \cmark & re*cu-a \xmark \\
+recuo & re*cu*o \cmark & re*cu-o \xmark \\
+rédea & ré*de*a \cmark & ré*de-a \xmark \\
+redistribuir & re*dis*tri*bu-ir \xmark & re*dis*tri*bu*ir \cmark \\
+reengenharia & re*en*ge*nha*ri*a \cmark & re*en*ge*nha*ri-a \xmark \\
+reentrância & re*en*trân*ci.a \xmark & re*en*trân*cia \cmark \\
+reenvio & re*en*vi*o \cmark & re*en*vi-o \xmark \\
+refeitório & re*fei*tó*ri.o \xmark & re*fei*tó*rio \cmark \\
+referência & re*fe*rên*ci.a \xmark & re*fe*rên*cia \cmark \\
+refinaria & re*fi*na*ri*a \cmark & re*fi*na*ri-a \xmark \\
+reflexologia & re*fle*xo*lo*gi*a \cmark & re*fle*xo*lo*gi-a \xmark \\
+refluir & re*flu-ir \xmark & re*flu*ir \cmark \\
+refúgio & re*fú*gi.o \xmark & re*fú*gio \cmark \\
+regalia & re*ga*li*a \cmark & re*ga*li-a \xmark \\
+regateio & re*ga*tei*o \cmark & re*ga*tei-o \xmark \\
+regência & re*gên*ci.a \xmark & re*gên*cia \cmark \\
+região & re*gi-ão \xmark & re*gi*ão \cmark \\
+régia & ré*gi.a \xmark & ré*gia \cmark \\
+régio & ré*gi.o \xmark & ré*gio \cmark \\
+reimplantação & re-im*plan*ta*ção \xmark & re*im*plan*ta*ção \cmark \\
+reimplantar & re-im*plan*tar \xmark & re*im*plan*tar \cmark \\
 reimportar & re-im*por*tar \xmark & re*im*por*tar \cmark \\
 reimpressão & re-im*pres*são \xmark & re*im*pres*são \cmark \\
+reimprimir & re-im*pri*mir \xmark & re*im*pri*mir \cmark \\
+reincidente & re-in*ci*den*te \xmark & re*in*ci*den*te \cmark \\
+reincidir & re-in*ci*dir \xmark & re*in*ci*dir \cmark \\
+reincorporação & re-in*cor*po*ra*ção \xmark & re*in*cor*po*ra*ção \cmark \\
+reindexação & re-in*de*xa*ção \xmark & re-in*de*xa*ção \xmark \\
+reingressar & re-in*gres*sar \xmark & re*in*gres*sar \cmark \\
+reingresso & re-in*gres*so \xmark & re*in*gres*so \cmark \\
 reinscrever & re-ins*cre*ver \xmark & re*ins*cre*ver \cmark \\
+reinserção & re-in*ser*ção \xmark & re*in*ser*ção \cmark \\
 reinserir & re-in*se*rir \xmark & re*in*se*rir \cmark \\
-remediável & re*me*di-á*vel \xmark & re*me*di*á*vel \cmark \\
-rubiácea & ru*bi-á*ce*a \xmark & ru*bi*á*ce*a \cmark \\
+reinstalação & re-ins*ta*la*ção \xmark & re*ins*ta*la*ção \cmark \\
+reinstalar & re-ins*ta*lar \xmark & re*ins*ta*lar \cmark \\
+reinstituir & re-ins*ti*tu-ir \xmark & re*ins*ti*tu*ir \cmark \\
+reintegração & re-in*te*gra*ção \xmark & re*in*te*gra*ção \cmark \\
+reintegrar & re-in*te*grar \xmark & re*in*te*grar \cmark \\
+reintrodução & re-in*tro*du*ção \xmark & re*in*tro*du*ção \cmark \\
+reintroduzir & re-in*tro*du*zir \xmark & re*in*tro*du*zir \cmark \\
+reinventar & re-in*ven*tar \xmark & re*in*ven*tar \cmark \\
+reinvestir & re-in*ves*tir \xmark & re*in*ves*tir \cmark \\
+reitoria & rei*to*ri*a \cmark & rei*to*ri-a \xmark \\
+relatoria & re*la*to*ri*a \cmark & re*la*to*ri-a \xmark \\
+relatório & re*la*tó*ri.o \xmark & re*la*tó*rio \cmark \\
+relevância & re*le*vân*ci.a \xmark & re*le*vân*cia \cmark \\
+relicário & re*li*cá*ri.o \xmark & re*li*cá*rio \cmark \\
+religião & re*li*gi-ão \xmark & re*li*gi*ão \cmark \\
+relíquia & re*lí*qui.a \xmark & re*lí*quia \cmark \\
+relógio & re*ló*gi.o \xmark & re*ló*gio \cmark \\
+relutância & re*lu*tân*ci.a \xmark & re*lu*tân*cia \cmark \\
+reminiscência & re*mi*nis*cên*ci.a \xmark & re*mi*nis*cên*cia \cmark \\
+renúncia & re*nún*ci.a \xmark & re*nún*cia \cmark \\
+repertório & re*per*tó*ri.o \xmark & re*per*tó*rio \cmark \\
+repetência & re*pe*tên*ci.a \xmark & re*pe*tên*cia \cmark \\
+replantio & re*plan*ti*o \cmark & re*plan*ti-o \xmark \\
+repositório & re*po*si*tó*ri.o \xmark & re*po*si*tó*rio \cmark \\
+represália & re*pre*sá*li.a \xmark & re*pre*sá*lia \cmark \\
+reprografia & re*pro*gra*fi*a \cmark & re*pro*gra*fi-a \xmark \\
+repúdio & re*pú*di.o \xmark & re*pú*dio \cmark \\
+repugnância & re*pug*nân*ci.a \xmark & re*pug*nân*cia \cmark \\
+reservatório & re*ser*va*tó*ri.o \xmark & re*ser*va*tó*rio \cmark \\
+residência & re*si*dên*ci.a \xmark & re*si*dên*cia \cmark \\
+resiliência & re*si*li*ên*ci.a \xmark & re*si*li*ên*cia \cmark \\
+resistência & re*sis*tên*ci.a \xmark & re*sis*tên*cia \cmark \\
+respiratório & res*pi*ra*tó*ri.o \xmark & res*pi*ra*tó*rio \cmark \\
+resquício & res-quí*ci.o \xmark & res*quí*cio \cmark \\
+ressonância & res*so*nân*ci.a \xmark & res*so*nân*cia \cmark \\
+restituição & res*ti*tu-i*ção \xmark & res*ti*tu*i*ção \cmark \\
+restituir & res*ti*tu-ir \xmark & res*ti*tu*ir \cmark \\
+retardatário & re*tar*da*tá*ri.o \xmark & re*tar*da*tá*rio \cmark \\
+reticência & re*ti*cên*ci.a \xmark & re*ti*cên*cia \cmark \\
+retinopatia & re*ti*no*pa*ti*a \cmark & re*ti*no*pa*ti-a \xmark \\
+retraído & re*tra-í*do \xmark & re*tra*í*do \cmark \\
+retrair & re*tra-ir \xmark & re*tra*ir \cmark \\
+retribuição & re*tri*bu-i*ção \xmark & re*tri*bu*i*ção \cmark \\
+retribuir & re*tri*bu-ir \xmark & re*tri*bu*ir \cmark \\
+reumatologia & reu*ma*to*lo*gi*a \cmark & reu*ma*to*lo*gi-a \xmark \\
+reunir & re-u*nir \xmark & re-u*nir \xmark \\
+reurbanizar & re-ur*ba*ni*zar \xmark & re-ur*ba*ni*zar \xmark \\
+revelia & re*ve*li*a \cmark & re*ve*li-a \xmark \\
+reverência & re*ve*rên*ci.a \xmark & re*ve*rên*cia \cmark \\
+revolucionário & re*vo*lu*ci*o*ná*ri.o \xmark & re*vo*lu*ci*o*ná*rio \cmark \\
+ria & ri*a \cmark & ri-a \xmark \\
+ridicularia & ri*di*cu*la*ri*a \cmark & ri*di*cu*la*ri-a \xmark \\
+rinoplastia & ri*no*plas*ti*a \cmark & ri*no*plas*ti-a \xmark \\
+rio & ri*o \cmark & ri-o \xmark \\
+robô & ro-bô \xmark & ro*bô \cmark \\
+rocio & ro*ci*o \cmark & ro*ci-o \xmark \\
+rodeio & ro*dei*o \cmark & ro*dei-o \xmark \\
+ródio & ró*di.o \xmark & ró*dio \cmark \\
+rodízio & ro*dí*zi.o \xmark & ro*dí*zio \cmark \\
+rodopio & ro*do*pi*o \cmark & ro*do*pi-o \xmark \\
+rodoviário & ro*do*vi-á*ri.o \xmark & ro*do*vi*á*rio \cmark \\
+rodovia & ro*do*vi*a \cmark & ro*do*vi-a \xmark \\
+roído & ro-í*do \xmark & ro*í*do \cmark \\
+romaria & ro*ma*ri*a \cmark & ro*ma*ri-a \xmark \\
+rosácea & ro*sá*ce.a \xmark & ro*sá*cea \cmark \\
+rosário & ro*sá*ri.o \xmark & ro*sá*rio \cmark \\
+roséola & ro*sé-o*la \xmark & ro*sé*o*la \cmark \\
+róseo & ró*se.o \xmark & ró*seo \cmark \\
+rossio & ros*si*o \cmark & ros*si-o \xmark \\
+rouparia & rou*pa*ri*a \cmark & rou*pa*ri-a \xmark \\
+ruão & ru-ão \xmark & ru*ão \cmark \\
+rua & ru*a \cmark & ru-a \xmark \\
+rubéola & ru*bé-o*la \xmark & ru*bé*o*la \cmark \\
+rubídio & ru*bí*di.o \xmark & ru*bí*dio \cmark \\
+rufião & ru*fi-ão \xmark & ru*fi*ão \cmark \\
+ruído & ru-í*do \xmark & ru*í*do \cmark \\
+ruim & ru-im \xmark & ru-im \xmark \\
+ruína & ru-í*na \xmark & ru*í*na \cmark \\
+ruindade & ru-in*da*de \xmark & ru*in*da*de \cmark \\
 ruinoso & ru-i*no*so \xmark & ru*i*no*so \cmark \\
-sainha & sa-i*nha \xmark & sa*i*nha \cmark \\
-sardônica & sar-dô*ni*ca \xmark & sar*dô*ni*ca \cmark \\
+ruir & ru-ir \xmark & ru*ir \cmark \\
+rupia & ru*pi*a \cmark & ru*pi-a \xmark \\
+rutênio & ru*tê*ni.o \xmark & ru*tê*nio \cmark \\
+rutherford & ru-ther*ford \xmark & ru-ther*ford \xmark \\
+sabedoria & sa*be*do*ri*a \cmark & sa*be*do*ri-a \xmark \\
+sabiá & sa*bi-á \xmark & sa*bi*á \cmark \\
+sábio & sá*bi.o \xmark & sá*bio \cmark \\
+sacaria & sa*ca*ri*a \cmark & sa*ca*ri-a \xmark \\
+sacerdócio & sa*cer*dó*ci.o \xmark & sa*cer*dó*cio \cmark \\
+sacramentário & sa*cra*men*tá*ri*o \cmark & sa*cra*men*tá*ri-o \xmark \\
+sacrário & sa*crá*ri.o \xmark & sa*crá*rio \cmark \\
+sacrifício & sa*cri*fí*ci.o \xmark & sa*cri*fí*cio \cmark \\
+sacrilégio & sa*cri*lé*gi.o \xmark & sa*cri*lé*gio \cmark \\
+sacristia & sa*cris*ti*a \cmark & sa*cris*ti-a \xmark \\
+saia & sai*a \cmark & sai-a \xmark \\
+saída & sa-í*da \xmark & sa*í*da \cmark \\
+saído & sa-í*do \xmark & sa*í*do \cmark \\
+saio & sai*o \cmark & sai-o \xmark \\
+sair & sa-ir \xmark & sa*ir \cmark \\
+saí & sa-í \xmark & sa*í \cmark \\
+salafrário & sa*la*frá*ri.o \xmark & sa*la*frá*rio \cmark \\
+salário & sa*lá*ri.o \xmark & sa*lá*rio \cmark \\
+saliência & sa*li*ên*ci.a \xmark & sa*li*ên*cia \cmark \\
+salmodia & sal*mo*di*a \cmark & sal*mo*di-a \xmark \\
+saloio & sa*loi*o \cmark & sa*loi-o \xmark \\
+salomônico & sa*lo-mô*ni*co \xmark & sa*lo*mô*ni*co \cmark \\
+salsicharia & sal*si*cha*ri*a \cmark & sal*si*cha*ri-a \xmark \\
+samambaia & sa*mam*bai*a \cmark & sa*mam*bai-a \xmark \\
+samário & sa*má*ri.o \xmark & sa*má*rio \cmark \\
+sambaíba & sam*ba-í*ba \xmark & sam*ba*í*ba \cmark \\
+sandália & san*dá*li.a \xmark & san*dá*lia \cmark \\
+sanduíche & san*du-í*che \xmark & san*du*í*che \cmark \\
+sangria & san*gri*a \cmark & san*gri-a \xmark \\
+sanguinário & san*gui*ná*ri.o \xmark & san*gui*ná*rio \cmark \\
+sanguínea & san*guí*ne.a \xmark & san*guí*nea \cmark \\
+sanitário & sa*ni*tá*ri.o \xmark & sa*ni*tá*rio \cmark \\
+santuário & san*tu-á*ri.o \xmark & san*tu*á*rio \cmark \\
+sapataria & sa*pa*ta*ri*a \cmark & sa*pa*ta*ri-a \xmark \\
+sapiência & sa*pi*ên*ci.a \xmark & sa*pi*ên*cia \cmark \\
+saponáceo & sa*po*ná*ce.o \xmark & sa*po*ná*ceo \cmark \\
+sapucaia & sa*pu*cai*a \cmark & sa*pu*cai-a \xmark \\
+saquê & sa-quê \xmark & sa*quê \cmark \\
+sardônico & sar-dô*ni*co \xmark & sar*dô*ni*co \cmark \\
 satiríase & sa*ti*rí-a*se \xmark & sa*ti*rí*a*se \cmark \\
-setentrião & se*ten*tri-ão \xmark & se*ten*tri*ão \cmark \\
-sievert & si.e*vert \xmark & si.e*vert \xmark \\
-sismômetro & sis-mô*me*tro \xmark & sis*mô*me*tro \cmark \\
-solipsista & so*lip*sis*ta \cmark & so*lip-sis*ta \xmark \\
-suaíle & su*a-í*le \xmark & su*a*í*le \cmark \\
-sublevado & su.b-le*va*do \xmark & sub*le*va*do \cmark \\
+satisfatório & sa*tis*fa*tó*ri.o \xmark & sa*tis*fa*tó*rio \cmark \\
+satrapia & sa*tra*pi*a \cmark & sa*tra*pi-a \xmark \\
+saúde & sa-ú*de \xmark & sa*ú*de \cmark \\
+saúva & sa-ú*va \xmark & sa*ú*va \cmark \\
+sebastião & se*bas*ti-ão \xmark & se*bas*ti*ão \cmark \\
+seborreia & se*bor*rei*a \cmark & se*bor*rei-a \xmark \\
+secretaria & se*cre*ta*ri*a \cmark & se*cre*ta*ri-a \xmark \\
+secretária & se*cre*tá*ri.a \xmark & se*cre*tá*ria \cmark \\
+secretário & se*cre*tá*ri.o \xmark & se*cre*tá*rio \cmark \\
+sectário & sec*tá*ri.o \xmark & sec*tá*rio \cmark \\
+secundário & se*cun*dá*ri.o \xmark & se*cun*dá*rio \cmark \\
+securitário & se*cu*ri*tá*ri.o \xmark & se*cu*ri*tá*rio \cmark \\
+sedentário & se*den*tá*ri.o \xmark & se*den*tá*rio \cmark \\
+seio & sei*o \cmark & sei-o \xmark \\
+selaria & se*la*ri*a \cmark & se*la*ri-a \xmark \\
+selenografia & se*le*no*gra*fi*a \cmark & se*le*no*gra*fi-a \xmark \\
+selvageria & sel*va*ge*ri*a \cmark & sel*va*ge*ri-a \xmark \\
+selvajaria & sel*va*ja*ri*a \cmark & sel*va*ja*ri-a \xmark \\
+semanário & se*ma*ná*ri.o \xmark & se*ma*ná*rio \cmark \\
+sematologia & se*ma*to*lo*gi*a \cmark & se*ma*to*lo*gi-a \xmark \\
+semiárido & se*mi-á*ri*do \xmark & se*mi*á*ri*do \cmark \\
+semicolcheia & se*mi*col*chei*a \cmark & se*mi*col*chei-a \xmark \\
+seminário & se*mi*ná*ri.o \xmark & se*mi*ná*rio \cmark \\
+semiologia & se*mi*o*lo*gi*a \cmark & se*mi*o*lo*gi-a \xmark \\
+senescência & se*nes*cên*ci.a \xmark & se*nes*cên*cia \cmark \\
+senhoria & se*nho*ri*a \cmark & se*nho*ri-a \xmark \\
+senhorio & se*nho*ri*o \cmark & se*nho*ri-o \xmark \\
+sensaboria & sen*sa*bo*ri*a \cmark & sen*sa*bo*ri-a \xmark \\
+sépia & sé*pi.a \xmark & sé*pia \cmark \\
+septicemia & sep*ti*ce*mi*a \cmark & sep*ti*ce*mi-a \xmark \\
+sequência & se-quên*ci.a \xmark & se*quên*cia \cmark \\
+sequoia & se*quoi*a \cmark & se*quoi-a \xmark \\
+sereia & se*rei*a \cmark & se*rei-a \xmark \\
+série & sé*ri.e \xmark & sé*rie \cmark \\
+serigrafia & se*ri*gra*fi*a \cmark & se*ri*gra*fi-a \xmark \\
+sério & sé*ri.o \xmark & sé*rio \cmark \\
+serôdio & se-rô*di.o \xmark & se*rô*dio \cmark \\
+serologia & se*ro*lo*gi*a \cmark & se*ro*lo*gi-a \xmark \\
+serralharia & ser*ra*lha*ri*a \cmark & ser*ra*lha*ri-a \xmark \\
+serrania & ser*ra*ni*a \cmark & ser*ra*ni-a \xmark \\
+serventia & ser*ven*ti*a \cmark & ser*ven*ti-a \xmark \\
+serventuário & ser*ven*tu-á*ri.o \xmark & ser*ven*tu*á*rio \cmark \\
+sérvio & sér*vi.o \xmark & sér*vio \cmark \\
+servofreio & ser*vo*frei*o \cmark & ser*vo*frei-o \xmark \\
+sesmaria & ses*ma*ri*a \cmark & ses*ma*ri-a \xmark \\
+sesquicentenário & ses*qui*cen*te*ná*ri.o \xmark & ses*qui*cen*te*ná*rio \cmark \\
+sestércio & ses*tér*ci.o \xmark & ses*tér*cio \cmark \\
+sexagenário & se*xa*ge*ná*ri.o \xmark & se*xa*ge*ná*rio \cmark \\
+sexologia & se*xo*lo*gi*a \cmark & se*xo*lo*gi-a \xmark \\
+siálico & si-á*li*co \xmark & si*á*li*co \cmark \\
+sialorreia & si*a*lor*rei*a \cmark & si*a*lor*rei-a \xmark \\
+sibilância & si*bi*lân*ci.a \xmark & si*bi*lân*cia \cmark \\
+siderurgia & si*de*rur*gi*a \cmark & si*de*rur*gi-a \xmark \\
+signatário & sig*na*tá*ri.o \xmark & sig*na*tá*rio \cmark \\
+significância & sig*ni*fi*cân*ci.a \xmark & sig*ni*fi*cân*cia \cmark \\
+silêncio & si*lên*ci.o \xmark & si*lên*cio \cmark \\
+silício & si*lí*ci.o \xmark & si*lí*cio \cmark \\
+sílvia & síl*vi.a \xmark & síl*via \cmark \\
+simbologia & sim*bo*lo*gi*a \cmark & sim*bo*lo*gi-a \xmark \\
+simetria & si*me*tri*a \cmark & si*me*tri-a \xmark \\
+símio & sí*mi.o \xmark & sí*mio \cmark \\
+simonia & si*mo*ni*a \cmark & si*mo*ni-a \xmark \\
+simpatia & sim*pa*ti*a \cmark & sim*pa*ti-a \xmark \\
+simpatria & sim*pa*tri*a \cmark & sim*pa*tri-a \xmark \\
+simpósio & sim*pó*si.o \xmark & sim*pó*sio \cmark \\
+simultâneo & si*mul*tâ*ne.o \xmark & si*mul*tâ*neo \cmark \\
+sincronia & sin*cro*ni*a \cmark & sin*cro*ni-a \xmark \\
+sindicância & sin*di*cân*ci.a \xmark & sin*di*cân*cia \cmark \\
+sinergia & si*ner*gi*a \cmark & si*ner*gi-a \xmark \\
+sinestesia & si*nes*te*si*a \cmark & si*nes*te*si-a \xmark \\
+sinfonia & sin*fo*ni*a \cmark & sin*fo*ni-a \xmark \\
+sinfônica & sin-fô*ni*ca \xmark & sin*fô*ni*ca \cmark \\
+sinfônico & sin-fô*ni*co \xmark & sin*fô*ni*co \cmark \\
+sinologia & si*no*lo*gi*a \cmark & si*no*lo*gi-a \xmark \\
+sinonímia & si*no*ní*mi.a \xmark & si*no*ní*mia \cmark \\
+sinônimo & si-nô*ni*mo \xmark & si*nô*ni*mo \cmark \\
+sintomatologia & sin*to*ma*to*lo*gi*a \cmark & sin*to*ma*to*lo*gi-a \xmark \\
+sintonia & sin*to*ni*a \cmark & sin*to*ni-a \xmark \\
+siríaco & si*rí-a*co \xmark & si*rí*a*co \cmark \\
+sírio & sí*ri.o \xmark & sí*rio \cmark \\
+sítio & sí*ti.o \xmark & sí*tio \cmark \\
+sizígia & si*zí*gi.a \xmark & si*zí*gia \cmark \\
+soberania & so*be*ra*ni*a \cmark & so*be*ra*ni-a \xmark \\
+sobressaia & so*bres*sai*a \cmark & so*bres*sai-a \xmark \\
+sobressair & so*bres*sa-ir \xmark & so*bres*sa*ir \cmark \\
+sobrevivência & so*bre*vi*vên*ci.a \xmark & so*bre*vi*vên*cia \cmark \\
+sobrevoo & so*bre*vo*o \cmark & so*bre*vo-o \xmark \\
+sóbrio & só*bri.o \xmark & só*brio \cmark \\
+societário & so*ci*e*tá*ri.o \xmark & so*ci*e*tá*rio \cmark \\
+sociologia & so*ci*o*lo*gi*a \cmark & so*ci*o*lo*gi-a \xmark \\
+sociólogo & so*ci-ó*lo*go \xmark & so*ci*ó*lo*go \cmark \\
+sociopatia & so*ci*o*pa*ti*a \cmark & so*ci*o*pa*ti-a \xmark \\
+sócio & só*ci.o \xmark & só*cio \cmark \\
+sodalício & so*da*lí*ci.o \xmark & so*da*lí*cio \cmark \\
+sódio & só*di.o \xmark & só*dio \cmark \\
+sodomia & so*do*mi*a \cmark & so*do*mi-a \xmark \\
+solário & so*lá*ri.o \xmark & so*lá*rio \cmark \\
+solidário & so*li*dá*ri.o \xmark & so*li*dá*rio \cmark \\
+sólio & só*li.o \xmark & só*lio \cmark \\
+solitária & so*li*tá*ri.a \xmark & so*li*tá*ria \cmark \\
+solitário & so*li*tá*ri.o \xmark & so*li*tá*rio \cmark \\
+solstício & sols*tí*ci.o \xmark & sols*tí*cio \cmark \\
+somatório & so*ma*tó*ri.o \xmark & so*ma*tó*rio \cmark \\
+sombrio & som*bri*o \cmark & som*bri-o \xmark \\
+sonolência & so*no*lên*ci.a \xmark & so*no*lên*cia \cmark \\
+sonômetro & so-nô*me*tro \xmark & so*nô*me*tro \cmark \\
+sonoplastia & so*no*plas*ti*a \cmark & so*no*plas*ti-a \xmark \\
+sorologia & so*ro*lo*gi*a \cmark & so*ro*lo*gi-a \xmark \\
+soroterapia & so*ro*te*ra*pi*a \cmark & so*ro*te*ra*pi-a \xmark \\
+sorteio & sor*tei*o \cmark & sor*tei-o \xmark \\
+sortilégio & sor*ti*lé*gi.o \xmark & sor*ti*lé*gio \cmark \\
+sorveteria & sor*ve*te*ri*a \cmark & sor*ve*te*ri-a \xmark \\
+sósia & só*si.a \xmark & só*sia \cmark \\
+soslaio & sos*lai*o \cmark & sos*lai-o \xmark \\
+soviético & so*vi-é*ti*co \xmark & so*vi*é*ti*co \cmark \\
+stalinismo & s.ta*li*nis*mo \xmark & sta*li*nis*mo \cmark \\
+stalinista & s.ta*li*nis*ta \xmark & sta*li*nis*ta \cmark \\
+suaíli & su*a-í*li \xmark & su*a*í*li \cmark \\
+suão & su-ão \xmark & su*ão \cmark \\
+suástica & su-ás*ti*ca \xmark & su*ás*ti*ca \cmark \\
+suã & su-ã \xmark & su*ã \cmark \\
+subaquático & su*ba-quá*ti*co \xmark & su*ba*quá*ti*co \cmark \\
+subcategoria & sub*ca*te*go*ri*a \cmark & sub*ca*te*go*ri-a \xmark \\
+subcutâneo & sub*cu*tâ*ne.o \xmark & sub*cu*tâ*neo \cmark \\
+subdiácono & sub*di-á*co*no \xmark & sub*di*á*co*no \cmark \\
+subespécie & su*bes*pé*ci.e \xmark & su*bes*pé*cie \cmark \\
+subliminar & su.b-li*mi*nar \xmark & su.b-li*mi*nar \xmark \\
+sublingual & su.b-lin*gual \xmark & su.b-lin*gual \xmark \\
+sublinha & su.b-li*nha \xmark & su.b-li*nha \xmark \\
+subliteratura & su.b-li*te*ra*tu*ra \xmark & su.b-li*te*ra*tu*ra \xmark \\
+sublocação & su.b-lo*ca*ção \xmark & sub*lo*ca*ção \cmark \\
 sublocar & su.b-lo*car \xmark & sub*lo*car \cmark \\
-sublocatário & su.b-lo*ca*tá*ri*o \xmark & sub*lo*ca*tá*ri*o \cmark \\
-subsônico & sub-sô*ni*co \xmark & sub*sô*ni*co \cmark \\
-sucuriú & su*cu*ri-ú \xmark & su*cu*ri*ú \cmark \\
-suingar & su-in*gar \xmark & su-in*gar \xmark \\
+sublunar & su.b-lu*nar \xmark & sub*lu*nar \cmark \\
+subsecretário & sub*se*cre*tá*ri.o \xmark & sub*se*cre*tá*rio \cmark \\
+subserviência & sub*ser*vi*ên*ci.a \xmark & sub*ser*vi*ên*cia \cmark \\
+subsidiário & sub*si*di-á*ri.o \xmark & sub*si*di*á*rio \cmark \\
+subsídio & sub*sí*di.o \xmark & sub*sí*dio \cmark \\
+subsistência & sub*sis*tên*ci.a \xmark & sub*sis*tên*cia \cmark \\
+substância & subs*tân*ci.a \xmark & subs*tân*cia \cmark \\
+substituição & subs*ti*tu-i*ção \xmark & subs*ti*tu*i*ção \cmark \\
+substituído & subs*ti*tu-í*do \xmark & subs*ti*tu*í*do \cmark \\
+substituir & subs*ti*tu-ir \xmark & subs*ti*tu*ir \cmark \\
+substituível & subs*ti*tu-í*vel \xmark & subs*ti*tu*í*vel \cmark \\
+subterrâneo & sub*ter*râ*ne.o \xmark & sub*ter*râ*neo \cmark \\
+subtraído & sub*tra-í*do \xmark & sub*tra*í*do \cmark \\
+subtrair & sub*tra-ir \xmark & sub*tra*ir \cmark \\
+subúrbio & su*búr*bi.o \xmark & su*búr*bio \cmark \\
+sucedâneo & su*ce*dâ*ne.o \xmark & su*ce*dâ*neo \cmark \\
+sucessório & su*ces*só*ri.o \xmark & su*ces*só*rio \cmark \\
+súcia & sú*ci.a \xmark & sú*cia \cmark \\
+sudário & su*dá*ri.o \xmark & su*dá*rio \cmark \\
+suéter & su-é*ter \xmark & su*é*ter \cmark \\
+suficiência & su*fi*ci*ên*ci.a \xmark & su*fi*ci*ên*cia \cmark \\
+sufragâneo & su*fra*gâ*ne.o \xmark & su*fra*gâ*neo \cmark \\
+sufrágio & su*frá*gi.o \xmark & su*frá*gio \cmark \\
+suíça & su-í*ça \xmark & su*í*ça \cmark \\
+suíço & su-í*ço \xmark & su*í*ço \cmark \\
+suingue & su-in*gue \xmark & su*in*gue \cmark \\
+suíno & su-í*no \xmark & su*í*no \cmark \\
+suíte & su-í*te \xmark & su*í*te \cmark \\
+sumário & su*má*ri.o \xmark & su*má*rio \cmark \\
+sumério & su*mé*ri.o \xmark & su*mé*rio \cmark \\
+sumô & su-mô \xmark & su*mô \cmark \\
+supedâneo & su*pe*dâ*ne.o \xmark & su*pe*dâ*neo \cmark \\
+superavitário & su*pe*ra*vi*tá*ri.o \xmark & su*pe*ra*vi*tá*rio \cmark \\
+supercampeão & su*per*cam*pe-ão \xmark & su*per*cam*pe*ão \cmark \\
+superfície & su*per*fí*ci.e \xmark & su*per*fí*cie \cmark \\
+supérfluo & su*pér*flu.o \xmark & su*pér*fluo \cmark \\
+superintendência & su*pe*rin*ten*dên*ci.a \xmark & su*pe*rin*ten*dên*cia \cmark \\
+supersônico & su*per-sô*ni*co \xmark & su*per*sô*ni*co \cmark \\
+superveniência & su*per*ve*ni*ên*ci.a \xmark & su*per*ve*ni*ên*cia \cmark \\
+supremacia & su*pre*ma*ci*a \cmark & su*pre*ma*ci-a \xmark \\
+surucuá & su*ru*cu-á \xmark & su*ru*cu*á \cmark \\
+suspensório & sus*pen*só*ri.o \xmark & sus*pen*só*rio \cmark \\
+sutiã & su*ti-ã \xmark & su*ti*ã \cmark \\
+tabacaria & ta*ba*ca*ri*a \cmark & ta*ba*ca*ri-a \xmark \\
+tabelião & ta*be*li-ão \xmark & ta*be*li*ão \cmark \\
+tabuão & ta*bu-ão \xmark & ta*bu*ão \cmark \\
+tabua & ta*bu*a \cmark & ta*bu-a \xmark \\
 tacômetro & ta-cô*me*tro \xmark & ta*cô*me*tro \cmark \\
-taiuiá & tai-ui-á \xmark & tai-ui*á \xmark \\
+tainha & ta-i*nha \xmark & ta*i*nha \cmark \\
+taiuiá & tai-ui-á \xmark & tai*ui*á \cmark \\
 taiwanês & tai-wa*nês \xmark & tai-wa*nês \xmark \\
+talassemia & ta*las*se*mi*a \cmark & ta*las*se*mi-a \xmark \\
+talassocracia & ta*las*so*cra*ci*a \cmark & ta*las*so*cra*ci-a \xmark \\
+talassoterapia & ta*las*so*te*ra*pi*a \cmark & ta*las*so*te*ra*pi-a \xmark \\
 talião & ta*li-ão \xmark & ta*li*ão \cmark \\
-tchecoslovaco & t.che*cos*lo*va*co \xmark & tche*cos*lo*va*co \cmark \\
+tálio & tá*li.o \xmark & tá*lio \cmark \\
+tanatofobia & ta*na*to*fo*bi*a \cmark & ta*na*to*fo*bi-a \xmark \\
+tanatologia & ta*na*to*lo*gi*a \cmark & ta*na*to*lo*gi-a \xmark \\
+tangência & tan*gên*ci.a \xmark & tan*gên*cia \cmark \\
+tanoaria & ta*no*a*ri*a \cmark & ta*no*a*ri-a \xmark \\
+tapuia & ta*pui*a \cmark & ta*pui-a \xmark \\
+tapuio & ta*pui*o \cmark & ta*pui-o \xmark \\
+taquicardia & ta*qui*car*di*a \cmark & ta*qui*car*di-a \xmark \\
+taquigrafia & ta*qui*gra*fi*a \cmark & ta*qui*gra*fi-a \xmark \\
+taquígrafo & ta-quí*gra*fo \xmark & ta*quí*gra*fo \cmark \\
+taquímetro & ta-quí*me*tro \xmark & ta*quí*me*tro \cmark \\
+taquipneia & ta*quip*nei*a \cmark & ta*quip*nei-a \xmark \\
+tardio & tar*di*o \cmark & tar*di-o \xmark \\
+tarô & ta-rô \xmark & ta*rô \cmark \\
+tataravô & ta*ta*ra-vô \xmark & ta*ta*ra*vô \cmark \\
+tatuí & ta*tu-í \xmark & ta*tu*í \cmark \\
+taumaturgia & tau*ma*tur*gi*a \cmark & tau*ma*tur*gi-a \xmark \\
+tauromaquia & tau*ro*ma*qui*a \cmark & tau*ro*ma*qui-a \xmark \\
+tautologia & tau*to*lo*gi*a \cmark & tau*to*lo*gi-a \xmark \\
+taxionomia & ta*xi*o*no*mi*a \cmark & ta*xi*o*no*mi-a \xmark \\
+taxonomia & ta*xo*no*mi*a \cmark & ta*xo*no*mi-a \xmark \\
+taxonômico & ta*xo-nô*mi*co \xmark & ta*xo*nô*mi*co \cmark \\
+tcheco & t.che*co \xmark & tche*co \cmark \\
+tecnécio & tec*né*ci.o \xmark & tec*né*cio \cmark \\
+tecnocracia & tec*no*cra*ci*a \cmark & tec*no*cra*ci-a \xmark \\
+tecnologia & tec*no*lo*gi*a \cmark & tec*no*lo*gi-a \xmark \\
+tédio & té*di.o \xmark & té*dio \cmark \\
+teia & tei*a \cmark & tei-a \xmark \\
+teimosia & tei*mo*si*a \cmark & tei*mo*si-a \xmark \\
+teísmo & te-ís*mo \xmark & te*ís*mo \cmark \\
 teísta & te-ís*ta \xmark & te*ís*ta \cmark \\
 teiú & tei-ú \xmark & tei*ú \cmark \\
-telômero & te-lô*me*ro \xmark & te*lô*me*ro \cmark \\
+telecinesia & te*le*ci*ne*si*a \cmark & te*le*ci*ne*si-a \xmark \\
+teleconferência & te*le*con*fe*rên*ci.a \xmark & te*le*con*fe*rên*cia \cmark \\
+teledramaturgia & te*le*dra*ma*tur*gi*a \cmark & te*le*dra*ma*tur*gi-a \xmark \\
+telefonia & te*le*fo*ni*a \cmark & te*le*fo*ni-a \xmark \\
+telefônico & te*le-fô*ni*co \xmark & te*le*fô*ni*co \cmark \\
+telegrafia & te*le*gra*fi*a \cmark & te*le*gra*fi-a \xmark \\
+telemetria & te*le*me*tri*a \cmark & te*le*me*tri-a \xmark \\
+teleologia & te*le*o*lo*gi*a \cmark & te*le*o*lo*gi-a \xmark \\
+teleósteo & te*le-ós*te.o \xmark & te*le*ós*teo \cmark \\
+telepatia & te*le*pa*ti*a \cmark & te*le*pa*ti-a \xmark \\
+telescópio & te*les*có*pi.o \xmark & te*les*có*pio \cmark \\
+telúrio & te*lú*ri.o \xmark & te*lú*rio \cmark \\
+temário & te*má*ri.o \xmark & te*má*rio \cmark \\
+temerário & te*me*rá*ri.o \xmark & te*me*rá*rio \cmark \\
+templário & tem*plá*ri.o \xmark & tem*plá*rio \cmark \\
+temporário & tem*po*rá*ri.o \xmark & tem*po*rá*rio \cmark \\
+tendência & ten*dên*ci.a \xmark & ten*dên*cia \cmark \\
 teníase & te*ní-a*se \xmark & te*ní*a*se \cmark \\
-terciário & ter*ci-á*ri*o \xmark & ter*ci*á*ri*o \cmark \\
+teocracia & te*o*cra*ci*a \cmark & te*o*cra*ci-a \xmark \\
+teofania & te*o*fa*ni*a \cmark & te*o*fa*ni-a \xmark \\
+teófobo & te-ó*fo*bo \xmark & te*ó*fo*bo \cmark \\
+teologia & te*o*lo*gi*a \cmark & te*o*lo*gi-a \xmark \\
+teólogo & te-ó*lo*go \xmark & te*ó*lo*go \cmark \\
+teônimo & te-ô*ni*mo \xmark & te*ô*ni*mo \cmark \\
+teoria & te*o*ri*a \cmark & te*o*ri-a \xmark \\
+teórica & te-ó*ri*ca \xmark & te*ó*ri*ca \cmark \\
+teórico & te-ó*ri*co \xmark & te*ó*ri*co \cmark \\
+teosofia & te*o*so*fi*a \cmark & te*o*so*fi-a \xmark \\
+terapia & te*ra*pi*a \cmark & te*ra*pi-a \xmark \\
+teratologia & te*ra*to*lo*gi*a \cmark & te*ra*to*lo*gi-a \xmark \\
+térbio & tér*bi.o \xmark & tér*bio \cmark \\
+terciário & ter*ci-á*ri.o \xmark & ter*ci*á*rio \cmark \\
+tércia & tér*ci.a \xmark & tér*cia \cmark \\
+terminologia & ter*mi*no*lo*gi*a \cmark & ter*mi*no*lo*gi-a \xmark \\
+termografia & ter*mo*gra*fi*a \cmark & ter*mo*gra*fi-a \xmark \\
+termologia & ter*mo*lo*gi*a \cmark & ter*mo*lo*gi-a \xmark \\
+termômetro & ter-mô*me*tro \xmark & ter*mô*me*tro \cmark \\
+termoquímica & ter*mo-quí*mi*ca \xmark & ter*mo*quí*mi*ca \cmark \\
+termoquímico & ter*mo-quí*mi*co \xmark & ter*mo*quí*mi*co \cmark \\
+térreo & tér*re.o \xmark & tér*reo \cmark \\
+território & ter*ri*tó*ri.o \xmark & ter*ri*tó*rio \cmark \\
+tertúlia & ter*tú*li.a \xmark & ter*tú*lia \cmark \\
+tesouraria & te*sou*ra*ri*a \cmark & te*sou*ra*ri-a \xmark \\
+testamentário & tes*ta*men*tá*ri.o \xmark & tes*ta*men*tá*rio \cmark \\
+tetania & te*ta*ni*a \cmark & te*ta*ni-a \xmark \\
+tetracampeão & te*tra*cam*pe-ão \xmark & te*tra*cam*pe*ão \cmark \\
+tetraédrico & te*tra-é*dri*co \xmark & te*tra*é*dri*co \cmark \\
+tetraplegia & te*tra*ple*gi*a \cmark & te*tra*ple*gi-a \xmark \\
+tetrarquia & te*trar*qui*a \cmark & te*trar*qui-a \xmark \\
+tetravô & te*tra-vô \xmark & te*tra*vô \cmark \\
+teúrgico & te-úr*gi*co \xmark & te*úr*gi*co \cmark \\
+teutônico & teu-tô*ni*co \xmark & teu*tô*ni*co \cmark \\
+tia & ti*a \cmark & ti-a \xmark \\
+tíbia & tí*bi.a \xmark & tí*bia \cmark \\
+tíbio & tí*bi.o \xmark & tí*bio \cmark \\
+tília & tí*li.a \xmark & tí*lia \cmark \\
+timocracia & ti*mo*cra*ci*a \cmark & ti*mo*cra*ci-a \xmark \\
+tinturaria & tin*tu*ra*ri*a \cmark & tin*tu*ra*ri-a \xmark \\
+tio & ti*o \cmark & ti-o \xmark \\
+tipografia & ti*po*gra*fi*a \cmark & ti*po*gra*fi-a \xmark \\
+tipoia & ti*poi*a \cmark & ti*poi-a \xmark \\
+tiptologia & tip*to*lo*gi*a \cmark & tip*to*lo*gi-a \xmark \\
+tirania & ti*ra*ni*a \cmark & ti*ra*ni-a \xmark \\
+tirocínio & ti*ro*cí*ni.o \xmark & ti*ro*cí*nio \cmark \\
+tiromancia & ti*ro*man*ci*a \cmark & ti*ro*man*ci-a \xmark \\
+tiroteio & ti*ro*tei*o \cmark & ti*ro*tei-o \xmark \\
+titânio & ti*tâ*ni.o \xmark & ti*tâ*nio \cmark \\
+titia & ti*ti*a \cmark & ti*ti-a \xmark \\
+titio & ti*ti*o \cmark & ti*ti-o \xmark \\
+tiú & ti-ú \xmark & ti*ú \cmark \\
+tmese & t.me*se \xmark & tme*se \cmark \\
+toa & to*a \cmark & to-a \xmark \\
+toboágua & to*bo-á*gua \xmark & to*bo*á*gua \cmark \\
+tocaia & to*cai*a \cmark & to*cai-a \xmark \\
+todavia & to*da*vi*a \cmark & to*da*vi-a \xmark \\
+tolerância & to*le*rân*ci.a \xmark & to*le*rân*cia \cmark \\
+tomografia & to*mo*gra*fi*a \cmark & to*mo*gra*fi-a \xmark \\
+tonelaria & to*ne*la*ri*a \cmark & to*ne*la*ri-a \xmark \\
+topázio & to*pá*zi.o \xmark & to*pá*zio \cmark \\
+topiaria & to*pi*a*ri*a \cmark & to*pi*a*ri-a \xmark \\
+topografia & to*po*gra*fi*a \cmark & to*po*gra*fi-a \xmark \\
+topologia & to*po*lo*gi*a \cmark & to*po*lo*gi-a \xmark \\
+toponímia & to*po*ní*mi.a \xmark & to*po*ní*mia \cmark \\
+topônimo & to-pô*ni*mo \xmark & to*pô*ni*mo \cmark \\
+toracoscopia & to*ra*cos*co*pi*a \cmark & to*ra*cos*co*pi-a \xmark \\
+toracotomia & to*ra*co*to*mi*a \cmark & to*ra*co*to*mi-a \xmark \\
+torquês & tor-quês \xmark & tor*quês \cmark \\
 torreão & tor*re-ão \xmark & tor*re*ão \cmark \\
+tosquia & tos*qui*a \cmark & tos*qui-a \xmark \\
+totalitário & to*ta*li*tá*ri.o \xmark & to*ta*li*tá*rio \cmark \\
+toxicologia & to*xi*co*lo*gi*a \cmark & to*xi*co*lo*gi-a \xmark \\
+toxicomania & to*xi*co*ma*ni*a \cmark & to*xi*co*ma*ni-a \xmark \\
+toxicômano & to*xi-cô*ma*no \xmark & to*xi*cô*ma*no \cmark \\
+trácio & trá*ci*o \cmark & trá*ci-o \xmark \\
+tragédia & tra*gé*di.a \xmark & tra*gé*dia \cmark \\
+tragediógrafo & tra*ge*di-ó*gra*fo \xmark & tra*ge*di*ó*gra*fo \cmark \\
+tragicomédia & tra*gi*co*mé*di.a \xmark & tra*gi*co*mé*dia \cmark \\
+traído & tra-í*do \xmark & tra*í*do \cmark \\
+traíra & tra-í*ra \xmark & tra*í*ra \cmark \\
+trair & tra-ir \xmark & tra*ir \cmark \\
+tramoia & tra*moi*a \cmark & tra*moi-a \xmark \\
+transcendência & trans*cen*dên*ci.a \xmark & trans*cen*dên*cia \cmark \\
 transeunte & tran*se-un*te \xmark & tran*se-un*te \xmark \\
-triádico & tri-á*di*co \xmark & tri*á*di*co \cmark \\
+transferência & trans*fe*rên*ci.a \xmark & trans*fe*rên*cia \cmark \\
+transigência & tran*si*gên*ci.a \xmark & tran*si*gên*cia \cmark \\
+transitório & tran*si*tó*ri.o \xmark & tran*si*tó*rio \cmark \\
+transoceânico & tran*so*ce-â*ni*co \xmark & tran*so*ce*â*ni*co \cmark \\
+transumância & tran*su*mân*ci.a \xmark & tran*su*mân*cia \cmark \\
+trapézio & tra*pé*zi.o \xmark & tra*pé*zio \cmark \\
+traqueia & tra*quei*a \cmark & tra*quei-a \xmark \\
+traumatologia & trau*ma*to*lo*gi*a \cmark & trau*ma*to*lo*gi-a \xmark \\
+travessia & tra*ves*si*a \cmark & tra*ves*si-a \xmark \\
+tríade & trí-a*de \xmark & trí*a*de \cmark \\
+triarquia & tri*ar*qui*a \cmark & tri*ar*qui-a \xmark \\
+tributário & tri*bu*tá*ri.o \xmark & tri*bu*tá*rio \cmark \\
+tricampeão & tri*cam*pe-ão \xmark & tri*cam*pe*ão \cmark \\
+tricentenário & tri*cen*te*ná*ri.o \xmark & tri*cen*te*ná*rio \cmark \\
+tricotilomania & tri*co*ti*lo*ma*ni*a \cmark & tri*co*ti*lo*ma*ni-a \xmark \\
+tricotomia & tri*co*to*mi*a \cmark & tri*co*to*mi-a \xmark \\
+tricô & tri-cô \xmark & tri*cô \cmark \\
+tricromia & tri*cro*mi*a \cmark & tri*cro*mi-a \xmark \\
+tríduo & trí*du.o \xmark & trí*duo \cmark \\
+trigonometria & tri*go*no*me*tri*a \cmark & tri*go*no*me*tri-a \xmark \\
+trilogia & tri*lo*gi*a \cmark & tri*lo*gi-a \xmark \\
+trinitário & tri*ni*tá*ri.o \xmark & tri*ni*tá*rio \cmark \\
+trio & tri*o \cmark & tri-o \xmark \\
 tripanossomíase & tri*pa*nos*so*mí-a*se \xmark & tri*pa*nos*so*mí*a*se \cmark \\
+trisavô & tri*sa-vô \xmark & tri*sa*vô \cmark \\
+trissomia & tris*so*mi*a \cmark & tris*so*mi-a \xmark \\
+trítio & trí*ti.o \xmark & trí*tio \cmark \\
 triunfador & tri-un*fa*dor \xmark & tri*un*fa*dor \cmark \\
+triunfalismo & tri-un*fa*lis*mo \xmark & tri*un*fa*lis*mo \cmark \\
+triunfalista & tri-un*fa*lis*ta \xmark & tri*un*fa*lis*ta \cmark \\
+triunfal & tri-un*fal \xmark & tri*un*fal \cmark \\
+triunfante & tri-un*fan*te \xmark & tri*un*fan*te \cmark \\
+triunfar & tri-un*far \xmark & tri*un*far \cmark \\
+triunfo & tri-un*fo \xmark & tri*un*fo \cmark \\
+triúnviro & tri-ún*vi*ro \xmark & tri*ún*vi*ro \cmark \\
+trívio & trí*vi.o \xmark & trí*vio \cmark \\
+trombocitopenia & trom*bo*ci*to*pe*ni*a \cmark & trom*bo*ci*to*pe*ni-a \xmark \\
+truculência & tru*cu*lên*ci.a \xmark & tru*cu*lên*cia \cmark \\
 truísmo & tru-ís*mo \xmark & tru*ís*mo \cmark \\
-tuim & tu-im \xmark & tu-im \xmark \\
-tuiuiú & tui-ui-ú \xmark & tui-ui*ú \xmark \\
-tumultuário & tu*mul*tu-á*ri*o \xmark & tu*mul*tu*á*ri*o \cmark \\
+tua & tu*a \cmark & tu-a \xmark \\
+tuim & tu-im \xmark & tu*im \cmark \\
+túlio & tú*li.o \xmark & tú*lio \cmark \\
+tumultuário & tu*mul*tu-á*ri.o \xmark & tu*mul*tu*á*rio \cmark \\
 tzarista & t.za*ris*ta \xmark & tza*ris*ta \cmark \\
-vietcongue & vi*et*con*gue \cmark & vi*et-con*gue \xmark \\
+ufania & u*fa*ni*a \cmark & u*fa*ni-a \xmark \\
+uísque & u-ís*que \xmark & u*ís*que \cmark \\
+uíste & u-ís*te \xmark & u*ís*te \cmark \\
+umbaúba & um*ba-ú*ba \xmark & um*ba*ú*ba \cmark \\
+umbria & um*bri*a \cmark & um*bri-a \xmark \\
+úmbrio & úm*bri.o \xmark & úm*brio \cmark \\
+união & u*ni-ão \xmark & u*ni*ão \cmark \\
+unicórnio & u*ni*cór*ni.o \xmark & u*ni*cór*nio \cmark \\
+unitário & u*ni*tá*ri.o \xmark & u*ni*tá*rio \cmark \\
+universitário & u*ni*ver*si*tá*ri.o \xmark & u*ni*ver*si*tá*rio \cmark \\
+urânio & u*râ*ni.o \xmark & u*râ*nio \cmark \\
+ureia & u*rei*a \cmark & u*rei-a \xmark \\
+uremia & u*re*mi*a \cmark & u*re*mi-a \xmark \\
+urgência & ur*gên*ci.a \xmark & ur*gên*cia \cmark \\
+urinário & u*ri*ná*ri.o \xmark & u*ri*ná*rio \cmark \\
+urnário & ur*ná*ri*o \cmark & ur*ná*ri-o \xmark \\
+urologia & u*ro*lo*gi*a \cmark & u*ro*lo*gi-a \xmark \\
+uropígio & u*ro*pí*gi.o \xmark & u*ro*pí*gio \cmark \\
+urticária & ur*ti*cá*ri.a \xmark & ur*ti*cá*ria \cmark \\
+uruguaio & u*ru*guai*o \cmark & u*ru*guai-o \xmark \\
+usuário & u*su-á*ri.o \xmark & u*su*á*rio \cmark \\
+usucapião & u*su*ca*pi-ão \xmark & u*su*ca*pi*ão \cmark \\
+usufruir & u*su*fru-ir \xmark & u*su*fru*ir \cmark \\
+usurário & u*su*rá*ri.o \xmark & u*su*rá*rio \cmark \\
+utensílio & u*ten*sí*li.o \xmark & u*ten*sí*lio \cmark \\
+utilitário & u*ti*li*tá*ri.o \xmark & u*ti*li*tá*rio \cmark \\
+utopia & u*to*pi*a \cmark & u*to*pi-a \xmark \\
+uvaia & u*vai*a \cmark & u*vai-a \xmark \\
+úvea & ú*ve*a \cmark & ú*ve-a \xmark \\
+uveíte & u*ve-í*te \xmark & u*ve*í*te \cmark \\
+vacância & va*cân*ci.a \xmark & va*cân*cia \cmark \\
+vacaria & va*ca*ri*a \cmark & va*ca*ri-a \xmark \\
+vacúolo & va*cú-o*lo \xmark & va*cú*o*lo \cmark \\
+vácuo & vá*cu.o \xmark & vá*cuo \cmark \\
+vadia & va*di*a \cmark & va*di-a \xmark \\
+vaia & vai*a \cmark & vai-a \xmark \\
+valência & va*lên*ci.a \xmark & va*lên*cia \cmark \\
+valentia & va*len*ti*a \cmark & va*len*ti-a \xmark \\
+valia & va*li*a \cmark & va*li-a \xmark \\
+vanádio & va*ná*di.o \xmark & va*ná*dio \cmark \\
+vanglória & van*gló*ri.a \xmark & van*gló*ria \cmark \\
+vária & vá*ri.a \xmark & vá*ria \cmark \\
+variável & va*ri-á*vel \xmark & va*ri*á*vel \cmark \\
+varíola & va*rí-o*la \xmark & va*rí*o*la \cmark \\
+vário & vá*ri.o \xmark & vá*rio \cmark \\
+varonia & va*ro*ni*a \cmark & va*ro*ni-a \xmark \\
+várzea & vár*ze.a \xmark & vár*zea \cmark \\
+vascaíno & vas*ca-í*no \xmark & vas*ca*í*no \cmark \\
+vasectomia & va*sec*to*mi*a \cmark & va*sec*to*mi-a \xmark \\
+vazia & va*zi*a \cmark & va*zi-a \xmark \\
+vazio & va*zi*o \cmark & va*zi-o \xmark \\
+veemência & ve*e*mên*ci.a \xmark & ve*e*mên*cia \cmark \\
+veia & vei*a \cmark & vei-a \xmark \\
+veículo & ve-í*cu*lo \xmark & ve*í*cu*lo \cmark \\
+velário & ve*lá*ri.o \xmark & ve*lá*rio \cmark \\
+velhacaria & ve*lha*ca*ri*a \cmark & ve*lha*ca*ri-a \xmark \\
+velharia & ve*lha*ri*a \cmark & ve*lha*ri-a \xmark \\
+velório & ve*ló*ri.o \xmark & ve*ló*rio \cmark \\
+venéreo & ve*né*re.o \xmark & ve*né*reo \cmark \\
+ventania & ven*ta*ni*a \cmark & ven*ta*ni-a \xmark \\
+ventriloquia & ven*tri*lo*qui*a \cmark & ven*tri*lo*qui-a \xmark \\
+veraneio & ve*ra*nei*o \cmark & ve*ra*nei-o \xmark \\
+verborragia & ver*bor*ra*gi*a \cmark & ver*bor*ra*gi-a \xmark \\
+vestiário & ves*ti-á*ri.o \xmark & ves*ti*á*rio \cmark \\
+véstia & vés*ti*a \cmark & vés*ti-a \xmark \\
+vestígio & ves*tí*gi.o \xmark & ves*tí*gio \cmark \\
+vestuário & ves*tu-á*ri.o \xmark & ves*tu*á*rio \cmark \\
+veterinária & ve*te*ri*ná*ri.a \xmark & ve*te*ri*ná*ria \cmark \\
+veterinário & ve*te*ri*ná*ri.o \xmark & ve*te*ri*ná*rio \cmark \\
+viário & vi-á*ri.o \xmark & vi*á*rio \cmark \\
+viável & vi-á*vel \xmark & vi*á*vel \cmark \\
+via & vi*a \cmark & vi-a \xmark \\
+vibrião & vi*bri-ão \xmark & vi*bri*ão \cmark \\
+vicário & vi*cá*ri.o \xmark & vi*cá*rio \cmark \\
+vício & ví*ci.o \xmark & ví*cio \cmark \\
+vidência & vi*dên*ci.a \xmark & vi*dên*cia \cmark \\
+videoconferência & vi*de*o*con*fe*rên*ci.a \xmark & vi*de*o*con*fe*rên*cia \cmark \\
+vídeo & ví*de.o \xmark & ví*deo \cmark \\
+vidraçaria & vi*dra*ça*ri*a \cmark & vi*dra*ça*ri-a \xmark \\
+vidraria & vi*dra*ri*a \cmark & vi*dra*ri-a \xmark \\
+viés & vi-és \xmark & vi*és \cmark \\
+vigário & vi*gá*ri.o \xmark & vi*gá*rio \cmark \\
+vigência & vi*gên*ci.a \xmark & vi*gên*cia \cmark \\
+vigia & vi*gi*a \cmark & vi*gi-a \xmark \\
+vigilância & vi*gi*lân*ci.a \xmark & vi*gi*lân*cia \cmark \\
+vigília & vi*gí*li.a \xmark & vi*gí*lia \cmark \\
+vilania & vi*la*ni*a \cmark & vi*la*ni-a \xmark \\
+vilipêndio & vi*li*pên*di.o \xmark & vi*li*pên*dio \cmark \\
+violáceo & vi*o*lá*ce.o \xmark & vi*o*lá*ceo \cmark \\
+violência & vi*o*lên*ci.a \xmark & vi*o*lên*cia \cmark \\
+virologia & vi*ro*lo*gi*a \cmark & vi*ro*lo*gi-a \xmark \\
+virulência & vi*ru*lên*ci.a \xmark & vi*ru*lên*cia \cmark \\
+visionário & vi*si*o*ná*ri.o \xmark & vi*si*o*ná*rio \cmark \\
+vistoria & vis*to*ri*a \cmark & vis*to*ri-a \xmark \\
+vitalício & vi*ta*lí*ci.o \xmark & vi*ta*lí*cio \cmark \\
+vitória & vi*tó*ri.a \xmark & vi*tó*ria \cmark \\
+vítreo & ví*tre.o \xmark & ví*treo \cmark \\
 vitriólico & vi*tri-ó*li*co \xmark & vi*tri*ó*li*co \cmark \\
-vitríolo & vi*trí-o*lo \xmark & vi*trí*o*lo \cmark \\
+vitupério & vi*tu*pé*ri.o \xmark & vi*tu*pé*rio \cmark \\
+viúva & vi-ú*va \xmark & vi*ú*va \cmark \\
+viúvo & vi-ú*vo \xmark & vi*ú*vo \cmark \\
+vivência & vi*vên*ci.a \xmark & vi*vên*cia \cmark \\
+vocabulário & vo*ca*bu*lá*ri.o \xmark & vo*ca*bu*lá*rio \cmark \\
+volfrâmio & vol*frâ*mi.o \xmark & vol*frâ*mio \cmark \\
+voluntário & vo*lun*tá*ri.o \xmark & vo*lun*tá*rio \cmark \\
+voo & vo*o \cmark & vo-o \xmark \\
+vovô & vo-vô \xmark & vo*vô \cmark \\
+voyeurismo & voy-eu*ris*mo \xmark & voy-eu*ris*mo \xmark \\
+voyeurista & voy-eu*ris*ta \xmark & voy-eu*ris*ta \xmark \\
+voyeurístico & voy-eu*rís*ti*co \xmark & voy-eu*rís*ti*co \xmark \\
+vozerio & vo*ze*ri*o \cmark & vo*ze*ri-o \xmark \\
+vulcanologia & vul*ca*no*lo*gi*a \cmark & vul*ca*no*lo*gi-a \xmark \\
+xaria & xa*ri*a \cmark & xa*ri-a \xmark \\
+xátria & xá*tri.a \xmark & xá*tria \cmark \\
+xenofilia & xe*no*fi*li*a \cmark & xe*no*fi*li-a \xmark \\
+xenofobia & xe*no*fo*bi*a \cmark & xe*no*fo*bi-a \xmark \\
+xenomania & xe*no*ma*ni*a \cmark & xe*no*ma*ni-a \xmark \\
+xeroftalmia & xe*rof*tal*mi*a \cmark & xe*rof*tal*mi-a \xmark \\
+xerografia & xe*ro*gra*fi*a \cmark & xe*ro*gra*fi-a \xmark \\
 xilocaína & xi*lo*ca-í*na \xmark & xi*lo*ca*í*na \cmark \\
-abluir & a*blu-ir \xmark & a*blu*ir \cmark \\
-balaústre & ba*la-ús*tre \xmark & ba*la*ús*tre \cmark \\
-cabriúva & ca*bri-ú*va \xmark & ca*bri*ú*va \cmark \\
-daguerreótipo & da*guer*re-ó*ti*po \xmark & da*guer*re*ó*ti*po \cmark \\
-daltônico & dal-tô*ni*co \xmark & dal*tô*ni*co \cmark \\
-ecônomo & e-cô*no*mo \xmark & e*cô*no*mo \cmark \\
-egoístico & e*go-ís*ti*co \xmark & e*go*ís*ti*co \cmark \\
-eletrocardiógrafo & e*le*tro*car*di-ó*gra*fo \xmark & e*le*tro*car*di*ó*gra*fo \cmark \\
-eletroquímica & e*le*tro-quí*mi*ca \xmark & e*le*tro*quí*mi*ca \cmark \\
-eletroquímico & e*le*tro-quí*mi*co \xmark & e*le*tro*quí*mi*co \cmark \\
-embainhar & em*ba-i*nhar \xmark & em*ba*i*nhar \cmark \\
-faiscar & fa-is*car \xmark & fa-is*car \xmark \\
-faúlha & fa-ú*lha \xmark & fa*ú*lha \cmark \\
-galvanômetro & gal*va-nô*me*tro \xmark & gal*va*nô*me*tro \cmark \\
-hagiógrafo & ha*gi-ó*gra*fo \xmark & ha*gi*ó*gra*fo \cmark \\
-hebraísmo & he*bra-ís*mo \xmark & he*bra*ís*mo \cmark \\
-hebraísta & he*bra-ís*ta \xmark & he*bra*ís*ta \cmark \\
-hipertônico & hi*per-tô*ni*co \xmark & hi*per*tô*ni*co \cmark \\
-historiógrafo & his*to*ri-ó*gra*fo \xmark & his*to*ri*ó*gra*fo \cmark \\
-histrião & his*tri-ão \xmark & his*tri*ão \cmark \\
-jesuitismo & je*su-i*tis*mo \xmark & je*su*i*tis*mo \cmark \\
-macedônico & ma*ce-dô*ni*co \xmark & ma*ce*dô*ni*co \cmark \\
-ninfomaníaco & nin*fo*ma*ní-a*co \xmark & nin*fo*ma*ní*a*co \cmark \\
-paquímetro & pa-quí*me*tro \xmark & pa*quí*me*tro \cmark \\
-tabuinha & ta*bu-i*nha \xmark & ta*bu*i*nha \cmark \\
-taquígrafo & ta-quí*gra*fo \xmark & ta*quí*gra*fo \cmark \\
-taquímetro & ta-quí*me*tro \xmark & ta*quí*me*tro \cmark \\
-tectônico & tec-tô*ni*co \xmark & tec*tô*ni*co \cmark \\
+xilografia & xi*lo*gra*fi*a \cmark & xi*lo*gra*fi-a \xmark \\
+xilomancia & xi*lo*man*ci*a \cmark & xi*lo*man*ci-a \xmark \\
+xintoísmo & xin*to-ís*mo \xmark & xin*to*ís*mo \cmark \\
 xintoísta & xin*to-ís*ta \xmark & xin*to*ís*ta \cmark \\
-abiótica & a*bi-ó*ti*ca \xmark & a*bi*ó*ti*ca \cmark \\
-abiótico & a*bi-ó*ti*co \xmark & a*bi*ó*ti*co \cmark \\
-abraâmico & a*bra-â*mi*co \xmark & a*bra*â*mi*co \cmark \\
-abstraído & abs*tra-í*do \xmark & abs*tra*í*do \cmark \\
-acauã & a*cau-ã \xmark & a*cau*ã \cmark \\
-acelerômetro & a*ce*le-rô*me*tro \xmark & a*ce*le*rô*me*tro \cmark \\
-acetaldeído & a*ce*tal*de-í*do \xmark & a*ce*tal*de*í*do \cmark \\
-acroleína & a*cro*le-í*na \xmark & a*cro*le*í*na \cmark \\
-adônis & a-dô*nis \xmark & a*dô*nis \cmark \\
-ainsa & a-in*sa \xmark & a-in*sa \xmark \\
-aiquidô & ai*qui-dô \xmark & ai*qui*dô \cmark \\
-alcíone & al*cí-o*ne \xmark & al*cí*o*ne \cmark \\
-aldeído & al*de-í*do \xmark & al*de*í*do \cmark \\
-aleúte & a*le-ú*te \xmark & a*le*ú*te \cmark \\
-aliá & a*li-á \xmark & a*li*á \cmark \\
-almóada & al*mó-a*da \xmark & al*mó-a*da \xmark \\
-aloé & a*lo-é \xmark & a*lo*é \cmark \\
-aloés & a*lo-és \xmark & a*lo*és \cmark \\
-aluá & a*lu-á \xmark & a*lu*á \cmark \\
-alvéolo & al*vé-o*lo \xmark & al*vé*o*lo \cmark \\
-amebíase & a*me*bí-a*se \xmark & a*me*bí*a*se \cmark \\
-âmnio & âm*ni*o \cmark & â.m-ni*o \xmark \\
-ancilostomíase & an*ci*los*to*mí-a*se \xmark & an*ci*los*to*mí*a*se \cmark \\
-anemômetro & a*ne-mô*me*tro \xmark & a*ne*mô*me*tro \cmark \\
-anfião & an*fi-ão \xmark & an*fi*ão \cmark \\
-anfictião & an*fic*ti-ão \xmark & an*fic*ti*ão \cmark \\
-anião & a*ni-ão \xmark & a*ni*ão \cmark \\
-aórtico & a-ór*ti*co \xmark & a*ór*ti*co \cmark \\
-apuí & a*pu-í \xmark & a*pu*í \cmark \\
-aquífero & a-quí*fe*ro \xmark & a*quí*fe*ro \cmark \\
-areão & a*re-ão \xmark & a*re*ão \cmark \\
-areópago & a*re-ó*pa*go \xmark & a*re*ó*pa*go \cmark \\
-arquidiácono & ar*qui*di-á*co*no \xmark & ar*qui*di*á*co*no \cmark \\
-arteríola & ar*te*rí-o*la \xmark & ar*te*rí*o*la \cmark \\
-assiriólogo & as*si*ri-ó*lo*go \xmark & as*si*ri*ó*lo*go \cmark \\
-astroquímica & as*tro-quí*mi*ca \xmark & as*tro*quí*mi*ca \cmark \\
-ateísta & a*te-ís*ta \xmark & a*te*ís*ta \cmark \\
-autoimunidade & au*to-i*mu*ni*da*de \xmark & au*to-i*mu*ni*da*de \xmark \\
-autônimo & au-tô*ni*mo \xmark & au*tô*ni*mo \cmark \\
-autonômico & au*to-nô*mi*co \xmark & au*to*nô*mi*co \cmark \\
-averroísmo & a*ver*ro-ís*mo \xmark & a*ver*ro*ís*mo \cmark \\
-bacteriófago & bac*te*ri-ó*fa*go \xmark & bac*te*ri*ó*fa*go \cmark \\
-baleárico & ba*le-á*ri*co \xmark & ba*le*á*ri*co \cmark \\
-banjoísta & ban*jo-ís*ta \xmark & ban*jo*ís*ta \cmark \\
-batuíra & ba*tu-í*ra \xmark & ba*tu*í*ra \cmark \\
-behaviorismo & be-ha*vi*o*ris*mo \xmark & be-ha*vi*o*ris*mo \xmark \\
-benjoim & ben*jo-im \xmark & ben*jo-im \xmark \\
-bibliógrafo & bi*bli-ó*gra*fo \xmark & bi*bli*ó*gra*fo \cmark \\
-bilião & bi*li-ão \xmark & bi*li*ão \cmark \\
-biótico & bi-ó*ti*co \xmark & bi*ó*ti*co \cmark \\
-biótopo & bi-ó*to*po \xmark & bi*ó*to*po \cmark \\
-biscainho & bis*ca-i*nho \xmark & bis*ca*i*nho \cmark \\
-blastômero & blas-tô*me*ro \xmark & blas*tô*me*ro \cmark \\
-boé & bo-é \xmark & bo*é \cmark \\
-bosníaco & bos*ní-a*co \xmark & bos*ní*a*co \cmark \\
-braquiópode & bra*qui-ó*po*de \xmark & bra*qui*ó*po*de \cmark \\
-bué & bu-é \xmark & bu*é \cmark \\
-cafarnaum & ca*far*na-um \xmark & ca*far*na-um \xmark \\
-cajuína & ca*ju-í*na \xmark & ca*ju*í*na \cmark \\
-camião & ca*mi-ão \xmark & ca*mi*ão \cmark \\
-candidíase & can*di*dí-a*se \xmark & can*di*dí*a*se \cmark \\
-canoísta & ca*no-ís*ta \xmark & ca*no*ís*ta \cmark \\
-carnaubal & car*na-u*bal \xmark & car*na-u*bal \xmark \\
-caroá & ca*ro-á \xmark & ca*ro*á \cmark \\
-caseína & ca*se-í*na \xmark & ca*se*í*na \cmark \\
-catequético & ca*te-qué*ti*co \xmark & ca*te*qué*ti*co \cmark \\
-catião & ca*ti-ão \xmark & ca*ti*ão \cmark \\
-cauã & cau-ã \xmark & cau*ã \cmark \\
-celíaco & ce*lí-a*co \xmark & ce*lí*a*co \cmark \\
-cnidário & c.ni*dá*ri*o \xmark & c.ni*dá*ri*o \xmark \\
-coimbrão & co-im*brão \xmark & co*im*brão \cmark \\
-coleóptero & co*le-óp*te*ro \xmark & co*le*óp*te*ro \cmark \\
-contraindicação & con*tra-in*di*ca*ção \xmark & con*tra*in*di*ca*ção \cmark \\
-contribuidor & con*tri*bu-i*dor \xmark & con*tri*bu*i*dor \cmark \\
-coriáceo & co*ri-á*ce*o \xmark & co*ri*á*ce*o \cmark \\
-curião & cu*ri-ão \xmark & cu*ri*ão \cmark \\
-curiúva & cu*ri-ú*va \xmark & cu*ri*ú*va \cmark \\
-cuxiú & cu*xi-ú \xmark & cu*xi*ú \cmark \\
-decurião & de*cu*ri-ão \xmark & de*cu*ri*ão \cmark \\
-deiscente & de-is*cen*te \xmark & de-is*cen*te \xmark \\
-deísmo & de-ís*mo \xmark & de*ís*mo \cmark \\
-díade & dí-a*de \xmark & dí*a*de \cmark \\
-diádico & di-á*di*co \xmark & di*á*di*co \cmark \\
-diádoco & di-á*do*co \xmark & di*á*do*co \cmark \\
-diáfise & di-á*fi*se \xmark & di*á*fi*se \cmark \\
-diatômico & di*a-tô*mi*co \xmark & di*a*tô*mi*co \cmark \\
-diérese & di-é*re*se \xmark & di*é*re*se \cmark \\
-diferenciável & di*fe*ren*ci-á*vel \xmark & di*fe*ren*ci*á*vel \cmark \\
-difluência & di*flu-ên*ci*a \xmark & di*flu*ên*ci*a \cmark \\
-díodo & dí-o*do \xmark & dí*o*do \cmark \\
-domiciliário & do*mi*ci*li-á*ri*o \xmark & do*mi*ci*li*á*ri*o \cmark \\
-dríade & drí-a*de \xmark & drí*a*de \cmark \\
-elastômero & e*las-tô*me*ro \xmark & e*las*tô*me*ro \cmark \\
-eluição & e*lu-i*ção \xmark & e*lu*i*ção \cmark \\
-éon & é-on \xmark & é*on \cmark \\
-epicôndilo & e*pi-côn*di*lo \xmark & e*pi*côn*di*lo \cmark \\
-épsilon & ép*si*lon \cmark & ép-si*lon \xmark \\
-equidna & e*quid*na \cmark & e*qui.d*na \xmark \\
-estatuário & es*ta*tu-á*ri*o \xmark & es*ta*tu*á*ri*o \cmark \\
-esteárico & es*te-á*ri*co \xmark & es*te*á*ri*co \cmark \\
-estereoquímica & es*te*re*o-quí*mi*ca \xmark & es*te*re*o*quí*mi*ca \cmark \\
-etnônimo & et-nô*ni*mo \xmark & et*nô*ni*mo \cmark \\
-eucariótico & eu*ca*ri-ó*ti*co \xmark & eu*ca*ri*ó*ti*co \cmark \\
-eurasiático & eu*ra*si-á*ti*co \xmark & eu*ra*si*á*ti*co \cmark \\
-europeísmo & eu*ro*pe-ís*mo \xmark & eu*ro*pe*ís*mo \cmark \\
-europeísta & eu*ro*pe-ís*ta \xmark & eu*ro*pe*ís*ta \cmark \\
-evangeliário & e*van*ge*li-á*ri*o \xmark & e*van*ge*li*á*ri*o \cmark \\
-feroês & fe*ro-ês \xmark & fe*ro*ês \cmark \\
-fiável & fi-á*vel \xmark & fi*á*vel \cmark \\
-fisiólogo & fi*si-ó*lo*go \xmark & fi*si*ó*lo*go \cmark \\
-fluídico & flu-í*di*co \xmark & flu-í*di*co \xmark \\
-foliáceo & fo*li-á*ce*o \xmark & fo*li*á*ce*o \cmark \\
-folíolo & fo*lí-o*lo \xmark & fo*lí*o*lo \cmark \\
-fotoperíodo & fo*to*pe*rí-o*do \xmark & fo*to*pe*rí*o*do \cmark \\
-fotoquímica & fo*to-quí*mi*ca \xmark & fo*to*quí*mi*ca \cmark \\
-fotoquímico & fo*to-quí*mi*co \xmark & fo*to*quí*mi*co \cmark \\
-friável & fri-á*vel \xmark & fri*á*vel \cmark \\
-ftálico & f.tá*li*co \xmark & f.tá*li*co \xmark \\
-fuá & fu-á \xmark & fu*á \cmark \\
-genômico & ge-nô*mi*co \xmark & ge*nô*mi*co \cmark \\
-genuinidade & ge*nu-i*ni*da*de \xmark & ge*nu*i*ni*da*de \cmark \\
-geoquímica & ge*o-quí*mi*ca \xmark & ge*o*quí*mi*ca \cmark \\
-geoquímico & ge*o-quí*mi*co \xmark & ge*o*quí*mi*co \cmark \\
-geotectônica & ge*o*tec-tô*ni*ca \xmark & ge*o*tec*tô*ni*ca \cmark \\
-gimnodesportivo & gim*no*des*por*ti*vo \cmark & gi.m-no*des*por*ti*vo \xmark \\
-glaciário & gla*ci-á*ri*o \xmark & gla*ci*á*ri*o \cmark \\
-glicoproteína & gli*co*pro*te-í*na \xmark & gli*co*pro*te*í*na \cmark \\
-gnaisse & g.nais*se \xmark & g.nais*se \xmark \\
-goês & go-ês \xmark & go*ês \cmark \\
-graxaim & gra*xa-im \xmark & gra*xa-im \xmark \\
-helíaco & he*lí-a*co \xmark & he*lí*a*co \cmark \\
-henoteísmo & he*no*te-ís*mo \xmark & he*no*te*ís*mo \cmark \\
-heptacampeão & hep*ta*cam*pe-ão \xmark & hep*ta*cam*pe*ão \cmark \\
-heteroátomo & he*te*ro-á*to*mo \xmark & he*te*ro*á*to*mo \cmark \\
-higiénico & hi*gi-é*ni*co \xmark & hi*gi*é*ni*co \cmark \\
-hióideo & hi-ói*de*o \xmark & hi*ói*de*o \cmark \\
-hipersônico & hi*per-sô*ni*co \xmark & hi*per*sô*ni*co \cmark \\
-hipocôndrio & hi*po-côn*dri*o \xmark & hi*po*côn*dri*o \cmark \\
-hipomaníaco & hi*po*ma*ní-a*co \xmark & hi*po*ma*ní*a*co \cmark \\
-histoquímica & his*to-quí*mi*ca \xmark & his*to*quí*mi*ca \cmark \\
-iá & i-á \xmark & i*á \cmark \\
-ião & i-ão \xmark & i*ão \cmark \\
-iatroquímica & i*a*tro-quí*mi*ca \xmark & i*a*tro*quí*mi*ca \cmark \\
-icônico & i-cô*ni*co \xmark & i*cô*ni*co \cmark \\
-ictiólogo & ic*ti-ó*lo*go \xmark & ic*ti*ó*lo*go \cmark \\
-indeiscente & in*de-is*cen*te \xmark & in*de-is*cen*te \xmark \\
-indemnização & in*dem*ni*za*ção \cmark & in*de.m-ni*za*ção \xmark \\
-indemnizar & in*dem*ni*zar \cmark & in*de.m-ni*zar \xmark \\
-instituidor & ins*ti*tu-i*dor \xmark & ins*ti*tu*i*dor \cmark \\
-intercambiável & in*ter*cam*bi-á*vel \xmark & in*ter*cam*bi*á*vel \cmark \\
-interferômetro & in*ter*fe-rô*me*tro \xmark & in*ter*fe*rô*me*tro \cmark \\
-íon & í-on \xmark & í*on \cmark \\
-ipsilateral & ip*si*la*te*ral \cmark & ip-si*la*te*ral \xmark \\
-ípsilon & íp*si*lon \cmark & íp-si*lon \xmark \\
-isômero & i-sô*me*ro \xmark & i*sô*me*ro \cmark \\
-isotônico & i*so-tô*ni*co \xmark & i*so*tô*ni*co \cmark \\
-itaúba & i*ta-ú*ba \xmark & i*ta*ú*ba \cmark \\
-jandaíra & jan*da-í*ra \xmark & jan*da*í*ra \cmark \\
-jaó & ja-ó \xmark & ja*ó \cmark \\
-jauá & jau-á \xmark & jau*á \cmark \\
-jihadista & ji-ha*dis*ta \xmark & ji-ha*dis*ta \xmark \\
-joinvilense & jo-in*vi*len*se \xmark & jo-in*vi*len*se \xmark \\
-jundiá & jun*di-á \xmark & jun*di*á \cmark \\
-jutaí & ju*ta-í \xmark & ju*ta*í \cmark \\
-kuwaitiano & ku-wai*ti*a*no \xmark & ku-wai*ti*a*no \xmark \\
-lemna & lem*na \cmark & le.m-na \xmark \\
-lemniscata & lem*nis*ca*ta \cmark & le.m-nis*ca*ta \xmark \\
-lemnisco & lem*nis*co \cmark & le.m-nis*co \xmark \\
-leônico & le-ô*ni*co \xmark & le*ô*ni*co \cmark \\
-lidocaína & li*do*ca-í*na \xmark & li*do*ca*í*na \cmark \\
-liechtensteinense & li*e.ch*tens*tei*nen*se \xmark & li*e.ch*tens*tei*nen*se \xmark \\
-limnologia & lim*no*lo*gi*a \cmark & li.m-no*lo*gi*a \xmark \\
-litíase & li*tí-a*se \xmark & li*tí*a*se \cmark \\
-macaúba & ma*ca-ú*ba \xmark & ma*ca*ú*ba \cmark \\
-magnetômetro & mag*ne-tô*me*tro \xmark & mag*ne*tô*me*tro \cmark \\
-maís & ma-ís \xmark & ma*ís \cmark \\
-malauiano & ma*lau-i*a*no \xmark & ma*lau-i*a*no \xmark \\
-malônico & ma-lô*ni*co \xmark & ma*lô*ni*co \cmark \\
-maruí & ma*ru-í \xmark & ma*ru*í \cmark \\
-maruim & ma*ru-im \xmark & ma*ru-im \xmark \\
-meã & me-ã \xmark & me*ã \cmark \\
-meão & me-ão \xmark & me*ão \cmark \\
-meiótico & mei-ó*ti*co \xmark & mei*ó*ti*co \cmark \\
-microbiólogo & mi*cro*bi-ó*lo*go \xmark & mi*cro*bi*ó*lo*go \cmark \\
-midríase & mi*drí-a*se \xmark & mi*drí*a*se \cmark \\
-miíase & mi-í-a*se \xmark & mi*í*a*se \cmark \\
-miliário & mi*li-á*ri*o \xmark & mi*li*á*ri*o \cmark \\
-mnemônico & m.ne-mô*ni*co \xmark & mne*mô*ni*co \cmark \\
-monofônico & mo*no-fô*ni*co \xmark & mo*no*fô*ni*co \cmark \\
-moquém & mo-quém \xmark & mo*quém \cmark \\
-morrião & mor*ri-ão \xmark & mor*ri*ão \cmark \\
-neodarwinismo & ne*o*dar-wi*nis*mo \xmark & ne*o*dar-wi*nis*mo \xmark \\
-nobiliário & no*bi*li-á*ri*o \xmark & no*bi*li*á*ri*o \cmark \\
-nucléolo & nu*clé-o*lo \xmark & nu*clé*o*lo \cmark \\
-octaédrico & oc*ta-é*dri*co \xmark & oc*ta*é*dri*co \cmark \\
-odeão & o*de-ão \xmark & o*de*ão \cmark \\
-oídio & o-í*di*o \xmark & o*í*di*o \cmark \\
-omíada & o*mí-a*da \xmark & o*mí*a*da \cmark \\
-omnipotente & om*ni*po*ten*te \cmark & o.m-ni*po*ten*te \xmark \\
-omnisciente & om*nis*ci*en*te \cmark & o.m-nis*ci*en*te \xmark \\
-omnívoro & om*ní*vo*ro \cmark & o.m-ní*vo*ro \xmark \\
-oócito & o-ó*ci*to \xmark & o*ó*ci*to \cmark \\
-orfeão & or*fe-ão \xmark & or*fe*ão \cmark \\
-oriá & o*ri-á \xmark & o*ri*á \cmark \\
-ortodôntico & or*to-dôn*ti*co \xmark & or*to*dôn*ti*co \cmark \\
-ossuário & os*su-á*ri*o \xmark & os*su*á*ri*o \cmark \\
-osteíte & os*te-í*te \xmark & os*te*í*te \cmark \\
-ostiário & os*ti-á*ri*o \xmark & os*ti*á*ri*o \cmark \\
-paleógrafo & pa*le-ó*gra*fo \xmark & pa*le*ó*gra*fo \cmark \\
-paleólogo & pa*le-ó*lo*go \xmark & pa*le*ó*lo*go \cmark \\
-panenteísmo & pa*nen*te-ís*mo \xmark & pa*nen*te*ís*mo \cmark \\
-patauá & pa*tau-á \xmark & pa*tau*á \cmark \\
-patoá & pa*to-á \xmark & pa*to*á \cmark \\
-pecíolo & pe*cí-o*lo \xmark & pe*cí*o*lo \cmark \\
-pequiá & pe*qui-á \xmark & pe*qui*á \cmark \\
-periélio & pe*ri-é*li*o \xmark & pe*ri*é*li*o \cmark \\
-píon & pí-on \xmark & pí*on \cmark \\
-pitiríase & pi*ti*rí-a*se \xmark & pi*ti*rí*a*se \cmark \\
-pium & pi-um \xmark & pi-um \xmark \\
-planctônico & planc-tô*ni*co \xmark & planc*tô*ni*co \cmark \\
-pneuma & p.neu*ma \xmark & pneu*ma \cmark \\
-pneumonite & p.neu*mo*ni*te \xmark & pneu*mo*ni*te \cmark \\
-pneumotórax & p.neu*mo*tó*rax \xmark & pneu*mo*tó*rax \cmark \\
-poliúria & po*li-ú*ri*a \xmark & po*li*ú*ri*a \cmark \\
-poraquê & po*ra-quê \xmark & po*ra*quê \cmark \\
-preênsil & pre-ên*sil \xmark & pre*ên*sil \cmark \\
-príon & prí-on \xmark & prí*on \cmark \\
-procariótico & pro*ca*ri-ó*ti*co \xmark & pro*ca*ri*ó*ti*co \cmark \\
-procônsul & pro-côn*sul \xmark & pro*côn*sul \cmark \\
-proteólise & pro*te-ó*li*se \xmark & pro*te*ó*li*se \cmark \\
-pseudocientífico & p.seu*do*ci*en*tí*fi*co \xmark & pseu*do*ci*en*tí*fi*co \cmark \\
-pseudofruto & p.seu*do*fru*to \xmark & pseu*do*fru*to \cmark \\
-psicadélico & p.si*ca*dé*li*co \xmark & psi*ca*dé*li*co \cmark \\
-psicoativo & p.si*co*a*ti*vo \xmark & psi*co*a*ti*vo \cmark \\
-psicocirurgia & p.si*co*ci*rur*gi*a \xmark & psi*co*ci*rur*gi*a \cmark \\
-psicofisiologia & p.si*co*fi*si*o*lo*gi*a \xmark & psi*co*fi*si*o*lo*gi*a \cmark \\
-psicofonia & p.si*co*fo*ni*a \xmark & psi*co*fo*ni*a \cmark \\
-psicografia & p.si*co*gra*fi*a \xmark & psi*co*gra*fi*a \cmark \\
-psicopompo & p.si*co*pom*po \xmark & psi*co*pom*po \cmark \\
-psicoterápico & p.si*co*te*rá*pi*co \xmark & psi*co*te*rá*pi*co \cmark \\
-psoas & p.so*as \xmark & p.so*as \xmark \\
-pterodáctilo & p.te*ro*dác*ti*lo \xmark & pte*ro*dác*ti*lo \cmark \\
-ptialina & p.ti*a*li*na \xmark & pti*a*li*na \cmark \\
-ptolemaico & p.to*le*mai*co \xmark & pto*le*mai*co \cmark \\
-radioquímica & ra*di*o-quí*mi*ca \xmark & ra*di*o*quí*mi*ca \cmark \\
-randômico & ran-dô*mi*co \xmark & ran*dô*mi*co \cmark \\
-reciário & re*ci-á*ri*o \xmark & re*ci*á*ri*o \cmark \\
-reimpresso & re-im*pres*so \xmark & re*im*pres*so \cmark \\
-reimprimir & re-im*pri*mir \xmark & re*im*pri*mir \cmark \\
-sambaíba & sam*ba-í*ba \xmark & sam*ba*í*ba \cmark \\
-samnita & sam*ni*ta \cmark & sa.m-ni*ta \xmark \\
-saxônico & sa-xô*ni*co \xmark & sa*xô*ni*co \cmark \\
-semiárido & se*mi-á*ri*do \xmark & se*mi*á*ri*do \cmark \\
-semiótico & se*mi-ó*ti*co \xmark & se*mi*ó*ti*co \cmark \\
-semipermeável & se*mi*per*me-á*vel \xmark & se*mi*per*me*á*vel \cmark \\
-sépsis & sép*sis \cmark & sép-sis \xmark \\
-serôdio & se-rô*di*o \xmark & se*rô*di*o \cmark \\
-serventuário & ser*ven*tu-á*ri*o \xmark & ser*ven*tu*á*ri*o \cmark \\
-siálico & si-á*li*co \xmark & si*á*li*co \cmark \\
-siríaco & si*rí-a*co \xmark & si*rí*a*co \cmark \\
-sonômetro & so-nô*me*tro \xmark & so*nô*me*tro \cmark \\
-suaíli & su*a-í*li \xmark & su*a*í*li \cmark \\
-subatômico & su*ba-tô*mi*co \xmark & su*ba*tô*mi*co \cmark \\
-subdiácono & sub*di-á*co*no \xmark & sub*di*á*co*no \cmark \\
-sublevar & su.b-le*var \xmark & sub*le*var \cmark \\
-subliminal & su.b-li*mi*nal \xmark & sub*li*mi*nal \cmark \\
-sublinear & su.b-li*ne*ar \xmark & sub*li*ne*ar \cmark \\
-sublingual & su.b-lin*gual \xmark & sub*lin*gual \cmark \\
-sublunar & su.b-lu*nar \xmark & sub*lu*nar \cmark \\
-subsequência & sub*se-quên*ci*a \xmark & sub*se*quên*ci*a \cmark \\
-substituinte & subs*ti*tu-in*te \xmark & subs*ti*tu-in*te \xmark \\
-coimbra & co-im*bra \xmark & co*im*bra \cmark \\
-coimperador & co-im*pe*ra*dor \xmark & co*im*pe*ra*dor \cmark \\
-reimposição & re-im*po*si*ção \xmark & re*im*po*si*ção \cmark \\
-bioimpressão & bi*o-im*pres*são \xmark & bi*o*im*pres*são \cmark \\
-neoimpressionista & ne*o-im*pres*si*o*nis*ta \xmark & ne*o*im*pres*si*o*nis*ta \cmark \\
-autoimposto & au*to-im*pos*to \xmark & au*to*im*pos*to \cmark \\
-reimplementação & re-im*ple*men*ta*ção \xmark & re*im*ple*men*ta*ção \cmark \\
-teleimpressor & te*le-im*pres*sor \xmark & te*le*im*pres*sor \cmark \\
-reimposta & re-im*pos*ta \xmark & re*im*pos*ta \cmark \\
-reimplementar & re-im*ple*men*tar \xmark & re*im*ple*men*tar \cmark \\
-reimpulsionar & re-im*pul*si*o*nar \xmark & re*im*pul*si*o*nar \cmark \\
-autoimposição & au*to-im*po*si*ção \xmark & au*to*im*po*si*ção \cmark \\
-cacauicultor & ca*cau-i*cul*tor \xmark & ca*cau*i*cul*tor \cmark \\
-sanduiche & san*du-i*che \xmark & san*du*i*che \cmark \\
-ruidosamente & ru-i*do*sa*men*te \xmark & ru*i*do*sa*men*te \cmark \\
-promiscuidade & pro*mis*cu-i*da*de \xmark & pro*mis*cu*i*da*de \cmark \\
-inocuidade & i*no*cu-i*da*de \xmark & i*no*cu*i*da*de \cmark \\
-reincidência & re-in*ci*dên*ci.a \xmark & re*in*ci*dên*ci.a \xmark \\
-reincluir & re-in*clu-ir \xmark & re*in*clu*ir \cmark \\
-reinfecção & re-in*fec*ção \xmark & re*in*fec*ção \cmark \\
-reinforçar & re-in*for*çar \xmark & re*in*for*çar \cmark \\
-reinsurgir & re-in*sur*gir \xmark & re*in*sur*gir \cmark \\
-reinstalado & re-ins*ta*la*do \xmark & re*ins*ta*la*do \cmark \\
-reinstituído & re-ins*ti*tu-í*do \xmark & re*ins*ti*tu*í*do \cmark \\
-reinvindicar & re-in*vin*di*car \xmark & re*in*vin*di*car \cmark \\
-bioincrustação & bi*o-in*crus*ta*ção \xmark & bi*o*in*crus*ta*ção \cmark \\
-agroindustrial & a*gro-in*dus*tri*al \xmark & a*gro*in*dus*tri*al \cmark \\
-bioindicadores & bi*o-in*di*ca*do*res \xmark & bi*o*in*di*ca*do*res \cmark \\
-autoindulgência & au*to-in*dul*gên*ci.a \xmark & au*to*in*dul*gên*ci.a \xmark \\
-autoinduzida & au*to-in*du*zi*da \xmark & au*to*in*du*zi*da \cmark \\
-microindústria & mi*cro-in*dús*tri*a \xmark & mi*cro*in*dús*tri*a \cmark \\
-tecnoindustrial & tec*no-in*dus*tri*al \xmark & tec*no*in*dus*tri*al \cmark \\
-bioinformática & bi*o-in*for*má*ti*ca \xmark & bi*o*in*for*má*ti*ca \cmark \\
-coinfecção & co-in*fec*ção \xmark & co*in*fec*ção \cmark \\
-geoinformação & ge.o-in*for*ma*ção \xmark & ge.o*in*for*ma*ção \xmark \\
-autoinfecção & au*to-in*fec*ção \xmark & au*to*in*fec*ção \cmark \\
-neuroinformática & neu*ro-in*for*má*ti*ca \xmark & neu*ro*in*for*má*ti*ca \cmark \\
-amendoins & a*men*do-ins \xmark & a*men*do*ins \cmark \\
-videoinstalação & vi*de*o-ins*ta*la*ção \xmark & vi*de*o*ins*ta*la*ção \cmark \\
-autointitulado & au*to-in*ti*tu*la*do \xmark & au*to*in*ti*tu*la*do \cmark \\
-saindo & sa-in*do \xmark & sa*in*do \cmark \\
-caindo & ca-in*do \xmark & ca*in*do \cmark \\
-contraindicações & con*tra-in*di*ca*ções \xmark & con*tra*in*di*ca*ções \cmark \\
-abstraindo & abs*tra-in*do \xmark & abs*tra*in*do \cmark \\
-prainha & pra-i*nha \xmark & pra*i*nha \cmark \\
-lagoinha & la*go-i*nha \xmark & la*go*i*nha \cmark \\
-canoinha & ca*no-i*nha \xmark & ca*no*i*nha \cmark \\
-reimpresso & re-im*pres*so \xmark & re*im*pres*so \cmark \\
-genuino & ge*nu-i*no \xmark & ge*nu*i*no \cmark \\
-ruina & ru-i*na \xmark & ru*i*na \cmark \\
-arruinado & ar*ru-i*na*do \xmark & ar*ru*i*na*do \cmark \\
-arruinou & ar*ru-i*nou \xmark & ar*ru*i*nou \cmark \\
-suino & su-i*no \xmark & su*i*no \cmark \\
-suina & su-i*na \xmark & su*i*na \cmark \\
-ajuizamento & a*ju-i*za*men*to \xmark & a*ju*i*za*men*to \cmark \\
-luiz & lu-iz \xmark & lu*iz \cmark \\
-luiza & lu-i*za \xmark & lu*i*za \cmark \\
-amnésia & a-m.né*si*a \xmark & a*mné*si*a \cmark \\
-amniota & a-m.ni*o*ta \xmark & a*mni*o*ta \cmark \\
-amniótico & a-m.ni-ó*ti*co \xmark & a*mni*ó*ti*co \cmark \\
-diuréticos & di-u*ré*ti*cos \xmark & di*u*ré*ti*cos \cmark \\
-diurese & di-u*re*se \xmark & di*u*re*se \cmark \\
-feiurinha & fei-u*ri*nha \xmark & fei*u*ri*nha \cmark \\
-íodo & í-o*do \xmark & í*o*do \cmark \\
-íons & í-ons \xmark & í*ons \cmark \\
-antíope & an*tí-o*pe \xmark & an*tí*o*pe \cmark \\
-médiuns & mé*di-uns \xmark & mé*di*uns \cmark \\
-fluór & flu-ór \xmark & flu*ór \cmark \\
-sequóia & se-quói*a \xmark & se*quói*a \cmark \\
-subquântico & sub-quân*ti*co \xmark & sub*quân*ti*co \cmark \\
-\\
-\hline
-37798 & 1368 & 132 \\
-\hline
+zaragatoa & za*ra*ga*to*a \cmark & za*ra*ga*to-a \xmark \\
+zodíaco & zo*dí-a*co \xmark & zo*dí*a*co \cmark \\
+zombaria & zom*ba*ri*a \cmark & zom*ba*ri-a \xmark \\
+zoofilia & zo*o*fi*li*a \cmark & zo*o*fi*li-a \xmark \\
+zoogeografia & zo*o*ge*o*gra*fi*a \cmark & zo*o*ge*o*gra*fi-a \xmark \\
+zoolagnia & zo*o*lag*ni*a \cmark & zo*o*lag*ni-a \xmark \\
+zoologia & zo*o*lo*gi*a \cmark & zo*o*lo*gi-a \xmark \\
+zoósporo & zo-ós*po*ro \xmark & zo*ós*po*ro \cmark \\
+zootecnia & zo*o*tec*ni*a \cmark & zo*o*tec*ni-a \xmark \\
+zoo & zo*o \cmark & zo-o \xmark \\
+zurraria & zur*ra*ri*a \cmark & zur*ra*ri-a \xmark \\
+total correct & 1331 & 1992 \\

### 2024-06-14 article/comparedresults_nofinalvowel.tex
updates

--- 2023-04-11 article/comparedresults.tex
@@
+aarônico & a*a-rô*ni*co \xmark & a*a*rô*ni*co \cmark \\
+abdômen & ab-dô*men \xmark & ab*dô*men \cmark \\
+abiótico & a*bi-ó*ti*co \xmark & a*bi*ó*ti*co \cmark \\
+abluir & a*blu-ir \xmark & a*blu*ir \cmark \\
+abraâmico & a*bra-â*mi*co \xmark & a*bra*â*mi*co \cmark \\
+abrupto & a.b-rup*to \xmark & a.b-rup*to \xmark \\
+absenteísmo & ab*sen*te-ís*mo \xmark & ab*sen*te*ís*mo \cmark \\
+abstraído & abs*tra-í*do \xmark & abs*tra*í*do \cmark \\
+abstrair & abs*tra-ir \xmark & abs*tra*ir \cmark \\
+acetaldeído & a*ce*tal*de-í*do \xmark & a*ce*tal*de*í*do \cmark \\
+acônito & a-cô*ni*to \xmark & a*cô*ni*to \cmark \\
+acordeão & a*cor*de-ão \xmark & a*cor*de*ão \cmark \\
+acuidade & a*cu-i*da*de \xmark & a*cu-i*da*de \xmark \\
+adail & a*da-il \xmark & a*da-il \xmark \\
+adriático & a*dri-á*ti*co \xmark & a*dri*á*ti*co \cmark \\
+aético & a-é*ti*co \xmark & a*é*ti*co \cmark \\
+afluir & a*flu-ir \xmark & a*flu*ir \cmark \\
+afrodisíaco & a*fro*di*sí-a*co \xmark & a*fro*di*sí*a*co \cmark \\
+agogô & a*go-gô \xmark & a*go*gô \cmark \\
+agrião & a*gri-ão \xmark & a*gri*ão \cmark \\
+agronômico & a*gro-nô*mi*co \xmark & a*gro*nô*mi*co \cmark \\
 ainda & a-in*da \xmark & a*in*da \cmark \\
-país & pa-ís \xmark & pa*ís \cmark \\
-região & re*gi-ão \xmark & re*gi*ão \cmark \\
-saúde & sa-ú*de \xmark & sa*ú*de \cmark \\
-período & pe*rí-o*do \xmark & pe*rí*o*do \cmark \\
-juiz & ju-iz \xmark & ju*iz \cmark \\
-união & u*ni-ão \xmark & u*ni*ão \cmark \\
-econômico & e*co-nô*mi*co \xmark & e*co*nô*mi*co \cmark \\
-aí & a-í \xmark & a*í \cmark \\
-sair & sa-ir \xmark & sa*ir \cmark \\
-opinião & o*pi*ni-ão \xmark & o*pi*ni*ão \cmark \\
-constituição & cons*ti*tu-i*ção \xmark & cons*ti*tu*i*ção \cmark \\
-saída & sa-í*da \xmark & sa*í*da \cmark \\
-luís & lu-ís \xmark & lu*ís \cmark \\
-campeão & cam*pe-ão \xmark & cam*pe*ão \cmark \\
+ajuizar & a*ju-i*zar \xmark & a*ju*i*zar \cmark \\
+alaúde & a*la-ú*de \xmark & a*la*ú*de \cmark \\
+alcíone & al*cí-o*ne \xmark & al*cí*o*ne \cmark \\
+alcoólatra & al*co-ó*la*tra \xmark & al*co*ó*la*tra \cmark \\
+alcoólico & al*co-ó*li*co \xmark & al*co*ó*li*co \cmark \\
+aldeão & al*de-ão \xmark & al*de*ão \cmark \\
+aldeído & al*de-í*do \xmark & al*de*í*do \cmark \\
+aleúte & a*le-ú*te \xmark & a*le*ú*te \cmark \\
 aliás & a*li-ás \xmark & a*li*ás \cmark \\
-distribuição & dis*tri*bu-i*ção \xmark & dis*tri*bu*i*ção \cmark \\
-avião & a*vi-ão \xmark & a*vi*ão \cmark \\
-diário & di-á*ri*o \xmark & di*á*ri*o \cmark \\
-diária & di-á*ri*a \xmark & di*á*ri*a \cmark \\
-daí & da-í \xmark & da*í \cmark \\
-cair & ca-ir \xmark & ca*ir \cmark \\
-paraíba & pa*ra-í*ba \xmark & pa*ra*í*ba \cmark \\
-prejuízo & pre*ju-í*zo \xmark & pre*ju*í*zo \cmark \\
-judiciário & ju*di*ci-á*ri*o \xmark & ju*di*ci*á*ri*o \cmark \\
-suíça & su-í*ça \xmark & su*í*ça \cmark \\
-influência & in*flu-ên*ci*a \xmark & in*flu*ên*ci*a \cmark \\
-depoimento & de*po-i*men*to \xmark & de*po-i*men*to \xmark \\
-instituição & ins*ti*tu-i*ção \xmark & ins*ti*tu*i*ção \cmark \\
-consequência & con*se-quên*ci*a \xmark & con*se*quên*ci*a \cmark \\
-usuário & u*su-á*ri*o \xmark & u*su*á*ri*o \cmark \\
-contribuição & con*tri*bu-i*ção \xmark & con*tri*bu*i*ção \cmark \\
-diminuir & di*mi*nu-ir \xmark & di*mi*nu*ir \cmark \\
-fenômeno & fe-nô*me*no \xmark & fe*nô*me*no \cmark \\
-ruim & ru-im \xmark & ru-im \xmark \\
-construir & cons*tru-ir \xmark & cons*tru*ir \cmark \\
-veículo & ve-í*cu*lo \xmark & ve*í*cu*lo \cmark \\
-cocaína & co*ca-í*na \xmark & co*ca*í*na \cmark \\
-paul & pa-ul \xmark & pa-ul \xmark \\
-reunir & re-u*nir \xmark & re-u*nir \xmark \\
-continuidade & con*ti*nu-i*da*de \xmark & con*ti*nu*i*da*de \cmark \\
-diálogo & di-á*lo*go \xmark & di*á*lo*go \cmark \\
-atrair & a*tra-ir \xmark & a*tra*ir \cmark \\
-ocasião & o*ca*si-ão \xmark & o*ca*si*ão \cmark \\
-sebastião & se*bas*ti-ão \xmark & se*bas*ti*ão \cmark \\
-sequência & se-quên*ci*a \xmark & se*quên*ci*a \cmark \\
-substituir & subs*ti*tu-ir \xmark & subs*ti*tu*ir \cmark \\
-incluir & in*clu-ir \xmark & in*clu*ir \cmark \\
-gaúcho & ga-ú*cho \xmark & ga*ú*cho \cmark \\
-poluição & po*lu-i*ção \xmark & po*lu*i*ção \cmark \\
-proibido & pro-i*bi*do \xmark & pro*i*bi*do \cmark \\
-rainha & ra-i*nha \xmark & ra*i*nha \cmark \\
-religião & re*li*gi-ão \xmark & re*li*gi*ão \cmark \\
-paraíso & pa*ra-í*so \xmark & pa*ra*í*so \cmark \\
-frequência & fre-quên*ci*a \xmark & fre*quên*ci*a \cmark \\
-distribuir & dis*tri*bu-ir \xmark & dis*tri*bu*ir \cmark \\
-substituição & subs*ti*tu-i*ção \xmark & subs*ti*tu*i*ção \cmark \\
-contribuinte & con*tri*bu-in*te \xmark & con*tri*bu*in*te \cmark \\
-conteúdo & con*te-ú*do \xmark & con*te*ú*do \cmark \\
-leão & le-ão \xmark & le*ão \cmark \\
-concluir & con*clu-ir \xmark & con*clu*ir \cmark \\
-proibição & pro-i*bi*ção \xmark & pro*i*bi*ção \cmark \\
-sociólogo & so*ci-ó*lo*go \xmark & so*ci*ó*lo*go \cmark \\
-construído & cons*tru-í*do \xmark & cons*tru*í*do \cmark \\
-maceió & ma*cei-ó \xmark & ma*cei*ó \cmark \\
-diminuição & di*mi*nu-i*ção \xmark & di*mi*nu*i*ção \cmark \\
-crediário & cre*di-á*ri*o \xmark & cre*di*á*ri*o \cmark \\
-pivô & pi-vô \xmark & pi*vô \cmark \\
-substituído & subs*ti*tu-í*do \xmark & subs*ti*tu*í*do \cmark \\
-razoável & ra*zo-á*vel \xmark & ra*zo*á*vel \cmark \\
-juíza & ju-í*za \xmark & ju*í*za \cmark \\
-coincidência & co-in*ci*dên*ci*a \xmark & co*in*ci*dên*ci*a \cmark \\
-rebelião & re*be*li-ão \xmark & re*be*li*ão \cmark \\
-noticiário & no*ti*ci-á*ri*o \xmark & no*ti*ci*á*ri*o \cmark \\
-olimpíada & o*lim*pí-a*da \xmark & o*lim*pí*a*da \cmark \\
-imobiliário & i*mo*bi*li-á*ri*o \xmark & i*mo*bi*li*á*ri*o \cmark \\
-austríaco & aus*trí-a*co \xmark & aus*trí*a*co \cmark \\
-penitenciária & pe*ni*ten*ci-á*ri*a \xmark & pe*ni*ten*ci*á*ri*a \cmark \\
-psicologia & p.si*co*lo*gi*a \xmark & psi*co*lo*gi*a \cmark \\
-contribuir & con*tri*bu-ir \xmark & con*tri*bu*ir \cmark \\
-aéreo & a-é*re*o \xmark & a*é*re*o \cmark \\
-psicanálise & p.si*ca*ná*li*se \xmark & psi*ca*ná*li*se \cmark \\
-vestuário & ves*tu-á*ri*o \xmark & ves*tu*á*ri*o \cmark \\
-destruição & des*tru-i*ção \xmark & des*tru*i*ção \cmark \\
-viúva & vi-ú*va \xmark & vi*ú*va \cmark \\
-distribuído & dis*tri*bu-í*do \xmark & dis*tri*bu*í*do \cmark \\
-juízo & ju-í*zo \xmark & ju*í*zo \cmark \\
-constituinte & cons*ti*tu-in*te \xmark & cons*ti*tu-in*te \xmark \\
-presidenciável & pre*si*den*ci-á*vel \xmark & pre*si*den*ci*á*vel \cmark \\
-viável & vi-á*vel \xmark & vi*á*vel \cmark \\
-suíço & su-í*ço \xmark & su*í*ço \cmark \\
-destruir & des*tru-ir \xmark & des*tru*ir \cmark \\
-saído & sa-í*do \xmark & sa*í*do \cmark \\
-concluído & con*clu-í*do \xmark & con*clu*í*do \cmark \\
-distribuidora & dis*tri*bu-i*do*ra \xmark & dis*tri*bu*i*do*ra \cmark \\
-imobiliária & i*mo*bi*li-á*ri*a \xmark & i*mo*bi*li*á*ri*a \cmark \\
-sinfônica & sin-fô*ni*ca \xmark & sin*fô*ni*ca \cmark \\
-uísque & u-ís*que \xmark & u*ís*que \cmark \\
-poética & po-é*ti*ca \xmark & po*é*ti*ca \cmark \\
-prostituição & pros*ti*tu-i*ção \xmark & pros*ti*tu*i*ção \cmark \\
-rodoviário & ro*do*vi-á*ri*o \xmark & ro*do*vi*á*ri*o \cmark \\
-bicampeão & bi*cam*pe-ão \xmark & bi*cam*pe*ão \cmark \\
-psicológico & p.si*co*ló*gi*co \xmark & psi*co*ló*gi*co \cmark \\
-proibir & pro-i*bir \xmark & pro*i*bir \cmark \\
-triunfo & tri-un*fo \xmark & tri*un*fo \cmark \\
-variável & va*ri-á*vel \xmark & va*ri*á*vel \cmark \\
-criciúma & cri*ci-ú*ma \xmark & cri*ci*ú*ma \cmark \\
-sinônimo & si-nô*ni*mo \xmark & si*nô*ni*mo \cmark \\
-legião & le*gi-ão \xmark & le*gi*ão \cmark \\
-caído & ca-í*do \xmark & ca*í*do \cmark \\
-equívoco & e-quí*vo*co \xmark & e*quí*vo*co \cmark \\
-baía & ba-í-a \xmark & ba*í*a \cmark \\
-quilômetro & qui-lô*me*tro \xmark & qui*lô*me*tro \cmark \\
-raiz & ra-iz \xmark & ra-iz \xmark \\
-psiquiatra & p.si*qui*a*tra \xmark & psi*qui*a*tra \cmark \\
-tricampeão & tri*cam*pe-ão \xmark & tri*cam*pe*ão \cmark \\
-psicanalista & p.si*ca*na*lis*ta \xmark & psi*ca*na*lis*ta \cmark \\
-ruído & ru-í*do \xmark & ru*í*do \cmark \\
-possuir & pos*su-ir \xmark & pos*su*ir \cmark \\
-coibir & co-i*bir \xmark & co-i*bir \xmark \\
-soviético & so*vi-é*ti*co \xmark & so*vi*é*ti*co \cmark \\
-inviável & in*vi-á*vel \xmark & in*vi*á*vel \cmark \\
+almôndega & al-môn*de*ga \xmark & al*môn*de*ga \cmark \\
 alô & a-lô \xmark & a*lô \cmark \\
-heroína & he*ro-í*na \xmark & he*ro*í*na \cmark \\
-destruído & des*tru-í*do \xmark & des*tru*í*do \cmark \\
-telefônico & te*le-fô*ni*co \xmark & te*le*fô*ni*co \cmark \\
-saí & sa-í \xmark & sa*í \cmark \\
-suíte & su-í*te \xmark & su*í*te \cmark \\
-asiático & a*si-á*ti*co \xmark & a*si*á*ti*co \cmark \\
-irônico & i-rô*ni*co \xmark & i*rô*ni*co \cmark \\
-avô & a-vô \xmark & a*vô \cmark \\
-restituição & res*ti*tu-i*ção \xmark & res*ti*tu*i*ção \cmark \\
-atribuir & a*tri*bu-ir \xmark & a*tri*bu*ir \cmark \\
-ingenuidade & in*ge*nu-i*da*de \xmark & in*ge*nu*i*da*de \cmark \\
-psicólogo & p.si*có*lo*go \xmark & psi*có*lo*go \cmark \\
-pneu & p.neu \xmark & pneu \cmark \\
-tetracampeão & te*tra*cam*pe-ão \xmark & te*tra*cam*pe*ão \cmark \\
-vestiário & ves*ti-á*ri*o \xmark & ves*ti*á*ri*o \cmark \\
-proteína & pro*te-í*na \xmark & pro*te*í*na \cmark \\
-espião & es*pi-ão \xmark & es*pi*ão \cmark \\
-ciúme & ci-ú*me \xmark & ci*ú*me \cmark \\
-napoleão & na*po*le-ão \xmark & na*po*le*ão \cmark \\
-teórica & te-ó*ri*ca \xmark & te*ó*ri*ca \cmark \\
-intermediário & in*ter*me*di-á*ri*o \xmark & in*ter*me*di*á*ri*o \cmark \\
-constituir & cons*ti*tu-ir \xmark & cons*ti*tu*ir \cmark \\
-embrião & em*bri-ão \xmark & em*bri*ão \cmark \\
-autônomo & au-tô*no*mo \xmark & au*tô*no*mo \cmark \\
-confiável & con*fi-á*vel \xmark & con*fi*á*vel \cmark \\
-teórico & te-ó*ri*co \xmark & te*ó*ri*co \cmark \\
-estômago & es-tô*ma*go \xmark & es*tô*ma*go \cmark \\
-termômetro & ter-mô*me*tro \xmark & ter*mô*me*tro \cmark \\
-homônimo & ho-mô*ni*mo \xmark & ho*mô*ni*mo \cmark \\
-excluído & ex*clu-í*do \xmark & ex*clu*í*do \cmark \\
-penitenciário & pe*ni*ten*ci-á*ri*o \xmark & pe*ni*ten*ci*á*ri*o \cmark \\
-cardíaco & car*dí-a*co \xmark & car*dí*a*co \cmark \\
-mutuário & mu*tu-á*ri*o \xmark & mu*tu*á*ri*o \cmark \\
-aquém & a-quém \xmark & a*quém \cmark \\
-viário & vi-á*ri*o \xmark & vi*á*ri*o \cmark \\
-despoluição & des*po*lu-i*ção \xmark & des*po*lu*i*ção \cmark \\
-medíocre & me*dí-o*cre \xmark & me*dí*o*cre \cmark \\
-reintegração & re-in*te*gra*ção \xmark & re*in*te*gra*ção \cmark \\
-marquês & mar-quês \xmark & mar*quês \cmark \\
-beneficiário & be*ne*fi*ci-á*ri*o \xmark & be*ne*fi*ci*á*ri*o \cmark \\
-atribuição & a*tri*bu-i*ção \xmark & a*tri*bu*i*ção \cmark \\
-balneário & bal*ne-á*ri*o \xmark & bal*ne*á*ri*o \cmark \\
-coreógrafo & co*re-ó*gra*fo \xmark & co*re*ó*gra*fo \cmark \\
-incômodo & in-cô*mo*do \xmark & in*cô*mo*do \cmark \\
-sanduíche & san*du-í*che \xmark & san*du*í*che \cmark \\
-pecuária & pe*cu-á*ri*a \xmark & pe*cu*á*ri*a \cmark \\
-cirurgião & ci*rur*gi-ão \xmark & ci*rur*gi*ão \cmark \\
-jaú & ja-ú \xmark & ja*ú \cmark \\
-reconstruir & re*cons*tru-ir \xmark & re*cons*tru*ir \cmark \\
-influir & in*flu-ir \xmark & in*flu*ir \cmark \\
-santuário & san*tu-á*ri*o \xmark & san*tu*á*ri*o \cmark \\
-sutiã & su*ti-ã \xmark & su*ti*ã \cmark \\
-poético & po-é*ti*co \xmark & po*é*ti*co \cmark \\
-ensaísta & en*sa-ís*ta \xmark & en*sa*ís*ta \cmark \\
-porquê & por-quê \xmark & por*quê \cmark \\
-biólogo & bi-ó*lo*go \xmark & bi*ó*lo*go \cmark \\
-extrair & ex*tra-ir \xmark & ex*tra*ir \cmark \\
-reconstituição & re*cons*ti*tu-i*ção \xmark & re*cons*ti*tu*i*ção \cmark \\
+aloés & a*lo-és \xmark & a*lo*és \cmark \\
+alquímico & al-quí*mi*co \xmark & al*quí*mi*co \cmark \\
+altruísmo & al*tru-ís*mo \xmark & al*tru*ís*mo \cmark \\
+altruísta & al*tru-ís*ta \xmark & al*tru*ís*ta \cmark \\
+aluimento & a*lu-i*men*to \xmark & a*lu-i*men*to \xmark \\
+aluir & a*lu-ir \xmark & a*lu*ir \cmark \\
+aluvião & a*lu*vi-ão \xmark & a*lu*vi*ão \cmark \\
+alvéolo & al*vé-o*lo \xmark & al*vé*o*lo \cmark \\
+amazônico & a*ma-zô*ni*co \xmark & a*ma*zô*ni*co \cmark \\
+amebíase & a*me*bí-a*se \xmark & a*me*bí*a*se \cmark \\
+amendoim & a*men*do-im \xmark & a*men*do*im \cmark \\
+aminoácido & a*mi*no-á*ci*do \xmark & a*mi*no*á*ci*do \cmark \\
+amiúde & a*mi-ú*de \xmark & a*mi*ú*de \cmark \\
+amoníaco & a*mo*ní-a*co \xmark & a*mo*ní*a*co \cmark \\
+anafrodisíaco & a*na*fro*di*sí-a*co \xmark & a*na*fro*di*sí*a*co \cmark \\
+anatômico & a*na-tô*mi*co \xmark & a*na*tô*mi*co \cmark \\
+ancião & an*ci-ão \xmark & an*ci*ão \cmark \\
+ancilostomíase & an*ci*los*to*mí-a*se \xmark & an*ci*los*to*mí*a*se \cmark \\
+anemômetro & a*ne-mô*me*tro \xmark & a*ne*mô*me*tro \cmark \\
 anfitrião & an*fi*tri-ão \xmark & an*fi*tri*ão \cmark \\
 anônimo & a-nô*ni*mo \xmark & a*nô*ni*mo \cmark \\
+antagônico & an*ta-gô*ni*co \xmark & an*ta*gô*ni*co \cmark \\
+antiácido & an*ti-á*ci*do \xmark & an*ti*á*ci*do \cmark \\
+antialcoólico & an*ti*al*co-ó*li*co \xmark & an*ti*al*co*ó*li*co \cmark \\
+antibiótico & an*ti*bi-ó*ti*co \xmark & an*ti*bi*ó*ti*co \cmark \\
+antipatriótico & an*ti*pa*tri-ó*ti*co \xmark & an*ti*pa*tri*ó*ti*co \cmark \\
+antiquíssimo & an*ti-quís*si*mo \xmark & an*ti*quís*si*mo \cmark \\
+antônimo & an-tô*ni*mo \xmark & an*tô*ni*mo \cmark \\
+antropônimo & an*tro-pô*ni*mo \xmark & an*tro*pô*ni*mo \cmark \\
+anuidade & a*nu-i*da*de \xmark & a*nu*i*da*de \cmark \\
+anuir & a*nu-ir \xmark & a*nu*ir \cmark \\
+aórtico & a-ór*ti*co \xmark & a*ór*ti*co \cmark \\
+apreciável & a*pre*ci-á*vel \xmark & a*pre*ci*á*vel \cmark \\
 aquático & a-quá*ti*co \xmark & a*quá*ti*co \cmark \\
+aquém & a-quém \xmark & a*quém \cmark \\
+aquícola & a-quí*co*la \xmark & a*quí*co*la \cmark \\
+aquífero & a-quí*fe*ro \xmark & a*quí*fe*ro \cmark \\
+arábias & a*rá*bi.as \xmark & a*rá*bi.as \xmark \\
+arcaísmo & ar*ca-ís*mo \xmark & ar*ca*ís*mo \cmark \\
+aríete & a*rí-e*te \xmark & a*rí*e*te \cmark \\
+arqueólogo & ar*que-ó*lo*go \xmark & ar*que*ó*lo*go \cmark \\
+arquétipo & ar-qué*ti*po \xmark & ar*qué*ti*po \cmark \\
+arquidiácono & ar*qui*di-á*co*no \xmark & ar*qui*di*á*co*no \cmark \\
+arquitetônica & ar*qui*te-tô*ni*ca \xmark & ar*qui*te*tô*ni*ca \cmark \\
+arquitetônico & ar*qui*te-tô*ni*co \xmark & ar*qui*te*tô*ni*co \cmark \\
+arrais & ar*ra-is \xmark & ar*ra-is \xmark \\
+arruinar & ar*ru-i*nar \xmark & ar*ru*i*nar \cmark \\
+ascaridíase & as*ca*ri*dí-a*se \xmark & as*ca*ri*dí*a*se \cmark \\
+asiática & a*si-á*ti*ca \xmark & a*si*á*ti*ca \cmark \\
+asiático & a*si-á*ti*co \xmark & a*si*á*ti*co \cmark \\
+assiduidade & as*si*du-i*da*de \xmark & as*si*du*i*da*de \cmark \\
+associável & as*so*ci-á*vel \xmark & as*so*ci*á*vel \cmark \\
+astronômico & as*tro-nô*mi*co \xmark & as*tro*nô*mi*co \cmark \\
+ataúde & a*ta-ú*de \xmark & a*ta*ú*de \cmark \\
+ateísmo & a*te-ís*mo \xmark & a*te*ís*mo \cmark \\
+ateísta & a*te-ís*ta \xmark & a*te*ís*ta \cmark \\
+atômico & a-tô*mi*co \xmark & a*tô*mi*co \cmark \\
+atraído & a*tra-í*do \xmark & a*tra*í*do \cmark \\
+atrair & a*tra-ir \xmark & a*tra*ir \cmark \\
+atribuição & a*tri*bu-i*ção \xmark & a*tri*bu*i*ção \cmark \\
+atribuir & a*tri*bu-ir \xmark & a*tri*bu*ir \cmark \\
+atribuível & a*tri*bu-í*vel \xmark & a*tri*bu*í*vel \cmark \\
+auréola & au*ré-o*la \xmark & au*ré*o*la \cmark \\
+austríaco & aus*trí-a*co \xmark & aus*trí*a*co \cmark \\
+autônimo & au-tô*ni*mo \xmark & au*tô*ni*mo \cmark \\
+autônomo & au-tô*no*mo \xmark & au*tô*no*mo \cmark \\
+avião & a*vi-ão \xmark & a*vi*ão \cmark \\
+avô & a-vô \xmark & a*vô \cmark \\
+babuíno & ba*bu-í*no \xmark & ba*bu*í*no \cmark \\
+bacteriófago & bac*te*ri-ó*fa*go \xmark & bac*te*ri*ó*fa*go \cmark \\
+bafômetro & ba-fô*me*tro \xmark & ba*fô*me*tro \cmark \\
+bahamense & ba-ha*men*se \xmark & ba-ha*men*se \xmark \\
+baião & bai-ão \xmark & bai*ão \cmark \\
+bainha & ba-i*nha \xmark & ba*i*nha \cmark \\
+baiuca & bai-u*ca \xmark & bai*u*ca \cmark \\
+balaustrada & ba*la-us*tra*da \xmark & ba*la-us*tra*da \xmark \\
+balaústre & ba*la-ús*tre \xmark & ba*la*ús*tre \cmark \\
+bangalô & ban*ga-lô \xmark & ban*ga*lô \cmark \\
+bastião & bas*ti-ão \xmark & bas*ti*ão \cmark \\
+batuíra & ba*tu-í*ra \xmark & ba*tu*í*ra \cmark \\
+benjoim & ben*jo-im \xmark & ben*jo*im \cmark \\
+bibelô & bi*be-lô \xmark & bi*be*lô \cmark \\
+bibliófilo & bi*bli-ó*fi*lo \xmark & bi*bli*ó*fi*lo \cmark \\
+bicampeão & bi*cam*pe-ão \xmark & bi*cam*pe*ão \cmark \\
+bioética & bi*o-é*ti*ca \xmark & bi*o*é*ti*ca \cmark \\
+biófilo & bi-ó*fi*lo \xmark & bi*ó*fi*lo \cmark \\
+biógrafo & bi-ó*gra*fo \xmark & bi*ó*gra*fo \cmark \\
+biólogo & bi-ó*lo*go \xmark & bi*ó*lo*go \cmark \\
+bioquímica & bi*o-quí*mi*ca \xmark & bi*o*quí*mi*ca \cmark \\
+biótico & bi-ó*ti*co \xmark & bi*ó*ti*co \cmark \\
+biótipo & bi-ó*ti*po \xmark & bi*ó*ti*po \cmark \\
+biquíni & bi-quí*ni \xmark & bi*quí*ni \cmark \\
+birô & bi-rô \xmark & bi*rô \cmark \\
+bisavô & bi*sa-vô \xmark & bi*sa*vô \cmark \\
+biscainho & bis*ca-i*nho \xmark & bis*ca*i*nho \cmark \\
+bocaiuva & bo*cai-u*va \xmark & bo*cai*u*va \cmark \\
+boião & boi-ão \xmark & boi*ão \cmark \\
+boiuna & boi-u*na \xmark & boi*u*na \cmark \\
+bongô & bon-gô \xmark & bon*gô \cmark \\
+bordô & bor-dô \xmark & bor*dô \cmark \\
+brechtiano & bre.ch*ti*a*no \xmark & bre.ch*ti*a*no \xmark \\
+bronquíolo & bron-quí-o*lo \xmark & bron*quí*o*lo \cmark \\
+buir & bu-ir \xmark & bu*ir \cmark \\
+buquê & bu-quê \xmark & bu*quê \cmark \\
+cafarnaum & ca*far*na-um \xmark & ca*far*na-um \xmark \\
+cafeína & ca*fe-í*na \xmark & ca*fe*í*na \cmark \\
+caíco & ca-í*co \xmark & ca*í*co \cmark \\
+caída & ca-í*da \xmark & ca*í*da \cmark \\
+caído & ca-í*do \xmark & ca*í*do \cmark \\
+caim & ca-im \xmark & ca-im \xmark \\
+caíque & ca-í*que \xmark & ca*í*que \cmark \\
+cair & ca-ir \xmark & ca*ir \cmark \\
+cajuína & ca*ju-í*na \xmark & ca*ju*í*na \cmark \\
+camaleão & ca*ma*le-ão \xmark & ca*ma*le*ão \cmark \\
+camelô & ca*me-lô \xmark & ca*me*lô \cmark \\
+camião & ca*mi-ão \xmark & ca*mi*ão \cmark \\
+campainha & cam*pa-i*nha \xmark & cam*pa*i*nha \cmark \\
+campeão & cam*pe-ão \xmark & cam*pe*ão \cmark \\
+candidíase & can*di*dí-a*se \xmark & can*di*dí*a*se \cmark \\
+canoísta & ca*no-ís*ta \xmark & ca*no*ís*ta \cmark \\
+caótico & ca-ó*ti*co \xmark & ca*ó*ti*co \cmark \\
+capô & ca-pô \xmark & ca*pô \cmark \\
+caraíba & ca*ra-í*ba \xmark & ca*ra*í*ba \cmark \\
+carbônico & car-bô*ni*co \xmark & car*bô*ni*co \cmark \\
+cardíaco & car*dí-a*co \xmark & car*dí*a*co \cmark \\
+cariótipo & ca*ri-ó*ti*po \xmark & ca*ri*ó*ti*po \cmark \\
+carnaúba & car*na-ú*ba \xmark & car*na*ú*ba \cmark \\
+caseína & ca*se-í*na \xmark & ca*se*í*na \cmark \\
+casuísmo & ca*su-ís*mo \xmark & ca*su*ís*mo \cmark \\
+casuísta & ca*su-ís*ta \xmark & ca*su*ís*ta \cmark \\
+casuística & ca*su-ís*ti*ca \xmark & ca*su*ís*ti*ca \cmark \\
+casuístico & ca*su-ís*ti*co \xmark & ca*su*ís*ti*co \cmark \\
+catequético & ca*te-qué*ti*co \xmark & ca*te*qué*ti*co \cmark \\
+catião & ca*ti-ão \xmark & ca*ti*ão \cmark \\
+cauim & cau-im \xmark & cau*im \cmark \\
+caúna & ca-ú*na \xmark & ca*ú*na \cmark \\
+centurião & cen*tu*ri-ão \xmark & cen*tu*ri*ão \cmark \\
+chatô & cha-tô \xmark & cha*tô \cmark \\
+ciático & ci-á*ti*co \xmark & ci*á*ti*co \cmark \\
+cirurgião & ci*rur*gi-ão \xmark & ci*rur*gi*ão \cmark \\
+ciúme & ci-ú*me \xmark & ci*ú*me \cmark \\
+coágulo & co-á*gu*lo \xmark & co*á*gu*lo \cmark \\
+cocaína & co*ca-í*na \xmark & co*ca*í*na \cmark \\
+cocô & co-cô \xmark & co*cô \cmark \\
+codeína & co*de-í*na \xmark & co*de*í*na \cmark \\
+coibir & co-i*bir \xmark & co-i*bir \xmark \\
+coincidente & co-in*ci*den*te \xmark & co*in*ci*den*te \cmark \\
+coincidir & co-in*ci*dir \xmark & co*in*ci*dir \cmark \\
+coleóptero & co*le-óp*te*ro \xmark & co*le*óp*te*ro \cmark \\
+comediógrafo & co*me*di-ó*gra*fo \xmark & co*me*di*ó*gra*fo \cmark \\
+conciliábulo & con*ci*li-á*bu*lo \xmark & con*ci*li*á*bu*lo \cmark \\
+conciliável & con*ci*li-á*vel \xmark & con*ci*li*á*vel \cmark \\
+concluído & con*clu-í*do \xmark & con*clu*í*do \cmark \\
+concluinte & con*clu-in*te \xmark & con*clu*in*te \cmark \\
+concluir & con*clu-ir \xmark & con*clu*ir \cmark \\
+condoído & con*do-í*do \xmark & con*do*í*do \cmark \\
+confiável & con*fi-á*vel \xmark & con*fi*á*vel \cmark \\
+confluir & con*flu-ir \xmark & con*flu*ir \cmark \\
+constituição & cons*ti*tu-i*ção \xmark & cons*ti*tu*i*ção \cmark \\
+constituído & cons*ti*tu-í*do \xmark & cons*ti*tu*í*do \cmark \\
+constituinte & cons*ti*tu-in*te \xmark & cons*ti*tu*in*te \cmark \\
+constituir & cons*ti*tu-ir \xmark & cons*ti*tu*ir \cmark \\
+construído & cons*tru-í*do \xmark & cons*tru*í*do \cmark \\
+construir & cons*tru-ir \xmark & cons*tru*ir \cmark \\
+conteúdo & con*te-ú*do \xmark & con*te*ú*do \cmark \\
+contraído & con*tra-í*do \xmark & con*tra*í*do \cmark \\
+contrair & con*tra-ir \xmark & con*tra*ir \cmark \\
+contribuição & con*tri*bu-i*ção \xmark & con*tri*bu*i*ção \cmark \\
+contribuidor & con*tri*bu-i*dor \xmark & con*tri*bu*i*dor \cmark \\
+contribuinte & con*tri*bu-in*te \xmark & con*tri*bu*in*te \cmark \\
+contribuir & con*tri*bu-ir \xmark & con*tri*bu*ir \cmark \\
+copaíba & co*pa-í*ba \xmark & co*pa*í*ba \cmark \\
+coreógrafo & co*re-ó*gra*fo \xmark & co*re*ó*gra*fo \cmark \\
+coroinha & co*ro-i*nha \xmark & co*ro*i*nha \cmark \\
+corroído & cor*ro-í*do \xmark & cor*ro*í*do \cmark \\
+criciúma & cri*ci-ú*ma \xmark & cri*ci*ú*ma \cmark \\
+criptônimo & crip-tô*ni*mo \xmark & crip*tô*ni*mo \cmark \\
+cronômetro & cro-nô*me*tro \xmark & cro*nô*me*tro \cmark \\
+cuíca & cu-í*ca \xmark & cu*í*ca \cmark \\
+curião & cu*ri-ão \xmark & cu*ri*ão \cmark \\
+czarina & c.za*ri*na \xmark & cza*ri*na \cmark \\
+czarismo & c.za*ris*mo \xmark & cza*ris*mo \cmark \\
+czarista & c.za*ris*ta \xmark & cza*ris*ta \cmark \\
+dadaísmo & da*da-ís*mo \xmark & da*da*ís*mo \cmark \\
+dadaísta & da*da-ís*ta \xmark & da*da*ís*ta \cmark \\
+daguerreótipo & da*guer*re-ó*ti*po \xmark & da*guer*re*ó*ti*po \cmark \\
+daltônico & dal-tô*ni*co \xmark & dal*tô*ni*co \cmark \\
+darwinismo & dar-wi*nis*mo \xmark & dar-wi*nis*mo \xmark \\
+darwinista & dar-wi*nis*ta \xmark & dar-wi*nis*ta \xmark \\
+deão & de-ão \xmark & de*ão \cmark \\
+decacampeão & de*ca*cam*pe-ão \xmark & de*ca*cam*pe*ão \cmark \\
+decaída & de*ca-í*da \xmark & de*ca*í*da \cmark \\
+decaído & de*ca-í*do \xmark & de*ca*í*do \cmark \\
+decair & de*ca-ir \xmark & de*ca*ir \cmark \\
+decurião & de*cu*ri-ão \xmark & de*cu*ri*ão \cmark \\
+deísmo & de-ís*mo \xmark & de*ís*mo \cmark \\
+deísta & de-ís*ta \xmark & de*ís*ta \cmark \\
+demiurgo & de*mi-ur*go \xmark & de*mi*ur*go \cmark \\
+demoníaco & de*mo*ní-a*co \xmark & de*mo*ní*a*co \cmark \\
+depoimento & de*po-i*men*to \xmark & de*po*i*men*to \cmark \\
+descaída & des*ca-í*da \xmark & des*ca*í*da \cmark \\
+descair & des*ca-ir \xmark & des*ca*ir \cmark \\
+desconstruir & des*cons*tru-ir \xmark & des*cons*tru*ir \cmark \\
+descontraído & des*con*tra-í*do \xmark & des*con*tra*í*do \cmark \\
+descontrair & des*con*tra-ir \xmark & des*con*tra*ir \cmark \\
+desembainhar & de*sem*ba-i*nhar \xmark & de*sem*ba*i*nhar \cmark \\
+desobstruir & de*sobs*tru-ir \xmark & de*sobs*tru*ir \cmark \\
+despoluição & des*po*lu-i*ção \xmark & des*po*lu*i*ção \cmark \\
+despoluir & des*po*lu-ir \xmark & des*po*lu*ir \cmark \\
+destituição & des*ti*tu-i*ção \xmark & des*ti*tu*i*ção \cmark \\
+destituído & des*ti*tu-í*do \xmark & des*ti*tu*í*do \cmark \\
+destituir & des*ti*tu-ir \xmark & des*ti*tu*ir \cmark \\
+destruição & des*tru-i*ção \xmark & des*tru*i*ção \cmark \\
+destruído & des*tru-í*do \xmark & des*tru*í*do \cmark \\
+destruir & des*tru-ir \xmark & des*tru*ir \cmark \\
+diácono & di-á*co*no \xmark & di*á*co*no \cmark \\
+díade & dí-a*de \xmark & dí*a*de \cmark \\
+diáfano & di-á*fa*no \xmark & di*á*fa*no \cmark \\
+diálise & di-á*li*se \xmark & di*á*li*se \cmark \\
+diálogo & di-á*lo*go \xmark & di*á*lo*go \cmark \\
+diáspora & di-ás*po*ra \xmark & di*ás*po*ra \cmark \\
+diástole & di-ás*to*le \xmark & di*ás*to*le \cmark \\
+dicroísmo & di*cro-ís*mo \xmark & di*cro*ís*mo \cmark \\
+diérese & di-é*re*se \xmark & di*é*re*se \cmark \\
+diferenciável & di*fe*ren*ci-á*vel \xmark & di*fe*ren*ci*á*vel \cmark \\
+diluído & di*lu-í*do \xmark & di*lu*í*do \cmark \\
+diluir & di*lu-ir \xmark & di*lu*ir \cmark \\
+diminuição & di*mi*nu-i*ção \xmark & di*mi*nu*i*ção \cmark \\
+diminuído & di*mi*nu-í*do \xmark & di*mi*nu*í*do \cmark \\
+diminuir & di*mi*nu-ir \xmark & di*mi*nu*ir \cmark \\
+dinamarquês & di*na*mar-quês \xmark & di*na*mar*quês \cmark \\
+dionisíaco & di*o*ni*sí-a*co \xmark & di*o*ni*sí*a*co \cmark \\
+dióxido & di-ó*xi*do \xmark & di*ó*xi*do \cmark \\
+distraído & dis*tra-í*do \xmark & dis*tra*í*do \cmark \\
+distrair & dis*tra-ir \xmark & dis*tra*ir \cmark \\
+distribuição & dis*tri*bu-i*ção \xmark & dis*tri*bu*i*ção \cmark \\
+distribuído & dis*tri*bu-í*do \xmark & dis*tri*bu*í*do \cmark \\
+distribuidora & dis*tri*bu-i*do*ra \xmark & dis*tri*bu*i*do*ra \cmark \\
+distribuidor & dis*tri*bu-i*dor \xmark & dis*tri*bu*i*dor \cmark \\
+distribuir & dis*tri*bu-ir \xmark & dis*tri*bu*ir \cmark \\
+diurno & di-ur*no \xmark & di*ur*no \cmark \\
+dodecafônico & do*de*ca-fô*ni*co \xmark & do*de*ca*fô*ni*co \cmark \\
+doído & do-í*do \xmark & do*í*do \cmark \\
+dríade & drí-a*de \xmark & drí*a*de \cmark \\
+dzeta & d.ze*ta \xmark & d.ze*ta \xmark \\
+eclesiástico & e*cle*si-ás*ti*co \xmark & e*cle*si*ás*ti*co \cmark \\
+econômico & e*co-nô*mi*co \xmark & e*co*nô*mi*co \cmark \\
+ecônomo & e-cô*no*mo \xmark & e*cô*no*mo \cmark \\
+egoísmo & e*go-ís*mo \xmark & e*go*ís*mo \cmark \\
+egoísta & e*go-ís*ta \xmark & e*go*ís*ta \cmark \\
+egoístico & e*go-ís*ti*co \xmark & e*go*ís*ti*co \cmark \\
+elastômero & e*las-tô*me*ro \xmark & e*las*tô*me*ro \cmark \\
+elefantíase & e*le*fan*tí-a*se \xmark & e*le*fan*tí*a*se \cmark \\
+eletrocardiógrafo & e*le*tro*car*di-ó*gra*fo \xmark & e*le*tro*car*di*ó*gra*fo \cmark \\
+eletroímã & e*le*tro-í*mã \xmark & e*le*tro*í*mã \cmark \\
+eletroquímica & e*le*tro-quí*mi*ca \xmark & e*le*tro*quí*mi*ca \cmark \\
+elogiável & e*lo*gi-á*vel \xmark & e*lo*gi*á*vel \cmark \\
+eluição & e*lu-i*ção \xmark & e*lu*i*ção \cmark \\
+embainhar & em*ba-i*nhar \xmark & em*ba*i*nhar \cmark \\
+embrião & em*bri-ão \xmark & em*bri*ão \cmark \\
+ensaísmo & en*sa-ís*mo \xmark & en*sa*ís*mo \cmark \\
+ensaísta & en*sa-ís*ta \xmark & en*sa*ís*ta \cmark \\
+entusiástico & en*tu*si-ás*ti*co \xmark & en*tu*si*ás*ti*co \cmark \\
+eólico & e-ó*li*co \xmark & e*ó*li*co \cmark \\
+éon & é-on \xmark & é*on \cmark \\
+equânime & e-quâ*ni*me \xmark & e*quâ*ni*me \cmark \\
+equívoco & e-quí*vo*co \xmark & e*quí*vo*co \cmark \\
+ergonômico & er*go-nô*mi*co \xmark & er*go*nô*mi*co \cmark \\
+escorpião & es*cor*pi-ão \xmark & es*cor*pi*ão \cmark \\
+esfigmomanômetro & es*fig*mo*ma-nô*me*tro \xmark & es*fig*mo*ma*nô*me*tro \cmark \\
+espião & es*pi-ão \xmark & es*pi*ão \cmark \\
+esponsais & es*pon*sa-is \xmark & es*pon*sa-is \xmark \\
+esquálido & es-quá*li*do \xmark & es*quá*li*do \cmark \\
+esteárico & es*te-á*ri*co \xmark & es*te*á*ri*co \cmark \\
+estereótipo & es*te*re-ó*ti*po \xmark & es*te*re*ó*ti*po \cmark \\
+estômago & es-tô*ma*go \xmark & es*tô*ma*go \cmark \\
+esvair & es*va-ir \xmark & es*va*ir \cmark \\
+etíope & e*tí-o*pe \xmark & e*tí*o*pe \cmark \\
+etnônimo & et-nô*ni*mo \xmark & et*nô*ni*mo \cmark \\
+eucariótico & eu*ca*ri-ó*ti*co \xmark & eu*ca*ri*ó*ti*co \cmark \\
+eurasiático & eu*ra*si-á*ti*co \xmark & eu*ra*si*á*ti*co \cmark \\
+evoluído & e*vo*lu-í*do \xmark & e*vo*lu*í*do \cmark \\
+evoluir & e*vo*lu-ir \xmark & e*vo*lu*ir \cmark \\
+excluído & ex*clu-í*do \xmark & ex*clu*í*do \cmark \\
 excluir & ex*clu-ir \xmark & ex*clu*ir \cmark \\
+exéquias & e*xé*qui.as \xmark & e*xé*qui.as \xmark \\
+exequível & e*xe-quí*vel \xmark & e*xe*quí*vel \cmark \\
+extrair & ex*tra-ir \xmark & ex*tra*ir \cmark \\
+faim & fa-im \xmark & fa-im \xmark \\
+faísca & fa-ís*ca \xmark & fa*ís*ca \cmark \\
+farisaísmo & fa*ri*sa-ís*mo \xmark & fa*ri*sa*ís*mo \cmark \\
+faúlha & fa-ú*lha \xmark & fa*ú*lha \cmark \\
+feérico & fe-é*ri*co \xmark & fe*é*ri*co \cmark \\
+feiura & fei-u*ra \xmark & fei*u*ra \cmark \\
+fenômeno & fe-nô*me*no \xmark & fe*nô*me*no \cmark \\
+fiável & fi-á*vel \xmark & fi*á*vel \cmark \\
+fideísmo & fi*de-ís*mo \xmark & fi*de*ís*mo \cmark \\
 filarmônica & fi*lar-mô*ni*ca \xmark & fi*lar*mô*ni*ca \cmark \\
+filarmônico & fi*lar-mô*ni*co \xmark & fi*lar*mô*ni*co \cmark \\
+financiável & fi*nan*ci-á*vel \xmark & fi*nan*ci*á*vel \cmark \\
+fisiólogo & fi*si-ó*lo*go \xmark & fi*si*ó*lo*go \cmark \\
+fiúza & fi-ú*za \xmark & fi*ú*za \cmark \\
+fluidez & flu-i*dez \xmark & flu-i*dez \xmark \\
+fluídico & flu-í*di*co \xmark & flu*í*di*co \cmark \\
+fluir & flu-ir \xmark & flu*ir \cmark \\
+flúor & flú-or \xmark & flú*or \cmark \\
+folião & fo*li-ão \xmark & fo*li*ão \cmark \\
+formaldeído & for*mal*de-í*do \xmark & for*mal*de*í*do \cmark \\
+fotoquímica & fo*to-quí*mi*ca \xmark & fo*to*quí*mi*ca \cmark \\
+fotoquímico & fo*to-quí*mi*co \xmark & fo*to*quí*mi*co \cmark \\
+freático & fre-á*ti*co \xmark & fre*á*ti*co \cmark \\
+friável & fri-á*vel \xmark & fri*á*vel \cmark \\
+fruição & fru-i*ção \xmark & fru*i*ção \cmark \\
+fruir & fru-ir \xmark & fru*ir \cmark \\
+fuinha & fu-i*nha \xmark & fu*i*nha \cmark \\
+futevôlei & fu*te-vô*lei \xmark & fu*te*vô*lei \cmark \\
+gabião & ga*bi-ão \xmark & ga*bi*ão \cmark \\
+gaélico & ga-é*li*co \xmark & ga*é*li*co \cmark \\
+galeão & ga*le-ão \xmark & ga*le*ão \cmark \\
+gastrointestinal & gas*tro-in*tes*ti*nal \xmark & gas*tro*in*tes*ti*nal \cmark \\
+gastronômico & gas*tro-nô*mi*co \xmark & gas*tro*nô*mi*co \cmark \\
+gaúcho & ga-ú*cho \xmark & ga*ú*cho \cmark \\
+gavião & ga*vi-ão \xmark & ga*vi*ão \cmark \\
+genuíno & ge*nu-í*no \xmark & ge*nu*í*no \cmark \\
+geógrafo & ge-ó*gra*fo \xmark & ge*ó*gra*fo \cmark \\
+geólogo & ge-ó*lo*go \xmark & ge*ó*lo*go \cmark \\
+gigolô & gi*go-lô \xmark & gi*go*lô \cmark \\
+gladíolo & gla*dí-o*lo \xmark & gla*dí*o*lo \cmark \\
+glicoproteína & gli*co*pro*te-í*na \xmark & gli*co*pro*te*í*na \cmark \\
+gnaisse & g.nais*se \xmark & g.nais*se \xmark \\
+gnomo & g.no*mo \xmark & gno*mo \cmark \\
+gnose & g.no*se \xmark & gno*se \cmark \\
+gnosticismo & g.nos*ti*cis*mo \xmark & gnos*ti*cis*mo \cmark \\
+gnóstico & g.nós*ti*co \xmark & gnós*ti*co \cmark \\
+grafomaníaco & gra*fo*ma*ní-a*co \xmark & gra*fo*ma*ní*a*co \cmark \\
+grapiúna & gra*pi-ú*na \xmark & gra*pi*ú*na \cmark \\
+graúdo & gra-ú*do \xmark & gra*ú*do \cmark \\
+graúna & gra-ú*na \xmark & gra*ú*na \cmark \\
+guardião & guar*di-ão \xmark & guar*di*ão \cmark \\
+guião & gui-ão \xmark & gui*ão \cmark \\
+hagiógrafo & ha*gi-ó*gra*fo \xmark & ha*gi*ó*gra*fo \cmark \\
+hanseático & han*se-á*ti*co \xmark & han*se*á*ti*co \cmark \\
+hanseníase & han*se*ní-a*se \xmark & han*se*ní*a*se \cmark \\
+harmônica & har-mô*ni*ca \xmark & har*mô*ni*ca \cmark \\
+harmônico & har-mô*ni*co \xmark & har*mô*ni*co \cmark \\
+hebraísmo & he*bra-ís*mo \xmark & he*bra*ís*mo \cmark \\
+hebraísta & he*bra-ís*ta \xmark & he*bra*ís*ta \cmark \\
+hegemônico & he*ge-mô*ni*co \xmark & he*ge*mô*ni*co \cmark \\
+helíaco & he*lí-a*co \xmark & he*lí*a*co \cmark \\
+heliógrafo & he*li-ó*gra*fo \xmark & he*li*ó*gra*fo \cmark \\
+hemodiálise & he*mo*di-á*li*se \xmark & he*mo*di*á*li*se \cmark \\
+heptacampeão & hep*ta*cam*pe-ão \xmark & hep*ta*cam*pe*ão \cmark \\
+heroína & he*ro-í*na \xmark & he*ro*í*na \cmark \\
+heroísmo & he*ro-ís*mo \xmark & he*ro*ís*mo \cmark \\
+heteroátomo & he*te*ro-á*to*mo \xmark & he*te*ro*á*to*mo \cmark \\
+heterônimo & he*te-rô*ni*mo \xmark & he*te*rô*ni*mo \cmark \\
+hexacampeão & he*xa*cam*pe-ão \xmark & he*xa*cam*pe*ão \cmark \\
+hidroavião & hi*dro*a*vi-ão \xmark & hi*dro*a*vi*ão \cmark \\
+hidropônico & hi*dro-pô*ni*co \xmark & hi*dro*pô*ni*co \cmark \\
+hinduísmo & hin*du-ís*mo \xmark & hin*du*ís*mo \cmark \\
+hipocondríaco & hi*po*con*drí-a*co \xmark & hi*po*con*drí*a*co \cmark \\
+hipônimo & hi-pô*ni*mo \xmark & hi*pô*ni*mo \cmark \\
+histoquímica & his*to-quí*mi*ca \xmark & his*to*quí*mi*ca \cmark \\
+homônimo & ho-mô*ni*mo \xmark & ho*mô*ni*mo \cmark \\
+ictiólogo & ic*ti-ó*lo*go \xmark & ic*ti*ó*lo*go \cmark \\
+ideólogo & i*de-ó*lo*go \xmark & i*de*ó*lo*go \cmark \\
+iídiche & i-í*di*che \xmark & i*í*di*che \cmark \\
+ilíaco & i*lí-a*co \xmark & i*lí*a*co \cmark \\
+ilíada & i*lí-a*da \xmark & i*lí*a*da \cmark \\
+imbuído & im*bu-í*do \xmark & im*bu*í*do \cmark \\
+imbuir & im*bu-ir \xmark & im*bu*ir \cmark \\
+imperdoável & im*per*do-á*vel \xmark & im*per*do*á*vel \cmark \\
+impronunciável & im*pro*nun*ci-á*vel \xmark & im*pro*nun*ci*á*vel \cmark \\
+inadiável & i*na*di-á*vel \xmark & i*na*di*á*vel \cmark \\
+incluir & in*clu-ir \xmark & in*clu*ir \cmark \\
+incômodo & in-cô*mo*do \xmark & in*cô*mo*do \cmark \\
+inconciliável & in*con*ci*li-á*vel \xmark & in*con*ci*li*á*vel \cmark \\
+indeiscente & in*de-is*cen*te \xmark & in*de-is*cen*te \xmark \\
+inegociável & i*ne*go*ci-á*vel \xmark & i*ne*go*ci*á*vel \cmark \\
+inequívoco & i*ne-quí*vo*co \xmark & i*ne*quí*vo*co \cmark \\
+inexequível & i*ne*xe-quí*vel \xmark & i*ne*xe*quí*vel \cmark \\
+influenciável & in*flu*en*ci-á*vel \xmark & in*flu*en*ci*á*vel \cmark \\
+influído & in*flu-í*do \xmark & in*flu*í*do \cmark \\
+influir & in*flu-ir \xmark & in*flu*ir \cmark \\
+ingenuidade & in*ge*nu-i*da*de \xmark & in*ge*nu*i*da*de \cmark \\
+iniciático & i*ni*ci-á*ti*co \xmark & i*ni*ci*á*ti*co \cmark \\
+insaciável & in*sa*ci-á*vel \xmark & in*sa*ci*á*vel \cmark \\
+instituído & ins*ti*tu-í*do \xmark & ins*ti*tu*í*do \cmark \\
+instituir & ins*ti*tu-ir \xmark & ins*ti*tu*ir \cmark \\
+instruído & ins*tru-í*do \xmark & ins*tru*í*do \cmark \\
+instruir & ins*tru-ir \xmark & ins*tru*ir \cmark \\
+insubstituível & in*subs*ti*tu-í*vel \xmark & in*subs*ti*tu*í*vel \cmark \\
+intercambiável & in*ter*cam*bi-á*vel \xmark & in*ter*cam*bi*á*vel \cmark \\
+interoceânico & in*te*ro*ce-â*ni*co \xmark & in*te*ro*ce*â*ni*co \cmark \\
+intuição & in*tu-i*ção \xmark & in*tu*i*ção \cmark \\
+intuir & in*tu-ir \xmark & in*tu*ir \cmark \\
+intuitivo & in*tu-i*ti*vo \xmark & in*tu-i*ti*vo \xmark \\
+invariável & in*va*ri-á*vel \xmark & in*va*ri*á*vel \cmark \\
+inviável & in*vi-á*vel \xmark & in*vi*á*vel \cmark \\
+iódico & i-ó*di*co \xmark & i*ó*di*co \cmark \\
+irônico & i-rô*ni*co \xmark & i*rô*ni*co \cmark \\
+iroquês & i*ro-quês \xmark & i*ro*quês \cmark \\
+irreconciliável & ir*re*con*ci*li-á*vel \xmark & ir*re*con*ci*li*á*vel \cmark \\
+irrefreável & ir*re*fre-á*vel \xmark & ir*re*fre*á*vel \cmark \\
+irremediável & ir*re*me*di-á*vel \xmark & ir*re*me*di*á*vel \cmark \\
+irrenunciável & ir*re*nun*ci-á*vel \xmark & ir*re*nun*ci*á*vel \cmark \\
+irretorquível & ir*re*tor-quí*vel \xmark & ir*re*tor*quí*vel \cmark \\
+isotônico & i*so-tô*ni*co \xmark & i*so*tô*ni*co \cmark \\
+jabô & ja-bô \xmark & ja*bô \cmark \\
+jesuíta & je*su-í*ta \xmark & je*su*í*ta \cmark \\
+jesuítico & je*su-í*ti*co \xmark & je*su*í*ti*co \cmark \\
+jesuitismo & je*su-i*tis*mo \xmark & je*su*i*tis*mo \cmark \\
+joinvilense & jo-in*vi*len*se \xmark & jo*in*vi*len*se \cmark \\
+judaísmo & ju*da-ís*mo \xmark & ju*da*ís*mo \cmark \\
+judô & ju-dô \xmark & ju*dô \cmark \\
 juizado & ju-i*za*do \xmark & ju*i*za*do \cmark \\
+juíza & ju-í*za \xmark & ju*í*za \cmark \\
+juiz & ju-iz \xmark & ju*iz \cmark \\
+juízo & ju-í*zo \xmark & ju*í*zo \cmark \\
+kuwaitiano & ku-wai*ti*a*no \xmark & ku-wai*ti*a*no \xmark \\
+lacônico & la-cô*ni*co \xmark & la*cô*ni*co \cmark \\
+ladainha & la*da-i*nha \xmark & la*da*i*nha \cmark \\
+lamaísmo & la*ma-ís*mo \xmark & la*ma*ís*mo \cmark \\
+lampião & lam*pi-ão \xmark & lam*pi*ão \cmark \\
+laquê & la-quê \xmark & la*quê \cmark \\
+leão & le-ão \xmark & le*ão \cmark \\
+legião & le*gi-ão \xmark & le*gi*ão \cmark \\
+litíase & li*tí-a*se \xmark & li*tí*a*se \cmark \\
+luís & lu-ís \xmark & lu*ís \cmark \\
+lusíada & lu*sí-a*da \xmark & lu*sí*a*da \cmark \\
+luteína & lu*te-í*na \xmark & lu*te*í*na \cmark \\
+macaúba & ma*ca-ú*ba \xmark & ma*ca*ú*ba \cmark \\
+maçônico & ma-çô*ni*co \xmark & ma*çô*ni*co \cmark \\
+macrobiótica & ma*cro*bi-ó*ti*ca \xmark & ma*cro*bi*ó*ti*ca \cmark \\
+macrobiótico & ma*cro*bi-ó*ti*co \xmark & ma*cro*bi*ó*ti*co \cmark \\
+macroeconômico & ma*cro*e*co-nô*mi*co \xmark & ma*cro*e*co*nô*mi*co \cmark \\
+macrorregião & ma*cror*re*gi-ão \xmark & ma*cror*re*gi*ão \cmark \\
+maiólica & mai-ó*li*ca \xmark & mai*ó*li*ca \cmark \\
+maís & ma-ís \xmark & ma*ís \cmark \\
+maiúscula & mai-ús*cu*la \xmark & mai*ús*cu*la \cmark \\
+maiúsculo & mai-ús*cu*lo \xmark & mai*ús*cu*lo \cmark \\
+malauiano & ma*lau-i*a*no \xmark & ma*lau*i*a*no \cmark \\
+maleável & ma*le-á*vel \xmark & ma*le*á*vel \cmark \\
+malthusianismo & mal-thu*si*a*nis*mo \xmark & mal-thu*si*a*nis*mo \xmark \\
+malthusiano & mal-thu*si*a*no \xmark & mal-thu*si*a*no \xmark \\
+mandrião & man*dri-ão \xmark & man*dri*ão \cmark \\
+maníaco & ma*ní-a*co \xmark & ma*ní*a*co \cmark \\
+maniqueísmo & ma*ni*que-ís*mo \xmark & ma*ni*que*ís*mo \cmark \\
+maniqueísta & ma*ni*que-ís*ta \xmark & ma*ni*que*ís*ta \cmark \\
+manômetro & ma-nô*me*tro \xmark & ma*nô*me*tro \cmark \\
+mantô & man-tô \xmark & man*tô \cmark \\
+marquês & mar-quês \xmark & mar*quês \cmark \\
+maruim & ma*ru-im \xmark & ma*ru-im \xmark \\
+masdeísmo & mas*de-ís*mo \xmark & mas*de*ís*mo \cmark \\
+meão & me-ão \xmark & me*ão \cmark \\
+mediático & me*di-á*ti*co \xmark & me*di*á*ti*co \cmark \\
+medíocre & me*dí-o*cre \xmark & me*dí*o*cre \cmark \\
+megalomaníaco & me*ga*lo*ma*ní-a*co \xmark & me*ga*lo*ma*ní*a*co \cmark \\
+megawatt & me*ga-watt \xmark & me*ga-watt \xmark \\
+meteórico & me*te-ó*ri*co \xmark & me*te*ó*ri*co \cmark \\
+microbiólogo & mi*cro*bi-ó*lo*go \xmark & mi*cro*bi*ó*lo*go \cmark \\
+micuim & mi*cu-im \xmark & mi*cu-im \xmark \\
+midríase & mi*drí-a*se \xmark & mi*drí*a*se \cmark \\
+mimeógrafo & mi*me-ó*gra*fo \xmark & mi*me*ó*gra*fo \cmark \\
+míope & mí-o*pe \xmark & mí*o*pe \cmark \\
+miríade & mi*rí-a*de \xmark & mi*rí*a*de \cmark \\
+miúdo & mi-ú*do \xmark & mi*ú*do \cmark \\
+mnemônica & m.ne-mô*ni*ca \xmark & mne*mô*ni*ca \cmark \\
+mnemônico & m.ne-mô*ni*co \xmark & mne*mô*ni*co \cmark \\
+moído & mo-í*do \xmark & mo*í*do \cmark \\
+moinha & mo-i*nha \xmark & mo*i*nha \cmark \\
+moinho & mo-i*nho \xmark & mo*i*nho \cmark \\
+monomaníaco & mo*no*ma*ní-a*co \xmark & mo*no*ma*ní*a*co \cmark \\
+monômero & mo-nô*me*ro \xmark & mo*nô*me*ro \cmark \\
+monoteísmo & mo*no*te-ís*mo \xmark & mo*no*te*ís*mo \cmark \\
+monoteísta & mo*no*te-ís*ta \xmark & mo*no*te*ís*ta \cmark \\
+moquém & mo-quém \xmark & mo*quém \cmark \\
+morrião & mor*ri-ão \xmark & mor*ri*ão \cmark \\
+mucuim & mu*cu-im \xmark & mu*cu-im \xmark \\
+museólogo & mu*se-ó*lo*go \xmark & mu*se*ó*lo*go \cmark \\
+napoleão & na*po*le-ão \xmark & na*po*le*ão \cmark \\
+neerlandês & ne*er*lan*dês \cmark & ne*er*lan*dês \cmark \\
+neocolonialismo & ne*o*co*lo*ni*a*lis*mo \cmark & ne-o*co*lo*ni*a*lis*mo \xmark \\
+neofascista & ne*o*fas*cis*ta \cmark & ne-o*fas*cis*ta \xmark \\
+neófito & ne-ó*fi*to \xmark & ne*ó*fi*to \cmark \\
+neolatino & ne*o*la*ti*no \cmark & ne-o*la*ti*no \xmark \\
+neoliberalismo & ne*o*li*be*ra*lis*mo \cmark & ne-o*li*be*ra*lis*mo \xmark \\
+neoliberal & ne*o*li*be*ral \cmark & ne-o*li*be*ral \xmark \\
+neolítico & ne*o*lí*ti*co \cmark & ne-o*lí*ti*co \xmark \\
+neologismo & ne*o*lo*gis*mo \cmark & ne-o*lo*gis*mo \xmark \\
+neonato & ne*o*na*to \cmark & ne-o*na*to \xmark \\
+neonazismo & ne*o*na*zis*mo \cmark & ne-o*na*zis*mo \xmark \\
+neonazista & ne*o*na*zis*ta \cmark & ne-o*na*zis*ta \xmark \\
+neon & ne*on \cmark & ne-on \xmark \\
+néon & né-on \xmark & né*on \cmark \\
+neoplatonismo & ne*o*pla*to*nis*mo \cmark & ne-o*pla*to*nis*mo \xmark \\
+neozelandês & ne*o*ze*lan*dês \cmark & ne-o*ze*lan*dês \xmark \\
+neurocirurgião & neu*ro*ci*rur*gi-ão \xmark & neu*ro*ci*rur*gi*ão \cmark \\
+ninfomaníaca & nin*fo*ma*ní-a*ca \xmark & nin*fo*ma*ní*a*ca \cmark \\
+ninfomaníaco & nin*fo*ma*ní-a*co \xmark & nin*fo*ma*ní*a*co \cmark \\
+nobiliárquico & no*bi*li-ár*qui*co \xmark & no*bi*li*ár*qui*co \cmark \\
+núpcias & núp*ci.as \xmark & núp*ci.as \xmark \\
+oboísta & o*bo-ís*ta \xmark & o*bo*ís*ta \cmark \\
+obstruído & obs*tru-í*do \xmark & obs*tru*í*do \cmark \\
+obstruir & obs*tru-ir \xmark & obs*tru*ir \cmark \\
+ocasião & o*ca*si-ão \xmark & o*ca*si*ão \cmark \\
+oceânico & o*ce-â*ni*co \xmark & o*ce*â*ni*co \cmark \\
+ocluir & o*clu-ir \xmark & o*clu*ir \cmark \\
+octaédrico & oc*ta-é*dri*co \xmark & oc*ta*é*dri*co \cmark \\
+odeão & o*de-ão \xmark & o*de*ão \cmark \\
+odômetro & o-dô*me*tro \xmark & o*dô*me*tro \cmark \\
+oleícola & o*le-í*co*la \xmark & o*le*í*co*la \cmark \\
+oleína & o*le-í*na \xmark & o*le*í*na \cmark \\
+olimpíada & o*lim*pí-a*da \xmark & o*lim*pí*a*da \cmark \\
+oócito & o-ó*ci*to \xmark & o*ó*ci*to \cmark \\
+opinião & o*pi*ni-ão \xmark & o*pi*ni*ão \cmark \\
+orfeão & or*fe-ão \xmark & or*fe*ão \cmark \\
+oriundo & o*ri-un*do \xmark & o*ri*un*do \cmark \\
+ortodôntico & or*to-dôn*ti*co \xmark & or*to*dôn*ti*co \cmark \\
+osteíte & os*te-í*te \xmark & os*te*í*te \cmark \\
+painço & pa-in*ço \xmark & pa-in*ço \xmark \\
+país & pa-ís \xmark & pa*ís \cmark \\
+paleógrafo & pa*le-ó*gra*fo \xmark & pa*le*ó*gra*fo \cmark \\
+pantagruélico & pan*ta*gru-é*li*co \xmark & pan*ta*gru*é*li*co \cmark \\
+panteão & pan*te-ão \xmark & pan*te*ão \cmark \\
+panteísmo & pan*te-ís*mo \xmark & pan*te*ís*mo \cmark \\
+panteísta & pan*te-ís*ta \xmark & pan*te*ís*ta \cmark \\
+paquímetro & pa-quí*me*tro \xmark & pa*quí*me*tro \cmark \\
+paradisíaco & pa*ra*di*sí-a*co \xmark & pa*ra*di*sí*a*co \cmark \\
+paraibano & pa*ra-i*ba*no \xmark & pa*ra-i*ba*no \xmark \\
+paraíba & pa*ra-í*ba \xmark & pa*ra*í*ba \cmark \\
+paraíso & pa*ra-í*so \xmark & pa*ra*í*so \cmark \\
+parnaíba & par*na-í*ba \xmark & par*na*í*ba \cmark \\
+parquê & par-quê \xmark & par*quê \cmark \\
+parquímetro & par-quí*me*tro \xmark & par*quí*me*tro \cmark \\
+parvoíce & par*vo-í*ce \xmark & par*vo*í*ce \cmark \\
+patchuli & pat*chu*li \cmark & pat-chu*li \xmark \\
+patenteável & pa*ten*te-á*vel \xmark & pa*ten*te*á*vel \cmark \\
+patriótico & pa*tri-ó*ti*co \xmark & pa*tri*ó*ti*co \cmark \\
+paul & pa-ul \xmark & pa-ul \xmark \\
+paxiúba & pa*xi-ú*ba \xmark & pa*xi*ú*ba \cmark \\
 peão & pe-ão \xmark & pe*ão \cmark \\
-previdenciário & pre*vi*den*ci-á*ri*o \xmark & pre*vi*den*ci*á*ri*o \cmark \\
-constituído & cons*ti*tu-í*do \xmark & cons*ti*tu*í*do \cmark \\
+pecíolo & pe*cí-o*lo \xmark & pe*cí*o*lo \cmark \\
+pediátrico & pe*di-á*tri*co \xmark & pe*di*á*tri*co \cmark \\
+perdoável & per*do-á*vel \xmark & per*do*á*vel \cmark \\
+periódico & pe*ri-ó*di*co \xmark & pe*ri*ó*di*co \cmark \\
+período & pe*rí-o*do \xmark & pe*rí*o*do \cmark \\
+periurbano & pe*ri-ur*ba*no \xmark & pe*ri*ur*ba*no \cmark \\
+permeável & per*me-á*vel \xmark & per*me*á*vel \cmark \\
+petroquímica & pe*tro-quí*mi*ca \xmark & pe*tro*quí*mi*ca \cmark \\
+petroquímico & pe*tro-quí*mi*co \xmark & pe*tro*quí*mi*co \cmark \\
+piauiense & pi*au-i*en*se \xmark & pi*au*i*en*se \cmark \\
+picuinha & pi*cu-i*nha \xmark & pi*cu*i*nha \cmark \\
+pindaíba & pin*da-í*ba \xmark & pin*da*í*ba \cmark \\
+pintainho & pin*ta-i*nho \xmark & pin*ta*i*nho \cmark \\
+piromaníaco & pi*ro*ma*ní-a*co \xmark & pi*ro*ma*ní*a*co \cmark \\
+pitiríase & pi*ti*rí-a*se \xmark & pi*ti*rí*a*se \cmark \\
+pium & pi-um \xmark & pi*um \cmark \\
+pivô & pi-vô \xmark & pi*vô \cmark \\
+pixaim & pi*xa-im \xmark & pi*xa-im \xmark \\
+platônico & pla-tô*ni*co \xmark & pla*tô*ni*co \cmark \\
+platô & pla-tô \xmark & pla*tô \cmark \\
+plebeísmo & ple*be-ís*mo \xmark & ple*be*ís*mo \cmark \\
+pneumática & p.neu*má*ti*ca \xmark & pneu*má*ti*ca \cmark \\
+pneumático & p.neu*má*ti*co \xmark & pneu*má*ti*co \cmark \\
+pneumococo & p.neu*mo*co*co \xmark & pneu*mo*co*co \cmark \\
+pneumoconiose & p.neu*mo*co*ni*o*se \xmark & pneu*mo*co*ni*o*se \cmark \\
+pneumogástrico & p.neu*mo*gás*tri*co \xmark & pneu*mo*gás*tri*co \cmark \\
+pneumônico & p.neu-mô*ni*co \xmark & pneu*mô*ni*co \cmark \\
+pneumotórax & p.neu*mo*tó*rax \xmark & pneu*mo*tó*rax \cmark \\
+pneu & p.neu \xmark & pneu \cmark \\
+poética & po-é*ti*ca \xmark & po*é*ti*ca \cmark \\
+poético & po-é*ti*co \xmark & po*é*ti*co \cmark \\
+poliéster & po*li-és*ter \xmark & po*li*és*ter \cmark \\
+polifônico & po*li-fô*ni*co \xmark & po*li*fô*ni*co \cmark \\
+politeísmo & po*li*te-ís*mo \xmark & po*li*te*ís*mo \cmark \\
+politeísta & po*li*te-ís*ta \xmark & po*li*te*ís*ta \cmark \\
+poluir & po*lu-ir \xmark & po*lu*ir \cmark \\
+poraquê & po*ra-quê \xmark & po*ra*quê \cmark \\
 pornô & por-nô \xmark & por*nô \cmark \\
+porquê & por-quê \xmark & por*quê \cmark \\
+possuído & pos*su-í*do \xmark & pos*su*í*do \cmark \\
+possuidor & pos*su-i*dor \xmark & pos*su*i*dor \cmark \\
+possuir & pos*su-ir \xmark & pos*su*ir \cmark \\
+preâmbulo & pre-âm*bu*lo \xmark & pre*âm*bu*lo \cmark \\
+preênsil & pre-ên*sil \xmark & pre*ên*sil \cmark \\
+prejuízo & pre*ju-í*zo \xmark & pre*ju*í*zo \cmark \\
+presidenciável & pre*si*den*ci-á*vel \xmark & pre*si*den*ci*á*vel \cmark \\
+procaína & pro*ca-í*na \xmark & pro*ca*í*na \cmark \\
+procariótico & pro*ca*ri-ó*ti*co \xmark & pro*ca*ri*ó*ti*co \cmark \\
+prolegômenos & pro*le-gô*me*nos \xmark & pro*le*gô*me*nos \cmark \\
+prosaísmo & pro*sa-ís*mo \xmark & pro*sa*ís*mo \cmark \\
+prostituição & pros*ti*tu-i*ção \xmark & pros*ti*tu*i*ção \cmark \\
+prostituir & pros*ti*tu-ir \xmark & pros*ti*tu*ir \cmark \\
+proteína & pro*te-í*na \xmark & pro*te*í*na \cmark \\
+proteólise & pro*te-ó*li*se \xmark & pro*te*ó*li*se \cmark \\
+pseudônimo & p.seu-dô*ni*mo \xmark & pseu*dô*ni*mo \cmark \\
+psicanálise & p.si*ca*ná*li*se \xmark & psi*ca*ná*li*se \cmark \\
+psicanalista & p.si*ca*na*lis*ta \xmark & psi*ca*na*lis*ta \cmark \\
+psicanalítico & p.si*ca*na*lí*ti*co \xmark & psi*ca*na*lí*ti*co \cmark \\
+psicodrama & p.si*co*dra*ma \xmark & psi*co*dra*ma \cmark \\
+psicógrafo & p.si*có*gra*fo \xmark & psi*có*gra*fo \cmark \\
+psicolinguista & p.si*co*lin*guis*ta \xmark & psi*co*lin*guis*ta \cmark \\
+psicologicamente & p.si*co*lo*gi*ca*men*te \xmark & psi*co*lo*gi*ca*men*te \cmark \\
+psicológico & p.si*co*ló*gi*co \xmark & psi*co*ló*gi*co \cmark \\
+psicologismo & p.si*co*lo*gis*mo \xmark & psi*co*lo*gis*mo \cmark \\
+psicologista & p.si*co*lo*gis*ta \xmark & psi*co*lo*gis*ta \cmark \\
+psicologizar & p.si*co*lo*gi*zar \xmark & psi*co*lo*gi*zar \cmark \\
+psicólogo & p.si*có*lo*go \xmark & psi*có*lo*go \cmark \\
+psicométrico & p.si*co*mé*tri*co \xmark & psi*co*mé*tri*co \cmark \\
+psicomotor & p.si*co*mo*tor \xmark & psi*co*mo*tor \cmark \\
+psicomotricidade & p.si*co*mo*tri*ci*da*de \xmark & psi*co*mo*tri*ci*da*de \cmark \\
+psicopata & p.si*co*pa*ta \xmark & psi*co*pa*ta \cmark \\
+psicopático & p.si*co*pá*ti*co \xmark & psi*co*pá*ti*co \cmark \\
+psicopatológico & p.si*co*pa*to*ló*gi*co \xmark & psi*co*pa*to*ló*gi*co \cmark \\
+psicopedagógico & p.si*co*pe*da*gó*gi*co \xmark & psi*co*pe*da*gó*gi*co \cmark \\
+psicopedagogo & p.si*co*pe*da*go*go \xmark & psi*co*pe*da*go*go \cmark \\
+psicose & p.si*co*se \xmark & psi*co*se \cmark \\
+psicossexual & p.si*cos*se*xu*al \xmark & psi*cos*se*xu*al \cmark \\
+psicossomático & p.si*cos*so*má*ti*co \xmark & psi*cos*so*má*ti*co \cmark \\
+psicotécnico & p.si*co*téc*ni*co \xmark & psi*co*téc*ni*co \cmark \\
+psicoterapeuta & p.si*co*te*ra*peu*ta \xmark & psi*co*te*ra*peu*ta \cmark \\
+psicoterápico & p.si*co*te*rá*pi*co \xmark & psi*co*te*rá*pi*co \cmark \\
+psicótico & p.si*có*ti*co \xmark & psi*có*ti*co \cmark \\
+psicotrópico & p.si*co*tró*pi*co \xmark & psi*co*tró*pi*co \cmark \\
+psique & p.si*que \xmark & psi*que \cmark \\
+psiquiatra & p.si*qui*a*tra \xmark & psi*qui*a*tra \cmark \\
 psiquiátrico & p.si*qui-á*tri*co \xmark & psi*qui*á*tri*co \cmark \\
-moinho & mo-i*nho \xmark & mo*i*nho \cmark \\
-obstruir & obs*tru-ir \xmark & obs*tru*ir \cmark \\
-psiquiatria & p.si*qui*a*tri*a \xmark & psi*qui*a*tri*a \cmark \\
+psíquico & p.sí*qui*co \xmark & psí*qui*co \cmark \\
+psiquismo & p.si*quis*mo \xmark & psi*quis*mo \cmark \\
+psitaciforme & p.si*ta*ci*for*me \xmark & psi*ta*ci*for*me \cmark \\
+psitacismo & p.si*ta*cis*mo \xmark & psi*ta*cis*mo \cmark \\
+psoas & p.so*as \xmark & p.so*as \xmark \\
+psoríase & p.so*rí-a*se \xmark & p.so*rí*a*se \xmark \\
+pterossauro & p.te*ros*sau*ro \xmark & pte*ros*sau*ro \cmark \\
+ptose & p.to*se \xmark & pto*se \cmark \\
+pulôver & pu-lô*ver \xmark & pu*lô*ver \cmark \\
+quartzito & quart*zi*to \cmark & quart*zi*to \cmark \\
+quartzo & quart*zo \cmark & quart*zo \cmark \\
+questiúncula & ques*ti-ún*cu*la \xmark & ques*ti*ún*cu*la \cmark \\
+quilômetro & qui-lô*me*tro \xmark & qui*lô*me*tro \cmark \\
+quilowatt & qui*lo-watt \xmark & qui*lo-watt \xmark \\
+quiproquó & qui*pro-quó \xmark & qui*pro*quó \cmark \\
+radiólise & ra*di-ó*li*se \xmark & ra*di*ó*li*se \cmark \\
+rainha & ra-i*nha \xmark & ra*i*nha \cmark \\
+raiz & ra-iz \xmark & ra*iz \cmark \\
+randômico & ran-dô*mi*co \xmark & ran*dô*mi*co \cmark \\
+raquítico & ra-quí*ti*co \xmark & ra*quí*ti*co \cmark \\
+ravióli & ra*vi-ó*li \xmark & ra*vi*ó*li \cmark \\
+razoável & ra*zo-á*vel \xmark & ra*zo*á*vel \cmark \\
+rebelião & re*be*li-ão \xmark & re*be*li*ão \cmark \\
+recaída & re*ca-í*da \xmark & re*ca*í*da \cmark \\
+recair & re*ca-ir \xmark & re*ca*ir \cmark \\
+recôncavo & re-côn*ca*vo \xmark & re*côn*ca*vo \cmark \\
+recôndito & re-côn*di*to \xmark & re*côn*di*to \cmark \\
+reconstituição & re*cons*ti*tu-i*ção \xmark & re*cons*ti*tu*i*ção \cmark \\
+reconstituinte & re*cons*ti*tu-in*te \xmark & re*cons*ti*tu*in*te \cmark \\
+reconstituir & re*cons*ti*tu-ir \xmark & re*cons*ti*tu*ir \cmark \\
+reconstruído & re*cons*tru-í*do \xmark & re*cons*tru*í*do \cmark \\
+reconstruir & re*cons*tru-ir \xmark & re*cons*tru*ir \cmark \\
+redistribuir & re*dis*tri*bu-ir \xmark & re*dis*tri*bu*ir \cmark \\
+refluir & re*flu-ir \xmark & re*flu*ir \cmark \\
+região & re*gi-ão \xmark & re*gi*ão \cmark \\
+reimplantação & re-im*plan*ta*ção \xmark & re*im*plan*ta*ção \cmark \\
+reimplantar & re-im*plan*tar \xmark & re*im*plan*tar \cmark \\
+reimportar & re-im*por*tar \xmark & re*im*por*tar \cmark \\
+reimpressão & re-im*pres*são \xmark & re*im*pres*são \cmark \\
+reimprimir & re-im*pri*mir \xmark & re*im*pri*mir \cmark \\
+reincidente & re-in*ci*den*te \xmark & re*in*ci*den*te \cmark \\
+reincidir & re-in*ci*dir \xmark & re*in*ci*dir \cmark \\
+reincorporação & re-in*cor*po*ra*ção \xmark & re*in*cor*po*ra*ção \cmark \\
 reindexação & re-in*de*xa*ção \xmark & re-in*de*xa*ção \xmark \\
-aquário & a-quá*ri*o \xmark & a*quá*ri*o \cmark \\
-amendoim & a*men*do-im \xmark & a*men*do-im \xmark \\
-baú & ba-ú \xmark & ba*ú \cmark \\
-distribuidor & dis*tri*bu-i*dor \xmark & dis*tri*bu*i*dor \cmark \\
-trair & tra-ir \xmark & tra*ir \cmark \\
-intuição & in*tu-i*ção \xmark & in*tu*i*ção \cmark \\
-petroquímica & pe*tro-quí*mi*ca \xmark & pe*tro*quí*mi*ca \cmark \\
-evoluir & e*vo*lu-ir \xmark & e*vo*lu*ir \cmark \\
-petroquímico & pe*tro-quí*mi*co \xmark & pe*tro*quí*mi*co \cmark \\
-asiática & a*si-á*ti*ca \xmark & a*si*á*ti*ca \cmark \\
-dinamarquês & di*na*mar-quês \xmark & di*na*mar*quês \cmark \\
-tcheco & t.che*co \xmark & tche*co \cmark \\
-diminuído & di*mi*nu-í*do \xmark & di*mi*nu*í*do \cmark \\
-instituir & ins*ti*tu-ir \xmark & ins*ti*tu*ir \cmark \\
-lampião & lam*pi-ão \xmark & lam*pi*ão \cmark \\
-arquitetônico & ar*qui*te-tô*ni*co \xmark & ar*qui*te*tô*ni*co \cmark \\
-atraído & a*tra-í*do \xmark & a*tra*í*do \cmark \\
-gastronômico & gas*tro-nô*mi*co \xmark & gas*tro*nô*mi*co \cmark \\
-vibrião & vi*bri-ão \xmark & vi*bri*ão \cmark \\
-caraíba & ca*ra-í*ba \xmark & ca*ra*í*ba \cmark \\
-ferroviário & fer*ro*vi-á*ri*o \xmark & fer*ro*vi*á*ri*o \cmark \\
-mobiliário & mo*bi*li-á*ri*o \xmark & mo*bi*li*á*ri*o \cmark \\
+reingressar & re-in*gres*sar \xmark & re*in*gres*sar \cmark \\
+reingresso & re-in*gres*so \xmark & re*in*gres*so \cmark \\
+reinscrever & re-ins*cre*ver \xmark & re*ins*cre*ver \cmark \\
+reinserção & re-in*ser*ção \xmark & re*in*ser*ção \cmark \\
+reinserir & re-in*se*rir \xmark & re*in*se*rir \cmark \\
+reinstalação & re-ins*ta*la*ção \xmark & re*ins*ta*la*ção \cmark \\
+reinstalar & re-ins*ta*lar \xmark & re*ins*ta*lar \cmark \\
+reinstituir & re-ins*ti*tu-ir \xmark & re*ins*ti*tu*ir \cmark \\
+reintegração & re-in*te*gra*ção \xmark & re*in*te*gra*ção \cmark \\
+reintegrar & re-in*te*grar \xmark & re*in*te*grar \cmark \\
+reintrodução & re-in*tro*du*ção \xmark & re*in*tro*du*ção \cmark \\
+reintroduzir & re-in*tro*du*zir \xmark & re*in*tro*du*zir \cmark \\
+reinventar & re-in*ven*tar \xmark & re*in*ven*tar \cmark \\
+reinvestir & re-in*ves*tir \xmark & re*in*ves*tir \cmark \\
+religião & re*li*gi-ão \xmark & re*li*gi*ão \cmark \\
+restituição & res*ti*tu-i*ção \xmark & res*ti*tu*i*ção \cmark \\
+restituir & res*ti*tu-ir \xmark & res*ti*tu*ir \cmark \\
+retraído & re*tra-í*do \xmark & re*tra*í*do \cmark \\
+retrair & re*tra-ir \xmark & re*tra*ir \cmark \\
+retribuição & re*tri*bu-i*ção \xmark & re*tri*bu*i*ção \cmark \\
+retribuir & re*tri*bu-ir \xmark & re*tri*bu*ir \cmark \\
+reunir & re-u*nir \xmark & re-u*nir \xmark \\
+reurbanizar & re-ur*ba*ni*zar \xmark & re-ur*ba*ni*zar \xmark \\
 robô & ro-bô \xmark & ro*bô \cmark \\
-traído & tra-í*do \xmark & tra*í*do \cmark \\
-chatô & cha-tô \xmark & cha*tô \cmark \\
-viés & vi-és \xmark & vi*és \cmark \\
-biquíni & bi-quí*ni \xmark & bi*quí*ni \cmark \\
-pneumonia & p.neu*mo*ni*a \xmark & pneu*mo*ni*a \cmark \\
-galeão & ga*le-ão \xmark & ga*le*ão \cmark \\
-pseudônimo & p.seu-dô*ni*mo \xmark & pseu*dô*ni*mo \cmark \\
-psicologicamente & p.si*co*lo*gi*ca*men*te \xmark & psi*co*lo*gi*ca*men*te \cmark \\
-tatuí & ta*tu-í \xmark & ta*tu*í \cmark \\
-anuário & a*nu-á*ri*o \xmark & a*nu*á*ri*o \cmark \\
-contrair & con*tra-ir \xmark & con*tra*ir \cmark \\
-curió & cu*ri-ó \xmark & cu*ri*ó \cmark \\
-egoísmo & e*go-ís*mo \xmark & e*go*ís*mo \cmark \\
-poliéster & po*li-és*ter \xmark & po*li*és*ter \cmark \\
-caótico & ca-ó*ti*co \xmark & ca*ó*ti*co \cmark \\
-descontraído & des*con*tra-í*do \xmark & des*con*tra*í*do \cmark \\
-hanseníase & han*se*ní-a*se \xmark & han*se*ní*a*se \cmark \\
-macedônia & ma*ce-dô*ni*a \xmark & ma*ce*dô*ni*a \cmark \\
-heroísmo & he*ro-ís*mo \xmark & he*ro*ís*mo \cmark \\
-instituído & ins*ti*tu-í*do \xmark & ins*ti*tu*í*do \cmark \\
-periódico & pe*ri-ó*di*co \xmark & pe*ri*ó*di*co \cmark \\
-abdômen & ab-dô*men \xmark & ab*dô*men \cmark \\
-paraibano & pa*ra-i*ba*no \xmark & pa*ra-i*ba*no \xmark \\
-psíquico & p.sí*qui*co \xmark & psí*qui*co \cmark \\
-reconstituir & re*cons*ti*tu-ir \xmark & re*cons*ti*tu*ir \cmark \\
-oásis & o-á*sis \xmark & o*á*sis \cmark \\
-parnaíba & par*na-í*ba \xmark & par*na*í*ba \cmark \\
-usufruir & u*su*fru-ir \xmark & u*su*fru*ir \cmark \\
-camelô & ca*me-lô \xmark & ca*me*lô \cmark \\
-maníaco & ma*ní-a*co \xmark & ma*ní*a*co \cmark \\
-sabiá & sa*bi-á \xmark & sa*bi*á \cmark \\
-agronômico & a*gro-nô*mi*co \xmark & a*gro*nô*mi*co \cmark \\
-astronômico & as*tro-nô*mi*co \xmark & as*tro*nô*mi*co \cmark \\
-psicopata & p.si*co*pa*ta \xmark & psi*co*pa*ta \cmark \\
-geógrafo & ge-ó*gra*fo \xmark & ge*ó*gra*fo \cmark \\
-ideário & i*de-á*ri*o \xmark & i*de*á*ri*o \cmark \\
-piá & pi-á \xmark & pi*á \cmark \\
-alcoólatra & al*co-ó*la*tra \xmark & al*co*ó*la*tra \cmark \\
-biógrafo & bi-ó*gra*fo \xmark & bi*ó*gra*fo \cmark \\
-coincidir & co-in*ci*dir \xmark & co*in*ci*dir \cmark \\
-escorpião & es*cor*pi-ão \xmark & es*cor*pi*ão \cmark \\
-fluência & flu-ên*ci*a \xmark & flu*ên*ci*a \cmark \\
+roído & ro-í*do \xmark & ro*í*do \cmark \\
+roséola & ro*sé-o*la \xmark & ro*sé*o*la \cmark \\
+ruão & ru-ão \xmark & ru*ão \cmark \\
+rubéola & ru*bé-o*la \xmark & ru*bé*o*la \cmark \\
+rufião & ru*fi-ão \xmark & ru*fi*ão \cmark \\
+ruído & ru-í*do \xmark & ru*í*do \cmark \\
+ruim & ru-im \xmark & ru-im \xmark \\
 ruína & ru-í*na \xmark & ru*í*na \cmark \\
-delinquência & de*lin-quên*ci*a \xmark & de*lin*quên*ci*a \cmark \\
-contraído & con*tra-í*do \xmark & con*tra*í*do \cmark \\
-diluir & di*lu-ir \xmark & di*lu*ir \cmark \\
-psicose & p.si*co*se \xmark & psi*co*se \cmark \\
-bioquímica & bi*o-quí*mi*ca \xmark & bi*o*quí*mi*ca \cmark \\
-fluidez & flu-i*dez \xmark & flu-i*dez \xmark \\
-futevôlei & fu*te-vô*lei \xmark & fu*te*vô*lei \cmark \\
-judaísmo & ju*da-ís*mo \xmark & ju*da*ís*mo \cmark \\
-viúvo & vi-ú*vo \xmark & vi*ú*vo \cmark \\
-capô & ca-pô \xmark & ca*pô \cmark \\
-casuísmo & ca*su-ís*mo \xmark & ca*su*ís*mo \cmark \\
-receituário & re*cei*tu-á*ri*o \xmark & re*cei*tu*á*ri*o \cmark \\
-agrião & a*gri-ão \xmark & a*gri*ão \cmark \\
-comerciário & co*mer*ci-á*ri*o \xmark & co*mer*ci*á*ri*o \cmark \\
-estereótipo & es*te*re-ó*ti*po \xmark & es*te*re*ó*ti*po \cmark \\
-psicoterapia & p.si*co*te*ra*pi*a \xmark & psi*co*te*ra*pi*a \cmark \\
-vascaíno & vas*ca-í*no \xmark & vas*ca*í*no \cmark \\
-arquitetônica & ar*qui*te-tô*ni*ca \xmark & ar*qui*te*tô*ni*ca \cmark \\
-macroeconômico & ma*cro*e*co-nô*mi*co \xmark & ma*cro*e*co*nô*mi*co \cmark \\
-restituir & res*ti*tu-ir \xmark & res*ti*tu*ir \cmark \\
+ruindade & ru-in*da*de \xmark & ru*in*da*de \cmark \\
+ruinoso & ru-i*no*so \xmark & ru*i*no*so \cmark \\
+ruir & ru-ir \xmark & ru*ir \cmark \\
 rutherford & ru-ther*ford \xmark & ru-ther*ford \xmark \\
-triunfal & tri-un*fal \xmark & tri*un*fal \cmark \\
-guardião & guar*di-ão \xmark & guar*di*ão \cmark \\
-oriundo & o*ri-un*do \xmark & o*ri*un*do \cmark \\
-arqueólogo & ar*que-ó*lo*go \xmark & ar*que*ó*lo*go \cmark \\
-carbônico & car-bô*ni*co \xmark & car*bô*ni*co \cmark \\
+saída & sa-í*da \xmark & sa*í*da \cmark \\
+saído & sa-í*do \xmark & sa*í*do \cmark \\
+sair & sa-ir \xmark & sa*ir \cmark \\
+salomônico & sa*lo-mô*ni*co \xmark & sa*lo*mô*ni*co \cmark \\
+sambaíba & sam*ba-í*ba \xmark & sam*ba*í*ba \cmark \\
+sanduíche & san*du-í*che \xmark & san*du*í*che \cmark \\
+saquê & sa-quê \xmark & sa*quê \cmark \\
+sardônico & sar-dô*ni*co \xmark & sar*dô*ni*co \cmark \\
+satiríase & sa*ti*rí-a*se \xmark & sa*ti*rí*a*se \cmark \\
+saúde & sa-ú*de \xmark & sa*ú*de \cmark \\
+saúva & sa-ú*va \xmark & sa*ú*va \cmark \\
+sebastião & se*bas*ti-ão \xmark & se*bas*ti*ão \cmark \\
+semiárido & se*mi-á*ri*do \xmark & se*mi*á*ri*do \cmark \\
+siálico & si-á*li*co \xmark & si*á*li*co \cmark \\
+sinfônica & sin-fô*ni*ca \xmark & sin*fô*ni*ca \cmark \\
+sinfônico & sin-fô*ni*co \xmark & sin*fô*ni*co \cmark \\
+sinônimo & si-nô*ni*mo \xmark & si*nô*ni*mo \cmark \\
+siríaco & si*rí-a*co \xmark & si*rí*a*co \cmark \\
+sobressair & so*bres*sa-ir \xmark & so*bres*sa*ir \cmark \\
+sociólogo & so*ci-ó*lo*go \xmark & so*ci*ó*lo*go \cmark \\
+sonômetro & so-nô*me*tro \xmark & so*nô*me*tro \cmark \\
+soviético & so*vi-é*ti*co \xmark & so*vi*é*ti*co \cmark \\
+stalinismo & s.ta*li*nis*mo \xmark & sta*li*nis*mo \cmark \\
 stalinista & s.ta*li*nis*ta \xmark & sta*li*nis*ta \cmark \\
-egoísta & e*go-ís*ta \xmark & e*go*ís*ta \cmark \\
-portuário & por*tu-á*ri*o \xmark & por*tu*á*ri*o \cmark \\
-recaída & re*ca-í*da \xmark & re*ca*í*da \cmark \\
-reiniciar & re-i*ni*ci*ar \xmark & re-i*ni*ci*ar \xmark \\
-reurbanização & re-ur*ba*ni*za*ção \xmark & re-ur*ba*ni*za*ção \xmark \\
-teólogo & te-ó*lo*go \xmark & te*ó*lo*go \cmark \\
-baião & bai-ão \xmark & bai*ão \cmark \\
-genuíno & ge*nu-í*no \xmark & ge*nu*í*no \cmark \\
-hegemônico & he*ge-mô*ni*co \xmark & he*ge*mô*ni*co \cmark \\
-resquício & res-quí*ci*o \xmark & res*quí*ci*o \cmark \\
-retribuição & re*tri*bu-i*ção \xmark & re*tri*bu*i*ção \cmark \\
-confluência & con*flu-ên*ci*a \xmark & con*flu*ên*ci*a \cmark \\
-fluir & flu-ir \xmark & flu*ir \cmark \\
-imperdoável & im*per*do-á*vel \xmark & im*per*do*á*vel \cmark \\
-distrair & dis*tra-ir \xmark & dis*tra*ir \cmark \\
-guaíba & gua-í*ba \xmark & gua*í*ba \cmark \\
-intuitivo & in*tu-i*ti*vo \xmark & in*tu*i*ti*vo \cmark \\
-orquídea & or-quí*de*a \xmark & or*quí*de*a \cmark \\
-semiótica & se*mi-ó*ti*ca \xmark & se*mi*ó*ti*ca \cmark \\
-vovô & vo-vô \xmark & vo*vô \cmark \\
-campainha & cam*pa-i*nha \xmark & cam*pa*i*nha \cmark \\
-czar & c.zar \xmark & czar \cmark \\
-diluição & di*lu-i*ção \xmark & di*lu*i*ção \cmark \\
-distraído & dis*tra-í*do \xmark & dis*tra*í*do \cmark \\
-eloquência & e*lo-quên*ci*a \xmark & e*lo*quên*ci*a \cmark \\
-insubstituível & in*subs*ti*tu-í*vel \xmark & in*subs*ti*tu*í*vel \cmark \\
-reinventar & re-in*ven*tar \xmark & re*in*ven*tar \cmark \\
-retribuir & re*tri*bu-ir \xmark & re*tri*bu*ir \cmark \\
-rubéola & ru*bé-o*la \xmark & ru*bé*o*la \cmark \\
-abruptamente & a.b-rup*ta*men*te \xmark & a.b-rup*ta*men*te \xmark \\
-maniqueísmo & ma*ni*que-ís*mo \xmark & ma*ni*que*ís*mo \cmark \\
-antiquário & an*ti-quá*ri*o \xmark & an*ti*quá*ri*o \cmark \\
-harmônica & har-mô*ni*ca \xmark & har*mô*ni*ca \cmark \\
-judô & ju-dô \xmark & ju*dô \cmark \\
-maniqueísta & ma*ni*que-ís*ta \xmark & ma*ni*que*ís*ta \cmark \\
-tchau & t.chau \xmark & tchau \cmark \\
-moído & mo-í*do \xmark & mo*í*do \cmark \\
-psicanalítico & p.si*ca*na*lí*ti*co \xmark & psi*ca*na*lí*ti*co \cmark \\
-caíco & ca-í*co \xmark & ca*í*co \cmark \\
-descontinuidade & des*con*ti*nu-i*da*de \xmark & des*con*ti*nu*i*da*de \cmark \\
-tarô & ta-rô \xmark & ta*rô \cmark \\
-absenteísmo & ab*sen*te-ís*mo \xmark & ab*sen*te*ís*mo \cmark \\
-anuência & a*nu-ên*ci*a \xmark & a*nu*ên*ci*a \cmark \\
-etíope & e*tí-o*pe \xmark & e*tí*o*pe \cmark \\
-ofurô & o*fu-rô \xmark & o*fu*rô \cmark \\
-panteão & pan*te-ão \xmark & pan*te*ão \cmark \\
-atômico & a-tô*mi*co \xmark & a*tô*mi*co \cmark \\
-corroído & cor*ro-í*do \xmark & cor*ro*í*do \cmark \\
-destituído & des*ti*tu-í*do \xmark & des*ti*tu*í*do \cmark \\
-estagiário & es*ta*gi-á*ri*o \xmark & es*ta*gi*á*ri*o \cmark \\
-inadiável & i*na*di-á*vel \xmark & i*na*di*á*vel \cmark \\
-instruído & ins*tru-í*do \xmark & ins*tru*í*do \cmark \\
-amazônico & a*ma-zô*ni*co \xmark & a*ma*zô*ni*co \cmark \\
-anuidade & a*nu-i*da*de \xmark & a*nu*i*da*de \cmark \\
-evoluído & e*vo*lu-í*do \xmark & e*vo*lu*í*do \cmark \\
-faísca & fa-ís*ca \xmark & fa*ís*ca \cmark \\
-harmônico & har-mô*ni*co \xmark & har*mô*ni*co \cmark \\
-patriótico & pa*tri-ó*ti*co \xmark & pa*tri*ó*ti*co \cmark \\
-presidiário & pre*si*di-á*ri*o \xmark & pre*si*di*á*ri*o \cmark \\
-reconstruído & re*cons*tru-í*do \xmark & re*cons*tru*í*do \cmark \\
-tricô & tri-cô \xmark & tri*cô \cmark \\
-antiético & an*ti-é*ti*co \xmark & an*ti*é*ti*co \cmark \\
-cronômetro & cro-nô*me*tro \xmark & cro*nô*me*tro \cmark \\
-destituição & des*ti*tu-i*ção \xmark & des*ti*tu*i*ção \cmark \\
-fiúza & fi-ú*za \xmark & fi*ú*za \cmark \\
-píer & pí-er \xmark & pí-er \xmark \\
-psique & p.si*que \xmark & psi*que \cmark \\
-recair & re*ca-ir \xmark & re*ca*ir \cmark \\
-sinfônico & sin-fô*ni*co \xmark & sin*fô*ni*co \cmark \\
-triunfante & tri-un*fan*te \xmark & tri*un*fan*te \cmark \\
-adail & a*da-il \xmark & a*da-il \xmark \\
-atônito & a-tô*ni*to \xmark & a*tô*ni*to \cmark \\
-birô & bi-rô \xmark & bi*rô \cmark \\
-cafeína & ca*fe-í*na \xmark & ca*fe*í*na \cmark \\
-ideólogo & i*de-ó*lo*go \xmark & i*de*ó*lo*go \cmark \\
-inequívoco & i*ne-quí*vo*co \xmark & i*ne*quí*vo*co \cmark \\
-míope & mí-o*pe \xmark & mí*o*pe \cmark \\
-poá & po-á \xmark & po*á \cmark \\
-stalinismo & s.ta*li*nis*mo \xmark & sta*li*nis*mo \cmark \\
-suíno & su-í*no \xmark & su*í*no \cmark \\
-voyeurismo & voy-eu*ris*mo \xmark & voy-eu*ris*mo \xmark \\
-camaleão & ca*ma*le-ão \xmark & ca*ma*le*ão \cmark \\
-dióxido & di-ó*xi*do \xmark & di*ó*xi*do \cmark \\
-geólogo & ge-ó*lo*go \xmark & ge*ó*lo*go \cmark \\
-ilíada & i*lí-a*da \xmark & i*lí*a*da \cmark \\
-impermeável & im*per*me-á*vel \xmark & im*per*me*á*vel \cmark \\
-jesuíta & je*su-í*ta \xmark & je*su*í*ta \cmark \\
+suaíli & su*a-í*li \xmark & su*a*í*li \cmark \\
+suão & su-ão \xmark & su*ão \cmark \\
 suástica & su-ás*ti*ca \xmark & su*ás*ti*ca \cmark \\
-bioquímico & bi*o-quí*mi*co \xmark & bi*o*quí*mi*co \cmark \\
-buquê & bu-quê \xmark & bu*quê \cmark \\
-esôfago & e-sô*fa*go \xmark & e*sô*fa*go \cmark \\
-folião & fo*li-ão \xmark & fo*li*ão \cmark \\
-quilowatt & qui*lo-watt \xmark & qui*lo-watt \xmark \\
-ruir & ru-ir \xmark & ru*ir \cmark \\
-altruísmo & al*tru-ís*mo \xmark & al*tru*ís*mo \cmark \\
-equânime & e-quâ*ni*me \xmark & e*quâ*ni*me \cmark \\
-fruição & fru-i*ção \xmark & fru*i*ção \cmark \\
-insaciável & in*sa*ci-á*vel \xmark & in*sa*ci*á*vel \cmark \\
-caída & ca-í*da \xmark & ca*í*da \cmark \\
-ciático & ci-á*ti*co \xmark & ci*á*ti*co \cmark \\
-gavião & ga*vi-ão \xmark & ga*vi*ão \cmark \\
-gratuidade & gra*tu-i*da*de \xmark & gra*tu*i*da*de \cmark \\
-irremediável & ir*re*me*di-á*vel \xmark & ir*re*me*di*á*vel \cmark \\
-ladainha & la*da-i*nha \xmark & la*da*i*nha \cmark \\
-piauiense & pi*au-i*en*se \xmark & pi*au-i*en*se \xmark \\
-prostituir & pros*ti*tu-ir \xmark & pros*ti*tu*ir \cmark \\
-triunfar & tri-un*far \xmark & tri*un*far \cmark \\
-acuidade & a*cu-i*da*de \xmark & a*cu*i*da*de \cmark \\
-adriático & a*dri-á*ti*co \xmark & a*dri*á*ti*co \cmark \\
-afrodisíaco & a*fro*di*sí-a*co \xmark & a*fro*di*sí*a*co \cmark \\
-bioética & bi*o-é*ti*ca \xmark & bi*o*é*ti*ca \cmark \\
-cocô & co-cô \xmark & co*cô \cmark \\
-instruir & ins*tru-ir \xmark & ins*tru*ir \cmark \\
-paradisíaco & pa*ra*di*sí-a*co \xmark & pa*ra*di*sí*a*co \cmark \\
-poluir & po*lu-ir \xmark & po*lu*ir \cmark \\
-possuído & pos*su-í*do \xmark & pos*su*í*do \cmark \\
+subaquático & su*ba-quá*ti*co \xmark & su*ba*quá*ti*co \cmark \\
+subdiácono & sub*di-á*co*no \xmark & sub*di*á*co*no \cmark \\
+subliminar & su.b-li*mi*nar \xmark & su.b-li*mi*nar \xmark \\
+sublingual & su.b-lin*gual \xmark & su.b-lin*gual \xmark \\
 sublinha & su.b-li*nha \xmark & su.b-li*nha \xmark \\
-antibiótico & an*ti*bi-ó*ti*co \xmark & an*ti*bi*ó*ti*co \cmark \\
-apreciável & a*pre*ci-á*vel \xmark & a*pre*ci*á*vel \cmark \\
-desobstruir & de*sobs*tru-ir \xmark & de*sobs*tru*ir \cmark \\
-destruidor & des*tru-i*dor \xmark & des*tru*i*dor \cmark \\
-diáspora & di-ás*po*ra \xmark & di*ás*po*ra \cmark \\
-diluído & di*lu-í*do \xmark & di*lu*í*do \cmark \\
-maiúsculo & mai-ús*cu*lo \xmark & mai*ús*cu*lo \cmark \\
-miúdo & mi-ú*do \xmark & mi*ú*do \cmark \\
-pentacampeão & pen*ta*cam*pe-ão \xmark & pen*ta*cam*pe*ão \cmark \\
-retraído & re*tra-í*do \xmark & re*tra*í*do \cmark \\
+subliteratura & su.b-li*te*ra*tu*ra \xmark & su.b-li*te*ra*tu*ra \xmark \\
+sublocação & su.b-lo*ca*ção \xmark & sub*lo*ca*ção \cmark \\
+sublocar & su.b-lo*car \xmark & sub*lo*car \cmark \\
+sublunar & su.b-lu*nar \xmark & sub*lu*nar \cmark \\
+substituição & subs*ti*tu-i*ção \xmark & subs*ti*tu*i*ção \cmark \\
+substituído & subs*ti*tu-í*do \xmark & subs*ti*tu*í*do \cmark \\
+substituir & subs*ti*tu-ir \xmark & subs*ti*tu*ir \cmark \\
+substituível & subs*ti*tu-í*vel \xmark & subs*ti*tu*í*vel \cmark \\
+subtraído & sub*tra-í*do \xmark & sub*tra*í*do \cmark \\
 subtrair & sub*tra-ir \xmark & sub*tra*ir \cmark \\
 suéter & su-é*ter \xmark & su*é*ter \cmark \\
-açaí & a*ça-í \xmark & a*ça*í \cmark \\
-alcoólico & al*co-ó*li*co \xmark & al*co*ó*li*co \cmark \\
-despoluir & des*po*lu-ir \xmark & des*po*lu*ir \cmark \\
-diurno & di-ur*no \xmark & di*ur*no \cmark \\
-inexequível & i*ne*xe-quí*vel \xmark & i*ne*xe*quí*vel \cmark \\
-prontuário & pron*tu-á*ri*o \xmark & pron*tu*á*ri*o \cmark \\
-psicoterapeuta & p.si*co*te*ra*peu*ta \xmark & psi*co*te*ra*peu*ta \cmark \\
-saúva & sa-ú*va \xmark & sa*ú*va \cmark \\
-tabelião & ta*be*li-ão \xmark & ta*be*li*ão \cmark \\
-abrupto & a.b-rup*to \xmark & a.b-rup*to \xmark \\
-destituir & des*ti*tu-ir \xmark & des*ti*tu*ir \cmark \\
-dionisíaco & di*o*ni*sí-a*co \xmark & di*o*ni*sí*a*co \cmark \\
-lacônico & la-cô*ni*co \xmark & la*cô*ni*co \cmark \\
-megawatt & me*ga-watt \xmark & me*ga-watt \xmark \\
-poliuretano & po*li-u*re*ta*no \xmark & po*li*u*re*ta*no \cmark \\
-protozoário & pro*to*zo-á*ri*o \xmark & pro*to*zo*á*ri*o \cmark \\
-reincidente & re-in*ci*den*te \xmark & re*in*ci*den*te \cmark \\
-reintegrar & re-in*te*grar \xmark & re*in*te*grar \cmark \\
-reinvenção & re-in*ven*ção \xmark & re*in*ven*ção \cmark \\
-afluência & a*flu-ên*ci*a \xmark & a*flu*ên*ci*a \cmark \\
-assiduidade & as*si*du-i*da*de \xmark & as*si*du*i*da*de \cmark \\
-coágulo & co-á*gu*lo \xmark & co*á*gu*lo \cmark \\
-cuíca & cu-í*ca \xmark & cu*í*ca \cmark \\
-faraó & fa*ra-ó \xmark & fa*ra*ó \cmark \\
-fundiário & fun*di-á*ri*o \xmark & fun*di*á*ri*o \cmark \\
-incendiário & in*cen*di-á*ri*o \xmark & in*cen*di*á*ri*o \cmark \\
-itapuã & i*ta*pu-ã \xmark & i*ta*pu*ã \cmark \\
-parcimônia & par*ci-mô*ni*a \xmark & par*ci*mô*ni*a \cmark \\
-psicótico & p.si*có*ti*co \xmark & psi*có*ti*co \cmark \\
-redemoinho & re*de*mo-i*nho \xmark & re*de*mo*i*nho \cmark \\
-redistribuir & re*dis*tri*bu-ir \xmark & re*dis*tri*bu*ir \cmark \\
-reintrodução & re-in*tro*du*ção \xmark & re*in*tro*du*ção \cmark \\
-triunfalismo & tri-un*fa*lis*mo \xmark & tri*un*fa*lis*mo \cmark \\
-zodíaco & zo*dí-a*co \xmark & zo*dí*a*co \cmark \\
-aminoácido & a*mi*no-á*ci*do \xmark & a*mi*no*á*ci*do \cmark \\
-arruinar & ar*ru-i*nar \xmark & ar*ru*i*nar \cmark \\
-ateísmo & a*te-ís*mo \xmark & a*te*ís*mo \cmark \\
-caim & ca-im \xmark & ca-im \xmark \\
-exequível & e*xe-quí*vel \xmark & e*xe*quí*vel \cmark \\
-inconsequência & in*con*se-quên*ci*a \xmark & in*con*se*quên*ci*a \cmark \\
-laquê & la-quê \xmark & la*quê \cmark \\
-megalomaníaco & me*ga*lo*ma*ní-a*co \xmark & me*ga*lo*ma*ní*a*co \cmark \\
-pantaleão & pan*ta*le-ão \xmark & pan*ta*le*ão \cmark \\
-poluidor & po*lu-i*dor \xmark & po*lu*i*dor \cmark \\
-preâmbulo & pre-âm*bu*lo \xmark & pre*âm*bu*lo \cmark \\
-arcaísmo & ar*ca-ís*mo \xmark & ar*ca*ís*mo \cmark \\
-auréola & au*ré-o*la \xmark & au*ré*o*la \cmark \\
-autodestruição & au*to*des*tru-i*ção \xmark & au*to*des*tru*i*ção \cmark \\
-casuística & ca*su-ís*ti*ca \xmark & ca*su*ís*ti*ca \cmark \\
-desunião & de*su*ni-ão \xmark & de*su*ni*ão \cmark \\
-elogiável & e*lo*gi-á*vel \xmark & e*lo*gi*á*vel \cmark \\
-gnomo & g.no*mo \xmark & gno*mo \cmark \\
-neurocirurgião & neu*ro*ci*rur*gi-ão \xmark & neu*ro*ci*rur*gi*ão \cmark \\
-pediátrico & pe*di-á*tri*co \xmark & pe*di*á*tri*co \cmark \\
-permeável & per*me-á*vel \xmark & per*me*á*vel \cmark \\
-piraí & pi*ra-í \xmark & pi*ra*í \cmark \\
-psicodélico & p.si*co*dé*li*co \xmark & psi*co*dé*li*co \cmark \\
-psicotécnico & p.si*co*téc*ni*co \xmark & psi*co*téc*ni*co \cmark \\
-saíra & sa-í*ra \xmark & sa*í*ra \cmark \\
-sobressair & so*bres*sa-ir \xmark & so*bres*sa*ir \cmark \\
-subliminar & su.b-li*mi*nar \xmark & sub*li*mi*nar \cmark \\
-ajuizado & a*ju-i*za*do \xmark & a*ju*i*za*do \cmark \\
-antipoluição & an*ti*po*lu-i*ção \xmark & an*ti*po*lu*i*ção \cmark \\
-arquétipo & ar-qué*ti*po \xmark & ar*qué*ti*po \cmark \\
-dadaísmo & da*da-ís*mo \xmark & da*da*ís*mo \cmark \\
-descontrair & des*con*tra-ir \xmark & des*con*tra*ir \cmark \\
-gasômetro & ga-sô*me*tro \xmark & ga*sô*me*tro \cmark \\
-hidroviário & hi*dro*vi-á*ri*o \xmark & hi*dro*vi*á*ri*o \cmark \\
-inegociável & i*ne*go*ci-á*vel \xmark & i*ne*go*ci*á*vel \cmark \\
-maiúscula & mai-ús*cu*la \xmark & mai*ús*cu*la \cmark \\
-miúdas & mi-ú*das \xmark & mi*ú*das \cmark \\
-perequê & pe*re-quê \xmark & pe*re*quê \cmark \\
-recôncavo & re-côn*ca*vo \xmark & re*côn*ca*vo \cmark \\
-saquê & sa-quê \xmark & sa*quê \cmark \\
-ancião & an*ci-ão \xmark & an*ci*ão \cmark \\
-bafômetro & ba-fô*me*tro \xmark & ba*fô*me*tro \cmark \\
-bongô & bon-gô \xmark & bon*gô \cmark \\
-ciberespaço & ci*be.r-es*pa*ço \xmark & ci*be.r-es*pa*ço \xmark \\
-condômino & con-dô*mi*no \xmark & con*dô*mi*no \cmark \\
-dadaísta & da*da-ís*ta \xmark & da*da*ís*ta \cmark \\
-freático & fre-á*ti*co \xmark & fre*á*ti*co \cmark \\
-hipocondríaco & hi*po*con*drí-a*co \xmark & hi*po*con*drí*a*co \cmark \\
-indaiá & in*dai-á \xmark & in*dai*á \cmark \\
-jacuí & ja*cu-í \xmark & ja*cu*í \cmark \\
-maleável & ma*le-á*vel \xmark & ma*le*á*vel \cmark \\
-ministeriável & mi*nis*te*ri-á*vel \xmark & mi*nis*te*ri*á*vel \cmark \\
-obituário & o*bi*tu-á*ri*o \xmark & o*bi*tu*á*ri*o \cmark \\
-picuinha & pi*cu-i*nha \xmark & pi*cu-i*nha \xmark \\
-platô & pla-tô \xmark & pla*tô \cmark \\
-possuidor & pos*su-i*dor \xmark & pos*su*i*dor \cmark \\
-psicodelismo & p.si*co*de*lis*mo \xmark & psi*co*de*lis*mo \cmark \\
-reinserção & re-in*ser*ção \xmark & re*in*ser*ção \cmark \\
-suingue & su-in*gue \xmark & su-in*gue \xmark \\
-triunfalista & tri-un*fa*lis*ta \xmark & tri*un*fa*lis*ta \cmark \\
-varíola & va*rí-o*la \xmark & va*rí*o*la \cmark \\
-apoteótico & a*po*te-ó*ti*co \xmark & a*po*te*ó*ti*co \cmark \\
-bainha & ba-i*nha \xmark & ba*i*nha \cmark \\
-bibliófilo & bi*bli-ó*fi*lo \xmark & bi*bli*ó*fi*lo \cmark \\
-caimento & ca-i*men*to \xmark & ca-i*men*to \xmark \\
-cambuí & cam*bu-í \xmark & cam*bu*í \cmark \\
-cauim & cau-im \xmark & cau-im \xmark \\
-darwinismo & dar-wi*nis*mo \xmark & dar-wi*nis*mo \xmark \\
-eclesiástico & e*cle*si-ás*ti*co \xmark & e*cle*si*ás*ti*co \cmark \\
-estuário & es*tu-á*ri*o \xmark & es*tu*á*ri*o \cmark \\
-gigolô & gi*go-lô \xmark & gi*go*lô \cmark \\
-imbuído & im*bu-í*do \xmark & im*bu*í*do \cmark \\
-bastião & bas*ti-ão \xmark & bas*ti*ão \cmark \\
-caíque & ca-í*que \xmark & ca*í*que \cmark \\
-coincidente & co-in*ci*den*te \xmark & co*in*ci*den*te \cmark \\
-flúor & flú-or \xmark & flú-or \xmark \\
-incongruência & in*con*gru-ên*ci*a \xmark & in*con*gru*ên*ci*a \cmark \\
-indissociável & in*dis*so*ci-á*vel \xmark & in*dis*so*ci*á*vel \cmark \\
-invariável & in*va*ri-á*vel \xmark & in*va*ri*á*vel \cmark \\
-mostruário & mos*tru-á*ri*o \xmark & mos*tru*á*ri*o \cmark \\
-néon & né-on \xmark & né*on \cmark \\
-oboé & o*bo-é \xmark & o*bo*é \cmark \\
-oceânico & o*ce-â*ni*co \xmark & o*ce*â*ni*co \cmark \\
-panteísmo & pan*te-ís*mo \xmark & pan*te*ís*mo \cmark \\
-platônico & pla-tô*ni*co \xmark & pla*tô*ni*co \cmark \\
-pneumologia & p.neu*mo*lo*gi*a \xmark & pneu*mo*lo*gi*a \cmark \\
-proibitivo & pro-i*bi*ti*vo \xmark & pro*i*bi*ti*vo \cmark \\
-raquítico & ra-quí*ti*co \xmark & ra*quí*ti*co \cmark \\
-reinterpretação & re-in*ter*pre*ta*ção \xmark & re*in*ter*pre*ta*ção \cmark \\
-subtraído & sub*tra-í*do \xmark & sub*tra*í*do \cmark \\
-suinocultura & su-i*no*cul*tu*ra \xmark & su*i*no*cul*tu*ra \cmark \\
+suíça & su-í*ça \xmark & su*í*ça \cmark \\
+suíço & su-í*ço \xmark & su*í*ço \cmark \\
+suingue & su-in*gue \xmark & su*in*gue \cmark \\
+suíno & su-í*no \xmark & su*í*no \cmark \\
+suíte & su-í*te \xmark & su*í*te \cmark \\
 sumô & su-mô \xmark & su*mô \cmark \\
-tainha & ta-i*nha \xmark & ta*i*nha \cmark \\
-acordeão & a*cor*de-ão \xmark & a*cor*de*ão \cmark \\
-aético & a-é*ti*co \xmark & a*é*ti*co \cmark \\
-baiuca & bai-u*ca \xmark & bai-u*ca \xmark \\
-centurião & cen*tu*ri-ão \xmark & cen*tu*ri*ão \cmark \\
-comediógrafo & co*me*di-ó*gra*fo \xmark & co*me*di*ó*gra*fo \cmark \\
-conduíte & con*du-í*te \xmark & con*du*í*te \cmark \\
-coroinha & co*ro-i*nha \xmark & co*ro*i*nha \cmark \\
-ergonômico & er*go-nô*mi*co \xmark & er*go*nô*mi*co \cmark \\
-gaélico & ga-é*li*co \xmark & ga*é*li*co \cmark \\
-grandiloquência & gran*di*lo-quên*ci*a \xmark & gran*di*lo*quên*ci*a \cmark \\
-impatriótico & im*pa*tri-ó*ti*co \xmark & im*pa*tri*ó*ti*co \cmark \\
-megalômano & me*ga-lô*ma*no \xmark & me*ga*lô*ma*no \cmark \\
-miríade & mi*rí-a*de \xmark & mi*rí*a*de \cmark \\
-neófito & ne-ó*fi*to \xmark & ne*ó*fi*to \cmark \\
-nipônico & ni-pô*ni*co \xmark & ni*pô*ni*co \cmark \\
-obstruído & obs*tru-í*do \xmark & obs*tru*í*do \cmark \\
-pecuniário & pe*cu*ni-á*ri*o \xmark & pe*cu*ni*á*ri*o \cmark \\
-psicopatologia & p.si*co*pa*to*lo*gi*a \xmark & psi*co*pa*to*lo*gi*a \cmark \\
-reindexar & re-in*de*xar \xmark & re-in*de*xar \xmark \\
-reinstalar & re-ins*ta*lar \xmark & re*ins*ta*lar \cmark \\
-reintroduzir & re-in*tro*du*zir \xmark & re*in*tro*du*zir \cmark \\
-teleinformática & te*le-in*for*má*ti*ca \xmark & te*le*in*for*má*ti*ca \cmark \\
-timbaúba & tim*ba-ú*ba \xmark & tim*ba*ú*ba \cmark \\
-agônico & a-gô*ni*co \xmark & a*gô*ni*co \cmark \\
-anatômico & a*na-tô*mi*co \xmark & a*na*tô*mi*co \cmark \\
-anômalo & a-nô*ma*lo \xmark & a*nô*ma*lo \cmark \\
-ataúde & a*ta-ú*de \xmark & a*ta*ú*de \cmark \\
-auê & au-ê \xmark & au*ê \cmark \\
-bestiário & bes*ti-á*ri*o \xmark & bes*ti*á*ri*o \cmark \\
-boá & bo-á \xmark & bo*á \cmark \\
-copião & co*pi-ão \xmark & co*pi*ão \cmark \\
-ensaística & en*sa-ís*ti*ca \xmark & en*sa*ís*ti*ca \cmark \\
-fonoaudiólogo & fo*no*au*di-ó*lo*go \xmark & fo*no*au*di*ó*lo*go \cmark \\
-imiscuir & i*mis*cu-ir \xmark & i*mis*cu-ir \xmark \\
-jupiá & ju*pi-á \xmark & ju*pi*á \cmark \\
-monoteísmo & mo*no*te-ís*mo \xmark & mo*no*te*ís*mo \cmark \\
-nagô & na-gô \xmark & na*gô \cmark \\
-psicofarmacologia & p.si*co*far*ma*co*lo*gi*a \xmark & psi*co*far*ma*co*lo*gi*a \cmark \\
-psicologismo & p.si*co*lo*gis*mo \xmark & psi*co*lo*gis*mo \cmark \\
-ruindade & ru-in*da*de \xmark & ru-in*da*de \xmark \\
-sanduicheria & san*du-i*che*ri*a \xmark & san*du*i*che*ri*a \cmark \\
-sociável & so*ci-á*vel \xmark & so*ci*á*vel \cmark \\
-sublevação & su.b-le*va*ção \xmark & sub*le*va*ção \cmark \\
-abstrair & abs*tra-ir \xmark & abs*tra*ir \cmark \\
-alaúde & a*la-ú*de \xmark & a*la*ú*de \cmark \\
-almôndega & al-môn*de*ga \xmark & al*môn*de*ga \cmark \\
-antiaéreo & an*ti*a-é*re*o \xmark & an*ti*a*é*re*o \cmark \\
-atrabiliário & a*tra*bi*li-á*ri*o \xmark & a*tra*bi*li*á*ri*o \cmark \\
-bangalô & ban*ga-lô \xmark & ban*ga*lô \cmark \\
-bôer & bô-er \xmark & bô-er \xmark \\
-breviário & bre*vi-á*ri*o \xmark & bre*vi*á*ri*o \cmark \\
-canônico & ca-nô*ni*co \xmark & ca*nô*ni*co \cmark \\
-carnaúba & car*na-ú*ba \xmark & car*na*ú*ba \cmark \\
-doído & do-í*do \xmark & do*í*do \cmark \\
-ensaísmo & en*sa-ís*mo \xmark & en*sa*ís*mo \cmark \\
-esfiha & es*fi-ha \xmark & es*fi-ha \xmark \\
-graúna & gra-ú*na \xmark & gra*ú*na \cmark \\
-hemodiálise & he*mo*di-á*li*se \xmark & he*mo*di*á*li*se \cmark \\
-hinduísmo & hin*du-ís*mo \xmark & hin*du*ís*mo \cmark \\
-influído & in*flu-í*do \xmark & in*flu-í*do \xmark \\
-intuir & in*tu-ir \xmark & in*tu*ir \cmark \\
-latifundiário & la*ti*fun*di-á*ri*o \xmark & la*ti*fun*di*á*ri*o \cmark \\
-mimeógrafo & mi*me-ó*gra*fo \xmark & mi*me*ó*gra*fo \cmark \\
-pajeú & pa*je-ú \xmark & pa*je*ú \cmark \\
-prosaísmo & pro*sa-ís*mo \xmark & pro*sa*ís*mo \cmark \\
-psicodrama & p.si*co*dra*ma \xmark & psi*co*dra*ma \cmark \\
-psicopedagogia & p.si*co*pe*da*go*gi*a \xmark & psi*co*pe*da*go*gi*a \cmark \\
-quinquênio & quin-quê*ni*o \xmark & quin*quê*ni*o \cmark \\
-radiofrequência & ra*di*o*fre-quên*ci*a \xmark & ra*di*o*fre*quên*ci*a \cmark \\
-reinstituir & re-ins*ti*tu-ir \xmark & re*ins*ti*tu*ir \cmark \\
 supercampeão & su*per*cam*pe-ão \xmark & su*per*cam*pe*ão \cmark \\
 supersônico & su*per-sô*ni*co \xmark & su*per*sô*ni*co \cmark \\
-tragicômico & tra*gi-cô*mi*co \xmark & tra*gi*cô*mi*co \cmark \\
-tríade & trí-a*de \xmark & trí*a*de \cmark \\
-vacuidade & va*cu-i*da*de \xmark & va*cu*i*da*de \cmark \\
-agogô & a*go-gô \xmark & a*go*gô \cmark \\
-altruísta & al*tru-ís*ta \xmark & al*tru*ís*ta \cmark \\
-antiácido & an*ti-á*ci*do \xmark & an*ti*á*ci*do \cmark \\
-autobiógrafo & au*to*bi-ó*gra*fo \xmark & au*to*bi*ó*gra*fo \cmark \\
-beduíno & be*du-í*no \xmark & be*du*í*no \cmark \\
-bordô & bor-dô \xmark & bor*dô \cmark \\
-casuístico & ca*su-ís*ti*co \xmark & ca*su*ís*ti*co \cmark \\
-czarina & c.za*ri*na \xmark & cza*ri*na \cmark \\
-demoníaco & de*mo*ní-a*co \xmark & de*mo*ní*a*co \cmark \\
-desconstruir & des*cons*tru-ir \xmark & des*cons*tru*ir \cmark \\
-ergômetro & er-gô*me*tro \xmark & er*gô*me*tro \cmark \\
-evoé & e*vo-é \xmark & e*vo*é \cmark \\
-graúdo & gra-ú*do \xmark & gra*ú*do \cmark \\
-iídiche & i-í*di*che \xmark & i*í*di*che \cmark \\
-impronunciável & im*pro*nun*ci-á*vel \xmark & im*pro*nun*ci*á*vel \cmark \\
-influenciável & in*flu*en*ci-á*vel \xmark & in*flu*en*ci*á*vel \cmark \\
-irrefreável & ir*re*fre-á*vel \xmark & ir*re*fre*á*vel \cmark \\
-irretorquível & ir*re*tor-quí*vel \xmark & ir*re*tor*quí*vel \cmark \\
-jataí & ja*ta-í \xmark & ja*ta*í \cmark \\
-juquiá & ju*qui-á \xmark & ju*qui*á \cmark \\
-painho & pa-i*nho \xmark & pa*i*nho \cmark \\
-pindaíba & pin*da-í*ba \xmark & pin*da*í*ba \cmark \\
-pneumologista & p.neu*mo*lo*gis*ta \xmark & pneu*mo*lo*gis*ta \cmark \\
-porciúncula & por*ci-ún*cu*la \xmark & por*ci*ún*cu*la \cmark \\
-prolegômenos & pro*le-gô*me*nos \xmark & pro*le*gô*me*nos \cmark \\
-psiquismo & p.si*quis*mo \xmark & psi*quis*mo \cmark \\
-quiproquó & qui*pro-quó \xmark & qui*pro*quó \cmark \\
-refluir & re*flu-ir \xmark & re*flu*ir \cmark \\
-reimplantar & re-im*plan*tar \xmark & re*im*plan*tar \cmark \\
-reurbanizar & re-ur*ba*ni*zar \xmark & re-ur*ba*ni*zar \xmark \\
-reutilizar & re-u*ti*li*zar \xmark & re-u*ti*li*zar \xmark \\
-sainte & sa-in*te \xmark & sa-in*te \xmark \\
-tsunami & t.su*na*mi \xmark & tsu*na*mi \cmark \\
-usucapião & u*su*ca*pi-ão \xmark & u*su*ca*pi*ão \cmark \\
-zebuíno & ze*bu-í*no \xmark & ze*bu*í*no \cmark \\
-aeroportuário & a*e*ro*por*tu-á*ri*o \xmark & a*e*ro*por*tu*á*ri*o \cmark \\
-agroquímica & a*gro-quí*mi*ca \xmark & a*gro*quí*mi*ca \cmark \\
-ajuizar & a*ju-i*zar \xmark & a*ju*i*zar \cmark \\
-baraúna & ba*ra-ú*na \xmark & ba*ra*ú*na \cmark \\
-casuísta & ca*su-ís*ta \xmark & ca*su*ís*ta \cmark \\
-catatônico & ca*ta-tô*ni*co \xmark & ca*ta*tô*ni*co \cmark \\
-conteudista & con*te-u*dis*ta \xmark & con*te-u*dis*ta \xmark \\
-continuísta & con*ti*nu-ís*ta \xmark & con*ti*nu*ís*ta \cmark \\
-czarista & c.za*ris*ta \xmark & cza*ris*ta \cmark \\
-decair & de*ca-ir \xmark & de*ca*ir \cmark \\
-deísta & de-ís*ta \xmark & de*ís*ta \cmark \\
-diácono & di-á*co*no \xmark & di*á*co*no \cmark \\
-elegíaco & e*le*gí-a*co \xmark & e*le*gí*a*co \cmark \\
-faraônico & fa*ra-ô*ni*co \xmark & fa*ra*ô*ni*co \cmark \\
-feérico & fe-é*ri*co \xmark & fe*é*ri*co \cmark \\
-hidroavião & hi*dro*a*vi-ão \xmark & hi*dro*a*vi*ão \cmark \\
-hodômetro & ho-dô*me*tro \xmark & ho*dô*me*tro \cmark \\
-inconciliável & in*con*ci*li-á*vel \xmark & in*con*ci*li*á*vel \cmark \\
-ioiô & i.o-i.ô \xmark & i.o-i.ô \xmark \\
-macrobiótica & ma*cro*bi-ó*ti*ca \xmark & ma*cro*bi*ó*ti*ca \cmark \\
-marruá & mar*ru-á \xmark & mar*ru*á \cmark \\
-meteórico & me*te-ó*ri*co \xmark & me*te*ó*ri*co \cmark \\
-panteísta & pan*te-ís*ta \xmark & pan*te*ís*ta \cmark \\
-papaína & pa*pa-í*na \xmark & pa*pa*í*na \cmark \\
-patuá & pa*tu-á \xmark & pa*tu*á \cmark \\
-perdoável & per*do-á*vel \xmark & per*do*á*vel \cmark \\
-prostituído & pros*ti*tu-í*do \xmark & pros*ti*tu*í*do \cmark \\
-pulôver & pu-lô*ver \xmark & pu*lô*ver \cmark \\
-ravióli & ra*vi-ó*li \xmark & ra*vi*ó*li \cmark \\
-reincorporação & re-in*cor*po*ra*ção \xmark & re*in*cor*po*ra*ção \cmark \\
-reingresso & re-in*gres*so \xmark & re*in*gres*so \cmark \\
-reinquirir & re-in*qui*rir \xmark & re-in*qui*rir \xmark \\
-reinstalação & re-ins*ta*la*ção \xmark & re*ins*ta*la*ção \cmark \\
-reinterpretar & re-in*ter*pre*tar \xmark & re*in*ter*pre*tar \cmark \\
-saião & sai-ão \xmark & sai*ão \cmark \\
-samaúma & sa*ma-ú*ma \xmark & sa*ma*ú*ma \cmark \\
-sublocação & su.b-lo*ca*ção \xmark & sub*lo*ca*ção \cmark \\
-turboélice & tur*bo-é*li*ce \xmark & tur*bo*é*li*ce \cmark \\
-ventoinha & ven*to-i*nha \xmark & ven*to*i*nha \cmark \\
-voyeurista & voy-eu*ris*ta \xmark & voy-eu*ris*ta \xmark \\
-alagoinha & a*la*go-i*nha \xmark & a*la*go*i*nha \cmark \\
-aluvião & a*lu*vi-ão \xmark & a*lu*vi*ão \cmark \\
-amiúde & a*mi-ú*de \xmark & a*mi*ú*de \cmark \\
-amoníaco & a*mo*ní-a*co \xmark & a*mo*ní*a*co \cmark \\
-antagônico & an*ta-gô*ni*co \xmark & an*ta*gô*ni*co \cmark \\
-antiquíssimo & an*ti-quís*si*mo \xmark & an*ti*quís*si*mo \cmark \\
-babuíno & ba*bu-í*no \xmark & ba*bu*í*no \cmark \\
-bahamense & ba-ha*men*se \xmark & ba-ha*men*se \xmark \\
-barômetro & ba-rô*me*tro \xmark & ba*rô*me*tro \cmark \\
-bibelô & bi*be-lô \xmark & bi*be*lô \cmark \\
-biótipo & bi-ó*ti*po \xmark & bi*ó*ti*po \cmark \\
-bisavô & bi*sa-vô \xmark & bi*sa*vô \cmark \\
-bocaiuva & bo*cai-u*va \xmark & bo*cai-u*va \xmark \\
-borderô & bor*de-rô \xmark & bor*de*rô \cmark \\
-brechtiano & bre.ch*ti*a*no \xmark & bre.ch*ti*a*no \xmark \\
-cariótipo & ca*ri-ó*ti*po \xmark & ca*ri*ó*ti*po \cmark \\
-chororô & cho*ro-rô \xmark & cho*ro*rô \cmark \\
-copaíba & co*pa-í*ba \xmark & co*pa*í*ba \cmark \\
-czarismo & c.za*ris*mo \xmark & cza*ris*mo \cmark \\
-darwinista & dar-wi*nis*ta \xmark & dar-wi*nis*ta \xmark \\
-decaída & de*ca-í*da \xmark & de*ca*í*da \cmark \\
-diálise & di-á*li*se \xmark & di*á*li*se \cmark \\
-diástole & di-ás*to*le \xmark & di*ás*to*le \cmark \\
-esquálido & es-quá*li*do \xmark & es*quá*li*do \cmark \\
-esvair & es*va-ir \xmark & es*va*ir \cmark \\
-farisaísmo & fa*ri*sa-ís*mo \xmark & fa*ri*sa*ís*mo \cmark \\
-fiduciário & fi*du*ci-á*ri*o \xmark & fi*du*ci*á*ri*o \cmark \\
-filarmônico & fi*lar-mô*ni*co \xmark & fi*lar*mô*ni*co \cmark \\
-financiável & fi*nan*ci-á*vel \xmark & fi*nan*ci*á*vel \cmark \\
-fruir & fru-ir \xmark & fru*ir \cmark \\
-fuzuê & fu*zu-ê \xmark & fu*zu*ê \cmark \\
-geômetra & ge-ô*me*tra \xmark & ge*ô*me*tra \cmark \\
-gnose & g.no*se \xmark & gno*se \cmark \\
-jabô & ja-bô \xmark & ja*bô \cmark \\
-janaúba & ja*na-ú*ba \xmark & ja*na*ú*ba \cmark \\
-lusíada & lu*sí-a*da \xmark & lu*sí*a*da \cmark \\
-maçônico & ma-çô*ni*co \xmark & ma*çô*ni*co \cmark \\
-macrobiótico & ma*cro*bi-ó*ti*co \xmark & ma*cro*bi*ó*ti*co \cmark \\
-mafuá & ma*fu-á \xmark & ma*fu*á \cmark \\
-manômetro & ma-nô*me*tro \xmark & ma*nô*me*tro \cmark \\
-mediúnico & me*di-ú*ni*co \xmark & me*di*ú*ni*co \cmark \\
-microrregião & mi*cror*re*gi-ão \xmark & mi*cror*re*gi*ão \cmark \\
-neoplatônico & ne*o*pla-tô*ni*co \xmark & ne*o*pla*tô*ni*co \cmark \\
-patchuli & pat*chu*li \cmark & pat-chu*li \xmark \\
-pecuário & pe*cu-á*ri*o \xmark & pe*cu*á*ri*o \cmark \\
-psicolinguista & p.si*co*lin*guis*ta \xmark & psi*co*lin*guis*ta \cmark \\
-psicolinguística & p.si*co*lin*guís*ti*ca \xmark & psi*co*lin*guís*ti*ca \cmark \\
-psicomotor & p.si*co*mo*tor \xmark & psi*co*mo*tor \cmark \\
-psicomotricista & p.si*co*mo*tri*cis*ta \xmark & psi*co*mo*tri*cis*ta \cmark \\
-psicopatia & p.si*co*pa*ti*a \xmark & psi*co*pa*ti*a \cmark \\
-psicopedagogo & p.si*co*pe*da*go*go \xmark & psi*co*pe*da*go*go \cmark \\
-psicossomática & p.si*cos*so*má*ti*ca \xmark & psi*cos*so*má*ti*ca \cmark \\
-reconstituinte & re*cons*ti*tu-in*te \xmark & re*cons*ti*tu-in*te \xmark \\
-reincidir & re-in*ci*dir \xmark & re*in*ci*dir \cmark \\
-saruê & sa*ru-ê \xmark & sa*ru*ê \cmark \\
-subaquático & su*ba-quá*ti*co \xmark & su*ba*quá*ti*co \cmark \\
-subliteratura & su.b-li*te*ra*tu*ra \xmark & sub*li*te*ra*tu*ra \cmark \\
-subsidiário & sub*si*di-á*ri*o \xmark & sub*si*di*á*ri*o \cmark \\
-substituível & subs*ti*tu-í*vel \xmark & subs*ti*tu*í*vel \cmark \\
+tabelião & ta*be*li-ão \xmark & ta*be*li*ão \cmark \\
+tabuão & ta*bu-ão \xmark & ta*bu*ão \cmark \\
+tacômetro & ta-cô*me*tro \xmark & ta*cô*me*tro \cmark \\
+tainha & ta-i*nha \xmark & ta*i*nha \cmark \\
+taiwanês & tai-wa*nês \xmark & tai-wa*nês \xmark \\
+talião & ta*li-ão \xmark & ta*li*ão \cmark \\
+taquígrafo & ta-quí*gra*fo \xmark & ta*quí*gra*fo \cmark \\
+taquímetro & ta-quí*me*tro \xmark & ta*quí*me*tro \cmark \\
+tarô & ta-rô \xmark & ta*rô \cmark \\
+tataravô & ta*ta*ra-vô \xmark & ta*ta*ra*vô \cmark \\
+taxonômico & ta*xo-nô*mi*co \xmark & ta*xo*nô*mi*co \cmark \\
+tcheco & t.che*co \xmark & tche*co \cmark \\
+teísmo & te-ís*mo \xmark & te*ís*mo \cmark \\
+teísta & te-ís*ta \xmark & te*ís*ta \cmark \\
+telefônico & te*le-fô*ni*co \xmark & te*le*fô*ni*co \cmark \\
+teníase & te*ní-a*se \xmark & te*ní*a*se \cmark \\
+teófobo & te-ó*fo*bo \xmark & te*ó*fo*bo \cmark \\
+teólogo & te-ó*lo*go \xmark & te*ó*lo*go \cmark \\
+teônimo & te-ô*ni*mo \xmark & te*ô*ni*mo \cmark \\
+teórica & te-ó*ri*ca \xmark & te*ó*ri*ca \cmark \\
+teórico & te-ó*ri*co \xmark & te*ó*ri*co \cmark \\
+termômetro & ter-mô*me*tro \xmark & ter*mô*me*tro \cmark \\
+termoquímica & ter*mo-quí*mi*ca \xmark & ter*mo*quí*mi*ca \cmark \\
+termoquímico & ter*mo-quí*mi*co \xmark & ter*mo*quí*mi*co \cmark \\
+tetracampeão & te*tra*cam*pe-ão \xmark & te*tra*cam*pe*ão \cmark \\
+tetraédrico & te*tra-é*dri*co \xmark & te*tra*é*dri*co \cmark \\
+tetravô & te*tra-vô \xmark & te*tra*vô \cmark \\
+teúrgico & te-úr*gi*co \xmark & te*úr*gi*co \cmark \\
 teutônico & teu-tô*ni*co \xmark & teu*tô*ni*co \cmark \\
@@
 toboágua & to*bo-á*gua \xmark & to*bo*á*gua \cmark \\
-aldeão & al*de-ão \xmark & al*de*ão \cmark \\
-amniocentese & am*ni*o*cen*te*se \cmark & a.m-ni*o*cen*te*se \xmark \\
-anamnese & a*nam*ne*se \cmark & a*na.m-ne*se \xmark \\
-anauê & a*nau-ê \xmark & a*nau*ê \cmark \\
-antipatriótico & an*ti*pa*tri-ó*ti*co \xmark & an*ti*pa*tri*ó*ti*co \cmark \\
-antônimo & an-tô*ni*mo \xmark & an*tô*ni*mo \cmark \\
-antropônimo & an*tro-pô*ni*mo \xmark & an*tro*pô*ni*mo \cmark \\
-aviário & a*vi-á*ri*o \xmark & a*vi*á*ri*o \cmark \\
-babalaô & ba*ba*la-ô \xmark & ba*ba*la*ô \cmark \\
-braúna & bra-ú*na \xmark & bra*ú*na \cmark \\
-corruíra & cor*ru-í*ra \xmark & cor*ru*í*ra \cmark \\
-corrupião & cor*ru*pi-ão \xmark & cor*ru*pi*ão \cmark \\
-decaído & de*ca-í*do \xmark & de*ca*í*do \cmark \\
-deificação & de-i*fi*ca*ção \xmark & de-i*fi*ca*ção \xmark \\
-demiurgo & de*mi-ur*go \xmark & de*mi*ur*go \cmark \\
-descair & des*ca-ir \xmark & des*ca*ir \cmark \\
-desembainhar & de*sem*ba-i*nhar \xmark & de*sem*ba*i*nhar \cmark \\
-diáfano & di-á*fa*no \xmark & di*á*fa*no \cmark \\
-dicotômico & di*co-tô*mi*co \xmark & di*co*tô*mi*co \cmark \\
-dodecafônico & do*de*ca-fô*ni*co \xmark & do*de*ca*fô*ni*co \cmark \\
-ensaístico & en*sa-ís*ti*co \xmark & en*sa*ís*ti*co \cmark \\
-entusiástico & en*tu*si-ás*ti*co \xmark & en*tu*si*ás*ti*co \cmark \\
-epônimo & e-pô*ni*mo \xmark & e*pô*ni*mo \cmark \\
-espectrofotômetro & es*pec*tro*fo-tô*me*tro \xmark & es*pec*tro*fo*tô*me*tro \cmark \\
-estatuária & es*ta*tu-á*ri*a \xmark & es*ta*tu*á*ri*a \cmark \\
-faim & fa-im \xmark & fa-im \xmark \\
-fitoquímica & fi*to-quí*mi*ca \xmark & fi*to*quí*mi*ca \cmark \\
-formaldeído & for*mal*de-í*do \xmark & for*mal*de*í*do \cmark \\
-fuinha & fu-i*nha \xmark & fu*i*nha \cmark \\
-gabião & ga*bi-ão \xmark & ga*bi*ão \cmark \\
-gauchada & ga-u*cha*da \xmark & ga-u*cha*da \xmark \\
-gauchismo & ga-u*chis*mo \xmark & ga-u*chis*mo \xmark \\
-geriátrico & ge*ri-á*tri*co \xmark & ge*ri*á*tri*co \cmark \\
-gipsita & gip*si*ta \cmark & gip-si*ta \xmark \\
-guião & gui-ão \xmark & gui*ão \cmark \\
-ilíaco & i*lí-a*co \xmark & i*lí*a*co \cmark \\
-iniciático & i*ni*ci-á*ti*co \xmark & i*ni*ci*á*ti*co \cmark \\
-itapuá & i*ta*pu-á \xmark & i*ta*pu*á \cmark \\
-japuí & ja*pu-í \xmark & ja*pu*í \cmark \\
-jesuítico & je*su-í*ti*co \xmark & je*su*í*ti*co \cmark \\
-lamaísmo & la*ma-ís*mo \xmark & la*ma*ís*mo \cmark \\
-mantô & man-tô \xmark & man*tô \cmark \\
-metapsicologia & me*tap*si*co*lo*gi*a \cmark & me*tap-si*co*lo*gi*a \xmark \\
-mitocôndria & mi*to-côn*dri*a \xmark & mi*to*côn*dri*a \cmark \\
-miudeza & mi-u*de*za \xmark & mi-u*de*za \xmark \\
-monomaníaco & mo*no*ma*ní-a*co \xmark & mo*no*ma*ní*a*co \cmark \\
-museólogo & mu*se-ó*lo*go \xmark & mu*se*ó*lo*go \cmark \\
-ninfomaníaca & nin*fo*ma*ní-a*ca \xmark & nin*fo*ma*ní*a*ca \cmark \\
-nobiliárquico & no*bi*li-ár*qui*co \xmark & no*bi*li*ár*qui*co \cmark \\
-odômetro & o-dô*me*tro \xmark & o*dô*me*tro \cmark \\
-orgiástico & or*gi-ás*ti*co \xmark & or*gi*ás*ti*co \cmark \\
-painço & pa-in*ço \xmark & pa-in*ço \xmark \\
-pantagruélico & pan*ta*gru-é*li*co \xmark & pan*ta*gru*é*li*co \cmark \\
-parquímetro & par-quí*me*tro \xmark & par*quí*me*tro \cmark \\
-pixaim & pi*xa-im \xmark & pi*xa-im \xmark \\
-pneumática & p.neu*má*ti*ca \xmark & pneu*má*ti*ca \cmark \\
-pneumático & p.neu*má*ti*co \xmark & pneu*má*ti*co \cmark \\
-preá & pre-á \xmark & pre*á \cmark \\
-priápico & pri-á*pi*co \xmark & pri*á*pi*co \cmark \\
-psicopedagógico & p.si*co*pe*da*gó*gi*co \xmark & psi*co*pe*da*gó*gi*co \cmark \\
-psicossomático & p.si*cos*so*má*ti*co \xmark & psi*cos*so*má*ti*co \cmark \\
-psicotrópico & p.si*co*tró*pi*co \xmark & psi*co*tró*pi*co \cmark \\
-pterossauro & p.te*ros*sau*ro \xmark & pte*ros*sau*ro \cmark \\
-quilohertz & qui*lo-hertz \xmark & qui*lo-hertz \xmark \\
-recôndito & re-côn*di*to \xmark & re*côn*di*to \cmark \\
-reimplantação & re-im*plan*ta*ção \xmark & re*im*plan*ta*ção \cmark \\
-reincorporar & re-in*cor*po*rar \xmark & re*in*cor*po*rar \cmark \\
-reingressar & re-in*gres*sar \xmark & re*in*gres*sar \cmark \\
-reinvestir & re-in*ves*tir \xmark & re*in*ves*tir \cmark \\
-restituível & res*ti*tu-í*vel \xmark & res*ti*tu*í*vel \cmark \\
-retrair & re*tra-ir \xmark & re*tra*ir \cmark \\
-rodamoinho & ro*da*mo-i*nho \xmark & ro*da*mo*i*nho \cmark \\
-roído & ro-í*do \xmark & ro*í*do \cmark \\
-ruão & ru-ão \xmark & ru*ão \cmark \\
-salomônico & sa*lo-mô*ni*co \xmark & sa*lo*mô*ni*co \cmark \\
-sardônico & sar-dô*ni*co \xmark & sar*dô*ni*co \cmark \\
-semiólogo & se*mi-ó*lo*go \xmark & se*mi*ó*lo*go \cmark \\
-solipsismo & so*lip*sis*mo \cmark & so*lip-sis*mo \xmark \\
-sumaúma & su*ma-ú*ma \xmark & su*ma*ú*ma \cmark \\
-tataravô & ta*ta*ra-vô \xmark & ta*ta*ra*vô \cmark \\
-termoquímica & ter*mo-quí*mi*ca \xmark & ter*mo*quí*mi*ca \cmark \\
 topônimo & to-pô*ni*mo \xmark & to*pô*ni*mo \cmark \\
+torquês & tor-quês \xmark & tor*quês \cmark \\
+torreão & tor*re-ão \xmark & tor*re*ão \cmark \\
 toxicômano & to*xi-cô*ma*no \xmark & to*xi*cô*ma*no \cmark \\
+tragediógrafo & tra*ge*di-ó*gra*fo \xmark & tra*ge*di*ó*gra*fo \cmark \\
+traído & tra-í*do \xmark & tra*í*do \cmark \\
+traíra & tra-í*ra \xmark & tra*í*ra \cmark \\
+trair & tra-ir \xmark & tra*ir \cmark \\
+transeunte & tran*se-un*te \xmark & tran*se-un*te \xmark \\
+transoceânico & tran*so*ce-â*ni*co \xmark & tran*so*ce*â*ni*co \cmark \\
+tríade & trí-a*de \xmark & trí*a*de \cmark \\
+tricampeão & tri*cam*pe-ão \xmark & tri*cam*pe*ão \cmark \\
+tricô & tri-cô \xmark & tri*cô \cmark \\
+tripanossomíase & tri*pa*nos*so*mí-a*se \xmark & tri*pa*nos*so*mí*a*se \cmark \\
 trisavô & tri*sa-vô \xmark & tri*sa*vô \cmark \\
-triunvirato & tri-un*vi*ra*to \xmark & tri*un*vi*ra*to \cmark \\
+triunfador & tri-un*fa*dor \xmark & tri*un*fa*dor \cmark \\
+triunfalismo & tri-un*fa*lis*mo \xmark & tri*un*fa*lis*mo \cmark \\
+triunfalista & tri-un*fa*lis*ta \xmark & tri*un*fa*lis*ta \cmark \\
+triunfal & tri-un*fal \xmark & tri*un*fal \cmark \\
+triunfante & tri-un*fan*te \xmark & tri*un*fan*te \cmark \\
+triunfar & tri-un*far \xmark & tri*un*far \cmark \\
+triunfo & tri-un*fo \xmark & tri*un*fo \cmark \\
+triúnviro & tri-ún*vi*ro \xmark & tri*ún*vi*ro \cmark \\
+truísmo & tru-ís*mo \xmark & tru*ís*mo \cmark \\
+tuim & tu-im \xmark & tu*im \cmark \\
+tzarista & t.za*ris*ta \xmark & tza*ris*ta \cmark \\
+uísque & u-ís*que \xmark & u*ís*que \cmark \\
+uíste & u-ís*te \xmark & u*ís*te \cmark \\
+umbaúba & um*ba-ú*ba \xmark & um*ba*ú*ba \cmark \\
+união & u*ni-ão \xmark & u*ni*ão \cmark \\
+usucapião & u*su*ca*pi-ão \xmark & u*su*ca*pi*ão \cmark \\
+usufruir & u*su*fru-ir \xmark & u*su*fru*ir \cmark \\
+uveíte & u*ve-í*te \xmark & u*ve*í*te \cmark \\
+vacúolo & va*cú-o*lo \xmark & va*cú*o*lo \cmark \\
+variável & va*ri-á*vel \xmark & va*ri*á*vel \cmark \\
+varíola & va*rí-o*la \xmark & va*rí*o*la \cmark \\
+vascaíno & vas*ca-í*no \xmark & vas*ca*í*no \cmark \\
+veículo & ve-í*cu*lo \xmark & ve*í*cu*lo \cmark \\
+viável & vi-á*vel \xmark & vi*á*vel \cmark \\
+vibrião & vi*bri-ão \xmark & vi*bri*ão \cmark \\
+viés & vi-és \xmark & vi*és \cmark \\
+vitriólico & vi*tri-ó*li*co \xmark & vi*tri*ó*li*co \cmark \\
+viúva & vi-ú*va \xmark & vi*ú*va \cmark \\
+viúvo & vi-ú*vo \xmark & vi*ú*vo \cmark \\
+vovô & vo-vô \xmark & vo*vô \cmark \\
+voyeurismo & voy-eu*ris*mo \xmark & voy-eu*ris*mo \xmark \\
+voyeurista & voy-eu*ris*ta \xmark & voy-eu*ris*ta \xmark \\
 voyeurístico & voy-eu*rís*ti*co \xmark & voy-eu*rís*ti*co \xmark \\
+xilocaína & xi*lo*ca-í*na \xmark & xi*lo*ca*í*na \cmark \\
 xintoísmo & xin*to-ís*mo \xmark & xin*to*ís*mo \cmark \\
-absenteísta & ab*sen*te-ís*ta \xmark & ab*sen*te*ís*ta \cmark \\
-aeroviário & a*e*ro*vi-á*ri*o \xmark & a*e*ro*vi*á*ri*o \cmark \\
-afluir & a*flu-ir \xmark & a*flu*ir \cmark \\
-agroquímico & a*gro-quí*mi*co \xmark & a*gro*quí*mi*co \cmark \\
-aguaí & a*gua-í \xmark & a*gua*í \cmark \\
-alquímico & al-quí*mi*co \xmark & al*quí*mi*co \cmark \\
-amnesia & am*ne*si*a \cmark & a.m-ne*si*a \xmark \\
-amnésico & am*né*si*co \cmark & a.m-né*si*co \xmark \\
-anafrodisíaco & a*na*fro*di*sí-a*co \xmark & a*na*fro*di*sí*a*co \cmark \\
-antialcoólico & an*ti*al*co-ó*li*co \xmark & an*ti*al*co*ó*li*co \cmark \\
-antinômico & an*ti-nô*mi*co \xmark & an*ti*nô*mi*co \cmark \\
-anuir & a*nu-ir \xmark & a*nu*ir \cmark \\
-arapuá & a*ra*pu-á \xmark & a*ra*pu*á \cmark \\
-aríete & a*rí-e*te \xmark & a*rí-e*te \xmark \\
-associável & as*so*ci-á*vel \xmark & as*so*ci*á*vel \cmark \\
-atribuível & a*tri*bu-í*vel \xmark & a*tri*bu*í*vel \cmark \\
-babilônico & ba*bi-lô*ni*co \xmark & ba*bi*lô*ni*co \cmark \\
-balaustrada & ba*la-us*tra*da \xmark & ba*la-us*tra*da \xmark \\
-beócio & be-ó*ci*o \xmark & be*ó*ci*o \cmark \\
-biófilo & bi-ó*fi*lo \xmark & bi*ó*fi*lo \cmark \\
-biunívoco & bi-u*ní*vo*co \xmark & bi*u*ní*vo*co \cmark \\
-boião & boi-ão \xmark & boi*ão \cmark \\
-boiuna & boi-u*na \xmark & boi*u*na \cmark \\
-butiá & bu*ti-á \xmark & bu*ti*á \cmark \\
-caingangue & ca-in*gan*gue \xmark & ca-in*gan*gue \xmark \\
-carnaíba & car*na-í*ba \xmark & car*na*í*ba \cmark \\
-caúna & ca-ú*na \xmark & ca*ú*na \cmark \\
-ciática & ci-á*ti*ca \xmark & ci*á*ti*ca \cmark \\
-clepsidra & clep*si*dra \cmark & clep-si*dra \xmark \\
-codeína & co*de-í*na \xmark & co*de*í*na \cmark \\
-conciliábulo & con*ci*li-á*bu*lo \xmark & con*ci*li*á*bu*lo \cmark \\
-conciliável & con*ci*li-á*vel \xmark & con*ci*li*á*vel \cmark \\
-condoído & con*do-í*do \xmark & con*do*í*do \cmark \\
-confluir & con*flu-ir \xmark & con*flu*ir \cmark \\
-congruência & con*gru-ên*ci*a \xmark & con*gru*ên*ci*a \cmark \\
-crapô & cra-pô \xmark & cra*pô \cmark \\
-criptônimo & crip-tô*ni*mo \xmark & crip*tô*ni*mo \cmark \\
-deão & de-ão \xmark & de*ão \cmark \\
-decacampeão & de*ca*cam*pe-ão \xmark & de*ca*cam*pe*ão \cmark \\
-demiúrgico & de*mi-úr*gi*co \xmark & de*mi*úr*gi*co \cmark \\
-depreciável & de*pre*ci-á*vel \xmark & de*pre*ci*á*vel \cmark \\
-descaída & des*ca-í*da \xmark & des*ca*í*da \cmark \\
-dzeta & d.ze*ta \xmark & d.ze*ta \xmark \\
-elefantíase & e*le*fan*tí-a*se \xmark & e*le*fan*tí*a*se \cmark \\
-eletroímã & e*le*tro-í*mã \xmark & e*le*tro*í*mã \cmark \\
-eólico & e-ó*li*co \xmark & e*ó*li*co \cmark \\
-eólio & e-ó*li*o \xmark & e*ó*li*o \cmark \\
-epifenômeno & e*pi*fe-nô*me*no \xmark & e*pi*fe*nô*me*no \cmark \\
-escarabeídeo & es*ca*ra*be-í*de*o \xmark & es*ca*ra*be*í*de*o \cmark \\
-espadaúdo & es*pa*da-ú*do \xmark & es*pa*da*ú*do \cmark \\
-espeleólogo & es*pe*le-ó*lo*go \xmark & es*pe*le*ó*lo*go \cmark \\
-faiscante & fa-is*can*te \xmark & fa-is*can*te \xmark \\
-feiura & fei-u*ra \xmark & fei*u*ra \cmark \\
-fotômetro & fo-tô*me*tro \xmark & fo*tô*me*tro \cmark \\
-franqueável & fran*que-á*vel \xmark & fran*que*á*vel \cmark \\
-gastrointestinal & gas*tro-in*tes*ti*nal \xmark & gas*tro*in*tes*ti*nal \cmark \\
-gauchar & ga-u*char \xmark & ga-u*char \xmark \\
-gnosticismo & g.nos*ti*cis*mo \xmark & gnos*ti*cis*mo \cmark \\
-gnóstico & g.nós*ti*co \xmark & gnós*ti*co \cmark \\
-gnu & g.nu \xmark & g.nu \xmark \\
-grafomaníaco & gra*fo*ma*ní-a*co \xmark & gra*fo*ma*ní*a*co \cmark \\
-grafômano & gra-fô*ma*no \xmark & gra*fô*ma*no \cmark \\
-grapiúna & gra*pi-ú*na \xmark & gra*pi*ú*na \cmark \\
-heterônimo & he*te-rô*ni*mo \xmark & he*te*rô*ni*mo \cmark \\
-hexacampeão & he*xa*cam*pe-ão \xmark & he*xa*cam*pe*ão \cmark \\
-hinduísta & hin*du-ís*ta \xmark & hin*du*ís*ta \cmark \\
-holonômico & ho*lo-nô*mi*co \xmark & ho*lo*nô*mi*co \cmark \\
-homofônico & ho*mo-fô*ni*co \xmark & ho*mo*fô*ni*co \cmark \\
-ibijaú & i*bi*ja-ú \xmark & i*bi*ja*ú \cmark \\
-idiótico & i*di-ó*ti*co \xmark & i*di*ó*ti*co \cmark \\
-imbuir & im*bu-ir \xmark & im*bu*ir \cmark \\
-inclinômetro & in*cli-nô*me*tro \xmark & in*cli*nô*me*tro \cmark \\
-irreconciliável & ir*re*con*ci*li-á*vel \xmark & ir*re*con*ci*li*á*vel \cmark \\
-irreligião & ir*re*li*gi-ão \xmark & ir*re*li*gi*ão \cmark \\
-irrenunciável & ir*re*nun*ci-á*vel \xmark & ir*re*nun*ci*á*vel \cmark \\
-isquêmico & is-quê*mi*co \xmark & is*quê*mi*co \cmark \\
-itapiúna & i*ta*pi-ú*na \xmark & i*ta*pi*ú*na \cmark \\
-juá & ju-á \xmark & ju*á \cmark \\
-lamaísta & la*ma-ís*ta \xmark & la*ma*ís*ta \cmark \\
-luteína & lu*te-í*na \xmark & lu*te*í*na \cmark \\
-macrorregião & ma*cror*re*gi-ão \xmark & ma*cror*re*gi*ão \cmark \\
-mandrião & man*dri-ão \xmark & man*dri*ão \cmark \\
-masdeísmo & mas*de-ís*mo \xmark & mas*de*ís*mo \cmark \\
-maué & mau-é \xmark & mau*é \cmark \\
-mediático & me*di-á*ti*co \xmark & me*di*á*ti*co \cmark \\
-melômano & me-lô*ma*no \xmark & me*lô*ma*no \cmark \\
-mnemônica & m.ne-mô*ni*ca \xmark & mne*mô*ni*ca \cmark \\
-moinha & mo-i*nha \xmark & mo*i*nha \cmark \\
-monômero & mo-nô*me*ro \xmark & mo*nô*me*ro \cmark \\
-monoquíni & mo*no-quí*ni \xmark & mo*no*quí*ni \cmark \\
-monoteísta & mo*no*te-ís*ta \xmark & mo*no*te*ís*ta \cmark \\
-mortuárias & mor*tu-á*ri*as \xmark & mor*tu*á*ri*as \cmark \\
-mucuim & mu*cu-im \xmark & mu*cu-im \xmark \\
-negligenciável & ne*gli*gen*ci-á*vel \xmark & ne*gli*gen*ci*á*vel \cmark \\
-neuropsiquiatria & neu*rop*si*qui*a*tri*a \cmark & neu*rop-si*qui*a*tri*a \xmark \\
-oboísta & o*bo-ís*ta \xmark & o*bo*ís*ta \cmark \\
-ofidiário & o*fi*di-á*ri*o \xmark & o*fi*di*á*ri*o \cmark \\
-oleína & o*le-í*na \xmark & o*le*í*na \cmark \\
-opiáceo & o*pi-á*ce*o \xmark & o*pi*á*ce*o \cmark \\
-pancreático & pan*cre-á*ti*co \xmark & pan*cre*á*ti*co \cmark \\
-panô & pa-nô \xmark & pa*nô \cmark \\
-parquê & par-quê \xmark & par*quê \cmark \\
-parvoíce & par*vo-í*ce \xmark & par*vo*í*ce \cmark \\
-patenteável & pa*ten*te-á*vel \xmark & pa*ten*te*á*vel \cmark \\
-peã & pe-ã \xmark & pe*ã \cmark \\
-periósteo & pe*ri-ós*te*o \xmark & pe*ri*ós*te*o \cmark \\
-picuá & pi*cu-á \xmark & pi*cu*á \cmark \\
-piquê & pi-quê \xmark & pi*quê \cmark \\
-piromaníaco & pi*ro*ma*ní-a*co \xmark & pi*ro*ma*ní*a*co \cmark \\
-piruá & pi*ru-á \xmark & pi*ru*á \cmark \\
-piúria & pi-ú*ri*a \xmark & pi*ú*ri*a \cmark \\
-plagiário & pla*gi-á*ri*o \xmark & pla*gi*á*ri*o \cmark \\
-plebeísmo & ple*be-ís*mo \xmark & ple*be*ís*mo \cmark \\
-plenipotenciário & ple*ni*po*ten*ci-á*ri*o \xmark & ple*ni*po*ten*ci*á*ri*o \cmark \\
-pneumatologia & p.neu*ma*to*lo*gi*a \xmark & pneu*ma*to*lo*gi*a \cmark \\
-pneumônico & p.neu-mô*ni*co \xmark & pneu*mô*ni*co \cmark \\
-polifônico & po*li-fô*ni*co \xmark & po*li*fô*ni*co \cmark \\
-politeísmo & po*li*te-ís*mo \xmark & po*li*te*ís*mo \cmark \\
-politeísta & po*li*te-ís*ta \xmark & po*li*te*ís*ta \cmark \\
-politiquês & po*li*ti-quês \xmark & po*li*ti*quês \cmark \\
-procaína & pro*ca-í*na \xmark & pro*ca*í*na \cmark \\
-pronunciável & pro*nun*ci-á*vel \xmark & pro*nun*ci*á*vel \cmark \\
-pseudociência & p.seu*do*ci*ên*ci*a \xmark & pseu*do*ci*ên*ci*a \cmark \\
-psicofísico & p.si*co*fí*si*co \xmark & psi*co*fí*si*co \cmark \\
-psicologizar & p.si*co*lo*gi*zar \xmark & psi*co*lo*gi*zar \cmark \\
-psicometria & p.si*co*me*tri*a \xmark & psi*co*me*tri*a \cmark \\
-psicomotricidade & p.si*co*mo*tri*ci*da*de \xmark & psi*co*mo*tri*ci*da*de \cmark \\
-psicopatológico & p.si*co*pa*to*ló*gi*co \xmark & psi*co*pa*to*ló*gi*co \cmark \\
-psicoprofilaxia & p.si*co*pro*fi*la*xi*a \xmark & psi*co*pro*fi*la*xi*a \cmark \\
-psicossexual & p.si*cos*se*xu*al \xmark & psi*cos*se*xu*al \cmark \\
-psicoterapêutico & p.si*co*te*ra*pêu*ti*co \xmark & psi*co*te*ra*pêu*ti*co \cmark \\
-psiquê & p.si-quê \xmark & psi*quê \cmark \\
-psitacismo & p.si*ta*cis*mo \xmark & psi*ta*cis*mo \cmark \\
-psoríase & p.so*rí-a*se \xmark & p.so*rí*a*se \xmark \\
-ptose & p.to*se \xmark & pto*se \cmark \\
-puído & pu-í*do \xmark & pu*í*do \cmark \\
-putrião & pu*tri-ão \xmark & pu*tri*ão \cmark \\
-questiúncula & ques*ti-ún*cu*la \xmark & ques*ti*ún*cu*la \cmark \\
-reimportar & re-im*por*tar \xmark & re*im*por*tar \cmark \\
-reimpressão & re-im*pres*são \xmark & re*im*pres*são \cmark \\
-reinscrever & re-ins*cre*ver \xmark & re*ins*cre*ver \cmark \\
-reinserir & re-in*se*rir \xmark & re*in*se*rir \cmark \\
-remediável & re*me*di-á*vel \xmark & re*me*di*á*vel \cmark \\
-rubiácea & ru*bi-á*ce*a \xmark & ru*bi*á*ce*a \cmark \\
-ruinoso & ru-i*no*so \xmark & ru*i*no*so \cmark \\
-sainha & sa-i*nha \xmark & sa*i*nha \cmark \\
-sardônica & sar-dô*ni*ca \xmark & sar*dô*ni*ca \cmark \\
-satiríase & sa*ti*rí-a*se \xmark & sa*ti*rí*a*se \cmark \\
-setentrião & se*ten*tri-ão \xmark & se*ten*tri*ão \cmark \\
-sievert & si.e*vert \xmark & si.e*vert \xmark \\
-sismômetro & sis-mô*me*tro \xmark & sis*mô*me*tro \cmark \\
-solipsista & so*lip*sis*ta \cmark & so*lip-sis*ta \xmark \\
-suaíle & su*a-í*le \xmark & su*a*í*le \cmark \\
-sublevado & su.b-le*va*do \xmark & sub*le*va*do \cmark \\
-sublocar & su.b-lo*car \xmark & sub*lo*car \cmark \\
-sublocatário & su.b-lo*ca*tá*ri*o \xmark & sub*lo*ca*tá*ri*o \cmark \\
-subsônico & sub-sô*ni*co \xmark & sub*sô*ni*co \cmark \\
-sucuriú & su*cu*ri-ú \xmark & su*cu*ri*ú \cmark \\
-suingar & su-in*gar \xmark & su-in*gar \xmark \\
-tacômetro & ta-cô*me*tro \xmark & ta*cô*me*tro \cmark \\
-taiuiá & tai-ui-á \xmark & tai-ui*á \xmark \\
-taiwanês & tai-wa*nês \xmark & tai-wa*nês \xmark \\
-talião & ta*li-ão \xmark & ta*li*ão \cmark \\
-tchecoslovaco & t.che*cos*lo*va*co \xmark & tche*cos*lo*va*co \cmark \\
-teísta & te-ís*ta \xmark & te*ís*ta \cmark \\
-teiú & tei-ú \xmark & tei*ú \cmark \\
-telômero & te-lô*me*ro \xmark & te*lô*me*ro \cmark \\
-teníase & te*ní-a*se \xmark & te*ní*a*se \cmark \\
-terciário & ter*ci-á*ri*o \xmark & ter*ci*á*ri*o \cmark \\
-torreão & tor*re-ão \xmark & tor*re*ão \cmark \\
-transeunte & tran*se-un*te \xmark & tran*se-un*te \xmark \\
-triádico & tri-á*di*co \xmark & tri*á*di*co \cmark \\
-tripanossomíase & tri*pa*nos*so*mí-a*se \xmark & tri*pa*nos*so*mí*a*se \cmark \\
-triunfador & tri-un*fa*dor \xmark & tri*un*fa*dor \cmark \\
-truísmo & tru-ís*mo \xmark & tru*ís*mo \cmark \\
-tuim & tu-im \xmark & tu-im \xmark \\
-tuiuiú & tui-ui-ú \xmark & tui-ui*ú \xmark \\
-tumultuário & tu*mul*tu-á*ri*o \xmark & tu*mul*tu*á*ri*o \cmark \\
-tzarista & t.za*ris*ta \xmark & tza*ris*ta \cmark \\
-vietcongue & vi*et*con*gue \cmark & vi*et-con*gue \xmark \\
-vitriólico & vi*tri-ó*li*co \xmark & vi*tri*ó*li*co \cmark \\
-vitríolo & vi*trí-o*lo \xmark & vi*trí*o*lo \cmark \\
-xilocaína & xi*lo*ca-í*na \xmark & xi*lo*ca*í*na \cmark \\
-abluir & a*blu-ir \xmark & a*blu*ir \cmark \\
-balaústre & ba*la-ús*tre \xmark & ba*la*ús*tre \cmark \\
-cabriúva & ca*bri-ú*va \xmark & ca*bri*ú*va \cmark \\
-daguerreótipo & da*guer*re-ó*ti*po \xmark & da*guer*re*ó*ti*po \cmark \\
-daltônico & dal-tô*ni*co \xmark & dal*tô*ni*co \cmark \\
-ecônomo & e-cô*no*mo \xmark & e*cô*no*mo \cmark \\
-egoístico & e*go-ís*ti*co \xmark & e*go*ís*ti*co \cmark \\
-eletrocardiógrafo & e*le*tro*car*di-ó*gra*fo \xmark & e*le*tro*car*di*ó*gra*fo \cmark \\
-eletroquímica & e*le*tro-quí*mi*ca \xmark & e*le*tro*quí*mi*ca \cmark \\
-eletroquímico & e*le*tro-quí*mi*co \xmark & e*le*tro*quí*mi*co \cmark \\
-embainhar & em*ba-i*nhar \xmark & em*ba*i*nhar \cmark \\
-faiscar & fa-is*car \xmark & fa-is*car \xmark \\
-faúlha & fa-ú*lha \xmark & fa*ú*lha \cmark \\
-galvanômetro & gal*va-nô*me*tro \xmark & gal*va*nô*me*tro \cmark \\
-hagiógrafo & ha*gi-ó*gra*fo \xmark & ha*gi*ó*gra*fo \cmark \\
-hebraísmo & he*bra-ís*mo \xmark & he*bra*ís*mo \cmark \\
-hebraísta & he*bra-ís*ta \xmark & he*bra*ís*ta \cmark \\
-hipertônico & hi*per-tô*ni*co \xmark & hi*per*tô*ni*co \cmark \\
-historiógrafo & his*to*ri-ó*gra*fo \xmark & his*to*ri*ó*gra*fo \cmark \\
-histrião & his*tri-ão \xmark & his*tri*ão \cmark \\
-jesuitismo & je*su-i*tis*mo \xmark & je*su*i*tis*mo \cmark \\
-macedônico & ma*ce-dô*ni*co \xmark & ma*ce*dô*ni*co \cmark \\
-ninfomaníaco & nin*fo*ma*ní-a*co \xmark & nin*fo*ma*ní*a*co \cmark \\
-paquímetro & pa-quí*me*tro \xmark & pa*quí*me*tro \cmark \\
-tabuinha & ta*bu-i*nha \xmark & ta*bu*i*nha \cmark \\
-taquígrafo & ta-quí*gra*fo \xmark & ta*quí*gra*fo \cmark \\
-taquímetro & ta-quí*me*tro \xmark & ta*quí*me*tro \cmark \\
-tectônico & tec-tô*ni*co \xmark & tec*tô*ni*co \cmark \\
 xintoísta & xin*to-ís*ta \xmark & xin*to*ís*ta \cmark \\
-abiótica & a*bi-ó*ti*ca \xmark & a*bi*ó*ti*ca \cmark \\
-abiótico & a*bi-ó*ti*co \xmark & a*bi*ó*ti*co \cmark \\
-abraâmico & a*bra-â*mi*co \xmark & a*bra*â*mi*co \cmark \\
-abstraído & abs*tra-í*do \xmark & abs*tra*í*do \cmark \\
-acauã & a*cau-ã \xmark & a*cau*ã \cmark \\
-acelerômetro & a*ce*le-rô*me*tro \xmark & a*ce*le*rô*me*tro \cmark \\
-acetaldeído & a*ce*tal*de-í*do \xmark & a*ce*tal*de*í*do \cmark \\
-acroleína & a*cro*le-í*na \xmark & a*cro*le*í*na \cmark \\
-adônis & a-dô*nis \xmark & a*dô*nis \cmark \\
-ainsa & a-in*sa \xmark & a-in*sa \xmark \\
-aiquidô & ai*qui-dô \xmark & ai*qui*dô \cmark \\
-alcíone & al*cí-o*ne \xmark & al*cí*o*ne \cmark \\
-aldeído & al*de-í*do \xmark & al*de*í*do \cmark \\
-aleúte & a*le-ú*te \xmark & a*le*ú*te \cmark \\
-aliá & a*li-á \xmark & a*li*á \cmark \\
-almóada & al*mó-a*da \xmark & al*mó-a*da \xmark \\
-aloé & a*lo-é \xmark & a*lo*é \cmark \\
-aloés & a*lo-és \xmark & a*lo*és \cmark \\
-aluá & a*lu-á \xmark & a*lu*á \cmark \\
-alvéolo & al*vé-o*lo \xmark & al*vé*o*lo \cmark \\
-amebíase & a*me*bí-a*se \xmark & a*me*bí*a*se \cmark \\
-âmnio & âm*ni*o \cmark & â.m-ni*o \xmark \\
-ancilostomíase & an*ci*los*to*mí-a*se \xmark & an*ci*los*to*mí*a*se \cmark \\
-anemômetro & a*ne-mô*me*tro \xmark & a*ne*mô*me*tro \cmark \\
-anfião & an*fi-ão \xmark & an*fi*ão \cmark \\
-anfictião & an*fic*ti-ão \xmark & an*fic*ti*ão \cmark \\
-anião & a*ni-ão \xmark & a*ni*ão \cmark \\
-aórtico & a-ór*ti*co \xmark & a*ór*ti*co \cmark \\
-apuí & a*pu-í \xmark & a*pu*í \cmark \\
-aquífero & a-quí*fe*ro \xmark & a*quí*fe*ro \cmark \\
-areão & a*re-ão \xmark & a*re*ão \cmark \\
-areópago & a*re-ó*pa*go \xmark & a*re*ó*pa*go \cmark \\
-arquidiácono & ar*qui*di-á*co*no \xmark & ar*qui*di*á*co*no \cmark \\
-arteríola & ar*te*rí-o*la \xmark & ar*te*rí*o*la \cmark \\
-assiriólogo & as*si*ri-ó*lo*go \xmark & as*si*ri*ó*lo*go \cmark \\
-astroquímica & as*tro-quí*mi*ca \xmark & as*tro*quí*mi*ca \cmark \\
-ateísta & a*te-ís*ta \xmark & a*te*ís*ta \cmark \\
-autoimunidade & au*to-i*mu*ni*da*de \xmark & au*to-i*mu*ni*da*de \xmark \\
-autônimo & au-tô*ni*mo \xmark & au*tô*ni*mo \cmark \\
-autonômico & au*to-nô*mi*co \xmark & au*to*nô*mi*co \cmark \\
-averroísmo & a*ver*ro-ís*mo \xmark & a*ver*ro*ís*mo \cmark \\
-bacteriófago & bac*te*ri-ó*fa*go \xmark & bac*te*ri*ó*fa*go \cmark \\
-baleárico & ba*le-á*ri*co \xmark & ba*le*á*ri*co \cmark \\
-banjoísta & ban*jo-ís*ta \xmark & ban*jo*ís*ta \cmark \\
-batuíra & ba*tu-í*ra \xmark & ba*tu*í*ra \cmark \\
-behaviorismo & be-ha*vi*o*ris*mo \xmark & be-ha*vi*o*ris*mo \xmark \\
-benjoim & ben*jo-im \xmark & ben*jo-im \xmark \\
-bibliógrafo & bi*bli-ó*gra*fo \xmark & bi*bli*ó*gra*fo \cmark \\
-bilião & bi*li-ão \xmark & bi*li*ão \cmark \\
-biótico & bi-ó*ti*co \xmark & bi*ó*ti*co \cmark \\
-biótopo & bi-ó*to*po \xmark & bi*ó*to*po \cmark \\
-biscainho & bis*ca-i*nho \xmark & bis*ca*i*nho \cmark \\
-blastômero & blas-tô*me*ro \xmark & blas*tô*me*ro \cmark \\
-boé & bo-é \xmark & bo*é \cmark \\
-bosníaco & bos*ní-a*co \xmark & bos*ní*a*co \cmark \\
-braquiópode & bra*qui-ó*po*de \xmark & bra*qui*ó*po*de \cmark \\
-bué & bu-é \xmark & bu*é \cmark \\
-cafarnaum & ca*far*na-um \xmark & ca*far*na-um \xmark \\
-cajuína & ca*ju-í*na \xmark & ca*ju*í*na \cmark \\
-camião & ca*mi-ão \xmark & ca*mi*ão \cmark \\
-candidíase & can*di*dí-a*se \xmark & can*di*dí*a*se \cmark \\
-canoísta & ca*no-ís*ta \xmark & ca*no*ís*ta \cmark \\
-carnaubal & car*na-u*bal \xmark & car*na-u*bal \xmark \\
-caroá & ca*ro-á \xmark & ca*ro*á \cmark \\
-caseína & ca*se-í*na \xmark & ca*se*í*na \cmark \\
-catequético & ca*te-qué*ti*co \xmark & ca*te*qué*ti*co \cmark \\
-catião & ca*ti-ão \xmark & ca*ti*ão \cmark \\
-cauã & cau-ã \xmark & cau*ã \cmark \\
-celíaco & ce*lí-a*co \xmark & ce*lí*a*co \cmark \\
-cnidário & c.ni*dá*ri*o \xmark & c.ni*dá*ri*o \xmark \\
-coimbrão & co-im*brão \xmark & co*im*brão \cmark \\
-coleóptero & co*le-óp*te*ro \xmark & co*le*óp*te*ro \cmark \\
-contraindicação & con*tra-in*di*ca*ção \xmark & con*tra*in*di*ca*ção \cmark \\
-contribuidor & con*tri*bu-i*dor \xmark & con*tri*bu*i*dor \cmark \\
-coriáceo & co*ri-á*ce*o \xmark & co*ri*á*ce*o \cmark \\
-curião & cu*ri-ão \xmark & cu*ri*ão \cmark \\
-curiúva & cu*ri-ú*va \xmark & cu*ri*ú*va \cmark \\
-cuxiú & cu*xi-ú \xmark & cu*xi*ú \cmark \\
-decurião & de*cu*ri-ão \xmark & de*cu*ri*ão \cmark \\
-deiscente & de-is*cen*te \xmark & de-is*cen*te \xmark \\
-deísmo & de-ís*mo \xmark & de*ís*mo \cmark \\
-díade & dí-a*de \xmark & dí*a*de \cmark \\
-diádico & di-á*di*co \xmark & di*á*di*co \cmark \\
-diádoco & di-á*do*co \xmark & di*á*do*co \cmark \\
-diáfise & di-á*fi*se \xmark & di*á*fi*se \cmark \\
-diatômico & di*a-tô*mi*co \xmark & di*a*tô*mi*co \cmark \\
-diérese & di-é*re*se \xmark & di*é*re*se \cmark \\
-diferenciável & di*fe*ren*ci-á*vel \xmark & di*fe*ren*ci*á*vel \cmark \\
-difluência & di*flu-ên*ci*a \xmark & di*flu*ên*ci*a \cmark \\
-díodo & dí-o*do \xmark & dí*o*do \cmark \\
-domiciliário & do*mi*ci*li-á*ri*o \xmark & do*mi*ci*li*á*ri*o \cmark \\
-dríade & drí-a*de \xmark & drí*a*de \cmark \\
-elastômero & e*las-tô*me*ro \xmark & e*las*tô*me*ro \cmark \\
-eluição & e*lu-i*ção \xmark & e*lu*i*ção \cmark \\
-éon & é-on \xmark & é*on \cmark \\
-epicôndilo & e*pi-côn*di*lo \xmark & e*pi*côn*di*lo \cmark \\
-épsilon & ép*si*lon \cmark & ép-si*lon \xmark \\
-equidna & e*quid*na \cmark & e*qui.d*na \xmark \\
-estatuário & es*ta*tu-á*ri*o \xmark & es*ta*tu*á*ri*o \cmark \\
-esteárico & es*te-á*ri*co \xmark & es*te*á*ri*co \cmark \\
-estereoquímica & es*te*re*o-quí*mi*ca \xmark & es*te*re*o*quí*mi*ca \cmark \\
-etnônimo & et-nô*ni*mo \xmark & et*nô*ni*mo \cmark \\
-eucariótico & eu*ca*ri-ó*ti*co \xmark & eu*ca*ri*ó*ti*co \cmark \\
-eurasiático & eu*ra*si-á*ti*co \xmark & eu*ra*si*á*ti*co \cmark \\
-europeísmo & eu*ro*pe-ís*mo \xmark & eu*ro*pe*ís*mo \cmark \\
-europeísta & eu*ro*pe-ís*ta \xmark & eu*ro*pe*ís*ta \cmark \\
-evangeliário & e*van*ge*li-á*ri*o \xmark & e*van*ge*li*á*ri*o \cmark \\
-feroês & fe*ro-ês \xmark & fe*ro*ês \cmark \\
-fiável & fi-á*vel \xmark & fi*á*vel \cmark \\
-fisiólogo & fi*si-ó*lo*go \xmark & fi*si*ó*lo*go \cmark \\
-fluídico & flu-í*di*co \xmark & flu-í*di*co \xmark \\
-foliáceo & fo*li-á*ce*o \xmark & fo*li*á*ce*o \cmark \\
-folíolo & fo*lí-o*lo \xmark & fo*lí*o*lo \cmark \\
-fotoperíodo & fo*to*pe*rí-o*do \xmark & fo*to*pe*rí*o*do \cmark \\
-fotoquímica & fo*to-quí*mi*ca \xmark & fo*to*quí*mi*ca \cmark \\
-fotoquímico & fo*to-quí*mi*co \xmark & fo*to*quí*mi*co \cmark \\
-friável & fri-á*vel \xmark & fri*á*vel \cmark \\
-ftálico & f.tá*li*co \xmark & f.tá*li*co \xmark \\
-fuá & fu-á \xmark & fu*á \cmark \\
-genômico & ge-nô*mi*co \xmark & ge*nô*mi*co \cmark \\
-genuinidade & ge*nu-i*ni*da*de \xmark & ge*nu*i*ni*da*de \cmark \\
-geoquímica & ge*o-quí*mi*ca \xmark & ge*o*quí*mi*ca \cmark \\
-geoquímico & ge*o-quí*mi*co \xmark & ge*o*quí*mi*co \cmark \\
-geotectônica & ge*o*tec-tô*ni*ca \xmark & ge*o*tec*tô*ni*ca \cmark \\
-gimnodesportivo & gim*no*des*por*ti*vo \cmark & gi.m-no*des*por*ti*vo \xmark \\
-glaciário & gla*ci-á*ri*o \xmark & gla*ci*á*ri*o \cmark \\
-glicoproteína & gli*co*pro*te-í*na \xmark & gli*co*pro*te*í*na \cmark \\
-gnaisse & g.nais*se \xmark & g.nais*se \xmark \\
-goês & go-ês \xmark & go*ês \cmark \\
-graxaim & gra*xa-im \xmark & gra*xa-im \xmark \\
-helíaco & he*lí-a*co \xmark & he*lí*a*co \cmark \\
-henoteísmo & he*no*te-ís*mo \xmark & he*no*te*ís*mo \cmark \\
-heptacampeão & hep*ta*cam*pe-ão \xmark & hep*ta*cam*pe*ão \cmark \\
-heteroátomo & he*te*ro-á*to*mo \xmark & he*te*ro*á*to*mo \cmark \\
-higiénico & hi*gi-é*ni*co \xmark & hi*gi*é*ni*co \cmark \\
-hióideo & hi-ói*de*o \xmark & hi*ói*de*o \cmark \\
-hipersônico & hi*per-sô*ni*co \xmark & hi*per*sô*ni*co \cmark \\
-hipocôndrio & hi*po-côn*dri*o \xmark & hi*po*côn*dri*o \cmark \\
-hipomaníaco & hi*po*ma*ní-a*co \xmark & hi*po*ma*ní*a*co \cmark \\
-histoquímica & his*to-quí*mi*ca \xmark & his*to*quí*mi*ca \cmark \\
-iá & i-á \xmark & i*á \cmark \\
-ião & i-ão \xmark & i*ão \cmark \\
-iatroquímica & i*a*tro-quí*mi*ca \xmark & i*a*tro*quí*mi*ca \cmark \\
-icônico & i-cô*ni*co \xmark & i*cô*ni*co \cmark \\
-ictiólogo & ic*ti-ó*lo*go \xmark & ic*ti*ó*lo*go \cmark \\
-indeiscente & in*de-is*cen*te \xmark & in*de-is*cen*te \xmark \\
-indemnização & in*dem*ni*za*ção \cmark & in*de.m-ni*za*ção \xmark \\
-indemnizar & in*dem*ni*zar \cmark & in*de.m-ni*zar \xmark \\
-instituidor & ins*ti*tu-i*dor \xmark & ins*ti*tu*i*dor \cmark \\
-intercambiável & in*ter*cam*bi-á*vel \xmark & in*ter*cam*bi*á*vel \cmark \\
-interferômetro & in*ter*fe-rô*me*tro \xmark & in*ter*fe*rô*me*tro \cmark \\
-íon & í-on \xmark & í*on \cmark \\
-ipsilateral & ip*si*la*te*ral \cmark & ip-si*la*te*ral \xmark \\
-ípsilon & íp*si*lon \cmark & íp-si*lon \xmark \\
-isômero & i-sô*me*ro \xmark & i*sô*me*ro \cmark \\
-isotônico & i*so-tô*ni*co \xmark & i*so*tô*ni*co \cmark \\
-itaúba & i*ta-ú*ba \xmark & i*ta*ú*ba \cmark \\
-jandaíra & jan*da-í*ra \xmark & jan*da*í*ra \cmark \\
-jaó & ja-ó \xmark & ja*ó \cmark \\
-jauá & jau-á \xmark & jau*á \cmark \\
-jihadista & ji-ha*dis*ta \xmark & ji-ha*dis*ta \xmark \\
-joinvilense & jo-in*vi*len*se \xmark & jo-in*vi*len*se \xmark \\
-jundiá & jun*di-á \xmark & jun*di*á \cmark \\
-jutaí & ju*ta-í \xmark & ju*ta*í \cmark \\
-kuwaitiano & ku-wai*ti*a*no \xmark & ku-wai*ti*a*no \xmark \\
-lemna & lem*na \cmark & le.m-na \xmark \\
-lemniscata & lem*nis*ca*ta \cmark & le.m-nis*ca*ta \xmark \\
-lemnisco & lem*nis*co \cmark & le.m-nis*co \xmark \\
-leônico & le-ô*ni*co \xmark & le*ô*ni*co \cmark \\
-lidocaína & li*do*ca-í*na \xmark & li*do*ca*í*na \cmark \\
-liechtensteinense & li*e.ch*tens*tei*nen*se \xmark & li*e.ch*tens*tei*nen*se \xmark \\
-limnologia & lim*no*lo*gi*a \cmark & li.m-no*lo*gi*a \xmark \\
-litíase & li*tí-a*se \xmark & li*tí*a*se \cmark \\
-macaúba & ma*ca-ú*ba \xmark & ma*ca*ú*ba \cmark \\
-magnetômetro & mag*ne-tô*me*tro \xmark & mag*ne*tô*me*tro \cmark \\
-maís & ma-ís \xmark & ma*ís \cmark \\
-malauiano & ma*lau-i*a*no \xmark & ma*lau-i*a*no \xmark \\
-malônico & ma-lô*ni*co \xmark & ma*lô*ni*co \cmark \\
-maruí & ma*ru-í \xmark & ma*ru*í \cmark \\
-maruim & ma*ru-im \xmark & ma*ru-im \xmark \\
-meã & me-ã \xmark & me*ã \cmark \\
-meão & me-ão \xmark & me*ão \cmark \\
-meiótico & mei-ó*ti*co \xmark & mei*ó*ti*co \cmark \\
-microbiólogo & mi*cro*bi-ó*lo*go \xmark & mi*cro*bi*ó*lo*go \cmark \\
-midríase & mi*drí-a*se \xmark & mi*drí*a*se \cmark \\
-miíase & mi-í-a*se \xmark & mi*í*a*se \cmark \\
-miliário & mi*li-á*ri*o \xmark & mi*li*á*ri*o \cmark \\
-mnemônico & m.ne-mô*ni*co \xmark & mne*mô*ni*co \cmark \\
-monofônico & mo*no-fô*ni*co \xmark & mo*no*fô*ni*co \cmark \\
-moquém & mo-quém \xmark & mo*quém \cmark \\
-morrião & mor*ri-ão \xmark & mor*ri*ão \cmark \\
-neodarwinismo & ne*o*dar-wi*nis*mo \xmark & ne*o*dar-wi*nis*mo \xmark \\
-nobiliário & no*bi*li-á*ri*o \xmark & no*bi*li*á*ri*o \cmark \\
-nucléolo & nu*clé-o*lo \xmark & nu*clé*o*lo \cmark \\
-octaédrico & oc*ta-é*dri*co \xmark & oc*ta*é*dri*co \cmark \\
-odeão & o*de-ão \xmark & o*de*ão \cmark \\
-oídio & o-í*di*o \xmark & o*í*di*o \cmark \\
-omíada & o*mí-a*da \xmark & o*mí*a*da \cmark \\
-omnipotente & om*ni*po*ten*te \cmark & o.m-ni*po*ten*te \xmark \\
-omnisciente & om*nis*ci*en*te \cmark & o.m-nis*ci*en*te \xmark \\
-omnívoro & om*ní*vo*ro \cmark & o.m-ní*vo*ro \xmark \\
-oócito & o-ó*ci*to \xmark & o*ó*ci*to \cmark \\
-orfeão & or*fe-ão \xmark & or*fe*ão \cmark \\
-oriá & o*ri-á \xmark & o*ri*á \cmark \\
-ortodôntico & or*to-dôn*ti*co \xmark & or*to*dôn*ti*co \cmark \\
-ossuário & os*su-á*ri*o \xmark & os*su*á*ri*o \cmark \\
-osteíte & os*te-í*te \xmark & os*te*í*te \cmark \\
-ostiário & os*ti-á*ri*o \xmark & os*ti*á*ri*o \cmark \\
-paleógrafo & pa*le-ó*gra*fo \xmark & pa*le*ó*gra*fo \cmark \\
-paleólogo & pa*le-ó*lo*go \xmark & pa*le*ó*lo*go \cmark \\
-panenteísmo & pa*nen*te-ís*mo \xmark & pa*nen*te*ís*mo \cmark \\
-patauá & pa*tau-á \xmark & pa*tau*á \cmark \\
-patoá & pa*to-á \xmark & pa*to*á \cmark \\
-pecíolo & pe*cí-o*lo \xmark & pe*cí*o*lo \cmark \\
-pequiá & pe*qui-á \xmark & pe*qui*á \cmark \\
-periélio & pe*ri-é*li*o \xmark & pe*ri*é*li*o \cmark \\
-píon & pí-on \xmark & pí*on \cmark \\
-pitiríase & pi*ti*rí-a*se \xmark & pi*ti*rí*a*se \cmark \\
-pium & pi-um \xmark & pi-um \xmark \\
-planctônico & planc-tô*ni*co \xmark & planc*tô*ni*co \cmark \\
-pneuma & p.neu*ma \xmark & pneu*ma \cmark \\
-pneumonite & p.neu*mo*ni*te \xmark & pneu*mo*ni*te \cmark \\
-pneumotórax & p.neu*mo*tó*rax \xmark & pneu*mo*tó*rax \cmark \\
-poliúria & po*li-ú*ri*a \xmark & po*li*ú*ri*a \cmark \\
-poraquê & po*ra-quê \xmark & po*ra*quê \cmark \\
-preênsil & pre-ên*sil \xmark & pre*ên*sil \cmark \\
-príon & prí-on \xmark & prí*on \cmark \\
-procariótico & pro*ca*ri-ó*ti*co \xmark & pro*ca*ri*ó*ti*co \cmark \\
-procônsul & pro-côn*sul \xmark & pro*côn*sul \cmark \\
-proteólise & pro*te-ó*li*se \xmark & pro*te*ó*li*se \cmark \\
-pseudocientífico & p.seu*do*ci*en*tí*fi*co \xmark & pseu*do*ci*en*tí*fi*co \cmark \\
-pseudofruto & p.seu*do*fru*to \xmark & pseu*do*fru*to \cmark \\
-psicadélico & p.si*ca*dé*li*co \xmark & psi*ca*dé*li*co \cmark \\
-psicoativo & p.si*co*a*ti*vo \xmark & psi*co*a*ti*vo \cmark \\
-psicocirurgia & p.si*co*ci*rur*gi*a \xmark & psi*co*ci*rur*gi*a \cmark \\
-psicofisiologia & p.si*co*fi*si*o*lo*gi*a \xmark & psi*co*fi*si*o*lo*gi*a \cmark \\
-psicofonia & p.si*co*fo*ni*a \xmark & psi*co*fo*ni*a \cmark \\
-psicografia & p.si*co*gra*fi*a \xmark & psi*co*gra*fi*a \cmark \\
-psicopompo & p.si*co*pom*po \xmark & psi*co*pom*po \cmark \\
-psicoterápico & p.si*co*te*rá*pi*co \xmark & psi*co*te*rá*pi*co \cmark \\
-psoas & p.so*as \xmark & p.so*as \xmark \\
-pterodáctilo & p.te*ro*dác*ti*lo \xmark & pte*ro*dác*ti*lo \cmark \\
-ptialina & p.ti*a*li*na \xmark & pti*a*li*na \cmark \\
-ptolemaico & p.to*le*mai*co \xmark & pto*le*mai*co \cmark \\
-radioquímica & ra*di*o-quí*mi*ca \xmark & ra*di*o*quí*mi*ca \cmark \\
-randômico & ran-dô*mi*co \xmark & ran*dô*mi*co \cmark \\
-reciário & re*ci-á*ri*o \xmark & re*ci*á*ri*o \cmark \\
-reimpresso & re-im*pres*so \xmark & re*im*pres*so \cmark \\
-reimprimir & re-im*pri*mir \xmark & re*im*pri*mir \cmark \\
-sambaíba & sam*ba-í*ba \xmark & sam*ba*í*ba \cmark \\
-samnita & sam*ni*ta \cmark & sa.m-ni*ta \xmark \\
-saxônico & sa-xô*ni*co \xmark & sa*xô*ni*co \cmark \\
-semiárido & se*mi-á*ri*do \xmark & se*mi*á*ri*do \cmark \\
-semiótico & se*mi-ó*ti*co \xmark & se*mi*ó*ti*co \cmark \\
-semipermeável & se*mi*per*me-á*vel \xmark & se*mi*per*me*á*vel \cmark \\
-sépsis & sép*sis \cmark & sép-sis \xmark \\
-serôdio & se-rô*di*o \xmark & se*rô*di*o \cmark \\
-serventuário & ser*ven*tu-á*ri*o \xmark & ser*ven*tu*á*ri*o \cmark \\
-siálico & si-á*li*co \xmark & si*á*li*co \cmark \\
-siríaco & si*rí-a*co \xmark & si*rí*a*co \cmark \\
-sonômetro & so-nô*me*tro \xmark & so*nô*me*tro \cmark \\
-suaíli & su*a-í*li \xmark & su*a*í*li \cmark \\
-subatômico & su*ba-tô*mi*co \xmark & su*ba*tô*mi*co \cmark \\
-subdiácono & sub*di-á*co*no \xmark & sub*di*á*co*no \cmark \\
-sublevar & su.b-le*var \xmark & sub*le*var \cmark \\
-subliminal & su.b-li*mi*nal \xmark & sub*li*mi*nal \cmark \\
-sublinear & su.b-li*ne*ar \xmark & sub*li*ne*ar \cmark \\
-sublingual & su.b-lin*gual \xmark & sub*lin*gual \cmark \\
-sublunar & su.b-lu*nar \xmark & sub*lu*nar \cmark \\
-subsequência & sub*se-quên*ci*a \xmark & sub*se*quên*ci*a \cmark \\
-substituinte & subs*ti*tu-in*te \xmark & subs*ti*tu-in*te \xmark \\
-coimbra & co-im*bra \xmark & co*im*bra \cmark \\
-coimperador & co-im*pe*ra*dor \xmark & co*im*pe*ra*dor \cmark \\
-reimposição & re-im*po*si*ção \xmark & re*im*po*si*ção \cmark \\
-bioimpressão & bi*o-im*pres*são \xmark & bi*o*im*pres*são \cmark \\
-neoimpressionista & ne*o-im*pres*si*o*nis*ta \xmark & ne*o*im*pres*si*o*nis*ta \cmark \\
-autoimposto & au*to-im*pos*to \xmark & au*to*im*pos*to \cmark \\
-reimplementação & re-im*ple*men*ta*ção \xmark & re*im*ple*men*ta*ção \cmark \\
-teleimpressor & te*le-im*pres*sor \xmark & te*le*im*pres*sor \cmark \\
-reimposta & re-im*pos*ta \xmark & re*im*pos*ta \cmark \\
-reimplementar & re-im*ple*men*tar \xmark & re*im*ple*men*tar \cmark \\
-reimpulsionar & re-im*pul*si*o*nar \xmark & re*im*pul*si*o*nar \cmark \\
-autoimposição & au*to-im*po*si*ção \xmark & au*to*im*po*si*ção \cmark \\
-cacauicultor & ca*cau-i*cul*tor \xmark & ca*cau*i*cul*tor \cmark \\
-sanduiche & san*du-i*che \xmark & san*du*i*che \cmark \\
-ruidosamente & ru-i*do*sa*men*te \xmark & ru*i*do*sa*men*te \cmark \\
-promiscuidade & pro*mis*cu-i*da*de \xmark & pro*mis*cu*i*da*de \cmark \\
-inocuidade & i*no*cu-i*da*de \xmark & i*no*cu*i*da*de \cmark \\
-reincidência & re-in*ci*dên*ci.a \xmark & re*in*ci*dên*ci.a \xmark \\
-reincluir & re-in*clu-ir \xmark & re*in*clu*ir \cmark \\
-reinfecção & re-in*fec*ção \xmark & re*in*fec*ção \cmark \\
-reinforçar & re-in*for*çar \xmark & re*in*for*çar \cmark \\
-reinsurgir & re-in*sur*gir \xmark & re*in*sur*gir \cmark \\
-reinstalado & re-ins*ta*la*do \xmark & re*ins*ta*la*do \cmark \\
-reinstituído & re-ins*ti*tu-í*do \xmark & re*ins*ti*tu*í*do \cmark \\
-reinvindicar & re-in*vin*di*car \xmark & re*in*vin*di*car \cmark \\
-bioincrustação & bi*o-in*crus*ta*ção \xmark & bi*o*in*crus*ta*ção \cmark \\
-agroindustrial & a*gro-in*dus*tri*al \xmark & a*gro*in*dus*tri*al \cmark \\
-bioindicadores & bi*o-in*di*ca*do*res \xmark & bi*o*in*di*ca*do*res \cmark \\
-autoindulgência & au*to-in*dul*gên*ci.a \xmark & au*to*in*dul*gên*ci.a \xmark \\
-autoinduzida & au*to-in*du*zi*da \xmark & au*to*in*du*zi*da \cmark \\
-microindústria & mi*cro-in*dús*tri*a \xmark & mi*cro*in*dús*tri*a \cmark \\
-tecnoindustrial & tec*no-in*dus*tri*al \xmark & tec*no*in*dus*tri*al \cmark \\
-bioinformática & bi*o-in*for*má*ti*ca \xmark & bi*o*in*for*má*ti*ca \cmark \\
-coinfecção & co-in*fec*ção \xmark & co*in*fec*ção \cmark \\
-geoinformação & ge.o-in*for*ma*ção \xmark & ge.o*in*for*ma*ção \xmark \\
-autoinfecção & au*to-in*fec*ção \xmark & au*to*in*fec*ção \cmark \\
-neuroinformática & neu*ro-in*for*má*ti*ca \xmark & neu*ro*in*for*má*ti*ca \cmark \\
-amendoins & a*men*do-ins \xmark & a*men*do*ins \cmark \\
-videoinstalação & vi*de*o-ins*ta*la*ção \xmark & vi*de*o*ins*ta*la*ção \cmark \\
-autointitulado & au*to-in*ti*tu*la*do \xmark & au*to*in*ti*tu*la*do \cmark \\
-saindo & sa-in*do \xmark & sa*in*do \cmark \\
-caindo & ca-in*do \xmark & ca*in*do \cmark \\
-contraindicações & con*tra-in*di*ca*ções \xmark & con*tra*in*di*ca*ções \cmark \\
-abstraindo & abs*tra-in*do \xmark & abs*tra*in*do \cmark \\
-prainha & pra-i*nha \xmark & pra*i*nha \cmark \\
-lagoinha & la*go-i*nha \xmark & la*go*i*nha \cmark \\
-canoinha & ca*no-i*nha \xmark & ca*no*i*nha \cmark \\
-reimpresso & re-im*pres*so \xmark & re*im*pres*so \cmark \\
-genuino & ge*nu-i*no \xmark & ge*nu*i*no \cmark \\
-ruina & ru-i*na \xmark & ru*i*na \cmark \\
-arruinado & ar*ru-i*na*do \xmark & ar*ru*i*na*do \cmark \\
-arruinou & ar*ru-i*nou \xmark & ar*ru*i*nou \cmark \\
-suino & su-i*no \xmark & su*i*no \cmark \\
-suina & su-i*na \xmark & su*i*na \cmark \\
-ajuizamento & a*ju-i*za*men*to \xmark & a*ju*i*za*men*to \cmark \\
-luiz & lu-iz \xmark & lu*iz \cmark \\
-luiza & lu-i*za \xmark & lu*i*za \cmark \\
-amnésia & a-m.né*si*a \xmark & a*mné*si*a \cmark \\
-amniota & a-m.ni*o*ta \xmark & a*mni*o*ta \cmark \\
-amniótico & a-m.ni-ó*ti*co \xmark & a*mni*ó*ti*co \cmark \\
-diuréticos & di-u*ré*ti*cos \xmark & di*u*ré*ti*cos \cmark \\
-diurese & di-u*re*se \xmark & di*u*re*se \cmark \\
-feiurinha & fei-u*ri*nha \xmark & fei*u*ri*nha \cmark \\
-íodo & í-o*do \xmark & í*o*do \cmark \\
-íons & í-ons \xmark & í*ons \cmark \\
-antíope & an*tí-o*pe \xmark & an*tí*o*pe \cmark \\
-médiuns & mé*di-uns \xmark & mé*di*uns \cmark \\
-fluór & flu-ór \xmark & flu*ór \cmark \\
-sequóia & se-quói*a \xmark & se*quói*a \cmark \\
-subquântico & sub-quân*ti*co \xmark & sub*quân*ti*co \cmark \\
-\\
-\hline
-37798 & 1368 & 132 \\
-\hline
+zodíaco & zo*dí-a*co \xmark & zo*dí*a*co \cmark \\
+zoósporo & zo-ós*po*ro \xmark & zo*ós*po*ro \cmark \\
+total correct & 17 & 811 \\

### 2024-06-14 article/conclusion.tex
updates

\section{Concluding Remarks and Future Directions}\label{sec-conclusion}

In this study, we explored the default TeX hyphenation rules and proposed
additional rules to improve hyphenation performance in Portuguese. By
addressing the limitations of the old rules and existing approaches within the
TeX typesetting system, and by incorporating morphological and phonological
considerations, we significantly reduced the number of hyphenation errors.

However, the patched set of rules is still not enough to achieve perfect
accuracy, and it is not even desired since our dataset is noisy and there are
many dubious hyphenation cases. We have opted to create a concise set of rules
that could better generalize and, therefore, align more closely with the
underlying hyphenation rules in the language.

We also tested rules created by patgen, which generated an extensive set of
rules that were unable to generalize effectively. In contrast, our handcrafted
rules performed superiorly in a validation set.

In conclusion, while our enhanced rule set demonstrates significant
improvements in hyphenation accuracy, there could remains room for further
refinement.

Wide character support and universal syllabic segmentation, as considered by
\cite{sojka2023roadmap}, are additional points for consideration. Incorporating
regular expressions, creating classes of characters, and supporting word stress
positions might further enhance the efficiency and generality of the
hyphenation system.

### 2024-06-14 article/dictionary.tex
updates

@@
 one used previously. Many words garnered only four votes, indicating a lack of
-alternative hyphenations provided by any dictionary, and were thus initially
+alternative hyphenations provided by any dictionary, and they were thus initially
 hyphenated as proparoxytones. These instances were typically distinguished by
@@
 highest frequency of votes. This procedure is implemented in the script
-\texttt{get4.sh}.
+\texttt{get4.sh}, and the resulting list has \num{\NumberOfFourAgrees} words.
 

### 2024-06-14 article/hyphenpatches.tex
updates

\section{Hyphenation rule patches}\label{sec-hyph-rpatches}
We systematize the set of new rules in this section, and provide a few examples for
each instance. These rules are intended as a complement for the default \TeX{} hyphenation
rules created by \cite{hyphpt}.

\begin{rules}
\refstepcounter{numberRulesGroups}\item\label{rulegrp_gno} rule: \texttt{.g2no}, \texttt{.g2nó}, \texttt{.g2nô} -- \emph{gnomo}, \emph{gnóstico}, \emph{gnômon}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_tc} rule: \texttt{t2c} -- \emph{tchau}, \emph{tcheco}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_pneu} rule: \texttt{1p2neu} -- \emph{pneumonia}, \emph{pneumotórax}, \emph{pneumático}, \emph{hidropneumático}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_tm} rule: \texttt{.t2m} -- \emph{tmese}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_pt} rule: \texttt{.p2t} -- \emph{ptose}, \emph{pterossauro}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_mn} rule: \texttt{.m2n} -- \emph{mnemônico}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_cza} rule: \texttt{c2za} -- \emph{czar}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_s2} rule: \texttt{.s2} -- \emph{stalinismo}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_t2} rule: \texttt{.t2} -- tsunami, tzarista

\refstepcounter{numberRulesGroups}\item\label{rulegrp_psi} rule: \texttt{.p2si}, \texttt{.p2sí} -- \emph{psicologia}, \emph{psíquico} % update (word-initial pattern, exception not necessary (?)) 
%\item\label{rulegrp_psi} regra: \texttt{p2si}, \texttt{p2sí} -- psicologia, psíquico\\
%exceção: \texttt{p3sia}, \texttt{p3sin} -- epilepsia, rodopsina

\refstepcounter{numberRulesGroups}\item\label{rulegrp_sub} rule: \texttt{su2b3r}, \texttt{su2b3l} -- \emph{sublunar}, \emph{subrotina} \\
exception: \texttt{.su3b4li} -- \emph{sublinhar}, \emph{sublimar}
%exceção: \texttt{su3b4li1nh}, \texttt{su3b4li1ma}, \texttt{su3b4li1me}, \texttt{su3b4li1mid} -- sublinhar, sublimar, sublime, sublimidade

\refstepcounter{numberRulesGroups}\item\label{rulegrp_neo} rule: \texttt{.ne4o} -- \emph{neoliberal}, \emph{neonazista}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_pseu} rule: \texttt{1p2seu1d} -- \emph{pseudônimo}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_qu} rule: \texttt{1qu} -- \emph{enquanto}, \emph{inquieto}, \emph{farquhar}, \emph{qubit}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_air} rule: \texttt{a1ir.}, \texttt{u1ir.} -- \emph{sair}, \emph{extrair}, \emph{diminuir}, \emph{incluir}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_ain} rule: \texttt{a1ind}, \texttt{a1i1nh} -- \emph{ainda}, \emph{rainha}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_eim} rule: \texttt{e1imp} -- \emph{reimpresso}, \emph{teleimpressor}%, coimbra, coimperador
%exceção: \texttt{que2i}, \texttt{te2im} -- queimar, queimadura, teimosia, tirateima

\refstepcounter{numberRulesGroups}\item\label{rulegrp_ein} rule: \texttt{e1inc}, \texttt{e1inf}, \texttt{e1ing}, \texttt{e1ins}, \texttt{e1int}, \texttt{e1inv} -- \emph{reincidência}, \emph{reinfecção}, \emph{reingressa}, \emph{reinserção}, \emph{reintegração}, \emph{reinventar} 
%exceção: \texttt{e1in2st}, \texttt{e1in2sc} -- reinstalado, reinscrever

%\item\label{rulegrp_unit} rule: \texttt{u1int}, \texttt{u1ind} -- \emph{contribuinte}, \emph{excluindo}
%não precisa, temos a regra u1in

\refstepcounter{numberRulesGroups}\item\label{rulegrp_aiz} rule: \texttt{u1iz.}, \texttt{a1iz.} -- \emph{juiz}, \emph{raiz}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_proi} rule: \texttt{pro1i1b} -- proibição

\refstepcounter{numberRulesGroups}\item\label{rulegrp_Vi} rule: \texttt{tu1i}, \texttt{bu1i}, \texttt{nu1i}, \texttt{o1im}, \texttt{o1in}, \texttt{u1in}, \texttt{su1i}, \texttt{í1e}, \texttt{ju1i}, \texttt{fu1i}, \texttt{du1i}, \texttt{do1im}, \texttt{au1i}, \texttt{u1i1ç} -- \emph{intuitivo}, \emph{contribuidor}, \emph{ingenuidade}, \emph{coimbra}, \emph{coincide}, \emph{ruindade}, \emph{suicida}, \emph{píer}, \emph{juizado}, \emph{fuinha}, \emph{assiduidade}, \emph{amendoim}, \emph{cacauicultor}, \emph{constituição} \\
exception: \texttt{tu2id}, \texttt{tu2it}, \texttt{co2ima}, \texttt{o2i1na} -- \emph{gratuidade}, \emph{intuito}, \emph{coima}, \emph{boina}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_aa} rule: \texttt{a1â}, \texttt{a1ã}, \texttt{a1é}, \texttt{a1í}, \texttt{a1ó}, \texttt{a1ô}, \texttt{a1ú}, \texttt{e1á}, \texttt{e1â}, \texttt{e1ã}, \texttt{e1é}, \texttt{e1ê}, \texttt{e1í}, \texttt{e1ó}, \texttt{e1ô}, \texttt{e1ú}, \texttt{é1o}, \texttt{i1á}, \texttt{i1ã}, \texttt{i1é}, \texttt{i1í}, \texttt{i1ó}, \texttt{i1u}, \texttt{i1ú}, \texttt{í1a}, \texttt{í1o}, \texttt{o1á}, \texttt{o1ã}, \texttt{o1é}, \texttt{o1ê}, \texttt{o1í}, \texttt{o1ó}, \texttt{u1á}, \texttt{u1ã}, \texttt{u1â}, \texttt{u1é}, \texttt{u1ê}, \texttt{u1í}, \texttt{ú1o} --  \emph{abraâmico}, \emph{abraão}, \emph{aéreo}, \emph{país}, \emph{caótico}, \emph{faraônico}, \emph{saúde}, \emph{balneário}, \emph{oceânico}, \emph{campeã}, \emph{feérico}, \emph{veêm}, \emph{veículo}, \emph{teórico}, \emph{napoleônico}, \emph{conteúdo}, \emph{néon}, \emph{diário}, \emph{região}, \emph{soviético}, \emph{iídiche}, \emph{periódico}, \emph{feiura}, \emph{viúva}, \emph{maníaco}, \emph{íon}, \emph{razoável}, \emph{joão}, \emph{poético}, \emph{boêmia}, \emph{heroísmo}, \emph{alcoólico}, \emph{usuário}, \emph{itapuã}, \emph{lituânia}, \emph{suécia}, \emph{cauê}, \emph{suíça}, \emph{flúor} \\
exception: \texttt{1gu2á}, \texttt{1gu2ã}, \texttt{1gu2é}, \texttt{1gu2ê}, \texttt{1gu2í}, \texttt{1qu2á}, \texttt{1qu2ã}, \texttt{1qu2â}, \texttt{1qu2é}, \texttt{1qu2ê}, \texttt{1qu2í}, -- \emph{jaraguá}, \emph{saguão}, \emph{alguém}, \emph{português}, \emph{linguística}, \emph{aquático}, \emph{camaquã}, \emph{equânime}, \emph{inquérito}, \emph{sequência}, \emph{química} 
% the inclusion of rules e1é, é1o, i1í and í1a cause problem and if exceptions are necessary

%\item\label{rulegrp_gua} rule: \texttt{1gu2á}, \texttt{1gu2ã}, \texttt{1qu2ã} -- \emph{jaraguá}, \emph{saguão}, \emph{quão}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_bo} rule: \texttt{1bô}, \texttt{1cô}, \texttt{1çô}, \texttt{1dô}, \texttt{1fô}, \texttt{1gô}, \texttt{1lô}, \texttt{1pô}, \texttt{1mô}, \texttt{1nô}, \texttt{1rô}, \texttt{1sô}, \texttt{1tô}, \texttt{1vô}, \texttt{1xô}, \texttt{1zô} -- \emph{robô}, \emph{recôncavo}, \emph{maçônico}, \emph{judô}, \emph{telefônica}, \emph{xangô}, \emph{camelô}, \emph{capô}, \emph{sumô}, \emph{econômico}, \emph{subsônico}, \emph{tarô}, \emph{chatô}, \emph{vovô}, \emph{saxônia}, \emph{amazônia}

\refstepcounter{numberRulesGroups}\item\label{rulegrp_Vf} rule: \texttt{4a.}, \texttt{4e.}, \texttt{4o.} -- \emph{secretária}, \emph{planície}, \emph{paratormônio}

  % co1in (parace não ser necessário, já que o1in faz o seu papel)
  % cu1i (não faze sentido, já que temos cu2i)
  % ra1is (excluir, só existe a arrais e me parece que a forma correta é ar-rais)

%rules not necessary
%\item\label{rulegrp_cui} rule: \texttt{cu2i} -- \emph{cuidado} \\
%exception: \texttt{cu3in} -- \emph{picuinha}

%\item\label{rulegrp_aui} regra: \texttt{au1i1c}, \texttt{du1i1c}, \texttt{u1i1ç}, \texttt{u1i1d}, \texttt{cu2i}, \texttt{dru2i}, \texttt{flu2id}, \texttt{bu1i1n}, \texttt{cu1i1n}, \texttt{fu1i1n}, \texttt{nu1i1n}, \texttt{ru1i1na}, \texttt{ru1i1no}, \texttt{su1i1ti}, \texttt{tu1i1ti}, \texttt{u1iz} -- cacauicultor, sanduicheira, constituição, continuidade, cuidador, druida, fluido, tabuinha, picuinha, fuinha, genuinamente, arruinado, arruinou, jesuitismo, intuitivo, juizado \\ 
%exceção: \texttt{cu3i1da1de}, \texttt{bu1i2n1d}, \texttt{bu1i2n1t}  -- acuidade, contribuindo, contribuinte
% not necessary

%\item\label{rulegrp_oin} regra: \texttt{o1in} -- coincidência, agroindustrial, bioinformática, amendoins, gastrointestinal
%exceção: \texttt{oi1na} -- boina
% already includede

%\item\label{rulegrp_zz} regra: \texttt{z1z}, \texttt{p1p}, \texttt{z2z.} -- pizza, shopping, jazz
% not necessary

%\item\label{rulegrp_so} regra: \texttt{1sô} -- subsônico
% already included above

%\item\label{rulegrp_ein} regra: \texttt{e1in1c}, \texttt{e1in1f}, \texttt{e1in1g}, \texttt{e1in1s}, \texttt{e1in1t}, \texttt{e1in1v} -- reincidência, reinfecção, reingressa, reinserção, reintegração, reinventar \\
%exceção: \texttt{e1in2st}, \texttt{e1in2sc} -- reinstalado, reinscrever

%\item\label{rulegrp_ia} regra: \texttt{í1a} -- baía
% already included above

%\item\label{rulegrp_oin} regra: \texttt{o1i1nh} -- moinho
% not necessary, we have o1in and 1n2h

%\item\label{rulegrp_aui} regra: \texttt{au1i1c}, \texttt{du1i1c}, \texttt{u1i1ç}, \texttt{u1i1d}, \texttt{cu2i}, \texttt{dru2i}, \texttt{flu2id}, \texttt{bu1i1n}, \texttt{cu1i1n}, \texttt{fu1i1n}, \texttt{nu1i1n}, \texttt{ru1i1na}, \texttt{ru1i1no}, \texttt{su1i1ti}, \texttt{tu1i1ti}, \texttt{u1iz} -- cacauicultor, sanduicheira, constituição, continuidade, cuidador, druida, fluido, tabuinha, picuinha, fuinha, genuinamente, arruinado, arruinou, jesuitismo, intuitivo, juizado \\ 
%exceção: \texttt{cu3i1da1de}, \texttt{bu1i2n1d}, \texttt{bu1i2n1t}  -- acuidade, contribuindo, contribuinte
% not necessary

%\item\label{rulegrp_iur} regra: \texttt{i1ur} -- diurno
% not necessary

%\item\label{rulegrp_uo} regra: \texttt{ú1o} -- flúor
% not necessary

%\item\label{rulegrp_iun} regra: \texttt{i1un} -- triunfar
% not necessary

%\item\label{rulegrp_quo} regra: \texttt{1qu4ó}, \texttt{1qu4â} -- quórum, equânime
% created rule u1â and 1qu2â
% three is no word with u-ó, so rule u1ó is not necessary, therefore 1qu2ó is also not necessary

%\item\label{rulegrp_eo} regra: \texttt{é3o} -- alvéolo
% rule é1o included

%\item\label{rulegrp_ia} \st{regra: \texttt{i4a.}, \texttt{i4e.}, \texttt{i4o.}, \texttt{o4a.}, \texttt{u4a.} -- economia, espécie, vazio, destoa, institua}
% not necessary

%\item\label{rulegrp_lo} regra: \texttt{1lô} -- camelô

%\item\label{rulegrp_co} regra: \texttt{1cô} -- recôncavo

%\item\label{rulegrp_cco} regra: \texttt{1çô} -- maçônico
% included

% As sequências gráficas ia, ie, io, oa, ua quando em posição
% final átona, que são normalmente pronunciadas como ditongos
% crescentes, mas que podem corresponder foneticamente a duas
% vogais (hiato), sobretudo quando pronunciadas pausadamente:
% vitó-ria, espé-cie, exercí-cio, nó-doa, lé-gua, tê-nue, ambí-guo.
%\setcounter{numberRulesGroups}{\value{enumi}}
\end{rules}

% script to extract the rules above (inside \texttt{ })
% head -n 142 ../article/hyphenpatches.tex | grep -v "^%" | grep -oP '\\texttt\{.*?\}' | sed 's/\\texttt{//; s/}//' 
% meld <(head -n 142 ../article/hyphenpatches.tex | grep -v "^%" | grep -oP '\\texttt\{.*?\}' | sed 's/\\texttt{//; s/}//' | sort) <(sort ../data/patch.TeX.pt-br.patterns.v2)

The \NumberOfNewRules{} rules were grouped above in a list of
\thenumberRulesGroups\ types of rules. They may be further organized into five
large groups. The first, which comprises rules %\ref{rulegrp_gno} to \ref{rulegrp_t2}, 
\cref{rulegrp_gno,rulegrp_tc,rulegrp_pneu,rulegrp_tm,rulegrp_pt,rulegrp_mn,rulegrp_cza,rulegrp_s2,rulegrp_t2},
includes consonant clusters such as \emph{czar}, \emph{ptose}
and \emph{gnomo}. 
%They, unlike the examples that will be exposed in section \ref{secxxx} (exceptions - item 9 currently), present a set of derived words,
%which makes their marking advantageous in view of the number of cases that are included in this marking rule. 
The second group, comprising rules
%\ref{rulegrp_psi} to \ref{rulegrp_eim}, 
\cref{rulegrp_psi,rulegrp_sub,rulegrp_neo,rulegrp_pseu},
delimits the morphological boundary
between prefixes and radicals. As noted, although phonological issues guide the
separation of numerous words in Portuguese, there are also those that are
guided by morphology. This is the case of words that have the prefixes
\emph{sub-} and \emph{re-}, such as \emph{sublunar} and \emph{reinserção}. The
third group, comprising rules \cref{rulegrp_qu,rulegrp_air,rulegrp_ain,rulegrp_eim,rulegrp_ein,rulegrp_aiz,rulegrp_proi,rulegrp_Vi,rulegrp_aa}, seeks to
understand a set of words that have vowel combinations that do not follow the
general rules. This is because the Portuguese language has vowel encounters
with the second vowel graphically marked that can be separated, forming
hiatuses, such as \emph{caótico}, \emph{balneário} and \emph{razoável}, while
there are also words with a similar structure that constitute a diphthong, such
as \emph{português}, \emph{alguém} and \emph{linguística}. It is remarkable, of
course, that the latter are formed by the digraphs \emph{qu-} and \emph{gu-},
while the former by vowels other than \emph{i} and \emph{u}. The fourth group, 
in turn, which comprises \cref{rulegrp_aa,rulegrp_bo}\footnote{Note that \cref{rulegrp_aa} is in the intersection
between the third and fourth group of rules.}, 
which are counterparts of rules that were already in the
default rules, but did not contemplate the cases with certain accents. They
were then added to encompass words such as \emph{camelô}, \emph{recôncavo},
\emph{amazônia}, and \emph{maçônico}. 
The fifth, and last group, has just a single instance, \cref{rulegrp_Vf},
which represents our choice in how to deal the apparent proparoxytones,
avoiding a final hyphenation with the vowels \emph{a}, \emph{e}, or \emph{o}.

%It is important to highlight that the words included in these rules are, in
%general, of low frequency and were incorporated into the Portuguese language
%without a phonotactic adaptation, which causes these idiosyncrasies and
%exceptions to the language. They are characterized as marked cases, since it is
%not possible to defend that they reproduce a phonological pattern of the
%language because they are not productive, that is, they are not taken as an
%example and/or derive new words.

The set made of \NumberOfNewRules{} rules is presented below:
\begin{multicols}{6}
    \footnotesize
    \verbatiminput{../data/patch.TeX.pt-br.patterns}
\end{multicols}

\Cref{tab-resultados} presents the hyphenation errors in a set of 876 words.
We have omitted those words where both rules let to a correct hyphenation and
those that have incorrect hyphenation in a vowel in the last position. 
Once again, we are using the \emph{patgen} notation to mark correct, incorrect,
and missing hyphenation points: \texttt{*}, \texttt{.}, and \texttt{-}, respectively.
Incorrect or missing hyphenation points are considered errors. In these cases,
we place mark \xmark. Correct hyphenations are marked with \cmark.
The default rules achieved 17 correct hyphenations in this set, against 811 
of the patched rules.
%A Tabela \ref{tab-resultados} apresenta os erros cometidos no conjunto das
%37798 palavras analisadas. As palavras omitidas são aquelas que foram
%hifenizadas corretamente pelos dois conjuntos de regra. Utilizamos aqui a
%marcação adotada pelo \emph{Patgen}: \texttt{*} para indicar pontos de
%hifenização corretamente marcados, \texttt{.} para indicar pontos de hifenização
%marcados erroneamente e \texttt{-} para indicar pontos de hifenização não
%encontrados. 
%Os pontos marcados erroneamente e aqueles não encontrados são
%considerados erros. Quando ocorre algum erro de hifenização, marcaremos a
%palavra com \xmark. Quando não houver erro algum, marcaremos a palavra com
%\cmark. Ao final, podemos verificar que as regras padrão apresentaram 1368 erros
%(3,62\%) e as novas regras 132 erros (0,35\%).

### 2024-06-14 article/limitations.tex
updates

@@
 \begin{description} 
-    \item[Morphological determination:\label{morpho-det}] Prefixes such as \emph{re-},
+    \item [Morphological determination\label{morpho-det}] Prefixes such as \emph{re-},
 	\emph{sub-}, \emph{ciber-}, \emph{hiper-}, and \emph{auto-}, among others, require separating the
@@
 
-    \item[Foreignness:\label{foreignness}] There is a group of words %20 words 
+    \item [Foreignness\label{foreignness}] There is a group of words %20 words 
 	in the corpus that are terminologies or words incorporated into the 
@@
 
-    \item[Word-initial consonant clusters:\label{word-init-cc}] Portuguese has few cases of
+    \item [Word-initial consonant clusters\label{word-init-cc}] Portuguese has few cases of
 	consonant clusters at the beginning of a word. They are, in general, 
@@
 
-    \item[Abbreviations, Acronyms, or Initialisms:\label{abbrev}] 
+    \item [Abbreviations, Acronyms, or Initialisms\label{abbrev}] 
        Whether for efficiency, convenience, clarity, or specialized jargon, 

### 2024-06-14 article/patgenrules.tex
updates

@@
 As an example of execution, when choosing \texttt{hyph\_start}=1, \texttt{hyph\_finish}=9, \texttt{pat\_start}=2, \texttt{pat\_finish}=5,
-\texttt{good weight}=1, \texttt{bad weight}=1, and \texttt{threshold}=1, we achieve 99.97\%(86799) correct 
-hyphenations, 0.01\%(12) incorrect hyphenations, and 0.03\%(25) missing hyphenations.
-It produced a set of 799 rules, where just 123 are present in the handcrafted set of rules.
+\texttt{good weight}=1, \texttt{bad weight}=1, and \texttt{threshold}=1, we achieve 99.97\% (86799) correct 
+hyphenations, 0.01\% (12) incorrect hyphenations, and 0.03\% (25) missing hyphenations.
+It produced a set of 799 rules, where just 123 are present in our handcrafted set of rules.
 
@@
 Using this approach with the 8 level parameters they used to create hyphenation rules to German,
-we achieved 99.98\%(86820) correct hyphenations, 0.01\%(9) incorrect hyphenations, and 0.00\%(4) missed hyphenations.
+we achieved 99.98\% (86820) correct hyphenations, 0.01\% (9) incorrect hyphenations, and 0.00\% (4) missed hyphenations.
 The result was a set of 593 rules, with only 69 in common with those handcrafted rules proposed earlier.
@@
 is given \Cref{tbl-comres-hy3}.
+
 \begin{table}[h]
 \centering
-\caption{Compared results between two use cases of \emph{patgen} and the handcrafted rule set.}\label{tbl-comres-hy3}
+\caption{Compared results between two use cases of \emph{patgen} and the handcrafted rule set when hyphenating the set of words from the dictionary built from those words with 3 agreements on the online dictionaries.}\label{tbl-comres-hy3}
 \begin{tabular}{llll}
@@
 \end{table}
+
 It is important to hightlight that, among those 385 missing hyphenations in the handcrafted rules,

### 2024-06-14 article/resultsdefaultrules.tex
updates

@@
 the number of words correctly hyphenated words by the default rules, the number
-of words wrongly hyphenated and the number of words where a hyphenation point
+of words incorrectly hyphenated and the number of words where a hyphenation point
 was missed.
@@
 \toprule
-word list 	& \# correct 		& \# wrong 		& \# missing 		& \# entries 		\\
+word list 	& \# correct 		& \# incorrect		& \# missing 		& \# entries 		\\
 \midrule
@@
 
-For the list comprised in \texttt{hyphenations6}, below is the complete list of
-\NumberOfWrongSix{} words that were incorrectly hyphenated:
-% wrong
-\begin{multicols}{3}
-\setlength{\columnsep}{0pt}
-\setlength{\parindent}{0pt}
-\emph{
-    \input{/tmp/hyphenations6result-default-patterns_wrong.dic}
-}
-\end{multicols}
-In each instance, an erroneous hyphenation point was placed at the beginning of
-a word, indicating a potential issue in recognizing certain prefixing morphemes
-in the language.  Among those, 20 occurred in words containing the \emph{psi}
-morpheme, where the algorithm erroneously hyphenated between the initial
-\emph{p} and the following \emph{s}. Additionally, 3 cases involved the
-starting \emph{gno} sequence, while the remaining errors were observed in the
-sequences \emph{pneu} (3), \emph{tch} (1), \emph{tme} (1), \emph{pto} (1), and
-\emph{sub} (1).
-
-Those erroneous hyphenation points might be corrected by the introduction of a few rules:
-\texttt{.p2si, .p2sí} (see \cref{rulegrp_psi}), \texttt{.g2no, .g2nó} (see \cref{rulegrp_gno}), 
-\texttt{p2neu} (see \cref{rulegrp_pneu}),
-\texttt{t2c} (see \cref{rulegrp_tc}), \texttt{.t2m} (see \cref{rulegrp_tm}), \texttt{.p2t} (see \cref{rulegrp_pt}) 
-and \texttt{su2b3r}, \texttt{su2b3l}  (see \cref{rulegrp_sub}). They are deeply 
-discussed in \Cref{sec-hyph-rpatches}.
-
-% $ ../scripts/resultfileexamples.sh -m -f ../data/hyphenations6result-default-patterns.dic | grep -o "[^-]-[^-]" | sort | uniq -c | sort -nr | column
-
-The first 20 examples of missing hyphenations are displayed in the following list:
-% missing
-\begin{multicols}{3}
-\setlength{\columnsep}{0pt}
-\setlength{\parindent}{0pt}
-\emph{
-\input{/tmp/hyphenations6result-default-patterns_missing.dic}
-...
-}
-\end{multicols}
-It is a long list with \NumberOfMissingSix{} entries, therefore it is
-unavoidable to analyse it through clusters of certain patterns. It is presented
-below the counts of immediate context in which those missing hyphenations were
-found:
-\begin{multicols}{5}
-\setlength{\columnsep}{0pt}
-\setlength{\parindent}{0pt}
-\emph{
-\input{/tmp/hyphenations6result-default-patterns_missing_context}
-}
-\end{multicols}
-
-% number of words correctly hyphenated using default TeX rules when analysing the words in hyphenations6.dic
-%\captureshell*[\NumberOfCorrectSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -c}
-
-% number of words with wrong hyphenations using default TeX rules when analysing the words in hyphenations6.dic
-%\captureshell*[\NumberOfWrongSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -w}
-
-% number of words with missing hyphenations using default TeX rules when analysing the words in hyphenations6.dic
-%\captureshell*[\NumberOfMissingSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -m}
-
-% tra-b.a*lho
-%    ^ ^ ^
-%    | | |
-%    | | + -- correct (*)
-%    | + ---- wrong   (.)  
-%    + ------ missed  (-)
-
-On the top of the list we see the missing hyphen in \emph{u-i}, accounting for
-38 cases. Among those, 34 were originated from the pattern \texttt{u-ir} in the
-end of word and 13 from \texttt{a-ir} in the end of word. 
-To fix them, We will include the rules \texttt{u1ir.} and \texttt{a1ir.} (see 
-\cref{rulegrp_air}). The cases that are not covered by this rule are:
-\emph{tu-im}, \emph{je*su-i*tis*mo}, \emph{ma*lau-i*a*no}, and
-\emph{con*tri*bu-in*te}. On \Cref{sec-hyph-rpatches} we see how to deal with
-them.
-
-The default rules already include 17 separating rules for vowel sequences:
-% vowel="[aeiouáãàâéêíóõôú]"; grep "$vowel[13579]$vowel" ../data/default.TeX.pt-br.patterns | sed ':a;N;$!ba;s/\n/ \\\\ /g'
-\begin{multicols}{5}
-\setlength{\columnsep}{0pt}
-\setlength{\parindent}{0pt}
-\texttt{a3a \\ a3e \\ a3o \\ e3a \\ e3e \\ e3o \\ i3a \\ i3e \\ i3i \\ i3o \\ i3â \\ i3ê \\ i3ô \\ o3a \\ o3e \\ o3o \\ u3a \\ u3e \\ u3o \\ u3u}
-\end{multicols}
-but there are just 3 rules to hyphenate between vowels when one has a diacritic: \texttt{i3â}, \texttt{i3ê}, \texttt{i3ô}.
-We could then add more 29 rules to account for the missing hyphenations between vowels with diacritics and also the
-missing rule \texttt{i1u}:
-% ../scripts/resultfileexamples.sh -m -f ../data/hyphenations6result-default-patterns.dic | ../scripts/filtersurrounding.sh -c '-' -n 1 | sort | uniq -c | sort -nr | grep "[áàâãéêíóôõú]" | awk '{print $2}' | sort | sed ':a;N;$!ba;s/\n/ \\\\ /g'
-\begin{multicols}{5}
-\setlength{\columnsep}{0pt}
-\setlength{\parindent}{0pt}
-\texttt{
-% complete set of 37 rules
-%a1â \\ a1ã \\ a1é \\ a1í \\ a1ó \\ a1ô \\ a1ú \\ 
-%e1á \\ e1â \\ e1ã \\ e1é \\ e1ê \\ e1í \\ e1ó \\ e1ô \\ e1ú \\ é1o \\ 
-%i1á \\ i1ã \\ i1ã \\ i1é \\ i1í \\ i1ó \\ i1u \\ i1ú \\ í1a \\ 
-%o1á \\ o1ã \\ o1é \\ o1ê \\ o1í \\ o1ó \\ 
-%u1á \\ u1ã \\ u1é \\ u1ê \\ u1í \\ ú1o
-%
-% 29 rules necessary for hyphenations6 dic
-a1é \\ a1í \\ a1ó \\ a1ú \\ 
-e1á \\ e1â \\ e1ã \\ e1é \\ e1ê \\ e1í \\ e1ó \\ é1o \\ e1ú \\ 
-i1á \\ i1ã \\ í1a \\ i1é \\ i1í \\ i1ó \\ í1o \\ i1u \\ i1ú \\ 
-o1á \\ o1é \\ o1í \\ o1ó \\ 
-u1á \\ u1ã \\ u1í \\ ú1o
-}
-%\emph{a-é \\ a-í \\ a-ó \\ a-ú \\ e-á \\ e-â \\ e-ã \\ e-é \\ e-ê \\ e-í \\ e-ó \\ é-o \\ e-ú \\ i-á \\ i-ã \\ í-a \\ i-é \\ i-í \\ i-ó \\ í-o \\ i-ú \\ o-á \\ o-é \\ o-í \\ o-ó \\ u-á \\ u-ã \\ u-í \\ ú-o}
-\end{multicols}
-See more about this on \cref{rulegrp_aa}. These rules will require exceptions for sequences with \emph{[qg]uV'} 
-(where we used \emph{V'} to represent a vowel with a diacritic). See more on \cref{rulegrp_aa,rulegrp_gua}.
-
-From the list of missing hyphenations above, we find another recurring pattern, a missing hyphen preceding \emph{q}: 
-% ../scripts/resultfileexamples.sh -m -f ../data/hyphenations6result-default-patterns.dic | ../scripts/filtersurrounding.sh -c '-' -n 1 | sort | uniq -c | sort -nr | awk '{print $2}' | sort | grep "q$" | sort | sed ':a;N;$!ba;s/\n/ \\\\ /g'
-\begin{multicols}{5}
-\setlength{\columnsep}{0pt}
-\setlength{\parindent}{0pt}
-\emph{a-q \\ e-q \\ i-q \\ o-q \\ r-q \\ s-q \\ u-q}
-\end{multicols}
-That issue might be easily solved by adding a hyphenation rule: \texttt{1qu}, but as the \emph{q} is always followed by 
-a sequence \emph{uV}, and there are already four hyphenation rules involving this sort of sequence in the default rules
-(\texttt{1qu4a}, \texttt{1qu4e}, \texttt{1qu4i} and \texttt{1qu4o}), the rules 
-% $ grep "q" ../data/patch.TeX.pt-br.patterns | awk '{print "\\texttt{" $1 "}"}' | sed ':a;N;$!ba;s/\n/, /g'
-\texttt{1qu2á}, \texttt{1qu2é}, \texttt{1qu2ê}, \texttt{1qu2í}, \texttt{que2i}, \texttt{1qu4ã}, \texttt{1qu4ó}, \texttt{1qu4â}
-could be added (see \cref{rulegrp_aa,rulegrp_gua,rulegrp_quo}) but they have not proven to be necessary.
-%%% XXX check if they are not really necessary
-
-The missing hyphens in \emph{a-v} and \emph{i-v} might be easily solved by introducing the rule \texttt{1vô} (see \cref{rulegrp_bo}) which 
-complements the rule \texttt{1vo} already included in the default set of rules.
-% pi-vô, a-vô, bi*sa-vô ...
-Similarly, the missing hyphens \emph{e-l}, \emph{u-l}, \emph{o-l}, and \emph{a-l} are corrected by the introduction of the rule \texttt{1lô} rule (see \cref{rulegrp_bo}),
-complementing the already included rule \texttt{1lo}.
-In the same way, the rules \texttt{1cô}, \texttt{1gô}, \texttt{1bô}, \texttt{1tô}, \texttt{1rô}, and \texttt{1pô} (see \cref{rulegrp_bo}) 
-should be added to fix the missing hyphens \emph{e-c}, \emph{i-c}, \emph{o-g}, \emph{o-b}, \emph{a-t}, \emph{a-r},
-and \emph{a-p}, respectively.
-% ca*me-lô, gi*go-lô, ..., bi*be-lô, su.b-lu*nar
-%                                       rule 1b2l causes wrong hyphen
-%
-%    .   s   u   b   l   u   n   a   r   .
-%     1   0   0   |   |   |   |   |   |    1su
-%     |   |   1   2   0   |   |   |   |    1b2l
-%     |   |   |   1   0   0   |   |   |    1lu
-%     |   |   |   |   |   1   0   0   |    1na
-%max: 1   0   1   2   0   1   0   0   0
-%final: s   u - b   l   u - n   a   r
-The missing hyphen \emph{b-l} happened in \emph{su.b-lu*nar}, which also has a wrong hyphenation.
-Those errors were caused by the default rule \texttt{1b2l}. The introduction of rule \texttt{su2b3l} 
-will help solve this matter (see details in \cref{rulegrp_sub}).
-
-% e-c, i-c: missing rule 1cô
-% o-g: missing rule 1gô
-% o-b: missing rule 1bô
-% a-t: missing rule 1tô
-% a-r: missing rule 1rô
-% a-p: missing rule 1pô
-
-The remaining missing hyphen is \emph{o-w}, which comes from the foreign \emph{kilowatt}.
-Those cases of words borrowed from other languages are dealt in the \ref{foreignness} topic ahead.
-% o-w: qui*lo-watt
-
-% number of words with missing hyphenations using default TeX rules when analysing the words in hyphenations6.dic
+Each word in the list is hyphenated using the set of default rules using the \texttt{gohyphen} script
+(the \texttt{gohyphenfull} script is used to see in the interplay among all rules that apply to a given word) \parencite{gundlach2021}.
+The hyphenation resulted from the given rules is compared to the hyphenation in our dictionary, so
+we may check if there were erros (incorrect or missing hyphenation points).

### 2024-06-14 article/updatingrules.tex
updates

@@
 \section{Updating the rules}
-We now begin incorporating the rules proposed in the previous section and
-appraise the results of each one. During this process, we will consider the
-necessity of updating those rules, including exceptions, or even discarding the
-proposed rules if needed.
+
+In this section we will analyse the results of the default rules on our dictionaries,
+find patterns, and gradually incorporate new rules to the set, appraising the result of
+each one, to avoid causing more damage than good, create exception rules when necessary,
+and, if necessary, discard rules. We will stick to the \emph{patgen} notation to express
+a wrong, a missing, and a correct hyphenation point (`.', `-', and `*', respectively).
+
+For the list comprised in \texttt{hyphenations6}, below is the complete list of
+\NumberOfWrongSix{} words that were incorrectly hyphenated:
+% wrong
+\begin{multicols}{3}
+\setlength{\columnsep}{0pt}
+\setlength{\parindent}{0pt}
+\emph{\input{/tmp/hyphenations6result-default-patterns_wrong.dic}}
+\end{multicols}
+In each instance, an erroneous hyphenation point was placed at the beginning of
+a word, indicating a potential issue in recognizing certain prefixing morphemes
+in the language.  Among those, 20 occurred in words containing the \emph{psi}
+morpheme, where the algorithm erroneously hyphenated between the initial
+\emph{p} and the following \emph{s}. Additionally, 3 cases involved the
+starting \emph{gno} sequence, while the remaining errors were observed in the
+sequences \emph{pneu} (3), \emph{tch} (1), \emph{tme} (1), \emph{pto} (1), and
+\emph{sub} (1).
+
+Those erroneous hyphenation points might be corrected by the introduction of a few rules:
+\texttt{.p2si, .p2sí} (see \cref{rulegrp_psi}), \texttt{.g2no, .g2nó} (see \cref{rulegrp_gno}), 
+\texttt{1p2neu} (see \cref{rulegrp_pneu}),
+\texttt{t2c} (see \cref{rulegrp_tc}), \texttt{.t2m} (see \cref{rulegrp_tm}), \texttt{.p2t} (see \cref{rulegrp_pt}) 
+and \texttt{su2b3r}, \texttt{su2b3l}  (see \cref{rulegrp_sub}). They are deeply 
+discussed in \Cref{sec-hyph-rpatches}.
+
+% $ ../scripts/resultfileexamples.sh -m -f ../data/hyphenations6result-default-patterns.dic | grep -o "[^-]-[^-]" | sort | uniq -c | sort -nr | column
+
+The first 20 examples of missing hyphenations are displayed in the following list:
+% missing
+\begin{multicols}{3}
+\setlength{\columnsep}{0pt}
+\setlength{\parindent}{0pt}
+\emph{\input{/tmp/hyphenations6result-default-patterns_missing.dic}
+...}
+\end{multicols}
+It is a long list with \NumberOfMissingSix{} entries, therefore it is
+unavoidable to analyse it through clusters of certain patterns. It is presented
+below the counts of immediate context in which those missing hyphenations were
+found:
+\begin{multicols}{5}
+\setlength{\columnsep}{0pt}
+\setlength{\parindent}{0pt}
+\emph{\input{/tmp/hyphenations6result-default-patterns_missing_context}}
+\end{multicols}
+
+% number of words correctly hyphenated using default TeX rules when analysing the words in hyphenations6.dic
+%\captureshell*[\NumberOfCorrectSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -c}
+
+% number of words with wrong hyphenations using default TeX rules when analysing the words in hyphenations6.dic
+%\captureshell*[\NumberOfWrongSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -w}
+
+% number of words with missing hyphenations using default TeX rules when analysing the words in hyphenations6.dic
+%\captureshell*[\NumberOfMissingSix]{../scripts/resultfilemetrics.sh -f ../data/hyphenations6result-default-patterns.dic -m}
+
+% tra-b.a*lho
+%    ^ ^ ^
+%    | | |
+%    | | + -- correct (*)
+%    | + ---- wrong   (.)  
+%    + ------ missed  (-)
+
+On the top of the list we see the missing hyphen in \emph{u-i}, accounting for
+38 cases. Among those, 34 were originated from the pattern \texttt{u-ir} in the
+end of word and 13 from \texttt{a-ir} in the end of word. 
+To fix them, We will include the rules \texttt{u1ir.} and \texttt{a1ir.} (see 
+\cref{rulegrp_air}). The cases that are not covered by this rule are:
+\emph{tu-im}, \emph{je*su-i*tis*mo}, \emph{ma*lau-i*a*no}, and
+\emph{con*tri*bu-in*te}. On \cref{rulegrp_Vi} we see how to deal with
+them.
+
+The default rules already include 17 separating rules for vowel sequences:
+% vowel="[aeiouáãàâéêíóõôú]"; grep "$vowel[13579]$vowel" ../data/default.TeX.pt-br.patterns | sed ':a;N;$!ba;s/\n/ \\\\ /g'
+\begin{multicols}{5}
+\setlength{\columnsep}{0pt}
+\setlength{\parindent}{0pt}
+\texttt{a3a \\ a3e \\ a3o \\ e3a \\ e3e \\ e3o \\ i3a \\ i3e \\ i3i \\ i3o \\ i3â \\ i3ê \\ i3ô \\ o3a \\ o3e \\ o3o \\ u3a \\ u3e \\ u3o \\ u3u}
+\end{multicols}
+\noindent{}but there are just 3 rules to hyphenate between vowels when one has a diacritic: \texttt{i3â}, \texttt{i3ê}, \texttt{i3ô}.
+We could then add more 29 rules to account for the missing hyphenations between vowels with diacritics and also the
+missing rule \texttt{i1u}:
+% ../scripts/resultfileexamples.sh -m -f ../data/hyphenations6result-default-patterns.dic | ../scripts/filtersurrounding.sh -c '-' -n 1 | sort | uniq -c | sort -nr | grep "[áàâãéêíóôõú]" | awk '{print $2}' | sort | sed ':a;N;$!ba;s/\n/ \\\\ /g'
+\begin{multicols}{5}
+\setlength{\columnsep}{0pt}
+\setlength{\parindent}{0pt}
+\texttt{%
+% complete set of 37 rules
+%a1â \\ a1ã \\ a1é \\ a1í \\ a1ó \\ a1ô \\ a1ú \\ 
+%e1á \\ e1â \\ e1ã \\ e1é \\ e1ê \\ e1í \\ e1ó \\ e1ô \\ e1ú \\ é1o \\ 
+%i1á \\ i1ã \\ i1ã \\ i1é \\ i1í \\ i1ó \\ i1u \\ i1ú \\ í1a \\ 
+%o1á \\ o1ã \\ o1é \\ o1ê \\ o1í \\ o1ó \\ 
+%u1á \\ u1ã \\ u1é \\ u1ê \\ u1í \\ ú1o
+%
+% 29 rules necessary for hyphenations6 dic
+a1é \\ a1í \\ a1ó \\ a1ú \\ 
+e1á \\ e1â \\ e1ã \\ e1é \\ e1ê \\ e1í \\ e1ó \\ e1ú \\ é1o \\ 
+i1á \\ i1ã \\ í1a \\ i1é \\ i1í \\ i1ó \\ i1u \\ i1ú \\ í1o \\ 
+o1á \\ o1é \\ o1í \\ o1ó \\ 
+u1á \\ u1ã \\ u1í \\ ú1o
+}
+%\emph{a-é \\ a-í \\ a-ó \\ a-ú \\ e-á \\ e-â \\ e-ã \\ e-é \\ e-ê \\ e-í \\ e-ó \\ é-o \\ e-ú \\ i-á \\ i-ã \\ í-a \\ i-é \\ i-í \\ i-ó \\ í-o \\ i-ú \\ o-á \\ o-é \\ o-í \\ o-ó \\ u-á \\ u-ã \\ u-í \\ ú-o}
+\end{multicols}
+See more about this on \cref{rulegrp_aa}. These rules will require exceptions for sequences with \emph{[qg]uV'} 
+(where we used \emph{V'} to represent a vowel with a diacritic). See more on \cref{rulegrp_aa}.
+
+From the list of missing hyphenations above, we find another recurring pattern, a missing hyphen preceding \emph{q}: 
+% ../scripts/resultfileexamples.sh -m -f ../data/hyphenations6result-default-patterns.dic | ../scripts/filtersurrounding.sh -c '-' -n 1 | sort | uniq -c | sort -nr | awk '{print $2}' | sort | grep "q$" | sort | sed ':a;N;$!ba;s/\n/ \\\\ /g'
+\begin{multicols}{5}
+\setlength{\columnsep}{0pt}
+\setlength{\parindent}{0pt}
+\emph{a-q \\ e-q \\ i-q \\ o-q \\ r-q \\ s-q \\ u-q}
+\end{multicols}
+That issue might be easily solved by adding a hyphenation rule \texttt{1qu}. The \emph{q} is always followed by 
+a sequence \emph{uV}, and there are already four hyphenation rules involving this sort of sequence in the default rules
+(\texttt{1qu4a}, \texttt{1qu4e}, \texttt{1qu4i} and \texttt{1qu4o})\footnote{The default rules uses level three to hyphenate
+between those vowels: \texttt{u3a}, \texttt{u3e}, \texttt{u3i}, and \texttt{u3o}. Apparently, they could have used 
+a lower degree rule and, consequently, a lower degree rule to discourage the hyphen in sequences with \emph{q} or \emph{q}}. 
+The only valid exceptions\footnote{The other exceptions we are not considering include typos and proper names (names of places, for example \emph{Urquhart}, \emph{
+Qurgonteppa
+}, \emph{Al-Qusayr}, etc.).} found in Wikipedia corpus are
+the words \emph{far-quhar} and \emph{qu-bit}. We could then add the rule \texttt{1qu} along with the exception rules
+for those hyphenation rules between \emph{u} and the following vowel (see \cref{rulegrp_aa}):
+% $ grep "q" ../data/patch.TeX.pt-br.patterns | awk '{print "\\texttt{" $1 "}"}' | sed ':a;N;$!ba;s/\n/, /g'
+\texttt{1qu2á}, \texttt{1qu2ã}, \texttt{1qu2â}, \texttt{1qu4é}, \texttt{1qu2ê}, and \texttt{1qu2í} (see \cref{rulegrp_aa}). 
+Note that \texttt{1qu2ó} was not added since we will not use a rule to hyphenate between these vowels.
+%since there are rules to create hyphenation points between \emph{u} and the following vowel (see \cref{rulegrp_aa}).  
+%could be added (see \cref{rulegrp_aa,rulegrp_quo}), but they have not necessary at this moment.
+%%% XXX check if they are not really necessary
+% cut -d, -f1 ../data/hyphenations.csv | grep -Po "qu[aeioáéíóâêôãõ]" | sort | uniq -c | column
+% 1354 qua          52 quá           8 quâ           3 quã        4411 que          99 qué          79 quê        3655 qui         224 quí         102 quo           9 quó
+
+The missing hyphens in \emph{a-v} and \emph{i-v} might be easily solved by introducing the rule \texttt{1vô} (see \cref{rulegrp_bo}) which 
+complements the rule \texttt{1vo} already included in the default set of rules.
+% pi-vô, a-vô, bi*sa-vô ...
+Similarly, the missing hyphens \emph{e-l}, \emph{u-l}, \emph{o-l}, and \emph{a-l} are corrected by the introduction of the rule \texttt{1lô} rule (see \cref{rulegrp_bo}),
+complementing the already included rule \texttt{1lo}.
+In the same way, the rules \texttt{1cô}, \texttt{1gô}, \texttt{1bô}, \texttt{1tô}, \texttt{1rô}, and \texttt{1pô} (see \cref{rulegrp_bo}) 
+should be added to fix the missing hyphens \emph{e-c}, \emph{i-c}, \emph{o-g}, \emph{o-b}, \emph{a-t}, \emph{a-r},
+and \emph{a-p}, respectively.
+% ca*me-lô, gi*go-lô, ..., bi*be-lô, su.b-lu*nar
+%                                       rule 1b2l causes wrong hyphen
+%
+%    .   s   u   b   l   u   n   a   r   .
+%     1   0   0   |   |   |   |   |   |    1su
+%     |   |   1   2   0   |   |   |   |    1b2l
+%     |   |   |   1   0   0   |   |   |    1lu
+%     |   |   |   |   |   1   0   0   |    1na
+%max: 1   0   1   2   0   1   0   0   0
+%final: s   u - b   l   u - n   a   r
+The missing hyphen \emph{b-l} happened in %\emph{su.b-lu*nar}
+\emph{su.b-lu*nar}, which also has a wrong hyphenation.
+Those errors were caused by the default rule \texttt{1b2l}. The introduction of rule \texttt{su2b3l} 
+will help solve this matter (see details in \cref{rulegrp_sub}).
+
+% e-c, i-c: missing rule 1cô
+% o-g: missing rule 1gô
+% o-b: missing rule 1bô
+% a-t: missing rule 1tô
+% a-r: missing rule 1rô
+% a-p: missing rule 1pô
+
+The remaining missing hyphen is \emph{o-w}, which comes from the foreign \emph{kilo-watt}.
+Those cases of words borrowed from other languages are dealt in the topic \ref{foreignness}.
+% o-w: qui*lo-watt
+
+% number of words with missing hyphenations using default TeX rules when analysing the words in hyphenations6.dic
 
@@
 
-% cat ../data/default.TeX.pt-br.patterns <(echo -e "p2si\np2sí\n.g2no\n.g2nó\nt2c\np2neu\n.t2m\n.p2t\nsu2b3r\nsu2b3l") > /tmp/patts
+% cat ../data/default.TeX.pt-br.patterns <(echo -e "p2si\np2sí\n.g2no\n.g2nó\nt2c\n1p2neu\n.t2m\n.p2t\nsu2b3r\nsu2b3l") > /tmp/patts
 % ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts > /tmp/hyphenations6result_001.dic
@@
 %
-% cat ../data/default.TeX.pt-br.patterns <(echo -e ".p2si\n.p2sí\n.g2no\n.g2nó\nt2c\np2neu\n.t2m\n.p2t\nsu2b3r\nsu2b3l") > /tmp/patts
+% cat ../data/default.TeX.pt-br.patterns <(echo -e ".p2si\n.p2sí\n.g2no\n.g2nó\nt2c\n1p2neu\n.t2m\n.p2t\nsu2b3r\nsu2b3l") > /tmp/patts
 % ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts > /tmp/hyphenations6result_001.dic
@@
 After introducing the rules: \texttt{.p2si}, \texttt{.p2sí}, \texttt{.g2no}, \texttt{.g2nó}, \texttt{t2c}, 
-\texttt{p2neu}, \texttt{.t2m}, \texttt{.p2t}, \texttt{su2b3r}, and \texttt{su2b3l}, 
+\texttt{1p2neu}, \texttt{.t2m}, \texttt{.p2t}, \texttt{su2b3r}, and \texttt{su2b3l}, 
 the number of incorrect hyphenations decreased to 3, and the number of missing hyphenations decreased to 278.
@@
 the introduction of rule \texttt{su2b3l} introduced hyphenation errors in \emph{su-b.li*me}, \emph{su-b.li*ma*ção} and \emph{su-b.li*ma*do}.
+%\emph{sublime}, \emph{sublimação}, and \emph{sublimado}.
+%\emph{su-b.li*me}, \emph{su-b.li*ma*ção} and \emph{su-b.li*ma*do}.
 
@@
 as illustrated in \Cref{sublimehyphenation}. This adjustment resulted in zero hyphenation errors and 276 missing hyphens.
-% cat ../data/default.TeX.pt-br.patterns <(echo -e ".p2si\n.p2sí\n.g2no\n.g2nó\nt2c\np2neu\n.t2m\n.p2t\nsu2b3r\nsu2b3l\n.su3b4li") > /tmp/patts
+% cat ../data/default.TeX.pt-br.patterns <(echo -e ".p2si\n.p2sí\n.g2no\n.g2nó\nt2c\n1p2neu\n.t2m\n.p2t\nsu2b3r\nsu2b3l\n.su3b4li") > /tmp/patts
 % ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts > /tmp/hyphenations6result_001.dic
@@
 
-The next step is to introduce the rules o address the missing hyphenation points. These rules are: 
-\texttt{a1ir.}, \texttt{u1ir.}, \texttt{i3â}, \texttt{i3ê}, \texttt{i3ô}, \texttt{1qu}, \texttt{1vô}, \texttt{1lô}, \texttt{1cô}, \texttt{1gô}, \texttt{1bô}, 
+The next step is to introduce the rules to address the missing hyphenation points. These rules are: 
+\texttt{a1ir.}, \texttt{u1ir.}, \texttt{1qu}, \texttt{1vô}, \texttt{1lô}, \texttt{1cô}, \texttt{1gô}, \texttt{1bô}, 
 \texttt{1tô}, \texttt{1rô}, \texttt{1pô}, \texttt{a1é}, \texttt{a1í}, \texttt{a1ó}, \texttt{a1ú}, \texttt{e1á}, \texttt{e1â}, \texttt{e1ã}, 
@@
 % \texttt{1gu2é}, \texttt{1gu2ê}, \texttt{1gu2í} 
-% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o" | tr -d ' ' | tr ',' '\n') > /tmp/patts2
+% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, 1p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o" | tr -d ' ' | tr ',' '\n') > /tmp/patts2
 % %%% a1â, a1ã, a1é, a1í, a1ó, a1ô, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, e1ô, e1ú, é1o, i1á, i1ã, i1é, i1í, i1ó, i1u, i1ú, í1a, o1á, o1ã, o1é, o1ê, o1í, o1ó, u1á, u1ã, u1é, u1ê, u1í, ú1o
@@
 After inserting these rules, the number of incorrect hyphenations increases to 18 due to the inclusion of hyphens in \emph{qu.í}, \emph{gu.í} and \emph{qu.á}. 
-To overcome these errors, we need to add exception rules: \texttt{1qu2á}, \texttt{1qu2í}, and \texttt{1gu2í}.
-See more on this on \cref{rulegrp_aa,rulegrp_gua}.
-% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í" | tr -d ' ' | tr ',' '\n') > /tmp/patts3
+To overcome these errors, we need to add the exception rules: \texttt{1qu2á}, \texttt{1qu2í}, and \texttt{1gu2í}.
+See more on this on \cref{rulegrp_aa}.
+% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, 1p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í" | tr -d ' ' | tr ',' '\n') > /tmp/patts3
 % ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts3 > /tmp/hyphenations6result_003.dic
@@
 \texttt{e1inc}, \texttt{e1inf}, \texttt{e1ing}, \texttt{e1ins}, \texttt{e1int}, \texttt{e1inv}, (see \cref{rulegrp_ein}), 
-\texttt{u1int}, \texttt{u1ind} (see \cref{rulegrp_unit}), and \texttt{u1iz.}, \texttt{a1iz.} (see \cref{rulegrp_aiz}).
+%\texttt{u1int}, \texttt{u1ind} (see \cref{rulegrp_unit}),  (not necessary since we have the rule u1in)
+and \texttt{u1iz.}, \texttt{a1iz.} (see \cref{rulegrp_aiz}).
 % rulegrp_ain regra: a1ind, a1i1nh – ainda, rainha
@@
 
-% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz." | tr -d ' ' | tr ',' '\n') > /tmp/patts4
+% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, 1p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz." | tr -d ' ' | tr ',' '\n') > /tmp/patts4
 % ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts4 > /tmp/hyphenations6result_004.dic
@@
 avoiding the final hyphen which leaves the vowels \emph{a}, \emph{e} or \emph{o} alone in the last syllable.
-To address this, we introduce rules \texttt{4a.}, \texttt{4e.}, \texttt{4o.} (see \cref{rulesxxx}).
+To address this, we introduce rules \texttt{4a.}, \texttt{4e.}, \texttt{4o.} (see \cref{rulegrp_Vf}).
 While a more comprehensive rule set could be developed to account for all scenarios\footnote{A better rule would be to restrain the final hyphenation, leaving the vowel alone, if the preceding syllable has a vowel with diacritic.
 That would require an exhaustive list of all scenarios.}, we opted for these more concise rules despite their limitations.
-% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o." | tr -d ' ' | tr ',' '\n') > /tmp/patts5
+Note that, this set of three rules might be easily suppressed if someone intend to get the final vowel hyphenated.
+% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, 1p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o." | tr -d ' ' | tr ',' '\n') > /tmp/patts5
 % ./gocreateresultfile.sh ../data/hyphenations5.dic /tmp/patts5 > /tmp/hyphenations5result_005.dic
@@
 \end{multicols}
-\noindent{}From these, we have proposed the rules: \texttt{1gu4á}, \texttt{1gu4ã}, \texttt{1qu4ã} (see \cref{rulegrp_gua}),
+\noindent{}From these, we have proposed the rules: \texttt{1gu2á}, \texttt{1gu2ã}, \texttt{1qu2ã} (see \cref{rulegrp_aa}),
 \texttt{.m2n} (see \cref{rulegrp_mn}), \texttt{c2za} (see \cref{rulegrp_cza}), \texttt{.s2} (see \cref{rulegrp_s2}), and \texttt{1p2seu1d} (see \cref{rulegrp_pseu}).
@@
 % regra: 1p2seu1d – pseudônimo
-% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d" | tr -d ' ' | tr ',' '\n') > /tmp/patts6
+% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, 1p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d" | tr -d ' ' | tr ',' '\n') > /tmp/patts6
 % ./gocreateresultfile.sh ../data/hyphenations5.dic /tmp/patts6 > /tmp/hyphenations5result_006.dic
@@
 We observe that a few additional rules with diacritic counterpart need to be introduced: 
-\texttt{1dô}, \texttt{1fô}, \texttt{1mô}, \texttt{1nô}, \texttt{1sô}, \texttt{1zô} (see \cref{xxx}), 
+\texttt{1dô}, \texttt{1fô}, \texttt{1mô}, \texttt{1nô}, \texttt{1sô}, \texttt{1zô} (see \cref{rulegrp_bo}), 
 %\texttt{1ên} (see \cref{}), 
-\texttt{u3é}, \texttt{1gu4é}, \texttt{1qu4é} (see \cref{xxxx}).
-% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, u3é, 1gu4é, 1qu4é" | tr -d ' ' | tr ',' '\n') > /tmp/patts7
+\texttt{u1é}, \texttt{1gu2é}, \texttt{1qu2é} (see \cref{rulegrp_aa}).
+% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, 1p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, 1gu2é, 1qu2é" | tr -d ' ' | tr ',' '\n') > /tmp/patts7
 % ./gocreateresultfile.sh ../data/hyphenations5.dic /tmp/patts7 > /tmp/hyphenations5result_007.dic
@@
 To account for a few more missing cases, we propose the inclusion of the following rules: 
-\texttt{tu1i}, \texttt{bu1i}, \texttt{co1in}, \texttt{nu1i}, \texttt{cu1i}, \texttt{o1in}, \texttt{u1in}, \texttt{su1i}, \texttt{í1e}, \texttt{ra1is},
-\texttt{ju1i}, \texttt{fu1i}, \texttt{du1i}, \texttt{do1im}, \texttt{au1i}, \texttt{u1i1ç}.
-% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, u3é, 1gu4é, 1qu4é, tu1i, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç" | tr -d ' ' | tr ',' '\n') > /tmp/patts8
+\texttt{tu1i}, \texttt{bu1i}, %\texttt{co1in}, 
+\texttt{nu1i}, %\texttt{cu1i}, 
+\texttt{o1in}, \texttt{u1in}, \texttt{su1i}, \texttt{í1e}, %\texttt{ra1is},
+\texttt{ju1i}, \texttt{fu1i}, \texttt{du1i}, \texttt{do1im}, \texttt{au1i}, \texttt{u1i1ç} (see \cref{rulegrp_Vi}).
+% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, 1p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, 1gu2é, 1qu2é, tu1i, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç" | tr -d ' ' | tr ',' '\n') > /tmp/patts8
 % ./gocreateresultfile.sh ../data/hyphenations5.dic /tmp/patts8 > /tmp/hyphenations5result_008.dic
@@
 With these additions, the number of missing hyphenations drops to 818, with 772 cases involving final vowels,
-as mentioned earlier. Among these, only two cases involve a final vowel with a diacritic: \emph{fu*zu-ê} and \emph{ba*ba*la-ô}).
+as mentioned earlier.
+Among these, only two cases involve a final vowel with a diacritic: \emph{fu*zu-ê} and \emph{ba*ba*la-ô}.
+% \emph{fuzuê} and \emph{babalaô}.
+%\emph{fu*zu-ê} and \emph{ba*ba*la-ô}.
 The list of the remaining 46 follows:
@@
 \end{multicols}
-From this list, we may create a new rule: \texttt{u1ê}, which would also require two exception rules: \texttt{gu2ê} and \texttt{qu2ê}.
+From this list, we may create a new rule: \texttt{u1ê}, which would also require two exception rules: \texttt{1gu2ê} and \texttt{1qu2ê}.
 % rules: u1ê (u3ê, since the default rule has a u3e)
-%   exception rules: gu2ê, qu2ê
+%   exception rules: 1gu2ê, 1qu2ê
 %
-% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, u3é, 1gu4é, 1qu4é, tu1i, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç, u1ê, gu2ê, qu2ê" | tr -d ' ' | tr ',' '\n') > /tmp/patts9
+% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, 1p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, 1gu2é, 1qu2é, tu1i, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç, u1ê, 1gu2ê, 1qu2ê" | tr -d ' ' | tr ',' '\n') > /tmp/patts9
 % ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts9 > /tmp/hyphenations6result_009.dic
@@
 
-% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, .g2nô, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, u3é, 1gu4é, 1qu4é, tu1i, tu2it, tu2id, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç, u1ê, gu2ê, qu2ê, 1çô, u1é, 1gu2é, 1qu2é, 1xô, a1â, a1ã, a1ô, cu2i, cu3in, e1ô, .ne4o, o1ã, o1ê, o1im, o2i1na, pro1i1b, co2ima" | tr -d ' ' | tr ',' '\n') > /tmp/patts10
+% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, .g2nô, t2c, 1p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, 1gu2é, 1qu2é, tu1i, tu2it, tu2id, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç, u1ê, 1gu2ê, 1qu2ê, 1çô, u1é, 1gu2é, 1qu2é, 1xô, a1â, a1ã, a1ô, cu2i, cu3in, e1ô, .ne4o, o1ã, o1ê, o1im, o2i1na, pro1i1b, co2ima" | tr -d ' ' | tr ',' '\n') > /tmp/patts10
 
-% echo ".p2si, .p2sí, .g2no, .g2nó, .g2nô, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, u3é, 1gu4é, 1qu4é, tu1i, tu2it, tu2id, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç, u1ê, gu2ê, qu2ê, 1çô, u1é, 1gu2é, 1qu2é, 1xô, a1â, a1ã, a1ô, cu2i, cu3in, e1ô,.ne4o, o1ã, o1ê, o1im, o2i1na, pro1i1b, co2ima" | tr -d ' ' | tr ',' '\n' > ../data/patch.TeX.pt-br.patterns.v2
+% echo ".p2si, .p2sí, .g2no, .g2nó, .g2nô, t2c, 1p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, 1gu2é, 1qu2é, tu1i, tu2it, tu2id, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç, u1ê, 1gu2ê, 1qu2ê, 1çô, u1é, 1gu2é, 1qu2é, 1xô, a1â, a1ã, a1ô, cu2i, cu3in, e1ô,.ne4o, o1ã, o1ê, o1im, o2i1na, pro1i1b, co2ima" | tr -d ' ' | tr ',' '\n' > ../data/patch.TeX.pt-br.patterns.v2
 
-% cat ../data/default.TeX.pt-br.patterns ../data/patch.TeX.pt-br.patterns.v2 > ../data/patched-default.TeX.pt-br.patterns.v2
+% sed -e '$e cat ../data/patch.TeX.pt-br.patterns.v2' ../data/default.TeX.pt-br.patterns > ../data/patched-default.TeX.pt-br.patterns.v2
 
@@
 be incorporated: 
-\texttt{1çô} (e.g., \emph{ma-çô-ni-co}), 
-\texttt{1xô} (e.g., \emph{a-xô-nio}, \emph{sa-xô-ni-co}),
-\texttt{a1â} (e.g., \emph{a-bra-â-mi-co}), 
-\texttt{a1ã} (e.g., \emph{a-bra-ão}, \emph{ca-na-ã}), 
-\texttt{a1ô} (e.g., \emph{fa-ra-ô-ni-co}), 
-\texttt{e1ô} (e.g., \emph{le-ô-ni-das}, \emph{na-po-le-ô-ni-co}),
-\texttt{o1ã} (e.g., \emph{jo-ão}, \emph{la-go-ão}),
-\texttt{o1ê} (e.g., \emph{bo-ê-mi-o}),
-\texttt{cu2i} (e.g., \emph{cui-da-do}, \emph{cir-cui-to}; this rule requires the exception rule \texttt{cu3in} to avoid unintended errors in words like \emph{pi-cu-i-nha}, \emph{i-mis-cu-in-do}), 
-\texttt{.ne4o} (e.g., \emph{neo-li-be-ral}, \emph{neo-na-zis-ta}),
-\texttt{o1im} (e.g., \emph{co-im-bra}; this rule requires the exception rule \texttt{co2ima} to avoid unintended errors in words like \emph{coi-ma}),
-\texttt{o2i1na} (e.g., \emph{boi-na}, \emph{coi-na}), and 
-\texttt{pro1i1b} (e.g., \emph{pro-i-bir}).
+\texttt{1çô}, and \texttt{1xô} (e.g., \emph{ma-çô*ni*co}, \emph{a-xô*nio}, \emph{sa-xô*ni*co}; see \cref{rulegrp_bo});
+\texttt{a1â}, \texttt{a1ã}, \texttt{a1ô}, \texttt{e1ô}, \texttt{o1ã}, and \texttt{o1ê} (e.g., \emph{a*bra-â*mi*co}, \emph{a*bra-ão}, \emph{ca*na-ã}, \emph{fa*ra-ô*ni*co}, \emph{le-ô*ni*das}, \emph{na*po*le-ô*ni*co}, \emph{jo-ão}, \emph{la*go-ão}, \emph{bo-ê*mio}; see \cref{rulegrp_aa});
+%\texttt{cu2i} (e.g., \emph{cui-da-do}, \emph{cir-cui-to}; this rule requires the exception rule \texttt{cu3in} to avoid unintended errors in words like \emph{pi-cu-i-nha}, \emph{i-mis-cu-in-do}), 
+\texttt{.ne4o} (e.g., \emph{ne.o*li*be*ral}, \emph{ne.o-na*zis*ta}; see \cref{rulegrp_neo}),
+\texttt{o1im} (e.g., \emph{co-im*bra}; this rule requires the exception rule \texttt{co2ima} to avoid unintended errors in words like \emph{coi-ma}; see \cref{rulegrp_Vi}),
+\texttt{o2i1na} (e.g., \emph{bo.i*na}, \emph{co.i*na}; created as an exception for \texttt{o1in}, see \cref{rulegrp_Vi}), and 
+\texttt{pro1i1b} (e.g., \emph{pro-i*bir}, see \cref{rulegrp_proi}).
 After incorporating those rules, the number of incorrect and missing hyphenations, respectively,
@@
 %
-% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., i3â, i3ê, i3ô, 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, u3é, 1gu4é, 1qu4é, tu1i, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç, cu2i, tu2i1t, o2i1na" | tr -d ' ' | tr ',' '\n') > /tmp/patts9
+% cat ../data/default.TeX.pt-br.patterns <(echo ".p2si, .p2sí, .g2no, .g2nó, t2c, 1p2neu, .t2m, .p2t, su2b3r, su2b3l, .su3b4li, a1ir., u1ir., 1qu, 1vô, 1lô, 1cô, 1gô, 1bô, 1tô, 1rô, 1pô, a1é, a1í, a1ó, a1ú, e1á, e1â, e1ã, e1é, e1ê, e1í, e1ó, é1o, e1ú, i1á, i1ã, í1a, i1é, i1í, i1ó, í1o, i1u, i1ú, o1á, o1é, o1í, o1ó, u1á, u1ã, u1í, ú1o, 1qu2á, 1qu2í, 1gu2í, a1ind, a1i1nh, e1imp, e1inc, e1inf, e1ing, e1ins, e1int, e1inv, u1int, u1ind, u1iz., a1iz., 4a., 4e., 4o., 1gu4á, 1gu4ã, 1qu4ã, .m2n, c2za, .s2, 1p2seu1d, 1dô, 1fô, 1mô, 1nô, 1sô, 1zô, 1gu2é, 1qu2é, tu1i, bu1i, co1in, nu1i, cu1i, o1in, u1in, su1i, í1e, ra1is, ju1i, fu1i, du1i, do1im, au1i, u1i1ç, cu2i, tu2i1t, o2i1na" | tr -d ' ' | tr ',' '\n') > /tmp/patts9
 % ./gocreateresultfile.sh ../data/hyphenations6.dic /tmp/patts9 > /tmp/hyphenations6result_009.dic

### 2024-06-17 article/methodology.tex
small fixes

@@
 
-To assess the performance of each set of rules, we require a collection of
+To assess the performance of each set of rules, we required a collection of
 correctly hyphenated Portuguese words. We employed word frequency data to
 ensure we selected representative, commonly used words, avoiding excessively
-rare ones. Our comprehensive word list was curated using online dictionaries,
-Portuguese corpora, and verified against Portuguese grammars to validate
-hyphenation rules. We also performed manual corrections where necessary.
+rare ones. Our comprehensive word list was curated from online dictionaries,
+and Portuguese corpora, and verified against Portuguese grammars to validate
+hyphenation rules. We also performed manual corrections, where necessary.
 We should not expect an entire corpus to follow a set of conventions for a written 

### 2024-06-17 article/texrulespt.tex
small fixes

@@
 and \verb|õ|), resulting in these CV patterns that indicate favorable
-hyphenation points before the consonants\footnote{The complete list of these
+hyphenation points before the consonants\footnote{In Portuguese, usually 
+the letter \emph{h} appears at word initial position or before the consonants
+\emph{c}, \emph{l}, or \emph{n}. Therefore, it is not worthy encouraging a hyphenation point
+before an \emph{h}V. Examples of words that have an \emph{h} in the middle and
+not preceded by \emph{c}, \emph{l}, or \emph{n} are: \emph{Bahia}, \emph{Corinthians}, 
+\emph{show}, \emph{shopping}, \emph{Matheus}, and \emph{sushi}. They are proper names
+or loanwords whose spelling have not been adapted to Portuguese.}
+\footnote{The complete list of these
 252 patterns is given here: \ExceptionRulesCV{}.}. 
@@
 \begin{itemize}
-    \item 20 rules created for cases involving consonants \verb|b|, \verb|c|, \verb|d|, \verb|f|, \verb|g|, \verb|k|, \verb|p|, \verb|t|, \verb|v|, or \verb|w| followed by \verb|l| or \verb|r|\footnote{The 20 additional rules are: \ExceptionRulesLR{}.};
+    \item 20 rules created for cases involving consonants \verb|b|, \verb|c|, \verb|d|, \verb|f|, \verb|g|, \verb|k|, \verb|p|, \verb|t|, \verb|v|, or \verb|w| followed by \verb|l| or \verb|r|\footnote{We don't know why \cite{hyphpt} have added the rules \texttt{1w2l} and \texttt{1w2r}, since the is no Portuguese word with such sequence, we could only find foreignism like \emph{showroom}, \emph{wrestling}, \emph{bowling}, or other rather rarer foreign words.}\footnote{The 20 additional rules are: \ExceptionRulesLR{}.};
     \item 3 rules for \verb|c|, \verb|l| or \verb|n| followed by \verb|h|\footnote{Those 3 rules are: \ExceptionRulesCLNH{}.};

### 2024-07-01 article/portuguesespelling.tex
fix #46

@@
     \item\label{rule-decreasing} decreasing diphthongs should not be split (e.g. 
-	\emph{\underline{ai}-ro-so}, \emph{ca-d\underline{ei}-ra}, 
-	\emph{o-ra-ç\underline{ão}});
+	\emph{\underline{ai}-ro-so}, \emph{c\underline{au}-te-la}, \emph{ca-d\underline{ei}-ra}, \emph{cha-p\underline{éu}},
+	\emph{o-ra-ç\underline{ão}}), \emph{n\underline{oi}-te}, \emph{ca-la-b\underline{ou}-ço}, \emph{as-te-r\underline{ói}-de},
+  \emph{re-tri-b\underline{ui}});
     \item\label{rule-rising} rising diphthong should not be split (e.g.
-	\emph{a-b\underline{ai}-xo}; \emph{c\underline{au}-te-la}, 
-	\emph{pa-p\underline{éi}s}, \emph{cha-p\underline{éu}}, 
-	\emph{pre-f\underline{ei}-to}, \emph{r\underline{eu}-nir},
-	\emph{n\underline{oi}-te}; \emph{ca-la-b\underline{ou}-ço}, 
-	\emph{as-te-r\underline{ói}-de}; 
-	\emph{re-tri-b\underline{ui}});
+  \emph{his-tó-r\underline{ia}}, \emph{má-g\underline{oa}}, 
+  \emph{sé-\underline{rio}}, \emph{gló-r\underline{ia}}, \emph{fre-q\underline{ue}n-te},
+  \emph{pá-tr\underline{ia}});
     \item\label{rule-singlev} disyllables whose syllable has a single vowel should 

### 2024-07-01 article/portuguesespelling.tex
fix #47

@@
 	\emph{xc} (e.g. \emph{te\underline{r-r}a}, \emph{pro-fe\underline{s-s}or},
-	\emph{co-mu\underline{\emph{m-m}}en-te}, \emph{co\underline{n-n}os-co},
+  \emph{co-mu\underline{\emph{m-m}}en-te}, \emph{co\underline{n-n}os-co}\footnote{It is noteworthy that the forms \emph{conosco} and \emph{comummente} are not used in all varieties of Portuguese.
+For example, Europeans adopt these forms, while Brazilians do not.},
 	\emph{de\underline{s-c}er}, \emph{cre\underline{s-ç}a}, \emph{e\underline{x-c}e-der}).

### 2024-07-01 article/dictionary.tex
fix #48

@@
 To establish our gold standard for hyphenation, we will compare the
-hyphenations offered by all six dictionaries. First, we will determine the total count
-of unique hyphenations across these dictionaries using the script
-\texttt{hyphenation\-agreements.sh}.
-It's worth noting that certain dictionaries annotate words with a colon (`:') to
-indicate potential variations in pronunciation or production.
-Particularly, `apparent proparoxytones' might appear marked by this colon sign, indicating 
-the possibility of a diphthongs or hiatuses in the word ending.
-In Portuguese, words ending in \emph{ea}, \emph{eo}, \emph{ia}, \emph{ie},
-\emph{io}, \emph{ua}, \emph{ue}, or \emph{uo}, with the stressed syllable
-before these endings, can be considered either paroxytones ending in a rising
-diphthong or proparoxytones ending in a hiatus. For instance, words like \emph{his-tó-ri:a}
+hyphenations offered by all six dictionaries. First, we will determine the
+total count of unique hyphenations across these dictionaries using the script
+\texttt{hyphenation\-agreements.sh}. It's worth noting that certain
+dictionaries annotate words with a colon (`:') to indicate potential variations
+in pronunciation or production. Particularly, `apparent proparoxytones' might
+appear marked by this colon sign, indicating the possibility of a diphthongs or
+hiatuses in the word ending. In Portuguese, words ending in \emph{-ea},
+\emph{-eo}, \emph{-ia}, \emph{-ie}, \emph{-io}, \emph{-ua}, \emph{-ue}, or
+\emph{-uo}, with the stressed syllable preceding these endings, are
+grammatically considered paroxytones, though they can sometimes be produced as
+proparoxytones ending in a hiatus. For instance, words like \emph{his-tó-ri:a}
 and \emph{on-du-la-tó-ri:o} are examples of words marked as apparent
-proparoxytones, suggesting they could be regarded as paroxytones (\emph{his-tó-ria}
-and \emph{on-du-la-tó-rio}) or proparoxytones (\emph{his-tó-ri-a} and
-\emph{on-du-la-tó-ri-o}). The script \texttt{hyphenationagreements.sh} 
-offers four potential approaches to handle these apparent proparoxytones:
-retaining the hyphenations with the colon mark to indicate an apparent proparoxytone; 
-selecting only the paroxytone or only the proparoxytone counterpart; or counting both paroxytones and proparoxytones. 
+proparoxytones, suggesting they could be regarded as paroxytones
+(\emph{his-tó-ria} and \emph{on-du-la-tó-rio}) or proparoxytones
+(\emph{his-tó-ri-a} and \emph{on-du-la-tó-ri-o}). The script
+\texttt{hyphenationagreements.sh} offers four potential approaches to handle
+these apparent proparoxytones: retaining the hyphenations with the colon mark
+to indicate an apparent proparoxytone; selecting only the paroxytone or only
+the proparoxytone counterpart; or counting both paroxytones and proparoxytones.
 Given the lack of consensus in the literature, our initial approach involves
 counting both hyphenations, and we will detail below how we resolve this issue.
-In our hyphenation dictionary, we have identified \NumberOfAppProp{} words marked as apparent proparoxytones.
+In our hyphenation dictionary, we have identified \NumberOfAppProp{} words
+marked as apparent proparoxytones.
 

### 2024-07-01 article/limitations.tex
fix #52

@@
 
-    \item [Foreignness\label{foreignness}] There is a group of words %20 words 
-	in the corpus that are terminologies or words incorporated into the 
-	Portuguese language without full phonological adaptation, such as 
-	\emph{darwinismo}, \emph{quilowatt}, and \emph{esfiha}. The lack of
-	adaptation makes the phonological pattern very specific to the word,
-	making it impossible to incorporate their cases \TeX{}'s rules alongside the
-	other rules. The solution is to add them to the exception word list.
+    \item [Foreignness\label{foreignness}] There is a group of words in the
+      corpus that are terminologies or words incorporated into the Portuguese
+      language without full phonological adaptation, such as \emph{darwinismo},
+      \emph{quilowatt}, and \emph{esfiha}. This lack of adaptation results in
+      phonological patterns that are highly specific to each word, making it
+      impractical to integrate their cases into \TeX{}'s rules alongside other
+      rules. Especially for words like \emph{farquhar} and \emph{qubit}, which
+      are not only foreign but also rarely used in the language, the solution
+      is to add them to the exception word list.
 

### 2024-07-01 article/hyphenpatches.tex
fix #53
fix #54
fix #55

@@
 
-\refstepcounter{numberRulesGroups}\item\label{rulegrp_t2} rule: \texttt{.t2} -- tsunami, tzarista
+\refstepcounter{numberRulesGroups}\item\label{rulegrp_t2} rule: \texttt{.t2} -- \emph{tsunami}, \emph{tzarista}
 
@@
 
-\refstepcounter{numberRulesGroups}\item\label{rulegrp_proi} rule: \texttt{pro1i1b} -- proibição
+\refstepcounter{numberRulesGroups}\item\label{rulegrp_proi} rule: \texttt{pro1i1b} -- \emph{proibição}
 
@@
 
-\refstepcounter{numberRulesGroups}\item\label{rulegrp_aa} rule: \texttt{a1â}, \texttt{a1ã}, \texttt{a1é}, \texttt{a1í}, \texttt{a1ó}, \texttt{a1ô}, \texttt{a1ú}, \texttt{e1á}, \texttt{e1â}, \texttt{e1ã}, \texttt{e1é}, \texttt{e1ê}, \texttt{e1í}, \texttt{e1ó}, \texttt{e1ô}, \texttt{e1ú}, \texttt{é1o}, \texttt{i1á}, \texttt{i1ã}, \texttt{i1é}, \texttt{i1í}, \texttt{i1ó}, \texttt{i1u}, \texttt{i1ú}, \texttt{í1a}, \texttt{í1o}, \texttt{o1á}, \texttt{o1ã}, \texttt{o1é}, \texttt{o1ê}, \texttt{o1í}, \texttt{o1ó}, \texttt{u1á}, \texttt{u1ã}, \texttt{u1â}, \texttt{u1é}, \texttt{u1ê}, \texttt{u1í}, \texttt{ú1o} --  \emph{abraâmico}, \emph{abraão}, \emph{aéreo}, \emph{país}, \emph{caótico}, \emph{faraônico}, \emph{saúde}, \emph{balneário}, \emph{oceânico}, \emph{campeã}, \emph{feérico}, \emph{veêm}, \emph{veículo}, \emph{teórico}, \emph{napoleônico}, \emph{conteúdo}, \emph{néon}, \emph{diário}, \emph{região}, \emph{soviético}, \emph{iídiche}, \emph{periódico}, \emph{feiura}, \emph{viúva}, \emph{maníaco}, \emph{íon}, \emph{razoável}, \emph{joão}, \emph{poético}, \emph{boêmia}, \emph{heroísmo}, \emph{alcoólico}, \emph{usuário}, \emph{itapuã}, \emph{lituânia}, \emph{suécia}, \emph{cauê}, \emph{suíça}, \emph{flúor} \\
+\refstepcounter{numberRulesGroups}\item\label{rulegrp_aa} rule: \texttt{a1â}, \texttt{a1ã}, \texttt{a1é}, \texttt{a1í}, \texttt{a1ó}, \texttt{a1ô}, \texttt{a1ú}, \texttt{e1á}, \texttt{e1â}, \texttt{e1ã}, \texttt{e1é}, \texttt{e1ê}, \texttt{e1í}, \texttt{e1ó}, \texttt{e1ô}, \texttt{e1ú}, \texttt{é1o}, \texttt{i1á}, \texttt{i1ã}, \texttt{i1é}, \texttt{i1í}, \texttt{i1ó}, \texttt{i1u}, \texttt{i1ú}, \texttt{í1a}, \texttt{í1o}, \texttt{o1á}, \texttt{o1ã}, \texttt{o1é}, \texttt{o1ê}, \texttt{o1í}, \texttt{o1ó}, \texttt{u1á}, \texttt{u1ã}, \texttt{u1â}, \texttt{u1é}, \texttt{u1ê}, \texttt{u1í}, \texttt{ú1o} --  \emph{abraâmico}, \emph{abraão}, \emph{aéreo}, \emph{país}, \emph{caótico}, \emph{faraônico}, \emph{saúde}, \emph{balneário}, \emph{oceânico}, \emph{campeã}, \emph{feérico}, \emph{preênsil}, \emph{veículo}, \emph{teórico}, \emph{napoleônico}, \emph{conteúdo}, \emph{néon}, \emph{diário}, \emph{região}, \emph{soviético}, \emph{iídiche}, \emph{periódico}, \emph{feiura}, \emph{viúva}, \emph{maníaco}, \emph{íon}, \emph{razoável}, \emph{joão}, \emph{poético}, \emph{boêmia}, \emph{heroísmo}, \emph{alcoólico}, \emph{usuário}, \emph{itapuã}, \emph{lituânia}, \emph{suécia}, \emph{cauê}, \emph{suíça}, \emph{flúor} \\
 exception: \texttt{1gu2á}, \texttt{1gu2ã}, \texttt{1gu2é}, \texttt{1gu2ê}, \texttt{1gu2í}, \texttt{1qu2á}, \texttt{1qu2ã}, \texttt{1qu2â}, \texttt{1qu2é}, \texttt{1qu2ê}, \texttt{1qu2í}, -- \emph{jaraguá}, \emph{saguão}, \emph{alguém}, \emph{português}, \emph{linguística}, \emph{aquático}, \emph{camaquã}, \emph{equânime}, \emph{inquérito}, \emph{sequência}, \emph{química}

### 2024-07-02 article/comparedresults.tex
fix #56

@@
 abecedário & a*be*ce*dá*ri.o \xmark & a*be*ce*dá*rio \cmark \\
+abegoaria & a*be*go*a*ri*a \cmark & a*be*go*a*ri-a \xmark \\
+abiótica & a*bi-ó*ti*ca \xmark & a*bi*ó*ti*ca \cmark \\
 abiótico & a*bi-ó*ti*co \xmark & a*bi*ó*ti*co \cmark \\
 abissínio & a*bis*sí*ni.o \xmark & a*bis*sí*nio \cmark \\
+abiu & a*bi-u \xmark & a*bi*u \cmark \\
 abluir & a*blu-ir \xmark & a*blu*ir \cmark \\
 aboio & a*boi*o \cmark & a*boi-o \xmark \\
+abortício & a*bor*tí*ci.o \xmark & a*bor*tí*cio \cmark \\
 abraâmico & a*bra-â*mi*co \xmark & a*bra*â*mi*co \cmark \\
@@
 abrótea & a*bró*te.a \xmark & a*bró*tea \cmark \\
+abruptamente & a.b-rup*ta*men*te \xmark & a.b-rup*ta*men*te \xmark \\
 abrupto & a.b-rup*to \xmark & a.b-rup*to \xmark \\
 absenteísmo & ab*sen*te-ís*mo \xmark & ab*sen*te*ís*mo \cmark \\
+absenteísta & ab*sen*te-ís*ta \xmark & ab*sen*te*ís*ta \cmark \\
+absorvância & ab*sor*vân*ci.a \xmark & ab*sor*vân*cia \cmark \\
+absorvência & ab*sor*vên*ci.a \xmark & ab*sor*vên*cia \cmark \\
+abstêmio & abs*tê*mi.o \xmark & abs*tê*mio \cmark \\
 abstinência & abs*ti*nên*ci.a \xmark & abs*ti*nên*cia \cmark \\
@@
 acácia & a*cá*ci.a \xmark & a*cá*cia \cmark \\
+acácio & a*cá*ci.o \xmark & a*cá*cio \cmark \\
 academia & a*ca*de*mi*a \cmark & a*ca*de*mi-a \xmark \\
+acadêmia & a*ca*dê*mi.a \xmark & a*ca*dê*mia \cmark \\
+acádio & a*cá*di.o \xmark & a*cá*dio \cmark \\
 açaí & a*ça-í \xmark & a*ça*í \cmark \\
+acalmia & a*cal*mi*a \cmark & a*cal*mi-a \xmark \\
 acatisia & a*ca*ti*si*a \cmark & a*ca*ti*si-a \xmark \\
+acauã & a*cau-ã \xmark & a*cau*ã \cmark \\
 acefalia & a*ce*fa*li*a \cmark & a*ce*fa*li-a \xmark \\
+acelerômetro & a*ce*le-rô*me*tro \xmark & a*ce*le*rô*me*tro \cmark \\
 acéquia & a*cé*qui.a \xmark & a*cé*quia \cmark \\
@@
 acidemia & a*ci*de*mi*a \cmark & a*ci*de*mi-a \xmark \\
+acidúria & a*ci*dú*ri.a \xmark & a*ci*dú*ria \cmark \\
 acônito & a-cô*ni*to \xmark & a*cô*ni*to \cmark \\
@@
 acrofobia & a*cro*fo*bi*a \cmark & a*cro*fo*bi-a \xmark \\
+acroleína & a*cro*le-í*na \xmark & a*cro*le*í*na \cmark \\
+acromatopsia & a*cro*ma*top*si*a \cmark & a*cro*ma*top*si-a \xmark \\
 acromegalia & a*cro*me*ga*li*a \cmark & a*cro*me*ga*li-a \xmark \\
+acrotério & a*cro*té*ri.o \xmark & a*cro*té*rio \cmark \\
 actínio & ac*tí*ni.o \xmark & ac*tí*nio \cmark \\
-acuidade & a*cu-i*da*de \xmark & a*cu-i*da*de \xmark \\
 acurácia & a*cu*rá*ci.a \xmark & a*cu*rá*cia \cmark \\
+acusatório & a*cu*sa*tó*ri.o \xmark & a*cu*sa*tó*rio \cmark \\
 adágio & a*dá*gi.o \xmark & a*dá*gio \cmark \\
 adail & a*da-il \xmark & a*da-il \xmark \\
+adenia & a*de*ni*a \cmark & a*de*ni-a \xmark \\
+aderência & a*de*rên*ci.a \xmark & a*de*rên*cia \cmark \\
 adimplência & a*dim*plên*ci.a \xmark & a*dim*plên*cia \cmark \\
+adjacência & ad*ja*cên*ci.a \xmark & ad*ja*cên*cia \cmark \\
 adjutório & ad*ju*tó*ri.o \xmark & ad*ju*tó*rio \cmark \\
 adolescência & a*do*les*cên*ci.a \xmark & a*do*les*cên*cia \cmark \\
+adônis & a-dô*nis \xmark & a*dô*nis \cmark \\
 adriático & a*dri-á*ti*co \xmark & a*dri*á*ti*co \cmark \\
+adstringência & ads*trin*gên*ci.a \xmark & ads*trin*gên*cia \cmark \\
+adua & a*du*a \cmark & a*du-a \xmark \\
+adulária & a*du*lá*ri.a \xmark & a*du*lá*ria \cmark \\
 adultério & a*dul*té*ri.o \xmark & a*dul*té*rio \cmark \\
+adventícia & ad*ven*tí*ci.a \xmark & ad*ven*tí*cia \cmark \\
 adventício & ad*ven*tí*ci.o \xmark & ad*ven*tí*cio \cmark \\
@@
 advocacia & ad*vo*ca*ci*a \cmark & ad*vo*ca*ci-a \xmark \\
+advogacia & ad*vo*ga*ci*a \cmark & ad*vo*ga*ci-a \xmark \\
 aéreo & a-é*re.o \xmark & a*é*reo \cmark \\
@@
 aerofobia & a*e*ro*fo*bi*a \cmark & a*e*ro*fo*bi-a \xmark \\
+aerofólio & a*e*ro*fó*li.o \xmark & a*e*ro*fó*lio \cmark \\
 aerofotografia & a*e*ro*fo*to*gra*fi*a \cmark & a*e*ro*fo*to*gra*fi-a \xmark \\
 aerografia & a*e*ro*gra*fi*a \cmark & a*e*ro*gra*fi-a \xmark \\
+aeromancia & a*e*ro*man*ci*a \cmark & a*e*ro*man*ci-a \xmark \\
 aeronomia & a*e*ro*no*mi*a \cmark & a*e*ro*no*mi-a \xmark \\
@@
 agenesia & a*ge*ne*si*a \cmark & a*ge*ne*si-a \xmark \\
+ágio & á*gi*o \cmark & á*gi-o \xmark \\
 aglossia & a*glos*si*a \cmark & a*glos*si-a \xmark \\
@@
 agonia & a*go*ni*a \cmark & a*go*ni-a \xmark \\
+agônico & a-gô*ni*co \xmark & a*gô*ni*co \cmark \\
 agorafobia & a*go*ra*fo*bi*a \cmark & a*go*ra*fo*bi-a \xmark \\
@@
 agrião & a*gri-ão \xmark & a*gri*ão \cmark \\
+agroindústria & a*gro-in*dús*tri.a \xmark & a*gro*in*dús*tria \cmark \\
 agronomia & a*gro*no*mi*a \cmark & a*gro*no*mi-a \xmark \\
 agronômico & a*gro-nô*mi*co \xmark & a*gro*nô*mi*co \cmark \\
+agropecuária & a*gro*pe*cu-á*ri.a \xmark & a*gro*pe*cu*á*ria \cmark \\
+agroquímica & a*gro-quí*mi*ca \xmark & a*gro*quí*mi*ca \cmark \\
+agroquímico & a*gro-quí*mi*co \xmark & a*gro*quí*mi*co \cmark \\
+aguaí & a*gua-í \xmark & a*gua*í \cmark \\
 águia & á*gui.a \xmark & á*guia \cmark \\
@@
 ainda & a-in*da \xmark & a*in*da \cmark \\
+ainsa & a-in*sa \xmark & a-in*sa \xmark \\
 aio & ai*o \cmark & ai-o \xmark \\
+aiquidô & ai*qui-dô \xmark & ai*qui*dô \cmark \\
+ajuizado & a*ju-i*za*do \xmark & a*ju*i*za*do \cmark \\
 ajuizar & a*ju-i*zar \xmark & a*ju*i*zar \cmark \\
+alagoa & a*la*go*a \cmark & a*la*go-a \xmark \\
+alagoinha & a*la*go-i*nha \xmark & a*la*go*i*nha \cmark \\
 alaúde & a*la-ú*de \xmark & a*la*ú*de \cmark \\
@@
 albugínea & al*bu*gí*ne*a \cmark & al*bu*gí*ne-a \xmark \\
+albuminúria & al*bu*mi*nú*ri.a \xmark & al*bu*mi*nú*ria \cmark \\
 alcaidaria & al*cai*da*ri*a \cmark & al*cai*da*ri-a \xmark \\
+alcaptonúria & al*cap*to*nú*ri.a \xmark & al*cap*to*nú*ria \cmark \\
 alcaravia & al*ca*ra*vi*a \cmark & al*ca*ra*vi-a \xmark \\
@@
 aldeído & al*de-í*do \xmark & al*de*í*do \cmark \\
+álea & á*le.a \xmark & á*lea \cmark \\
 aleatório & a*le*a*tó*ri.o \xmark & a*le*a*tó*rio \cmark \\
@@
 alfaiataria & al*fai*a*ta*ri*a \cmark & al*fai*a*ta*ri-a \xmark \\
+alfandegário & al*fan*de*gá*ri.o \xmark & al*fan*de*gá*rio \cmark \\
 alfarrábio & al*far*rá*bi.o \xmark & al*far*rá*bio \cmark \\
@@
 alívio & a*lí*vi.o \xmark & a*lí*vio \cmark \\
+almóada & al*mó-a*da \xmark & al*mó-a*da \xmark \\
 almôndega & al-môn*de*ga \xmark & al*môn*de*ga \cmark \\
@@
 altruísta & al*tru-ís*ta \xmark & al*tru*ís*ta \cmark \\
+aluá & a*lu-á \xmark & a*lu*á \cmark \\
 alucinatório & a*lu*ci*na*tó*ri.o \xmark & a*lu*ci*na*tó*rio \cmark \\
-aluimento & a*lu-i*men*to \xmark & a*lu-i*men*to \xmark \\
 aluir & a*lu-ir \xmark & a*lu*ir \cmark \\
@@
 alvéolo & al*vé-o*lo \xmark & al*vé*o*lo \cmark \\
+amalteia & a*mal*tei*a \cmark & a*mal*tei-a \xmark \\
 amásia & a*má*si.a \xmark & a*má*sia \cmark \\
 amásio & a*má*si.o \xmark & a*má*sio \cmark \\
+amazia & a*ma*zi*a \cmark & a*ma*zi-a \xmark \\
 amazônico & a*ma-zô*ni*co \xmark & a*ma*zô*ni*co \cmark \\
 ambidestria & am*bi*des*tri*a \cmark & am*bi*des*tri-a \xmark \\
+ambiência & am*bi*ên*ci.a \xmark & am*bi*ên*cia \cmark \\
+ambivalência & am*bi*va*lên*ci.a \xmark & am*bi*va*lên*cia \cmark \\
+ambliopia & am*bli*o*pi*a \cmark & am*bli*o*pi-a \xmark \\
 ambrosia & am*bro*si*a \cmark & am*bro*si-a \xmark \\
+ambrósia & am*bró*si.a \xmark & am*bró*sia \cmark \\
+ambulacrário & am*bu*la*crá*ri.o \xmark & am*bu*la*crá*rio \cmark \\
 ambulância & am*bu*lân*ci.a \xmark & am*bu*lân*cia \cmark \\
@@
 ameia & a*mei*a \cmark & a*mei-a \xmark \\
+amêijoa & a*mêi*jo.a \xmark & a*mêi*joa \cmark \\
+amelia & a*me*li*a \cmark & a*me*li-a \xmark \\
 amélia & a*mé*li.a \xmark & a*mé*lia \cmark \\
@@
 amenorreia & a*me*nor*rei*a \cmark & a*me*nor*rei-a \xmark \\
+americanofilia & a*me*ri*ca*no*fi*li*a \cmark & a*me*ri*ca*no*fi*li-a \xmark \\
+americanofobia & a*me*ri*ca*no*fo*bi*a \cmark & a*me*ri*ca*no*fo*bi-a \xmark \\
 amerício & a*me*rí*ci.o \xmark & a*me*rí*cio \cmark \\
 ameríndio & a*me*rín*di.o \xmark & a*me*rín*dio \cmark \\
+amigdalectomia & a*mig*da*lec*to*mi*a \cmark & a*mig*da*lec*to*mi-a \xmark \\
 aminoácido & a*mi*no-á*ci*do \xmark & a*mi*no*á*ci*do \cmark \\
 amiúde & a*mi-ú*de \xmark & a*mi*ú*de \cmark \\
+amnesia & am*ne*si*a \cmark & am*ne*si-a \xmark \\
+âmnio & âm*ni.o \xmark & âm*nio \cmark \\
+amônia & a-mô*ni.a \xmark & a*mô*nia \cmark \\
 amoníaco & a*mo*ní-a*co \xmark & a*mo*ní*a*co \cmark \\
@@
 anarquia & a*nar*qui*a \cmark & a*nar*qui-a \xmark \\
+anastácio & a*nas*tá*ci.o \xmark & a*nas*tá*cio \cmark \\
+anatólio & a*na*tó*li.o \xmark & a*na*tó*lio \cmark \\
 anatomia & a*na*to*mi*a \cmark & a*na*to*mi-a \xmark \\
 anatômico & a*na-tô*mi*co \xmark & a*na*tô*mi*co \cmark \\
+anauê & a*nau-ê \xmark & a*nau*ê \cmark \\
 ancião & an*ci-ão \xmark & an*ci*ão \cmark \\
 ancilostomíase & an*ci*los*to*mí-a*se \xmark & an*ci*los*to*mí*a*se \cmark \\
+androfilia & an*dro*fi*li*a \cmark & an*dro*fi*li-a \xmark \\
 androfobia & an*dro*fo*bi*a \cmark & an*dro*fo*bi-a \xmark \\
@@
 anedonia & a*ne*do*ni*a \cmark & a*ne*do*ni-a \xmark \\
+anedotário & a*ne*do*tá*ri.o \xmark & a*ne*do*tá*rio \cmark \\
 anelídeo & a*ne*lí*de.o \xmark & a*ne*lí*deo \cmark \\
@@
 anemômetro & a*ne-mô*me*tro \xmark & a*ne*mô*me*tro \cmark \\
+anencefalia & a*nen*ce*fa*li*a \cmark & a*nen*ce*fa*li-a \xmark \\
 anestesia & a*nes*te*si*a \cmark & a*nes*te*si-a \xmark \\
@@
 aneuploidia & a*neu*ploi*di*a \cmark & a*neu*ploi*di-a \xmark \\
+anfião & an*fi-ão \xmark & an*fi*ão \cmark \\
 anfíbio & an*fí*bi.o \xmark & an*fí*bio \cmark \\
+anfibólio & an*fi*bó*li.o \xmark & an*fi*bó*lio \cmark \\
 anfibologia & an*fi*bo*lo*gi*a \cmark & an*fi*bo*lo*gi-a \xmark \\
+anfictião & an*fic*ti-ão \xmark & an*fic*ti*ão \cmark \\
+anfictionia & an*fic*ti*o*ni*a \cmark & an*fic*ti*o*ni-a \xmark \\
 anfitrião & an*fi*tri-ão \xmark & an*fi*tri*ão \cmark \\
+angelologia & an*ge*lo*lo*gi*a \cmark & an*ge*lo*lo*gi-a \xmark \\
+angiografia & an*gi*o*gra*fi*a \cmark & an*gi*o*gra*fi-a \xmark \\
 angiologia & an*gi*o*lo*gi*a \cmark & an*gi*o*lo*gi-a \xmark \\
 angioplastia & an*gi*o*plas*ti*a \cmark & an*gi*o*plas*ti-a \xmark \\
+angioscopia & an*gi*os*co*pi*a \cmark & an*gi*os*co*pi-a \xmark \\
+anglofilia & an*glo*fi*li*a \cmark & an*glo*fi*li-a \xmark \\
+anglofonia & an*glo*fo*ni*a \cmark & an*glo*fo*ni-a \xmark \\
 angústia & an*gús*ti.a \xmark & an*gús*tia \cmark \\
+anião & a*ni-ão \xmark & a*ni*ão \cmark \\
+aniridia & a*ni*ri*di*a \cmark & a*ni*ri*di-a \xmark \\
 anisogamia & a*ni*so*ga*mi*a \cmark & a*ni*so*ga*mi-a \xmark \\
@@
 anomalia & a*no*ma*li*a \cmark & a*no*ma*li-a \xmark \\
+anômalo & a-nô*ma*lo \xmark & a*nô*ma*lo \cmark \\
 anomia & a*no*mi*a \cmark & a*no*mi-a \xmark \\
@@
 anseio & an*sei*o \cmark & an*sei-o \xmark \\
+ânsia & ân*si.a \xmark & ân*sia \cmark \\
 antagônico & an*ta-gô*ni*co \xmark & an*ta*gô*ni*co \cmark \\
 antecedência & an*te*ce*dên*ci.a \xmark & an*te*ce*dên*cia \cmark \\
+anterídio & an*te*rí*di.o \xmark & an*te*rí*dio \cmark \\
+antestreia & an*tes*trei*a \cmark & an*tes*trei-a \xmark \\
 antiácido & an*ti-á*ci*do \xmark & an*ti*á*ci*do \cmark \\
+antiaéreo & an*ti*a-é*re.o \xmark & an*ti*a*é*reo \cmark \\
 antialcoólico & an*ti*al*co-ó*li*co \xmark & an*ti*al*co*ó*li*co \cmark \\
 antibiótico & an*ti*bi-ó*ti*co \xmark & an*ti*bi*ó*ti*co \cmark \\
+antidemocracia & an*ti*de*mo*cra*ci*a \cmark & an*ti*de*mo*cra*ci-a \xmark \\
+antiético & an*ti-é*ti*co \xmark & an*ti*é*ti*co \cmark \\
+antifonário & an*ti*fo*ná*ri.o \xmark & an*ti*fo*ná*rio \cmark \\
+antimatéria & an*ti*ma*té*ri.a \xmark & an*ti*ma*té*ria \cmark \\
+antimônio & an*ti-mô*ni.o \xmark & an*ti*mô*nio \cmark \\
 antinomia & an*ti*no*mi*a \cmark & an*ti*no*mi-a \xmark \\
+antinômico & an*ti-nô*mi*co \xmark & an*ti*nô*mi*co \cmark \\
 antipatia & an*ti*pa*ti*a \cmark & an*ti*pa*ti-a \xmark \\
 antipatriótico & an*ti*pa*tri-ó*ti*co \xmark & an*ti*pa*tri*ó*ti*co \cmark \\
+antipoluição & an*ti*po*lu-i*ção \xmark & an*ti*po*lu*i*ção \cmark \\
 antiquário & an*ti-quá*ri.o \xmark & an*ti*quá*rio \cmark \\
@@
 antroposofia & an*tro*po*so*fi*a \cmark & an*tro*po*so*fi-a \xmark \\
+antúrio & an*tú*ri.o \xmark & an*tú*rio \cmark \\
 anuário & a*nu-á*ri.o \xmark & a*nu*á*rio \cmark \\
@@
 anúncio & a*nún*ci.o \xmark & a*nún*cio \cmark \\
+anúria & a*nú*ri.a \xmark & a*nú*ria \cmark \\
 aórtico & a-ór*ti*co \xmark & a*ór*ti*co \cmark \\
@@
 aparência & a*pa*rên*ci.a \xmark & a*pa*rên*cia \cmark \\
+apartidário & a*par*ti*dá*ri.o \xmark & a*par*ti*dá*rio \cmark \\
 apatia & a*pa*ti*a \cmark & a*pa*ti-a \xmark \\
 apendicectomia & a*pen*di*cec*to*mi*a \cmark & a*pen*di*cec*to*mi-a \xmark \\
+aperiódico & a*pe*ri-ó*di*co \xmark & a*pe*ri*ó*di*co \cmark \\
 apetência & a*pe*tên*ci.a \xmark & a*pe*tên*cia \cmark \\
@@
 apologia & a*po*lo*gi*a \cmark & a*po*lo*gi-a \xmark \\
+apomixia & a*po*mi*xi*a \cmark & a*po*mi*xi-a \xmark \\
 apoplexia & a*po*ple*xi*a \cmark & a*po*ple*xi-a \xmark \\
@@
 apostasia & a*pos*ta*si*a \cmark & a*pos*ta*si-a \xmark \\
+apoteótico & a*po*te-ó*ti*co \xmark & a*po*te*ó*ti*co \cmark \\
 apraxia & a*pra*xi*a \cmark & a*pra*xi-a \xmark \\
@@
 aquário & a-quá*ri.o \xmark & a*quá*rio \cmark \\
+aquariofilia & a*qua*ri*o*fi*li*a \cmark & a*qua*ri*o*fi*li-a \xmark \\
 aquático & a-quá*ti*co \xmark & a*quá*ti*co \cmark \\
 aquém & a-quém \xmark & a*quém \cmark \\
+aquênio & a-quê*ni.o \xmark & a*quê*nio \cmark \\
 aquícola & a-quí*co*la \xmark & a*quí*co*la \cmark \\
@@
 arábias & a*rá*bi.as \xmark & a*rá*bi.as \xmark \\
+aracnídeo & a*rac*ní*de.o \xmark & a*rac*ní*deo \cmark \\
 aracnofobia & a*rac*no*fo*bi*a \cmark & a*rac*no*fo*bi-a \xmark \\
 aracnologia & a*rac*no*lo*gi*a \cmark & a*rac*no*lo*gi-a \xmark \\
+arapuá & a*ra*pu-á \xmark & a*ra*pu*á \cmark \\
 araucária & a*rau*cá*ri.a \xmark & a*rau*cá*ria \cmark \\
+araúna & a*ra-ú*na \xmark & a*ra*ú*na \cmark \\
 arbitrário & ar*bi*trá*ri.o \xmark & ar*bi*trá*rio \cmark \\
@@
 arbóreo & ar*bó*re.o \xmark & ar*bó*reo \cmark \\
+arcádia & ar*cá*di.a \xmark & ar*cá*dia \cmark \\
 arcaísmo & ar*ca-ís*mo \xmark & ar*ca*ís*mo \cmark \\
+arcaria & ar*ca*ri*a \cmark & ar*ca*ri-a \xmark \\
 ardência & ar*dên*ci.a \xmark & ar*dên*cia \cmark \\
@@
 área & á*re.a \xmark & á*rea \cmark \\
+areão & a*re-ão \xmark & a*re*ão \cmark \\
 areia & a*rei*a \cmark & a*rei-a \xmark \\
+areópago & a*re-ó*pa*go \xmark & a*re*ó*pa*go \cmark \\
 argênteo & ar*gên*te*o \cmark & ar*gên*te-o \xmark \\
+argônio & ar-gô*ni.o \xmark & ar*gô*nio \cmark \\
 argúcia & ar*gú*ci.a \xmark & ar*gú*cia \cmark \\
+ária & á*ri.a \xmark & á*ria \cmark \\
 aríete & a*rí-e*te \xmark & a*rí*e*te \cmark \\
@@
 armário & ar*má*ri.o \xmark & ar*má*rio \cmark \\
+armênio & ar*mê*ni.o \xmark & ar*mê*nio \cmark \\
 armistício & ar*mis*tí*ci.o \xmark & ar*mis*tí*cio \cmark \\
 aromaterapia & a*ro*ma*te*ra*pi*a \cmark & a*ro*ma*te*ra*pi-a \xmark \\
+arquegônio & ar*que-gô*ni.o \xmark & ar*que*gô*nio \cmark \\
 arqueologia & ar*que*o*lo*gi*a \cmark & ar*que*o*lo*gi-a \xmark \\
@@
 arquétipo & ar-qué*ti*po \xmark & ar*qué*ti*po \cmark \\
+arquiconfraria & ar*qui*con*fra*ri*a \cmark & ar*qui*con*fra*ri-a \xmark \\
 arquidiácono & ar*qui*di-á*co*no \xmark & ar*qui*di*á*co*no \cmark \\
+arquimilionário & ar*qui*mi*li*o*ná*ri.o \xmark & ar*qui*mi*li*o*ná*rio \cmark \\
 arquitetônica & ar*qui*te-tô*ni*ca \xmark & ar*qui*te*tô*ni*ca \cmark \\
 arquitetônico & ar*qui*te-tô*ni*co \xmark & ar*qui*te*tô*ni*co \cmark \\
-arrais & ar*ra-is \xmark & ar*ra-is \xmark \\
+arraia & ar*rai*a \cmark & ar*rai-a \xmark \\
+arredio & ar*re*di*o \cmark & ar*re*di-o \xmark \\
 arreio & ar*rei*o \cmark & ar*rei-o \xmark \\
@@
 arritmia & ar*rit*mi*a \cmark & ar*rit*mi-a \xmark \\
+arrogância & ar*ro*gân*ci.a \xmark & ar*ro*gân*cia \cmark \\
 arroio & ar*roi*o \cmark & ar*roi-o \xmark \\
+arroteia & ar*ro*tei*a \cmark & ar*ro*tei-a \xmark \\
 arruinar & ar*ru-i*nar \xmark & ar*ru*i*nar \cmark \\
+arsênio & ar*sê*ni.o \xmark & ar*sê*nio \cmark \\
 artemísia & ar*te*mí*si.a \xmark & ar*te*mí*sia \cmark \\
+artéria & ar*té*ri.a \xmark & ar*té*ria \cmark \\
+arteriografia & ar*te*ri*o*gra*fi*a \cmark & ar*te*ri*o*gra*fi-a \xmark \\
+arteríola & ar*te*rí-o*la \xmark & ar*te*rí*o*la \cmark \\
 articulatório & ar*ti*cu*la*tó*ri*o \cmark & ar*ti*cu*la*tó*ri-o \xmark \\
@@
 artroscopia & ar*tros*co*pi*a \cmark & ar*tros*co*pi-a \xmark \\
+aruá & a*ru-á \xmark & a*ru*á \cmark \\
 ascaridíase & as*ca*ri*dí-a*se \xmark & as*ca*ri*dí*a*se \cmark \\
@@
 assédio & as*sé*di.o \xmark & as*sé*dio \cmark \\
+assembleia & as*sem*blei*a \cmark & as*sem*blei-a \xmark \\
 assepsia & as*sep*si*a \cmark & as*sep*si-a \xmark \\
@@
 assimetria & as*si*me*tri*a \cmark & as*si*me*tri-a \xmark \\
+assincronia & as*sin*cro*ni*a \cmark & as*sin*cro*ni-a \xmark \\
+assiriologia & as*si*ri*o*lo*gi*a \cmark & as*si*ri*o*lo*gi-a \xmark \\
+assiriólogo & as*si*ri-ó*lo*go \xmark & as*si*ri*ó*lo*go \cmark \\
 assistência & as*sis*tên*ci.a \xmark & as*sis*tên*cia \cmark \\
+assobio & as*so*bi*o \cmark & as*so*bi-o \xmark \\
 associável & as*so*ci-á*vel \xmark & as*so*ci*á*vel \cmark \\
@@
 astenia & as*te*ni*a \cmark & as*te*ni-a \xmark \\
+astéria & as*té*ri.a \xmark & as*té*ria \cmark \\
+astreia & as*trei*a \cmark & as*trei-a \xmark \\
+astrobiologia & as*tro*bi*o*lo*gi*a \cmark & as*tro*bi*o*lo*gi-a \xmark \\
+astrofotografia & as*tro*fo*to*gra*fi*a \cmark & as*tro*fo*to*gra*fi-a \xmark \\
 astrolábio & as*tro*lá*bi.o \xmark & as*tro*lá*bio \cmark \\
 astrologia & as*tro*lo*gi*a \cmark & as*tro*lo*gi-a \xmark \\
+astrometria & as*tro*me*tri*a \cmark & as*tro*me*tri-a \xmark \\
 astronomia & as*tro*no*mi*a \cmark & as*tro*no*mi-a \xmark \\
 astronômico & as*tro-nô*mi*co \xmark & as*tro*nô*mi*co \cmark \\
+astroquímica & as*tro-quí*mi*ca \xmark & as*tro*quí*mi*ca \cmark \\
 astúcia & as*tú*ci.a \xmark & as*tú*cia \cmark \\
@@
 ataúde & a*ta-ú*de \xmark & a*ta*ú*de \cmark \\
+ataxia & a*ta*xi*a \cmark & a*ta*xi-a \xmark \\
 ateísmo & a*te-ís*mo \xmark & a*te*ís*mo \cmark \\
@@
 atonia & a*to*ni*a \cmark & a*to*ni-a \xmark \\
+atônito & a-tô*ni*to \xmark & a*tô*ni*to \cmark \\
+atopia & a*to*pi*a \cmark & a*to*pi-a \xmark \\
 atrabiliário & a*tra*bi*li-á*ri.o \xmark & a*tra*bi*li*á*rio \cmark \\
@@
 atrofia & a*tro*fi*a \cmark & a*tro*fi-a \xmark \\
+atuário & a*tu-á*ri.o \xmark & a*tu*á*rio \cmark \\
+audácia & au*dá*ci.a \xmark & au*dá*cia \cmark \\
 audiência & au*di*ên*ci*a \cmark & au*di*ên*ci-a \xmark \\
@@
 audiologia & au*di*o*lo*gi*a \cmark & au*di*o*lo*gi-a \xmark \\
+audiometria & au*di*o*me*tri*a \cmark & au*di*o*me*tri-a \xmark \\
 auditoria & au*di*to*ri*a \cmark & au*di*to*ri-a \xmark \\
 auditório & au*di*tó*ri.o \xmark & au*di*tó*rio \cmark \\
+auê & au-ê \xmark & au*ê \cmark \\
 augúrio & au*gú*ri.o \xmark & au*gú*rio \cmark \\
+aurélia & au*ré*li.a \xmark & au*ré*lia \cmark \\
 áureo & áu*re.o \xmark & áu*reo \cmark \\
@@
 autobiografia & au*to*bi*o*gra*fi*a \cmark & au*to*bi*o*gra*fi-a \xmark \\
+autobiógrafo & au*to*bi-ó*gra*fo \xmark & au*to*bi*ó*gra*fo \cmark \\
+autocomplacência & au*to*com*pla*cên*ci.a \xmark & au*to*com*pla*cên*cia \cmark \\
+autoconsciência & au*to*cons*ci*ên*ci.a \xmark & au*to*cons*ci*ên*cia \cmark \\
 autocracia & au*to*cra*ci*a \cmark & au*to*cra*ci-a \xmark \\
+autodestruição & au*to*des*tru-i*ção \xmark & au*to*des*tru*i*ção \cmark \\
+autodomínio & au*to*do*mí*ni.o \xmark & au*to*do*mí*nio \cmark \\
 autofagia & au*to*fa*gi*a \cmark & au*to*fa*gi-a \xmark \\
+autogamia & au*to*ga*mi*a \cmark & au*to*ga*mi-a \xmark \\
+autogestionário & au*to*ges*ti*o*ná*ri.o \xmark & au*to*ges*ti*o*ná*rio \cmark \\
 autografia & au*to*gra*fi*a \cmark & au*to*gra*fi-a \xmark \\
+autoimunidade & au*to-i*mu*ni*da*de \xmark & au*to*i*mu*ni*da*de \cmark \\
 autônimo & au-tô*ni*mo \xmark & au*tô*ni*mo \cmark \\
 autonomia & au*to*no*mi*a \cmark & au*to*no*mi-a \xmark \\
+autonômico & au*to-nô*mi*co \xmark & au*to*nô*mi*co \cmark \\
 autônomo & au-tô*no*mo \xmark & au*tô*no*mo \cmark \\
@@
 aveia & a*vei*a \cmark & a*vei-a \xmark \\
+averroísmo & a*ver*ro-ís*mo \xmark & a*ver*ro*ís*mo \cmark \\
+avessia & a*ves*si*a \cmark & a*ves*si-a \xmark \\
 avião & a*vi-ão \xmark & a*vi*ão \cmark \\
 aviário & a*vi-á*ri.o \xmark & a*vi*á*rio \cmark \\
+avio & a*vi*o \cmark & a*vi-o \xmark \\
 avô & a-vô \xmark & a*vô \cmark \\
 axiologia & a*xi*o*lo*gi*a \cmark & a*xi*o*lo*gi-a \xmark \\
+azagaia & a*za*gai*a \cmark & a*za*gai-a \xmark \\
 azálea & a*zá*le*a \cmark & a*zá*le-a \xmark \\
+azaleia & a*za*lei*a \cmark & a*za*lei-a \xmark \\
 azia & a*zi*a \cmark & a*zi-a \xmark \\
+azotemia & a*zo*te*mi*a \cmark & a*zo*te*mi-a \xmark \\
 azulejaria & a*zu*le*ja*ri*a \cmark & a*zu*le*ja*ri-a \xmark \\
 babalaô & ba*ba*la-ô \xmark & ba*ba*la*ô \cmark \\
+babilônico & ba*bi-lô*ni*co \xmark & ba*bi*lô*ni*co \cmark \\
 babuíno & ba*bu-í*no \xmark & ba*bu*í*no \cmark \\
@@
 bacteriologia & bac*te*ri*o*lo*gi*a \cmark & bac*te*ri*o*lo*gi-a \xmark \\
+bacterioscopia & bac*te*ri*os*co*pi*a \cmark & bac*te*ri*os*co*pi-a \xmark \\
 bafio & ba*fi*o \cmark & ba*fi-o \xmark \\
@@
 baião & bai-ão \xmark & bai*ão \cmark \\
+bailio & bai*li*o \cmark & bai*li-o \xmark \\
 bainha & ba-i*nha \xmark & ba*i*nha \cmark \\
@@
 balboa & bal*bo*a \cmark & bal*bo-a \xmark \\
+balbuciência & bal*bu*ci*ên*ci*a \cmark & bal*bu*ci*ên*ci-a \xmark \\
 balbucio & bal*bu*ci*o \cmark & bal*bu*ci-o \xmark \\
@@
 baldio & bal*di*o \cmark & bal*di-o \xmark \\
+baleárico & ba*le-á*ri*co \xmark & ba*le*á*ri*co \cmark \\
 baleia & ba*lei*a \cmark & ba*lei-a \xmark \\
+baleio & ba*lei*o \cmark & ba*lei-o \xmark \\
+balio & ba*li*o \cmark & ba*li-o \xmark \\
 balneário & bal*ne-á*ri*o \xmark & bal*ne*á*ri-o \xmark \\
@@
 bamboleio & bam*bo*lei*o \cmark & bam*bo*lei-o \xmark \\
+bancaria & ban*ca*ri*a \cmark & ban*ca*ri-a \xmark \\
 bancário & ban*cá*ri.o \xmark & ban*cá*rio \cmark \\
 bangalô & ban*ga-lô \xmark & ban*ga*lô \cmark \\
+banjoísta & ban*jo-ís*ta \xmark & ban*jo*ís*ta \cmark \\
 barataria & ba*ra*ta*ri*a \cmark & ba*ra*ta*ri-a \xmark \\
 barateio & ba*ra*tei*o \cmark & ba*ra*tei-o \xmark \\
+baraúna & ba*ra-ú*na \xmark & ba*ra*ú*na \cmark \\
+barbaria & bar*ba*ri*a \cmark & bar*ba*ri-a \xmark \\
 barbárie & bar*bá*ri.e \xmark & bar*bá*rie \cmark \\
@@
 bário & bá*ri.o \xmark & bá*rio \cmark \\
+barômetro & ba-rô*me*tro \xmark & ba*rô*me*tro \cmark \\
+baronia & ba*ro*ni*a \cmark & ba*ro*ni-a \xmark \\
 bastião & bas*ti-ão \xmark & bas*ti*ão \cmark \\
@@
 batimetria & ba*ti*me*tri*a \cmark & ba*ti*me*tri-a \xmark \\
+batistério & ba*tis*té*ri.o \xmark & ba*tis*té*rio \cmark \\
 batráquio & ba*trá*qui.o \xmark & ba*trá*quio \cmark \\
@@
 bazófia & ba*zó*fi.a \xmark & ba*zó*fia \cmark \\
+beduíno & be*du-í*no \xmark & be*du*í*no \cmark \\
+behaviorismo & be-ha*vi*o*ris*mo \xmark & be-ha*vi*o*ris*mo \xmark \\
+beligerância & be*li*ge*rân*ci.a \xmark & be*li*ge*rân*cia \cmark \\
 belisário & be*li*sá*ri.o \xmark & be*li*sá*rio \cmark \\
@@
 benefício & be*ne*fí*ci.o \xmark & be*ne*fí*cio \cmark \\
+benemerência & be*ne*me*rên*ci.a \xmark & be*ne*me*rên*cia \cmark \\
 benevolência & be*ne*vo*lên*ci.a \xmark & be*ne*vo*lên*cia \cmark \\
+benfeitoria & ben*fei*to*ri*a \cmark & ben*fei*to*ri-a \xmark \\
 benjoim & ben*jo-im \xmark & ben*jo*im \cmark \\
+benzocaína & ben*zo*ca-í*na \xmark & ben*zo*ca*í*na \cmark \\
 beócio & be-ó*ci.o \xmark & be*ó*cio \cmark \\
@@
 berílio & be*rí*li.o \xmark & be*rí*lio \cmark \\
+berquélio & ber-qué*li.o \xmark & ber*qué*lio \cmark \\
 béstia & bés*ti*a \cmark & bés*ti-a \xmark \\
+bestiário & bes*ti-á*ri.o \xmark & bes*ti*á*rio \cmark \\
 bia & bi*a \cmark & bi-a \xmark \\
 bibelô & bi*be-lô \xmark & bi*be*lô \cmark \\
+bíblia & bí*bli.a \xmark & bí*blia \cmark \\
 bibliofilia & bi*bli*o*fi*li*a \cmark & bi*bli*o*fi*li-a \xmark \\
 bibliófilo & bi*bli-ó*fi*lo \xmark & bi*bli*ó*fi*lo \cmark \\
+bibliofobia & bi*bli*o*fo*bi*a \cmark & bi*bli*o*fo*bi-a \xmark \\
 bibliografia & bi*bli*o*gra*fi*a \cmark & bi*bli*o*gra*fi-a \xmark \\
+bibliógrafo & bi*bli-ó*gra*fo \xmark & bi*bli*ó*gra*fo \cmark \\
 bibliologia & bi*bli*o*lo*gi*a \cmark & bi*bli*o*lo*gi-a \xmark \\
+bibliotecário & bi*bli*o*te*cá*ri.o \xmark & bi*bli*o*te*cá*rio \cmark \\
 biblioteconomia & bi*bli*o*te*co*no*mi*a \cmark & bi*bli*o*te*co*no*mi-a \xmark \\
@@
 bicromia & bi*cro*mi*a \cmark & bi*cro*mi-a \xmark \\
+bicuíba & bi*cu-í*ba \xmark & bi*cu*í*ba \cmark \\
+biênio & bi*ê*ni.o \xmark & bi*ê*nio \cmark \\
 bigamia & bi*ga*mi*a \cmark & bi*ga*mi-a \xmark \\
 bijuteria & bi*ju*te*ri*a \cmark & bi*ju*te*ri-a \xmark \\
+bilbaíno & bil*ba-í*no \xmark & bil*ba*í*no \cmark \\
 bilheteria & bi*lhe*te*ri*a \cmark & bi*lhe*te*ri-a \xmark \\
+bilião & bi*li-ão \xmark & bi*li*ão \cmark \\
+bilionário & bi*li*o*ná*ri.o \xmark & bi*li*o*ná*rio \cmark \\
 binário & bi*ná*ri.o \xmark & bi*ná*rio \cmark \\
+binômio & bi-nô*mi.o \xmark & bi*nô*mio \cmark \\
+biociência & bi*o*ci*ên*ci.a \xmark & bi*o*ci*ên*cia \cmark \\
 bioenergia & bi*o*e*ner*gi*a \cmark & bi*o*e*ner*gi-a \xmark \\
 bioética & bi*o-é*ti*ca \xmark & bi*o*é*ti*ca \cmark \\
+biofilia & bi*o*fi*li*a \cmark & bi*o*fi*li-a \xmark \\
 biófilo & bi-ó*fi*lo \xmark & bi*ó*fi*lo \cmark \\
@@
 biólogo & bi-ó*lo*go \xmark & bi*ó*lo*go \cmark \\
+bioluminescência & bi*o*lu*mi*nes*cên*ci.a \xmark & bi*o*lu*mi*nes*cên*cia \cmark \\
 bioquímica & bi*o-quí*mi*ca \xmark & bi*o*quí*mi*ca \cmark \\
+bioquímico & bi*o-quí*mi*co \xmark & bi*o*quí*mi*co \cmark \\
 biotecnologia & bi*o*tec*no*lo*gi*a \cmark & bi*o*tec*no*lo*gi-a \xmark \\
@@
 biótipo & bi-ó*ti*po \xmark & bi*ó*ti*po \cmark \\
+biótopo & bi-ó*to*po \xmark & bi*ó*to*po \cmark \\
+bipartidário & bi*par*ti*dá*ri.o \xmark & bi*par*ti*dá*rio \cmark \\
 biquíni & bi-quí*ni \xmark & bi*quí*ni \cmark \\
@@
 biscainho & bis*ca-i*nho \xmark & bis*ca*i*nho \cmark \\
+bissemanário & bis*se*ma*ná*ri.o \xmark & bis*se*ma*ná*rio \cmark \\
+biunívoco & bi-u*ní*vo*co \xmark & bi*u*ní*vo*co \cmark \\
+bizâncio & bi*zân*ci.o \xmark & bi*zân*cio \cmark \\
 bizarria & bi*zar*ri*a \cmark & bi*zar*ri-a \xmark \\
+blasfêmia & blas*fê*mi.a \xmark & blas*fê*mia \cmark \\
+blastômero & blas-tô*me*ro \xmark & blas*tô*me*ro \cmark \\
 bloqueio & blo*quei*o \cmark & blo*quei-o \xmark \\
@@
 boá & bo-á \xmark & bo*á \cmark \\
+boataria & bo*a*ta*ri*a \cmark & bo*a*ta*ri-a \xmark \\
 bocaiuva & bo*cai-u*va \xmark & bo*cai*u*va \cmark \\
+bócio & bó*ci.o \xmark & bó*cio \cmark \\
+boé & bo-é \xmark & bo*é \cmark \\
+boemia & bo*e*mi*a \cmark & bo*e*mi-a \xmark \\
+bôer & bô-er \xmark & bô-er \xmark \\
+boia & boi*a \cmark & boi-a \xmark \\
 boião & boi-ão \xmark & boi*ão \cmark \\
@@
 bonomia & bo*no*mi*a \cmark & bo*no*mi-a \xmark \\
+borderô & bor*de-rô \xmark & bor*de*rô \cmark \\
 bordô & bor-dô \xmark & bor*dô \cmark \\
 borracharia & bor*ra*cha*ri*a \cmark & bor*ra*cha*ri-a \xmark \\
+bosníaco & bos*ní-a*co \xmark & bos*ní*a*co \cmark \\
 bósnio & bós*ni.o \xmark & bós*nio \cmark \\
@@
 bradicardia & bra*di*car*di*a \cmark & bra*di*car*di-a \xmark \\
+brânquia & brân*qui.a \xmark & brân*quia \cmark \\
+braquicefalia & bra*qui*ce*fa*li*a \cmark & bra*qui*ce*fa*li-a \xmark \\
+braquidactilia & bra*qui*dac*ti*li*a \cmark & bra*qui*dac*ti*li-a \xmark \\
+braquiópode & bra*qui-ó*po*de \xmark & bra*qui*ó*po*de \cmark \\
+brasiguaio & bra*si*guai*o \cmark & bra*si*guai-o \xmark \\
 brasílio & bra*sí*li.o \xmark & bra*sí*lio \cmark \\
+braúna & bra-ú*na \xmark & bra*ú*na \cmark \\
 bravio & bra*vi*o \cmark & bra*vi-o \xmark \\
@@
 bromélia & bro*mé*li.a \xmark & bro*mé*lia \cmark \\
+broncoscopia & bron*cos*co*pi*a \cmark & bron*cos*co*pi-a \xmark \\
 brônquio & brôn*qui.o \xmark & brôn*quio \cmark \\
@@
 bruxaria & bru*xa*ri*a \cmark & bru*xa*ri-a \xmark \\
+bucelário & bu*ce*lá*ri.o \xmark & bu*ce*lá*rio \cmark \\
 bué & bu-é \xmark & bu*é \cmark \\
+bugia & bu*gi*a \cmark & bu*gi-a \xmark \\
 bugio & bu*gi*o \cmark & bu*gi-o \xmark \\
@@
 butiá & bu*ti-á \xmark & bu*ti*á \cmark \\
+bútio & bú*ti.o \xmark & bú*tio \cmark \\
 búzio & bú*zi.o \xmark & bú*zio \cmark \\
+cabeceio & ca*be*cei*o \cmark & ca*be*cei-o \xmark \\
+cabrião & ca*bri-ão \xmark & ca*bri*ão \cmark \\
+cabriúva & ca*bri-ú*va \xmark & ca*bri*ú*va \cmark \\
 cacaio & ca*cai*o \cmark & ca*cai-o \xmark \\
 cacatua & ca*ca*tu*a \cmark & ca*ca*tu-a \xmark \\
+cacauicultura & ca*cau-i*cul*tu*ra \xmark & ca*cau*i*cul*tu*ra \cmark \\
 cacofonia & ca*co*fo*ni*a \cmark & ca*co*fo*ni-a \xmark \\
+cactácea & cac*tá*ce.a \xmark & cac*tá*cea \cmark \\
 cadeia & ca*dei*a \cmark & ca*dei-a \xmark \\
 cadência & ca*dên*ci.a \xmark & ca*dên*cia \cmark \\
+cádmio & cád*mi.o \xmark & cád*mio \cmark \\
 cafarnaum & ca*far*na-um \xmark & ca*far*na-um \xmark \\
@@
 caim & ca-im \xmark & ca-im \xmark \\
+caimento & ca-i*men*to \xmark & ca-i*men*to \xmark \\
+caingangue & ca-in*gan*gue \xmark & ca-in*gan*gue \xmark \\
 caíque & ca-í*que \xmark & ca*í*que \cmark \\
 cair & ca-ir \xmark & ca*ir \cmark \\
+caixilharia & cai*xi*lha*ri*a \cmark & cai*xi*lha*ri-a \xmark \\
+caixotaria & cai*xo*ta*ri*a \cmark & cai*xo*ta*ri-a \xmark \\
 cajuína & ca*ju-í*na \xmark & ca*ju*í*na \cmark \\
 calafrio & ca*la*fri*o \cmark & ca*la*fri-o \xmark \\
+calcâneo & cal*câ*ne.o \xmark & cal*câ*neo \cmark \\
 calcário & cal*cá*ri*o \cmark & cal*cá*ri-o \xmark \\
+calcedônia & cal*ce-dô*ni.a \xmark & cal*ce*dô*nia \cmark \\
+calcemia & cal*ce*mi*a \cmark & cal*ce*mi-a \xmark \\
 cálcio & cál*ci.o \xmark & cál*cio \cmark \\
 calcografia & cal*co*gra*fi*a \cmark & cal*co*gra*fi-a \xmark \\
+caldário & cal*dá*ri.o \xmark & cal*dá*rio \cmark \\
+caldeiraria & cal*dei*ra*ri*a \cmark & cal*dei*ra*ri-a \xmark \\
 caleidoscópio & ca*lei*dos*có*pi.o \xmark & ca*lei*dos*có*pio \cmark \\
 calendário & ca*len*dá*ri.o \xmark & ca*len*dá*rio \cmark \\
+califasia & ca*li*fa*si*a \cmark & ca*li*fa*si-a \xmark \\
+califórnia & ca*li*fór*ni*a \cmark & ca*li*fór*ni-a \xmark \\
+califórnio & ca*li*fór*ni.o \xmark & ca*li*fór*nio \cmark \\
 caligrafia & ca*li*gra*fi*a \cmark & ca*li*gra*fi-a \xmark \\
+calistenia & ca*lis*te*ni*a \cmark & ca*lis*te*ni-a \xmark \\
 calmaria & cal*ma*ri*a \cmark & cal*ma*ri-a \xmark \\
@@
 calorimetria & ca*lo*ri*me*tri*a \cmark & ca*lo*ri*me*tri-a \xmark \\
+calúnia & ca*lú*ni.a \xmark & ca*lú*nia \cmark \\
 calvário & cal*vá*ri.o \xmark & cal*vá*rio \cmark \\
+calvície & cal*ví*ci.e \xmark & cal*ví*cie \cmark \\
 camaleão & ca*ma*le-ão \xmark & ca*ma*le*ão \cmark \\
+camarário & ca*ma*rá*ri.o \xmark & ca*ma*rá*rio \cmark \\
 cambaio & cam*bai*o \cmark & cam*bai-o \xmark \\
+cambaleio & cam*ba*lei*o \cmark & cam*ba*lei-o \xmark \\
 câmbio & câm*bi.o \xmark & câm*bio \cmark \\
@@
 canária & ca*ná*ri.a \xmark & ca*ná*ria \cmark \\
+canário & ca*ná*ri.o \xmark & ca*ná*rio \cmark \\
+cancelário & can*ce*lá*ri.o \xmark & can*ce*lá*rio \cmark \\
 cancerologia & can*ce*ro*lo*gi*a \cmark & can*ce*ro*lo*gi-a \xmark \\
@@
 canoísta & ca*no-ís*ta \xmark & ca*no*ís*ta \cmark \\
+canônico & ca-nô*ni*co \xmark & ca*nô*ni*co \cmark \\
 cantaria & can*ta*ri*a \cmark & can*ta*ri-a \xmark \\
@@
 caótico & ca-ó*ti*co \xmark & ca*ó*ti*co \cmark \\
+capacitância & ca*pa*ci*tân*ci.a \xmark & ca*pa*ci*tân*cia \cmark \\
 capadócio & ca*pa*dó*ci.o \xmark & ca*pa*dó*cio \cmark \\
 capatazia & ca*pa*ta*zi*a \cmark & ca*pa*ta*zi-a \xmark \\
+capeia & ca*pei*a \cmark & ca*pei-a \xmark \\
 capelania & ca*pe*la*ni*a \cmark & ca*pe*la*ni-a \xmark \\
@@
 capitânia & ca*pi*tâ*ni.a \xmark & ca*pi*tâ*nia \cmark \\
+capnomancia & cap*no*man*ci*a \cmark & cap*no*man*ci-a \xmark \\
 capô & ca-pô \xmark & ca*pô \cmark \\
+capricórnio & ca*pri*cór*ni.o \xmark & ca*pri*cór*nio \cmark \\
 caquexia & ca*que*xi*a \cmark & ca*que*xi-a \xmark \\
+carabídeo & ca*ra*bí*de.o \xmark & ca*ra*bí*deo \cmark \\
+caracterologia & ca*rac*te*ro*lo*gi*a \cmark & ca*rac*te*ro*lo*gi-a \xmark \\
 caraíba & ca*ra-í*ba \xmark & ca*ra*í*ba \cmark \\
@@
 cardápio & car*dá*pi.o \xmark & car*dá*pio \cmark \\
+cárdia & cár*di.a \xmark & cár*dia \cmark \\
 cardíaco & car*dí-a*co \xmark & car*dí*a*co \cmark \\
+cardinalício & car*di*na*lí*ci.o \xmark & car*di*na*lí*cio \cmark \\
 cardiologia & car*di*o*lo*gi*a \cmark & car*di*o*lo*gi-a \xmark \\
+cardiomiopatia & car*di*o*mi*o*pa*ti*a \cmark & car*di*o*mi*o*pa*ti-a \xmark \\
+cardiopatia & car*di*o*pa*ti*a \cmark & car*di*o*pa*ti-a \xmark \\
+cardiorrespiratório & car*di*or*res*pi*ra*tó*ri.o \xmark & car*di*or*res*pi*ra*tó*rio \cmark \\
+carélio & ca*ré*li.o \xmark & ca*ré*lio \cmark \\
 carência & ca*rên*ci.a \xmark & ca*rên*cia \cmark \\
@@
 cárie & cá*ri.e \xmark & cá*rie \cmark \\
+cariogamia & ca*ri*o*ga*mi*a \cmark & ca*ri*o*ga*mi-a \xmark \\
 cariótipo & ca*ri-ó*ti*po \xmark & ca*ri*ó*ti*po \cmark \\
+carnaíba & car*na-í*ba \xmark & car*na*í*ba \cmark \\
 carnaúba & car*na-ú*ba \xmark & car*na*ú*ba \cmark \\
+carnaubal & car*na-u*bal \xmark & car*na-u*bal \xmark \\
+caroá & ca*ro-á \xmark & ca*ro*á \cmark \\
 carolíngio & ca*ro*lín*gi.o \xmark & ca*ro*lín*gio \cmark \\
@@
 carpintaria & car*pin*ta*ri*a \cmark & car*pin*ta*ri-a \xmark \\
+carroçaria & car*ro*ça*ri*a \cmark & car*ro*ça*ri-a \xmark \\
 carroceria & car*ro*ce*ri*a \cmark & car*ro*ce*ri-a \xmark \\
@@
 cartomancia & car*to*man*ci*a \cmark & car*to*man*ci-a \xmark \\
+cartorário & car*to*rá*ri.o \xmark & car*to*rá*rio \cmark \\
 cartório & car*tó*ri.o \xmark & car*tó*rio \cmark \\
+cartulário & car*tu*lá*ri.o \xmark & car*tu*lá*rio \cmark \\
 carvoaria & car*vo*a*ri*a \cmark & car*vo*a*ri-a \xmark \\
@@
 cássia & cás*si.a \xmark & cás*sia \cmark \\
+castelania & cas*te*la*ni*a \cmark & cas*te*la*ni-a \xmark \\
 casuísmo & ca*su-ís*mo \xmark & ca*su*ís*mo \cmark \\
@@
 catalepsia & ca*ta*lep*si*a \cmark & ca*ta*lep*si-a \xmark \\
+cataplexia & ca*ta*ple*xi*a \cmark & ca*ta*ple*xi-a \xmark \\
 catatonia & ca*ta*to*ni*a \cmark & ca*ta*to*ni-a \xmark \\
+catatônico & ca*ta-tô*ni*co \xmark & ca*ta*tô*ni*co \cmark \\
+catenária & ca*te*ná*ri.a \xmark & ca*te*ná*ria \cmark \\
 catequético & ca*te-qué*ti*co \xmark & ca*te*qué*ti*co \cmark \\
+catexia & ca*te*xi*a \cmark & ca*te*xi-a \xmark \\
 catião & ca*ti-ão \xmark & ca*ti*ão \cmark \\
@@
 ceceio & ce*cei*o \cmark & ce*cei-o \xmark \\
+cedência & ce*dên*ci.a \xmark & ce*dên*cia \cmark \\
 cefaleia & ce*fa*lei*a \cmark & ce*fa*lei-a \xmark \\
 ceia & cei*a \cmark & cei-a \xmark \\
+celíaco & ce*lí-a*co \xmark & ce*lí*a*co \cmark \\
+celibatário & ce*li*ba*tá*ri.o \xmark & ce*li*ba*tá*rio \cmark \\
 cemitério & ce*mi*té*ri.o \xmark & ce*mi*té*rio \cmark \\
@@
 censitário & cen*si*tá*ri.o \xmark & cen*si*tá*rio \cmark \\
+censório & cen*só*ri.o \xmark & cen*só*rio \cmark \\
 centáurea & cen*táu*re.a \xmark & cen*táu*rea \cmark \\
@@
 centurião & cen*tu*ri-ão \xmark & cen*tu*ri*ão \cmark \\
+cerambicídeo & ce*ram*bi*cí*de.o \xmark & ce*ram*bi*cí*deo \cmark \\
+ceratoplastia & ce*ra*to*plas*ti*a \cmark & ce*ra*to*plas*ti-a \xmark \\
+cercania & cer*ca*ni*a \cmark & cer*ca*ni-a \xmark \\
 cércea & cér*ce.a \xmark & cér*cea \cmark \\
 cerefólio & ce*re*fó*li.o \xmark & ce*re*fó*lio \cmark \\
+cerimônia & ce*ri-mô*ni.a \xmark & ce*ri*mô*nia \cmark \\
 cério & cé*ri.o \xmark & cé*rio \cmark \\
@@
 cervejaria & cer*ve*ja*ri*a \cmark & cer*ve*ja*ri-a \xmark \\
+cervídeo & cer*ví*de.o \xmark & cer*ví*deo \cmark \\
 cesárea & ce*sá*re.a \xmark & ce*sá*rea \cmark \\
+cesáreo & ce*sá*re.o \xmark & ce*sá*reo \cmark \\
 césio & cé*si.o \xmark & cé*sio \cmark \\
 cessionário & ces*si*o*ná*ri.o \xmark & ces*si*o*ná*rio \cmark \\
+cestaria & ces*ta*ri*a \cmark & ces*ta*ri-a \xmark \\
 cetáceo & ce*tá*ce.o \xmark & ce*tá*ceo \cmark \\
+champô & cham-pô \xmark & cham*pô \cmark \\
 chancelaria & chan*ce*la*ri*a \cmark & chan*ce*la*ri-a \xmark \\
+chapelaria & cha*pe*la*ri*a \cmark & cha*pe*la*ri-a \xmark \\
+charcutaria & char*cu*ta*ri*a \cmark & char*cu*ta*ri-a \xmark \\
 charrua & char*ru*a \cmark & char*ru-a \xmark \\
@@
 choperia & cho*pe*ri*a \cmark & cho*pe*ri-a \xmark \\
+chororô & cho*ro-rô \xmark & cho*ro*rô \cmark \\
+chuleio & chu*lei*o \cmark & chu*lei-o \xmark \\
 churrascaria & chur*ras*ca*ri*a \cmark & chur*ras*ca*ri-a \xmark \\
+ciática & ci-á*ti*ca \xmark & ci*á*ti*ca \cmark \\
 ciático & ci-á*ti*co \xmark & ci*á*ti*co \cmark \\
+ciberespaço & ci*be.r-es*pa*ço \xmark & ci*be.r-es*pa*ço \xmark \\
+cibório & ci*bó*ri.o \xmark & ci*bó*rio \cmark \\
+cicio & ci*ci*o \cmark & ci*ci-o \xmark \\
+ciclídeo & ci*clí*de.o \xmark & ci*clí*deo \cmark \\
 ciclotimia & ci*clo*ti*mi*a \cmark & ci*clo*ti*mi-a \xmark \\
 ciclovia & ci*clo*vi*a \cmark & ci*clo*vi-a \xmark \\
+cicloviário & ci*clo*vi-á*ri.o \xmark & ci*clo*vi*á*rio \cmark \\
 cidadania & ci*da*da*ni*a \cmark & ci*da*da*ni-a \xmark \\
 ciência & ci*ên*ci.a \xmark & ci*ên*cia \cmark \\
+cientologia & ci*en*to*lo*gi*a \cmark & ci*en*to*lo*gi-a \xmark \\
+cilício & ci*lí*ci.o \xmark & ci*lí*cio \cmark \\
 cílio & cí*li.o \xmark & cí*lio \cmark \\
@@
 cinematografia & ci*ne*ma*to*gra*fi*a \cmark & ci*ne*ma*to*gra*fi-a \xmark \\
+cinérea & ci*né*re.a \xmark & ci*né*rea \cmark \\
 cinescópio & ci*nes*có*pi.o \xmark & ci*nes*có*pio \cmark \\
+cinesiologia & ci*ne*si*o*lo*gi*a \cmark & ci*ne*si*o*lo*gi-a \xmark \\
+cinesioterapia & ci*ne*si*o*te*ra*pi*a \cmark & ci*ne*si*o*te*ra*pi-a \xmark \\
 cinestesia & ci*nes*te*si*a \cmark & ci*nes*te*si-a \xmark \\
@@
 cio & ci*o \cmark & ci-o \xmark \\
+ciprinídeo & ci*pri*ní*de.o \xmark & ci*pri*ní*deo \cmark \\
+circulatório & cir*cu*la*tó*ri.o \xmark & cir*cu*la*tó*rio \cmark \\
 circunferência & cir*cun*fe*rên*ci.a \xmark & cir*cun*fe*rên*cia \cmark \\
@@
 cistoscopia & cis*tos*co*pi*a \cmark & cis*tos*co*pi-a \xmark \\
+cistoscópio & cis*tos*có*pi.o \xmark & cis*tos*có*pio \cmark \\
 citânia & ci*tâ*ni.a \xmark & ci*tâ*nia \cmark \\
 citologia & ci*to*lo*gi*a \cmark & ci*to*lo*gi-a \xmark \\
+citopatologia & ci*to*pa*to*lo*gi*a \cmark & ci*to*pa*to*lo*gi-a \xmark \\
 ciúme & ci-ú*me \xmark & ci*ú*me \cmark \\
 cizânia & ci*zâ*ni.a \xmark & ci*zâ*nia \cmark \\
+clamídia & cla*mí*di.a \xmark & cla*mí*dia \cmark \\
 claraboia & cla*ra*boi*a \cmark & cla*ra*boi-a \xmark \\
@@
 cleptomania & clep*to*ma*ni*a \cmark & clep*to*ma*ni-a \xmark \\
+climatério & cli*ma*té*ri.o \xmark & cli*ma*té*rio \cmark \\
 climatologia & cli*ma*to*lo*gi*a \cmark & cli*ma*to*lo*gi-a \xmark \\
+clípeo & clí*pe.o \xmark & clí*peo \cmark \\
 clorofórmio & clo*ro*fór*mi.o \xmark & clo*ro*fór*mio \cmark \\
@@
 coágulo & co-á*gu*lo \xmark & co*á*gu*lo \cmark \\
+coalescência & co*a*les*cên*ci.a \xmark & co*a*les*cên*cia \cmark \\
+coautoria & co*au*to*ri*a \cmark & co*au*to*ri-a \xmark \\
 cobaia & co*bai*a \cmark & co*bai-a \xmark \\
@@
 cocaína & co*ca-í*na \xmark & co*ca*í*na \cmark \\
+cóclea & có*cle.a \xmark & có*clea \cmark \\
 cocô & co-cô \xmark & co*cô \cmark \\
@@
 coibir & co-i*bir \xmark & co-i*bir \xmark \\
+coimbrão & co-im*brão \xmark & co*im*brão \cmark \\
 coincidência & co-in*ci*dên*ci.a \xmark & co*in*ci*dên*cia \cmark \\
@@
 coincidir & co-in*ci*dir \xmark & co*in*ci*dir \cmark \\
+coirmão & co-ir*mão \xmark & co-ir*mão \xmark \\
 colcheia & col*chei*a \cmark & col*chei-a \xmark \\
@@
 coleóptero & co*le-óp*te*ro \xmark & co*le*óp*te*ro \cmark \\
+coletânea & co*le*tâ*ne.a \xmark & co*le*tâ*nea \cmark \\
+coletoria & co*le*to*ri*a \cmark & co*le*to*ri-a \xmark \\
+colírio & co*lí*ri.o \xmark & co*lí*rio \cmark \\
 colmeia & col*mei*a \cmark & col*mei-a \xmark \\
+colódio & co*ló*di.o \xmark & co*ló*dio \cmark \\
 colonia & co*lo*ni*a \cmark & co*lo*ni-a \xmark \\
+colônia & co-lô*ni.a \xmark & co*lô*nia \cmark \\
 colonoscopia & co*lo*nos*co*pi*a \cmark & co*lo*nos*co*pi-a \xmark \\
 colóquio & co*ló*qui.o \xmark & co*ló*quio \cmark \\
+colorimetria & co*lo*ri*me*tri*a \cmark & co*lo*ri*me*tri-a \xmark \\
+colostomia & co*los*to*mi*a \cmark & co*los*to*mi-a \xmark \\
+colposcopia & col*pos*co*pi*a \cmark & col*pos*co*pi-a \xmark \\
+colposcópio & col*pos*có*pi.o \xmark & col*pos*có*pio \cmark \\
+columbário & co*lum*bá*ri.o \xmark & co*lum*bá*rio \cmark \\
+colúmbio & co*lúm*bi.o \xmark & co*lúm*bio \cmark \\
 columbofilia & co*lum*bo*fi*li*a \cmark & co*lum*bo*fi*li-a \xmark \\
+colutório & co*lu*tó*ri.o \xmark & co*lu*tó*rio \cmark \\
+comandância & co*man*dân*ci.a \xmark & co*man*dân*cia \cmark \\
 combinatório & com*bi*na*tó*ri.o \xmark & com*bi*na*tó*rio \cmark \\
 comboio & com*boi*o \cmark & com*boi-o \xmark \\
+comedia & co*me*di*a \cmark & co*me*di-a \xmark \\
 comédia & co*mé*di.a \xmark & co*mé*dia \cmark \\
 comediógrafo & co*me*di-ó*gra*fo \xmark & co*me*di*ó*gra*fo \cmark \\
+comedoria & co*me*do*ri*a \cmark & co*me*do*ri-a \xmark \\
+comendatário & co*men*da*tá*ri.o \xmark & co*men*da*tá*rio \cmark \\
 comentário & co*men*tá*ri.o \xmark & co*men*tá*rio \cmark \\
@@
 comércio & co*mér*ci.o \xmark & co*mér*cio \cmark \\
+cometário & co*me*tá*ri.o \xmark & co*me*tá*rio \cmark \\
 comício & co*mí*ci.o \xmark & co*mí*cio \cmark \\
 comissário & co*mis*sá*ri.o \xmark & co*mis*sá*rio \cmark \\
+compadrio & com*pa*dri*o \cmark & com*pa*dri-o \xmark \\
 companhia & com*pa*nhi*a \cmark & com*pa*nhi-a \xmark \\
+comparência & com*pa*rên*ci.a \xmark & com*pa*rên*cia \cmark \\
 comparsaria & com*par*sa*ri*a \cmark & com*par*sa*ri-a \xmark \\
@@
 competência & com*pe*tên*ci.a \xmark & com*pe*tên*cia \cmark \\
+compilatório & com*pi*la*tó*ri.o \xmark & com*pi*la*tó*rio \cmark \\
 complacência & com*pla*cên*ci.a \xmark & com*pla*cên*cia \cmark \\
@@
 compulsório & com*pul*só*ri.o \xmark & com*pul*só*rio \cmark \\
+comunitário & co*mu*ni*tá*ri.o \xmark & co*mu*ni*tá*rio \cmark \\
+concelhio & con*ce*lhi*o \cmark & con*ce*lhi-o \xmark \\
+concessionária & con*ces*si*o*ná*ri.a \xmark & con*ces*si*o*ná*ria \cmark \\
+concessionário & con*ces*si*o*ná*ri.o \xmark & con*ces*si*o*ná*rio \cmark \\
 conciliábulo & con*ci*li-á*bu*lo \xmark & con*ci*li*á*bu*lo \cmark \\
+conciliatório & con*ci*li*a*tó*ri.o \xmark & con*ci*li*a*tó*rio \cmark \\
 conciliável & con*ci*li-á*vel \xmark & con*ci*li*á*vel \cmark \\
@@
 concluir & con*clu-ir \xmark & con*clu*ir \cmark \\
+concomitância & con*co*mi*tân*ci.a \xmark & con*co*mi*tân*cia \cmark \\
 concordância & con*cor*dân*ci.a \xmark & con*cor*dân*cia \cmark \\
+concordatário & con*cor*da*tá*ri.o \xmark & con*cor*da*tá*rio \cmark \\
 concórdia & con*cór*di.a \xmark & con*cór*dia \cmark \\
@@
 condomínio & con*do*mí*ni.o \xmark & con*do*mí*nio \cmark \\
+condômino & con-dô*mi*no \xmark & con*dô*mi*no \cmark \\
+conduíte & con*du-í*te \xmark & con*du*í*te \cmark \\
+condutância & con*du*tân*ci.a \xmark & con*du*tân*cia \cmark \\
 confeitaria & con*fei*ta*ri*a \cmark & con*fei*ta*ri-a \xmark \\
@@
 confidência & con*fi*dên*ci.a \xmark & con*fi*dên*cia \cmark \\
+confirmatório & con*fir*ma*tó*ri.o \xmark & con*fir*ma*tó*rio \cmark \\
 confluência & con*flu-ên*ci.a \xmark & con*flu*ên*cia \cmark \\
@@
 confraria & con*fra*ri*a \cmark & con*fra*ri-a \xmark \\
+côngio & côn*gi.o \xmark & côn*gio \cmark \\
 congruência & con*gru-ên*ci.a \xmark & con*gru*ên*cia \cmark \\
+conivência & co*ni*vên*ci.a \xmark & co*ni*vên*cia \cmark \\
 conluio & con*lui*o \cmark & con*lui-o \xmark \\
@@
 consistório & con*sis*tó*ri*o \cmark & con*sis*tó*ri-o \xmark \\
+consócio & con*só*ci.o \xmark & con*só*cio \cmark \\
 consonância & con*so*nân*ci*a \cmark & con*so*nân*ci-a \xmark \\
@@
 conspícuo & cons*pí*cu.o \xmark & cons*pí*cuo \cmark \\
+conspiratório & cons*pi*ra*tó*ri.o \xmark & cons*pi*ra*tó*rio \cmark \\
 constância & cons*tân*ci.a \xmark & cons*tân*cia \cmark \\
@@
 consultório & con*sul*tó*ri.o \xmark & con*sul*tó*rio \cmark \\
+contadoria & con*ta*do*ri*a \cmark & con*ta*do*ri-a \xmark \\
 contágio & con*tá*gi.o \xmark & con*tá*gio \cmark \\
@@
 contemporâneo & con*tem*po*râ*ne.o \xmark & con*tem*po*râ*neo \cmark \\
+conterrâneo & con*ter*râ*ne.o \xmark & con*ter*râ*neo \cmark \\
+conteudista & con*te-u*dis*ta \xmark & con*te-u*dis*ta \xmark \\
 conteúdo & con*te-ú*do \xmark & con*te*ú*do \cmark \\
@@
 contínua & con*tí*nu.a \xmark & con*tí*nua \cmark \\
+continuidade & con*ti*nu-i*da*de \xmark & con*ti*nu*i*da*de \cmark \\
+continuísta & con*ti*nu-ís*ta \xmark & con*ti*nu*ís*ta \cmark \\
 contínuo & con*tí*nu.o \xmark & con*tí*nuo \cmark \\
+contrabateria & con*tra*ba*te*ri*a \cmark & con*tra*ba*te*ri-a \xmark \\
+contraditória & con*tra*di*tó*ri.a \xmark & con*tra*di*tó*ria \cmark \\
 contraditório & con*tra*di*tó*ri.o \xmark & con*tra*di*tó*rio \cmark \\
+contradomínio & con*tra*do*mí*ni.o \xmark & con*tra*do*mí*nio \cmark \\
 contraído & con*tra-í*do \xmark & con*tra*í*do \cmark \\
+contraindicação & con*tra-in*di*ca*ção \xmark & con*tra*in*di*ca*ção \cmark \\
 contrair & con*tra-ir \xmark & con*tra*ir \cmark \\
 contrário & con*trá*ri.o \xmark & con*trá*rio \cmark \\
+contrastaria & con*tras*ta*ri*a \cmark & con*tras*ta*ri-a \xmark \\
 contribuição & con*tri*bu-i*ção \xmark & con*tri*bu*i*ção \cmark \\
@@
 convívio & con*ví*vi*o \cmark & con*ví*vi-o \xmark \\
+convocatória & con*vo*ca*tó*ri.a \xmark & con*vo*ca*tó*ria \cmark \\
+convocatório & con*vo*ca*tó*ri.o \xmark & con*vo*ca*tó*rio \cmark \\
 coordenadoria & co*or*de*na*do*ri*a \cmark & co*or*de*na*do*ri-a \xmark \\
@@
 cópia & có*pi.a \xmark & có*pia \cmark \\
+copião & co*pi-ão \xmark & co*pi*ão \cmark \\
+copio & co*pi*o \cmark & co*pi-o \xmark \\
+coprofagia & co*pro*fa*gi*a \cmark & co*pro*fa*gi-a \xmark \\
 coprofilia & co*pro*fi*li*a \cmark & co*pro*fi*li-a \xmark \\
 coprolalia & co*pro*la*li*a \cmark & co*pro*la*li-a \xmark \\
+coqueria & co*que*ri*a \cmark & co*que*ri-a \xmark \\
+coquetelaria & co*que*te*la*ri*a \cmark & co*que*te*la*ri-a \xmark \\
+coqueteria & co*que*te*ri*a \cmark & co*que*te*ri-a \xmark \\
+cordoaria & cor*do*a*ri*a \cmark & cor*do*a*ri-a \xmark \\
 coreia & co*rei*a \cmark & co*rei-a \xmark \\
@@
 coreógrafo & co*re-ó*gra*fo \xmark & co*re*ó*gra*fo \cmark \\
+coreomania & co*re*o*ma*ni*a \cmark & co*re*o*ma*ni-a \xmark \\
+coriáceo & co*ri-á*ce.o \xmark & co*ri*á*ceo \cmark \\
 coríntio & co*rín*ti.o \xmark & co*rín*tio \cmark \\
+cório & có*ri.o \xmark & có*rio \cmark \\
 córnea & cór*ne.a \xmark & cór*nea \cmark \\
@@
 coroa & co*ro*a \cmark & co*ro-a \xmark \\
+corografia & co*ro*gra*fi*a \cmark & co*ro*gra*fi-a \xmark \\
+coroideia & co*roi*dei*a \cmark & co*roi*dei-a \xmark \\
 coroinha & co*ro-i*nha \xmark & co*ro*i*nha \cmark \\
@@
 corpóreo & cor*pó*re.o \xmark & cor*pó*reo \cmark \\
+corpulência & cor*pu*lên*ci.a \xmark & cor*pu*lên*cia \cmark \\
 corregedoria & cor*re*ge*do*ri*a \cmark & cor*re*ge*do*ri-a \xmark \\
@@
 corroído & cor*ro-í*do \xmark & cor*ro*í*do \cmark \\
+corruíra & cor*ru-í*ra \xmark & cor*ru*í*ra \cmark \\
+corrupião & cor*ru*pi-ão \xmark & cor*ru*pi*ão \cmark \\
+corrupio & cor*ru*pi*o \cmark & cor*ru*pi-o \xmark \\
 corsário & cor*sá*ri.o \xmark & cor*sá*rio \cmark \\
@@
 corveia & cor*vei*a \cmark & cor*vei-a \xmark \\
+cosmetologia & cos*me*to*lo*gi*a \cmark & cos*me*to*lo*gi-a \xmark \\
 cosmogonia & cos*mo*go*ni*a \cmark & cos*mo*go*ni-a \xmark \\
@@
 cotia & co*ti*a \cmark & co*ti-a \xmark \\
+cotonifício & co*to*ni*fí*ci.o \xmark & co*to*ni*fí*cio \cmark \\
 cotovia & co*to*vi*a \cmark & co*to*vi-a \xmark \\
@@
 crânio & crâ*ni.o \xmark & crâ*nio \cmark \\
+craniometria & cra*ni*o*me*tri*a \cmark & cra*ni*o*me*tri-a \xmark \\
+craniotomia & cra*ni*o*to*mi*a \cmark & cra*ni*o*to*mi-a \xmark \\
+crapô & cra-pô \xmark & cra*pô \cmark \\
+credência & cre*dên*ci.a \xmark & cre*dên*cia \cmark \\
 crediário & cre*di-á*ri.o \xmark & cre*di*á*rio \cmark \\
+creditício & cre*di*tí*ci.o \xmark & cre*di*tí*cio \cmark \\
+creperia & cre*pe*ri*a \cmark & cre*pe*ri-a \xmark \\
 cretáceo & cre*tá*ce.o \xmark & cre*tá*ceo \cmark \\
 cria & cri*a \cmark & cri-a \xmark \\
+criatório & cri*a*tó*ri.o \xmark & cri*a*tó*rio \cmark \\
 criciúma & cri*ci-ú*ma \xmark & cri*ci*ú*ma \cmark \\
 criminologia & cri*mi*no*lo*gi*a \cmark & cri*mi*no*lo*gi-a \xmark \\
+criobiologia & cri*o*bi*o*lo*gi*a \cmark & cri*o*bi*o*lo*gi-a \xmark \\
+criocirurgia & cri*o*ci*rur*gi*a \cmark & cri*o*ci*rur*gi-a \xmark \\
+criogenia & cri*o*ge*ni*a \cmark & cri*o*ge*ni-a \xmark \\
+crioscopia & cri*os*co*pi*a \cmark & cri*os*co*pi-a \xmark \\
+crioterapia & cri*o*te*ra*pi*a \cmark & cri*o*te*ra*pi-a \xmark \\
 criptologia & crip*to*lo*gi*a \cmark & crip*to*lo*gi-a \xmark \\
 criptônimo & crip-tô*ni*mo \xmark & crip*tô*ni*mo \cmark \\
+criptônio & crip-tô*ni.o \xmark & crip*tô*nio \cmark \\
+criptorquidia & crip*tor*qui*di*a \cmark & crip*tor*qui*di-a \xmark \\
 cristalografia & cris*ta*lo*gra*fi*a \cmark & cris*ta*lo*gra*fi-a \xmark \\
@@
 critério & cri*té*ri.o \xmark & cri*té*rio \cmark \\
+criticaria & cri*ti*ca*ri*a \cmark & cri*ti*ca*ri-a \xmark \\
+cróceo & cró*ce.o \xmark & cró*ceo \cmark \\
 cromatografia & cro*ma*to*gra*fi*a \cmark & cro*ma*to*gra*fi-a \xmark \\
@@
 cronômetro & cro-nô*me*tro \xmark & cro*nô*me*tro \cmark \\
+crotalária & cro*ta*lá*ri.a \xmark & cro*ta*lá*ria \cmark \\
 crustáceo & crus*tá*ce.o \xmark & crus*tá*ceo \cmark \\
+crúzio & crú*zi.o \xmark & crú*zio \cmark \\
+cubiculário & cu*bi*cu*lá*ri.o \xmark & cu*bi*cu*lá*rio \cmark \\
 cucurbitácea & cu*cur*bi*tá*ce.a \xmark & cu*cur*bi*tá*cea \cmark \\
@@
 culminância & cul*mi*nân*ci.a \xmark & cul*mi*nân*cia \cmark \\
+cúneo & cú*ne.o \xmark & cú*neo \cmark \\
 curadoria & cu*ra*do*ri*a \cmark & cu*ra*do*ri-a \xmark \\
@@
 cúrio & cú*ri.o \xmark & cú*rio \cmark \\
+curiúva & cu*ri-ú*va \xmark & cu*ri*ú*va \cmark \\
 curvilíneo & cur*vi*lí*ne.o \xmark & cur*vi*lí*neo \cmark \\
@@
 custódio & cus*tó*di.o \xmark & cus*tó*dio \cmark \\
+cutâneo & cu*tâ*ne.o \xmark & cu*tâ*neo \cmark \\
 cutelaria & cu*te*la*ri*a \cmark & cu*te*la*ri-a \xmark \\
 cutia & cu*ti*a \cmark & cu*ti-a \xmark \\
+cuxiú & cu*xi-ú \xmark & cu*xi*ú \cmark \\
+czar & c.zar \xmark & czar \cmark \\
 czarina & c.za*ri*na \xmark & cza*ri*na \cmark \\
@@
 czarista & c.za*ris*ta \xmark & cza*ris*ta \cmark \\
+dáblio & dá*bli.o \xmark & dá*blio \cmark \\
+dácio & dá*ci.o \xmark & dá*cio \cmark \\
 dactiloscopia & dac*ti*los*co*pi*a \cmark & dac*ti*los*co*pi-a \xmark \\
@@
 darwinista & dar-wi*nis*ta \xmark & dar-wi*nis*ta \xmark \\
+datário & da*tá*ri.o \xmark & da*tá*rio \cmark \\
+datilografia & da*ti*lo*gra*fi*a \cmark & da*ti*lo*gra*fi-a \xmark \\
+datiloscopia & da*ti*los*co*pi*a \cmark & da*ti*los*co*pi-a \xmark \\
+deambulatório & de*am*bu*la*tó*ri.o \xmark & de*am*bu*la*tó*rio \cmark \\
 deão & de-ão \xmark & de*ão \cmark \\
+debelatório & de*be*la*tó*ri.o \xmark & de*be*la*tó*rio \cmark \\
 decacampeão & de*ca*cam*pe-ão \xmark & de*ca*cam*pe*ão \cmark \\
@@
 decalcomania & de*cal*co*ma*ni*a \cmark & de*cal*co*ma*ni-a \xmark \\
+decania & de*ca*ni*a \cmark & de*ca*ni-a \xmark \\
 decência & de*cên*ci.a \xmark & de*cên*cia \cmark \\
 decêndio & de*cên*di.o \xmark & de*cên*dio \cmark \\
+decênio & de*cê*ni.o \xmark & de*cê*nio \cmark \\
+decídua & de*cí*du.a \xmark & de*cí*dua \cmark \\
+decíduo & de*cí*du.o \xmark & de*cí*duo \cmark \\
 decisório & de*ci*só*ri.o \xmark & de*ci*só*rio \cmark \\
+declamatório & de*cla*ma*tó*ri.o \xmark & de*cla*ma*tó*rio \cmark \\
+declaratório & de*cla*ra*tó*ri.o \xmark & de*cla*ra*tó*rio \cmark \\
 declínio & de*clí*ni.o \xmark & de*clí*nio \cmark \\
@@
 decurião & de*cu*ri-ão \xmark & de*cu*ri*ão \cmark \\
+dedicatória & de*di*ca*tó*ri.a \xmark & de*di*ca*tó*ria \cmark \\
 defensoria & de*fen*so*ri*a \cmark & de*fen*so*ri-a \xmark \\
@@
 deficitário & de*fi*ci*tá*ri.o \xmark & de*fi*ci*tá*rio \cmark \\
+definitório & de*fi*ni*tó*ri.o \xmark & de*fi*ni*tó*rio \cmark \\
+deflacionário & de*fla*ci*o*ná*ri.o \xmark & de*fla*ci*o*ná*rio \cmark \\
+deflúvio & de*flú*vi.o \xmark & de*flú*vio \cmark \\
+degenerescência & de*ge*ne*res*cên*ci.a \xmark & de*ge*ne*res*cên*cia \cmark \\
 deia & dei*a \cmark & dei-a \xmark \\
+deificação & de-i*fi*ca*ção \xmark & de-i*fi*ca*ção \xmark \\
+deiscente & de-is*cen*te \xmark & de-is*cen*te \xmark \\
 deísmo & de-ís*mo \xmark & de*ís*mo \cmark \\
@@
 deletério & de*le*té*ri.o \xmark & de*le*té*rio \cmark \\
+delfínio & del*fí*ni.o \xmark & del*fí*nio \cmark \\
 delícia & de*lí*ci.a \xmark & de*lí*cia \cmark \\
 delinquência & de*lin-quên*ci.a \xmark & de*lin*quên*cia \cmark \\
+délio & dé*li.o \xmark & dé*lio \cmark \\
 delírio & de*lí*ri.o \xmark & de*lí*rio \cmark \\
@@
 demasia & de*ma*si*a \cmark & de*ma*si-a \xmark \\
+demência & de*mên*ci.a \xmark & de*mên*cia \cmark \\
 demissionário & de*mis*si*o*ná*ri.o \xmark & de*mis*si*o*ná*rio \cmark \\
+demiúrgico & de*mi-úr*gi*co \xmark & de*mi*úr*gi*co \cmark \\
 demiurgo & de*mi-ur*go \xmark & de*mi*ur*go \cmark \\
@@
 demoníaco & de*mo*ní-a*co \xmark & de*mo*ní*a*co \cmark \\
+demônio & de-mô*ni.o \xmark & de*mô*nio \cmark \\
 demonologia & de*mo*no*lo*gi*a \cmark & de*mo*no*lo*gi-a \xmark \\
+denário & de*ná*ri.o \xmark & de*ná*rio \cmark \\
 dendrocronologia & den*dro*cro*no*lo*gi*a \cmark & den*dro*cro*no*lo*gi-a \xmark \\
@@
 densitometria & den*si*to*me*tri*a \cmark & den*si*to*me*tri-a \xmark \\
+dentária & den*tá*ri.a \xmark & den*tá*ria \cmark \\
+dentário & den*tá*ri.o \xmark & den*tá*rio \cmark \\
 dentifrício & den*ti*frí*ci.o \xmark & den*ti*frí*cio \cmark \\
@@
 depositário & de*po*si*tá*ri.o \xmark & de*po*si*tá*rio \cmark \\
+depreciável & de*pre*ci-á*vel \xmark & de*pre*ci*á*vel \cmark \\
 dermatologia & der*ma*to*lo*gi*a \cmark & der*ma*to*lo*gi-a \xmark \\
+derrisório & der*ri*só*ri.o \xmark & der*ri*só*rio \cmark \\
 desafio & de*sa*fi*o \cmark & de*sa*fi-o \xmark \\
+deságio & de*sá*gi.o \xmark & de*sá*gio \cmark \\
 desarmonia & de*sar*mo*ni*a \cmark & de*sar*mo*ni-a \xmark \\
+desassistência & de*sas*sis*tên*ci.a \xmark & de*sas*sis*tên*cia \cmark \\
 desbloqueio & des*blo*quei*o \cmark & des*blo*quei-o \xmark \\
@@
 desconstruir & des*cons*tru-ir \xmark & des*cons*tru*ir \cmark \\
+descontinuidade & des*con*ti*nu-i*da*de \xmark & des*con*ti*nu*i*da*de \cmark \\
 descontraído & des*con*tra-í*do \xmark & des*con*tra*í*do \cmark \\
@@
 desídia & de*sí*di.a \xmark & de*sí*dia \cmark \\
+desígnio & de*síg*ni.o \xmark & de*síg*nio \cmark \\
 desinência & de*si*nên*ci.a \xmark & de*si*nên*cia \cmark \\
@@
 desmaio & des*mai*o \cmark & des*mai-o \xmark \\
+desmemória & des*me*mó*ri.a \xmark & des*me*mó*ria \cmark \\
 desnecessário & des*ne*ces*sá*ri.o \xmark & des*ne*ces*sá*rio \cmark \\
+desnorteio & des*nor*tei*o \cmark & des*nor*tei-o \xmark \\
 desobediência & de*so*be*di*ên*ci.a \xmark & de*so*be*di*ên*cia \cmark \\
 desobstruir & de*sobs*tru-ir \xmark & de*sobs*tru*ir \cmark \\
+despautério & des*pau*té*ri.o \xmark & des*pau*té*rio \cmark \\
+desperdício & des*per*dí*ci.o \xmark & des*per*dí*cio \cmark \\
 despoluição & des*po*lu-i*ção \xmark & des*po*lu*i*ção \cmark \\
@@
 desprestígio & des*pres*tí*gi*o \cmark & des*pres*tí*gi-o \xmark \\
+destampatório & des*tam*pa*tó*ri.o \xmark & des*tam*pa*tó*rio \cmark \\
+destilaria & des*ti*la*ri*a \cmark & des*ti*la*ri-a \xmark \\
 destinatário & des*ti*na*tá*ri.o \xmark & des*ti*na*tá*rio \cmark \\
@@
 destruído & des*tru-í*do \xmark & des*tru*í*do \cmark \\
+destruidor & des*tru-i*dor \xmark & des*tru-i*dor \xmark \\
 destruir & des*tru-ir \xmark & des*tru*ir \cmark \\
+desunião & de*su*ni-ão \xmark & de*su*ni*ão \cmark \\
 desvario & des*va*ri*o \cmark & des*va*ri-o \xmark \\
@@
 devaneio & de*va*nei*o \cmark & de*va*nei-o \xmark \\
+diábase & di-á*ba*se \xmark & di*á*ba*se \cmark \\
+diabásio & di*a*bá*si.o \xmark & di*a*bá*sio \cmark \\
 diaconia & di*a*co*ni*a \cmark & di*a*co*ni-a \xmark \\
@@
 diacronia & di*a*cro*ni*a \cmark & di*a*cro*ni-a \xmark \\
+díada & dí-a*da \xmark & dí*a*da \cmark \\
 díade & dí-a*de \xmark & dí*a*de \cmark \\
 dia & di*a \cmark & di-a \xmark \\
+diádico & di-á*di*co \xmark & di*á*di*co \cmark \\
+diádoco & di-á*do*co \xmark & di*á*do*co \cmark \\
 diáfano & di-á*fa*no \xmark & di*á*fa*no \cmark \\
+diáfise & di-á*fi*se \xmark & di*á*fi*se \cmark \\
+dialetologia & di*a*le*to*lo*gi*a \cmark & di*a*le*to*lo*gi-a \xmark \\
 diálise & di-á*li*se \xmark & di*á*li*se \cmark \\
@@
 diáspora & di-ás*po*ra \xmark & di*ás*po*ra \cmark \\
+diásporo & di-ás*po*ro \xmark & di*ás*po*ro \cmark \\
 diástole & di-ás*to*le \xmark & di*ás*to*le \cmark \\
+diatômico & di*a-tô*mi*co \xmark & di*a*tô*mi*co \cmark \\
+dicastério & di*cas*té*ri.o \xmark & di*cas*té*rio \cmark \\
 dicionário & di*ci*o*ná*ri.o \xmark & di*ci*o*ná*rio \cmark \\
+dicogamia & di*co*ga*mi*a \cmark & di*co*ga*mi-a \xmark \\
 dicotomia & di*co*to*mi*a \cmark & di*co*to*mi-a \xmark \\
+dicotômico & di*co-tô*mi*co \xmark & di*co*tô*mi*co \cmark \\
 dicroísmo & di*cro-ís*mo \xmark & di*cro*ís*mo \cmark \\
+didímio & di*dí*mi.o \xmark & di*dí*mio \cmark \\
+diédrico & di-é*dri*co \xmark & di*é*dri*co \cmark \\
 diérese & di-é*re*se \xmark & di*é*re*se \cmark \\
+difamatório & di*fa*ma*tó*ri.o \xmark & di*fa*ma*tó*rio \cmark \\
 diferenciável & di*fe*ren*ci-á*vel \xmark & di*fe*ren*ci*á*vel \cmark \\
@@
 difteria & dif*te*ri*a \cmark & dif*te*ri-a \xmark \\
+digestório & di*ges*tó*ri.o \xmark & di*ges*tó*rio \cmark \\
 diglossia & di*glos*si*a \cmark & di*glos*si-a \xmark \\
@@
 diligência & di*li*gên*ci.a \xmark & di*li*gên*cia \cmark \\
+diluição & di*lu-i*ção \xmark & di*lu*i*ção \cmark \\
 diluído & di*lu-í*do \xmark & di*lu*í*do \cmark \\
@@
 dinamarquês & di*na*mar-quês \xmark & di*na*mar*quês \cmark \\
+dinamômetro & di*na-mô*me*tro \xmark & di*na*mô*me*tro \cmark \\
 dinastia & di*nas*ti*a \cmark & di*nas*ti-a \xmark \\
+díodo & dí-o*do \xmark & dí*o*do \cmark \\
+dioneia & di*o*nei*a \cmark & di*o*nei-a \xmark \\
 dionisíaco & di*o*ni*sí-a*co \xmark & di*o*ni*sí*a*co \cmark \\
+dioptria & di*op*tri*a \cmark & di*op*tri-a \xmark \\
+dióptrica & di-óp*tri*ca \xmark & di*óp*tri*ca \cmark \\
 dióxido & di-ó*xi*do \xmark & di*ó*xi*do \cmark \\
@@
 diplomacia & di*plo*ma*ci*a \cmark & di*plo*ma*ci-a \xmark \\
+diplopia & di*plo*pi*a \cmark & di*plo*pi-a \xmark \\
 diretoria & di*re*to*ri*a \cmark & di*re*to*ri-a \xmark \\
@@
 disartria & di*sar*tri*a \cmark & di*sar*tri-a \xmark \\
+discalculia & dis*cal*cu*li*a \cmark & dis*cal*cu*li-a \xmark \\
 discinesia & dis*ci*ne*si*a \cmark & dis*ci*ne*si-a \xmark \\
@@
 discricionário & dis*cri*ci*o*ná*ri.o \xmark & dis*cri*ci*o*ná*rio \cmark \\
+discriminatório & dis*cri*mi*na*tó*ri.o \xmark & dis*cri*mi*na*tó*rio \cmark \\
 disenteria & di*sen*te*ri*a \cmark & di*sen*te*ri-a \xmark \\
@@
 disgenesia & dis*ge*ne*si*a \cmark & dis*ge*ne*si-a \xmark \\
+disgrafia & dis*gra*fi*a \cmark & dis*gra*fi-a \xmark \\
 dislalia & dis*la*li*a \cmark & dis*la*li-a \xmark \\
@@
 dismenorreia & dis*me*nor*rei*a \cmark & dis*me*nor*rei-a \xmark \\
+dismorfia & dis*mor*fi*a \cmark & dis*mor*fi-a \xmark \\
+dispareunia & dis*pa*reu*ni*a \cmark & dis*pa*reu*ni-a \xmark \\
 dispêndio & dis*pên*di.o \xmark & dis*pên*dio \cmark \\
+dispensário & dis*pen*sá*ri.o \xmark & dis*pen*sá*rio \cmark \\
 dispepsia & dis*pep*si*a \cmark & dis*pep*si-a \xmark \\
@@
 dispneia & disp*nei*a \cmark & disp*nei-a \xmark \\
+dispraxia & dis*pra*xi*a \cmark & dis*pra*xi-a \xmark \\
 disprósio & dis*pró*si.o \xmark & dis*pró*sio \cmark \\
@@
 distonia & dis*to*ni*a \cmark & dis*to*ni-a \xmark \\
+distopia & dis*to*pi*a \cmark & dis*to*pi-a \xmark \\
 distraído & dis*tra-í*do \xmark & dis*tra*í*do \cmark \\
@@
 distribuir & dis*tri*bu-ir \xmark & dis*tri*bu*ir \cmark \\
+distrofia & dis*tro*fi*a \cmark & dis*tro*fi-a \xmark \\
 distúrbio & dis*túr*bi.o \xmark & dis*túr*bio \cmark \\
@@
 divergência & di*ver*gên*ci.a \xmark & di*ver*gên*cia \cmark \\
+divinatório & di*vi*na*tó*ri.o \xmark & di*vi*na*tó*rio \cmark \\
+divisionário & di*vi*si*o*ná*ri.o \xmark & di*vi*si*o*ná*rio \cmark \\
 divisória & di*vi*só*ri.a \xmark & di*vi*só*ria \cmark \\
@@
 divórcio & di*vór*ci.o \xmark & di*vór*cio \cmark \\
+doçaria & do*ça*ri*a \cmark & do*ça*ri-a \xmark \\
+docência & do*cên*ci.a \xmark & do*cên*cia \cmark \\
 doceria & do*ce*ri*a \cmark & do*ce*ri-a \xmark \\
@@
 doído & do-í*do \xmark & do*í*do \cmark \\
+dolência & do*lên*ci.a \xmark & do*lên*cia \cmark \\
 domiciliário & do*mi*ci*li-á*ri.o \xmark & do*mi*ci*li*á*rio \cmark \\
 domicílio & do*mi*cí*li.o \xmark & do*mi*cí*lio \cmark \\
+dominância & do*mi*nân*ci.a \xmark & do*mi*nân*cia \cmark \\
 domínio & do*mí*ni.o \xmark & do*mí*nio \cmark \\
@@
 donatário & do*na*tá*ri.o \xmark & do*na*tá*rio \cmark \\
+dório & dó*ri.o \xmark & dó*rio \cmark \\
+dormência & dor*mên*ci.a \xmark & dor*mên*cia \cmark \\
 dormitório & dor*mi*tó*ri*o \cmark & dor*mi*tó*ri-o \xmark \\
+dosimetria & do*si*me*tri*a \cmark & do*si*me*tri-a \xmark \\
 doutrinário & dou*tri*ná*ri.o \xmark & dou*tri*ná*rio \cmark \\
 doxografia & do*xo*gra*fi*a \cmark & do*xo*gra*fi-a \xmark \\
+doxologia & do*xo*lo*gi*a \cmark & do*xo*lo*gi-a \xmark \\
 drágea & drá*ge.a \xmark & drá*gea \cmark \\
+dramatologia & dra*ma*to*lo*gi*a \cmark & dra*ma*to*lo*gi-a \xmark \\
 dramaturgia & dra*ma*tur*gi*a \cmark & dra*ma*tur*gi-a \xmark \\
@@
 dromedário & dro*me*dá*ri.o \xmark & dro*me*dá*rio \cmark \\
+drupáceo & dru*pá*ce.o \xmark & dru*pá*ceo \cmark \\
 dúbio & dú*bi.o \xmark & dú*bio \cmark \\
 dulcineia & dul*ci*nei*a \cmark & dul*ci*nei-a \xmark \\
+dulia & du*li*a \cmark & du*li-a \xmark \\
 duo & du*o \cmark & du-o \xmark \\
 duralumínio & du*ra*lu*mí*ni.o \xmark & du*ra*lu*mí*nio \cmark \\
+durião & du*ri-ão \xmark & du*ri*ão \cmark \\
+duúnviro & du-ún*vi*ro \xmark & du-ún*vi*ro \xmark \\
 dúzia & dú*zi.a \xmark & dú*zia \cmark \\
@@
 ebúrneo & e*búr*ne.o \xmark & e*búr*neo \cmark \\
+eclampsia & e*clamp*si*a \cmark & e*clamp*si-a \xmark \\
+eclâmpsia & e*clâmp*si*a \cmark & e*clâmp*si-a \xmark \\
 eclesiástico & e*cle*si-ás*ti*co \xmark & e*cle*si*ás*ti*co \cmark \\
+eclesiologia & e*cle*si*o*lo*gi*a \cmark & e*cle*si*o*lo*gi-a \xmark \\
+ecocídio & e*co*cí*di.o \xmark & e*co*cí*dio \cmark \\
 ecografia & e*co*gra*fi*a \cmark & e*co*gra*fi-a \xmark \\
@@
 ectasia & ec*ta*si*a \cmark & ec*ta*si-a \xmark \\
+ectopia & ec*to*pi*a \cmark & ec*to*pi-a \xmark \\
+edafologia & e*da*fo*lo*gi*a \cmark & e*da*fo*lo*gi-a \xmark \\
 edifício & e*di*fí*ci.o \xmark & e*di*fí*cio \cmark \\
@@
 educandário & e*du*can*dá*ri.o \xmark & e*du*can*dá*rio \cmark \\
+efervescência & e*fer*ves*cên*ci.a \xmark & e*fer*ves*cên*cia \cmark \\
 eficácia & e*fi*cá*ci.a \xmark & e*fi*cá*cia \cmark \\
@@
 efígie & e*fí*gi.e \xmark & e*fí*gie \cmark \\
+eflorescência & e*flo*res*cên*ci.a \xmark & e*flo*res*cên*cia \cmark \\
 eflúvio & e*flú*vi.o \xmark & e*flú*vio \cmark \\
+egéria & e*gé*ri.a \xmark & e*gé*ria \cmark \\
 egípcio & e*gíp*ci.o \xmark & e*gíp*cio \cmark \\
@@
 egoístico & e*go-ís*ti*co \xmark & e*go*ís*ti*co \cmark \\
+egolatria & e*go*la*tri*a \cmark & e*go*la*tri-a \xmark \\
 egrégio & e*gré*gi.o \xmark & e*gré*gio \cmark \\
 eia & ei*a \cmark & ei-a \xmark \\
+ejaculatório & e*ja*cu*la*tó*ri.o \xmark & e*ja*cu*la*tó*rio \cmark \\
+elastério & e*las*té*ri.o \xmark & e*las*té*rio \cmark \\
 elastômero & e*las-tô*me*ro \xmark & e*las*tô*me*ro \cmark \\
+elatério & e*la*té*ri.o \xmark & e*la*té*rio \cmark \\
 elefantíase & e*le*fan*tí-a*se \xmark & e*le*fan*tí*a*se \cmark \\
 elegância & e*le*gân*ci.a \xmark & e*le*gân*cia \cmark \\
+elegíaco & e*le*gí-a*co \xmark & e*le*gí*a*co \cmark \\
 elegia & e*le*gi*a \cmark & e*le*gi-a \xmark \\
@@
 eletroquímica & e*le*tro-quí*mi*ca \xmark & e*le*tro*quí*mi*ca \cmark \\
+eletroquímico & e*le*tro-quí*mi*co \xmark & e*le*tro*quí*mi*co \cmark \\
+eletrotecnia & e*le*tro*tec*ni*a \cmark & e*le*tro*tec*ni-a \xmark \\
+eletroterapia & e*le*tro*te*ra*pi*a \cmark & e*le*tro*te*ra*pi-a \xmark \\
+elevatório & e*le*va*tó*ri.o \xmark & e*le*va*tó*rio \cmark \\
 eliminatória & e*li*mi*na*tó*ri.a \xmark & e*li*mi*na*tó*ria \cmark \\
+eliminatório & e*li*mi*na*tó*ri.o \xmark & e*li*mi*na*tó*rio \cmark \\
 elogiável & e*lo*gi-á*vel \xmark & e*lo*gi*á*vel \cmark \\
@@
 empório & em*pó*ri.o \xmark & em*pó*rio \cmark \\
+empregatício & em*pre*ga*tí*ci.o \xmark & em*pre*ga*tí*cio \cmark \\
+empresário & em*pre*sá*ri.o \xmark & em*pre*sá*rio \cmark \\
+encantatório & en*can*ta*tó*ri.o \xmark & en*can*ta*tó*rio \cmark \\
 encefalopatia & en*ce*fa*lo*pa*ti*a \cmark & en*ce*fa*lo*pa*ti-a \xmark \\
+enchia & en*chi*a \cmark & en*chi-a \xmark \\
 enciclopédia & en*ci*clo*pé*di.a \xmark & en*ci*clo*pé*dia \cmark \\
@@
 endodontia & en*do*don*ti*a \cmark & en*do*don*ti-a \xmark \\
+endodôntico & en*do-dôn*ti*co \xmark & en*do*dôn*ti*co \cmark \\
 endogamia & en*do*ga*mi*a \cmark & en*do*ga*mi-a \xmark \\
@@
 endoscopia & en*dos*co*pi*a \cmark & en*dos*co*pi-a \xmark \\
+endoscópio & en*dos*có*pi.o \xmark & en*dos*có*pio \cmark \\
+endotélio & en*do*té*li.o \xmark & en*do*té*lio \cmark \\
 energia & e*ner*gi*a \cmark & e*ner*gi-a \xmark \\
@@
 ensaísta & en*sa-ís*ta \xmark & en*sa*ís*ta \cmark \\
+ensaística & en*sa-ís*ti*ca \xmark & en*sa*ís*ti*ca \cmark \\
+ensaístico & en*sa-ís*ti*co \xmark & en*sa*ís*ti*co \cmark \\
 entalpia & en*tal*pi*a \cmark & en*tal*pi-a \xmark \\
+enteléquia & en*te*lé*qui.a \xmark & en*te*lé*quia \cmark \\
 enteropatia & en*te*ro*pa*ti*a \cmark & en*te*ro*pa*ti-a \xmark \\
+entomofagia & en*to*mo*fa*gi*a \cmark & en*to*mo*fa*gi-a \xmark \\
+entomofilia & en*to*mo*fi*li*a \cmark & en*to*mo*fi*li-a \xmark \\
 entomologia & en*to*mo*lo*gi*a \cmark & en*to*mo*lo*gi-a \xmark \\
+entrância & en*trân*ci.a \xmark & en*trân*cia \cmark \\
 entremeio & en*tre*mei*o \cmark & en*tre*mei-o \xmark \\
@@
 envoltório & en*vol*tó*ri.o \xmark & en*vol*tó*rio \cmark \\
+envolvência & en*vol*vên*ci.a \xmark & en*vol*vên*cia \cmark \\
 enxertia & en*xer*ti*a \cmark & en*xer*ti-a \xmark \\
@@
 eólico & e-ó*li*co \xmark & e*ó*li*co \cmark \\
+eólio & e-ó*li.o \xmark & e*ó*lio \cmark \\
 éon & é-on \xmark & é*on \cmark \\
+eoo & e*o*o \cmark & e*o-o \xmark \\
+eosinofilia & e*o*si*no*fi*li*a \cmark & e*o*si*no*fi*li-a \xmark \\
 eparquia & e*par*qui*a \cmark & e*par*qui-a \xmark \\
+epicôndilo & e*pi-côn*di*lo \xmark & e*pi*côn*di*lo \cmark \\
 epidemia & e*pi*de*mi*a \cmark & e*pi*de*mi-a \xmark \\
 epidemiologia & e*pi*de*mi*o*lo*gi*a \cmark & e*pi*de*mi*o*lo*gi-a \xmark \\
+epifenômeno & e*pi*fe-nô*me*no \xmark & e*pi*fe*nô*me*no \cmark \\
 epigrafia & e*pi*gra*fi*a \cmark & e*pi*gra*fi-a \xmark \\
 epilepsia & e*pi*lep*si*a \cmark & e*pi*lep*si-a \xmark \\
+epipódio & e*pi*pó*di.o \xmark & e*pi*pó*dio \cmark \\
+episcópio & e*pis*có*pi.o \xmark & e*pis*có*pio \cmark \\
+episiotomia & e*pi*si*o*to*mi*a \cmark & e*pi*si*o*to*mi-a \xmark \\
+episódio & e*pi*só*di.o \xmark & e*pi*só*dio \cmark \\
 epistemologia & e*pis*te*mo*lo*gi*a \cmark & e*pis*te*mo*lo*gi-a \xmark \\
+epistolário & e*pis*to*lá*ri.o \xmark & e*pis*to*lá*rio \cmark \\
+epistolografia & e*pis*to*lo*gra*fi*a \cmark & e*pis*to*lo*gra*fi-a \xmark \\
 epitáfio & e*pi*tá*fi.o \xmark & e*pi*tá*fio \cmark \\
+epitalâmio & e*pi*ta*lâ*mi.o \xmark & e*pi*ta*lâ*mio \cmark \\
+epitélio & e*pi*té*li.o \xmark & e*pi*té*lio \cmark \\
 epizootia & e*pi*zo*o*ti*a \cmark & e*pi*zo*o*ti-a \xmark \\
+epônimo & e-pô*ni*mo \xmark & e*pô*ni*mo \cmark \\
 epopeia & e*po*pei*a \cmark & e*po*pei-a \xmark \\
@@
 equídeo & e-quí*de.o \xmark & e*quí*deo \cmark \\
+equidistância & e*qui*dis*tân*ci.a \xmark & e*qui*dis*tân*cia \cmark \\
 equilíbrio & e*qui*lí*bri.o \xmark & e*qui*lí*brio \cmark \\
@@
 equívoco & e-quí*vo*co \xmark & e*quí*vo*co \cmark \\
+equoterapia & e*quo*te*ra*pi*a \cmark & e*quo*te*ra*pi-a \xmark \\
 erário & e*rá*ri.o \xmark & e*rá*rio \cmark \\
 érbio & ér*bi.o \xmark & ér*bio \cmark \\
+erétria & e*ré*tri.a \xmark & e*ré*tria \cmark \\
 ergometria & er*go*me*tri*a \cmark & er*go*me*tri-a \xmark \\
+ergômetro & er-gô*me*tro \xmark & er*gô*me*tro \cmark \\
 ergonomia & er*go*no*mi*a \cmark & er*go*no*mi-a \xmark \\
@@
 erotomania & e*ro*to*ma*ni*a \cmark & e*ro*to*ma*ni-a \xmark \\
+errância & er*rân*ci.a \xmark & er*rân*cia \cmark \\
 esbórnia & es*bór*ni.a \xmark & es*bór*nia \cmark \\
 escadaria & es*ca*da*ri*a \cmark & es*ca*da*ri-a \xmark \\
+escadório & es*ca*dó*ri.o \xmark & es*ca*dó*rio \cmark \\
 escândio & es*cân*di.o \xmark & es*cân*dio \cmark \\
 escanteio & es*can*tei*o \cmark & es*can*tei-o \xmark \\
+escapulário & es*ca*pu*lá*ri.o \xmark & es*ca*pu*lá*rio \cmark \\
+escarabeídeo & es*ca*ra*be-í*de.o \xmark & es*ca*ra*be*í*deo \cmark \\
 escárnio & es*cár*ni.o \xmark & es*cár*nio \cmark \\
@@
 escleroterapia & es*cle*ro*te*ra*pi*a \cmark & es*cle*ro*te*ra*pi-a \xmark \\
+escoa & es*co*a \cmark & es*co-a \xmark \\
 escócia & es*có*ci.a \xmark & es*có*cia \cmark \\
@@
 escorregadio & es*cor*re*ga*di*o \cmark & es*cor*re*ga*di-o \xmark \\
+escorrência & es*cor*rên*ci.a \xmark & es*cor*rên*cia \cmark \\
+escravaria & es*cra*va*ri*a \cmark & es*cra*va*ri-a \xmark \\
 escritório & es*cri*tó*ri.o \xmark & es*cri*tó*rio \cmark \\
@@
 esfigmomanômetro & es*fig*mo*ma-nô*me*tro \xmark & es*fig*mo*ma*nô*me*tro \cmark \\
+esfiha & es*fi-ha \xmark & es*fi-ha \xmark \\
 esguio & es*gui*o \cmark & es*gui-o \xmark \\
 esofagectomia & e*so*fa*gec*to*mi*a \cmark & e*so*fa*gec*to*mi-a \xmark \\
+esôfago & e-sô*fa*go \xmark & e*sô*fa*go \cmark \\
+espadaúdo & es*pa*da-ú*do \xmark & es*pa*da*ú*do \cmark \\
 especiaria & es*pe*ci*a*ri*a \cmark & es*pe*ci*a*ri-a \xmark \\
 espécie & es*pé*ci.e \xmark & es*pé*cie \cmark \\
+espectrofotômetro & es*pec*tro*fo-tô*me*tro \xmark & es*pec*tro*fo*tô*me*tro \cmark \\
+espectrografia & es*pec*tro*gra*fi*a \cmark & es*pec*tro*gra*fi-a \xmark \\
+espectrometria & es*pec*tro*me*tri*a \cmark & es*pec*tro*me*tri-a \xmark \\
+espectroscopia & es*pec*tros*co*pi*a \cmark & es*pec*tros*co*pi-a \xmark \\
+espeleologia & es*pe*le*o*lo*gi*a \cmark & es*pe*le*o*lo*gi-a \xmark \\
+espeleólogo & es*pe*le-ó*lo*go \xmark & es*pe*le*ó*lo*go \cmark \\
 espia & es*pi*a \cmark & es*pi-a \xmark \\
 espião & es*pi-ão \xmark & es*pi*ão \cmark \\
+espirometria & es*pi*ro*me*tri*a \cmark & es*pi*ro*me*tri-a \xmark \\
+esplenectomia & es*ple*nec*to*mi*a \cmark & es*ple*nec*to*mi-a \xmark \\
 esplenomegalia & es*ple*no*me*ga*li*a \cmark & es*ple*no*me*ga*li-a \xmark \\
-esponsais & es*pon*sa-is \xmark & es*pon*sa-is \xmark \\
+espólio & es*pó*li.o \xmark & es*pó*lio \cmark \\
 espontâneo & es*pon*tâ*ne.o \xmark & es*pon*tâ*neo \cmark \\
+esporângio & es*po*rân*gi.o \xmark & es*po*rân*gio \cmark \\
 espúrio & es*pú*ri.o \xmark & es*pú*rio \cmark \\
@@
 esquizofrenia & es*qui*zo*fre*ni*a \cmark & es*qui*zo*fre*ni-a \xmark \\
+esquizogonia & es*qui*zo*go*ni*a \cmark & es*qui*zo*go*ni-a \xmark \\
 essência & es*sên*ci.a \xmark & es*sên*cia \cmark \\
@@
 estádio & es*tá*di.o \xmark & es*tá*dio \cmark \\
+estagiário & es*ta*gi-á*ri.o \xmark & es*ta*gi*á*rio \cmark \\
 estágio & es*tá*gi.o \xmark & es*tá*gio \cmark \\
+estaminódio & es*ta*mi*nó*di.o \xmark & es*ta*mi*nó*dio \cmark \\
 estamparia & es*tam*pa*ri*a \cmark & es*tam*pa*ri-a \xmark \\
 estância & es*tân*ci.a \xmark & es*tân*cia \cmark \\
+estapafúrdio & es*ta*pa*fúr*di.o \xmark & es*ta*pa*fúr*dio \cmark \\
 estátua & es*tá*tu.a \xmark & es*tá*tua \cmark \\
+estatuária & es*ta*tu-á*ri.a \xmark & es*ta*tu*á*ria \cmark \\
+estatuário & es*ta*tu-á*ri.o \xmark & es*ta*tu*á*rio \cmark \\
+estatutário & es*ta*tu*tá*ri.o \xmark & es*ta*tu*tá*rio \cmark \\
 esteárico & es*te-á*ri*co \xmark & es*te*á*ri*co \cmark \\
 esteatorreia & es*te*a*tor*rei*a \cmark & es*te*a*tor*rei-a \xmark \\
+esteganografia & es*te*ga*no*gra*fi*a \cmark & es*te*ga*no*gra*fi-a \xmark \\
 esteio & es*tei*o \cmark & es*tei-o \xmark \\
@@
 estequiometria & es*te*qui*o*me*tri*a \cmark & es*te*qui*o*me*tri-a \xmark \\
+estereóbata & es*te*re-ó*ba*ta \xmark & es*te*re*ó*ba*ta \cmark \\
 estéreo & es*té*re.o \xmark & es*té*reo \cmark \\
+estereofonia & es*te*re*o*fo*ni*a \cmark & es*te*re*o*fo*ni-a \xmark \\
+estereologia & es*te*re*o*lo*gi*a \cmark & es*te*re*o*lo*gi-a \xmark \\
+estereoquímica & es*te*re*o-quí*mi*ca \xmark & es*te*re*o*quí*mi*ca \cmark \\
+estereoquímico & es*te*re*o-quí*mi*co \xmark & es*te*re*o*quí*mi*co \cmark \\
+estereoscopia & es*te*re*os*co*pi*a \cmark & es*te*re*os*co*pi-a \xmark \\
+estereoscópio & es*te*re*os*có*pi.o \xmark & es*te*re*os*có*pio \cmark \\
+estereotipia & es*te*re*o*ti*pi*a \cmark & es*te*re*o*ti*pi-a \xmark \\
 estereótipo & es*te*re-ó*ti*po \xmark & es*te*re*ó*ti*po \cmark \\
+estereotomia & es*te*re*o*to*mi*a \cmark & es*te*re*o*to*mi-a \xmark \\
+estetoscópio & es*te*tos*có*pi.o \xmark & es*te*tos*có*pio \cmark \\
 estígio & es*tí*gi.o \xmark & es*tí*gio \cmark \\
@@
 estomatologia & es*to*ma*to*lo*gi*a \cmark & es*to*ma*to*lo*gi-a \xmark \\
+estória & es*tó*ri.a \xmark & es*tó*ria \cmark \\
 estratégia & es*tra*té*gi.a \xmark & es*tra*té*gia \cmark \\
@@
 estroboscópio & es*tro*bos*có*pi.o \xmark & es*tro*bos*có*pio \cmark \\
+estrogênio & es*tro*gê*ni.o \xmark & es*tro*gê*nio \cmark \\
 estrôncio & es*trôn*ci.o \xmark & es*trôn*cio \cmark \\
@@
 esvair & es*va-ir \xmark & es*va*ir \cmark \\
+etário & e*tá*ri.o \xmark & e*tá*rio \cmark \\
 etéreo & e*té*re.o \xmark & e*té*reo \cmark \\
@@
 etíope & e*tí-o*pe \xmark & e*tí*o*pe \cmark \\
+etiópico & e*ti-ó*pi*co \xmark & e*ti*ó*pi*co \cmark \\
 etnia & et*ni*a \cmark & et*ni-a \xmark \\
+etnocídio & et*no*cí*di.o \xmark & et*no*cí*dio \cmark \\
 etnografia & et*no*gra*fi*a \cmark & et*no*gra*fi-a \xmark \\
@@
 etnônimo & et-nô*ni*mo \xmark & et*nô*ni*mo \cmark \\
+etólio & e*tó*li.o \xmark & e*tó*lio \cmark \\
 etologia & e*to*lo*gi*a \cmark & e*to*lo*gi-a \xmark \\
@@
 eufonia & eu*fo*ni*a \cmark & eu*fo*ni-a \xmark \\
+eufônico & eu-fô*ni*co \xmark & eu*fô*ni*co \cmark \\
 euforia & eu*fo*ri*a \cmark & eu*fo*ri-a \xmark \\
+eufrásia & eu*frá*si.a \xmark & eu*frá*sia \cmark \\
 eugenia & eu*ge*ni*a \cmark & eu*ge*ni-a \xmark \\
@@
 eurasiático & eu*ra*si-á*ti*co \xmark & eu*ra*si*á*ti*co \cmark \\
+europeísmo & eu*ro*pe-ís*mo \xmark & eu*ro*pe*ís*mo \cmark \\
+europeísta & eu*ro*pe-ís*ta \xmark & eu*ro*pe*ís*ta \cmark \\
 európio & eu*ró*pi.o \xmark & eu*ró*pio \cmark \\
@@
 eutanásia & eu*ta*ná*si.a \xmark & eu*ta*ná*sia \cmark \\
+eutério & eu*té*ri.o \xmark & eu*té*rio \cmark \\
+eutonia & eu*to*ni*a \cmark & eu*to*ni-a \xmark \\
+evangeliário & e*van*ge*li-á*ri.o \xmark & e*van*ge*li*á*rio \cmark \\
 evidência & e*vi*dên*ci.a \xmark & e*vi*dên*cia \cmark \\
 evoé & e*vo-é \xmark & e*vo*é \cmark \\
+evolucionário & e*vo*lu*ci*o*ná*ri.o \xmark & e*vo*lu*ci*o*ná*rio \cmark \\
 evoluído & e*vo*lu-í*do \xmark & e*vo*lu*í*do \cmark \\
@@
 excelência & ex*ce*lên*ci.a \xmark & ex*ce*lên*cia \cmark \\
+excitatório & ex*ci*ta*tó*ri.o \xmark & ex*ci*ta*tó*rio \cmark \\
 excluído & ex*clu-í*do \xmark & ex*clu*í*do \cmark \\
@@
 excrescência & ex*cres*cên*ci.a \xmark & ex*cres*cên*cia \cmark \\
+excretório & ex*cre*tó*ri.o \xmark & ex*cre*tó*rio \cmark \\
+executória & e*xe*cu*tó*ri.a \xmark & e*xe*cu*tó*ria \cmark \\
+executório & e*xe*cu*tó*ri.o \xmark & e*xe*cu*tó*rio \cmark \\
 exéquias & e*xé*qui.as \xmark & e*xé*qui.as \xmark \\
 exequível & e*xe-quí*vel \xmark & e*xe*quí*vel \cmark \\
+exercício & e*xer*cí*ci.o \xmark & e*xer*cí*cio \cmark \\
 exigência & e*xi*gên*ci.a \xmark & e*xi*gên*cia \cmark \\
+exílio & e*xí*li*o \cmark & e*xí*li-o \xmark \\
 exímio & e*xí*mi.o \xmark & e*xí*mio \cmark \\
 existência & e*xis*tên*ci.a \xmark & e*xis*tên*cia \cmark \\
+exobiologia & e*xo*bi*o*lo*gi*a \cmark & e*xo*bi*o*lo*gi-a \xmark \\
+exodontia & e*xo*don*ti*a \cmark & e*xo*don*ti-a \xmark \\
 exoftalmia & e*xof*tal*mi*a \cmark & e*xof*tal*mi-a \xmark \\
 exogamia & e*xo*ga*mi*a \cmark & e*xo*ga*mi-a \xmark \\
+exorbitância & e*xor*bi*tân*ci.a \xmark & e*xor*bi*tân*cia \cmark \\
 exórdio & e*xór*di.o \xmark & e*xór*dio \cmark \\
@@
 experiência & ex*pe*ri*ên*ci.a \xmark & ex*pe*ri*ên*cia \cmark \\
+expiatório & ex*pi*a*tó*ri.o \xmark & ex*pi*a*tó*rio \cmark \\
+explanatório & ex*pla*na*tó*ri.o \xmark & ex*pla*na*tó*rio \cmark \\
+exploratório & ex*plo*ra*tó*ri.o \xmark & ex*plo*ra*tó*rio \cmark \\
+extemporâneo & ex*tem*po*râ*ne.o \xmark & ex*tem*po*râ*neo \cmark \\
 extermínio & ex*ter*mí*ni.o \xmark & ex*ter*mí*nio \cmark \\
 extrair & ex*tra-ir \xmark & ex*tra*ir \cmark \\
+extranumerário & ex*tra*nu*me*rá*ri.o \xmark & ex*tra*nu*me*rá*rio \cmark \\
 extraordinário & ex*tra*or*di*ná*ri.o \xmark & ex*tra*or*di*ná*rio \cmark \\
+extravagância & ex*tra*va*gân*ci.a \xmark & ex*tra*va*gân*cia \cmark \\
 extravio & ex*tra*vi*o \cmark & ex*tra*vi-o \xmark \\
 exuberância & e*xu*be*rân*ci.a \xmark & e*xu*be*rân*cia \cmark \\
+exutório & e*xu*tó*ri.o \xmark & e*xu*tó*rio \cmark \\
+fabulário & fa*bu*lá*ri.o \xmark & fa*bu*lá*rio \cmark \\
+facaia & fa*cai*a \cmark & fa*cai-a \xmark \\
 factício & fac*tí*ci.o \xmark & fac*tí*cio \cmark \\
+facúndia & fa*cún*di.a \xmark & fa*cún*dia \cmark \\
 faia & fai*a \cmark & fai-a \xmark \\
@@
 faísca & fa-ís*ca \xmark & fa*ís*ca \cmark \\
+faiscante & fa-is*can*te \xmark & fa-is*can*te \xmark \\
+faiscar & fa-is*car \xmark & fa-is*car \xmark \\
 falácia & fa*lá*ci.a \xmark & fa*lá*cia \cmark \\
+falanstério & fa*lans*té*ri.o \xmark & fa*lans*té*rio \cmark \\
+falatório & fa*la*tó*ri.o \xmark & fa*la*tó*rio \cmark \\
 falcatrua & fal*ca*tru*a \cmark & fal*ca*tru-a \xmark \\
+falcoaria & fal*co*a*ri*a \cmark & fal*co*a*ri-a \xmark \\
 falência & fa*lên*ci.a \xmark & fa*lên*cia \cmark \\
 falésia & fa*lé*si.a \xmark & fa*lé*sia \cmark \\
+faloplastia & fa*lo*plas*ti*a \cmark & fa*lo*plas*ti-a \xmark \\
+falsário & fal*sá*ri.o \xmark & fal*sá*rio \cmark \\
+família & fa*mí*li.a \xmark & fa*mí*lia \cmark \\
+familistério & fa*mi*lis*té*ri.o \xmark & fa*mi*lis*té*rio \cmark \\
 fancaria & fan*ca*ri*a \cmark & fan*ca*ri-a \xmark \\
@@
 faraó & fa*ra-ó \xmark & fa*ra*ó \cmark \\
+faraônico & fa*ra-ô*ni*co \xmark & fa*ra*ô*ni*co \cmark \\
+farfalharia & far*fa*lha*ri*a \cmark & far*fa*lha*ri-a \xmark \\
+farináceo & fa*ri*ná*ce.o \xmark & fa*ri*ná*ceo \cmark \\
 faríngeo & fa*rín*ge.o \xmark & fa*rín*geo \cmark \\
@@
 farmacoterapia & far*ma*co*te*ra*pi*a \cmark & far*ma*co*te*ra*pi-a \xmark \\
+fáscia & fás*ci.a \xmark & fás*cia \cmark \\
 fascínio & fas*cí*ni.o \xmark & fas*cí*nio \cmark \\
+fascíola & fas*cí-o*la \xmark & fas*cí*o*la \cmark \\
+fasquia & fas*qui*a \cmark & fas*qui-a \xmark \\
 fastígio & fas*tí*gi.o \xmark & fas*tí*gio \cmark \\
@@
 fatia & fa*ti*a \cmark & fa*ti-a \xmark \\
+fátuo & fá*tu.o \xmark & fá*tuo \cmark \\
 faúlha & fa-ú*lha \xmark & fa*ú*lha \cmark \\
+favônio & fa-vô*ni.o \xmark & fa*vô*nio \cmark \\
 fazendário & fa*zen*dá*ri.o \xmark & fa*zen*dá*rio \cmark \\
+fecharia & fe*cha*ri*a \cmark & fe*cha*ri-a \xmark \\
 feérico & fe-é*ri*co \xmark & fe*é*ri*co \cmark \\
@@
 feiura & fei-u*ra \xmark & fei*u*ra \cmark \\
+felícia & fe*lí*ci.a \xmark & fe*lí*cia \cmark \\
 felídeo & fe*lí*de.o \xmark & fe*lí*deo \cmark \\
@@
 fenício & fe*ní*ci.o \xmark & fe*ní*cio \cmark \\
+fenilcetonúria & fe*nil*ce*to*nú*ri.a \xmark & fe*nil*ce*to*nú*ria \cmark \\
 fenologia & fe*no*lo*gi*a \cmark & fe*no*lo*gi-a \xmark \\
@@
 férmio & fér*mi.o \xmark & fér*mio \cmark \\
+feroês & fe*ro-ês \xmark & fe*ro*ês \cmark \\
+ferramentaria & fer*ra*men*ta*ri*a \cmark & fer*ra*men*ta*ri-a \xmark \\
 ferraria & fer*ra*ri*a \cmark & fer*ra*ri-a \xmark \\
+férreo & fér*re.o \xmark & fér*reo \cmark \\
 ferrovia & fer*ro*vi*a \cmark & fer*ro*vi-a \xmark \\
+ferroviário & fer*ro*vi-á*ri.o \xmark & fer*ro*vi*á*rio \cmark \\
+ferrugíneo & fer*ru*gí*ne.o \xmark & fer*ru*gí*neo \cmark \\
+feudatário & feu*da*tá*ri.o \xmark & feu*da*tá*rio \cmark \\
 fiável & fi-á*vel \xmark & fi*á*vel \cmark \\
@@
 fictício & fic*tí*ci.o \xmark & fic*tí*cio \cmark \\
+fidalguia & fi*dal*gui*a \cmark & fi*dal*gui-a \xmark \\
 fideísmo & fi*de-ís*mo \xmark & fi*de*ís*mo \cmark \\
+fidejussória & fi*de*jus*só*ri.a \xmark & fi*de*jus*só*ria \cmark \\
 fidúcia & fi*dú*ci.a \xmark & fi*dú*cia \cmark \\
@@
 filmografia & fil*mo*gra*fi*a \cmark & fil*mo*gra*fi-a \xmark \\
+filmologia & fil*mo*lo*gi*a \cmark & fil*mo*lo*gi-a \xmark \\
 filogenia & fi*lo*ge*ni*a \cmark & fi*lo*ge*ni-a \xmark \\
@@
 filosofia & fi*lo*so*fi*a \cmark & fi*lo*so*fi-a \xmark \\
+filotaxia & fi*lo*ta*xi*a \cmark & fi*lo*ta*xi-a \xmark \\
 fímbria & fím*bri.a \xmark & fím*bria \cmark \\
@@
 fio & fi*o \cmark & fi-o \xmark \\
+fisiatria & fi*si*a*tri*a \cmark & fi*si*a*tri-a \xmark \\
 fisiocracia & fi*si*o*cra*ci*a \cmark & fi*si*o*cra*ci-a \xmark \\
+fisiografia & fi*si*o*gra*fi*a \cmark & fi*si*o*gra*fi-a \xmark \\
 fisiologia & fi*si*o*lo*gi*a \cmark & fi*si*o*lo*gi-a \xmark \\
@@
 fisioterapia & fi*si*o*te*ra*pi*a \cmark & fi*si*o*te*ra*pi-a \xmark \\
+fitogeografia & fi*to*ge*o*gra*fi*a \cmark & fi*to*ge*o*gra*fi-a \xmark \\
 fitopatologia & fi*to*pa*to*lo*gi*a \cmark & fi*to*pa*to*lo*gi-a \xmark \\
+fitoquímica & fi*to-quí*mi*ca \xmark & fi*to*quí*mi*ca \cmark \\
 fitotecnia & fi*to*tec*ni*a \cmark & fi*to*tec*ni-a \xmark \\
+fitoterapia & fi*to*te*ra*pi*a \cmark & fi*to*te*ra*pi-a \xmark \\
 fiúza & fi-ú*za \xmark & fi*ú*za \cmark \\
+flagrância & fla*grân*ci.a \xmark & fla*grân*cia \cmark \\
+flamínio & fla*mí*ni.o \xmark & fla*mí*nio \cmark \\
 flatulência & fla*tu*lên*ci.a \xmark & fla*tu*lên*cia \cmark \\
+flebografia & fle*bo*gra*fi*a \cmark & fle*bo*gra*fi-a \xmark \\
+flebotomia & fle*bo*to*mi*a \cmark & fle*bo*to*mi-a \xmark \\
+flexografia & fle*xo*gra*fi*a \cmark & fle*xo*gra*fi-a \xmark \\
 floreio & flo*rei*o \cmark & flo*rei-o \xmark \\
+florescência & flo*res*cên*ci.a \xmark & flo*res*cên*cia \cmark \\
 florilégio & flo*ri*lé*gi.o \xmark & flo*ri*lé*gio \cmark \\
@@
 flúor & flú-or \xmark & flú*or \cmark \\
+fluoroscopia & flu*o*ros*co*pi*a \cmark & flu*o*ros*co*pi-a \xmark \\
 fobia & fo*bi*a \cmark & fo*bi-a \xmark \\
+focídeo & fo*cí*de.o \xmark & fo*cí*deo \cmark \\
+foguetório & fo*gue*tó*ri.o \xmark & fo*gue*tó*rio \cmark \\
 folheio & fo*lhei*o \cmark & fo*lhei-o \xmark \\
+foliáceo & fo*li-á*ce.o \xmark & fo*li*á*ceo \cmark \\
 folia & fo*li*a \cmark & fo*li-a \xmark \\
 folião & fo*li-ão \xmark & fo*li*ão \cmark \\
+folíolo & fo*lí-o*lo \xmark & fo*lí*o*lo \cmark \\
+fonoaudiólogo & fo*no*au*di-ó*lo*go \xmark & fo*no*au*di*ó*lo*go \cmark \\
 fonografia & fo*no*gra*fi*a \cmark & fo*no*gra*fi-a \xmark \\
 fonologia & fo*no*lo*gi*a \cmark & fo*no*lo*gi-a \xmark \\
+fontanário & fon*ta*ná*ri.o \xmark & fon*ta*ná*rio \cmark \\
+forâneo & fo*râ*ne.o \xmark & fo*râ*neo \cmark \\
 formaldeído & for*mal*de-í*do \xmark & for*mal*de*í*do \cmark \\
+formaria & for*ma*ri*a \cmark & for*ma*ri-a \xmark \\
 formulário & for*mu*lá*ri.o \xmark & for*mu*lá*rio \cmark \\
@@
 fotografia & fo*to*gra*fi*a \cmark & fo*to*gra*fi-a \xmark \\
+fotogrametria & fo*to*gra*me*tri*a \cmark & fo*to*gra*me*tri-a \xmark \\
 fotolitografia & fo*to*li*to*gra*fi*a \cmark & fo*to*li*to*gra*fi-a \xmark \\
+fotoluminescência & fo*to*lu*mi*nes*cên*ci.a \xmark & fo*to*lu*mi*nes*cên*cia \cmark \\
 fotometria & fo*to*me*tri*a \cmark & fo*to*me*tri-a \xmark \\
+fotômetro & fo-tô*me*tro \xmark & fo*tô*me*tro \cmark \\
+fotoperíodo & fo*to*pe*rí-o*do \xmark & fo*to*pe*rí*o*do \cmark \\
 fotoquímica & fo*to-quí*mi*ca \xmark & fo*to*quí*mi*ca \cmark \\
 fotoquímico & fo*to-quí*mi*co \xmark & fo*to*quí*mi*co \cmark \\
+fototaxia & fo*to*ta*xi*a \cmark & fo*to*ta*xi-a \xmark \\
 fototerapia & fo*to*te*ra*pi*a \cmark & fo*to*te*ra*pi-a \xmark \\
 fototipia & fo*to*ti*pi*a \cmark & fo*to*ti*pi-a \xmark \\
+fototipografia & fo*to*ti*po*gra*fi*a \cmark & fo*to*ti*po*gra*fi-a \xmark \\
+fóvea & fó*ve.a \xmark & fó*vea \cmark \\
+fracionário & fra*ci*o*ná*ri.o \xmark & fra*ci*o*ná*rio \cmark \\
+fragmentário & frag*men*tá*ri.o \xmark & frag*men*tá*rio \cmark \\
 fragrância & fra*grân*ci.a \xmark & fra*grân*cia \cmark \\
+fraldário & fral*dá*ri.o \xmark & fral*dá*rio \cmark \\
 frâncio & frân*ci.o \xmark & frân*cio \cmark \\
+francofilia & fran*co*fi*li*a \cmark & fran*co*fi*li-a \xmark \\
 francofonia & fran*co*fo*ni*a \cmark & fran*co*fo*ni-a \xmark \\
+franqueável & fran*que-á*vel \xmark & fran*que*á*vel \cmark \\
 franquia & fran*qui*a \cmark & fran*qui-a \xmark \\
 fraseologia & fra*se*o*lo*gi*a \cmark & fra*se*o*lo*gi-a \xmark \\
+fratria & fra*tri*a \cmark & fra*tri-a \xmark \\
 fratricídio & fra*tri*cí*di.o \xmark & fra*tri*cí*dio \cmark \\
@@
 friável & fri-á*vel \xmark & fri*á*vel \cmark \\
+frígio & frí*gi.o \xmark & frí*gio \cmark \\
+frigoria & fri*go*ri*a \cmark & fri*go*ri-a \xmark \\
 frio & fri*o \cmark & fri-o \xmark \\
@@
 frutaria & fru*ta*ri*a \cmark & fru*ta*ri-a \xmark \\
+ftálico & f.tá*li*co \xmark & f.tá*li*co \xmark \\
 fuá & fu-á \xmark & fu*á \cmark \\
+fúcsia & fúc*si.a \xmark & fúc*sia \cmark \\
 fúfio & fú*fi.o \xmark & fú*fio \cmark \\
@@
 fuinha & fu-i*nha \xmark & fu*i*nha \cmark \\
+fulgurância & ful*gu*rân*ci.a \xmark & ful*gu*rân*cia \cmark \\
 funcionário & fun*ci*o*ná*ri.o \xmark & fun*ci*o*ná*rio \cmark \\
+fundiário & fun*di-á*ri.o \xmark & fun*di*á*rio \cmark \\
 funerária & fu*ne*rá*ri.a \xmark & fu*ne*rá*ria \cmark \\
@@
 gaélico & ga-é*li*co \xmark & ga*é*li*co \cmark \\
+gafaria & ga*fa*ri*a \cmark & ga*fa*ri-a \xmark \\
+gaia & gai*a \cmark & gai-a \xmark \\
 gaio & gai*o \cmark & gai-o \xmark \\
 galanteio & ga*lan*tei*o \cmark & ga*lan*tei-o \xmark \\
+galanteria & ga*lan*te*ri*a \cmark & ga*lan*te*ri-a \xmark \\
+galateia & ga*la*tei*a \cmark & ga*la*tei-a \xmark \\
+galáxia & ga*lá*xi.a \xmark & ga*lá*xia \cmark \\
 galeão & ga*le-ão \xmark & ga*le*ão \cmark \\
@@
 gálio & gá*li.o \xmark & gá*lio \cmark \\
+galizia & ga*li*zi*a \cmark & ga*li*zi-a \xmark \\
+galvanômetro & gal*va-nô*me*tro \xmark & gal*va*nô*me*tro \cmark \\
+galvanoplastia & gal*va*no*plas*ti*a \cmark & gal*va*no*plas*ti-a \xmark \\
+gamagrafia & ga*ma*gra*fi*a \cmark & ga*ma*gra*fi-a \xmark \\
 gâmbia & gâm*bi.a \xmark & gâm*bia \cmark \\
 gamboa & gam*bo*a \cmark & gam*bo-a \xmark \\
+gametângio & ga*me*tân*gi.o \xmark & ga*me*tân*gio \cmark \\
 ganância & ga*nân*ci.a \xmark & ga*nân*cia \cmark \\
 gandaia & gan*dai*a \cmark & gan*dai-a \xmark \\
+gandaio & gan*dai*o \cmark & gan*dai-o \xmark \\
 gânglio & gân*gli.o \xmark & gân*glio \cmark \\
 garantia & ga*ran*ti*a \cmark & ga*ran*ti-a \xmark \\
+gardênia & gar*dê*ni.a \xmark & gar*dê*nia \cmark \\
 garoa & ga*ro*a \cmark & ga*ro-a \xmark \\
+gasóleo & ga*só*le.o \xmark & ga*só*leo \cmark \\
+gasometria & ga*so*me*tri*a \cmark & ga*so*me*tri-a \xmark \\
+gasômetro & ga-sô*me*tro \xmark & ga*sô*me*tro \cmark \\
 gastrectomia & gas*trec*to*mi*a \cmark & gas*trec*to*mi-a \xmark \\
+gastroenterologia & gas*tro*en*te*ro*lo*gi*a \cmark & gas*tro*en*te*ro*lo*gi-a \xmark \\
 gastrointestinal & gas*tro-in*tes*ti*nal \xmark & gas*tro*in*tes*ti*nal \cmark \\
@@
 gastronômico & gas*tro-nô*mi*co \xmark & gas*tro*nô*mi*co \cmark \\
+gastroplastia & gas*tro*plas*ti*a \cmark & gas*tro*plas*ti-a \xmark \\
+gastrostomia & gas*tros*to*mi*a \cmark & gas*tros*to*mi-a \xmark \\
+gauchada & ga-u*cha*da \xmark & ga-u*cha*da \xmark \\
+gauchar & ga-u*char \xmark & ga-u*char \xmark \\
+gauchismo & ga-u*chis*mo \xmark & ga-u*chis*mo \xmark \\
 gaúcho & ga-ú*cho \xmark & ga*ú*cho \cmark \\
@@
 gelosia & ge*lo*si*a \cmark & ge*lo*si-a \xmark \\
+gêmeo & gê*me.o \xmark & gê*meo \cmark \\
 gemologia & ge*mo*lo*gi*a \cmark & ge*mo*lo*gi-a \xmark \\
@@
 genealogia & ge*ne*a*lo*gi*a \cmark & ge*ne*a*lo*gi-a \xmark \\
+generalício & ge*ne*ra*lí*ci.o \xmark & ge*ne*ra*lí*cio \cmark \\
+geneterapia & ge*ne*te*ra*pi*a \cmark & ge*ne*te*ra*pi-a \xmark \\
+gênio & gê*ni.o \xmark & gê*nio \cmark \\
 genitália & ge*ni*tá*li.a \xmark & ge*ni*tá*lia \cmark \\
@@
 genocídio & ge*no*cí*di.o \xmark & ge*no*cí*dio \cmark \\
+genômico & ge-nô*mi*co \xmark & ge*nô*mi*co \cmark \\
+gentilício & gen*ti*lí*ci.o \xmark & gen*ti*lí*cio \cmark \\
 gentio & gen*ti*o \cmark & gen*ti-o \xmark \\
 genuflexório & ge*nu*fle*xó*ri.o \xmark & ge*nu*fle*xó*rio \cmark \\
+genuinidade & ge*nu-i*ni*da*de \xmark & ge*nu*i*ni*da*de \cmark \\
 genuíno & ge*nu-í*no \xmark & ge*nu*í*no \cmark \\
+geocronologia & ge*o*cro*no*lo*gi*a \cmark & ge*o*cro*no*lo*gi-a \xmark \\
 geodesia & ge*o*de*si*a \cmark & ge*o*de*si-a \xmark \\
+geodésia & ge*o*dé*si.a \xmark & ge*o*dé*sia \cmark \\
+geoestacionário & ge*o*es*ta*ci*o*ná*ri.o \xmark & ge*o*es*ta*ci*o*ná*rio \cmark \\
+geofagia & ge*o*fa*gi*a \cmark & ge*o*fa*gi-a \xmark \\
+geófito & ge-ó*fi*to \xmark & ge*ó*fi*to \cmark \\
+geognosia & ge*og*no*si*a \cmark & ge*og*no*si-a \xmark \\
 geografia & ge*o*gra*fi*a \cmark & ge*o*gra*fi-a \xmark \\
@@
 geólogo & ge-ó*lo*go \xmark & ge*ó*lo*go \cmark \\
+geomancia & ge*o*man*ci*a \cmark & ge*o*man*ci-a \xmark \\
+geômetra & ge-ô*me*tra \xmark & ge*ô*me*tra \cmark \\
 geometria & ge*o*me*tri*a \cmark & ge*o*me*tri-a \xmark \\
+geomorfologia & ge*o*mor*fo*lo*gi*a \cmark & ge*o*mor*fo*lo*gi-a \xmark \\
+geoquímica & ge*o-quí*mi*ca \xmark & ge*o*quí*mi*ca \cmark \\
+geoquímico & ge*o-quí*mi*co \xmark & ge*o*quí*mi*co \cmark \\
+geotectônica & ge*o*tec-tô*ni*ca \xmark & ge*o*tec*tô*ni*ca \cmark \\
 gerânio & ge*râ*ni.o \xmark & ge*râ*nio \cmark \\
@@
 geriatria & ge*ri*a*tri*a \cmark & ge*ri*a*tri-a \xmark \\
+geriátrico & ge*ri-á*tri*co \xmark & ge*ri*á*tri*co \cmark \\
 germania & ger*ma*ni*a \cmark & ger*ma*ni-a \xmark \\
@@
 gerontocracia & ge*ron*to*cra*ci*a \cmark & ge*ron*to*cra*ci-a \xmark \\
+gerontologia & ge*ron*to*lo*gi*a \cmark & ge*ron*to*lo*gi-a \xmark \\
 gerúndio & ge*rún*di.o \xmark & ge*rún*dio \cmark \\
+gerúsia & ge*rú*si.a \xmark & ge*rú*sia \cmark \\
+giardíase & gi*ar*dí-a*se \xmark & gi*ar*dí*a*se \cmark \\
+gigantomaquia & gi*gan*to*ma*qui*a \cmark & gi*gan*to*ma*qui-a \xmark \\
 gigolô & gi*go-lô \xmark & gi*go*lô \cmark \\
@@
 glaciário & gla*ci-á*ri.o \xmark & gla*ci*á*rio \cmark \\
+glaciologia & gla*ci*o*lo*gi*a \cmark & gla*ci*o*lo*gi-a \xmark \\
 gládio & glá*di.o \xmark & glá*dio \cmark \\
@@
 gláucia & gláu*ci.a \xmark & gláu*cia \cmark \\
+gláucio & gláu*ci.o \xmark & gláu*cio \cmark \\
 glia & gli*a \cmark & gli-a \xmark \\
 glicemia & gli*ce*mi*a \cmark & gli*ce*mi-a \xmark \\
+glicéria & gli*cé*ri.a \xmark & gli*cé*ria \cmark \\
 glicínia & gli*cí*ni.a \xmark & gli*cí*nia \cmark \\
+glicogênio & gli*co*gê*ni.o \xmark & gli*co*gê*nio \cmark \\
 glicoproteína & gli*co*pro*te-í*na \xmark & gli*co*pro*te*í*na \cmark \\
+glicosúria & gli*co*sú*ri.a \xmark & gli*co*sú*ria \cmark \\
 glória & gló*ri.a \xmark & gló*ria \cmark \\
 glossário & glos*sá*ri.o \xmark & glos*sá*rio \cmark \\
+glossofaríngeo & glos*so*fa*rín*ge.o \xmark & glos*so*fa*rín*geo \cmark \\
 glossolalia & glos*so*la*li*a \cmark & glos*so*la*li-a \xmark \\
@@
 glutonaria & glu*to*na*ri*a \cmark & glu*to*na*ri-a \xmark \\
+glutoneria & glu*to*ne*ri*a \cmark & glu*to*ne*ri-a \xmark \\
 gnaisse & g.nais*se \xmark & g.nais*se \xmark \\
@@
 gnóstico & g.nós*ti*co \xmark & gnós*ti*co \cmark \\
+gnu & g.nu \xmark & g.nu \xmark \\
+goês & go-ês \xmark & go*ês \cmark \\
 gonorreia & go*nor*rei*a \cmark & go*nor*rei-a \xmark \\
+górdio & gór*di.o \xmark & gór*dio \cmark \\
 gorjeio & gor*jei*o \cmark & gor*jei-o \xmark \\
@@
 grafomaníaco & gra*fo*ma*ní-a*co \xmark & gra*fo*ma*ní*a*co \cmark \\
+grafômano & gra-fô*ma*no \xmark & gra*fô*ma*no \cmark \\
 gramatologia & gra*ma*to*lo*gi*a \cmark & gra*ma*to*lo*gi-a \xmark \\
+gramínea & gra*mí*ne.a \xmark & gra*mí*nea \cmark \\
+gramíneo & gra*mí*ne.o \xmark & gra*mí*neo \cmark \\
+grandiloquência & gran*di*lo-quên*ci.a \xmark & gran*di*lo*quên*cia \cmark \\
 granulometria & gra*nu*lo*me*tri*a \cmark & gra*nu*lo*me*tri-a \xmark \\
 grapiúna & gra*pi-ú*na \xmark & gra*pi*ú*na \cmark \\
+gratuidade & gra*tu-i*da*de \xmark & gra*tu-i*da*de \xmark \\
 graúdo & gra-ú*do \xmark & gra*ú*do \cmark \\
 graúna & gra-ú*na \xmark & gra*ú*na \cmark \\
+gravimetria & gra*vi*me*tri*a \cmark & gra*vi*me*tri-a \xmark \\
+graxaim & gra*xa-im \xmark & gra*xa-im \xmark \\
 gregário & gre*gá*ri.o \xmark & gre*gá*rio \cmark \\
@@
 grua & gru*a \cmark & gru-a \xmark \\
+gruiforme & gru-i*for*me \xmark & gru-i*for*me \xmark \\
+guaíba & gua-í*ba \xmark & gua*í*ba \cmark \\
+guarânia & gua*râ*ni.a \xmark & gua*râ*nia \cmark \\
+guardiania & guar*di*a*ni*a \cmark & guar*di*a*ni-a \xmark \\
 guardião & guar*di-ão \xmark & guar*di*ão \cmark \\
@@
 guria & gu*ri*a \cmark & gu*ri-a \xmark \\
+háfnio & háf*ni.o \xmark & háf*nio \cmark \\
+hagiografia & ha*gi*o*gra*fi*a \cmark & ha*gi*o*gra*fi-a \xmark \\
 hagiógrafo & ha*gi-ó*gra*fo \xmark & ha*gi*ó*gra*fo \cmark \\
+hagiologia & ha*gi*o*lo*gi*a \cmark & ha*gi*o*lo*gi-a \xmark \\
+hagiológio & ha*gi*o*ló*gi.o \xmark & ha*gi*o*ló*gio \cmark \\
+halogêneo & ha*lo*gê*ne.o \xmark & ha*lo*gê*neo \cmark \\
+halogênio & ha*lo*gê*ni.o \xmark & ha*lo*gê*nio \cmark \\
+halterofilia & hal*te*ro*fi*li*a \cmark & hal*te*ro*fi*li-a \xmark \\
 hamburgueria & ham*bur*gue*ri*a \cmark & ham*bur*gue*ri-a \xmark \\
@@
 harmônico & har-mô*ni*co \xmark & har*mô*ni*co \cmark \\
+harmônio & har-mô*ni.o \xmark & har*mô*nio \cmark \\
 harpia & har*pi*a \cmark & har*pi-a \xmark \\
+haustório & haus*tó*ri.o \xmark & haus*tó*rio \cmark \\
 hebdomadário & heb*do*ma*dá*ri.o \xmark & heb*do*ma*dá*rio \cmark \\
@@
 hebraísta & he*bra-ís*ta \xmark & he*bra*ís*ta \cmark \\
+hedônico & he-dô*ni*co \xmark & he*dô*ni*co \cmark \\
 hegemonia & he*ge*mo*ni*a \cmark & he*ge*mo*ni-a \xmark \\
@@
 helíaco & he*lí-a*co \xmark & he*lí*a*co \cmark \\
+heliografia & he*li*o*gra*fi*a \cmark & he*li*o*gra*fi-a \xmark \\
 heliógrafo & he*li-ó*gra*fo \xmark & he*li*ó*gra*fo \cmark \\
 hélio & hé*li.o \xmark & hé*lio \cmark \\
+helmintologia & hel*min*to*lo*gi*a \cmark & hel*min*to*lo*gi-a \xmark \\
 helvécio & hel*vé*ci*o \cmark & hel*vé*ci-o \xmark \\
+hemácia & he*má*ci.a \xmark & he*má*cia \cmark \\
 hematologia & he*ma*to*lo*gi*a \cmark & he*ma*to*lo*gi-a \xmark \\
+hematopoiético & he*ma*to*poi-é*ti*co \xmark & he*ma*to*poi*é*ti*co \cmark \\
+hematúria & he*ma*tú*ri.a \xmark & he*ma*tú*ria \cmark \\
 hemeralopia & he*me*ra*lo*pi*a \cmark & he*me*ra*lo*pi-a \xmark \\
+hemianopsia & he*mi*a*nop*si*a \cmark & he*mi*a*nop*si-a \xmark \\
 hemiparesia & he*mi*pa*re*si*a \cmark & he*mi*pa*re*si-a \xmark \\
@@
 hemofilia & he*mo*fi*li*a \cmark & he*mo*fi*li-a \xmark \\
+hemoglobinemia & he*mo*glo*bi*ne*mi*a \cmark & he*mo*glo*bi*ne*mi-a \xmark \\
+hemoglobinúria & he*mo*glo*bi*nú*ri.a \xmark & he*mo*glo*bi*nú*ria \cmark \\
 hemorragia & he*mor*ra*gi*a \cmark & he*mor*ra*gi-a \xmark \\
@@
 hemoterapia & he*mo*te*ra*pi*a \cmark & he*mo*te*ra*pi-a \xmark \\
+henoteísmo & he*no*te-ís*mo \xmark & he*no*te*ís*mo \cmark \\
+henoteísta & he*no*te-ís*ta \xmark & he*no*te*ís*ta \cmark \\
 hepatologia & he*pa*to*lo*gi*a \cmark & he*pa*to*lo*gi-a \xmark \\
@@
 heptacampeão & hep*ta*cam*pe-ão \xmark & hep*ta*cam*pe*ão \cmark \\
+heptarquia & hep*tar*qui*a \cmark & hep*tar*qui-a \xmark \\
 herbáceo & her*bá*ce.o \xmark & her*bá*ceo \cmark \\
@@
 heterocromia & he*te*ro*cro*mi*a \cmark & he*te*ro*cro*mi-a \xmark \\
+heterocronia & he*te*ro*cro*ni*a \cmark & he*te*ro*cro*ni-a \xmark \\
 heterodoxia & he*te*ro*do*xi*a \cmark & he*te*ro*do*xi-a \xmark \\
 heterofilia & he*te*ro*fi*li*a \cmark & he*te*ro*fi*li-a \xmark \\
+heterogêneo & he*te*ro*gê*ne.o \xmark & he*te*ro*gê*neo \cmark \\
 heterologia & he*te*ro*lo*gi*a \cmark & he*te*ro*lo*gi-a \xmark \\
@@
 heteronomia & he*te*ro*no*mi*a \cmark & he*te*ro*no*mi-a \xmark \\
+heterotopia & he*te*ro*to*pi*a \cmark & he*te*ro*to*pi-a \xmark \\
+hévea & hé*ve.a \xmark & hé*vea \cmark \\
 hexacampeão & he*xa*cam*pe-ão \xmark & he*xa*cam*pe*ão \cmark \\
@@
 hidrofobia & hi*dro*fo*bi*a \cmark & hi*dro*fo*bi-a \xmark \\
+hidrogênio & hi*dro*gê*ni.o \xmark & hi*dro*gê*nio \cmark \\
+hidrogeologia & hi*dro*ge*o*lo*gi*a \cmark & hi*dro*ge*o*lo*gi-a \xmark \\
 hidrologia & hi*dro*lo*gi*a \cmark & hi*dro*lo*gi-a \xmark \\
 hidromancia & hi*dro*man*ci*a \cmark & hi*dro*man*ci-a \xmark \\
+hidrometria & hi*dro*me*tri*a \cmark & hi*dro*me*tri-a \xmark \\
 hidropisia & hi*dro*pi*si*a \cmark & hi*dro*pi*si-a \xmark \\
+hidroponia & hi*dro*po*ni*a \cmark & hi*dro*po*ni-a \xmark \\
 hidropônico & hi*dro-pô*ni*co \xmark & hi*dro*pô*ni*co \cmark \\
@@
 hidroviário & hi*dro*vi-á*ri.o \xmark & hi*dro*vi*á*rio \cmark \\
+hidrozoário & hi*dro*zo-á*ri.o \xmark & hi*dro*zo*á*rio \cmark \\
 hierarquia & hi*e*rar*qui*a \cmark & hi*e*rar*qui-a \xmark \\
+hierofania & hi*e*ro*fa*ni*a \cmark & hi*e*ro*fa*ni-a \xmark \\
+higiénico & hi*gi-é*ni*co \xmark & hi*gi*é*ni*co \cmark \\
 hilária & hi*lá*ri.a \xmark & hi*lá*ria \cmark \\
 hilário & hi*lá*ri.o \xmark & hi*lá*rio \cmark \\
+hileia & hi*lei*a \cmark & hi*lei-a \xmark \\
+hilozoísmo & hi*lo*zo-ís*mo \xmark & hi*lo*zo*ís*mo \cmark \\
 hinário & hi*ná*ri.o \xmark & hi*ná*rio \cmark \\
 hinduísmo & hin*du-ís*mo \xmark & hin*du*ís*mo \cmark \\
+hinduísta & hin*du-ís*ta \xmark & hin*du*ís*ta \cmark \\
 hinologia & hi*no*lo*gi*a \cmark & hi*no*lo*gi-a \xmark \\
+hinterlândia & hin*ter*lân*di.a \xmark & hin*ter*lân*dia \cmark \\
+hióideo & hi-ói*de.o \xmark & hi*ói*deo \cmark \\
+hiperacusia & hi*pe*ra*cu*si*a \cmark & hi*pe*ra*cu*si-a \xmark \\
 hiperalgesia & hi*pe*ral*ge*si*a \cmark & hi*pe*ral*ge*si-a \xmark \\
@@
 hipercalcemia & hi*per*cal*ce*mi*a \cmark & hi*per*cal*ce*mi-a \xmark \\
+hipercapnia & hi*per*cap*ni*a \cmark & hi*per*cap*ni-a \xmark \\
 hiperdulia & hi*per*du*li*a \cmark & hi*per*du*li-a \xmark \\
 hiperemia & hi*pe*re*mi*a \cmark & hi*pe*re*mi-a \xmark \\
+hiperestesia & hi*pe*res*te*si*a \cmark & hi*pe*res*te*si-a \xmark \\
+hiperlipidemia & hi*per*li*pi*de*mi*a \cmark & hi*per*li*pi*de*mi-a \xmark \\
+hipernatremia & hi*per*na*tre*mi*a \cmark & hi*per*na*tre*mi-a \xmark \\
+hiperplasia & hi*per*pla*si*a \cmark & hi*per*pla*si-a \xmark \\
+hipersônico & hi*per-sô*ni*co \xmark & hi*per*sô*ni*co \cmark \\
 hipertermia & hi*per*ter*mi*a \cmark & hi*per*ter*mi-a \xmark \\
 hipertonia & hi*per*to*ni*a \cmark & hi*per*to*ni-a \xmark \\
+hipertônico & hi*per-tô*ni*co \xmark & hi*per*tô*ni*co \cmark \\
 hipertrofia & hi*per*tro*fi*a \cmark & hi*per*tro*fi-a \xmark \\
+hipnoterapia & hip*no*te*ra*pi*a \cmark & hip*no*te*ra*pi-a \xmark \\
 hipocalcemia & hi*po*cal*ce*mi*a \cmark & hi*po*cal*ce*mi-a \xmark \\
 hipocalemia & hi*po*ca*le*mi*a \cmark & hi*po*ca*le*mi-a \xmark \\
+hipocapnia & hi*po*cap*ni*a \cmark & hi*po*cap*ni-a \xmark \\
 hipocondríaco & hi*po*con*drí-a*co \xmark & hi*po*con*drí*a*co \cmark \\
 hipocondria & hi*po*con*dri*a \cmark & hi*po*con*dri-a \xmark \\
+hipocôndrio & hi*po-côn*dri.o \xmark & hi*po*côn*drio \cmark \\
 hipocrisia & hi*po*cri*si*a \cmark & hi*po*cri*si-a \xmark \\
+hipofisário & hi*po*fi*sá*ri.o \xmark & hi*po*fi*sá*rio \cmark \\
 hipoglicemia & hi*po*gli*ce*mi*a \cmark & hi*po*gli*ce*mi-a \xmark \\
+hipomaníaco & hi*po*ma*ní-a*co \xmark & hi*po*ma*ní*a*co \cmark \\
+hipomania & hi*po*ma*ni*a \cmark & hi*po*ma*ni-a \xmark \\
+hiponatremia & hi*po*na*tre*mi*a \cmark & hi*po*na*tre*mi-a \xmark \\
 hipônimo & hi-pô*ni*mo \xmark & hi*pô*ni*mo \cmark \\
 hipoplasia & hi*po*pla*si*a \cmark & hi*po*pla*si-a \xmark \\
+hipotecário & hi*po*te*cá*ri.o \xmark & hi*po*te*cá*rio \cmark \\
+hipoterapia & hi*po*te*ra*pi*a \cmark & hi*po*te*ra*pi-a \xmark \\
 hipotermia & hi*po*ter*mi*a \cmark & hi*po*ter*mi-a \xmark \\
 hipotonia & hi*po*to*ni*a \cmark & hi*po*to*ni-a \xmark \\
+hipotônico & hi*po-tô*ni*co \xmark & hi*po*tô*ni*co \cmark \\
 hipotrofia & hi*po*tro*fi*a \cmark & hi*po*tro*fi-a \xmark \\
+hipovolemia & hi*po*vo*le*mi*a \cmark & hi*po*vo*le*mi-a \xmark \\
 hipoxemia & hi*po*xe*mi*a \cmark & hi*po*xe*mi-a \xmark \\
@@
 histeroscopia & his*te*ros*co*pi*a \cmark & his*te*ros*co*pi-a \xmark \\
+histeroscópio & his*te*ros*có*pi.o \xmark & his*te*ros*có*pio \cmark \\
 histologia & his*to*lo*gi*a \cmark & his*to*lo*gi-a \xmark \\
@@
 historiografia & his*to*ri*o*gra*fi*a \cmark & his*to*ri*o*gra*fi-a \xmark \\
+historiógrafo & his*to*ri-ó*gra*fo \xmark & his*to*ri*ó*gra*fo \cmark \\
+historiologia & his*to*ri*o*lo*gi*a \cmark & his*to*ri*o*lo*gi-a \xmark \\
+histrião & his*tri-ão \xmark & his*tri*ão \cmark \\
+hodômetro & ho-dô*me*tro \xmark & ho*dô*me*tro \cmark \\
 hólmio & hól*mi.o \xmark & hól*mio \cmark \\
 holografia & ho*lo*gra*fi*a \cmark & ho*lo*gra*fi-a \xmark \\
+holonomia & ho*lo*no*mi*a \cmark & ho*lo*no*mi-a \xmark \\
+holonômico & ho*lo-nô*mi*co \xmark & ho*lo*nô*mi*co \cmark \\
 homeopatia & ho*me*o*pa*ti*a \cmark & ho*me*o*pa*ti-a \xmark \\
 homeostasia & ho*me*os*ta*si*a \cmark & ho*me*os*ta*si-a \xmark \\
+homeotermia & ho*me*o*ter*mi*a \cmark & ho*me*o*ter*mi-a \xmark \\
 homicídio & ho*mi*cí*di.o \xmark & ho*mi*cí*dio \cmark \\
@@
 hominídeo & ho*mi*ní*de.o \xmark & ho*mi*ní*deo \cmark \\
+homizio & ho*mi*zi*o \cmark & ho*mi*zi-o \xmark \\
 homofilia & ho*mo*fi*li*a \cmark & ho*mo*fi*li-a \xmark \\
@@
 homofonia & ho*mo*fo*ni*a \cmark & ho*mo*fo*ni-a \xmark \\
+homofônico & ho*mo-fô*ni*co \xmark & ho*mo*fô*ni*co \cmark \\
+homogêneo & ho*mo*gê*ne.o \xmark & ho*mo*gê*neo \cmark \\
+homogenia & ho*mo*ge*ni*a \cmark & ho*mo*ge*ni-a \xmark \\
 homografia & ho*mo*gra*fi*a \cmark & ho*mo*gra*fi-a \xmark \\
+homologatório & ho*mo*lo*ga*tó*ri.o \xmark & ho*mo*lo*ga*tó*rio \cmark \\
 homologia & ho*mo*lo*gi*a \cmark & ho*mo*lo*gi-a \xmark \\
@@
 homotetia & ho*mo*te*ti*a \cmark & ho*mo*te*ti-a \xmark \\
+honorário & ho*no*rá*ri.o \xmark & ho*no*rá*rio \cmark \\
+honraria & hon*ra*ri*a \cmark & hon*ra*ri-a \xmark \\
 horário & ho*rá*ri.o \xmark & ho*rá*rio \cmark \\
+hormônio & hor-mô*ni.o \xmark & hor*mô*nio \cmark \\
+hormonoterapia & hor*mo*no*te*ra*pi*a \cmark & hor*mo*no*te*ra*pi-a \xmark \\
 hortênsia & hor*tên*si.a \xmark & hor*tên*sia \cmark \\
@@
 hospício & hos*pí*ci.o \xmark & hos*pí*cio \cmark \\
+hospitalário & hos*pi*ta*lá*ri.o \xmark & hos*pi*ta*lá*rio \cmark \\
 hóstia & hós*ti.a \xmark & hós*tia \cmark \\
@@
 humanitário & hu*ma*ni*tá*ri.o \xmark & hu*ma*ni*tá*rio \cmark \\
+iá & i-á \xmark & i*á \cmark \\
+ião & i-ão \xmark & i*ão \cmark \\
+iatrogenia & i*a*tro*ge*ni*a \cmark & i*a*tro*ge*ni-a \xmark \\
+iatroquímica & i*a*tro-quí*mi*ca \xmark & i*a*tro*quí*mi*ca \cmark \\
+ibijaú & i*bi*ja-ú \xmark & i*bi*ja*ú \cmark \\
+icônico & i-cô*ni*co \xmark & i*cô*ni*co \cmark \\
 iconoclastia & i*co*no*clas*ti*a \cmark & i*co*no*clas*ti-a \xmark \\
@@
 identitário & i*den*ti*tá*ri.o \xmark & i*den*ti*tá*rio \cmark \\
+ideografia & i*de*o*gra*fi*a \cmark & i*de*o*gra*fi-a \xmark \\
 ideologia & i*de*o*lo*gi*a \cmark & i*de*o*lo*gi-a \xmark \\
@@
 idiotia & i*di*o*ti*a \cmark & i*di*o*ti-a \xmark \\
+idiótico & i*di-ó*ti*co \xmark & i*di*ó*ti*co \cmark \\
 idolatria & i*do*la*tri*a \cmark & i*do*la*tri-a \xmark \\
+idôneo & i-dô*ne.o \xmark & i*dô*neo \cmark \\
 ígneo & íg*ne.o \xmark & íg*neo \cmark \\
+ignomínia & ig*no*mí*ni*a \cmark & ig*no*mí*ni-a \xmark \\
 ignorância & ig*no*rân*ci.a \xmark & ig*no*rân*cia \cmark \\
 igualitário & i*gua*li*tá*ri.o \xmark & i*gua*li*tá*rio \cmark \\
+iguaria & i*gua*ri*a \cmark & i*gua*ri-a \xmark \\
 iídiche & i-í*di*che \xmark & i*í*di*che \cmark \\
+ileíte & i*le-í*te \xmark & i*le*í*te \cmark \\
 íleo & í*le.o \xmark & í*leo \cmark \\
+ileostomia & i*le*os*to*mi*a \cmark & i*le*os*to*mi-a \xmark \\
 ilhoa & i*lho*a \cmark & i*lho-a \xmark \\
@@
 ilíada & i*lí-a*da \xmark & i*lí*a*da \cmark \\
+ilício & i*lí*ci.o \xmark & i*lí*cio \cmark \\
+ílio & í*li.o \xmark & í*lio \cmark \\
+ilírio & i*lí*ri.o \xmark & i*lí*rio \cmark \\
 iliteracia & i*li*te*ra*ci*a \cmark & i*li*te*ra*ci-a \xmark \\
+ilocutório & i*lo*cu*tó*ri.o \xmark & i*lo*cu*tó*rio \cmark \\
+iluminância & i*lu*mi*nân*ci.a \xmark & i*lu*mi*nân*cia \cmark \\
 ilusório & i*lu*só*ri.o \xmark & i*lu*só*rio \cmark \\
@@
 imbuir & im*bu-ir \xmark & im*bu*ir \cmark \\
+imigratório & i*mi*gra*tó*ri.o \xmark & i*mi*gra*tó*rio \cmark \\
 iminência & i*mi*nên*ci.a \xmark & i*mi*nên*cia \cmark \\
+imiscuir & i*mis*cu-ir \xmark & i*mis*cu*ir \cmark \\
 imobiliária & i*mo*bi*li-á*ri.a \xmark & i*mo*bi*li*á*ria \cmark \\
@@
 impaciência & im*pa*ci*ên*ci.a \xmark & im*pa*ci*ên*cia \cmark \\
+impatriótico & im*pa*tri-ó*ti*co \xmark & im*pa*tri*ó*ti*co \cmark \\
+impedância & im*pe*dân*ci.a \xmark & im*pe*dân*cia \cmark \\
 impenitência & im*pe*ni*tên*ci.a \xmark & im*pe*ni*tên*cia \cmark \\
 imperdoável & im*per*do-á*vel \xmark & im*per*do*á*vel \cmark \\
+imperícia & im*pe*rí*ci.a \xmark & im*pe*rí*cia \cmark \\
 império & im*pé*ri.o \xmark & im*pé*rio \cmark \\
+impermanência & im*per*ma*nên*ci.a \xmark & im*per*ma*nên*cia \cmark \\
+impermeável & im*per*me-á*vel \xmark & im*per*me*á*vel \cmark \\
 impertinência & im*per*ti*nên*ci.a \xmark & im*per*ti*nên*cia \cmark \\
 ímpio & ím*pi.o \xmark & ím*pio \cmark \\
+implantodontia & im*plan*to*don*ti*a \cmark & im*plan*to*don*ti-a \xmark \\
 implicância & im*pli*cân*ci.a \xmark & im*pli*cân*cia \cmark \\
+implúvio & im*plú*vi.o \xmark & im*plú*vio \cmark \\
+imponência & im*po*nên*ci.a \xmark & im*po*nên*cia \cmark \\
 importância & im*por*tân*ci.a \xmark & im*por*tân*cia \cmark \\
@@
 imprevidência & im*pre*vi*dên*ci.a \xmark & im*pre*vi*dên*cia \cmark \\
+improcedência & im*pro*ce*dên*ci.a \xmark & im*pro*ce*dên*cia \cmark \\
 impronunciável & im*pro*nun*ci-á*vel \xmark & im*pro*nun*ci*á*vel \cmark \\
@@
 imprudência & im*pru*dên*ci.a \xmark & im*pru*dên*cia \cmark \\
+imunitário & i*mu*ni*tá*ri.o \xmark & i*mu*ni*tá*rio \cmark \\
+imunodeficiência & i*mu*no*de*fi*ci*ên*ci.a \xmark & i*mu*no*de*fi*ci*ên*cia \cmark \\
 imunologia & i*mu*no*lo*gi*a \cmark & i*mu*no*lo*gi-a \xmark \\
+imunopatologia & i*mu*no*pa*to*lo*gi*a \cmark & i*mu*no*pa*to*lo*gi-a \xmark \\
 imunoterapia & i*mu*no*te*ra*pi*a \cmark & i*mu*no*te*ra*pi-a \xmark \\
+inácia & i*ná*ci.a \xmark & i*ná*cia \cmark \\
 inadiável & i*na*di-á*vel \xmark & i*na*di*á*vel \cmark \\
+inadimplência & i*na*dim*plên*ci.a \xmark & i*na*dim*plên*cia \cmark \\
 inapetência & i*na*pe*tên*ci.a \xmark & i*na*pe*tên*cia \cmark \\
@@
 incidência & in*ci*dên*ci.a \xmark & in*ci*dên*cia \cmark \\
+incipiência & in*ci*pi*ên*ci.a \xmark & in*ci*pi*ên*cia \cmark \\
 inclemência & in*cle*mên*ci.a \xmark & in*cle*mên*cia \cmark \\
+inclinômetro & in*cli-nô*me*tro \xmark & in*cli*nô*me*tro \cmark \\
 incluir & in*clu-ir \xmark & in*clu*ir \cmark \\
+incoerência & in*co*e*rên*ci.a \xmark & in*co*e*rên*cia \cmark \\
 incômodo & in-cô*mo*do \xmark & in*cô*mo*do \cmark \\
+incompetência & in*com*pe*tên*ci.a \xmark & in*com*pe*tên*cia \cmark \\
 inconciliável & in*con*ci*li-á*vel \xmark & in*con*ci*li*á*vel \cmark \\
@@
 inconsequência & in*con*se-quên*ci.a \xmark & in*con*se*quên*cia \cmark \\
+inconsistência & in*con*sis*tên*ci.a \xmark & in*con*sis*tên*cia \cmark \\
 inconspícuo & in*cons*pí*cu.o \xmark & in*cons*pí*cuo \cmark \\
@@
 inconveniência & in*con*ve*ni*ên*ci.a \xmark & in*con*ve*ni*ên*cia \cmark \\
+incorpóreo & in*cor*pó*re.o \xmark & in*cor*pó*reo \cmark \\
 incumbência & in*cum*bên*ci.a \xmark & in*cum*bên*cia \cmark \\
@@
 indaiá & in*dai-á \xmark & in*dai*á \cmark \\
+indecência & in*de*cên*ci.a \xmark & in*de*cên*cia \cmark \\
 indeiscente & in*de-is*cen*te \xmark & in*de-is*cen*te \xmark \\
@@
 índio & ín*di.o \xmark & ín*dio \cmark \\
+indissociável & in*dis*so*ci-á*vel \xmark & in*dis*so*ci*á*vel \cmark \\
 indolência & in*do*lên*ci.a \xmark & in*do*lên*cia \cmark \\
+indologia & in*do*lo*gi*a \cmark & in*do*lo*gi-a \xmark \\
 indonésio & in*do*né*si.o \xmark & in*do*né*sio \cmark \\
+indulgência & in*dul*gên*ci.a \xmark & in*dul*gên*cia \cmark \\
 indumentária & in*du*men*tá*ri.a \xmark & in*du*men*tá*ria \cmark \\
+indúsio & in*dú*si.o \xmark & in*dú*sio \cmark \\
 indústria & in*dús*tri.a \xmark & in*dús*tria \cmark \\
+indutância & in*du*tân*ci.a \xmark & in*du*tân*cia \cmark \\
 inédia & i*né*di.a \xmark & i*né*dia \cmark \\
+ineficácia & i*ne*fi*cá*ci.a \xmark & i*ne*fi*cá*cia \cmark \\
 ineficiência & i*ne*fi*ci*ên*ci.a \xmark & i*ne*fi*ci*ên*cia \cmark \\
 inegociável & i*ne*go*ci-á*vel \xmark & i*ne*go*ci*á*vel \cmark \\
+inépcia & i*nép*ci.a \xmark & i*nép*cia \cmark \\
 inequívoco & i*ne-quí*vo*co \xmark & i*ne*quí*vo*co \cmark \\
 inércia & i*nér*ci.a \xmark & i*nér*cia \cmark \\
+inerência & i*ne*rên*ci.a \xmark & i*ne*rên*cia \cmark \\
+inerrância & i*ner*rân*ci.a \xmark & i*ner*rân*cia \cmark \\
 inexequível & i*ne*xe-quí*vel \xmark & i*ne*xe*quí*vel \cmark \\
@@
 infantaria & in*fan*ta*ri*a \cmark & in*fan*ta*ri-a \xmark \\
+infanteria & in*fan*te*ri*a \cmark & in*fan*te*ri-a \xmark \\
 infanticídio & in*fan*ti*cí*di.o \xmark & in*fan*ti*cí*dio \cmark \\
+infectologia & in*fec*to*lo*gi*a \cmark & in*fec*to*lo*gi-a \xmark \\
 inferência & in*fe*rên*ci.a \xmark & in*fe*rên*cia \cmark \\
@@
 ingenuidade & in*ge*nu-i*da*de \xmark & in*ge*nu*i*da*de \cmark \\
+ingênuo & in*gê*nu.o \xmark & in*gê*nuo \cmark \\
 ingerência & in*ge*rên*ci.a \xmark & in*ge*rên*cia \cmark \\
+inglório & in*gló*ri.o \xmark & in*gló*rio \cmark \\
+inibitória & i*ni*bi*tó*ri.a \xmark & i*ni*bi*tó*ria \cmark \\
+inibitório & i*ni*bi*tó*ri.o \xmark & i*ni*bi*tó*rio \cmark \\
 iniciático & i*ni*ci-á*ti*co \xmark & i*ni*ci*á*ti*co \cmark \\
@@
 injúria & in*jú*ri.a \xmark & in*jú*ria \cmark \\
+inobservância & i*nob*ser*vân*ci.a \xmark & i*nob*ser*vân*cia \cmark \\
 inocência & i*no*cên*ci.a \xmark & i*no*cên*cia \cmark \\
+inócuo & i*nó*cu.o \xmark & i*nó*cuo \cmark \\
+inoperância & i*no*pe*rân*ci.a \xmark & i*no*pe*rân*cia \cmark \\
 inópia & i*nó*pi.a \xmark & i*nó*pia \cmark \\
+inquisitório & in*qui*si*tó*ri.o \xmark & in*qui*si*tó*rio \cmark \\
 insaciável & in*sa*ci-á*vel \xmark & in*sa*ci*á*vel \cmark \\
+insatisfatório & in*sa*tis*fa*tó*ri.o \xmark & in*sa*tis*fa*tó*rio \cmark \\
 insídia & in*sí*di*a \cmark & in*sí*di-a \xmark \\
@@
 insolvência & in*sol*vên*ci.a \xmark & in*sol*vên*cia \cmark \\
+insônia & in-sô*ni.a \xmark & in*sô*nia \cmark \\
 inspiratório & ins*pi*ra*tó*ri*o \cmark & ins*pi*ra*tó*ri-o \xmark \\
@@
 instantâneo & ins*tan*tâ*ne*o \cmark & ins*tan*tâ*ne-o \xmark \\
+instituição & ins*ti*tu-i*ção \xmark & ins*ti*tu*i*ção \cmark \\
 instituído & ins*ti*tu-í*do \xmark & ins*ti*tu*í*do \cmark \\
+instituidor & ins*ti*tu-i*dor \xmark & ins*ti*tu-i*dor \xmark \\
 instituir & ins*ti*tu-ir \xmark & ins*ti*tu*ir \cmark \\
@@
 instruir & ins*tru-ir \xmark & ins*tru*ir \cmark \\
+insubsistência & in*sub*sis*tên*ci.a \xmark & in*sub*sis*tên*cia \cmark \\
 insubstituível & in*subs*ti*tu-í*vel \xmark & in*subs*ti*tu*í*vel \cmark \\
 insuficiência & in*su*fi*ci*ên*ci.a \xmark & in*su*fi*ci*ên*cia \cmark \\
+insulinoterapia & in*su*li*no*te*ra*pi*a \cmark & in*su*li*no*te*ra*pi-a \xmark \\
 inteligência & in*te*li*gên*ci.a \xmark & in*te*li*gên*cia \cmark \\
+intempérie & in*tem*pé*ri.e \xmark & in*tem*pé*rie \cmark \\
+intendência & in*ten*dên*ci.a \xmark & in*ten*dên*cia \cmark \\
 interbancário & in*ter*ban*cá*ri.o \xmark & in*ter*ban*cá*rio \cmark \\
@@
 intercâmbio & in*ter*câm*bi.o \xmark & in*ter*câm*bio \cmark \\
+intercorrência & in*ter*cor*rên*ci.a \xmark & in*ter*cor*rên*cia \cmark \\
 interdependência & in*ter*de*pen*dên*ci.a \xmark & in*ter*de*pen*dên*cia \cmark \\
 interferência & in*ter*fe*rên*ci.a \xmark & in*ter*fe*rên*cia \cmark \\
+interferometria & in*ter*fe*ro*me*tri*a \cmark & in*ter*fe*ro*me*tri-a \xmark \\
+interferômetro & in*ter*fe-rô*me*tro \xmark & in*ter*fe*rô*me*tro \cmark \\
 interflúvio & in*ter*flú*vi.o \xmark & in*ter*flú*vio \cmark \\
+interlocutória & in*ter*lo*cu*tó*ri.a \xmark & in*ter*lo*cu*tó*ria \cmark \\
 interlúdio & in*ter*lú*di.o \xmark & in*ter*lú*dio \cmark \\
@@
 intermitência & in*ter*mi*tên*ci.a \xmark & in*ter*mi*tên*cia \cmark \\
+internúncio & in*ter*nún*ci.o \xmark & in*ter*nún*cio \cmark \\
 interoceânico & in*te*ro*ce-â*ni*co \xmark & in*te*ro*ce*â*ni*co \cmark \\
@@
 interstício & in*ters*tí*ci.o \xmark & in*ters*tí*cio \cmark \\
+interuniversitário & in*te*ru*ni*ver*si*tá*ri.o \xmark & in*te*ru*ni*ver*si*tá*rio \cmark \\
 interventoria & in*ter*ven*to*ri*a \cmark & in*ter*ven*to*ri-a \xmark \\
@@
 intransigência & in*tran*si*gên*ci.a \xmark & in*tran*si*gên*cia \cmark \\
+introdutório & in*tro*du*tó*ri.o \xmark & in*tro*du*tó*rio \cmark \\
 intuição & in*tu-i*ção \xmark & in*tu*i*ção \cmark \\
 intuir & in*tu-ir \xmark & in*tu*ir \cmark \\
-intuitivo & in*tu-i*ti*vo \xmark & in*tu-i*ti*vo \xmark \\
+intumescência & in*tu*mes*cên*ci.a \xmark & in*tu*mes*cên*cia \cmark \\
+inúbia & i*nú*bi.a \xmark & i*nú*bia \cmark \\
 invariância & in*va*ri*ân*ci.a \xmark & in*va*ri*ân*cia \cmark \\
@@
 iódico & i-ó*di*co \xmark & i*ó*di*co \cmark \\
+ioiô & i.o-i.ô \xmark & i.o-i.ô \xmark \\
+íon & í-on \xmark & í*on \cmark \\
+iraúna & i*ra-ú*na \xmark & i*ra*ú*na \cmark \\
+iridescência & i*ri*des*cên*ci.a \xmark & i*ri*des*cên*cia \cmark \\
 irídio & i*rí*di.o \xmark & i*rí*dio \cmark \\
@@
 irrefreável & ir*re*fre-á*vel \xmark & ir*re*fre*á*vel \cmark \\
+irrelevância & ir*re*le*vân*ci.a \xmark & ir*re*le*vân*cia \cmark \\
+irreligião & ir*re*li*gi-ão \xmark & ir*re*li*gi*ão \cmark \\
 irremediável & ir*re*me*di-á*vel \xmark & ir*re*me*di*á*vel \cmark \\
@@
 isomeria & i*so*me*ri*a \cmark & i*so*me*ri-a \xmark \\
+isômero & i-sô*me*ro \xmark & i*sô*me*ro \cmark \\
 isometria & i*so*me*tri*a \cmark & i*so*me*tri-a \xmark \\
@@
 isotônico & i*so-tô*ni*co \xmark & i*so*tô*ni*co \cmark \\
+isotopia & i*so*to*pi*a \cmark & i*so*to*pi-a \xmark \\
+isotropia & i*so*tro*pi*a \cmark & i*so*tro*pi-a \xmark \\
 isquemia & is*que*mi*a \cmark & is*que*mi-a \xmark \\
+isquêmico & is-quê*mi*co \xmark & is*quê*mi*co \cmark \\
+isquiático & is*qui-á*ti*co \xmark & is*qui*á*ti*co \cmark \\
+ísquio & ís*qui.o \xmark & ís*quio \cmark \\
+itaimbé & i*ta-im*bé \xmark & i*ta-im*bé \xmark \\
+itapiúna & i*ta*pi-ú*na \xmark & i*ta*pi*ú*na \cmark \\
+itapuá & i*ta*pu-á \xmark & i*ta*pu*á \cmark \\
+itapuã & i*ta*pu-ã \xmark & i*ta*pu*ã \cmark \\
+itaúba & i*ta-ú*ba \xmark & i*ta*ú*ba \cmark \\
 itérbio & i*tér*bi.o \xmark & i*tér*bio \cmark \\
@@
 jabô & ja-bô \xmark & ja*bô \cmark \\
+jacobeia & ja*co*bei*a \cmark & ja*co*bei-a \xmark \\
 jactância & jac*tân*ci.a \xmark & jac*tân*cia \cmark \\
+jacuí & ja*cu-í \xmark & ja*cu*í \cmark \\
 jaculatória & ja*cu*la*tó*ri.a \xmark & ja*cu*la*tó*ria \cmark \\
+jambalaia & jam*ba*lai*a \cmark & jam*ba*lai-a \xmark \\
+janaúba & ja*na-ú*ba \xmark & ja*na*ú*ba \cmark \\
 jandaia & jan*dai*a \cmark & jan*dai-a \xmark \\
+jandaíra & jan*da-í*ra \xmark & jan*da*í*ra \cmark \\
+januária & ja*nu-á*ri.a \xmark & ja*nu*á*ria \cmark \\
 jaó & ja-ó \xmark & ja*ó \cmark \\
+japuí & ja*pu-í \xmark & ja*pu*í \cmark \\
 jaracatiá & ja*ra*ca*ti-á \xmark & ja*ra*ca*ti*á \cmark \\
+jaramataia & ja*ra*ma*tai*a \cmark & ja*ra*ma*tai-a \xmark \\
+jataí & ja*ta-í \xmark & ja*ta*í \cmark \\
+jataúba & ja*ta-ú*ba \xmark & ja*ta*ú*ba \cmark \\
+jauá & jau-á \xmark & jau*á \cmark \\
 jaú & ja-ú \xmark & ja*ú \cmark \\
@@
 jia & ji*a \cmark & ji-a \xmark \\
+jiboia & ji*boi*a \cmark & ji*boi-a \xmark \\
+jihadista & ji-ha*dis*ta \xmark & ji-ha*dis*ta \xmark \\
+jiquitaia & ji*qui*tai*a \cmark & ji*qui*tai-a \xmark \\
+joalharia & jo*a*lha*ri*a \cmark & jo*a*lha*ri-a \xmark \\
 joalheria & jo*a*lhe*ri*a \cmark & jo*a*lhe*ri-a \xmark \\
@@
 juízo & ju-í*zo \xmark & ju*í*zo \cmark \\
+júlio & jú*li.o \xmark & jú*lio \cmark \\
+jundiá & jun*di-á \xmark & jun*di*á \cmark \\
+juó & ju-ó \xmark & ju-ó \xmark \\
+jupiá & ju*pi-á \xmark & ju*pi*á \cmark \\
 juquiá & ju*qui-á \xmark & ju*qui*á \cmark \\
+jurisprudência & ju*ris*pru*dên*ci.a \xmark & ju*ris*pru*dên*cia \cmark \\
+jutaí & ju*ta-í \xmark & ju*ta*í \cmark \\
+juvenília & ju*ve*ní*li.a \xmark & ju*ve*ní*lia \cmark \\
 kuwaitiano & ku-wai*ti*a*no \xmark & ku-wai*ti*a*no \xmark \\
 lábia & lá*bi.a \xmark & lá*bia \cmark \\
+lábio & lá*bi.o \xmark & lá*bio \cmark \\
 laboratório & la*bo*ra*tó*ri.o \xmark & la*bo*ra*tó*rio \cmark \\
+laborterapia & la*bor*te*ra*pi*a \cmark & la*bor*te*ra*pi-a \xmark \\
 lacaio & la*cai*o \cmark & la*cai-o \xmark \\
 laçaria & la*ça*ri*a \cmark & la*ça*ri-a \xmark \\
+lacínia & la*cí*ni.a \xmark & la*cí*nia \cmark \\
 lacônico & la-cô*ni*co \xmark & la*cô*ni*co \cmark \\
+lacraia & la*crai*a \cmark & la*crai-a \xmark \\
+lacrimatório & la*cri*ma*tó*ri.o \xmark & la*cri*ma*tó*rio \cmark \\
+lacrimogêneo & la*cri*mo*gê*ne.o \xmark & la*cri*mo*gê*neo \cmark \\
+lactário & lac*tá*ri.o \xmark & lac*tá*rio \cmark \\
+lácteo & lác*te.o \xmark & lác*teo \cmark \\
+lactucário & lac*tu*cá*ri.o \xmark & lac*tu*cá*rio \cmark \\
 ladainha & la*da-i*nha \xmark & la*da*i*nha \cmark \\
+ladraria & la*dra*ri*a \cmark & la*dra*ri-a \xmark \\
 lagoa & la*go*a \cmark & la*go-a \xmark \\
@@
 lamaísmo & la*ma-ís*mo \xmark & la*ma*ís*mo \cmark \\
+lamaísta & la*ma-ís*ta \xmark & la*ma*ís*ta \cmark \\
 lâmia & lâ*mi.a \xmark & lâ*mia \cmark \\
+lampadário & lam*pa*dá*ri.o \xmark & lam*pa*dá*rio \cmark \\
 lampião & lam*pi-ão \xmark & lam*pi*ão \cmark \\
@@
 lanifício & la*ni*fí*ci.o \xmark & la*ni*fí*cio \cmark \\
+lantânio & lan*tâ*ni.o \xmark & lan*tâ*nio \cmark \\
 laparoscopia & la*pa*ros*co*pi*a \cmark & la*pa*ros*co*pi-a \xmark \\
 laparotomia & la*pa*ro*to*mi*a \cmark & la*pa*ro*to*mi-a \xmark \\
+lapidaria & la*pi*da*ri*a \cmark & la*pi*da*ri-a \xmark \\
+lapidário & la*pi*dá*ri.o \xmark & la*pi*dá*rio \cmark \\
 laquê & la-quê \xmark & la*quê \cmark \\
 larápio & la*rá*pi.o \xmark & la*rá*pio \cmark \\
+larário & la*rá*ri.o \xmark & la*rá*rio \cmark \\
+larício & la*rí*ci.o \xmark & la*rí*cio \cmark \\
+laringectomia & la*rin*gec*to*mi*a \cmark & la*rin*gec*to*mi-a \xmark \\
 laríngeo & la*rín*ge.o \xmark & la*rín*geo \cmark \\
 lascívia & las*cí*vi.a \xmark & las*cí*via \cmark \\
+lataria & la*ta*ri*a \cmark & la*ta*ri-a \xmark \\
+latência & la*tên*ci.a \xmark & la*tên*cia \cmark \\
+laticínio & la*ti*cí*ni.o \xmark & la*ti*cí*nio \cmark \\
+laticlávio & la*ti*clá*vi.o \xmark & la*ti*clá*vio \cmark \\
+latifundiário & la*ti*fun*di-á*ri.o \xmark & la*ti*fun*di*á*rio \cmark \\
 latifúndio & la*ti*fún*di.o \xmark & la*ti*fún*dio \cmark \\
 latinório & la*ti*nó*ri.o \xmark & la*ti*nó*rio \cmark \\
+latoaria & la*to*a*ri*a \cmark & la*to*a*ri-a \xmark \\
 latrocínio & la*tro*cí*ni.o \xmark & la*tro*cí*nio \cmark \\
 laudatório & lau*da*tó*ri.o \xmark & lau*da*tó*rio \cmark \\
+láurea & láu*re.a \xmark & láu*rea \cmark \\
 laurêncio & lau*rên*ci.o \xmark & lau*rên*cio \cmark \\
+lavanderia & la*van*de*ri*a \cmark & la*van*de*ri-a \xmark \\
 lavatório & la*va*tó*ri.o \xmark & la*va*tó*rio \cmark \\
@@
 leão & le-ão \xmark & le*ão \cmark \\
+lecanomancia & le*ca*no*man*ci*a \cmark & le*ca*no*man*ci-a \xmark \\
+legatário & le*ga*tá*ri.o \xmark & le*ga*tá*rio \cmark \\
 legendário & le*gen*dá*ri.o \xmark & le*gen*dá*rio \cmark \\
@@
 legionário & le*gi*o*ná*ri.o \xmark & le*gi*o*ná*rio \cmark \\
+leguleio & le*gu*lei*o \cmark & le*gu*lei-o \xmark \\
 leitaria & lei*ta*ri*a \cmark & lei*ta*ri-a \xmark \\
+leiteria & lei*te*ri*a \cmark & lei*te*ri-a \xmark \\
 leitoa & lei*to*a \cmark & lei*to-a \xmark \\
@@
 leoa & le*o*a \cmark & le*o-a \xmark \\
+leônico & le-ô*ni*co \xmark & le*ô*ni*co \cmark \\
 lepidopterologia & le*pi*dop*te*ro*lo*gi*a \cmark & le*pi*dop*te*ro*lo*gi-a \xmark \\
 leporídeo & le*po*rí*de.o \xmark & le*po*rí*deo \cmark \\
+leprologia & le*pro*lo*gi*a \cmark & le*pro*lo*gi-a \xmark \\
+leprosaria & le*pro*sa*ri*a \cmark & le*pro*sa*ri-a \xmark \\
+leprosário & le*pro*sá*ri.o \xmark & le*pro*sá*rio \cmark \\
+lésbia & lés*bi.a \xmark & lés*bia \cmark \\
 lésbio & lés*bi.o \xmark & lés*bio \cmark \\
@@
 letícia & le*tí*ci.a \xmark & le*tí*cia \cmark \\
+letria & le*tri*a \cmark & le*tri-a \xmark \\
 leucemia & leu*ce*mi*a \cmark & leu*ce*mi-a \xmark \\
+leucocitário & leu*co*ci*tá*ri.o \xmark & leu*co*ci*tá*rio \cmark \\
 leucopenia & leu*co*pe*ni*a \cmark & leu*co*pe*ni-a \xmark \\
@@
 leucotomia & leu*co*to*mi*a \cmark & leu*co*to*mi-a \xmark \\
+levadia & le*va*di*a \cmark & le*va*di-a \xmark \\
 lexicografia & le*xi*co*gra*fi*a \cmark & le*xi*co*gra*fi-a \xmark \\
@@
 lia & li*a \cmark & li-a \xmark \\
+liberatório & li*be*ra*tó*ri.o \xmark & li*be*ra*tó*rio \cmark \\
 libertário & li*ber*tá*ri.o \xmark & li*ber*tá*rio \cmark \\
@@
 licantropia & li*can*tro*pi*a \cmark & li*can*tro*pi-a \xmark \\
+lichia & li*chi*a \cmark & li*chi-a \xmark \\
 lício & lí*ci.o \xmark & lí*cio \cmark \\
+lidocaína & li*do*ca-í*na \xmark & li*do*ca*í*na \cmark \\
+liechtensteinense & li*e.ch*tens*tei*nen*se \xmark & li*e.ch*tens*tei*nen*se \xmark \\
+lígio & lí*gi.o \xmark & lí*gio \cmark \\
+lílio & lí*li.o \xmark & lí*lio \cmark \\
 limnologia & lim*no*lo*gi*a \cmark & lim*no*lo*gi-a \xmark \\
+linfadenectomia & lin*fa*de*nec*to*mi*a \cmark & lin*fa*de*nec*to*mi-a \xmark \\
+linfadenopatia & lin*fa*de*no*pa*ti*a \cmark & lin*fa*de*no*pa*ti-a \xmark \\
 linóleo & li*nó*le*o \cmark & li*nó*le-o \xmark \\
+lio & li*o \cmark & li-o \xmark \\
+lipídeo & li*pí*de.o \xmark & li*pí*deo \cmark \\
+lipídio & li*pí*di.o \xmark & li*pí*dio \cmark \\
+lipodistrofia & li*po*dis*tro*fi*a \cmark & li*po*dis*tro*fi-a \xmark \\
 lírio & lí*ri*o \cmark & lí*ri-o \xmark \\
@@
 litania & li*ta*ni*a \cmark & li*ta*ni-a \xmark \\
+litargírio & li*tar*gí*ri.o \xmark & li*tar*gí*rio \cmark \\
+literacia & li*te*ra*ci*a \cmark & li*te*ra*ci-a \xmark \\
+literário & li*te*rá*ri.o \xmark & li*te*rá*rio \cmark \\
 litíase & li*tí-a*se \xmark & li*tí*a*se \cmark \\
@@
 lítio & lí*ti.o \xmark & lí*tio \cmark \\
+litisconsórcio & li*tis*con*sór*ci.o \xmark & li*tis*con*sór*cio \cmark \\
 litispendência & li*tis*pen*dên*ci*a \cmark & li*tis*pen*dên*ci-a \xmark \\
+litofania & li*to*fa*ni*a \cmark & li*to*fa*ni-a \xmark \\
 litografia & li*to*gra*fi*a \cmark & li*to*gra*fi-a \xmark \\
 litologia & li*to*lo*gi*a \cmark & li*to*lo*gi-a \xmark \\
+litorâneo & li*to*râ*ne.o \xmark & li*to*râ*neo \cmark \\
 litotripsia & li*to*trip*si*a \cmark & li*to*trip*si-a \xmark \\
 liturgia & li*tur*gi*a \cmark & li*tur*gi-a \xmark \\
+livônio & li-vô*ni.o \xmark & li*vô*nio \cmark \\
 livraria & li*vra*ri*a \cmark & li*vra*ri-a \xmark \\
@@
 logosofia & lo*go*so*fi*a \cmark & lo*go*so*fi-a \xmark \\
+lólio & ló*li.o \xmark & ló*lio \cmark \\
 lombalgia & lom*bal*gi*a \cmark & lom*bal*gi-a \xmark \\
+longilíneo & lon*gi*lí*ne.o \xmark & lon*gi*lí*neo \cmark \\
+lotaria & lo*ta*ri*a \cmark & lo*ta*ri-a \xmark \\
 loteria & lo*te*ri*a \cmark & lo*te*ri-a \xmark \\
+loxodromia & lo*xo*dro*mi*a \cmark & lo*xo*dro*mi-a \xmark \\
 lua & lu*a \cmark & lu-a \xmark \\
+lúcio & lú*ci.o \xmark & lú*cio \cmark \\
+ludião & lu*di-ão \xmark & lu*di*ão \cmark \\
+lúdio & lú*di.o \xmark & lú*dio \cmark \\
+ludopédio & lu*do*pé*di.o \xmark & lu*do*pé*dio \cmark \\
 ludoterapia & lu*do*te*ra*pi*a \cmark & lu*do*te*ra*pi-a \xmark \\
 luís & lu-ís \xmark & lu*ís \cmark \\
+luminância & lu*mi*nân*ci.a \xmark & lu*mi*nân*cia \cmark \\
+luminária & lu*mi*ná*ri.a \xmark & lu*mi*ná*ria \cmark \\
 luminescência & lu*mi*nes*cên*ci.a \xmark & lu*mi*nes*cên*cia \cmark \\
@@
 luteína & lu*te-í*na \xmark & lu*te*í*na \cmark \\
+lúteo & lú*te.o \xmark & lú*teo \cmark \\
 luteria & lu*te*ri*a \cmark & lu*te*ri-a \xmark \\
@@
 macedônia & ma*ce-dô*ni.a \xmark & ma*ce*dô*nia \cmark \\
+macedônico & ma*ce-dô*ni*co \xmark & ma*ce*dô*ni*co \cmark \\
+macedônio & ma*ce-dô*ni.o \xmark & ma*ce*dô*nio \cmark \\
 maceió & ma*cei-ó \xmark & ma*cei*ó \cmark \\
+machio & ma*chi*o \cmark & ma*chi-o \xmark \\
 macio & ma*ci*o \cmark & ma*ci-o \xmark \\
@@
 maçônico & ma-çô*ni*co \xmark & ma*çô*ni*co \cmark \\
+macróbio & ma*cró*bi.o \xmark & ma*cró*bio \cmark \\
 macrobiótica & ma*cro*bi-ó*ti*ca \xmark & ma*cro*bi*ó*ti*ca \cmark \\
 macrobiótico & ma*cro*bi-ó*ti*co \xmark & ma*cro*bi*ó*ti*co \cmark \\
+macrocefalia & ma*cro*ce*fa*li*a \cmark & ma*cro*ce*fa*li-a \xmark \\
 macroeconomia & ma*cro*e*co*no*mi*a \cmark & ma*cro*e*co*no*mi-a \xmark \\
@@
 macrorregião & ma*cror*re*gi-ão \xmark & ma*cror*re*gi*ão \cmark \\
+macrossomia & ma*cros*so*mi*a \cmark & ma*cros*so*mi-a \xmark \\
+macua & ma*cu*a \cmark & ma*cu-a \xmark \\
+mádia & má*di.a \xmark & má*dia \cmark \\
 maestria & ma*es*tri*a \cmark & ma*es*tri-a \xmark \\
@@
 magnésio & mag*né*si.o \xmark & mag*né*sio \cmark \\
+magnetômetro & mag*ne-tô*me*tro \xmark & mag*ne*tô*me*tro \cmark \\
+magnetoscópio & mag*ne*tos*có*pi.o \xmark & mag*ne*tos*có*pio \cmark \\
 magnificência & mag*ni*fi*cên*ci.a \xmark & mag*ni*fi*cên*cia \cmark \\
@@
 malaio & ma*lai*o \cmark & ma*lai-o \xmark \\
+malária & ma*lá*ri.a \xmark & ma*lá*ria \cmark \\
+malásio & ma*lá*si.o \xmark & ma*lá*sio \cmark \\
 malauiano & ma*lau-i*a*no \xmark & ma*lau*i*a*no \cmark \\
@@
 maledicência & ma*le*di*cên*ci.a \xmark & ma*le*di*cên*cia \cmark \\
+malefício & ma*le*fí*ci.o \xmark & ma*le*fí*cio \cmark \\
+maléolo & ma*lé-o*lo \xmark & ma*lé*o*lo \cmark \\
+malevolência & ma*le*vo*lên*ci.a \xmark & ma*le*vo*lên*cia \cmark \\
+malharia & ma*lha*ri*a \cmark & ma*lha*ri-a \xmark \\
 malícia & ma*lí*ci.a \xmark & ma*lí*cia \cmark \\
+malônico & ma-lô*ni*co \xmark & ma*lô*ni*co \cmark \\
 malthusianismo & mal-thu*si*a*nis*mo \xmark & mal-thu*si*a*nis*mo \xmark \\
@@
 mamário & ma*má*ri.o \xmark & ma*má*rio \cmark \\
+mamoa & ma*mo*a \cmark & ma*mo-a \xmark \\
 mamografia & ma*mo*gra*fi*a \cmark & ma*mo*gra*fi-a \xmark \\
+manaia & ma*nai*a \cmark & ma*nai-a \xmark \\
 mancebia & man*ce*bi*a \cmark & man*ce*bi-a \xmark \\
+mancheia & man*chei*a \cmark & man*chei-a \xmark \\
 mandaçaia & man*da*çai*a \cmark & man*da*çai-a \xmark \\
+mandatário & man*da*tá*ri.o \xmark & man*da*tá*rio \cmark \\
 mandrião & man*dri-ão \xmark & man*dri*ão \cmark \\
 maneia & ma*nei*a \cmark & ma*nei-a \xmark \\
+maneio & ma*nei*o \cmark & ma*nei-o \xmark \\
 maníaco & ma*ní-a*co \xmark & ma*ní*a*co \cmark \\
 mania & ma*ni*a \cmark & ma*ni-a \xmark \\
+manicômio & ma*ni-cô*mi.o \xmark & ma*ni*cô*mio \cmark \\
 maniqueísmo & ma*ni*que-ís*mo \xmark & ma*ni*que*ís*mo \cmark \\
@@
 mantô & man-tô \xmark & man*tô \cmark \\
+manúbrio & ma*nú*bri.o \xmark & ma*nú*brio \cmark \\
 manuseio & ma*nu*sei*o \cmark & ma*nu*sei-o \xmark \\
@@
 maquinário & ma*qui*ná*ri.o \xmark & ma*qui*ná*rio \cmark \\
+maracutaia & ma*ra*cu*tai*a \cmark & ma*ra*cu*tai-a \xmark \\
 marambaia & ma*ram*bai*a \cmark & ma*ram*bai-a \xmark \\
@@
 maresia & ma*re*si*a \cmark & ma*re*si-a \xmark \\
+marginália & mar*gi*ná*li.a \xmark & mar*gi*ná*lia \cmark \\
 maria & ma*ri*a \cmark & ma*ri-a \xmark \\
 marinharia & ma*ri*nha*ri*a \cmark & ma*ri*nha*ri-a \xmark \\
+mariologia & ma*ri*o*lo*gi*a \cmark & ma*ri*o*lo*gi-a \xmark \\
+marmoraria & mar*mo*ra*ri*a \cmark & mar*mo*ra*ri-a \xmark \\
+marmóreo & mar*mó*re.o \xmark & mar*mó*reo \cmark \\
 marquês & mar-quês \xmark & mar*quês \cmark \\
+marruá & mar*ru-á \xmark & mar*ru*á \cmark \\
+marsúpio & mar*sú*pi.o \xmark & mar*sú*pio \cmark \\
 martírio & mar*tí*ri.o \xmark & mar*tí*rio \cmark \\
+martirológio & mar*ti*ro*ló*gi.o \xmark & mar*ti*ro*ló*gio \cmark \\
+maruí & ma*ru-í \xmark & ma*ru*í \cmark \\
 maruim & ma*ru-im \xmark & ma*ru-im \xmark \\
 masdeísmo & mas*de-ís*mo \xmark & mas*de*ís*mo \cmark \\
+massoterapia & mas*so*te*ra*pi*a \cmark & mas*so*te*ra*pi-a \xmark \\
 mastectomia & mas*tec*to*mi*a \cmark & mas*tec*to*mi-a \xmark \\
+mastigatório & mas*ti*ga*tó*ri.o \xmark & mas*ti*ga*tó*rio \cmark \\
 mastologia & mas*to*lo*gi*a \cmark & mas*to*lo*gi-a \xmark \\
+mastozoologia & mas*to*zo*o*lo*gi*a \cmark & mas*to*zo*o*lo*gi-a \xmark \\
 matéria & ma*té*ri.a \xmark & ma*té*ria \cmark \\
 matricídio & ma*tri*cí*di.o \xmark & ma*tri*cí*dio \cmark \\
+matrimônio & ma*tri-mô*ni.o \xmark & ma*tri*mô*nio \cmark \\
+maué & mau-é \xmark & mau*é \cmark \\
+mavórcio & ma*vór*ci.o \xmark & ma*vór*cio \cmark \\
+meã & me-ã \xmark & me*ã \cmark \\
 meão & me-ão \xmark & me*ão \cmark \\
@@
 mediterrâneo & me*di*ter*râ*ne.o \xmark & me*di*ter*râ*neo \cmark \\
+mediúnico & me*di-ú*ni*co \xmark & me*di*ú*ni*co \cmark \\
+mediunidade & me*di-u*ni*da*de \xmark & me*di*u*ni*da*de \cmark \\
 megalomaníaco & me*ga*lo*ma*ní-a*co \xmark & me*ga*lo*ma*ní*a*co \cmark \\
 megalomania & me*ga*lo*ma*ni*a \cmark & me*ga*lo*ma*ni-a \xmark \\
+megalômano & me*ga-lô*ma*no \xmark & me*ga*lô*ma*no \cmark \\
 megatério & me*ga*té*ri.o \xmark & me*ga*té*rio \cmark \\
@@
 meio & mei*o \cmark & mei-o \xmark \\
+meiótico & mei-ó*ti*co \xmark & mei*ó*ti*co \cmark \\
 melancia & me*lan*ci*a \cmark & me*lan*ci-a \xmark \\
 melancolia & me*lan*co*li*a \cmark & me*lan*co*li-a \xmark \\
+melanésio & me*la*né*si.o \xmark & me*la*né*sio \cmark \\
+melania & me*la*ni*a \cmark & me*la*ni-a \xmark \\
+melânia & me*lâ*ni.a \xmark & me*lâ*nia \cmark \\
 melhoria & me*lho*ri*a \cmark & me*lho*ri-a \xmark \\
 melífluo & me*lí*flu.o \xmark & me*lí*fluo \cmark \\
+meloa & me*lo*a \cmark & me*lo-a \xmark \\
 melodia & me*lo*di*a \cmark & me*lo*di-a \xmark \\
@@
 melomania & me*lo*ma*ni*a \cmark & me*lo*ma*ni-a \xmark \\
+melômano & me-lô*ma*no \xmark & me*lô*ma*no \cmark \\
+membranáceo & mem*bra*ná*ce.o \xmark & mem*bra*ná*ceo \cmark \\
 memória & me*mó*ri.a \xmark & me*mó*ria \cmark \\
 mendelévio & men*de*lé*vi.o \xmark & men*de*lé*vio \cmark \\
+mendicância & men*di*cân*ci.a \xmark & men*di*cân*cia \cmark \\
 meneio & me*nei*o \cmark & me*nei-o \xmark \\
+menológio & me*no*ló*gi.o \xmark & me*no*ló*gio \cmark \\
 menorragia & me*nor*ra*gi*a \cmark & me*nor*ra*gi-a \xmark \\
+mensário & men*sá*ri.o \xmark & men*sá*rio \cmark \\
 mênstruo & mêns*tru.o \xmark & mêns*truo \cmark \\
@@
 mercenário & mer*ce*ná*ri.o \xmark & mer*ce*ná*rio \cmark \\
+mércia & mér*ci.a \xmark & mér*cia \cmark \\
 mercúrio & mer*cú*ri.o \xmark & mer*cú*rio \cmark \\
@@
 merovíngio & me*ro*vín*gi.o \xmark & me*ro*vín*gio \cmark \\
+mesário & me*sá*ri.o \xmark & me*sá*rio \cmark \\
+mesentério & me*sen*té*ri.o \xmark & me*sen*té*rio \cmark \\
+mesogleia & me*so*glei*a \cmark & me*so*glei-a \xmark \\
+mesotélio & me*so*té*li.o \xmark & me*so*té*lio \cmark \\
+mesoterapia & me*so*te*ra*pi*a \cmark & me*so*te*ra*pi-a \xmark \\
 mesquinharia & mes*qui*nha*ri*a \cmark & mes*qui*nha*ri-a \xmark \\
@@
 metalurgia & me*ta*lur*gi*a \cmark & me*ta*lur*gi-a \xmark \\
+metameria & me*ta*me*ri*a \cmark & me*ta*me*ri-a \xmark \\
 metaplasia & me*ta*pla*si*a \cmark & me*ta*pla*si-a \xmark \\
+metapsicologia & me*tap*si*co*lo*gi*a \cmark & me*tap*si*co*lo*gi-a \xmark \\
 meteórico & me*te-ó*ri*co \xmark & me*te*ó*ri*co \cmark \\
@@
 mialgia & mi*al*gi*a \cmark & mi*al*gi-a \xmark \\
+miastenia & mi*as*te*ni*a \cmark & mi*as*te*ni-a \xmark \\
 micélio & mi*cé*li.o \xmark & mi*cé*lio \cmark \\
+micobactéria & mi*co*bac*té*ri.a \xmark & mi*co*bac*té*ria \cmark \\
 micologia & mi*co*lo*gi*a \cmark & mi*co*lo*gi-a \xmark \\
@@
 microcirurgia & mi*cro*ci*rur*gi*a \cmark & mi*cro*ci*rur*gi-a \xmark \\
+microempresário & mi*cro*em*pre*sá*ri.o \xmark & mi*cro*em*pre*sá*rio \cmark \\
 microfonia & mi*cro*fo*ni*a \cmark & mi*cro*fo*ni-a \xmark \\
 microfotografia & mi*cro*fo*to*gra*fi*a \cmark & mi*cro*fo*to*gra*fi-a \xmark \\
+microftalmia & mi*crof*tal*mi*a \cmark & mi*crof*tal*mi-a \xmark \\
+micrografia & mi*cro*gra*fi*a \cmark & mi*cro*gra*fi-a \xmark \\
+microrregião & mi*cror*re*gi-ão \xmark & mi*cror*re*gi*ão \cmark \\
 microscopia & mi*cros*co*pi*a \cmark & mi*cros*co*pi-a \xmark \\
 microscópio & mi*cros*có*pi.o \xmark & mi*cros*có*pio \cmark \\
+microsporângio & mi*cros*po*rân*gi.o \xmark & mi*cros*po*rân*gio \cmark \\
 mictório & mic*tó*ri.o \xmark & mic*tó*rio \cmark \\
@@
 midríase & mi*drí-a*se \xmark & mi*drí*a*se \cmark \\
+mielopatia & mi*e*lo*pa*ti*a \cmark & mi*e*lo*pa*ti-a \xmark \\
 migratório & mi*gra*tó*ri.o \xmark & mi*gra*tó*rio \cmark \\
+miíase & mi-í-a*se \xmark & mi*í*a*se \cmark \\
+míldio & míl*di.o \xmark & míl*dio \cmark \\
+milefólio & mi*le*fó*li.o \xmark & mi*le*fó*lio \cmark \\
 milenário & mi*le*ná*ri.o \xmark & mi*le*ná*rio \cmark \\
+milênio & mi*lê*ni.o \xmark & mi*lê*nio \cmark \\
+miliário & mi*li-á*ri.o \xmark & mi*li*á*rio \cmark \\
+milícia & mi*lí*ci.a \xmark & mi*lí*cia \cmark \\
 milionário & mi*li*o*ná*ri*o \cmark & mi*li*o*ná*ri-o \xmark \\
@@
 minifúndio & mi*ni*fún*di.o \xmark & mi*ni*fún*dio \cmark \\
+minissaia & mi*nis*sai*a \cmark & mi*nis*sai-a \xmark \\
 minissérie & mi*nis*sé*ri.e \xmark & mi*nis*sé*rie \cmark \\
+ministeriável & mi*nis*te*ri-á*vel \xmark & mi*nis*te*ri*á*vel \cmark \\
 ministério & mi*nis*té*ri.o \xmark & mi*nis*té*rio \cmark \\
@@
 minudência & mi*nu*dên*ci.a \xmark & mi*nu*dên*cia \cmark \\
+miocárdio & mi*o*cár*di.o \xmark & mi*o*cár*dio \cmark \\
+mioclonia & mi*o*clo*ni*a \cmark & mi*o*clo*ni-a \xmark \\
+miologia & mi*o*lo*gi*a \cmark & mi*o*lo*gi-a \xmark \\
+mio & mi*o \cmark & mi-o \xmark \\
+miopatia & mi*o*pa*ti*a \cmark & mi*o*pa*ti-a \xmark \\
 míope & mí-o*pe \xmark & mí*o*pe \cmark \\
@@
 miríade & mi*rí-a*de \xmark & mi*rí*a*de \cmark \\
+miringotomia & mi*rin*go*to*mi*a \cmark & mi*rin*go*to*mi-a \xmark \\
+misandria & mi*san*dri*a \cmark & mi*san*dri-a \xmark \\
 misantropia & mi*san*tro*pi*a \cmark & mi*san*tro*pi-a \xmark \\
@@
 mistério & mis*té*ri.o \xmark & mis*té*rio \cmark \\
+mistifório & mis*ti*fó*ri.o \xmark & mis*ti*fó*rio \cmark \\
 mitocôndria & mi*to-côn*dri.a \xmark & mi*to*côn*dria \cmark \\
@@
 mitomania & mi*to*ma*ni*a \cmark & mi*to*ma*ni-a \xmark \\
+miúdas & mi-ú*das \xmark & mi*ú*das \cmark \\
+miudeza & mi-u*de*za \xmark & mi*u*de*za \cmark \\
 miúdo & mi-ú*do \xmark & mi*ú*do \cmark \\
@@
 mobiliário & mo*bi*li-á*ri.o \xmark & mo*bi*li*á*rio \cmark \\
+mocoa & mo*co*a \cmark & mo*co-a \xmark \\
 modéstia & mo*dés*ti.a \xmark & mo*dés*tia \cmark \\
@@
 moléstia & mo*lés*ti.a \xmark & mo*lés*tia \cmark \\
+molibdênio & mo*lib*dê*ni.o \xmark & mo*lib*dê*nio \cmark \\
 momentâneo & mo*men*tâ*ne.o \xmark & mo*men*tâ*neo \cmark \\
+monadologia & mo*na*do*lo*gi*a \cmark & mo*na*do*lo*gi-a \xmark \\
 monarquia & mo*nar*qui*a \cmark & mo*nar*qui-a \xmark \\
+monastério & mo*nas*té*ri.o \xmark & mo*nas*té*rio \cmark \\
 monetário & mo*ne*tá*ri.o \xmark & mo*ne*tá*rio \cmark \\
 monitoria & mo*ni*to*ri*a \cmark & mo*ni*to*ri-a \xmark \\
+monitória & mo*ni*tó*ri.a \xmark & mo*ni*tó*ria \cmark \\
+monocórdio & mo*no*cór*di.o \xmark & mo*no*cór*dio \cmark \\
 monocromia & mo*no*cro*mi*a \cmark & mo*no*cro*mi-a \xmark \\
 monofonia & mo*no*fo*ni*a \cmark & mo*no*fo*ni-a \xmark \\
+monofônico & mo*no-fô*ni*co \xmark & mo*no*fô*ni*co \cmark \\
 monografia & mo*no*gra*fi*a \cmark & mo*no*gra*fi-a \xmark \\
@@
 monômero & mo-nô*me*ro \xmark & mo*nô*me*ro \cmark \\
+monômio & mo-nô*mi.o \xmark & mo*nô*mio \cmark \\
 monopólio & mo*no*pó*li.o \xmark & mo*no*pó*lio \cmark \\
+monoquíni & mo*no-quí*ni \xmark & mo*no*quí*ni \cmark \\
+monossacarídeo & mo*nos*sa*ca*rí*de.o \xmark & mo*nos*sa*ca*rí*deo \cmark \\
 monossomia & mo*nos*so*mi*a \cmark & mo*nos*so*mi-a \xmark \\
@@
 monoteísta & mo*no*te-ís*ta \xmark & mo*no*te*ís*ta \cmark \\
+monotipia & mo*no*ti*pi*a \cmark & mo*no*ti*pi-a \xmark \\
 monotonia & mo*no*to*ni*a \cmark & mo*no*to*ni-a \xmark \\
@@
 moratória & mo*ra*tó*ri.a \xmark & mo*ra*tó*ria \cmark \\
+moratório & mo*ra*tó*ri.o \xmark & mo*ra*tó*rio \cmark \\
 mordomia & mor*do*mi*a \cmark & mor*do*mi-a \xmark \\
@@
 morfologia & mor*fo*lo*gi*a \cmark & mor*fo*lo*gi-a \xmark \\
+morgadio & mor*ga*di*o \cmark & mor*ga*di-o \xmark \\
 morrião & mor*ri-ão \xmark & mor*ri*ão \cmark \\
+mortuárias & mor*tu-á*ri*as \xmark & mor*tu*á*ri*as \cmark \\
+moscóvia & mos*có*vi.a \xmark & mos*có*via \cmark \\
 mostruário & mos*tru-á*ri.o \xmark & mos*tru*á*rio \cmark \\
@@
 multimídia & mul*ti*mí*di.a \xmark & mul*ti*mí*dia \cmark \\
+multimilionário & mul*ti*mi*li*o*ná*ri.o \xmark & mul*ti*mi*li*o*ná*rio \cmark \\
 multitudinário & mul*ti*tu*di*ná*ri*o \cmark & mul*ti*tu*di*ná*ri-o \xmark \\
 múmia & mú*mi.a \xmark & mú*mia \cmark \\
+mundaréu & mun*da*ré-u \xmark & mun*da*ré-u \xmark \\
 município & mu*ni*cí*pi.o \xmark & mu*ni*cí*pio \cmark \\
+muriático & mu*ri-á*ti*co \xmark & mu*ri*á*ti*co \cmark \\
 murmúrio & mur*mú*ri.o \xmark & mur*mú*rio \cmark \\
+museografia & mu*se*o*gra*fi*a \cmark & mu*se*o*gra*fi-a \xmark \\
 museologia & mu*se*o*lo*gi*a \cmark & mu*se*o*lo*gi-a \xmark \\
@@
 mustelídeo & mus*te*lí*de.o \xmark & mus*te*lí*deo \cmark \\
+mútua & mú*tu.a \xmark & mú*tua \cmark \\
 mutuário & mu*tu-á*ri.o \xmark & mu*tu*á*rio \cmark \\
 mútuo & mú*tu.o \xmark & mú*tuo \cmark \\
+nagô & na-gô \xmark & na*gô \cmark \\
 nanotecnologia & na*no*tec*no*lo*gi*a \cmark & na*no*tec*no*lo*gi-a \xmark \\
 napoleão & na*po*le-ão \xmark & na*po*le*ão \cmark \\
+narratologia & nar*ra*to*lo*gi*a \cmark & nar*ra*to*lo*gi-a \xmark \\
 natalício & na*ta*lí*ci.o \xmark & na*ta*lí*cio \cmark \\
+natatório & na*ta*tó*ri.o \xmark & na*ta*tó*rio \cmark \\
+naturopatia & na*tu*ro*pa*ti*a \cmark & na*tu*ro*pa*ti-a \xmark \\
 naufrágio & nau*frá*gi.o \xmark & nau*frá*gio \cmark \\
+naumaquia & nau*ma*qui*a \cmark & nau*ma*qui-a \xmark \\
+náuplio & náu*pli.o \xmark & náu*plio \cmark \\
+náusea & náu*se.a \xmark & náu*sea \cmark \\
 navio & na*vi*o \cmark & na*vi-o \xmark \\
@@
 necrologia & ne*cro*lo*gi*a \cmark & ne*cro*lo*gi-a \xmark \\
+necrológio & ne*cro*ló*gi.o \xmark & ne*cro*ló*gio \cmark \\
 necromancia & ne*cro*man*ci*a \cmark & ne*cro*man*ci-a \xmark \\
@@
 necrotério & ne*cro*té*ri.o \xmark & ne*cro*té*rio \cmark \\
+nectário & nec*tá*ri.o \xmark & nec*tá*rio \cmark \\
+nédio & né*di.o \xmark & né*dio \cmark \\
 neerlandês & ne*er*lan*dês \cmark & ne*er*lan*dês \cmark \\
 nefrectomia & ne*frec*to*mi*a \cmark & ne*frec*to*mi-a \xmark \\
+nefrolitíase & ne*fro*li*tí-a*se \xmark & ne*fro*li*tí*a*se \cmark \\
 nefrologia & ne*fro*lo*gi*a \cmark & ne*fro*lo*gi-a \xmark \\
@@
 negligência & ne*gli*gên*ci.a \xmark & ne*gli*gên*cia \cmark \\
+negligenciável & ne*gli*gen*ci-á*vel \xmark & ne*gli*gen*ci*á*vel \cmark \\
 negócio & ne*gó*ci.o \xmark & ne*gó*cio \cmark \\
+nênia & nê*ni.a \xmark & nê*nia \cmark \\
+neocapitalismo & ne*o*ca*pi*ta*lis*mo \cmark & ne-o*ca*pi*ta*lis*mo \xmark \\
+neoclassicismo & ne*o*clas*si*cis*mo \cmark & ne-o*clas*si*cis*mo \xmark \\
+neoclássico & ne*o*clás*si*co \cmark & ne-o*clás*si*co \xmark \\
 neocolonialismo & ne*o*co*lo*ni*a*lis*mo \cmark & ne-o*co*lo*ni*a*lis*mo \xmark \\
+neodarwinismo & ne*o*dar-wi*nis*mo \xmark & ne-o*dar-wi*nis*mo \xmark \\
 neodímio & ne*o*dí*mi.o \xmark & ne-o*dí*mio \xmark \\
+neofascismo & ne*o*fas*cis*mo \cmark & ne-o*fas*cis*mo \xmark \\
 neofascista & ne*o*fas*cis*ta \cmark & ne-o*fas*cis*ta \xmark \\
 neófito & ne-ó*fi*to \xmark & ne*ó*fi*to \cmark \\
+neogótico & ne*o*gó*ti*co \cmark & ne-o*gó*ti*co \xmark \\
+neokantismo & ne*o*kan*tis*mo \cmark & ne-o*kan*tis*mo \xmark \\
 neolatino & ne*o*la*ti*no \cmark & ne-o*la*ti*no \xmark \\
@@
 neologismo & ne*o*lo*gis*mo \cmark & ne-o*lo*gis*mo \xmark \\
+neologista & ne*o*lo*gis*ta \cmark & ne-o*lo*gis*ta \xmark \\
+neonatal & ne*o*na*tal \cmark & ne-o*na*tal \xmark \\
 neonatologia & ne*o*na*to*lo*gi*a \cmark & ne-o*na*to*lo*gi-a \xmark \\
+neonatologista & ne*o*na*to*lo*gis*ta \cmark & ne-o*na*to*lo*gis*ta \xmark \\
 neonato & ne*o*na*to \cmark & ne-o*na*to \xmark \\
@@
 neonazista & ne*o*na*zis*ta \cmark & ne-o*na*zis*ta \xmark \\
+neônio & ne-ô*ni.o \xmark & ne*ô*nio \cmark \\
 neon & ne*on \cmark & ne-on \xmark \\
@@
 neoplasia & ne*o*pla*si*a \cmark & ne-o*pla*si-a \xmark \\
+neoplásico & ne*o*plá*si*co \cmark & ne-o*plá*si*co \xmark \\
+neoplasma & ne*o*plas*ma \cmark & ne-o*plas*ma \xmark \\
+neoplatônico & ne*o*pla-tô*ni*co \xmark & ne-o*pla*tô*ni*co \xmark \\
 neoplatonismo & ne*o*pla*to*nis*mo \cmark & ne-o*pla*to*nis*mo \xmark \\
+neopositivismo & ne*o*po*si*ti*vis*mo \cmark & ne-o*po*si*ti*vis*mo \xmark \\
+neotenia & ne*o*te*ni*a \cmark & ne-o*te*ni-a \xmark \\
+neotomismo & ne*o*to*mis*mo \cmark & ne-o*to*mis*mo \xmark \\
+neotrópico & ne*o*tró*pi*co \cmark & ne-o*tró*pi*co \xmark \\
 neozelandês & ne*o*ze*lan*dês \cmark & ne-o*ze*lan*dês \xmark \\
@@
 néscio & nés*ci.o \xmark & nés*cio \cmark \\
+netúnio & ne*tú*ni.o \xmark & ne*tú*nio \cmark \\
 neuralgia & neu*ral*gi*a \cmark & neu*ral*gi-a \xmark \\
@@
 neurobiologia & neu*ro*bi*o*lo*gi*a \cmark & neu*ro*bi*o*lo*gi-a \xmark \\
+neurociência & neu*ro*ci*ên*ci.a \xmark & neu*ro*ci*ên*cia \cmark \\
 neurocirurgia & neu*ro*ci*rur*gi*a \cmark & neu*ro*ci*rur*gi-a \xmark \\
 neurocirurgião & neu*ro*ci*rur*gi-ão \xmark & neu*ro*ci*rur*gi*ão \cmark \\
+neurofisiologia & neu*ro*fi*si*o*lo*gi*a \cmark & neu*ro*fi*si*o*lo*gi-a \xmark \\
 neurologia & neu*ro*lo*gi*a \cmark & neu*ro*lo*gi-a \xmark \\
+neurônio & neu-rô*ni.o \xmark & neu*rô*nio \cmark \\
 neuropatia & neu*ro*pa*ti*a \cmark & neu*ro*pa*ti-a \xmark \\
 neuropatologia & neu*ro*pa*to*lo*gi*a \cmark & neu*ro*pa*to*lo*gi-a \xmark \\
+neuropsiquiatria & neu*rop*si*qui*a*tri*a \cmark & neu*rop*si*qui*a*tri-a \xmark \\
 neutropenia & neu*tro*pe*ni*a \cmark & neu*tro*pe*ni-a \xmark \\
@@
 nevralgia & ne*vral*gi*a \cmark & ne*vral*gi-a \xmark \\
+ninfolepsia & nin*fo*lep*si*a \cmark & nin*fo*lep*si-a \xmark \\
 ninfomaníaca & nin*fo*ma*ní-a*ca \xmark & nin*fo*ma*ní*a*ca \cmark \\
@@
 ninfomania & nin*fo*ma*ni*a \cmark & nin*fo*ma*ni-a \xmark \\
+nióbio & ni-ó*bi.o \xmark & ni*ó*bio \cmark \\
+nipônico & ni-pô*ni*co \xmark & ni*pô*ni*co \cmark \\
+nitrogênio & ni*tro*gê*ni.o \xmark & ni*tro*gê*nio \cmark \\
 nobélio & no*bé*li.o \xmark & no*bé*lio \cmark \\
+nobiliário & no*bi*li-á*ri.o \xmark & no*bi*li*á*rio \cmark \\
 nobiliarquia & no*bi*li*ar*qui*a \cmark & no*bi*li*ar*qui-a \xmark \\
 nobiliárquico & no*bi*li-ár*qui*co \xmark & no*bi*li*ár*qui*co \cmark \\
+noético & no-é*ti*co \xmark & no*é*ti*co \cmark \\
 nomografia & no*mo*gra*fi*a \cmark & no*mo*gra*fi-a \xmark \\
@@
 noologia & no*o*lo*gi*a \cmark & no*o*lo*gi-a \xmark \\
+nosocômio & no*so-cô*mi.o \xmark & no*so*cô*mio \cmark \\
 nosologia & no*so*lo*gi*a \cmark & no*so*lo*gi-a \xmark \\
@@
 notório & no*tó*ri.o \xmark & no*tó*rio \cmark \\
+novenário & no*ve*ná*ri.o \xmark & no*ve*ná*rio \cmark \\
 núbio & nú*bi.o \xmark & nú*bio \cmark \\
+nucléolo & nu*clé-o*lo \xmark & nu*clé*o*lo \cmark \\
 núcleo & nú*cle.o \xmark & nú*cleo \cmark \\
+nucleotídeo & nu*cle*o*tí*de.o \xmark & nu*cle*o*tí*deo \cmark \\
+nuclídeo & nu*clí*de.o \xmark & nu*clí*deo \cmark \\
+nudibrânquio & nu*di*brân*qui.o \xmark & nu*di*brân*quio \cmark \\
 núncio & nún*ci.o \xmark & nún*cio \cmark \\
 núpcias & núp*ci.as \xmark & núp*ci.as \xmark \\
+nutrologia & nu*tro*lo*gi*a \cmark & nu*tro*lo*gi-a \xmark \\
+oásis & o-á*sis \xmark & o*á*sis \cmark \\
 obediência & o*be*di*ên*ci.a \xmark & o*be*di*ên*cia \cmark \\
@@
 ocluir & o*clu-ir \xmark & o*clu*ir \cmark \\
+ocorrência & o*cor*rên*ci.a \xmark & o*cor*rên*cia \cmark \\
+ocráceo & o*crá*ce.o \xmark & o*crá*ceo \cmark \\
 octaédrico & oc*ta-é*dri*co \xmark & oc*ta*é*dri*co \cmark \\
@@
 odisseia & o*dis*sei*a \cmark & o*dis*sei-a \xmark \\
+odometria & o*do*me*tri*a \cmark & o*do*me*tri-a \xmark \\
 odômetro & o-dô*me*tro \xmark & o*dô*me*tro \cmark \\
@@
 oftalmoscopia & of*tal*mos*co*pi*a \cmark & of*tal*mos*co*pi-a \xmark \\
+oftalmoscópio & of*tal*mos*có*pi.o \xmark & of*tal*mos*có*pio \cmark \\
+ofurô & o*fu-rô \xmark & o*fu*rô \cmark \\
+oídio & o-í*di.o \xmark & o*í*dio \cmark \\
 olaia & o*lai*a \cmark & o*lai-a \xmark \\
 olaria & o*la*ri*a \cmark & o*la*ri-a \xmark \\
+olearia & o*le*a*ri*a \cmark & o*le*a*ri-a \xmark \\
 oleícola & o*le-í*co*la \xmark & o*le*í*co*la \cmark \\
 oleína & o*le-í*na \xmark & o*le*í*na \cmark \\
+óleo & ó*le.o \xmark & ó*leo \cmark \\
+olfatometria & ol*fa*to*me*tri*a \cmark & ol*fa*to*me*tri-a \xmark \\
 oligarquia & o*li*gar*qui*a \cmark & o*li*gar*qui-a \xmark \\
@@
 oligopólio & o*li*go*pó*li.o \xmark & o*li*go*pó*lio \cmark \\
+oligúria & o*li*gú*ri.a \xmark & o*li*gú*ria \cmark \\
 olimpíada & o*lim*pí-a*da \xmark & o*lim*pí*a*da \cmark \\
+oliváceo & o*li*vá*ce.o \xmark & o*li*vá*ceo \cmark \\
+omíada & o*mí-a*da \xmark & o*mí*a*da \cmark \\
 oncologia & on*co*lo*gi*a \cmark & on*co*lo*gi-a \xmark \\
@@
 oócito & o-ó*ci*to \xmark & o*ó*ci*to \cmark \\
+ooforectomia & o*o*fo*rec*to*mi*a \cmark & o*o*fo*rec*to*mi-a \xmark \\
+oogamia & o*o*ga*mi*a \cmark & o*o*ga*mi-a \xmark \\
+oólito & o-ó*li*to \xmark & o*ó*li*to \cmark \\
 operário & o*pe*rá*ri.o \xmark & o*pe*rá*rio \cmark \\
+operatório & o*pe*ra*tó*ri.o \xmark & o*pe*ra*tó*rio \cmark \\
+opiáceo & o*pi-á*ce.o \xmark & o*pi*á*ceo \cmark \\
 opinião & o*pi*ni-ão \xmark & o*pi*ni*ão \cmark \\
@@
 orgia & or*gi*a \cmark & or*gi-a \xmark \\
+orgiástico & or*gi-ás*ti*co \xmark & or*gi*ás*ti*co \cmark \\
 oriá & o*ri-á \xmark & o*ri*á \cmark \\
 orifício & o*ri*fí*ci.o \xmark & o*ri*fí*cio \cmark \\
+originário & o*ri*gi*ná*ri.o \xmark & o*ri*gi*ná*rio \cmark \\
 oriundo & o*ri-un*do \xmark & o*ri*un*do \cmark \\
@@
 orografia & o*ro*gra*fi*a \cmark & o*ro*gra*fi-a \xmark \\
+orquidário & or*qui*dá*ri.o \xmark & or*qui*dá*rio \cmark \\
+orquídea & or-quí*de.a \xmark & or*quí*dea \cmark \\
+orquiectomia & or*qui*ec*to*mi*a \cmark & or*qui*ec*to*mi-a \xmark \\
+ortoclásio & or*to*clá*si.o \xmark & or*to*clá*sio \cmark \\
 ortodontia & or*to*don*ti*a \cmark & or*to*don*ti-a \xmark \\
@@
 ortodromia & or*to*dro*mi*a \cmark & or*to*dro*mi-a \xmark \\
+ortografia & or*to*gra*fi*a \cmark & or*to*gra*fi-a \xmark \\
 ortopedia & or*to*pe*di*a \cmark & or*to*pe*di-a \xmark \\
@@
 oscilatório & os*ci*la*tó*ri.o \xmark & os*ci*la*tó*rio \cmark \\
+osciloscópio & os*ci*los*có*pi.o \xmark & os*ci*los*có*pio \cmark \\
 ósmio & ós*mi.o \xmark & ós*mio \cmark \\
+ossário & os*sá*ri.o \xmark & os*sá*rio \cmark \\
 ósseo & ós*se.o \xmark & ós*seo \cmark \\
+ossuário & os*su-á*ri.o \xmark & os*su*á*rio \cmark \\
 osteíte & os*te-í*te \xmark & os*te*í*te \cmark \\
+ostensório & os*ten*só*ri.o \xmark & os*ten*só*rio \cmark \\
+osteologia & os*te*o*lo*gi*a \cmark & os*te*o*lo*gi-a \xmark \\
+osteomalacia & os*te*o*ma*la*ci*a \cmark & os*te*o*ma*la*ci-a \xmark \\
 osteopatia & os*te*o*pa*ti*a \cmark & os*te*o*pa*ti-a \xmark \\
+osteotomia & os*te*o*to*mi*a \cmark & os*te*o*to*mi-a \xmark \\
+ostiário & os*ti-á*ri.o \xmark & os*ti*á*rio \cmark \\
+ostíolo & os*tí-o*lo \xmark & os*tí*o*lo \cmark \\
+ostomia & os*to*mi*a \cmark & os*to*mi-a \xmark \\
 otalgia & o*tal*gi*a \cmark & o*tal*gi-a \xmark \\
@@
 ouvidoria & ou*vi*do*ri*a \cmark & ou*vi*do*ri-a \xmark \\
+ovídeo & o*ví*de.o \xmark & o*ví*deo \cmark \\
+oxiácido & o*xi-á*ci*do \xmark & o*xi*á*ci*do \cmark \\
+oxigênio & o*xi*gê*ni.o \xmark & o*xi*gê*nio \cmark \\
+ozônio & o-zô*ni.o \xmark & o*zô*nio \cmark \\
 paciência & pa*ci*ên*ci.a \xmark & pa*ci*ên*cia \cmark \\
@@
 painço & pa-in*ço \xmark & pa-in*ço \xmark \\
+painho & pa-i*nho \xmark & pa*i*nho \cmark \\
 paio & pai*o \cmark & pai-o \xmark \\
 país & pa-ís \xmark & pa*ís \cmark \\
+pajeú & pa*je-ú \xmark & pa*je*ú \cmark \\
 palácio & pa*lá*ci.o \xmark & pa*lá*cio \cmark \\
@@
 palavrório & pa*la*vró*ri.o \xmark & pa*la*vró*rio \cmark \\
+paleantropologia & pa*le*an*tro*po*lo*gi*a \cmark & pa*le*an*tro*po*lo*gi-a \xmark \\
+paleoclimatologia & pa*le*o*cli*ma*to*lo*gi*a \cmark & pa*le*o*cli*ma*to*lo*gi-a \xmark \\
+paleogeografia & pa*le*o*ge*o*gra*fi*a \cmark & pa*le*o*ge*o*gra*fi-a \xmark \\
+paleografia & pa*le*o*gra*fi*a \cmark & pa*le*o*gra*fi-a \xmark \\
 paleógrafo & pa*le-ó*gra*fo \xmark & pa*le*ó*gra*fo \cmark \\
+paleólogo & pa*le-ó*lo*go \xmark & pa*le*ó*lo*go \cmark \\
+paleontologia & pa*le*on*to*lo*gi*a \cmark & pa*le*on*to*lo*gi-a \xmark \\
+paleozoologia & pa*le*o*zo*o*lo*gi*a \cmark & pa*le*o*zo*o*lo*gi-a \xmark \\
 palinologia & pa*li*no*lo*gi*a \cmark & pa*li*no*lo*gi-a \xmark \\
@@
 pancadaria & pan*ca*da*ri*a \cmark & pan*ca*da*ri-a \xmark \\
+pancrácio & pan*crá*ci.o \xmark & pan*crá*cio \cmark \\
+pancreático & pan*cre-á*ti*co \xmark & pan*cre*á*ti*co \cmark \\
 pandemia & pan*de*mi*a \cmark & pan*de*mi-a \xmark \\
+pandemônio & pan*de-mô*ni.o \xmark & pan*de*mô*nio \cmark \\
+panenteísmo & pa*nen*te-ís*mo \xmark & pa*nen*te*ís*mo \cmark \\
 panfletário & pan*fle*tá*ri*o \cmark & pan*fle*tá*ri-o \xmark \\
+pangeia & pan*gei*a \cmark & pan*gei-a \xmark \\
+panô & pa-nô \xmark & pa*nô \cmark \\
+panóplia & pa*nó*pli.a \xmark & pa*nó*plia \cmark \\
+panspermia & pans*per*mi*a \cmark & pans*per*mi-a \xmark \\
 pantagruélico & pan*ta*gru-é*li*co \xmark & pan*ta*gru*é*li*co \cmark \\
+pantaleão & pan*ta*le-ão \xmark & pan*ta*le*ão \cmark \\
 panteão & pan*te-ão \xmark & pan*te*ão \cmark \\
@@
 papagaio & pa*pa*gai*o \cmark & pa*pa*gai-o \xmark \\
+papagueio & pa*pa*guei*o \cmark & pa*pa*guei-o \xmark \\
 papaia & pa*pai*a \cmark & pa*pai-a \xmark \\
+papaína & pa*pa-í*na \xmark & pa*pa*í*na \cmark \\
 papelaria & pa*pe*la*ri*a \cmark & pa*pe*la*ri-a \xmark \\
+papelório & pa*pe*ló*ri.o \xmark & pa*pe*ló*rio \cmark \\
 papua & pa*pu*a \cmark & pa*pu-a \xmark \\
+papuásio & pa*pu-á*si.o \xmark & pa*pu*á*sio \cmark \\
 paquímetro & pa-quí*me*tro \xmark & pa*quí*me*tro \cmark \\
@@
 paraíso & pa*ra-í*so \xmark & pa*ra*í*so \cmark \\
+paralipômenos & pa*ra*li-pô*me*nos \xmark & pa*ra*li*pô*me*nos \cmark \\
 paralisia & pa*ra*li*si*a \cmark & pa*ra*li*si-a \xmark \\
@@
 paraplegia & pa*ra*ple*gi*a \cmark & pa*ra*ple*gi-a \xmark \\
+parasitário & pa*ra*si*tá*ri.o \xmark & pa*ra*si*tá*rio \cmark \\
 parasitologia & pa*ra*si*to*lo*gi*a \cmark & pa*ra*si*to*lo*gi-a \xmark \\
 parceria & par*ce*ri*a \cmark & par*ce*ri-a \xmark \\
+parcimônia & par*ci-mô*ni.a \xmark & par*ci*mô*nia \cmark \\
+pareia & pa*rei*a \cmark & pa*rei-a \xmark \\
+parélio & pa*ré*li.o \xmark & pa*ré*lio \cmark \\
 páreo & pá*re.o \xmark & pá*reo \cmark \\
@@
 paritário & pa*ri*tá*ri*o \cmark & pa*ri*tá*ri-o \xmark \\
+parlamentário & par*la*men*tá*ri.o \xmark & par*la*men*tá*rio \cmark \\
+parlapatório & par*la*pa*tó*ri.o \xmark & par*la*pa*tó*rio \cmark \\
 parlatório & par*la*tó*ri.o \xmark & par*la*tó*rio \cmark \\
@@
 partidário & par*ti*dá*ri.o \xmark & par*ti*dá*rio \cmark \\
+partidocracia & par*ti*do*cra*ci*a \cmark & par*ti*do*cra*ci-a \xmark \\
 parusia & pa*ru*si*a \cmark & pa*ru*si-a \xmark \\
@@
 pastelaria & pas*te*la*ri*a \cmark & pas*te*la*ri-a \xmark \\
+pastifício & pas*ti*fí*ci.o \xmark & pas*ti*fí*cio \cmark \\
 pastoreio & pas*to*rei*o \cmark & pas*to*rei-o \xmark \\
+pastorícia & pas*to*rí*ci.a \xmark & pas*to*rí*cia \cmark \\
+patágio & pa*tá*gi.o \xmark & pa*tá*gio \cmark \\
+patauá & pa*tau-á \xmark & pa*tau*á \cmark \\
 patchuli & pat*chu*li \cmark & pat-chu*li \xmark \\
@@
 patrício & pa*trí*ci.o \xmark & pa*trí*cio \cmark \\
+patrimônio & pa*tri-mô*ni.o \xmark & pa*tri*mô*nio \cmark \\
 pátrio & pá*tri.o \xmark & pá*trio \cmark \\
@@
 patroa & pa*tro*a \cmark & pa*tro-a \xmark \\
+patrocínio & pa*tro*cí*ni*o \cmark & pa*tro*cí*ni-o \xmark \\
+patrologia & pa*tro*lo*gi*a \cmark & pa*tro*lo*gi-a \xmark \\
 patuá & pa*tu-á \xmark & pa*tu*á \cmark \\
 patuleia & pa*tu*lei*a \cmark & pa*tu*lei-a \xmark \\
+paulínia & pau*lí*ni.a \xmark & pau*lí*nia \cmark \\
 paul & pa-ul \xmark & pa-ul \xmark \\
+pavia & pa*vi*a \cmark & pa*vi-a \xmark \\
 pavio & pa*vi*o \cmark & pa*vi-o \xmark \\
@@
 pediátrico & pe*di-á*tri*co \xmark & pe*di*á*tri*co \cmark \\
+peditório & pe*di*tó*ri.o \xmark & pe*di*tó*rio \cmark \\
 pedofilia & pe*do*fi*li*a \cmark & pe*do*fi*li-a \xmark \\
@@
 pedraria & pe*dra*ri*a \cmark & pe*dra*ri-a \xmark \\
+pegomancia & pe*go*man*ci*a \cmark & pe*go*man*ci-a \xmark \\
 peia & pei*a \cmark & pei-a \xmark \\
 peixaria & pei*xa*ri*a \cmark & pei*xa*ri-a \xmark \\
+pelágio & pe*lá*gi.o \xmark & pe*lá*gio \cmark \\
 pelúcia & pe*lú*ci.a \xmark & pe*lú*cia \cmark \\
@@
 peneplanície & pe*ne*pla*ní*ci.e \xmark & pe*ne*pla*ní*cie \cmark \\
+penitência & pe*ni*tên*ci.a \xmark & pe*ni*tên*cia \cmark \\
+penitenciaria & pe*ni*ten*ci*a*ri*a \cmark & pe*ni*ten*ci*a*ri-a \xmark \\
 penitenciária & pe*ni*ten*ci-á*ri.a \xmark & pe*ni*ten*ci*á*ria \cmark \\
 penitenciário & pe*ni*ten*ci-á*ri.o \xmark & pe*ni*ten*ci*á*rio \cmark \\
+pensionário & pen*si*o*ná*ri.o \xmark & pen*si*o*ná*rio \cmark \\
+pentacampeão & pen*ta*cam*pe-ão \xmark & pen*ta*cam*pe*ão \cmark \\
 pentarquia & pen*tar*qui*a \cmark & pen*tar*qui-a \xmark \\
 penúria & pe*nú*ri.a \xmark & pe*nú*ria \cmark \\
+peoa & pe*o*a \cmark & pe*o-a \xmark \\
+peônia & pe-ô*ni.a \xmark & pe*ô*nia \cmark \\
+péon & pé-on \xmark & pé*on \cmark \\
+peptídeo & pep*tí*de.o \xmark & pep*tí*deo \cmark \\
+pequiá & pe*qui-á \xmark & pe*qui*á \cmark \\
+percuciência & per*cu*ci*ên*ci.a \xmark & per*cu*ci*ên*cia \cmark \\
+percutâneo & per*cu*tâ*ne.o \xmark & per*cu*tâ*neo \cmark \\
 perdoável & per*do-á*vel \xmark & per*do*á*vel \cmark \\
 perdulário & per*du*lá*ri.o \xmark & per*du*lá*rio \cmark \\
+peremptório & pe*remp*tó*ri.o \xmark & pe*remp*tó*rio \cmark \\
+perenifólio & pe*re*ni*fó*li.o \xmark & pe*re*ni*fó*lio \cmark \\
+perequê & pe*re-quê \xmark & pe*re*quê \cmark \\
 perfídia & per*fí*di.a \xmark & per*fí*dia \cmark \\
 perfumaria & per*fu*ma*ri*a \cmark & per*fu*ma*ri-a \xmark \\
+pericárdio & pe*ri*cár*di.o \xmark & pe*ri*cár*dio \cmark \\
 perícia & pe*rí*ci.a \xmark & pe*rí*cia \cmark \\
+pericôndrio & pe*ri-côn*dri.o \xmark & pe*ri*côn*drio \cmark \\
 periélio & pe*ri-é*li.o \xmark & pe*ri*é*lio \cmark \\
 periferia & pe*ri*fe*ri*a \cmark & pe*ri*fe*ri-a \xmark \\
+perigônio & pe*ri-gô*ni.o \xmark & pe*ri*gô*nio \cmark \\
 períneo & pe*rí*ne.o \xmark & pe*rí*neo \cmark \\
@@
 período & pe*rí-o*do \xmark & pe*rí*o*do \cmark \\
+periósteo & pe*ri-ós*te.o \xmark & pe*ri*ós*teo \cmark \\
 peripécia & pe*ri*pé*ci.a \xmark & pe*ri*pé*cia \cmark \\
@@
 periurbano & pe*ri-ur*ba*no \xmark & pe*ri*ur*ba*no \cmark \\
+perlocucionário & per*lo*cu*ci*o*ná*ri.o \xmark & per*lo*cu*ci*o*ná*rio \cmark \\
+permanência & per*ma*nên*ci.a \xmark & per*ma*nên*cia \cmark \\
 permeável & per*me-á*vel \xmark & per*me*á*vel \cmark \\
 permeio & per*mei*o \cmark & per*mei-o \xmark \\
+permissionário & per*mis*si*o*ná*ri.o \xmark & per*mis*si*o*ná*rio \cmark \\
+perpétua & per*pé*tu.a \xmark & per*pé*tua \cmark \\
+persecutório & per*se*cu*tó*ri.o \xmark & per*se*cu*tó*rio \cmark \\
+persicária & per*si*cá*ri.a \xmark & per*si*cá*ria \cmark \\
 pérsio & pér*si.o \xmark & pér*sio \cmark \\
 persistência & per*sis*tên*ci.a \xmark & per*sis*tên*cia \cmark \\
+perspicácia & pers*pi*cá*ci.a \xmark & pers*pi*cá*cia \cmark \\
 pertinácia & per*ti*ná*ci.a \xmark & per*ti*ná*cia \cmark \\
@@
 pescaria & pes*ca*ri*a \cmark & pes*ca*ri-a \xmark \\
+pessário & pes*sá*ri.o \xmark & pes*sá*rio \cmark \\
 pessoa & pes*so*a \cmark & pes*so-a \xmark \\
 pestilência & pes*ti*lên*ci.a \xmark & pes*ti*lên*cia \cmark \\
+peticionário & pe*ti*ci*o*ná*ri.o \xmark & pe*ti*ci*o*ná*rio \cmark \\
 pétreo & pé*tre.o \xmark & pé*treo \cmark \\
+petrografia & pe*tro*gra*fi*a \cmark & pe*tro*gra*fi-a \xmark \\
 petróleo & pe*tró*le.o \xmark & pe*tró*leo \cmark \\
@@
 picardia & pi*car*di*a \cmark & pi*car*di-a \xmark \\
+picaria & pi*ca*ri*a \cmark & pi*ca*ri-a \xmark \\
 pictografia & pic*to*gra*fi*a \cmark & pic*to*gra*fi-a \xmark \\
+picuá & pi*cu-á \xmark & pi*cu*á \cmark \\
 picuinha & pi*cu-i*nha \xmark & pi*cu*i*nha \cmark \\
 piério & pi-é*ri.o \xmark & pi*é*rio \cmark \\
+píer & pí-er \xmark & pí*er \cmark \\
 pífio & pí*fi*o \cmark & pí*fi-o \xmark \\
@@
 pintainho & pin*ta-i*nho \xmark & pin*ta*i*nho \cmark \\
+píon & pí-on \xmark & pí*on \cmark \\
 pio & pi*o \cmark & pi-o \xmark \\
+piquê & pi-quê \xmark & pi*quê \cmark \\
 piraí & pi*ra-í \xmark & pi*ra*í \cmark \\
 pirataria & pi*ra*ta*ri*a \cmark & pi*ra*ta*ri-a \xmark \\
+pirelióforo & pi*re*li-ó*fo*ro \xmark & pi*re*li*ó*fo*ro \cmark \\
 piromancia & pi*ro*man*ci*a \cmark & pi*ro*man*ci-a \xmark \\
@@
 piromania & pi*ro*ma*ni*a \cmark & pi*ro*ma*ni-a \xmark \\
+pirômetro & pi-rô*me*tro \xmark & pi*rô*me*tro \cmark \\
 pirotecnia & pi*ro*tec*ni*a \cmark & pi*ro*tec*ni-a \xmark \\
@@
 piscatória & pis*ca*tó*ri.a \xmark & pis*ca*tó*ria \cmark \\
+piscatório & pis*ca*tó*ri.o \xmark & pis*ca*tó*rio \cmark \\
 pisoteio & pi*so*tei*o \cmark & pi*so*tei-o \xmark \\
+pítia & pí*ti.a \xmark & pí*tia \cmark \\
 pitiríase & pi*ti*rí-a*se \xmark & pi*ti*rí*a*se \cmark \\
 pium & pi-um \xmark & pi*um \cmark \\
+piúria & pi-ú*ri.a \xmark & pi*ú*ria \cmark \\
 pivô & pi-vô \xmark & pi*vô \cmark \\
 pixaim & pi*xa-im \xmark & pi*xa-im \xmark \\
+pizaria & pi*za*ri*a \cmark & pi*za*ri-a \xmark \\
 pizzaria & piz*za*ri*a \cmark & piz*za*ri-a \xmark \\
+placentário & pla*cen*tá*ri.o \xmark & pla*cen*tá*rio \cmark \\
 plagiário & pla*gi-á*ri.o \xmark & pla*gi*á*rio \cmark \\
+plagioclásio & pla*gi*o*clá*si.o \xmark & pla*gi*o*clá*sio \cmark \\
 plágio & plá*gi.o \xmark & plá*gio \cmark \\
+planctônico & planc-tô*ni*co \xmark & planc*tô*ni*co \cmark \\
 planetário & pla*ne*tá*ri.o \xmark & pla*ne*tá*rio \cmark \\
 planície & pla*ní*ci.e \xmark & pla*ní*cie \cmark \\
+planimetria & pla*ni*me*tri*a \cmark & pla*ni*me*tri-a \xmark \\
+planisfério & pla*nis*fé*ri.o \xmark & pla*nis*fé*rio \cmark \\
 plantio & plan*ti*o \cmark & plan*ti-o \xmark \\
+plasmódio & plas*mó*di.o \xmark & plas*mó*dio \cmark \\
 plateia & pla*tei*a \cmark & pla*tei-a \xmark \\
@@
 plebeísmo & ple*be-ís*mo \xmark & ple*be*ís*mo \cmark \\
+pleiotropia & plei*o*tro*pi*a \cmark & plei*o*tro*pi-a \xmark \\
 plenário & ple*ná*ri.o \xmark & ple*ná*rio \cmark \\
 plenilúnio & ple*ni*lú*ni.o \xmark & ple*ni*lú*nio \cmark \\
+plenipotenciário & ple*ni*po*ten*ci-á*ri.o \xmark & ple*ni*po*ten*ci*á*rio \cmark \\
 pleurisia & pleu*ri*si*a \cmark & pleu*ri*si-a \xmark \\
 plúmbeo & plúm*be.o \xmark & plúm*beo \cmark \\
+pluripartidário & plu*ri*par*ti*dá*ri.o \xmark & plu*ri*par*ti*dá*rio \cmark \\
 plutocracia & plu*to*cra*ci*a \cmark & plu*to*cra*ci-a \xmark \\
+plutônio & plu-tô*ni.o \xmark & plu*tô*nio \cmark \\
 pluviometria & plu*vi*o*me*tri*a \cmark & plu*vi*o*me*tri-a \xmark \\
+plúvio & plú*vi.o \xmark & plú*vio \cmark \\
+pneuma & p.neu*ma \xmark & pneu*ma \cmark \\
 pneumática & p.neu*má*ti*ca \xmark & pneu*má*ti*ca \cmark \\
@@
 pneumologia & p.neu*mo*lo*gi*a \xmark & pneu*mo*lo*gi-a \xmark \\
+pneumologista & p.neu*mo*lo*gis*ta \xmark & pneu*mo*lo*gis*ta \cmark \\
 pneumonia & p.neu*mo*ni*a \xmark & pneu*mo*ni-a \xmark \\
 pneumônico & p.neu-mô*ni*co \xmark & pneu*mô*ni*co \cmark \\
+pneumonite & p.neu*mo*ni*te \xmark & pneu*mo*ni*te \cmark \\
 pneumotórax & p.neu*mo*tó*rax \xmark & pneu*mo*tó*rax \cmark \\
 pneu & p.neu \xmark & pneu \cmark \\
+poaia & po*ai*a \cmark & po*ai-a \xmark \\
+poa & po*a \cmark & po-a \xmark \\
+poá & po-á \xmark & po*á \cmark \\
 poderio & po*de*ri*o \cmark & po*de*ri-o \xmark \\
@@
 poio & poi*o \cmark & poi-o \xmark \\
+polarimetria & po*la*ri*me*tri*a \cmark & po*la*ri*me*tri-a \xmark \\
 poliandria & po*li*an*dri*a \cmark & po*li*an*dri-a \xmark \\
@@
 policromia & po*li*cro*mi*a \cmark & po*li*cro*mi-a \xmark \\
+polidactilia & po*li*dac*ti*li*a \cmark & po*li*dac*ti*li-a \xmark \\
 polidipsia & po*li*dip*si*a \cmark & po*li*dip*si-a \xmark \\
@@
 poliginia & po*li*gi*ni*a \cmark & po*li*gi*ni-a \xmark \\
+polimatia & po*li*ma*ti*a \cmark & po*li*ma*ti-a \xmark \\
 polimorfia & po*li*mor*fi*a \cmark & po*li*mor*fi-a \xmark \\
+polinésio & po*li*né*si.o \xmark & po*li*né*sio \cmark \\
+polinômio & po*li-nô*mi.o \xmark & po*li*nô*mio \cmark \\
+pólio & pó*li.o \xmark & pó*lio \cmark \\
 poliploidia & po*li*ploi*di*a \cmark & po*li*ploi*di-a \xmark \\
@@
 polissemia & po*lis*se*mi*a \cmark & po*lis*se*mi-a \xmark \\
+polissonografia & po*lis*so*no*gra*fi*a \cmark & po*lis*so*no*gra*fi-a \xmark \\
 politeísmo & po*li*te-ís*mo \xmark & po*li*te*ís*mo \cmark \\
 politeísta & po*li*te-ís*ta \xmark & po*li*te*ís*ta \cmark \\
+politiquês & po*li*ti-quês \xmark & po*li*ti*quês \cmark \\
+poliuretano & po*li-u*re*ta*no \xmark & po*li*u*re*ta*no \cmark \\
 poliúria & po*li-ú*ri.a \xmark & po*li*ú*ria \cmark \\
+polivalência & po*li*va*lên*ci.a \xmark & po*li*va*lên*cia \cmark \\
+polônio & po-lô*ni.o \xmark & po*lô*nio \cmark \\
+poluição & po*lu-i*ção \xmark & po*lu*i*ção \cmark \\
+poluidor & po*lu-i*dor \xmark & po*lu-i*dor \xmark \\
 poluir & po*lu-ir \xmark & po*lu*ir \cmark \\
+pomologia & po*mo*lo*gi*a \cmark & po*mo*lo*gi-a \xmark \\
 pontaria & pon*ta*ri*a \cmark & pon*ta*ri-a \xmark \\
 pontifício & pon*ti*fí*ci.o \xmark & pon*ti*fí*cio \cmark \\
+poplíteo & po*plí*te.o \xmark & po*plí*teo \cmark \\
 poraquê & po*ra-quê \xmark & po*ra*quê \cmark \\
 porcaria & por*ca*ri*a \cmark & por*ca*ri-a \xmark \\
+porciúncula & por*ci-ún*cu*la \xmark & por*ci*ún*cu*la \cmark \\
 porfia & por*fi*a \cmark & por*fi-a \xmark \\
+porfiria & por*fi*ri*a \cmark & por*fi*ri-a \xmark \\
 pornografia & por*no*gra*fi*a \cmark & por*no*gra*fi-a \xmark \\
@@
 possuir & pos*su-ir \xmark & pos*su*ir \cmark \\
+postectomia & pos*tec*to*mi*a \cmark & pos*tec*to*mi-a \xmark \\
 potássio & po*tás*si.o \xmark & po*tás*sio \cmark \\
@@
 pousio & pou*si*o \cmark & pou*si-o \xmark \\
+póvoa & pó*vo.a \xmark & pó*voa \cmark \\
 pradaria & pra*da*ri*a \cmark & pra*da*ri-a \xmark \\
@@
 precário & pre*cá*ri.o \xmark & pre*cá*rio \cmark \\
+precatória & pre*ca*tó*ri.a \xmark & pre*ca*tó*ria \cmark \\
 precatório & pre*ca*tó*ri.o \xmark & pre*ca*tó*rio \cmark \\
+precedência & pre*ce*dên*ci.a \xmark & pre*ce*dên*cia \cmark \\
+precipício & pre*ci*pí*ci.o \xmark & pre*ci*pí*cio \cmark \\
 precípuo & pre*cí*pu.o \xmark & pre*cí*puo \cmark \\
+predatório & pre*da*tó*ri.o \xmark & pre*da*tó*rio \cmark \\
+prédio & pré*di.o \xmark & pré*dio \cmark \\
 predominância & pre*do*mi*nân*ci.a \xmark & pre*do*mi*nân*cia \cmark \\
@@
 preênsil & pre-ên*sil \xmark & pre*ên*sil \cmark \\
+preexistência & pre*e*xis*tên*ci.a \xmark & pre*e*xis*tên*cia \cmark \\
 prefácio & pre*fá*ci.o \xmark & pre*fá*cio \cmark \\
 preferência & pre*fe*rên*ci.a \xmark & pre*fe*rên*cia \cmark \\
+pregaria & pre*ga*ri*a \cmark & pre*ga*ri-a \xmark \\
+pregnância & preg*nân*ci.a \xmark & preg*nân*cia \cmark \\
 preia & prei*a \cmark & prei-a \xmark \\
 prejuízo & pre*ju-í*zo \xmark & pre*ju*í*zo \cmark \\
+prelatício & pre*la*tí*ci.o \xmark & pre*la*tí*cio \cmark \\
 prelazia & pre*la*zi*a \cmark & pre*la*zi-a \xmark \\
@@
 prelúdio & pre*lú*di.o \xmark & pre*lú*dio \cmark \\
+premência & pre*mên*ci.a \xmark & pre*mên*cia \cmark \\
+premonitório & pre*mo*ni*tó*ri.o \xmark & pre*mo*ni*tó*rio \cmark \\
 prenúncio & pre*nún*ci.o \xmark & pre*nún*cio \cmark \\
@@
 prepotência & pre*po*tên*ci.a \xmark & pre*po*tên*cia \cmark \\
+prepúcio & pre*pú*ci.o \xmark & pre*pú*cio \cmark \\
 presbiopia & pres*bi*o*pi*a \cmark & pres*bi*o*pi-a \xmark \\
@@
 presidenciável & pre*si*den*ci-á*vel \xmark & pre*si*den*ci*á*vel \cmark \\
+presidiário & pre*si*di-á*ri.o \xmark & pre*si*di*á*rio \cmark \\
+presídio & pre*sí*di.o \xmark & pre*sí*dio \cmark \\
 presságio & pres*sá*gi.o \xmark & pres*sá*gio \cmark \\
 prestígio & pres*tí*gi.o \xmark & pres*tí*gio \cmark \\
+presúria & pre*sú*ri.a \xmark & pre*sú*ria \cmark \\
 pretoria & pre*to*ri*a \cmark & pre*to*ri-a \xmark \\
 pretório & pre*tó*ri.o \xmark & pre*tó*rio \cmark \\
+prevalência & pre*va*lên*ci.a \xmark & pre*va*lên*cia \cmark \\
+preventório & pre*ven*tó*ri.o \xmark & pre*ven*tó*rio \cmark \\
 previdenciário & pre*vi*den*ci-á*ri.o \xmark & pre*vi*den*ci*á*rio \cmark \\
 prévio & pré*vi.o \xmark & pré*vio \cmark \\
+priápico & pri-á*pi*co \xmark & pri*á*pi*co \cmark \\
+primária & pri*má*ri.a \xmark & pri*má*ria \cmark \\
 primário & pri*má*ri.o \xmark & pri*má*rio \cmark \\
@@
 primazia & pri*ma*zi*a \cmark & pri*ma*zi-a \xmark \\
+primicério & pri*mi*cé*ri.o \xmark & pri*mi*cé*rio \cmark \\
 primórdio & pri*mór*di.o \xmark & pri*mór*dio \cmark \\
 princípio & prin*cí*pi.o \xmark & prin*cí*pio \cmark \\
+príon & prí-on \xmark & prí*on \cmark \\
 prioritário & pri*o*ri*tá*ri.o \xmark & pri*o*ri*tá*rio \cmark \\
@@
 proa & pro*a \cmark & pro-a \xmark \\
+probatório & pro*ba*tó*ri.o \xmark & pro*ba*tó*rio \cmark \\
 procaína & pro*ca-í*na \xmark & pro*ca*í*na \cmark \\
 procariótico & pro*ca*ri-ó*ti*co \xmark & pro*ca*ri*ó*ti*co \cmark \\
+procedência & pro*ce*dên*ci.a \xmark & pro*ce*dên*cia \cmark \\
+procônsul & pro-côn*sul \xmark & pro*côn*sul \cmark \\
 proctologia & proc*to*lo*gi*a \cmark & proc*to*lo*gi-a \xmark \\
@@
 proeminência & pro*e*mi*nên*ci.a \xmark & pro*e*mi*nên*cia \cmark \\
+proêmio & pro-ê*mi.o \xmark & pro*ê*mio \cmark \\
 profecia & pro*fe*ci*a \cmark & pro*fe*ci-a \xmark \\
@@
 profilaxia & pro*fi*la*xi*a \cmark & pro*fi*la*xi-a \xmark \\
+progênie & pro*gê*ni.e \xmark & pro*gê*nie \cmark \\
+proibição & pro-i*bi*ção \xmark & pro*i*bi*ção \cmark \\
+proibido & pro-i*bi*do \xmark & pro*i*bi*do \cmark \\
+proibir & pro-i*bir \xmark & pro*i*bir \cmark \\
+proibitivo & pro-i*bi*ti*vo \xmark & pro*i*bi*ti*vo \cmark \\
 prolegômenos & pro*le-gô*me*nos \xmark & pro*le*gô*me*nos \cmark \\
 proletário & pro*le*tá*ri.o \xmark & pro*le*tá*rio \cmark \\
+promécio & pro*mé*ci.o \xmark & pro*mé*cio \cmark \\
+promissória & pro*mis*só*ri.a \xmark & pro*mis*só*ria \cmark \\
 promontório & pro*mon*tó*ri.o \xmark & pro*mon*tó*rio \cmark \\
 promotoria & pro*mo*to*ri*a \cmark & pro*mo*to*ri-a \xmark \\
+prontuário & pron*tu-á*ri.o \xmark & pron*tu*á*rio \cmark \\
 pronúncia & pro*nún*ci.a \xmark & pro*nún*cia \cmark \\
+pronunciável & pro*nun*ci-á*vel \xmark & pro*nun*ci*á*vel \cmark \\
+propiciatório & pro*pi*ci*a*tó*ri.o \xmark & pro*pi*ci*a*tó*rio \cmark \\
 propício & pro*pí*ci.o \xmark & pro*pí*cio \cmark \\
@@
 prosaísmo & pro*sa-ís*mo \xmark & pro*sa*ís*mo \cmark \\
+proscênio & pros*cê*ni.o \xmark & pros*cê*nio \cmark \\
 prosódia & pro*só*di.a \xmark & pro*só*dia \cmark \\
 prosopagnosia & pro*so*pag*no*si*a \cmark & pro*so*pag*no*si-a \xmark \\
+prosopografia & pro*so*po*gra*fi*a \cmark & pro*so*po*gra*fi-a \xmark \\
 prosopopeia & pro*so*po*pei*a \cmark & pro*so*po*pei-a \xmark \\
@@
 prostituição & pros*ti*tu-i*ção \xmark & pros*ti*tu*i*ção \cmark \\
+prostituído & pros*ti*tu-í*do \xmark & pros*ti*tu*í*do \cmark \\
 prostituir & pros*ti*tu-ir \xmark & pros*ti*tu*ir \cmark \\
@@
 protofonia & pro*to*fo*ni*a \cmark & pro*to*fo*ni-a \xmark \\
+protoginia & pro*to*gi*ni*a \cmark & pro*to*gi*ni-a \xmark \\
+protonotário & pro*to*no*tá*ri.o \xmark & pro*to*no*tá*rio \cmark \\
 protozoário & pro*to*zo-á*ri.o \xmark & pro*to*zo*á*rio \cmark \\
+protozoologia & pro*to*zo*o*lo*gi*a \cmark & pro*to*zo*o*lo*gi-a \xmark \\
 protuberância & pro*tu*be*rân*ci.a \xmark & pro*tu*be*rân*cia \cmark \\
 provedoria & pro*ve*do*ri*a \cmark & pro*ve*do*ri-a \xmark \\
+proveniência & pro*ve*ni*ên*ci.a \xmark & pro*ve*ni*ên*cia \cmark \\
 provérbio & pro*vér*bi.o \xmark & pro*vér*bio \cmark \\
@@
 prudência & pru*dên*ci.a \xmark & pru*dên*cia \cmark \\
+pseudociência & p.seu*do*ci*ên*ci.a \xmark & pseu*do*ci*ên*cia \cmark \\
+pseudocientífico & p.seu*do*ci*en*tí*fi*co \xmark & pseu*do*ci*en*tí*fi*co \cmark \\
+pseudofruto & p.seu*do*fru*to \xmark & pseu*do*fru*to \cmark \\
 pseudônimo & p.seu-dô*ni*mo \xmark & pseu*dô*ni*mo \cmark \\
+psicadélico & p.si*ca*dé*li*co \xmark & psi*ca*dé*li*co \cmark \\
 psicanálise & p.si*ca*ná*li*se \xmark & psi*ca*ná*li*se \cmark \\
@@
 psicanalítico & p.si*ca*na*lí*ti*co \xmark & psi*ca*na*lí*ti*co \cmark \\
+psicoativo & p.si*co*a*ti*vo \xmark & psi*co*a*ti*vo \cmark \\
+psicocirurgia & p.si*co*ci*rur*gi*a \xmark & psi*co*ci*rur*gi-a \xmark \\
+psicodélico & p.si*co*dé*li*co \xmark & psi*co*dé*li*co \cmark \\
+psicodelismo & p.si*co*de*lis*mo \xmark & psi*co*de*lis*mo \cmark \\
 psicodrama & p.si*co*dra*ma \xmark & psi*co*dra*ma \cmark \\
+psicofarmacologia & p.si*co*far*ma*co*lo*gi*a \xmark & psi*co*far*ma*co*lo*gi-a \xmark \\
+psicofísico & p.si*co*fí*si*co \xmark & psi*co*fí*si*co \cmark \\
+psicofisiologia & p.si*co*fi*si*o*lo*gi*a \xmark & psi*co*fi*si*o*lo*gi-a \xmark \\
+psicofonia & p.si*co*fo*ni*a \xmark & psi*co*fo*ni-a \xmark \\
 psicografia & p.si*co*gra*fi*a \xmark & psi*co*gra*fi-a \xmark \\
@@
 psicolinguista & p.si*co*lin*guis*ta \xmark & psi*co*lin*guis*ta \cmark \\
+psicolinguística & p.si*co*lin*guís*ti*ca \xmark & psi*co*lin*guís*ti*ca \cmark \\
 psicologia & p.si*co*lo*gi*a \xmark & psi*co*lo*gi-a \xmark \\
@@
 psicólogo & p.si*có*lo*go \xmark & psi*có*lo*go \cmark \\
+psicometria & p.si*co*me*tri*a \xmark & psi*co*me*tri-a \xmark \\
 psicométrico & p.si*co*mé*tri*co \xmark & psi*co*mé*tri*co \cmark \\
@@
 psicomotricidade & p.si*co*mo*tri*ci*da*de \xmark & psi*co*mo*tri*ci*da*de \cmark \\
+psicomotricista & p.si*co*mo*tri*cis*ta \xmark & psi*co*mo*tri*cis*ta \cmark \\
 psicopata & p.si*co*pa*ta \xmark & psi*co*pa*ta \cmark \\
+psicopatia & p.si*co*pa*ti*a \xmark & psi*co*pa*ti-a \xmark \\
 psicopático & p.si*co*pá*ti*co \xmark & psi*co*pá*ti*co \cmark \\
@@
 psicopedagogo & p.si*co*pe*da*go*go \xmark & psi*co*pe*da*go*go \cmark \\
+psicopompo & p.si*co*pom*po \xmark & psi*co*pom*po \cmark \\
+psicoprofilaxia & p.si*co*pro*fi*la*xi*a \xmark & psi*co*pro*fi*la*xi-a \xmark \\
 psicose & p.si*co*se \xmark & psi*co*se \cmark \\
 psicossexual & p.si*cos*se*xu*al \xmark & psi*cos*se*xu*al \cmark \\
+psicossomática & p.si*cos*so*má*ti*ca \xmark & psi*cos*so*má*ti*ca \cmark \\
 psicossomático & p.si*cos*so*má*ti*co \xmark & psi*cos*so*má*ti*co \cmark \\
@@
 psicoterapeuta & p.si*co*te*ra*peu*ta \xmark & psi*co*te*ra*peu*ta \cmark \\
+psicoterapêutico & p.si*co*te*ra*pêu*ti*co \xmark & psi*co*te*ra*pêu*ti*co \cmark \\
 psicoterapia & p.si*co*te*ra*pi*a \xmark & psi*co*te*ra*pi-a \xmark \\
@@
 psique & p.si*que \xmark & psi*que \cmark \\
+psiquê & p.si-quê \xmark & psi*quê \cmark \\
 psiquiatra & p.si*qui*a*tra \xmark & psi*qui*a*tra \cmark \\
@@
 psoríase & p.so*rí-a*se \xmark & p.so*rí*a*se \xmark \\
+pterígio & p.te*rí*gi.o \xmark & pte*rí*gio \cmark \\
+pterodáctilo & p.te*ro*dác*ti*lo \xmark & pte*ro*dác*ti*lo \cmark \\
 pterossauro & p.te*ros*sau*ro \xmark & pte*ros*sau*ro \cmark \\
+ptialina & p.ti*a*li*na \xmark & pti*a*li*na \cmark \\
+ptolemaico & p.to*le*mai*co \xmark & pto*le*mai*co \cmark \\
 ptose & p.to*se \xmark & pto*se \cmark \\
@@
 pudicícia & pu*di*cí*ci.a \xmark & pu*di*cí*cia \cmark \\
+puerpério & pu*er*pé*ri.o \xmark & pu*er*pé*rio \cmark \\
+puído & pu-í*do \xmark & pu*í*do \cmark \\
 pulôver & pu-lô*ver \xmark & pu*lô*ver \cmark \\
+pungência & pun*gên*ci.a \xmark & pun*gên*cia \cmark \\
 purgatório & pur*ga*tó*ri.o \xmark & pur*ga*tó*rio \cmark \\
+purificatório & pu*ri*fi*ca*tó*ri.o \xmark & pu*ri*fi*ca*tó*rio \cmark \\
+purpúreo & pur*pú*re.o \xmark & pur*pú*reo \cmark \\
+putaria & pu*ta*ri*a \cmark & pu*ta*ri-a \xmark \\
+putrião & pu*tri-ão \xmark & pu*tri*ão \cmark \\
 quadricromia & qua*dri*cro*mi*a \cmark & qua*dri*cro*mi-a \xmark \\
+quadriênio & qua*dri*ê*ni.o \xmark & qua*dri*ê*nio \cmark \\
+quadrifólio & qua*dri*fó*li.o \xmark & qua*dri*fó*lio \cmark \\
 quadringentenário & qua*drin*gen*te*ná*ri.o \xmark & qua*drin*gen*te*ná*rio \cmark \\
@@
 quaternário & qua*ter*ná*ri.o \xmark & qua*ter*ná*rio \cmark \\
+quaternião & qua*ter*ni-ão \xmark & qua*ter*ni*ão \cmark \\
+quatriênio & qua*tri*ê*ni.o \xmark & qua*tri*ê*nio \cmark \\
 quéchua & qué*chu*a \cmark & qué*chu-a \xmark \\
 queijaria & quei*ja*ri*a \cmark & quei*ja*ri-a \xmark \\
+querência & que*rên*ci.a \xmark & que*rên*cia \cmark \\
 questionário & ques*ti*o*ná*ri.o \xmark & ques*ti*o*ná*rio \cmark \\
 questiúncula & ques*ti-ún*cu*la \xmark & ques*ti*ún*cu*la \cmark \\
+quiáltera & qui-ál*te*ra \xmark & qui*ál*te*ra \cmark \\
 quíchua & quí*chu.a \xmark & quí*chua \cmark \\
+quilohertz & qui*lo-hertz \xmark & qui*lo-hertz \xmark \\
 quilômetro & qui-lô*me*tro \xmark & qui*lô*me*tro \cmark \\
 quilowatt & qui*lo-watt \xmark & qui*lo-watt \xmark \\
+quimiotaxia & qui*mi*o*ta*xi*a \cmark & qui*mi*o*ta*xi-a \xmark \\
 quimioterapia & qui*mi*o*te*ra*pi*a \cmark & qui*mi*o*te*ra*pi-a \xmark \\
@@
 quinquilharia & quin*qui*lha*ri*a \cmark & quin*qui*lha*ri-a \xmark \\
+quintessência & quin*tes*sên*ci.a \xmark & quin*tes*sên*cia \cmark \\
+quintílio & quin*tí*li.o \xmark & quin*tí*lio \cmark \\
+quinzenário & quin*ze*ná*ri.o \xmark & quin*ze*ná*rio \cmark \\
 quiproquó & qui*pro-quó \xmark & qui*pro*quó \cmark \\
 quiromancia & qui*ro*man*ci*a \cmark & qui*ro*man*ci-a \xmark \\
+quiropraxia & qui*ro*pra*xi*a \cmark & qui*ro*pra*xi-a \xmark \\
 raciocínio & ra*ci*o*cí*ni.o \xmark & ra*ci*o*cí*nio \cmark \\
+radiância & ra*di*ân*ci.a \xmark & ra*di*ân*cia \cmark \\
 radiestesia & ra*di*es*te*si*a \cmark & ra*di*es*te*si-a \xmark \\
+radioastronomia & ra*di*o*as*tro*no*mi*a \cmark & ra*di*o*as*tro*no*mi-a \xmark \\
+radiobiologia & ra*di*o*bi*o*lo*gi*a \cmark & ra*di*o*bi*o*lo*gi-a \xmark \\
+radiofonia & ra*di*o*fo*ni*a \cmark & ra*di*o*fo*ni-a \xmark \\
+radiofrequência & ra*di*o*fre-quên*ci.a \xmark & ra*di*o*fre*quên*cia \cmark \\
+radiogoniometria & ra*di*o*go*ni*o*me*tri*a \cmark & ra*di*o*go*ni*o*me*tri-a \xmark \\
 radiografia & ra*di*o*gra*fi*a \cmark & ra*di*o*gra*fi-a \xmark \\
@@
 radiologia & ra*di*o*lo*gi*a \cmark & ra*di*o*lo*gi-a \xmark \\
+radiometria & ra*di*o*me*tri*a \cmark & ra*di*o*me*tri-a \xmark \\
+radionuclídeo & ra*di*o*nu*clí*de.o \xmark & ra*di*o*nu*clí*deo \cmark \\
+radioquímica & ra*di*o-quí*mi*ca \xmark & ra*di*o*quí*mi*ca \cmark \\
 rádio & rá*di.o \xmark & rá*dio \cmark \\
+radioscopia & ra*di*os*co*pi*a \cmark & ra*di*os*co*pi-a \xmark \\
+radiotelefonia & ra*di*o*te*le*fo*ni*a \cmark & ra*di*o*te*le*fo*ni-a \xmark \\
+radiotelegrafia & ra*di*o*te*le*gra*fi*a \cmark & ra*di*o*te*le*gra*fi-a \xmark \\
 radiotelescópio & ra*di*o*te*les*có*pi.o \xmark & ra*di*o*te*les*có*pio \cmark \\
@@
 raiz & ra-iz \xmark & ra*iz \cmark \\
+ralídeo & ra*lí*de.o \xmark & ra*lí*deo \cmark \\
 ramaria & ra*ma*ri*a \cmark & ra*ma*ri-a \xmark \\
@@
 rancharia & ran*cha*ri*a \cmark & ran*cha*ri-a \xmark \\
+râncio & rân*ci.o \xmark & rân*cio \cmark \\
 randômico & ran-dô*mi*co \xmark & ran*dô*mi*co \cmark \\
 rapsódia & rap*só*di.a \xmark & rap*só*dia \cmark \\
+raquianestesia & ra*qui*a*nes*te*si*a \cmark & ra*qui*a*nes*te*si-a \xmark \\
 raquítico & ra-quí*ti*co \xmark & ra*quí*ti*co \cmark \\
+rastreio & ras*trei*o \cmark & ras*trei-o \xmark \\
 rataria & ra*ta*ri*a \cmark & ra*ta*ri-a \xmark \\
@@
 razoável & ra*zo-á*vel \xmark & ra*zo*á*vel \cmark \\
+reacionário & re*a*ci*o*ná*ri.o \xmark & re*a*ci*o*ná*rio \cmark \\
 rebeldia & re*bel*di*a \cmark & re*bel*di-a \xmark \\
@@
 recair & re*ca-ir \xmark & re*ca*ir \cmark \\
+recebedoria & re*ce*be*do*ri*a \cmark & re*ce*be*do*ri-a \xmark \\
 receio & re*cei*o \cmark & re*cei-o \xmark \\
@@
 recheio & re*chei*o \cmark & re*chei-o \xmark \\
+reciário & re*ci-á*ri.o \xmark & re*ci*á*rio \cmark \\
 recôncavo & re-côn*ca*vo \xmark & re*côn*ca*vo \cmark \\
@@
 rédea & ré*de*a \cmark & ré*de-a \xmark \\
+redemoinho & re*de*mo-i*nho \xmark & re*de*mo*i*nho \cmark \\
 redistribuir & re*dis*tri*bu-ir \xmark & re*dis*tri*bu*ir \cmark \\
+redundância & re*dun*dân*ci.a \xmark & re*dun*dân*cia \cmark \\
 reengenharia & re*en*ge*nha*ri*a \cmark & re*en*ge*nha*ri-a \xmark \\
@@
 reenvio & re*en*vi*o \cmark & re*en*vi-o \xmark \\
+reequilíbrio & re*e*qui*lí*bri.o \xmark & re*e*qui*lí*brio \cmark \\
 refeitório & re*fei*tó*ri.o \xmark & re*fei*tó*rio \cmark \\
 referência & re*fe*rên*ci.a \xmark & re*fe*rên*cia \cmark \\
+referendário & re*fe*ren*dá*ri.o \xmark & re*fe*ren*dá*rio \cmark \\
 refinaria & re*fi*na*ri*a \cmark & re*fi*na*ri-a \xmark \\
 reflexologia & re*fle*xo*lo*gi*a \cmark & re*fle*xo*lo*gi-a \xmark \\
+reflexoterapia & re*fle*xo*te*ra*pi*a \cmark & re*fle*xo*te*ra*pi-a \xmark \\
 refluir & re*flu-ir \xmark & re*flu*ir \cmark \\
+reformatório & re*for*ma*tó*ri.o \xmark & re*for*ma*tó*rio \cmark \\
+refratário & re*fra*tá*ri.o \xmark & re*fra*tá*rio \cmark \\
+refrigério & re*fri*gé*ri.o \xmark & re*fri*gé*rio \cmark \\
 refúgio & re*fú*gi.o \xmark & re*fú*gio \cmark \\
+regadio & re*ga*di*o \cmark & re*ga*di-o \xmark \\
 regalia & re*ga*li*a \cmark & re*ga*li-a \xmark \\
@@
 régia & ré*gi.a \xmark & ré*gia \cmark \\
+regicídio & re*gi*cí*di.o \xmark & re*gi*cí*dio \cmark \\
 régio & ré*gi.o \xmark & ré*gio \cmark \\
@@
 reimpressão & re-im*pres*são \xmark & re*im*pres*são \cmark \\
+reimpresso & re-im*pres*so \xmark & re*im*pres*so \cmark \\
 reimprimir & re-im*pri*mir \xmark & re*im*pri*mir \cmark \\
@@
 reincorporação & re-in*cor*po*ra*ção \xmark & re*in*cor*po*ra*ção \cmark \\
+reincorporar & re-in*cor*po*rar \xmark & re*in*cor*po*rar \cmark \\
 reindexação & re-in*de*xa*ção \xmark & re-in*de*xa*ção \xmark \\
+reindexar & re-in*de*xar \xmark & re-in*de*xar \xmark \\
 reingressar & re-in*gres*sar \xmark & re*in*gres*sar \cmark \\
 reingresso & re-in*gres*so \xmark & re*in*gres*so \cmark \\
+reiniciar & re-i*ni*ci*ar \xmark & re-i*ni*ci*ar \xmark \\
+reinquirir & re-in*qui*rir \xmark & re-in*qui*rir \xmark \\
 reinscrever & re-ins*cre*ver \xmark & re*ins*cre*ver \cmark \\
@@
 reintegrar & re-in*te*grar \xmark & re*in*te*grar \cmark \\
+reinterpretação & re-in*ter*pre*ta*ção \xmark & re*in*ter*pre*ta*ção \cmark \\
+reinterpretar & re-in*ter*pre*tar \xmark & re*in*ter*pre*tar \cmark \\
 reintrodução & re-in*tro*du*ção \xmark & re*in*tro*du*ção \cmark \\
 reintroduzir & re-in*tro*du*zir \xmark & re*in*tro*du*zir \cmark \\
+reinvenção & re-in*ven*ção \xmark & re*in*ven*ção \cmark \\
 reinventar & re-in*ven*tar \xmark & re*in*ven*tar \cmark \\
 reinvestir & re-in*ves*tir \xmark & re*in*ves*tir \cmark \\
+reio & rei*o \cmark & rei-o \xmark \\
 reitoria & rei*to*ri*a \cmark & rei*to*ri-a \xmark \\
+reivindicatório & rei*vin*di*ca*tó*ri*o \cmark & rei*vin*di*ca*tó*ri-o \xmark \\
 relatoria & re*la*to*ri*a \cmark & re*la*to*ri-a \xmark \\
@@
 relógio & re*ló*gi.o \xmark & re*ló*gio \cmark \\
+relojoaria & re*lo*jo*a*ri*a \cmark & re*lo*jo*a*ri-a \xmark \\
 relutância & re*lu*tân*ci.a \xmark & re*lu*tân*cia \cmark \\
+remanência & re*ma*nên*ci.a \xmark & re*ma*nên*cia \cmark \\
+remediável & re*me*di-á*vel \xmark & re*me*di*á*vel \cmark \\
+remédio & re*mé*di.o \xmark & re*mé*dio \cmark \\
+remígio & re*mí*gi.o \xmark & re*mí*gio \cmark \\
 reminiscência & re*mi*nis*cên*ci.a \xmark & re*mi*nis*cên*cia \cmark \\
+remuneratório & re*mu*ne*ra*tó*ri.o \xmark & re*mu*ne*ra*tó*rio \cmark \\
+rênio & rê*ni.o \xmark & rê*nio \cmark \\
+renitência & re*ni*tên*ci.a \xmark & re*ni*tên*cia \cmark \\
 renúncia & re*nún*ci.a \xmark & re*nún*cia \cmark \\
+reologia & re*o*lo*gi*a \cmark & re*o*lo*gi-a \xmark \\
 repertório & re*per*tó*ri.o \xmark & re*per*tó*rio \cmark \\
@@
 respiratório & res*pi*ra*tó*ri.o \xmark & res*pi*ra*tó*rio \cmark \\
+responsório & res*pon*só*ri.o \xmark & res*pon*só*rio \cmark \\
 resquício & res-quí*ci.o \xmark & res*quí*cio \cmark \\
 ressonância & res*so*nân*ci.a \xmark & res*so*nân*cia \cmark \\
+ressurgência & res*sur*gên*ci.a \xmark & res*sur*gên*cia \cmark \\
 restituição & res*ti*tu-i*ção \xmark & res*ti*tu*i*ção \cmark \\
 restituir & res*ti*tu-ir \xmark & res*ti*tu*ir \cmark \\
+restituível & res*ti*tu-í*vel \xmark & res*ti*tu*í*vel \cmark \\
+retaliatório & re*ta*li*a*tó*ri.o \xmark & re*ta*li*a*tó*rio \cmark \\
 retardatário & re*tar*da*tá*ri.o \xmark & re*tar*da*tá*rio \cmark \\
 reticência & re*ti*cên*ci.a \xmark & re*ti*cên*cia \cmark \\
+retilíneo & re*ti*lí*ne.o \xmark & re*ti*lí*neo \cmark \\
 retinopatia & re*ti*no*pa*ti*a \cmark & re*ti*no*pa*ti-a \xmark \\
@@
 retribuir & re*tri*bu-ir \xmark & re*tri*bu*ir \cmark \\
+retrosaria & re*tro*sa*ri*a \cmark & re*tro*sa*ri-a \xmark \\
+retumbância & re*tum*bân*ci.a \xmark & re*tum*bân*cia \cmark \\
 reumatologia & reu*ma*to*lo*gi*a \cmark & reu*ma*to*lo*gi-a \xmark \\
 reunir & re-u*nir \xmark & re-u*nir \xmark \\
+reurbanização & re-ur*ba*ni*za*ção \xmark & re-ur*ba*ni*za*ção \xmark \\
 reurbanizar & re-ur*ba*ni*zar \xmark & re-ur*ba*ni*zar \xmark \\
+reutilizar & re-u*ti*li*zar \xmark & re-u*ti*li*zar \xmark \\
 revelia & re*ve*li*a \cmark & re*ve*li-a \xmark \\
 reverência & re*ve*rên*ci.a \xmark & re*ve*rên*cia \cmark \\
+revisório & re*vi*só*ri.o \xmark & re*vi*só*rio \cmark \\
+revivência & re*vi*vên*ci.a \xmark & re*vi*vên*cia \cmark \\
+revivescência & re*vi*ves*cên*ci.a \xmark & re*vi*ves*cên*cia \cmark \\
+revogatório & re*vo*ga*tó*ri.o \xmark & re*vo*ga*tó*rio \cmark \\
 revolucionário & re*vo*lu*ci*o*ná*ri.o \xmark & re*vo*lu*ci*o*ná*rio \cmark \\
@@
 rinoplastia & ri*no*plas*ti*a \cmark & ri*no*plas*ti-a \xmark \\
+rinorreia & ri*nor*rei*a \cmark & ri*nor*rei-a \xmark \\
+rinoscopia & ri*nos*co*pi*a \cmark & ri*nos*co*pi-a \xmark \\
 rio & ri*o \cmark & ri-o \xmark \\
+ritidoplastia & ri*ti*do*plas*ti*a \cmark & ri*ti*do*plas*ti-a \xmark \\
 robô & ro-bô \xmark & ro*bô \cmark \\
 rocio & ro*ci*o \cmark & ro*ci-o \xmark \\
+rócio & ró*ci.o \xmark & ró*cio \cmark \\
+rodamoinho & ro*da*mo-i*nho \xmark & ro*da*mo*i*nho \cmark \\
 rodeio & ro*dei*o \cmark & ro*dei-o \xmark \\
@@
 rodopio & ro*do*pi*o \cmark & ro*do*pi-o \xmark \\
+rodoviária & ro*do*vi-á*ri.a \xmark & ro*do*vi*á*ria \cmark \\
 rodoviário & ro*do*vi-á*ri.o \xmark & ro*do*vi*á*rio \cmark \\
 rodovia & ro*do*vi*a \cmark & ro*do*vi-a \xmark \\
+rogatória & ro*ga*tó*ri.a \xmark & ro*ga*tó*ria \cmark \\
 roído & ro-í*do \xmark & ro*í*do \cmark \\
@@
 rossio & ros*si*o \cmark & ros*si-o \xmark \\
+rotário & ro*tá*ri.o \xmark & ro*tá*rio \cmark \\
+rotatório & ro*ta*tó*ri.o \xmark & ro*ta*tó*rio \cmark \\
+rotisseria & ro*tis*se*ri*a \cmark & ro*tis*se*ri-a \xmark \\
 rouparia & rou*pa*ri*a \cmark & rou*pa*ri-a \xmark \\
@@
 rubéola & ru*bé-o*la \xmark & ru*bé*o*la \cmark \\
+rúbeo & rú*be.o \xmark & rú*beo \cmark \\
+rubiácea & ru*bi-á*ce.a \xmark & ru*bi*á*cea \cmark \\
 rubídio & ru*bí*di.o \xmark & ru*bí*dio \cmark \\
 rufião & ru*fi-ão \xmark & ru*fi*ão \cmark \\
+rúfio & rú*fi.o \xmark & rú*fio \cmark \\
 ruído & ru-í*do \xmark & ru*í*do \cmark \\
@@
 rupia & ru*pi*a \cmark & ru*pi-a \xmark \\
+rúpia & rú*pi.a \xmark & rú*pia \cmark \\
+russofilia & rus*so*fi*li*a \cmark & rus*so*fi*li-a \xmark \\
+russofobia & rus*so*fo*bi*a \cmark & rus*so*fo*bi-a \xmark \\
 rutênio & ru*tê*ni.o \xmark & ru*tê*nio \cmark \\
@@
 sabiá & sa*bi-á \xmark & sa*bi*á \cmark \\
+sábia & sá*bi.a \xmark & sá*bia \cmark \\
 sábio & sá*bi.o \xmark & sá*bio \cmark \\
+saboaria & sa*bo*a*ri*a \cmark & sa*bo*a*ri-a \xmark \\
 sacaria & sa*ca*ri*a \cmark & sa*ca*ri-a \xmark \\
@@
 sacristia & sa*cris*ti*a \cmark & sa*cris*ti-a \xmark \\
+sadio & sa*di*o \cmark & sa*di-o \xmark \\
+safaria & sa*fa*ri*a \cmark & sa*fa*ri-a \xmark \\
+sagitário & sa*gi*tá*ri.o \xmark & sa*gi*tá*rio \cmark \\
+saião & sai-ão \xmark & sai*ão \cmark \\
 saia & sai*a \cmark & sai-a \xmark \\
@@
 saído & sa-í*do \xmark & sa*í*do \cmark \\
+sainha & sa-i*nha \xmark & sa*i*nha \cmark \\
+sainte & sa-in*te \xmark & sa-in*te \xmark \\
 saio & sai*o \cmark & sai-o \xmark \\
+saíra & sa-í*ra \xmark & sa*í*ra \cmark \\
 sair & sa-ir \xmark & sa*ir \cmark \\
 saí & sa-í \xmark & sa*í \cmark \\
+salácia & sa*lá*ci.a \xmark & sa*lá*cia \cmark \\
 salafrário & sa*la*frá*ri.o \xmark & sa*la*frá*rio \cmark \\
@@
 saliência & sa*li*ên*ci.a \xmark & sa*li*ên*cia \cmark \\
+sálio & sá*li.o \xmark & sá*lio \cmark \\
 salmodia & sal*mo*di*a \cmark & sal*mo*di-a \xmark \\
@@
 salsicharia & sal*si*cha*ri*a \cmark & sal*si*cha*ri-a \xmark \\
+saltério & sal*té*ri.o \xmark & sal*té*rio \cmark \\
 samambaia & sa*mam*bai*a \cmark & sa*mam*bai-a \xmark \\
 samário & sa*má*ri.o \xmark & sa*má*rio \cmark \\
+samaúma & sa*ma-ú*ma \xmark & sa*ma*ú*ma \cmark \\
 sambaíba & sam*ba-í*ba \xmark & sam*ba*í*ba \cmark \\
+sanatório & sa*na*tó*ri.o \xmark & sa*na*tó*rio \cmark \\
 sandália & san*dá*li.a \xmark & san*dá*lia \cmark \\
+sandia & san*di*a \cmark & san*di-a \xmark \\
+sanduicheria & san*du-i*che*ri*a \xmark & san*du*i*che*ri-a \xmark \\
 sanduíche & san*du-í*che \xmark & san*du*í*che \cmark \\
 sangria & san*gri*a \cmark & san*gri-a \xmark \\
+sanguinária & san*gui*ná*ri.a \xmark & san*gui*ná*ria \cmark \\
 sanguinário & san*gui*ná*ri.o \xmark & san*gui*ná*rio \cmark \\
 sanguínea & san*guí*ne.a \xmark & san*guí*nea \cmark \\
+sanguíneo & san*guí*ne.o \xmark & san*guí*neo \cmark \\
 sanitário & sa*ni*tá*ri.o \xmark & sa*ni*tá*rio \cmark \\
@@
 saquê & sa-quê \xmark & sa*quê \cmark \\
+sardônica & sar-dô*ni*ca \xmark & sar*dô*ni*ca \cmark \\
 sardônico & sar-dô*ni*co \xmark & sar*dô*ni*co \cmark \\
+sartório & sar*tó*ri.o \xmark & sar*tó*rio \cmark \\
+saruê & sa*ru-ê \xmark & sa*ru*ê \cmark \\
 satiríase & sa*ti*rí-a*se \xmark & sa*ti*rí*a*se \cmark \\
@@
 saúva & sa-ú*va \xmark & sa*ú*va \cmark \\
+saxônico & sa-xô*ni*co \xmark & sa*xô*ni*co \cmark \\
+seabórgio & se*a*bór*gi.o \xmark & se*a*bór*gio \cmark \\
+sebáceo & se*bá*ce.o \xmark & se*bá*ceo \cmark \\
 sebastião & se*bas*ti-ão \xmark & se*bas*ti*ão \cmark \\
 seborreia & se*bor*rei*a \cmark & se*bor*rei-a \xmark \\
+sécia & sé*ci.a \xmark & sé*cia \cmark \\
 secretaria & se*cre*ta*ri*a \cmark & se*cre*ta*ri-a \xmark \\
@@
 selaria & se*la*ri*a \cmark & se*la*ri-a \xmark \\
+selênio & se*lê*ni.o \xmark & se*lê*nio \cmark \\
 selenografia & se*le*no*gra*fi*a \cmark & se*le*no*gra*fi-a \xmark \\
@@
 semiárido & se*mi-á*ri*do \xmark & se*mi*á*ri*do \cmark \\
+semicircunferência & se*mi*cir*cun*fe*rên*ci.a \xmark & se*mi*cir*cun*fe*rên*cia \cmark \\
 semicolcheia & se*mi*col*chei*a \cmark & se*mi*col*chei-a \xmark \\
@@
 semiologia & se*mi*o*lo*gi*a \cmark & se*mi*o*lo*gi-a \xmark \\
+semiólogo & se*mi-ó*lo*go \xmark & se*mi*ó*lo*go \cmark \\
+semiótica & se*mi-ó*ti*ca \xmark & se*mi*ó*ti*ca \cmark \\
+semiótico & se*mi-ó*ti*co \xmark & se*mi*ó*ti*co \cmark \\
+semipermeável & se*mi*per*me-á*vel \xmark & se*mi*per*me*á*vel \cmark \\
 senescência & se*nes*cên*ci.a \xmark & se*nes*cên*cia \cmark \\
@@
 sensaboria & sen*sa*bo*ri*a \cmark & sen*sa*bo*ri-a \xmark \\
+sensório & sen*só*ri.o \xmark & sen*só*rio \cmark \\
 sépia & sé*pi.a \xmark & sé*pia \cmark \\
+sepsia & sep*si*a \cmark & sep*si-a \xmark \\
 septicemia & sep*ti*ce*mi*a \cmark & sep*ti*ce*mi-a \xmark \\
+septuagenário & sep*tu*a*ge*ná*ri.o \xmark & sep*tu*a*ge*ná*rio \cmark \\
 sequência & se-quên*ci.a \xmark & se*quên*cia \cmark \\
 sequoia & se*quoi*a \cmark & se*quoi-a \xmark \\
+serápia & se*rá*pi.a \xmark & se*rá*pia \cmark \\
 sereia & se*rei*a \cmark & se*rei-a \xmark \\
+seríceo & se*rí*ce.o \xmark & se*rí*ceo \cmark \\
 série & sé*ri.e \xmark & sé*rie \cmark \\
@@
 serologia & se*ro*lo*gi*a \cmark & se*ro*lo*gi-a \xmark \\
+serpentário & ser*pen*tá*ri.o \xmark & ser*pen*tá*rio \cmark \\
 serralharia & ser*ra*lha*ri*a \cmark & ser*ra*lha*ri-a \xmark \\
+serralheria & ser*ra*lhe*ri*a \cmark & ser*ra*lhe*ri-a \xmark \\
 serrania & ser*ra*ni*a \cmark & ser*ra*ni-a \xmark \\
+serraria & ser*ra*ri*a \cmark & ser*ra*ri-a \xmark \\
 serventia & ser*ven*ti*a \cmark & ser*ven*ti-a \xmark \\
@@
 sestércio & ses*tér*ci.o \xmark & ses*tér*cio \cmark \\
+setenário & se*te*ná*ri.o \xmark & se*te*ná*rio \cmark \\
+setentrião & se*ten*tri-ão \xmark & se*ten*tri*ão \cmark \\
+setia & se*ti*a \cmark & se*ti-a \xmark \\
 sexagenário & se*xa*ge*ná*ri.o \xmark & se*xa*ge*ná*rio \cmark \\
@@
 sibilância & si*bi*lân*ci.a \xmark & si*bi*lân*cia \cmark \\
+sicário & si*cá*ri.o \xmark & si*cá*rio \cmark \\
+sicômoro & si-cô*mo*ro \xmark & si*cô*mo*ro \cmark \\
+sideromancia & si*de*ro*man*ci*a \cmark & si*de*ro*man*ci-a \xmark \\
 siderurgia & si*de*rur*gi*a \cmark & si*de*rur*gi-a \xmark \\
+sievert & si.e*vert \xmark & si.e*vert \xmark \\
+sigilografia & si*gi*lo*gra*fi*a \cmark & si*gi*lo*gra*fi-a \xmark \\
 signatário & sig*na*tá*ri.o \xmark & sig*na*tá*rio \cmark \\
 significância & sig*ni*fi*cân*ci.a \xmark & sig*ni*fi*cân*cia \cmark \\
+silabário & si*la*bá*ri.o \xmark & si*la*bá*rio \cmark \\
 silêncio & si*lên*ci.o \xmark & si*lên*cio \cmark \\
+silharia & si*lha*ri*a \cmark & si*lha*ri-a \xmark \\
 silício & si*lí*ci.o \xmark & si*lí*cio \cmark \\
@@
 simpatria & sim*pa*tri*a \cmark & sim*pa*tri-a \xmark \\
+simplório & sim*pló*ri.o \xmark & sim*pló*rio \cmark \\
 simpósio & sim*pó*si.o \xmark & sim*pó*sio \cmark \\
@@
 sindicância & sin*di*cân*ci.a \xmark & sin*di*cân*cia \cmark \\
+sinédrio & si*né*dri.o \xmark & si*né*drio \cmark \\
 sinergia & si*ner*gi*a \cmark & si*ner*gi-a \xmark \\
@@
 sírio & sí*ri.o \xmark & sí*rio \cmark \\
+sismologia & sis*mo*lo*gi*a \cmark & sis*mo*lo*gi-a \xmark \\
+sismômetro & sis-mô*me*tro \xmark & sis*mô*me*tro \cmark \\
 sítio & sí*ti.o \xmark & sí*tio \cmark \\
@@
 soberania & so*be*ra*ni*a \cmark & so*be*ra*ni-a \xmark \\
+sobranceria & so*bran*ce*ri*a \cmark & so*bran*ce*ri-a \xmark \\
 sobressaia & so*bres*sai*a \cmark & so*bres*sai-a \xmark \\
@@
 sóbrio & só*bri.o \xmark & só*brio \cmark \\
+sociável & so*ci-á*vel \xmark & so*ci*á*vel \cmark \\
 societário & so*ci*e*tá*ri.o \xmark & so*ci*e*tá*rio \cmark \\
@@
 sodomia & so*do*mi*a \cmark & so*do*mi-a \xmark \\
+solanácea & so*la*ná*ce.a \xmark & so*la*ná*cea \cmark \\
+solaria & so*la*ri*a \cmark & so*la*ri-a \xmark \\
 solário & so*lá*ri.o \xmark & so*lá*rio \cmark \\
+solicitadoria & so*li*ci*ta*do*ri*a \cmark & so*li*ci*ta*do*ri-a \xmark \\
 solidário & so*li*dá*ri.o \xmark & so*li*dá*rio \cmark \\
+solilóquio & so*li*ló*qui.o \xmark & so*li*ló*quio \cmark \\
 sólio & só*li.o \xmark & só*lio \cmark \\
@@
 solstício & sols*tí*ci.o \xmark & sols*tí*cio \cmark \\
+solvência & sol*vên*ci.a \xmark & sol*vên*cia \cmark \\
 somatório & so*ma*tó*ri.o \xmark & so*ma*tó*rio \cmark \\
@@
 soslaio & sos*lai*o \cmark & sos*lai-o \xmark \\
+soteriologia & so*te*ri*o*lo*gi*a \cmark & so*te*ri*o*lo*gi-a \xmark \\
 soviético & so*vi-é*ti*co \xmark & so*vi*é*ti*co \cmark \\
@@
 stalinista & s.ta*li*nis*ta \xmark & sta*li*nis*ta \cmark \\
+suaíle & su*a-í*le \xmark & su*a*í*le \cmark \\
 suaíli & su*a-í*li \xmark & su*a*í*li \cmark \\
@@
 suástica & su-ás*ti*ca \xmark & su*ás*ti*ca \cmark \\
+sua & su*a \cmark & su-a \xmark \\
 suã & su-ã \xmark & su*ã \cmark \\
 subaquático & su*ba-quá*ti*co \xmark & su*ba*quá*ti*co \cmark \\
+subatômico & su*ba-tô*mi*co \xmark & su*ba*tô*mi*co \cmark \\
 subcategoria & sub*ca*te*go*ri*a \cmark & sub*ca*te*go*ri-a \xmark \\
+subcomissário & sub*co*mis*sá*ri.o \xmark & sub*co*mis*sá*rio \cmark \\
+subconsciência & sub*cons*ci*ên*ci.a \xmark & sub*cons*ci*ên*cia \cmark \\
 subcutâneo & sub*cu*tâ*ne.o \xmark & sub*cu*tâ*neo \cmark \\
@@
 subespécie & su*bes*pé*ci.e \xmark & su*bes*pé*cie \cmark \\
+subfamília & sub*fa*mí*li.a \xmark & sub*fa*mí*lia \cmark \\
+sublevação & su.b-le*va*ção \xmark & sub*le*va*ção \cmark \\
+sublevado & su.b-le*va*do \xmark & sub*le*va*do \cmark \\
+sublevar & su.b-le*var \xmark & sub*le*var \cmark \\
+subliminal & su.b-li*mi*nal \xmark & su.b-li*mi*nal \xmark \\
 subliminar & su.b-li*mi*nar \xmark & su.b-li*mi*nar \xmark \\
+sublinear & su.b-li*ne*ar \xmark & su.b-li*ne*ar \xmark \\
 sublingual & su.b-lin*gual \xmark & su.b-lin*gual \xmark \\
@@
 sublocar & su.b-lo*car \xmark & sub*lo*car \cmark \\
+sublocatário & su.b-lo*ca*tá*ri.o \xmark & sub*lo*ca*tá*rio \cmark \\
 sublunar & su.b-lu*nar \xmark & sub*lu*nar \cmark \\
+subluxação & su.b-lu*xa*ção \xmark & sub*lu*xa*ção \cmark \\
 subsecretário & sub*se*cre*tá*ri.o \xmark & sub*se*cre*tá*rio \cmark \\
+subsequência & sub*se-quên*ci.a \xmark & sub*se*quên*cia \cmark \\
 subserviência & sub*ser*vi*ên*ci.a \xmark & sub*ser*vi*ên*cia \cmark \\
+subsidência & sub*si*dên*ci.a \xmark & sub*si*dên*cia \cmark \\
 subsidiário & sub*si*di-á*ri.o \xmark & sub*si*di*á*rio \cmark \\
@@
 subsistência & sub*sis*tên*ci.a \xmark & sub*sis*tên*cia \cmark \\
+subsônico & sub-sô*ni*co \xmark & sub*sô*ni*co \cmark \\
 substância & subs*tân*ci.a \xmark & subs*tân*cia \cmark \\
@@
 substituído & subs*ti*tu-í*do \xmark & subs*ti*tu*í*do \cmark \\
+substituinte & subs*ti*tu-in*te \xmark & subs*ti*tu*in*te \cmark \\
 substituir & subs*ti*tu-ir \xmark & subs*ti*tu*ir \cmark \\
@@
 súcia & sú*ci.a \xmark & sú*cia \cmark \\
+suculência & su*cu*lên*ci.a \xmark & su*cu*lên*cia \cmark \\
+sucumbência & su*cum*bên*ci.a \xmark & su*cum*bên*cia \cmark \\
+sucuriú & su*cu*ri-ú \xmark & su*cu*ri*ú \cmark \\
 sudário & su*dá*ri.o \xmark & su*dá*rio \cmark \\
@@
 suíça & su-í*ça \xmark & su*í*ça \cmark \\
+suicida & su-i*ci*da \xmark & su*i*ci*da \cmark \\
+suicídio & su-i*cí*di*o \xmark & su*i*cí*di-o \xmark \\
 suíço & su-í*ço \xmark & su*í*ço \cmark \\
+suídeo & su-í*de.o \xmark & su*í*deo \cmark \\
+suingar & su-in*gar \xmark & su*in*gar \cmark \\
 suingue & su-in*gue \xmark & su*in*gue \cmark \\
+suinicultura & su-i*ni*cul*tu*ra \xmark & su*i*ni*cul*tu*ra \cmark \\
+suinocultura & su-i*no*cul*tu*ra \xmark & su*i*no*cul*tu*ra \cmark \\
 suíno & su-í*no \xmark & su*í*no \cmark \\
 suíte & su-í*te \xmark & su*í*te \cmark \\
+sulfúreo & sul*fú*re.o \xmark & sul*fú*reo \cmark \\
 sumário & su*má*ri.o \xmark & su*má*rio \cmark \\
+sumaúma & su*ma-ú*ma \xmark & su*ma*ú*ma \cmark \\
 sumério & su*mé*ri.o \xmark & su*mé*rio \cmark \\
 sumô & su-mô \xmark & su*mô \cmark \\
+suntuário & sun*tu-á*ri.o \xmark & sun*tu*á*rio \cmark \\
 supedâneo & su*pe*dâ*ne.o \xmark & su*pe*dâ*neo \cmark \\
+superabundância & su*pe*ra*bun*dân*ci.a \xmark & su*pe*ra*bun*dân*cia \cmark \\
 superavitário & su*pe*ra*vi*tá*ri.o \xmark & su*pe*ra*vi*tá*rio \cmark \\
 supercampeão & su*per*cam*pe-ão \xmark & su*per*cam*pe*ão \cmark \\
+supercílio & su*per*cí*li.o \xmark & su*per*cí*lio \cmark \\
 superfície & su*per*fí*ci.e \xmark & su*per*fí*cie \cmark \\
@@
 superintendência & su*pe*rin*ten*dên*ci.a \xmark & su*pe*rin*ten*dên*cia \cmark \\
+supernumerário & su*per*nu*me*rá*ri.o \xmark & su*per*nu*me*rá*rio \cmark \\
+superpotência & su*per*po*tên*ci.a \xmark & su*per*po*tên*cia \cmark \\
 supersônico & su*per-sô*ni*co \xmark & su*per*sô*ni*co \cmark \\
 superveniência & su*per*ve*ni*ên*ci.a \xmark & su*per*ve*ni*ên*cia \cmark \\
+supervivência & su*per*vi*vên*ci.a \xmark & su*per*vi*vên*cia \cmark \\
+suplência & su*plên*ci.a \xmark & su*plên*cia \cmark \\
+suplício & su*plí*ci.o \xmark & su*plí*cio \cmark \\
+supositório & su*po*si*tó*ri.o \xmark & su*po*si*tó*rio \cmark \\
+supranumerário & su*pra*nu*me*rá*ri.o \xmark & su*pra*nu*me*rá*rio \cmark \\
+suprapartidário & su*pra*par*ti*dá*ri.o \xmark & su*pra*par*ti*dá*rio \cmark \\
 supremacia & su*pre*ma*ci*a \cmark & su*pre*ma*ci-a \xmark \\
 surucuá & su*ru*cu-á \xmark & su*ru*cu*á \cmark \\
+suserania & su*se*ra*ni*a \cmark & su*se*ra*ni-a \xmark \\
 suspensório & sus*pen*só*ri.o \xmark & sus*pen*só*rio \cmark \\
+sustância & sus*tân*ci.a \xmark & sus*tân*cia \cmark \\
 sutiã & su*ti-ã \xmark & su*ti*ã \cmark \\
@@
 tabelião & ta*be*li-ão \xmark & ta*be*li*ão \cmark \\
+taboa & ta*bo*a \cmark & ta*bo-a \xmark \\
 tabuão & ta*bu-ão \xmark & ta*bu*ão \cmark \\
 tabua & ta*bu*a \cmark & ta*bu-a \xmark \\
+tabuinha & ta*bu-i*nha \xmark & ta*bu*i*nha \cmark \\
+tabulário & ta*bu*lá*ri.o \xmark & ta*bu*lá*rio \cmark \\
 tacômetro & ta-cô*me*tro \xmark & ta*cô*me*tro \cmark \\
@@
 talassoterapia & ta*las*so*te*ra*pi*a \cmark & ta*las*so*te*ra*pi-a \xmark \\
+talharia & ta*lha*ri*a \cmark & ta*lha*ri-a \xmark \\
 talião & ta*li-ão \xmark & ta*li*ão \cmark \\
+tália & tá*li.a \xmark & tá*lia \cmark \\
 tálio & tá*li.o \xmark & tá*lio \cmark \\
+talonário & ta*lo*ná*ri.o \xmark & ta*lo*ná*rio \cmark \\
+tâmia & tâ*mi.a \xmark & tâ*mia \cmark \\
 tanatofobia & ta*na*to*fo*bi*a \cmark & ta*na*to*fo*bi-a \xmark \\
@@
 tanoaria & ta*no*a*ri*a \cmark & ta*no*a*ri-a \xmark \\
+taoismo & ta.o-is*mo \xmark & ta.o-is*mo \xmark \\
+tapeçaria & ta*pe*ça*ri*a \cmark & ta*pe*ça*ri-a \xmark \\
 tapuia & ta*pui*a \cmark & ta*pui-a \xmark \\
@@
 tardio & tar*di*o \cmark & tar*di-o \xmark \\
+tarifário & ta*ri*fá*ri.o \xmark & ta*ri*fá*rio \cmark \\
 tarô & ta-rô \xmark & ta*rô \cmark \\
+tasmânia & tas*mâ*ni.a \xmark & tas*mâ*nia \cmark \\
 tataravô & ta*ta*ra-vô \xmark & ta*ta*ra*vô \cmark \\
@@
 tautologia & tau*to*lo*gi*a \cmark & tau*to*lo*gi-a \xmark \\
+tautomeria & tau*to*me*ri*a \cmark & tau*to*me*ri-a \xmark \\
+tautômero & tau-tô*me*ro \xmark & tau*tô*me*ro \cmark \\
 taxionomia & ta*xi*o*no*mi*a \cmark & ta*xi*o*no*mi-a \xmark \\
@@
 taxonômico & ta*xo-nô*mi*co \xmark & ta*xo*nô*mi*co \cmark \\
+tchau & t.chau \xmark & tchau \cmark \\
+tchecoslovaco & t.che*cos*lo*va*co \xmark & tche*cos*lo*va*co \cmark \\
 tcheco & t.che*co \xmark & tche*co \cmark \\
@@
 tecnocracia & tec*no*cra*ci*a \cmark & tec*no*cra*ci-a \xmark \\
+tecnofobia & tec*no*fo*bi*a \cmark & tec*no*fo*bi-a \xmark \\
 tecnologia & tec*no*lo*gi*a \cmark & tec*no*lo*gi-a \xmark \\
+tectônico & tec-tô*ni*co \xmark & tec*tô*ni*co \cmark \\
 tédio & té*di.o \xmark & té*dio \cmark \\
@@
 teiú & tei-ú \xmark & tei*ú \cmark \\
+telangiectasia & te*lan*gi*ec*ta*si*a \cmark & te*lan*gi*ec*ta*si-a \xmark \\
 telecinesia & te*le*ci*ne*si*a \cmark & te*le*ci*ne*si-a \xmark \\
@@
 telegrafia & te*le*gra*fi*a \cmark & te*le*gra*fi-a \xmark \\
+teleinformática & te*le-in*for*má*ti*ca \xmark & te*le*in*for*má*ti*ca \cmark \\
 telemetria & te*le*me*tri*a \cmark & te*le*me*tri-a \xmark \\
@@
 telepatia & te*le*pa*ti*a \cmark & te*le*pa*ti-a \xmark \\
+telescopia & te*les*co*pi*a \cmark & te*les*co*pi-a \xmark \\
 telescópio & te*les*có*pi.o \xmark & te*les*có*pio \cmark \\
+telômero & te-lô*me*ro \xmark & te*lô*me*ro \cmark \\
 telúrio & te*lú*ri.o \xmark & te*lú*rio \cmark \\
@@
 tendência & ten*dên*ci.a \xmark & ten*dên*cia \cmark \\
+tenência & te*nên*ci.a \xmark & te*nên*cia \cmark \\
 teníase & te*ní-a*se \xmark & te*ní*a*se \cmark \\
+tentório & ten*tó*ri.o \xmark & ten*tó*rio \cmark \\
+tênue & tê*nu.e \xmark & tê*nue \cmark \\
 teocracia & te*o*cra*ci*a \cmark & te*o*cra*ci-a \xmark \\
+teodiceia & te*o*di*cei*a \cmark & te*o*di*cei-a \xmark \\
 teofania & te*o*fa*ni*a \cmark & te*o*fa*ni-a \xmark \\
 teófobo & te-ó*fo*bo \xmark & te*ó*fo*bo \cmark \\
+teogonia & te*o*go*ni*a \cmark & te*o*go*ni-a \xmark \\
 teologia & te*o*lo*gi*a \cmark & te*o*lo*gi-a \xmark \\
@@
 teosofia & te*o*so*fi*a \cmark & te*o*so*fi-a \xmark \\
+teósofo & te-ó*so*fo \xmark & te*ó*so*fo \cmark \\
 terapia & te*ra*pi*a \cmark & te*ra*pi-a \xmark \\
@@
 tércia & tér*ci.a \xmark & tér*cia \cmark \\
+tércio & tér*ci.o \xmark & tér*cio \cmark \\
 terminologia & ter*mi*no*lo*gi*a \cmark & ter*mi*no*lo*gi-a \xmark \\
@@
 termoquímico & ter*mo-quí*mi*co \xmark & ter*mo*quí*mi*co \cmark \\
+ternário & ter*ná*ri.o \xmark & ter*ná*rio \cmark \\
+terráqueo & ter*rá*que.o \xmark & ter*rá*queo \cmark \\
+terrário & ter*rá*ri.o \xmark & ter*rá*rio \cmark \\
 térreo & tér*re.o \xmark & tér*reo \cmark \\
@@
 tesouraria & te*sou*ra*ri*a \cmark & te*sou*ra*ri-a \xmark \\
+tessálio & tes*sá*li.o \xmark & tes*sá*lio \cmark \\
 testamentário & tes*ta*men*tá*ri.o \xmark & tes*ta*men*tá*rio \cmark \\
@@
 tetravô & te*tra-vô \xmark & te*tra*vô \cmark \\
+teurgia & te-ur*gi*a \xmark & te-ur*gi-a \xmark \\
 teúrgico & te-úr*gi*co \xmark & te*úr*gi*co \cmark \\
@@
 tíbio & tí*bi.o \xmark & tí*bio \cmark \\
+tié & ti-é \xmark & ti*é \cmark \\
 tília & tí*li.a \xmark & tí*lia \cmark \\
+timbaúba & tim*ba-ú*ba \xmark & tim*ba*ú*ba \cmark \\
 timocracia & ti*mo*cra*ci*a \cmark & ti*mo*cra*ci-a \xmark \\
+tinamídeo & ti*na*mí*de.o \xmark & ti*na*mí*deo \cmark \\
 tinturaria & tin*tu*ra*ri*a \cmark & tin*tu*ra*ri-a \xmark \\
@@
 tipoia & ti*poi*a \cmark & ti*poi-a \xmark \\
+tipologia & ti*po*lo*gi*a \cmark & ti*po*lo*gi-a \xmark \\
 tiptologia & tip*to*lo*gi*a \cmark & tip*to*lo*gi-a \xmark \\
 tirania & ti*ra*ni*a \cmark & ti*ra*ni-a \xmark \\
+tiranicídio & ti*ra*ni*cí*di.o \xmark & ti*ra*ni*cí*dio \cmark \\
+tireoidectomia & ti*re*oi*dec*to*mi*a \cmark & ti*re*oi*dec*to*mi-a \xmark \\
 tirocínio & ti*ro*cí*ni.o \xmark & ti*ro*cí*nio \cmark \\
@@
 tiroteio & ti*ro*tei*o \cmark & ti*ro*tei-o \xmark \\
+tisiologia & ti*si*o*lo*gi*a \cmark & ti*si*o*lo*gi-a \xmark \\
 titânio & ti*tâ*ni.o \xmark & ti*tâ*nio \cmark \\
@@
 tonelaria & to*ne*la*ri*a \cmark & to*ne*la*ri-a \xmark \\
+tonsilectomia & ton*si*lec*to*mi*a \cmark & ton*si*lec*to*mi-a \xmark \\
 topázio & to*pá*zi.o \xmark & to*pá*zio \cmark \\
@@
 toracotomia & to*ra*co*to*mi*a \cmark & to*ra*co*to*mi-a \xmark \\
+tório & tó*ri*o \cmark & tó*ri-o \xmark \\
+tormentório & tor*men*tó*ri.o \xmark & tor*men*tó*rio \cmark \\
+tornearia & tor*ne*a*ri*a \cmark & tor*ne*a*ri-a \xmark \\
 torquês & tor-quês \xmark & tor*quês \cmark \\
@@
 totalitário & to*ta*li*tá*ri.o \xmark & to*ta*li*tá*rio \cmark \\
+toureio & tou*rei*o \cmark & tou*rei-o \xmark \\
+toxicodependência & to*xi*co*de*pen*dên*ci.a \xmark & to*xi*co*de*pen*dên*cia \cmark \\
 toxicologia & to*xi*co*lo*gi*a \cmark & to*xi*co*lo*gi-a \xmark \\
@@
 toxicômano & to*xi-cô*ma*no \xmark & to*xi*cô*ma*no \cmark \\
+trábea & trá*be.a \xmark & trá*bea \cmark \\
 trácio & trá*ci*o \cmark & trá*ci-o \xmark \\
@@
 tragicomédia & tra*gi*co*mé*di.a \xmark & tra*gi*co*mé*dia \cmark \\
+tragicômico & tra*gi-cô*mi*co \xmark & tra*gi*cô*mi*co \cmark \\
 traído & tra-í*do \xmark & tra*í*do \cmark \\
@@
 trair & tra-ir \xmark & tra*ir \cmark \\
+trajetória & tra*je*tó*ri.a \xmark & tra*je*tó*ria \cmark \\
 tramoia & tra*moi*a \cmark & tra*moi-a \xmark \\
@@
 transitório & tran*si*tó*ri.o \xmark & tran*si*tó*rio \cmark \\
+transmitância & trans*mi*tân*ci.a \xmark & trans*mi*tân*cia \cmark \\
 transoceânico & tran*so*ce-â*ni*co \xmark & tran*so*ce*â*ni*co \cmark \\
+transparência & trans*pa*rên*ci.a \xmark & trans*pa*rên*cia \cmark \\
 transumância & tran*su*mân*ci.a \xmark & tran*su*mân*cia \cmark \\
+tranvia & tran*vi*a \cmark & tran*vi-a \xmark \\
 trapézio & tra*pé*zi.o \xmark & tra*pé*zio \cmark \\
 traqueia & tra*quei*a \cmark & tra*quei-a \xmark \\
+traqueotomia & tra*que*o*to*mi*a \cmark & tra*que*o*to*mi-a \xmark \\
+traquítico & tra-quí*ti*co \xmark & tra*quí*ti*co \cmark \\
 traumatologia & trau*ma*to*lo*gi*a \cmark & trau*ma*to*lo*gi-a \xmark \\
 travessia & tra*ves*si*a \cmark & tra*ves*si-a \xmark \\
+trematódeo & tre*ma*tó*de.o \xmark & tre*ma*tó*deo \cmark \\
 tríade & trí-a*de \xmark & trí*a*de \cmark \\
+triádico & tri-á*di*co \xmark & tri*á*di*co \cmark \\
 triarquia & tri*ar*qui*a \cmark & tri*ar*qui-a \xmark \\
+triásico & tri-á*si*co \xmark & tri*á*si*co \cmark \\
+triássico & tri-ás*si*co \xmark & tri*ás*si*co \cmark \\
+tribunício & tri*bu*ní*ci.o \xmark & tri*bu*ní*cio \cmark \\
 tributário & tri*bu*tá*ri.o \xmark & tri*bu*tá*rio \cmark \\
@@
 tricentenário & tri*cen*te*ná*ri.o \xmark & tri*cen*te*ná*rio \cmark \\
+triclínio & tri*clí*ni.o \xmark & tri*clí*nio \cmark \\
+tricórnio & tri*cór*ni.o \xmark & tri*cór*nio \cmark \\
 tricotilomania & tri*co*ti*lo*ma*ni*a \cmark & tri*co*ti*lo*ma*ni-a \xmark \\
@@
 tríduo & trí*du.o \xmark & trí*duo \cmark \\
+triênio & tri*ê*ni.o \xmark & tri*ê*nio \cmark \\
+trifólio & tri*fó*li.o \xmark & tri*fó*lio \cmark \\
+trifório & tri*fó*ri.o \xmark & tri*fó*rio \cmark \\
 trigonometria & tri*go*no*me*tri*a \cmark & tri*go*no*me*tri-a \xmark \\
@@
 trinitário & tri*ni*tá*ri.o \xmark & tri*ni*tá*rio \cmark \\
+trinômio & tri-nô*mi.o \xmark & tri*nô*mio \cmark \\
+tríodo & trí-o*do \xmark & trí*o*do \cmark \\
 trio & tri*o \cmark & tri-o \xmark \\
+trióxido & tri-ó*xi*do \xmark & tri*ó*xi*do \cmark \\
 tripanossomíase & tri*pa*nos*so*mí-a*se \xmark & tri*pa*nos*so*mí*a*se \cmark \\
@@
 triunfo & tri-un*fo \xmark & tri*un*fo \cmark \\
+triunvirato & tri-un*vi*ra*to \xmark & tri*un*vi*ra*to \cmark \\
 triúnviro & tri-ún*vi*ro \xmark & tri*ún*vi*ro \cmark \\
 trívio & trí*vi.o \xmark & trí*vio \cmark \\
+tróclea & tró*cle.a \xmark & tró*clea \cmark \\
+troia & troi*a \cmark & troi-a \xmark \\
 trombocitopenia & trom*bo*ci*to*pe*ni*a \cmark & trom*bo*ci*to*pe*ni-a \xmark \\
+tropologia & tro*po*lo*gi*a \cmark & tro*po*lo*gi-a \xmark \\
 truculência & tru*cu*lên*ci.a \xmark & tru*cu*lên*cia \cmark \\
 truísmo & tru-ís*mo \xmark & tru*ís*mo \cmark \\
+tsonga & t.son*ga \xmark & tson*ga \cmark \\
+tsunami & t.su*na*mi \xmark & tsu*na*mi \cmark \\
 tua & tu*a \cmark & tu-a \xmark \\
+tugúrio & tu*gú*ri.o \xmark & tu*gú*rio \cmark \\
+tuia & tui*a \cmark & tu.i-a \xmark \\
 tuim & tu-im \xmark & tu*im \cmark \\
+tuiuiú & tui-ui-ú \xmark & tu.i*ui*ú \xmark \\
 túlio & tú*li.o \xmark & tú*lio \cmark \\
+tumescência & tu*mes*cên*ci.a \xmark & tu*mes*cên*cia \cmark \\
 tumultuário & tu*mul*tu-á*ri.o \xmark & tu*mul*tu*á*rio \cmark \\
+tungstênio & tungs*tê*ni.o \xmark & tungs*tê*nio \cmark \\
+tupaia & tu*pai*a \cmark & tu*pai-a \xmark \\
+turboélice & tur*bo-é*li*ce \xmark & tur*bo*é*li*ce \cmark \\
+turbulência & tur*bu*lên*ci.a \xmark & tur*bu*lên*cia \cmark \\
+turgência & tur*gên*ci.a \xmark & tur*gên*cia \cmark \\
+turgescência & tur*ges*cên*ci.a \xmark & tur*ges*cên*cia \cmark \\
+turíngia & tu*rín*gi.a \xmark & tu*rín*gia \cmark \\
+tutoria & tu*to*ri*a \cmark & tu*to*ri-a \xmark \\
+tuxaua & tu*xau*a \cmark & tu*xau-a \xmark \\
 tzarista & t.za*ris*ta \xmark & tza*ris*ta \cmark \\
 ufania & u*fa*ni*a \cmark & u*fa*ni-a \xmark \\
+ufologia & u*fo*lo*gi*a \cmark & u*fo*lo*gi-a \xmark \\
 uísque & u-ís*que \xmark & u*ís*que \cmark \\
 uíste & u-ís*te \xmark & u*ís*te \cmark \\
+ultrassonografia & ul*tras*so*no*gra*fi*a \cmark & ul*tras*so*no*gra*fi-a \xmark \\
 umbaúba & um*ba-ú*ba \xmark & um*ba*ú*ba \cmark \\
@@
 universitário & u*ni*ver*si*tá*ri.o \xmark & u*ni*ver*si*tá*rio \cmark \\
+urânia & u*râ*ni.a \xmark & u*râ*nia \cmark \\
 urânio & u*râ*ni.o \xmark & u*râ*nio \cmark \\
+uranometria & u*ra*no*me*tri*a \cmark & u*ra*no*me*tri-a \xmark \\
 ureia & u*rei*a \cmark & u*rei-a \xmark \\
@@
 urologia & u*ro*lo*gi*a \cmark & u*ro*lo*gi-a \xmark \\
+uropatágio & u*ro*pa*tá*gi.o \xmark & u*ro*pa*tá*gio \cmark \\
 uropígio & u*ro*pí*gi.o \xmark & u*ro*pí*gio \cmark \\
@@
 usufruir & u*su*fru-ir \xmark & u*su*fru*ir \cmark \\
+usufrutuário & u*su*fru*tu-á*ri.o \xmark & u*su*fru*tu*á*rio \cmark \\
 usurário & u*su*rá*ri.o \xmark & u*su*rá*rio \cmark \\
@@
 vacaria & va*ca*ri*a \cmark & va*ca*ri-a \xmark \\
+vacínio & va*cí*ni.o \xmark & va*cí*nio \cmark \\
+vacuidade & va*cu-i*da*de \xmark & va*cu-i*da*de \xmark \\
 vacúolo & va*cú-o*lo \xmark & va*cú*o*lo \cmark \\
 vácuo & vá*cu.o \xmark & vá*cuo \cmark \\
+vadiaria & va*di*a*ri*a \cmark & va*di*a*ri-a \xmark \\
 vadia & va*di*a \cmark & va*di-a \xmark \\
 vaia & vai*a \cmark & vai-a \xmark \\
+valáquio & va*lá*qui.o \xmark & va*lá*quio \cmark \\
 valência & va*lên*ci.a \xmark & va*lên*cia \cmark \\
 valentia & va*len*ti*a \cmark & va*len*ti-a \xmark \\
+valetudinário & va*le*tu*di*ná*ri.o \xmark & va*le*tu*di*ná*rio \cmark \\
 valia & va*li*a \cmark & va*li-a \xmark \\
@@
 vanglória & van*gló*ri.a \xmark & van*gló*ria \cmark \\
+vanilóquio & va*ni*ló*qui.o \xmark & va*ni*ló*quio \cmark \\
+vareio & va*rei*o \cmark & va*rei-o \xmark \\
+variância & va*ri*ân*ci.a \xmark & va*ri*ân*cia \cmark \\
 vária & vá*ri.a \xmark & vá*ria \cmark \\
@@
 vasectomia & va*sec*to*mi*a \cmark & va*sec*to*mi-a \xmark \\
+vaticínio & va*ti*cí*ni.o \xmark & va*ti*cí*nio \cmark \\
 vazia & va*zi*a \cmark & va*zi-a \xmark \\
 vazio & va*zi*o \cmark & va*zi-o \xmark \\
+vedoria & ve*do*ri*a \cmark & ve*do*ri-a \xmark \\
 veemência & ve*e*mên*ci.a \xmark & ve*e*mên*cia \cmark \\
@@
 velharia & ve*lha*ri*a \cmark & ve*lha*ri-a \xmark \\
+velocimetria & ve*lo*ci*me*tri*a \cmark & ve*lo*ci*me*tri-a \xmark \\
 velório & ve*ló*ri.o \xmark & ve*ló*rio \cmark \\
+venefício & ve*ne*fí*ci.o \xmark & ve*ne*fí*cio \cmark \\
+venereologia & ve*ne*re*o*lo*gi*a \cmark & ve*ne*re*o*lo*gi-a \xmark \\
 venéreo & ve*né*re.o \xmark & ve*né*reo \cmark \\
+vênia & vê*ni.a \xmark & vê*nia \cmark \\
 ventania & ven*ta*ni*a \cmark & ven*ta*ni-a \xmark \\
+ventoinha & ven*to-i*nha \xmark & ven*to*i*nha \cmark \\
 ventriloquia & ven*tri*lo*qui*a \cmark & ven*tri*lo*qui-a \xmark \\
@@
 verborragia & ver*bor*ra*gi*a \cmark & ver*bor*ra*gi-a \xmark \\
+vergência & ver*gên*ci.a \xmark & ver*gên*cia \cmark \\
+verônica & ve-rô*ni*ca \xmark & ve*rô*ni*ca \cmark \\
+vestiaria & ves*ti*a*ri*a \cmark & ves*ti*a*ri-a \xmark \\
 vestiário & ves*ti-á*ri.o \xmark & ves*ti*á*rio \cmark \\
@@
 veterinário & ve*te*ri*ná*ri.o \xmark & ve*te*ri*ná*rio \cmark \\
+vexatório & ve*xa*tó*ri.o \xmark & ve*xa*tó*rio \cmark \\
+vexilologia & ve*xi*lo*lo*gi*a \cmark & ve*xi*lo*lo*gi-a \xmark \\
 viário & vi-á*ri.o \xmark & vi*á*rio \cmark \\
+viático & vi-á*ti*co \xmark & vi*á*ti*co \cmark \\
 viável & vi-á*vel \xmark & vi*á*vel \cmark \\
 via & vi*a \cmark & vi-a \xmark \\
+vibratório & vi*bra*tó*ri.o \xmark & vi*bra*tó*rio \cmark \\
 vibrião & vi*bri-ão \xmark & vi*bri*ão \cmark \\
@@
 viés & vi-és \xmark & vi*és \cmark \\
+vietcongue & vi*et*con*gue \cmark & vi*et-con*gue \xmark \\
+vigairaria & vi*gai*ra*ri*a \cmark & vi*gai*ra*ri-a \xmark \\
+vigária & vi*gá*ri.a \xmark & vi*gá*ria \cmark \\
 vigário & vi*gá*ri.o \xmark & vi*gá*rio \cmark \\
@@
 vigília & vi*gí*li.a \xmark & vi*gí*lia \cmark \\
+vigorexia & vi*go*re*xi*a \cmark & vi*go*re*xi-a \xmark \\
 vilania & vi*la*ni*a \cmark & vi*la*ni-a \xmark \\
 vilipêndio & vi*li*pên*di.o \xmark & vi*li*pên*dio \cmark \\
+vináceo & vi*ná*ce.o \xmark & vi*ná*ceo \cmark \\
+violácea & vi*o*lá*ce*a \cmark & vi*o*lá*ce-a \xmark \\
 violáceo & vi*o*lá*ce.o \xmark & vi*o*lá*ceo \cmark \\
@@
 vitalício & vi*ta*lí*ci.o \xmark & vi*ta*lí*cio \cmark \\
+vitimologia & vi*ti*mo*lo*gi*a \cmark & vi*ti*mo*lo*gi-a \xmark \\
 vitória & vi*tó*ri.a \xmark & vi*tó*ria \cmark \\
@@
 vitriólico & vi*tri-ó*li*co \xmark & vi*tri*ó*li*co \cmark \\
+vitríolo & vi*trí-o*lo \xmark & vi*trí*o*lo \cmark \\
 vitupério & vi*tu*pé*ri.o \xmark & vi*tu*pé*rio \cmark \\
@@
 vivência & vi*vên*ci.a \xmark & vi*vên*cia \cmark \\
+vixnuísmo & vix*nu-ís*mo \xmark & vix*nu*ís*mo \cmark \\
 vocabulário & vo*ca*bu*lá*ri.o \xmark & vo*ca*bu*lá*rio \cmark \\
+voivodia & voi*vo*di*a \cmark & voi*vo*di-a \xmark \\
+voleio & vo*lei*o \cmark & vo*lei-o \xmark \\
+volemia & vo*le*mi*a \cmark & vo*le*mi-a \xmark \\
 volfrâmio & vol*frâ*mi.o \xmark & vol*frâ*mio \cmark \\
+volteio & vol*tei*o \cmark & vol*tei-o \xmark \\
+volumetria & vo*lu*me*tri*a \cmark & vo*lu*me*tri-a \xmark \\
 voluntário & vo*lun*tá*ri.o \xmark & vo*lun*tá*rio \cmark \\
+volúpia & vo*lú*pi.a \xmark & vo*lú*pia \cmark \\
 voo & vo*o \cmark & vo-o \xmark \\
@@
 vozerio & vo*ze*ri*o \cmark & vo*ze*ri-o \xmark \\
+vreia & vrei*a \cmark & vrei-a \xmark \\
 vulcanologia & vul*ca*no*lo*gi*a \cmark & vul*ca*no*lo*gi-a \xmark \\
 xaria & xa*ri*a \cmark & xa*ri-a \xmark \\
+xariá & xa*ri-á \xmark & xa*ri*á \cmark \\
 xátria & xá*tri.a \xmark & xá*tria \cmark \\
@@
 xenomania & xe*no*ma*ni*a \cmark & xe*no*ma*ni-a \xmark \\
+xenônio & xe-nô*ni.o \xmark & xe*nô*nio \cmark \\
+xerocópia & xe*ro*có*pi.a \xmark & xe*ro*có*pia \cmark \\
 xeroftalmia & xe*rof*tal*mi*a \cmark & xe*rof*tal*mi-a \xmark \\
 xerografia & xe*ro*gra*fi*a \cmark & xe*ro*gra*fi-a \xmark \\
+xerostomia & xe*ros*to*mi*a \cmark & xe*ros*to*mi-a \xmark \\
+xibiu & xi*biu \cmark & xi*bi.u \xmark \\
 xilocaína & xi*lo*ca-í*na \xmark & xi*lo*ca*í*na \cmark \\
@@
 xintoísta & xin*to-ís*ta \xmark & xin*to*ís*ta \cmark \\
+xivaísmo & xi*va-ís*mo \xmark & xi*va*ís*mo \cmark \\
+xivaíta & xi*va-í*ta \xmark & xi*va*í*ta \cmark \\
+zagaia & za*gai*a \cmark & za*gai-a \xmark \\
 zaragatoa & za*ra*ga*to*a \cmark & za*ra*ga*to-a \xmark \\
+zebuíno & ze*bu-í*no \xmark & ze*bu*í*no \cmark \\
+zeladoria & ze*la*do*ri*a \cmark & ze*la*do*ri-a \xmark \\
+zimbório & zim*bó*ri.o \xmark & zim*bó*rio \cmark \\
+zircônio & zir-cô*ni.o \xmark & zir*cô*nio \cmark \\
+zizânia & zi*zâ*ni.a \xmark & zi*zâ*nia \cmark \\
 zodíaco & zo*dí-a*co \xmark & zo*dí*a*co \cmark \\
@@
 zoo & zo*o \cmark & zo-o \xmark \\
+zoroástrico & zo*ro-ás*tri*co \xmark & zo*ro*ás*tri*co \cmark \\
 zurraria & zur*ra*ri*a \cmark & zur*ra*ri-a \xmark \\
-total correct & 1331 & 1992 \\
+total correct & 1848 & 3137 \\

### 2024-07-02 article/comparedresults_nofinalvowel.tex
fix #56

@@
 abdômen & ab-dô*men \xmark & ab*dô*men \cmark \\
+abiótica & a*bi-ó*ti*ca \xmark & a*bi*ó*ti*ca \cmark \\
 abiótico & a*bi-ó*ti*co \xmark & a*bi*ó*ti*co \cmark \\
@@
 abraâmico & a*bra-â*mi*co \xmark & a*bra*â*mi*co \cmark \\
+abruptamente & a.b-rup*ta*men*te \xmark & a.b-rup*ta*men*te \xmark \\
 abrupto & a.b-rup*to \xmark & a.b-rup*to \xmark \\
 absenteísmo & ab*sen*te-ís*mo \xmark & ab*sen*te*ís*mo \cmark \\
+absenteísta & ab*sen*te-ís*ta \xmark & ab*sen*te*ís*ta \cmark \\
 abstraído & abs*tra-í*do \xmark & abs*tra*í*do \cmark \\
 abstrair & abs*tra-ir \xmark & abs*tra*ir \cmark \\
+acelerômetro & a*ce*le-rô*me*tro \xmark & a*ce*le*rô*me*tro \cmark \\
 acetaldeído & a*ce*tal*de-í*do \xmark & a*ce*tal*de*í*do \cmark \\
@@
 acordeão & a*cor*de-ão \xmark & a*cor*de*ão \cmark \\
-acuidade & a*cu-i*da*de \xmark & a*cu-i*da*de \xmark \\
+acroleína & a*cro*le-í*na \xmark & a*cro*le*í*na \cmark \\
 adail & a*da-il \xmark & a*da-il \xmark \\
+adônis & a-dô*nis \xmark & a*dô*nis \cmark \\
 adriático & a*dri-á*ti*co \xmark & a*dri*á*ti*co \cmark \\
@@
 agogô & a*go-gô \xmark & a*go*gô \cmark \\
+agônico & a-gô*ni*co \xmark & a*gô*ni*co \cmark \\
 agrião & a*gri-ão \xmark & a*gri*ão \cmark \\
 agronômico & a*gro-nô*mi*co \xmark & a*gro*nô*mi*co \cmark \\
+agroquímica & a*gro-quí*mi*ca \xmark & a*gro*quí*mi*ca \cmark \\
+agroquímico & a*gro-quí*mi*co \xmark & a*gro*quí*mi*co \cmark \\
 ainda & a-in*da \xmark & a*in*da \cmark \\
+ainsa & a-in*sa \xmark & a-in*sa \xmark \\
+aiquidô & ai*qui-dô \xmark & ai*qui*dô \cmark \\
+ajuizado & a*ju-i*za*do \xmark & a*ju*i*za*do \cmark \\
 ajuizar & a*ju-i*zar \xmark & a*ju*i*zar \cmark \\
+alagoinha & a*la*go-i*nha \xmark & a*la*go*i*nha \cmark \\
 alaúde & a*la-ú*de \xmark & a*la*ú*de \cmark \\
@@
 aliás & a*li-ás \xmark & a*li*ás \cmark \\
+almóada & al*mó-a*da \xmark & al*mó-a*da \xmark \\
 almôndega & al-môn*de*ga \xmark & al*môn*de*ga \cmark \\
@@
 altruísta & al*tru-ís*ta \xmark & al*tru*ís*ta \cmark \\
-aluimento & a*lu-i*men*to \xmark & a*lu-i*men*to \xmark \\
 aluir & a*lu-ir \xmark & a*lu*ir \cmark \\
@@
 anemômetro & a*ne-mô*me*tro \xmark & a*ne*mô*me*tro \cmark \\
+anfião & an*fi-ão \xmark & an*fi*ão \cmark \\
+anfictião & an*fic*ti-ão \xmark & an*fic*ti*ão \cmark \\
 anfitrião & an*fi*tri-ão \xmark & an*fi*tri*ão \cmark \\
+anião & a*ni-ão \xmark & a*ni*ão \cmark \\
+anômalo & a-nô*ma*lo \xmark & a*nô*ma*lo \cmark \\
 anônimo & a-nô*ni*mo \xmark & a*nô*ni*mo \cmark \\
@@
 antibiótico & an*ti*bi-ó*ti*co \xmark & an*ti*bi*ó*ti*co \cmark \\
+antiético & an*ti-é*ti*co \xmark & an*ti*é*ti*co \cmark \\
+antinômico & an*ti-nô*mi*co \xmark & an*ti*nô*mi*co \cmark \\
 antipatriótico & an*ti*pa*tri-ó*ti*co \xmark & an*ti*pa*tri*ó*ti*co \cmark \\
+antipoluição & an*ti*po*lu-i*ção \xmark & an*ti*po*lu*i*ção \cmark \\
 antiquíssimo & an*ti-quís*si*mo \xmark & an*ti*quís*si*mo \cmark \\
@@
 aórtico & a-ór*ti*co \xmark & a*ór*ti*co \cmark \\
+aperiódico & a*pe*ri-ó*di*co \xmark & a*pe*ri*ó*di*co \cmark \\
+apoteótico & a*po*te-ó*ti*co \xmark & a*po*te*ó*ti*co \cmark \\
 apreciável & a*pre*ci-á*vel \xmark & a*pre*ci*á*vel \cmark \\
@@
 arábias & a*rá*bi.as \xmark & a*rá*bi.as \xmark \\
+araúna & a*ra-ú*na \xmark & a*ra*ú*na \cmark \\
 arcaísmo & ar*ca-ís*mo \xmark & ar*ca*ís*mo \cmark \\
+areão & a*re-ão \xmark & a*re*ão \cmark \\
+areópago & a*re-ó*pa*go \xmark & a*re*ó*pa*go \cmark \\
 aríete & a*rí-e*te \xmark & a*rí*e*te \cmark \\
@@
 arquitetônico & ar*qui*te-tô*ni*co \xmark & ar*qui*te*tô*ni*co \cmark \\
-arrais & ar*ra-is \xmark & ar*ra-is \xmark \\
 arruinar & ar*ru-i*nar \xmark & ar*ru*i*nar \cmark \\
+arteríola & ar*te*rí-o*la \xmark & ar*te*rí*o*la \cmark \\
 ascaridíase & as*ca*ri*dí-a*se \xmark & as*ca*ri*dí*a*se \cmark \\
@@
 assiduidade & as*si*du-i*da*de \xmark & as*si*du*i*da*de \cmark \\
+assiriólogo & as*si*ri-ó*lo*go \xmark & as*si*ri*ó*lo*go \cmark \\
 associável & as*so*ci-á*vel \xmark & as*so*ci*á*vel \cmark \\
 astronômico & as*tro-nô*mi*co \xmark & as*tro*nô*mi*co \cmark \\
+astroquímica & as*tro-quí*mi*ca \xmark & as*tro*quí*mi*ca \cmark \\
 ataúde & a*ta-ú*de \xmark & a*ta*ú*de \cmark \\
@@
 atômico & a-tô*mi*co \xmark & a*tô*mi*co \cmark \\
+atônito & a-tô*ni*to \xmark & a*tô*ni*to \cmark \\
 atraído & a*tra-í*do \xmark & a*tra*í*do \cmark \\
@@
 austríaco & aus*trí-a*co \xmark & aus*trí*a*co \cmark \\
+autobiógrafo & au*to*bi-ó*gra*fo \xmark & au*to*bi*ó*gra*fo \cmark \\
+autodestruição & au*to*des*tru-i*ção \xmark & au*to*des*tru*i*ção \cmark \\
+autoimunidade & au*to-i*mu*ni*da*de \xmark & au*to*i*mu*ni*da*de \cmark \\
 autônimo & au-tô*ni*mo \xmark & au*tô*ni*mo \cmark \\
+autonômico & au*to-nô*mi*co \xmark & au*to*nô*mi*co \cmark \\
 autônomo & au-tô*no*mo \xmark & au*tô*no*mo \cmark \\
+averroísmo & a*ver*ro-ís*mo \xmark & a*ver*ro*ís*mo \cmark \\
 avião & a*vi-ão \xmark & a*vi*ão \cmark \\
 avô & a-vô \xmark & a*vô \cmark \\
+babilônico & ba*bi-lô*ni*co \xmark & ba*bi*lô*ni*co \cmark \\
 babuíno & ba*bu-í*no \xmark & ba*bu*í*no \cmark \\
@@
 balaústre & ba*la-ús*tre \xmark & ba*la*ús*tre \cmark \\
+baleárico & ba*le-á*ri*co \xmark & ba*le*á*ri*co \cmark \\
 bangalô & ban*ga-lô \xmark & ban*ga*lô \cmark \\
+banjoísta & ban*jo-ís*ta \xmark & ban*jo*ís*ta \cmark \\
+baraúna & ba*ra-ú*na \xmark & ba*ra*ú*na \cmark \\
+barômetro & ba-rô*me*tro \xmark & ba*rô*me*tro \cmark \\
 bastião & bas*ti-ão \xmark & bas*ti*ão \cmark \\
 batuíra & ba*tu-í*ra \xmark & ba*tu*í*ra \cmark \\
+beduíno & be*du-í*no \xmark & be*du*í*no \cmark \\
+behaviorismo & be-ha*vi*o*ris*mo \xmark & be-ha*vi*o*ris*mo \xmark \\
 benjoim & ben*jo-im \xmark & ben*jo*im \cmark \\
+benzocaína & ben*zo*ca-í*na \xmark & ben*zo*ca*í*na \cmark \\
 bibelô & bi*be-lô \xmark & bi*be*lô \cmark \\
 bibliófilo & bi*bli-ó*fi*lo \xmark & bi*bli*ó*fi*lo \cmark \\
+bibliógrafo & bi*bli-ó*gra*fo \xmark & bi*bli*ó*gra*fo \cmark \\
 bicampeão & bi*cam*pe-ão \xmark & bi*cam*pe*ão \cmark \\
+bicuíba & bi*cu-í*ba \xmark & bi*cu*í*ba \cmark \\
+bilbaíno & bil*ba-í*no \xmark & bil*ba*í*no \cmark \\
+bilião & bi*li-ão \xmark & bi*li*ão \cmark \\
 bioética & bi*o-é*ti*ca \xmark & bi*o*é*ti*ca \cmark \\
@@
 bioquímica & bi*o-quí*mi*ca \xmark & bi*o*quí*mi*ca \cmark \\
+bioquímico & bi*o-quí*mi*co \xmark & bi*o*quí*mi*co \cmark \\
 biótico & bi-ó*ti*co \xmark & bi*ó*ti*co \cmark \\
 biótipo & bi-ó*ti*po \xmark & bi*ó*ti*po \cmark \\
+biótopo & bi-ó*to*po \xmark & bi*ó*to*po \cmark \\
 biquíni & bi-quí*ni \xmark & bi*quí*ni \cmark \\
@@
 biscainho & bis*ca-i*nho \xmark & bis*ca*i*nho \cmark \\
+biunívoco & bi-u*ní*vo*co \xmark & bi*u*ní*vo*co \cmark \\
+blastômero & blas-tô*me*ro \xmark & blas*tô*me*ro \cmark \\
 bocaiuva & bo*cai-u*va \xmark & bo*cai*u*va \cmark \\
+bôer & bô-er \xmark & bô-er \xmark \\
 boião & boi-ão \xmark & boi*ão \cmark \\
@@
 bongô & bon-gô \xmark & bon*gô \cmark \\
+borderô & bor*de-rô \xmark & bor*de*rô \cmark \\
 bordô & bor-dô \xmark & bor*dô \cmark \\
+bosníaco & bos*ní-a*co \xmark & bos*ní*a*co \cmark \\
+braquiópode & bra*qui-ó*po*de \xmark & bra*qui*ó*po*de \cmark \\
+braúna & bra-ú*na \xmark & bra*ú*na \cmark \\
 brechtiano & bre.ch*ti*a*no \xmark & bre.ch*ti*a*no \xmark \\
@@
 buquê & bu-quê \xmark & bu*quê \cmark \\
+cabrião & ca*bri-ão \xmark & ca*bri*ão \cmark \\
+cabriúva & ca*bri-ú*va \xmark & ca*bri*ú*va \cmark \\
+cacauicultura & ca*cau-i*cul*tu*ra \xmark & ca*cau*i*cul*tu*ra \cmark \\
 cafarnaum & ca*far*na-um \xmark & ca*far*na-um \xmark \\
@@
 caim & ca-im \xmark & ca-im \xmark \\
+caimento & ca-i*men*to \xmark & ca-i*men*to \xmark \\
+caingangue & ca-in*gan*gue \xmark & ca-in*gan*gue \xmark \\
 caíque & ca-í*que \xmark & ca*í*que \cmark \\
@@
 canoísta & ca*no-ís*ta \xmark & ca*no*ís*ta \cmark \\
+canônico & ca-nô*ni*co \xmark & ca*nô*ni*co \cmark \\
 caótico & ca-ó*ti*co \xmark & ca*ó*ti*co \cmark \\
@@
 cariótipo & ca*ri-ó*ti*po \xmark & ca*ri*ó*ti*po \cmark \\
+carnaíba & car*na-í*ba \xmark & car*na*í*ba \cmark \\
 carnaúba & car*na-ú*ba \xmark & car*na*ú*ba \cmark \\
+carnaubal & car*na-u*bal \xmark & car*na-u*bal \xmark \\
 caseína & ca*se-í*na \xmark & ca*se*í*na \cmark \\
@@
 casuístico & ca*su-ís*ti*co \xmark & ca*su*ís*ti*co \cmark \\
+catatônico & ca*ta-tô*ni*co \xmark & ca*ta*tô*ni*co \cmark \\
 catequético & ca*te-qué*ti*co \xmark & ca*te*qué*ti*co \cmark \\
@@
 caúna & ca-ú*na \xmark & ca*ú*na \cmark \\
+celíaco & ce*lí-a*co \xmark & ce*lí*a*co \cmark \\
 centurião & cen*tu*ri-ão \xmark & cen*tu*ri*ão \cmark \\
+champô & cham-pô \xmark & cham*pô \cmark \\
 chatô & cha-tô \xmark & cha*tô \cmark \\
+chororô & cho*ro-rô \xmark & cho*ro*rô \cmark \\
+ciática & ci-á*ti*ca \xmark & ci*á*ti*ca \cmark \\
 ciático & ci-á*ti*co \xmark & ci*á*ti*co \cmark \\
+ciberespaço & ci*be.r-es*pa*ço \xmark & ci*be.r-es*pa*ço \xmark \\
 cirurgião & ci*rur*gi-ão \xmark & ci*rur*gi*ão \cmark \\
@@
 coibir & co-i*bir \xmark & co-i*bir \xmark \\
+coimbrão & co-im*brão \xmark & co*im*brão \cmark \\
 coincidente & co-in*ci*den*te \xmark & co*in*ci*den*te \cmark \\
 coincidir & co-in*ci*dir \xmark & co*in*ci*dir \cmark \\
+coirmão & co-ir*mão \xmark & co-ir*mão \xmark \\
 coleóptero & co*le-óp*te*ro \xmark & co*le*óp*te*ro \cmark \\
@@
 condoído & con*do-í*do \xmark & con*do*í*do \cmark \\
+condômino & con-dô*mi*no \xmark & con*dô*mi*no \cmark \\
+conduíte & con*du-í*te \xmark & con*du*í*te \cmark \\
 confiável & con*fi-á*vel \xmark & con*fi*á*vel \cmark \\
@@
 construir & cons*tru-ir \xmark & cons*tru*ir \cmark \\
+conteudista & con*te-u*dis*ta \xmark & con*te-u*dis*ta \xmark \\
 conteúdo & con*te-ú*do \xmark & con*te*ú*do \cmark \\
+continuidade & con*ti*nu-i*da*de \xmark & con*ti*nu*i*da*de \cmark \\
+continuísta & con*ti*nu-ís*ta \xmark & con*ti*nu*ís*ta \cmark \\
 contraído & con*tra-í*do \xmark & con*tra*í*do \cmark \\
+contraindicação & con*tra-in*di*ca*ção \xmark & con*tra*in*di*ca*ção \cmark \\
 contrair & con*tra-ir \xmark & con*tra*ir \cmark \\
@@
 copaíba & co*pa-í*ba \xmark & co*pa*í*ba \cmark \\
+copião & co*pi-ão \xmark & co*pi*ão \cmark \\
 coreógrafo & co*re-ó*gra*fo \xmark & co*re*ó*gra*fo \cmark \\
@@
 corroído & cor*ro-í*do \xmark & cor*ro*í*do \cmark \\
+corruíra & cor*ru-í*ra \xmark & cor*ru*í*ra \cmark \\
+corrupião & cor*ru*pi-ão \xmark & cor*ru*pi*ão \cmark \\
+crapô & cra-pô \xmark & cra*pô \cmark \\
 criciúma & cri*ci-ú*ma \xmark & cri*ci*ú*ma \cmark \\
@@
 curião & cu*ri-ão \xmark & cu*ri*ão \cmark \\
+curiúva & cu*ri-ú*va \xmark & cu*ri*ú*va \cmark \\
+czar & c.zar \xmark & czar \cmark \\
 czarina & c.za*ri*na \xmark & cza*ri*na \cmark \\
@@
 decurião & de*cu*ri-ão \xmark & de*cu*ri*ão \cmark \\
+deificação & de-i*fi*ca*ção \xmark & de-i*fi*ca*ção \xmark \\
+deiscente & de-is*cen*te \xmark & de-is*cen*te \xmark \\
 deísmo & de-ís*mo \xmark & de*ís*mo \cmark \\
 deísta & de-ís*ta \xmark & de*ís*ta \cmark \\
+demiúrgico & de*mi-úr*gi*co \xmark & de*mi*úr*gi*co \cmark \\
 demiurgo & de*mi-ur*go \xmark & de*mi*ur*go \cmark \\
@@
 depoimento & de*po-i*men*to \xmark & de*po*i*men*to \cmark \\
+depreciável & de*pre*ci-á*vel \xmark & de*pre*ci*á*vel \cmark \\
 descaída & des*ca-í*da \xmark & des*ca*í*da \cmark \\
@@
 destruído & des*tru-í*do \xmark & des*tru*í*do \cmark \\
+destruidor & des*tru-i*dor \xmark & des*tru-i*dor \xmark \\
 destruir & des*tru-ir \xmark & des*tru*ir \cmark \\
+desunião & de*su*ni-ão \xmark & de*su*ni*ão \cmark \\
+diábase & di-á*ba*se \xmark & di*á*ba*se \cmark \\
 diácono & di-á*co*no \xmark & di*á*co*no \cmark \\
+díada & dí-a*da \xmark & dí*a*da \cmark \\
 díade & dí-a*de \xmark & dí*a*de \cmark \\
+diádico & di-á*di*co \xmark & di*á*di*co \cmark \\
+diádoco & di-á*do*co \xmark & di*á*do*co \cmark \\
 diáfano & di-á*fa*no \xmark & di*á*fa*no \cmark \\
+diáfise & di-á*fi*se \xmark & di*á*fi*se \cmark \\
 diálise & di-á*li*se \xmark & di*á*li*se \cmark \\
@@
 diáspora & di-ás*po*ra \xmark & di*ás*po*ra \cmark \\
+diásporo & di-ás*po*ro \xmark & di*ás*po*ro \cmark \\
 diástole & di-ás*to*le \xmark & di*ás*to*le \cmark \\
+diatômico & di*a-tô*mi*co \xmark & di*a*tô*mi*co \cmark \\
+dicotômico & di*co-tô*mi*co \xmark & di*co*tô*mi*co \cmark \\
 dicroísmo & di*cro-ís*mo \xmark & di*cro*ís*mo \cmark \\
+diédrico & di-é*dri*co \xmark & di*é*dri*co \cmark \\
 diérese & di-é*re*se \xmark & di*é*re*se \cmark \\
 diferenciável & di*fe*ren*ci-á*vel \xmark & di*fe*ren*ci*á*vel \cmark \\
+diluição & di*lu-i*ção \xmark & di*lu*i*ção \cmark \\
 diluído & di*lu-í*do \xmark & di*lu*í*do \cmark \\
@@
 dinamarquês & di*na*mar-quês \xmark & di*na*mar*quês \cmark \\
+dinamômetro & di*na-mô*me*tro \xmark & di*na*mô*me*tro \cmark \\
+díodo & dí-o*do \xmark & dí*o*do \cmark \\
 dionisíaco & di*o*ni*sí-a*co \xmark & di*o*ni*sí*a*co \cmark \\
+dióptrica & di-óp*tri*ca \xmark & di*óp*tri*ca \cmark \\
 dióxido & di-ó*xi*do \xmark & di*ó*xi*do \cmark \\
@@
 dríade & drí-a*de \xmark & drí*a*de \cmark \\
+durião & du*ri-ão \xmark & du*ri*ão \cmark \\
+duúnviro & du-ún*vi*ro \xmark & du-ún*vi*ro \xmark \\
 dzeta & d.ze*ta \xmark & d.ze*ta \xmark \\
@@
 elefantíase & e*le*fan*tí-a*se \xmark & e*le*fan*tí*a*se \cmark \\
+elegíaco & e*le*gí-a*co \xmark & e*le*gí*a*co \cmark \\
 eletrocardiógrafo & e*le*tro*car*di-ó*gra*fo \xmark & e*le*tro*car*di*ó*gra*fo \cmark \\
@@
 eletroquímica & e*le*tro-quí*mi*ca \xmark & e*le*tro*quí*mi*ca \cmark \\
+eletroquímico & e*le*tro-quí*mi*co \xmark & e*le*tro*quí*mi*co \cmark \\
 elogiável & e*lo*gi-á*vel \xmark & e*lo*gi*á*vel \cmark \\
@@
 embrião & em*bri-ão \xmark & em*bri*ão \cmark \\
+endodôntico & en*do-dôn*ti*co \xmark & en*do*dôn*ti*co \cmark \\
 ensaísmo & en*sa-ís*mo \xmark & en*sa*ís*mo \cmark \\
 ensaísta & en*sa-ís*ta \xmark & en*sa*ís*ta \cmark \\
+ensaística & en*sa-ís*ti*ca \xmark & en*sa*ís*ti*ca \cmark \\
+ensaístico & en*sa-ís*ti*co \xmark & en*sa*ís*ti*co \cmark \\
 entusiástico & en*tu*si-ás*ti*co \xmark & en*tu*si*ás*ti*co \cmark \\
@@
 éon & é-on \xmark & é*on \cmark \\
+epicôndilo & e*pi-côn*di*lo \xmark & e*pi*côn*di*lo \cmark \\
+epifenômeno & e*pi*fe-nô*me*no \xmark & e*pi*fe*nô*me*no \cmark \\
+epônimo & e-pô*ni*mo \xmark & e*pô*ni*mo \cmark \\
 equânime & e-quâ*ni*me \xmark & e*quâ*ni*me \cmark \\
 equívoco & e-quí*vo*co \xmark & e*quí*vo*co \cmark \\
+ergômetro & er-gô*me*tro \xmark & er*gô*me*tro \cmark \\
 ergonômico & er*go-nô*mi*co \xmark & er*go*nô*mi*co \cmark \\
@@
 esfigmomanômetro & es*fig*mo*ma-nô*me*tro \xmark & es*fig*mo*ma*nô*me*tro \cmark \\
+esfiha & es*fi-ha \xmark & es*fi-ha \xmark \\
+esôfago & e-sô*fa*go \xmark & e*sô*fa*go \cmark \\
+espadaúdo & es*pa*da-ú*do \xmark & es*pa*da*ú*do \cmark \\
+espectrofotômetro & es*pec*tro*fo-tô*me*tro \xmark & es*pec*tro*fo*tô*me*tro \cmark \\
+espeleólogo & es*pe*le-ó*lo*go \xmark & es*pe*le*ó*lo*go \cmark \\
 espião & es*pi-ão \xmark & es*pi*ão \cmark \\
-esponsais & es*pon*sa-is \xmark & es*pon*sa-is \xmark \\
 esquálido & es-quá*li*do \xmark & es*quá*li*do \cmark \\
 esteárico & es*te-á*ri*co \xmark & es*te*á*ri*co \cmark \\
+estereóbata & es*te*re-ó*ba*ta \xmark & es*te*re*ó*ba*ta \cmark \\
+estereoquímica & es*te*re*o-quí*mi*ca \xmark & es*te*re*o*quí*mi*ca \cmark \\
+estereoquímico & es*te*re*o-quí*mi*co \xmark & es*te*re*o*quí*mi*co \cmark \\
 estereótipo & es*te*re-ó*ti*po \xmark & es*te*re*ó*ti*po \cmark \\
@@
 etíope & e*tí-o*pe \xmark & e*tí*o*pe \cmark \\
+etiópico & e*ti-ó*pi*co \xmark & e*ti*ó*pi*co \cmark \\
 etnônimo & et-nô*ni*mo \xmark & et*nô*ni*mo \cmark \\
 eucariótico & eu*ca*ri-ó*ti*co \xmark & eu*ca*ri*ó*ti*co \cmark \\
+eufônico & eu-fô*ni*co \xmark & eu*fô*ni*co \cmark \\
 eurasiático & eu*ra*si-á*ti*co \xmark & eu*ra*si*á*ti*co \cmark \\
+europeísmo & eu*ro*pe-ís*mo \xmark & eu*ro*pe*ís*mo \cmark \\
+europeísta & eu*ro*pe-ís*ta \xmark & eu*ro*pe*ís*ta \cmark \\
 evoluído & e*vo*lu-í*do \xmark & e*vo*lu*í*do \cmark \\
@@
 faísca & fa-ís*ca \xmark & fa*ís*ca \cmark \\
+faiscante & fa-is*can*te \xmark & fa-is*can*te \xmark \\
+faiscar & fa-is*car \xmark & fa-is*car \xmark \\
+faraônico & fa*ra-ô*ni*co \xmark & fa*ra*ô*ni*co \cmark \\
 farisaísmo & fa*ri*sa-ís*mo \xmark & fa*ri*sa*ís*mo \cmark \\
+fascíola & fas*cí-o*la \xmark & fas*cí*o*la \cmark \\
 faúlha & fa-ú*lha \xmark & fa*ú*lha \cmark \\
@@
 fenômeno & fe-nô*me*no \xmark & fe*nô*me*no \cmark \\
+feroês & fe*ro-ês \xmark & fe*ro*ês \cmark \\
 fiável & fi-á*vel \xmark & fi*á*vel \cmark \\
@@
 fisiólogo & fi*si-ó*lo*go \xmark & fi*si*ó*lo*go \cmark \\
+fitoquímica & fi*to-quí*mi*ca \xmark & fi*to*quí*mi*ca \cmark \\
 fiúza & fi-ú*za \xmark & fi*ú*za \cmark \\
@@
 folião & fo*li-ão \xmark & fo*li*ão \cmark \\
+folíolo & fo*lí-o*lo \xmark & fo*lí*o*lo \cmark \\
+fonoaudiólogo & fo*no*au*di-ó*lo*go \xmark & fo*no*au*di*ó*lo*go \cmark \\
 formaldeído & for*mal*de-í*do \xmark & for*mal*de*í*do \cmark \\
+fotômetro & fo-tô*me*tro \xmark & fo*tô*me*tro \cmark \\
+fotoperíodo & fo*to*pe*rí-o*do \xmark & fo*to*pe*rí*o*do \cmark \\
 fotoquímica & fo*to-quí*mi*ca \xmark & fo*to*quí*mi*ca \cmark \\
 fotoquímico & fo*to-quí*mi*co \xmark & fo*to*quí*mi*co \cmark \\
+franqueável & fran*que-á*vel \xmark & fran*que*á*vel \cmark \\
 freático & fre-á*ti*co \xmark & fre*á*ti*co \cmark \\
@@
 fruir & fru-ir \xmark & fru*ir \cmark \\
+ftálico & f.tá*li*co \xmark & f.tá*li*co \xmark \\
 fuinha & fu-i*nha \xmark & fu*i*nha \cmark \\
@@
 galeão & ga*le-ão \xmark & ga*le*ão \cmark \\
+galvanômetro & gal*va-nô*me*tro \xmark & gal*va*nô*me*tro \cmark \\
+gasômetro & ga-sô*me*tro \xmark & ga*sô*me*tro \cmark \\
 gastrointestinal & gas*tro-in*tes*ti*nal \xmark & gas*tro*in*tes*ti*nal \cmark \\
 gastronômico & gas*tro-nô*mi*co \xmark & gas*tro*nô*mi*co \cmark \\
+gauchada & ga-u*cha*da \xmark & ga-u*cha*da \xmark \\
+gauchar & ga-u*char \xmark & ga-u*char \xmark \\
+gauchismo & ga-u*chis*mo \xmark & ga-u*chis*mo \xmark \\
 gaúcho & ga-ú*cho \xmark & ga*ú*cho \cmark \\
 gavião & ga*vi-ão \xmark & ga*vi*ão \cmark \\
+genômico & ge-nô*mi*co \xmark & ge*nô*mi*co \cmark \\
+genuinidade & ge*nu-i*ni*da*de \xmark & ge*nu*i*ni*da*de \cmark \\
 genuíno & ge*nu-í*no \xmark & ge*nu*í*no \cmark \\
+geófito & ge-ó*fi*to \xmark & ge*ó*fi*to \cmark \\
 geógrafo & ge-ó*gra*fo \xmark & ge*ó*gra*fo \cmark \\
 geólogo & ge-ó*lo*go \xmark & ge*ó*lo*go \cmark \\
+geômetra & ge-ô*me*tra \xmark & ge*ô*me*tra \cmark \\
+geoquímica & ge*o-quí*mi*ca \xmark & ge*o*quí*mi*ca \cmark \\
+geoquímico & ge*o-quí*mi*co \xmark & ge*o*quí*mi*co \cmark \\
+geotectônica & ge*o*tec-tô*ni*ca \xmark & ge*o*tec*tô*ni*ca \cmark \\
+geriátrico & ge*ri-á*tri*co \xmark & ge*ri*á*tri*co \cmark \\
+giardíase & gi*ar*dí-a*se \xmark & gi*ar*dí*a*se \cmark \\
 gigolô & gi*go-lô \xmark & gi*go*lô \cmark \\
@@
 gnóstico & g.nós*ti*co \xmark & gnós*ti*co \cmark \\
+gnu & g.nu \xmark & g.nu \xmark \\
+goês & go-ês \xmark & go*ês \cmark \\
 grafomaníaco & gra*fo*ma*ní-a*co \xmark & gra*fo*ma*ní*a*co \cmark \\
+grafômano & gra-fô*ma*no \xmark & gra*fô*ma*no \cmark \\
 grapiúna & gra*pi-ú*na \xmark & gra*pi*ú*na \cmark \\
+gratuidade & gra*tu-i*da*de \xmark & gra*tu-i*da*de \xmark \\
 graúdo & gra-ú*do \xmark & gra*ú*do \cmark \\
 graúna & gra-ú*na \xmark & gra*ú*na \cmark \\
+graxaim & gra*xa-im \xmark & gra*xa-im \xmark \\
+gruiforme & gru-i*for*me \xmark & gru-i*for*me \xmark \\
+guaíba & gua-í*ba \xmark & gua*í*ba \cmark \\
 guardião & guar*di-ão \xmark & guar*di*ão \cmark \\
@@
 hebraísta & he*bra-ís*ta \xmark & he*bra*ís*ta \cmark \\
+hedônico & he-dô*ni*co \xmark & he*dô*ni*co \cmark \\
 hegemônico & he*ge-mô*ni*co \xmark & he*ge*mô*ni*co \cmark \\
@@
 heliógrafo & he*li-ó*gra*fo \xmark & he*li*ó*gra*fo \cmark \\
+hematopoiético & he*ma*to*poi-é*ti*co \xmark & he*ma*to*poi*é*ti*co \cmark \\
 hemodiálise & he*mo*di-á*li*se \xmark & he*mo*di*á*li*se \cmark \\
+henoteísmo & he*no*te-ís*mo \xmark & he*no*te*ís*mo \cmark \\
+henoteísta & he*no*te-ís*ta \xmark & he*no*te*ís*ta \cmark \\
 heptacampeão & hep*ta*cam*pe-ão \xmark & hep*ta*cam*pe*ão \cmark \\
@@
 hidropônico & hi*dro-pô*ni*co \xmark & hi*dro*pô*ni*co \cmark \\
+higiénico & hi*gi-é*ni*co \xmark & hi*gi*é*ni*co \cmark \\
+hilozoísmo & hi*lo*zo-ís*mo \xmark & hi*lo*zo*ís*mo \cmark \\
 hinduísmo & hin*du-ís*mo \xmark & hin*du*ís*mo \cmark \\
+hinduísta & hin*du-ís*ta \xmark & hin*du*ís*ta \cmark \\
+hipersônico & hi*per-sô*ni*co \xmark & hi*per*sô*ni*co \cmark \\
+hipertônico & hi*per-tô*ni*co \xmark & hi*per*tô*ni*co \cmark \\
 hipocondríaco & hi*po*con*drí-a*co \xmark & hi*po*con*drí*a*co \cmark \\
+hipomaníaco & hi*po*ma*ní-a*co \xmark & hi*po*ma*ní*a*co \cmark \\
 hipônimo & hi-pô*ni*mo \xmark & hi*pô*ni*mo \cmark \\
+hipotônico & hi*po-tô*ni*co \xmark & hi*po*tô*ni*co \cmark \\
 histoquímica & his*to-quí*mi*ca \xmark & his*to*quí*mi*ca \cmark \\
+historiógrafo & his*to*ri-ó*gra*fo \xmark & his*to*ri*ó*gra*fo \cmark \\
+histrião & his*tri-ão \xmark & his*tri*ão \cmark \\
+hodômetro & ho-dô*me*tro \xmark & ho*dô*me*tro \cmark \\
+holonômico & ho*lo-nô*mi*co \xmark & ho*lo*nô*mi*co \cmark \\
+homofônico & ho*mo-fô*ni*co \xmark & ho*mo*fô*ni*co \cmark \\
 homônimo & ho-mô*ni*mo \xmark & ho*mô*ni*mo \cmark \\
+ião & i-ão \xmark & i*ão \cmark \\
+iatroquímica & i*a*tro-quí*mi*ca \xmark & i*a*tro*quí*mi*ca \cmark \\
+icônico & i-cô*ni*co \xmark & i*cô*ni*co \cmark \\
 ictiólogo & ic*ti-ó*lo*go \xmark & ic*ti*ó*lo*go \cmark \\
 ideólogo & i*de-ó*lo*go \xmark & i*de*ó*lo*go \cmark \\
+idiótico & i*di-ó*ti*co \xmark & i*di*ó*ti*co \cmark \\
 iídiche & i-í*di*che \xmark & i*í*di*che \cmark \\
+ileíte & i*le-í*te \xmark & i*le*í*te \cmark \\
 ilíaco & i*lí-a*co \xmark & i*lí*a*co \cmark \\
@@
 imbuir & im*bu-ir \xmark & im*bu*ir \cmark \\
+imiscuir & i*mis*cu-ir \xmark & i*mis*cu*ir \cmark \\
+impatriótico & im*pa*tri-ó*ti*co \xmark & im*pa*tri*ó*ti*co \cmark \\
 imperdoável & im*per*do-á*vel \xmark & im*per*do*á*vel \cmark \\
+impermeável & im*per*me-á*vel \xmark & im*per*me*á*vel \cmark \\
 impronunciável & im*pro*nun*ci-á*vel \xmark & im*pro*nun*ci*á*vel \cmark \\
 inadiável & i*na*di-á*vel \xmark & i*na*di*á*vel \cmark \\
+inclinômetro & in*cli-nô*me*tro \xmark & in*cli*nô*me*tro \cmark \\
 incluir & in*clu-ir \xmark & in*clu*ir \cmark \\
@@
 indeiscente & in*de-is*cen*te \xmark & in*de-is*cen*te \xmark \\
+indissociável & in*dis*so*ci-á*vel \xmark & in*dis*so*ci*á*vel \cmark \\
 inegociável & i*ne*go*ci-á*vel \xmark & i*ne*go*ci*á*vel \cmark \\
@@
 insaciável & in*sa*ci-á*vel \xmark & in*sa*ci*á*vel \cmark \\
+instituição & ins*ti*tu-i*ção \xmark & ins*ti*tu*i*ção \cmark \\
 instituído & ins*ti*tu-í*do \xmark & ins*ti*tu*í*do \cmark \\
+instituidor & ins*ti*tu-i*dor \xmark & ins*ti*tu-i*dor \xmark \\
 instituir & ins*ti*tu-ir \xmark & ins*ti*tu*ir \cmark \\
@@
 intercambiável & in*ter*cam*bi-á*vel \xmark & in*ter*cam*bi*á*vel \cmark \\
+interferômetro & in*ter*fe-rô*me*tro \xmark & in*ter*fe*rô*me*tro \cmark \\
 interoceânico & in*te*ro*ce-â*ni*co \xmark & in*te*ro*ce*â*ni*co \cmark \\
@@
 intuir & in*tu-ir \xmark & in*tu*ir \cmark \\
-intuitivo & in*tu-i*ti*vo \xmark & in*tu-i*ti*vo \xmark \\
 invariável & in*va*ri-á*vel \xmark & in*va*ri*á*vel \cmark \\
@@
 iódico & i-ó*di*co \xmark & i*ó*di*co \cmark \\
+íon & í-on \xmark & í*on \cmark \\
+iraúna & i*ra-ú*na \xmark & i*ra*ú*na \cmark \\
 irônico & i-rô*ni*co \xmark & i*rô*ni*co \cmark \\
@@
 irrefreável & ir*re*fre-á*vel \xmark & ir*re*fre*á*vel \cmark \\
+irreligião & ir*re*li*gi-ão \xmark & ir*re*li*gi*ão \cmark \\
 irremediável & ir*re*me*di-á*vel \xmark & ir*re*me*di*á*vel \cmark \\
@@
 irretorquível & ir*re*tor-quí*vel \xmark & ir*re*tor*quí*vel \cmark \\
+isômero & i-sô*me*ro \xmark & i*sô*me*ro \cmark \\
 isotônico & i*so-tô*ni*co \xmark & i*so*tô*ni*co \cmark \\
+isquêmico & is-quê*mi*co \xmark & is*quê*mi*co \cmark \\
+isquiático & is*qui-á*ti*co \xmark & is*qui*á*ti*co \cmark \\
+itaimbé & i*ta-im*bé \xmark & i*ta-im*bé \xmark \\
+itapiúna & i*ta*pi-ú*na \xmark & i*ta*pi*ú*na \cmark \\
+itaúba & i*ta-ú*ba \xmark & i*ta*ú*ba \cmark \\
 jabô & ja-bô \xmark & ja*bô \cmark \\
+janaúba & ja*na-ú*ba \xmark & ja*na*ú*ba \cmark \\
+jandaíra & jan*da-í*ra \xmark & jan*da*í*ra \cmark \\
+jataúba & ja*ta-ú*ba \xmark & ja*ta*ú*ba \cmark \\
 jesuíta & je*su-í*ta \xmark & je*su*í*ta \cmark \\
@@
 jesuitismo & je*su-i*tis*mo \xmark & je*su*i*tis*mo \cmark \\
+jihadista & ji-ha*dis*ta \xmark & ji-ha*dis*ta \xmark \\
 joinvilense & jo-in*vi*len*se \xmark & jo*in*vi*len*se \cmark \\
@@
 lamaísmo & la*ma-ís*mo \xmark & la*ma*ís*mo \cmark \\
+lamaísta & la*ma-ís*ta \xmark & la*ma*ís*ta \cmark \\
 lampião & lam*pi-ão \xmark & lam*pi*ão \cmark \\
@@
 legião & le*gi-ão \xmark & le*gi*ão \cmark \\
+leônico & le-ô*ni*co \xmark & le*ô*ni*co \cmark \\
+lidocaína & li*do*ca-í*na \xmark & li*do*ca*í*na \cmark \\
+liechtensteinense & li*e.ch*tens*tei*nen*se \xmark & li*e.ch*tens*tei*nen*se \xmark \\
 litíase & li*tí-a*se \xmark & li*tí*a*se \cmark \\
+ludião & lu*di-ão \xmark & lu*di*ão \cmark \\
 luís & lu-ís \xmark & lu*ís \cmark \\
@@
 macaúba & ma*ca-ú*ba \xmark & ma*ca*ú*ba \cmark \\
+macedônico & ma*ce-dô*ni*co \xmark & ma*ce*dô*ni*co \cmark \\
 maçônico & ma-çô*ni*co \xmark & ma*çô*ni*co \cmark \\
@@
 macrorregião & ma*cror*re*gi-ão \xmark & ma*cror*re*gi*ão \cmark \\
+magnetômetro & mag*ne-tô*me*tro \xmark & mag*ne*tô*me*tro \cmark \\
 maiólica & mai-ó*li*ca \xmark & mai*ó*li*ca \cmark \\
@@
 maleável & ma*le-á*vel \xmark & ma*le*á*vel \cmark \\
+maléolo & ma*lé-o*lo \xmark & ma*lé*o*lo \cmark \\
+malônico & ma-lô*ni*co \xmark & ma*lô*ni*co \cmark \\
 malthusianismo & mal-thu*si*a*nis*mo \xmark & mal-thu*si*a*nis*mo \xmark \\
@@
 medíocre & me*dí-o*cre \xmark & me*dí*o*cre \cmark \\
+mediúnico & me*di-ú*ni*co \xmark & me*di*ú*ni*co \cmark \\
+mediunidade & me*di-u*ni*da*de \xmark & me*di*u*ni*da*de \cmark \\
 megalomaníaco & me*ga*lo*ma*ní-a*co \xmark & me*ga*lo*ma*ní*a*co \cmark \\
+megalômano & me*ga-lô*ma*no \xmark & me*ga*lô*ma*no \cmark \\
 megawatt & me*ga-watt \xmark & me*ga-watt \xmark \\
+meiótico & mei-ó*ti*co \xmark & mei*ó*ti*co \cmark \\
+melômano & me-lô*ma*no \xmark & me*lô*ma*no \cmark \\
 meteórico & me*te-ó*ri*co \xmark & me*te*ó*ri*co \cmark \\
 microbiólogo & mi*cro*bi-ó*lo*go \xmark & mi*cro*bi*ó*lo*go \cmark \\
+microrregião & mi*cror*re*gi-ão \xmark & mi*cror*re*gi*ão \cmark \\
 micuim & mi*cu-im \xmark & mi*cu-im \xmark \\
 midríase & mi*drí-a*se \xmark & mi*drí*a*se \cmark \\
+miíase & mi-í-a*se \xmark & mi*í*a*se \cmark \\
 mimeógrafo & mi*me-ó*gra*fo \xmark & mi*me*ó*gra*fo \cmark \\
+ministeriável & mi*nis*te*ri-á*vel \xmark & mi*nis*te*ri*á*vel \cmark \\
 míope & mí-o*pe \xmark & mí*o*pe \cmark \\
 miríade & mi*rí-a*de \xmark & mi*rí*a*de \cmark \\
+miúdas & mi-ú*das \xmark & mi*ú*das \cmark \\
+miudeza & mi-u*de*za \xmark & mi*u*de*za \cmark \\
 miúdo & mi-ú*do \xmark & mi*ú*do \cmark \\
@@
 moinho & mo-i*nho \xmark & mo*i*nho \cmark \\
+monofônico & mo*no-fô*ni*co \xmark & mo*no*fô*ni*co \cmark \\
 monomaníaco & mo*no*ma*ní-a*co \xmark & mo*no*ma*ní*a*co \cmark \\
 monômero & mo-nô*me*ro \xmark & mo*nô*me*ro \cmark \\
+monoquíni & mo*no-quí*ni \xmark & mo*no*quí*ni \cmark \\
 monoteísmo & mo*no*te-ís*mo \xmark & mo*no*te*ís*mo \cmark \\
@@
 morrião & mor*ri-ão \xmark & mor*ri*ão \cmark \\
+mortuárias & mor*tu-á*ri*as \xmark & mor*tu*á*ri*as \cmark \\
 mucuim & mu*cu-im \xmark & mu*cu-im \xmark \\
+muriático & mu*ri-á*ti*co \xmark & mu*ri*á*ti*co \cmark \\
 museólogo & mu*se-ó*lo*go \xmark & mu*se*ó*lo*go \cmark \\
+nagô & na-gô \xmark & na*gô \cmark \\
 napoleão & na*po*le-ão \xmark & na*po*le*ão \cmark \\
 neerlandês & ne*er*lan*dês \cmark & ne*er*lan*dês \cmark \\
+nefrolitíase & ne*fro*li*tí-a*se \xmark & ne*fro*li*tí*a*se \cmark \\
+negligenciável & ne*gli*gen*ci-á*vel \xmark & ne*gli*gen*ci*á*vel \cmark \\
+neocapitalismo & ne*o*ca*pi*ta*lis*mo \cmark & ne-o*ca*pi*ta*lis*mo \xmark \\
+neoclassicismo & ne*o*clas*si*cis*mo \cmark & ne-o*clas*si*cis*mo \xmark \\
+neoclássico & ne*o*clás*si*co \cmark & ne-o*clás*si*co \xmark \\
 neocolonialismo & ne*o*co*lo*ni*a*lis*mo \cmark & ne-o*co*lo*ni*a*lis*mo \xmark \\
+neodarwinismo & ne*o*dar-wi*nis*mo \xmark & ne-o*dar-wi*nis*mo \xmark \\
+neofascismo & ne*o*fas*cis*mo \cmark & ne-o*fas*cis*mo \xmark \\
 neofascista & ne*o*fas*cis*ta \cmark & ne-o*fas*cis*ta \xmark \\
 neófito & ne-ó*fi*to \xmark & ne*ó*fi*to \cmark \\
+neogótico & ne*o*gó*ti*co \cmark & ne-o*gó*ti*co \xmark \\
+neokantismo & ne*o*kan*tis*mo \cmark & ne-o*kan*tis*mo \xmark \\
 neolatino & ne*o*la*ti*no \cmark & ne-o*la*ti*no \xmark \\
@@
 neologismo & ne*o*lo*gis*mo \cmark & ne-o*lo*gis*mo \xmark \\
+neologista & ne*o*lo*gis*ta \cmark & ne-o*lo*gis*ta \xmark \\
+neonatal & ne*o*na*tal \cmark & ne-o*na*tal \xmark \\
+neonatologista & ne*o*na*to*lo*gis*ta \cmark & ne-o*na*to*lo*gis*ta \xmark \\
 neonato & ne*o*na*to \cmark & ne-o*na*to \xmark \\
@@
 néon & né-on \xmark & né*on \cmark \\
+neoplásico & ne*o*plá*si*co \cmark & ne-o*plá*si*co \xmark \\
+neoplasma & ne*o*plas*ma \cmark & ne-o*plas*ma \xmark \\
+neoplatônico & ne*o*pla-tô*ni*co \xmark & ne-o*pla*tô*ni*co \xmark \\
 neoplatonismo & ne*o*pla*to*nis*mo \cmark & ne-o*pla*to*nis*mo \xmark \\
+neopositivismo & ne*o*po*si*ti*vis*mo \cmark & ne-o*po*si*ti*vis*mo \xmark \\
+neotomismo & ne*o*to*mis*mo \cmark & ne-o*to*mis*mo \xmark \\
+neotrópico & ne*o*tró*pi*co \cmark & ne-o*tró*pi*co \xmark \\
 neozelandês & ne*o*ze*lan*dês \cmark & ne-o*ze*lan*dês \xmark \\
@@
 ninfomaníaco & nin*fo*ma*ní-a*co \xmark & nin*fo*ma*ní*a*co \cmark \\
+nipônico & ni-pô*ni*co \xmark & ni*pô*ni*co \cmark \\
 nobiliárquico & no*bi*li-ár*qui*co \xmark & no*bi*li*ár*qui*co \cmark \\
+noético & no-é*ti*co \xmark & no*é*ti*co \cmark \\
+nucléolo & nu*clé-o*lo \xmark & nu*clé*o*lo \cmark \\
 núpcias & núp*ci.as \xmark & núp*ci.as \xmark \\
+oásis & o-á*sis \xmark & o*á*sis \cmark \\
 oboísta & o*bo-ís*ta \xmark & o*bo*ís*ta \cmark \\
@@
 odômetro & o-dô*me*tro \xmark & o*dô*me*tro \cmark \\
+ofurô & o*fu-rô \xmark & o*fu*rô \cmark \\
 oleícola & o*le-í*co*la \xmark & o*le*í*co*la \cmark \\
@@
 olimpíada & o*lim*pí-a*da \xmark & o*lim*pí*a*da \cmark \\
+omíada & o*mí-a*da \xmark & o*mí*a*da \cmark \\
 oócito & o-ó*ci*to \xmark & o*ó*ci*to \cmark \\
+oólito & o-ó*li*to \xmark & o*ó*li*to \cmark \\
 opinião & o*pi*ni-ão \xmark & o*pi*ni*ão \cmark \\
 orfeão & or*fe-ão \xmark & or*fe*ão \cmark \\
+orgiástico & or*gi-ás*ti*co \xmark & or*gi*ás*ti*co \cmark \\
 oriundo & o*ri-un*do \xmark & o*ri*un*do \cmark \\
@@
 osteíte & os*te-í*te \xmark & os*te*í*te \cmark \\
+ostíolo & os*tí-o*lo \xmark & os*tí*o*lo \cmark \\
+oxiácido & o*xi-á*ci*do \xmark & o*xi*á*ci*do \cmark \\
 painço & pa-in*ço \xmark & pa-in*ço \xmark \\
+painho & pa-i*nho \xmark & pa*i*nho \cmark \\
 país & pa-ís \xmark & pa*ís \cmark \\
 paleógrafo & pa*le-ó*gra*fo \xmark & pa*le*ó*gra*fo \cmark \\
+paleólogo & pa*le-ó*lo*go \xmark & pa*le*ó*lo*go \cmark \\
+pancreático & pan*cre-á*ti*co \xmark & pan*cre*á*ti*co \cmark \\
+panenteísmo & pa*nen*te-ís*mo \xmark & pa*nen*te*ís*mo \cmark \\
+panô & pa-nô \xmark & pa*nô \cmark \\
 pantagruélico & pan*ta*gru-é*li*co \xmark & pan*ta*gru*é*li*co \cmark \\
+pantaleão & pan*ta*le-ão \xmark & pan*ta*le*ão \cmark \\
 panteão & pan*te-ão \xmark & pan*te*ão \cmark \\
@@
 panteísta & pan*te-ís*ta \xmark & pan*te*ís*ta \cmark \\
+papaína & pa*pa-í*na \xmark & pa*pa*í*na \cmark \\
 paquímetro & pa-quí*me*tro \xmark & pa*quí*me*tro \cmark \\
@@
 paraíso & pa*ra-í*so \xmark & pa*ra*í*so \cmark \\
+paralipômenos & pa*ra*li-pô*me*nos \xmark & pa*ra*li*pô*me*nos \cmark \\
 parnaíba & par*na-í*ba \xmark & par*na*í*ba \cmark \\
@@
 pediátrico & pe*di-á*tri*co \xmark & pe*di*á*tri*co \cmark \\
+pentacampeão & pen*ta*cam*pe-ão \xmark & pen*ta*cam*pe*ão \cmark \\
+péon & pé-on \xmark & pé*on \cmark \\
 perdoável & per*do-á*vel \xmark & per*do*á*vel \cmark \\
+perequê & pe*re-quê \xmark & pe*re*quê \cmark \\
 periódico & pe*ri-ó*di*co \xmark & pe*ri*ó*di*co \cmark \\
@@
 picuinha & pi*cu-i*nha \xmark & pi*cu*i*nha \cmark \\
+píer & pí-er \xmark & pí*er \cmark \\
 pindaíba & pin*da-í*ba \xmark & pin*da*í*ba \cmark \\
 pintainho & pin*ta-i*nho \xmark & pin*ta*i*nho \cmark \\
+píon & pí-on \xmark & pí*on \cmark \\
+piquê & pi-quê \xmark & pi*quê \cmark \\
+pirelióforo & pi*re*li-ó*fo*ro \xmark & pi*re*li*ó*fo*ro \cmark \\
 piromaníaco & pi*ro*ma*ní-a*co \xmark & pi*ro*ma*ní*a*co \cmark \\
+pirômetro & pi-rô*me*tro \xmark & pi*rô*me*tro \cmark \\
 pitiríase & pi*ti*rí-a*se \xmark & pi*ti*rí*a*se \cmark \\
@@
 pixaim & pi*xa-im \xmark & pi*xa-im \xmark \\
+planctônico & planc-tô*ni*co \xmark & planc*tô*ni*co \cmark \\
 platônico & pla-tô*ni*co \xmark & pla*tô*ni*co \cmark \\
@@
 plebeísmo & ple*be-ís*mo \xmark & ple*be*ís*mo \cmark \\
+pneuma & p.neu*ma \xmark & pneu*ma \cmark \\
 pneumática & p.neu*má*ti*ca \xmark & pneu*má*ti*ca \cmark \\
@@
 pneumogástrico & p.neu*mo*gás*tri*co \xmark & pneu*mo*gás*tri*co \cmark \\
+pneumologista & p.neu*mo*lo*gis*ta \xmark & pneu*mo*lo*gis*ta \cmark \\
 pneumônico & p.neu-mô*ni*co \xmark & pneu*mô*ni*co \cmark \\
+pneumonite & p.neu*mo*ni*te \xmark & pneu*mo*ni*te \cmark \\
 pneumotórax & p.neu*mo*tó*rax \xmark & pneu*mo*tó*rax \cmark \\
@@
 politeísta & po*li*te-ís*ta \xmark & po*li*te*ís*ta \cmark \\
+politiquês & po*li*ti-quês \xmark & po*li*ti*quês \cmark \\
+poliuretano & po*li-u*re*ta*no \xmark & po*li*u*re*ta*no \cmark \\
+poluição & po*lu-i*ção \xmark & po*lu*i*ção \cmark \\
+poluidor & po*lu-i*dor \xmark & po*lu-i*dor \xmark \\
 poluir & po*lu-ir \xmark & po*lu*ir \cmark \\
 poraquê & po*ra-quê \xmark & po*ra*quê \cmark \\
+porciúncula & por*ci-ún*cu*la \xmark & por*ci*ún*cu*la \cmark \\
 pornô & por-nô \xmark & por*nô \cmark \\
@@
 presidenciável & pre*si*den*ci-á*vel \xmark & pre*si*den*ci*á*vel \cmark \\
+priápico & pri-á*pi*co \xmark & pri*á*pi*co \cmark \\
+príon & prí-on \xmark & prí*on \cmark \\
 procaína & pro*ca-í*na \xmark & pro*ca*í*na \cmark \\
 procariótico & pro*ca*ri-ó*ti*co \xmark & pro*ca*ri*ó*ti*co \cmark \\
+procônsul & pro-côn*sul \xmark & pro*côn*sul \cmark \\
+proibição & pro-i*bi*ção \xmark & pro*i*bi*ção \cmark \\
+proibido & pro-i*bi*do \xmark & pro*i*bi*do \cmark \\
+proibir & pro-i*bir \xmark & pro*i*bir \cmark \\
+proibitivo & pro-i*bi*ti*vo \xmark & pro*i*bi*ti*vo \cmark \\
 prolegômenos & pro*le-gô*me*nos \xmark & pro*le*gô*me*nos \cmark \\
+pronunciável & pro*nun*ci-á*vel \xmark & pro*nun*ci*á*vel \cmark \\
 prosaísmo & pro*sa-ís*mo \xmark & pro*sa*ís*mo \cmark \\
 prostituição & pros*ti*tu-i*ção \xmark & pros*ti*tu*i*ção \cmark \\
+prostituído & pros*ti*tu-í*do \xmark & pros*ti*tu*í*do \cmark \\
 prostituir & pros*ti*tu-ir \xmark & pros*ti*tu*ir \cmark \\
@@
 proteólise & pro*te-ó*li*se \xmark & pro*te*ó*li*se \cmark \\
+pseudocientífico & p.seu*do*ci*en*tí*fi*co \xmark & pseu*do*ci*en*tí*fi*co \cmark \\
+pseudofruto & p.seu*do*fru*to \xmark & pseu*do*fru*to \cmark \\
 pseudônimo & p.seu-dô*ni*mo \xmark & pseu*dô*ni*mo \cmark \\
+psicadélico & p.si*ca*dé*li*co \xmark & psi*ca*dé*li*co \cmark \\
 psicanálise & p.si*ca*ná*li*se \xmark & psi*ca*ná*li*se \cmark \\
@@
 psicanalítico & p.si*ca*na*lí*ti*co \xmark & psi*ca*na*lí*ti*co \cmark \\
+psicoativo & p.si*co*a*ti*vo \xmark & psi*co*a*ti*vo \cmark \\
+psicodélico & p.si*co*dé*li*co \xmark & psi*co*dé*li*co \cmark \\
+psicodelismo & p.si*co*de*lis*mo \xmark & psi*co*de*lis*mo \cmark \\
 psicodrama & p.si*co*dra*ma \xmark & psi*co*dra*ma \cmark \\
+psicofísico & p.si*co*fí*si*co \xmark & psi*co*fí*si*co \cmark \\
 psicógrafo & p.si*có*gra*fo \xmark & psi*có*gra*fo \cmark \\
 psicolinguista & p.si*co*lin*guis*ta \xmark & psi*co*lin*guis*ta \cmark \\
+psicolinguística & p.si*co*lin*guís*ti*ca \xmark & psi*co*lin*guís*ti*ca \cmark \\
 psicologicamente & p.si*co*lo*gi*ca*men*te \xmark & psi*co*lo*gi*ca*men*te \cmark \\
@@
 psicomotricidade & p.si*co*mo*tri*ci*da*de \xmark & psi*co*mo*tri*ci*da*de \cmark \\
+psicomotricista & p.si*co*mo*tri*cis*ta \xmark & psi*co*mo*tri*cis*ta \cmark \\
 psicopata & p.si*co*pa*ta \xmark & psi*co*pa*ta \cmark \\
@@
 psicopedagogo & p.si*co*pe*da*go*go \xmark & psi*co*pe*da*go*go \cmark \\
+psicopompo & p.si*co*pom*po \xmark & psi*co*pom*po \cmark \\
 psicose & p.si*co*se \xmark & psi*co*se \cmark \\
 psicossexual & p.si*cos*se*xu*al \xmark & psi*cos*se*xu*al \cmark \\
+psicossomática & p.si*cos*so*má*ti*ca \xmark & psi*cos*so*má*ti*ca \cmark \\
 psicossomático & p.si*cos*so*má*ti*co \xmark & psi*cos*so*má*ti*co \cmark \\
@@
 psicoterapeuta & p.si*co*te*ra*peu*ta \xmark & psi*co*te*ra*peu*ta \cmark \\
+psicoterapêutico & p.si*co*te*ra*pêu*ti*co \xmark & psi*co*te*ra*pêu*ti*co \cmark \\
 psicoterápico & p.si*co*te*rá*pi*co \xmark & psi*co*te*rá*pi*co \cmark \\
@@
 psoríase & p.so*rí-a*se \xmark & p.so*rí*a*se \xmark \\
+pterodáctilo & p.te*ro*dác*ti*lo \xmark & pte*ro*dác*ti*lo \cmark \\
 pterossauro & p.te*ros*sau*ro \xmark & pte*ros*sau*ro \cmark \\
+ptialina & p.ti*a*li*na \xmark & pti*a*li*na \cmark \\
+ptolemaico & p.to*le*mai*co \xmark & pto*le*mai*co \cmark \\
 ptose & p.to*se \xmark & pto*se \cmark \\
+puído & pu-í*do \xmark & pu*í*do \cmark \\
 pulôver & pu-lô*ver \xmark & pu*lô*ver \cmark \\
+putrião & pu*tri-ão \xmark & pu*tri*ão \cmark \\
 quartzito & quart*zi*to \cmark & quart*zi*to \cmark \\
 quartzo & quart*zo \cmark & quart*zo \cmark \\
+quaternião & qua*ter*ni-ão \xmark & qua*ter*ni*ão \cmark \\
 questiúncula & ques*ti-ún*cu*la \xmark & ques*ti*ún*cu*la \cmark \\
+quiáltera & qui-ál*te*ra \xmark & qui*ál*te*ra \cmark \\
+quilohertz & qui*lo-hertz \xmark & qui*lo-hertz \xmark \\
 quilômetro & qui-lô*me*tro \xmark & qui*lô*me*tro \cmark \\
@@
 radiólise & ra*di-ó*li*se \xmark & ra*di*ó*li*se \cmark \\
+radioquímica & ra*di*o-quí*mi*ca \xmark & ra*di*o*quí*mi*ca \cmark \\
 rainha & ra-i*nha \xmark & ra*i*nha \cmark \\
@@
 reconstruir & re*cons*tru-ir \xmark & re*cons*tru*ir \cmark \\
+redemoinho & re*de*mo-i*nho \xmark & re*de*mo*i*nho \cmark \\
 redistribuir & re*dis*tri*bu-ir \xmark & re*dis*tri*bu*ir \cmark \\
@@
 reintegrar & re-in*te*grar \xmark & re*in*te*grar \cmark \\
+reinterpretação & re-in*ter*pre*ta*ção \xmark & re*in*ter*pre*ta*ção \cmark \\
+reinterpretar & re-in*ter*pre*tar \xmark & re*in*ter*pre*tar \cmark \\
 reintrodução & re-in*tro*du*ção \xmark & re*in*tro*du*ção \cmark \\
 reintroduzir & re-in*tro*du*zir \xmark & re*in*tro*du*zir \cmark \\
+reinvenção & re-in*ven*ção \xmark & re*in*ven*ção \cmark \\
 reinventar & re-in*ven*tar \xmark & re*in*ven*tar \cmark \\
@@
 religião & re*li*gi-ão \xmark & re*li*gi*ão \cmark \\
+remediável & re*me*di-á*vel \xmark & re*me*di*á*vel \cmark \\
 restituição & res*ti*tu-i*ção \xmark & res*ti*tu*i*ção \cmark \\
 restituir & res*ti*tu-ir \xmark & res*ti*tu*ir \cmark \\
+restituível & res*ti*tu-í*vel \xmark & res*ti*tu*í*vel \cmark \\
 retraído & re*tra-í*do \xmark & re*tra*í*do \cmark \\
@@
 reunir & re-u*nir \xmark & re-u*nir \xmark \\
+reurbanização & re-ur*ba*ni*za*ção \xmark & re-ur*ba*ni*za*ção \xmark \\
 reurbanizar & re-ur*ba*ni*zar \xmark & re-ur*ba*ni*zar \xmark \\
+reutilizar & re-u*ti*li*zar \xmark & re-u*ti*li*zar \xmark \\
 robô & ro-bô \xmark & ro*bô \cmark \\
+rodamoinho & ro*da*mo-i*nho \xmark & ro*da*mo*i*nho \cmark \\
 roído & ro-í*do \xmark & ro*í*do \cmark \\
@@
 rutherford & ru-ther*ford \xmark & ru-ther*ford \xmark \\
+saião & sai-ão \xmark & sai*ão \cmark \\
 saída & sa-í*da \xmark & sa*í*da \cmark \\
 saído & sa-í*do \xmark & sa*í*do \cmark \\
+sainha & sa-i*nha \xmark & sa*i*nha \cmark \\
+sainte & sa-in*te \xmark & sa-in*te \xmark \\
+saíra & sa-í*ra \xmark & sa*í*ra \cmark \\
 sair & sa-ir \xmark & sa*ir \cmark \\
 salomônico & sa*lo-mô*ni*co \xmark & sa*lo*mô*ni*co \cmark \\
+samaúma & sa*ma-ú*ma \xmark & sa*ma*ú*ma \cmark \\
 sambaíba & sam*ba-í*ba \xmark & sam*ba*í*ba \cmark \\
@@
 saquê & sa-quê \xmark & sa*quê \cmark \\
+sardônica & sar-dô*ni*ca \xmark & sar*dô*ni*ca \cmark \\
 sardônico & sar-dô*ni*co \xmark & sar*dô*ni*co \cmark \\
@@
 saúva & sa-ú*va \xmark & sa*ú*va \cmark \\
+saxônico & sa-xô*ni*co \xmark & sa*xô*ni*co \cmark \\
 sebastião & se*bas*ti-ão \xmark & se*bas*ti*ão \cmark \\
 semiárido & se*mi-á*ri*do \xmark & se*mi*á*ri*do \cmark \\
+semiólogo & se*mi-ó*lo*go \xmark & se*mi*ó*lo*go \cmark \\
+semiótica & se*mi-ó*ti*ca \xmark & se*mi*ó*ti*ca \cmark \\
+semiótico & se*mi-ó*ti*co \xmark & se*mi*ó*ti*co \cmark \\
+semipermeável & se*mi*per*me-á*vel \xmark & se*mi*per*me*á*vel \cmark \\
+setentrião & se*ten*tri-ão \xmark & se*ten*tri*ão \cmark \\
 siálico & si-á*li*co \xmark & si*á*li*co \cmark \\
+sicômoro & si-cô*mo*ro \xmark & si*cô*mo*ro \cmark \\
+sievert & si.e*vert \xmark & si.e*vert \xmark \\
 sinfônica & sin-fô*ni*ca \xmark & sin*fô*ni*ca \cmark \\
@@
 siríaco & si*rí-a*co \xmark & si*rí*a*co \cmark \\
+sismômetro & sis-mô*me*tro \xmark & sis*mô*me*tro \cmark \\
 sobressair & so*bres*sa-ir \xmark & so*bres*sa*ir \cmark \\
+sociável & so*ci-á*vel \xmark & so*ci*á*vel \cmark \\
 sociólogo & so*ci-ó*lo*go \xmark & so*ci*ó*lo*go \cmark \\
@@
 subaquático & su*ba-quá*ti*co \xmark & su*ba*quá*ti*co \cmark \\
+subatômico & su*ba-tô*mi*co \xmark & su*ba*tô*mi*co \cmark \\
 subdiácono & sub*di-á*co*no \xmark & sub*di*á*co*no \cmark \\
+sublevação & su.b-le*va*ção \xmark & sub*le*va*ção \cmark \\
+sublevado & su.b-le*va*do \xmark & sub*le*va*do \cmark \\
+sublevar & su.b-le*var \xmark & sub*le*var \cmark \\
+subliminal & su.b-li*mi*nal \xmark & su.b-li*mi*nal \xmark \\
 subliminar & su.b-li*mi*nar \xmark & su.b-li*mi*nar \xmark \\
+sublinear & su.b-li*ne*ar \xmark & su.b-li*ne*ar \xmark \\
 sublingual & su.b-lin*gual \xmark & su.b-lin*gual \xmark \\
@@
 sublunar & su.b-lu*nar \xmark & sub*lu*nar \cmark \\
+subluxação & su.b-lu*xa*ção \xmark & sub*lu*xa*ção \cmark \\
+subsônico & sub-sô*ni*co \xmark & sub*sô*ni*co \cmark \\
 substituição & subs*ti*tu-i*ção \xmark & subs*ti*tu*i*ção \cmark \\
 substituído & subs*ti*tu-í*do \xmark & subs*ti*tu*í*do \cmark \\
+substituinte & subs*ti*tu-in*te \xmark & subs*ti*tu*in*te \cmark \\
 substituir & subs*ti*tu-ir \xmark & subs*ti*tu*ir \cmark \\
@@
 suíça & su-í*ça \xmark & su*í*ça \cmark \\
+suicida & su-i*ci*da \xmark & su*i*ci*da \cmark \\
 suíço & su-í*ço \xmark & su*í*ço \cmark \\
+suingar & su-in*gar \xmark & su*in*gar \cmark \\
 suingue & su-in*gue \xmark & su*in*gue \cmark \\
+suinicultura & su-i*ni*cul*tu*ra \xmark & su*i*ni*cul*tu*ra \cmark \\
+suinocultura & su-i*no*cul*tu*ra \xmark & su*i*no*cul*tu*ra \cmark \\
 suíno & su-í*no \xmark & su*í*no \cmark \\
 suíte & su-í*te \xmark & su*í*te \cmark \\
+sumaúma & su*ma-ú*ma \xmark & su*ma*ú*ma \cmark \\
 sumô & su-mô \xmark & su*mô \cmark \\
@@
 tabuão & ta*bu-ão \xmark & ta*bu*ão \cmark \\
+tabuinha & ta*bu-i*nha \xmark & ta*bu*i*nha \cmark \\
 tacômetro & ta-cô*me*tro \xmark & ta*cô*me*tro \cmark \\
@@
 talião & ta*li-ão \xmark & ta*li*ão \cmark \\
+taoismo & ta.o-is*mo \xmark & ta.o-is*mo \xmark \\
 taquígrafo & ta-quí*gra*fo \xmark & ta*quí*gra*fo \cmark \\
@@
 tataravô & ta*ta*ra-vô \xmark & ta*ta*ra*vô \cmark \\
+tautômero & tau-tô*me*ro \xmark & tau*tô*me*ro \cmark \\
 taxonômico & ta*xo-nô*mi*co \xmark & ta*xo*nô*mi*co \cmark \\
+tchau & t.chau \xmark & tchau \cmark \\
+tchecoslovaco & t.che*cos*lo*va*co \xmark & tche*cos*lo*va*co \cmark \\
 tcheco & t.che*co \xmark & tche*co \cmark \\
+tectônico & tec-tô*ni*co \xmark & tec*tô*ni*co \cmark \\
 teísmo & te-ís*mo \xmark & te*ís*mo \cmark \\
@@
 telefônico & te*le-fô*ni*co \xmark & te*le*fô*ni*co \cmark \\
+teleinformática & te*le-in*for*má*ti*ca \xmark & te*le*in*for*má*ti*ca \cmark \\
+telômero & te-lô*me*ro \xmark & te*lô*me*ro \cmark \\
 teníase & te*ní-a*se \xmark & te*ní*a*se \cmark \\
@@
 teórico & te-ó*ri*co \xmark & te*ó*ri*co \cmark \\
+teósofo & te-ó*so*fo \xmark & te*ó*so*fo \cmark \\
 termômetro & ter-mô*me*tro \xmark & ter*mô*me*tro \cmark \\
@@
 teutônico & teu-tô*ni*co \xmark & teu*tô*ni*co \cmark \\
+timbaúba & tim*ba-ú*ba \xmark & tim*ba*ú*ba \cmark \\
 tmese & t.me*se \xmark & tme*se \cmark \\
@@
 tragediógrafo & tra*ge*di-ó*gra*fo \xmark & tra*ge*di*ó*gra*fo \cmark \\
+tragicômico & tra*gi-cô*mi*co \xmark & tra*gi*cô*mi*co \cmark \\
 traído & tra-í*do \xmark & tra*í*do \cmark \\
@@
 transoceânico & tran*so*ce-â*ni*co \xmark & tran*so*ce*â*ni*co \cmark \\
+traquítico & tra-quí*ti*co \xmark & tra*quí*ti*co \cmark \\
 tríade & trí-a*de \xmark & trí*a*de \cmark \\
+triádico & tri-á*di*co \xmark & tri*á*di*co \cmark \\
+triásico & tri-á*si*co \xmark & tri*á*si*co \cmark \\
+triássico & tri-ás*si*co \xmark & tri*ás*si*co \cmark \\
 tricampeão & tri*cam*pe-ão \xmark & tri*cam*pe*ão \cmark \\
 tricô & tri-cô \xmark & tri*cô \cmark \\
+tríodo & trí-o*do \xmark & trí*o*do \cmark \\
+trióxido & tri-ó*xi*do \xmark & tri*ó*xi*do \cmark \\
 tripanossomíase & tri*pa*nos*so*mí-a*se \xmark & tri*pa*nos*so*mí*a*se \cmark \\
@@
 triunfo & tri-un*fo \xmark & tri*un*fo \cmark \\
+triunvirato & tri-un*vi*ra*to \xmark & tri*un*vi*ra*to \cmark \\
 triúnviro & tri-ún*vi*ro \xmark & tri*ún*vi*ro \cmark \\
 truísmo & tru-ís*mo \xmark & tru*ís*mo \cmark \\
+tsonga & t.son*ga \xmark & tson*ga \cmark \\
+tsunami & t.su*na*mi \xmark & tsu*na*mi \cmark \\
 tuim & tu-im \xmark & tu*im \cmark \\
+turboélice & tur*bo-é*li*ce \xmark & tur*bo*é*li*ce \cmark \\
 tzarista & t.za*ris*ta \xmark & tza*ris*ta \cmark \\
@@
 uveíte & u*ve-í*te \xmark & u*ve*í*te \cmark \\
+vacuidade & va*cu-i*da*de \xmark & va*cu-i*da*de \xmark \\
 vacúolo & va*cú-o*lo \xmark & va*cú*o*lo \cmark \\
@@
 veículo & ve-í*cu*lo \xmark & ve*í*cu*lo \cmark \\
+ventoinha & ven*to-i*nha \xmark & ven*to*i*nha \cmark \\
+verônica & ve-rô*ni*ca \xmark & ve*rô*ni*ca \cmark \\
+viático & vi-á*ti*co \xmark & vi*á*ti*co \cmark \\
 viável & vi-á*vel \xmark & vi*á*vel \cmark \\
@@
 viés & vi-és \xmark & vi*és \cmark \\
+vietcongue & vi*et*con*gue \cmark & vi*et-con*gue \xmark \\
 vitriólico & vi*tri-ó*li*co \xmark & vi*tri*ó*li*co \cmark \\
+vitríolo & vi*trí-o*lo \xmark & vi*trí*o*lo \cmark \\
 viúva & vi-ú*va \xmark & vi*ú*va \cmark \\
 viúvo & vi-ú*vo \xmark & vi*ú*vo \cmark \\
+vixnuísmo & vix*nu-ís*mo \xmark & vix*nu*ís*mo \cmark \\
 vovô & vo-vô \xmark & vo*vô \cmark \\
@@
 xintoísta & xin*to-ís*ta \xmark & xin*to*ís*ta \cmark \\
+xivaísmo & xi*va-ís*mo \xmark & xi*va*ís*mo \cmark \\
+xivaíta & xi*va-í*ta \xmark & xi*va*í*ta \cmark \\
+zebuíno & ze*bu-í*no \xmark & ze*bu*í*no \cmark \\
 zodíaco & zo*dí-a*co \xmark & zo*dí*a*co \cmark \\
 zoósporo & zo-ós*po*ro \xmark & zo*ós*po*ro \cmark \\
-total correct & 17 & 811 \\
+zoroástrico & zo*ro-ás*tri*co \xmark & zo*ro*ás*tri*co \cmark \\
+total correct & 1848 & 3137 \\

### 2024-07-02 article/hyphenpatches.tex
fix #56

@@
 
-\Cref{tab-resultados} presents the hyphenation errors in a set of 876 words.
+\Cref{tab-resultados} presents the hyphenation errors in a set of 1259 words.
 We have omitted those words where both rules let to a correct hyphenation and
@@
 we place mark \xmark. Correct hyphenations are marked with \cmark.
-The default rules achieved 17 correct hyphenations in this set, against 811 
+The default rules achieved 32 correct hyphenations in this set, against 1138 
 of the patched rules.

### 2024-07-05 article/dictionary.tex
fix #49

@@
 	  \item if not, choose the proparoxytone option (e.g.
-\emph{au-to-ri-a} instead of \emph{au-to-ri-a} and \emph{mar-ce-nei-ro} instead of \emph{mar-ce-neiro})\footnote{We just have to make sure we are not selecting those cases where there is a sequence of the form \texttt{[gq]u-[aeio]} (using regex notation), as in \emph{a-pa-zi-gu-ar} and \emph{en-xa-gu-ar}.}.
+\emph{au-to-ri-a} instead of \emph{au-to-ria} and \emph{mar-ce-nei-ro} instead of \emph{mar-ce-neiro})\footnote{We just have to make sure we are not selecting those cases where there is a sequence of the form \texttt{[gq]u-[aeio]} (using regex notation), as in \emph{a-pa-zi-gu-ar} and \emph{en-xa-gu-ar}.}.
 	      % [gq]u-[aeio]
